---
title: 'Rubin Causal Model'
author: Sophia Zhu, Arghayan Jeiyasarangkan, and Mann Talati
tutorial:
  id: rubin-causal-model-overview
output:
  learnr::tutorial:
    progressive: yes
    'allow_skip:': yes
runtime: shiny_prerendered
description: Chapter 1 Tutorial: Rubin Casual Model
---

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(tidyverse)
library(gt)
library(knitr)

# Key Data 

gt_obj <- tibble(subject = c("Yao", "Emma", "Cassidy", "Tahmid", "Diego"),
       treatment = c("Treated", "Treated", "Control", "Control", "Treated"), 
       ytreat = c("13", "14", "11", "9", "3"),
       ycontrol = c("9", "11", "6", "12", "4"),
       ydiff = c("? ", "? ", "? ", "? ", "? ")) |>
   gt() |>
  cols_label(subject = md("ID"),
                treatment = md("Treatment"),
                ytreat = md("$$Y_t(u)$$"),
                ycontrol = md("$$Y_c(u)$$"),
                ydiff = md("$$Y_t(u) - Y_c(u)$$")) |>
  cols_move(columns = c(treatment, ytreat, ycontrol), after = c(subject)) |>
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(subject))) |>
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"), 
            locations = cells_column_labels(columns = c(subject, treatment))) |>
  cols_align(align = "center", columns = everything()) |>
  cols_align(align = "left", columns = c(subject)) |>
  fmt_markdown(columns = everything()) |>
  tab_spanner(label = "Outcomes", c(ytreat, ycontrol))  |>
  tab_spanner(label = "$$\\text{Estimand}$$", c(ydiff))


knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

<!-- First priority: Does not suck. Covers key terms. -->

<!-- Knowledge drops? -->

<!-- Order of the questions? -->

<!-- Why not be like the book? -->

<!-- Tutorial just stops with no clear ending. Not really connected to the chapter. Doesn;t even cover Population Tables! Nor terms like validity and so on! -->

<!-- Seems like we should do less silly algebra questions and more reviews of the key concepts. The simple questions about defining causal effects and potential outcomes are fine, as far as they go. But shouldn't we have more, applying them in more specific scenarios? Might even cover scenarios in which things like SUTVA fail. -->

<!-- Match this closely to the chapter because, someday, we are going to stick all of these questions in the chapter. Does not need to be 90 minutes of questions. -->

<!--  And fix the 2 taus table in the 2nd tutorial so that tau is easier to calculate mentally. --> 

<!-- How do we give students information about being wrong or right? Easy for code! -->

<!-- After the definitions, we could have some problems which use the actual train data, calculate some causal effects and then plot them. Lots of good staff there. First, assume a single tau. What is it? How sure are you? Then separate taus for men and women. Or some other grouping. Show facetted plot. -->

<!-- One question could take the trains data and make a Preceptor table. Learn a little gt! Would also need some manipulation to create the two potential outcome columns. -->

<!-- More about confounding. Of course, it needs to be in the book. -->

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

## Introduction
###

This tutorial covers [Chapter 1](https://ppbds.github.io/primer/04-rubin-causal-model.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/). This tutorial will review key concepts including the Preceptor Table, the Population Table, potential outcomes, causal effect, validity, stability, representativeness, and unconfoundedness.

<!-- ### Exercise 5 -->

<!-- <!-- DK: Do we still discuss this in the chapter? No! Same next question. --> -->

<!-- In two sentences, explain what what an *ideal* Preceptor Table is, and why it is generally impossible to observe. Use the phrase "potential outcomes" in your answer. -->

<!-- ```{r definitions-5} -->
<!-- question_text(NULL, -->
<!--     message = "An ideal Preceptor Table is a table that does not have any missing data. This table is generally seen as impossible since it means that you can observe all potential outcomes of a situation, which should be impossible due to the Fundamental Problem of Causal Inference.", -->
<!--     answer(NULL, correct = TRUE), -->
<!--     allow_retry = FALSE, -->
<!--     incorrect = NULL, -->
<!--     rows = 5) -->
<!-- ``` -->

<!-- ### Exercise 6 -->

<!-- In one sentence, explain the difference between an *actual* Preceptor Table and an *ideal* Preceptor Table. -->

<!-- ```{r definitions-6} -->
<!-- question_text(NULL, -->
<!--     message = "An actual Preceptor Table has missing values, whereas an ideal Preceptor Table doesn’t have any missing values.", -->
<!--     answer(NULL, correct = TRUE), -->
<!--     allow_retry = FALSE, -->
<!--     incorrect = NULL, -->
<!--     rows = 3) -->
<!-- ``` -->

## 1.1 Preceptor Table
###

A Preceptor Table is a table with rows and columns such that, if none of the data is missing, the thing we want to know is trivial to calculate.

### Exercise 1

In your own words, give a one sentence definition of a Preceptor Table.

```{r preceptor-table-1}
question_text(NULL,
    message = "A table such that, if none of the data is missing, you can easily calculate your quantity of interest.",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 3)
```

###

Preceptor Tables vary in the number of their rows and columns. We use question marks to indicate missing data in a Preceptor Table. The rows in the Preceptor Table are the units — people, galaxies, oak trees — which are the subjects of interest.

### Exercise 2

Use the following Preceptor Table to learn about how Preceptor Table's work.

```{r preceptor-table-2}
tibble(id = c("Robert", "Andy", "Beau", "Ishan", "Nicholas"),
       height_cm = c("178", "?", "172", "173", "165")) |>
  gt() |>
  cols_label(id = md("ID"),
                height_cm = md("Height (cm)")) |>
  cols_move(columns = height_cm, after = c(id)) |>
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(id))) |>
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"), 
            locations = cells_column_labels(columns = c(id))) |>
  cols_align(align = "center", columns = everything()) |>
  cols_align(align = "left", columns = c(id)) |>
  fmt_markdown(columns = everything())
```

###

In this case, we have a row for each brother and a column for their heights. An individual unit is a brother. An outcome is that brother’s height. We will always have an ID column in Preceptor Tables so that we can identify different units.

###

Implicitly in every Preceptor Table is a notion of time. When, exactly, are we making this prediction? Since heights of adults change very, very slowly, we can ignore for this problem whether or not we are making this prediction tomorrow or a year from now.

## 1.2 Population Table

###

The aim of the Population Table is to illustrate the broader population in which we are interested, while also including the data from our Preceptor Table and from our dataset. This table has three sources of data: the data for units we want to have (the Preceptor Table), the data for units which we actually have (our actual data), and the data for units we do not care about (the rest of the population, not included in the data or the Preceptor Table).

### Exercise 1

In your own words, give a one sentence definition of a Population Table.

```{r population-table-1}
question_text(NULL,
    message = "A table constructed based on the validity that includes rows and columns from the Preceptor Table, data set, and other unit/time combinations.",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 3)
```

###

Our Population rows sometimes contain no data. These are subjects which fall within our population, but for which we have no data. As such, all values are missing.

### Exercise 2

Use the following Population Table to learn how Population Table's work.

```{r population-table-2}
tibble(subject = c("...", "Preceptor Table", "Data", "Data", "Preceptor Table"),
       year = c("2010", "?", "2015", "2015", "2023"),
       age = c("?", "?", "18", "23", "19"),
       height = c("?", "172", "180", "163", "?")) |>
  gt() |>
  cols_label(subject = md("Source"),
                year = md("Year"),
                age = md("Age"),
                height = md("Height")) |>
  cols_move(columns = year, after = c(subject)) |>
  cols_move(columns = age, after = c(year)) |>
  cols_move(columns = height, after = c(age)) |>
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(subject))) |>
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"), 
            locations = cells_column_labels(columns = c(subject))) |>
  cols_align(align = "center", columns = everything()) |>
  cols_align(align = "left", columns = c(subject)) |>
  fmt_markdown(columns = everything())

```

###

Our actual data rows contain the information that we do know. These rows contain entries for both our covariates and the outcomes. In this case, the actual data comes from a survey of Harvard students in 2015, so Age value for those students — none of whom are still at Harvard — will be their ages in 2015, and the Year value for these rows will be “2015.”

###

Implicit in the Preceptor Table is a notion of time. Now that we can see our actual data compared with our greater population and our desired data, we must expand our observations. That is to say that, given our data is sourced from 2015 and our desired data is from 2023, we must include a greater time span in our population.

## 1.3 Casual Effect
### 

The **Rubin Causal Model (RCM)** is based on the idea of **potential outcomes**. However, it is impossible to observe both potential outcomes at once. One of the potential outcomes is always missing, since a unit cannot travel back in time, and experience both treatments. This dilemma is the **Fundamental Problem of Causal Inference**.

### Exercise 1

In your own words, give a one sentence definition of a causal effect.

```{r casual-effect-1}
question_text(NULL,
    message = "The difference between two potential outcomes.",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 3)
```

### 

In most circumstances, we are interested in comparing two experimental manipulations, one generally termed “treatment” and the other “control.” The difference between the potential outcome under treatment and the potential outcome under control is a “causal effect” or a “treatment effect.” 

###

Use the following ideal Preceptor Table to answer some questions about "estimands," quantities in which we might be interested.

```{r}
gt_obj
```

### Exercise 2

```{r casual-effect-2}
quiz(question("What is the causal effect of the treatment on Yao?",
    answer("1"),
    answer("2"),
    answer("3"),
    answer("4", correct = TRUE),
    answer("5"),
    allow_retry = FALSE))
```

###

According to the RCM, the causal effect of being on the platform with treatment is the difference between what your attitude would have been under “treatment” (with treatment) and under “control” (no treatment).

### Exercise 3

```{r casual-effect-3}
quiz(question("For how many of the five people is the causal effect of the treatment positive?",
    answer("1"),
    answer("2"),
    answer("3", correct = TRUE),
    answer("4"),
    answer("5"),
    allow_retry = FALSE))
```

###

To calculate the causal effect of positive casual effect, we need to compare the outcome for an individual in one possible state of the world (with treatment) to the outcome for that same individual in another state of the world (without treatment).

### Exercise 4

```{r casual-effect-4}
quiz(question("On whom did the treatment have the most negative causal effect?",
    answer("Yao"),
    answer("Emma"),
    answer("Cassidy"),
    answer("Tahmid", correct = TRUE),
    answer("Diego"),
    allow_retry = FALSE))
```

###

We will use the symbol $$Y$$ to represent potential outcomes, the variable we are interested in understanding and modeling. $$Y$$ is called the response or outcome variable. It is the variable we want to “explain.” In our case this would be the attitude score. If we are trying to understand a causal effect, we need two symbols so that control and treated values can be represented separately: $$Y_t(u)$$ and $$Y_c(u)$$.

### Exercise 5

We did not have to deal with the Fundamental Problem of Casual Inference because we knew the outcomes for both treatment and control. Write a paragraph explaining the Fundamental Problem of Causal Inference. Include an example relating to your own life.

```{r casual-effect-5}
question_text(NULL,
    message = "The Fundamental Problem of Causal Inference is that, because we can never observe more than one potential outcome, we can never be certain about the value of a causal effect. For example, to determine the causal effect of studying on my SAT score, I need to know two things: my score if I study and my score if I don't study. The causal effect is the difference between the two. But I can only either study or not study. I can't do both! So, I can only observe one potential outcome.",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 7)
```

###

Many times if we don't know the outcomes for the source under both treatment and control so we are not able to ignore the Fundamental Problem of Casual Inference. 

## 1.4 One tau
### 

In these exercises, we will assume that the causal effect, $\tau$ (pronounced tau, rhymes with "cow"), is the same for everyone.


Use the following Preceptor Table to answer questions about the single value for tau.

```{r one-tau-0-setup}
tibble(subject = c("Yao", "Emma", "Cassidy", "Tahmid", "Diego"),
       treatment = c("Treated", "Treated", "Control", "Control", "Treated"),
       ytreat = c("13", "14", "?", "?", "3"),
       ycontrol = c("?", "?", "6", "12", "?"),
       ydiff = c("?", "?", "?", "?", "?")) |>
  gt() |>
  cols_label(subject = md("ID"),
                treatment = md("Treatment"),
                ytreat = md("$$Y_t(u)$$"),
                ycontrol = md("$$Y_c(u)$$"),
                ydiff = md("$$Y_t(u) - Y_c(u)$$")) |>
  cols_move(columns = c(treatment, ytreat, ycontrol), after = c(subject)) |>
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(subject))) |>
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"), 
            locations = cells_column_labels(columns = c(subject))) |>
  cols_align(align = "center", columns = everything()) |>
  cols_align(align = "left", columns = c(subject)) |>
  tab_spanner(label = "Outcomes", c(ytreat, ycontrol)) |>
  tab_spanner(label = "$$\\text{Estimand}$$", c(ydiff)) |>
  fmt_markdown(columns = everything())
```

### Exercise 1

<!-- DK: Are these next few questions useful? -->

Describe in one sentence/equation how you would estimate Yao's $Y_c(u)$. (Do not use actual numbers, use "tau" in your explanation).

```{r one-tau-1}
question_text(NULL,
    message = "Yao's $Y_t(u)$ - (Sum of all values in $Y_t(u)$ / Number of Values - Sum of all values in $Y_c(u)$ / Number of Values)",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

### Exercise 2

Describe in one sentence/equation how you would estimate Tahmids's $Y_t(u)$. (Do not use actual numbers, use "tau" in your explanation).

```{r one-tau-2}
question_text(NULL,
    message = "(Sum of values in $Y_t(u)$ / Number of Values - Sum of values in $Y_c(u)$ / Number of values) + Tahmid's $Y_c(u)$",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

###

One model might be that the causal effect is the same for everyone. There is a single parameter, `τ`, which we then estimate. Once we have an estimate, we can fill in the Preceptor Table because, knowing it, we can estimate what the unobserved potential outcome is for each person. We use our assumption about `τ` to estimate the counterfactual outcome for each unit.

### Exercise 3

Describe in one sentence/equation how you would estimate a single value for tau.

```{r one-tau-3}
question_text(NULL,
    message = "(Sum of values in $Y_t(u)$ / Number of Values - Sum of values in $Y_c(u)$ / Number of values)",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

### Exercise 4

```{r one-tau-4}
quiz(

  question("What is your estimate for a single value for tau?",
    answer("-2"),
    answer("2"),
    answer("1", correct = TRUE),
    answer("-1"),
    answer("1.5"),
    allow_retry = FALSE),

  question("What is your estimate for $Y_c(u)$ for Emma?",
    answer("10"),
    answer("11"),
    answer("12"),
    answer("13", correct = TRUE),
    answer("14"),
    allow_retry = FALSE),

  question("What is your estimate for $Y_t(u)$ for Cassidy?",
    answer("6"),
    answer("5"),
    answer("7", correct = TRUE),
    answer("9"),
    answer("8"),
    allow_retry = FALSE)
)
```

## 1.4 Two taus
### 

Assume that the causal effect varies by sex. We will now estimate two values for $\tau$: $\tau_F$ and $\tau_M$. (Cassidy and Emma are female; Tahmid, Diego, and Yao are male).

```{r}
tibble(subject = c("Yao", "Emma", "Cassidy", "Tahmid", "Diego"),
       treatment = c("Treated", "Treated", "Control", "Control", "Treated"),
       ytreat = c("13", "14", "$$6 + \\tau_F$$", "$$12 + \\tau_M$$", "3"),
       ycontrol = c("$$13 - \\tau_M$$", "$$14 - \\tau_F$$", "6", "12", "$$3 - \\tau_M$$"),
       ydiff = c("$$\\tau_M$$", "$$\\tau_F$$", "$$\\tau_F$$", "$$\\tau_M$$", "$$\\tau_M$$")) |>
  gt() |>
  cols_label(subject = md("ID"),
                treatment = md("Treatment"),
                ytreat = md("$$Y_t(u)$$"),
                ycontrol = md("$$Y_c(u)$$"),
                ydiff = md("$$Y_t(u) - Y_c(u)$$")) |>
  cols_move(columns = c(treatment, ytreat, ycontrol), after = c(subject)) |>
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(subject))) |>
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"), 
            locations = cells_column_labels(columns = c(subject))) |>
  cols_align(align = "center", columns = everything()) |>
  cols_align(align = "left", columns = c(subject)) |>
  tab_spanner(label = "Outcomes", c(ytreat, ycontrol)) |>
  tab_spanner(label = "$$\\text{Estimand}$$", c(ydiff)) |>
  fmt_markdown(columns = everything())
```

### Exercise 1

How would you calculate $\tau_F$? Use only words and no numbers in your explanation.

```{r two-taus-1}
question_text(NULL,
    message = "(Average $Y_t(u)$ for females - Average $Y_c(u)$ for females)",
    # AJ: You would average $Y_c(u)$ for females and subtract that from the average $Y_t(u)$ for females
    # AJ: which is better?
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

###

A second model used by two taus might assume that the causal effect is different between levels of a category but the same within those levels. For example, perhaps there is a `τf` for females and `τm` for males where.

### Exercise 2

What is the meaning of $\tau_M$? 

```{r two-taus-2}
question_text(NULL,
    message = "$t_M$ is an estimate of the average difference between the treatment effect and the control effect for males",
# AJ: This explanation could be made more clear and also needs to be added to the primer
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

### Exercise 3

What is your new estimate for Diego's $Y_c(u)$? 

```{r two-taus-3}
question_text(NULL,
    message = "7",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

### Exercise 4

Discuss for a sentence or two why an assumption that the causal effect varies by sex leads to a different estimate for Diego's $Y_c(u)$ compared to Cassidy's $Y_c(u)$.

```{r two-taus-4}
question_text(NULL,
    message = "Since Diego is male and Cassidy is female, the tau used to calculate the causal effect is different for each.",
    # AJ: Add this into the primer
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

## 1.4 Average Treatment Effect
###

We will no longer make any assumptions about $\tau$ for any individual or group. Instead, we are interested in estimating the average treatment effect ($ATE$). We have the same data as the previous sections.

```{r}
gt_obj
```

### Exercise 1

Using words only, explain how we estimate the $ATE$.

```{r average-treatment-ef-1}
question_text(NULL,
    message = "Average of treated values minus the average of control values.",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

###

The average treatment effect (ATE) is the average difference in potential outcomes between the treated group and the control groups. Because averaging is a linear operator, the average difference is the same as the difference between the averages. Particularly useful because we don’t have to assume anything about each individuals’ `τ`, like `τyao`, but can still understand something about the average causal effect across the whole population.

### Exercise 2

Calculate the $ATE$ based on the data given to you in the above Preceptor Table.

```{r average-treatment-ef-2}
question_text(NULL,
    message = "1.6",
# AJ: think of a way to make this a non decimal answer without screwing up the other questions
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

### Exercise 3

What is Cassidy's outcome under treatment if we assume $\tau$ to be the $ATE$ we calculated above? Note that the answer will just be a number, without any symbol.

```{r average-treatment-ef-3}
question_text(NULL,
    message = "9.4",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

### Exercise 4

Write a pararaph about the many, many reasons why $ATE$ may be a bad estimate of the true average treatment effect.

<!-- AJ: add this to primer -->

```{r average-treatment-ef-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    rows = 7)
```

### Exercise 5

Write a paragraph about what a heterogeneous treatment effect is and the situations when it is more or less common.

```{r average-treatment-ef-5}
question_text(NULL,
    message = "A heterogeneous treatment effect means that the effect of the treatment varies from individual to individual. A situation where this would be common is when testing drugs. Most people will have a different reaction to the drug, so we can't just assume that the causal effect of the drug is the same for everyone.",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 7)
```

## 1.5 Assumptions
### 

This section reviews the key assumptions required in every attempt at inference: *validity*, *stability*, *representativeness*, and *unconfoundedness*.

### Exercise 1

Write two sentences about *validity*, as used as an assumption in the *Primer*.

```{r assumptions-1}
question_text(NULL,
	message = "The assumption of validity allows us ignore any variation in treatment. It allows us to 'stack' the rows from the data, the Preceptor Table, and the population into a single Population Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Each of our two sources for rows --- the Preceptor Table and the actual data --- are coherent in terms of what the columns mean on their own. The assumption of validity, if true, allows us to "stack" them together and to consider both of them to have been drawn from the same larger population.

### Exercise 2

Write two sentences about *stability*, as used as an assumption in the *Primer*.

```{r assumptions-2}
question_text(NULL,
	message = "Stability means that the relationship between the columns is the same for three categories of rows: the data, the Preceptor Table, and the larger population from which both are drawn. That is, however connected two columns are in the data, we assume that this same connection holds for the Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

*Validity* is about the columns. For example, does "exposure to Spanish-speakers" mean the same thing in our data from 2014 as it does in the data we want to have --- for our Preceptor Table --- in 2023? *Stability* is about the rows. Is the connection between the treatment and the potential outcomes the same in 2023 as it was in 2014

### Exercise 3

In your own words, give a one sentence definition of a potential outcome.

```{r assumptions-3}
question_text(NULL,
    message = "An outcome which occurs if the treatment has the specified value.",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 3)
```

###

We use potential outcomes for an individual which depends on whether they receive the treatment or not.

### Exercise 4

Write two sentences about *representativeness*, as used as an assumption in the *Primer*.

```{r assumptions-4}
question_text(NULL,
	message = "Representativeness, or the lack thereof, is the relationship, among the rows in the Population Table, between our data and the other rows. Ideally, we would like our data to be a random sample from the population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Why do we have the data that we have? The easiest way to draw inferences about other rows, especially the rows in the Preceptor Table subpart of the Population Table, is if our data is a random draw from the entire population. This is almost never true. How untrue it is determines how much we need to worry about the representativeness of our data.

### Exercise 5

Write two sentences about *unconfoundedness*, as used as an assumption in the *Primer*.

```{r assumptions-5}
question_text(NULL,
	message = "If whether or not a unit received treatment or control is random, we write that treatment assignment is not 'confounded.' If, however, treatment assignment depends on the value of a potential outcome, then treatment assignment is confounded.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

"Unconfoundedness" as an assumption only applies in the case of causal, not predictive, models.

### Exercise 6

Write two sentences that explain the difference between a causal model and a predictive model. 

```{r assumptions-6}
question_text(NULL,
    message = "A predictive model assumes one outcome whereas a causal model allows for more than one outcome, which we term 'potential' outcomes in that case. In the Preceptor Table, a predictive model has only one outcome column while a causal model has at least two.",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

## Summary
###

This tutorial covered [Chapter 1](https://ppbds.github.io/primer/04-rubin-causal-model.html) of Preceptor's Primer. This tutorial reviewed key concepts including the Preceptor Table, the Population Table, potential outcomes, causal effect, validity, stability, representativeness, and unconfoundedness. For further clarification of these concepts view [**Key Concepts**](https://ppbds.github.io/primer/glossary.html). 

```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
