---
title: 'rtweet'
author: Ajay Malik
tutorial:
  id: rtweet
output:
  learnr::tutorial:
    progressive:  true
    allow_skip::  true
runtime: shiny_prerendered
description: Review the rtweet package.
---

```{r setup, include = FALSE}
library(learnr)
library(all.primer.tutorials)
library(tidyverse)
library(primer.data)
library(rtweet)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

<!-- CHECKLIST BEFORE STARTING: -->
<!-- * Load necessary libraries for tutorial in the first code chunk -->
<!-- * Edit yaml at the TOP OF THIS FILE -->
<!-- * Review: https://ppbds.github.io/primer.tutorials/articles/instructions.html -->
<!-- * Delete this and the other comment instructions below. -->

<!-- USE THIS RESOURCE TO COME UP WITH EXAMPLES: -->
<!-- https://cran.r-project.org/web/packages/rtweet/vignettes/intro.html -->

## Introduction
###

In this tutorial, we will be exploring the basics of the `rtweet` package in R, which can interact with Twitter's APIs in all sorts of ways. With `rtweet`, you can view random tweets, tweets from a certain part of the world, tweets containing a certain hashtag, an account's followers, and all the accounts a user follows. It can even be used to visualize Twitter data, post your own tweets, and follow other accounts.

## First section (use sentence case)
###

## Summary
###

In this tutorial, you learned how to use the `rtweet` package in R to interact with Twitter's APIs in a multitude of ways, all of which can be highly relevant for data science and personal use. There are plenty more applications of `rtweet` that we haven't fully discussed in this tutorial, so you may utilize the following resources to check them out on your own:

* [A beautiful presentation about rtweet by Michael W. Kearney from the School of Journalism at the University of Missouri](https://mkearney.github.io/nicar_tworkshop/#1)
* [RDocumentation's rtweet page](https://www.rdocumentation.org/packages/rtweet/versions/0.7.0)
* [Official rtweet GitHub page](https://github.com/ropensci/rtweet)
* [CRAN's intro to rtweet](https://cran.r-project.org/web/packages/rtweet/vignettes/intro.html)

<!-- Two to four sentences which bring the lessons of the tutorial together for the student. What do they know now that they did not know before? How does this tutorial connect to future tutorials? OK if this is very similar to the Introduction. You made a promise as to what they would learn. You (I hope!) kept that promise.-->

```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
