---
title: Stops
author: Sanaka Dash and David Kane
tutorial:
  id: stops
output:
  learnr::tutorial:
    progressive: yes
    'allow_skip:': yes
runtime: shiny_prerendered
description: 'Tutorial: Stops'
---

```{r setup, include = FALSE}
# First packages are ones which students don't know about or load up. learnr and
# tutorial.helpers are required for the tutorial to work at all. gt is often
# needed because we often show a Preceptor Table to the students, which is built
# with this package, even though we don't show students how to create it.

library(learnr)
library(tutorial.helpers)
library(gt)

# Any package from here is something that we want students to explicitly load up
# in the tutorial. This serves two purposes. First, it provides an occasion for
# knowledge drops. Second, it reminds students that these packages must be
# loaded in the Console if they want any of the code from the tutorial to work
# in the Console. (Of course, different lines of code require different
# packages.) The most common package to be added to this section, and which
# should also be loaded by students, is a data source like primer.data.

library(tidyverse)
library(brms)
library(tidybayes)
library(gtsummary)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 

# XX: Never include setup code that takes more than a few seconds to run. For
# example, using brm() takes too much time. Instead, do the below, and see the
# relevant discussion in instructions.html.

#nhanes_1 <- brm(height ~ age,
#               data = no_na_nhanes,
#               family = gaussian(),
#               silent = 2,
#               refresh = 0,
#               seed = 16)
#write_rds(nhanes_1, "data/nhanes_1.rds")

#nhanes_1 <- read_rds("data/nhanes_1.rds")

```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

<!-- Should we add the Temperance start and finish quotes from the Primer chapters? What about other classical quotes, like "You can never look at the data too much."?   -->

<!-- Every EDA should show a scatter plot of the outcome variable on the y-axis and one of (probably the most important or the treatment) covariates on the x-axis. -->

<!-- Consider adding the model creation and saving code to a separate model.R script. Then, in analysis.R, you could just read it in. Would also be useful, in at least some tutorials, to highlight using a small sample of the data in initial fitting. -->

<!-- Whenever you tell a student to make a change in the QMD, you should tell them to `Command/Ctrl + Shift + K` in order to render the document. Then, the last step in these exercises is often some version of show_file() and then CP/CR. -->

<!-- Make use of, e.g., `show_file("tutorial-6.qmd", start = -5)` to get just the last 5 lines of the QMD. -->


## Introduction
### 

This tutorial is best understood when done after reading [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). It covers the `stops` dataset from the [primer.data](https://github.com/PPBDS/primer.data/) package.


## The Question
### 

*The power to question is the basis of all human progress.* - Indira Gandhi

<!-- FIX - add these in later: -->
<!-- Both a causal effect and a prediction are much fuzzier notions than you might think because there are so many, depending on AGGREGATION. -->

<!-- If you don't care what Joe would have done in a counter-factual world in which we got a different treatment, if all you care about is predicting what Joe does *given the treatment he received*, then you just need a predictive model. -->

### Exercise 1

Load **tidyverse**.

```{r the-question-1, exercise = TRUE}

```

```{r the-question-1-hint-1, eval = FALSE}
library(tidyverse)
```

```{r the-question-1-test, include = FALSE}
library(tidyverse)
```

### 

The data that we will use was sourced from the [Open Policing project](https://openpolicing.stanford.edu/findings/). Based at Stanford University, the project aims to improve police accountability and transparency by providing data on traffic stops across the United States. They have many downloadable datasets, and our data is specifically derived from their [New Orleans dataset.](https://openpolicing.stanford.edu/data/)


### Exercise 2

Load the **primer.data** package.

```{r the-question-2, exercise = TRUE}

```

```{r the-question-2-hint-1, eval = FALSE}
library(primer.data)
```

```{r the-question-2-test, include = FALSE}
library(primer.data)
```

### 

A version of the data from the Open Policing project is available in the `stops` tibble.


### Exercise 3

After loading **primer.data** in your Console, type `?stops` in the Console, and paste in the Description below.

```{r the-question-3}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

`stops` contains data from over 400,000 traffic stops in New Orleans from July 1, 2011 to July 18, 2018. The dataset includes information about the date, time, and location of each stop, as well as demographic details about the driver and the outcomes of the stop.


### Exercise 4

<!-- SD: Here, would arrests be the broad topic or would it be the specific topic? Basically, how much hand-holding are we doing here? -->

Arrests in traffic stops are the broad topic of this tutorial. Given that topic, which variable in `stops` should we use as our outcome variable? 

```{r the-question-4}
question_text(NULL,
	message = "We should be using the `arrested` variable.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 2)
```

### 

`arrested` indicates whether an arrest was made in the traffic stop. Note that later, when we're dealing with the data, this column is in TRUE/FALSE notation.

<!-- SD: Again, idk if I can use the following: -->
<!-- There are many acceptable answers that we could measure, but, for this tutorial we will stick wil `arrested`. -->


### Exercise 5

<!-- SD: I'm confused - why are we intoeducing a non-existent variable whe we could be introducing the real treatment variable? -->
<!-- SD: For now, I left the rest of this section blank until I understand what I need to do :) -->
Let's imagine a brand new variable which **does not exists** in the data. This variable should be binary, meaning that it only takes on one of two values. It should also, at least in theory, by manipulable. In other words, if the value of the variable is "X," or whatever, then it generates one potential outcome and if it is "Y," or whatever, it generates another potential outcome.

How might we manipulate this variable?


```{r the-question-5}
question_text(NULL,
	message = "Imagine a variable called `XX`. We can manipulate the value of `XX`, at least in theory, by . . .",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- There is nothing wrong with naming an imaginary variable which is not in the data set if there is not a natural one. For example, if `height` is our outcome and `nhanes` is our tibble, then maybe there isn't a good candidate treatment variable. In that case, just assume the existence of a `vitamin` binary variable for which `1` means that the individual ate vitamins growing up and `0` means they did not. -->

<!-- XX: This question and the ones that follow are tricky. We are trying to drive home some related points. First, any data set can be used to construct a causal model as long as there is at least one covariate that we can, at least in theory, manipulate. It does not matter whether or not anyone did, in fact, manipulate it. Second, any data set can be used to construct a predictive model. Third, the same data set can be used to create, separately, lots and lots of different models, both causal and predictive. We can just use different outcome variables and/or specify different treatment variables. All of this stuff is a *conceptual* framework we apply to the data. It is never inherent in the data itself.-->

<!-- XX: Explain that there is no right answer and that the student's response was probably fine. But, going forward, the student should use the variable we have selected. That variable should be named in future questions so that this is clear to the student. -->

### Exercise 6

Given our choice of treatment variable `XX`, how many potential outcomes are there for each [XX: unit]? Explain why.


```{r the-question-6}
question_text(NULL,
	message = "There are XX potential outcomes because the treatment variable `XX` takes on XX posible values: list-the-values-here, i.e., exposure to Spanish-speakers on a train paltform versus no such exposure.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: I am not satisfied with the wording of this next question. Our end goal is the calculation, by the student, of a causal effect, as in Exercise 8. The previous step was to just determine the number of potential outcomes, as in Exercise 6. This question wants to get students to see that each different treatment is associated with a potential outcome. Is there a better approach? -->

### Exercise 7

Write a sentence which speculates as to value of the XX different potential outcomes which we might observe in `XX: outcome variable` for each [XX: unit] when we change the value of the treatment variable `XX`. 


```{r the-question-7}
question_text(NULL,
	message = "XX.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Again, we allow the student to answer however they like. But, in succeeding questions, we make it clear that they should use our answer. For example, once we specify different values for treatment in this questions, we use those values in the next. -->

<!-- XX: More tricky discussion. The point of the Rubin Causal Models is that the definition of a causal effect is the difference between potential outcomes. So, there must be two (or more) potential outcomes for any causal model to make sense. This is simplest to discuss when the treatment only has two different values, thereby generating only two potential outcomes. But, if the treatment variable is continuous, (like income) then there are lots and lots of potential outcomes, one for each possible value of the treatment variable. -->

### Exercise 8

Write a few sentences which specify two different values for the treatment variable, for a single unit, and then guesses at the potential outcomes which would result, and then calculates the causal effect for that unit given those guesses.

<!-- XX: Replace [XX: unit] with a better word below given the actual data set we are using. Replace all the XX terms as appropriate. -->

```{r the-question-8}
question_text(NULL,
	message = "For a given [XX: unit], assume that the value of the treatment variables might be [XX: treatment] or [XX: control]. If the [XX: unit] gets [XX: treatment], then [XX: the outcome] would be [XX: a number]. If the [XX: unit] gets [XX: control], then [XX: the outcome] would be [XX: a different number]. The causal effect on the outcome of a treatment of [XX: treatment] versus [XX: control] is [XX: a number] - [XX: a different number] --- i.e., the difference between two potential outcomes --- which equals [XX: the causal effect], which is the causal effect.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Stiff confused? Here is an example answer. Note that you can adjust the language as needed to account for the exact wording of the different treatments: -->

<!-- For a given individual, assume that the value of the treatment variables might be 'exposure to Spanish-speakers' or 'no exposure'. If the individual gets 'exposure to Spanish-speakers', then her attitude toward immigration would be 10. If the individual gets 'no exposure', then her attitude would be 8. The causal effect on the outcome of a treatment of exposure to Spanish-speakers versus no exposure is 10 - 8 --- i.e., the difference between two potential outcomes --- which equals 2, which is the causal effect. -->

<!-- XX: More trickiness. Again, we are trying to reinforce the the definition of a causal effect as the difference between two potential outcomes. Of course, you can't just say that the causal effect is 10. The exact value depends on which potential outcome comes first in the subtraction and which second. (There is, perhaps, a default sense in which the causal effect is defined as treatment minus control. But regardless, it is better to be clear.) -->

<!-- XX: Something like: "The causal effect on attitude toward immigration of treatment versus control is 1.5." Which implies that it is treatment minus control. Or: "The causal effect on longevity of receiving an income of 20,000 versus one of 19,000 is 6 years." In both cases, we specify the outcome variable explicitly. -->

<!-- XX: Throughout, we are making clear that any causal connection means exploring the *within row* different between two potential outcomes. We don't need to look at any other rows to have that conversation. -->

### Exercise 9

<!-- Replace stuff like `[XX: the tibble]` with just the name of the tibble, i.e., `trains`. -->

Let's consider a *predictive* model. Which variable in `stops` do you think might have an important connection to `arrested`? (If you don't see a reasonable variable in the data, you can just name a variable which *might have been* included in the data.)

<!-- XX: Key question: Should we use the same variable in causal as in predictive? I am not sure which approach is best. You decide! -->

```{r the-question-9}
question_text(NULL,
	message = "XX: Describe the (or one of) the key covariate whose connection to the outcome variable we most want to explore.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 2)
```

### 

<!-- XX: Acknowledge that there is no right answer. There are other interesting variable in this data set --- mention some of them --- that we might also explore. But, again, in this tutorial, we have selected the outcome and the key covariate which will be used. -->

### Exercise 10

Write a few sentences which specify two different groups of [XX: units] with different values for [XX: covariate]. Explain that the average value of the outcome variable might differ between these two groups.

```{r the-question-10}
question_text(NULL,
	message = "XX: Some [XX: units] might have a value for [XX: covariate] of [XX: a value]. Others might have a value of [XX: a different value]. Those two groups will, on average, have different values for the outcome variable.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Again, the key point is that, with a predictive model, there is only one outcome for each individual unit. There are not two potential outcomes because we are not considering any of the covariates to be treatment variables. We assuming that all covariates are "fixed." In that case, we should not use words like "cause," "influence," "impact," or anything else which suggests causation. The best phrasing is in terms of "differences" between groups of units with different values for the covariate of interest. -->

### Exercise 11

<!-- XX: This is a draft. Maybe rework? -->

Write a [XX: choose causal or predictive] question which connects the outcome variable XX to a covariate of interest. 

```{r the-question-11}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: The goal is to get the student to write the question which we want. But it is OK if she doesn't! There are lots of interesting questions which one might write. Whatever she writes, here is where we give our question, which then leads into Wisdom.  Note that the question we decide on might use a variable which we have not yet considered. That is OK! But maybe not for the best? -->

<!-- XX: If it is a causal model, use the words "causal effect," or something very similar, in the question.  -->

### Exercise 12

What is a Quantity of Interest which might help us to explore the answer to our question?

<!-- XX: In general, our initial question does not include any specific numbers. It just uses words. For precision, we need to specify a Quantity of Interest that we are interested in. This is harder than it might look! It also helps to set the stage of Temperance. In all cases, the quantity of interest involves the outcome variable. (How could it not?) It also involves specific values of the covariates.  -->

<!-- XX: For predictive models, the specific question is generally of two types. First, what is the *expected* value of the outcome for various values of the independent variables? Second, what is the comparison in the expected outcome between two different groups? We are *not* simply interested in predicting the outcome variable for one unit. (In fact, of course, we might ultimately be interested in just one unit, but we need to *pretend* to be interested in lots of units in order to motivate the creation of a model.) -->

<!-- XX: For causal models, we are almost always interested in the average causal effect of treatment versus control. We are *not* simply interested in the causal effect for one specific unit. (In fact, of course, we might ultimately be interested in just one unit, but we need to *pretend* to be interested in lots of units in order to motivate the creation of a model.) -->


```{r the-question-12}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Our Quantity of Interest might appear too specific, too narrow to capture the full complexity of the topic. There are many, many numbers which we are interested in, many numbers that we want to know. But we don't need to list them all here! We just need to choose one of them since our goal is just to have a specific number which helps to guide us in the creation of the Preceptor Table and, then, the model.


## Wisdom
### 

<!-- XX: Pick one. -->

*The only true wisdom is in knowing you know nothing.* - Socrates

Our question:

<!-- SD: Why do we need to repeat? Why not introduce the specific question here and have the general question in the last section? -->
> *XX: Repeat the question with which you ended The Question topic.*

<!-- The specific question: How does race impact the likelihood of getting arrested in a traffic stop? -->


### Exercise 1

In your own words, describe the key components of Wisdom when working on a data science problem.

```{r wisdom-1}
question_text(NULL,
	message = "Wisdom requires the creation of a Preceptor Table, an examination of our data, and a determination, using the concept of validity, as to whether or not we can (reasonably!) assume that the two come from the same population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The Open Policing project also has [visual maps](https://openpolicing.stanford.edu/explore/) regarding traffic stops. Sadly, there isn't one for New Orleans, but observe how different parts of Hartford, CT pull over different races of people!

<!-- XX: You have the opportunity, in this and the next few questions, to drop a lot of knowledge about the data and the overall topic. Do so! But, remember, students won't read more than 2 or so sentences in a knowledge drop. -->

<!-- Not only are you discussing the data, but you are also discussing potential problems with the data, problems which will be more fully fleshed out in the Justice section. You want to pick 5 to 10 interesting facts about the data. (You may need to go to the original source, not simply relying on the chapter. ) 

It is always a good idea to knowledge drop a link to the actual data and to any articles/books/websites related to it. -->


### Exercise 2

Define a Preceptor Table.

```{r wisdom-2}
question_text(NULL,
	message = "A Preceptor Table is the smallest possible table of data with rows and columns such that, if there is no missing data, we can easily calculate the quantities of interest.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The Preceptor Table does not include all the covariates which you will eventually including in your model. It only includes covariates which you need to answer your question.


### Exercise 3

Describe the key components of Preceptor Tables in general, without worrying about this specific problem. Use words like "units," "outcomes," and "covariates."

```{r wisdom-3}
question_text(NULL,
	message = "The rows of the Preceptor Table are the units. The outcome is at least one of the columns. If the problem is causal, there will be at least two (potential) outcome columns. The other columns are covariates. If the problem is causal, at least one of the covariates will be a treatment.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 4

Create a Github repo called `stops`. Make sure to click the "Add a README file" check box.

Connect the `stops` Github repo to an R project on your computer. Name the R project `stops` also.

Select `File -> New File -> Quarto Document ...`. Provide a title (`"Stops"`) and an author (you). Render the document and save it as `stops.qmd`.

Edit the `.gitignore` by adding `*Rproj`. Save and commit this in the Git tab. Push the commit.

In the Console, run:

```         
show_file(".gitignore")
```

CP/CR.

```{r wisdom-4}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

Remove everything below the YAML header from `stops.qmd` and render the file. `Command/Ctrl + Shift + K` renders the file, this automatically saves the file as well.


### Exercise 5

What are the units for this problem?

```{r wisdom-5}
question_text(NULL,
	message = "The units are the races of the people that have been pulled over.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

If our question were to have concerned the percentage of people that got arrested from traffic stops, then our units would have been the individual people. However, since it concerns the broad groups of people, it only makes sense for our units to be thos ebroad groups (the races).


### Exercise 6

What is/are the outcome/outcomes for this problem?

<!-- SD: Would it be valid to state all of th outcomes here, or should I just talk about the outcome variable? -->
```{r wisdom-6}
question_text(NULL,
	message = "We consider multiple outcomes from our outcome variable `arrested`: arrested, white; arrested, black; etc.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The variable `race` has multiple values, and with each value comes the the condition of the `arrested` variable. So, XX variables for `race` * 2 values for `arrested` (TRUE or FALSE) = XX total outcomes.

<!-- XX: A good knowledge drop for this exercise might involve other outcomes which might be useful for related questions. For example, if the outcome for a presidential election are votes cast than, with a slightly different question, the outcomes might be the electoral votes. We want to show them the interplay between the exact question and which outcomes define the Preceptor Table. -->

<!-- Specifying the Preceptor Table forces us to think clearly about the units and outcomes implied by the question. The resulting discussion sometimes leads us to modify the question we started with. No data science project follows a single direction. We always backtrack. There is always dialogue. -->


### Exercise 7

What are some covariates which you think might be useful for this problem, regardless of whether or not they might be included in the data?

```{r wisdom-7}
question_text(NULL,
	message = "We obviously need `race`. However, other characteristics like the person's age, sex, and the type of car they're driving might also affect `race`.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

For your information, the term "covariates" is used in at least three ways in data science. First, it is all the variables which might be useful, regardless of whether or not we have the data. Second, it is all the variables which we have data for. Third, it is the set of covariates which we end up using in the model.


### Exercise 8

What are the treatments, if any, for this problem?

```{r wisdom-8}
question_text(NULL,
	message = "Our treatment variable would be `arrested`.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Again, we dialogue. Any question, or broad topic, will use words. And words are not precise! Lots of possible treatments, each different from the other, are close to the original words. Drop some knowledge, or even speculation, about what sorts of treatments might be relevant in similar problems.  -->


### Exercise 9

What moment in time does the Preceptor Table refer to?

<!-- SD: How should I go about handling this situation? Do I make a random Preceptor Table or do I use something else, or do I just not make one at all? -->
```{r wisdom-9}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- FIX - XX: Add question: Explain why you want to use a predictive model or a causal model. Answer is almost always, you care about what happens to the same unit under two different treatments or you don't care. Often uses words like "causal," or "effect" or "affect" or "influence" or "impact" or . . . Actually, this should now be handled in The Question section. -->


### Exercise 10

Define causal effect.

```{r wisdom-10}
question_text(NULL,
	message = "A causal effect is the difference between two potential outcomes.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

In this case, our causal effect would measure the different in probability of getting arrested between the different races.

Note that this isn't to be confused with a predictive model, where we would be just predicting the probability of getting arrested for, say, the average white person (or to any specific given scenario). AGAIN, WE AREN'T DOING THIS!!!


### Exercise 11

What is the fundamental problem of causal inference?

```{r wisdom-11}
question_text(NULL,
	message = "The fundamental problem of causal inference is that we can only observe one potential outcome.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- FIX - XX: More discussion about potential outcomes. Counter-factuals are hard to think about. Help students by providing discussion of the ones under consideration here, or which might be under consideration with a different question. Are they plausible? What would make them more plausible? -->

### Exercise 12

How does the motto "No causal inference without manipulation." apply in this problem?

```{r wisdom-12}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- FIX -  -->
<!-- XX: With tutorial which uses a predictive model, it is fair for your answer to this question to be. "The motto does not apply because this is a predictive, not causal, model." -->

<!-- XX: For a causal model, can you really manipulate the treatments? In reality or in theory? How? What details would need to change to make this more or less plausible? -->

### Exercise 13

Describe in words the Preceptor Table for this problem.

```{r wisdom-13}
question_text(NULL,
	message = "XX. Make sure your words given an excellent description of the Preceptor Table which you are about to show the student.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The Preceptor Table for this problem looks something like this:

<!-- SD: Again, how would I go about doing this? -->
<!-- XX. Show the Preceptor Table. You can just copy/paste the code from the Primer, or use that code as a guide for creating your own ...-->

<!-- XX: Note that, like all aspects of a data science problem, the Preceptor Table evolves as we work on the problem. For example, at the start, we aren't sure what right-hand side variables will be included in the model, so we are not yet sure which columns must be in the Preceptor Table. -->


### Exercise 14

Write one sentence describing the data you have to answer your question.

```{r wisdom-14}
question_text(NULL,
	message = "FIX - XX. Make sure that your example sentence is a good one. Obviously, the date that the data was gathered is important, as well as the person/organization doing the gathering. The number of observations might also be useful, along with an indication as to the sort of variables included. But no need to include all of that! Use your best judgement. ",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 15

In `stops.qmd`, load the **tidyverse** and the **primer.data** packages in a new code chunk. Label it the set up by adding `#| label: setup`. Render the file.

Notice that the file does not look good because it is has code that is showing and it also has messages. To take care of this, add `#| message: false` to remove all the messages in the setup chunk. Also add the following to the YAML header to remove all echo from the whole file:

```         
execute: 
  echo: false
```

In the Console, run:

```         
show_file("analysis.qmd", start = -5)
```

CP/CR.

```{r wisdom-15}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

Render again. Everything looks nice because we have added code to make the file look better and more professional.


### Exercise 16

Load the **tidyverse** package.

```{r wisdom-16, exercise = TRUE}

```

```{r wisdom-16-hint-1, eval = FALSE}
library(...)
```

```{r wisdom-16-test, include = FALSE}
library(tidyverse)
```

### 

<!-- FIX -  -->
<!-- XX: Insert comments about the data. This continues to be the primary type of knowledge drop. These comments can also be sophisticated, especially in the way that they connect the data to the Preceptor Table and to the population. -->

<!-- XX: Load any other packages that are needed, one package per question. (But make sure that they are also included in the setup chunk.) primer.data, for example, is often needed. But save brms and tidybayes for the Courage section. -->

<!-- XX: It is now time for the third set of QMD edits. Add a new code chunk, the setup chunk, to the QMD. Copy/paste all the library commands to it. Render. Note all the ugliness. Add #| message: false. Add execute: echo: false to the YAML header. Add #| label: setup. Render again. Everything looks nice. Again, these could be several questions in the earlier tutorials or just one long question later. Ends with show_file("analysis.qmd", start = -5). This will be the most common ending question in QMD-editing exercises to come. -->

<!-- XX: Add code questions about EDA with your data. In particular, add at least one question about the dependent variable in the model along with one or more questions about covariates. If there is a treatment variable, you must include a question about it. -->

<!-- Variable questions come in two types. First there are questions which require the student to run, say, summary() on the variable. Then, knowledge about the variable can be dropped. Second, there are questions which ask for a one sentence summary about the variable, something which could be used in our summary of the project. For example: "Civility is measured on a 1 through 7 scale with higher values corresponding to greater civility." -->

<!-- XX: If necessary, provide code exercises which, line-by-line, create the pipeline which creates the cleaned data that will be used in modeling. For many tutorials, this is unnecessary since we can just use the raw tibble that is available in whatever package. But we sometimes need some code like

nes |> 
  filter(year == 1992) |> 
  drop_na()

We have three code exercises, each adding one line to the pipeline, explaining what we are doing and why. It is nice that, for each exercise, something is spat out.
-->

<!-- XX: If such a pipeline was built, there is one QMD question which requires that you add a new code chunk to the QMD, copy/paste the pipeline and assign the result to some object like `model_data` or whatever:

nes_92 <- nes |> 
  filter(year == 1992) |> 
  drop_na()

`Command/ctrl + Shift + K` follows, perhaps with a show_file("analysis.qmd", start = -5)
-->



### Exercise 17

In your own words, define "validity" as we use the term.

```{r wisdom-17}
question_text(NULL,
	message = "Validity is the consistency, or lack thereof, in the columns of the data set and the corresponding columns in the Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Validity is always about the *columns* in the Preceptor Table and the data. Just because columns from these two different tables have the same *name* does not mean that they are the same *thing*.

### Exercise 18

<!-- FIX - XX: For the validity questions, specifics matter. There is always a reason why the outcome column in the data is not the same as the outcome columns in the Preceptor Table, even in the case of simple sampling. For example, consider a historical question connecting sex with presidential vote. Our data is a subset of our Preceptor Table. We have information on a few thousand voters and want to draw inferences about millions of voters. But, even in this case, the outcome columns are different. The data is who people told a survey they voted for. The Preceptor Table is who people actually did vote for. Those are not the same things. If they, in your view, are different enough than validity is violated. -->

Provide one reason why the assumption of validity might not hold for the outcome variable: `arrested`.

```{r wisdom-18}
question_text(NULL,
	message = "FIX - XX: Answers to validity question should always use the word 'column(s)'.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Note that these questions are all about detecting issues early on so that they don't become a problem (however minor they may be) later. -->


### Exercise 19

<!-- FIX - XX: Pick the most important covariate or at least one that you know/suspect will be used in the model. This is similar to the previous question, but we want to ensure that students understand that validity is about comparing the columns in the data set with the columns in the Preceptor Table. -->

Provide one reason why the assumption of validity might not hold for the covariate: `XX`.

```{r wisdom-19}
question_text(NULL,
	message = "XX: Don't forget the word 'column'.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 20

<!-- FIX - Example: *Using data from a 2012 survey of Boston-area commuters, we seek to understand the relationship between income and political ideology in Chicago and similar cities in 2020. In particular, what percentage of individuals who make more than $100,000 per year are liberal?* -->

<!-- It is very difficult to craft a question which causes students to give a sentence that is good. Do your best. -->

Summarize the state of your work so far in one sentence. Make reference to the data you have and to the specific question you are trying to answer. 


```{r wisdom-20}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Edit you answer as you see fit, but do not copy/paste our answer exactly. Add this summary to `stops.qmd`, `Command/Ctrl + Shift + K`, and then commit/push.


## Justice
### 

*Justice delayed is justice denied.* - William E. Gladstone


### Exercise 1

In your own words, name the four key components of Justice for working on a data science problem.

```{r justice-1}
question_text(NULL,
	message = "Justice concerns four topics: the Population Table, stability, representativeness, and unconfoundedness.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Justice is about concerns that you (or your critics) might have, reasons why the model you create might not work as well as you hope. 

### Exercise 2

In your own words, define a Population Table.

```{r justice-2}
question_text(NULL,
	message = "The Population Table includes a row for each unit/time combination in the underlying population from which both the Preceptor Table and the data are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The Population Table is almost always much bigger than the combination of the Preceptor Table and the data because, if we can really assume that both the Preceptor Table and the data are part of the same population, than that population must cover a broad universe of time and units since the Preceptor Table and the data are, themselves, often far apart from each other.

### Exercise 3

In your own words, define the assumption of "stability" when employed in the context of data science.

```{r justice-3}
question_text(NULL,
	message = "Stability means that the relationship between the columns in the Population Table is the same for three categories of rows: the data, the Preceptor Table, and the larger population from which both are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Stability is all about *time*. Is the relationship among the columns in the Population Table stable over time? In particular, is the relationship --- which is another way of saying "mathematical formula" --- at the time the data was gathered the same as the relationship at the (generally later) time references by the Preceptor Table.


### Exercise 4

Provide one reason why the assumption of stability might not be true in this case.

```{r justice-4}
question_text(NULL,
	message = "FIX - XX. Again, students read these 'official' answers as closely as anything else you will write. Make your example precise and excellent.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 5

We use our data to make inferences about the overall population. We use information about the population to make inferences about the Preceptor Table: `Data -> Population -> Preceptor Table`. In your own words, define the assumption of "representativeness" when employed in the context of data science.

```{r justice-5}
question_text(NULL,
	message = "Representativeness, or the lack thereof, concerns two relationships among the rows in the Population Table. The first is between the data and the other rows. The second is between the other rows and the Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Stability looks across time periods. Representativeness looks within time periods.


### Exercise 6

We do not use the data, directly, to estimate missing values in the Preceptor Table. Instead, we use the data to learn about the overall population. Provide one reason, involving the relationship between the data and the population, for why the assumption of representativeness might not be true in this case.

```{r justice-6}
question_text(NULL,
	message = "FIX - XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Remember that our data and our Preceptor Table are two completely different datasets, and are only able to merge once we have identified that they both concern the same population.

It's always a concern regarding the methods that the data was collected. If they were collected from different bodies or populations that didn't meet eye-to-eye in key aspects, the data may be conflicting.


### Exercise 7

We use information about the population to make inferences about the Preceptor Table. Provide one reason, involving the relationship between the population and the Preceptor Table, for why the assumption of representativeness might not be true in this case.

<!-- SD: Isn't this the same as the last question? Wouldn't the first part oft this question be better as a knowledge drop to the last? -->
```{r justice-7}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```


### Exercise 8

In your own words, define the assumption of "unconfoundedness" when employed in the context of data science.

```{r justice-8}
question_text(NULL,
	message = "Unconfoundedness means that the treatment assignment is independent of the potential outcomes, when we condition on pre-treatment covariates.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- FIX - XX: Keep one. -->

<!-- This assumption is only relevant for causal models. We describe a model as "confounded" if this is not true.  -->

<!-- The easiest way to ensure unconfoundedness is to assign treatment randomly. -->

### Exercise 9

<!-- FIX - XX: Delete this question for non-causal models. -->

Provide one reason why the assumption of unconfoundedness might not be true (or relevant) in this case.

```{r justice-9}
question_text(NULL,
	message = "FIX - XX. There is nothing harder for students than coming up with examples of possible confounds. So, your example should be a good one, should specify precisely how treatment assignment is correlated with the potential outcomes.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- FIX - XX: Most of our simple examples use random assignment. So, if fact, confoundedness is not a concern. But this knowledge drop, and perhaps the couple before, should address this topic, by pondering what we would worry about if treatment assignment had not been random.  -->


### Exercise 10

Summarize the state of your work so far in two or three sentences. Make reference to the data you have and to the question you are trying to answer. Feel free to copy from your answer at the end of the Wisdom Section. Mention one specific problem which casts doubt on your approach. 
```{r justice-10}
question_text(NULL,
	message = "FIX - XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Edit the summary paragraph in `stops.qmd` as you see fit, but do not copy/paste our answer exactly. `Command/Ctrl + Shift + K`, and then commit/push.


## Courage
### 

*Courage is the commitment to begin without any guarantee of success.* - Johann Wolfgang von Goethe

<!-- Questions about models, tests, and the DGM. -->


### Exercise 1

In your own words, describe the components of the virtue of Courage for analyzing data.

```{r courage-1}
question_text(NULL,
	message = "Courage begins with the exploration and testing of different models. It concludes with the creation of a Data Generating Mechanism.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

Load the **brms** package.

```{r courage-2, exercise = TRUE}

```

```{r courage-2-hint-1, eval = FALSE}
library(...)
```

```{r courage-2-test, include = FALSE}
library(brms)
```

### 

<!-- XX: The Courage section of each chapter is the most complex because modeling is hard. Use opportunities for knowledge drops, like this one, judiciously. -->

### Exercise 3

Load the **tidybayes** package.

```{r courage-3, exercise = TRUE}

```

```{r courage-3-hint-1, eval = FALSE}
library(...)
```

```{r courage-3-test, include = FALSE}
library(tidybayes)
```

### 

### Exercise 4

Add `library(brms)` and `library(tidybayes)` to `stops.qmd`. `Command/Ctrl + Shift + K`. At the Console, run:

```
tutorial.helpers::show_file("stops.qmd", pattern = "brms|tidybayes")
```

CP/CR.

```{r courage-4}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

<!-- XX: For a knowledge drop, there is nothing wrong with discussion regular expressions, which is the magic which allows us to just pull out the two lines in the QMD which we want. But better would just be more Courage knowledge drops. -->


### Exercise 5

Create a model using `brm()` from the **brms** package. Your arguments should be XX. 

<!-- Search and replace "fit_XX" as appropriate. As a convention, the name of a fitted model object should always start with `fit_`. -->

<!-- Don't forget to create this model yourself in the setup chunk. Do this once, save the object, comment out that code and then just read_rds to create the object for his tutorial. -->


```{r courage-5, exercise = TRUE}

```

```{r courage-5-hint-1, eval = FALSE}

```

<!-- XX: Note how there is no test case. If there were one, then a student would fit the model each time she hit "Run Tutorial." That takes too much time. -->

### 

### Exercise 6

Behind the scenes, we have assigned the result of the `brm()` call to an object named `fit_XX`. Type `fit_XX` and hit "Run Code." This generates the same results as using `print(fit_XX)`.


```{r courage-6, exercise = TRUE}

```

```{r courage-6-hint-1, eval = FALSE}
fit_XX
```

```{r courage-6-test, include = FALSE}
# fit_XX
```

### 

<!-- XX Say some general words about the object. Note that we are about to go through the top 4 rows. -->


### Exercise 7

Run `family()` on `fit_XX`. `family()` provides information about the "family" of the error term and the link between it and the dependent variable. 

```{r courage-7, exercise = TRUE}

```

```{r courage-7-hint-1, eval = FALSE}
family(...)
```

```{r courage-7-test, include = FALSE}
# family(fit_XX)
```

### 

<!-- XX: This is a great location for explanations which get much more detailed in later chapters. That is, we want students to have a more sophisticated understanding of probability distributions, and there use in modeling, as we move through the Primer.

But, at a minimum, you would comment about how the family that is shown --- which is either gaussian, bernoulli or categorical --- is determined by the family argument which you passed in to the brm() call, and that you determined that by looking at the distribution of the output variable. Continuous means gaussian, 2 possible values means bernoullu, and 2+ possible values means categorical.

-->

In this case, XX . . .

### Exercise 8

Run `formula()` on `fit_XX`. `formula()` returns the statistical equation which relates the dependent variable to the independent variable(s). 

```{r courage-8, exercise = TRUE}

```

```{r courage-8-hint-1, eval = FALSE}
formula(...)
```

```{r courage-8-test, include = FALSE}
# formula(fit_XX)
```

### 

In this case, XX . . .

### Exercise 9

Run `nobs()` on `fit_XX`. The `nobs()` function returns the **n**umber of **obs**ervations.

```{r courage-9, exercise = TRUE}

```

```{r courage-9-hint-1, eval = FALSE}
nobs(...)
```

```{r courage-9-test, include = FALSE}
# nobs(fit_XX)
```

### 

In this case, XX

### Exercise 10

Write the mathematical formula for your model, using $\LaTeX$ math notation.

```{r courage-10}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Add the formula to `stops.qmd`. `Command/Ctrl + Shift + K`. Ensure that the formula is looks correct. 

### Exercise 11

Create a new code chunk in `stops.qmd`. Add two code chunk options: `label: model` and `cache: true`. Copy/paste the code from above for estimating the model using `brm()` into the code chunk, assigning the result to `fit_XX`. 

`Command/Ctrl + Shift + K`. It may take some time to render `stops.qmd`, depending on how complex your model is. But, by including `cache: true` you cause Quarto to cache the results of the chunk. The next time you render `stops.qmd`, as long as you have not changed the code, Quarto will just load up the saved fitted object.

To confirm, `Command/Ctrl + Shift + K` again. It should be quick.

At the Console, run:

```
tutorial.helpers::show_file("stops.qmd", start = -8)
```

CP/CR.

```{r courage-11}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

### Exercise 12

<!-- XX: Note that, in my advanced models, there are some subtle differences between what fixef() and posterior_interval() do. But we won't worry about that here. -->

Run `posterior_interval()` on `fit_XX`. The `posterior_interval()` function returns 95% intervals for all the parameters in our model.

```{r courage-12, exercise = TRUE}

```

```{r courage-12-hint-1, eval = FALSE}
posterior_interval(...)
```

```{r courage-12-test, include = FALSE}
# posterior_interval(fit_XX)
```

### 

In this case, XX . . .


### Exercise 13

Run `fixef()` on `fit_XX`. The `fixef()` returns information about the **fix**ed **ef**fects in the model.

```{r courage-13, exercise = TRUE}

```

```{r courage-13-hint-1, eval = FALSE}
fixef(...)
```

```{r courage-13-test, include = FALSE}
# fixef(fit_XX)
```

### 

In this case, XX . . .

<!-- XX: Add at least three questions which require the student to interpret the meanings of a parameter estimate and/or its associated confidence interval. This is something that students are very bad at! And so we need to give them practice, both by asking them to do it and by providing excellent answers. These questions also feature good opportunities to knowledge drop about the meaning of intervals (confidence verus uncertainty) and about Frequentist versus Bayesian interpretations. See -->

<!-- Let's me give a couple of questions/answers to serve as examples, all based on this display. This is good for linear (meaning the Gaussian family) models. For other models, see the comments below. -->

<!-- fit_obj <- brm(formula = att_end ~ sex + treatment + age, data = trains) -->

<!-- > round(fixef(fit_obj), 2) -->
<!--                  Estimate Est.Error  Q2.5 Q97.5 -->
<!-- Intercept           10.99      0.95  9.17 12.83 -->
<!-- sexMale             -0.83      0.54 -1.88  0.22 -->
<!-- treatmentControl    -1.42      0.54 -2.45 -0.32 -->
<!-- age                 -0.01      0.02 -0.06  0.03 -->

<!-- Q: Write a sentence interpreting the -0.34 estimate for sexMale. -->

<!-- A: When comparing men with women, men have a 0.83 lower value for att_end, meaning that they are more liberal about immigration, relative to women, conditional on the other variables in the model. -->

<!-- Comment_1: Note how, whenever we consider non-treatment variables, we must never use terms like "cause," "impact" and so on. We can't make any statement which implies the existence of more than one potential outcome based on changes in non-treatment variables. We can't make any claims about within row effects. Instead, we can only compare across rows. Always use the phrase "when comparing X and Y" or something very similar. -->

<!-- Comment_2: The phrase "conditional on the other variables in the model" is important. It could be shorted as "conditional on the model." This phrase acknowledges that there are many, many possible models, just considering all the different combintions of indepdendent variables we might include. Each one would produce a different coefficient for sexmale. None of these is the *true* cofficient. Any claim we make about  -0.83, or any specific number, is always conditional on the fact that we assume that this model is true, that these covariates, and no others, belong in the regression. Does that mean that we always use the phrase? No. We leave it out all the time. But it is always understood to be there but knowledge readers. Still, this is probably a point worth making in various knowledge drops. -->


<!-- Q: Write a sentence interpreting the confidence interval for sexMale. -->

<!-- A: We do not know the true value for the coefficient for sexMale, but we can by 95% confident that it lies somewhere between -1.88  and 0.22.  -->

<!-- Comment: Because we are Bayesians, we believe that there is a true value and that the confidence or uncertainty interval includes it at the stated level. These questions provide an occasion in the knowledge drop to compare/contrast the Frequenist interpretation. See: https://ppbds.github.io/primer/cardinal-virtues.html#confidencecredibleuncertainty-intervals -->

<!-- Q: Write a sentence interpreting the -1.42  estimate for treatmentControl. -->

<!-- A: The causal effect of receiving the treatment of hearing Spanish-speakers on the train platform, relative to the control, is to have a 1.42  higher value for att_end, meaning that the treatment, relative to the control, makes one more conservative about immigration. (Note that you need to keep track of signs and of which 0/1 variable is being used.) -->

<!-- Comment: The interpretation of a treatment variable is very different than the interpretation of a standard covariate. Whenever your model includes a treatment variable, you must always have a question about it and about the associated confidence interval. -->

<!-- Q: Write one sentence interpreting the -2.45 to -0.32 interval for the treatmentControl coefficient. -->

<!-- A: Our best estimate for the causal effect is -1.42, meaning that being treated makes someone 1.42 units more conservative about immigration. Yet, the true value could be lower or higher. We are 95% certain that the true effect is somewhere between -2.45 to -0.32.  -->

<!-- Comment: It is OK if our answers are slightly longer than what we might expect from students, as long as those answers are *tight*, meaning that no word is wasted. In this case, the first two sentences are an attempt to ensure that the student understands what is going on. The last sentence is what we might expect students to write.  -->

<!-- Q: Write a sentence interpreting the -0.1 estimate for age.  -->

<!-- A: If we compare one group of people ten years older than another, the older group will, on average, have an attitude toward immigration 1 unit lower, i.e., less conservative. -->

<!-- Comment: Numeric variables are harder than binary variables because there are no longer just two well-defined groups to compare with each other. We must make those two groups ourselves. Fortunately, as long as there are no interaction terms, we can just pick two groups with any values for the variable. The most common two groups differ by one unit of the variable. But it is quite common to use groups which differ by more/less if doing so seems sensible and/or if it makes the math easier. In this case, two groups which differ by 10 years makes sense for both reasons. -->

<!-- Further comment: With a linear model, all these interpretations are fairly straightforward. With any other type of model, the math is too difficult to do in your head. You can't just look at a coefficient of 5 and know what it means in magnitude. But you can tell the direction, that a positive 5 means that -->

### Exercise 14

Run `pp_check()` on `fit_XX`. The `pp_check()` runs a **p**osterior **p**redictive check.

```{r courage-14, exercise = TRUE}

```

```{r courage-14-hint-1, eval = FALSE}
pp_check(...)
```

```{r courage-14-test, include = FALSE}
# pp_check(fit_XX)
```

### 

In this case, XX

<!-- If the fake data had looked very different from the real data, we have had a problem. But, for the most part, we conclude that, although not perfect, pp_check() shows that the fake outcomes generated by our model are like the actual outcome data. -->


### Exercise 15

Use `library()` to load the [**gtsummary**](https://www.danieldsjoberg.com/gtsummary) package.

```{r courage-15, exercise = TRUE}

```

```{r courage-15-hint-1, eval = FALSE}
library(gtsummary)
```

```{r courage-15-test, include = FALSE}
library(gtsummary)
```

### 

<!-- Drop some knowledge about gtsummary. Or say something more about your DGM. -->

### Exercise 16

<!-- XX: This can be just one question or several, especially if you want to teach some more gtsummary or gt tricks. Make any adjustments to this question, like `intercept = TRUE`, so that this question works. -->

Pipe `fit_XX` to `tbl_regression()`.


```{r courage-16, exercise = TRUE}

```

```{r courage-16-hint-1, eval = FALSE}
fit_XX |> 
  tbl_...()
```

```{r courage-16-test, include = FALSE}
# fit_XX |> 
#   tbl_regression()
```

### 

<!-- XX: Drop some knowledge about what you have learned by looking at the resulting table. Of course, you could have learned the same thing when you first took a look at fit_XX. But the table makes it easier to see the relationships between the variables and the outcome. With luck, students will take the hint when they answer the next question. -->

<!-- https://www.danieldsjoberg.com/gtsummary/articles/tbl_regression.html -->


### Exercise 17

Write a few sentence which summarize your work so far. The first few sentences are the same as what you had at the end of the Justice Section. Add one sentence which describes the modelling approach which you are using, specifying the functional form and the dependent variable. Add one sentence which describes the *direction* (not the magnitude) of the relationship between one of your independent variables and your dependent variable.

```{r courage-17}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 18

Update `stops.qmd`. First, add `library(gtsummary)` to the `setup` code chunk,. Second, add the mathematical formula, in $\LaTeX$ and surrounded by double dollar signs, for your model. Third, add a new code chunk which creates the table of model parameters. `Command/Ctrl + Shift + K` to ensure that everything works.

At the Console, run:

```
tutorial.helpers::show_file("stops.qmd", start = -8)
```

CP/CR.

```{r courage-18}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

## Temperance
### 

<!-- XX: Choose one. -->

*Temperance is a tree which as for its root very little contentment, and for its fruit calm and peace.* - Buddha
*Temperance is the greatest of all virtues. It subdues every passion and emotion, and almost creates a Heaven upon Earth.* - Joseph Smith Jr.
*Temperance is a bridle of gold; he, who uses it rightly, is more like a god than a man.* - Robert Burton
*Temperance is the firm and moderate dominion of reason over passion and other unrighteous impulses of the mind.* - Marcus Tullius Cicero
*Temperance to be a virtue must be free, and not forced.* - Philip Massinger
*Temperance is simply a disposition of the mind which binds the passion.* - Thomas Aquinas


### Exercise 1

In your own words, describe the use of Temperance in data science.

```{r temperance-1}
question_text(NULL,
	message = "Temperance uses the Data Generating Mechanism to answer the question with which we began. Humility reminds us that this answer is always a lie.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

What is the general topic we are investigating? What is the specific question we are trying to answer? 

```{r temperance-2}
question_text(NULL,
	message = "XX: Should be exactly how you started the Wisdom section.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Data science projects almost always begin with a broad topic of interest. Yet, in order to make progress, we need to drill down to a specific question. This leads to the creation of a data generating mechanism, which can now be used to answer lots of questions, thus allowing us to explore the original topic broadly.

### Exercise 3

To answer our question, we need to create a `newdata` object. Which variables (e.g., which columns) do we need to include in this object?

```{r temperance-3}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Must be all the right hand side variables in fit_XX. And note that the type must (maybe not always . . .) match, like if `treatment` is a factor in the original data used to create fit_XX then it must (?) be a factor in ndata. -->


### Exercise 4

<!-- XX: Sometimes useful to think about this question and the number of posterior questions together, or event to reverse them. -->

Which values do you want the variables in your `newdata` object to have? This is not easy! At the very least, one of the rows should have values which allow you to answer your original question. But, now that you have a model, there are many questions which you might want to answer, the better to get a fuller understanding.

```{r temperance-4}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Chapter 10 is a great example of this in its full complexity. We want to know how "different" units behave, where the very definition of "different" is that they do not have identical values for all the variables used in fit_XX. -->

<!-- For example, one row in ndata will generally represent the answer to the specific question we started with. But that is just the posterior for one sort of unit. There are lots of different units! Which others might we be interested in? We can generate posteriors for each of them, and then, in some cool graphic, display all those posteriors together. -->

<!-- Note that, previously, this document claimed that the number of rows in ndata corresponded to the number of posteriors you wanted to calculate. But that is not true! -->

### Exercise 5

Here is the R code which creates the `newdata` object: `tibble(whatever) code here`. Type it into the code exercise block and hit "Run Code."

<!-- Asking students to create this object --- even after you help them figure out the columns, rows and values --- is too hard, at least until they get more experiences. Your knowledge drop, for this question and the next, should give them advice on the broad topic of how they can create newdata objects themselves. -->

```{r temperance-5, exercise = TRUE}

```

```{r temperance-5-hint-1, eval = FALSE}

```

```{r temperance-5-test, include = FALSE}

```

### 

### Exercise 6

Behind the scenes, we have created the `ndata` object using this code. To confirm, type `ndata` and hit "Run Code."

<!-- Of course, you need to have added the code to create `ndata` in the setup chunk at the top of the file. -->

```{r temperance-6, exercise = TRUE}

```

```{r temperance-6-hint-1, eval = FALSE}

```

```{r temperance-6-test, include = FALSE}

```

### 

Note that, when you add Temperance-related code to your QMD, you will need to also add code which creates the `ndata` object.

### Exercise 7

Now that we have the `newdata` object, we can create a pipe which uses out fitted model to answer our question. Begin by typing `fit_XX` and clicking "Run Code."

```{r temperance-7, exercise = TRUE}

```

```{r temperance-7-hint-1, eval = FALSE}

```

```{r temperance-7-test, include = FALSE}

```

### 

<!-- XX: Again, the main point of knowledge drops is this area is to explain to students why the newdata object looks the way it does and what it will produce. A great way to teach is via example. That is, explaining that if we had another way with these values, then we would get this posterior. Or, explaining what would be produced if we used add_epred instead of add_predict, and vice verse. -->


### Exercise 8

Pipe `fit_XX` to [XX: either `add_epred_draws()` or `add_predicted_draws()`] with the argument `newdata = ndata`. 



```{r temperance-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-8-hint-1, eval = FALSE}

```

```{r temperance-8-test, include = FALSE}

```

### 

<!-- XX: How do students know whether to use add_epred_draws or add_predicted_draws? This is non-trivial. On some level, we just tell them with the above command. (We don't make them guess.) But we also address this issue explicitly in various knowledg drops, especially this one. -->

<!-- XX: Insert as many questions as necessary to build a nice-looking example of your final plot. In early chapters, this is simple since our questions are simple. They are just one posterior. In later chapters, they become more complex, with the inclusion of several posteriors, as well as manipulation of them to calculate causal effects and whatnot. See the voting postcard example. -->

### Exercise 9

Create a new code chunk in `stops.qmd`. Label it with `label: plot`. Copy/paste the code which creates your graphic. Don't forget that, at the top of this chunk, you must include code which creates the `ndata` object.

`Command/Ctrl + Shift + K` to ensure that it all works as intended.

At the Console, run:

```
tutorial.helpers::show_file("stops.qmd", start = -8)
```

CP/CR.

```{r temperance-9}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

### Exercise 10

Write a paragraph which summarizes the project in your own words. The first few sentences are the same as what you had at the end of the Courage section. But, since your question may have evolved, you should feel free to change those sentences. Add at least one sentence which describes at least one quantity of interest (QoI) --- presumably one that answers your question -- and which provides a measure of uncertainty about that QoI.

<!-- XX: Most of the time, there will be some measure of uncertainty associated with your QoI. But not always! The most common counter-example involves a question which asks about the odds or probability of something happening. We would answer such a question by simulating the event with `add_predicted_draws()`. We would then calculate the odds/probability of something happening by seeing how many of the 4,000 draws met the criteria for the event. Assume that was 40%. So, we think that there is a 40% chance that event A will happen. Yet there is no uncertainty associated with that estimate because it, itself, is an expression of uncertainty. (DK: Flesh this out further.) -->

```{r temperance-10}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Edit the summary paragraph in `stops.qmd` as you see fit, but do not copy/paste our answer exactly. `Command/Ctrl + Shift + K`.


<!-- XX: Again, spend time to make your recommended paragraph perfect. Study the examples in https://ppbds.github.io/primer/cardinal-virtues.html closely. -->

### Exercise 11

Write a few sentences which explain why the estimates for the quantities of interest, and the uncertainty thereof, might be wrong. Suggest an alternative estimate and confidence interval, if you think either might be warranted.

```{r temperance-11}
question_text(NULL,
	message = "XX: This is another example in which the quality of your answer is important. You might or might not suggest an alternate estimate. I always adjust the estimate toward my own subjective sense of a longrun average and/or typical value and/or zero. But that is not necessary. However, you should always increase the confidence interval since the assumptions of your model are always false.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 12

Rearrange the material in `stops.qmd` so that the order is graphic, paragraph, math and table. Doing so, of course, requires sensible judgment. For example, the code chunk which creates the fitted model must occur before the chunk which creates the graphic. `Command/Ctrl + Shift + K` to ensure that everything works.

At the Console, run:

```
tutorial.helpers::show_file("stops.qmd")
```

CP/CR.

```{r temperance-12}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

Add `rsconnect` to the `.gitignore` file. You don't want your personal Rpubs details stored in the clear on Github. Commit/push everything.

### Exercise 13

Publish `stops.qmd` to Rpubs. Choose a sensible slug. Copy/paste the url below.

```{r temperance-13}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

## Summary
### 

This tutorial covered [Chapter XX: XX](https://ppbds.github.io/primer/XX.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 



```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
