---
title: "Visualization D"
tutorial:
  id: "visualization-d"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 1 Tutorial Part D"
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)



knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

# Key Data

set.seed(9)
results <- rnorm(10000)

```

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```

## Summary Statistics 
###


### Exercise 1

Start by using `set.seed()` to ensure we can reproduce our results later. Within `set.seed()` use the argument `9`.

```{r ss-1, exercise = TRUE}

```

### Exercise 2

Now use `rnorm()` to randomly generate a normal distribution of 10000. Save your work to an object named `results`.

```{r ss-2, exercise = TRUE}

```

```{r ss-2-hint, eval = FALSE}
results <- rnorm(...)
```

### Exercise 3

Now use the `c()` function to find the `min()`, `median()`, and `max()` of our normal distribution of `results`

```{r ss-3, exercise = TRUE}

```

```{r ss-3-hint, eval = FALSE}
c(min(results), median(...), max(...))
```

### Exercise 4

Let's now find the 5th, 50th, and 100th percentiles using `quantile()`. Set the first argument to `quantile()` as `results`. The second argument should set `probs` to the function `c()` with arguments 0, .5, and 1.

```{r ss-4, exercise = TRUE}

```

```{r ss-4-hint, eval = FALSE}
quantile(..., probs = c(..., ..., ...))
```

Notice that we get the same values as our min, median, and max, respectively. What does this mean? 
* 0% of the data falls below -3.818 (the min)
* The point .005 splits the data into two separate/equal parts (the median)
* 95% of the data falls below 3.793 (the max)


### Exercise 5

Let's now consider the `trains` data set. Extract the `age` column.

```{r ss-5, exercise = TRUE}

```

```{r ss-5-hint, eval = FALSE}
Use the $ operator.
```

### Exercise 6

Calculate the `mean()` of the `age` column.

```{r ss-6, exercise = TRUE}

```

```{r ss-6-hint, eval = FALSE}
mean(trains$age)
```

### Exercise 7

Now use `quantile()` to find the 2.5th and 97.5th percentiles of `age`. Set the first argument to `quantile()` as `trains$age`. The second argument should set `probs` to the function `c()` with arguments.025, and .975.

```{r ss-7, exercise = TRUE}

```

```{r ss-7-hint, eval = FALSE}
quantile(trains$age, probs = c(...,...))
```

### Exercise 8

Let's now find `sd()` of the age column. 

```{r ss-8, exercise = TRUE}

```

```{r ss-8-hint, eval = FALSE}
sd(trains$age)
```

### Exercise 9

Great. Let's now calculate the 95th confidence interval of `trains$age`. First, take the `mean()` value and add it to 2 times the `sd()`. 

```{r ss-9, exercise = TRUE}

```

```{r ss-9-hint-1, eval = FALSE}
Inside mean() and sd() use the argument trains$age
```

```{r ss-9-hint-2, eval = FALSE}
To add, use +, and to multiply use *
```

For the 95th confidence interval, you take the center of the distribution +/- two times the standard deviation. Note that we just found the upper bound of our interval. Let's now find the lower bound.


### Exercise 10

Now take the `mean()` value and subtract 2 times the value of the `sd()`. 

```{r ss-10, exercise = TRUE}
c(mean(trains$age) - 2 * sd(trains$age), mean(trains$age) + 2 * sd(trains$age))
```

```{r ss-10-hint-1, eval = FALSE}
Inside mean() and sd() use the argument trains$age
```

```{r ss-10-hint-2, eval = FALSE}
To add, use +, and to multiply use *
```


### Exercise 11

In your own words, write one sentence that explains the significance of the 95th percentile. 

```{r ex-6}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 6))
```


