---
title: "Visualization D"
tutorial:
  id: "visualization-d"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 1 Tutorial Part D"
---

<!-- Things to Do -->

<!-- Make a plot of one of them that shows this somehow? Plot histogram then put 6 vertical lines, two each for mean +/- 2 sd, median +/- 2 mad, 95% quantile. The mean + 2 x the sd should be about the 97.5th percentile. Won't be exact! But about. The median + 2 x the mad should be about the 97.5th percentile. Won't be exact! But about. Same with substraction. -->


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)



knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

# Key Data

set.seed(9)
results <- rnorm(10000)

```

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```

## Summary Statistics 
###


### Exercise 1

Start by using `set.seed()` to ensure we can reproduce our results later. Within `set.seed()` use the argument `9`.

```{r ss-1, exercise = TRUE}

```

### Exercise 2

Now use `rnorm()` to randomly generate a normal distribution of 10000. Save your work to an object named `results`.

```{r ss-2, exercise = TRUE}

```

```{r ss-2-hint, eval = FALSE}
results <- rnorm(...)
```

### Exercise 3

Now use the `c()` function to find the `min()`, `median()`, and `max()` of our normal distribution of `results`

```{r ss-3, exercise = TRUE}

```

```{r ss-3-hint-1, eval = FALSE}
c(min(...), median(...), max(...))
```

```{r ss-3-hint-2, eval = FALSE}
Inside min(), median(), max(), use the argument `results`.
```

### Exercise 4

Let's now find the 5th, 50th, and 100th percentiles using `quantile()`. Set the first argument to `quantile()` as `results`. The second argument should set `probs` to the function `c()` with arguments 0, .5, and 1.

```{r ss-4, exercise = TRUE}

```

```{r ss-4-hint, eval = FALSE}
quantile(..., probs = c(..., ..., ...))
```

Notice that we get the same values as our min, median, and max, respectively. What does this mean? 
* 0% of the data falls below -3.818 (the min)
* The point .005 splits the data into two separate/equal parts (the median)
* 95% of the data falls below 3.793 (the max)


### Exercise 5

Let's now consider the `trains` data set. Extract the `age` column.

```{r ss-5, exercise = TRUE}

```

```{r ss-5-hint, eval = FALSE}
Use the $ operator.
```

### Exercise 6

Calculate the `mean()` and `median()` of the `trains$age`. 

```{r ss-6, exercise = TRUE}

```

```{r ss-6-hint-1, eval = FALSE}
You can use the `c()` function to do both functions at the same time and to return their output values as a vector.
```

```{r ss-6-hint-2, eval = FALSE}
c(mean(...), median(...))
```

### Exercise 7

Let's get a measure of variation around age. Calculate the `sd()` and `mad()` of `trains$age`.

```{r ss-66, exercise = TRUE}

```

```{r ss-66-hint-1, eval = FALSE}
You can use the `c()` function to return the values as a vector.
```

```{r ss-66-hint-2, eval = FALSE}
c(sd(...), mad(...))
```

### Exercise 8

Now use `quantile()` to find the 2.5th and 97.5th percentiles of `age`. Set the first argument to `quantile()` as `trains$age`. The second argument should set `probs` to the function `c()` with arguments.025, and .975.

```{r ss-7, exercise = TRUE}

```

```{r ss-7-hint, eval = FALSE}
quantile(trains$age, probs = c(...,...))
```

### Exercise 9

Let's calculate the 95th confidence interval, the center of the distribtion +/- two times the standard deviation. 

To do so, use the `c()` function. The first argument to `c()` should take the `mean()` and add it to two times the value of `sd()`.  The second argument to `c()` should take the `mean()`of  and subtract the value of 2 times the `sd()`.

```{r qscores22, exercise = TRUE}

```

```{r qscores22-hint-1, eval = FALSE}
Inside mean() and sd() use the argument trains$age.
Use + to add and * to multiply.
```

```{r qscores22-hint-2, eval = FALSE}
c(mean(...) + 2 * sd(...), 
  mean(...) - 2 * sd(...))
```

### Exercise 10

Let's now calculate the 95th confidence interval using `mad()`. Copy and paste your code above and replace `sd()`with `mad()`.

```{r ss-9, exercise = TRUE}

```

```{r ss-9-hint-1, eval = FALSE}
Inside mean() and mad() use the argument trains$age
```

Note that the 95th confidence interval we get using `sd()` and `mad()` do not match. However, they are more or less the same. 







