---
title: "One Parameter"
tutorial:
  id: "one-parameter"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 6 tutorial"
---

<!-- Things to Fix: -->

<!-- DONE: Virtual shovel culminates in making "Distributions of 1,000 red" -->

<!-- DONE: Different sample sizes culminates in Figure 6.7, maybe simpler. Not 100 shovel size. Maybe just 5, 10, 50, 100, 500. -->

<!-- Standard error just needs a question or two --- maybe a written sentence or two --- about what a standard error is. Like ch 4 tutorial questions at start. -->

<!--  DONE: Posterior distribution is for the proportion red beads or whatever. Located at "To visualize this in a 3D plot" -->

<!-- Need one more section which using the posterior to, for example, create the posterior of number red which will be drawn with a shovel of size 20. Use a posterior to create a new postrerior. Turtles all the way down. -->






<!-- Add a use the posterior section to answer a question. Add a standard error. Change standard deviation section to standard error section. -->

 <!-- Read the chapter and see how we have removed the infer package. The sampling is done "by hand" now. Change the exercises below to do the same. This means that functions like use_shovel may not be needed. But prop_red might still be? Key: Make it like the chapter. Maybe we don't need extra functions at all? -->

<!-- DK: Add use of posterior to make a forecast exercise. Note that we might end up simplifying how this is done in the chapter. -->

<!-- 0) Find all the DK comments and address them -->
<!-- 1) Each section finishes with a nice plot. The student is show the plot in the last step and told to, approximately, replicate it. Of course, this will just involve adding a couple of items to whatever was the version in the second to last question. -->

<!-- DK: Should we do something with sta_glm? Probably not. -->


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(skimr)
library(infer)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

# Key Data

set.seed(10)
urn <- tibble(color = c(rep("red", 400), rep("white", 600))) %>%
  sample_frac() %>% 
  mutate(ID = 1:1000) %>% 
  select(ID, color)

set.seed(9)
virtual_samples <- tibble(ID = 1:1000) %>% 
  mutate(shovel = map(ID, ~ sample_n(urn, size = 50))) %>% 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) %>% 
  mutate(numb_beads = map_int(shovel, ~ length(.$color))) %>% 
  mutate(prop_red = numb_red / numb_beads)

prop_red <- function(x, shovel_size, reps){
  tibble(ID = 1:reps) %>% 
    mutate(shovel = map(ID, ~ sample_n(x, size = shovel_size))) %>% 
    mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) %>% 
    mutate(numb_beads = map_int(shovel, ~ length(.$color))) %>% 
    mutate(prop_red = numb_red / numb_beads)
}



```

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```


## Virtual sampling
###

Let's create the following plot that shows sampling variation for 1000 samples from an urn that contains red and white beads.

```{r virts_p}
set.seed(9)
virtual_samples <- tibble(ID = 1:1000) %>% 
  mutate(shovel = map(ID, ~ sample_n(urn, size = 50))) %>% 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) %>% 
  mutate(numb_beads = map_int(shovel, ~ length(.$color))) %>% 
  mutate(prop_red = numb_red / numb_beads)

virtual_samples %>% 
  ggplot(aes(x = prop_red)) +
    geom_histogram(binwidth = 0.01, 
                   boundary = 0.4, 
                   color = "white") +
    labs(x = expression(hat(p)), 
         y = "Count",
         title = "Distribution of 1,000 proportions red") 

```

### Exercise 1

Type `urn` below to inspect the urn we will be using in this section.

```{r shovel1, exercise = TRUE}
set.seed(10)
urn <- tibble(color = c(rep("red", 400), rep("white", 600))) %>%
  sample_frac() %>% 
  mutate(ID = 1:1000) %>% 
  select(ID, color)
```

### Exercise 2

To simulate the process of real-world sampling, let’s take a sample of 50 beads from our virtual urn. To do so, start a pipe by creating a `tibble()` that has one variable `ID` that takes on the values 1 to 1000.

```{r shovel2, exercise = TRUE}

```

```{r shovel2-hint, eval = FALSE}
tibble(ID = ...)
```

### Exercise 3

Great. Now pipe your results to the function `mutate()` to create the variable `shovel`, which is set to the function `map()`. The first argument to `map()` should be `ID`. The second argument should use `sample_n()` to take a sample of 50 beads from `urn`.

```{r shovel3, exercise = TRUE}

```

```{r shovel3-hint, eval = FALSE}
tibble(ID = 1:1000) %>% 
  mutate(shovel = map(..., ~ sample_n(urn, size = ...)))
```

### Exercise 4

Continue your pipe with `mutate()` to create the variable `numb_red`, which tells us the number of red beads present. Set `numb_red` to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `sum()` of where the column `color` of `shovel` is equal to red.

```{r shovel4, exercise = TRUE}

```

```{r shovel4-hint, eval = FALSE}
... %>% 
  mutate(... = map_int(..., ~ sum(.$color == "red")))
```

### Exercise 5

Great. Now use `mutate()` to create the variable `numb_beads`, which is set to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `length()` of the column `color` of `shovel`.
 

```{r shovel5, exercise = TRUE}

```

```{r shovel5-hint-1, eval = FALSE}
... %>% 
  mutate(numb_beads = map_int(..., ~ length(...)))
```

```{r shovel5-hint-2, eval = FALSE}
... %>% 
  mutate(numb_beads = map_int(..., ~ length(.$color)))
```

### Exercise 6

Use `mutate()` one last time to create the variable `prop_red`, our estimate of the proportion of red beads in the urn. Set `prop_red` to `numb_red` divided by `numb_beads`.

```{r shovel6, exercise = TRUE}

```

```{r shovel6-hint, eval = FALSE}
... %>% 
   mutate(prop_red = ... / ...)
```

### Exercise 7

Copy/paste your code from above. Assign your code to an object named `virtual_samples`.

```{r shovel7, exercise = TRUE}

```

```{r shovel7-hint, eval = FALSE}
Use the assignment operator to do so.
```

### Exercise 8

Awesome. Now start a pipe with `virtual_samples`. Use `ggplot()`to map `prop_red` to the x-axis. Also, add the layer `geom_histogram()` to create a histogram of our data.

```{r shovel8, exercise = TRUE}

```


```{r shovel8-hint-1, eval = FALSE}
ggplot(aes(...)) + 
  geom_histogram()
```

### Exercise 9

Within `geom_histrogram()` set `binwidth` to .01, boundary to .4, and `color` to "white".

```{r shovel9, exercise = TRUE}

```

```{r shovel9-hint, eval = FALSE}
... +
  geom_histrogram(..., ..., ...)
```

### Exercise 10

To finish, use `labs()` to give your graph the appropriate title and axis labels. See **hint** for guidance to create the symbol $\hat{p}$.


```{r shovel10, exercise = TRUE}

```

Reminder: This is what your plot should look like. 

```{r}
set.seed(9)
virtual_samples <- tibble(ID = 1:1000) %>% 
  mutate(shovel = map(ID, ~ sample_n(urn, size = 50))) %>% 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) %>% 
  mutate(numb_beads = map_int(shovel, ~ length(.$color))) %>% 
  mutate(prop_red = numb_red / numb_beads)

virtual_samples %>% 
  ggplot(aes(x = prop_red)) +
    geom_histogram(binwidth = 0.01, 
                   boundary = 0.4, 
                   color = "white") +
    labs(x = expression(hat(p)), 
         y = "Count",
         title = "Distribution of 1,000 proportions red") 
```

```{r shovel10-hint, eval = FALSE}
Within labs(), set x to expression(hat(p))
```

## Different shovel sizes
###

Let's create the following plot that displays different standard deviations of red bead proportions for 100 different shovels.

```{r}
prop_red <- function(x, shovel_size, reps){
  tibble(ID = 1:reps) %>% 
    mutate(shovel = map(ID, ~ sample_n(x, size = shovel_size))) %>% 
    mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) %>% 
    mutate(numb_beads = map_int(shovel, ~ length(.$color))) %>% 
    mutate(prop_red = numb_red / numb_beads)
}

shovels_100 <- tibble(shovel_size = 1:100) %>%
  mutate(prop_red_results = map(shovel_size,
                                ~ prop_red(x = urn, 
                                           shovel_size = .x, 
                                           reps = 1000))) %>% 
  mutate(prop_red_sd = map_dbl(prop_red_results, 
                               ~ pull(., prop_red) %>% sd()))

shovels_100 %>%
 ggplot(aes(x = shovel_size, y = prop_red_sd)) +
 geom_point() +
 stat_function(aes(x = 1:100, colour = "red"), 
               fun = function(.x) 1/(2 * sqrt(.x)), 
               show.legend = FALSE) +
 labs(x = "Shovel size",
      y = "Standard deviation of the proportion red")
```

### Exercise 1

Before we begin, write two sentences explaining the significance of standard error.

```{r map11, exercise = TRUE}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```


### Exercise 2

Let's create a function that calculates the proportion of red beads. We start with hard code. Recall our code for  `virtual_samples` in the previous section. Place the code within { } of `function()`. Name the function `prop_red()`.

```{r map1, exercise = TRUE}
tibble(ID = 1:1000) %>% 
  mutate(shovel = map(ID, ~ sample_n(urn, size = 50))) %>% 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) %>% 
  mutate(numb_beads = map_int(shovel, ~ length(.$color))) %>% 
  mutate(prop_red = numb_red / numb_beads)
```

```{r map1-hint, eval = FALSE}
prop_red <- function(){
  
  ...
  
}

```

### Exercise 3

Copy/paste your code from above. Add the parameter `reps` within `function()`. Also replace the value 1000 within `tibble()` with `reps`.

```{r map2, exercise = TRUE}

```

```{r map2-hint-1, eval = FALSE}
prop_red <- function(...){
  tibble(ID = 1:reps) %>% 
    ...
}
```

### Exercise 4

Copy/paste your code from above. Add the parameter `x` within `function()`. Also replace the argument `urn` with `x` within `sample_n()`.

```{r map3, exercise = TRUE}

```

```{r map3-hint, eval = FALSE}
prop_red <- function(reps, ...){
  tibble(ID = 1:reps) %>% 
  mutate(shovel = map(ID, ~ sample_n(x, size = 50))) %>% 
    ...
}
```

### Exercise 5

Copy/paste your code from above. Add the parameter `shovel_size` within `function()`. Also set `size` to `shovel_size` within 

```{r map4, exercise = TRUE}

```

```{r map4-hint-1, eval = FALSE}
prop_red <- function(reps, x, ...){
  tibble(ID = 1:reps) %>% 
  mutate(shovel = map(ID, ~ sample_n(x, size = ...))) %>% 
    ...
}
```

<!-- ### Exercise 5 -->

<!-- Now, let's test our new function `prop_red` by drawing from our urn with a size of 30 and 2 repetitions. -->

<!-- ```{r map5, exercise = TRUE} -->

<!-- ``` -->

<!-- ```{r map5-hint, eval = FALSE} -->
<!-- prop_red(x = urn, size = ..., reps = ...) -->
<!-- ``` -->


### Exercise 6

Great. Let's now create a `tibble()` with one variable `shovel_size`, which takes on the values 1 to 100. 

```{r map5, exercise = TRUE}

```

```{r map5-hint, eval = FALSE}
tibble(shovel_size = ...)
```

### Exercise 7

Pipe your results to `mutate()` to create the variable `prop_red_results`, which is set to the function `map()`.The first argument to `map()` should be `shovel_size`. The second argument should be our function `prop_red()` where `x` is set to `urn`, `shovel_size` set to `.x` and `reps` set to 1000.
 

```{r map6, exercise = TRUE}

```

```{r map6-hint, eval = FALSE}
... %>% 
  mutate(prop_red_results = map(...,
                                ~ prop_red(..., ..., ...)))
```

### Exercise 8

Use `mutate()` once more to create the variable `prop_red_sd` which is set to the function `map_dbl()`. The first argument to `map_dbl()` should be `prop_red_results`. The second argument should be `pull()`. The first argument to `pull()` should be `.`. The second argument should be `prop_red`.

```{r map7, exercise = TRUE}

```

```{r map7-hint, eval = FALSE}
... %>% 
mutate(... = map_dbl(..., 
                      ~ pull(., prop_red) %>% 
```

### Exercise 9

Use `mutate()` once more to create the variable `prop_red_sd` which is set to the function `map_dbl()`. The first argument to `map_dbl()` should be `prop_red_results`. The second argument should be `pull()`. The first argument to `pull()` should be `.`. The second argument should be `prop_red`.

```{r map8, exercise = TRUE}

```

```{r map8-hint, eval = FALSE}

```

### Exercise 10

Let's find the standard deviation of proportions red for all shovel sizes between 1 and 100. Pipe the results of `pull()` to the function `sd()`. **Note**: You are still inside `map_dbl()`.

```{r map9, exercise = TRUE}

```

```{r map9-hint, eval = FALSE}
mutate(prop_red_sd = map_dbl(prop_red_results, 
                               ~ pull(., prop_red) %>% ...))
```

### Exercise 11

Copy/paste your code from above. Assign your code to an object named `shovels_100`. 

```{r map10, exercise = TRUE}

```

```{r map10-hint, eval = FALSE}

```

### Exercise 12

Start a pipe with `shovels_100`. Use `ggplot()` to map `shovel_size` to the x-axis and `prop_red_sd` to the y-axis. Also add the layer `geom_point()`.

```{r map11, exercise = TRUE}

```

```{r map11-hint, eval = FALSE}
... %>% 
  ggplot(aes(x = ..., y = ...)) +
 geom_point() 
```

### Exercise 13

Add the layer `stat_function()`. Map the values 1 to 100 to the x-axis. Also set `color` to "red".

```{r map12, exercise = TRUE}

```

```{r map12-hint, eval = FALSE}
... + 
  stat_function(aes(x = ..., ...))
```

### Exercise 14

Also set `fun` to `function(.x) 1/(2 * sqrt(.x))` within `stat_function()`.Also set `show.legend` to FALSE.

```{r map13, exercise = TRUE}

```

```{r map13-hint, eval = FALSE}
... + 
  stat_function(aes(x = 1:100, colour = "red"), 
               fun = ..., 
               show.legend = ...) 
```

### Exercise 15

Great. Now use `labs()` to label the x-axis "Shovel size" and the y-axis 
"Standard deviation of the proportion red". 

```{r map14, exercise = TRUE}

```

Reminder: This is what your plot should look like.

```{r}
prop_red <- function(x, shovel_size, reps){
  tibble(ID = 1:reps) %>% 
    mutate(shovel = map(ID, ~ sample_n(x, size = shovel_size))) %>% 
    mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) %>% 
    mutate(numb_beads = map_int(shovel, ~ length(.$color))) %>% 
    mutate(prop_red = numb_red / numb_beads)
}

shovels_100 <- tibble(shovel_size = 1:100) %>%
  mutate(prop_red_results = map(shovel_size,
                                ~ prop_red(x = urn, 
                                           shovel_size = .x, 
                                           reps = 1000))) %>% 
  mutate(prop_red_sd = map_dbl(prop_red_results, 
                               ~ pull(., prop_red) %>% sd()))

shovels_100 %>%
 ggplot(aes(x = shovel_size, y = prop_red_sd)) +
 geom_point() +
 stat_function(aes(x = 1:100, colour = "red"), 
               fun = function(.x) 1/(2 * sqrt(.x)), 
               show.legend = FALSE) +
 labs(x = "Shovel size",
      y = "Standard deviation of the proportion red")
```

```{r map14-hint, eval = FALSE}

```


## Posterior Distribution
###


Let's create the following plot  <!-- BG: need further explanation here -->

```{r }
joint_dist <- 
  tibble(red_in_urn = seq(from = 0, to = 1000, by = 1)) %>% 
    mutate(p = red_in_urn / urn_size) %>% 
    mutate(red_in_paddle = map(p, ~ rbinom(n = 100, 
                                               size = 50, 
                                               prob = .))) %>%
    unnest(red_in_paddle) 

joint_dist %>% 
  filter(red_in_paddle == 17) %>% 
  ggplot(aes(x = p)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 50) + 
    labs(title = "Posterior Probability Distribution",
         subtitle = "Proportion of red beads in urn is centered around 0.34",
         x = "Proportion p of Red Beads in Urn",
         y = "Probability") + 
    scale_x_continuous(labels = scales::number_format()) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()


```

### Exercise 1

Create a `tibble()` with one variable `red_in_urn` that is set to the function `seq()`. Within `seq()` set `from` to 0, `to` to 1000, and `by` to 1.

```{r pp1, exercise = TRUE}

```

```{r pp1-hint, eval = FALSE}
tibble(red_in_urn = seq(...,...,...))
```

### Exercise 2

Great. Now pipe your results to the function `mutate()` to create the variable `p`, which is set to the `red_in_urn` divided by the `urn_size`.

```{r pp2, exercise = TRUE}

```

```{r pp2-hint, eval = FALSE}
... %>% 
    mutate(p = ... / ...) 
```

### Exercise 3

Great. Now pipe your results to the function `mutate()` to create the variable `red_in_paddle`, which is set to the function `map()`. The first argument to `map()` should be `p`. The second argument should use `rbinom()`. Within `rbinom()` set `n` to 100, `size` to 50, and `prob` to `.`

```{r pp3, exercise = TRUE}

```

```{r pp3-hint, eval = FALSE}
... %>% 
    mutate(red_in_paddle = map(..., ~ rbinom(..., 
                                             ..., 
                                              ...)))
```

### Exercise 4

Continue your pipe with the function `unnest()` with the argument `red_in_paddle`. **Note**: unnesting flattens list columns back into regular columns.

```{r pp4, exercise = TRUE}

```

```{r pp4-hint, eval = FALSE}
... %>%
    unnest(...) 
```

### Exercise 5

Copy/paste your code from above. Assign your code to an object named `joint_dist`.

```{r pp5, exercise = TRUE}

```

### Exercise 6

Copy/paste your code from above. Assign your code to an object named `joint_dist`.

```{r pp6, exercise = TRUE}

```

```{r pp6-hint, eval = FALSE}

```

### Exercise 7

Let's plot our joint distribution we just created. Start a pipe with `joint_dist` and `filter()` where `red_in_paddle` is equal to 17.

```{r pp7, exercise = TRUE}

```

```{r pp7-hint, eval = FALSE}
...%>% 
  filter(red_in_paddle == ...)
```

### Exercise 8

Continue your pipe with `ggplot()`to map `p` to the x-axis. Also, add the layer `geom_histogram()`.

```{r pp8, exercise = TRUE}

```

```{r pp8-hint, eval = FALSE}
...%>% 
  ggplot(aes(...)) +
    geom_histogram()
```

### Exercise 9

Within `geom_histogram()`, use `after_stat()` . Inside `after_stat()`, use `aes()` with the argument `y = count/sum(count)` to convert the y-axis to percent values.

```{r pp9, exercise = TRUE}

```

```{r pp9-hint, eval = FALSE}
...%>% 
    geom_histogram(aes(y = after_stat(...))
```

### Exercise 10

Add the layer `scale_x_continuous()` with the argument `labels` set to `scales::number_format()`.

```{r pp10, exercise = TRUE}

```

```{r pp10-hint, eval = FALSE}
...%>% 
   scale_x_continuous(labels = ...)
```

### Exercise 11

Great. Now add the layer `scale_y_continuous()` with the argument `labels` set to `scales::percent_format()`.

```{r pp11, exercise = TRUE}

```

```{r pp11-hint, eval = FALSE}
...%>% 
   scale_y_continuous(labels = ...)
```

### Exercise 12

To finish, use `labs()` to give your graph the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.


```{r pp12, exercise = TRUE}

```

Reminder: This is what your plot should look like. 

```{r}
joint_dist <- 
  tibble(red_in_urn = seq(from = 0, to = 1000, by = 1)) %>% 
    mutate(p = red_in_urn / urn_size) %>% 
    mutate(red_in_paddle = map(p, ~ rbinom(n = 100, 
                                               size = 50, 
                                               prob = .))) %>%
    unnest(red_in_paddle) 

joint_dist %>% 
  filter(red_in_paddle == 17) %>% 
  ggplot(aes(x = p)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 50) + 
    labs(title = "Posterior Probability Distribution",
         subtitle = "Proportion of red beads in urn is centered around 0.34",
         x = "Proportion p of Red Beads in Urn",
         y = "Probability") + 
    scale_x_continuous(labels = scales::number_format()) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()

```

## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```

