---
title: "One Parameter"
tutorial:
  id: "one-parameter"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 6 tutorial"
---

<!-- Things to Fix: -->

 <!-- Read the chapter and see how we have removed the infer package. The sampling is done "by hand" now. Change the exercises below to do the same. This means that functions like use_shovel may not be needed. But prop_red might still be? Key: Make it like the chapter. Maybe we don't need extra functions at all? -->

<!-- DK: Add use of posterior to make a forecast exercise. Note that we might end up simplifying how this is done in the chapter. -->

<!-- 0) Find all the DK comments and address them -->
<!-- 1) Each section finishes with a nice plot. The student is show the plot in the last step and told to, approximately, replicate it. Of course, this will just involve adding a couple of items to whatever was the version in the second to last question. -->

<!-- DK: Should we do something with sta_glm? Probably not. -->


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(skimr)
library(infer)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

# Key Data

set.seed(9)
urn <- tibble(color = c(rep("red", 925), rep("white", 575))) %>%
  slice_sample(prop = 1)

use_shovel <- function(x, size, reps){
  x %>% rep_sample_n(size = size, reps = reps)
}

prop_red <- function(x, size, reps){
  use_shovel(x = x, size = size, reps = reps) %>% 
  group_by(replicate) %>% 
  summarize(red = sum(color == "red"), .groups = "drop_last") %>% 
  mutate(prop_red = red/size)
}

```

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```


## The "virtual shovel"
###

We have created a virtual urn with some unknown amount of red beads and white beads. Our goal will eventually be to estimate the total number of red beads in the urn. 

For this portion of the tutorial, we will be replicating the graph below. The goal is to build this graph step-by-step, using the knowledge from The Primer's Chapter 6. 

```{r}
urn %>%
  rep_sample_n(size = 20, reps = 50, replace = TRUE) %>%
  mutate(is_red = (color == "red"), 
         is_white = (color == "white"), 
         .groups = "drop") %>%
  summarize(num_red = sum(is_red), 
            num_white = sum(is_white),
            .groups = "drop") %>%
  mutate(prop_red = num_red / (num_red + num_white)) %>%
  mutate(estimated_red = prop_red * 1500) %>%
  ggplot(mapping = aes(x = estimated_red)) +
    geom_histogram(binwidth = 75, color = "white") +
    scale_y_continuous(breaks = seq(from = 0, to = 20, by = 2)) +
    scale_x_continuous(breaks = seq(from = 0, to = 1500, by = 100)) +
    labs(title = "Range of Estimates Using Shovel of Size 20",
         x = "Estimated number of red beads")
```


### Exercise 1

To view the urn, simply type `urn` in window below and hit Run Code.


```{r shovel1, exercise = TRUE}

```

### Exercise 2

It appears that there are 1,500 beads in the urn (i.e. 1,500 rows in our tibble). Run `nrow()` on `urn` to confirm the number of beads in the urn.

```{r shovel2, exercise = TRUE}

```

### Exercise 3

To simulate the process of real-world sampling, where we generally won't know exactly how many items are in our population, pipe `urn` into `rep_sample_n()` from the **infer** package, with a shovel `size` of 20 (i.e. the sample should have 20 observations).

```{r shovel3, exercise = TRUE}

```

```{r shovel3-hint, eval = FALSE}
urn %>%
  rep_sample_n(size =...)
```

### Exercise 4

Copy and paste your code from the previous exercise. Continuing your pipe, use `mutate()` to create two new variables: `is_red` should be a logical equal to the result of asking if `color` is "red," and `is_white` should be identical but replaced with the `color` "white."

```{r shovel4, exercise = TRUE}

```

```{r shovel4-hint, eval=FALSE}
is_red should be equal to (color == "red").
```

### Exercise 5

Next, use `summarize()` to create two more variables. `num_red` should be equal to the `sum()` of the `is_red` column, and `num_white` should be equal to the `sum()` of the `is_white` column. 

```{r shovel5, exercise = TRUE}

```

```{r shovel5-hint, eval = FALSE}
summarize(num_red = ..., num_white = ...)
```

### Exercise 6

Call `mutate()` to create the variable `prop_red`, the proportion of the sampled beads that are red. Set `prop_red` equal to the number of red beads divided by the sum of the number of red beads and white beads.

```{r shovel6, exercise = TRUE}

```

```{r shovel6-hint, eval=FALSE}
The proportion of red beads is num_red / (num_red + num_white).
```

### Exercise 7

Finally, use `mutate()` to create the `estimated_red` variable, our estimate of the number of red beads in the urn. `estimated_red` should be equal to `prop_red` multiplied by 1,500, the total number of beads in the urn.

```{r shovel7, exercise = TRUE}

```

```{r shovel7-hint, eval=FALSE}
The estimated_red variable should be equal to (prop_red * 1500).
```


### Exercise 8

Nice work! Running the code below gives us a way to virtually sample our urn in 20-bead increments. Notice that running the code multiple times gives us different estimates for the number of red beads in the urn. Each time we re-run the code, `rep_sample_n()` grabs a different sample from the urn.

Our next step will be to use our "virtual shovel" 50 times and create a distribution of our results. Start by setting the `reps` argument of `rep_sample_n()` to 50. Up until now, the default value of `reps` has been 1. By setting `reps` to 50, we are telling our machine to sample 20 beads from the urn fifty times. Set the `replace` argument to `TRUE`. This is equivalent to sampling with replacement, which is what we want. You will also need to set the `.groups` argument in summarize to something like "drop" to get rid of the error message.

```{r shovel8, exercise = TRUE, exercise.lines = 7}
urn %>%
  rep_sample_n(size = 20) %>%
  mutate(is_red = (color == "red"), is_white = (color == "white")) %>%
  summarize(num_red = sum(is_red), 
            num_white = sum(is_white)) %>%
  mutate(prop_red = num_red / (num_red + num_white)) %>%
  mutate(estimated_red = prop_red * 1500)
```

### Exercise 9

Use `ggplot()` and `geom_histogram()` to create a histogram that maps our 50 values of `estimated_red` to the x-axis. Set `binwidth` to 75 and `color` to "white".

```{r shovel9, exercise = TRUE}

```


```{r shovel9-hint-1, eval=FALSE}
First copy and paste your previous our code from above
```


```{r shovel9-hint-2, eval=FALSE}
ggplot(mapping = aes(...) + geom_histogram(binwidth= 75, color= "white")
```



### Exercise 10

We can use the `breaks` argument of a `scale_` function, alongside the `seq()` function, to reset the location of the tick marks on either axis. Run the code below to see how we can reset the tick marks on the y-axis to the even numbers from 0 to 20.

```{r shovel11, exercise = TRUE, exercise.lines = 10}
urn %>%
  rep_sample_n(size = 20, reps = 50, replace = TRUE) %>%
  mutate(is_red = (color == "red"), 
         is_white = (color == "white"), 
         .groups = "drop") %>%
  summarize(num_red = sum(is_red), 
            num_white = sum(is_white)) %>%
  mutate(prop_red = num_red / (num_red + num_white)) %>%
  mutate(estimated_red = prop_red * 1500) %>%
  ggplot(mapping = aes(x = estimated_red)) +
    geom_histogram(binwidth = 75, color = "white") +
    scale_y_continuous(breaks = seq(from = 0, to = 20, by = 2))
```


### Exercise 11

Use `scale_x_continuous()` to reset the tick marks on the x-axis to the multiples of 100 between 0 and 1,500. Copy and paste the code from the previous exercise to visualize the adjustment that we made to the y-axis and apply it to this prompt.

```{r shovel12, exercise = TRUE}

```

```{r shovel12-hint, eval = FALSE}
The "by" argument of your seq() function should be 100.
```


### Exercise 12

Great job! By running the code below a few times, we see that the number of red beads in the urn is probably somewhere between 700 and 1,100. 

To finish this graph, use `labs()` to rename the x-axis label to "Estimated number of red beads". Set `reps` equal to 50.



```{r shovel13, exercise = TRUE, exercise.lines = 20}

```


## Different Sample Sizes
###

Imagine we have three choices of shovels to extract a sample of beads with: shovels of size 30, 60, and 120.

Our eventual goal will be to create this graph, which shows the standard deviation in results for our three different shovel sizes. **Remember**: the lower the standard deviation, the more precise our response. 

```{r}
shovels <- tibble(shovel_size = c(30, 60, 120))

shovels <- shovels %>% 
  mutate(use_shovel_results = map(shovel_size,
                                  ~ use_shovel(x = urn,
                                               size = .x,
                                               reps = 1000))) %>% 
  mutate(prop_red_results = map(shovel_size,
                                ~ prop_red(x = urn,
                                            size = .x,
                                            reps = 1000)))
  


shovels_plot <- shovels %>%
 unnest(prop_red_results) %>%   
 ggplot(aes(x = shovel_size, y = prop_red)) +
  geom_point() +
   labs(x = "Shovel size",
        y = "Proportion of red beads")

shovels_plot
```

### Exercise 1

Create the object `virtual_samples_30` by performing `rep_sample_n` on our object `urn` with a size of 30 and reps of 1000. 

```{r map2, exercise = TRUE}

```

```{r map2-hint, eval = FALSE}
virtual_samples_30 <- urn %>%
  rep_sample_n(size = ..., reps = ...)
```


### Exercise 2

To perform the above code three more times, let's create a function called `use_shovel`. This function draws a specified sample size with a specified number of reps. Remember that we want for size and reps to **not** be explicitly declared, so that we may use the function for any shovel size and any number of reps. 

```{r map3-setup}
virtual_samples_30 <- urn %>%
  rep_sample_n(size = 30, reps = 1000)
```

```{r map3, exercise = TRUE}

```

```{r map3-hint-1, eval = FALSE}
use_shovel <- function(x, size, reps){
  x %>% ...
}
```

```{r map3-hint-2, eval = FALSE}
use_shovel <- function(x, size, reps){
  x %>% 
    rep_sample_n(size = size, ...)
}
```

### Exercise 3

To test our function, call `use_shovel` with `(x = urn, size = 30, and reps = 2)`

```{r map4, exercise = TRUE}

```

```{r map4-hint, eval = FALSE}
use_shovel(x = urn, ..., ...)
```

### Exercise 4

Now we need a function that will calculate the proportion of beads that are red. To accomplish this, we will need to use the function `use_shovel` within another function, which we will call `prop_red`. The first line of the function `prop_red` should be `use_shovel` as we have created prior. The next parts should group results by replicate, summarize red for where the `color == "red"`, and use `mutate` to create `prop_red` for the number of red beads divided by size. 


```{r map5, exercise = TRUE}

```

```{r map5-hint-1, eval = FALSE}
prop_red <- function(x, size, reps) {
  use_shovel(x = x, ..., ...) %>% 
  group_by(...) %>% 
  summarize(red = sum(...), .groups = ...) %>% 
  mutate(prop_red = .../size)
}
```

```{r map5-hint-2, eval = FALSE}
Read "Functions are your friend!". The answer can be found there. 
```

### Exercise 5

Now, let's test our new function `prop_red` by drawing from our urn with a size of 30 and 2 repetitions. 

```{r map6, exercise = TRUE}

```

```{r map6-hint, eval = FALSE}
prop_red(x = urn, size = ..., reps = ...)
```


### Exercise 6

Now that we have confirmed that both the `prop_red` and `use_shovel` functions are working properly, let's begin making our graph. 

To construct this graph, we will be using some mapping. This saves us the time of making three different objects (for shovels of 30, 60, and 120). Start by creating the object `shovels` which should construct a `shovel_size` column of 30, 60, and 120. 

```{r map7, exercise = TRUE}

```

```{r map7-hint, eval = FALSE}
shovels <- tibble(shovel_size = c(...))
```

### Exercise 7

We will now modify the object shovels by using a mutate to create the column `use_shovel_results`. `use_shovel_results` should use map `shovel_size` by using our function `use_shovel` with x = urn, size = ., and reps = 1000. If this sounds confusing, make sure you've looked at "Functions are your friends" carefully.

```{r map8, exercise = TRUE}

```

```{r map8-hint, eval = FALSE}
shovels <- shovels %>% 
  mutate(use_shovel_results = map(shovel_size,
                                  ~ use_shovel(x = ...,
                                               size = ...,
                                               reps = ...)
```

### Exercise 8

To add another column, copy the above code and call another mutate to create the column `prop_red_results`. Like our last exercise, we want to use `map` using shovel size, but (this time) with our function `prop_red` to get the proportion of red beads. We will retain the same characteristics for `prop_red` as we did for `use_shovel`: x = urn, size = .x, and reps = 1000.

```{r map9, exercise = TRUE}

```

```{r map9-hint, eval = FALSE}
shovels <- shovels %>% 
  ... %>% 
  mutate(prop_red_results = map(shovel_size,
                                ~ prop_red (...))
```


### Exercise 9 

<!-- DK: Make sure book covers unnnest. -->

Now that we have finished modifying our object `shovels`, let's construct our graph using ggplot! Recall that `shovels`, like any tibble with list columns, may require some manipulation before you can plot it. The key command is often `unnest()`, which splits up the specified column so that each element gets its own row.

Start by calling `shovels` and then calling `unnest` to split up the observations. Look at the resulting tibble so that you understand it. (Hint: There are some new columns.) Then, use ggplot with the `shovel_size` as the x-axis and `prop_red` as the y-axis. Add geom_point. 

```{r map10, exercise = TRUE}

```

```{r map10-hint, eval = FALSE}
shovels %>% 
  unnest(...) %>% 
  ggplot(aes(x = ..., y = ...)) +
  geom_point()
```

### Exercise 10

Fantastic work! To finish this graph, use labs to create a label for the x and y axis. Here is our graph for reference: 

```{r map-final}
shovels_plot
```

```{r map11, exercise = TRUE, exercise.lines = 20}

```


## Standard deviation
###


In the last section, we figured out that an increase in sample size leads to greater precision in the sampling distribution. But how can we mathematically measure this increase in precision? The **standard deviation** of a set of values gives us a mathematical framework for measuring precision---reread chapter 2 in the textbook if you need clarification.

###

### Exercise 1

In the code chunk below, run `sd()` (the function that returns standard deviation) on the vector `c(1, 2, 3, 4, 5)`.

```{r sd1, exercise = TRUE}
sd (c(1, 2, 3, 4, 5))
```

```{r sd1-hint}
# Remember that the vector above is equal to 1:5.
```

### Exercise 2

Now calculate the standard deviation of the vector `c(143, 144, 145, 146, 147)`. See if you can predict what the result will be before you run the code.

```{r sd2, exercise = TRUE}
sd(c(143, 144, 145, 146, 147))
```

```{r sd2-hint, eval = FALSE}
sd(c(...))
```

### Exercise 3

Calculate the standard deviation of the vector `c(2, 3, 4)` and compare the result to the results from the previous two exercises.

```{r sd3, exercise = TRUE}
sd(c(2, 3, 4))
```


### Exercise 4

Finally, calculate the standard deviation of `c(1, 1, 1, 5, 5)` and compare the result to the result of the first exercise.

```{r sd5, exercise = TRUE}
sd(c(1, 1, 1, 5, 5))

```

```{r sd5-hint, eval = FALSE}
sd(c(...))
```

### Exercise 5

Let's recap the `seq()` function. Run the code below to see how we can return all multiples of 3 between 21 and 48.

```{r sd5_2, exercise = TRUE}
seq(from = 21, to = 48, by = 3)
```

### Exercise 6

The code below contains our final work from the previous section, excluding our `ggplot()`.

Because we want to be more precise than the previous exercise, let's see if we can look at shovel sizes from 1 to 100, instead of 30, 60, and 120. Instead of our first line being `shovels` lets start by creating a tibble to redefine `shovel_size` for all values between 1 and 100.



```{r sd6, exercise = TRUE,  exercise.lines = 13}
shovels <- shovels %>% 
  mutate(use_shovel_results = map(shovel_size,
                                  ~ use_shovel(x = urn,
                                               size = .x,
                                               reps = 1000))) %>%
  mutate(prop_red_results = map(shovel_size,
                                ~ prop_red(x = urn, 
                                           size = .x, 
                                           reps = 1000)))
```

```{r sd6-hint, eval = FALSE}
Replace "shovels" with tibble(shovel_size = 1:100)
```

### Exercise 7

Now we will need to use `mutate()` to create a column that takes the standard deviation of the proportion red found from `prop_red_results`. After copying the above work, add the column `prop_red_sd` using `map_dbl` with prop_red_results. After the ~ sign, you will want to pull using (., prop_red) to isolate the proportion red. Finally, you will take the `sd()` of that pulled value.

Save your new work as `shovels_100` instead of the previous `shovels`.

```{r sd7, exercise = TRUE, message = FALSE}

```

```{r sd7-hint, eval = FALSE}
shovels_100 <- tibble(shovel_size = 1:100) %>% 
  mutate(prop_red_sd = map_dbl(prop_red_results,
                               ~ pull(...) %>% ...))
```

### Exercise 8

To visualize what we have created, perform `glimpse()` on `shovels_100`.

```{r sd8, exercise = TRUE, message = FALSE}

```

### Exercise 9

We now have the standard deviation of proportions red for all shovel sizes between 1 and 100. We now want to use `ggplot` to visualize this difference in a `geom_point`. Assign `shovel_size` to the x-axis and `prop_red_sd` to the y-axis. 

```{r sd9, exercise = TRUE, message = FALSE}

```

```{r sd9-hint, eval = FALSE}
shovels_100 <- %>% 
  ggplot(aes(...)) +
  geom_point()
```



## Posterior distribution from sample


###

<!-- MF: This is where I stopped. Will finish before our next meeting. -->


Finally, let's return to our question from the original section: _how can we predict the number of beads in the urn based on the results of a sample_? In the first section, we discovered that the number of red beads in the urn was probably somewhere between 700 and 1,100, but we could not come up with a better estimate. In this section, we will both improve our estimate and better simulate real-world sampling by estimating the number of beads in the urn from the result of a single sample.

Suppose that in a single 45-bead sample from our urn, 28 of the 45 beads are red. Let's use this information to predict the number of beads in the urn.

### Exercise 1 

We're going to start by analyzing a single model: 800 of the 1,500 beads being red. Using `tibble()`, create a tibble with a single column, `color`. `color` should be equal to the combination (`c()`) of "red" 800 times and "white" 700 times. 

```{r posterior1, exercise = TRUE}

```


```{r posterior1-hint-2, eval = FALSE}
tibble(color = c(rep(...), rep(...)))
```

### Exercise 2

Let's now take some samples from our table using `rep_sample_n()`. The first parameter of your `rep_sample_n()` statement should be equal to the tibble that you made in the previous exercise (remember to copy and paste!). Also set the `size` to 45, the `reps` to 1,000 (any reasonably large number works here), and `replace` to "TRUE."

```{r posterior2, exercise = TRUE}

```

```{r posterior2-hint, eval = FALSE}
tibble(...) %>% 
  rep_sample_n(size = ..., reps = ..., replace = ...)
```

### Exercise 3

Pipe what you have into `group_by()` to group the tibble by the `replicate` variable.

```{r posterior3, exercise = TRUE}

```

### Exercise 4

Use `summarize()`to create the variable `red_in_sample`, which should be equal to the `sum()` of the number of rows in each group with `color` equal to "red."

```{r posterior4, exercise = TRUE}

```

```{r posterior4-hint}
sample_given_urn <- function(...) {
  tibble(color = c(rep("red", ...), rep("white", ...))) %>% 
    rep_sample_n(size = 45, reps = 1000, replace = TRUE) %>%
    group_by(replicate) %>%
    summarize(red_in_sample = sum(color == ...), .groups = ...)
}
```

### Exercise 5

We now have code that makes 1,000 random samples from our 800-red-bead urn, but we want to generalize it to urns with other amounts of red beads. To do so, wrap the code above in a function named `sample_given_urn`.  that has one parameter, `red_in_urn`. Replace the 800 in the first `rep()` statement with `red_in_urn` and the 700 in the second `rep()` statement with `red_in_urn` subtracted from 1,500. 

```{r posterior5, exercise = TRUE}

```

```{r posterior5-hint, eval = FALSE}
sample_given_urn <- function(...) {
  tibble(color = c(rep("red", ...), rep("white", ...))) %>% 
    rep_sample_n(size = 45, reps = 1000, replace = TRUE) %>%
    group_by(replicate) %>%
    summarize(red_in_sample = sum(color == "red"), .groups = "drop")
}
```

### Exercise 6

To get a sense of how our function works, call `sample_given_urn()` below the function definition to calculate 1,000 random samples from an urn with 650 red beads.

```{r posterior6, exercise = TRUE, exercise.lines = 7}
sample_given_urn <- function(red_in_urn){
  tibble(color = c(rep("red", red_in_urn), 
                   rep("white", 1500 - red_in_urn))) %>% 
    rep_sample_n(size = 45, reps = 1000, replace = TRUE) %>%
    group_by(replicate) %>%
    summarize(red_in_sample = sum(color == "red"), .groups = "drop")
}
```

### Exercise 7

Now, below the function definition, call `tibble()` to create a new tibble with one column, `nums`, equal to the vector containing every multiple of 25 `from` 650 `to` 1,150.


```{r posterior7, exercise = TRUE, exercise.lines = 7}
sample_given_urn <- function(red_in_urn){
  tibble(color = c(rep("red", red_in_urn), 
                   rep("white", 1500 - red_in_urn))) %>% 
    rep_sample_n(size = 45, reps = 1000, replace = TRUE) %>%
    group_by(replicate) %>%
    summarize(red_in_sample = sum(color == "red"), .groups = "drop")
}
```

```{r posterior7-hint, eval = FALSE}
tibble(nums = seq(...))
```

### Exercise 8

Pipe your tibble into a `mutate()` statement to create the new variable `sample_results`. `sample_results` should be equal to the result of a `map()` statement whose first parameter is `nums` and whose second parameter is `sample_given_urn(nums)`. Don't worry about the error for the time being.

```{r posterior8, exercise = TRUE}

```

### Exercise 9

To fix the error from our `map()` statement, remember the two rules of using `map()`: replace `nums` with `.x` in `sample_given_urn()`, and precede `sample_given_urn()` with the `~` symbol.

```{r posterior9, exercise = TRUE}

```

### Exercise 10

Nice job! Unfortunately, we are now left with a list column. Just as we did in the previous sections, pipe the tibble into `unnest()` to convert the list column into a standard tibble. Set the `cols` argument of `unnest()` equal to `sample_results`.

```{r posterior10, exercise = TRUE}

```

### Exercise 11

Continuing your pipe, group the tibble by `nums`. Then use `summarize()` to create the variable `num_samples`, which should be equal to the `sum()` of the number of rows in each group with `red_in_sample` equal to 28.

```{r posterior11, exercise = TRUE, exercise.lines = 11}
sample_given_urn <- function(red_in_urn){
  tibble(color = c(rep("red", red_in_urn), 
                   rep("white", 1500 - red_in_urn))) %>% 
    rep_sample_n(size = 45, reps = 1000, replace = TRUE) %>%
    group_by(replicate) %>%
    summarize(red_in_sample = sum(color == "red"), .groups = "drop")
}

tibble(nums = seq(from = 650, to = 1150, by = 25)) %>%
  mutate(sample_results = map(nums, ~ sample_given_urn(.x))) %>%
  unnest(cols = sample_results)
```



### Exercise 12

Pipe the tibble into `ggplot()` to create a bar graph that maps `nums` to the x-axis and `num_samples` to the y-axis.

```{r posterior13, exercise = TRUE}

```

```{r posterior13-hint, eval = FALSE}
Remember to use geom_col().
```

### Exercise 13

Normalize the distribution by changing the y-axis mapping from `num_samples` to `num_samples` divided by the `sum()` of all `num_samples`. In addition, because the probabilities are so small, multiply `num_samples` by 100 before you divide by the `sum()` so we get percents instead of decimal probabilities.

```{r posterior14, exercise = TRUE}

```

```{r posterior14-hint, eval = FALSE}
ggplot(mapping = aes(x = nums, y = ... * ... / sum(...)))
```


### Exercise 14

Fantastic job! From this graph, we can see that the most likely outcome for the number of red beads in the urn is between 900 and 975. Notably, though, there is a *ton* of variance in the outcome: the probability that the number of red beads is between 900 and 950 is only about 30%. The major lesson here is that a single small sample is not very predictive---you need either many samples or a very large sample size to be confident in your estimate.

To finish off this tutorial, you probably want to know how many red beads are actually in the urn. Below the `ggplot()`, pipe `urn` into a `count()` statement that takes `color` as its argument.

```{r posterior17, exercise = TRUE, exercise.lines = 20}
sample_given_urn <- function(red_in_urn){
  tibble(color = c(rep("red", red_in_urn), 
                   rep("white", 1500 - red_in_urn))) %>% 
    rep_sample_n(size = 45, reps = 1000, replace = TRUE) %>%
    group_by(replicate) %>%
    summarize(red_in_sample = sum(color == "red"), .groups = "drop")
}

tibble(nums = seq(from = 650, to = 1150, by = 25)) %>%
  mutate(sample_results = map(nums, ~ sample_given_urn(.x))) %>%
  unnest(cols = sample_results) %>%
  group_by(nums) %>%
  summarize(num_samples = sum(red_in_sample == 28), .groups = "drop") %>%
  ggplot(mapping = aes(x = nums, y = 100 * num_samples / sum(num_samples))) +
    geom_col() +
    scale_x_continuous(breaks = seq(from = 650, to = 1150, by = 50)) +
    labs(title = "Posterior Probability Distribution of Red Beads in Urn",
         subtitle = "Based on a 45-bead sample with 28 red beads",
         x = "Number of red beads",
         y = "Probability (percent)")
```

```{r posterior17-hint, eval = FALSE}
urn %>%
  count(...)
```


## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```

