---
title: "One Parameter"
tutorial:
  id: "one-parameter"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 6 tutorial"
---

<!-- Make it more like the chapter, and the chapter more like it. -->

<!-- Need one more section which using the posterior to, for example, create the posterior of number red which will be drawn with a shovel of size 20. Use a posterior to create a new posterior. Turtles all the way down. Could also create the plot of the joint distribution. Try to teach again just what a joint distribution. -->

<!-- Maybe make the shovels_100 have 100 shovel sizes again? We cut that down to make it quicker, but maybe having 100 reps instead of a 1,000 was enough to solve our speed problem. -->

<!-- Should we do something with stan_glm? Probably not. -->


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(skimr)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

# Key Data

set.seed(10)
urn <- tibble(color = c(rep("red", 400), rep("white", 600))) %>%
  sample_frac() %>% 
  mutate(ID = 1:1000) %>% 
  select(ID, color)

virtual_samples <- tibble(ID = 1:1000) %>% 
  mutate(shovel = map(ID, ~ sample_n(urn, size = 50))) %>% 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) %>% 
  mutate(numb_beads = map_int(shovel, ~ length(.$color))) %>% 
  mutate(prop_red = numb_red / numb_beads)

make_prop_red <- function(x, shovel_size, reps){
  tibble(ID = 1:reps) %>% 
    mutate(shovel = map(ID, ~ sample_n(x, size = shovel_size))) %>% 
    mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) %>% 
    mutate(numb_beads = map_int(shovel, ~ length(.$color))) %>% 
    mutate(prop_red = numb_red / numb_beads)
}
```

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```


## Virtual sampling
###

Let's create the following plot that shows sampling variation for 1000 samples from an urn that contains red and white beads.

```{r virts_p}
virt_p <- virtual_samples %>% 
  ggplot(aes(x = prop_red)) +
    geom_histogram(binwidth = 0.01, 
                   boundary = 0.4, 
                   color = "white") +
    labs(x = expression(hat(p)), 
         y = "Count",
         title = "Distribution of 1,000 proportions red") 

virt_p
```

### Exercise 1

Type `urn` below to inspect the urn we will be using in this section.

```{r shovel1, exercise = TRUE}
set.seed(10)
urn <- tibble(color = c(rep("red", 400), rep("white", 600))) %>%
  sample_frac() %>% 
  mutate(ID = 1:1000) %>% 
  select(ID, color)
```

### Exercise 2

To simulate the process of real-world sampling, let’s take a sample of 50 beads from our virtual urn. To do so, start a pipe by creating a `tibble()` that has one variable `ID` that takes on the values 1 to 1000.

```{r shovel2, exercise = TRUE}

```

```{r shovel2-hint, eval = FALSE}
tibble(ID = ...)
```

### Exercise 3

Great. Now pipe your results to the function `mutate()` to create the variable `shovel`, which is set to the function `map()`. The first argument to `map()` should be `ID`. The second argument should use `sample_n()` to take a sample `size` 50 beads from `urn`.

```{r shovel3, exercise = TRUE}

```

```{r shovel3-hint, eval = FALSE}
tibble(ID = 1:1000) %>% 
  mutate(shovel = map(..., ~ sample_n(urn, size = ...)))
```

### Exercise 4

Continue your pipe with `mutate()` to create the variable `numb_red`, which will tells us the number of red beads present. Set `numb_red` to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `sum()` of where the column `color` of `shovel` is equal to red.

```{r shovel4, exercise = TRUE}

```

```{r shovel4-hint, eval = FALSE}
... %>% 
  mutate(... = map_int(..., ~ sum(.$color == "red")))
```

### Exercise 5

Great. Now use `mutate()` to create the variable `numb_beads`, which is set to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `length()` of the column `color` of `shovel`.
 

```{r shovel5, exercise = TRUE}

```

```{r shovel5-hint-1, eval = FALSE}
... %>% 
  mutate(numb_beads = map_int(..., ~ length(...)))
```

```{r shovel5-hint-2, eval = FALSE}
... %>% 
  mutate(numb_beads = map_int(..., ~ length(.$color)))
```

### Exercise 6

Use `mutate()` one last time to create the variable `prop_red`, which is our estimate of the proportion of red beads in the urn. Set `prop_red` to `numb_red` divided by `numb_beads`.

```{r shovel6, exercise = TRUE}

```

```{r shovel6-hint, eval = FALSE}
... %>% 
   mutate(prop_red = ... / ...)
```

### Exercise 7

Copy/paste your code from above. Assign your code to an object named `virtual_samples`.

```{r shovel7, exercise = TRUE}

```

```{r shovel7-hint, eval = FALSE}
Use the assignment operator <-  to do so.
```

### Exercise 8

Awesome. Now start a pipe with `virtual_samples`. Use `ggplot()`to map `prop_red` to the x-axis. Also, add the layer `geom_histogram()` to create a histogram of our data.

```{r shovel8, exercise = TRUE}

```


```{r shovel8-hint-1, eval = FALSE}
virtual_samples %>% 
  ggplot(aes(...)) + 
  geom_histogram()
```

### Exercise 9

Within `geom_histrogram()` set `binwidth` to .01, `boundary` to .4, and `color` to "white".

```{r shovel9, exercise = TRUE}

```

```{r shovel9-hint, eval = FALSE}
... +
  geom_histrogram(..., ..., ...)
```

### Exercise 10

To finish, use `labs()` to give your graph the appropriate title and axis labels. See **hint** for guidance to create the symbol $\hat{p}$.


```{r shovel10, exercise = TRUE}

```

Reminder: This is what your plot should look like. 

```{r}
virt_p
```

```{r shovel10-hint, eval = FALSE}
Within labs(), set x to expression(hat(p))
```


## Different shovel sizes
###

Let's create the following plot that displays different standard deviations of red bead proportions for 100 different shovels.

```{r}
shovel_sizes <- c(2, 5, 10, 25, 50, 100)

shovels_100 <- tibble(shovel_size = shovel_sizes) %>%
  mutate(prop_red_results = map(shovel_size,
                                ~ make_prop_red(x = urn, 
                                           shovel_size = .x, 
                                           reps = 100))) %>% 
  mutate(prop_red_sd = map_dbl(prop_red_results, 
                               ~ pull(., prop_red) %>% sd()))

shovel_p <- shovels_100 %>%
 ggplot(aes(x = shovel_size, y = prop_red_sd)) +
 geom_point() +
 stat_function(aes(x = shovel_sizes, color = "red"), 
               fun = function(.x) 1/(2 * sqrt(.x)), 
               show.legend = FALSE) +
 labs(x = "Shovel size",
      y = "Standard deviation of the proportion red")

shovel_p
```

### Exercise 1

Before we begin, write two sentences explaining standard error.

```{r map0, exercise = TRUE}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```


### Exercise 2

Let's create a function that calculates the proportion of red beads. We start with hard code. Recall our code for  `virtual_samples` in the previous section. Place the code within { } of `function()`. Name the function `make_prop_red()`.

```{r map1, exercise = TRUE}
tibble(ID = 1:1000) %>% 
  mutate(shovel = map(ID, ~ sample_n(urn, size = 50))) %>% 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) %>% 
  mutate(numb_beads = map_int(shovel, ~ length(.$color))) %>% 
  mutate(prop_red = numb_red / numb_beads)
```

```{r map1-hint, eval = FALSE}
make_prop_red <- function(){
  
  ...
  
}

```

### Exercise 3

Copy/paste your code from above. Add the parameter `reps` within `function()`. Also replace the value 1000 within `tibble()` with `reps`.

```{r map2, exercise = TRUE}

```

```{r map2-hint-1, eval = FALSE}
make_prop_red <- function(...){
  tibble(ID = 1:reps) %>% 
    ...
}
```

### Exercise 4

Copy/paste your code from above. Add the parameter `x` within `function()`. Also replace the argument `urn` with `x` within `sample_n()`.

```{r map3, exercise = TRUE}

```

```{r map3-hint, eval = FALSE}
make_prop_red <- function(reps, ...){
  tibble(ID = 1:reps) %>% 
  mutate(shovel = map(ID, ~ sample_n(x, size = 50))) %>% 
    ...
}
```

### Exercise 5

Copy/paste your code from above. Add the parameter `shovel_size` within `function()`. Also set `size` to `shovel_size` within `sample_n()`.

```{r map4, exercise = TRUE}

```

```{r map4-hint-1, eval = FALSE}
make_prop_red <- function(reps, x, ...){
  tibble(ID = 1:reps) %>% 
  mutate(shovel = map(ID, ~ sample_n(x, size = ...))) %>% 
    ...
}
```

### Exercise 6

Great. Let's now create a `tibble()` with one variable `shovel_size`, which takes on the values 2, 5, 10, 25, 50 and 100. 

```{r map5, exercise = TRUE}

```

```{r map5-hint, eval = FALSE}
tibble(shovel_size = ...)
```

### Exercise 7

Pipe your results to `mutate()` to create the variable `prop_red_results`, which is set to the function `map()`.The first argument to `map()` should be `shovel_size`. The second argument should be our function `make_prop_red()` where `x` is set to `urn`, `shovel_size` set to `.x`, and `reps` set to 100.
 

```{r map6, exercise = TRUE}

```

```{r map6-hint, eval = FALSE}
... %>% 
  mutate(prop_red_results = map(...,
                                ~ make_prop_red(..., ..., ...)))
```

### Exercise 8

Use `mutate()` once more to create the variable `prop_red_sd`, which is set to the function `map_dbl()`. The first argument to `map_dbl()` should be `prop_red_results`. The second argument should be `pull()`. The first argument to `pull()` should be `.`. The second argument should be `prop_red`.

```{r map7, exercise = TRUE}

```

```{r map7-hint, eval = FALSE}
... %>% 
mutate(... = map_dbl(..., 
                      ~ pull(., prop_red))
```

### Exercise 9

Use `mutate()` once more to create the variable `prop_red_sd` which is set to the function `map_dbl()`. The first argument to `map_dbl()` should be `prop_red_results`. The second argument should be `pull()`. The first argument to `pull()` should be `.`. The second argument should be `prop_red`.

```{r map8, exercise = TRUE}

```

```{r map8-hint, eval = FALSE}
... %>% 
  mutate(prop_red_sd = map_dbl(..., 
                               ~ pull(., prop_red) %>% sd()))
```

### Exercise 10

Let's find the standard deviation of proportions red for our shovel sizes. Pipe the results of `pull()` to the function `sd()`. **Note**: You are still inside `map_dbl()`.

```{r map9, exercise = TRUE}

```

```{r map9-hint, eval = FALSE}
mutate(prop_red_sd = map_dbl(prop_red_results, 
                               ~ pull(., prop_red) %>% ...)
```

### Exercise 11

Copy/paste your code from above. Assign your code to an object named `shovels_100`. 

```{r map10, exercise = TRUE}

```

### Exercise 12

Start a pipe with `shovels_100`. Use `ggplot()` to map `shovel_size` to the x-axis and `prop_red_sd` to the y-axis. Also add the layer `geom_point()`.

```{r map11-y, exercise = TRUE}

```

```{r map11-y-hint, eval = FALSE}
... %>% 
  ggplot(aes(x = ..., y = ...)) +
 geom_point() 
```

### Exercise 13

Add the layer `stat_function()`. Map the values of our shovel sizes to the x-axis. Also set `color` to "red".

```{r map12, exercise = TRUE}

```

```{r map12-hint, eval = FALSE}
... + 
  stat_function(aes(x = ..., ...))
```

### Exercise 14

Also set `fun` to `function(.x) 1/(2 * sqrt(.x))` within `stat_function()`.Also set `show.legend` to FALSE.

```{r map13, exercise = TRUE}

```

```{r map13-hint, eval = FALSE}
... + 
  stat_function(aes(x = c(2, 5, 10, 25, 50, 100), color = "red"), 
               fun = ..., 
               show.legend = ...) 
```

### Exercise 15

Great. Now use `labs()` to label the x-axis "Shovel size" and the y-axis 
"Standard deviation of the proportion red". 

```{r map14, exercise = TRUE}

```

Reminder: This is what your plot should look like.

```{r}
shovel_p
```

```{r map14-hint, eval = FALSE}

```


## Posterior Distribution
###


Let's create the following plot showing the posterior probability distribution of the proportion, $p$, of red beads in the urn.

```{r}
joint_dist <- 
  tibble(red_in_urn = seq(from = 0, to = 1000, by = 1)) %>% 
    mutate(p = red_in_urn / nrow(urn)) %>% 
    mutate(red_in_paddle = map(p, ~ rbinom(n = 100, 
                                               size = 50, 
                                               prob = .))) %>%
    unnest(red_in_paddle) 

posterior_p <- joint_dist %>% 
  filter(red_in_paddle == 17) %>% 
  ggplot(aes(x = p)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 50) + 
    labs(title = "Posterior Probability Distribution",
         subtitle = "Proportion of red beads in urn is centered around 0.34",
         x = "Proportion p of Red Beads in Urn",
         y = "Probability") + 
    scale_x_continuous(labels = scales::number_format()) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()

posterior_p
```

### Exercise 1

Create a `tibble()` with one variable `red_in_urn` that is set to the function `seq()`. Within `seq()` set `from` to 0, `to` to 1000, and `by` to 1.

```{r pp1, exercise = TRUE}

```

```{r pp1-hint, eval = FALSE}
tibble(red_in_urn = seq(...,...,...))
```

### Exercise 2

Great. Now pipe your results to the function `mutate()` to create the variable `p`, which is set to the `red_in_urn` divided by the `nrow(urn)`.

```{r pp2, exercise = TRUE}

```

```{r pp2-hint, eval = FALSE}
... %>% 
    mutate(p = ... / ...) 
```

### Exercise 3

Great. Now pipe your results to the function `mutate()` to create the variable `red_in_paddle`, which is set to the function `map()`. The first argument to `map()` should be `p`. The second argument should use `rbinom()`. Within `rbinom()` set `n` to 100, `size` to 50, and `prob` to `.`

```{r pp3, exercise = TRUE}

```

```{r pp3-hint, eval = FALSE}
... %>% 
    mutate(red_in_paddle = map(..., ~ rbinom(..., 
                                             ..., 
                                              ...)))
```

### Exercise 4

Continue your pipe with the function `unnest()` with the argument `red_in_paddle`. **Note**: unnesting flattens list columns back into regular columns.

```{r pp4, exercise = TRUE}

```

```{r pp4-hint, eval = FALSE}
... %>%
    unnest(...) 
```

### Exercise 5

Copy/paste your code from above. Assign your code to an object named `joint_dist`.

```{r pp5, exercise = TRUE}

```

### Exercise 6

Copy/paste your code from above. Assign your code to an object named `joint_dist`.

```{r pp6, exercise = TRUE}

```

```{r pp6-hint, eval = FALSE}

```

### Exercise 7

Let's plot our joint distribution we just created. Start a pipe with `joint_dist` and `filter()` where `red_in_paddle` is equal to 17.

```{r pp7, exercise = TRUE}

```

```{r pp7-hint, eval = FALSE}
...%>% 
  filter(red_in_paddle == ...)
```

### Exercise 8

Continue your pipe with `ggplot()`to map `p` to the x-axis. Also, add the layer `geom_histogram()`.

```{r pp8, exercise = TRUE}

```

```{r pp8-hint, eval = FALSE}
...%>% 
  ggplot(aes(...)) +
    geom_histogram()
```

### Exercise 9

Within `geom_histogram()`, use `after_stat()` . Inside `after_stat()`, use `aes()` with the argument `y = count/sum(count)` to convert the y-axis to percent values.

```{r pp9, exercise = TRUE}

```

```{r pp9-hint, eval = FALSE}
...%>% 
    geom_histogram(aes(y = after_stat(...))
```

### Exercise 10

Add the layer `scale_x_continuous()` with the argument `labels` set to `scales::number_format()`.

```{r pp10, exercise = TRUE}

```

```{r pp10-hint, eval = FALSE}
...%>% 
   scale_x_continuous(labels = ...)
```

### Exercise 11

Great. Now add the layer `scale_y_continuous()` with the argument `labels` set to `scales::percent_format()`.

```{r pp11, exercise = TRUE}

```

```{r pp11-hint, eval = FALSE}
...%>% 
   scale_y_continuous(labels = ...)
```

### Exercise 12

To finish, use `labs()` to give your graph the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.


```{r pp12, exercise = TRUE}

```

Reminder: This is what your plot should look like. 

```{r}
posterior_p
```

## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```

