---
title: "Recruits: Courage"
author: David Kane
tutorial:
  id: 05-recruits-courage
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: "Tutorial #05 (Courage) for Preceptor's Primer"
---

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(gt)

library(tidyverse)
library(tidymodels)
library(primer.tutorials)
library(broom)

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(out.width = "90%")
options(tutorial.exercise.timelimit = 600,
        tutorial.storage = "local")

fit_recruits <- linear_reg() |>
  set_engine("lm") |>
  fit(height ~ sex, data = recruits)
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```


## Introduction
###

This tutorial supports the [Recruits](https://ppbds.github.io/primer/05-recruits.html) chapter of [*Preceptor's Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/).

The world confronts us. Make decisions we must.

Imagine that you are a logistics analyst at U.S. Marine Corps Supply, planning next year's bootcamp uniform order. The Quartermaster General has a big-picture goal --- every recruit kitted out at the right size on day one, within a fixed procurement budget --- and trusts you to figure out what to order and in what quantities. Many models would inform the order: distributions of height, weight, chest, foot length; the male-female mix in incoming recruits; the size-tail dynamics that drive how many extra-large uniforms to keep in inventory. This tutorial builds just one of them: the average height of male and female recruits. The number alone won't determine the order, but the height-by-sex split is one good input to the larger forecast. There are many decisions to make.

###

This is the third of four Recruits tutorials, one per Cardinal Virtue. **Wisdom** produced the question --- *What is the average height of male and female USMC recruits next year?* --- along with the Preceptor Table and a look at the data. **Justice** audited the assumptions behind the project and chose the functional form of the model: linear, with normally distributed errors. **Courage**, here, builds the data generating mechanism itself.

Here is the Preceptor Table from Wisdom --- the smallest table such that, if every cell were filled in, the question would be easy to answer:

```{r}
#| echo: false
#| results: asis
pre_tibble_recap <- tibble::tribble(
  ~`Recruit`,       ~`Height (cm)`, ~`Sex`,
  "Maya Castillo",  "150",          "Female",
  "Tyler Brooks",   "170",          "Male",
  "...",            "...",          "...",
  "Grace Sullivan", "160",          "Female"
)

pre_title_footnote_recap     <- "A Preceptor Table is the smallest table such that, if every cell were filled with its true value, answering the question 'What is the average height of male and female USMC recruits?' would be easy."
pre_units_footnote_recap     <- "Each row is one USMC recruit expected to enlist during the coming year. Missing rows represent the other recruits not shown."
pre_outcome_footnote_recap   <- "Height in centimeters, measured at enlistment."
pre_covariate_footnote_recap <- "Sex, taking values 'Male' or 'Female', as recorded at enlistment."

pre_gt_html_recap <- gt::gt(pre_tibble_recap, id = "preceptor_tbl_courage") |>
  gt::tab_header(title = "Preceptor Table") |>
  gt::tab_spanner(label = "Unit",      id = "unit_span",
                  columns = c(`Recruit`)) |>
  gt::tab_spanner(label = "Outcome",   id = "outcome_span",
                  columns = c(`Height (cm)`)) |>
  gt::tab_spanner(label = "Covariate", id = "covariates_span",
                  columns = c(`Sex`)) |>
  gt::cols_align(align = "left" , columns = c(`Recruit`, `Sex`)) |>
  gt::cols_align(align = "right", columns = c(`Height (cm)`)) |>
  gt::fmt_markdown(columns = gt::everything()) |>
  gt::tab_options(
    heading.title.font.size   = "1.5em",
    heading.title.font.weight = "bolder",
    column_labels.font.weight = "normal"
  ) |>
  gt::tab_style(
    style     = gt::cell_text(weight = "bold"),
    locations = gt::cells_column_spanners()
  ) |>
  gt::tab_style(
    style     = gt::cell_text(align = "left"),
    locations = gt::cells_column_spanners(spanners = c("unit_span", "covariates_span"))
  ) |>
  gt::tab_style(
    style     = gt::cell_text(align = "right"),
    locations = gt::cells_column_spanners(spanners = "outcome_span")
  ) |>
  gt::tab_footnote(footnote = pre_title_footnote_recap,
                   locations = gt::cells_title()) |>
  gt::tab_footnote(footnote = pre_units_footnote_recap,
                   locations = gt::cells_column_spanners(spanners = "unit_span")) |>
  gt::tab_footnote(footnote = pre_outcome_footnote_recap,
                   locations = gt::cells_column_spanners(spanners = "outcome_span")) |>
  gt::tab_footnote(footnote = pre_covariate_footnote_recap,
                   locations = gt::cells_column_spanners(spanners = "covariates_span")) |>
  gt::opt_css(
    css = "
      #preceptor_tbl_courage .gt_footnote {
        max-width: 1px;
        word-break: break-word;
      }
    "
  ) |>
  gt::as_raw_html(inline_css = FALSE)

cat(
  "```{=html}\n",
  '<div style="display: inline-block; width: auto; max-width: 100%;">',
  pre_gt_html_recap,
  "</div>\n",
  "```\n",
  sep = ""
)
```

The data you have is never the thing you care about. The data is a shadow cast by some underlying process --- the *data generating mechanism* --- and it is the process you actually want to understand. Our `recruits` sample is one such shadow.

### Exercise 1

You should be connected to a repo named `recruits`, with an `analysis.qmd` you have been building through the Wisdom and Justice tutorials. If you are starting fresh here: create the repo and connect to it, create a Quarto document titled `"Recruits"` with yourself as author, save it as `analysis.qmd`, put `library(tidyverse)`, `library(tidymodels)`, `library(primer.tutorials)`, and `library(broom)` in a setup chunk with `#| message: false`, add

```
execute:
  echo: false
```

to the YAML header, render, and open `analysis.html` with Live Server.

In the R Terminal, run `show_file("analysis.qmd", chunk = "setup")`. CP/CR.

```{r introduction-1}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 6)
```

###

The `recruits` tibble is a 50-row teaching cut of NHANES: 40 male and 10 female young adults aged 18--27, with columns `height` (centimeters), `sex`, and `age`. The deliberately uneven 40/10 split will matter when we get to the precision of the two group means in Temperance.

### Exercise 2

Add a code chunk to `analysis.qmd` that prints the `recruits` tibble (just `recruits` on its own line). Render. Copy the first few rows from the rendered HTML below.

```{r introduction-2}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 6)
```

###

Each row is one young adult, examined once. `height` is measured directly by an examiner; `sex` is recorded as Male or Female; `age` is in whole years. These 50 rows are the data --- the shadow. Courage's job is to write down a guess at the mechanism that cast it.


## Courage
###

Justice gives us the Population Table and the abstract data generating mechanism.

```{r}
#| echo: false
#| results: asis
pop_tibble_c <- tibble::tribble(
  ~Source    , ~`Young Adult`    , ~`Year`, ~`Height (cm)`, ~`Sex`   ,
  "..."      , "..."             , "..."  , "..."         , "..."    ,
  "Data"     , "Emily Tran"      , "2002" , "162"         , "Female" ,
  "Data"     , "James Okafor"    , "2005" , "178"         , "Male"   ,
  "Data"     , "..."             , "..."  , "..."         , "..."    ,
  "Data"     , "Tyler Brooks"    , "2024" , "170"         , "Male"   ,
  "..."      , "..."             , "..."  , "..."         , "..."    ,
  "Preceptor", "Maya Castillo"   , "2026" , "150"         , "Female" ,
  "Preceptor", "Tyler Brooks"    , "2026" , "170"         , "Male"   ,
  "Preceptor", "..."             , "..."  , "..."         , "..."    ,
  "Preceptor", "Grace Sullivan"  , "2026" , "160"         , "Female" ,
  "..."      , "..."             , "..."  , "..."         , "..."
)

pop_title_footnote_c     <- "This table combines NHANES adult-height data from 1999 onward with the Preceptor Table's 2026 USMC recruits, drawn from the same broader population of US young adults aged 18--27."
pop_units_footnote_c     <- "Each row is one young adult at one point in time. Data rows are NHANES survey participants between the ages of 18 and 27. Preceptor rows are the ~5,000 USMC recruits expected to enlist in the coming year. Tyler Brooks appears in both blocks."
pop_outcome_footnote_c   <- "Height in centimeters. NHANES measures height directly in the Mobile Examination Center; USMC records height at enlistment."
pop_covariate_footnote_c <- "Sex, recorded as Male or Female in both data sources."

pop_gt_html_c <- gt::gt(pop_tibble_c, id = "population_tbl_courage") |>
  gt::tab_header(title = "Population Table") |>
  gt::tab_spanner(label = "Unit/Time", id = "unit_span",
                  columns = c(`Young Adult`, `Year`)) |>
  gt::tab_spanner(label = "Outcome"  , id = "outcome_span",
                  columns = c(`Height (cm)`)) |>
  gt::tab_spanner(label = "Covariate", id = "covariates_span",
                  columns = c(`Sex`)) |>
  gt::cols_align(align = "left" , columns = c(`Source`, `Young Adult`, `Sex`)) |>
  gt::cols_align(align = "right", columns = c(`Year`, `Height (cm)`)) |>
  gt::fmt_markdown(columns = gt::everything()) |>
  gt::tab_options(
    heading.title.font.size   = "1.5em",
    heading.title.font.weight = "bolder",
    column_labels.font.weight = "normal"
  ) |>
  gt::tab_style(
    style     = gt::cell_text(weight = "bold"),
    locations = gt::cells_column_spanners()
  ) |>
  gt::tab_style(
    style     = gt::cell_text(align = "left"),
    locations = gt::cells_column_spanners(spanners = c("unit_span", "covariates_span"))
  ) |>
  gt::tab_style(
    style     = gt::cell_text(align = "right"),
    locations = gt::cells_column_spanners(spanners = "outcome_span")
  ) |>
  gt::tab_footnote(footnote = pop_title_footnote_c,
                   locations = gt::cells_title()) |>
  gt::tab_footnote(footnote = pop_units_footnote_c,
                   locations = gt::cells_column_spanners(spanners = "unit_span")) |>
  gt::tab_footnote(footnote = pop_outcome_footnote_c,
                   locations = gt::cells_column_spanners(spanners = "outcome_span")) |>
  gt::tab_footnote(footnote = pop_covariate_footnote_c,
                   locations = gt::cells_column_spanners(spanners = "covariates_span")) |>
  gt::opt_css(
    css = "
      #population_tbl_courage .gt_footnote {
        max-width: 1px;
        word-break: break-word;
      }
    "
  ) |>
  gt::as_raw_html(inline_css = FALSE)

cat(
  "```{=html}\n",
  '<div style="display: inline-block; width: auto; max-width: 100%;">',
  pop_gt_html_c,
  "</div>\n",
  "```\n",
  sep = ""
)
```

$$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \cdots + \beta_n X_n + \epsilon$$

with $\epsilon \sim N(0, \sigma^2)$.

### Exercise 1

In your own words, describe the components of the virtue of Courage for analyzing data.

```{r courage-1}
question_text(NULL,
  message = "Courage creates the data generating mechanism.",
  answer(NULL, correct = TRUE),
  allow_retry = FALSE,
  incorrect = NULL,
  rows = 5)
```

###

Building a model of the data generating mechanism takes three steps, and none of them has anything to do with software.

First, **propose a structure**. What kind of outcome does the mechanism produce? The distribution of the outcome variable determines the structure of the DGM. A mechanism that produces numerical heights is a fundamentally different machine from one that produces pass/fail results.

Second, **choose a method** for learning about the mechanism from data --- your philosophy of estimation. Will you seek the single version of the machine that best fits the data, or keep a whole collection of plausible versions?

Third, **fit the DGM**. Your structure is really a family of machines --- regressions with every conceivable slope and intercept. Fitting means using the data to work out which settings are most plausible.

**Structure &rarr; Method &rarr; Fitting.** That three-word chain is the discipline of the whole enterprise.

###

The abstract data generating mechanism shown in the preamble uses generic variables --- $Y$, $X_1$, $X_2$, and so on --- because its purpose is to describe the general mathematical structure. At the end of Justice we chose the functional family (linear with normal errors), but not the number or identity of the covariates we will ultimately include. Courage fills in the missing pieces.

### Exercise 2

Because our outcome variable is continuous, add a code chunk to `analysis.qmd` that begins building the model with `linear_reg(engine = "lm")`. Render. In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r courage-2}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 5)
```

###

```{r courage-2-test}
#| echo: true
linear_reg(engine = "lm")
```

###

`linear_reg()` is step one: it announces the **structure**, proposing that heights are centered on a value that shifts with the covariates, plus random noise. If our outcome recorded pass/fail instead, the same substantive question would demand a different machine.

`engine = "lm"` is step two, the **method**: R's classical least-squares machinery, which returns the single best-fitting version of the mechanism. The structure and the method are kept separate on purpose, because the DGM (the truth out there) and our procedure for estimating it (the tool in here) are separate things.

### Exercise 3

Extend the chunk in `analysis.qmd` to `linear_reg(engine = "lm") |> fit(height ~ sex, data = recruits)`. This is our first candidate model: outcome on the binary `sex`. Render. In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r courage-3}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 5)
```

###

```{r courage-3-test}
#| echo: true
linear_reg(engine = "lm") |>
  fit(height ~ sex, data = recruits)
```

###

`fit()` is step three, where the mechanism meets real data. You hand it a formula and the data, and the engine estimates the parameters --- the numerical settings of the proposed machine that best explain the shadow you have.

A two-level character variable like `sex` is turned into a 0/1 "dummy" variable, renamed `sexMale` (the level for which the dummy is 1). Math doesn't speak text; dummies do the translation.

### Exercise 4

Here is the parameter table for this candidate model:

```{r}
#| echo: false
linear_reg() |>
  set_engine("lm") |>
  fit(height ~ sex, data = recruits) |>
  tidy(conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high) |>
  mutate(across(where(is.numeric), \(x) round(x, 1)))
```

Write a sentence interpreting the `sexMale` estimate of 8.9.

```{r courage-4}
question_text(NULL,
  message = "When we compare two groups of recruits differing only in sex, the male group has an expected height about 8.9 centimeters taller than the female group. The intercept of 165.9 is the expected height of a female recruit; adding `sexMale` (= 1 for male) gives the expected male height of about 174.8 cm.",
  answer(NULL, correct = TRUE),
  allow_retry = FALSE,
  incorrect = NULL,
  rows = 6)
```

###

Notice the language: *"when we compare two groups,"* not *"raising sex by one unit increases height."* For a binary covariate the comparison framing is the only honest reading. The 95% confidence interval for `sexMale` is [4.3, 13.4] centimeters; zero is well outside that interval, so the model says the *expected* height of male recruits is taller than the expected height of female recruits. That does not mean every male is taller than every female --- the two distributions overlap.

### Exercise 5

Change the formula to `fit(height ~ age, data = recruits)`. This refits with `age`, a continuous covariate, instead of `sex`. Render. In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r courage-5}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 5)
```

###

```{r courage-5-test}
#| echo: true
linear_reg(engine = "lm") |>
  fit(height ~ age, data = recruits)
```

###

Continuous covariates produce a single slope coefficient. The reading is a per-unit comparison: how much do two groups, differing by one unit of the covariate, differ in expected outcome?

### Exercise 6

Here is the parameter table for the second candidate model:

```{r}
#| echo: false
linear_reg() |>
  set_engine("lm") |>
  fit(height ~ age, data = recruits) |>
  tidy(conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high) |>
  mutate(across(where(is.numeric), \(x) round(x, 1)))
```

Write a sentence interpreting the slope on `age`.

```{r courage-6}
question_text(NULL,
  message = "The slope on `age` is essentially zero (0.0 cm per year, with a 95% confidence interval that crosses zero in both directions). When we compare two groups of recruits differing by one year of age (within our 18--27 window), their expected heights are indistinguishable. Adult height has stopped changing by the late teens; this fit confirms that.",
  answer(NULL, correct = TRUE),
  allow_retry = FALSE,
  incorrect = NULL,
  rows = 6)
```

###

There is no single "correct" DGM for a given question. Which right-hand-side variables to include is a judgment call --- one we make, and could remake. We tried `age`, and its wide confidence interval, straddling zero in both directions, is exactly what *"this covariate doesn't help"* looks like in a parameter table. Our final model is therefore `height ~ sex` --- the candidate from Exercise 4 --- which is the model the rest of the tutorial uses.

### Exercise 7

We've settled on the final fit. In `analysis.qmd`, add a new code chunk that assigns the result of `linear_reg() |> set_engine("lm") |> fit(height ~ sex, data = recruits)` to `fit_recruits`, then on the next line prints `fit_recruits`. Render. In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r courage-7}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 5)
```

###

```{r courage-7-test}
#| echo: true
fit_recruits <- linear_reg() |>
  set_engine("lm") |>
  fit(height ~ sex, data = recruits)
fit_recruits
```

###

Only once the parameters are estimated do you have a usable DGM --- one you can use to predict new observations, or to ask what would happen if you changed one part of the mechanism. `fit_recruits` is that object: the fitted machine every later question will be addressed to.

### Exercise 8

Re-fitting the model on every render is wasteful --- the fit's the same each time. `fit_recruits` earns its own cached create chunk. The next three exercises set that up: clean the chunk, turn caching on, add the cache directory to `.gitignore`.

First, clean up. In your chunk from Exercise 7, delete the `fit_recruits` line at the bottom, leaving just the `fit_recruits <- linear_reg() ...` assignment. Render. In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r courage-8}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 8)
```

###

<pre><code>fit_recruits <- linear_reg() |>
  set_engine("lm") |>
  fit(height ~ sex, data = recruits)
</code></pre>

###

A chunk ready to cache should contain only the artifact it builds --- nothing else.

### Exercise 9

Add `#| cache: true` as the first line inside the chunk. Render the QMD. Rendering creates an `analysis_cache/` directory next to your `analysis.qmd`, which holds the saved fit so Quarto can reload it on subsequent renders rather than re-fitting every time. To confirm the directory is there, run `ls` in the **bash Terminal**. CP/CR.

```{r courage-9}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 5)
```

###

<pre><code>$ ls
analysis.qmd  analysis_cache  analysis_files  analysis.html
</code></pre>

###

For a 50-row linear regression the savings are small; for the larger model fits in later tutorials, caching can be the difference between a one-second and a one-minute render.

### Exercise 10

The Source Control change count just jumped, because `analysis_cache/` and everything inside it now look like untracked work to git. Cached files should never go to GitHub --- they're machine-specific and regenerated on every render.

Add `analysis_cache` to your `.gitignore` on its own line. In the R Terminal, run `show_file(".gitignore")`. CP/CR.

```{r courage-10}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 5)
```

###

<pre><code>analysis_files
analysis_cache
</code></pre>

###

The Source Control change count should drop back to whatever it was before the render. Cached objects live next to the QMD, not in version control.

With the parameters estimated, we can write the fitted model as a concrete formula:

$$\widehat{\text{height}} = 165.9 + 8.9 \cdot \text{sexMale}$$

with residuals drawn from $N(0, 41.0)$ --- a residual standard deviation of about 6.4 cm.

Three differences from the abstract form in the preamble. First, the parameters are replaced by their estimates. Second, the error term is gone --- this version of the DGM answers an expected-value question, so the randomness sits to the side in the residuals line until a question needs it. Third, the left-hand side has a hat, because hats mark estimated values.

**This is our data generating mechanism.** A data generating mechanism is a formal, mathematical guess about the process that cast the shadow --- something we can write down and implement with computer code. The randomness built into it lives in the residuals line.

### Exercise 11

Start a new working chunk below the cached `fit_recruits` chunk that runs `tidy(fit_recruits, conf.int = TRUE)`. This returns 95% intervals for all the parameters in our model. Render. In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r courage-11}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 5)
```

###

```{r courage-11-test}
#| echo: true
tidy(fit_recruits, conf.int = TRUE)
```

###

Here is a nicer-looking version of that parameter table:

```{r}
#| echo: false
tidy(fit_recruits, conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high) |>
  mutate(across(where(is.numeric), \(x) round(x, 1))) |>
  knitr::kable(
    caption = "Estimates and 95% Confidence Intervals for Parameters.  Source: 50-row sample from NHANES via primer.tutorials::recruits"
  )
```

Rounding to one decimal place keeps the displayed values consistent with the fitted formula above and is fine enough that the estimate and its confidence-interval bounds stay visibly distinct in every row --- you need rounding finer than the standard error to keep adjacent values apart. At the very least, a table like this should carry a title and a caption naming the data source.

###

We don't really care about coefficients. Nobody ever asked, *"What are the parameters of a linear regression relating height to sex?"* The fitted DGM is not the answer to anything --- it is the machine we built so that we can answer questions like *"What height should we expect for a male recruit?"* The Temperance tutorial runs that machine.

### Exercise 12

Add a sentence to your project summary explaining the structure of the model. Something like: "We model XX [concept of outcome, not variable name], [values of XX], as a [linear/logistic/multinomial/ordinal] function of XX [and maybe other covariates]."

Recall the beginning of our version of the summary:

> People vary in height, and that variation is strongly patterned by sex. Using data from the National Health and Nutrition Examination Survey (NHANES) conducted by the Centers for Disease Control and Prevention, we seek to estimate the average height of male and female USMC recruits for the coming year. One concern is that USMC recruits are more physically fit than the general young-adult population and so may be systematically taller, meaning that the NHANES-based estimates probably understate recruit heights.

```{r courage-12}
question_text(NULL,
  message = "We model height as a normally distributed variable which is a linear function of sex.",
  answer(NULL, correct = TRUE),
  allow_retry = FALSE,
  incorrect = NULL,
  rows = 5)
```

###

Read our answer. Do not copy/paste exactly. Add your two sentences to the summary paragraph. Render the QMD.

### Exercise 13

Commit and push, with a message like "Fit final linear regression DGM for recruits." In the bash Terminal, run:

```
git log -1
```

CP/CR.

```{r courage-13}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 5)
```

###

`fit_recruits` is saved, cached, and committed. It is not the answer to anything by itself --- it is the machine we built so we can answer questions, which is exactly what the Temperance tutorial does with it.


## Summary
###

This tutorial covered the **Courage** stage of the [Recruits](https://ppbds.github.io/primer/05-recruits.html) chapter of [*Preceptor's Primer for Bayesian Data Science*](https://ppbds.github.io/primer/).

Building a model of the data generating mechanism takes three steps: **propose a structure** (the distribution of the outcome variable determines it --- a continuous height calls for `linear_reg()`), **choose a method** (`set_engine("lm")` for a classical least-squares fit), and **fit the DGM** (`fit(height ~ sex, data = recruits)`, which estimates the parameters). Structure &rarr; Method &rarr; Fitting.

We tried `sex` and `age` as candidate covariates, kept `sex` because its confidence interval cleared zero and dropped `age` because its did not, and saved the final fit as `fit_recruits`:

$$\widehat{\text{height}} = 165.9 + 8.9 \cdot \text{sexMale}$$

with residuals drawn from $N(0, 41.0)$. In words: we model height as a normally distributed variable which is a linear function of sex.

The fitted DGM is not the answer to anything by itself. It is the machine we built so that we can answer questions --- expected heights, and the uncertainty around them --- which the **Temperance** tutorial takes up next.

The world is always more uncertain than our models would have us believe.

```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
