---
title: 'XX: Overview'
author: David Kane
tutorial:
  id: models-overview
output:
  learnr::tutorial:
    progressive: yes
    'allow_skip:': yes
runtime: shiny_prerendered
description: 'Chapter XX Tutorial: XX'
---

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(tidyverse)
library(gt)
library(brms)
library(tidybayes)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 
```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

<!-- This is the template tutorial for creating any tutorial which uses the Cardinal Virtues to answer a question given a data set. Although its primary use is for the main chapters in the Primer, it could be used for other assignments as well. The letters `XX` are used to indicate locations which require editing. Comments with instructions are interspersed. Read https://ppbds.github.io/primer/key-concepts.html for details on the Cardinal Virtues. -->

<!-- The four main sections of the tutorial always correspond to the four virtues. There are always questions which require definitions, in your own words, for the dozen or so key terms. -->

<!-- Add creation of the summary sentences which are created as we move through the process. -->

<!-- There should be a bunch of quotes for each cardinal virtue. All quotes are listed at the introduction of each section. We then select one for an individual tutorial. -->


## Introduction
### 

This tutorial covers [Chapter XX: XX](https://ppbds.github.io/primer/XX.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 

## Wisdom
### 

*The only true wisdom is in knowing you know nothing.* - Socrates
*Patience is the companion of wisdom.* - Saint Augustine
*Wonder is the beginning of wisdom.* - Socrates
*Wisdom begins in wonder.* - Plato
*The doorstep to the temple of wisdom is a knowledge of our own ignorance.* - Benjamin Franklin
*It is the province of knowledge to speak, and it is the privilege of wisdom to listen.* - Oliver Wendell Holmes Sr.

### Exercise 1

In your own words, describe the key components of Wisdom for working on a data science problem.

```{r wisdom-1}
question_text(NULL,
	message = "Wisdom requires the creation of a Preceptor Table, an examination of our data, and a determination, using the concept of validity, as to whether or not we can (reasonably!) assume that the two come from the same population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 2

Define a Preceptor Table.

```{r wisdom-2}
question_text(NULL,
	message = "A Preceptor Table is the smallest possible table of data with rows and columns such that, if there is no missing data, it is easy to calculate the quantities of interest.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 3

Describe the key components of Preceptor Tables in general, without worrying about this specific problem.

```{r wisdom-3}
question_text(NULL,
	message = "The rows of the Preceptor Table are the units. The outcome is at least one of the columns. If the problem is causal, there will be at least two (potential) outcome columns. The other columns are covariates. If the problem is causal, at least one of the covariates will be a treatment.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 4

What are the units for this problem?

```{r wisdom-4}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 5

What is/are the outcome/outcomes for this problem?

```{r wisdom-5}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 6

What are the covariates for this problem?

```{r wisdom-6}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 7

What are the treatments, if any, for this problem?

```{r wisdom-7}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 8

What moment in time does the Preceptor Table refer to?

```{r wisdom-8}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- If a causal problem, define potential outcome, causal effect, RCM, fundamental problem and no causation motto? Could not hurt to do that everytime! -->


### Exercise 9

Write one sentence describing the data you have to answer your question.

```{r wisdom-9}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

<!-- Include more questions about EDA with this data? -->

### Exercise 10

In your own words, define "validity" as we use the term.

```{r wisdom-10}
question_text(NULL,
	message = "Validity is the consistency, or lack thereof, in the columns of the data set and the corresponding columns in the Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```



### Exercise 11
<!-- DK: Keep this question? -->
What can't we do if the assumption of validity is not true?

```{r wisdom-11}
question_text(NULL,
	message = "We can't combine the Preceptor Table and the data in order to construct the Population Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 12

Provide one reason why the assumption of validity might not hold for this problem.

```{r wisdom-12}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 13

Summarize the state of your work so far in one or two sentences. Make reference to the data you have and to the question you are trying to answer. 


```{r wisdom-13}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

## Justice
### 

*Justice is truth in action.* - Benjamin Disraeli
*The arc of the moral universe is long, but it bends toward justice.* - Theodore Parker
*Justice delayed is justice denied.* - William E. Gladstone
*It is in justice that the ordering of society is centered.* - Aristotle
*Charity is no substitute for justice withheld.* - Saint Augustine

### Exercise 1

In your own words, name the four key components of Justice for working on a data science problem.

```{r justice-1}
question_text(NULL,
	message = "Justice concerns four topics: the Population Table, stability, representativeness, and unconfoundedness.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 2

In your own words, define a Population Table.

```{r justice-2}
question_text(NULL,
	message = "The Population Table includes a row for each unit/time combination in the underlying population from which both the Preceptor Table and the data are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 3

Describe the Population Table for this problem. In particular, are any of the rows in the Preceptor Table also rows in the data? Are there other rows in the Population Table which are not from the Preceptor Table or the data? If so, describe some of those rows.

```{r justice-3}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 4

In your own words, define the assumption of "stability" when employed in the context of data science.

```{r justice-4}
question_text(NULL,
	message = "Stability means that the relationship between the columns in the Population Table is the same for three categories of rows: the data, the Preceptor Table, and the larger population from which both are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Keep just one of these two. -->

<!-- Stability is all about *time*. Is the relationship among the columns in the Population Table stable over time? In particular, is the relationship --- which is another way of saying "mathematical formula" --- at the time the data was gathered the same as the relationship at the (generally later) time references by the Preceptor Table. -->

<!-- *The longer the time period covered by the Preceptor Table (and the data), the more suspect the assumption of stability becomes.*  -->

### Exercise 5

Provide one reason why the assumption of stability might not be true in this case.

```{r justice-5}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

###



### Exercise 6

In your own words, define the assumption of "representativeness" when employed in the context of data science.


```{r justice-6}
question_text(NULL,
	message = "Representativeness, or the lack thereof, concerns two relationship, among the rows in the Population Table. The first is between the Preceptor Table and the other rows. The second is between our data and the other rows.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Keep one of these. -->

<!-- Ideally, we would like both the Preceptor Table *and* our data to be random samples from the population. Sadly, this is almost never the case. -->

<!-- Stability looks across time periods. Reprentativeness looks within time periods. -->

<!-- The more expansive your Preceptor Table, the more important the assumption of representativeness becomes. -->

### Exercise 7

Provide one reason why the assumption of representativeness might not be true in this case.

```{r justice-7}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 8

In your own words, define the assumption of "unconfoundedness" when employed in the context of data science.

```{r justice-8}
question_text(NULL,
	message = "Unconfoundedness means that the treatment assignment is independent of the potential outcomes, when we condition on pre-treatment covariates.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Keep one. -->

<!-- This assumption is only relevant for causal models. We describe a model as "confounded" if this is not true.  -->

<!-- The easiest way to ensure unconfoundedness is to assign treatment randomly. -->

### Exercise 9

Provide one reason why the assumption of unconfoundedness might not be true (or relevant) in this case.

```{r justice-9}
question_text(NULL,
	message = "Place correct answer here.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 10

Summarize the state of your work so far in one or two sentences. Make reference to the data you have and to the question you are trying to answer. 


```{r justice-10}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 11

Summarize the state of your work so far in two or three sentences. Make reference to the data you have and to the question you are trying to answer. Feel free to copy from your answer at the end of the Wisdom Section. Mention at least one specific problem which casts doubt on your approach. 


```{r justice-11}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

## Courage
### 

*Courage is found in unlikely places.* - J.R.R. Tolkien
*Courage is being scared to death, but saddling up anyway.* - John Wayne
*Courage is going from failure to failure without losing enthusiasm.* - Winston Churchill
*Courage is the commitment to begin without any guarantee of success.* - Johann Wolfgang von Goethe

### Exercise 1

<!-- DK: Not sure I like this answer. -->

In your own words, name the key goal of Courage and the process we use to get there.

```{r courage-1}
question_text(NULL,
	message = "Courage selects the data generating mechanism. We first specify the mathematical formula which connects the outcome variable we are interested in with the other data that we have. We explore different models. We need to decide which variables to include and to estimate the values of unknown parameters. We check our models for consistency with the data we have. We avoid hypothesis tests. We select one model.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

<!-- Questions about models, tests, and the DGM. -->


### Exercise 2

Write a few sentence which summarize your work so far. The first few sentences are the same as what you had at the end of the Justice Section. Add at least one sentence which describes the modelling approach which you are using. Also add at least one sentence which describes the *direction* (not the magnitude) of the relationship between one of your independent variables and your dependent variable.

```{r courage-2}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

## Temperance
### 

*Temperance is a tree which as for its root very little contentment, and for its fruit calm and peace.* - Buddha
*Temperance is the greatest of all virtues. It subdues every passion and emotion, and almost creates a Heaven upon Earth.* - Joseph Smith Jr.
*Temperance is a bridle of gold; he, who uses it rightly, is more like a god than a man.* - Robert Burton
*Temperance is the firm and moderate dominion of reason over passion and other unrighteous impulses of the mind.* - Marcus Tullius Cicero
*Temperance to be a virtue must be free, and not forced.* - Philip Massinger
*Temperance is simply a disposition of the mind which binds the passion.* - Thomas Aquinas

### Exercise 1

In your own words, describe the use of Temperance in finishing our data science project.

```{r temperance-1}
question_text(NULL,
	message = "Temperance guides us in the use of the data generating mechanism --- or the 'model' ---  we have created to answer the questions with which we began. We create posteriors for the quantities of interest.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

<!-- Questions and Answers; Humility -->

### Exercise 2

Write a paragraph which summarizes your project. The first few sentences are the same as what you had at the end of the Courage Section. But, since your question may have evolved, you should feel free to change those sentences. Add at least one sentence which describes at least one quantity of interest --- presumably one that answers your question -- and which provides a measure of uncertainty about that QoI. 

```{r temperance-2}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

## Summary
### 

This tutorial covered [Chapter XX: XX](https://ppbds.github.io/primer/XX.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 



```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
