---
title: XX
author: David Kane
tutorial:
  id: XX
output:
  learnr::tutorial:
    progressive: yes
    'allow_skip:': yes
runtime: shiny_prerendered
description: 'Chapter XX Tutorial: XX'
---

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(tidyverse)
library(gt)
library(brms)
library(tidybayes)
library(gtsummary)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 
```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

<!-- Next major change in this template is require the creation of a Github repo/R project/Quarto document which includes the key results of the tutorial. The last question then becomes the url for the Rpubs published version. Some details:

* How much hand-holding you do depends on tutorial number. For tutorial 4, we would want to provide the same sort of questions and verbiage as we see in Project #2 in the RStudio and Github tutorial. For tutorial 10, we can go much more quickly.

* Make use of `show_file("tutorial-6.qmd", start = -5)` to get just the last 5 lines of the QMD. We don't want students to both copy/pasting the whole document. We also don't need to ensure that we get whatever it is that was just changed. We never look! Instead, we are just plausibly threatening to look. In fact, we might only look at the completed document, for which they do need to run `show_file("tutorial-6.qmd")` as the second to last question in Temperance.

* The QMD includes four main parts. First, the mathematical formula for the model. (They will need to use latex math for this, just like we do in the Primer.)  Second, a gtsummary table with the parameter estimates. Third, a nice plot showing the answer to the question. Fourth, the paragraph which summarizes what they have concluded. 

* We build the document step-by-step. In general, we always add the latest thing to the bottom of the document, which makes the `start = -5` trick work well. This is tricky with regard to the paragraph since we add to it bit-by-bit. Solve this problem by always having sentences for the paragraph requiring answers in the tutorial itself, followed by a knowledge drop which instructs students to add the sentences to the QMD. But we don't need to check that they have done so. Then, the other material is always at the bottom, and so `start = -5` works.

* Once the document is complete, we have students re-arrange the parts before the final rendering. After all, we probably want the top to be the graphic, followed by the paragraph, then the math, then the parameter estimates. These instructions proceed the final show_file() question.

* The QMD additions come in discrete groupings: several questions together, surrounded by non-QMD questions. Note that several steps within a grouping can be combined into a single exercise. 
  + The first group is the GitHub/Project creation. This includes editing .gitignore and commit/push. 
  + The second group is the libraries in the setup code chunk. Starts by making the QMD and adding all the libraries at once to the first code chunk. Render. Note all the ugliness. Add #| message: false. Add execute: echo: false to the YAML header. Render again. 
  + The third grouping, if necessary, is the creation of a cleaned up tibble for use in modeling. Again, we have done all the steps in the pipe in the tutorial first, the better to understand what each step does. Then we just need one question which says "Make a new code chunk. Add the pipe, assigning the result to an object called whatever. Render."
  + The fourth grouping is the mathematical formula. It is in the main text, using LaTeX.
  + The fifth grouping is the brm call. Again, the call itself was made in the tutorial first. When you add the brm call, also add #| cache: TRUE. Render. Explain that it still takes a while since the cache does not exist. Render again. See how fast that went! All of that is only one question (or maybe two), using `show_file(..., start = -5)`.
  + The sixth grouping is the gtsummary table created with brmsfit object, the thing returned by brm(). Again, we build this step-by-step in the tutorial, the better to accomplish two goals: show students what each step does and have an opportunity for more knowledge drops. See: https://www.danieldsjoberg.com/gtsummary/articles/tbl_regression.html. 
  + The seventh grouping is the graphic. In early chapters, this is simple since our questions are simple. They are just one posterior. In later chapters, they become more complex, with the inclusion of several posteriors, as with the voting postcard example. Again, these are built line-by-line in the tutorial. A single question that moves the final plot over to the QMD.
  + The eighth grouping is the paragraph summary. We have been building this up line-by-line throughout the whole tutorial, generally adding/editing it at the end of each Virtue section, just as in the Primer.

* We spread out the QMD related questions as much as possible. 
  + Wisdom: After the first few questions, we add Github repo/R project setup. After the library loads, we do the same on QMD. We add the first sentence to the paragraph at the end.
  + Justice: The only change in the QMD during Justice comes at the end, when we add one sentence to the paragraph.
  + Courage: We add the mathematical formula just before making the brm call. We add the brm() call to the QMD after spending several questions analysing the object which we created in the tutorial, maybe right after the `nobs()` question. We add the gtsummary table to the QMD after finishing it in the tutorial. At the end, we add two new sentences to the parapgraph.
  + Temperance: We create the entire graphic in the tutorial. We move it over to the QMD all at once. We finish the paragraph at the end of Temperance.

-->

<!-- Whenever you tell a student to make a change in the QMD. You should tell them to `Command/Ctrl + Shift + K` in order to render the document. This will also cause it to be saved. This is good practice for catching bugs early. (Professionals do this.) Then, the last step in these exercises is often some verion of show_file() and then CP/CR. -->

<!-- A knowledge drop should not be a road sign. -->


<!-- Instructions to Users of this Template: -->

<!-- This is the template tutorial for creating any tutorial which uses the Cardinal Virtues to answer a question given a data set. Although its primary use is for the main chapters in the Primer, it could be used for independent tutorials as well. The letters `XX` are used to indicate locations which require editing. Comments with instructions are interspersed. Read https://ppbds.github.io/primer/key-concepts.html for details on the Cardinal Virtues. -->

<!-- Once you have followed an instruction, feel free to delete it. -->

<!-- Quotes related to the virtues are listed at the introduction of each section. Select one. -->

<!-- There are many opportunities for knowledge drops, especially after definition questions. Use them! Point out something about the details of the particular problem from the chapter. Recall that students generally won't read the chapter, so we need to pull out the highlights. -->

<!-- Most of the questions in the Temperance section relate to constructing a graphic. This leads lots of opportunities for knowledge drops. This is a good place to mention items from Courage which you might not have had room for in that section. -->

<!-- The more that questions force students to consult the chapter, the better. -->

<!-- Make sure to uncomment the test code chunks once you have created the necessary objects. -->

<!-- First pass, don't hesitate to skip knowledge drops for which you don't have something to say. -->

<!-- Always create any modeling objects and then save them in data/ by hand. Then, when building the tutorial, just read in the object. See the below example. Note that the commented code is run once, by hand, but saved so that it could be modified in the future. The fit_gauss assignment is run every time one hits Run Tutorial. But it is fast, so there is no cost. -->

<!-- #fit_gauss <- brm(formula = att_end ~ treatment, -->
<!-- #             data = trains, -->
<!-- #             family = gaussian(), -->
<!-- #             silent = 2, -->
<!-- #             refresh = 0, -->
<!-- #             seed = 9) -->
<!-- #write_rds(fit_gauss, "data/fit_gauss.rds") -->

<!-- fit_gauss <- read_rds("data/fit_gauss.rds") -->


<!-- Future improvements to make in this document:

Turn it into a vignette at some point? 

We need (?) to flesh out the Courage and Temperance sections. Key skills to practice each time including writing math formulas in Quarto and creating nice looking tables of regression results. 

In the same way that we give several quotes to choose from at the start of each section, we ought to give several different knowledge drops to choose from, in order of sophistication, for many of the standard questions. No need for authors to reinvent the wheel. 

Would be nice if part of the testing would run all the object creation code so that we can be sure all that code works. But that would have to be during testing only.
-->

<!-- ?governors as an example of a good question. -->

## Introduction
### 

This tutorial covers [Chapter XX: XX](https://ppbds.github.io/primer/XX.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 

## Wisdom
### 

<!-- XX: Pick one. -->

*The only true wisdom is in knowing you know nothing.* - Socrates
*Patience is the companion of wisdom.* - Saint Augustine
*Wonder is the beginning of wisdom.* - Socrates
*Wisdom begins in wonder.* - Plato
*The doorstep to the temple of wisdom is a knowledge of our own ignorance.* - Benjamin Franklin
*It is the province of knowledge to speak, and it is the privilege of wisdom to listen.* - Oliver Wendell Holmes Sr.
*All we can know is that we know nothing. And that’s the height of human wisdom.* - Leo Tolstoy

<!-- Update on Wisdom introduction. It should always include a quote. Then it asks the general question, indented and italized. Then it asks the specific question, also indented and italized. This is exactly the way the Primer works. There might also be some explanatory sentences around that, and the use of triple hashes to force a "Continue" button. -->

### Exercise 1

In your own words, describe the key components of Wisdom when working on a data science problem.

```{r wisdom-1}
question_text(NULL,
	message = "Wisdom requires the creation of a Preceptor Table, an examination of our data, and a determination, using the concept of validity, as to whether or not we can (reasonably!) assume that the two come from the same population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: You have the opportunity, in this and the next few questions, to drop a lot of knowledge about the data and the overall topic. Do so! But, remember, students won't read more than 2 or so sentences in a knowledge drop. -->

<!-- Not only are you discussing the data, but you are also discussing potential problems with the data, problems which will be more fully fleshed out in the Justice section. You want to pick 5 to 10 interesting facts about the data. (You may need to go to the original source, not simply relying on the chapter.) 

You won't be drawing any conclusions or pointing out any problems. That discussion is saved until Justice and the specific questions about stability and representativeness. You are, hwoever, providing the details which you and the students can then use later. -->

### Exercise 2

Define a Preceptor Table.

```{r wisdom-2}
question_text(NULL,
	message = "A Preceptor Table is the smallest possible table of data with rows and columns such that, if there is no missing data, we can easily calculate the quantities of interest.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 3

Describe the key components of Preceptor Tables in general, without worrying about this specific problem. Use words like "units," "outcomes," and "covariates."

```{r wisdom-3}
question_text(NULL,
	message = "The rows of the Preceptor Table are the units. The outcome is at least one of the columns. If the problem is causal, there will be at least two (potential) outcome columns. The other columns are covariates. If the problem is causal, at least one of the covariates will be a treatment.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 4

What are the units for this problem?

```{r wisdom-4}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 5

What is/are the outcome/outcomes for this problem?

```{r wisdom-5}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 6

<!-- XX. You will probably need to make this question much more specific. In other words, you want the student to list some of the covariates that are available for him to consider. We are not just looking for the select few covariates which will end up in the model. Maybe some EDA needs to come first? -->

<!-- This is a lousy question! Which meaning of covariates do you intend? -->

What are some covariates which you think might be useful for this problem?

```{r wisdom-6}
question_text(NULL,
	message = "XX. Answer should be some sensible variables which are plausibly connected to the outcome. Some should be in the data but some shouldn't. You might also add that `You need to have variable X` if the question itself mentions that variable.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 7

What are the treatments, if any, for this problem?

```{r wisdom-7}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 8

What moment in time does the Preceptor Table refer to?

```{r wisdom-8}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Next three questions are only included for a causal model. -->

### Exercise 9

Define causal effect.

```{r wisdom-9}
question_text(NULL,
	message = "A causal effect is the difference between two potential outcomes.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 10

What is the fundamental problem of causal inference?

```{r wisdom-10}
question_text(NULL,
	message = "The fundamental problem of causal inference is that we can only observe one potential outcome.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 11

How does the motto "No causal inference without manipulation." apply in this problem?

```{r wisdom-11}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: End causal model section. If there is not one, you will need to run Format Tutorial Chunk Labels in order to renumber the exercises once you delete these.  -->

### Exercise 12

Describe in words the Preceptor Table for this problem.

```{r wisdom-12}
question_text(NULL,
	message = "XX.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The Preceptor Table for this problem looks something like this:

<!-- XX. Show the Preceptor Table. You can just copy/paste the code from the Primer. -->


### Exercise 13

<!-- XX: It is a feature that this question almost forces students to go to the chapter and read about the data. This entire sentence will not be included in your summary at the end of Wisdom, but bits of it will be mentioned. -->

Write one sentence describing the data you have to answer your question.

```{r wisdom-13}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 14

Load the **tidyverse** package.

```{r wisdom-14, exercise = TRUE}

```

```{r wisdom-14-hint-1, eval = FALSE}
library(...)
```

```{r wisdom-14-test, include = FALSE}
library(tidyverse)
```

### 

<!-- XX: Insert comments about the data. -->

<!-- XX: Load any other packages that are needed, one package per question. (But make sure that they are also included in the setup chunk.) primer.data, for example, is often needed. But save brms and tidybayes for the Courage section. -->

<!-- XX: Add questions about EDA with your data. In particular, add at least one question about the dependent variable in the model along with one or more questions about covariates. If there is a treatment variable, you must include a question about it. -->

<!-- Variable questions come in two types. First there are questions which require the student to run, say, summary() on the variable. Then, knowledge about the variable can be dropped. Second, there are questions which ask for a one sentence summary about the variable, something which could be used in our summary of the project. For example: "Civility is measured on a 1 through 7 scale with higher values corresponding to greater civility." -->

### Exercise 15

In your own words, define "validity" as we use the term.

```{r wisdom-15}
question_text(NULL,
	message = "Validity is the consistency, or lack thereof, in the columns of the data set and the corresponding columns in the Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 16

What can't we do if the assumption of validity is not true?

```{r wisdom-16}
question_text(NULL,
	message = "We can't combine the Preceptor Table and the data in order to construct the Population Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 17

Provide one reason why the assumption of validity might not hold for this problem.

```{r wisdom-17}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 18

<!-- XX: In creating your own answer to questions like this, check with the chapter. One might already be provided! If not, it is often useful to revisit the relevant section of the Key Concepts chapter in the Primer. -->

<!-- Example: *Using data from a 2012 survey of Boston-area commuters, we seek to understand the relationship between income and political ideology in Chicago and similar cities in 2020. In particular, what percentage of individuals who make more than $100,000 per year are liberal?* -->

Summarize the state of your work so far in one sentence. Make reference to the data you have and to the specific question you are trying to answer. 


```{r wisdom-18}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

## Justice
### 

<!-- XX: Choose one. -->

*Justice is truth in action.* - Benjamin Disraeli
*The arc of the moral universe is long, but it bends toward justice.* - Theodore Parker
*Justice delayed is justice denied.* - William E. Gladstone
*It is in justice that the ordering of society is centered.* - Aristotle
*Charity is no substitute for justice withheld.* - Saint Augustine

### Exercise 1

In your own words, name the four key components of Justice for working on a data science problem.

```{r justice-1}
question_text(NULL,
	message = "Justice concerns four topics: the Population Table, stability, representativeness, and unconfoundedness.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

In your own words, define a Population Table.

```{r justice-2}
question_text(NULL,
	message = "The Population Table includes a row for each unit/time combination in the underlying population from which both the Preceptor Table and the data are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 3

In your own words, define the assumption of "stability" when employed in the context of data science.

```{r justice-3}
question_text(NULL,
	message = "Stability means that the relationship between the columns in the Population Table is the same for three categories of rows: the data, the Preceptor Table, and the larger population from which both are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Keep just one of these two. -->

<!-- Stability is all about *time*. Is the relationship among the columns in the Population Table stable over time? In particular, is the relationship --- which is another way of saying "mathematical formula" --- at the time the data was gathered the same as the relationship at the (generally later) time references by the Preceptor Table. -->

<!-- *The longer the time period covered by the Preceptor Table (and the data), the more suspect the assumption of stability becomes.*  -->

### Exercise 4

Provide one reason why the assumption of stability might not be true in this case.

```{r justice-4}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 5

In your own words, define the assumption of "representativeness" when employed in the context of data science.

```{r justice-5}
question_text(NULL,
	message = "Representativeness, or the lack thereof, concerns two relationship, among the rows in the Population Table. The first is between the Preceptor Table and the other rows. The second is between our data and the other rows.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Keep one of these. -->

<!-- Ideally, we would like both the Preceptor Table *and* our data to be random samples from the population. Sadly, this is almost never the case. -->

<!-- Stability looks across time periods. Reprentativeness looks within time periods. -->

<!-- The more expansive your Preceptor Table, the more important the assumption of representativeness becomes. -->

### Exercise 6

Provide one reason why the assumption of representativeness might not be true in this case.

```{r justice-6}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 7

In your own words, define the assumption of "unconfoundedness" when employed in the context of data science.

```{r justice-7}
question_text(NULL,
	message = "Unconfoundedness means that the treatment assignment is independent of the potential outcomes, when we condition on pre-treatment covariates.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Keep one. -->

<!-- This assumption is only relevant for causal models. We describe a model as "confounded" if this is not true.  -->

<!-- The easiest way to ensure unconfoundedness is to assign treatment randomly. -->

### Exercise 8

<!-- XX: Delete this question for non-causal models. -->

Provide one reason why the assumption of unconfoundedness might not be true (or relevant) in this case.

```{r justice-8}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 9

Summarize the state of your work so far in two or three sentences. Make reference to the data you have and to the question you are trying to answer. Feel free to copy from your answer at the end of the Wisdom Section. Mention one specific problem which casts doubt on your approach. 


```{r justice-9}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

## Courage
### 

<!-- XX: Choose one. -->

*Courage is found in unlikely places.* - J.R.R. Tolkien
*Courage is being scared to death, but saddling up anyway.* - John Wayne
*Courage is going from failure to failure without losing enthusiasm.* - Winston Churchill
*Courage is the commitment to begin without any guarantee of success.* - Johann Wolfgang von Goethe


<!-- Questions about models, tests, and the DGM. -->


### Exercise 1

In your own words, describe the components of the virtue of Courage for analyzing data.

```{r courage-1}
question_text(NULL,
	message = "Courage begins with the exploration and testing of different models. It concludes with the creation of a Data Generating Mechanism.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

Load the **brms** package.

```{r courage-2, exercise = TRUE}

```

```{r courage-2-hint-1, eval = FALSE}
library(...)
```

```{r courage-2-test, include = FALSE}
library(brms)
```

### 

<!-- XX: Some comments about this problem. -->

### Exercise 3

Load the **tidybayes** package.

```{r courage-3, exercise = TRUE}

```

```{r courage-3-hint-1, eval = FALSE}
library(...)
```

```{r courage-3-test, include = FALSE}
library(tidybayes)
```

### 

<!-- XX: Some comments about this problem. -->

<!-- XX: Might need an exercise which gets/creates/cleans the data you need for fitting the model. -->

### Exercise 4

Create a model using `brm()` from the **brms** package. Your arguments should XX. 

Assign the result to an object called `fit_XX`.

<!-- Search and replace "fit_XX" as appropriate. -->

<!-- Don't forget to create this model yourself in the setup chunk. Do this once, save the object, comment out that code and then just read_rds to create the object for his tutorial. -->

<!-- Depending on code speed, you can run this function multiple times, without assigning the return value, looking at the printout, and seeing how things change. -->

```{r courage-4, exercise = TRUE}

```

```{r courage-4-hint-1, eval = FALSE}

```

### 

### Exercise 5

Type `fit_XX` and hit "Run Code." This generates the same results as using `print(fit_XX)`.


```{r courage-5, exercise = TRUE}

```

```{r courage-5-hint-1, eval = FALSE}
print(...)
```

```{r courage-5-test, include = FALSE}
# print(fit_XX)
```

### 

<!-- XX Same some general words about the object. Note that we are about to go through the top 4 rows. -->

<!-- Add summary() Exercise if it gives a different answer -->

### Exercise 6

Run `family()` on `fit_XX`. `family()` provides information about the "family" of the error term and the link between it and the dependent variable. 

```{r courage-6, exercise = TRUE}

```

```{r courage-6-hint-1, eval = FALSE}
family(...)
```

```{r courage-6-test, include = FALSE}
# family(fit_XX)
```

### 

<!-- XX: This is a great location for explanations which get much more detailed in later chapters. That is, we want students to have a more sophisticated understanding of probability distributions, and there use in modeling, as we move through the Primer.

But, at a minimum, you would comment about how the family that is shown --- which is either gaussian, bernoulli or categorical --- is determined by the family argument which you passed in to the brm() call, and that you determined that by looking at the distribution of the output variable. Continuous means gaussian, 2 possible values means bernoullu, and 2+ possible values means categorical.

-->

In this case, XX . . .

### Exercise 7

Run `formula()` on `fit_XX`. `formula()` returns the statistical equation which relates the dependent variable to the independent variable(s). 

```{r courage-7, exercise = TRUE}

```

```{r courage-7-hint-1, eval = FALSE}
formula(...)
```

```{r courage-7-test, include = FALSE}
# formula(fit_XX)
```

### 

In this case, XX . . .

### Exercise 8

Run `nobs()` on `fit_XX`. The `nobs()` function returns the **n**umber of **obs**ervations.

```{r courage-8, exercise = TRUE}

```

```{r courage-8-hint-1, eval = FALSE}
nobs(...)
```

```{r courage-8-test, include = FALSE}
# nobs(fit_XX)
```

### 

In this case, XX

### Exercise 9

Run `posterior_interval()` on `fit_XX`. The `posterior_interval()` function returns 95% intervals for all the parameters in our model.

```{r courage-9, exercise = TRUE}

```

```{r courage-9-hint-1, eval = FALSE}
posterior_interval(...)
```

```{r courage-9-test, include = FALSE}
# posterior_interval(fit_XX)
```

### 

In this case, XX


### Exercise 10

Run `fixef()` on `fit_XX`. The `fixef()` returns information about the **fix**ed **ef**fects in the model.

```{r courage-10, exercise = TRUE}

```

```{r courage-10-hint-1, eval = FALSE}
fixef(...)
```

```{r courage-10-test, include = FALSE}
# fixef(fit_XX)
```

### 

In this case, XX

<!-- XX: Consider adding questions about conditional_effects(), ranef() and other commands, if relevant. -->

### Exercise 11

Run `pp_check()` on `fit_XX`. The `pp_check()` runs a **p**osterior **p**redictive check.

```{r courage-11, exercise = TRUE}

```

```{r courage-11-hint-1, eval = FALSE}
pp_check(...)
```

```{r courage-11-test, include = FALSE}
# pp_check(fit_XX)
```

### 

In this case, XX

<!-- If the fake data had looked very different from the real data, we have had a problem. But, for the most part, we conclude that, although not perfect, pp_check() shows that the fake outcomes generated by our model are like the actual outcome data. -->


### Exercise 12

Use `library()` to load the [**gtsummary**](https://www.danieldsjoberg.com/gtsummary) package.

```{r courage-12, exercise = TRUE}

```

```{r courage-12-hint-1, eval = FALSE}
library(gtsummary)
```

```{r courage-12-test, include = FALSE}
library(gtsummary)
```

### 

<!-- Drop some knowledge about gtsummary. Or say something more about your DGM. -->

### Exercise 13

<!-- XX: This can be just one question or several, especially if you want to teach some more gtsummary or gt tricks. Note that you need to adjust the test to make sure it works. -->

Run `tbl_regression()` on `fit_XX`. 


```{r courage-13, exercise = TRUE}

```

```{r courage-13-hint-1, eval = FALSE}
tbl_regression(...)
```

```{r courage-13-test, include = FALSE}
# tbl_regression(fit_XX)
```

### 

<!-- XX: Give something like the same sentence which you want the students to use at the end of the next question. -->


### Exercise 14

Write a few sentence which summarize your work so far. The first few sentences are the same as what you had at the end of the Justice Section. Add one sentence which describes the modelling approach which you are using, specifying the functional form and the dependent variable. Add one sentence which describes the *direction* (not the magnitude) of the relationship between one of your independent variables and your dependent variable.

```{r courage-14}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

## Temperance
### 

<!-- XX: Discuss newdata objects slowly. "A newdata tibble must include columns for all the right-hand side variables --- all the "covariates" --- in the model, and with all the same variable names and, mostly, variable types." 

First ask a question about which columns are needed in the newdata object. This might just be a written question. The answer is all the variables which are on the rightside of the formula used in this tutorial. This and the next question are written exercises with answers. 

Second, ask a question about how many rows we need in the newdata object. Recall that each row will generate a posterior for something. That is, if you have two rows in your newdata object, you will get two posteriors. It is up to you to determine what those two posteriors are and what you want to do with them.

Third, ask a question about which values you want those variables to have. That is not easy! Again, a written answer, which is specific for this tutorial. For each row in the newdata tibble, you get a new posterior. How many posteriors do you want? 

Fourth, give them the R code which creates the newdata object. All they need to do is run it. Asking them to create it, even after you help them figure out the columns (question 1) and rows (question 2) is too hard, at least until they get more experiences. This is a code exercise. This does not include the assignment of this R code to an object.

Fifth, inform them that you have, behind the scenes (which really means the setup code chunk), already assigned this tibble to the `ndata` object. In this question, they just type `ndata` to confirm. This is a code exercise.

The knowledge drops for all four of these questions allow you to explain/teach more about what goes in the argument for newdata and what does not. Explaining what other newdata objects would produce, if we used them, is a good idea.

-->

<!-- XX: Choose one. -->

*Temperance is a tree which as for its root very little contentment, and for its fruit calm and peace.* - Buddha
*Temperance is the greatest of all virtues. It subdues every passion and emotion, and almost creates a Heaven upon Earth.* - Joseph Smith Jr.
*Temperance is a bridle of gold; he, who uses it rightly, is more like a god than a man.* - Robert Burton
*Temperance is the firm and moderate dominion of reason over passion and other unrighteous impulses of the mind.* - Marcus Tullius Cicero
*Temperance to be a virtue must be free, and not forced.* - Philip Massinger
*Temperance is simply a disposition of the mind which binds the passion.* - Thomas Aquinas

<!--  -->

### Exercise 1

In your own words, describe the use of Temperance in finishing your data science project.

```{r temperance-1}
question_text(NULL,
	message = "Temperance uses the Data Generating Mechanism to answer the question with which we began. Humility reminds us that this answer is always a lie.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

Recall the question with which we began:

> ...

Pipe `fit_XX` to . . .

```{r temperance-2, exercise = TRUE}

```

```{r temperance-2-hint-1, eval = FALSE}

```

```{r temperance-2-test, include = FALSE}

```

### 

### Exercise 3

Write a paragraph which summarizes the project in your own words. The first few sentences are the same as what you had at the end of the Courage section. But, since your question may have evolved, you should feel free to change those sentences. Add at least one sentence which describes at least one quantity of interest (QoI) --- presumably one that answers your question -- and which provides a measure of uncertainty about that QoI.

<!-- XX: Most of the time, there will be some measure of uncertainty associated with your QoI. But not always! The most common counter-example involves a question which asks about the odds or probability of something happening. We would answer such a question by simulating the event with `add_predicted_draws()`. We would then calculate the odds/probability of something happening by seeing how many of the 4,000 draws met the criteria for the event. Assume that was 40%. So, we think that there is a 40% chance that event A will happen. Yet there is no uncertainty associated with that estimate because it, itself, is an expression of uncertainty. (DK: Flesh this out further.) -->

```{r temperance-3}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 4

Write a few sentences which explain why the estimates for the quantities of interest, and the uncertainty thereof, might be wrong. Suggest an alternative estimate and confidence interval.

```{r temperance-4}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

## Summary
### 

This tutorial covered [Chapter XX: XX](https://ppbds.github.io/primer/XX.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 



```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
