---
title: XX
author: XX
tutorial:
  id: XX (should be the number + title, everything in lower case, all spaces and weird
    characters replaced with dashes)
output:
  learnr::tutorial:
    progressive: yes
    'allow_skip:': yes
runtime: shiny_prerendered
description: 'Chapter XX Tutorial: XX'
---

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(tidyverse)
library(gt)
library(brms)
library(tidybayes)
library(gtsummary)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 
```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

<!-- Instructions to Users of this Template: -->

<!-- This is the template tutorial for creating any tutorial which uses the Cardinal Virtues to answer a question given a data set. Although its primary use is for the main chapters in the Primer, it could be used for independent tutorials as well. The letters `XX` are used to indicate locations which require editing. Comments with instructions are interspersed. Read https://ppbds.github.io/primer/key-concepts.html for details on the Cardinal Virtues. -->

<!-- Once you decide the appropriate replacement for `fit_XX` and `XX.qmd`, you can do a global replace to fix them all. -->

<!-- Once you have followed an instruction, you should delete it. -->

<!-- How much hand-holding you do depends on tutorial number. For tutorial 4, we would want to provide the same sort of questions and verbiage as we see in Project #2 in the RStudio and Github tutorial. For tutorial 10, we can go much more quickly. -->

<!-- Note that the questions are a mixture of our three types: code, written (with answer) and written (without answer). The last is only (?) used for questions in which we ask the student to run a command like `show_file()`. Otherwise, we always provide an excellent written answer because students will generally look closely at our answer because they are concerned about whether or not their written answer matches ours. -->

<!-- Whenever you tell a student to make a change in the QMD. You should tell them to `Command/Ctrl + Shift + K` in order to render the document. This will also cause it to be saved. This is good practice for catching bugs early. (Professionals do this.) Then, the last step in these exercises is often some version of show_file() and then CP/CR. -->

<!-- Make use of `show_file("tutorial-6.qmd", start = -5)` to get just the last 5 lines of the QMD. We don't want students to both copy/pasting the whole document. We also don't need to ensure that we get whatever it is that was just changed. We never look! Instead, we are just plausibly threatening to look.  -->

<!-- There are many opportunities for knowledge drops, especially after definition questions. Use them! Point out something about the details of the particular problem from the chapter. Recall that students generally won't read the chapter, so we need to pull out the highlights. -->

<!-- Most of the questions in the Temperance section relate to constructing a graphic. This leads lots of opportunities for knowledge drops. This is a good place to mention items from Courage which you might not have had room for in that section. -->

<!-- Make sure to uncomment the test code chunks once you have created the necessary objects. -->

<!-- Always create any modeling objects and then save them in data/ by hand. Then, when building the tutorial, just read in the object. See the below example. This is also discussed in Instructions for Writing Tutorials.

Note that the commented code is run once, by hand, but saved so that it could be modified in the future. The fit_gauss assignment is run every time one hits Run Tutorial. But it is fast, so there is no cost. -->

<!-- #fit_gauss <- brm(formula = att_end ~ treatment, -->
<!-- #             data = trains, -->
<!-- #             family = gaussian(), -->
<!-- #             silent = 2, -->
<!-- #             refresh = 0, -->
<!-- #             seed = 9) -->
<!-- #write_rds(fit_gauss, "data/fit_gauss.rds") -->

<!-- fit_gauss <- read_rds("data/fit_gauss.rds") -->


<!-- Future improvements to make in this document:

Turn it into a vignette at some point? 

In the same way that we give several quotes to choose from at the start of each section, we ought to give several different knowledge drops to choose from, in order of sophistication, for many of the standard questions, especially related to things like families and link functions. No need for authors to reinvent the wheel. 

Would be nice if part of the testing would run all the object creation code so that we can be sure all that code works. But that would have to be during testing only.
-->


## Introduction
### 

This tutorial covers [Chapter XX: XX](https://ppbds.github.io/primer/XX.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 

## Wisdom
### 

<!-- XX: Pick one. -->

*The only true wisdom is in knowing you know nothing.* - Socrates
*Patience is the companion of wisdom.* - Saint Augustine
*Wonder is the beginning of wisdom.* - Socrates
*Wisdom begins in wonder.* - Plato
*The doorstep to the temple of wisdom is a knowledge of our own ignorance.* - Benjamin Franklin
*It is the province of knowledge to speak, and it is the privilege of wisdom to listen.* - Oliver Wendell Holmes Sr.
*All we can know is that we know nothing. And that’s the height of human wisdom.* - Leo Tolstoy

<!-- Update on Wisdom introduction. It should always include a quote. Then it asks the general question, indented and italized. Then it asks the specific question, also indented and italized. This is exactly the way the Primer works. There might also be some explanatory sentences around that, and the use of triple hashes to force a "Continue" button. -->

### Exercise 1

In your own words, describe the key components of Wisdom when working on a data science problem.

```{r wisdom-1}
question_text(NULL,
	message = "Wisdom requires the creation of a Preceptor Table, an examination of our data, and a determination, using the concept of validity, as to whether or not we can (reasonably!) assume that the two come from the same population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: You have the opportunity, in this and the next few questions, to drop a lot of knowledge about the data and the overall topic. Do so! But, remember, students won't read more than 2 or so sentences in a knowledge drop. -->

<!-- Not only are you discussing the data, but you are also discussing potential problems with the data, problems which will be more fully fleshed out in the Justice section. You want to pick 5 to 10 interesting facts about the data. (You may need to go to the original source, not simply relying on the chapter.) 

You won't be drawing any conclusions or discussing explicit violations with any assumptions. That discussion is saved until Justice and the specific questions about stability and representativeness. You are, hwoever, providing the details which you and the students can then use later. -->

### Exercise 2

Define a Preceptor Table.

```{r wisdom-2}
question_text(NULL,
	message = "A Preceptor Table is the smallest possible table of data with rows and columns such that, if there is no missing data, we can easily calculate the quantities of interest.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 3

Describe the key components of Preceptor Tables in general, without worrying about this specific problem. Use words like "units," "outcomes," and "covariates."

```{r wisdom-3}
question_text(NULL,
	message = "The rows of the Preceptor Table are the units. The outcome is at least one of the columns. If the problem is causal, there will be at least two (potential) outcome columns. The other columns are covariates. If the problem is causal, at least one of the covariates will be a treatment.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX. Insert questions for setting up repo/project/.gitignore. In later tutorials, this might all be accomplised in one question. In earlier tutorials, you would want to break this up into different questions. But, you must set up a Github repo (with a sensible name like `tutorial-x`), connect it to an R project of the same name, edit the .gitignore to include `*Rproj` and then commit/push everything. A reasonable last quetsion is show_file(".gitignore"). CP/CR. -->

### Exercise 4

What are the units for this problem?

```{r wisdom-4}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 5

What is/are the outcome/outcomes for this problem?

```{r wisdom-5}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 6

<!-- XX. You will probably need to make this question much more specific. In other words, you want the student to list some of the covariates that one might consider. We are not just looking for the select few covariates which will end up in the model. -->

What are some covariates which you think might be useful for this problem, regardless of whether or not they might be included in the data?

```{r wisdom-6}
question_text(NULL,
	message = "XX. Answer should be some sensible variables which are plausibly connected to the outcome. Some should be in the data but some shouldn't. You might also add that `You need to have variable X` if the question itself mentions that variable.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 7

What are the treatments, if any, for this problem?

```{r wisdom-7}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 8

What moment in time does the Preceptor Table refer to?

```{r wisdom-8}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Next three questions are only included for a causal model. -->

### Exercise 9

Define causal effect.

```{r wisdom-9}
question_text(NULL,
	message = "A causal effect is the difference between two potential outcomes.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 10

What is the fundamental problem of causal inference?

```{r wisdom-10}
question_text(NULL,
	message = "The fundamental problem of causal inference is that we can only observe one potential outcome.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 11

How does the motto "No causal inference without manipulation." apply in this problem?

```{r wisdom-11}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: End causal model section. If there is not one, you will need to run Format Tutorial Chunk Labels in order to renumber the exercises once you delete these.  -->

### Exercise 12

Describe in words the Preceptor Table for this problem.

```{r wisdom-12}
question_text(NULL,
	message = "XX.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The Preceptor Table for this problem looks something like this:

<!-- XX. Show the Preceptor Table. You can just copy/paste the code from the Primer. -->


### Exercise 13

<!-- XX: It is a feature that this question almost forces students to go to the chapter and read about the data. This entire sentence will not be included in your summary at the end of Wisdom, but bits of it will be mentioned. -->

Write one sentence describing the data you have to answer your question.

```{r wisdom-13}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX. Insert a question or two which accomplishes the second chunk of QMD work. This begins with the creation of an `analysis.qmd` file (although you can use any name for it), its rendering to ensure that your computer setup is correct. The addition of *_files to the .gitignore so that we do not commit those junk files. It ends with a commit and push. show_file(".gitignore", start = -5) is not a bad last question. -->

### Exercise 14

Load the **tidyverse** package.

```{r wisdom-14, exercise = TRUE}

```

```{r wisdom-14-hint-1, eval = FALSE}
library(...)
```

```{r wisdom-14-test, include = FALSE}
library(tidyverse)
```

### 

<!-- XX: Insert comments about the data. This continues to be the primary type of knowledge drop. These comments can also be sophisticated, especially in th way that they connect the data to the Preceptor Table and to the population. -->

<!-- XX: Load any other packages that are needed, one package per question. (But make sure that they are also included in the setup chunk.) primer.data, for example, is often needed. But save brms and tidybayes for the Courage section. -->

<!-- XX: It is now time for the third set of QMD edits. Add a new code chunk, the setup chunk, to the QMD. Copy/paste all the library commands to it. Render. Note all the ugliness. Add #| message: false. Add execute: echo: false to the YAML header. Add #| label: setup. Render again. Everything looks nice. Again, these could be several questions in the earlier tutorials or just one long question later. Ends with show_file("analysis.qmd", start = -5). This will be the most common ending question in QMD-editing exercises to come. -->

<!-- XX: Add code questions about EDA with your data. In particular, add at least one question about the dependent variable in the model along with one or more questions about covariates. If there is a treatment variable, you must include a question about it. -->

<!-- Variable questions come in two types. First there are questions which require the student to run, say, summary() on the variable. Then, knowledge about the variable can be dropped. Second, there are questions which ask for a one sentence summary about the variable, something which could be used in our summary of the project. For example: "Civility is measured on a 1 through 7 scale with higher values corresponding to greater civility." -->

<!-- XX: If necessary, provide code exercises which, line-by-line, create the pipeline which creates the cleaned data that will be used in modeling. For many tutorials, this is unnecessary since we can just use the raw tibble that is available in whatever package. But we sometimes need some code like

nes |> 
  filter(year == 1992) |> 
  drop_na()

We have three code exercises, each adding one line to the pipeline, explaining what we are doing and why. It is nice that, for each exercise, something is spat out.
-->

<!-- XX: If such a pipeline was built, there is one QMD question which requires that you add a new code chunk to the QMD, copy/paste the pipeline and assign the result to some object like `model_data` or whatever:

nes_92 <- nes |> 
  filter(year == 1992) |> 
  drop_na()

`Command/ctrl + Shift + K` follows, perhaps with a show_file("analysis.qmd", start = -5)
-->


### Exercise 15

In your own words, define "validity" as we use the term.

```{r wisdom-15}
question_text(NULL,
	message = "Validity is the consistency, or lack thereof, in the columns of the data set and the corresponding columns in the Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 16

Provide one reason why the assumption of validity might not hold for this problem.

<!-- This is an important question, as are the similar questions for other assumptions! Spend some time making sure that your example answer is a good one. -->

```{r wisdom-16}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 17

<!-- XX: In creating your own answer to questions like this, check with the chapter. One might already be provided! If not, it is often useful to revisit the relevant section of the Key Concepts chapter in the Primer. -->

<!-- Example: *Using data from a 2012 survey of Boston-area commuters, we seek to understand the relationship between income and political ideology in Chicago and similar cities in 2020. In particular, what percentage of individuals who make more than $100,000 per year are liberal?* -->

<!-- It is very difficult to craft a question which causes students to give a sentence that is good. Do your best. -->

Summarize the state of your work so far in one sentence. Make reference to the data you have and to the specific question you are trying to answer. 


```{r wisdom-17}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Edit you answer as you see fit, but do not copy/paste our answer exactly. Add this summary to `XX.qmd`, `Command/Ctrl + Shift + K`, and then commit/push.

<!-- XX: As always, we like to do something in the tutorial before we do it in the QMD. But, in this case, we can just include the directions in the knowledge drop for the last question. -->


## Justice
### 

<!-- XX: Choose one. -->

*Justice is truth in action.* - Benjamin Disraeli
*The arc of the moral universe is long, but it bends toward justice.* - Theodore Parker
*Justice delayed is justice denied.* - William E. Gladstone
*It is in justice that the ordering of society is centered.* - Aristotle
*Charity is no substitute for justice withheld.* - Saint Augustine

### Exercise 1

In your own words, name the four key components of Justice for working on a data science problem.

```{r justice-1}
question_text(NULL,
	message = "Justice concerns four topics: the Population Table, stability, representativeness, and unconfoundedness.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

In your own words, define a Population Table.

```{r justice-2}
question_text(NULL,
	message = "The Population Table includes a row for each unit/time combination in the underlying population from which both the Preceptor Table and the data are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 3

In your own words, define the assumption of "stability" when employed in the context of data science.

```{r justice-3}
question_text(NULL,
	message = "Stability means that the relationship between the columns in the Population Table is the same for three categories of rows: the data, the Preceptor Table, and the larger population from which both are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Keep just one of these two. -->

<!-- Stability is all about *time*. Is the relationship among the columns in the Population Table stable over time? In particular, is the relationship --- which is another way of saying "mathematical formula" --- at the time the data was gathered the same as the relationship at the (generally later) time references by the Preceptor Table. -->

<!-- *The longer the time period covered by the Preceptor Table (and the data), the more suspect the assumption of stability becomes.*  -->

### Exercise 4

Provide one reason why the assumption of stability might not be true in this case.

```{r justice-4}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 5

In your own words, define the assumption of "representativeness" when employed in the context of data science.

```{r justice-5}
question_text(NULL,
	message = "Representativeness, or the lack thereof, concerns two relationship, among the rows in the Population Table. The first is between the Preceptor Table and the other rows. The second is between our data and the other rows.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Keep one of these. -->

<!-- Ideally, we would like both the Preceptor Table *and* our data to be random samples from the population. Sadly, this is almost never the case. -->

<!-- Stability looks across time periods. Reprentativeness looks within time periods. -->

<!-- The more expansive your Preceptor Table, the more important the assumption of representativeness becomes. -->

### Exercise 6

Provide one reason why the assumption of representativeness might not be true in this case.

```{r justice-6}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 7

In your own words, define the assumption of "unconfoundedness" when employed in the context of data science.

```{r justice-7}
question_text(NULL,
	message = "Unconfoundedness means that the treatment assignment is independent of the potential outcomes, when we condition on pre-treatment covariates.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Keep one. -->

<!-- This assumption is only relevant for causal models. We describe a model as "confounded" if this is not true.  -->

<!-- The easiest way to ensure unconfoundedness is to assign treatment randomly. -->

### Exercise 8

<!-- XX: Delete this question for non-causal models. -->

Provide one reason why the assumption of unconfoundedness might not be true (or relevant) in this case.

```{r justice-8}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 9

Summarize the state of your work so far in two or three sentences. Make reference to the data you have and to the question you are trying to answer. Feel free to copy from your answer at the end of the Wisdom Section. Mention one specific problem which casts doubt on your approach. 


```{r justice-9}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: We could pull this out as a new question, includin show_file(), but that probably isn't necessary. -->

Edit the summary paragrpah in `XX.qmd` as you see fit, but do not copy/paste our answer exactly. `Command/Ctrl + Shift + K`, and then commit/push.


## Courage
### 

<!-- XX: Choose one. -->

*Courage is found in unlikely places.* - J.R.R. Tolkien
*Courage is being scared to death, but saddling up anyway.* - John Wayne
*Courage is going from failure to failure without losing enthusiasm.* - Winston Churchill
*Courage is the commitment to begin without any guarantee of success.* - Johann Wolfgang von Goethe


<!-- Questions about models, tests, and the DGM. -->


### Exercise 1

In your own words, describe the components of the virtue of Courage for analyzing data.

```{r courage-1}
question_text(NULL,
	message = "Courage begins with the exploration and testing of different models. It concludes with the creation of a Data Generating Mechanism.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

Load the **brms** package.

```{r courage-2, exercise = TRUE}

```

```{r courage-2-hint-1, eval = FALSE}
library(...)
```

```{r courage-2-test, include = FALSE}
library(brms)
```

### 

<!-- XX: The Courage section of each chapter is the most complex because modeling is hard. Use opportunities for knowledge drops, like this one, judiciously. -->

### Exercise 3

Load the **tidybayes** package.

```{r courage-3, exercise = TRUE}

```

```{r courage-3-hint-1, eval = FALSE}
library(...)
```

```{r courage-3-test, include = FALSE}
library(tidybayes)
```

### 

### Exercise 4

Add `library(brms)` and `library(tidybayes)` to `XX.qmd`. `Command/Ctrl + Shift + K`. At the Console, run:

```
tutorial.helpers::show_file("XX.qmd", pattern = "brms|tidybayes")
```

CP/CR.

```{r courage-4}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

<!-- XX: For a knowledge drop, there is nothing wrong with discussion regular expressions, which is the magic which allows us to just pull out the two lines in the QMD which we want. But better would just be more Courage knowledge drops. -->


### Exercise 5

Create a model using `brm()` from the **brms** package. Your arguments should be XX. 

<!-- Search and replace "fit_XX" as appropriate. As a convention, the name of a fitted model object should always start with `fit_`. -->

<!-- Don't forget to create this model yourself in the setup chunk. Do this once, save the object, comment out that code and then just read_rds to create the object for his tutorial. -->


```{r courage-5, exercise = TRUE}

```

```{r courage-5-hint-1, eval = FALSE}

```

<!-- XX: Note how there is no test case. If there were one, then a student would fit the model each time she hit "Run Tutorial." That takes too much time. -->

### 

### Exercise 6

Behind the scenes, we have assigned the result of the `brm()` call to an object named `fit_XX`. Type `fit_XX` and hit "Run Code." This generates the same results as using `print(fit_XX)`.


```{r courage-6, exercise = TRUE}

```

```{r courage-6-hint-1, eval = FALSE}
fit_XX
```

```{r courage-6-test, include = FALSE}
# fit_XX
```

### 

<!-- XX Same some general words about the object. Note that we are about to go through the top 4 rows. -->


### Exercise 7

Run `family()` on `fit_XX`. `family()` provides information about the "family" of the error term and the link between it and the dependent variable. 

```{r courage-7, exercise = TRUE}

```

```{r courage-7-hint-1, eval = FALSE}
family(...)
```

```{r courage-7-test, include = FALSE}
# family(fit_XX)
```

### 

<!-- XX: This is a great location for explanations which get much more detailed in later chapters. That is, we want students to have a more sophisticated understanding of probability distributions, and there use in modeling, as we move through the Primer.

But, at a minimum, you would comment about how the family that is shown --- which is either gaussian, bernoulli or categorical --- is determined by the family argument which you passed in to the brm() call, and that you determined that by looking at the distribution of the output variable. Continuous means gaussian, 2 possible values means bernoullu, and 2+ possible values means categorical.

-->

In this case, XX . . .

### Exercise 8

Run `formula()` on `fit_XX`. `formula()` returns the statistical equation which relates the dependent variable to the independent variable(s). 

```{r courage-8, exercise = TRUE}

```

```{r courage-8-hint-1, eval = FALSE}
formula(...)
```

```{r courage-8-test, include = FALSE}
# formula(fit_XX)
```

### 

In this case, XX . . .

### Exercise 9

Run `nobs()` on `fit_XX`. The `nobs()` function returns the **n**umber of **obs**ervations.

```{r courage-9, exercise = TRUE}

```

```{r courage-9-hint-1, eval = FALSE}
nobs(...)
```

```{r courage-9-test, include = FALSE}
# nobs(fit_XX)
```

### 

In this case, XX

### Exercise 10

Write the mathematical formula for your model, using $\LaTeX$ math notation.

```{r courage-10}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Add the formula to `XX.qmd`. `Command/Ctrl + Shift + K`. Ensure that the formula is looks correct. 

### Exercise 11

Create a new code chunk in `XX.qmd`. Add two code chunk options: `label: model` and `cache: true`. Copy/paste the code from above for estimating the model using `brm()` into the code chunk, assining the result to `fit_XX`. 

`Command/Ctrl + Shift + K`. It may take some time to render `XX.qmd`, depending on how complex your model is. But, by including `cache: true` you cause Quarto to cache the results of the chunk. The next time you render `XX.qmd`, as long as you have not changed the code, Quarto will just load up the saved fitted object.

To confirm, `Command/Ctrl + Shift + K` again. It should be quick.

At the Console, run:

```
tutorial.helpers::show_file("XX.qmd", start = -8)
```

CP/CR.

```{r courage-11}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

### Exercise 12

Run `posterior_interval()` on `fit_XX`. The `posterior_interval()` function returns 95% intervals for all the parameters in our model.

```{r courage-12, exercise = TRUE}

```

```{r courage-12-hint-1, eval = FALSE}
posterior_interval(...)
```

```{r courage-12-test, include = FALSE}
# posterior_interval(fit_XX)
```

### 

In this case, XX . . .


### Exercise 13

Run `fixef()` on `fit_XX`. The `fixef()` returns information about the **fix**ed **ef**fects in the model.

```{r courage-13, exercise = TRUE}

```

```{r courage-13-hint-1, eval = FALSE}
fixef(...)
```

```{r courage-13-test, include = FALSE}
# fixef(fit_XX)
```

### 

In this case, XX . . .

<!-- XX: Consider adding questions about conditional_effects(), ranef() and other commands, if relevant. -->

### Exercise 14

Run `pp_check()` on `fit_XX`. The `pp_check()` runs a **p**osterior **p**redictive check.

```{r courage-14, exercise = TRUE}

```

```{r courage-14-hint-1, eval = FALSE}
pp_check(...)
```

```{r courage-14-test, include = FALSE}
# pp_check(fit_XX)
```

### 

In this case, XX

<!-- If the fake data had looked very different from the real data, we have had a problem. But, for the most part, we conclude that, although not perfect, pp_check() shows that the fake outcomes generated by our model are like the actual outcome data. -->


### Exercise 15

Use `library()` to load the [**gtsummary**](https://www.danieldsjoberg.com/gtsummary) package.

```{r courage-15, exercise = TRUE}

```

```{r courage-15-hint-1, eval = FALSE}
library(gtsummary)
```

```{r courage-15-test, include = FALSE}
library(gtsummary)
```

### 

<!-- Drop some knowledge about gtsummary. Or say something more about your DGM. -->

### Exercise 16

<!-- XX: This can be just one question or several, especially if you want to teach some more gtsummary or gt tricks. Make any adjustments to this question, like `intercept = TRUE`, so that this question works. -->

Pipe `fit_XX` to `tbl_regression()`.


```{r courage-16, exercise = TRUE}

```

```{r courage-16-hint-1, eval = FALSE}
fit_XX |> 
  tbl_...()
```

```{r courage-16-test, include = FALSE}
# fit_XX |> 
#   tbl_regression()
```

### 

<!-- XX: Drop some knowledge about what you have learned by looking at the resulting table. Of course, you could have learned the same thing when you first took a look at fit_XX. But the table makes it easier to see the relationships between the variables and the outcome. With luck, students will take the hint when they answer the next question. -->

<!-- https://www.danieldsjoberg.com/gtsummary/articles/tbl_regression.html -->


### Exercise 17

Write a few sentence which summarize your work so far. The first few sentences are the same as what you had at the end of the Justice Section. Add one sentence which describes the modelling approach which you are using, specifying the functional form and the dependent variable. Add one sentence which describes the *direction* (not the magnitude) of the relationship between one of your independent variables and your dependent variable.

```{r courage-17}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 18

Update `XX.qmd`. First, add `library(gtsummary)` to the `setup` code chunk,. Second, add the mathematical formula, in $\LaTeX$ and surrounded by double dollar signs, for your model. Third, add a new code chunk which creates the table of model parameters. `Command/Ctrl + Shift + K` to ensure that everything works.

At the Console, run:

```
tutorial.helpers::show_file("XX.qmd", start = -8)
```

CP/CR.

```{r courage-18}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

## Temperance
### 

<!-- XX: Choose one. -->

*Temperance is a tree which as for its root very little contentment, and for its fruit calm and peace.* - Buddha
*Temperance is the greatest of all virtues. It subdues every passion and emotion, and almost creates a Heaven upon Earth.* - Joseph Smith Jr.
*Temperance is a bridle of gold; he, who uses it rightly, is more like a god than a man.* - Robert Burton
*Temperance is the firm and moderate dominion of reason over passion and other unrighteous impulses of the mind.* - Marcus Tullius Cicero
*Temperance to be a virtue must be free, and not forced.* - Philip Massinger
*Temperance is simply a disposition of the mind which binds the passion.* - Thomas Aquinas


### Exercise 1

In your own words, describe the use of Temperance in data science.

```{r temperance-1}
question_text(NULL,
	message = "Temperance uses the Data Generating Mechanism to answer the question with which we began. Humility reminds us that this answer is always a lie.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

What is the general topic we are investigating? What is the specific question we are trying to answer? 

```{r temperance-2}
question_text(NULL,
	message = "XX: Should be exactly how you started the Wisdom section.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Data science projects almost always begin with a broad topic of interest. Yet, in order to make progress, we need to drill down to a specific question. This leads to the creation of a data generating mechanism, which can now be used to answer lots of questions, thus allowing us to explore the original topic broadly.

### Exercise 3

To answer our question, we need to create a `newdata` object. Which variables do we need to include in this object?

```{r temperance-3}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 4

How many rows do we need in the `newdata` object? Recall that each row will generate a posterior for something. That is, if you have two rows in your `newdata` object, you will get two posteriors. It is up to you to determine what those two posteriors are and what you want to do with them.

```{r temperance-4}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 5

Which values do you want the variables in your `newdata` object to have? This is not easy! 

```{r temperance-5}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 6

Here is the R code which creates the `newdata` object: `tibble(whatever) code here`. Type it into the code exercise block and hit "Run Code."

<!-- Asking students to create this object --- even after you help them figure out the columns, rows and values --- is too hard, at least until they get more experiences. Your knowledge drop, for this question and the next, should give them advice on the broad topic of how they can create newdata objects themselves. -->

```{r temperance-6, exercise = TRUE}

```

```{r temperance-6-hint-1, eval = FALSE}

```

```{r temperance-6-test, include = FALSE}

```

### 

### Exercise 7

Behind the scenes, we have created the `ndata` object using this code. To confirm, type `ndata` and hit "Run Code."

<!-- Of course, you need to have added the code to create `ndata` in the setup chunk at the top of the file. -->

```{r temperance-7, exercise = TRUE}

```

```{r temperance-7-hint-1, eval = FALSE}

```

```{r temperance-7-test, include = FALSE}

```

### 

### Exercise 8

Now that we have the `newdata` object, we can create a pipe which uses out fitted model to answer our question. Begin by typing `fit_XX` and clicking "Run Code."

```{r temperance-8, exercise = TRUE}

```

```{r temperance-8-hint-1, eval = FALSE}

```

```{r temperance-8-test, include = FALSE}

```

### 

<!-- XX: Again, the main point of knowledge drops is this area is to explain to students why the newdata object looks the way it does and what it will produce. A great way to teach is via example. That is, explaining that if we had another way with these values, then we would get this posterior. Or, explaining what would be produced if we used add_epred instead of add_predict, and vice verse. -->


### Exercise 9

Pipe `fit_XX` to [XX: either `add_epred_draws()` or `add_predicted_draws()`] with the argument `newdata = ndata`.



```{r temperance-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-9-hint-1, eval = FALSE}

```

```{r temperance-9-test, include = FALSE}

```

### 

<!-- XX: How do students know whether to use add_epred_draws or add_predicted_draws? This is non-trivial. On some level, we just tell them with the above command. (We don't make them guess.) But we also address this issue explicitly in various knowledg drops, especially this one. -->

<!-- XX: Insert as many questions as necessary to build a nice-looking example of your final plot. In early chapters, this is simple since our questions are simple. They are just one posterior. In later chapters, they become more complex, with the inclusion of several posteriors, as well as manipulation of them to calculate causal effects and whatnot. See the voting postcard example. -->

### Exercise 10

Create a new code chunk in `XX.qmd`. Label it with `label: plot`. Copy/paste the code which creates your graphic. `Command/Ctrl + Shift + K` to ensure that it all works as intended.

At the Console, run:

```
tutorial.helpers::show_file("XX.qmd", start = -8)
```

CP/CR.

```{r temperance-10}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

### Exercise 11

Write a paragraph which summarizes the project in your own words. The first few sentences are the same as what you had at the end of the Courage section. But, since your question may have evolved, you should feel free to change those sentences. Add at least one sentence which describes at least one quantity of interest (QoI) --- presumably one that answers your question -- and which provides a measure of uncertainty about that QoI.

<!-- XX: Most of the time, there will be some measure of uncertainty associated with your QoI. But not always! The most common counter-example involves a question which asks about the odds or probability of something happening. We would answer such a question by simulating the event with `add_predicted_draws()`. We would then calculate the odds/probability of something happening by seeing how many of the 4,000 draws met the criteria for the event. Assume that was 40%. So, we think that there is a 40% chance that event A will happen. Yet there is no uncertainty associated with that estimate because it, itself, is an expression of uncertainty. (DK: Flesh this out further.) -->

```{r temperance-11}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Edit the summary paragrpah in `XX.qmd` as you see fit, but do not copy/paste our answer exactly. `Command/Ctrl + Shift + K`.


<!-- XX: Again, spend time to make your recommended paragraph perfect. Study the examples in https://ppbds.github.io/primer/key-concepts.html closely. -->

### Exercise 12

Write a few sentences which explain why the estimates for the quantities of interest, and the uncertainty thereof, might be wrong. Suggest an alternative estimate and confidence interval, if you think either might be warranted.

```{r temperance-12}
question_text(NULL,
	message = "XX: This is another example in which the quality of your answer is important. You might or might not suggest an alternate estimate. I always adjust the estimate toward my own subjective sense of a longrun average and/or typical value and/or zero. But that is not necessary. However, you should always increase the confidence interval since the assumptions of your model are always false.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 13

Publish `XX.qmd` to Rpubs. Choose a sensible slug. Copy/paste the url below.

```{r temperance-13}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

### Exercise 14

Rearrange the material in `XX.qmd` so that the order is graphic, paragraph, math and table. Doing so, of course, requires sensible judgment. For example, the code chunk which creates the fitted model must occur before the chunk which creates the graphic. `Command/Ctrl + Shift + K` to ensure that everything works.

At the Console, run:

```
tutorial.helpers::show_file("XX.qmd")
```

CP/CR.

```{r temperance-14}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

Add `rsconnect` to the `.gitignore` file. You don't want your personal Rpubs details stored in the clear on Github. Commit/push everything.


## Summary
### 

This tutorial covered [Chapter XX: XX](https://ppbds.github.io/primer/XX.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 



```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
