---
title: "Wrangling A"
tutorial:
  id: "wrangling-a"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Chapter 2 Wrangling Data"
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(readxl)
library(png)
library(grid)


knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

# Dealing with external files in tutorials is confusing! The biggest problem is
# figuring out when things will be evaluated and where. There is some discussion
# here: https://rstudio.github.io/learnr/. It certainly seems that setup chunks
# are not evaluated until Run Code is pressed on the Exercise chunk.

# We need to get the example file into the working area for each question. I
# initially had this material in its own R code chunk. But then the function was
# not available when the tutorial was run from the Tutorial Pane. Why? 

# I used to believe that any objects which you always want around for the entire
# portfolio should be created here, in the main set-up chunk. That seems to both
# work (an object is available) and fail (you get a weird warning message about
# the object not being available).  For example, code which creates an object
# called `www` does work in that www is around for later questions, but it also
# makes this warning:

# Warning: Error in paste0: object 'www' not found

# Very confusing! Since everything works, this must be a weird evaluation timing
# issue . . .

# For some usage, you want to interact with the file in its main location,
# without copying it over. For that purpose, you need the path to where the
# package is installed.

# Is there a way to force the deletion of any previous work, whenever you
# install a new version of the package? (Maybe just changing the version number
# does this. Maybe using the `id` designation.) There seem to be at least two
# kinds of work that stay on. First, the answers which you have already given,
# which can be removed by hitting the Start Over button. Second, the html file
# itself seems to (often) be a previous version, rather than the latest.
```

<!-- Would be nice if running the code did not produce TRUE and the col types. But I can't think of a way to get rid of that, and still get the object printed out. -->


## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```


## CSV Files
###

We begin by learning how to use `read_csv()` to read in CSV files. "CSV" stands for **c**omma-**s**eparated **v**alues, meaning that the variable names and data values are separated by commas in the file.

### Exercise 1

```{r ex-1-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_1.csv"), ".")
```

Consider the contents of the `test_1.csv` file.

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"),
                     "test_1.csv")), sep = "\n")
```

Write code for reading this file in to R.


```{r ex-1, exercise=TRUE}

```

```{r ex-1-hint, eval=FALSE}
Use `read_csv()` and set the `file` argument to `test_1.csv`.
```

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_1.csv"),
         col_types = cols(a = col_double(),
                          b = col_double(),
                          c = col_double()))
```

The rest of the exercises in this tutorial are like this one. We aren't creating any new R objects. We are just reading in data from different files and looking at the resulting object, which will almost always be a tibble.

### Exercise 2

```{r ex-2-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_2.csv"), ".")
```

Consider the contents of the `test_2.csv` file. 

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"), 
                     "test_2.csv")), sep = "\n")
```

Write code for reading this file in to R.

```{r ex-2, exercise=TRUE}

```

```{r ex-2-hint, eval=FALSE}
Use the `skip` argument to skip the first two lines.
```

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_2.csv"),
         skip = 2,
         col_types = cols(a = col_double(),
                          b = col_double(),
                          c = col_double()))
```

There are many arguments to `read_csv()` which allow us to deal with data formatted in different ways. Many of these argument also apply to other functions for reading in data, like `read_excel()`.

### Exercise 3

<!-- Using col_names = FALSE -->

```{r ex-3-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_3.csv"), ".")
```

Consider the contents of the `test_3.csv` file. 

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"), 
                     "test_3.csv")), sep = "\n")
```

Write code for reading this file in to R.

```{r ex-3, exercise=TRUE}

```

```{r ex-3-hint, eval=FALSE}
Use the `col_names argument and set it to FALSE
```

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_3.csv"),
         col_names = FALSE)
        
```

### Exercise 4


```{r ex-4-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_3.csv"), ".")
```

Consider, again, the contents of the `test_3.csv` file. 

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"), 
                     "test_3.csv")), sep = "\n")
```

Write code for reading this file in to R. We want the variable names for these three columns to be `a`, `b` and `c`.

```{r ex-4, exercise=TRUE}

```

```{r ex-4-hint, eval=FALSE}
Use the `col_names` argument and set its argument to c("a", "b", "c") 
```

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_3.csv"),
         col_names = (c("a", "b", "c")),
         col_types = cols(a = col_double(),
                          b = col_double(),
                          c = col_double()))
```

### Exercise 5

```{r ex-5-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_5.csv"), ".")
```

Consider the contents of the `test_5.csv` file. Note the "." for the first value for `b`. In this file, a period indicates a missing value. **This is not always true.** Missing values can be indicated in many different ways. And, sometimes, a period is just a period.

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"), 
                     "test_5.csv")), sep = "\n")
```

Write code for reading this file in to R, making sure that the first value for `b` is NA.

```{r ex-5, exercise=TRUE}

```

```{r ex-5-hint, eval=FALSE}
Set the value of the `na` argument to "."
```

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_5.csv"),
         na = ".")
```


### Exercise 6


```{r ex-6-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_6.csv"), ".")
```

Consider the contents of the `test_6.csv` file. 

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"), 
                     "test_6.csv")), sep = "\n")
```

Write code for reading this file in to R.


```{r ex-6, exercise=TRUE}

```

```{r ex-6-hint, eval=FALSE}
Use the `comment` argument and set it to "#".
```

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_6.csv"),
         comment = "#")
```

### Exercise 7


```{r ex-7-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_7.csv"), ".")
```

Consider the contents of the `test_7.csv` file. 

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"), 
                     "test_7.csv")), sep = "\n")
```

Write code for reading this file in to R. Make sure that `grade` comes in as an integer variable.


```{r ex-7, exercise=TRUE}

```

```{r ex-7-hint, eval=FALSE}
set col_types to cols(grade = col_integer(),
                      student = col_character())
```

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_7.csv"),
         col_types = cols(
  grade = col_integer(),
  student = col_character()
))
```





## Excel Files
###

Excel is a spreadsheet program that use tables to analyze, store, or manipulate data. The tables are composed of cells which include text, numbers, or formulas.


### Exercise 1

```{r excel-1-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "excel_1.xlsx"), ".")
```

Consider the contents of the excel file `excel_1.xlsx`:

```{r}
file <- paste0(system.file("images/", 
                           package = "primer.tutorials"),
               "excel_1.png")
img <- readPNG(file)
grid.raster(img)
```

Write code for reading this file in to R. Use the `read_excel()` function from the **readxl** package. (You may assume that the package has already been loaded for you.)

```{r excel-1, exercise=TRUE}

```

```{r excel-1-hint, eval = FALSE}
Use `read_excel()` and set the `file` argument to `excel_1.xlsx`.
```


The result when your code is run should look like this:

```{r}
read_excel(paste0(system.file("www/", package = "primer.tutorials"), 
                 "excel_1.xlsx"))

```

### Exercise 2

```{r excel-2-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "excel_1.xlsx"), ".")
```

Let's once again consider the contents of `excel_1.xlsx`. However, we want to look at the second sheet of the file. **Note**: Sheet 1 is the default when looking at an Excel file, so the last exercise only showed us the contents of Sheet 1.


```{r}
file <- paste0(system.file("images/", 
                           package = "primer.tutorials"),
               "excel_2.png")
img <- readPNG(file)
grid.raster(img)
```

Write code for reading this file in to R.

```{r excel-2, exercise = TRUE}

```

```{r excel-2-hint, eval = FALSE}
Use the `sheet` argument to look at other sheets. Set `sheet` to "Sheet2".
```


The result when your code is run should look like this:

```{r}
read_excel(paste0(system.file("www/", package = "primer.tutorials"), 
                 "excel_1.xlsx"), sheet = "Sheet2")
```




<!-- ### More Stuff -->

<!-- Couple questions using col_types argument. Start with examples which show you reading in a number as a character, useful for postal codes, for example.  -->

<!-- Then, show how to use the result from running it initially to make the warning disappear. -->

<!-- Questions using read_delim to read in a csv file. Then, to read in a file with other deliminators, like spaces.  -->


<!-- Couple questions on read json? Like we do in the book? -->

<!-- Couple questions on reading in data from the web, like a Wikipedia table? -->

<!-- Couple questions on using an API? -->



