---
title: "Wrangling A"
tutorial:
  id: "wrangling-A"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 2: Wrangling -- A"
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(lubridate)
library(stringr)
library(skimr)
library(primer.data)
library(nycflights13)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 

# Key Data

cces_filt <- cces %>%
  filter(ideology %in% c("Conservative", "Not Sure", 
                        "Moderate", "Liberal")) 
```

<!-- DK: Put police data in primer.tutorials/inst/www and then adjut your link.  -->

<!-- DK: Make this 2 or 3 times longer. Lots of little questions. Things like left_join are so important that they deserve many, many questions. -->



```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

## Mutating Strings 
###

A string is one or more characters that are enclosed inside a pair of matching 'single' or "double quotes". We will now use various functions to manipulate strings

### Exercise 1

Run the following code. This downloads data on 2016 PA police complaints and saves it to an R object named `x`. For your convenience, this code will be included in all the following exercises. 

```{r str-1, exercise = TRUE}
x <- read_csv("https://raw.githubusercontent.com/lawanin/PA-policing-data/master/philly-clean.csv", col_types = cols())
```

### 

The argument `col_types = cols()` tells R to use its default reasoning to assign column types. R will still do this if this argument is omitted, but will also output a lengthy message telling you each column type it assigned.

### Exercise 2

Start a new pipe with `x`, i.e type `x` on a line below the `read_csv()` and then place the `%>%` operator after this `x`. Select the columns `po_race`, `district_occurrence`,`investigative_findings`, and `summary`. 

```{r str-2, exercise = TRUE}
x <- read_csv("https://raw.githubusercontent.com/lawanin/PA-policing-data/master/philly-clean.csv", col_types = cols())  



```

```{r str-2-hint, eval = FALSE}
x <- read_csv("https://raw.githubusercontent.com/lawanin/PA-policing-data/master/philly-clean.csv", col_types = cols())  

x %>% %>% 
  select(..., ..., ..., ...)
```

###

Use the arrow in the top right hand corner to navigate through all the columns. 

### Exercise 3

Copy/paste your pipe from the previous exercise, i.e. the `select()` function piped to `x`. Continue your pipe and use `mutate()` and `str_detect()` to create a new column called `race` with value `TRUE` when the column `summary` contains the string `"race"` and `FALSE` if it does not. The first argument in string detect is the column in which you want to detect a string, the second argument is the quoted string you want to detect. 

```{r str-3, exercise = TRUE}
x <- read_csv("https://raw.githubusercontent.com/lawanin/PA-policing-data/master/philly-clean.csv", col_types = cols()) 



```

```{r str-3-hint-1, eval = FALSE}
x %>% 
  select(po_race, district_occurrence, investigative_findings, summary) %>% 
  mutate(race = str_detect(..., "..."))
```

```{r str-3-hint-2, eval = FALSE}
x %>% 
  select(po_race, district_occurrence, investigative_findings, summary) %>% 
  mutate(race = str_detect(summary, "rac"))
```


### Exercise 4

Copy/paste your pipe from the previous exercise. Filter so that you keep rows only where the column `race` has value `TRUE`. 

```{r str-4, exercise = TRUE}
x <- read_csv("https://raw.githubusercontent.com/lawanin/PA-policing-data/master/philly-clean.csv", col_types = cols()) 




```

```{r str-4-hint, eval = FALSE}
x %>% 
  select(po_race, district_occurrence, investigative_findings, summary) %>% 
  mutate(race = str_detect(summary, "rac")) %>% 
  filter(race == TRUE) 
```

### 

There should be 415 rows in which the `race` column has value `TRUE`. Though it will work, `TRUE` does not need to be quoted when we filter because it is a boolean value. 

### Exercise 5

Copy/paste your pipe from the previous exercise. Use `mutate()` and `str_detect()` to create a new column called `physical` with value `TRUE` when the column `summary` contains the string `"physical"` and `FALSE` if it does not. Then filter so that you keep rows only when the column `physical` has value `TRUE`. 

```{r str-5, exercise = TRUE}
x <- read_csv("https://raw.githubusercontent.com/lawanin/PA-policing-data/master/philly-clean.csv", col_types = cols()) 





```

```{r str-5-hint, eval = FALSE}
x %>% 
  select(po_race, district_occurrence, investigative_findings, summary) %>% 
  mutate(race = str_detect(summary, "rac")) %>% 
  filter(race == TRUE) %>% 
  mutate(... = str_detect(..., "...")) %>% 
  filter(... == ...)
```


### 

There should be 111 columns in which both the race and the physical columns have value `TRUE`. 

### Exercise 6

Copy/paste your pipe from the previous exercise. Use `mutate()` and `str_sub()` to change the column `po_race` so that it only contains the first two letters of each state. The second argument should be the character position from where you want to start, and the third argument should be the character position where you want to end. 

```{r str-6, exercise = TRUE}
x <- read_csv("https://raw.githubusercontent.com/lawanin/PA-policing-data/master/philly-clean.csv", col_types = cols()) 



```

```{r str-6-hint-1, eval = FALSE}
x %>% 
  select(po_race, district_occurrence, investigative_findings, summary) %>% 
  mutate(race = str_detect(summary, "rac")) %>% 
  filter(race == TRUE) %>% 
  mutate(physical = str_detect(summary, "physical")) %>% 
  filter(physical  == TRUE) %>% 
  mutate(po_race = str_sub(..., ..., ...))
```

```{r str-6-hint-2, eval = FALSE}
x %>% 
  select(po_race, district_occurrence, investigative_findings, summary) %>% 
  mutate(race = str_detect(summary, "rac")) %>% 
  filter(race == TRUE) %>% 
  mutate(physical = str_detect(summary, "physical")) %>% 
  filter(physical  == TRUE) %>% 
  mutate(po_race = str_sub(po_race, 1, ...))
```

###

The "sub" in `str_sub()` stands for `substrings`. This function extracts "substrings" based on the `start` and `end` arguments.

### Exercise 7

Copy/paste your pipe from the previous exercise. Use `mutate()` and `str_c()` to add the string `"PA-"` in front of every string in the column `district_occurrence`. `str_c` **c**ombines two strings and its syntax is similar to `c()`. The first argument is what you want to appear first in the combined string, `"PA-"`. The second argument should be the name of the column, `district_occurrence`. 

```{r str-7, exercise = TRUE}
x <- read_csv("https://raw.githubusercontent.com/lawanin/PA-policing-data/master/philly-clean.csv", col_types = cols()) 



```

```{r str-7-hint-1, eval = FALSE}
x %>% 
  select(po_race, district_occurrence, investigative_findings, summary) %>% 
  mutate(race = str_detect(summary, "rac")) %>% 
  filter(race == TRUE) %>% 
  mutate(physical = str_detect(summary, "physical")) %>% 
  filter(physical  == TRUE) %>% 
  mutate(po_race = str_sub(po_race, 1, 2)) %>% 
  mutate(... = str_c("PA-", ...))
```

```{r str-7-hint-2, eval = FALSE}
x %>% 
  select(po_race, district_occurrence, investigative_findings, summary) %>% 
  mutate(race = str_detect(summary, "rac")) %>% 
  filter(race == TRUE) %>% 
  mutate(physical = str_detect(summary, "physical")) %>% 
  filter(physical  == TRUE) %>% 
  mutate(po_race = str_sub(po_race, 1, 2)) %>% 
  mutate(... = str_c("PA-", district_occurrence))
```

###

A useful context for this operation might be if we were going to add analogous data from another state into this tibble, which might have overlapping district numbers. 

###

Note that R assigned this column to a character variable. If this were a numeric variable, the command would still work. R would coerce the edited column from a numeric variable to a character variable. 


### Exercise 8

Copy/paste your pipe from the previous exercise. Use `mutate()` and `str_replace()` to replace the pattern `"Sustained "` with `"S"` in the column `investigative_findings`.  Note that we have included a space after the word "Sustained". Set the second argument to the pattern in the current vector which you want to change. Set the third argument to the replacement which you want to replace the pattern with. 

```{r str-8, exercise = TRUE}
x <- read_csv("https://raw.githubusercontent.com/lawanin/PA-policing-data/master/philly-clean.csv", col_types = cols()) 



```

```{r str-8-hint, eval = FALSE}
x %>% 
  select(po_race, district_occurrence, investigative_findings, summary) %>% 
  mutate(race = str_detect(summary, "rac")) %>% 
  filter(race == TRUE) %>% 
  mutate(physical = str_detect(summary, "physical")) %>% 
  filter(physical  == TRUE) %>% 
  mutate(po_race = str_sub(po_race, 1, 2)) %>% 
  mutate(... = str_c("PA-", district_occurrence)) %>% 
  mutate(investigative_findings = str_replace(investigative_findings, "... ", "..."))
```


### Exercise 9

Copy/paste your pipe from the previous exercise. Use `mutate()` and `str_replace()` to replace the pattern `"Finding"` with `"F"` in the column `investigative_findings`. 

```{r str-9, exercise = TRUE}
x <- read_csv("https://raw.githubusercontent.com/lawanin/PA-policing-data/master/philly-clean.csv", col_types = cols()) 



```

```{r str-9-hint, eval = FALSE}
x %>% 
  select(po_race, district_occurrence, investigative_findings, summary) %>% 
  mutate(race = str_detect(summary, "rac")) %>% 
  filter(race == TRUE) %>% 
  mutate(physical = str_detect(summary, "physical")) %>% 
  filter(physical  == TRUE) %>% 
  mutate(po_race = str_sub(po_race, 1, 2)) %>% 
  mutate(... = str_c("PA-", district_occurrence)) %>% 
  mutate(investigative_findings = str_replace(investigative_findings, "Sustained ", "S")) %>% 
  mutate(... = str_replace(..., "...", "..."))

```


## Factors 
###

Factors are categorical variables that may only take on a specified set of values. 

### Exercise 1

Use `select()` to look at the `ideology` variable of the `cces` data set.

```{r factors-1, exercise = TRUE}

```

```{r factors-1-hint, eval = FALSE}
cces %>% 
  select(...)
```

Look underneath the column name. Notice that this is a factor (`<fctr>`) variable. 


### Exercise 2

Use `str()` with the argument `cces$ideology`. On the line below, use `levels()` with the same argument. 

```{r factors-2, exercise = TRUE}

```

```{r factors-2-hint, eval = FALSE}
str(...)
levels(...)
```

### Exercise 3

Let's now get a frequency table as a tibble. Use `fct_count()` with the argument `cces$ideology`.

```{r factors-3, exercise = TRUE}

```

```{r factors-3-hint, eval = FALSE}
fct_count(...)
```

### Exercise 4

Now use `nlevels()` with the argument `cces$ideology` to find the number of existing levels.

```{r factors-4, exercise = TRUE}

```

```{r factors-4-hint, eval = FALSE}
nlevels(...)
```

### Exercise 5

Now try ordering the levels of `cces$ideology` by frequency. Start a pipe with `cces$ideology` and use the function `fct_infreq()`. Then on the line below, use `levels()` to display the new order of the levels. 

```{r factors-5, exercise = TRUE}

```

```{r factors-5-hint, eval = FALSE}
cces$ideology %>% 
  fct_infreq() 

levels(cces$ideology)
```

###

Compare this with the old order of the levels in Exercise 2 and the frequency table in Exercise 3.

### Exercise 6

Now `filter()` `cces` to only a few ideologies: `Conservative` , `Moderate`, `Liberal` and `Not Sure`. Save your work to an object named `cces_filt`.

```{r factors-6, exercise = TRUE}

```

```{r factors-6-hint-1, eval = FALSE}
Use %in%  and c() within filter(). Within c(), place the ideologies in quotes. 
```

```{r factors-6-hint-2, eval = FALSE}
cces_filt <- cces %>%
  filter(... %in% c(..., ..., ..., ...))
```

The ideologies are in quotes because they are not column names, but strings within the column. 

### Exercise 7

On a new line, use `nlevels()` with the argument `cces_filt$ideology`. The code which creates `cces_filt` has been included for you. Notice that you have  the same number of levels even though you have filtered to include fewer ideologies.

```{r factors-7, exercise = TRUE}
cces_filt <- cces %>%
  filter(ideology %in% c("Conservative", "Moderate", " Liberal","Not Sure"))


```

```{r factors-7-hint, eval = FALSE}
cces_filt <- cces %>%
  filter(ideology %in% c("Conservative", "Moderate", " Liberal","Not Sure"))

nlevels(...)
```

<!-- I had to pipe the code from the previous exercise in order to get the desired output. The code in the hint kept the output at 6 levels.
What worked for me was cces_filt <- cces %>% filter(ideology %in% c("Conservative" ...)) %>% droplevels() -->

### Exercise 8

Let's drop all the unused levels from `cces_filt`. Continue the pipe started for you and add the `droplevels()` function. 


```{r factors-8, exercise = TRUE}
cces_filt <- cces %>%
  filter(ideology %in% c("Conservative", "Moderate", " Liberal","Not Sure")) 

```

```{r factors-8-hint-1, eval = FALSE}
cces_filt <- cces %>%
  filter(ideology %in% c("Conservative", "Moderate", " Liberal","Not Sure")) %>% 
  droplevels()
```

### Exercise 9

On a new line, use `nlevels()` with the argument `cces_filt$ideology` to see how many levels exist after you dropped levels. The code which creates `cces_filt` has been included for you. 

```{r factors-9, exercise = TRUE}
cces_filt <- cces %>%
  filter(ideology %in% c("Conservative", "Moderate", " Liberal","Not Sure")) %>% 
  droplevels()
  

```

```{r factors-9-hint-1, eval = FALSE}
cces_filt <- cces %>%
  filter(ideology %in% c("Conservative", "Moderate", " Liberal","Not Sure")) %>% 
  droplevels()

nlevels(...)
```

## Lists
###

A list is the object which contains various data types such as logicals, integers, characters, and even another list!


### Exercise 1

Create a list with three items `a`, `b`, and `c`. Have `a` take on the values 1, 2, and 3. Have `b` take on the values 4, 5, and 6. Have `c` take on the values  7, 8, and 9. Assign your list to an object named `my_list`. 


```{r lists-1, exercise = TRUE}

```

```{r lists-1-hint-1, eval = FALSE}
Use the c() function to create the individual vectors for a, b, and c. 
```

```{r lists-1-hint-2, eval = FALSE}
my_list <- list(a = c(...), b = c(...), c = c(...))
```

### Exercise 2

Now, use `str()` with the argument `my_list`. 

```{r lists-2, exercise = TRUE}
my_list <- list(a = c(1, 2, 3), b = c(4, 5, 6), c = c(7, 8, 9))

```

### Exercise 3

Let's now extract a single component `a` from `my_list` using `[ ]`. The code for the creation of `my_list` has been included for you. 

```{r lists-3, exercise = TRUE}
my_list <- list(a = c(1, 2, 3), b = c(4, 5, 6), c = c(7, 8, 9))

```

```{r lists-3-hint-1, eval = FALSE}
You need to use quotation marks because a is a character.


```

```{r lists-3-hint-2, eval = FALSE}
str(my_list[" "])
```

### Exercise 4

Now, extract the number 5 from `my_list` using `[[]]` and `[ ]`.

```{r lists-4, exercise = TRUE}
my_list <- list(a = c(1, 2, 3), b = c(4, 5, 6), c = c(7, 8, 9))

```

```{r lists-4-hint-1, eval = FALSE}
Refer to the name of the list item in the double brackets, and the position in that item in the single brackets.
```

```{r lists-4-hint-2, eval = FALSE}
my_list[["..."]][...]
```


## Combining Data
###

Bringing together data from different sources is one of the most common data science tasks. 

### Exercise 1

Inspect the dataset `band_instruments2` and `band_members` by typing their names below and hitting Run Code.

```{r comb-1, exercise = TRUE}

```

Consider the discrepancies between the columns of `band_instruments2` and `band_members`. Predict, in your head, what will happen when you bind the rows of these two tibbles.

### Exercise 2

Use `bind_rows()` to join these two tibbles. 

```{r comb-2, exercise = TRUE}

```

```{r comb-2-hint, eval = FALSE}
bind_rows(..., ...)
```

### 

Though the first columns of both tibbles have similar information, because one is named `artist` and the other `band`, they remain separate `columns` after we bind the rows. 

### Exercise 3

Start a pipe with `band_instruments2`. Use `rename()` to change the name of the `artist` column to `name`. Assign this ouput to a new object called `band_instruments`. 

```{r comb-3, exercise = TRUE}

```

```{r comb-3-hint, eval = FALSE}
band_instruments <- band_instruments2 %>% 
  rename(name = ...names())
```

###

Remember that `rename()` takes the same syntax as `mutate()`.

### Exercise 4

Now use `bind_rows()` to join `band_instruments` and `band_members`. 

```{r question-combining-11, exercise = TRUE}

```

```{r question-combining-11-hint, eval = FALSE}
bind_rows(band_instruments, band_members)
```

###

The names are now all in one column. However, rows containing data about the same person in the two tibbles remain separate. 

### Exercise 5

`inner_join()` allows you to combine the contents of rows based on exact matches they have in one or more columns. Use `inner_join()` to join `band_instruments` and `band_members` and use the `by` argument to set the name of the column with matches to `name`. 

```{r comb-5, exercise = TRUE}

```

```{r comb-5-hint, eval = FALSE}
inner_join(..., ..., by = "...")
```

Without the `by` argument, `inner_join` will use all variables in common to join. The result would be the same here, since `name` is the only column with matching variables. 

### Exercise 6

Using `inner_join()`, Keith, who is not in the `band_members` tibble, and Mick, who is not in the `band_instruments` tibble, were excluded.  Use `left_join()` to combine the data in the rows in the same way as `inner_join()`, but keeping those who would have`N/A` values in some columns. Join the same tibbles, `band_instruments`, and `band_members`, and use the same column for the `by` argument. 


```{r, comb-6, exercise = TRUE}

```

```{r, comb-6-hint, eval = FALSE}
left_join(..., ..., by = "...")
```

<!-- DK: Could do some more. -->

## Date-Times 
###

Let's practice using some functions that work with date and time.

### Exercise 1

Run the `today()` and `now()` functions below.

```{r dttm-1, exercise = TRUE}

```

### Exercise 2

Now use the function `ymd()` to convert the string `date_1` below into the proper date-time format. 

```{r dttm-2, exercise = TRUE}
date_1 <- "2020-2-29"
```

```{r dttm-2-hint, eval = FALSE}
Use the argument date_1 within ymd()
```

###

`ymd()` stands for **y**ear, **m**onth, **d**ate.

### Exercise 3

Now make `date_2` a date-time.  Use the function `ymd_hms()`. Use the argument `tz` to set the timezone to `EST`.

```{r dttm-3, exercise = TRUE}
date_2 <- "2017-01-31 20:11:59"

```

```{r dttm-3-hint, eval = FALSE}
Use the function ymd_hms() with the argument date_2.
```

`hms()` stands for **h**our, **m**inute, **s**econd.

### Exercise 4

The following code below selects time-related data from the `flights` data set in the **nycflights13** package. Use `mutate()` to create a new variable `arrival`. `arrival` should be set to the function `make_datetime()` with all selected variables as its argument.

```{r dttm-4, exercise = TRUE}
flights %>% 
  select(year, month, day, hour, minute)
```

```{r dttm-4-hint, eval = FALSE}
flights %>% 
  select(year, month, day, hour, minute) %>% 
  mutate(... = make_datetime(year, ...,...,..., ...))
```


## Tidying Data
###

### Exercise 1

Run `relig_income` in the code chunk below. Notice how wide it is. 

```{r tidy-1, exercise = TRUE}

```

###

Instead of each religion having one row, each religion could have 10 rows, one for each income group. Arranged this way, the income groups, which are currently column headings would be located in one column. Each observation of religion and income would have its own row, and all the counts would be in one column.  

### Exercise 2

You can use the `pivot_longer()` to convert wide data to long data. Let's use the `pivot_longer` to tidy the `relig_income` data. Pivot all columns except for the `cols` to everything but the `religion` column. Set the argument `names_to` to "income" and `values_to` to "count". 

```{r tidy-2, exercise = TRUE}

```

```{r tidy-2-hint-1, eval = FALSE}
Consider using - to select the columns you do not want to pivot
```

```{r tidy-2-hint-2, eval = FALSE}
relig_income %>% 
  pivot_longer(cols = -religion,
               names_to = "...",
               values_to = "...")
```

### Exercise 3

Let's now look at the `us_rent_income` dataset. Call the data set below. 

```{r tidy-3, exercise = TRUE}

```

```{r tidy-3-hint, eval = FALSE}

```

###

Instead state having two rows, each state could have one row, with the two variables "income" and "rent" in their own columns. Arranged this way, the values in the current `estimate` column would populate the values of the new columns for rent and income, and the values in `moe` would populate two columns for the moe of rent and income. 

### Exercise 4

You can "spread" the keys in a key column across their own set of columns with the `pivot_wider()`. Use `pivot_wider()` to tidy the `us_rent_income` data. Set `names_from` to `variable` and set `values_from`  to `c(estimate, moe))`.


```{r tidy-4, exercise = TRUE}

```

```{r tidy-4-hint, eval = FALSE}
... %>% 
  pivot_wider(names_from = ..., 
              values_from = c(..., ...))
```

```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
