---
title: Final Project
author: David Kane and Tejas Mundhe
tutorial:
  id: final-project
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: Terminal Tutorial
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

<!-- How do we check things like the existence of an About page? How do we check that that About page has what we want? -->


<!-- There are two ways to confirm details of final project: url to Github pages or interaction with R project on student computer. Maybe best is to tell them to open up this tutorial from within the RStudio instance which is showing their final project project. Then you know where stuff is. -->

<!-- About page should have a link to the Github repo. An email address for contacting you. Check with grep from the Terminal. And a link to Kane’s Free High School Data Science Bootcamp. -->

<!-- Make sure that the index.Rmd page is cool, grabs the readers attention. Must show nice plot at top. -->

<!-- Make sure "About this site -->
<!-- Additional details about this project" and other junk is gone. -->

<!-- Also delete garbage from index.Rmd, like "Learn more about creating websites" -->

<!-- Check out the Github repo for their project. Github repo should not be "final project". Must be descriptive! Good occasion to teach them how to change the name of a Github repo. -->

<!-- TM: Done Create the four sentences. First sentence includes the key nouns in the title, either as a simple statement like "This is important" or a rhetorical question. Fourth sentence is the key takeaway that you want people to remember, almost always a statistical claim about how variable X varies with variable Y. Second and third sentences are about your data. Where did you get it? How did you clean it? How are variables X and Y measured and defined. Give examples, both before and after. Last question is write your entire summary.  -->

<!-- Fill out the spreadsheet. https://docs.google.com/spreadsheets/d/1ORlFaqPAVZAwPc6vP0GDWyzuyhiTCzgvSiRLu5nfomE/edit?usp=sharing -->

<!-- Minimize the stuff in the index.Rmd. You will knit this file a million times. So, remove all stuff from there that you can.  -->

<!-- Something which shows you added some code comments. -->



## Introduction
### 

Your final project is the first entry in your professional portfolio. Few employers will ever ask to see your high school or college transcripts. They will want to see what you can **do**, what you can **make** with your own two hands. 


## Pimp Your Github Account
### 

Your Github account should look professional. Read [this essay](https://www.davidkane.info/post/2020-01-18-pimp-my-github/) for details about what that means. This section will guide you. 

### Exercise 1

Write a bio for your Github account. Once you have added it to your account, copy and paste the bio below.

### 

```{r pimp-your-github-acc-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    rows = 6)
```


### Exercise 2

Add a photo to your Github account. You do not have to use a photo of yourself — some people are shy — but you should use something other than the GitHub default.


###

Once the photo is uploaded, you can click on it and a URL will appear. It will looking something like this:

https://avatars.githubusercontent.com/u/some-number-and-stuff

Copy/paste the url for your photo here:


```{r pimp-your-github-acc-2}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 1)
```


### Exercise 3

Pin the repo(s) that you are most proud of. Your final project repo should be first.

###

Paste the URL of your pimped github account below. It should looks like `github.com/your-username`.

```{r pimp-your-github-acc-3}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 1)
```

## Meet Final Project Requirements
###
Now, we'll make sure that your final project has everything it needs to look professional.


## Create Your Project Summary
### 

Next we'll be making a four sentence summary of your final project. This will be how each of your presentations begins.

### Exercise 1

The first sentence includes the key nouns in the title, either as a simple statement or a rhetorical question.

###
Enter your first sentence in the box below. For example, "COVID-19 has affected people from all sorts of educational backgrounds".

```{r final-project-summary-1}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 2)
```

###
A good first sentence will set the foundation for the rest of the introduction while keeping the listener engaged.

### Exercise 2

Next we'll be making our fourth sentence(Yes we're going out of order). This should include the key takeaway from your project that you want people to remember, almost always a statistical claim about how variable X varies with variable Y.

###
Enter your fourth sentence in the box below. For example, "The biggest wage gap is in the financial industry where men earn on average $45,000 more than women do."

```{r final-project-summary-2}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 2)
```

###
You will highlight this observation when it is seen through your plots during your presentation.

### Exercise 3
The second and third sentences are all about your data. Where did you get it? How did you clean it? How are variables X and Y measured and defined? 

###

Enter your second and third sentences into the box below. For example, "The following data is sourced from a Kaggle community-provided dataset scraped from the 774 WEBTOON series that are company-sponsored and thus reach more viewers on their platform. Though cut-and-dry figures are not the sole indicator of a "good" WEBTOON, figures like the series ratings can identify patterns in Originals that statistically perform well among readers."

```{r final-project-summary-3}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### Exercise 4
It's time to put all all 4 sentences together! Start by pasting your answer to Exercise 1, Exercise 3, and then Exercise 2(since we went out of order) in the answer box below.

```{r final-project-summary-4}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 5)
```

Read this aloud to make sure it sounds right and makes sense to the listener as a paragraph. If needed add transitions between sentences and extra information.

###

You're ready to practice presenting your final project in class!


<!-- TM: Add more examples? -->

## Final Project Spreadsheet
###
To "submit" your project, we'll be adding it as a row in [this spreadsheet](https://docs.google.com/spreadsheets/d/1ORlFaqPAVZAwPc6vP0GDWyzuyhiTCzgvSiRLu5nfomE/edit?usp=sharing). This section will guide you through that process.

<!-- TM: Will need to update spreadsheet link for each bootcamp -->

### Exercise 1
Open the spreadsheet linked above. In the first column enter your email. This should be your personal email(not associated with your school or organization). Enter your name in column two as well.

###
Paste the email you entered in the spreadsheet below.

```{r final-project-spreadsheet-1}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 2)
```

### Exercise 2
In the third column you should paste the link to your Github account. This should be the page that you personalized when you "Pimped your Github".

###
Paste this Github account link in the answer box below.

```{r final-project-spreadsheet-2}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 2)
```

### Exercise 3
Next we'll enter your project name in the fourth column. This should be a relatively short title which describes your project's topic in [Title case](https://en.wikipedia.org/wiki/Title_case).

###
Enter your project title below.

```{r final-project-spreadsheet-3}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 2)
```

### Exercise 4
In column 5, you'll enter the **Github Pages URL** to your project website. It should look like `your-username.github.io/your-repo-name/`. This should **NOT** be the URL to your final project GitHub Repo.

###
Enter this project URL in the box below.

```{r final-project-spreadsheet-4}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 2)
```

### Exercise 5
In the final column, you'll enter a one sentence takeaway of your project. This can be similar to your fourth sentence from the project summary you created earlier. Make sure you use proper spelling and grammar conventions.

###
Enter your takeaway sentence below.

```{r final-project-spreadsheet-5}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 2)
```

Make sure you have the same information in the tutorial and on the spreadsheet. You may also submit a picture or link of your project in the Final-Projects discord channel.

## Summary
### 

Your final project is the first entry in your professional portfolio. As long as you follow all the instructions in this tutorial, people (including professional data scientists) will be impressed.


```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
