---
title: Final Project
author: David Kane and Tejas Mundhe
tutorial:
  id: final-project
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: Terminal Tutorial
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

<!-- How do we check things like the existence of an About page? How do we check that that About page has what we want? -->


<!-- There are two ways to confirm details of final project: url to Github pages or interaction with R project on student computer. Maybe best is to tell them to open up this tutorial from within the RStudio instance which is showing their final project project. Then you know where stuff is. -->

<!-- About page should have a link to the Github repo. An email address for contacting you. Check with grep from the Terminal. And a link to Kane’s Free High School Data Science Bootcamp. -->

<!-- Make sure that the index.Rmd page is cool, grabs the readers attention. Must show nice plot at top. -->

<!-- Make sure "About this site -->
<!-- Additional details about this project" and other junk is gone. -->

<!-- Also delete garbage from index.Rmd, like "Learn more about creating websites" -->

<!-- Check out the Github repo for their project. Github repo should not be "final project". Must be descriptive! Good occasion to teach them how to change the name of a Github repo. -->

<!-- Create the four sentences. First sentence includes the key nouns in the title, either as a simple statement like "This is important" or a rhetorical question. Fourth sentence is the key takeaway that you want people to remember, almost always a statistical claim about how variable X varies with variable Y. Second and third sentences are about your data. Where did you get it? How did you clean it? How are variables X and Y measured and defined. Give examples, both before and after. Last question is write your entire summary.  -->

<!-- Fill out the spreadsheet. https://docs.google.com/spreadsheets/d/1ORlFaqPAVZAwPc6vP0GDWyzuyhiTCzgvSiRLu5nfomE/edit?usp=sharing -->

<!-- Minimize the stuff in the index.Rmd. You will knit this file a million times. So, remove all stuff from there that you can.  -->

<!-- Something which shows you added some code comments. -->



## Introduction
### 

Your final project is the first entry in your professional portfolio. Few employers will ever ask to see your high school or college transcripts. They will want to see what you can **do**, what you can **make** with your own two 


## Pimp Your Github Account
### 

Your Github account should look professional. Read [this essay](https://www.davidkane.info/post/2020-01-18-pimp-my-github/) for details about what that means. This section will guide you. 

### Exercise 1

Write a bio for your Github account. Once you have added it to your account, copy and paste the bio below.

### 

```{r pimp-your-github-acc-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    rows = 6)
```

### 


### Exercise 2

Add a photo to your Github account. You do not have to use a photo of yourself — some people are shy — but you should use something other than the GitHub default.


###

Once the photo is uploaded, you can click on it and a URL will appear. It will looking something like this:

https://avatars.githubusercontent.com/u/some-number-and-stuff

Copy/paste the url for your photo here:


```{r pimp-your-github-acc-2}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 1)
```

###

### Exercise 3


## Create Your Project Summary
### 



## Summary
### 

Your final project is the first entry in your professional portfolio. As long as you follow all the instructions in this tutorial, people (including professional data scientists) will be impressed.


```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
