---
title: "Terminal"
tutorial:
  id: "terminal"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Terminal Tutorial"
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(png)
library(grid)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

<!-- No files/directories with the same name as commands! -->

<!-- Make .jpg files .txt. -->

<!-- Use car.txt and hat.txt and bet.txt-->

<!-- Davids-MBP-10:wildcards davidkane$ ls a -->
<!-- ls: a: No such file or directory -->
<!-- Davids-MBP-10:wildcards davidkane$ ls a* -->
<!-- apple.txt -->
<!-- Davids-MBP-10:wildcards davidkane$ ls *a* -->
<!-- apple.txt       banana.txt -->
<!-- Davids-MBP-10:wildcards davidkane$  -->

<!-- Then ls > files.txt -->

<!-- Davids-MBP-10:wildcards davidkane$ ls $R_HOME > files.txt -->
<!-- Davids-MBP-10:wildcards davidkane$ cat files.txt -->
<!-- COPYING -->
<!-- Info.plist -->
<!-- R -->
<!-- Rscript -->
<!-- SVN-REVISION -->
<!-- bin -->
<!-- doc -->
<!-- etc -->
<!-- fontconfig -->
<!-- include -->
<!-- lib -->
<!-- library -->
<!-- man1 -->
<!-- modules -->
<!-- share -->
<!-- tests -->
<!-- Davids-MBP-10:wildcards davidkane$ grep i files.txt  -->
<!-- Info.plist -->
<!-- Rscript -->
<!-- bin -->
<!-- fontconfig -->
<!-- include -->
<!-- lib -->
<!-- library -->
<!-- Davids-MBP-10:wildcards davidkane$ grep R files.txt  -->
<!-- R -->
<!-- Rscript -->
<!-- SVN-REVISION -->
<!-- Davids-MBP-10:wildcards davidkane$ grep ^R files.txt  -->
<!-- R -->
<!-- Rscript -->
<!-- Davids-MBP-10:wildcards davidkane$ grep t files.txt  -->
<!-- Info.plist -->
<!-- Rscript -->
<!-- etc -->
<!-- fontconfig -->
<!-- tests -->
<!-- Davids-MBP-10:wildcards davidkane$ grep t$ files.txt  -->
<!-- Info.plist -->
<!-- Rscript -->
<!-- Davids-MBP-10:wildcards davidkane$  -->



## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```

## Introduction
###

The Terminal pane is next to the Console pane in the lower left portion of RStudio. We use the Console pane to talk to R. We use the Terminal pane to talk directly with the computer. Sadly, the Console and the Terminal speak different languages.

### Exercise 1

Hit return two times to see what happens. The terminal has a string of characters ending in a $ before your cursor, called the **prompt**. After a command has been executed, a prompt will be generated on a new line to let you know that Terminal is ready for a new command.  Copy and paste the three lines here.

###

```{r term-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### 

The prompt acts as a quick way to tell you where in the computer you are. 

### Exercise 2

Let's figure out where we are. To see your current location within your computer, type the command `pwd` (**p**resent **w**orking **d**irectory) in the Terminal. Hitting return runs the command. Copy and paste all commands and results associated with this exercise, as you will do for all the following exercises.  

###

```{r term-ex-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

<!-- NL: Is this a good explanation of the concept?  -->
In a given working directory, Terminal assumes that all files and directories, unless otherwise specified, are within that directory.

Notice how the last directory (folder) in the **path** is included in the prompt.

Your pasted code should look something like:

```{r}
file <- paste0(system.file("images/", 
                           package = "primer.tutorials"),
               "/pwd.png")
img <- readPNG(file)
grid.raster(img)
```

### 

Note how, if you do not give any more information, `ls` assumes that you want a list of what is in your working directory. 

### Exercise 3

Let's see a **l**i**s**t of what is where we are, i.e. in our working directory. Run `ls`. Copy and paste the work.

###

```{r term-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 4

Let's create a file called `my.txt`. Run`touch my.txt`. Run `ls` to confirm that the new file exists inside the working directory. Copy and paste the work.

###

```{r term-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

`touch` creates an empty file. 

### Exercise 5

Let's **m**ake a **dir**ectory called `my-class`. Run `mkdir my-class`. Run `ls` to confirm that the new directory exists inside the working directory. Copy and paste the work.

###
 
```{r term-ex-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

`mkdir` creates an empty directory. 

### Exercise 6

Let's rename `my.txt` to `fake.txt`.  Run `mv my.txt fake.txt`. Copy and paste the work. 

###

```{r term-ex-6}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

<!-- NL: Is this a good explanation of move as rename, particularly with the unreal distinction between place and location? -->
`mv` stands for **m**o**v**e. The first argument is the place we want to move from, the second argument is the place we want to move to. Here the places have the same location, but different names. We will move things to different locations with `mv` later. 

Your pasted code should look something like:
```{r}
file <- paste0(system.file("images/", 
                           package = "primer.tutorials"),
               "/mv.png")
img <- readPNG(file)
grid.raster(img)
```

### Exercise 7 

Let's **r**e**m**ove the file `fake.txt`. Run `rm fake.txt`. 

###

```{r term-ex-7}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

**Be careful** with the rm command in Terminal. Unlike moving files to Trash, it is not reversible. If you delete certain things, it could cause damage to programs or your computer. 

### Exercise 8

Let's remove the directory `my-class`. Run `rm -r my-class`. 

###

```{r term-ex-8}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

`-r` is an **option** that allows us to delete a directory. We will learn more about options later. 

It is good to clean up. Good work. 

## Paths
###

You will practice using paths both inside and outside the working directory. You will learn a few shorthands to make this easier. 

### Exercise 1

By default, the Terminal in RStudio starts with a working directory which is the same as the folder in which the current project resides, i.e., the folder with the .Rproj file in it. Run `pwd` to see your working directory. 

###

```{r term1-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### 

By default, the files pane (bottom right corner) in RStudio shows the contents of the default working directory. Towards the top, you will see a series of directories on your computer beginning with a home icon. This should match the latter part of the path generated by `pwd`. 

### Exercise 2

Use `mk-dir` to make a directory named `paths`. 

###

```{r term1-ex-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

As in the introduction, the new directory is created directly inside the working directory.

### Exercise 3

Let's **c**hange the working **d**irectory to `paths`. Run `cd paths`.  Run `pwd` to confirm that you have changed the working directory.

###

```{r term1-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 4

Use `mkdir` to make a directory within `paths` called `lessons`. 

###

```{r term1-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### 

Because we have changed working directories, the new directory is created directly inside the new working directory. 

### Exercise 5

Let's make a directory within `lessons` called `wildcards`. Run `mk-dir lessons/wildcards`. Run `ls lessons` to check to see if `wildcards` exists inside.

###

```{r term1-ex-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### 

We could not, as before, simply name the folder we wanted to create because then it would be created directly inside our working directory. To refer to a location that is not directly inside the present working directory, we need to use a path, which describes the location directory by directory. The path above is called a **relative path**, because it still assumes the working directory as its starting point. 

### Exercise 6

Let's change our working directory to `sisters`. Run `cd lessons/sisters`. 

###

```{r term1-ex-6}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

As you can see from comparing Exercise 4 and 5, the path to refer to a  file or directory does not change between commands. 

### Exercise 7

Use `touch` to make a text file inside `sisters`, named `hekabe.txt`.

###

```{r term1-ex-7}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

`hekabe.txt` is still a relative path, but since the location is directly inside the assumed starting point of the present working directory `wildcards`, the name of the file is all we need. If we had used `lessons/sisters/hekabe.txt`, as we would have if our working directory were `paths`, we would have gotten an error because those directories would not be recognized with an assumed starting point of `

### Exercise 8

Use `touch` to make two more text files inside `sisters`, named `theano.txt` and `does-not-belong`. 

###

```{r term1-ex-8}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 9

Let's change our working directory to `lessons`. Run `cd ..` to go to the folder immediately above the working directory. Use `pwd` to confirm that you are in the right directory. 

###

```{r term1-ex-9}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

<!-- NL: Is above the right term? -->
`..` is shorthand for the directory immediately above the  working directory. `.` is shorthand for the working directory. 

### Exercise 10

Use `mkdir` to make a directory within `lessons`, named `tbd`. 

###

```{r term1-ex-10}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 11

It would be tedious to have to use `..` every time we wanted to refer to anywhere outside of our working directory. To refer to a specific folder outside of the working directory, we need to use an **absolute path**. An absolute path, as opposed to the relative paths we have been using, describes a place on your computer without respect to a working directory. An absolute path begins with the root directory, which is represented by a lone `/`. This is what `pwd` returns. Click continue to see the exercise. 

###
 
<!-- Is default working directory a clearer term? -->
Let's go back to our original working directory. Go to Exercise 2 to find the absolute path of the original working directory. Run `cd` with this as an argument. For example: `cd /Users/user-name/Desktop/sample/original-working-directory`. 

###

```{r term1-ex-11}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

<!-- Reverse notes and question (have the omitted name be presented first) -->

### Exercise 12

Let's move the file `does-not-belong` so that it is directly inside of the working directory. Run `mv paths/lessons/sisters/does-not-belong .`. Remember the first argument is the place where we want to move the file from, the second argument is the place where we want to move the file to. Remember also that `.` is shorthand for the present working directory.

###

```{r term1-ex-12}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

If we are moving a file or directory without changing the name, we do not need to add the name in the second argument because `mv` will retain the name by default. `mv paths/lessons/sisters/does-not-belong ./does-not-belong` is equivalent to the command you ran. 

### Exercise 13

Use `cd` to change the working directory to `paths`. Use `mv` and the `.` shorthand to move the directory `tbd` directly inside of `paths`. 

###

```{r term1-ex-13}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

There is no difference between moving a directory and moving a file. 

### Exercise 14

Run `cd` alone. Now, use `pwd` to check where you are. This is called the **home directory**, which contains all a user's files. Run `ls` to see what is inside your home directory.

###

```{r term1-ex-14}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 15

Use `cd` to change the the working directory back to your original home directory. You can again use the absolute path from the `pwd` in Exercise 1. 

###

```{r term1-ex-15}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

Since the original working directory is within the home directory, the full absolute path was not necessary. We could have omitted the user-name and everything before it. 

### Exercise 16

Run `ls ~`. The list should be identical to the list you generated for Exercise 12 in the home directory.Because the home directory is used in the absolute path of so many files, its path (`/Users/your-user-name-here/`) can be written with the shorthand `~`. 

###

```{r term1-ex-16}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

The shorthands we have learned so far, `.`, `..`, `~`, stand for the text of the paths for the corresponding directory. They are not specific to any function and can be used in any sitatuion where the full text could be used. 

### Exercise 17

Let's change the working directory to a directory of your choice within the home directory using the shorthand `~`. Run, for example, `cd ~/Desktop`.

###

```{r term1-ex-17}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

Here, unlike Exercise 15, an absolute path was necessary because `Desktop`, for example, is not within our working directory.

### Exercise 18

Use `cd` to change back to the original working directory using the shorthand for the home directory to write its absolute path. 

###

```{r term1-ex-18}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

Depending on which folder you chose, an absolute path may or may not have been necessary.

### Exercise 19

Use `rm` to remove the file `does-not-belong` from our working directory. 

###

```{r term1-ex-19}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

It is good to clean up. 

### Exercise 20

Use `rm -r` to remove the directory `paths` from our working directory. 

###

```{r term1-ex-20}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

Good work.

## Options
###

You will learn more about what options are and use them for functions you already know. 

### Exercise 1

Use `pwd` to confirm that you are in your default working directory. Make a directory directly inside the working directory, named `options`.

###

```{r term2-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 2

Without changing directories, add a text file to the `options` directory, named `.my-hidden.txt` (make sure to include the `.`). 

###

```{r term2-ex-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### 
Other than the `.`, avoid beginning file names with special characters or including spaces. These are more difficult to work with in Terminal. 

### Exercise 3

Run `ls` to check if the file is inside `options`. If you did the previous exercise correctly, you should **not** see the new file. This is because we prefixed the name with the `.`,  which hid the file from normal view.  Run `ls -a my-class`. Using the **option** `-a`, you should be able to see **a**ll the files in `my-class`.

###

```{r term2-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

Options are regularly preceded by a `-` and come before the argument. 

Hidden files live all over your computer. You can turn on your ability to see hidden files in the R Studio files pane (bottom right corner) by clicking the "More" button towards the top. 

### Exercise 4

We have already gone over a few shorthands that stand for paths. The **environmental variable** `$R_HOME` represents the path to a folder of set-up files that R has installed on your computer. Type and enter `$R_HOME$` alone to make sure we are telling you the truth. Then change your working directory to `$R_HOME`. 

###

```{r term2-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### 

Environmental variables are always precedeed by `$`. Like the shorthand, they represent the text of the path and are not specific to any one function. 

### Exercise 5

Run `ls $HOME`. This should generate a list of the items in your home directory. `$HOME` is an environmental variable that represents the home directory.

###

```{r term2-ex-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

There are many different environmental variables for places throughout your computer. You can also make your own. 

### Exercise 6

Use `pwd` to confirm that you are still in `$R_HOME`. Use `ls` to see check what is inside `$R_HOME`. You should see several unfamiliar items. Because this directory is unfamiliar, we may want more information. Let's run `ls -l`, so that we can see more information in a **l**ong list. 

###

```{r term2-ex-6}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### 

In a long list,  names are in the last column and file type is in the first: if the string in the first column begins with `d` it is a **d**irectory; if it begins with  `-` it is a file; if it begins with `l` it is a **l**ink to another file on the computer .The middle columns give, from left to right, the number of files, author, permission, file size (bytes), date last modified.

### Exercise 7

Without changing directories, use `ls -l` to check what is inside the `doc` directory. 

###

```{r term2-ex-7}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

As you could guess from the name, the directory contains mostly files, including `AUTHORS`. 

### Exercise 8

Use `cd` to change your directory  to `options`. Use the absolute path from Exercise 1 if you need it.

###

```{r term2-ex-8}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 9

Let's make a copy of the `AUTHORS` file in `$R_HOME/doc` in `options` Use the command `cp`, whose syntax is identical to `mv`, and the `.` shorthand. 

###

```{r term2-ex-9}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

Like `mv`, `cp` can change a file name. Like `mv`, if the destination file name is omitted, `cp` will retain the same name by default. 

### Exercise 10

Try to use `cp` and `.` to copy the `doc` directory into `options`. You will get an error informing you that the thing you tried to copy was a directory. Run the same command using the option `-r`.

###

```{r term2-ex-10}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### 

As we have seen for `rm`, `-r` allows us to use `cp` with directories. This is different from `mv`, which does not need `-r`. 

### Exercise 11

Let's view just the initial lines of the `AUTHORS`. Run `head AUTHORS`

###

```{r term2-ex-11}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### 

Now you know how R got its name. 

### Exercise 12

Let's view more than just the initial 10 lines. The option `-n` allows you to specify the number of initial lines you want to see. This option takes an argument, for example, `-n 18`. Use this option to view a different number of the file's initial lines.

###

```{r term2-ex-12}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### 

The option `-n` takes an argument which allows head to display any number of initial lines. 

### Exercise 13

Use the command `tails` and the same `-n` option to view the last 15 lines of `AUTHORS`. 

###

```{r term2-ex-13}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

If the argument of -`n`is greater than the number of lines in the file, `head` or `tails` will print the whole file and stop. 

### Exercise 14

Let's view the whole file at once. Run `cat` AUTHORS.

###

```{r term2-ex-14}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

`cat` stands for con**cat**enate, which means "to chain together." While it is often used to a single text file, the command can take two arguments and print the files together. 

### Exercise 15

Run `cat -n AUTHORS`. Notice that `-n` has no argument. 

###

```{r term2-ex-15}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### 

`cat -n` prints the text file with line numbers. Note that the names end at line 28. 

### Exercise 16

Let's make our own text file. Start by running `echo` which takes a quoted string, for example, "Your First and Last Name Here" as its argument. This "echoes" the argument by printing it in the next line of the terminal.

###

```{r term2-ex-16}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 17

We can change the place that we `echo` to, from the Terminal to a text file, using `>` for output redirection. Run `echo "Your First and Last Name Here" > test.txt`. Use `ls` to see if the file `test.txt` exists within your working directory. Then use `cat` to read this file. After you have confirmed that the file contains your name, use `rm` to remove `test.txt`. 

###

```{r term2-ex-17}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 18

`>` can be used to redirect the command of any command, not just echo. Let's try to make a new text file in `options` with just the first 28 lines of `AUTHORS` called `AUTHORS-fake`. Run `head -n 28 AUTHORS > AUTHORS-fake`. 

###

```{r term2-ex-18}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 19

Using `>>` we can append output to an existing document. Use `echo` and `>>` to append your name to the list of `AUTHORS-fake`. 

###

```{r term2-ex-19}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

Like `>`, `>>` is not limited to echo, but can be used to append the output of any command. 

### Exercise 20

Use `tails` and `>>` to append the last 11 lines of `AUTHORS` to `AUTHORS-fake`. 

###

```{r term2-ex-20}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### 

Your fake is not great because your name is likely not placed in correct alphabetical order. If you wish, practice these commands more by being more precise with the last numbers for your name. Or learn read on how to edit text files in the Terminal more sophisticatedly, with tools such as Nano. 

### Exercise 21

Use `cd` and `..` to change your directory to the default working directory. Use `rm -r` to remove the `options` directory. 

###

```{r term2-ex-21}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

Good work. 

## Wildcards and grep
###

You will learn how to search for files and search through individual files.

### Exercise 1

Use `pwd` to confirm that you are in your default working directory. Make a directory directly inside the working directory, named `wildcards`.

###

```{r term3-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```


### Exercise 2

Change your working directory to `wildcards`. Make four text files in `wildcards`, named `2020-02-19.jpg`, `2020-01-20.jpg`, `2019-02-01.jpg`, and `2019-01-19.jpg`.

###

```{r term3-ex-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

`touch` can only make text files. You have only named the files as if they were pictures. 

### Exercise 3

Terminal commands allow the use of **wildcards**. A wildcard `*` represents zero or more of any character, and it is used to work with similarly named files as a group. 

###

Let's for example generate a list of all our "photos" (ISO: YYYY-MM-DD) taken in 2020. First, use  `ls` to make a list of all the files in the `wildcards` directory. Then, run `ls 2020*`. This asks Terminal to make a list of any photos which must begin with 2020 but can have anything after it. 

###

```{r term3-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

You could have also run `ls 2020-*` and gotten the same results. You could not have produced the same result with `ls 20*` because one of the photos was taken on the 20th of the month. Wildcards sometimes require clever thought. 

### Exercise 4

Use `ls` and `*` to make a list of all the "photos" which were taken in January. You will need a wildcard at the beginning and at the end, since month occurs in the middle of our file names. Also keep in mind, that one of our "photos" was taken on the first (also `01`) of the month. 

###

```{r term3-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### 

### Exercise 5

Save the list of January "photos" to a file.  Use the `up` arrow key to access your last command. Use `>` to redirect the list into a file named `january-photos.txt`. 

###

```{r term3-ex-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

The up and down arrow keys can be used to navigate your command history. 

### Exercise 6

Use `ls` and `*` to make a list of "photos" taken in February and use `>` to redirect  the output to a file named `february-photos.txt`.

###

```{r term3-ex-6}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 7

We can use wildcards with a variety of functions. Let's move all the 2020 "photos" into a 2020 folder at once. Make a new directory, named `2020-photos`. Then, run `mv 2020* 2020-photos`

###

```{r term3-ex-7}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

The first argument identifies the place(s) we want to move from, and so contains the wildcard. The second argument identifies the place we want to move to. `mv` retains each filename by default.

### Exercise 8

Make a new directory, named `2019-photos`. Use `mv` and a `*` to move all the 2019 "photos" into the new directory. 

###

```{r term3-ex-8}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 9 

Use `cd` and `..` to change back to the default working directory. Make a new directory named `grep`. 

###

```{r term3-ex-9}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 10 

Make a copy of the `AUTHORS` file in `$R_HOME/doc` in the `grep` folder. Use `cat -n` to read through the file, and note at what line the names begin and end. 

###

```{r term3-ex-10}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 11 

Use `head -n` and `>` to print the first 28 lines of `AUTHORS` and redirect the output to a  text file called `AUTHORS-only`. Then, use `tails -n` to print the last 20 lines of `AUTHORS` and redirect the output to `AUTHORS-only`.

###

```{r term3-ex-11}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

Our second redirect overwrites the first `AUTHORS-only`. 

### Exercise 12

Let's make a list of R authors whose first or last names contain the letter `d`. Run `grep "d" AUTHORS-only`. 

###

```{r term3-ex-12}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### 

`grep` is used to search for a string of characters within a text file. Like echo, one of its arguments is a quoted string. 

### Exercise 13

Use `grep` to make a list of authors whose first or last names begin with the letter `D`.

###

```{r term3-ex-13}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 14

Use `grep` to make a list of authors whose first or last names begin contain the string `aa`. 

###

```{r term3-ex-14}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

egrep is an even more powerful tool to search for functions in the Terminal. You can find a helpful introduction in The Unix Workbench. 

## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```

