---
title: "Terminal"
tutorial:
  id: "terminal"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Terminal Tutorial"
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(png)
library(grid)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```


<!-- Add rm (and maybe echo and maybe other stuff) to the end of the Introduction. Why not introduce (almost?) every command we are going to use in the Introduction. -->

<!-- Clean up at the end of each section so that everything you created is now gone. -->

<!-- Each tour finishes by going back to the level you started from and then deleting any files/directories which you have created. -->

<!-- Use . and .. at least three times. Especially cd .. and mv something . Note that you can only use this trick if two conditions hold: you are in the location to which you want to move the file and you don't want to change its name. Otherwise you need the full move: mv something to-something-else. -->

<!-- Explain that ~ (tilde) means home directory. And even a sentence explain what a home directory. Use ls ~. Use  -->

<!-- Explain what an environment variable is. Give a couple of examples: $USER, $HOME and $R_HOME. -->



## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```

## Introduction
###

The Terminal pane is next to the Console pane in the lower left portion of RStudio. We use the Console pane to talk to R. We use the Terminal pane to talk directly with the computer. Sadly, the Console and the Terminal speak different languages.

### Exercise 1

The Terminal has a string of characters ending in a $ before your cursor, called the **prompt**. After a command has been executed, a prompt will be generated on a new line to let you know that Terminal is ready for a new command. Hit return two times to see what happens to the prompt. Copy and paste the three lines here.

```{r term-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 2

Let's figure out where we are. To see your current location within your computer, type the command `pwd` (**p**resent **w**orking **d**irectory) in the Terminal. Hitting return runs the command. Copy and paste all commands and results associated with this exercise, as you will do for all the following exercises.  

```{r term-ex-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```




###

In a given working directory, Terminal assumes that all files and directories, unless otherwise specified, are within that directory.

Notice how the last directory (folder) in the **path** is included in the prompt.

Your pasted code should look something like:

```{r}
file <- paste0(system.file("images/", 
                           package = "primer.tutorials"),
               "pwd.png")
img <- readPNG(file)
grid.raster(img)
```




### Exercise 3

Let's see a **l**i**s**t of what's in our working directory. Run `ls`. Copy and paste the work.

```{r term-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 4

Let's create a file called `my.txt`. Run`touch my.txt`. Run `ls` to confirm that the new file exists inside the working directory. Copy and paste the work.

```{r term-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

`touch` creates an empty file. 

### Exercise 5

Let's **m**ake a **dir**ectory called `my-class`. Run `mkdir my-class`. Run `ls` to confirm that the new directory exists inside the working directory. Copy and paste the work.
 
```{r term-ex-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

### Exercise 6

Let's rename `my.txt` to  `fake.txt`.  Run `mv my.txt fake.txt`. Copy and paste the work. 

```{r term-ex-6}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```


###

`mv` stands for **m**o**v**e. The first argument is the place we want to move from, the second argument is the place we want to move to. Here the places have the same location, but different names. We will move things with `mv` later. 

Your pasted code should look something like:
```{r}
file <- paste0(system.file("images/", 
                           package = "primer.tutorials"),
               "mv.png")
img <- readPNG(file)
grid.raster(img)
```


## Paths
###

You will practice using paths both inside and outside the working directory. You will learn a few shorthands to make this easier. 

### Exercise 1

By default, the Terminal in RStudio starts with a working directory which is the same as the folder in which the current project resides, i.e., the folder with the .Rproj file in it. Run `pwd` to see your working directory. 

```{r term1-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### 

By default, the files pane (bottom right corner) in RStudio shows the contents of this directory. Towards the top, you will see a path of directories on your computer starting from a home icon. This should match the latter part of the path given from `pwd`. 

### Exercise 2

Let's **c**hange the working **d**irectory to `my-class`. Run `cd my-class`.  Run `pwd` to confirm that you have changed the working directory. Copy and paste the work.

```{r term1-ex-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 3

Let's make a directory within `my-class` called `lessons`. Run `mk-dir lessons`.

```{r term1-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 4

Let's make a directory within `lessons` called `wildcards`. Run `mk-dir lessons/wildcards`. Run `ls lessons` to check to see if `wildcards` exists inside.

```{r term1-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### 

We could not simply name the folder we wanted to create because then it would be created directly inside our working directory. To refer to a location that is not directly inside the present working directory, we need to use a path, which describes the location directory by directory. The path above is called a **relative path**, because it still assumes the working directory as its starting point. 

### Exercise 5

Let's change our working directory to `wildcards`. Run `cd lessons/widlcards`. 

```{r term1-ex-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 6

Let's make a text file inside `wildcards`, named `2019-01-20.jpg`. Run `touch 2019-01-20.jpg`

```{r term1-ex-6}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

Touch still creates a text file. We have only named it as if it were a picture.

### Exercise 7

Make four more files inside `wildcards`, named `2019-02-19.jpg` `2020-01-19.jpg` `2020-02-01.jpg`, and, `does-not-belong`.

```{r term1-ex-7}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Excercise 8

Let's go back to `lessons`. Run `cd ..` to go to the folder immediately above the working directory. Run `pwd` to confirm that you are in the right directory. Create a folder called `tbd`.

```{r term1-ex-8}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

`..` is a shorthand for the directory immediately above the  working directory. `.` is a shorthand for the working directory. 

### Excercise 9

It would be slow to have to use `cd ..` every time we wanted to go anywhere outside of our working directory. To refer to a specific folder outside of the working directory, we need to use an **absolute path**. An absolute path, as opposed to the relative paths we have been using, describes a place on your computer without respect to a working directory. An absolute path begins with the root directory, which is represented by a lone `/`. This is what `pwd` returns. 

###

Let's go back to our original working directory. Go to Exercise 2 to find the absolute path of the original working directory. Run `cd` with this as an argument. For example: `cd /Users/user-name/Desktop/sample/original-working-directory`. 

```{r term1-ex-10}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 11

Let's move the file `does-not-belong` so that it is directly inside of `my-class`. Run `mv my-class/lessons/wildcards/does-not-belong my-class/does-not-belong`. Remember the first argument is the place where we want to move the file from, the second argument is the place where we want to move the file to. 

```{r term1-ex-11}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

If we are moving a file or directory without changing the name, we do not need to add the name in the second argument. `mv my-class/lessons/wildcards/does-not-belong my-class` is equivalent to what we have done above. 

### Exercise 12

Let's move the directory `tbd` to our present working directory. Run `mv my-class/lessons/tbd tbd`

```{r term1-ex-12}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

### Exercise 13

Run `cd` alone. Run `pwd` to check where you are. This is called the **home directory**, which contains all a user's files. Run `ls` to see what is inside your home directory.


```{r term1-ex-13}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 14

Change the working directory back to your original home directory. You can again use the absolute path from the `pwd` in Exercise 1. 

```{r term1-ex-14}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

Since the original working directory is within the home directory, the full absolute path was not necessary. We could have omitted the user-name and everything before it. 


### Exercise 15

Let's change the working directory to a directory of your choice within the home directory.  Because the home directory is used in the absolute path of so many files, its path (`/Users/user-name/`) can be written with the shorthand `~/`.  Run, for example, `cd ~/Desktop`.

```{r term1-ex-15}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 16

Change back to the original working directory, using the shorthand for the home directory to write its absolute path. 

```{r term1-ex-16}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

Good work.


## Options
###

You will learn what options are and use them for functions you already know.  

#### Exercise 1

Add another file to the `my-class` directory, named `.my-hidden.txt` (make sure to include the `.`). 

```{r term2-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 2

Run `ls` to check if the file is inside `my-class`. If you did the previous exercise correctly, you will **not** see the new file. This is because we prefixed the name with the `.`,  which hid the file from normal view. These files live all over your computer. Run `ls -a my-class`. Using the **option** `-a`, you should be able to see **a**ll the files in `my-class`.

```{r term2-ex-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

Options are regularly preceded by a `-` and come before the argument. 

You can turn on your ability to see hidden files in the R Studio files pane (bottom right corner) by clicking the "More" button towards the top.

### Exercise 3

We have already gone over a few shorthands that represent paths. The shortcut `$R_HOME` represents the path to a folder of set-up files that R has installed on your computer. Type and enter `$R_HOME$` alone to make sure we are telling you the truth. Then change your working directory to `$R_HOME`. 

```{r term2-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 4

We have never been in this directory before. Let's try to get situated by running `ls`. You should see several unfamiliar items. It is hard to proceed since we do not even know whether we are looking at files or folders. Let's use `ls -l`, so that we can see more information in a **l**ong list. The names are now in the last column and file type is in the first: if the string in the first column begins  `d` it is a **d**irectory; if it begins with  `-` it is a file; if it begins with `l` it is a **l**ink to another file on the computer.

```{r term2-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

Good work. The middle columns give, from left to right, the number of files, author, permission, file size in bytes, date last modified.

### Exercise 5

Use `ls -l` to take a look at the `doc` folder. 

```{r term2-ex-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 6

Let's make a copy of the `AUTHORS` file. Use the command `cp`, whose syntax is identical to `mv`. Then, without changing directories, use `ls` and `ls -a` to confirm that `my-class` still has all three files and that there is still a copy of `AUTHORS` in `doc`.

```{r term2-ex-6}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

Like `mv`, `cp` can change a file name. Like `mv`, if the destination file name is omitted, `cp` will retain the same name by default. 

### Exercise 7

Try to make the entire `doc` directory in the our original working directory. You will get an error informing you that the thing you tried to copy was a directory. Run the same command using the option `-r`.

```{r term2-ex-7}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```


### Exercise 8

Return to our original working directory. Use the absolute path from Exercise 1 if needed.

```{r term2-ex-8}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```


### Exercise 9

Let's **r**e**m**ove `my-class/does-not-belong`. Run `rm my-class/does-not-belong`.

```{r term2-ex-9}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

**Be careful** with the rm command in Terminal. Unlike moving files to Trash, it is not reversible. If you delete certain things, it could cause damage to programs or your computer. 

### Exercise 10

Try to remove the `tbd` directory. You will get an error informing you that thing you tried to copy was a directory. Run the same command using option `-r`. 

```{r term2-ex-10}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

Good work. 

## Creating and Editing Files
###

### Exercise 1

Let's read the file `AUTHORS`. First, make sure this is in the present working directory. Run `cat AUTHORS`. 

```{r term3-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

Reminder: like all commands,`cat` refers to files by a path. This path is only the name because it is directly inside the present working directory.

### Exercise 2

`cat` prints the whole text file in the Terminal. This is not often the most convenient way of viewing. Let's start by viewing just the initial lines. Use the function `head` to view the first ten lines of the file. 

```{r term3-ex-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

Now we know how R got it's name. 

### Exercise 3

`head` also has options. The option `-n` allows you to specify the number of initial lines you want to see. This option takes an argument, for example, `-n 18`. Use this option to view a different number of the file's initial lines.

```{r term3-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 4

Let's view 15 of the ending lines. Use the command `tails` and the same `-n` option. 

```{r term3-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 5

While we can use `cat` to view the whole document. Use the `less` command to see another method. Use  the `up` and `down` arrow keys to explore the document. When you are ready, press `q` to quit. (For your answer, just copy/paste the command line on which you use `less`.)

```{r term3-ex-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

The document is a list of contributors to R in alphabetical order. 

### Exercise 6

Run the `wc` command on the AUTHORS file. Note that `wc` stands for **w**ord **c**ount.

###

```{r term3-ex-6}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

The three numbers printed out are the number of lines, words and characters in the file, respectively.

### Exercise 7

Let's make our own text file. Start by running `echo` which takes a quoted string, for example, "Your First and Last Name Here" as its argument. This "echoes" the argument by printing it in the next line of the terminal.

```{r term3-ex-7}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 8

We can change the place that we `echo` to, from the Terminal to a text file, using `>` for output redirection. Run `echo "Your First and Last Name Here" > test.txt`. Check to see if the file `test.txt` exists within your working directory. Then use `cat` to read this file. After you have confirmed that the file contains your name, remove `test.txt`. 

```{r term3-ex-8}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 9 

We can also use `echo` to append to an existing document, using `>>`. Let's add the same text to `fake.txt`. First, make sure that `fake.txt` is empty. Then run `echo "Your First and Last Name Here" >> fake.txt`. Now read the file to make sure it has your name. 

```{r term3-ex-9}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 10

Append two more names of your classmates to `fake.txt`. Use `wc` to make sure that the file now has three lines. Then read the file. 

```{r term3-ex-10}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 11

Change your working directory to `wildcards`. See what is inside the folder. 

```{r term3-ex-11}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 12

Terminal commands allow the use of **wildcards**. A wildcard `*` represents zero or more of any character, and it is used to work with similarly named files as a group. Let's for example generate a list of all our "photos" taken in 2020. Run `ls 2020*`. This asks Terminal to produce a list of any photos which begin with 2020 and could have anything after it. 

```{r term3-ex-12}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 13

Wildcards sometimes require clever thought. Generate a list of all our "photos" which were taken in January. You will need a wildcard at the beginning and at the end, since month occurs in the middle of our file names. Also keep in mind, that one of our "photos" was taken on the first (also `01`) of the month. 

```{r term3-ex-13}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 14 

Output redirection `>` is not limited to echo. It can be used with any Terminal command. Use the `up` arrow key to access your last command. Redirect the list we generated into a file named `january-photos.txt`. 

```{r term3-ex-14}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 15 

Make a file named `february-photos.txt`, which contains a list of all "photos" taken in February. 

```{r term3-ex-15}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 16

We can use wildcards with a variety of functions. Make a new directory, named `2020`. Use `mv` to move all the 2020  "photos" as a group into our new directory. The first argument identifies the place(s) we want to move from, and so will contain the wildcard. The second argument identifies the place we want to move to, we will only specify a folder here and allow `mv` to retain their names by default, since we cannot specify multiple names. 

```{r term3-ex-16}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 17

Make a new directory, named `2019`. Use `mv`to move all the 2019 "photos" into our new directory. 

```{r term3-ex-17}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 18

Though `cat` is commonly used to print text files, it stands for con**cat**enate, which literally means "to chain together". In its intended use, it takes two arguments and prints them together. Let's print `AUTHORS` and `fake.txt` together. Save this output to a new file called `AUTHORS-fake`. 

```{r term3-ex-18}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 19

Let's make our fake more convincing. The new names are not in the same place as the other names. One tool to edit text files in Terminal is `nano`. Run `nano AUTHORS-fake.txt`. Use the up and down arrow keys to move your cursor. You can use your keyboard to add and delete text just as you would normally. Nano provides some shortcuts at the bottom of its interface. `^K` (`^` = `Control`) cuts a line, `^U` pastes that line wherever your cursor is. For your 3 names, find the correct alphabetical position and insert your name there.

```{r term3-ex-19}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

You can view more nano commands using `^G`. 

### Exercise 20

Let's save our new fake. Use `^X` to exit. You will be asked whether you want to save, type `Y`. Now use `less` or `cat` to view the edited `AUTHORS-fake`. Move this file to the `doc` folder in our working directory. Without changing directories, remove the old authors file. Rename `AUTHORS-fake` to `AUTHORS`. Use `ls` to make sure that there is only one `AUTHORS` file in `doc`. 

```{r term3-ex-20}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

Good work. 

## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```

