---
title: 'Rubin Causal Model: Overview'
author: Sophia Zhu & Arghayan Jeiyasarangkan
tutorial:
  id: rubin-causal-model-overview
output:
  learnr::tutorial:
    progressive: yes
    'allow_skip:': yes
runtime: shiny_prerendered
description: Chapter 4 Tutorial Part A
---

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(tidyverse)
library(gt)
library(knitr)

# Key Data 

gt_obj <- tibble(subject = c("Yao", "Emma", "Cassidy", "Tahmid", "Diego"),
       treatment = c("Treated", "Treated", "Control", "Control", "Treated"), 
       ytreat = c("13", "14", "11", "9", "3"),
       ycontrol = c("9", "11", "6", "12", "4"),
       ydiff = c("? ", "? ", "? ", "? ", "? ")) |>
   gt() |>
  cols_label(subject = md("ID"),
                treatment = md("Treatment"),
                ytreat = md("$$Y_t(u)$$"),
                ycontrol = md("$$Y_c(u)$$"),
                ydiff = md("$$Y_t(u) - Y_c(u)$$")) |>
  cols_move(columns = c(treatment, ytreat, ycontrol), after = c(subject)) |>
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(subject))) |>
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"), 
            locations = cells_column_labels(columns = c(subject, treatment))) |>
  cols_align(align = "center", columns = everything()) |>
  cols_align(align = "left", columns = c(subject)) |>
  fmt_markdown(columns = everything()) |>
  tab_spanner(label = "Outcomes", c(ytreat, ycontrol))  |>
  tab_spanner(label = "$$\\text{Estimand}$$", c(ydiff))


knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

<!-- Tutorial just stops with no clear ending. Not really connected to the chapter. Doesn;t even cover Population Tables! Nor terms like validity and so on! -->

<!-- Seems like we should do less silly algebra questions and more reviews of the key concepts. The simple questions about defining causal effects and potential outcomes are fine, as far as they go. But shouldn't we have more, applying them in more specific scenarios? Might even cover scenarios in which things like SUTVA fail. -->

<!-- Match this closely to the chapter because, someday, we are going to stick all of these questions in the chapter. Does not need to be 90 minutes of questions. -->

<!--  And fix the 2 taus table in the 2nd tutorial so that tau is easier to calculate mentally. --> 

<!-- How do we give students information about being wrong or right? Easy for code! -->

<!-- After the definitions, we could have some problems which use the actual train data, calculate some causal effects and then plot them. Lots of good staff there. First, assume a single tau. What is it? How sure are you? Then separate taus for men and women. Or some other grouping. Show facetted plot. -->

<!-- One question could take the trains data and make a Preceptor table. Learn a little gt! Would also need some manipulation to create the two potential outcome columns. -->

<!-- More about confounding. Of course, it needs to be in the book. -->



```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

## Introduction
###

This tutorial review [Chapter 4](https://ppbds.github.io/primer/04-rubin-causal-model.html) of Preceptor's Primer.

## Definitions
### 

If you have read the chapter, then these questions should be easy. Please note that you can not change your answers once you submit them. 

### Exercise 1

In your own words, give a one sentence definition of a Preceptor Table.

```{r definitions-1}
question_text(NULL,
    message = "A table such that, if none of the data is missing, you can easily calculate your quantity of interest.",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 3)
```

### Exercise 2

In your own words, give a one sentence definition of a potential outcome.

```{r definitions-2}
question_text(NULL,
    message = "An outcome which occurs if the treatment has the specified value.",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 3)
```

### Exercise 3

In your own words, give a one sentence definition of a causal effect.

```{r definitions-3}
question_text(NULL,
    message = "The difference between two potential outcomes.",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 3)
```

### Exercise 4

Write a paragraph explaining the Fundamental Problem of Causal Inference. Include an example relating to your own life.

```{r definitions-4}
question_text(NULL,
    message = "The Fundamental Problem of Causal Inference is that, because we can never observe more than one potential outcome, we can never be certain about the value of a causal effect. For example, to determine the causal effect of studying on my SAT score, I need to know two things: my score if I study and my score if I don't study. The causal effect is the difference between the two. But I can only either study or not study. I can't do both! So, I can only observe one potential outcome.",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 7)
```

### Exercise 5

<!-- DK: Do we still discuss this in the chapter? No! Same next question. -->

In two sentences, explain what what an *ideal* Preceptor Table is, and why it is generally impossible to observe. Use the phrase "potential outcomes" in your answer.

```{r definitions-5}
question_text(NULL,
    message = "An ideal Preceptor Table is a table that does not have any missing data. This table is generally seen as impossible since it means that you can observe all potential outcomes of a situation, which should be impossible due to the Fundamental Problem of Causal Inference.",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 5)
```

### Exercise 6

In one sentence, explain the difference between an *actual* Preceptor Table and an *ideal* Preceptor Table.

```{r definitions-6}
question_text(NULL,
    message = "An actual Preceptor Table has missing values, whereas an ideal Preceptor Table doesn’t have any missing values.",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 3)
```

## Causal Effect
### 

Use the following ideal Preceptor Table to answer some questions about "estimands," quantities in which we might be interested.

```{r}
gt_obj
```

### Exercise 1

```{r causal-effect-1}
quiz(

  question("What is the causal effect of the treatment on Yao?",
    answer("1"),
    answer("2"),
    answer("3"),
    answer("4", correct = TRUE),
    answer("5"),
    allow_retry = FALSE),

  question("For how many of the five people is the causal effect of the treatment positive?",
    answer("1"),
    answer("2"),
    answer("3", correct = TRUE),
    answer("4"),
    answer("5"),
    allow_retry = FALSE),

  question("On whom did the treatment have the most negative causal effect?",
    answer("Yao"),
    answer("Emma"),
    answer("Cassidy"),
    answer("Tahmid", correct = TRUE),
    answer("Diego"),
    allow_retry = FALSE)
)
```

<!-- DK: Split up above into separate questions. Add explanations/knowledge drops after each one. Spend more time teaching! -->

## One tau
### 

In these exercises, we will assume that the causal effect, $\tau$ (pronounced tau, rhymes with "cow"), is the same for everyone.


Use the following Preceptor Table to answer questions about the single value for tau.

```{r one-tau-0-setup}
tibble(subject = c("Yao", "Emma", "Cassidy", "Tahmid", "Diego"),
       treatment = c("Treated", "Treated", "Control", "Control", "Treated"),
       ytreat = c("13", "14", "?", "?", "3"),
       ycontrol = c("?", "?", "6", "12", "?"),
       ydiff = c("?", "?", "?", "?", "?")) |>
  gt() |>
  cols_label(subject = md("ID"),
                treatment = md("Treatment"),
                ytreat = md("$$Y_t(u)$$"),
                ycontrol = md("$$Y_c(u)$$"),
                ydiff = md("$$Y_t(u) - Y_c(u)$$")) |>
  cols_move(columns = c(treatment, ytreat, ycontrol), after = c(subject)) |>
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(subject))) |>
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"), 
            locations = cells_column_labels(columns = c(subject))) |>
  cols_align(align = "center", columns = everything()) |>
  cols_align(align = "left", columns = c(subject)) |>
  tab_spanner(label = "Outcomes", c(ytreat, ycontrol)) |>
  tab_spanner(label = "$$\\text{Estimand}$$", c(ydiff)) |>
  fmt_markdown(columns = everything())
```

### Exercise 1

<!-- DK: Are these next few questions useful? -->

Describe in one sentence/equation how you would estimate Yao's $Y_c(u)$. (Do not use actual numbers, use "tau" in your explanation).

```{r one-tau-1}
question_text(NULL,
    message = "Yao's $Y_t(u)$ - (Sum of all values in $Y_t(u)$ / Number of Values - Sum of all values in $Y_c(u)$ / Number of Values)",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

### Exercise 2

Describe in one sentence/equation how you would estimate Tahmids's $Y_t(u)$. (Do not use actual numbers, use "tau" in your explanation).

```{r one-tau-2}
question_text(NULL,
    message = "(Sum of values in $Y_t(u)$ / Number of Values - Sum of values in $Y_c(u)$ / Number of values) + Tahmid's $Y_c(u)$",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

### Exercise 3

Describe in one sentence/equation how you would estimate a single value for tau.

```{r one-tau-3}
question_text(NULL,
    message = "(Sum of values in $Y_t(u)$ / Number of Values - Sum of values in $Y_c(u)$ / Number of values)",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

### Exercise 4

```{r one-tau-4}
quiz(

  question("What is your estimate for a single value for tau?",
    answer("-2"),
    answer("2"),
    answer("1", correct = TRUE),
    answer("-1"),
    answer("1.5"),
    allow_retry = FALSE),

  question("What is your estimate for $Y_c(u)$ for Emma?",
    answer("10"),
    answer("11"),
    answer("12"),
    answer("13", correct = TRUE),
    answer("14"),
    allow_retry = FALSE),

  question("What is your estimate for $Y_t(u)$ for Cassidy?",
    answer("6"),
    answer("5"),
    answer("7", correct = TRUE),
    answer("9"),
    answer("8"),
    allow_retry = FALSE)
)
```

## Two taus
### 

Assume that the causal effect varies by sex. We will now estimate two values for $\tau$: $\tau_F$ and $\tau_M$. (Cassidy and Emma are female; Tahmid, Diego, and Yao are male).

```{r}
tibble(subject = c("Yao", "Emma", "Cassidy", "Tahmid", "Diego"),
       treatment = c("Treated", "Treated", "Control", "Control", "Treated"),
       ytreat = c("13", "14", "$$6 + \\tau_F$$", "$$12 + \\tau_M$$", "3"),
       ycontrol = c("$$13 - \\tau_M$$", "$$14 - \\tau_F$$", "6", "12", "$$3 - \\tau_M$$"),
       ydiff = c("$$\\tau_M$$", "$$\\tau_F$$", "$$\\tau_F$$", "$$\\tau_M$$", "$$\\tau_M$$")) |>
  gt() |>
  cols_label(subject = md("ID"),
                treatment = md("Treatment"),
                ytreat = md("$$Y_t(u)$$"),
                ycontrol = md("$$Y_c(u)$$"),
                ydiff = md("$$Y_t(u) - Y_c(u)$$")) |>
  cols_move(columns = c(treatment, ytreat, ycontrol), after = c(subject)) |>
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(subject))) |>
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"), 
            locations = cells_column_labels(columns = c(subject))) |>
  cols_align(align = "center", columns = everything()) |>
  cols_align(align = "left", columns = c(subject)) |>
  tab_spanner(label = "Outcomes", c(ytreat, ycontrol)) |>
  tab_spanner(label = "$$\\text{Estimand}$$", c(ydiff)) |>
  fmt_markdown(columns = everything())
```

### Exercise 1

How would you calculate $\tau_F$? Use only words and no numbers in your explanation.

```{r two-taus-1}
question_text(NULL,
    message = "(Average $Y_t(u)$ for females - Average $Y_c(u)$ for females)",
    # AJ: You would average $Y_c(u)$ for females and subtract that from the average $Y_t(u)$ for females
    # AJ: which is better?
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

### Exercise 2

What is the meaning of $\tau_M$? 

```{r two-taus-2}
question_text(NULL,
    message = "$t_M$ is an estimate of the average difference between the treatment effect and the control effect for males",
# AJ: This explanation could be made more clear and also needs to be added to the primer
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

### Exercise 3

What is your new estimate for Diego's $Y_c(u)$? 

```{r two-taus-3}
question_text(NULL,
    message = "7",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

### Exercise 4

Discuss for a sentence or two why an assumption that the causal effect varies by sex leads to a different estimate for Diego's $Y_c(u)$ compared to Cassidy's $Y_c(u)$.

```{r two-taus-4}
question_text(NULL,
    message = "Since Diego is male and Cassidy is female, the tau used to calculate the causal effect is different for each.",
    # AJ: Add this into the primer
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

## Average Treatment Effect
We will no longer make any assumptions about $\tau$ for any individual or group. Instead, we are interested in estimating the average treatment effect ($ATE$). We have the same data as the previous sections.

```{r}
gt_obj
```

### Exercise 1

Using words only, explain how we estimate the $ATE$.

```{r average-treatment-ef-1}
question_text(NULL,
    message = "Average of treated values minus the average of control values.",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

<!-- Average of treated values minus the average of control values is the standard way of estimating the ATE. -->


### Exercise 2

Calculate the $ATE$ based on the data given to you in the above Preceptor Table.

```{r average-treatment-ef-2}
question_text(NULL,
    message = "1.6",
# AJ: think of a way to make this a non decimal answer without screwing up the other questions
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

### Exercise 3

What is Cassidy's outcome under treatment if we assume $\tau$ to be the $ATE$ we calculated above? Note that the answer will just be a number, without any symbol.

```{r average-treatment-ef-3}
question_text(NULL,
    message = "9.4",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

### Exercise 4

Write a pararaph about the many, many reasons why $ATE$ may be a bad estimate of the true average treatment effect.

<!-- AJ: add this to primer -->

```{r average-treatment-ef-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    rows = 7)
```

### Exercise 5

Write a paragraph about what a heterogeneous treatment effect is and the situations when it is more or less common.

```{r average-treatment-ef-5}
question_text(NULL,
    message = "A heterogeneous treatment effect means that the effect of the treatment varies from individual to individual. A situation where this would be common is when testing drugs. Most people will have a different reaction to the drug, so we can't just assume that the causal effect of the drug is the same for everyone.",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 7)
```

## Assumptions
### 

This section reviews the key assumptions required in every attempt at inference: *validity*, *stability*, *representativeness*, and *unconfoundedness*.

### Exercise 1

Write two sentences about *validity*, as used as an assumption in the *Primer*.

```{r assumptions-1}
question_text(NULL,
	message = "The assumption of validity allows us ignore any variation in treatment. It allows us to 'stack' the rows from the data, the Preceptor Table, and the population into a single Population Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Each of our two sources for rows --- the Preceptor Table and the actual data --- are coherent in terms of what the columns mean on their own. The assumption of validity, if true, allows us to "stack" them together and to consider both of them to have been drawn from the same larger population.

### Exercise 2

Write two sentences about *stability*, as used as an assumption in the *Primer*.

```{r assumptions-2}
question_text(NULL,
	message = "Stability means that the relationship between the columns is the same for three categories of rows: the data, the Preceptor Table, and the larger population from which both are drawn. That is, however connected two columns are in the data, we assume that this same connection holds for the Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

*Validity* is about the columns. Does "exposure to Spanish-speakers" mean the same thing in our data from 2014 as it does in the data we want to have --- for our Preceptor Table --- in 2022? *Stability* is about the rows. Is the connection between the treatment and the potential outcomes the same in 2022 as it was in 2014?

### Exercise 3

Write two sentences about *representativeness*, as used as an assumption in the *Primer*.

```{r assumptions-3}
question_text(NULL,
	message = "Representativeness, or the lack thereof, is the relationship, among the rows in the Population Table, between our data and the other rows. Ideally, we would like our data to be a random sample from the population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Why do we have the data that we have? The easiest way to draw inferences about other rows, especially the rows in the Preceptor Table subpart of the Population Table, is if our data is a random draw from the entire population. This is almost never true. How untrue it is determines how much we need to worry about the representativeness of our data.

### Exercise 4

Write two sentences about *unconfoundedness*, as used as an assumption in the *Primer*.

```{r assumptions-4}
question_text(NULL,
	message = "If whether or not a unit received treatment or control is random, we write that treatment assignment is not 'confounded.' If, however, treatment assignment depends on the value of a potential outcome, then treatment assignment is confounded.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

"Unconfoundedness" as an assumption only applies in the case of causal, not predictive, models.


### Exercise 5

Write two sentences that explain the difference between a causal model and a predictive model. 

```{r assumptions-5}
question_text(NULL,
    message = "A predictive model assumes one outcome whereas a causal model allows for more than one outcome, which we term 'potential' outcomes in that case. In the Preceptor Table, a predictive model has only one outcome column while a causal model has at least two.",
    answer(NULL, correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 2)
```

## Summary
###

```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
