---
title: Models
author: David Kane and Sanaka Dash
tutorial:
  id: models
output:
  learnr::tutorial:
    progressive: yes
    'allow_skip:': yes
runtime: shiny_prerendered
description: 'Chapter 4 Tutorial: Models'
---

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(tidyverse)
library(gt)    # Need because library(gtsummary) does not load gt.
library(brms)
library(tidybayes)
library(gtsummary)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 

poll_data <- tibble(biden = c(rep(1, 655), 
                              rep(0, 904)))


# fit_bern <- brm(formula = biden ~ 1,
#                 data = poll_data,
#                 family = bernoulli(),
#                 refresh = 0,
#                 silent = 2,
#                 seed = 12)
# write_rds(fit_bern, "data/fit_bern.rds")

fit_bern <- read_rds("data/fit_bern.rds")

population_table <- 
tibble(source = c("...", "...", "...","...",  
                  "Data", "Data", "Data", "Data", "...",
                  "...", "...", "...","...", 
                  "Preceptor Table", "Preceptor Table", "Preceptor Table", "...",
                  "...", "...", "..."),
       time = c("February 2024", "February 2024", "February 2024", "...",
                "March 2024", "March 2024", "March 2024", "March 2024", "...",
                "October 2024", "October 2024", "October 2024", "...",
                "November 2024", "November 2024", "November 2024", "...",
                "December 2024", "December 2024", "December 2024"),
       id = c("1", "200", "976", "...",
              "1", "200", "...", "1559", "...",
              "1", "200", "2025", "...",
              "1", "200", "2078", "...",
              "1", "200", "2300"),
       biden = c("?", "?", "?", "...",
              "0", "1", "...", "1", "...",
              "?", "?", "?", "...",
              "1", "0", "1", "...",
              "?", "?", "?")) |>
  gt() |>
  cols_label(source = md("Source"),
             time = md("Time"),
             id = md("ID"),
             biden = md("Biden")) |>
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(source))) |>
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"),
            locations = cells_column_labels(columns = c(source))) |>
  cols_align(align = "center", columns = everything()) |>
  cols_align(align = "left", columns = c(source)) |>
  fmt_markdown(columns = everything())

```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

<!-- SD: Honestly the writing parts need to be wayyyy shorter than they are currently, and it would be beneficial to just cut out some of the writing questions. Overall, this tutorial took about 3 hours to complete! -->

<!-- We left out the by-hand calculation of the confidence interval. Add it in? -->

<!-- Sort of shame that the model takes so long to run. Maybe find an example with fewer observations? If we did, we could run the model many times, examining one-by-one what some of the arguments do. Might even do that here with subsets of the data. Annoyance would be that confidence intervals will be too wide if you do that. Best plan is to tell/show how intervals widen with less data, but to just keep using the one already-fitted model. -->

## Introduction
### 

This tutorial covers [Chapter 4: Models](https://ppbds.github.io/primer/models.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 

In Chapter 3, we learned about sampling, the process of gathering data to answer our questions. In this chapter, we will learn about constructing models, creating the data generating mechanism (DGM) which we will use to answer our questions.

## Wisdom
### 

*The only true wisdom is in knowing you know nothing.* - Socrates

The general question we are interested in is the future results of the 2024 election, as seen from a survey conducted March 2024.

Our specific question:

> *What proportion of all votes will be cast for Joe Biden in the 2024 election?*


### Exercise 1

In your own words, describe the key components of Wisdom when working on a data science problem.


```{r wisdom-1}
question_text(NULL,
	message = "Wisdom requires the creation of a Preceptor Table, an examination of our data, and a determination, using the concept of validity, as to whether or not we can (reasonably!) assume that the two come from the same population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 2

Define a Preceptor Table.


```{r wisdom-2}
question_text(NULL,
	message = "A Preceptor Table is the smallest possible table of data with rows and columns such that, if there is no missing data, we can easily calculate the quantities of interest.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Precisely describing the Preceptor Table for this problem is the first step in trying to solve it. 

### Exercise 3

Describe the key components of Preceptor Tables in general, without worrying about this specific problem. Use words like "units," "covariates," and "outcomes." 


```{r wisdom-3}
question_text(NULL,
	message = "The rows of the Preceptor Table are the units. The outcome is at least one of the columns. If the problem is causal, there will be at least two (potential) outcome columns. The other columns are covariates. If the problem is causal, at least one of the covariates will be a treatment.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- DK: Knowledge drop. - DONE -->
The way I like to think of it is that the units are the objects that are being affected (rows), while the outcome column is how the units are being affected.


### Exercise 4

Create a Github repo called `tutorial-4`. Connect it to an new R Project called `tutorial-4`. Edit the `.gitignore` file to ignore the Rproj file.

In the Console, run `show_file(".gitignore")`. CP/CR. Don't forget to run `library(tutorial.helpers)` if you get a "function not found" error message.

```{r wisdom-4}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 6)
```

### Exercise 5

In this new R Project, create a new Quarto Document, naming it `Models`. Now save the file as `models.qmd`. Note that the `.qmd` will be added automatically.

Type `show_file("models.qmd")` into the Console. CP/CR.

```{r wisdom-5}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

If everything was done correctly, you should get a blank response.


### Exercise 6

Here is our Preceptor Table:
```{r}
#| echo: false
tibble(voter_ID = c("1", "2", 
                   "...", "200", "201", "...", "2078", "2079", "..."),
       biden = c("0", "0", 
                   "...", "1", "0", "...", "1", "0", "...")) |>
  gt() |>
    tab_header(title = "Preceptor Table") |> 
    cols_label(voter_ID = "Voter ID",
               biden = "Voted for Biden") |>
    tab_style(cell_borders(sides = "right"),
              location = cells_body(columns = c(voter_ID))) |>
    cols_align(align = "center", columns = everything())
```

What are the units for this problem?

```{r wisdom-6}
question_text(NULL,
	message = "The units are the individual voters.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Note that this is not all American adults or even all registered voters. To answer our question, we only need information about actual voters. Any other rows would be superfluous.

### Exercise 7

What is the outcome for this problem?

```{r wisdom-7}
question_text(NULL,
	message = "The outcome is the candidate for whom the vote was cast.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Looking at the question, this formulation is too broad. We don't actually need to know the name of the candidate. We just need to know if the vote was cast for Biden or not. The name of the candidate, if it was not Biden, is irrelevant to our question. So, we can represent the outcome as 0 (did not vote for Biden) and 1 (did vote for Biden).

Realistically, then, this question only has 1 outcome. This means that the problem would be a predictive model.


### Exercise 8

What are the treatments, if any, for this problem?

```{r wisdom-8}
question_text(NULL,
	message = "There is no treatment.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 2)
```

### 

This is a predictive model, not a causal model, so there are no treatments, by definition. Recall that treatment is just a covariate which, given the question we are trying to answer, might at least in theory be manipulable.



### Exercise 9

Write one sentence describing the data you have to answer your question. 

In any question related to polling, you always want to include the name of the polling organization, the date and the number of individuals successfully contacted.


```{r wisdom-9}
question_text(NULL,
	message = "We have data from a YouGov poll of 1,559 US adult citizens, conducted March 10 - 12, 2024, indicating which respondents intend to vote for Joe Biden and which do not.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 10

Now type `show_file("models.qmd")` into the Console. CP/CR.

```{r wisdom-10}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

Throughout this tutorial, we will be expanding on this sentence, and by the end, it will have become a fully fledged paragraph.


### Exercise 11

In your own words, define "validity" as the term is used in the *Primer*.

```{r wisdom-11}
question_text(NULL,
	message = "Validity is the consistency, or lack thereof, in the columns of the data set and the corresponding columns in the Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 12

What data can't we combine when forming the Population Table if the assumption of validity does not hold?

<!-- DK: Fix as you see fit. - DONE -->

```{r wisdom-12}
question_text(NULL,
	message = "We can't combine the Preceptor Table and the data in order to construct the Population Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- DK: knowledge drop - DONE -->
Recall that our Population Table is a synthesis of all our data, and is used to describe the population as a whole. If the data being recorded is wrong, then the overall representation of the population would also be wrong.


### Exercise 13

Provide one reason why the assumption of validity might not hold for this problem.


```{r wisdom-13}
question_text(NULL,
	message = "People sometimes don't vote for the person they claim they are going to vote for.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

What we tell other people we will do is often not what we actually do. Consider a voter who is embarrassed about her support for Biden. Perhaps she perceives the interviewer as a Republican and doesn't care to admit to him, in March, her support for Biden. But, in November, in the privacy of the polling booth, she votes for Biden. In her case, the outcome from the data (what she told the pollster) did not have a *valid* correspondence with her behavior in the polling booth.


### Exercise 14

<!-- DK: Change as you see fit. - DONE -->

*So what do we want to get out of this data?* 
In one or two sentences, make a statement to this question that consists of 2 parts: 
1) Where the data is from/collected
2) What we intend to do with the data

For the second part, start with something along the lines of "we seek to".

```{r wisdom-14}
question_text(NULL,
	message = "Using data from a YouGov poll of 1,559 US adult citizens, conducted March 10 - 12, 2024, we seek to understand what proportion of voters will support Biden in the 2024 election. In particular, we want to estimate the proportion of all votes which will be cast for Joe Biden in the 2024 election.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 15

Remember that sentence that we added in our `models.qmd` file? Replace that sentence with the paragraph above. Feel free to modify it and use parts of our sentence if it helps.

Run `show_file("models.qmd")` in the Console. CP/CR.

```{r wisdom-15}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

Do you see how we evolved from that initial sentence to this wonderful statement? This is the beauty of Data Science, where we are given a vague question and we need to make it specific for our needs.


## Justice
### 

*Justice is truth in action.* - Benjamin Disraeli


### Exercise 1

In your own words, name the four key components of Justice (without describing them) for working on a data science problem.


```{r justice-1}
question_text(NULL,
	message = "Justice concerns four topics: the Population Table, stability, representativeness, and unconfoundedness.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- DK: Knowledge drops -->
<!-- SD: What should I add here? -->


### Exercise 2

In your own words, define a Population Table.

<!-- SD: Old answer:
 "The Population Table includes a row for each unit/time combination in the underlying population from which both the Preceptor Table and the data are drawn." 
 
This was bad, so I changed it. -->
```{r justice-2}
question_text(NULL,
	message = "The Population Table assesses the overall opinion of the population, using the Preceptor Table and the Data to formulate rows for each unit/time combination. It then adds other relevant data from the same population to further assist in assessing the state of the population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 3

Here is our Population Table:
```{r}
population_table
```

Describe the Population Table for this problem. In particular, are any of the rows in the Preceptor Table also rows in the data? Are there other rows in the Population Table which are not from the Preceptor Table or the data? If so, describe some of those rows.

```{r justice-3}
question_text(NULL,
	message = "Each row in the Population Table corresponds to a person/date combination. None of the rows for the Preceptor Table and the data overlap. Rows from the overall population feature dates outside the survey dates and the election.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Notice how, although the Population Table is helping us by adding data, the data that it's adding isn't doesn't convey validity, i.e. it is measuring a different metric (in this case the voters' opinions from different time periods). We don't know if the voters' opinions changed over that time period, making the data invalid.


### Exercise 4

In your own words, define the assumption of "stability" when employed in the context of data science.


```{r justice-4}
question_text(NULL,
	message = "Stability means that the relationship between the columns in the Population Table is the same for three categories of rows: the data, the Preceptor Table, and the larger population from which both are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Stability is all about *time*. Is the relationship among the columns in the Population Table stable over time? In particular, is the relationship --- which is another way of saying "mathematical formula" --- at the time the data was gathered the same as the relationship at the (generally later) time references by the Preceptor Table.


### Exercise 5

Provide one reason why the assumption of stability might not be true in this case. (This is somewhat of a trick question.)

```{r justice-5}
question_text(NULL,
	message = "Our Population Table is so simple that stability is almost automatically true. There is only one column!",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Stability might become important as we think about the actual process by which we might meet the two voters in our original question, but, in terms of the Population Table itself, there is no problem.


### Exercise 6

In your own words, define the assumption of "representativeness" when employed in the context of data science.


```{r justice-6}
question_text(NULL,
	message = "Representativeness, or the lack thereof, concerns two relationship, among the rows in the Population Table. The first is between the Preceptor Table and the other rows. The second is between our data and the other rows.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Ideally, we would like both the Preceptor Table *and* our data to be random samples from the population. Sadly, this is almost never the case.


### Exercise 7

Provide one reason why the assumption of representativeness might not be true in this case.

<!-- DK: Give an answer. - DONE -->

```{r justice-7}
question_text(NULL,
	message = "One concern might involve the process by which YouGov sampled potential voters in March. If that process were flawed, if the people it sampled were systematically different than the people it did not, then the assumption of representativeness would fail. Imagine that YouGov only polled residents in Washington DC. That would be bad, even if everyone polled answered truthfully. We would end up with data which was much more pro-Biden than the country as a whole.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The assumption of representativeness is never completely true. We can only hope/assume that it is true enough that the inferences we draw from our data can be roughly applied to our question. Let’s assume that is this case.


### Exercise 8

In your own words, define the assumption of "unconfoundedness" when employed in the context of data science.

```{r justice-8}
question_text(NULL,
	message = "Unconfoundedness means that the treatment assignment is independent of the potential outcomes, when we condition on pre-treatment covariates. This assumption is only relevant for casual models.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

This assumption is only relevant for causal models. We describe a model as "confounded" if this is not true.


### Exercise 9

Provide one reason why the assumption of unconfoundness might not be true (or relevant) in this case.

```{r justice-9}
question_text(NULL,
	message = "Since this is a predictive model, we do not have to worry about unconfoundedness.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 10

1. Copy your work from the end of the Wisdom section. This is also in your `models.qmd` file.

Modify your previous response to reflect the question we are trying to answer. Then, mention at least one specific problem which casts doubt on your approach. 

```{r justice-10}
question_text(NULL,
	message = "Using data from a YouGov poll of 1,559 US adult citizens, conducted March 10 - 12, 2024, we seek to understand what proportion of voters will support Biden in the 2024 election. Biden’s popularity might change significantly over the course of the election campaign.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 11

Now replace everything in the `models.qmd` file with this new paragraph that you wrote. Feel free to modify your response and use elements from our model response.

Run `show_file("models.qmd")` in the Console. CP/CR.

```{r justice-11}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

## Courage
### 

*Courage is found in unlikely places.* - J.R.R. Tolkien


### Exercise 1

<!-- DK: Switch to Cardinal Virtues. -->
<!-- SD: Potential Answer?: "Courage creates a mathematical model which connects the outcome variable to the covariates, if any. Then, using code, we create a fitted model, including posterior probability distributions for all the unknown parameters." -->
<!-- SD: SO in the end, do I use this answer? -->

In your own words, name the key goal of Courage in Data Science and the process we use to get there.

```{r courage-1}
question_text(NULL,
	message = "Courage selects the data generating mechanism. We first specify the mathematical formula which connects the outcome variable we are interested in with the other data that we have. We explore different models. We need to decide which variables to include and to estimate the values of unknown parameters. We check our models for consistency with the data we have. We avoid hypothesis tests. We select one model.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 2

Load the **brms** package.

```{r courage-2, exercise = TRUE}

```

```{r courage-2-hint-1, eval = FALSE}
library(...)
```

```{r courage-2-test, include = FALSE}
library(brms)
```

### 

The **brms** package provides a user-friendly interface to work with the statistical language [Stan](https://mc-stan.org/), the leading tool for Bayesian model building.

### Exercise 3

Load the **tidybayes** package.

```{r courage-3, exercise = TRUE}

```

```{r courage-3-hint-1, eval = FALSE}
library(...)
```

```{r courage-3-test, include = FALSE}
library(tidybayes)
```

<!-- XX: Some comments about this problem. - DONE -->
<!-- SD: I added a whole problem for this -->


### Exercise 4

To learn about what the `Tidybayes` package does, let's use the built-in help menu.

First, load in the `Tidybayes` package into the Console.

Now, type `?tidybayes` into the Console. Copy/Paste the first paragraph under the Details section.

```{r courage-4}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### Exercise 5

Run this code in order to generate the polling data.

```{r courage-5, exercise = TRUE}
poll_data <- tibble(biden = c(rep(1, 655), 
                              rep(0, 904)))

slice_sample(poll_data, n = 10)
```

```{r courage-5-test, include = FALSE}
poll_data <- tibble(biden = c(rep(1, 655), 
                              rep(0, 904)))

slice_sample(poll_data, n = 10)
```

### 

We don't care exactly who voted for Biden and who did not. In that sense, the rows of the data (and the Preceptor Table) are "exchangeable," which means (roughly) that nothing changes if we re-arrange the IDs of any of the rows.

### Exercise 6

Use `brm()` to fit a model, assigning the result to an object called `fit_bern`. Use the arguments: `formula = biden ~ 1`, `data = poll_data`, `family = bernoulli()`, `refresh = 0`, `silent = 2`, and `seed = 9`.


```{r courage-6, exercise = TRUE}

```

```{r courage-6-hint-1, eval = FALSE}
fit_bern <- brm(formula = ...,
                ... = poll_data,
                family = bernoulli(),
                ... = 0,
                silent = ...,
                ... = 9)
```

This will take a little while to run. It won't produce anything because of the `refresh` and `silent` arguments. 


### Exercise 7

Type `fit_bern` and hit "Run Code." This generates the same results as using `print(fit_bern)`.


```{r courage-7, exercise = TRUE}

```

```{r courage-7-hint-1, eval = FALSE}
...
```

```{r courage-7-test, include = FALSE}
print(fit_bern)
```

### 

<!-- XX Same some general words about the object. Note that we are about to go through the top 4 rows. -->

<!-- Add summary() Exercise if it gives a different answer -->

### Exercise 8

Run `family()` on `fit_bern`. `family()` provides information about the "family" of the error term and the link between it and the dependent variable. 

```{r courage-8, exercise = TRUE}

```

```{r courage-8-hint-1, eval = FALSE}
family(...)
```

```{r courage-8-test, include = FALSE}
family(fit_bern)
```

### 

<!-- DK: This is good material, but too long. And too complex for this first pass. -->

In this case, we see that the family of the error term is bernoulli. In a Bernoulli data generating mechanism, we have:

$$ biden_i  \sim Bernoulli(\rho) $$

Each voter $i$ which we sample either supports Biden or they do not. If person $i$ supports Biden, the value drawn is `1`, which is the standard way of representing `TRUE`.

The default link function for a Bernoulli model is logit, as in:

$$
\rho = \frac{e^{\beta_0}}{1 + e^{\beta_0}}
$$
By definition, the parameter $\rho$ is only allowed to take values between 0 and 1. We want to constrain the model so that only these values are even possible.

### Exercise 9

Run `formula()` on `fit_bern`. `formula()` returns the statistical equation which relates the dependent variable to the independent variable(s). 

```{r courage-9, exercise = TRUE}

```

```{r courage-9-hint-1, eval = FALSE}
formula(...)
```

```{r courage-9-test, include = FALSE}
formula(fit_bern)
```

### 

In this case, we have the simplest possible formula. `biden`, which is a zero/one binary variable is a function of a constant. There are no independent variables.

### Exercise 10

Run `nobs()` on `fit_bern`. The `nobs()` function returns the **n**umber of **obs**ervations.

```{r courage-10, exercise = TRUE}

```

```{r courage-10-hint-1, eval = FALSE}
nobs(...)
```

```{r courage-10-test, include = FALSE}
nobs(fit_bern)
```

### 

In this case, the number of observations is `r scales::comma(nobs(fit_bern))`. 

### Exercise 11

Run `posterior_interval()` on `fit_bern`. The `posterior_interval()` function returns 95% intervals for all the parameters in our model.

```{r courage-11, exercise = TRUE}

```

```{r courage-11-hint-1, eval = FALSE}
posterior_interval(...)
```

```{r courage-11-test, include = FALSE}
posterior_interval(fit_bern)
```

### 

There are several parameters in the model, almost all of them so-called "nuisance" parameters, meaning that we don't care about them. Their particular values don't really help us to directly calculate any quantity of interest.


### Exercise 12

Run `fixef()` on `fit_bern`. The `fixef()` returns information about the **fix**ed **ef**fects in the model.

```{r courage-12, exercise = TRUE}

```

```{r courage-12-hint-1, eval = FALSE}
fixef(...)
```

```{r courage-12-test, include = FALSE}
fixef(fit_bern)
```

### 

The "Intercept" is the key part of the model. Because the family is (incorrectly!) Gaussian and the link function an identity, the actual model we are estimating looks like:

$$ biden_i =  \mu + \epsilon_i $$

with $\epsilon_i \sim N(0, \sigma^2)$. $y_i$ is the height of male $i$. $\mu$ is true proportion of Biden voters. $\epsilon_i$ is the "error term," the difference between the vote of person $i$ and the true proportion of Biden voters.

### Exercise 13

Run `pp_check()` on `fit_bern` with the `type` argument set to `"bars"`.  The `pp_check()` runs a **p**osterior **p**redictive check.

<!-- DK: Agreed on below. Do it. -->

<!-- SD: It would be nice to include that pp_check() is a function from the *bayesplot* package, which is a completely different (from ggplot2) way of making graphs. This just clears the confusion. -->

```{r courage-13, exercise = TRUE}

```

```{r courage-13-hint-1, eval = FALSE}
pp_check(...,  type = "...")
```

```{r courage-13-test, include = FALSE}
pp_check(fit_bern,  type = "bars")
```

### 

In this case, there are two possible outcomes: 0/1. The actual values in the data are labeled `y`. We use our fitted model, `fit_bern` to generate 10 alternate data sets, 10 "fake" data sets. What might the number of votes for (and not for) Biden look like if `fit_bern` is true. The graphic demonstrates that the fake data is very similar to the real data, thus suggesting that our model has captured reality, at least somewhat. 

If the fake data had looked very different from the real data, we have had a problem.  


### Exercise 14

Use `library()` to load the [**gtsummary**](https://www.danieldsjoberg.com/gtsummary) package.

```{r courage-14, exercise = TRUE}

```

```{r courage-14-hint-1, eval = FALSE}
library(gtsummary)
```

```{r courage-14-test, include = FALSE}
library(gtsummary)
```

### 

Read [this tutorial](https://www.danieldsjoberg.com/gtsummary/articles/tbl_regression.html) for an introduction to `tbl_regression()`, the most important function in the [**gtsummary**](https://www.danieldsjoberg.com/gtsummary) package.

### Exercise 15

Run `tbl_regression()` on `fit_bern` with `intercept = TRUE`. 


```{r courage-15, exercise = TRUE}

```

```{r courage-15-hint-1, eval = FALSE}
tbl_regression(..., intercept = TRUE)
```

```{r courage-15-test, include = FALSE}
tbl_regression(fit_bern, intercept = TRUE)
```

### 

The [**gtsummary**](https://www.danieldsjoberg.com/gtsummary) package includes many functions for formatting our table. The better your work looks, the more seriously people will take it.


### Exercise 16

Write a few sentence which summarize your work so far. The first few sentences are the same as what you had at the end of the Justice Section. Add one sentence which describes the modelling approach which you are using. Then, add a sentence which tells us something about the model.

```{r courage-16}
question_text(NULL,
	message = "XX.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

## Temperance
### 

<!-- XX: Discuss newdata objects slowly. "A newdata tibble must include columns for all the right-hand side variables --- all the "covariates" --- in the model, and with all the same variable names and, mostly, variable types." 

First ask a question about which columns are needed in the newdata object. This might just be a written question. The answer is all the variables which are on the rightside of the formula. 

Second, ask a question about which values you want those variables to have. That is not easy! Again, a written answer. For each row in the newdata tibble, you get a new posterior. How many posteriors do you want? 

Third, give them the R code which creates the newdata object. All they need to do is run it. Asking them to create it, even after you help them figure out the columns (question 1) and rows (question 2) is too hard, at least until they get more experiences. 

Fourth, inform them that you have, behind the scenes (which really means the setup code chunk), already assigned this tibble to the `ndata` object. In this question, they just type `ndata` to confirm. 

The knowledge drops for all four of these questions allow you to explain/teach more about what goes in the argument for newdata and what does not. Explaining what other newdata objects would produce, if we used them, is a good idea.

-->

<!-- XX: Choose one. -->

*Temperance is a tree which as for its root very little contentment, and for its fruit calm and peace.* - Buddha


### Exercise 1

In your own words, describe the use of Temperance in finishing your data science project.

```{r temperance-1}
question_text(NULL,
	message = "Temperance uses the Data Generating Mechanism to answer the question with which we began. Humility reminds us that this answer is always a lie.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

Recall the question with which we began:

> ...

Pipe `fit_XX` to . . .

```{r temperance-2, exercise = TRUE}

```

```{r temperance-2-hint-1, eval = FALSE}

```

<!-- DK: Edit the below. -->

```{r temperance-2-test, include = FALSE}
fit_bern |> 
  add_epred_draws(newdata = tibble(.rows = 1)) |> 
  select(.epred) |> 
  ggplot(aes(x = .epred)) +
    geom_density(aes(y = after_stat(count/sum(count))))  +
    labs(title = expression(paste("Posterior Distribution for  ", rho)),
         subtitle = "There is a 95% chance for a value between XX and XX.",
         x = expression(paste("Proportion, ", rho, ", of Red Beads in Urn")),
         y = "Probability") +
    scale_x_continuous(labels = scales::percent_format()) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()
```

### 

### Exercise 3

Write a paragraph which summarizes the project in your own words. The first few sentences are the same as what you had at the end of the Courage Section. But, since your question may have evolved, you should feel free to change those sentences. Add at least one sentence which describes at least one quantity of interest (QoI) --- presumably one that answers your question -- and which provides a measure of uncertainty about that QoI. 

```{r temperance-3}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 4

Write a few sentences which explain why the estimates for the quantities of interest, and the uncertainty thereof, might be wrong. Suggest an alternative estimate and confidence interval.

```{r temperance-4}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

## Summary
### 

This tutorial covered [Chapter 4: Models](https://ppbds.github.io/primer/models.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 



```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
