---
title: 'Two Parameters: Gubernatorial Candidates'
tutorial:
  id: two-parameters-gubernatorial-candidates
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: Use data from US gubernatorial elections to construct a two-parameter
  model.
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(skimr)
library(rstanarm)
library(ggthemes)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local")

winners <- governors %>% 
  filter(win_margin > 0) %>% 
  select(year, first_name, last_name, election_age)

set.seed(1)

tests <- tibble(score = floor(rnorm(100, mean = 90, sd = 4))) %>% 
  filter(score < 101)

winners_ages <- winners %>% 
  select(election_age)

winners_model <- stan_glm(data = winners_ages,
                          formula = election_age ~ 1,
                          refresh = 0,
                          family = gaussian())

age_bias_plot <- governors %>% 
  select(year, election_age) %>% 
  group_by(year) %>% 
  summarise(avg_elec = mean(election_age)) %>% 
  ungroup() %>% 
  ggplot(aes(x = year, y = avg_elec)) +
  geom_point() +
  geom_smooth(method = 'loess',
              se = FALSE,
              formula = y ~ x) +
  theme_classic() +
  labs(title = "Average age of deceased US gubernatorial candidates over time",
       subtitle = "Recently deceased candidates were likely to have been older than those longer deceased",
       x = "Year",
       y = "Average age of candidates")
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

<!-- First do it stupidly, where you just use all the winners. In the discussion of Justice, you should mention your concerns, but maybe ignore them for now. -->

<!-- Then, do it all again (not Wisdom again, but a bunch of things again).  With winners restricted to just elections before 1970 or whatever. -->

<!-- Then do it all again with only one row per candidate. -->

<!-- Age bias: The ages will tend to be slightly older the greater the year is because we're only sampling from now-deceased candidates. The more we filter our data to only include early years, the more accurate data will be, but the less data points we'll have. So, in other words, we are trading PRECISION for ACCURACY. This is a super cool opportunity to discuss this type of tradeoff, and whether or not making it is worth it (- it is). -->

So, now we have three versions of the anwser, corresponding to three different assumptions. 

## Base Case

### 

In this tutorial, we'll be creating a two-parameter model using the `governors` data from **primer.data**.

### Exercise 1

Data science projects always begin with a question. 

_What is the probability of a governor elected in 2022 being over the age of 60?_

### 

Run `?governors`. Read the description of the data. 

```{r base-case-1, exercise = TRUE}

```

```{r base-case-1-hint-1, eval = FALSE}
?governors
```

### 

Notice that this data set only includes data for candidates who are now deceased. Keep details like these in mind as they may help in answering future questions about representativeness and validity.

### Exercise 2

Print out the `governors` tibble. 

```{r base-case-2, exercise = TRUE}

```

```{r base-case-2-hint-1, eval = FALSE}
print(...)
```

### 

Notice that James Folsom appears more than once in this data.

Duplicate candidates *could* make this data unsuitable for answering certain questions — another important detail to keep in mind.

### Exercise 3

Use `skim()` from the **skimr** package to skim the `governors` data.

```{r base-case-3, exercise = TRUE}

```

```{r base-case-3-hint-1, eval = FALSE}
skim(...)
```

### 

Look at the `election_age` variable. Notice it has zero missing values, and an average of 51.7.

### Exercise 4

In our case, we are asking a question about the next *elected* candidate, not just the next candidate. We only care about the winners.

Start a new pipe with `governors`. Use `filter()` to choose only rows with a positive win margin (i.e. elected candidates).

```{r base-case-4, exercise = TRUE}

```

```{r base-case-4-hint-1, eval = FALSE}
governors %>% 
  filter(...)
```

```{r base-case-4-hint-2, eval = FALSE}
governors %>% 
  filter(win_margin > ...)
```

### Exercise 5

Copy your code from above. Continue your pipe by using `select()` to select `year`, `first_name`, `last_name`, and `election_age`.

```{r base-case-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-5-hint-1, eval = FALSE}
governors %>% 
  filter(...) %>% 
  select(...)
```

### Exercise 6

Copy your code from above and assign it to a new object called `winners`.

```{r base-case-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-6-hint-1, eval = FALSE}
... <- governors %>% 
  filter(...) %>% 
  select(...)
```

### 

We'll be using `winners` in later questions in this tutorial.

### Exercise 7

Recall our question:

_WWhat is the probability of a governor elected in 2022 being over the age of 60?_

### 

Our population table has *Preceptor Table* rows, *actual data* rows, and outstanding *population* rows. Describe, in a single short paragraph, what each of these three types of rows look like.

```{r base-case-7}
question_text(NULL,
	message = "There are 36 Preceptor Table rows — one for each of the 36 states with gubernatorial elections in 2022. All columns besides year and state have entires that are \"?\" (unknowns). In our actual data rows, all column entires are known. However, we only have data for candidates who ran up until 2011, and who have passed away as of 2012. Our outstanding population rows include data from candiates in all years, as well as data from both currently alive and deceased candidates.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	options = list(nrows = 6))
```

### 

At this point, you may have some concerns regarding whether or not we can *accurately* answer our question using the given data.

Fortunately, Justice gives us a chance to address those concerns, and refine our data to eliminate those concerns if necessary.

### Exercise 8

<!-- GP: Since we changed the question from asking about Massachusetts to asking about all states with 2022 gubernatorial elections, I'm unsure what to put in the initial Justice segment. You said to *acknowledge* the problems, but not to fix them until the later 2nd and 3rd Justice segments. Well, I already acknowledged the problems near the beginning of Wisdom when we were examining the governors data (it's kinda impossible not to acknowledge them then). Still, even if I were to move the acknowledgements to this 1st Justice segment, it's not enough to warrant its own segment.

TL;DR: Not sure what to put in the initial Justice section. -->

### Exercise 9

Let's quickly review how to work with the `stan_glm()` function from the **rstanarm** package.

### 

Print out the `tests` tibble below.

```{r base-case-9, exercise = TRUE}

```

```{r base-case-9-hint-1, eval = FALSE}
print(tests)
```

### 

Let's use this data to remind ourselves how to create simple Bayesian models.

### Exercise 10

Run `stan_glm()` and set the `data` argument equal to `tests`, and the `formula` argument equal to `score ~ 1`.

```{r base-case-10, exercise = TRUE}

```

```{r base-case-10-hint-1, eval = FALSE}
stan_glm(data = ...,
         formula = ...)
```

### 

The `data` argument tells `stan_glm()` what data frame to work with.

The `formula` argument tells `stan_glm()` what model is to be fitted.

### Exercise 11

Let's tidy up our output a bit and get rid of the messy garbage lines.

Copy your code from above, and add a new argument called `refresh`. Set this argument to `0`.

```{r base-case-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-11-hint-1, eval = FALSE}
stan_glm(data = ...,
         formula = ...,
         refresh = ...)
```

### 

The `refresh` argument should usually be set to `0` lest you get R spitting back a bunch of garbage at you.

### Exercise 12

We should also tell `stan_glm()` what error distribution function to use in the model.

Copy your code from above. Insert a new argument called `family` and set it equal to `guassian()`.

```{r base-case-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-12-hint-1, eval = FALSE}
stan_glm(data = ...,
         formula = ...,
         refresh = ...,
         family = ...)
```

### 

Notice that our output did not change. This is because `family` is set to `gaussian()` by default. Still, it's good practice to always specify it yourself and eliminate some of the guesswork for R.

### Exercise 13

Now that we've recalled how to use `stan_glm()`, we can begin working with our data.

### 

Start a new pipe with `winners`. Use `select()` to select only the `election_age` variable. Assign this to a new object called `winners_ages`.

```{r base-case-13, exercise = TRUE}

```

```{r base-case-13-hint-1, eval = FALSE}
... <- winners %>% 
  select(...)
```

### 

`winners_ages` is what we'll be using to create our Bayesian model.

### Exercise 14

Use `stan_glm()` to create a Bayesian model of `winners_ages` with the formula `election_age ~ 1`. (Remember the four arguments that should be specified!)

```{r base-case-14, exercise = TRUE}

```

```{r base-case-14-hint-1, eval = FALSE}
stan_glm(data = ...,
         formula = ...,
         refresh = ...,
         family = ...)
```

### 

If you've done everything correctly, your output should look like this:

```{r stan-glm-output-1, echo = FALSE}
stan_glm(data = winners_ages,
         formula = election_age ~ 1,
         refresh = 0,
         family = gaussian)
```

### Exercise 15

Copy your code from above, and assign it to a new object called `winners_model`.

```{r base-case-15, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-15-hint-1, eval = FALSE}
winners_model <- stan_glm(data = ...,
                          formula = ...,
                          refresh = ...,
                          family = ...)
```

### 

We can now use this object to create our two-parameter model.

### Exercise 16

Start a new pipe with `winners_model`, and continue it with `as_tibble()`.

```{r base-case-16, exercise = TRUE}

```

```{r base-case-16-hint-1, eval = FALSE}
... %>% 
  as_tibble()
```

### Exercise 17

Now copy the code from above and continue your pipe using `rename()` to rename `(Intercept)` to `mu`.

```{r base-case-17, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-17-hint-1, eval = FALSE}
... %>% 
  as_tibble() %>% 
  rename(...)
```

### Exercise 18

Once again, copy the code from above and continue your pipe with `ggplot()`. Map `x` to `mu` in the `aes()` function. Use `geom_histogram()` and map `y` to the  `after_stat()` function. Set its argument to `count` divided by the `sum()` of `count`.

```{r base-case-18, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-18-hint-1, eval = FALSE}
... %>% 
  as_tibble() %>% 
  rename(...) %>% 
  ggplot(...) + 
  geom_histogram(...)
```

```{r base-case-18-hint-2, eval = FALSE}
... %>% 
  as_tibble() %>% 
  rename(...) %>% 
  ggplot(aes(x = ...)) + 
  geom_histogram(aes(y = ...))
```

### Exercise 19

Copy your code from above. Set the `bins` argument to 200 and the `color` argument to white within `geom_histogram()`.

```{r base-case-19, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-19-hint-1, eval = FALSE}
... %>% 
  as_tibble() %>% 
  rename(...) %>% 
  ggplot(aes(x = ...)) + 
  geom_histogram(aes(y = ...),
                 bins = ...,
                 color = ...)
```

### 

## Age Bias

### 

One concern we may have about our result is a potential bias towards older candidates.

This data's biggest drawback is that *all of the candidates in the data are now deceased*.

### 

This means that the candidates included in this data are likely to be older, since older candidates have a higher likelihood of now being dead than younger candidates.

This bias is more prevalent for later years, since the less time that passes between a candidate running for governor and a candidate dying, the older that candidate is likely to be.

Here is a graph illustrating the above point:

```{r age-bias-plot, echo = FALSE}
age_bias_plot
```

### Exercise 1

```{r age-bias-1}
question_text(NULL,
	message = "No answer yet",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	options = list(nrows = 6))
```

## Duplicate Candidates

```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
