---
title: 'Two Parameters: Gubernatorial Candidates'
tutorial:
  id: two-parameters-gubernatorial-candidates
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: Use data from US gubernatorial elections to construct a two-parameter
  model.
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(skimr)
library(rstanarm)
library(ggthemes)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local")

winners <- governors %>% 
  filter(win_margin > 0) %>% 
  select(year, first_name, last_name, election_age)

set.seed(1)

tests <- tibble(score = floor(rnorm(100, mean = 90, sd = 4))) %>% 
  filter(score < 101)

winners_ages <- winners %>% 
  select(election_age)

winners_model <- stan_glm(data = winners_ages,
                          formula = election_age ~ 1,
                          refresh = 0,
                          family = gaussian())

winners_model_draws <- posterior_predict(winners_model, newdata = tibble(constant = 1))

age_bias_plot <- governors %>% 
  select(year, election_age) %>% 
  group_by(year) %>% 
  summarise(avg_elec = mean(election_age)) %>% 
  ungroup() %>% 
  ggplot(aes(x = year, y = avg_elec)) +
  geom_point() +
  geom_smooth(method = 'loess',
              se = FALSE,
              formula = y ~ x) +
  theme_classic() +
  labs(title = "Average age of deceased US gubernatorial candidates over time",
       subtitle = "Recently deceased candidates were likely to have been older than those longer deceased",
       x = "Year",
       y = "Average age of candidates")
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

<!-- First do it stupidly, where you just use all the winners. In the discussion of Justice, you should mention your concerns, but maybe ignore them for now. -->

<!-- Then, do it all again (not Wisdom again, but a bunch of things again).  With winners restricted to just elections before 1970 or whatever. -->

<!-- Then do it all again with only one row per candidate. -->

<!-- Age bias: The ages will tend to be slightly older the greater the year is because we're only sampling from now-deceased candidates. The more we filter our data to only include early years, the more accurate data will be, but the less data points we'll have. So, in other words, we are trading PRECISION for ACCURACY. This is a super cool opportunity to discuss this type of tradeoff, and whether or not making it is worth it (- it is). -->

So, now we have three versions of the anwser, corresponding to three different assumptions. 

## Base Case

### 

In this tutorial, we'll be creating a two-parameter model using the `governors` data from **primer.data**.

### Exercise 1

Data science projects always begin with a question.

_What is the probability of a governor elected in 2022 being over the age of 60?_

### 

Run `?governors`. Read the description of the data. 

```{r base-case-1, exercise = TRUE}

```

```{r base-case-1-hint-1, eval = FALSE}
?governors
```

### 

Notice that this data set only includes data for candidates who are now deceased. Keep details like these in mind as they may help in answering future questions about representativeness and validity.

### Exercise 2

Print out the `governors` tibble. 

```{r base-case-2, exercise = TRUE}

```

```{r base-case-2-hint-1, eval = FALSE}
print(...)
```

### 

Notice that James Folsom appears more than once in this data.

Duplicate candidates *could* make this data unsuitable for answering certain questions — another important detail to keep in mind.

### Exercise 3

Use `skim()` from the **skimr** package to skim the `governors` data.

```{r base-case-3, exercise = TRUE}

```

```{r base-case-3-hint-1, eval = FALSE}
skim(...)
```

### 

Look at the `election_age` variable. Notice it has zero missing values, and an average of 51.7.

### Exercise 4

In our case, we are asking a question about the next *elected* candidate, not just the next candidate. We only care about the winners.

Start a new pipe with `governors`. Use `filter()` to choose only rows with a positive `win_margin` (i.e. elected candidates).

```{r base-case-4, exercise = TRUE}

```

```{r base-case-4-hint-1, eval = FALSE}
governors %>% 
  filter(...)
```

```{r base-case-4-hint-2, eval = FALSE}
governors %>% 
  filter(win_margin > ...)
```

### Exercise 5

Copy your code from above. Continue your pipe by using `select()` to select `year`, `first_name`, `last_name`, and `election_age`.

```{r base-case-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-5-hint-1, eval = FALSE}
governors %>% 
  filter(...) %>% 
  select(...)
```

### Exercise 6

Copy your code from above and assign it to a new object called `winners`.

```{r base-case-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-6-hint-1, eval = FALSE}
... <- governors %>% 
  filter(...) %>% 
  select(...)
```

### 

We'll be using `winners` in later questions in this tutorial.

### Exercise 7

Recall our question:

_What is the probability of a governor elected in 2022 being over the age of 60?_

### 

Our Population Table has *Preceptor Table* rows, *actual data* rows, and outstanding *Population* rows. Describe, in a single short paragraph, what each of these three types of rows look like.

```{r base-case-7}
question_text(NULL,
	message = "There are 36 Preceptor Table rows — one for each of the 36 states with gubernatorial elections in 2022. All columns besides year and state have entires that are \"?\" (unknowns). In our actual data rows, all column entires are known. However, we only have data for candidates who ran up until 2011, and who have passed away as of 2012. Our outstanding Population rows include data from candiates in all years, as well as data from both currently alive and deceased candidates.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

At this point, you may have some concerns regarding whether or not we can *accurately* answer our question using the given data.

Fortunately, _Justice_ gives us a chance to address those concerns, and refine our data to eliminate those concerns if necessary.

### Exercise 8

The first thing we must ask ourselves after we've determined what the rows of our Population Table look like, is whether or not our data demonstrates *validity*.

Validity is a question of whether or not the columns of our Preceptor table mean the same thing as the columns of our actual data. 

###

In 1-2 sentences, explain why we can assume that our data demonstrates validity as per our above definition.

```{r base-case-8}
question_text(NULL,
	message = "In the context of our data, validity is a question of whether the election ages recorded in our data (in 1945-2011) mean the same thing as election ages in our preceptor table (in 2022). Since we can assume that the average height of people hasn't changed all that much in the past 77 years, we can assume that our data demonstrates validity.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 


For the rest of this tutorial, we'll assume that our data demonstrates validity.

### Exercise 9

Our two-parameter model will have the following functional form:

$$ y_i =  \mu + \epsilon_i$$

$$\epsilon_i \sim \mathcal{N}(0, \sigma^2)$$

Our two parameters are $\mu$ (the mean election age) and $\sigma$ (the standard deviation).

### 

Justice requires us to ask whether or not the relationship among the variables demonstrates *stability*. That is, can we assume that our value of $\mu$ stays constant across different time periods?

In 2-3 sentences, answer the above question for our data:

```{r base-case-9}
question_text(NULL,
	message = "For now, we will be assuming that the answer is yes; that is, our data is stable. We have to be careful, though, because this question of stability is a nuanced one. For instance, we could make the argument that the average election age has increased because there may be more candidates now who had previously run for governor when they were younger, and are re-running now at an older age.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

There's a lot of arguments to be made against stability, but for now, we will assume that our model is stable. We'll discuss the potential age bias later in this tutorial.

### Exercise 10

We have addressed both the *validity*, and the *stability* of our data. All that's left now is to address its *representativeness*. That is, are the rows we have sufficiently representative of the rows we don't have?

### 

Another way to think about representativeness is that stability has told us we have a $\mu$ which stays constant. The question now is: can we *accurately* compute this $\mu$ using the data we have?

In 2-3 sentences, answer the above question for our data:

```{r base-case-10}
question_text(NULL,
	message = "The answer is, generally speaking, no. A key detail that you should remember from earlier is that all of our data comes from gubernatorial candidates who are now deceased. We cannot and should not assume that data coming from now-deceased candidates is sufficiently representative of alive candidates — especially when dealing with a variable such as age.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Although our data is not representative, we'll assume it is for now for the sake of the learning experience. Though rest assured, we'll make sure to discuss and fix this error in a later section of this tutorial.

### Exercise 11

Let's quickly review how to work with the `stan_glm()` function from the **rstanarm** package.

### 

Print out the `tests` tibble below.

```{r base-case-11, exercise = TRUE}

```

```{r base-case-11-hint-1, eval = FALSE}
print(tests)
```

### 

Let's use this data to remind ourselves how to create simple Bayesian models.

### Exercise 12

Run `stan_glm()` and set the `data` argument equal to `tests`, and the `formula` argument equal to `score ~ 1`.

```{r base-case-12, exercise = TRUE}

```

```{r base-case-12-hint-1, eval = FALSE}
stan_glm(data = ...,
         formula = ...)
```

### 

The `data` argument tells `stan_glm()` what data frame to work with.

The `formula` argument tells `stan_glm()` what model is to be fitted.

### Exercise 13

Let's tidy up our output a bit and get rid of the messy garbage lines.

Copy your code from above, and add a new argument called `refresh`. Set this argument to `0`.

```{r base-case-13, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-13-hint-1, eval = FALSE}
stan_glm(data = ...,
         formula = ...,
         refresh = ...)
```

### 

The `refresh` argument should usually be set to `0` lest you get R spitting back a bunch of garbage at you.

### Exercise 14

We should also tell `stan_glm()` what error distribution function to use in the model.

Copy your code from above. Insert a new argument called `family` and set it equal to `guassian()`.

```{r base-case-14, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-14-hint-1, eval = FALSE}
stan_glm(data = ...,
         formula = ...,
         refresh = ...,
         family = ...)
```

### 

Notice that our output did not change. This is because `family` is set to `gaussian()` by default. Still, it's good practice to always specify it yourself and eliminate some of the guesswork for R.

### Exercise 15

Now that we've recalled how to use `stan_glm()`, we can begin working with our data.

### 

Start a new pipe with `winners`. Use `select()` to select only the `election_age` variable. Assign this to a new object called `winners_ages`.

```{r base-case-15, exercise = TRUE}

```

```{r base-case-15-hint-1, eval = FALSE}
... <- winners %>% 
  select(...)
```

### 

`winners_ages` is what we'll be using to create our Bayesian model.

### Exercise 16

Use `stan_glm()` to create a Bayesian model of `winners_ages` with the formula `election_age ~ 1`. (Remember the four arguments that should be specified!)

```{r base-case-16, exercise = TRUE}

```

```{r base-case-16-hint-1, eval = FALSE}
stan_glm(data = ...,
         formula = ...,
         refresh = ...,
         family = ...)
```

### 

If you've done everything correctly, your output should look like this:

```{r stan-glm-output-1, echo = FALSE}
stan_glm(data = winners_ages,
         formula = election_age ~ 1,
         refresh = 0,
         family = gaussian)
```

### Exercise 17

Copy your code from above, and assign it to a new object called `winners_model`.

```{r base-case-17, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-17-hint-1, eval = FALSE}
winners_model <- stan_glm(data = ...,
                          formula = ...,
                          refresh = ...,
                          family = ...)
```

### 

We can now use this object to create our two-parameter model.

### Exercise 18

Start a new pipe with `winners_model`, and continue it with `as_tibble()`.

```{r base-case-18, exercise = TRUE}

```

```{r base-case-18-hint-1, eval = FALSE}
... %>% 
  as_tibble()
```

### Exercise 19

Now copy the code from above and continue your pipe using `rename()` to rename `(Intercept)` to `mu`.

```{r base-case-19, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-19-hint-1, eval = FALSE}
... %>% 
  as_tibble() %>% 
  rename(...)
```

### Exercise 20

Once again, copy the code from above and continue your pipe with `ggplot()`. Map `x` to `mu` in the `aes()` function. Use `geom_histogram()` and map `y` to the  `after_stat()` function. Set its argument to `count` divided by the `sum()` of `count`.

```{r base-case-20, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-20-hint-1, eval = FALSE}
... %>% 
  as_tibble() %>% 
  rename(...) %>% 
  ggplot(...) + 
  geom_histogram(...)
```

```{r base-case-20-hint-2, eval = FALSE}
... %>% 
  as_tibble() %>% 
  rename(...) %>% 
  ggplot(aes(x = ...)) + 
  geom_histogram(aes(y = ...))
```

### Exercise 21

Copy your code from above. Set the `bins` argument to 200 and the `color` argument to "white" within `geom_histogram()`.

```{r base-case-21, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-21-hint-1, eval = FALSE}
... %>% 
  as_tibble() %>% 
  rename(...) %>% 
  ggplot(aes(x = ...)) + 
  geom_histogram(aes(y = ...),
                 bins = ...,
                 color = ...)
```

### Exercise 22

Copy your code from above. Use `labs()` to give your histogram the title "Posterior Probability Distribution" and the subtitle "Average election age of US gubernatorial candidates deceased as of 2012". Rename the x-axis label to "Age" and the y-axis label to "Probability". Add a layer and use `theme_classic()` to make your plot look nice.

```{r base-case-22, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-22-hint-1, eval = FALSE}
... %>% 
  as_tibble() %>% 
  rename(...) %>% 
  ggplot(aes(x = ...)) + 
  geom_histogram(aes(y = ...),
                 bins = ...,
                 color = ...) +
  labs(title = ...,
       subtitle = ...,
       x = ...,
       y = ...)
```

### 

Reminder that your plot should look something like this:

```{r posterior-plot, echo = FALSE}
winners_model %>% 
  as_tibble() %>% 
  rename(mu = `(Intercept)`) %>% 
  ggplot(aes(x = mu)) + 
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = 200,
                 color = "white") +
  labs(title = "Posterior Probability Distribution",
       subtitle = "Average election age of US gubernatorial candidates deceased as of 2012",
       x = "Age",
       y = "Probability") +
  theme_classic()
```

### Exercise 23

We have a model of the average election age of US gubernatorial candidates. Temperance allows us to use our model to answer our initial question:

_What is the probability of a governor elected in 2022 being over the age of 60?_

### 

Use `posterior_predict()` with `winners_model` as the first argument to get some draws from our posterior distribution. Include an argument called `newdata` and set it equal to `tibble(constant = 1)`. 

```{r base-case-23, exercise = TRUE}

```

```{r base-case-23-hint-1, eval = FALSE}
posterior_predict(...)
```

```{r base-case-23-hint-2, eval = FALSE}
posterior_predict(winners_model, newdata = ...)
```

### 

Super! We now have 4000 estimates for a random gubernatorial candidate's election age.

### Exercise 24

Copy your code from above and assign it to a new object called `winners_model_draws`.

```{r base-case-24, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-24-hint-1, eval = FALSE}
... <- posterior_predict(...)
```

```{r base-case-24-hint-2, eval = FALSE}
... <- posterior_predict(winners_model, newdata = ...)
```

### Exercise 25

Copy your code from Exercise 22 (the exercise with our posterior plot). Replace `winners_model` with `as_tibble(winners_model_draws)`, replace `rename(mu = `(Intercept)`)` with `rename(mu = `1`)`, and retitle the plot "4000 Draws from a Posterior Distribution".

```{r base-case-25, exercise = TRUE}

```

### 

Your plot should look something like this:

```{r posterior-draws-plot, echo = FALSE}
as_tibble(winners_model_draws) %>% 
  as_tibble() %>% 
  rename(mu = `1`) %>% 
  ggplot(aes(x = mu)) + 
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = 200,
                 color = "white") +
  labs(title = "4000 Draws from a Posterior Distribution",
       subtitle = "Average election age of US gubernatorial candidates deceased as of 2012",
       x = "Age",
       y = "Probability") +
  theme_classic()
```

### Exercise 26

Recall our question: _What is the probability of a governor elected in 2022 being over the age of 60?_

Using _a single line of code_, determine the proportion of all candidates in `winners_model_draws` who are over the age of 60.

```{r base-case-26, exercise = TRUE}

```

```{r base-case-26-hint-1, eval = FALSE}
sum(... > 60) / length(...)
```

```{r base-case-26-hint-2, eval = FALSE}
sum(winners_model_draws$`1` > 60) / length(winners_model_draws$`1`)
```

## Age Bias

### 

One concern we have about our result is that it is biased towards older candidates.

### 

This data's biggest drawback is that *all of the candidates in the data are now deceased*. This means that the candidates included in this data are likely to be older, since older candidates have a higher likelihood of now being dead than younger candidates.

This bias is more prevalent for later years, since the less time that passes between a candidate running for governor and a candidate dying, the older that candidate is likely to be.

Here is a graph illustrating the above point:

```{r age-bias-plot, echo = FALSE}
age_bias_plot
```

### Exercise 1

Suppose we try to fix this bias by filtering the data so that it only includes candidates who ran in 1970 or earlier.

Describe, in one short paragraph, how this would affect the *precision* and the *accuracy* of the data.

```{r age-bias-1}
question_text(NULL,
	message = "No answer yet",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

## Duplicate Candidates

```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
