---
title: 'Two Parameters: Gubernatorial Candidates'
tutorial:
  id: two-parameters-gubernatorial-candidates
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: Chapter 7 tutorial part B
---

<!-- GP tutorial -->

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(skimr)
library(rstanarm)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local")

election <- governors %>% 
  select(election_age)
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

## Preliminaries

### 

In this tutorial, we'll be working with the `governors` data from `primer.data`.

### Exercise 1

Run `?governors`. Read the description of the data. 


```{r preliminaries-1, exercise = TRUE}

```

```{r preliminaries-1-hint-1, eval = FALSE}
?governors
```

###



### Exercise 2

Print out the `governors` tibble. 

```{r preliminaries-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r preliminaries-2-hint-1, eval = FALSE}
governors
```

### 



### Exercise 3

Use `skim()` from the `skimr` package to skim the `governors` data.

```{r preliminaries-3, exercise = TRUE}

```

```{r preliminaries-3-hint-1, eval = FALSE}
skim(...)
```

### 

Notice that the `election_age` has zero missing values, and an average of 51.7. This seems like a fun variable to work with!

### Exercise 4

Start a new pipe with `governors`. Select only the `election_age` variable. Assign this to a new object called `election`.

```{r preliminaries-4, exercise = TRUE}

```

```{r preliminaries-4-hint-1, eval = FALSE}
... <- governors %>% 
  select(...)
```

### 

We'll be using `election` later in this tutorial.

### Exercise 5

Let's quickly review how to work with the `stan_glm()` function from the `rstanarm` package.

### 

Recall that `stan_glm()` has four arguments that should always be specified:

* The `data` argument, which tells `stan_glm()` what data frame to work with.
* The `family` argument, which tells `stan_glm()` what error distribution and link function to use in the model.
* The `refresh` argument, which should usually be set to `0` lest you get R spitting back a bunch of garbage at you.
* The `formula` argument, which tells `stan_glm()` what model is to be fitted.

### 

Run

```{r preliminaries-5, exercise = TRUE}

```

```{r preliminaries-5-hint-1, eval = FALSE}

```

### 

<!-- 

Questions:

1. What is the average age of governors when they get elected?

2. What is the probability of the next elected governor being over the age of 60?

...

-->


## Wisdom

### Exercise 1

Suppose we wanted to answer the following question: _What is the probability of the next elected governor being over the age of 60?_

Write a paragraph about whether or not our data from `governors` is relevant in answering this question. Be sure to use terms like "population" and "Preceptor Table".

```{r wisdom-1}
question_text(NULL,
	message = "answer here",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	options = list(nrows = 6))
```

### 

## Justice

## Courage

## Temperance

```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
