---
title: 'Two Parameters: Gubernatorial Candidates'
tutorial:
  id: two-parameters-gubernatorial-candidates
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: Use data from US gubernatorial elections to construct a two-parameter
  model.
---

```{r setup, include = FALSE}
library(learnr)
library(all.primer.tutorials)
library(tidyverse)
library(primer.data)
library(skimr)
library(rstanarm)
library(ggthemes)
library(gt)
library(readr)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local")

winners <- governors |> 
  filter(win_margin > 0) |> 
  select(year, first_name, last_name, state, election_age)

set.seed(1)

winners_model <- stan_glm(data = winners,
                          formula = election_age ~ 1,
                          refresh = 0,
                          family = gaussian())

winners_draws <- posterior_predict(winners_model, newdata = tibble(constant = 1))

age_bias_plot <- governors |> 
  select(year, election_age) |> 
  summarise(avg_elec = mean(election_age),
            .by = year) |> 
  ggplot(aes(x = year, y = avg_elec)) +
  geom_point() +
  geom_smooth(method = 'loess',
              se = FALSE,
              formula = y ~ x) +
  theme_classic() +
  labs(title = "Average age of deceased US gubernatorial candidates over time",
       subtitle = "Recently deceased candidates were likely to have been older than those longer deceased",
       x = "Year",
       y = "Average age of candidates")

preceptor_table <- tibble(
  State = c("Alabama", "Alaska", "Arizona", "⋮"),
  Year = c("2022", "2022", "2022", "⋮"),
  `Election Age` = c("?", "?", "?", "⋮")
) |> 
  gt() |> 
  tab_header(title = "Preceptor Table")

population_table <- tibble(
  Source = c(
    rep("Preceptor Table", 3), "⋮",
    rep("Actual Data", 3), "⋮",
    rep("Outstanding Population", 3), "⋮"
  ),
  State = c(
    "Alabama", "Alaska", "Arizona", "⋮",
    "Virginia", "Connecticut", "Kentucky", "⋮",
    "Florida", "Montana", "Virginia", "⋮"
  ),
  Year = c(
    rep("2022", 3), "⋮",
    "1945", "1946", "1947", "⋮",
    "1990", "2000", "2025", "⋮"
  ),
  `Election Age` = c(
    rep("?", 3), "⋮",
    "49.1", "59.0", "52.5", "⋮",
    "60.6", "57.3", "?", "⋮"
  )
) |> 
  gt() |> 
  tab_header(title = "Population Table")

winners_1970 <- winners |> 
  filter(year <= 1970)

winners_1970_model <- stan_glm(data = winners_1970,
                               formula = election_age ~ 1,
                               refresh = 0,
                               family = gaussian)

winners_1970_draws <- posterior_predict(winners_1970_model,
                                        newdata = tibble(constant = 1))

# answer <- function(input) {
#   winners_year <- winners |> 
#     filter(year <= input)
#   winners_year_model <- stan_glm(data = winners_year,
#                                  formula = election_age ~ 1,
#                                  refresh = 0,
#                                  family = gaussian)
#   winners_year_draws <- posterior_predict(winners_year_model,
#                                           newdata = tibble(constant = 1))
#   return(sum(winners_year_draws > 60) / length(winners_year_draws))
# }
# 
# answ <- tibble(year = 1946:2003,
#                         answer = sapply(1946:2003, answer))
```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

<!-- GP: I decided against having the student make the age bias plot, as it would simply take too much time (it's a deceivingly simple plot to create) and it's not worth it in my opinion. -->

## Base Case

### 

In this tutorial, we'll be creating a two-parameter model using the `governors` data from **primer.data**.

### Exercise 1

Data science projects always begin with a question.

_What is the probability of a governor elected in 2022 being over the age of 60?_

### 

Run `?governors`. Read the description of the data. 

```{r base-case-1, exercise = TRUE}

```

```{r base-case-1-hint-1, eval = FALSE}
?governors
```

### 

Notice that this data set only includes data for candidates who are now deceased. Keep details like these in mind as they may help in answering future questions about representativeness and validity.

### Exercise 2

Print out the `governors` tibble. 

```{r base-case-2, exercise = TRUE}

```

```{r base-case-2-hint-1, eval = FALSE}
print(...)
```

### 

Notice that James Folsom appears more than once in this data. Duplicate candidates *could* make this data unsuitable for answering certain questions — another important detail to keep in mind.

### Exercise 3

Use `skim()` from the **skimr** package to skim the `governors` data.

```{r base-case-3, exercise = TRUE}

```

```{r base-case-3-hint-1, eval = FALSE}
skim(...)
```

### 

Look at the `election_age` variable. Notice it has zero missing values, and an average of 51.7.

### Exercise 4

In our case, we are asking a question about the next *elected* candidate, not just the next candidate. We only care about the winners.

Start a new pipe with `governors`. Use `filter()` to choose only rows with a positive `win_margin` (i.e. elected candidates).

```{r base-case-4, exercise = TRUE}

```

```{r base-case-4-hint-1, eval = FALSE}
governors |> 
  filter(...)
```

```{r base-case-4-hint-2, eval = FALSE}
governors |> 
  filter(win_margin > ...)
```

### Exercise 5

Copy your code from above. Continue your pipe by using `select()` to select `year`, `first_name`, `last_name`, `state`, and `election_age`.

```{r base-case-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-5-hint-1, eval = FALSE}
governors |> 
  filter(...) |> 
  select(...)
```

### Exercise 6

Copy your code from above and assign it to a new object called `winners`.

```{r base-case-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-6-hint-1, eval = FALSE}
... <- governors |> 
  filter(...) |> 
  select(...)
```

### 

We'll be using `winners` in later questions in this tutorial.

### Exercise 7

Recall our question:

_What is the probability of a governor elected in 2022 being over the age of 60?_

### 

Our _Preceptor Table_ is a table with minimal rows and columns such that we can perfectly answer our question using it. Describe, in 1-2 sentences, what the Preceptor Table for our question looks like.

```{r base-case-7}
question_text(NULL,
	message = "Our Preceptor Table will have 36 rows — one for each of the 36 states with gubernatorial elections in 2022. The table will have a state column, a year column (with all entries being \"2022\"), and an election age column.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Here is what our Preceptor Table would look like:

```{r echo = FALSE}
preceptor_table
```

### Exercise 8

When answering our question, we must also consider what our broader _Population Table_ looks like. List the three types of rows in our Population Table.

```{r base-case-8}
question_text(NULL,
	message = "Our Population Table has Preceptor Table rows, actual data rows, and outstanding Population rows.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Remember: the Preceptor Table is a _subset_ of the broader Population Table — meaning that all columns and rows in the Preceptor Table are, by definition, present in the Population Table as well.

### Exercise 9

What is a reasonable population from which we might consider the Preceptor Table and our actual data to have been drawn?

```{r base-case-9}
question_text(NULL,
	message = "Our broader population will closely resemble our actual data column-wise, except our broader population will also include data for more years (perhaps 1945-2025).",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

From the past three exercises, we can deduce that our Population Table will look something like this:

```{r echo = FALSE}
population_table
```

### Exercise 10

The first thing we must ask ourselves after we've determined what the rows of our Population Table look like, is whether or not our data demonstrates *validity*.

Validity is a question of whether or not the columns of our Preceptor table mean the same thing as the columns of our actual data. 

### 

In 1-2 sentences, explain why we _can_ assume that our data demonstrates validity as per our above definition.

```{r base-case-10}
question_text(NULL,
	message = "In the context of our data, validity is a question of whether the election ages recorded in our data (in 1945-2011) mean the same thing as election ages in our preceptor table (in 2022). Since we can assume that the average lifespan of people hasn't changed all that much in the past 77 years, we can assume that our data demonstrates validity.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

For the rest of this tutorial, we'll assume that our data demonstrates validity.

### Exercise 11

Our two-parameter model will have the following functional form:

$$ y_i =  \mu + \epsilon_i$$

$$\epsilon_i \sim \mathcal{N}(0, \sigma^2)$$

Our two parameters are $\mu$ (the mean election age) and $\sigma$ (the standard deviation).

### 

Justice requires us to ask whether or not the relationship among the variables demonstrates *stability*. That is, can we assume that our value of $\mu$ stays constant across different time periods?

In 2-3 sentences, give an argument for why we _cannot_ assume our data demonstrates stability:

```{r base-case-11}
question_text(NULL,
	message = "Many arguments can be made against the stability of this data. For instance, we could make the argument that the average election age has increased because there may be more candidates now who had previously run for governor when they were younger, and are re-running now at an older age.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

There's a lot of arguments to be made against stability, but for now, we will assume that our model _is_ stable. Do not worry however, we'll discuss this potential age bias later in the tutorial.

### Exercise 12

We have addressed both the *validity*, and the *stability* of our data. All that's left now is to address its *representativeness*. That is, are the rows we have sufficiently representative of the rows we don't have?

### 

Another way to think about representativeness is to recall our functional form:

$$ y_i =  \mu + \epsilon_i$$

$$\epsilon_i \sim \mathcal{N}(0, \sigma^2)$$

If stability tells us we have a $\mu$ which stays constant, representativeness asks whether or not we can *accurately* compute this $\mu$ using the data we have.

### 

In 2-3 sentences, give an argument for why we _cannot_ assume our data demonstrates representativeness:

```{r base-case-12}
question_text(NULL,
	message = "A key detail you should remember from earlier is that all of our data comes from gubernatorial candidates who are now deceased. We cannot and should not assume that data coming from now-deceased candidates is sufficiently representative of alive candidates — especially when dealing with a variable such as age.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Although our data is not representative, we'll assume it is for now for the sake of the learning experience. Though rest assured, we'll make sure to discuss and fix this error in a later section of this tutorial.

### Exercise 13

Let's quickly review how to work with the `stan_glm()` function from the **rstanarm** package.

### 

Run `stan_glm()` and set the `data` argument equal to `winners`, and the `formula` argument equal to `election_age ~ 1`.

```{r base-case-13, exercise = TRUE}

```

```{r base-case-13-hint-1, eval = FALSE}
stan_glm(data = ...,
         formula = ...)
```

### 

The `data` argument tells `stan_glm()` what data frame to work with.

The `formula` argument tells `stan_glm()` what model is to be fitted.

### Exercise 14

Let's tidy up our output a bit and get rid of the messy garbage lines.

Copy your code from above, and add a new argument called `refresh`. Set this argument to `0`.

```{r base-case-14, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-14-hint-1, eval = FALSE}
stan_glm(data = ...,
         formula = ...,
         refresh = ...)
```

### 

The `refresh` argument should usually be set to `0` lest you get R spitting back a bunch of garbage at you.

### Exercise 15

We should also tell `stan_glm()` what error distribution function to use in the model.

Copy your code from above. Insert a new argument called `family` and set it equal to `guassian`.

```{r base-case-15, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-15-hint-1, eval = FALSE}
stan_glm(data = ...,
         formula = ...,
         refresh = ...,
         family = ...)
```

### 

Notice that our output did not change. This is because `family` is set to `gaussian` by default. Still, it's good practice to always specify it yourself and eliminate some of the guesswork for R.

### Exercise 16

Copy your code from above, and assign it to a new object called `winners_model`.

```{r base-case-16, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-16-hint-1, eval = FALSE}
winners_model <- stan_glm(data = ...,
                          formula = ...,
                          refresh = ...,
                          family = ...)
```

### 

This is the object we're going to be using later to create our two-parameter model.

### Exercise 17

Use `print()` to print out `winners_model`, and set the `detail` argument equal to `FALSE`.

```{r base-case-17, exercise = TRUE}

```

```{r base-case-17-hint-1, eval = FALSE}
print(..., detail = ...)
```

### 

<!-- GP: You told me to explain the output of stan_glm() but I'm unsure how to make it fit. I'm having a hard time explaining it well enough without going off on a tangent. -->

### Exercise 18

Start a new pipe with `winners_model`, and continue it with `as_tibble()`.

```{r base-case-18, exercise = TRUE}

```

```{r base-case-18-hint-1, eval = FALSE}
... |> 
  as_tibble()
```

### Exercise 19

Now copy the code from above and continue your pipe using `rename()` to rename `(Intercept)` to `mu`.

```{r base-case-19, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-19-hint-1, eval = FALSE}
... |> 
  as_tibble() |> 
  rename(...)
```

### Exercise 20

Once again, copy the code from above and continue your pipe with `ggplot()`. Map `x` to `mu` in the `aes()` function. Use `geom_histogram()` and, within _its_ `aes()` function, map `y` to `after_stat(count/sum(count))`.

```{r base-case-20, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-20-hint-1, eval = FALSE}
... |> 
  as_tibble() |> 
  rename(...) |> 
  ggplot(...) + 
  geom_histogram(...)
```

```{r base-case-20-hint-2, eval = FALSE}
... |> 
  as_tibble() |> 
  rename(...) |> 
  ggplot(aes(x = ...)) + 
  geom_histogram(aes(y = ...))
```

### Exercise 21

Copy your code from above. Set the `bins` argument to 200 and the `color` argument to "white" within `geom_histogram()`.

```{r base-case-21, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-21-hint-1, eval = FALSE}
... |> 
  as_tibble() |> 
  rename(...) |> 
  ggplot(aes(x = ...)) + 
  geom_histogram(aes(y = ...),
                 bins = ...,
                 color = ...)
```

### Exercise 22

Copy your code from above. Use `scale_y_continuous()` and set its `labels` argument equal to `scales::percent` in order to represent your probabilities as percentages.

```{r base-case-22, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-22-hint-1, eval = FALSE}
... |> 
  as_tibble() |> 
  rename(...) |> 
  ggplot(aes(x = ...)) + 
  geom_histogram(aes(y = ...),
                 bins = ...,
                 color = ...) + 
  scale_y_continuous(...)
```

### Exercise 23

Copy your code from above. Use `labs()` to give your histogram the title "Posterior Probability Distribution" and the subtitle "Average election age of US gubernatorial candidates deceased as of 2012". Rename the x-axis label to "Age" and the y-axis label to "Probability". Add a layer of `theme_classic()` to make your plot look nice.

```{r base-case-23, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-23-hint-1, eval = FALSE}
... |> 
  as_tibble() |> 
  rename(...) |> 
  ggplot(aes(x = ...)) + 
  geom_histogram(aes(y = ...),
                 bins = ...,
                 color = ...) +
  scale_y_continuous(...) +
  labs(title = ...,
       subtitle = ...,
       x = ...,
       y = ...)
```

### 

Reminder that your plot should look something like this:

```{r posterior-plot, echo = FALSE}
winners_model |> 
  as_tibble() |> 
  rename(mu = `(Intercept)`) |> 
  ggplot(aes(x = mu)) + 
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = 200,
                 color = "white") +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Posterior Probability Distribution",
       subtitle = "Average election age of US gubernatorial candidates deceased as of 2012",
       x = "Age",
       y = "Probability") +
  theme_classic()
```

### Exercise 24

We have a model of the average election age of US gubernatorial candidates. Temperance allows us to use our model to answer our initial question:

_What is the probability of a governor elected in 2022 being over the age of 60?_

### 

Use `posterior_predict()` with `winners_model` as the first argument to get some draws from our posterior distribution. Include an argument called `newdata` and set it equal to `tibble(constant = 1)`. 

```{r base-case-24, exercise = TRUE}

```

```{r base-case-24-hint-1, eval = FALSE}
posterior_predict(...)
```

```{r base-case-24-hint-2, eval = FALSE}
posterior_predict(winners_model, newdata = ...)
```

### 

Super! We now have 4000 draws for a random gubernatorial candidate's election age.

### Exercise 25

Copy your code from above and assign it to a new object called `winners_draws`.

```{r base-case-25, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r base-case-25-hint-1, eval = FALSE}
... <- posterior_predict(...)
```

```{r base-case-25-hint-2, eval = FALSE}
... <- posterior_predict(winners_model, newdata = ...)
```

### Exercise 26

Copy your code from Exercise 23 (the exercise with our posterior plot). Replace `winners_model` with `winners_draws`, replace ``rename(mu = `(Intercept)`)`` with ``rename(mu = `1`)``, and re-title the plot "4000 Draws from a Posterior Distribution".

```{r base-case-26, exercise = TRUE}

```

```{r base-case-26-hint-1, eval = FALSE}
... |> 
  as_tibble() |> 
  rename(mu = ...) |> 
  ggplot(aes(x = mu)) + 
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = 200,
                 color = "white") +
  scale_y_continuous(labels = scales::percent) +
  labs(title = ...,
       subtitle = "Average election age of US gubernatorial candidates deceased as of 2012",
       x = "Age",
       y = "Probability") +
  theme_classic()
```

```{r base-case-26-hint-2, eval = FALSE}
winners_draws |> 
  as_tibble() |> 
  rename(mu = `1`) |> 
  ggplot(aes(x = mu)) + 
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = 200,
                 color = "white") +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "4000 Draws from a Posterior Distribution",
       subtitle = "Average election age of US gubernatorial candidates deceased as of 2012",
       x = "Age",
       y = "Probability") +
  theme_classic()
```

### 

Your plot should look something like this:

```{r posterior-draws-plot, echo = FALSE}
winners_draws |> 
  as.numeric() |> 
  as_tibble() |> 
  rename(mu = value) |> 
  ggplot(aes(x = mu)) + 
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = 200,
                 color = "white") +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "4000 Draws from a Posterior Distribution",
       subtitle = "Average election age of US gubernatorial candidates deceased as of 2012",
       x = "Age",
       y = "Probability") +
  theme_classic()
```

### Exercise 27

Recall our question: _What is the probability of a governor elected in 2022 being over the age of 60?_

Using _a single line of code_, determine the proportion of all candidates in `winners_draws` who are over the age of 60.

```{r base-case-27, exercise = TRUE}

```

```{r base-case-27-hint-1, eval = FALSE}
sum(... > 60) / length(...)
```

```{r base-case-27-hint-2, eval = FALSE}
sum(winners_draws > 60) / length(winners_draws)
```

## Age Bias

### 

The biggest drawback of the `governors` data is that *all of the candidates in the data are now deceased*. This means that the candidates included in this data are likely to be older, since older candidates have a higher likelihood of now being dead than younger candidates.

### 

This bias is more prevalent for later years, since the less time that passes between a candidate running for governor and a candidate dying, the older that candidate is likely to be.

Here is a graph illustrating the above point:

```{r age-bias-plot, echo = FALSE}
age_bias_plot
```

### Exercise 1

Let's try to fix this bias by filtering the data so that it only includes candidates who ran in 1970 or earlier.

Start a new pipe with `winners` and use `filter()` to select only rows with the `year` less than or equal to 1970.

```{r age-bias-1, exercise = TRUE}

```

```{r age-bias-1-hint-1, eval = FALSE}
winners |>
  filter(...)
```

### 

This tibble has only 421 rows, unlike the original `winners` tibble which has 576 rows.

### Exercise 2

Copy your code from above and assign it to a new object called `winners_1970`.

```{r age-bias-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r age-bias-2-hint-1, eval = FALSE}
... <- winners |> 
  filter(...)
```

### 

We'll use `winners_1970` to create a new model and examine how it differs from our original model.

### Exercise 3

Let's now create our Bayesian model. Use `stan_glm()` as we did before, except this time with `winners_1970` as our data argument. (Recall the four arguments that should be specified: `data`, `formula`, `refresh`, and `family`.)

```{r age-bias-3, exercise = TRUE}

```

```{r age-bias-3-hint-1, eval = FALSE}
stan_glm(data = ...,
         formula = ...,
         refresh = ...,
         family = ...)
```

```{r age-bias-3-hint-2, eval = FALSE}
stan_glm(data = winners_1970,
         formula = election_age ~ 1,
         refresh = 0,
         family = gaussian)
```

### 

Notice that the median of the `(Intercept)` (the average election age) is significantly lower in this model than in our last model.

### Exercise 4

Copy your code from above and assign it to a new object called `winners_1970_model`.

```{r age-bias-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r age-bias-4-hint-1, eval = FALSE}
... <- stan_glm(data = ...,
                formula = ...,
                refresh = ...,
                family = ...)
```

### 

We're going to forego making a plot of our posterior distribution this time, and instead skip to getting draws from the posterior distribution.

### Exercise 5

Use `posterior_predict()` with `winners_1970_model` as the first argument to get some draws from our posterior distribution. Include an argument called `newdata` and set it equal to `tibble(constant = 1)`. 

```{r age-bias-5-hint-1, eval = FALSE}
posterior_predict(...)
```

```{r age-bias-5-hint-2, eval = FALSE}
posterior_predict(winners_1970_model, newdata = ...)
```

### 

Wonderful! We now have 4000 draws for a random gubernatorial candidate's election age using our updated model.

### Exercise 6

Copy your above code and assign it to a new object called `winners_1970_draws`.

```{r age-bias-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r age-bias-6-hint-1, eval = FALSE}
... <- posterior_predict(winners_1970_model, newdata = ...)
```

### 

We're now going to create a plot using these draws similar to how we created our previous plot. 

### Exercise 7

Start a new pipe with `winners_1970`, and continue it with `as_tibble()`.

```{r age-bias-7, exercise = TRUE}

```

```{r age-bias-7-hint-1, eval = FALSE}
... |> 
  as_tibble()
```

### Exercise 8

Now copy the code from above and continue your pipe using `rename()` to rename the `1` variable to `mu`.

```{r age-bias-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r age-bias-8-hint-1, eval = FALSE}
... |> 
  as_tibble() |> 
  rename(...)
```

### Exercise 9

Once again, copy the code from above and continue your pipe with `ggplot()`. Map `x` to `mu` in the `aes()` function. Use `geom_histogram()` and, within _its_ `aes()` function, map `y` to `after_stat(count/sum(count))`.

```{r age-bias-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r age-bias-9-hint-1, eval = FALSE}
... |> 
  as_tibble() |> 
  rename(...) |> 
  ggplot(...) + 
  geom_histogram(...)
```

```{r age-bias-9-hint-2, eval = FALSE}
... |> 
  as_tibble() |> 
  rename(...) |> 
  ggplot(aes(x = ...)) + 
  geom_histogram(aes(y = ...))
```

### Exercise 10

Copy your code from above. Set the `bins` argument to 200 and the `color` argument to "white" within `geom_histogram()`.

```{r age-bias-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r age-bias-10-hint-1, eval = FALSE}
... |> 
  as_tibble() |> 
  rename(...) |> 
  ggplot(aes(x = ...)) + 
  geom_histogram(aes(y = ...),
                 bins = ...,
                 color = ...)
```

### Exercise 11

Copy your code from above. Use `scale_y_continuous()` and set its `labels` argument equal to `scales::percent` in order to represent your probabilities as percentages.

```{r age-bias-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r age-bias-11-hint-1, eval = FALSE}
... |> 
  as_tibble() |> 
  rename(...) |> 
  ggplot(aes(x = ...)) + 
  geom_histogram(aes(y = ...),
                 bins = ...,
                 color = ...) + 
  scale_y_continuous(...)
```

### Exercise 12

Copy your code from above. Use `labs()` to give your histogram the title "Posterior Probability Distribution" and the subtitle "Average election age of US gubernatorial candidates up to 1970 deceased as of 2012". Rename the x-axis label to "Age" and the y-axis label to "Probability". Add a layer of `theme_classic()` to make your plot look nice.

```{r age-bias-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r age-bias-12-hint-1, eval = FALSE}
... |> 
  as_tibble() |> 
  rename(...) |> 
  ggplot(aes(x = ...)) + 
  geom_histogram(aes(y = ...),
                 bins = ...,
                 color = ...) +
  scale_y_continuous(...) +
  labs(title = ...,
       subtitle = ...,
       x = ...,
       y = ...)
```

### 

Your plot should look something like this:

```{r 1970-posterior-draws-plot, echo = FALSE}
as.numeric(winners_1970_draws) |> 
  as_tibble() |> 
  rename(mu = value) |> 
  ggplot(aes(x = mu)) + 
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = 200,
                 color = "white") +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Posterior Probability Distribution",
       subtitle = "Average election age of US gubernatorial candidates up to 1970 deceased as of 2012",
       x = "Age",
       y = "Probability") +
  theme_classic()
```

### 

Let's take a look at this new plot (in blue) compared to our previous plot (in red):

```{r regular-vs-1970, echo = FALSE}
tibble(a = as.numeric(winners_1970_draws), b = as.numeric(winners_draws)) |> 
  ggplot() + 
  geom_histogram(aes(x = b, y = after_stat(count/sum(count))),
                 bins = 200,
                 fill = "red",
                 alpha = .5) +
  geom_histogram(aes(x = a, y = after_stat(count/sum(count))),
                 bins = 200,
                 fill = "blue",
                 alpha = .5) +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Posterior Probability Distribution",
       subtitle = "Average election age of US gubernatorial candidates up to 1970 deceased as of 2012",
       x = "Age",
       y = "Probability") +
  theme_classic()
```

### 

We can see that our new distribution (in blue) is shifted leftward from our original distribution. Therefore, we can expect the new answer to our question to be lower than our original answer.

### Exercise 13

Recall our question: _What is the probability of a governor elected in 2022 being over the age of 60?_

Using _a single line of code_, determine the proportion of all candidates in `winners_1970_draws` who are over the age of 60.

```{r age-bias-13, exercise = TRUE}

```

```{r age-bias-13-hint-1, eval = FALSE}
sum(... > 60) / length(...)
```

```{r age-bias-13-hint-2, eval = FALSE}
sum(winners_1970_draws > 60) / length(winners_1970_draws)
```

###

Our new answer is closer to 9% as opposed to our original answer which was closer to 15%. This is quite the difference!

### Exercise 14

We definitely did a good job of (at least partially) eliminating the age bias in our original answer by filtering only for candidates who ran in the year 1970 or earlier. But... _why 1970?_

###

To be completely honest, 1970 was an arbitrary choice. We just as easily could have chosen any other year $n$. In fact, here's a plot showing what different answers we would have gotten had we chosen different values of $n$:

```{r answer-plot, echo=FALSE}
answer_tibble <- read_rds(file = "data/answ.rds")

answer_tibble |> 
  ggplot(aes(x = year, y = answer)) + 
  geom_point() + 
  geom_smooth(se = FALSE, formula = y ~ x) +
  labs(title = "Answer to our question using different filtrations",
       x = "n",
       y = "Answer when filtering for year ≤ n")
```

###

## Duplicate Candidates

```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
