---
title: One Parameter
tutorial:
  id: one-parameter
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: Chapter 6 tutorial
---

<!-- Make it more like the chapter, and the chapter more like it. -->

<!-- Need one more section which using the posterior to, for example, create the posterior of number red which will be drawn with a shovel of size 20. Use a posterior to create a new posterior. Turtles all the way down. Could also create the plot of the joint distribution. Try to teach again just what a joint distribution. -->

<!-- Maybe make the shovels_100 have 100 shovel sizes again? We cut that down to make it quicker, but maybe having 100 reps instead of a 1,000 was enough to solve our speed problem. -->

<!-- Should we do something with stan_glm? Probably. -->


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

# Key Data

set.seed(10)
urn <- tibble(color = c(rep("red", 400), rep("white", 600))) %>%
  sample_frac() %>% 
  mutate(ID = 1:1000) %>% 
  select(ID, color)

virtual_samples <- tibble(ID = 1:1000) %>% 
  mutate(shovel = map(ID, ~ sample_n(urn, size = 50))) %>% 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) %>% 
  mutate(numb_beads = map_int(shovel, ~ length(.$color))) %>% 
  mutate(prop_red = numb_red / numb_beads)

make_prop_red <- function(x, shovel_size, reps){
  tibble(ID = 1:reps) %>% 
    mutate(shovel = map(ID, ~ sample_n(x, size = shovel_size))) %>% 
    mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) %>% 
    mutate(numb_beads = map_int(shovel, ~ length(.$color))) %>% 
    mutate(prop_red = numb_red / numb_beads)
}
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

## Virtual sampling

### 

Let's create the following plot that shows sampling variation for 1000 samples from an urn that contains red and white beads.

```{r}
virt_p <- virtual_samples %>% 
  ggplot(aes(x = prop_red)) +
    geom_histogram(binwidth = 0.01, 
                   boundary = 0.4, 
                   color = "white") +
    labs(x = expression(hat(p)), 
         y = "Count",
         title = "Distribution of 1,000 proportions red") 

virt_p
```

### Exercise 1

Type `urn` below to inspect the urn we will be using in this section.

```{r virtual-sampling-1, exercise = TRUE}
set.seed(10)
urn <- tibble(color = c(rep("red", 400), rep("white", 600))) %>%
  sample_frac() %>% 
  mutate(ID = 1:1000) %>% 
  select(ID, color)
```

### Exercise 2

To simulate the process of real-world sampling, let’s take a sample of 50 beads from our virtual urn. To do so, start a pipe by creating a `tibble()` that has one variable `ID` that takes on the values 1 to 1000.

```{r virtual-sampling-2, exercise = TRUE}

```

```{r virtual-sampling-2-hint-1, eval = FALSE}
tibble(ID = ...)
```

### Exercise 3

Great. Now pipe your results to the function `mutate()` to create the variable `shovel`, which is set to the function `map()`. The first argument to `map()` should be `ID`. The second argument should use `sample_n()` to take a sample `size` 50 beads from `urn`.

```{r virtual-sampling-3, exercise = TRUE}

```

```{r virtual-sampling-3-hint-1, eval = FALSE}
tibble(ID = 1:1000) %>% 
  mutate(shovel = map(..., ~ sample_n(urn, size = ...)))
```

### Exercise 4

Continue your pipe with `mutate()` to create the variable `numb_red`, which will tells us the number of red beads present. Set `numb_red` to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `sum()` of where the column `color` of `shovel` is equal to red.

```{r virtual-sampling-4, exercise = TRUE}

```

```{r virtual-sampling-4-hint-1, eval = FALSE}
... %>% 
  mutate(... = map_int(..., ~ sum(.$color == "red")))
```

### Exercise 5

Great. Now use `mutate()` to create the variable `numb_beads`, which is set to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `length()` of the column `color` of `shovel`.
 

```{r virtual-sampling-5, exercise = TRUE}

```

```{r virtual-sampling-5-hint-1, eval = FALSE}
... %>% 
  mutate(numb_beads = map_int(..., ~ length(...)))
```

```{r virtual-sampling-5-hint-2, eval = FALSE}
... %>% 
  mutate(numb_beads = map_int(..., ~ length(.$color)))
```

### Exercise 6

Use `mutate()` one last time to create the variable `prop_red`, which is our estimate of the proportion of red beads in the urn. Set `prop_red` to `numb_red` divided by `numb_beads`.

```{r virtual-sampling-6, exercise = TRUE}

```

```{r virtual-sampling-6-hint-1, eval = FALSE}
... %>% 
   mutate(prop_red = ... / ...)
```

### Exercise 7

Copy/paste your code from above. Assign your code to an object named `virtual_samples`.

```{r virtual-sampling-7, exercise = TRUE}

```

```{r virtual-sampling-7-hint-1, eval = FALSE}
Use the assignment operator <-  to do so.
```

### Exercise 8

Awesome. Now start a pipe with `virtual_samples`. Use `ggplot()`to map `prop_red` to the x-axis. Also, add the layer `geom_histogram()` to create a histogram of our data.

```{r virtual-sampling-8, exercise = TRUE}

```

```{r virtual-sampling-8-hint-1, eval = FALSE}
virtual_samples %>% 
  ggplot(aes(...)) + 
  geom_histogram()
```

### Exercise 9

Within `geom_histrogram()` set `binwidth` to .01, `boundary` to .4, and `color` to "white".

```{r virtual-sampling-9, exercise = TRUE}

```

```{r virtual-sampling-9-hint-1, eval = FALSE}
... +
  geom_histrogram(..., ..., ...)
```

### Exercise 10

To finish, use `labs()` to give your graph the appropriate title and axis labels. See **hint** for guidance to create the symbol $\hat{p}$.


```{r virtual-sampling-10, exercise = TRUE}

```

Reminder: This is what your plot should look like. 

```{r}
virt_p
```

```{r virtual-sampling-10-hint-1, eval = FALSE}
Within labs(), set x to expression(hat(p))
```

## Different shovel sizes

### 

Let's create the following plot that displays different standard deviations of red bead proportions for 100 different shovel sizes.

```{r}
shovels_100 <- tibble(shovel_size = 1:100) %>%
  mutate(prop_red_results = map(shovel_size,
                                ~ make_prop_red(x = urn, 
                                           shovel_size = .x, 
                                           reps = 100))) %>% 
  mutate(prop_red_sd = map_dbl(prop_red_results, 
                               ~ pull(., prop_red) %>% sd()))

shovel_p <- shovels_100 %>%
 ggplot(aes(x = shovel_size, y = prop_red_sd)) +
 geom_point() +
 labs(title = "Sampling Variation",
      subtitle = "Larger samples have less variation",
      x = "Shovel size",
      y = "Standard deviation of the proportion red")

shovel_p
```

### Exercise 1

Before we begin, write two sentences explaining standard error.
<!-- The code below is showing up as code within a code chunk. Not sure how to change it so that it shows up as a written response submittable question -->
```{r different-shovel-siz-1, exercise = TRUE}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 2

Let's create a function that calculates the proportion of red beads. We start with hard code. Recall our code for  `virtual_samples` in the previous section. Place the code within { } of `function()`. Name the function `make_prop_red()`.

```{r different-shovel-siz-2, exercise = TRUE}
tibble(ID = 1:1000) %>% 
  mutate(shovel = map(ID, ~ sample_n(urn, size = 50))) %>% 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) %>% 
  mutate(numb_beads = map_int(shovel, ~ length(.$color))) %>% 
  mutate(prop_red = numb_red / numb_beads)
```

```{r different-shovel-siz-2-hint-1, eval = FALSE}
make_prop_red <- function(){
  
  ...
  
}

```

### Exercise 3

Copy/paste your code from above. Add the parameter `reps` within `function()`. Also replace the value 1000 within `tibble()` with `reps`.

```{r different-shovel-siz-3, exercise = TRUE}

```

```{r different-shovel-siz-3-hint-1, eval = FALSE}
make_prop_red <- function(...){
  tibble(ID = 1:reps) %>% 
    ...
}
```

### Exercise 4

Copy/paste your code from above. Add the parameter `x` within `function()`. Also replace the argument `urn` with `x` within `sample_n()`.

```{r different-shovel-siz-4, exercise = TRUE}

```

```{r different-shovel-siz-4-hint-1, eval = FALSE}
make_prop_red <- function(reps, ...){
  tibble(ID = 1:reps) %>% 
  mutate(shovel = map(ID, ~ sample_n(x, size = 50))) %>% 
    ...
}
```

### Exercise 5

Copy/paste your code from above. Add the parameter `shovel_size` within `function()`. Also set `size` to `shovel_size` within `sample_n()`.

```{r different-shovel-siz-5, exercise = TRUE}

```

```{r different-shovel-siz-5-hint-1, eval = FALSE}
make_prop_red <- function(reps, x, ...){
  tibble(ID = 1:reps) %>% 
  mutate(shovel = map(ID, ~ sample_n(x, size = ...))) %>% 
    ...
}
```

### Exercise 6

Great. Let's now create a `tibble()` with one variable `shovel_size`, which takes on the values 1 through 100. 

```{r different-shovel-siz-6, exercise = TRUE}

```

```{r different-shovel-siz-6-hint-1, eval = FALSE}
tibble(shovel_size = ...)
```

### Exercise 7

Pipe your results to `mutate()` to create the variable `prop_red_results`, which is set to the function `map()`.The first argument to `map()` should be `shovel_size`. The second argument should be our function `make_prop_red()` where `x` is set to `urn`, `shovel_size` set to `.x`, and `reps` set to 100.
 

```{r different-shovel-siz-7, exercise = TRUE}

```

```{r different-shovel-siz-7-hint-1, eval = FALSE}
... %>% 
  mutate(prop_red_results = map(...,
                                ~ make_prop_red(..., ..., ...)))
```

### Exercise 8

Use `mutate()` once more to create the variable `prop_red_sd`, which is set to the function `map_dbl()`. The first argument to `map_dbl()` should be `prop_red_results`. The second argument should be `pull()`. The first argument to `pull()` should be `.`. The second argument should be `prop_red`.

```{r different-shovel-siz-8, exercise = TRUE}

```

```{r different-shovel-siz-8-hint-1, eval = FALSE}
... %>% 
mutate(... = map_dbl(..., 
                      ~ pull(., prop_red))
```

### Exercise 9

Let's find the standard deviation of proportions red for our shovel sizes. Pipe the results of `pull()` to the function `sd()`. **Note**: You are still inside `map_dbl()`.

```{r different-shovel-siz-9, exercise = TRUE}

```

```{r different-shovel-siz-9-hint-1, eval = FALSE}
mutate(prop_red_sd = map_dbl(prop_red_results, 
                               ~ pull(., prop_red) %>% ...)
```

### Exercise 11

Copy/paste your code from above. Assign your code to an object named `shovels_100`. 

```{r different-shovel-siz-11, exercise = TRUE}

```

### Exercise 12

Start a pipe with `shovels_100`. Use `ggplot()` to map `shovel_size` to the x-axis and `prop_red_sd` to the y-axis. Also add the layer `geom_point()`.

```{r different-shovel-siz-12, exercise = TRUE}

```

```{r different-shovel-siz-12-hint-1, eval = FALSE}
... %>% 
  ggplot(aes(x = ..., y = ...)) +
 geom_point() 
```

### Exercise 13

Now use `labs()` to label the x-axis "Shovel size" and the y-axis 
"Standard deviation of the proportion red". You should also provide a title and subtitle.

```{r different-shovel-siz-13, exercise = TRUE}

```

Reminder: This is what your plot should look like.

```{r}
shovel_p
```

```{r different-shovel-siz-13-hint-1, eval = FALSE}
... +
   labs(title = "Sampling Variation",
      subtitle = "Larger samples have less variation",
      x = "Shovel size",
      y = "Standard deviation of the proportion red")
```

## Posterior Distribution

### 

Let's create the following plot showing the posterior probability distribution of the proportion, $p$, of red beads in the urn.

```{r}
joint_dist <- 
  tibble(red_in_urn = seq(from = 0, to = 1000, by = 1)) %>% 
    mutate(p = red_in_urn / nrow(urn)) %>% 
    mutate(red_in_shovel = map(p, ~ rbinom(n = 100, 
                                               size = 50, 
                                               prob = .))) %>%
    unnest(red_in_shovel) 

posterior_p <- joint_dist %>% 
  filter(red_in_shovel == 17) %>% 
  ggplot(aes(x = p)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 50) + 
    labs(title = "Posterior Probability Distribution",
         subtitle = "Proportion of red beads in urn is centered around 0.34",
         x = "Proportion p of Red Beads in Urn",
         y = "Probability") + 
    scale_x_continuous(labels = scales::number_format()) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()

posterior_p
```

### Exercise 1

Create a `tibble()` with one variable `red_in_urn` that is set to the function `seq()`. Within `seq()` set `from` to 0, `to` to 1000, and `by` to 1.

```{r posterior-distributi-1, exercise = TRUE}

```

```{r posterior-distributi-1-hint-1, eval = FALSE}
tibble(red_in_urn = seq(...,...,...))
```

### Exercise 2

Great. Now pipe your results to the function `mutate()` to create the variable `p`, which is set to `red_in_urn` divided by the `nrow(urn)`.

```{r posterior-distributi-2, exercise = TRUE}

```

```{r posterior-distributi-2-hint-1, eval = FALSE}
... %>% 
    mutate(p = ... / ...) 
```

### Exercise 3

Great. Now pipe your results to the function `mutate()` to create the variable `red_in_shovel`, which is set to the function `map()`. The first argument to `map()` should be `p`. The second argument should use `rbinom()`. Within `rbinom()` set `n` to 100, `size` to 50, and `prob` to `.`

```{r posterior-distributi-3, exercise = TRUE}

```

```{r posterior-distributi-3-hint-1, eval = FALSE}
... %>% 
    mutate(red_in_shovel = map(..., ~ rbinom(..., 
                                             ..., 
                                              ...)))
```

### Exercise 4

Continue your pipe with the function `unnest()` with the argument `red_in_shovel`. **Note**: unnesting flattens list columns back into regular columns.

```{r posterior-distributi-4, exercise = TRUE}

```

```{r posterior-distributi-4-hint-1, eval = FALSE}
... %>%
    unnest(...) 
```

### Exercise 5

Copy/paste your code from above. Assign your code to an object named `joint_dist`.

```{r posterior-distributi-5, exercise = TRUE}

```

### Exercise 6

Let's plot our joint distribution we just created. Start a pipe with `joint_dist` and `filter()` where `red_in_shovel` is equal to 17.

```{r posterior-distributi-6, exercise = TRUE}

```

```{r posterior-distributi-6-hint-1, eval = FALSE}
...%>% 
  filter(red_in_shovel == ...)
```

### Exercise 7

Continue your pipe with `ggplot()`to map `p` to the x-axis. Also, add the layer `geom_histogram()`.

```{r posterior-distributi-7, exercise = TRUE}

```

```{r posterior-distributi-7-hint-1, eval = FALSE}
...%>% 
  ggplot(aes(...)) +
    geom_histogram()
```

### Exercise 8

Within `geom_histogram()`, use `after_stat()` . Inside `after_stat()`, use `aes()` with the argument `y = count/sum(count)` to convert the y-axis to percent values.

```{r posterior-distributi-8, exercise = TRUE}

```

```{r posterior-distributi-8-hint-1, eval = FALSE}
...%>% 
    geom_histogram(aes(y = after_stat(...))
```

### Exercise 9

Add the layer `scale_x_continuous()` with the argument `labels` set to `scales::number_format()`.

```{r posterior-distributi-9, exercise = TRUE}

```

```{r posterior-distributi-9-hint-1, eval = FALSE}
...%>% 
   scale_x_continuous(labels = ...)
```

### Exercise 10

Great. Now add the layer `scale_y_continuous()` with the argument `labels` set to `scales::percent_format()`.

```{r posterior-distributi-10, exercise = TRUE}

```

```{r posterior-distributi-10-hint-1, eval = FALSE}
...%>% 
   scale_y_continuous(labels = ...)
```

### Exercise 11

To finish, use `labs()` to give your graph the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.


```{r posterior-distributi-11, exercise = TRUE}

```

Reminder: This is what your plot should look like. 

```{r}
posterior_p
```

```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
