---
title: "Wrangling D"
tutorial:
  id: "wrangling-d"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Chapter 2 Tutorial Part D"
---

<!-- 20 or so questions, including making a plot or two which shows the results of some made up game like the coin tossing, using rnorm() and friends. -->


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 


# Key Data

set.seed(56)
games <- 1000 

tibble(A_heads = rbinom(n = games, size = 2, prob = 0.5),
       B_heads = rbinom(n = games, size = 4, prob = 0.5)) %>% 
  mutate(A_wins = ifelse(A_heads > B_heads, 1, 0)) %>% 
  summarize(A_chances = mean(A_wins))


```

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```

## Distributions
###

<!-- BG: test linking PR to issue -->

### Exercise 1

Let's create a distribution of the possible values from rolling a fair die. To do so, use the `c()` that contain values 1-6. Save your code to an object named `die`.

```{r d1, exercise = TRUE}

```

```{r d1-hint-1, eval = FALSE}
die <- c(...)
```

```{r d1-hint-2, eval = FALSE}
You can use the `:` operator as a shortcut! 
```

### Exercise 2

Let's now complete a single draw from our distribution using `sample()`. Within `sample()`, set the argument `x` to `die` and `size` to 1.

```{r d2, exercise = TRUE}

```

```{r d2-hint, eval = FALSE}
sample(x = ..., size = ...)
```

### Exercise 3

Copy and paste your code from above. Adjust the `size` argument to 12. Also add the argument `replace` set to TRUE.

```{r d3, exercise = TRUE}

```

```{r d3-hint, eval = FALSE}
Within `sample()`, you should have 3 arguments: x, size, and replace.
```

### Exercise 4

Let's say that before we draw, the probability of rolling a 5 is 0.5, and the probability of rolling any other value is 0.1. Copy and paste your code from above. Set the `prob` argument to a vector that contains each number's probability. 

```{r d4, exercise = TRUE}

```

```{r d4-hint-1, eval = FALSE}
Within c(), there should be six decimals (probability values) that correspond to each number of the die respectively. 
```

```{r d4-hint-2, eval = FALSE}
sample(x = die, 
       size = 10, 
       replace = TRUE, 
       prob = c(..., ..., ..., ... , 0.5, ...))
```

### Exercise 5

Let's now use `runif()` to try draw from a uniform distribution. Within `runif()`, set `n` to 5 (the number of draws), `min` to 5, and `max` to 8. 


```{r d5, exercise = TRUE}

```

```{r d5-hint, eval = FALSE}
runif(n = ..., min = ..., max =...)
```

### Exercise 6

Let's now use `rbinom` to try draw from a binomial distribution like flipping a coin. Within `rbinom()`, set `n` to 1, `size` to 1, and `prob` to .05.  

```{r d6, exercise = TRUE}

```

```{r d6-hint-1, eval = FALSE}
rbinom(... , ..., ....)
```

```{r d6-hint-2, eval = FALSE}
rbinom(n = ..., size = ..., prob = ....)
```

### Exercise 7

Let's put our code in tibble format using `tibble()`. Within `tibble()`, create a column `heads` which is set to the results of `rbinom()`. Within `rbinom()`, set `n` to 50, `size` to 1, and `prob` to .05. 

```{r d7, exercise = TRUE}

```

```{r d7-hint-1, eval = FALSE}
tibble(... = rbinom(..., ..., ...))
```

Notice that we now are drawing from a binomial distribution 50 times! We put the code in tibble format so we can plot it. 

### Exercise 8

Let's now plot our results. Copy and paste your code from above. Use ` %>% ` to add `ggplot()`. Map `heads` to the x-axis. Also add the layer `geom_bar()`.

```{r d8, exercise = TRUE}

```

```{r d8-hint, eval = FALSE}
... %>% 
  ggplot(aes(...)) +
    geom_bar() 
```

### Exercise 9

Use `labs()` to title your graph "Flipping a Coin 50 Times". Also label your x-axis "Result" and y-axis "Count".

```{r d9, exercise = TRUE}

```

```{r d9-hint, eval = FALSE}
... + 
  labs(title = "...",
       x= "...",
       y = "...")
```

### Exercise 10

Now use `scale_x_continuous()` so the x-axis has `breaks` at 0 and 1. Set the `labels` for the breaks as "Tails" and "Heads", respectively. 


```{r d10, exercise = TRUE}

```

Reminder: This is what your plot should look like.

```{r}
tibble(heads = rbinom(n = 50, size = 1, prob = 0.5)) %>% 
  ggplot(aes(x = heads)) +
    geom_bar() +
    labs(title = "Flipping a Fair Coin 50 Times",
         x = "Result",
         y = "Count") +
    scale_x_continuous(breaks = c(0, 1),
                       labels = c("Tails", "Heads"))
```

```{r d10-hint-1, eval = FALSE}
Use the c() function for specifying the breaks and labels.
```

```{r d10-hint-2, eval = FALSE}
... + 
  scale_x_continuous(breaks = ...,
                     labels = ...)
```

```{r d10-hint-3, eval = FALSE}
... + 
  scale_x_continuous(breaks = c(..., ...),
                     labels = c(..., ...))
```

### Exercise 11

Let's use `rnorm()` to draw from a normal distribution. Within `rnorm()`, set `n` to 40.

```{r d11, exercise = TRUE}

```

### Exercise 12

Let's now add the arguments `mean` and `sd` to our code above. Set `mean` to  0 and `sd` to 3.

```{r d12, exercise = TRUE}

```

```{r d12-hint, eval = FALSE}
rnorm() should now have three arguments: n, mean, and sd.
```

### Exercise 13

Save your code above to an object named `draws`.

```{r d13, exercise = TRUE}

```

```{r d13-hint, eval = FALSE}
draws <- rnorm(..., ..., ... )
```

### Exercise 14

Use `c()` to find the `mean()`, `sd()`,`median()`, and `mad()` of `draws`.

```{r d14, exercise = TRUE}

```

```{r d14-hint, eval = FALSE}
Place mean(), sd(), median(), and mad() all inside c(), each with the argument as draws.
```

### Exercise 15

Let's now use `quantile()` to find the values that occupies the 2.5th and 97.5th percentiles. The first argument to `quantile()` should be `draws`. The second argument should set `probs` to a `c()` function that contains values .025 and .975.

```{r d15, exercise = TRUE}


```

```{r d15-hint-1, eval = FALSE}
quantile(..., probs = ...)
```

```{r d15-hint-2, eval = FALSE}
quantile(..., probs = c(..., ..))
```

### Exercise 16

Let's now plot two distributions and their sum. First, let's use `tibble()` to create a column `Normal`, which is set to`rnorm()`. The first argument should be 10000. The second argument should set `mean` to 1. 

```{r d16, exercise = TRUE}


```

```{r d16-hint-1, eval = FALSE}
tibble(... = rnorm(..., ...)
```

```{r d16-hint-2, eval = FALSE}
tibble(... = rnorm(..., mean = ...)
```

### Exercise 17

Copy and paste your code above. Create a second column within `tibble()` named `Uniform`, which is set to a `runif()` statement. The first argument should be 10000. Then, set `min` to 2 and `max` to 3.

```{r d17, exercise = TRUE}


```

```{r d17-hint, eval = FALSE}
tibble(Normal = rnorm(n, mean = 1),
       Uniform = runif(..., min = ..., max = ...)
```

### Exercise 18

Copy and paste your code above. Create a third column within `tibble()` named `Combined`, which is set to `Normal + Uniform`.

```{r d18, exercise = TRUE}


```

```{r d18-hint, eval = FALSE}
tibble(Normal = rnorm(n, mean = 1),
       Uniform = runif(n, min = 2, max = 3),
       Combined = ... + ...)
```

### Execise 19

Let's plot our tibble. Copy and paste the code above. Use ` %>% ` to add the function `pivot_longer()`. Set `cols` to `everything()`, `names_to` to "Distribution", and `values_to` to  "draw".

```{r d19, exercise = TRUE}


```

```{r d19-hint, eval = FALSE}
... %>% 
    pivot_longer(cols = ...,
                 names_to = ...,
                 values to = ...)
```

### Exercise 20

Continue your pipe with `ggplot()` to map `x` to `draw` and `fill` to Distribution. Add the layer `geom_histogram()`. Within `geom_histogram()`, use `after_stat()` . Inside `after_stat()`, use `aes()` with the argument `y =count/sum(count)` to put percents on the y-axis.


```{r d20, exercise = TRUE}


```

```{r d20-hint, eval = FALSE}
... %>% 
  ggplot(aes(..., ...)) +
    geom_histogram(aes(...)
```

### Exercise 21

Also set `alpha` to .5, `bins` to 100, and `position` to "identity" within `geom_histogram()`.

```{r d21, exercise = TRUE}


```

```{r d21-hint, eval = FALSE}
... %>% 
   geom_histogram(aes(y = after_stat(count/sum(count))),
                  alpha =  ..., 
                  bins =  ..., 
                  position = ...)
```

### Exercise 22

Finally, use `labs()` to title your graph "Two Distributions and Their Sum". Also label your x-axis "Value" and y-axis "Probability".

```{r d22, exercise = TRUE}

```

Reminder: This is what your plot should look like. 

```{r}
tibble(Normal = rnorm(100000, mean = 1),
       Uniform = runif(100000, min = 2, max = 3),
       Combined = Normal + Uniform) %>% 
  pivot_longer(cols = everything(),
               names_to = "Distribution",
               values_to = "draw") %>% 
  ggplot(aes(x = draw, fill = Distribution)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   alpha = 0.5, 
                   bins = 100, 
                   position = "identity") +
    labs(title = "Two Distributions and Their Sum",
         subtitle = "You can sum distributions just like you sum numbers",
         x = "Value",
         y = "Probability")
```


## Draw Game
###

Let's imagine that **A** and *B* are both flipping fair coins. **A** flips the coin 2 times. *B* flips the coin 4 times. What is the probability that A flips more heads than B? To estimate the chances that **A** wins, simulate playing the game 1,000 times.

  
### Exercise 1

Let's use `tibble()` to create a column `A_heads`, which is set to an `rbinom()` statement. The first argument should be 1000. The second argument should set `size` to 2 and `prob` to .5. 

```{r dg1, exercise = TRUE}

```

```{r dg1-hint, eval = FALSE}

```

### Exercise 2

Copy and paste your code above. Create a second column within `tibble()` named `B_heads`, which is set to a `rbinom()` statement. The first argument should be 1000. Then, set `size` to 4 and `prob` to .5.

```{r dg2, exercise = TRUE}

```

```{r dg2-hint, eval = FALSE}

```

### Exercise 3

Copy and paste your code from above. Use `mutate()` to create a column `A_wins`, which is set to an `ifelse()` statement. The first argument to `ifelse()` should set `A_heads` greater than `B_heads`. The second argument should be 1, and the third argument should be 3.  

```{r dg3, exercise = TRUE}

```

```{r dg3-hint, eval = FALSE}

```

### Exercise 4

Finally, use `summarize()` to set `A_chances` to the `mean()` of `A_wins`.

```{r dg4, exercise = TRUE}

```

```{r dg4-hint, eval = FALSE}

```

## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```



