---
title: "Probability: Overview"
tutorial:
  id: "probability-overview"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Questions which map to the text in Chapter 5: Probablility."
---


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

<!-- Stop writing stuff like "Copy/paste your code from above." This is implicit, given the copy button. Done. -->

<!-- Take ownership of Probability A.  Make it follow the guidance in the Written Instructions. -->

<!-- Remove joint_dist. Done. -->

<!-- Add to list column questions something which explains why we need map_* functions for sampling from random variables. Done. -->

<!-- There are two separate but related issues. First, teach them about list columns and map functions in general, with no necessary reference to randomness or distributions. Then, show them how you need, at least, map functions to get a different random draw from each row. But that step does not require list-columns. But then list-columns can store a vector of random draws, which can be very convenient.Done. -->


<!-- scale_x and friends. There is a lot going on here.  Done.-->

<!-- Think about other cool plots to make with randomness. Save for later. -->


## List-columns and map functions

###

<!-- Delete all these questions. Only use things that map to the current version of the chapter. Done.-->

<!-- DK: Drop some knowledge. Some info from this link. Or share the link. Or something: -->

<!-- https://r4ds.had.co.nz/iteration.html?q=map#the-map-functions -->

<!-- https://www.rstudio.com/resources/webinars/how-to-work-with-list-columns/ -->

### Exercise 1

Use c() to combine the following numbers : 4, 16, 9

```{r listcolumns-and-map-functions-ex-1, exercise = TRUE}

```


```{r listcolumns-and-map-functions-ex-1-hint, eval = FALSE}
c(...,...,...)
```


### Exercise 2

Now use c() to combine two letters : A and Z
```{r listcolumns-and-map-functions-ex-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r listcolumns-and-map-functions-ex-2-hint, eval = FALSE}
c(...,...)
```


### Exercise 3

Use `list()` to create two elements the first element is the combine numbers in first exercise, the second is the combine letters in second excercise.
```{r listcolumns-and-map-functions-ex-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r listcolumns-and-map-functions-ex-3-hint, eval = FALSE}

```


### Exercise 4

Now assgign the list() we just created to an variable x, then run x[[1]], it should returns the first element which is the 3 numbers.
```{r listcolumns-and-map-functions-ex-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r listcolumns-and-map-functions-ex-4-hint, eval = FALSE}
x <- list(c(),c())
x[[1]]
```

### Exercise 5

Pick 10 random values in which the mean is 0 and standard deviation is 1. Recall chapter two if necessary. 
```{r listcolumns-and-map-functions-ex-5, exercise = TRUE}

```


```{r listcolumns-and-map-functions-ex-5-hint, eval = FALSE}
rnorm(10)

```

###
You could do something like rnorm(n = 10, mean = 0, sd = 1), but since we are using the default value of rnorm, we can simply do rnorm(10).


### Exercise 6

Use the `range()` to take the range of `rnorm(10)`
```{r listcolumns-and-map-functions-ex-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r listcolumns-and-map-functions-ex-6-hint, eval = FALSE}
range(rnorm(10))
```


### Exercise 7

Take the list of the range we created above using `list()`.
```{r listcolumns-and-map-functions-ex-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r listcolumns-and-map-functions-ex-7-hint, eval = FALSE}
list(range(rnorm(...)))
```


### Exercise 8

Now take the list we created above assign it into a tibble using `tibble()` in which the column name is col_1.
```{r listcolumns-and-map-functions-ex-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r listcolumns-and-map-functions-ex-8-hint, eval = FALSE}
tibble(col_1 = list(range(rnorm(...))))
```

###
Now you have created a list-column which is a 1-by-1 tibble with one observation, which is a list of one element.


### Exercise 9

Pipe down your result, use `map_dbl()`to create and work with the list-column we create. Within `map_dbl()`, set the first argument to `col_1`, the second to the formula that calculate the sum of the range in col_1 using `sum()`, don't forget the `~` before formula, and the `.` within `sum()`.
```{r listcolumns-and-map-functions-ex-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r listcolumns-and-map-functions-ex-9-hint, eval = FALSE}
tibble(col_1 = list(range(rnorm(10)))) %>% 
  mutate(col_2= map_dbl(col_1, ~sum(.)))

```

###
We can replace the `~sum(.)` to simply sum as an statement, but we generally working with formula more often, so we practice using ~sum(.) instead.

### Exercise 10

Let's try using other map_* functions, use `map_int()` set the first argument to col_1, replace `sum()` with `length()`, and assign the `map_int()` to a new column `col_3`.
```{r listcolumns-and-map-functions-ex-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r listcolumns-and-map-functions-ex-10-hint, eval = FALSE}
tibble(col_1 = list(range(rnorm(10)))) %>% 
  mutate(col_2= map_dbl(col_1, ~sum(.))) %>%
  mutate(col_3= map_int(col_1, ~length(.)))
```

###
Again if we replace ~length(.) with just length, we would got the same result.


### Exercise 11

Let's try using other map_* functions, use `map_chr()` set the first argument to col_1, replace `length()` with `mean()`, and assign the `map_chr()` to a new column `col_4`.
```{r listcolumns-and-map-functions-ex-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r listcolumns-and-map-functions-ex-11-hint, eval = FALSE}
tibble(col_1 = list(range(rnorm(10)))) %>% 
  mutate(col_2= map_dbl(col_1, ~sum(.))) %>%
  mutate(col_3= map_int(col_1, ~length(.)))%>%
  mutate(col_4= map_chr(col_1, ~mean(.)))
```

###
The reason for why we are doing these almost the same exercise is to show you how different map_* functions would returns different vectors for the new column we create.

### Exercise 12

Create a tibble using tibble(), set the first column ID equal to a set of integers form 1 to 10. 
```{r listcolumns-and-map-functions-ex-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r listcolumns-and-map-functions-ex-12-hint, eval = FALSE}
tibble(ID= 1:10)
```
We can get the consecuetive integers we want by using : instead of c().
###

### Exercise 13

Use mutate() to create a new column called N, set n equal an value from 10 random values in which the mean is 0 and standard deviation is 1. 
```{r listcolumns-and-map-functions-ex-13, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r listcolumns-and-map-functions-ex-13-hint, eval = FALSE}
tibble(ID = 1:10) %>%
  mutate(N = sample(rnorm(10),size=1))
```

###
Note how all N is equal, essentially what happened here is N calculate it self using the sample() function and copy it 10 times to matched the ID column.

### Exercise 14

Create an new column called Y using mutate(), this time use map_dbl(), set the first argument to Y represent data source, the second argument to the `sample()` *Formula* to create in last exercise.
```{r listcolumns-and-map-functions-ex-14, exercise = TRUE}

```

Remember for formula we always add the `~` at front. 

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r listcolumns-and-map-functions-ex-14-hint, eval = FALSE}
tibble(ID = 1:10) %>%
  mutate(N = sample(rnorm(10),size=1)) %>%
  mutate(Y = map_dbl(ID, ~ sample(rnorm(...),size=...)))
```

###
When we add on the map_* () function to the mutate, it grabs the data in this case is `ID`, and it deals with each one of the data using the formula in the second statement `~sample()`, that's why we would get different results for each ID in the Y column but not in the N column.



## Flipping a coin 


Let's create the following *empirical distribution* of flipping a fair coin. Recall, that empirical distribution is based on data therefore we need to simulated our data, that is "flipping the coin" by ourself.

```{r}
emp_p <- tibble(results = rbinom(n = 100, size = 1, prob = 0.5)) %>%
  ggplot(aes(x = results)) +
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 binwidth = 0.5,
                 color = "white") +
  scale_x_continuous(breaks = c(0, 1),
                     labels = c("Heads", "Tails")) +
  scale_y_continuous(labels =
                      scales::percent_format(accuracy = 1)) +
  labs(title = "Mathematical Probability Distribution",
       subtitle = "Expectations for flipping a fair coin",
       x = "Outcome\nResult of Coin Flip",
       y = "Probability") +
  theme_classic()

emp_p
```

### Exercise 1

Let's simulate a fair coin, i.e. $p_h = p_t = 0.5$. To do so, use the function `rbinom()`. Recall `rbinom()` is used to draw from a binomial distribution (when there are only two possible outcomes). Within `rbinom()`, set `n` to 100, `size` to 1, and `prob` to .5.  

```{r fac-1, exercise = TRUE}

```

```{r fac-1-hint-1, eval = FALSE}
rbinom(... , ..., ....)
```

```{r fac-1-hint-2, eval = FALSE}
rbinom(n = ..., size = ..., prob = ....)
```
###
We set the probability to 50% because we drawn our data from the population of "fair coin", and theoretically, for a fair coin, the probability of landing on heads should be equal to landing on tails. 


<!-- From https://stat.ethz.ch/R-manual/R-devel/library/stats/html/Binomial.html -->


### Exercise 2

Create a `tibble()` with one variable `results` . Have `results` take on the values of the `rbinom()` code in the previous exercise.  

```{r fac-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r fac-2-hint-1, eval = FALSE}
tibble(... = rbinom(..., ..., ...))
```


###
Family functions include `dbinom()`,`pbinom()``qbinom()`. In general, dbinom gives the density, pbinom gives the distribution function, qbinom gives the quantile function and rbinom generates random deviates.


### Exercise 3

Pipe your results to `ggplot()`. Map `results` to the x-axis. Also add the layer `geom_histogram()`. 

```{r fac-3, exercise = TRUE}

```


<button onclick = "transfer_code(this)">Copy previous code</button>

```{r fac-3-hint-1, eval = FALSE}
... %>% 
  ggplot(mapping = aes(...) + 
  geom_histogram()
```
###
The `aes()` within `geom_histogram()` can only be either `x` or `y`, if you want to use both of them, use `geom_col()` or `geom_bar()` instead.

### Exercise 4

Within `geom_histogram()`, use `after_stat()` . Inside `after_stat()`, use `aes()` with the argument `y = count/sum(count)` to put percents on the y-axis.

```{r fac-4, exercise = TRUE}

```


<button onclick = "transfer_code(this)">Copy previous code</button>

```{r fac-4-hint, eval = FALSE}
... +
    geom_histogram(aes(y = after_stat(...) 
```
###
There is three stages where you can put aesthetic, `aes()`, first the the normal or default stage that is we set the `aes()` within ggplot. Second stage is after where the data is transformed by layers like geom_histogram(), and the third stage is after the data been transformed and scale. So therefore, `after_stat()` is a function we use in the second stage, and it's family function `after_scale()` is used in the third stage.

### Exercise 5

Also set `binwidth` to .5 and `color` to "white" within `geom_histrogram()`.

```{r fac-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r fac-5-hint, eval = FALSE}
geom_histogram(aes(y = after_stat(count/sum(count))),
                 binwidth = 0.5,
                 color = "white")
```
###
The color argument within geom_histogram(), determines the color of the bar's framework, it helps us to seperate the bars from one another. To change the color of the bar, we would use the argument fill instead of color. 

### Exercies 6

Now use `scale_x_continuous()` so the x-axis has `breaks` at 0 and 1. Set the `labels` for the breaks as "Heads" and "Tails", respectively. 


```{r fac-6, exercise = TRUE}

```


<button onclick = "transfer_code(this)">Copy previous code</button>

```{r fac-6-hint-1, eval = FALSE}
Use the c() function for specifying the breaks and labels.
```

```{r fac-6-hint-2, eval = FALSE}
... + 
  scale_x_continuous(breaks = c(..., ...),
                     labels = c(..., ...))
```

To determine whether to use scale_x_continuous or scale_x_discrete, you need to determine the vector of the variable you want to plot, if your variable is numeric, then use `scale_x_continuous()`, if your variable is factor, then use `scale_x_discrete()`.

### Exercise 7

Now use `scale_y_continuous()` to put the x-axis in percent format. Within `scale_y_continuous()`, set `labels` to `scales::percent_format()`. Within `percent_format()` set `accuracy` to 1.

```{r fac-7, exercise = TRUE}

```


<button onclick = "transfer_code(this)">Copy previous code</button>

```{r fac-7-hint-1, eval = FALSE}
... + 
  scale_y_continuous(labels = scales::percent_format(...))
```

There is alot more function within scale_y_continuous, includes the limit, expand, guide, position, etc. To learn more about scale_continuous, click [here] (https://ggplot2.tidyverse.org/reference/scale_continuous.html)

### Exercise 8

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.

```{r face-8, exercise = TRUE}

```


<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: Your plot should look similar to the the one below. **Note**: the height of the bars will vary because our `rbinom()` statements generate different proportions every time! 

```{r}
emp_p
```

## Rolling Two Dice

Let's create the following *empirical distribution* for rolling two dice.

```{r}
set.seed(1)

emp_dist_dice <- tibble(ID = 1:100) %>% 
  mutate(die_1 = map_dbl(ID, ~ sample(c(1:6), size = 1))) %>% 
  mutate(die_2 = map_dbl(ID, ~ sample(c(1:6), size = 1))) %>% 
  mutate(sum = die_1 + die_2) %>% 
  ggplot(aes(x = sum)) +
    geom_histogram(aes(y = after_stat(count/sum(count))), 
                   binwidth = 1, 
                   color = "white") +
    labs(title = "Empirical Probability Distribution",
         subtitle = "Sum from rolling two dice, replicated one hundred times",
         x = "Outcome\nSum of Two Die",
         y = "Probability") +
    scale_x_continuous(breaks = seq(2, 12, 1), labels = 2:12) +
    scale_y_continuous(labels = 
                         scales::percent_format(accuracy = 1)) +
    theme_classic()

emp_dist_dice
```


### Exercise 1

Create a `tibble()` with variable `ID`, and the we make an list of value from 1 to 100 for the variable `ID`.

```{r rd-1, exercise = TRUE}

```



```{r rd-1-hint-1, eval = FALSE}
tibble(ID = ... : ...)
```

```{r rd-1-hint-2, eval = FALSE}
tibble(ID = 1:100)
```

###

`tibble()` function provides us a framework to generate our data, this function will be used throughout this tutorial.

### Exercise 2
Nice! Now let's pipe down the tibble we create in the last exercise, let's use th `map_dbl` function to create the results for an random dice rolling experiment. recalled the` map() and map_*()` functions, within it it will includes two argument one is the data source, which in this case is `ID`. and the formula we want to use to create the dice result is the `sample()` function, and use the argument `size` within the `sample()` function to only pick one out of the six faces of a standard dice.

```{r rd-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rd-2-hint-1, eval = FALSE}
...%>%
map_dbl(..., ~...)
```

```{r rd-2-hint-2, eval = FALSE}
...%>%
map_dbl(ID, ~sample(c(...:...), size = 1))
```



### Exercise 3
Nice! Now let's pipe down the above and use the `mutate()` function to assign the `map_dbl` functions we above to an value called "die_1".


```{r rd-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rd-3-hint-1, eval = FALSE}
...%>%
mutate(... =map_dbl(ID, ~sample(c(...:...), size = 1)))
```

```{r rd-3-hint-2, eval = FALSE}
...%>%
mutate(die_1 = map_dbl(ID, ~ sample(c(1:6), size = 1))) %>% 
```


### Exercise 4
Now copy and paste the results from above, and do the exact same thing again but instead now named to value to `die_2`, because we need the results for two dices.


```{r rd-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rd-4-hint-1, eval = FALSE}
...%>%
mutate(... =map_dbl(ID, ~sample(c(...:...), size = 1)))
```

```{r rd-4-hint-2, eval = FALSE}
...%>%
mutate(die_2 = map_dbl(ID, ~ sample(c(1:6), size = 1))) %>% 
```




### Exercise 5
Use the `mutate()` function once again, name the value of the sum of `die_1` and `die_2` to "sum"


```{r rd-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rd-5-hint-1, eval = FALSE}
...%>%
mutate(sum = die_1 + die_2)
```


### Exercise 6
Copy and paste the results from above, now use `ggplot()` to graph the Empirical Distribution, set `x = sum` within `aes()`, and then add a layer of `geom_histogram()`


```{r rd-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rd-6-hint-1, eval = FALSE}
...%>%
ggplot(aes())+
  geom_histogram()
```



### Exercise 7

Within `geom_histogram()`, use `after_stat()` . Inside `after_stat()`, use `aes()` with the argument `y = count/sum(count)` to put percents on the y-axis.

```{r rd-7, exercise = TRUE}

```


<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rd-7-hint, eval = FALSE}
... +
    geom_histogram(aes(y = after_stat(...)))
```

### Exercise 8

Also set `binwidth` to .5 and `color` to "white" within `geom_histrogram()`.

```{r rd-8, exercise = TRUE}

```


<button onclick = "transfer_code(this)">Copy previous code</button>


```{r rd-8-hint, eval = FALSE}
... +
    geom_histogram(aes(y = after_stat(count/sum(count))), 
                   binwidth = 1, 
                   color = "white") 
```



### Exercies 9

Now use `scale_x_continuous()` so the x-axis has `breaks` to the sequence between 2 and 12 common difference is 1 using `seq()`. Set the `labels` for the breaks as from 2 to 12.


```{r rd-9, exercise = TRUE}

```


<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rd-9-hint-1, eval = FALSE}
scale_x_continuous(breaks = seq(...,..., ...), labels = ...:...) 
```

```{r rd-9-hint-2, eval = FALSE}
... + 
  scale_x_continuous(breaks = seq(2, 12, 1), labels = 2:12) 
```

### Exercise 10

Now use `scale_y_continuous()` to put the x-axis in percent format. Within `scale_y_continuous()`, set `labels` to `scales::percent_format()`. Within `percent_format()` set `accuracy` to 1.

```{r rd-10, exercise = TRUE}

```


<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rd-10-hint-1, eval = FALSE}
... + 
  scale_y_continuous(labels = scales::percent_format(...))
```

### Exercise 11

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.

```{r rd-11, exercise = TRUE}

```


<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: Your plot should look similar to the the one below. 

```{r}
emp_dist_dice
```


## Height

Let's create the following *empirical distribution* about the "height of the next adult men you'll meet" using the data from the National Health and Nutrition Examination Survey (NHANES).

```{r}
emp_height <- nhanes %>%
  filter(gender == "Male", age >= 18) %>%
  select(height)%>%
  drop_na() %>%
  ggplot(aes(x = height)) +
    geom_histogram(aes(y = after_stat(count/sum(count))), 
                 binwidth = 1, 
                 color = "white")+
  labs(title = "Empiracal Probability Distribution",
       subtitle = "Height for male by NHANES",
       x = "Height",
       y = "Probability",caption = "Source:NHANES") +
  scale_y_continuous(labels =
                      scales::percent_format(accuracy = 1)) +
  theme_classic()
emp_height
```


### Exercise 1

glimpse the package `nhanes`

```{r h-1, exercise = TRUE}

```

```{r h-1-hint-1, eval = FALSE}
glimpse(nhanes)
```

Note that there is all sorts of column in this data set, but the two that we actually care about is gender and height.
 
### Exercise 2

Start a new pipe with `nhanes`, use `filter()` to filter out the rows where gender is equal to "Male", and age is greater or equal to 18

```{r h-2, exercise = TRUE}

```

```{r h-2-hint-1, eval = FALSE}
nhanes %>%
  filter(gender == ..., age >= ...) 
```

```{r h-2-hint-2, eval = FALSE}
nhanes %>%
  filter(gender == "Male", age >= 18) 
```

### Exercise 3
Use `select()` to pick out "height" column which is what we want.Then use `drop_na()` to drop the rows that contains NA which we don't want. 


```{r h-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r h-3-hint-1, eval = FALSE}
...%>%
  select(height)%>%
  drop_na()
```

### Exercise 4

Use `ggplot()` and `geom_histogram()` to graph out the distribution, set x equal to "height" within `ggplot()`.


```{r h-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r h-4-hint-1, eval = FALSE}
...%>%
  ggplot(aes(x=...)) +
  geom_histogram()
```

### Exercise 5

Within `geom_histogram()`, use `after_stat()` . Inside `after_stat()`, use `aes()` with the argument `y = count/sum(count)` to put percents on the y-axis.


```{r h-5, exercise = TRUE}

```


<button onclick = "transfer_code(this)">Copy previous code</button>

```{r h-5-hint, eval = FALSE}
... +
    geom_histogram(aes(y = after_stat(...) 
```

### Exercise 6

Also set `binwidth` to .5 and `color` to "white" within `geom_histrogram()`.

```{r h-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r h-6-hint, eval = FALSE}
... +
    geom_histogram(aes(y = after_stat(count/sum(count))), 
                   binwidth = 1, 
                   color = "white") 
```

### Exercise 7

Now use `scale_y_continuous()` to put the x-axis in percent format. Within `scale_y_continuous()`, set `labels` to `scales::percent_format()`. Within `percent_format()` set `accuracy` to 1.

```{r h-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r h-7-hint-1, eval = FALSE}
... + 
  scale_y_continuous(labels = scales::percent_format(...))
```

### Exercise 8

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.

```{r h-8, exercise = TRUE}

```


<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: Your plot should look exatly like this one because we used the exact same data from nhanes.
```{r}
emp_height
```


## Three Models 
###

Let's create the following *joint distribution* of the number of white marbles in a bag and the number of white marbles pulled out in the sample.

```{r}
joint_p <- tibble(in_bag = rep(c(0, 1, 2), 1000)) %>%
  mutate(in_sample = map_int(in_bag, ~ rbinom(n = 1, 
                                              size = 3, 
                                              p = ./2))) %>%
  ggplot(aes(x = in_sample, y = in_bag)) +
    geom_jitter(alpha = 0.5) +
    labs(title = "Black and White Marbles",
         subtitle = "More white marbles in bag mean more white marbles selected",
         x = "White Marbles Selected",
         y = "White Marbles in the Bag") +
    scale_y_continuous(breaks = c(0, 1, 2)) +
  theme_classic()

joint_p
```

### Exercise 1

Create a `tibble()` with one variable `in_bag`. Have `in_bag` take on the values of `rep()`. Within `rep()` use the arguments 0, 1, and 2. 

```{r tm-1, exercise = TRUE}

```

```{r tm-1-hint-1, eval = FALSE}
tibble(in_bag = rep(c(..., ..., ...)))
```

Great. We now have generated the number of white marbles that exist in our bag. 

### Exercise 2

Great. Let's have our code run 1000 times. Add the argument 1000 to `rep()`

```{r tm-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>


```{r tm-2-hint-1, eval = FALSE}
 tibble(in_bag = rep(c(0, 1, 2), ...))
```

### Exercise 3

Pipe your results to `mutate()` to create the variable `in_sample`. Set `in_sample` to the function `map_int()`. The first argument to `map_int()` should be `in_bag`. The second argument should be an `rbinom()` where `n` is set to 1, `size` is set to 3, and `p` is set to `./2`.

```{r tm-3, exercise = TRUE}

```


<button onclick = "transfer_code(this)">Copy previous code</button>

```{r tm-3-hint-1, eval = FALSE}
 ... %>% 
  mutate(in_sample = map_int(..., ~ rbinom(..., 
                                           ..., 
                                           ...)))
```


### Exercise 5

Pipe your result into `ggpplot()`. Map `in_sample` to the x-axis and `in_bag` to the y-axis. Also add the layer `geom_jitter()`. 

```{r tm-5, exercise = TRUE}

```


<button onclick = "transfer_code(this)">Copy previous code</button>


```{r tm-5-hint-1, eval = FALSE}
... %>% 
  ggplot(aes(x = ..., y = ...)) +
    geom_jitter()
```

### Exercise 6

Set `alpha` to .5 within `geom_jitter()`. 

```{r tm-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>


```{r tm-6-hint-1, eval = FALSE}
... +
    geom_jitter(...)
```

### Exercise 7

Now use `scale_y_continuous()` to break the y-axis into three values. Within `scale_y_continuous()`, set `breaks` to 0, 1, and 2.

```{r tm-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r tm-7-hint-1, eval = FALSE}
... + 
  scale_y_continuous(breaks = c(..., ..., ...)
```

Why do we do this? Each value on the y-axis represents a different version or belief about the world.

### Exercise 8

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.

```{r tm-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like.

```{r}
joint_p
```


```{r tm-8-hint-1, eval = FALSE}

```

### 

Awesome. We can now see the number of simulations in each "bucket." Take note that this distribution is normalized.

###

Let's create the following *unnormalized conditional distribution*. This is essentially a slice of the joint distribution we previously created. 

```{r}
unnorm_p <- tibble(in_bag = rep(c(0, 1, 2), 1000)) %>%
  mutate(in_sample = map_int(in_bag, ~ rbinom(n = 1, 
                                              size = 3, 
                                              p = ./2))) %>% 
  filter(in_sample == 3) %>% 
  ggplot(aes(in_bag)) +
    geom_histogram(binwidth = 0.25, color = "white") +
    labs(title = "Unnormalized Conditional Distribution",
         subtitle = "Number of white marbles in bag given that three were selected in the sample",
         x = "Number of White Marbles in the Bag",
         y = "Count") +
    scale_x_continuous(breaks = seq(1, 2)) +
    theme_classic()

unnorm_p
```

### Exercise 9

Copy down every part of the empirical distribution before `ggplot()` and then use `filter()` for where `in_sample` is equal to 3.

```{r tm-9, exercise = TRUE}

```

```{r tm-9-hint-1, eval = FALSE}
...%>% 
  filter(in_sample == ...)
```

### Exercise 10

Pipe your code above to `ggplot()`. Map `in_bag` to the x-axis. Also add the layer `geom_histogram()`.

```{r tm-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r tm-10-hint-1, eval = FALSE}
... %>% 
  ggplot(aes(...)) +
  geom_histogram()
```

### Exercise 11 

Set `binwidth` to .25 and `color` to "white" within `geom_histogram()`.

```{r tm-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r tm-11-hint-1, eval = FALSE}
... +
  geom_histogram(..., ...)
```

### Exercise 12

Now use `scale_x_continuous()`. Set `breaks` to `seq()` that contains the values 1 and 2.

```{r tm-13, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r tm-13-hint-1, eval = FALSE}
... +
  scale_x_continuous(... = seq(..., ...))
```

### Exercise 13

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.

```{r tm-14, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like.

```{r}
unnorm_p
```

### 

Let's create the following *normalized conditional distribution*. In other words, we are normalizing the graph we just created.

```{r}
norm_p <- tibble(in_bag = rep(c(0, 1, 2), 1000)) %>%
  mutate(in_sample = map_int(in_bag, ~ rbinom(n = 1, 
                                              size = 3, 
                                              p = ./2))) %>% 
  filter(in_sample == 3) %>% 
  ggplot(aes(in_bag)) +
    geom_histogram(aes(y = after_stat(count/sum(count))), 
                   binwidth = 0.25, 
                   color = "white") +
    labs(title = "Posterior Probability Distribution",
         subtitle = "Number of white marbles in bag given that three were selected in the sample",
         x = "Number of White Marbles in the Bag",
         y = "Probability") +
    scale_x_continuous(breaks = c(1, 2)) +
    scale_y_continuous(labels = 
                         scales::percent_format(accuracy = 1)) +
    theme_classic()

norm_p
```

### Exercise 14

We begin our code the same way we began our code for the *unnormalized conditional distribution*. We have provided the code for you below. To begin, add the `after_stat()` argument to `geom_histogram()`. Within `aes()`, use `after_stat()` with the argument `y = count/sum(count)` to put percents on the y-axis.


```{r tm-15, exercise = TRUE}
tibble(in_bag = rep(c(0, 1, 2), 1000)) %>%
  mutate(in_sample = map_int(in_bag, ~ rbinom(n = 1, 
                                              size = 3, 
                                              p = ./2))) %>% 
  filter(in_sample == 3) %>% 
  ggplot(aes(in_bag)) +
    geom_histogram(binwidth = 0.25, color = "white")
```

```{r tm-15-hint-1, eval = FALSE}
... +
  geom_histogram(binwidth = 0.25, color = "white",aes(y = after_stat(count/sum(count)))
```

### Exercies 15

Now use `scale_x_continuous()` so the x-axis has `breaks` at 1 and 2.

```{r tm-16, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r tm-16-hint-1, eval = FALSE}
Use the c() function for specifying the breaks and labels.
```

```{r tm-16-hint-2, eval = FALSE}
... + 
  scale_x_continuous(breaks = c(..., ...))
```

### Exercise 16

Now use `scale_y_continuous()` to put the y-axis in percent format. Within `scale_y_continuous()`, set `labels` to `scales::percent_format()`. Within `percent_format()` set `accuracy` to 1.

```{r tm-17, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r tm-17-hint-1, eval = FALSE}
... + 
  scale_y_continuous(labels = scales::percent_format(...))
```

### Exercise 17

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.

```{r tm-18, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like.

```{r}
norm_p
```

## N Models 
###

Let's create the following *empirical distribution* for possible simulations for $\rho_h$. In other words, we will create a joint distribution of models which might be true and of data which our experiment might generate. 

```{r}
emp_p <- tibble(p = rep(seq(0, 1, 0.1), 1000)) %>%
  mutate(heads = map_int(p, ~ rbinom(n = 1, size = 20, p = .))) %>%
  ggplot(aes(y = p, x = heads)) +
    geom_jitter(alpha = 0.1) +
    labs(title = "Empirical Distribution of Number of Heads",
         subtitle = expression(paste("Based on simulations with various values of ", rho[h])),
         x = "Number of Heads out of 20 Tosses",
         y = expression(rho[h])) +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) +
  theme_classic()

emp_p
```

### Exercise 1

Use `tibble()` with one variable `p` set to the function `rep()`. Within `rep()` use the argument `seq()` that takes on the values 0, 1, and .1.

```{r nm-1, exercise = TRUE}

```

```{r nm-1-hint-1, eval = FALSE}
tibble(... = rep(c(..., ..., ...)))
```

### Exercise 2

Great. Let's have our code run 1000 times. Add the argument 1000 to `rep()`

```{r nm-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r nm-2-hint-1, eval = FALSE}
 tibble(p = rep(c(0, 1, .1), ...))
```

### Exercise 3

Pipe your code to the function `mutate()` to create the variable `heads`. Set `heads` to the function `map_int()`. The first argument to `map_int()` should be `p`. The second argument should be an `rbinom()` where `n` is set to 1, `size` is set to 20, and `p` is set to `.`.

```{r nm-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r nm-3-hint-1, eval = FALSE}
 ... %>% 
  mutate(p = map_int(..., ~ rbinom(...,
                                   ..., 
                                   ...)))
```

### Exercise 4

Assign your code to an object named `x`.

```{r nm-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r nm-4-hint-1, eval = FALSE}

```

### Exercise 5

Continue your pipe to `ggplot()`. Map `heads` to the x-axis and `p` to the y-axis. Also add the layer `geom_jitter()`. 

```{r nm-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r nm-5-hint-1, eval = FALSE}
  ggplot(aes(x = ..., y = ...)) +
    geom_jitter()
```

### Exercise 6

Set `alpha` to .1 within `geom_jitter()`. 

```{r nm-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r nm-6-hint-1, eval = FALSE}
... +
  geom_jitter(...)
```

### Exercise 7

Now use `scale_y_continuous()`. Set `breaks` to the function `seq()` that contains the values 0, 1, and .1.

```{r nm-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r nm-7-hint-1, eval = FALSE}
... + 
  scale_y_continuous(breaks = seq(..., ..., ...)
```

### Exercise 8

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.

```{r nm-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like.

```{r}
emp_p
```

###

Let's create the following *unnormalized conditional distribution*. This is essentially a slice of the joint distribution we previously created. 

```{r}
unnorm_p <- tibble(p = rep(seq(0, 1, 0.1), 1000)) %>%
  mutate(heads = map_int(p, ~ rbinom(n = 1, size = 20, p = .))) %>% 
  filter(heads == 8) %>% 
  ggplot(aes(p)) +
    geom_bar() +
    labs(title = expression(paste("Values of ", rho[h], " Associated with 8 Heads")),
         x = expression(paste("Assumed value of ", rho[h], " in simulation")),
         y = "Count") +
  theme_classic()

unnorm_p
```

### Exercise 9

`filter()`  for where `heads` is equal to 8.

```{r nm-9, exercise = TRUE}

```

```{r nm-9-hint-1, eval = FALSE}
  filter(heads == ...)
```

### Exercise 10

Pipe your code above to `ggplot()`. Map `p` to the x-axis.  Also add the layer `geom_bar()`.

```{r nm-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r nm-10-hint-1, eval = FALSE}
... %>% 
  ggplot(aes(...)) +
  geom_histogram()
```

### Exercise 11

Finally, use `labs()` to add the title "Values of P(h) with 8 Heads". Then label your x-axis "Assumed value of P(h) in simulation". Also add the layer `theme_classic()`.

```{r nm-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like.

```{r}
unnorm_p
```


###

Let's create the following *normalized conditional distribution*. In other words, we are normalizing the graph we just created.

```{r}
norm_p <-tibble(p = rep(seq(0, 1, 0.1), 1000)) %>%
  mutate(heads = map_int(p, ~ rbinom(n = 1, size = 20, p = .))) %>% 
  filter(heads == 8) %>% 
  ggplot(aes(x = p)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 50) + 
    labs(title = expression(paste("Posterior Probability Distribution of ", rho[h])),
         x = expression(paste("Possible values for ", rho[h])),
         y = "Probability") +
    scale_x_continuous(breaks = seq(0.2, 0.7, by = 0.1)) +
    scale_y_continuous(labels = 
                        scales::percent_format(accuracy = 1)) +
  theme_classic()

norm_p

```

### Exercise 12

We begin our code the same way we began our code for the *unnormalized conditional distribution*. We have provided the code for you below. To begin, add the layer `geom_histogram()` and set `bins` to 50.


```{r nm-12, exercise = TRUE}
 tibble(p = rep(seq(0, 1, 0.1), 1000)) %>%
  mutate(heads = map_int(p, ~ rbinom(n = 1, size = 20, p = .))) %>% 
  filter(heads == 8) %>% 
  ggplot(aes(x = p))
```

```{r nm-12-hint-1, eval = FALSE}
... +
  geom_histogram(...)
```

### Exercise 13

Within `geom_histogram()`, use `after_stat()` . Inside `after_stat()`, use `aes()` with the argument `y = count/sum(count)` to put percents on the y-axis.

```{r nm-13, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r nm-13-hint-1, eval = FALSE}

```

### Exercise 14

Now use `scale_x_continuous()`. Set `breaks` to `seq()` that contains the values 0.2 and 0.7. Also set `by` to 0.1 within `seq()`.

```{r nm-14, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r nm-14-hint-1, eval = FALSE}
... +
  scale_x_continuous(... = seq(..., ..., ...))
```

### Exercise 15

Now use `scale_y_continuous()` to put the y-axis in percent format. Within `scale_y_continuous()`, set `labels` to `scales::percent_format()`. Within `percent_format()` set `accuracy` to 1.

```{r nm-15, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>


```{r nm-15-hint-1, eval = FALSE}
... + 
  scale_y_continuous(labels = scales::percent_format(...))
```



### Exercise 16

Finally, use `labs()` to add the title "Posterior Probability Distribution of P(h)". Then label your x-axis "Possibility values for P(h)" and y-axis "Probability". Also add the layer `theme_classic()`.


```{r nm-16, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like.

```{r}
norm_p
```

```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
