---
title: "Model Choice"
tutorial:
  id: "model-choice"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 10 tutorial"
---


```{r setup, include=FALSE}
library(tidyverse)
library(primer.tutorials)
library(learnr)
library(rstanarm)
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

# These models take awhile to build. 

options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local")


```



<!-- Make instructions more didactic. Make hints look more like code. Distinction between "Start a pipe" and "Assign to". -->


<!-- There are two main types of plots. The first type compares the the true values with the predicted values from the model. These are always interesting and highlight our central purpose: to make a model which replicates the outcomes we see in the world. The second type compares the predictions from two different models.  -->


## Name

```{r name, echo=FALSE}
question_text(
  "Student Name:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

## Email

``` {r email, echo=FALSE}
question_text(
  "Email:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

## Premilinaries
###


In this tutorial, we will be using the function `set.seed()`, which may seem unfamiliar. This function is useful for ensuring that we can reproduce the results of "random" computations.



### Exercise 1

Run the code below a few times. Notice how, each time, `rnorm()` produces a different random value. This is what we want any random number generator to do.

```{r before, exercise = TRUE}
rnorm(1)
```

### Exercise 2


But what happens if we want to reproduce the same "random" result again?

We can use `set.seed()` to make sure we get the same results again rather than different ones each time. Run the code a few times. Notice how we get the same 5 normally distributed numbers. 

```{r ss, exercise = TRUE}
set.seed(5)
rnorm(5)
```






## Submit

```{r context= "setup"}
submission_ui

```

```{r context="server"}
submission_server()
```


