---
title: Mapping
tutorial:
  id: mapping
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: Mapping data in R
---


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

<!-- CHECKLIST BEFORE STARTING: -->
<!-- * Load necessary libraries for tutorial in the first code chunk -->
<!-- * Edit yaml at the START OF THIS FILE -->
<!-- * Review: https://ppbds.github.io/primer.tutorials/articles/instructions.html -->


<!-- ## First section (use sentence case) -->
<!-- ### -->

## Map Basics
###

You've likely heard of longitude and latitude, the global coordinate system that lets us pinpoint 2D locations on a 3D surface. This is also known as a **c**oordinate **r**eference **s**ystem, or **CRS**. CRSs use a 3D model of the Earth to define locations on the surface of a grid, with longitude determining the east/west distance and the latitude determining the north/south distance. 

###

CRS are used to define spatial data that we can then map. 

###

Spatial data with a defined CRS can either be vector or raster data. Vector data is based on points that can be connected to form lines and polygons. It is located within a coordinate reference system and is similar to what a roadmap would look like.

###

Raster data, however, are values within a grid system, such as satellite imagery. In this Primer, we will only be dealing with vector data, which is the format in which we get data from the **tidycensus** package.

###

In order to parse this information, we will be using the **sf** package to process vector data.

### Exercise 1




















```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
