---
title: "Git"
tutorial:
  id: "git"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Git Tutorial"
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(png)
library(grid)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

<!-- This seems very fast. What other useful knowledge could we cover here? Maybe R packages? This should be matched more closely with the Primer. Have them confirm that they did all the primer steps by showing the results, from the Console, of 

pwd
ls
ls -a
cat .gitignore

Maybe the terminal tutorial should be done on day 2. Or maybe a couple of key terminal commands should be in Getting Started?


-->

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```


<!-- * Edit Github tutorial to add Github, RStudio, R Markdown, R Scripts. Do the questions in the order in which I start each class. See (and copy!) how Nosa does it. -->

## Setting up Github

GitHub is a Google Drive for all your R code and projects. In the professional world, people will use Github to backup and distribute their work. 


###

### Exercise 1

The first step to using GitHub is installing Git. To make sure you have Git, open RStudio on your computer. Click on the Terminal pane, which is next to the Console pane in the lower left portion of RStudio. Type `git --version`  at the Terminal. 


Copy/paste the result of the git command into the space below.

```{r git-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```


### Exercise 2

The next step is creating a GitHub account. To do so, follow the steps [here](https://github.com). Do not proceed with the tutorial until you have created an account.


### Exercise 3

Now that you have your Github account, you need to connect Git and RStudio to your account. Type `git config --global user.name` at the Terminal. It should return your name.


### Exercise 4

Great. Now type `git config --global user.email` at the Terminal. It should return the same email address you registered with Github.


###

**Note:** You cannot do the following sections of this tutorial if you did not get the correct outputs for the last two exercises.

## GitHub Repositories
###

Github is our Google Drive. Github repositories, or "repos" , are the Google folders where we store our work. Let's make a practice repo!

###

### Exercise 1

To begin, sign into GitHub and go to the homepage. Click the green new button on the left. 

<!-- image here -->



### Exercise 4

Type `packageVersion("usethis")` into the Console. (Not into the Terminal! This is an R command. The Terminal does not speak R.) It should return a version number equal to or higher than 2.0.0. Copy/paste the command and results. If this fails, you need to install the latest version of the **usethis** package. (You followed all the steps in the Getting Started appendix, right?) 

```{r git-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 10))
```


### Exercise 5

Type `usethis::git_sitrep()` into the Console. (Not into the Terminal! This is an R command. The Terminal does not speak R.) You will see a bunch of code divided into 4 sections. Copy/paste the first two sections: under **Git config (global)** and **GitHub**. Note that the double colon --- the "::" --- serves to tell R that the `git_sitrep()` function can be found in the **usethis** package.

```{r git-ex-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 10))
```

Your version won't be identical to mine, but it should be similar. The most important line is this one:

* Personal access token for 'https://github.com': '<discovered>'

If yours looks different, that probably means you have not set up your personal access token correctly. Please do so.

```{r}
file <- system.file("images/sitrep.png", 
                    package = "primer.tutorials")
img <- readPNG(file)
grid.raster(img)
```

<!-- Note that the above image is annoying because it is surrounded by way too much white space. Why? Maybe original creation of png file made it too small, on some sense? -->

<!-- DK: Discuss and demonstrate that you have done the personal access token thing? -->


## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```
