---
title: "Git"
tutorial:
  id: "git"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Git Tutorial"
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(png)
library(grid)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

<!-- This seems very fast. What other useful knowledge could we cover here? Maybe R packages? This should be matched more closely with the Primer. Have them confirm that they did all the primer steps by showing the results, from the Console, of 

pwd
ls
ls -a
cat .gitignore

Maybe the terminal tutorial should be done on day 2. Or maybe a couple of key terminal commands should be in Getting Started?


-->

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```


## Git/Github
### 

Professionals use Git/Guthub to backup and distribute their work. You want to be a professional, right? **Make sure to read (and follow the instructions in) the Tools appendix section about Git/Github/RStudio before doing these exercises.**

### Exercise 1

Let's check to see that you have git installed. To check, go to your Terminal and type `git --version`. Copy/paste the command and the results. 

```{r git-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```


### Exercise 2

Type `git config --global user.name` at the Terminal. It should return your name.

```{r git-ex-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```


### Exercise 3

Type `git config --global user.email` at the Terminal. It should return the same email address you use at Github.

```{r git-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

### Exercise 4

Type `packageVersion("usethis")` into the Console. (Not into the Terminal! This is an R command. The Terminal does not speak R.) It should return a version number equal to or higher than 2.0.0. Copy/paste the command and results. If this fails, you need to install the latest version of the **usethis** package. (You followed all the steps in the Getting Started appendix, right?) 

```{r git-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 10))
```


### Exercise 5

Type `usethis::git_sitrep()` into the Console. (Not into the Terminal! This is an R command. The Terminal does not speak R.) You will see a bunch of code divided into 4 sections. Copy/paste the first two sections: under **Git config (global)** and **GitHub**. Note that the double colon --- the "::" --- serves to tell R that the `git_sitrep()` function can be found in the **usethis** package.

```{r git-ex-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 10))
```

Your version won't be identical to mine, but it should be similar. The most important line is this one:

* Personal access token for 'https://github.com': '<discovered>'

If yours looks different, that probably means you have not set up your personal access token correctly. Please do so.

```{r}
file <- paste0(system.file("images/", 
                           package = "primer.tutorials"),
               "/sitrep.png")
img <- readPNG(file)
grid.raster(img)
```

<!-- Note that the above image is annoying because it is surrounded by way too much white space. Why? Maybe original creation of png file made it too small, on some sense? -->

<!-- DK: Discuss and demonstrate that you have done the personal access token thing? -->


## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```
