---
title: "Terminal"
tutorial:
  id: "terminal"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Terminal Tutorial"
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(png)
library(grid)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```

## The Terminal
###

The Terminal pane is next to the Console pane in the lower left portion of RStudio. We use the Console pane to talk to R. We use the Terminal pane to talk directly with the computer. Sadly, the Console and the Terminal speak different languages.

### Exercise 1

Let's figure out where we are. To see your current location, type `pwd` (**p**resent **w**orking **d**irectory) in the Terminal. Hit return, and copy/paste both the line on which you typed the command and the line below it. 


```{r term-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

This is the standard manner in which you will answer tutorial questions which use the command line. Your pasted answer should look like this:

```{r}
file <- paste0(system.file("images/", 
                           package = "primer.tutorials"),
               "pwd.png")
img <- readPNG(file)
grid.raster(img)
```

(You can include or not the prompt which follows the response to your command at your own discretion.)

Again, you paste in both the line with the command you issued and the result of that command. If the question asked you to issue two commands, then copy/paste them both. 

### Exercise 2

Type `ls` (list) in the terminal and hit return to see all the items that are located in the directory in which you are currently located. 

```{r term-ex-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 3

Let's make a folder called `Gov-1005`. Type the command `mkdir Gov-1005` and hit return. Now type `ls` to see your newly created folder! 
 
```{r term-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 4

Type in the command `cd Gov-1005` in order to **c**hange **d**irectories into the directory which we just created. There should not be anything in this directory. Type `ls` to be sure. 

```{r term-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 5

Let's now create a file. Type in `touch text.txt`and hit return. Now type `ls`. `touch` creates the file but does nothing else.

```{r term-ex-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 6

Let's change the name of `text.txt` to `my.text`. This is done with the `mv` command. (`mv` stands for **m**o**v**e.) First, type `ls` to confirm the existence of `text.txt`. Second, type `mv text.txt my.text`. Third, type `ls` to demonstrate that the renaming has worked. The (lack of) content in the file has not changed. 

```{r term-ex-6}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

Your pasted code should look something like:

```{r}
file <- paste0(system.file("images/", 
                           package = "primer.tutorials"),
               "mv.png")
img <- readPNG(file)
grid.raster(img)
```

### Exercise 7

Now let's try deleting `my.txt`. First, type `ls` to confirm it is there. Second, type with `rm my.text`. (`rm` stands for "remove.") Third, type `ls` to make sure the file is gone.


```{r term-ex-8}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 4))
```


## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```
