---
title: 'Wrangling: Plots'
tutorial:
  id: wrangling-plots
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: Complex pipes leading to plots.
---

<!-- How long is this tutorial? Add at least two more example plots. -->

<!-- Feel free to change any plot in any way, or even to delete a plot you feel is beyond repair. -->

<!-- Add Continue at the start of each section, after introductory words and before showing plot. -->

<!-- Replace ntile() because it is no longer in the book. Maybe quintile() can be used? -->

<!-- The effect of grouping with ntile() in Kenya was not obvious to me. Should this be more explicitly introduced as an alternative to fill? -->

<!-- Claus Wilke: https://clauswilke.com/ -->

<!-- https://ppbds.github.io/primer.tutorials/articles/instructions.html -->

<!-- ROAS plots about percentage accounted for by top 10 names and last letter in boys names. See: https://github.com/avehtari/ROS-Examples/tree/master/Names-->



```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(lubridate)
library(stringr)
library(skimr)
library(primer.data)
library(ggdist)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

# Needed for later sections of the tutorial 

library(ggthemes)
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

## National Health and Nutrition Survey

### 

`nhanes` includes data from the "National Health and Nutrition Examination Survey," which contains the personal and physical information of 10,000 Americans from two surveys in 2009 and 2011.

### 

Let's create the following plot.

```{r}
nhanes_p <- nhanes %>%
  mutate(weight = weight * 2.2, height = height / 30.48) %>%
  select(gender, weight, height, bmi) %>%
  drop_na(weight, height) %>% 
  ggplot(mapping = aes(x = weight, y = height, color = bmi)) +
    geom_jitter() +
    geom_smooth(se = FALSE, 
                method = "loess", 
                formula = y ~ x) +
    facet_wrap(~ gender) + 
    theme_clean() + 
    labs(y = "Height (feet)",
         x = "Weight (pounds)",
         title = "Height Versus Weight in the US",
         subtitle = "Association between weight and height is more positive for heavy men",
         color = "BMI",
         caption = "Source: NHANES (National Health and Examination Survey)")

nhanes_p
```

### Exercise 1

To view all columns and some of the respective values, `glimpse()` the `nhanes` data set.

```{r national-health-and--1, exercise = TRUE}

```

```{r national-health-and--1-hint-1, eval = FALSE}
glimpse(...)
```

### Exercise 2

In the tibble above, `weight` and `height` is measured in kg and cm, respectively. Using `mutate()`, multiply `weight` by 2.2 and divide `height` by 30.48 to convert units into pounds and feet. 

```{r national-health-and--2, exercise = TRUE}

```

```{r national-health-and--2-hint-1, eval = FALSE}
nhanes %>%
  mutate(weight = ..., 
         height = ...)
```

```{r national-health-and--2-hint-2, eval = FALSE}
Use * to multiply and / to divide.
```

```{r national-health-and--2-hint-3, eval = FALSE}
nhanes %>%
  mutate(weight = ... * ..., 
         height = .../ ...)
```

### Exercise 3

Now `select()` the `gender`, `weight`, `height`, and `bmi` columns. 

```{r national-health-and--3, exercise = TRUE}

```

```{r national-health-and--3-hint-1, eval = FALSE}
... %>%
  select(..., ..., ..., ...)
```

### Exercise 4

`nhanes` contains NA values in some rows. Start a pipe with `nhanes`. Use `drop_na()` with the arguments `weight`and `height` to remove all rows with NA value in these columns.

```{r national-health-and--4, exercise = TRUE}

```

```{r national-health-and--4-hint-1, eval = FALSE}
... %>%
  drop_na(..., ...)
```

### Exercise 5

Continue your pipe with `ggplot()`. Furthermore, add the layer `geom_jitter()` to make a jittered scatterplot. Map `weight` to the x-axis, `height` to the y-axis, and `bmi` to `color`.

```{r national-health-and--5, exercise = TRUE}

```

```{r national-health-and--5-hint-1, eval = FALSE}
... %>% 
  ggplot(data = ..., aes(x = ..., 
                        y = ..., 
                        color = ...)) +
  geom_jitter()
```

### Exercise 6

A trend line will help you visualize the general association between variables. Add one with the layer `geom_smooth()`. Set the argument `se` to FALSE and set `method` to "loess".

```{r national-health-and--6, exercise = TRUE}

```

```{r national-health-and--6-hint-1, eval = FALSE}
... + 
  geom_smooth(se = ..., method = ...)
```

### Exercise 7

Notice the raised message. Within `geom_smooth()` set the `formula` argument to `y ~ x` , which will make it disappear.

```{r national-health-and--7, exercise = TRUE}

```

```{r national-health-and--7-hint-1, eval = FALSE}
... + 
 geom_smooth(se = FALSE, 
             method = "loess", 
             formula = ...)
```

### Exercise 8

It's more insightful to separate the plot by gender , the process known as *faceting*, and displaying data of both genders as individual plots. Use `facet_wrap()` to facet the graph by `gender`.

```{r national-health-and--8, exercise = TRUE}

```

```{r national-health-and--8-hint-1, eval = FALSE}
... +
  facet_wrap( ~ ...) 
```

### Exercise 9

Adjust the theme of the graph. For a simplistic and clean theme, add `theme_clean()`.

```{r national-health-and--9, exercise = TRUE}

```

```{r national-health-and--9-hint-1, eval = FALSE}
Recall that when you add a theme, you add a layer! Use the + operator.
```

```{r national-health-and--9-hint-2, eval = FALSE}
... +
  theme_clean()
```

### Exercise 10

To finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, legend labels, and caption of your choice.

```{r national-health-and--10, exercise = TRUE}

```

Reminder: This is what your plot should look like.

```{r nhanes10-answer}
nhanes_p
```


## Covid-19

The `covid` contains data about Covid-19 and factors affecting Covid-19. Source of this data set is Johns Hopkins University. 

### 

Total Covid-19 cases over population proportion may be affected with ages of a country's residents, since Covid-19 has proven to be more infectious for elderly. 

###

If we look at this plot, we can see that there is roughly a positive association between median age and total Covid-19 cases over population proportion.

Let's create this plot.

```{r,include=FALSE}
covid <- read_csv('owid-covid-data.csv')
```

```{r covid, warning=FALSE}
covid_graph <- covid %>%
  select(continent, median_age, new_cases, location, population) %>%
   drop_na(new_cases) %>% 
   group_by(location) %>% 
    filter(location != 'World') %>%
    summarize(case_by_pop = sum(new_cases) / first(population),
              agemed = first(median_age),
              continent = first(continent), 
              rm.na = TRUE,
              .group = 'drop') %>%
               ggplot(mapping = aes(x = agemed, 
                         y = case_by_pop,
                         label = location,
                         color = continent)) +
               geom_point() + 
               theme_economist() +
               labs(x = "Median Age",
         y = "Total Covid-19 cases over population ",
         title = "Relation of Covid-19 cases and median age")
    
final_graph <-  ggplotly(covid_graph)

final_graph
```

### Exercise 1

`glimpse()` the `covid` data set. 

```{r covid-1, exercise = TRUE}

```

```{r covid-1-hint-1, eval = FALSE}
glimpse(...)
```

###

Although there are many Na values, these exist because of there isn't any of that variable. For example, for Covid-19 cases, there are Na values at the beginning since Covid-19 had not reached Afghanistan back then.

### Exercise 2

`select` the "continent", "location", "new_cases", and "median_age" variables.

```{r covid-2, exercise = TRUE}

```

```{r covid-2-hint-1, eval = FALSE}
covid %>%
  select(..., ..., ..., ...))
```


### Exercise 3

Because we do not want to include rows where there are no Covid-19 cases, drop Na values in the `new_cases` column. 

```{r covid-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r covid-3-hint-1, eval = FALSE}
... %>% 
  drop_na()
```
### 

If we did not `drop_na()`, errors would have been raised in further codes. 

### Exercise 4

To make our further country-based calculations easer, Now group by `location`.

```{r covid-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r covid-4-hint-1, eval = FALSE}
... %>%
  group_by(...)
```

###

Our dataset includes rows where the location is "world" and the continent is `NA`. However, we only want to analyse by country.

### Exercise 5

`filter` in a way that we extract all rows but the ones where the location is `world`.
```{r covid-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r covid-5-hint-1, eval = FALSE}
... %>%
  filter(...)
```

```{r covid-5-hint-2, eval = FALSE}
To exclude a value, use `!=`.
```

### Exercise 6

For our analysis, we want to calculate total Covid-19 cases divided by population for each country. To achieve, we need to create a variable using `summarize`

###

Create a variable `case_by_pop` that is equal to `sum()` of `new_cases` divided by population. 
Since the population is the same for every row for a country, to get the population, choose the `first()` value.

###

Using the `first()` function, create a "agemed" and "continent" variables that should be equal to median age and continent of the country, respectively.

###

Furthermore, to avoid any errors NA values might cause, set `na.rm` argument to `TRUE`.

```{r covid-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r covid-6-hint-1, eval = FALSE}
... %>%
      summarize(case_by_pop = sum(...) / first(...),
              agemed = first(...),
              continent = first(...),
              na.rm = ...)
```

###

Did you receive a warning message? 

### Exercise 7

Our job with groups is done since we have created the needed variables. However, we have to set an argument to choose what to do with groups. 

###

`.groups` is an argument that tells `summarize()` what to do with the grouping of the data after it has used the grouping to produce its summary. 

If you exclude `groups` argument, you will get a warning message.

### 

within `summarize` function from previous exercise, set `.group` argument equal to "drop". 


```{r covid-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r covid-7-hint-1, eval = FALSE}
... %>% 
  summarize(...,
            .groups = "...")
```

### 

 `.groups` does not affect the data in the summary tibble. You can either `"keep"` the grouping, `"drop"` the grouping, or `"drop_last"`, i.e. to drop the last of the specified grouping variables (this is because retaining all the same groups after summary creates groups which only contain single rows). `"drop_last"` is the default in most cases.  

### Exercise 8

To include all four variables on the plot, we have to map each of them to a different argument.

###

Continue your pipe and add  `ggplot()`.  Map `agemed` to the x-axis, `case_by_pop` to the y-axis, `location` to the label, and `continent` to color.

Then, to create a scatter, add a new layer `geom_point()`.

```{r covid-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r covid-8-hint-1, eval = FALSE}
... %>% 
  ggplot(mapping = aes(x = ..., 
                       y = ...,
                       label = ...,
                       location = ...) +
  geom_point()
```

### Exercise 9

Add the theme `theme_economist()` as a new layer to the plot.

```{r covid-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r covid-9-hint-1, eval = FALSE}
... +
  theme_economist()
```


### Exercise 10

To finish your plot, use `labs()` to give the graph a title and axis labels.

Reminder: This is what your plot should look like.

```{r covid10}
final_graph
```

```{r covid-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

###

Now, although our graph looks like the desired graph, it is not interactive, and unlike expected, nothing happens if you hover your mouse over the plot.

This is beacuse, we have to make use of ` plotly()` package to create interactive graphs.

### Exercise 11

Moreover, to use plotly, we have to save our graph to a variable. Therefore, save our plot to a variable names `covid_graph`.

```{r covid-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r covid-11-hint-1, eval = FALSE}
covid_graph <- covid %>%
  select(continent, median_age, new_cases, location, population) ...
.
.
.
```

###

Since we saved our graph as `covid_graph`, the only thing to do is pass our variable as an argument to `ggplotly` function.

### Exercise 12

```{r covid-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r covid-12-hint-1, eval = FALSE}
...

ggplotly(...)
```

###

Well done!


## Seguro Popular

### 

The `sps` data set contains information about a study done on a popular Mexican health insurance program, Seguro Popular. In the study, some Mexican health clusters were randomly "treated." The treatment consisted of encouragement for people in that health cluster to enroll in the health insurance program, as well as funds to improve health facilities in that cluster.

### 

Let's create the following plot.

```{r sps_plot}
sps_p <- sps %>%
  filter(education %in% c("preschool", "secondary", 
                          "high school", "college")) %>%
  select(-c(health_exp_1m, t2_health_exp_1m)) %>%
  mutate(change_in_expenses = t2_health_exp_3m - health_exp_3m) %>%
  group_by(treatment, education) %>%
  summarize(mean_change_in_expenses = mean(change_in_expenses),
            .groups = "drop") %>%
  mutate(treatment = as.factor(treatment)) %>% 
  ggplot(mapping = aes(x = fct_reorder(education, mean_change_in_expenses), 
                       y = mean_change_in_expenses, 
                       fill = treatment)) +
    scale_fill_manual(values= c("#00BCD8","#B983FF")) +
    geom_col(position = "dodge", alpha=0.9) + 
    theme_minimal() +
    labs(x = "Education",
         y = "Average Change in Expenses",
         title = "Spending Changes and Seguro Popular",
         subtitle = "Treatment 0  most effective at college level and treatment 1 at preschool level",
         fill = "Treatment",
         caption = "Source: King et al. (2009)")

sps_p
```

### Exercise 1 

`glimpse()` the dataset `sps`.

```{r seguro-popular-1, exercise = TRUE}

```

```{r seguro-popular-1-hint-1, eval = FALSE}
glimpse(...)
```

### Exercise 2

`filter()` `sps` to extract only the rows with an `education` level of "preschool," "secondary," "high school," or "college."  Use the `%in%` and `c()` to do so.

```{r seguro-popular-2, exercise = TRUE}

```

```{r seguro-popular-2-hint-1, eval = FALSE}
sps %>%
  filter(education %in% ...)
```

```{r seguro-popular-2-hint-2, eval = FALSE}
sps %>% 
  filter(education %in% c(..., ..., ..., ...))
```

### Exercise 3

Use `select()` to exclude the columns `health_exp_1m` and `t2_health_exp_1m`. 

```{r seguro-popular-3, exercise = TRUE}

```

```{r seguro-popular-3-hint-1, eval = FALSE}
Remember that select(-...) returns all columns except for the specified column(s) that come after "-". When you use a vector, you only need one -.
```

```{r seguro-popular-3-hint-2, eval = FALSE}
... %>% 
  select(-c(..., ...))
```

### Exercise 4 

Because we want to visualize the impact of treatments, we need a measure of the change in expenses after the treatment is needed. Use `mutate()` to create a new variable, `change_in_expenses`. This variable should be equal to `health_exp_3m` subtracted from `t2_health_exp_3m`.


```{r seguro-popular-4, exercise = TRUE}

```

```{r seguro-popular-4-hint-1, eval = FALSE}
... %>% 
  mutate(... = t2_health_exp_3m - health_exp_3m) 
```

### Exercise 5

Using group_by() function, group the data by `treatment` and `education`.

```{r seguro-popular-5, exercise = TRUE}

```

```{r seguro-popular-5-hint-1, eval = FALSE}
... %>%
  group_by(...)
```

### Exercise 6

Use `summarize()` to calculate `mean_change_in_expenses`, the` mean()` of the `change_in_expenses` for each group. Set the argument `.groups` equal to "drop".

```{r seguro-popular-6, exercise = TRUE}
  
```

```{r seguro-popular-6-hint-1, eval = FALSE}
... %>% 
  summarize(... = mean(...),
            .groups = "drop")
```

### Exercise 7

Because the `treatment` column is not a factor, we can't group our data by it. To fix this, use `mutate()` and set the column `treatment` to `as.factor()` with the argument `treatment`. 

```{r seguro-popular-7, exercise = TRUE}

```

```{r seguro-popular-7-hint-1, eval = FALSE}
 ... %>% 
  mutate(treatment = as.factor(...))
```

### Exercise 8

Use `%>%` to add `ggplot()`. Use `fct_reorder()` to reorder the `education` variable by `mean_change_in_expenses` and map this to x-axis. Map `mean_change_in_expenses` to the y-axis, and `treatment` to the `fill`. Also add the layer `geom_col()`.


```{r seguro-popular-8, exercise = TRUE}

```

```{r seguro-popular-8-hint-1, eval = FALSE}
.. %>% 
  ggplot(mapping = aes(x = fct_reorder(education, 
                                       mean_change_in_expenses), 
                     y = ..., 
                     fill = ...) +
  geom_col()
```

### Exercise 9 

When you set the `fill` argument in the `ggplot` equal to a variable, ggplot by default sets a color set.
To set make the bar charts color of your choice, you can use `scale_fill_manual` function. This function takes on values as a vector. Within this argument, set `values` equal to a vector of two color codes: `#00BCD8` and `#B983FF`.

```{r seguro-popular-9, exercise = TRUE}

```

```{r seguro-popular-9-hint-1, eval = FALSE}
... +
  scale_fill_manual(values= c("#00BCD8","#B983FF")) +
  geom_col()
```

### Exercise 10

Within `geom_col()`, set the `position` argument equal to `"dodge"`. Moreover, you can also set the transparency of the bars with the argument `alpha`, where the default value of 1.0 is opaque. For our graph in this section, we set the `alpha` equal to 0.9. 

```{r seguro-popular-10, exercise = TRUE}

```

```{r seguro-popular-10-hint-1, eval = FALSE}
... +
  geom_col(position = "dodge", alpha=0.9)
```

### Exercise 11

Add `theme_minimal()` to change the style of the graph.

```{r seguro-popular-11, exercise = TRUE}

```

### Exercise 12

To finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, and caption of your choice.

```{r seguro-popular-12, exercise = TRUE}

```

Reminder: This is what your plot should look like.

```{r sps12-answer}
sps_p
```

## Shaming 

### 

The `shaming` data set measures the impact of social pressure on voting. Nearly 350,000 people in Michigan were randomly assigned to 1 of 5 treatment groups before the 2006 Michigan primary. All 5 groups were sent mail before the primary: the "Civic Duty" group had an extra reminder that voting was a civic responsibility, the "Hawthorne" group was told that whether or not they voted would be in the public record, the "Self" group was actually *sent* the public record of whether or not they voted in 2004, and the "Neighbors" group was sent both their voting record and their neighbors' voting record from 2004. 

### 

Let's create the following plot.

```{r sh_goal}
shaming_p <- shaming %>%
  select(primary_04, primary_06, treatment) %>%
  mutate(primary_04 = if_else(condition = 
                                str_detect(primary_04, "Yes"),
                                true = 1,
                                false = 0)) %>%
  pivot_longer(cols = c(primary_04, primary_06), 
               names_to = "year", 
               values_to = "voted") %>%
  group_by(treatment, year, voted) %>%
  summarize(num_voters = n(), 
            .groups = "drop") %>%
  mutate(voted = if_else(condition = voted == 1,
                         true = "did_vote",
                         false = "did_not_vote")) %>%
  pivot_wider(names_from = voted, values_from = num_voters)  %>%
  mutate(pct_voted = did_vote / (did_vote + did_not_vote)) %>% 
  ggplot(mapping = aes(x = fct_reorder(treatment, pct_voted), 
                       y = pct_voted, fill = year)) +
    geom_col(position = "dodge") +
    geom_text(aes(label = sprintf("%0.2f", round(pct_voted, digits = 2))), vjust = 1.5,   position = position_dodge(0.9)) +
    labs(x = "Treatment",
         y = "Voting Percentage",
         title = "Voting Rates Based on Mailings",
         subtitle = "Shaming people makes them more likely to vote",
         fill = "Year",
         caption = "Source: Gerber, Green, and Larimer (2008).") +
    theme_fivethirtyeight()

shaming_p
```

### Exercise 1

`skim()` the `shaming` data set. Pay close attention to the data type of each variable.

```{r shaming-1, exercise = TRUE}

```

### Exercise 2

`select()` the columns `treatment`, `primary_04`, and `primary_06` of the `shaming` dataset.

```{r shaming-2, exercise = TRUE}

```

```{r shaming-2-hint-1, eval = FALSE}
shaming %>% 
  select(..., ..., ..., ...)
```

### Exercise 3

Use `mutate()` to change the `primary_04` column into binary. Set `primary_04` to an `if_else()` statement. Within `if_else()`, set `condition` to `str_detect()`, with arguments to detect the string "Yes" in `primary_04`. If the condition is true, the function should return `1`, and if false, `0`.

```{r shaming-3, exercise = TRUE}

```

```{r shaming-3-hint-1, eval = FALSE}
mutate(primary_04 = if_else(str_detect(primary_04, "..."), 1, 0))
```

### Exercise 4

A long data set is the dataset where there are more rows and less columns, every row representing an observation belonging to a category. Use `pivot_longer()` to map the *names* of the `primary_04` and `primary_06` columns to a new column, "year,". Map the  *values* of the two columns to a new column, "voted."


```{r shaming-4, exercise = TRUE}

```

```{r shaming-4-hint-1, eval = FALSE}
...  %>%
  pivot_longer(cols = c(..., ...), 
               names_to = ...,
               values_to = ...)
```

### Exercise 5

Great job! Now group the data by `treatment`, `year`, and `voted`.

```{r shaming-5, exercise = TRUE}

```

```{r shaming-5-hint-1, eval = FALSE}
Use the group_by() function.
```

### Exercise 6

Use `summarize()` to create the variable `num_voters`, which is set to the function `n()`. Then, set the `.groups` argument equal to `"drop"`.

**Note:** `n()` simply counts the number of rows in each group. 

```{r shaming-6, exercise = TRUE}

```

```{r shaming-6-hint-1, eval = FALSE}
... %>% 
  summarize(num_voters = n(), 
            .groups = "...")
```

### Exercise 7

The `voted` column is a bit difficult to understand because the numerical value (0 or 1) is used to represent an idea (the person did or did not vote). Use `mutate()` to set `voted` to an `if_else()` statement. Within `if_else()`, set the condition to where `voted` is equal to 1. Set the result for true to "did_vote," and the result for false to "did_not_vote."


```{r shaming-7, exercise = TRUE}

```

```{r shaming-7-hint-1, eval = FALSE}
...%>%
  mutate(voted = if_else(voted == ..., "...", "..."))
```

### Exercise 8

Widening a data set means the process of increasing the number of columns and decreasing the number of rows, which may prove to make the analysis part easier. Let's transform `did_vote` and `did_not_vote` into their own columns. Call `pivot_wider()` that gets its column `names_from` `voted` and its `values_from` `num_voters`.


```{r shaming-8, exercise = TRUE}

```

```{r shaming-8-hint-1, eval = FALSE}
...  %>%
  pivot_wider(names_from = ..., 
              values_from = ...)
```
###

In this case, we converted `did_vote` and `did_not_vote` into their own columns because we will calculate the proportion of people who voted. 

### Exercise 9

Use `mutate()` to create a new variable `pct_voted`, which is equal to the number of people who `did_vote` divided by the total number of people.

```{r shaming-9, exercise = TRUE}

```

```{r shaming-9-hint-1, eval = FALSE}
Note that the total number of people is equal to (did_vote + did_not_vote). Also, use / to divide. 
```

```{r shaming-9-hint-2, eval = FALSE}
... %>% 
  mutate(... = ... / (did_vote + did_not_vote))
```

### Exercise 10

Use `%>%` to add `ggplot()`. Use `fct_reorder()` to reorder the `treatment` variable by `pct_voted` and map this to x-axis. Map `pct_voted` to the y-axis, and `year` to the `fill`. Also add the layer `geom_col()`.


```{r shaming-10, exercise = TRUE}

```

```{r shaming-10-hint-1, eval = FALSE}
... %>% 
  ggplot(mapping = aes(x = fct_reorder(treatment, pct_voted), 
                       y = ..., 
                       fill = ...)) +
  geom_col()
```

### Exercise 11

Within `geom_col()`, set the position argument `position` equal to "dodge"`. 

```{r shaming-11, exercise = TRUE}

```

```{r shaming-11-hint-1, eval = FALSE}
... +
  geom_col(position = "dodge")
```

### Exercise 12
When observed bar values are close, it's better to have the values on top of bars. To do this, we have to use `geom_text()` function. Call `geom_text()`, and within this function, set `label` within `aes` equal to the `pct_voted`. Next, for vertical adjustment- where each text should appear- set the `vjust` argument of the `geom_text()` to the value of your choice. We decided on the `vjust` value of 1.5. Furthermore, because we are creating a dodged bar chart, set `position` argument equal to `position_dodge(0.9)`.

```{r shaming12, exercise = TRUE}

```

```{r shaming12-hint, eval = FALSE}
... +
  geom_text(aes(label = ...), vjust = ..., position = position_dodge(0.9))
```

### Exercise 13
If you did the above exercise, you may have got texts on top of bars with too many decimal places. To avoid this chaos, you have to set the number of decimal places. 

###
You can set the number of decimal places using `sprintf()` function. For 2 decimal places, within the `aes` argument of `geom_text()` function, set the `label` equal to 
`sprintf("%0.2f", round(pct_voted, digits = 2))`. This will round the `pct_voted` to two decimal places. 

```{r shaming13, exercise = TRUE}

```

```{r shaming13-hint, eval = FALSE}
... +
  geom_text(aes(label = ...), vjust = 1.5, position = position_dodge(0.9))
```

### Exercise 14

Add the theme `theme_fivethirtyeight()` to your plot. 

```{r shaming14, exercise = TRUE}

```

```{r shaming14-hint, eval = FALSE}
Remember when you add a theme, you add a layer. Use +.
```

### Exercise 15

To finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, legend labels, and caption of your choice.

Reminder: This is what your plot should look like. 

```{r shaming15-answer}
shaming_p
```

```{r shaming15, exercise = TRUE}

```


```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
