---
title: 'Wrangling: Plots'
author: Atilla Colak
tutorial:
  id: wrangling-plots
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: Complex pipes leading to plots.
---

<!-- Make shaming yours. -->

<!-- The below links should be dropped at least once, if not twice. -->

<!-- Select a new plot. -->

<!-- Claus Wilke: https://clauswilke.com/ -->

<!-- https://ggplot2.tidyverse.org/ -->
<!-- https://ggplot2-book.org/ -->
<!-- https://socviz.co/ -->
<!-- https://clauswilke.com/dataviz/ -->


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(lubridate)
library(stringr)
library(skimr)
library(primer.data)
library(babynames)
library(ggdist)
library(plotly)
library(dplyr)
library(gghighlight)
library(scales)
library(ggpubr)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

# Needed for later sections of the tutorial 

library(ggthemes)

covid <- read_csv('data/owid-covid-data.csv')


shaming_p <- shaming %>%
  select(primary_04, primary_06, treatment) %>%
  mutate(primary_04 = if_else(condition = 
                                str_detect(primary_04, "Yes"),
                                true = 1,
                                false = 0)) %>%
  pivot_longer(cols = c(primary_04, primary_06), 
               names_to = "year", 
               values_to = "voted") %>%
  group_by(treatment, year, voted) %>%
  summarize(num_voters = n(), 
            .groups = "drop") %>%
  mutate(voted = if_else(condition = voted == 1,
                         true = "did_vote",
                         false = "did_not_vote")) %>%
  pivot_wider(names_from = voted, values_from = num_voters)  %>%
  mutate(pct_voted = did_vote / (did_vote + did_not_vote)) %>%
  mutate(year = if_else(condition = year == "primary_04",
                        true = "2004",
                        false = "2006"))
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

## National Health and Nutrition Survey

### 

National Health and Nutrition Examination Survey (NHANES) is a survey distributed to adults and children in the United States. 
This research survey aimed to examine health and nutritional status worldwide. 

### 

Let's create the following plot.

```{r}
nhanes_p <- nhanes %>%
  mutate(weight = weight * 2.2, height = height / 30.48) %>%
  select(gender, weight, height, bmi) %>%
  drop_na(weight, height) %>% 
  ggplot(mapping = aes(x = weight, y = height, color = bmi)) +
    geom_jitter() +
    geom_smooth(se = FALSE, 
                method = "loess", 
                formula = y ~ x) +
    facet_wrap(~ gender) + 
    theme_clean() + 
    labs(y = "Height (feet)",
         x = "Weight (pounds)",
         title = "Height Versus Weight in the US",
         subtitle = "Association between weight and height is more positive for heavy men",
         color = "BMI",
         caption = "Source: NHANES (National Health and Examination Survey)")

nhanes_p
```

### Exercise 1

To view all columns and some of the respective values, `glimpse()` the `nhanes` data set.

```{r national-health-and--1, exercise = TRUE}

```

```{r national-health-and--1-hint-1, eval = FALSE}
glimpse(...)
```

### 

`nhanes` includes data from the "National Health and Nutrition Examination Survey," which contains the personal and physical information of 10,000 Americans from two surveys in 2009 and 2011.

### Exercise 2

In the tibble above, `weight` and `height` is measured in kg and cm, respectively. Using `mutate()`, multiply `weight` by 2.2 and divide `height` by 30.48 to convert units into pounds and feet. 

```{r national-health-and--2, exercise = TRUE}

```

```{r national-health-and--2-hint-1, eval = FALSE}
nhanes %>%
  mutate(weight = ..., 
         height = ...)
```

```{r national-health-and--2-hint-2, eval = FALSE}
Use * to multiply and / to divide.
```

```{r national-health-and--2-hint-3, eval = FALSE}
nhanes %>%
  mutate(weight = ... * ..., 
         height = ... / ...)
```

### Exercise 3

Now `select()` the `gender`, `weight`, `height`, and `bmi` columns. 

```{r national-health-and--3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r national-health-and--3-hint-1, eval = FALSE}
... %>%
  select(..., ..., ..., ...)
```

### 

Because there may be differences in heights and weights due to biological factors, we wanted to analyse the results gender-wise. 

### Exercise 4

`nhanes` contains NA values in some rows. Start a pipe with `nhanes`. Use `drop_na()` with the arguments `weight`and `height` to remove all rows with NA value in these columns.

```{r national-health-and--4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r national-health-and--4-hint-1, eval = FALSE}
... %>%
  drop_na(..., ...)
```

### 

For some cases, there are columns where more than 60% of data is NA. In those cases, we would consider dropping the column. 

### Exercise 5

Continue your pipe with `ggplot()`. Furthermore, add the layer `geom_jitter()` to make a jittered scatterplot. Map `weight` to the x-axis, `height` to the y-axis, and `bmi` to `color`.

```{r national-health-and--5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r national-health-and--5-hint-1, eval = FALSE}
... %>% 
  ggplot(data = ..., aes(x = ..., 
                        y = ..., 
                        color = ...)) +
  geom_jitter()
```

### 

Instead of `geom_jitter()`, we also can use `geom_pointdensity()` function from `ggpointdensity` package, which would color datapoints by how often they appear. 

### Exercise 6

A trend line will help you visualize the general association between variables. Add one with the layer `geom_smooth()`. Set the argument `se` to FALSE and set `method` to "loess".

```{r national-health-and--6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r national-health-and--6-hint-1, eval = FALSE}
... + 
  geom_smooth(se = ..., method = ...)
```

### 

`se` argument specifies whether the confidence interval should be displayed. If we set this true, we should also specify the `level` argument. `level` specifices the confidence level of the interval, 0.95 by default.

### Exercise 7

Notice the raised message. Within `geom_smooth()` set the `formula` argument to `y ~ x` , which will make it disappear.

```{r national-health-and--7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r national-health-and--7-hint-1, eval = FALSE}
... + 
 geom_smooth(se = FALSE, 
             method = "loess", 
             formula = ...)
```

### 

Although there is no warning, the output smoothed line is the same as before. This is because the reason of the warning is to remind us that we should specify the formula, even though by default ggplot uses `y ~ x` formula.

### Exercise 8

It's more insightful to separate the plot by gender , the process known as *faceting*, and displaying data of both genders as individual plots. Use `facet_wrap()` to facet the graph by `gender`.

```{r national-health-and--8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r national-health-and--8-hint-1, eval = FALSE}
... +
  facet_wrap( ~ ...) 
```

### 

In some cases, such as the case of graphing by one variable, we can use `facet_wrap()` and `facet_grid()` interchangeably. However, in general, the use of these two functions is different. `facet_grid()` produces a 2d grid of panels defined by variables, whereas `facet_wrap()` "wraps a 1d ribbon of panels into 2d. To learn more about this issue see [this thread](https://stackoverflow.com/questions/20457905/whats-the-difference-between-facet-wrap-and-facet-grid-in-ggplot2).

### Exercise 9

Adjust the theme of the graph. For a simplistic and clean theme, add `theme_clean()`.

```{r national-health-and--9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r national-health-and--9-hint-1, eval = FALSE}
Recall that when you add a theme, you add a layer! Use the + operator.
```

```{r national-health-and--9-hint-2, eval = FALSE}
... +
  theme_clean()
```

### 

Alternatively, we also can use similar themes such as `theme_light()` and `theme_classic()`.

### Exercise 10

To finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, legend labels, and caption of your choice.

```{r national-health-and--10, exercise = TRUE}

```

Reminder: This is what your plot should look like.

```{r nhanes10-answer}
nhanes_p
```

## Covid-19

### 

The `covid` contains data about Covid-19 and factors affecting Covid-19. Source of this data set is [Johns Hopkins University], and we downloaded it from [ourworldindata.org](https://ourworldindata.org/coronavirus-source-data).  


### 

Total Covid-19 cases over population proportion may be affected by ages of a country's residents, since Covid-19 has proven to be more infectious for elderly. 

### 

If we look at this plot, we can see that there is roughly a positive association between median age and total Covid-19 cases over population proportion.

Let's create this plot.


```{r covid}
covid_graph <- covid %>%
  select(continent, median_age, new_cases, location, population) %>%
  drop_na(new_cases) %>% 
  group_by(location) %>% 
  filter(continent != 'World') %>%
  summarize(case_by_pop = sum(new_cases) / first(population),
            agemed = first(median_age),
            continent = first(continent), 
            rm.na = TRUE,
            .group = 'drop') %>%
  ggplot(mapping = aes(x = agemed, 
                       y = case_by_pop,
                       label = location,
                       color = continent)) +
    geom_point() + 
    theme_economist() +
    labs(x = "Median Age",
         y = "Total Covid-19 cases over population ",
         title = "Relation of Covid-19 cases and median age")
    
final_graph <-  ggplotly(covid_graph)

final_graph
```

### Exercise 1

`glimpse()` the `covid` data set. 

```{r covid19-1, exercise = TRUE}

```

```{r covid19-1-hint-1, eval = FALSE}
glimpse(...)
```

### 

Although there are many NA values, these exist because of there isn't any of that variable. For example, for Covid-19 cases, there are NA values at the beginning since Covid-19 had not reached Afghanistan back then.

### Exercise 2

`select()` the "continent", "location", "new_cases", and "median_age" variables.

```{r covid19-2, exercise = TRUE}

```

```{r covid19-2-hint-1, eval = FALSE}
covid %>%
  select(..., ..., ..., ...))
```

### 

Because our graph will be interactive, we can easily analyse more variables than standard `ggplot` graphs. 

### Exercise 3

Because we do not want to include rows where there are no Covid-19 cases, drop NA values in the `new_cases` column. 

```{r covid19-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r covid19-3-hint-1, eval = FALSE}
... %>% 
  drop_na(...)
```

### 

If we did not `drop_na()`, errors would have been raised in further codes. 

### Exercise 4

To make our further country-based calculations easer, Now group by `location`.

```{r covid19-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r covid19-4-hint-1, eval = FALSE}
... %>%
  group_by(...)
```

### 

In our dataset, there is a continent value `world` that contains the summation of data of individual countries. For example, new cases of `world` is the total new cases recorded that day. 

### Exercise 5

`filter` in a way that we extract all rows but the ones where the continent is `world`.

```{r covid19-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r covid19-5-hint-1, eval = FALSE}
... %>%
  filter(...)
```

```{r covid19-5-hint-2, eval = FALSE}
To exclude a value, use `!=`.
```

### 

Because `world` is not  a continent and we want to make country-wise and country-wise analysis, we excluded the rows where the continent is equal to world.

### Exercise 6

For our analysis, we want to calculate total Covid-19 cases divided by population for each country. To achieve, we need to create a variable using `summarize`

### 

Create a variable `case_by_pop` that is equal to `sum()` of `new_cases` divided by population. 
Since the population is the same for every row for a country, to get the population, choose the `first()` value.

### 

Using the `first()` function, create a "agemed" and "continent" variables that should be equal to median age and continent of the country, respectively.

### 

Furthermore, to avoid any errors NA values might cause, set `na.rm` argument to `TRUE`.

```{r covid19-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r covid19-6-hint-1, eval = FALSE}
... %>%
      summarize(case_by_pop = sum(...) / first(...),
              agemed = first(...),
              continent = first(...),
              na.rm = ...)
```

### 

Did you receive a warning message? 

### Exercise 7

Our job with groups is done since we have created the needed variables. However, we have to set an argument to choose what to do with groups. 

### 

`.groups` is an argument that tells `summarize()` what to do with the grouping of the data after it has used the grouping to produce its summary. 

If you exclude `groups` argument, you will get a warning message.

### 

within `summarize` function from previous exercise, set `.group` argument equal to "drop". 


```{r covid19-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r covid19-7-hint-1, eval = FALSE}
... %>% 
  summarize(...,
            .groups = "...")
```

### 

 `.groups` does not affect the data in the summary tibble. You can either `"keep"` the grouping, `"drop"` the grouping, or `"drop_last"`, i.e. to drop the last of the specified grouping variables (this is because retaining all the same groups after summary creates groups which only contain single rows). `"drop_last"` is the default in most cases.  

### Exercise 8

To include all four variables on the plot, we have to map each of them to a different argument.

### 

Continue your pipe and add  `ggplot()`.  Map `agemed` to the x-axis, `case_by_pop` to the y-axis, `location` to the label, and `continent` to color.

Then, to create a scatter, add a new layer `geom_point()`.

```{r covid19-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r covid19-8-hint-1, eval = FALSE}
... %>% 
  ggplot(mapping = aes(x = ..., 
                       y = ...,
                       label = ...,
                       location = ...) +
  geom_point()
```

### Exercise 9

Add the theme `theme_economist()` as a new layer to the plot.

```{r covid19-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r covid19-9-hint-1, eval = FALSE}
... +
  theme_economist()
```

### 

Instead of `theme_economist()` we could have chosen a theme among choices such as `theme_minimal()`, `theme_classic()`, and many more. For all existing `ggplot2` themes, click [this link](https://ggplot2.tidyverse.org/reference/ggtheme.html).

### Exercise 10

To finish your plot, use `labs()` to give the graph a title and axis labels.

Reminder: This is what your plot should look like.

```{r covid19-10}
final_graph
```

```{r covid-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

### 

Now, although our graph looks like the desired graph, it is not interactive, and unlike expected, nothing happens if you hover your mouse over the plot.

This is beacuse, we have to make use of ` plotly()` package to create interactive graphs.

### Exercise 11

Moreover, to use plotly, we have to save our graph to a variable. Therefore, save our plot to a variable names `covid_graph`.

```{r covid19-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r covid19-11-hint-1, eval = FALSE}
covid_graph <- covid %>%
  select(continent, median_age, new_cases, location, population) ...
.
.
.
```

### 

Since we saved our graph as `covid_graph`, the only thing to do is pass our variable as an argument to `ggplotly` function.

### Exercise 12

```{r covid19-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r covid19-12-hint-1, eval = FALSE}
...

ggplotly(...)
```

### 

Well done!


## Seguro Popular

### 

The `sps` data set contains information about a study done on a popular Mexican health insurance program, Seguro Popular. In the study, some Mexican health clusters were randomly "treated." The treatment consisted of encouragement for people in that health cluster to enroll in the health insurance program, as well as funds to improve health facilities in that cluster.

### 

Let's create the following plot.

```{r sps_plot}
 
sps_p <- sps %>%
  filter(education %in% c("college", "high school", "secondary", "preschool")) %>%
  select(-c(health_exp_1m, t2_health_exp_1m)) %>%
  mutate(change_in_expenses = t2_health_exp_3m - health_exp_3m) %>%
  group_by(treatment, education) %>%
  summarize(mean_change_in_expenses = mean(change_in_expenses),
            .groups = "drop") %>%
  mutate(treatment = ifelse(treatment == "1", "Treatment Group", "Control Group")) %>%
  ggplot(mapping = aes(x = education, 
                       y = mean_change_in_expenses, 
                       fill = treatment)) +
    scale_fill_manual(values = c("cornflowerblue", "darkturquoise")) +
    geom_col(position = "dodge", alpha = 0.9) + 
    scale_x_discrete(limits = c("preschool", "secondary", "high school", "college")) +
    scale_y_continuous(labels = dollar_format(suffix = "₱", prefix = "")) +
    theme_minimal() +
    labs(x = "Education",
         y = "Average Change in Health Expenses",
         title = "Spending Changes and Seguro Popular",
         subtitle = "Treatment at college level reduced expenses the most",
         fill = "Treatment",
         caption = "Source: King et al. (2009)")

sps_p
```

### Exercise 1

`glimpse()` the dataset `sps`.

```{r seguro-popular-1, exercise = TRUE}

```

```{r seguro-popular-1-hint-1, eval = FALSE}
glimpse(...)
```

### 

The survey was conducted in two different periods of times. Initial period was for applying treatment to treatment group. The second period was for observing treatment results.



### Exercise 2

`filter()` `sps` to extract only the rows with an `education` level of `preschool`, `secondary`, `high school`, and `college`. 
Use the `%in%` to accelerate the process. 

```{r seguro-popular-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r seguro-popular-2-hint-1, eval = FALSE}
sps %>%
  filter(education %in% ...)
```

### Exercise 3

Use `select()` to exclude the columns `health_exp_1m` and `t2_health_exp_1m`. 

```{r seguro-popular-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r seguro-popular-3-hint-1, eval = FALSE}
Remember that select(-...) returns all columns except for the 
specified column(s) that come after "-". When you use a vector, 
you only need one -.
```

```{r seguro-popular-3-hint-2, eval = FALSE}
... %>% 
  select(-c(..., ...))
```

### 

These two columns were the health-related spending in the last month for 2005 initial and 2006 follow-up survey 10 months later.

### Exercise 4

Because we want to visualize the impact of treatments, we need a measure of the change in expenses after the treatment is applied. Use `mutate()` to create a new variable, `change_in_expenses`. This variable should be equal to `t2_health_exp_3m - health_exp_3m`.


```{r seguro-popular-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r seguro-popular-4-hint-1, eval = FALSE}
... %>% 
  mutate(... = t2_health_exp_3m - health_exp_3m) 
```

### 

From September 2005 to July 2006, Mexico encountered an inflation. `t2_health_exp_3m` contains the 3 months of health-related spendings from July 2006 to August 2006.

### Exercise 5

Using `group_by()` function, group the data by `treatment` and `education`.

```{r seguro-popular-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r seguro-popular-5-hint-1, eval = FALSE}
... %>%
  group_by(...)
```

### 

To ensure the results are accurate, we need findings that support that health-related spending did in fact decrease in treatment group. Therefore, taking into the inflation account, the difference between` t2_health_exp_3m` and `health_exp_3m` should be lower for the treatment group. 

### Exercise 6

Use `summarize()` to calculate `mean_change_in_expenses`, the` mean()` of the `change_in_expenses` for each group. Set the argument `.groups` equal to "drop".

```{r seguro-popular-6, exercise = TRUE}
  
```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r seguro-popular-6-hint-1, eval = FALSE}
... %>% 
  summarize(... = mean(...),
            .groups = "drop")
```

### 

If we didn't specify the `.groups` argument, R would raise a warning because our groups would still exist. These unwanted existing groups may distort with future calculations. Therefore, we used `"drop"` to get rid of these groups. 



### Exercise 7

The `treatment` variable is in binary form, taking values 1 and 0. 
For clarification purposes, using `mutate`, change the `treatment` variable. Set every 1 equal to `Treatment Group` and every 0 to `Control Group`. 

### 

Use `ifelse()` for this. Within `ifelse()`, set condition where `treatment == "1"` to `Treatment Group` and `Control Group` in other conditions.

```{r seguro-popular-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r seguro-popular-7-hint-1, eval = FALSE}
 ... %>% 
  mutate(treatment = ifelse(treatment == "...", "...", "Control Group")) 
```

### 

Alternatively, we could have used `if_else()` function from `dplyr` package. The difference between these two functions is that `if_else()` function is somewhat faster than base package function `ifelse()`.


### Exercise 8

Use `%>%` to add `ggplot()`.


```{r seguro-popular-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r seguro-popular-8-hint-1, eval = FALSE}
.. %>% 
  ggplot()
```

### 

We see that `ggplot()` gives us a blank sheet. Now, we should specify aesthetics to change this. 


### Exercise 9

Within `aes` within `ggplot` object from previous exercise, map `education` to x-axis. Map `mean_change_in_expenses` to the y-axis, and `treatment` to the `fill`. 

```{r seguro-popular-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r seguro-popular-9-hint-1, eval = FALSE}
.. %>% 
  ggplot(aes(x = "education",
             y = "mean_change_in_expenses",
             fill = "treatment"))
```

### 

Because we haven't specified the plot type yet, we don't see concrete results. We need to change that. 

### Exercise 10

Add the layer `geom_col()`.

```{r seguro-popular-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r seguro-popular-10-hint-1, eval = FALSE}
.. %>% 
  ggplot(aes(x = "education",
             y = "mean_change_in_expenses",
             fill = "treatment")) + 
  geom_col()
```

### 

When you set the `fill` argument in the `ggplot` equal to a variable, ggplot by default sets a color set.

### Exercise 11

To make the bar charts color of your choice, you can use `scale_fill_manual` function. This function takes on values as a vector. Within this argument, set `values` equal to a vector of two colors: `cornflowerblue` and `darkturquoise`.

```{r seguro-popular-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r seguro-popular-11-hint-1, eval = FALSE}
... +
  scale_fill_manual(values= c("cornflowerblue", "...")) +
  geom_col()
```

### 

If we had more categories of data, we also could have made use of `RColorBrewer` package. This package provides a function named `scale_fill_brewer()`. With this function, you can specify a color palette of your choice. 

### Exercise 12

Within `geom_col()`, set the `position` argument equal to `"dodge"`. Moreover, you can also set the transparency of the bars with the argument `alpha`, where the default value of 1.0 is opaque. For our graph in this section, we set the `alpha` equal to 0.9. 

```{r seguro-popular-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r seguro-popular-12-hint-1, eval = FALSE}
... +
  geom_col(position = "dodge", alpha = 0.9)
```

### 

Alternatively, we could have not specified position argument. In that case, we would see stacked bars, rather than side-by-side bars.

### Exercise 13

We also want to order bars in a descending educational level order.
In our case, we want the order "college", "high school, "secondary school", and "preschool".

### 

We can achieve this by setting `limits` argument of `scale_x_discrete()` equal to order of factors you want. We want the education levels in an increasing order. Therefore, pass in a vector of `preschool`, `secondary`, `high school`, and `college` in this order.

```{r seguro-popular-13, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r seguro-popular-13-hint-1, eval = FALSE}
... +
   scale_x_discrete(limits = ...)
```

### 

We also could have other scaling methods. For instance, if we used `scale_x_reverse()`, our bars would be in reverse order, and x-axis labels would be in decreasing order.

### Exercise 14

It would also be more representative if the y-axis values were displayed with pesos sign, since the observed change in health-related expenses is in pesos in Mexico. 

### 

We can achieve this with `scale_y_continuous()` function. Within this function, set `labels` equal to `dollar_format()`. Within `dollar_format()`, set `suffix` equal to pesos sign, `₱`, and set `prefix` equal to `""`.

```{r seguro-popular-14, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r seguro-popular-14-hint-1, eval = FALSE}
... +
   scale_y_continuous(labels = scales::dollar_format(suffix = "₱", 
                                                     prefix = "")) 
```

### 

`scale_y_continuous` have formatting values to dollar feature. However, it does not have it for other currencies. In those cases, we have to specify the currency sign by using `dollar_format()` argument and pass it to `labels`. 


### Exercise 15

Add `theme_minimal()` to change the style of the graph.

```{r seguro-popular-15, exercise = TRUE}

```

### 

Alternatively, we could have used themes such as `theme_light()` and `theme_dark()`. 



### Exercise 16

To finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, and caption of your choice.

```{r seguro-popular-16, exercise = TRUE}

```

Reminder: This is what your plot should look like.

```{r sps15-answer}
sps_p
```

## Shaming 

### 

The `shaming` data set measures the impact of social pressure on voting. Nearly 350,000 people in Michigan were randomly assigned to 1 of 5 treatment groups before the 2006 Michigan primary. All 5 groups were sent mail before the primary: the "Civic Duty" group had an extra reminder that voting was a civic responsibility, the "Hawthorne" group was told that whether or not they voted would be in the public record, the "Self" group was actually *sent* the public record of whether or not they voted in 2004, and the "Neighbors" group was sent both their voting record and their neighbors' voting record from 2004. 

### 

Let's create the following plot.
Change the exercises. Knowledges
```{r sh_goal}

graph <- 
  ggdotchart(data = shaming_p, 
             x = "treatment",
               y = "pct_voted",
               color = "year",                           # Color by groups
           palette = "jco",            # Custom color palette
           sorting = "descending",                       # Sort value in descending order
           add = "segments",                             # Add segments from y = 0 to dots
           rotate = TRUE,                                # Rotate vertically
           group = "year",                               # Order by groups
           dot.size = 10,                                 # Large dot size
           label = round(shaming_p$pct_voted, digits = 3),       # Add mpg values as dot labels
           font.label = list(color = "white", size = 9, 
                             vjust = 0.5),               # Adjust label parameters
           ggtheme = theme_pubclean()                        # ggplot2 theme
           ) +
    labs(x = "Treatment",
         y = "Voting Percentage",
         title = "Voting Rates Based on Mailings",
         subtitle = "Shaming people makes them more likely to vote",
         fill = "Year",
         caption = "Source: Gerber, Green, and Larimer (2008).") 

graph
```

### Exercise 1

`skim()` the `shaming` data set. Pay close attention to the data type of each variable.

```{r shaming-1, exercise = TRUE}

```

### Exercise 2

`select()` the columns `treatment`, `primary_04`, and `primary_06` of the `shaming` dataset.

```{r shaming-2, exercise = TRUE}

```

```{r shaming-2-hint-1, eval = FALSE}
shaming %>% 
  select(..., ..., ..., ...)
```

### Exercise 3

Use `mutate()` to change the `primary_04` column into binary. Set `primary_04` to an `if_else()` statement. Within `if_else()`, set `condition` to `str_detect()`, with arguments to detect the string "Yes" in `primary_04`. If the condition is true, the function should return `1`, and if false, `0`.

```{r shaming-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-3-hint-1, eval = FALSE}
mutate(primary_04 = if_else(str_detect(primary_04, "..."), 1, 0))
```

### Exercise 4

    
A long data set is the dataset where there are more rows and less columns, every row representing an observation belonging to a category. Use `pivot_longer()` to map the *names* of the `primary_04` and `primary_06` columns to a new column, "year,". Map the  *values* of the two columns to a new column, "voted."


```{r shaming-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-4-hint-1, eval = FALSE}
...  %>%
  pivot_longer(cols = c(..., ...), 
               names_to = ...,
               values_to = ...)
```

### Exercise 5

Great job! Now group the data by `treatment`, `year`, and `voted`. For clarification purposes, use `ielse` function

```{r shaming-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-5-hint-1, eval = FALSE}
Use the group_by() function.
```

### Exercise 6

Use `summarize()` to create the variable `num_voters`, which is set to the function `n()`. Then, set the `.groups` argument equal to `"drop"`.

**Note:** `n()` simply counts the number of rows in each group. 

```{r shaming-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-6-hint-1, eval = FALSE}
... %>% 
  summarize(num_voters = n(), 
            .groups = "...")
```

### Exercise 7

The `voted` column is a bit difficult to understand because the numerical value (0 or 1) is used to represent an idea (the person did or did not vote). Use `mutate()` to set `voted` to an `if_else()` statement. Within `if_else()`, set the condition to where `voted` is equal to 1. Set the result for true to "did_vote," and the result for false to "did_not_vote."


```{r shaming-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-7-hint-1, eval = FALSE}
...%>%
  mutate(voted = if_else(voted == ..., "...", "..."))
```

### Exercise 8

Widening a data set means the process of increasing the number of columns and decreasing the number of rows, which may prove to make the analysis part easier. We should transform `did_vote` and `did_not_vote` into their own columns. Call `pivot_wider()` that gets its column `names_from` `voted` and its `values_from` `num_voters`.


```{r shaming-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-8-hint-1, eval = FALSE}
...  %>%
  pivot_wider(names_from = ..., 
              values_from = ...)
```

### 

In this case, we converted `did_vote` and `did_not_vote` into their own columns because we will calculate the proportion of people who voted. 

### Exercise 9

Use `mutate()` to create a new variable `pct_voted`, which is equal to the number of people who `did_vote` divided by the total number of people.

```{r shaming-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-9-hint-1, eval = FALSE}
Note that the total number of people is equal to (did_vote + did_not_vote). Also, use / to divide. 
```

```{r shaming-9-hint-2, eval = FALSE}
... %>% 
  mutate(... = ... / (did_vote + did_not_vote))
```

### 

Data wrangling process is done!

### Exercise 10

Current version of function we will use to create the graph is not adaptable to continue the pipe. Therefore, your previous pipe has been stored to a variable named `shaming_p`.

### 

For our graph, we will use `ggdotchart` function from `ggpubr` package. 
Within this function, set `data` argument equal to `shaming_p`, `x` argument to `"treatment"`, y argument to `"pct_voted"`, and `color` to `"year"`.

```{r shaming-10, exercise = TRUE}

```

```{r shaming-10-hint-1, eval = FALSE}
ggdotchart(data = ..., 
             x = "...",
               y = "...",
               color = "...",                          
           palette = "jco",            # Custom color palette
           sorting = "descending",                       # Sort value in descending order
           add = "segments",                             # Add segments from y = 0 to dots
           rotate = TRUE,                                # Rotate vertically
           group = "year",                               # Order by groups
           dot.size = 10,                                 # Large dot size
           label = round(shaming_p$pct_voted, digits = 3),       # Add mpg values as dot labels
           font.label = list(color = "white", size = 9, 
                             vjust = 0.5),               # Adjust label parameters
           ggtheme = theme_pubclean()                        # ggplot2 theme
           ) +
```

### 

Although our graph shows the results, it is not appealing. 

### Exercise 11

Copy the code from previous function, and add the `rotate` argument and set it equal to `TRUE`. 
```{r shaming-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-11-hint-1, eval = FALSE}
... +
  ggdotchart(..., 
             rotate = ...)
```

### 

This argument changes the axes, making it easier to visualize the results. 

### Exercise 12

copy the code from previous chunk, and specfiy following arguments within the `ggdotchart()` function: set `palette` argument to `"jco"`, `sorting` argument to `"descending"`, and `add` argument to `"segments"`. 

```{r shaming-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-12-hint-1, eval = FALSE}
ggdotchart(..., 
           palette = "jco", 
           sorting = "descending",
           add = "segments")
```

### 

`sorting` is used to change the order of dots such as "ascending" and "descending". 
`add` argument is used for adding another plot element such as "error bars". When we set `add` equal to "segments", we add segments from the 0 point of the axis that dots are on to dots.  
`palette` is used to specify the color set to use. You could have used other palettes such as "npg" and "lancet".


### Exercise 13

To clarify the differences between close values of dots, we have to display the exact dot values. 
Copy the code from previous chunk and within `ggdotchart()`, set `label` equal to `round`ed `pct_voted` displaying 3 `digits`

```{r shaming-13, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-13-hint-1, eval = FALSE}
ggdotchart(...,
           ... = round(shaming_p$..., digits = 3))
```

### 

Because our values are continuous, if we did not specify the `digits` argument, we would get the results with too many decimal places. 

### Exercise 14

As we see, labels we created in the previous exercise overlaps. Therefore, we need to change `dot.size` and `font.label` to deal with this. 

### 

Copy the code from previous chunk and within the `ggdotchart()`, set `dot.size` equal to 10 and set `font.label` equal to `list` inside which the following arguments are specified as follows: `color` to "white", `size` to 9, and `vjust` to 0.5.

```{r shaming-14, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-14-hint-1, eval = FALSE}
ggodtchart(...,
           font.label = list(color = "...",
                             size = ...,
                             vjust = ...))
```

### 

`vjust` is used to specify the where the labels are centered. `vjust` of 0.5 means that labels are perfectly in the middle of dots. 

### Exercise 15

Copy the code from previous chunk, and within the `ggdotchart()` function, set `ggtheme` argument to `theme_pubclean()`. 

```{r shaming-15, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-15-hint-1, eval = FALSE}
ggodtchart(...,
           ggtheme = theme_pubclean())
```

### 

`ggtheme` argument is used to specify the theme. Alternatively, we could use official themes such as `theme_bw()` and `theme_gray()`. 

### Exercise 16

Copy the code from previous chunk, and to finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, legend labels, and caption of your choice.

Reminder: This is what your plot should look like. 

```{r shaming-16}
graph
```

```{r shaming15, exercise = TRUE}

```

```{r shaming-16-hint-1, eval = FALSE}
... + 
  labs(...)
```

## Last letter of boy names

Library `babynames` contains data about baby names through many years. 

### 

Using this data, let's create the folllowing graph.

```{r baby-lastnames}
boys_p <- babynames %>%
  filter(sex == 'M') %>%
  select(name, year, prop) %>%
  group_by(last_letter = stringr::str_sub(name, -1, -1), year) %>%
  summarize(frequency = sum(prop), .groups = 'drop') %>%
  ggplot(aes(x = year, y = frequency, colour = last_letter)) +
    geom_line() + 
    gghighlight(max(frequency) > 0.15,
                label_key = last_letter) + 
    scale_x_continuous(guide = guide_axis(angle = 70),
                       breaks = c(1880, 1900, 1925, 1950,
                                  1975, 2000, 2017)) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_minimal() + 
    labs(x = NULL,
         y = NULL,
         subtitle = "Names ending with 'N' increased rapidly after 1950",
         title = "Last Letter of Boy Baby Names",
         caption = "Source: http://hadley.github.io/babynames")

boys_p
```

### Exercise 1

`glimpse()` the `babynames` data set. Pay close attention to the data type of each variable.

```{r last-letter-of-boy-n-1, exercise = TRUE}

```

### 

We could have also used `head()` function to have insights about the dataset.

### Exercise 2

To check for NA values, use `any()` function with argument `is.na()`, argument of which should be the dataset. 

```{r last-letter-of-boy-n-2, exercise = TRUE}

```

```{r last-letter-of-boy-n-2-hint-1, eval = FALSE}
any(is.na(...))
```

### 

This function returned `FALSE`, which indicates that there is no NA values. 

### Exercise 3

Because we are trying to analyse only boy names by last letter, `filter()` the data set to only get the data of boy names. 

```{r last-letter-of-boy-n-3, exercise = TRUE}

```

```{r last-letter-of-boy-n-3-hint-1, eval = FALSE}
babynames %>%
  filter(... == 'M')

```

### Exercise 4

Extract only `name`, `year`, and `prop` columns. 

```{r last-letter-of-boy-n-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r last-letter-of-boy-n-4-hint-1, eval = FALSE}
...  %>%
  select(..., ..., ...)
```

### 

Our graph is associated with names of the baby names and their popularity over the years, which are their proportions among all baby boy names given in that period.

### Exercise 5

We want the last letters of boy names. Therefore, create a new variable names `last_letters` that should be equal to last letter of each boy name.To get the last letter of each boy name, we will make use of `str_sub()` function of `stringr` package. 

### 

Pass `name` -1 and -1 arguments to `str_sub()`. Since we will use this variable only for grouping, you can create it within the `group_by()` function. Moreover, because we will also calculate popularities of last letters *by year*, pass `year` into the `group_by()` function as well.

```{r last-letter-of-boy-n-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r last-letter-of-boy-n-5-hint-1, eval = FALSE}
... %>%
  group_by(last_letter = stringr::str_sub(..., ..., -1), ...)
```

### 

`str_sub` takes three arguments: character vector to work on, starting character, and ending character. Because we wanted to extract last letter, or -1 element, of each name, we set the starting and ending characters as -1.


### Exercise 6

Use `summarize()` to create the variable `frequencies` that is equal to `sum()` of proportions of each group. 

Moreover, to avoid warning and since we are done with groups, pass in the `.groups` argument and set it equal to `drop`. 

```{r last-letter-of-boy-n-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r last-letter-of-boy-n-6-hint-1, eval = FALSE}
... %>% 
   summarize(frequency = sum(prop), .groups = 'drop') 
```

### Exercise 7

Now, create a ggplot object, and within `ggplot(aes())`, set x-axis values to `year`, y-axis values to `frequencies`, and colour to `last_letter.` 


```{r last-letter-of-boy-n-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r last-letter-of-boy-n-7-hint-1, eval = FALSE}
...%>%
  ggplot(aes(x = ..., y = ..., colour = ...)) 
```

### Exercise 8

Add `geom_line()` to the ggplot object from previous exercise.


```{r last-letter-of-boy-n-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r last-letter-of-boy-n-8-hint-1, eval = FALSE}
...  +
  geom_line()
```

### 

Alternatively, we could have used other chart types such as scatter chart. However, for our goal, line plot is a great option. 

### Exercise 9

Because we want to analyse last letters that are prevalent, we want to color only last letters that have been above a certainn threshold.

### 

We use 15% as the threshold. Therefore, we only want to color last letters that for certain time have been the last letter of more than 15% of all baby boys that were born during that time. 

### 

We will utilize `gghighlight` library for this purpose. Add `gghighlight()` to the ggplot object. Within this function, set `max()` frequency to be greater than 0.15, and to avoid any warnings, set `label_key` equal to `last_letter`.

```{r last-letter-of-boy-n-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r last-letter-of-boy-n-9-hint-1, eval = FALSE}
...+ 
  gghighlight(max(...) > ...,
                label_key = ...) 
```

### 

We don't think current x-axis ticks are informative enough. Therefore, we should set custom x-axis ticks.

### Exercise 10

Add `scale_x_continuous`, and within this function, set `breaks` argument equal to numerical vector of years. You can choose any years within the data set. We preferred 1880, 1900, 1925, 1950, 1975, 2000, and 2017. 

```{r last-letter-of-boy-n-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r last-letter-of-boy-n-10-hint-1, eval = FALSE}
... +
  scale_x_continuous(breaks = c(1880, 1900, ..., ...,
                                ..., 2000, 2017)) 
```

### 

A rule of thumb, however, is to include ending and beginning years so that whoever sees your plot could understand the range of years that data is collected.

### Exercise 11

Moreover, we want to visualize y-axis as percentage instead of proportion. Therefore, add `scale_y_continuous`, and within this function, set labels argument equal to `scales::percent_format()`.

```{r last-letter-of-boy-n-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r last-letter-of-boy-n-11-hint-1, eval = FALSE}
... +
  scale_y_continuous(... = scales::...()) 
```

### 

`scale` library provides many functions to assist the scaling of axes. For example, `scale_y_binned()` can be used to discretize continuous position data.

### Exercise 12

Add `theme_minimal()`. 

```{r last-letter-of-boy-n-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r last-letter-of-boy-n-12-hint-1, eval = FALSE}
... +
  theme_minimal()
```

### 

We also could have used themes such as `theme_gray()`, `theme_void()`, and`theme_bw()`.

### Exercise 13

Finally, add `caption`, `title`, `subtitle`, and `axis` labels of your choice. Add `labs()` function to the plot. 

Reminder: This is what your plot should look like

```{r last-letter-of-boy-n-13}
boys_p
```

```{r baby-lastnames-13, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r last-letter-of-boy-n-13-hint-1, eval = FALSE}
... +
  labs(...)
```

### 

```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
