---
title: "Rubin Causal Model B"
tutorial:
  id: "rubin-causal-model"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 4 Tutorial Part B"
---


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(gt)

# Key Data 

gt_obj <- tibble(subject = c("Yao", "Emma", "Cassidy", "Tahmid", "Diego"),
       ytreat = c("13", "11", "11", "9", "6"),
       ycontrol = c("9", "11", "10", "12", "4"),
       ydiff = c("? ", "? ", "? ", "? ", "? ")) %>%
   gt() %>%
  cols_label(subject = md("ID"),
                ytreat = md("$$Y_t(u)$$"),
                ycontrol = md("$$Y_c(u)$$"),
                ydiff = md("$$Y_t(u) - Y_c(u)$$")) %>%
  cols_move(columns = vars(ytreat, ycontrol), after = vars(subject)) %>%
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = vars(subject))) %>%
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"), 
            locations = cells_column_labels(columns = vars(subject))) %>%
  cols_align(align = "center", columns = TRUE) %>%
  cols_align(align = "left", columns = vars(subject)) %>%
  fmt_markdown(columns = TRUE) %>%
  tab_spanner(label = "$$\\text{Outcomes}$$", vars(ytreat, ycontrol))  %>%
  tab_spanner(label = "$$\\text{Estimand}$$", vars(ydiff))


knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```


## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```

## Two taus
###

As we do in the book, let's now assume that the causal effect varies by sex. We will now estimate two values for $\tau$: $\tau_F$ and $\tau_M$. (Cassidy and Emma are female; Tahmid, Diego, and Yao are male).

```{r}
tibble(subject = c("Yao", "Emma", "Cassidy", "Tahmid", "Diego"),
       ytreat = c("13", "11", "$$10 + \\tau_F$$", "$$12 + \\tau_M$$", "6"),
       ycontrol = c("$$13 - \\tau_M$$", "$$11 - \\tau_F$$", "10", "12", "$$6 - \\tau_M$$"),
       ydiff = c("$$\\tau_M$$", "$$\\tau_F$$", "$$\\tau_F$$", "$$\\tau_M$$", "$$\\tau_M$$")) %>%
  gt() %>%
  cols_label(subject = md("ID"),
                ytreat = md("$$Y_t(u)$$"),
                ycontrol = md("$$Y_c(u)$$"),
                ydiff = md("$$Y_t(u) - Y_c(u)$$")) %>%
  cols_move(columns = vars(ytreat, ycontrol), after = vars(subject)) %>%
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = vars(subject))) %>%
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"), 
            locations = cells_column_labels(columns = vars(subject))) %>%
  cols_align(align = "center", columns = TRUE) %>%
  cols_align(align = "left", columns = vars(subject)) %>%
  tab_spanner(label = "$$\\text{Outcomes}$$", vars(ytreat, ycontrol)) %>%
  tab_spanner(label = "$$\\text{Estimand}$$", vars(ydiff)) %>%
  fmt_markdown(columns = TRUE)
```

### Exercise 1

How would you calculate $\tau_F$? Use only words and no numbers in your explanation.

```{r 2-tau-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 2

What is the meaning of $\tau_M$? 

```{r 2-tau-ex-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 1))
```

### Exercise 3

What is your new estimate for Diego's $Y_c(u)$? 

```{r 2-tau-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 1))
```

### Exercise 4

Discuss for a sentence or two why an assumption that the causal effect varies by sex leads to a different estimate for Diego's $Y_c(u)$ compared to Cassidy's $Y_c(u)$.

```{r 2-tau-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```


## Average treatment effect
###

We will no longer make any assumptions about $\tau$ for any individual or group. Instead, we are interested in estimating the average treatment effect ($ATE). We have the same data as the previous sections.

```{r}
gt_obj
```

### Exercise 1

Using words only, explain how we estimate the $ATE$.

```{r ate-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

<!-- Average of treated values minus the average of control values is the standard way of estimating the ATE. -->

### Exercise 2

Estimate the $ATE$ based on the data given to you in the above Preceptor Table.

```{r ate-ex-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 1))
```

### Exercise 3

What is Cassidy's outcome under treatment if we assume $\tau$ to be the $ATE$ we calculated above? Note that the answer will just be a number, without any symbol.

```{r ate-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 1))
```

### Exercise 4

Write a paragraph about the many, many reasons why $ATE$ may be a bad estimate of the true average treatment effect.

```{r ate-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 7))
```

### Exercise 5

Write a paragraph about what a heterogeneous treatment effect is and the situations when it is more or less common.

```{r ate-ex-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 7))
```

## Casual vs Predictive Models 
###

### Exercise 1

Write two sentences that explain the difference between a casual model and a predictive model. 

```{r models-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 7))
```


## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```

