---
title: "RStudio and Friends"
tutorial:
  id: "rstudio-and-friends"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Introduction to RStudio, Git, Github, R Markdown and R Pubs."
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(png)
library(grid)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```

<!-- This tutorial is a bit of a mess! -->

<!-- Check out the Distill tutorial. That does things the right way! Make this tutorial more like that. Want to cover all the material which we normally just practice in class. -->

<!-- Structure so that the beginning of this tutorial starts where Getting Started finished. First section called Set Up is confirming that your set up is correct. Example: library(tidyverse). Copy/paste result. Then confirm that they issued the blank_state() function. Then set up Github. DONE -->

<!-- rstudioapi::readRStudioPreference(name = "load_workspace", default = "Code failed.") DONE -->

<!-- Then maybe we do three case studies, each of which walks through all the steps. First one does little besides the basics, because it needs 5 questions to walk through .gitignore. Later case studies can go further because they can ask one question about .gitignore. DONE -->

<!-- At the end we need three or four case studies, each of which starts from nothing and then generates something. Be specific in the name of everything. (Similar to how the Distill tutorial gets the user all the way to a website.) First example is an Rpubs. Set up Github repo. Connect to computer. Create Rmd. Make nice plot. Publish it. Add Rproj and rsconnect to .gitignore and so on. May need some screen shots of R pubs questions. Last question is: Paste the url for your R Pub here. -->

<!-- Suggestion: Anmay suggested that it is very annoying to switch back and forth between the Terminal and the Console. So, instead of checking that things are done by using `ls` and `cat` from the Terminal, use `list.files()` and `readLines() %>% head()` from the Console. This also avoids various Windows annoyances. I'm going with the Terminal thing by popular vote in the discord - AG -->

<!-- Add a question which checks that there are no spaces in the path which leads to where projects are stored. (This might not be solvable if a student's user name has a space and she can't change it. But, at least she should be made aware of how dangerous this is.) This is kind of hard, currently just telling them no - AG-->

<!-- Need a section devoted to R scripts. What are they? How do we use them? When should we use them versus using R markdown? DONE - AG -->

## Checking your setup

### Exercise 1

<!-- AG: I'm doing a check for this part of the tutorial because they should have already done all this if they're even seeing this part. -->

In the [Getting Started section](https://ppbds.github.io/primer/getting-started.html), you should have installed the **remotes**, **tidyverse**, **usethis**, and **primer.tutorials** packages and then loaded them into R by using the `library()` command.

Type `search()` in the Console to see the libraries that you've currently loaded, then copy and paste the result into the tutorial into the space below. There should be strings such as "package:tidyverse" and "package:remotes" in the output, showing that they've been loaded.

```{r setup-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

### Exercise 2

We're also going to be working from a blank slate for every project. This makes it easier to repeat analyses without outside factors affecting your program. You should have already done this as part of the Getting Started section.

Copy and paste (or type) `rstudioapi::readRStudioPreference(name = "load_workspace", default = "Code failed.")` into the console, then copy and paste the command and the result into the space below. It should return FALSE.

```{r setup-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

## Setting up Github

<!-- AG: All of the Github tutorials are basically a repeat of the Github section in Tools. This is kind of weird and could be repetitive if both this tutorial and the Github section are assigned because they already did everything. For now though, I'm just going to put the images and checks in the areas that I can. -->

GitHub is, more or less, a Google Drive for all your R code and projects. In the professional world, what you have on your Github account is more important than what you have on your resume because it has all of your projects. 

###

### Exercise 1

The first step to using GitHub is installing Git. If you haven't installed Git, please download it from [here](https://git-scm.com/downloads). You'll be using Git and the Terminal throughout this course to act as version control for your projects. To make sure you have Git, open RStudio on your computer. Click on the Terminal pane, which is next to the Console pane in the lower left portion of RStudio. Type `git --version`  at the Terminal. 

The Terminal tab will have a dollar sign (`$`) as the prompt. If it doesn't have that and instead uses an arrow (`>`), you may have to check your global options.

```{r terminal_example.png}
file <- system.file("images/terminal_example.png",
                    package = "primer.tutorials")

img <- readPNG(file)
grid.raster(img)
```

Copy/paste the result of the git command into the space below.

```{r git-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

###

### Exercise 2

The next step is creating a GitHub account. To do so, follow the steps [here](https://github.com). Do not proceed with the tutorial until you have created an account.


### Exercise 3

Now that you have your Github account, you need to connect Git and RStudio to your account. Type `git config --global user.name` at the Terminal. It should return your name. If it does not match your name, run `git config --global user.name "Your Name"` in the Terminal, then do the previous command again.

Copy and paste the command and the result into the space below.

```{r git-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```


### Exercise 4

Great. Now type `git config --global user.email` at the Terminal. It should return the same email address you registered with Github. Again, if it does not match your email, run `git config --global user.email "your@email.com"` then run the previous command again.

Copy and paste the command as well as the result into the space below.

```{r git-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```


###

**Note:** You cannot do the following sections of this tutorial if you did not get the correct outputs for the last two exercises.

## GitHub Repositories
###

Github is our Google Drive. Github repositories, or "repos" , are the Google folders where we store our work. Let's make a practice repo!

###

### Exercise 1

To begin, sign into GitHub and go to the homepage. Click the green new button that says "New" on the left. 

```{r new_repo.png}
file <- system.file("images/new_repo.png",
                    package = "primer.tutorials")

img <- readPNG(file)
grid.raster(img)
```


###


### Exercise 2

Name your repository "First_Repo". Then, select the private option for your repo. Also click the box "Add a README file". This is a document where you can add more information.

```{r repo_details.png}
file <- system.file("images/repo_details.png",
                    package = "primer.tutorials")

img <- readPNG(file)
grid.raster(img)
```

<!-- BG: place image here DONE-AG -->

### Exercise 3

The next step will be to download it to your computer — aka “cloning” — and start editing and syncing using Git. To do this, we’ll need to copy the link to the repo and then use it in RStudio. Click on the green button that says "Code". Then copy the link shown. You can use the clipboard button on the right to automatically copy it.

```{r repo_clone.png}
file <- system.file("images/repo_clone.png",
                    package = "primer.tutorials")

img <- readPNG(file)
grid.raster(img)
```

###

## Connecting Github to RStudio

Let's connect your `First_Repo` repository to RStudio.

First off, create a new folder to place your R projects in. Make sure to name it something sensible without spaces or special characters (this makes things easier down the line).


###

<!-- AG: I'm going to add a section about PATs later since I'm working on the Rpubs section right now. This is a personal reminder to include one. -->

### Exercise 1

Open RStudio. Go to File, then New Project.

```{r new_project.png}
file <- system.file("images/new_project.png",
                    package = "primer.tutorials")

img <- readPNG(file)
grid.raster(img)
```

###

### Exercise 2

A window pops up. Select Version Control and then Git.

Paste the link you copied from Github into "Repository URL". Then click "Create Project".

Navigate to the terminal tab and run `git remote -v`. Then copy and paste both the command and the output into the space below. This should be the same link that you just copied from Github.

```{r connect-git-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

###

Congrats! You’ve linked your repo to RStudio! Github will ask you for a location in which to place this and other projects. We recommend creating a folder on your desktop called “projects” and placing all your RStudio projects there. 


## Updating .gitignore

The first thing you should always do when working with a new repo is updating the `.gitignore` file. You can open this file from the bottom right window under the Files tab. This file includes all the files that you don’t want to be uploaded to GitHub. This can come in handy when you are working with big datasets or files with private information. In our case, we want to add the `firstrepo.Rproj` file to the .gitignore list.

###

### Exercise 1

Open the `.gitignore` and add *.Rproj*  The * tells your computer that we want to prevent all files ending in `.Rproj` from being uploaded. We could also just add `First_Repo.Rproj`.

<!-- BG: place image here DONE-AG-->

```{r rproj.png}
file <- system.file("images/rproj.png",
                    package = "primer.tutorials")

img <- readPNG(file)
grid.raster(img)
```

###

### Exercise 2

Save the `.gitignore` file and you should see the `First_Repo.Rproj` file disappear from your Git tab in the top right window. If you don’t see any changes, click on the refresh button in the upper left.

```{r updated_gitignore.png}
file <- system.file("images/updated_gitignore.png",
                    package = "primer.tutorials")

img <- readPNG(file)
grid.raster(img)
```

Go to the Terminal tab and run `cat .gitignore`. This should output all of the lines in your `.gitignore` file. Copy and paste the command as well as the output into the space below.

```{r gitignore-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

###

### Exercise 3

Now that we’ve updated our .gitignore file, we want to upload this new version to GitHub. To do so, first select the `.gitignore` file and then click on the `Commit` button in the Git window.

<!-- BG: place image here DONE-AG -->

```{r commit.png}
file <- system.file("images/commit.png",
                    package = "primer.tutorials")

img <- readPNG(file)
grid.raster(img)
```


###

### Exercise 4

This will open a new window where you will write a commit message. The message is meant to note what you’re adding/changing within the repo. Write the commit message "Updating `.gitignore`", then press `Commit`. 

```{r commit_push.png}
file <- system.file("images/commit_push.png",
                    package = "primer.tutorials")

img <- readPNG(file)
grid.raster(img)
```

Run `git reflog` in the Terminal. This should output the commit that you just did. Copy and paste the command and result into the space below.

```{r gitignore-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

After this, enter `q` to exit the log and return to the terminal.

###

### Exercise 5

Next, press `Push`. This pushes or uploads the files to GitHub! Open up Github and refresh the page to see your commit message at the top of your repo page. 

Run `git reflog` in the Terminal again. Copy and paste the command and result below.

```{r gitignore-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

After this, enter `q` to exit the log and return to the terminal.

###

Congrats! You just uploaded your first file to GitHub.

## RPubs Publishing

<!-- AG: I'm trying to not put that much detail since it's the tutorial. This also marks the beginning of the second "case study". -->

Now it's time to do something cool. Let's go through how we can publish our R projects onto the internet by using RPubs.

You can find information about Rpubs [here](https://rpubs.com/).

### Exercise 1

Create a new GitHub repository titled "First_Rpubs" using the steps above.

###

### Exercise 2

Connect the repository to a new R project titled "First_Rpubs". We'll be using this process multiple times throughout these tutorials, so try to get used to it.

Run `git remote -v` in the Terminal and copy-paste the output below.

```{r rpubs-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

###

### Exercise 3

Edit the `.gitignore` file to include the line `*.Rproj`.

Run `cat .gitignore` and copy-paste the output below.

```{r rpubs-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

###

So far, we've set up the project, but let's actually make some content to put in our RPubs website. We can do this by using R Markdown files.

###

## R Markdown

###

R Markdown files are the primary way that we are going to be coding in R. 

R Markdown is a file format for making dynamic documents with R. An R Markdown document is written in markdown (an easy-to-write plain text format) and contains chunks of embedded R code.

You can learn more about how to write R Markdown files [here](https://rmarkdown.rstudio.com/articles_intro.html).

###

### Exercise 1

First off, let's create an R Markdown file. Go to File -> New File -> R Markdown. Title the file "main.Rmd" and proceed through the creation process.

```{r new_rmd.png}
file <- system.file("images/new_rmd.png",
                    package = "primer.tutorials")

image <- readPNG(file)
grid.raster(image)
```

Run `ls` in the Terminal and copy-paste the result below. The title of your R Markdown file should be shown here.

```{r rmd-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

###

### Exercise 2

The default R Markdown file should look like this:

```{r rmd_example.png}
file <- system.file("images/rmd_example.png",
                    package = "primer.tutorials")

image <- readPNG(file)
grid.raster(image)
```

As you can see, a lot of the text is actually plain text. However, there are code chunks that display R code. Here's an example of an R code chunk.

<!-- AG: How do I show things like this? -->

```
```{r}
plot(cars)
```
```

```{r, echo = FALSE}
plot(cars)
```

This allows you to use R to create graphs then display it in an R Markdown file with plain text descriptions.

<!-- AG: I do not explain knitting very well right here. It needs to be improved or at least explained further in the primer somewhere. -->

Delete everything except the YAML header and the setup code chunk, then add "This is my first R Markdown text." at the bottom. Then press the "Knit" button at the top to display your rendered R Markdown file. This should have your custom text.

Copy and paste the entirety of your file into the space below.

<!-- AG: Are there restrictions with the length of the response? This could be pretty long so... -->

```{r rmd-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

###

### Exercise 3

<!-- AG: This is going to be about Markdown text. -->

Now, we earlier saw how a majority of the text within that file was mainly plain text. however, there was that one piece that wasn't: the R Markdown Header.

Essentially, R Markdown allows for Markdown syntax. That lets you **bold** things, *italicize* them, or make them a header. By doing this, you can format your report easily and make it look nice by just adding in a few extra symbols.

Make the previous text a header by adding `## ` at the beginning, then adding this text under that as a description: `You can do a lot of cool things in R Markdown like **bold** and *italic* text.` Knit the file again and make sure that everything is showing up correctly.

Copy and paste the entire R Markdown file into the space below.

```{r rmd-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

###

### Exercise 4

<!-- AG: This is going to be about code chunks in R. -->

Now let's try to add code chunks into our R Markdown file. Under the text that we added earlier, add a code chunk either by pressing the Add Chunk command at the top of the editor (the green C button with a plus sign next to it) or just typing it out. The code chunk should look like this: 

```
```{r}

```
```

Copy and paste the entire R Markdown file into the space below.

```{r rmd-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

###

<!-- AG: Should this be its own section? There's a lot of stuff here. -->

### Exercise 5

<!-- AG: Is it OK to display the desired output to provide an example? It's probably better to improve my description of where we're typing though. Also, I'm going to be using the checks more often than runs here. -->

Let's try graphing the **trains** data within our code chunk.

First of all, we need to load the libraries that we need. In the setup chunk, load the **tidyverse** library using the `library()` command. Your setup chunk should look like this:

```
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```
```

This lets R know what packages you're going to be using throughout this R Markdown file.

Copy and paste your R Markdown file into the space below.

```{r rmd-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

###

Go back to the code chunk that you manually created. This is where we're going to be coding for the rest of this section.

Let's create the following scatter plot in an R Markdown file:

```{r scat_p}
scat_p <- ggplot(data = iris, 
                 mapping = aes(x = Sepal.Width, 
                               y = Sepal.Length, 
                              color = Species)) +
  geom_point() +
  labs(title = "Measurements for Different Species of Iris",
       subtitle = "Virginica has the longest sepals",
        x = "Sepal.Width",
        y = "Sepal.Length", 
       caption = "Fisher (1936)")
scat_p
```

This is similar to the one constructed in the Visualization A tutorial.

###

### Exercise 6

Within `ggplot()`, set `data` to `iris`. Also, map `Sepal.Width` to the x-axis and `Sepal.Length` to the y-axis. Add the layer `geom_point()`.

Whenever you want to run an R function, just press the "Run" button in the top right corner by the new code chunk button or the green arrow at the far left of your code chunk.

Copy and paste the code within the code chunk you're coding in below.

```{r rmd-6}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

###

### Exercise 7

Now we want to add a `color` aesthetic based on the different species of the iris flower. Set the argument `color` to `Species` inside the `aes()` function.

Copy and paste the code within the code chunk you're coding in below.

```{r rmd-7}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

###

### Exercise 8

Now use `labs()` to add a title and axis labels to the graph. Set the `title` to `"Measurements for Different Species of Iris"` and the `subtitle` to `"Virginica has the longest sepals"`. To label the the axes, set `x` to  `"Sepal.Width"` and `y` to `"Sepal.Length"`. Set the `caption` to `"Fisher (1936)"`.

Copy and paste the code within the code chunk you're coding in below.

```{r rmd-8}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

Reminder: This is what our graph should look like.

```{r show-scat-p}
scat_p
```

###

###

Congratulations on completing the plot. Go ahead and knit the file to see what it looks like.

###

## R Scripts

<!-- AG: I think that this one shouldn't include RDS files since that's chapter 3 stuff. I also don't know what to put here beyond a basic explanation. -->

###

Now, we just created a plot within an R Markdown file, and that's pretty common. However, that's just if we want to create *reports* where we can knit the file to create a thing. What if we want to just make the plot, without any fancy reports or text?

That's when we use **R Scripts**. Think of these like code chunks that make up an entire file. They only use R code and don't have any text, but they're very useful for when you want to create a graph or do an operation without actually displaying it in a rendered R Markdown file. They're often used to create graphs or other objects then store them for later use, reducing the amount of lag that the user experiences.

You can create an R Script by going to File -> New File -> R Script.

```{r rmd_example.png}
file <- system.file("images/new_rscript.png",
                    package = "primer.tutorials")

image <- readPNG(file)
grid.raster(image)
```

###

## Publishing to RPubs

###

Do the thing!

###

## Download answers

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```
