---
title: "Rubin Causal Model"
tutorial:
  id: "rubin-causal-model"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 4 Tutorial"
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(gt)

# Key Data 

gt_obj <- tibble(subject = c("Yao", "Emma", "Cassidy", "Tahmid", "Diego"),
       ytreat = c("13", "11", "11", "9", "6"),
       ycontrol = c("9", "11", "10", "12", "4"),
       ydiff = c("? ", "? ", "? ", "? ", "? ")) %>%
   gt() %>%
  cols_label(subject = md("ID"),
                ytreat = md("$$Y_t(u)$$"),
                ycontrol = md("$$Y_c(u)$$"),
                ydiff = md("$$Y_t(u) - Y_c(u)$$")) %>%
  cols_move(columns = vars(ytreat, ycontrol), after = vars(subject)) %>%
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = vars(subject))) %>%
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"), 
            locations = cells_column_labels(columns = vars(subject))) %>%
  cols_align(align = "center", columns = TRUE) %>%
  cols_align(align = "left", columns = vars(subject)) %>%
  fmt_markdown(columns = TRUE) %>%
  tab_spanner(label = "$$\\text{Outcomes}$$", vars(ytreat, ycontrol))  %>%
  tab_spanner(label = "$$\\text{Estimand}$$", vars(ydiff))


knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```


<!-- After the definitions, we could have some problems which use the actual train data, calculate some causal effects and then plot them. Lots of good staff there. First, assume a single tau. What is it? How sure are you? Then separate taus for men and women. Or some other grouping. Show facetted plot. -->

<!-- One question could take the trains data and make a Preceptor table. Learn a little gt! Would also need some manipulation to create the two potential outcome columns. -->

<!-- More about confounding. Of course, it needs to be in the book. -->


## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```


## Definitions
###

If you have read the chapter, then these questions should be easy.


### Exercise 1

In your own words, give a one sentence definition of a Preceptor Table.

```{r def-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 2

In your own words, give a one sentence definition of a potential outcome.

```{r def-ex-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```


### Exercise 3

In your own words, give a one sentence definition of a causal effect.

```{r def-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 4

Give a paragraph explanation about the Fundamental Problem of Causal Inference. Include an example relating to your own life.

```{r def-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 7))
```

### Exercise 5

In two sentences, explain what what an *ideal* Preceptor Table is, and why it is generally impossible to observe. Use the phrase 'potential outcomes' in your answer.

```{r def-ex-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 5))
```

### Exercise 6

In one sentence, explain the difference between an *actual* Preceptor Table and an *ideal* Preceptor Table.

```{r def-ex-6}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```


## Causal Effect
###

Use the following ideal Preceptor Table to answer some questions about potential estimands we might be interested in.

```{r}
gt_obj
```

 ### Exercises 1 to 3

```{r ce-ex-1}
quiz(

  question("What is the causal effect of the treatment on Yao?",
    answer("1"),
    answer("2"),
    answer("3"),
    answer("4", correct = TRUE),
    answer("5"),
    allow_retry = FALSE),

  question("For how many of the five people is the causal effect of the treatment positive?",
    answer("1"),
    answer("2"),
    answer("3", correct = TRUE),
    answer("4"),
    answer("5"),
    allow_retry = FALSE),

  question("On whom did the treatment have the most negative causal effect?",
    answer("Yao"),
    answer("Emma"),
    answer("Cassidy"),
    answer("Tahmid", correct = TRUE),
    answer("Diego"),
    allow_retry = FALSE)
)
```



## One tau
###

In these exercises, we will assume that the causal effect, $\tau$ (pronounced tau), is the same for everyone.


Use the following actual Preceptor Table to answer questions about a single value for tau.

```{r question-singletau-setup}
gt_obj
```

### Exercise 1

Describe in one sentence/equation how you would estimate Yao's $Y_c(u)$. (Do not use actual numbers, use "tau" in your explanation).

```{r 1-tau-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

### Exercise 2

Describe in one sentence/equation how you would estimate Tahmids's $Y_t(u)$. (Do not use actual numbers, use tau in your explanation).

```{r 1-tau-ex-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

### Exercise 3

Describe in one sentence/equation how you would estimate a single value for tau.

```{r 1-tau-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

### Exercises 4 to 6

```{r 1-tau-ex-4}
quiz(

  question("What is your estimate for a single value for tau?",
    answer("-2"),
    answer("2"),
    answer("-1", correct = TRUE),
    answer("1"),
    answer("1.5"),
    allow_retry = FALSE),

  question("What is your estimate for $Y_c(u)$ for Emma?",
    answer("10"),
    answer("11"),
    answer("12", correct = TRUE),
    answer("13"),
    answer("14"),
    allow_retry = FALSE),

  question("What is your estimate for $Y_t(u)$ for Cassidy?",
    answer("6"),
    answer("5"),
    answer("7"),
    answer("9", correct = TRUE),
    answer("8"),
    allow_retry = FALSE)
)
```



## Two taus
###

As we do in the book, let's now assume that the causal effect varies by sex. We will estimate two values for $\tau$: $\tau_F$ and $\tau_M$. (Cassidy and Emma are female;Tahmid, Diego, and Yao are male).

```{r}
gt_obj
```

### Exercise 1

How would you calculate $\tau_F$? Use only words and no numbers.

```{r 2-tau-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 2

What is $\tau_M$? 

```{r 2-tau-ex-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 1))
```

### Exercise 3

What is your new estimate for Diego's $Y_c(u)$? 

```{r 2-tau-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 1))
```

### Exercise 4

Discuss for a sentence or two why this assumption leads to a different estimate for Diego's $Y_c(u)$. Which one is correct?

```{r 2-tau-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```


## Average treatment effect
###

We will no longer make any assumptions about $\tau$ for any individual or group. Instead, we are interested in estimating the average treatment effect ($ATE). We have the same data as the previous sections.

```{r}
gt_obj
```

### Exercise 1

Describe in words how we estimate the $ATE$.

```{r ate-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

<!-- Average of treated values minus the average of control values is the standard way of estimating the ATE. -->

### Exercise 2

Estimate the $ATE$ based on the data given to you in the above Preceptor Table.

```{r ate-ex-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 1))
```

### Exercise 3

What is Cassidy's outcome under treatment if we assume $\tau$ to be the $ATE$ we calculated above? Note that the answer will just be a number, without any symbol.

```{r ate-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 1))
```

<!-- 10.5 -->

### Exercise 4

Write a paragraph about the many, many reasons why $ATE$ may be a bad estimate of the true average treatment effect.

```{r ate-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 7))
```

### Exercise 5

Write a paragraph about what a heterogeneous treatment effect is and situations when it is more or less common.

```{r ate-ex-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 7))
```

## Casual vs Predictive Models 
###

### Exercise 1

Write two sentences that explain the difference between a casual model and a predictive model. 

```{r models-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 7))
```


## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```

