---
title: "Getting Started"
tutorial:
  id: "getting-started"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "A simple tutorial which explains how to complete tutorials."
---

```{r setup, include=FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

<!-- Should this be more closely connected to the Primer somehow? We are no longer in the Shopping Week world. But there will always be a first class. So maybe reframe this exercise around that?  -->

<!-- Also, should this be longer, checking other installation issues like tidytex?  -->

<!-- What does it get to assume students have already done? Perhaps best would be if it only assumed the existence of R/RStudio and nothing else? (Although, obviously, it requires that primer.tutorials has been installed.) Then, it could walk students through other installations, like primer.data. And also usethis. And then use those packages. Right now, it assumes that a student has been through the shopping week chapter. -->

<!-- Summary: Change the Getting Started chapter to work more closely with this tutorial. Maybe first assignment is to read that Chapter and then do this tutorial? -->


## Introduction
###

Welcome to your first tutorial! The goal of this exercise is to learn how to complete and submit a tutorial. For every chapter, there will be one or more tutorials for you to complete and submit. 

You may complete the tutorials either on your laptop or on a cloud computing platform, if one is provided. Either way, you will download a copy of your work to the Downloads folder on your computer and then submit it.

You always begin a tutorial by filling out your name/email and then clicking the "Submit Answer" button. If you make a mistake, you can click **"Edit Answer"** and try again. 


## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```


## Tutorial Exercises 
###

In each tutorial, there will be a set of exercises for you to complete. You write your answer within the exercise coding area and hit the "Submit Code" button when you are done.

Clicking **"Start Over"** --- look for small letters at the bottom of the left-hand side menu --- deletes all your work for this tutorial and allows you to begin the entire tutorial again.

### Exercise 1

Let's practice some simple math. We've already assigned variables `x` to 5 and `y` to 4. On the line below those assignments, add the two variables by typing `x + y`. Hit **"Run Code"** to see your results. Clicking "**Hint"** gives you a hint about what to type. 

```{r ex-1, exercise = TRUE}
x <- 5
y <- 4
```

```{r ex-1-hint, eval = FALSE}
x <- 5
y <- 4
x + y
```

Once you click **"Run Code"** the answer --- [1] 9 --- should appear below the code you entered. This is the same behavior you would see if you ran this same code in the Console.

### Exercise 2

Let's examine our first dataset. We provide the code to load the `primer.data` library -- this is the package our dataset will come from. Type `trains` in the console and hit **"Run Code"**. This will display some observations from the `trains` dataset. 

```{r ex-2, exercise = TRUE}
library(primer.data)
```

```{r ex-2-hint, eval = FALSE}
trains
```

### Exercise 3

Let's check the version of R running on your computer. You can do this by copy-pasting `version[['version.string']]` into your console and then by hitting **"Run Code"**. You will use the output of this line of code to answer a later question. 

```{r ex-3, exercise = TRUE}

```

```{r ex-3-hint, eval = FALSE}
version[['version.string']]
```

### Exercise 4

Let's confirm that your progress on tutorials is automatically saved between sessions. **Close your tutorial and quit RStudio.** Restart RStudio and then run this tutorial again. Was your progress on the first three questions saved? If so, good! If not, ask for help. 

### Exercise 5

Tutorials can include **multiple choice** questions. If you get the wrong answer for this question, you haven't installed the most recent version of R. 

```{r ex-5}
question("What is the R version running on your computer?",
    answer("4.0.3", correct = TRUE),
    answer("4.0.1"),
    answer("4.0.0"),
    answer("3.9.9"),
    allow_retry = TRUE)
```

### Exercise 6

Tutorials can include written responses. You have already seen one example of that when you provided your name and e-mail address at the start.

Copy and paste everything from `Exercise 6` through the end of this sentence into the answer box below.

```{r ex-6}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 6))
```

### Exercise 7

Be careful about cutting and pasting code from elsewhere into tutorials. In general, *this will not work!* As an example of it not working, copy/paste the first `trains` plot from the [Basic Plots](https://ppbds.github.io/primer/visualization.html#basic-plots) section of *The Primer* and then hit "Run Code."

```{r ex-7, exercise = TRUE}

```


```{r ex-7-hint, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = age, 
                     y = income)) + 
  geom_point()
```

This should report an error like "object 'trains' not found" since we have not loaded the **primer.data** package. This code would work if the first line were `library(primer.data)`. No need to fix it.

## How To Save and Submit Your Completed Tutorial
###

At the end of every tutorial, you will save your work and submit it. We will do this in the next panel, labeled "Submit." Follow the instructions there. After hitting the "Download" button, you will be prompted to save a file named `getting-started.rds`. This file will be saved in the default downloads folder on your laptop, even if you completed the tutorial on a cloud computing platform.

Future tutorials will prompt you with a file name which matches the tutorial you have just completed. The suffix will always be `.rds`, indicating that the file was created by R.


## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```

