---
title: Getting Started
author: David Kane
tutorial:
  id: getting-started
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: A simple tutorial which introduces R/RStudio and explains how to complete
  tutorials.
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

<!-- Add an example which shows the Copy Code button and how to use it. -->

<!-- Add question about set binary. May need to add that to the Primer first.  -->

<!-- Explain what happens when you download the answers twice by mistake. -->

<!-- Plan is that students are told to read the Getting Started chapter before the first class. We want them to, at least, install R/RStudio before the first class. Then, in class, we do this tutorial together. Given that structure, we should make this a bit longer and ensure that all the important things in Getting Started have, in fact, been done. Maybe introduce R Markdown and R projects? Ensure that they create something like ~/Desktop/projects for a home for R projects. What else? This should really be 10 to 15 questions, but I am unsure which are most important. -->

<!-- Maybe there should be some images and even gifs which show how to do some things? -->

## Introduction
### 

Welcome to your first tutorial! Our goal is to learn how to complete a tutorial and then download your answers. This tutorial assumes that you have read and completed the instructions in the [Getting Started](https://ppbds.github.io/primer/getting-started.html) chapter in the *[Primer](https://ppbds.github.io/primer)*. 

You may complete the tutorials either on your laptop or on a cloud computing platform, if one is provided. Either way, you will download a copy of your work to the Downloads folder on your computer.

You always begin a tutorial by filling out your name/email and then clicking the "Submit Answer" button. If you make a mistake, you can click **"Edit Answer"** and try again. 


```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

## Tutorial exercises 
### 

In each tutorial, there will be a set of exercises for you to complete. You write your answer within the exercise code area and hit the "Submit Code" button when you are done.

Clicking **"Start Over"** --- look for small letters at the bottom of the left-hand side menu --- deletes all your work for this tutorial and allows you to begin the entire tutorial again.

### Exercise 1

Let's practice some simple math. We've already assigned 5 to `x` and 4 to `y`. On the line below those two given lines of code, add the two variables by typing `x + y`. Hit **"Run Code"** to see your results. Clicking "**Hint"** gives you a hint about what to type. 

```{r tutorial-exercises-1, exercise = TRUE}
x <- 5
y <- 4

```

```{r tutorial-exercises-1-hint-1, eval = FALSE}
x <- 5
y <- 4
x + y
```

Once you click **"Run Code"**, the answer `[1] 9` should appear below the code you entered. This is the same behavior you would see if you ran this code in the Console tab, which should be located as one of the tabs in the bottom left box of RStudio.

### Exercise 2

Let's examine our first dataset. We provide the code to load the `primer.data` library -- this is the package our dataset will come from. Type `trains` below  `library(primer.data)` and then hit **"Run Code"**. This will display some observations from the `trains` dataset. 

```{r tutorial-exercises-2, exercise = TRUE}
library(primer.data)

```

```{r tutorial-exercises-2-hint-1, eval = FALSE}
library(primer.data)
trains
```

### Exercise 3

Let's check the version of R running on your computer. You can do this by copy-pasting `version[['version.string']]` into the exercise box below and hitting **"Run Code"**. 

```{r tutorial-exercises-3, exercise = TRUE}

```

```{r tutorial-exercises-3-hint-1, eval = FALSE}
version[['version.string']]
```

### 

You should be running R version 4.2.0 or later. If not, reinstall R, following the instructions in [Getting Started](https://ppbds.github.io/primer/getting-started.html).


### Exercise 4

Let's confirm that your progress on tutorials is automatically saved between sessions. **Close your tutorial and quit RStudio.** Restart RStudio and then run this tutorial again. Was your progress on the first three questions saved? If so, good! If not, ask for help. 


### Exercise 5

Tutorials can include written responses. You have already seen one example of that when you provided your name and e-mail address at the start.

Copy and paste everything from `Exercise 5` through the end of this sentence into the answer box below.

```{r tutorial-exercises-5}
question_text(NULL,
    message = "We will sometimes provide an answer to written questions. Other times, like here, we won't. In the former case, we will not allow you to resubmit your answer. Don't stress! Tutorials are pass/fail, so, as long as you make an honest effort, you will do fine.",          
    answer(NULL, 
           correct = TRUE),
    allow_retry = FALSE,
    incorrect = NULL,
    rows = 6)
```

### Exercise 6

Be careful about cutting and pasting code from elsewhere into tutorials. In general, *this will not work!* As an example of it not working, copy/paste the `x + y` operation you just did in Exercise 1.

```{r tutorial-exercises-6, exercise = TRUE}

```

```{r tutorial-exercises-6-hint-1, eval = FALSE}
x + y
```

This should report an error like "object 'x' not found" since we did not define `x` or `y` in this specific exercise box. This code would work if you copied the entire exercise box from exercise 3. No need to fix it.

### Exercise 7

You should already have run the commands `writeRStudioPreference("save_workspace", "never")` and
`writeRStudioPreference("load_workspace", FALSE)` from the R Console. This causes RStudio to neither save nor reload old janky datasets. To confirm that you have done this, run `rstudioapi::readRStudioPreference(name = "load_workspace", default = "Code failed.")` from the RStudio Console (located as a tab in the bottom left section of RStudio). Copy/paste the command and the answer below.

```{r tutorial-exercises-7}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    rows = 3)
```

The response should be FALSE. If it is not, you probably didn't complete the Getting Started chapter in the *Primer*. Please do so now.


### Exercise 8

You should have already run `primer.tutorials::install_only_binary_packages()` as part the *Getting Started* chapter. To confirm that you have done so, type `options("pkgType")` in your RStudio Console and hit return. Copy/paste the command and the return value below. The return value should be "binary".

```{r tutorial-exercises-8}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    rows = 3)
```

## Your answers
### 

At the end of every tutorial, you will save your work and submit it. We will do this in the next panel, labeled "Submit." Follow the instructions there. After hitting the "Download" button, you will be prompted to save a file named `getting-started_answers.rds` or `getting-started_answers.html`, depending on which button you picked. This file will be saved in the default Downloads folder on your laptop, even if you completed the tutorial on a cloud computing platform.

Future tutorials will prompt you with a file name which matches the tutorial you have just completed. The suffix will always be `rds` or `html`, indicating the type of file.


```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
