---
title: "One Parameter: Overview"
author: Ryan Southward
tutorial:
  id: one-parameter-overview
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: Chapter 6 tutorial
---

<!-- Make it more like the chapter, and the chapter more like it. -->

<!-- Need one more section which using the posterior to, for example, create the posterior of number red which will be drawn with a shovel of size 20. Use a posterior to create a new posterior. Turtles all the way down. Could also create the plot of the joint distribution. Try to teach again just what a joint distribution. -->

<!-- Maybe make the shovels_100 have 100 shovel sizes again? We cut that down to make it quicker, but maybe having 100 reps instead of a 1,000 was enough to solve our speed problem. Done -->

<!-- Should we do something with stan_glm? Probably. -->

<!-- RS: Add graph of sampling distributions from shovels of size 25, 50, and 100 but using re factored code!! -->

<!-- RS: Add to 100 shovels graph to overlay theoretical standard deviation using equations. (Call this section standard deviation). -->

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(rstanarm)
library(gt)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

# Key Data

set.seed(10)
urn <- tibble(color = c(rep("red", 400), rep("white", 600))) %>%
  sample_frac() %>% 
  mutate(bead_ID = 1:1000) 

virtual_samples <- tibble(trial_ID = 1:1000) %>% 
  mutate(shovel = map(trial_ID, ~ sample_n(urn, size = 50))) %>% 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) %>% 
  mutate(numb_beads = map_int(shovel, ~ length(.$color))) %>% 
  mutate(prop_red = numb_red / numb_beads)

shovels_100 <- expand_grid(trial_ID = 1:100, shovel_size = 1:100) %>% 
  mutate(shovel = map(shovel_size, ~ slice_sample(urn, n = .))) %>% 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) %>% 
  mutate(prop_red = numb_red / shovel_size) %>% 
  group_by(shovel_size) %>% 
  summarize(st_dev_p_hat = sd(prop_red)) 

#rstanarm stuff:

urn_data <- tibble(red = c(rep(1, 17), rep(0, 33)))

fit_1 <- stan_glm(formula = red ~ 1, 
                  data = tibble(red = c(rep(1, 17), 
                                        rep(0, 33))),
                  family = binomial,
                  refresh = 0,
                  seed = 10) 

ppd_for_p <-posterior_epred(fit_1, 
            newdata = tibble(constant = 1)) %>% 
  as_tibble() %>%
  rename(p = `1`)  

ppd_reds_in_20 <- posterior_predict(fit_1, 
  newdata = tibble(constant = rep(1, 20))) %>% 
  as_tibble() %>% 
  mutate(total = rowSums(across(`1`:`20`))) %>% 
  select(total) 
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

## Virtual sampling

### 

Let's create the following plot that shows sampling variation for 1000 samples from an urn that contains red and white beads.

```{r}
virtual_samples %>% 
  ggplot(aes(x = prop_red)) +
    geom_histogram(binwidth = 0.01, 
                   boundary = 0.4, 
                   color = "white") +
    labs(x = expression(hat(p)), 
         y = "Count",
         title = "Distribution of 1,000 proportions red") 
```

### Exercise 1

Type `urn` below to inspect the urn we will be using in this section.

```{r virtual_sampling-1, exercise = TRUE}
set.seed(10)
urn <- tibble(color = c(rep("red", 400), rep("white", 600))) %>%
  sample_frac() %>% 
  mutate(bead_ID = 1:1000) 
```

### Exercise 2

Good. Recall that the `rep()` function will repeat the first argument a number of times specified by the second argument. We then combine our 400 red beads and 600 white beads using `c()`, and finally "mix" the urn using `sample_frac()`. 

To simulate the process of real-world sampling, let’s take a sample of 50 beads from our virtual urn. To do so, create a `tibble()` that has one variable `trial_ID` that takes on the values 1 to 1000.

```{r virtual_sampling-2, exercise = TRUE}

```

```{r virtual_sampling-2-hint-1, eval = FALSE}
tibble(trial_ID = ...)
```

```{r virtual_sampling-2-hint-2, eval = FALSE}
Use the : operator to create a range of integers.
```

### Exercise 3

Great. Now pipe your results to the function `mutate()` to create the variable `shovel`, which is set to the function `map()`. The first argument to `map()` should be `trial_ID`. The second argument should use `slice_sample()`. Within `slice_sample()`, the first argument should be `urn` (the data we want to sample from), and then set `n` equal to our sample size (we want a sample size of 50). 

```{r virtual_sampling-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual_sampling-3-hint-1, eval = FALSE}
... %>% 
  mutate(shovel = map(..., ~ ...))
```

```{r virtual_sampling-3-hint-2, eval = FALSE}
... %>% 
  mutate(shovel = map(..., ~slice_sample(urn, n = ...)))
```

### Exercise 4

Continue your pipe with `mutate()` to create the variable `numb_red`, which will tells us the number of red beads present. Set `numb_red` to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `sum()` of where the column `color` of `shovel` is equal to red.

```{r virtual_sampling-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual_sampling-4-hint-1, eval = FALSE}
... %>% 
  mutate(... = map_int(..., ~...))
```

```{r virtual_sampling-4-hint-2, eval = FALSE}
... %>% 
  mutate(... = map_int(..., ~ sum(.$color == "red")))
```

### Exercise 5

Use `mutate()` one last time to create the variable `prop_red`, which is our estimate of the proportion of red beads in the urn. Set `prop_red` to `numb_red` divided by the sample size (in this exercise we are using a set sample size of 50).

```{r virtual_sampling-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual_sampling-5-hint-1, eval = FALSE}
... %>% 
   mutate(prop_red = ... / ...)
```

### Exercise 6

Assign your code from above to an object named `virtual_samples`.

```{r virtual_sampling-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual_sampling-6-hint-1, eval = FALSE}
Use the assignment operator <-  to do so.
```

### Exercise 7

Awesome. Now start a pipe with `virtual_samples`. Use `ggplot()`to map `prop_red` to the x-axis. Also, add the layer `geom_histogram()` to create a histogram of our data.

```{r virtual_sampling-7, exercise = TRUE}

```

```{r virtual_sampling-7-hint-1, eval = FALSE}
virtual_samples %>% 
  ggplot(aes(...)) + 
  geom_histogram()
```

### Exercise 8

Within `geom_histrogram()` set `binwidth` to .01, `boundary` to .4, and `color` to "white".

```{r virtual_sampling-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual_sampling-8-hint-1, eval = FALSE}
... +
  geom_histrogram(binwidth = ..., boundary = ..., color = ...)
```

### Exercise 9

To finish, use `labs()` to give your graph the appropriate title and axis labels. See **hint** for guidance to create the symbol $\hat{p}$.


```{r virtual_sampling-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like. 

```{r}
virtual_samples %>% 
  ggplot(aes(x = prop_red)) +
    geom_histogram(binwidth = 0.01, 
                   boundary = 0.4, 
                   color = "white") +
    labs(x = expression(hat(p)), 
         y = "Count",
         title = "Distribution of 1,000 proportions red") 
```

```{r virtual_sampling-9-hint-1, eval = FALSE}
Within labs(), set x to expression(hat(p))
```

<!-- RS: Later on add exercises to build the graph that compares shovel size 25, 50, and 100. In a few days I will edit the primer to remove the bindrows() nonsense and create the graph using expand_grid(). -->

## SE of different shovel sizes

### 

Let's create the following plot that displays different standard deviations of red bead proportions for 100 different shovel sizes.

```{r}
shovel_p <- shovels_100 %>%
 ggplot(aes(x = shovel_size, y = st_dev_p_hat)) +
 geom_point() +
 labs(title = "Sampling Variation",
      subtitle = "Larger samples have less variation",
      x = "Shovel size",
      y = "Standard deviation of the proportion red")

shovel_p
```


### Exercise 1

First, let's use `expand_grid()` to create the foundation of our tibble. Our first column in `expand_grid()` should be called `trial_ID`, and it should be the range of integers between 1 and 1,000. The second column should be called `shovel_size`, and should be the range of integers between 1 and 100.

```{r different_shovel_siz-1, exercise = TRUE}

```

```{r different_shovel_siz-1-hint-1, eval = FALSE}
expand_grid(trial_ID = ..., shovel_size = ...)
```

```{r different_shovel_siz-1-hint-2, eval = FALSE}
Use the : operator to create a range of integers. 
```

### Exercise 2

Use the pipe operator with your code from above. Use `mutate()`, creating a new column called `shovel`. Set `shovel` equal to a `map()` function, passing in `shovel_size` as the first argument, and the `slice_sample()` function as the second argument. Within `slice_sample()`, the first argument should be `urn` (the data we want to sample from), and then set `n` equal to `.` (we want to pass in the `shovel_size` using `map()`).

```{r different_shovel_siz-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r different_shovel_siz-2-hint-1, eval = FALSE}
... %>%
  mutate(shovel = map(..., ~ ... ))
```

```{r different_shovel_siz-2-hint-2, eval = FALSE}
... %>%
  mutate(shovel = map(... , ~ slice_sample(..., n = ...)))
```

### Exercise 3

Continue your pipe with `mutate()` to create the variable `numb_red`, which will tells us the number of red beads present. Set `numb_red` to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `sum()` of where the column `color` of `shovel` is equal to red.

```{r different_shovel_siz-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r different_shovel_siz-3-hint-1, eval = FALSE}
... %>% 
  mutate(... = map_int(..., ~ ...))
```

```{r different_shovel_siz-3-hint-2, eval = FALSE}
... %>% 
  mutate(... = map_int(..., ~ sum(.$color == "red")))
```


### Exercise 4

Continue your pipe from above, using `mutate()` to create one final column called `prop_red` which represents the proportion of red beads in a sample. Set `prop_red` to `numb_red` divided by the `shovel_size` column. 

```{r different_shovel_siz-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r different_shovel_siz-4-hint-1, eval = FALSE}
... %>%
  mutate(prop_red = ... / ...)
```

### Exercise 5

Great. Continue your pipe and use the `group_by()` function to group our tibble by `shovel_size`. 

```{r different_shovel_siz-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r different_shovel_siz-5-hint-1, eval = FALSE}
... %>%
  group_by(...)
```

### Exercise 6

Continue your pipe one last time, and use `summarize()` to create a new column named `st_dev_p_hat` which is equal to the standard deviation of `prop_red`. (`sd()` calculates standard deviation).
 

```{r different_shovel_siz-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r different_shovel_siz-6-hint-1, eval = FALSE}
... %>% 
  summarize(st_dev_p_hat = sd(...))
```

### Exercise 7

Assign your code from above to an object named `shovels_100`.

```{r different_shovel_siz-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r different_shovel_siz-7-hint-1, eval = FALSE}
Use the assignment operator <-  to do so.
```

### Exercise 8

Start a new pipe from `shovels_100`. Use `ggplot()`to map `shovel_size` to the x-axis and `st_dev_p_hat` to the y axis. Also, add the layer `geom_point()` to create a scatterplot.

```{r different_shovel_siz-8, exercise = TRUE}

```

```{r different_shovel_siz-8-hint-1, eval = FALSE}
shovels_100 %>% 
  ggplot(aes(x = ..., y = ...)) + 
  geom_point()
```

### Exercise 9

Now use `labs()` to label the x-axis "Shovel size" and the y-axis 
"Standard deviation of the proportion red". You should also provide a title and subtitle.

```{r different_shovel_siz-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like.

```{r}
shovel_p
```

```{r different-shovel-siz-9-hint-1, eval = FALSE}
... +
   labs(title = "Sampling Variation",
      subtitle = "Larger samples have less variation",
      x = "Shovel size",
      y = "Standard deviation of the proportion red")
```

## Wisdom

### 

Consider the following question: 

> If we get 17 red beads in a random sample of size 50 taken from a mixed urn, what proportion $\rho$ of the beads in the urn are red?

Using *Wisdom*, write a paragraph explaining the relationship between the Preceptor Table and the data we have in our urn problem. 

```{r wisdom-1}
question_text(NULL,
	message = "answer here",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

## Justice

For the next 3 exercises, use the following Population Table for our urn problem:

```{r}
tibble(source = c("Population", "Population", "Population","...",  
                  "Data", "Data", "Data", "...",
                  "Population", "Population", "Population","...", 
                  "Preceptor Table", "Preceptor Table", "Preceptor Table", "...",
                  "Population", "Population", "Population"),
       location = c("Known, specific urn", "Known, specific urn", "Known, specific urn", "...",
                    "Known, specific urn", "Known, specific urn", "Known, specific urn", "...",
                    "Known, specific urn", "Known, specific urn", "Known, specific urn", "...",
                    "Known, specific urn", "Known, specific urn", "Known, specific urn", "...",
                  "Known, specific urn", "Known, specific urn", "Known, specific urn"),
       time = c("Time of sample - 2 years", "Time of sample - 3 weeks", "Time of sample - 10 days", "...",
                "Time of sample", "Time of sample", "Time of sample", "...",
                "Time of sample + 10 days", "Time of sample + 3 weeks", "Time of sample + 2 years", "...",
                "Now", "Now", "Now", "...",
                "Now + 10 days", "Now + 3 weeks", "Now + 2 years"),
       id = c("1", "200", "976", "...",
              "2", "200", "1080", "...",
              "1", "200", "2025", "...",
              "1", "200", "2078", "...",
              "1", "200", "2300"),
       color = c("?", "red", "?", "...",
              "white", "red", "white", "...",
              "?", "red", "?", "...",
              "?", "red", "?", "...",
              "?", "red", "?")) %>%

  # Then, we use the gt function to make it pretty

  gt() %>%
  cols_label(source = md("Source"),
             location = md("Location"),
             time = md("Time"),
             id = md("ID"),
             color = md("Color")) %>%
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(source))) %>%
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"),
            locations = cells_column_labels(columns = c(source))) %>%
  cols_align(align = "center", columns = everything()) %>%
  cols_align(align = "left", columns = c(source)) %>%
  fmt_markdown(columns = everything())
```

### Exercise 1

In 2 sentences, explain why the location column is the same for the Data, Preceptor Table, and Population.  

```{r justice-1}
question_text(NULL,
	message = "The sample from which ",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 2

Now explain, in 2 sentences, why each category has a different time value. 

```{r justice-2}
question_text(NULL,
	message = "answer here",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```


### Exercise 3

Great work! Finally, in 2 sentences, explain why the colors of some beads are known, while the colors for other beads are unknown. 

```{r justice-3}
question_text(NULL,
	message = "answer here",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 4

Good. Now let's turn our attention to the Data Generating Mechanism (DGM). Should our urn problem be modeled by a normal or binomial distribution? Explain your reasoning in 2 sentences.  

```{r justice-4}
question_text(NULL,
	message = "Our urn problem should be modeled by a binomial distribution, because we model the number of times a red bead is selected (successes) over a white bead (failures). Because there are only 2 possibilities to model, the urn problem can be modeled by a binomial distribution",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

## Courage

###

Consider our question:  

> If we get 17 red beads in a random sample of size 50 taken from a mixed urn, what proportion $\rho$ of the beads in the urn are red?

Let's create the posterior probability distribution of $\rho$ using **rstanarm** 

```{r}
ppd_for_p %>%
  ggplot(aes(x = p)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 50) + 
    labs(title = "Posterior Probability Distribution",
         subtitle = "Distribution is centered at .34",
         x = "Proportion p of Red Beads in Urn",
         y = "Probability") + 
  
    scale_x_continuous(labels = scales::number_format()) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()
```

### Exercise 1

Our urn problem can be represented by a binomial model, so we structure our data in a binomial format:  1's represent the number of successes (red beads drawn), and the 0's represent the number of failures (white beads drawn). 

Type `urn_data` below to inspect the data we will be using to create our model. 

```{r courage-1, exercise = TRUE}
library(rstanarm)
urn_data <- tibble(red = c(rep(1, 17), rep(0, 33)))
```

### Exercise 2

Next we'll use `stan_glm()` to create a simple Bayesian model. When using `stan_glm()`, there are always four arguments that should be specified:

* The `data` argument tells `stan_glm()` what data frame to work with. Set `data` to `urn_data`. 
* The `family` argument tells `stan_glm()` what mathematical formula should be used to create our model. Set `family` to `binomial`.
* The `formula` argument tells `stan_glm()` what model is to be fitted. Because we have no predictors, we use the argument `formula = red ~ 1`, which means that we only model the outcome based on the unknown proportion of red beads in the urn. 
* Set `refresh` to 0 in order to suppress the behavior of printing to the console, and `seed` to 10 so that we get the same output every time we run the code.

```{r courage-2, exercise = TRUE}


```

```{r courage-2-hint-1, eval = FALSE}
stan_glm(data = ...,
         family = ...,
         formula = ..., 
         refresh = ...,
         seed = ...)
```

###

You do not need to understand what the printed model means. 

### Exercise 3

Next, we should save our model to be able to work with it in later questions.

Copy your code from the previous exercise, and assign it to an object called `fit_1`.  

```{r courage-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r courage-3-hint-1, eval = FALSE}
Use the assignment operator <-  to do so.
```

### Exercise 4

Let's recreate our posterior distribution using `posterior_epred()`, assigning our code to a variable called `ppd_for_p`. Pass in `fit_1` as the first argument, and then set the argument `newdata` equal to a `tibble()`. Within the `tibble()`, include `constant = 1`. 

```{r courage-4, exercise = TRUE}

```

```{r courage-4-hint-1, eval = FALSE}
ppd_for_p <- posterior_epred(..., 
                 newdata = ...)
```

###

We use `constant = 1` as junk data to make sure our tibble has just 1 row. 

### Exercise 5

Copy your code from above. First pipe `as_tibble()` to your code. Then continue your pipe by renaming the column of the resulting tibble from `1` to `p` by using `p = 1` within `rename()`. **Remember to include backticks around 1**. 

```{r courage-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r courage-5-hint-1, eval = FALSE}
... %>%
  ... %>%
  rename(...)
```

```{r courage-5-hint-2, eval = FALSE}
Within rename, set p equal to `1`. Make sure to include backticks around 1!
```

### Exercise 6

Type `ppd_for_p` below to view 4,000 draws from our posterior. 

```{r courage-6, exercise = TRUE}

```

### Exercise 7

Awesome! Now let's graph the draws from the posterior. First, start a pipe with `ppd_for_p`, and using `ggplot()` map `p` to the x axis. 

```{r courage-7, exercise = TRUE}

```


```{r courage-7-hint-1, eval = FALSE}
ppd_for_p %>%
  ggplot(aes(... = ...))
```


### Exercise 8

Copy your code from the previous question and add the layer `geom_histogram()`. Within `geom_histogram()`, use `aes()` to set `y` equal to `after_stat(count/sum(count))` in order to convert the y-axis to percent values. Also set `bins` to 50. 


```{r courage-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r courage-8-hint-1, eval = FALSE}
... +
  geom_histogram(aes(... = ...),
                 bins = ...)
```

### Exercise 9

Add the layer `scale_x_continuous()` with the argument `labels` set to `scales::number_format()`.
    
```{r courage-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r courage-9-hint-1, eval = FALSE}
... +
  scale_x_continuous(... = ...)
```

### Exercise 10

Great. Now add the layer `scale_y_continuous()` with the argument `labels` set to `scales::percent_format()`.

```{r courage-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r courage-10-hint-1, eval = FALSE}
... +
   scale_y_continuous(... = ...)
```

### Exercise 11

To finish, use `labs()` to give your graph the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`. 

```{r courage-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: Your plot should look something like this:

```{r}
ppd_for_p %>% 
    ggplot(aes(x = p)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 50) + 
    labs(title = "Posterior Probability Distribution",
         subtitle = "Distribution is centered at .34",
         x = "Proportion p of Red Beads in Urn",
         y = "Probability") + 
  
    scale_x_continuous(labels = scales::number_format()) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()
```

## Temperance 

### 

Recall our second question: 

>What is the probability, using the same urn, that we will draw more than 8 red beads if we use a shovel of size 20?

In order to answer our question we need the probability of drawing one red bead from the urn. Because we do not know this probability exactly, we will use our `fit_1` posterior from *Courage*. 

The easiest way to calculate the probability of drawing more than 8 red beads out of 20 is to predict future samples using our new shovel size, and calculate the number of samples that yield more than 8 red beads. 


### Exercise 1

The two functions to predict future outcomes in **rstanarm** are `posterior_epred()` and `posterior_predict()` Let's compare the two to determine which one we should use. 

### 

First let's use `posterior_predict()`. 

```{r}
ppd_reds_in_20 %>% 
  ggplot(aes(x = total)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 50) +
    labs(title = "Posterior Probability Distribution",
         subtitle = "Created with posterior_predict()",
         x = "Number of Red Beads",
         y = "Probability") +  
    scale_x_continuous(labels = scales::number_format(accuracy = 1)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    theme_classic()
```

###

Next `posterior_epred()`.

```{r}
# Create posterior_epred() model
posterior_epred(fit_1, 
  newdata = tibble(constant = rep(1, 20))) %>% 
  as_tibble() %>% 
  mutate(total = rowSums(across(`1`:`20`))) %>% 
  select(total) %>% 
#Graph it
  ggplot(aes(x = total)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 50) +
    labs(title = "Posterior Probability Distribution",
         subtitle = "Created with posterior_epred()",
         x = "Number of red beads",
         y = "Probability") + 
    scale_x_continuous(labels = scales::number_format(accuracy = 1)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    theme_classic()
```

###

In a paragraph, compare the results of using `posterior_predict()` and `posterior_epred()`. Which one do you think we should use to answer our question and why? Refer to *Temperance* in the *Primer* for reference. Make sure to use the terms "individuals" and "population". 

```{r temperance-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    rows = 6)
```

### Exercise 2

The correct answer is that we should use `posterior_predict()`. Let's assign `posterior_predict()` to a variable called `ppd_reds_in_20`. Pass in `fit_1` as the first argument, and then set the argument `newdata` equal to a `tibble()`. Within the `tibble()`, set `constant` to a vector that repeats the number 1, 20 times. Hint: use the function `rep()` to repeat, passing what you want to repeat as the first argument, and the number of times you want to repeat it as the second argument. 

```{r temperance-2, exercise = TRUE}

```

```{r temperance-2-hint-1, eval = FALSE}
ppd_reds_in_20 <- posterior_predict(...,
                  newdata = tibble(constant = ...))
```

```{r temperance-2-hint-2, eval = FALSE}
ppd_reds_in_20 <- posterior_predict(...,
                  newdata = tibble(constant = rep(..., ...)))
```

###

We use pass a tibble with 20 rows into `newdata` because we want to estimate the number of red draws with a shovel size of 20. 

### Exercise 3

Copy your code from above and pipe on `as_tibble()`. Then type `ppd_reds_in_20` to view the results. 

```{r temperance-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-3-hint-1, eval = FALSE}
... %>%
  ...
```

###

Each of our 4,000 rows represent one instance of us predicting a future sample from the urn, and each column represents the color bead in a shovel slot. 

### Exercise 4

Let's find the total number of red beads drawn. Copy your code from above and create a column named `total` using `mutate()`. Set `total` to `rowSums(across(1:20))`, making sure to surround both the 1 and 20 in back ticks! Then continue your pipe and select the `total` column. 

```{r temperance-4, exercise = TRUE }

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-4-hint-1, eval = FALSE}
... %>%
  mutate(total = ...) %>%
  select(...)
```

### Exercise 5

Great work! We have created the posterior probability distribution for sampling  red beads out of urn with a shovel size of 20, which is where the name `ppd_reds_in_20` comes from. 

###

Now let's answer our question: 

*What is the probability, using the same urn, that we will draw more than 8 red beads if we use a shovel of size 20?*

To calculate the probability, we want to know the number of draws **above** 8, and divide by the total number of draws. 

*The number of draws above 8 can be calculated by using the `sum()` function, passing in a Boolean expression to evaluate the number of times `ppd_reds_in_20$total` is greater than 8. 

*The total number of draws can be calculated by using the `length()` function to find the length of the `total` column in `ppd_reds_in_20`


```{r temperance-5, exercise = TRUE}

```

```{r temperance-5-hint-1, eval = FALSE}
... / ...
```

```{r temperance-5-hint-2, eval = FALSE}
sum(ppd_reds_in_20$total > ...) / length(...)
```
### 

If your code doesn't output `r sum(ppd_reds_in_20$total > 8)/length(ppd_reds_in_20$total)`, go back and try again. 

### Exercise 6

The answer to our question is: there is approximately a `r round(100 *sum(ppd_reds_in_20$total > 8)/length(ppd_reds_in_20$total))`% chance that we will draw more than 8 red beads out of a sample size of 20. 

Let's visualize this graphically. To do so, first and add a new column called `above_eight`, and use `ifelse()` to set `above_eight` to `TRUE` if `total > 8`, and `FALSE` if not. 

<!-- RS: Are we concerned about students skipping to this exercise and copying the code? -->

```{r temperance-6, exercise = TRUE}
ppd_reds_in_20 <- posterior_predict(fit_1, 
                  newdata = tibble(constant = rep(1, 20))) %>% 
  as_tibble() %>% 
  mutate(total = rowSums(across(`1`:`20`))) %>% 
  select(total)
```

```{r temperance-6-hint-1, eval = FALSE}
... %>%
  mutate(above_eight = ...)
```

```{r temperance-6-hint-2, eval = FALSE}
... %>%
  mutate(above_eight = ifelse(..., ..., ...))
```

### Exercise 7

Awesome! Now let's graph our distribution. Start a new pipe with `ppd_reds_in_20`, and use `ggplot()` to map `new_reds` to the x axis, and fill to `above_eight`. 

```{r temperance-7, exercise = TRUE}

```

```{r temperance-7-hint-1, eval = FALSE}
prob_dist %>%
  ggplot(aes(x = ..., fill = ...))
```

### Exercise 8

Copy your code from the previous question and add the layer `geom_histogram()`. Within `geom_histogram()`, use `aes()` to set `y` equal to `after_stat(count/sum(count))` in order to convert the y-axis to percent values. Also set `bins` to 50. 

```{r temperance-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-8-hint-1, eval = FALSE}
... +
  geom_histogram(aes(y = ...),
                 bins = ...)
```

### Exercise 9

Now add a layer with `scale_fill_manual()` to change the color of our bars. Inside `scale_fill_manual()`, set `values` to a vector that combines 'grey50' and 'red'.

```{r temperance-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-9-hint-1, eval = FALSE}
... +
  scale_fill_manual(values = c(..., ...))
```

### Exercise 10

Add the layer `scale_x_continuous()` with the argument `labels` set to `scales::number_format()`.

```{r temperance-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-10-hint-1, eval = FALSE}
... +
  scale_x_continuous(labels = ...)
```

### Exercise 11

Great. Now add the layer `scale_y_continuous()` with the argument `labels` set to `scales::percent_format()`.

```{r temperance-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-11-hint-1, eval = FALSE}
... +
   scale_y_continuous(labels = ...)
```

### Exercise 12

To finish, use `labs()` to give your graph the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.

```{r probability_dist-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: Your plot should look something like this:

```{r}
ppd_reds_in_20 <- posterior_predict(fit_1, 
                    newdata = tibble(constant = rep(1, 20))) %>% 
  as_tibble() %>% 
  mutate(total = rowSums(across(`1`:`20`))) %>%
  select(total) %>%
  mutate(above_eight = ifelse(total > 8, TRUE, FALSE))

ppd_reds_in_20   %>% 
  
  # Set fill as above_eight. 
  
  ggplot(aes(x = total, fill = above_eight)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 50) +
  
  # Scale_fill_manual()  is calling grey for the first color and red for the
  # second color. This is going to highlight the portion of the curve that we
  # want to highlight in red.

  scale_fill_manual(values = c('grey50', 'red')) +
    labs(title = "Posterior Probability Distribution",
         subtitle = "Number of red beads in 20-slot shovel",
         x = "Number of Red Beads",
         y = "Probability",
         fill = "More than 8 Red Beads Drawn?") +  
    scale_x_continuous(labels = scales::number_format(accuracy = 1)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    theme_classic()
```

###

We sum the red area under the graph to calculate the cumalitive probability of drawing more than 8 red beads. 

```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
