---
title: "One Parameter: Overview"
tutorial:
  id: one-parameter-overview
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: Chapter 6 tutorial
---

<!-- Make it more like the chapter, and the chapter more like it. -->

<!-- Need one more section which using the posterior to, for example, create the posterior of number red which will be drawn with a shovel of size 20. Use a posterior to create a new posterior. Turtles all the way down. Could also create the plot of the joint distribution. Try to teach again just what a joint distribution. -->

<!-- Maybe make the shovels_100 have 100 shovel sizes again? We cut that down to make it quicker, but maybe having 100 reps instead of a 1,000 was enough to solve our speed problem. -->

<!-- Should we do something with stan_glm? Probably. -->

<!-- RS: Add graph of sampling distributions from shovels of size 25, 50, and 100 but using re factored code!! -->

<!-- RS: Add to 100 shovels graph to overlay theoretical standard deviation using equations. (Call this section standard deviation). -->

<!-- RS: Create box and whisker confidence intervals to demonstrate the connection between confidence intervals and standard error. (Call this section standard error). -->


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

# Key Data

set.seed(10)
urn <- tibble(color = c(rep("red", 400), rep("white", 600))) %>%
  sample_frac() %>% 
  mutate(bead_ID = 1:1000) 

virtual_samples <- tibble(trial_ID = 1:1000) %>% 
  mutate(shovel = map(trial_ID, ~ sample_n(urn, size = 50))) %>% 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) %>% 
  mutate(numb_beads = map_int(shovel, ~ length(.$color))) %>% 
  mutate(prop_red = numb_red / numb_beads)

```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

## Virtual sampling

### 

Let's create the following plot that shows sampling variation for 1000 samples from an urn that contains red and white beads.

```{r}
virtual_samples %>% 
  ggplot(aes(x = prop_red)) +
    geom_histogram(binwidth = 0.01, 
                   boundary = 0.4, 
                   color = "white") +
    labs(x = expression(hat(p)), 
         y = "Count",
         title = "Distribution of 1,000 proportions red") 
```

### Exercise 1

Type `urn` below to inspect the urn we will be using in this section.

```{r virtual_sampling-1, exercise = TRUE}
set.seed(10)
urn <- tibble(color = c(rep("red", 400), rep("white", 600))) %>%
  sample_frac() %>% 
  mutate(bead_ID = 1:1000) 
```

### Exercise 2

Good. Recall that the `rep()` function will repeat the first argument a number of times specified by the second argument. We then combine our 400 red beads and 600 white beads using `c()`, and finally "mix" the urn using `sample_frac()`. 

To simulate the process of real-world sampling, let’s take a sample of 50 beads from our virtual urn. To do so, create a `tibble()` that has one variable `trial_ID` that takes on the values 1 to 1000.

```{r virtual_sampling-2, exercise = TRUE}

```

```{r virtual_sampling-2-hint-1, eval = FALSE}
tibble(trial_ID = ...)
```

```{r virtual_sampling-2-hint-2, eval = FALSE}
Use the : operator to create a range of integers.
```

### Exercise 3

Great. Now pipe your results to the function `mutate()` to create the variable `shovel`, which is set to the function `map()`. The first argument to `map()` should be `trial_ID`. The second argument should use `slice_sample()`. Within `slice_sample()`, the first argument should be `urn` (the data we want to sample from), and then set `n` equal to our sample size (we want a sample size of 50). 

```{r virtual_sampling-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual_sampling-3-hint-1, eval = FALSE}
... %>% 
  mutate(shovel = map(..., ~ ...))
```

```{r virtual_sampling-3-hint-2, eval = FALSE}
... %>% 
  mutate(shovel = map(..., ~slice_sample(urn, n = ...)))
```

### Exercise 4

Continue your pipe with `mutate()` to create the variable `numb_red`, which will tells us the number of red beads present. Set `numb_red` to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `sum()` of where the column `color` of `shovel` is equal to red.

```{r virtual_sampling-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual_sampling-4-hint-1, eval = FALSE}
... %>% 
  mutate(... = map_int(..., ~...))
```

```{r virtual_sampling-4-hint-2, eval = FALSE}
... %>% 
  mutate(... = map_int(..., ~ sum(.$color == "red")))
```

### Exercise 5

Use `mutate()` one last time to create the variable `prop_red`, which is our estimate of the proportion of red beads in the urn. Set `prop_red` to `numb_red` divided by the sample size (in this exercise we are using a set sample size of 50).

```{r virtual_sampling-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual_sampling-5-hint-1, eval = FALSE}
... %>% 
   mutate(prop_red = ... / ...)
```

### Exercise 6

Assign your code from above to an object named `virtual_samples`.

```{r virtual_sampling-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual_sampling-6-hint-1, eval = FALSE}
Use the assignment operator <-  to do so.
```

### Exercise 7

Awesome. Now start a pipe with `virtual_samples`. Use `ggplot()`to map `prop_red` to the x-axis. Also, add the layer `geom_histogram()` to create a histogram of our data.

```{r virtual_sampling-7, exercise = TRUE}

```

```{r virtual_sampling-7-hint-1, eval = FALSE}
virtual_samples %>% 
  ggplot(aes(...)) + 
  geom_histogram()
```

### Exercise 8

Within `geom_histrogram()` set `binwidth` to .01, `boundary` to .4, and `color` to "white".

```{r virtual_sampling-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual_sampling-8-hint-1, eval = FALSE}
... +
  geom_histrogram(binwidth = ..., boundary = ..., color = ...)
```

### Exercise 9

To finish, use `labs()` to give your graph the appropriate title and axis labels. See **hint** for guidance to create the symbol $\hat{p}$.


```{r virtual_sampling-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like. 

```{r}
virtual_samples %>% 
  ggplot(aes(x = prop_red)) +
    geom_histogram(binwidth = 0.01, 
                   boundary = 0.4, 
                   color = "white") +
    labs(x = expression(hat(p)), 
         y = "Count",
         title = "Distribution of 1,000 proportions red") 
```

```{r virtual_sampling-9-hint-1, eval = FALSE}
Within labs(), set x to expression(hat(p))
```

<!-- RS: Later on add exercises to build the graph that compares shovel size 25, 50, and 100. In a few days I will edit the primer to remove the bindrows() nonsense and create the graph using expand_grid(). -->

## SE of different shovel sizes

### 

Let's create the following plot that displays different standard deviations of red bead proportions for 100 different shovel sizes.

```{r}
shovels_100 <- expand_grid(trial_ID = 1:1000, shovel_size = 1:100) %>% 
  mutate(shovel = map(shovel_size, ~ slice_sample(urn, n = .))) %>% 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) %>% 
  mutate(prop_red = numb_red / shovel_size) %>% 
  group_by(shovel_size) %>% 
  summarize(st_dev_p_hat = sd(prop_red))

shovel_p <- shovels_100 %>%
 ggplot(aes(x = shovel_size, y = st_dev_p_hat)) +
 geom_point() +
 labs(title = "Sampling Variation",
      subtitle = "Larger samples have less variation",
      x = "Shovel size",
      y = "Standard deviation of the proportion red")

shovel_p
```


### Exercise 1

First, let's use `expand_grid()` to create the foundation of our tibble. Our first column in `expand_grid()` should be called `trial_ID`, and it should be the range of integers between 1 and 1,000. The second column should be called `shovel_size`, and should be the range of integers between 1 and 100.

```{r different_shovel_siz-1, exercise = TRUE}

```

```{r different_shovel_siz-1-hint-1, eval = FALSE}
expand_grid(trial_ID = ..., shovel_size = ...)
```

```{r different_shovel_siz-1-hint-2, eval = FALSE}
Use the : operator to create a range of integers. 
```

### Exercise 2

Use the pipe operator with your code from above. Use `mutate()`, creating a new column called `shovel`. Set `shovel` equal to a `map()` function, passing in `shovel_size` as the first argument, and the `slice_sample()` function as the second argument. Within `slice_sample()`, the first argument should be `urn` (the data we want to sample from), and then set `n` equal to `.` (we want to pass in the `shovel_size` using `map()`).

```{r different_shovel_siz-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r different_shovel_siz-2-hint-1, eval = FALSE}
... %>%
  mutate(shovel = map(..., ~ ... ))
```

```{r different_shovel_siz-2-hint-2, eval = FALSE}
... %>%
  mutate(shovel = map(... , ~ slice_sample(..., n = ...)))
```

### Exercise 3

Continue your pipe with `mutate()` to create the variable `numb_red`, which will tells us the number of red beads present. Set `numb_red` to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `sum()` of where the column `color` of `shovel` is equal to red.

```{r different_shovel_siz-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r different_shovel_siz-3-hint-1, eval = FALSE}
... %>% 
  mutate(... = map_int(..., ~ ...))
```

```{r different_shovel_siz-3-hint-2, eval = FALSE}
... %>% 
  mutate(... = map_int(..., ~ sum(.$color == "red")))
```


### Exercise 4

Continue your pipe from above, using `mutate()` to create one final column called `prop_red` which represents the proportion of red beads in a sample. Set `prop_red` to `numb_red` divided by the `shovel_size` column. 

```{r different_shovel_siz-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r different_shovel_siz-4-hint-1, eval = FALSE}
... %>%
  mutate(prop_red = ... / ...)
```

### Exercise 5

Great. Continue your pipe and use the `group_by()` function to group our tibble by `shovel_size`. 

```{r different_shovel_siz-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r different_shovel_siz-5-hint-1, eval = FALSE}
... %>%
  group_by(...)
```

### Exercise 6

Continue your pipe one last time, and use `summarize()` to create a new column named `st_dev_p_hat` which is equal to the standard deviation of `prop_red`. (`sd()` calculates standard deviation).
 

```{r different_shovel_siz-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r different_shovel_siz-6-hint-1, eval = FALSE}
... %>% 
  summarize(st_dev_p_hat = sd(...))
```

### Exercise 7

Assign your code from above to an object named `shovels_100`.

```{r different_shovel_siz-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r different_shovel_siz-7-hint-1, eval = FALSE}
Use the assignment operator <-  to do so.
```

### Exercise 8

Start a new pipe from `shovels_100`. Use `ggplot()`to map `shovel_size` to the x-axis and `st_dev_p_hat` to the y axis. Also, add the layer `geom_point()` to create a scatterplot.

```{r different_shovel_siz-8, exercise = TRUE}

```

```{r different_shovel_siz-8-hint-1, eval = FALSE}
shovels_100 %>% 
  ggplot(aes(x = ..., y = ...)) + 
  geom_point()
```

### Exercise 9

Now use `labs()` to label the x-axis "Shovel size" and the y-axis 
"Standard deviation of the proportion red". You should also provide a title and subtitle.

```{r different_shovel_siz-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like.

```{r}
shovel_p
```

```{r different-shovel-siz-9-hint-1, eval = FALSE}
... +
   labs(title = "Sampling Variation",
      subtitle = "Larger samples have less variation",
      x = "Shovel size",
      y = "Standard deviation of the proportion red")
```



```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
