---
title: "Probability: Rolling Dice"
author: Yuhan Wu
tutorial:
  id: probability-rolling-dice
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: "Exploring simple dice rolls under various scenarios."
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(forcats)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

<!-- Everything is sum of two dice. -->

<!-- Key insight: We are in the business of comparing the model --- a data generating mechanism which we create with code --- with the data. In particular, we simulate from 10,000 draws (or create or just draw) from the DGM. Then, we look at the data we have. How well do those match up? If they match up OK, then we are good! If they match up poorly, we need a new DGM.  -->

<!-- Data Generating Mechanism: Five possible states of the world. Or five possible models. Or five possible assumptions. p_6 = c(0.15, 0.20, 0.3, 0.5, 0.75). Do 10,000 draws for each. The DGM is something which is made --- in theory --- before you even look at your data. So, let's make 5 of them. Of course, there are an infinite number of possible DGMs. -->

<!--  Fourth example: shows what happens when we directly compare data (which we know to be false) to simulations from the model (which we define as the truth.) With 10,000 draws, it is obvious that the data demonstrates that the model is false. (Maybe this is combined with second example. Maybe not.) Key is that we are comparing the model with the data and, on the basis of a discrepancy between the two, determining that we need to fix the model. Introduce the concept of model checking. -->

<!-- Forth example, assume that we know that  -->

<!-- Fifth example: Use the Statistical Rethinking chapter 2 example which is similar to, but more complex than, our  -->



## Two dice

### 

The larger the sample size, the more closely your empirical distribution will match the mathematical distribution **if** your mathematical assumptions are correct.

### 

This is the plot we will replicate.

```{r}
# Turn your N column into a factor and then give it the levels in the order you
# want it to be. Maybe use forcats. Consider having the plot by 6 x 1. Or maybe
# stacked but with only 4 N values.


set.seed(2)
dice_p <- tibble(N = c(rep("10", 10), 
                       rep("20", 20),
                       rep("50", 50),
                       rep("100", 100),
                       rep("1000", 1000),
                       rep("10000", 10000))) %>%
  mutate(die_1 = map_dbl(N, ~ sample(c(1:6), size = 1))) %>% 
  mutate(die_2 = map_dbl(N, ~ sample(c(1:6), size = 1))) %>% 
  mutate(result = die_1 + die_2) %>%
  mutate(N = as.factor(N)) %>%
  mutate(N = fct_inseq(N)) %>%
  summarise(N, result) %>%
  ggplot(aes(x = result)) +
  geom_histogram(aes(y = stat(density)),
                 binwidth = 1, 
                 color = "white") +
  labs(title = "Empirical Probability Distribution",
         subtitle = "Sum from rolling two dice, Sample size changes",
         x = "Outcome\nSum of Two Die",
         y = "Probability") +
  facet_wrap(~ N, scales = "free") +
  scale_x_continuous(breaks = seq(2, 12, 1), labels = 2:12) +
  scale_y_continuous(labels= scales::percent_format(accuracy = 1))

dice_p

#dice_p use to show the distribution

```



### Exercise 1

Before we begin, write two sentences explaining what is a *Empirical Probability Distribution*.


```{r rolling-two-dice-1}
question_text(NULL,
	message = "Empirical Probability Distribution is a type of distribution that is completely based on data.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	options = list(nrows = 6))
```

<!-- DK: Make answers good! -->


### Exercise 2

Use the `rep()` to repeat the value "10" three times.

```{r rolling-two-dice-2, exercise = TRUE}

```

```{r rolling-two-dice-2-hint-1, eval = FALSE}
rep(10 , = )
```

### Exercise 3

Create a tibble (with `tibble()`) which has one variable, `x`, with the value of `rep(10, 3)`.

```{r rolling-two-dice-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-3-hint-1, eval = FALSE}
tibble(C = rep(10, 3))
```

### Exercise 4

Modify your answer to the previous exercise by using `c()` so that `x` has a value which includes `rep(10, 3)` and `rep(500, 2)`.

```{r rolling-two-dice-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-4-hint-1, eval = FALSE}
tibble(x = c(rep(10, 3), rep(500, 2)))
```

### 

Your tibble should have 5 rows.

### Exercise 5

Pipe down your result, use `mutate()` to add a new variable "dice" and have "dice" equal to an random values from 1 : 6 using `sample()`, 
```{r rolling-two-dice-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-5-hint-1, eval = FALSE}
... %>%
  mutate(dice = sample(1:6))
```

### 

This should return an error saying dice` must be size 5 or 1, not 6.


### Exercise 6

We only want one value from 1 to 6, so add in another argument `size` and set it equal to 1.
```{r rolling-two-dice-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-6-hint-1, eval = FALSE}
... %>%
  mutate(dice = sample(1:6, size = 1))
```

### 

Notice the column dice will always return the same number, this is what we don't want. In order to fix this we need to use the map_* function.


### Exercise 7

Use `map_dbl()` and set the first argument to C and formula to the `sample()` function we create in the last exercise. 
```{r rolling-two-dice-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-7-hint-1, eval = FALSE}
mutate(dice = map_dbl(C, ~sample(1:6, size = 1)))
```

### 

Now let's move in to the real game.


### Exercise 8

<!-- DK: Split this into 3 or 4 separate questions. And then, ask this question. Firts, question has answer of rep(10, 3). Second question has answer of tibble(N = rep(10, 3)). Third question has answer of tibble(N = c(rep(10, 3), rep(500, 2))). Fourth question has answer  tibble(N = c(rep(10, 3), rep(500, 2))) %>%  mutate(result = ...) -->

Create a `tibble()` with variable `N`, and set N to a list of value representing our sample size, then use `rep()` to repeat the function same numbers of times as the sample size. We want 6 different sample size: 10, 20, 50, 100, 1000, 100000.

```{r rolling-two-dice-8, exercise = TRUE}

```

```{r rolling-two-dice-8-hint-1, eval = FALSE}
tibble(N = c(rep("...", ...), 
             rep("...", ...),
             rep("...", ...),
             rep("...", ...),
             rep("...", ...),
             rep("...", ...)))
```

```{r rolling-two-dice-8-hint-2, eval = FALSE}
tibble(N = c(rep("10", 10), 
             rep("20", 20),
             rep("...", ...),
             rep("...", ...),
             rep("...", ...),
             rep("...", ...)))
```

### Exercise 9

Recall exercise 7, let's create another dice,set it equal to one of the 6 value from (1,2,3,4,5,6) for each rows of N using both map_dbl() and `sample()`, lastly assign it to the name "die_1" using `mutate().`
```{r rolling-two-dice-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-9-hint-1, eval = FALSE}
... %>%
mutate(...= map_dbl(..., ~ ...))
```

```{r rolling-two-dice-9-hint-2, eval = FALSE}
... %>%
mutate(...= map_dbl(N, ~sample(c(...: ...), size = 1)))
```

### Exercise 10

Copy and paste the results from above, and do the exact same thing again but instead now named to value to `die_2`, because we need the results for two dices.

```{r rolling-two-dice-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-10-hint-1, eval = FALSE}
... %>%
mutate(...= map_dbl(N, ~sample(c(...:...), size = 1)))
```

### Exercise 11

Copy and paste the results from above, use the `mutate()` function once again, name the value of the sum of `die_1` and `die_2` to "result"

```{r rolling-two-dice-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-11-hint-1, eval = FALSE}
... %>%
mutate(result = die_1 + die_2)
```

### Exercise 12

Copy and paste the above, then use `summarise()` to include the column "N" and "result" only

```{r rolling-two-dice-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-12-hint-1, eval = FALSE}
summarise(N, ...)
```

### Exercise 13

Copy and paste the code above, use `ggplot()` to graph the Empirical Distribution, set `x = result` within `aes()`, and then add a layer of `geom_histogram()`

```{r rolling-two-dice-13, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-13-hint-1, eval = FALSE}
... %>%
  ggplot(aes(x = ...)) +
    geom_histogram()
```

### Exercise 14

Copy and paste your code from above, recalled `facet_wrap()`, use `facet_wrap()` to separate the graph into six small distribution, don't forget the `~` within `facet_wrap()`.

```{r rolling-two-dice-14, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-14-hint-1, eval = FALSE}
...+
  facet_wrap(...)
```

```{r rolling-two-dice-14-hint-2, eval = FALSE}
... +
  facet_wrap(~ N)
```

Your graph should looks similar to this.
```{r}
tibble(N = c(rep("10", 10), 
             rep("20", 20),
             rep("50", 50),
             rep("100", 100),
             rep("1000", 1000),
             rep("10000", 10000))) %>%
  mutate(die_1 = map_dbl(N, ~ sample(c(1:6), size = 1))) %>% 
  mutate(die_2 = map_dbl(N, ~ sample(c(1:6), size = 1))) %>% 
  mutate(result = die_1 + die_2) %>%
  ggplot(aes(x = result)) +
  geom_histogram() +
  facet_wrap(~ N)
```

### Exercise 15

Now we have a graph, but it's not looking very good, it seems like we only have the 10000 strip fills up with bars. This is because the 10000 scales is so big, that the bars in other strip is blocked. In order for them to shows, within `facet_wrap()`, add another argument `scales`, and set it equal to "free". 
```{r rolling-two-dice-15, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-15-hint-1, eval = FALSE}
...+
facet_wrap( ~ ..., scales = "...")
```

This allows the graph to use it's own scale, instead an universal scales that covered all plots.

Your graph should looks like this
```{r}
set.seed(2)
tibble(N = c(rep("10", 10), 
             rep("20", 20),
             rep("50", 50),
             rep("100", 100),
             rep("1000", 1000),
             rep("10000", 10000))) %>%
  mutate(die_1 = map_dbl(N, ~ sample(c(1:6), size = 1))) %>% 
  mutate(die_2 = map_dbl(N, ~ sample(c(1:6), size = 1))) %>% 
  mutate(result = die_1 + die_2) %>%
  ggplot(aes(x = result)) +
  geom_histogram() +
  facet_wrap(~ N,scales = "free")
```

### Exercise 16

Copy and paste your results from above. Note that you see the red `stat_bin()` using `bins = 30`. Pick better value with `binwidth`. Let's get rid of this by adjusting binwidth for our plots, within `geom_histogram()` set "binwidth" equal to 1, and "color" between bins equal to "white".
```{r rolling-two-dice-16, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-16-hint-1, eval = FALSE}
...+
geom_histogram(binwidth = ..., color = "...") +
  ...
```

```{r rolling-two-dice-16-hint-2,include = FALSE}
... %>%
  ggplot(aes(x = result)) +
  geom_histogram(binwidth = 1, color = "white") +
  facet_wrap(~ N,scales = "free")
```

### 

Notice the panal(gray bar) above each of the sixth distributions, they are out of order, we want to place them like this (10,20,50,100,1000,10000) so that we can see the evolution of the shape of the graph as the sample size increase.

### 

### Exercise 17

Go back to your previous code, right after the `summarize()` and before your `ggplot()`, use `mutate()` and `as.factor()` to reformat N into factor.

```{r rolling-two-dice-17, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-17-hint-1, eval = FALSE}
mutate(N = as.factor(N))
```

### Exercise 18

Pipe down your results, now do the exact same thing again for N, use `mutate()`, but this time we use th new function `fct_inseq()` to replace `as.factor()`, this allow us to ordered the in sequnce from small to large.
```{r rolling-two-dice-18, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-18-hint-1, eval = FALSE}
mutate(N = fct_inseq(N))
```

### Exercise 19

Copy and paste your code from above. Now look at the values on the y-axis, for each one of the sixth plot the value is different, this is because we have different sample size, and it makes sense for each to have different *count*. In order to create an *Empirical Probability distribution*. In order to *normalized* the plot, Within `geom_histogram()`, use `aes()` . Inside `aes()`, we use the argument `y = stat(density)` to set it to put percent on y-axis.
```{r rolling-two-dice-19, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-19-hint-1, eval = FALSE}
... +
    geom_histogram(aes(y = stat(...))) +
  ...
```

```{r include = FALSE}
set.seed(2)
tibble(N = c(rep("10", 10), 
             rep("20", 20),
             rep("50", 50),
             rep("100", 100),
             rep("1000", 1000),
             rep("10000", 10000))) %>%
  mutate(die_1 = map_dbl(N, ~ sample(c(1:6), size = 1))) %>% 
  mutate(die_2 = map_dbl(N, ~ sample(c(1:6), size = 1))) %>% 
  mutate(result = die_1 + die_2) %>%
  mutate(N = as.factor(N)) %>%
  mutate(N = fct_inseq(N)) %>%
  ggplot(aes(x = result)) +
  geom_histogram(aes(y = stat(density)),binwidth = 1, color = "white") +
  facet_wrap(~ N,scales = "free")
```

### Exercise 20

Now use `scale_x_continuous()` so the x-axis has `breaks` to the sequence between 2 and 12 common difference is 1 using `seq()`. Set the `labels` for the breaks as from 2 to 12.

```{r rolling-two-dice-20, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-20-hint-1, eval = FALSE}
... +
scale_x_continuous(breaks = seq(...,..., ...), labels = ...:...) 
```

```{r rolling-two-dice-20-hint-2, eval = FALSE}
... +
  scale_x_continuous(breaks = seq(2, 12, 1), labels = 2:12)
```

### Exercise 21

Now use `scale_y_continuous()` to put the x-axis in percent format. Within `scale_y_continuous()`, set `labels` to `scales::percent_format()`. Within `percent_format()` set `accuracy` to 1.

```{r rolling-two-dice-21, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-21-hint-1, eval = FALSE}
... +
  scale_y_continuous(labels = scales::percent_format(...))
```

### Exercise 22

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels.

```{r rolling-two-dice-22, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>


```{r rolling-two-dice-22-hint-1, eval = FALSE}
... +
  labs(title = "...",subtitle = "...")
```

Reminder: Your plot should look similar to the the one below. 

```{r}
dice_p
```


## Weighted dice
###

If your assumptions about the process which generates the data are false, then it may take a lot of data to see evidence of that.

###


Consider this plot:

```{r}
dicefalse_p <- tibble(m = c(rep("10", 10), 
                           rep("50", 50),
                           rep("10000", 10000))) %>%
  mutate(die_1 = map_dbl(m, ~ sample(1:6, 
                                     size = 1, 
                                     prob = c(0.1, 0.1,  0.1, 
                                              0.1, 0.25, 0.35)))) %>% 
   mutate(die_2 = map_dbl(m, ~ sample(1:6, 
                                      size = 1,
                                      prob = c(0.1, 0.1, 0.1, 
                                               0.1, 0.25, 0.35)))) %>% 
   mutate(result = die_1 + die_2) %>%
   mutate(m = as.factor(m)) %>%
   mutate(m = fct_inseq(m)) %>%
   summarise(m,result) %>%
   ggplot(aes(x=result))+
   geom_histogram( aes(y = stat(density)),
                   binwidth = 1, 
                   color = "white") +
   labs(title = "Empirical Probability Distribution (Bad assumtions)",
         subtitle = "Sum from rolling two dice, sample size change",
         x = "Outcome\nSum of Two Die",
         y = "Probability") +
   facet_wrap(~ m, scales = "free")+
   scale_x_continuous(breaks = seq(2, 12, 1), labels = 2:12) +
   scale_y_continuous(labels = scales::percent_format(accuracy = 1))

dicefalse_p
```

###

Note that this graph looks completly different from the mathematical assumption in the primer that looks like this.

```{r}
tibble(sum = c(rep(c(2, 12), 1), 
               rep(c(3, 11), 2),
               rep(c(4, 10), 3), 
               rep(c(5,  9), 4),
               rep(c(6,  8), 5),
               rep(c(7), 6))) %>% 
  ggplot(aes(x = sum)) +
  geom_histogram(aes(y = after_stat(count/sum(count))), 
                   binwidth = 1, 
                   color = "white") +
  labs(title = "Mathematical Probability Distribution",
         subtitle = "Expectation for the sum from rolling two dice",
         x = "Outcome\nSum of Two Die",
         y = "Probability") +
  scale_x_continuous(breaks = seq(2, 12, 1), labels = 2:12) +
  scale_y_continuous(labels = 
                         scales::percent_format(accuracy = 1)) +
  theme_classic()
```




### Exercise 1

Start a pipe with`tibble()` with variable `m`, and set m to a list of value representing our sample size, then use `rep()` to repeat the function same numbers of times as the sample size. We want 3 different sample size: 10,50, 100000.

```{r rolling-two-dice-bad-assumption-ex-1, exercise = TRUE}

```

```{r rolling-two-dice-bad-assumption-ex-1-hint, eval = FALSE}
tibble(m = c(rep("10", 10), 
             rep("50", 50),
             rep("10000", 10000)))
```

###

### Exercise 2

Use `sample()` to generate integers 1 to 6 for any order.
```{r rolling-two-dice-bad-assumption-ex-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-bad-assumption-ex-2-hint, eval = FALSE}
sample(1:6)
```


###

Remember do use the `:` because it is very convenient for any consecutive integers.

### Exercise 3

Within `sample()`, add another argument `size` set it equal to 1 because we only want to select 1 values from the list of 6 numbers. And click `run` multiple time to see what happened.
```{r rolling-two-dice-bad-assumption-ex-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-bad-assumption-ex-3-hint, eval = FALSE}
sample(1:6, size = 1)
```

###
Now you have run this statement multiple time, yous should realize the number for each one of the six number to appear, should be quite similar, that you haven't realize which number appears the most frequent.


### Exercise 4

Within the `sample()`, add another argument `prob`, let's add in the probability for the number to appear, which is in this case set the value of `prob` to equal to c(0.1,0.1,0.1,0.1,0.25,0.35)`. And run it multiple times.
```{r rolling-two-dice-bad-assumption-ex-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-bad-assumption-ex-4-hint, eval = FALSE}
sample(1:6, size = 1, prob = c(0.1,0.1,0.1,0.1,0.25,0.35))
```

###
This time the result should be easy to see, the 5s and 6s appears alot more frequent than other number, this is what the `prob` argument does, it allow us to manually assign the probability for number to appear during sampling. 

### Exercise 5

Use `mutate()`, set variable `die_1` to the sample() we just created. This should create a tibble with the first column called `m`, and the second column called `die_1`, and all die_1 values is the same.
```{r rolling-two-dice-bad-assumption-ex-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-bad-assumption-ex-5-hint, eval = FALSE}
tibble(m = c(rep("...", ...), 
             rep("...", ...),
             rep("...", ...))) %>%
  mutate(die_1 = sample(1:6, size = 1, prob = c(0.1,0.1,0.1,0.1,0.25,0.35)))
```

###
The reason for why die_1 is all the same, because for the mutate function, it just generate a single value from sample(), and then copy that for every rows in the tibble.

### Exercise 6

Within the same `mutate()` we created use set die_1 to the value of `map_dbl()`, and within `map_dbl()`, set the first argument to m, and formula to `sample()`, don't forget the `~` for `sample()`.
```{r rolling-two-dice-bad-assumption-ex-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-bad-assumption-ex-6-hint, eval = FALSE}
tibble(m = c(rep("10", 10), 
             rep("50", 50),
             rep("10000", 10000))) %>%
  mutate(die_1 = map_dbl(m, ~ sample(1:6, size = 1, prob = c(0.1, 0.1, 0.1, 0.1, 0.25,0.35))))
```

###
Now the number on the column `die_1` should be different, now you can visualize how 6s and 5s appear most frequent due to the probabiility we set for them. 


### Exercise 7

Pipe down your result, now let's create another dice called `die_2`, do the exact same thing again as `die_1`, the only difference should be the variable name.
```{r rolling-two-dice-false-assumption-ex-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-false-assumption-ex-7-hint, eval = FALSE}
... %>%
  mutate(die_2 = map_dbl(m, ~ sample(1:6, size = 1, prob = c(0.1, 0.1, 0.1, 0.1, 0.25,0.35))))
```

### Exercise 8

Use the `mutate()` function once again,set "result" to the value of the sum of `die_1` and `die_2`.

```{r rolling-two-dice-false-assumption-ex-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-false-assumption-ex-8-hint, eval = FALSE}
... %>%
  mutate(result = ... + ... )
```

###
The following will be really similar to the first excercise.

### Exercise 9

Use `summarise()`, only include `m` and `result`.
```{r rolling-two-dice-false-assumption-ex-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-false-assumption-ex-9-hint, eval = FALSE}
... %>%
  summarise(m, result)
```

### Exercise 10

Keep piping down your result, use mutate() and as.factor to change m to a factor.
```{r rolling-two-dice-false-assumption-ex-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-false-assumption-ex-10-hint, eval = FALSE}
... %>%
  mutate(m = as.factor(m))
```


### Exercise 11

Use `mutate()` once again to set m from smallest to largest using `fct_inseq()`.
```{r rolling-two-dice-false-assumption-ex-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-false-assumption-ex-11-hint, eval = FALSE}
... %>%
  mutate(m = fct_inseq(m))
```

###
Let's start plotting!

### Exercise 12

Use `ggplot()` to graph the Empirical Distribution, within `aes()`, set `x = result`, and then add a layer of `geom_histogram()`

```{r rolling-two-dice-false-assumption-ex-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-false-assumption-ex-12-hint, eval = FALSE}
... %>%
  ggplot(aes(...)) +
  geom_histogram()
  
```


### Exercise 13

Recalled `facet_wrap()`, use `facet_wrap()` and set the argument to m to separate the graph into 3 small distribution, don't forget the `~` within `facet_wrap()`.

```{r rolling-two-dice-false-assumption-ex-13, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-false-assumption-ex-13-hint, eval = FALSE}
... +
  facet_wrap( ~ ...)
```

### Exercise 14

Note that you see the red `stat_bin()` using `bins = 30`. Pick better value with `binwidth`. Let's get rid of this by adjusting binwidth for our plots, within `geom_histogram()` set "binwidth" equal to 1, and "color" between bins equal to "white".
```{r rolling-two-dice-false-assumption-ex-14, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-false-assumption-ex-14-hint, eval = FALSE}
... +
geom_histogram(binwidth = ..., color = "...") 
```

###


### Exercise 15

Within `facet_wrap()`, add another argument `scales`, and set it equal to "free". 
```{r rolling-two-dice-false-assumption-ex-15, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-false-assumption-ex-15-hint, eval = FALSE}
... +
facet_wrap(~ ..., scales = "...")

```

###
This allows the graph to scale freely. 

### Exercise 16

Now look at the values on the y-axis, for each one of the sixth plot the value is different, this is because we have different sample size, and it makes sense for each to have different *count*.  In order to *normalized* the plot, Within `geom_histogram()`, use `aes()` . Inside `aes()`, we use the argument `y = stat(density)` to set it to put percent on y-axis.

```{r rolling-two-dice-false-assumption-ex-16, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-false-assumption-ex-16-hint, eval = FALSE}
...+
    geom_histogram(aes(y = stat(...))) +
  ...
```


### Exercise 17

Now use `scale_x_continuous()` so the x-axis has `breaks` to the sequence between 2 and 12 common difference is 1 using `seq()`. Set the `labels` for the breaks as from 2 to 12.
```{r rolling-two-dice-false-assumption-ex-17, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-false-assumption-ex-17-hint, eval = FALSE}
... +
scale_x_continuous(breaks = seq(...,..., ...), labels = ...:...) 
```

### Exercise 18

Now use `scale_y_continuous()` to put the x-axis in percent format. Within `scale_y_continuous()`, set `labels` to `scales::percent_format()`. Within `percent_format()` set `accuracy` to 1.
```{r rolling-two-dice-false-assumption-ex-18, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r rolling-two-dice-false-assumption-ex-18-hint, eval = FALSE}
... +
  scale_y_continuous(labels = scales::percent_format(...))
```

### Exercise 19

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels.
```{r rolling-two-dice-false-assumption-ex-19, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>


```{r rolling-two-dice-false-assumption-ex-19-hint, eval = FALSE}
... +
  labs(title = "...",subtitle = "...")
```

Reminder: Your plot should look similar to the the one below. 

```{r}
dicefalse_p
```

###

With little data, we can't be sure that our model is correct. With lots of data, we can be sure that the model is false.






```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
