---
title: "Visualization C"
tutorial:
  id: "visualization-c"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Chapter 1 Tutorial Part C"
---




```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(ggthemes)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```


## Advanced Plotting - `geom_point()`
###


Let's begin by making this scatterplot using `geom_point()`.

```{r qcores, warning = FALSE}
scat_p <- nhanes %>% 
  filter(survey == 2009) %>% 
  ggplot(mapping= aes(x = height, 
                      y = weight)) + 
  geom_point(alpha = .5) +
  facet_wrap(~ gender) + 
  theme_bw()
 
scat_p
```

### Exercise 1

The dataset used here is `nhanes`. Use `filter()` to narrow our data where `survey` is equal to 2009. 

```{r gp-1, exercise = TRUE}

```

```{r gp-1-hint, eval = FALSE}
nhanes %>% 
  filter(survey == ...)
```

### Exercise 2

Copy and paste your code from above. Extend your code using `%>%` to add `ggplot()`. Map `height` to the x-axis axis and `weight` to the y-axis.

```{r adv-2, exercise = TRUE, warning = FALSE}

```

### Exercise 3

Now set `alpha` to .5 within `geom_point()`.

```{r adv-3, exercise = TRUE, warning = FALSE}

```

### Exercise 4

Use `facet_wrap()` to facet the graph by `~ gender`. Remember you are adding a layer here so use `+`.

```{r adv-4-hint, eval = FALSE}
...  +
  facet_wrap(~ gender)
```

```{r adv-4, exercise = TRUE, warning = FALSE}

```

Reminder: this is what our plot should look like: 

```{r}
scat_p
```

## Advanced Plotting - `geom_jitter()`
###

Let's make this scatterplot using `geom_jitter()`.

```{r}
jitt_p <- ggplot(data = diamonds, 
                 mapping= aes(x = price, 
                              y = carat)) +
  scale_x_log10() +
  geom_jitter(alpha = .5, height = .25, size = 1) +
  geom_smooth(method = "lm") +
  labs(title = "Price By Carat") 

jitt_p
```

### Exercise 1

Use the data set `diamonds`. Put `carat` on the y-axis, and `price` on the x-axis.

```{r gj-1, exercise = TRUE}

```

### Exercise 2

Let's minimize the overplotting. Within `geom_jitter()` set `size` to 1, `height` to 0.25, and `alpha` to 0.2.

```{r gj-2, exercise =  TRUE}

```

### Exercise 3

That looks a bit better! Now, try adding a trendline using `geom_smooth()`, with the argument `method` set to the `lm`. 

```{r gj-3, exercise = TRUE}

```

### Exercise 4

Let's also use the `scale_x_log10` function to make the scale of the plot logarithmic. Also use `labs()` to add the title "Price By Carat".

```{r gj-4-hint, eval = FALSE}
Remembder you are adding a layers here so use +  when adding each function!
```

Reminder: this is what our graph should look like:

```{r}
jitt_p
```

```{r gj-4, exercise = TRUE}

```

## Advanced Plotting - `geom_histogram()` 
###

Let's create the following histogram.

```{r}
hist_p <- mpg %>% 
  ggplot(aes(x = hwy, 
            color = class)) +
  geom_histogram(aes(y = after_stat(count/sum(count))),
                                    fill = "white",
                                    bins = 5, 
                                    position = "dodge") +
  labs(title = "Highway Fuel Economy by Car Type",
       x = "Miles Per Gallon",
       y = "Percent of Car Models")

hist_p
```

### Exercise 1

The dataset used for this histogram is `mpg`. Map `hwy` to the x-axis and map `class` to the `color` argument.

```{r gh-1, exercise = TRUE}

```

```{r gh-1-hint, eval = FALSE}
Recall the color argument goes inside `aes()`.
```

### Exercise 2

Within `geom_histogram()`, use `after_stat()` with the argument `count/sum(count)` to put percents on the y-axis.

```{r gh-2, exercise = TRUE}

```

```{r gh-2-hint, eval = FALSE}
... + 
  geom_histogram(aes(y = after_stat(count/sum(count)))
```

### Exercise 3

Set the number of `bins` to 5, `postion` to "dodge, and `fill` to "white".

```{r gh-3, exercise = TRUE}

```

```{r gh-3-hint, eval = FALSE}
All the arguments go inside `geom_histogram()`
```


### Exercise 4

Title your graph "Highway Fuel Economy by Car Type" and label your x-axis "Miles Per Gallon" and the y-axis "Percent of Car Models".

```{r gh-4-hint, eval = FALSE}

```

Reminder: this is what our graph should look like:

```{r}
hist_p
```

```{r gh-4, exercise = TRUE}

```

## Advanced Plotting - `geom_bar()`
###

Let's make the following dodged bar plot using `geom_bar`.

```{r}
bar_p <- ggplot(data = trains, 
                aes(x = att_start, 
                    fill = party)) +
  geom_bar() +
  facet_wrap(~liberal) + 
  theme_classic()

bar_p
```

### Exercise 1

Let's make a barplot using the `trains` tibble. Map our x variable to `att_start`.

```{r gb-1, exercise = TRUE}

```

### Exercise 2

Great. Now, map `fill` to `party`.

```{r gb-2, exercise = TRUE}

```

```{r gb-2-hint, eval = FALSE}
Recall that fill is an aesthetic!
```

### Exercise 3

Good work. Now, let's use `facet_wrap()` to divide our graph by the `liberal` variable.

```{r gb-3-hint, eval = FALSE}
... + 
  facet_wrap( ~ ...)
```

```{r gb-3, exercise = TRUE}

```

### Exercise 4

Let's add a theme to our graph. Add the layer `theme_classic()` to your code. 

```{r gd-4-hint, eval = FALSE}
Recall that when you add a theme to a plot, you are adding a layer! Use the + operator!
```

```{r gd-4, exercise = TRUE}

```

Reminder: this is what our plot should look like: 

```{r}
bar_p
```



## Advanced Plotting - `geom_smooth()`
###


Let's create this graph using `geom_smooth()`.

```{r}
smooth_p <- ggplot(data = trains, 
       mapping = aes(x =att_start, 
                     y = att_end, 
                     color = treatment)) +
  geom_smooth(method = "lm", 
              se = FALSE)

smooth_p
```

### Exercise 1

Use the data set `trains`. Put `att_start` on the x axis and `att_end` on the y axis. Use `geom_smooth()` as the only geom, do not use it with `geom_point()`. 

```{r gs-1, exercise = TRUE}

```

```{r gs-1-hint, eval = FALSE}
ggplot(data = ..., 
       mapping = aes(x = ..., 
                     y = ...)) +
  geom_smooth()
```

### Exercise 2

Within `geom_smooth()`, set `method` to`"lm"` and `se` to FALSE.

```{r gs-2, exercise = TRUE}

```

### Exercise 3

Now set `color` to treatment.

```{r gs-3-hint, eval = FALSE}
Recall color is an aesthetic.
```

```{r gs-3, exercise = TRUE}

```

Reminder: this is what our plot should look like: 

```{r}
smooth_p
```



## Advanced Plotting - `geom_density()`
###

Let's create the following density plot.

```{r}
dens_p <- ggplot(diamonds, aes(depth, 
                               fill = cut, 
                               color = cut)) +
  geom_density(alpha = 0.1) +
  xlim(55, 70)

dens_p
```

### Exercise 1

Use the `diamonds` tibble. Put `depth` on the x-axis.

```{r gd-1, exercise = TRUE}

```

### Exercise 2

Also set the `fill`  and `color` arguments to `cut`. 

```{r gd-2, exercise = TRUE}

```

### Exercise 3

Set the `alpha` argument to .1 within `geom_density()` 

```{r gd-3, exercise = TRUE}

```

### Exercise 4

Let's also add an `xlim()` function, to set the range of x values on our plot from 55 to 70.




```{r gd-new--4, exercise = TRUE}

```

```{r gd-new-4-hint, eval = FALSE}
Make sure you put a comma between 55 and 70 within the xlim() function.
```

Reminder: This is what our plot should look like:

```{r}
dens_p
```


## Submit

Congrats on finishing your first Gov 50 tutorial! You're on your way to being a master in data visualization and wrangling! :)

```{r context="setup"}
submission_ui
```

```{r context="server"}
submission_server()
```
