---
title: "Visualization C"
tutorial:
  id: "visualization-c"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Chapter 1 Tutorial Part C"
---




```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(ggthemes)
library(skimr)
library(plotly)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

# NL: To do the plotly question, you need to create a myplot_p object here so that students have access to it when they run plotly(myplot_p).

```

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```

<!-- NL: Change everything you hate! You own this tutorial. Delete entire sections of you don't like them! Make this more like wrangling B. Put in more ### as continue buttons. Drop some knowledge at the end of each exercise.  Always start by looking at the data with just print the data name (trains) or glimpse() or summary() or skim(). Always use select() for each question to keep just the variables you need. Nothing wrong with an arbitrary filter() in the pipe. Nothing wrong with using a simple mutate() to create a new variable, like change height to inches.  

Remove "Advanced Plotting in each exercise name."

Make longer. 100 or so questions total?

Example: nes %>% 
          count(income) %>%  
          ggplot(aes(x = income, y = n)) + 
            geom_col()
            
        nes %>% 
          group_by(income) %>% 
          summarize(n_inc = n()) %>%  
          ggplot(aes(x = income, y = n_inc)) + 
            geom_col()    
            
         nes %>%  
          ggplot(aes(x = income)) + 
            geom_bar()  

Last question should use plotly. Why not!            
-->

## `geom_point()`
###

Let's begin by making this scatterplot using `geom_point()`.

```{r make gp-1}
point_p <- nhanes %>% 
  drop_na(height, weight) %>% 
  filter(survey == 2009) %>% 
  ggplot(mapping= aes(x = weight, 
                      y = height)) + 
  geom_point(alpha = .5) +
  geom_smooth(method = "loess", 
              formula = y ~ x, 
              se = TRUE) +
  facet_wrap(~ gender) + 
  theme_bw() +
  labs(title = "The Relationship Between Height and Weight By Gender",
       subtitle = "Weight has a greater positive correlation with height for men \n of common heights than for women of common heights",
       x = "Weight",
       y = "Height",
       caption = "Source: National Center for Health Statistics")
 
point_p
```

### Exercise 1

Use `skim()` to look at  `nhanes`. 

```{r gp-1, exercise = TRUE}

```

```{r gp-1-hint-1, eval = FALSE}
skim(nhanes)
```

### Exercise 2 

Start a new pipe with `nhanes`. Use `drop_na() `to remove any rows with any missing values for `height` or for `weight`. 

```{r gp-2, exercise = TRUE}

```

```{r gp-2-hint-2, eval = FALSE}
nhanes %>% 
  drop_na(..., ...)
```

### Exercise 3

Copy/paste your code from above. Extend your pipe using `%>%` and ue `filter()` to keep rows where `survey` is equal to 2009. 

```{r gp-3, exercise = TRUE}

```

```{r gp-3-hint, eval = FALSE}
nhanes %>% 
  drop_na(height, weight) %>% 
  filter(survey == ...)
```

### Exercise 4 

Continue your pipe using `%>%` and select the columns `height`, `weight`, and `gender`. 

```{r gp-4, exercise = TRUE}

```

```{r gp-4-hint, eval = FALSE}
nhanes %>% 
  drop_na(height, weight) %>% 
  filter(survey == ...) %>% 
  select(height, weight)
```

### Exercise 5

Extend your pipe using `%>%` and add `ggplot()`. Map `weight` to the x-axis and `height` to the y-axis. Also, add the layer `geom_point()`.

```{r gp-5, exercise = TRUE}

```

```{r gp-5-hint, eval = FALSE}
nhanes %>% 
  drop_na(height, weight) %>% 
  filter(survey == 2009) %>% 
  ggplot(mapping = aes(x = ..., 
                       y = ... )) + 
    geom_point()
```

### Exercise 6

Now set the argument `alpha` to .5 within `geom_point()`.

```{r gp-6, exercise = TRUE}

```

```{r gp-6-hint, eval = FALSE}
...  %>%  
  ggplot(mapping = aes(x = ..., y = ... )) +
  geom_point(alpha = ...)
```

### Exercise 7 

Use `geom_smooth` to add a trendline. Set the argument `method` to `"loess"`, `formula` to `y ~ x`, and `se` to `TRUE`. 

```{r gp-7, exercise = TRUE}

```

```{r gp-7-hint, eval = FALSE}
...  %>%  
  ggplot(mapping = aes(x = ..., y = ... )) +
  geom_point(alpha = ...)
```

###

The shading created by `se` is a measurement of error. Observe how it increases at outlying heights for which we have few data points. 

### Exercise 8

Use `facet_wrap()` to facet the graph by `gender`. Remember to place a `~` before `gender`.

```{r gp-8, exercise = TRUE}

```

```{r gp-8-hint-1, eval = FALSE}
You are adding a layer here so use +
```

```{r gp-8-hint-2, eval = FALSE}
...  +
  ggplot(mapping = aes(x = ..., y = ... )) +
  geom_point(alpha = ...) +
  facet_wrap(~ gender)
```

### Exercise 9

Change the feel of the graph by adding the layer `theme_bw()`.

```{r gp-9, exercise = TRUE}

```

```{r gp-9-hint-1, eval = FALSE}
You are adding a layer here so use +
```

```{r gp-9-hint-2, eval = FALSE}
...  +
  ggplot(mapping = aes(x = ..., y = ... )) +
  geom_point(alpha = ...) +
  facet_wrap(~ gender) +
  theme_bw()
```

### Exercise 10

To finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, and caption of your choosing. For an overlong subtitle like the one we have in the example, add `\n` within the quoted string at the place you want to start a new line.

```{r gp-10, exercise = TRUE}

```

```{r gp-10-hint, eval = FALSE}
... +
  labs(title = "...",
       subtitle = "... \n ...",
       x = "...",
       y = "...",
       caption = "...")
```

Reminder: This is what your plot should look like.

```{r show gp-1}
point_p
```

## `geom_point()` with size 
###

Let's make this scatterplot using `geom_point()`.

```{r make-gp2}
point_p2 <- ggplot(data = diamonds, 
                 mapping = aes(x = price, 
                              y = carat,
                              color = clarity)) +
  geom_point(size = .25, alpha = .5) +
  scale_x_log10() +
  labs(title = "Diamond Carat and Price",
       subtitle = "3+ carat diamonds are rare and of low quality",
       x = "Price",
       y =  "Carat", 
       color = "Clarity",
       caption = "Source: R datasets") 

point_p2
```

### Exercise 1

Type `diamonds` to view the data set. 

```{r gp2-1, exercise = TRUE}

```

### Exercise 2

Start a pipe with `diamonds`. Run `summarize()` and create a summary tibble with two columns: the first, for the `mean()` of `carat`; the second, for the `median()` of the same column. 

```{r gp2-2, exercise =  TRUE}

```

```{r gp2-2-hint, eval = FALSE}
diamonds %>% 
  summarize(mean(...), median(...))
```

### 

Remember that `summarize()` does not require you to name new columns. 

### Exercise 3

Start a new pipe with `diamonds`. Select the columns `carat`, `price`, and `clarity`. 

```{r gp2-3, exercise =  TRUE}

```

```{r gp2-3-hint, eval = FALSE}
diamonds %>% 
  select(carat, price, clarity)
```

### Exercise 4

Continue your pipe and add `ggplot()`. Map `price` to the x-axis, `carat` to the y-axis, and `clarity` to `color`. Then, add the layer `geom_jitter()`.

```{r gp2-4, exercise = TRUE}

```

```{r gp2-4-hint-1, eval = FALSE}
geom_point() is a layer so use + to add it
```

```{r gp2-4-hint-2, eval = FALSE}
... %>% 
  ggplot(mapping = aes(x = ..., y = ..., color = ...)) +
  geom_point()
```

### 

We use color when we are dealing with points or lines. We use fill when we are dealing with other objects. 

### Exercise 5

Let's minimize the overplotting. First, within `geom_point()` set `alpha` to 0.5.

```{r gp2-5, exercise =  TRUE}

```

```{r gp2-5-hint, eval = FALSE}
... +
  geom_point(alpha = ...)
```

### Exercise 6

Now, within `geom_point()` set `size` to .25.

```{r gp2-6, exercise =  TRUE}

```

```{r gp2-6-hint, eval = FALSE}
... +
  geom_point(alpha = 0.5, size = ...)
```

###

Size controls the diameter of the points. The default diameter size is 1. 

### Exercise 7

Use the layer `scale_x_log10()` function to make the scale of the plot logarithmic.

```{r gp2-7, exercise = TRUE}

```

```{r gp2-7-hint-1, eval = FALSE}
Remembder you are adding a layers here so use + 
```

```{r gp2-7-hint-2, eval = FALSE}
... + 
  scale_x_log10()
```

### Exercise 8

To finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, legend label, and caption of your choosing. To set the legend label, use the argument `color`. 

```{r gp2-8, exercise = TRUE}

```

```{r gp2-8-hint, eval = FALSE}
... +
  labs(..., 
       color = "Clarity",
       ...)
```

Reminder: This is what your plot should look like.

```{r}
point_p2
```


## `geom_histogram()` 
###

Let's create the following histogram.

```{r}
hist_p <-mpg %>% 
  mutate(year = as.character(year)) %>% 
  ggplot(aes(cty, fill = year)) +
  geom_histogram(bins = 6,
                 color = "black",
                 position = "dodge") +
  labs(title = "Histogram of City Fuel Efficiency in 1999 and 2008 Models", 
       subtitle = "1999 had more models of high city fuel efficiency", 
       x = "City MPG", 
       y = "Count",
       fill = "Year",
       caption = "Source: EPA") 
hist_p
```

### Exercise 1

Use `glimpse` to look at the `mpg` data set. 

```{r gh-1, exercise = TRUE}

```

### Exercise 2

Use the `$` to extract the column `year` as a vector.

```{r gh-2, exercise = TRUE}

```

###

Notice that there are only two different years, 1999 and 2008.

### Exercise 3

Start a new pipe with `mpg`. Use `mutate()` and the function `as.character()` to change the `year` column from a numeric variable to a character variable.

```{r gh-3, exercise = TRUE}

```

```{r gh-3-hint, eval = FALSE}
...  %>% 
  mutate(year = as.character(year))
```

###

We make this change so that we can use year as a fill color when we plot. 

### Exercise 4

Select the columns `year` and `cty`.

```{r gh-4, exercise = TRUE}

```

```{r gh-4-hint, eval = FALSE}
...  %>% 
  select(..., ...)
```

### Exercise 5

Continue your pipe and add `ggplot()`. Map `cty` to the x-axis and `year`  to `fill`. Then, add the layer `geom_histogram()`.

```{r gh-5, exercise = TRUE}

```

```{r gh-5-hint-1, eval = FALSE}
geom_histogram() is a layer so use + to add it
```

```{r gh-5-hint-2, eval = FALSE}
... %>% 
  ggplot(mapping = aes(x = ..., fill = ...)) +
  geom_histogram()
```

### Exercise 6

Within `geom_histogram()` set the number of `bins` to 6.

```{r gh-6, exercise = TRUE}

```

```{r gh-6-hint, eval = FALSE}
... +
  geom_histogram(bins = ...)
```

### Exercise 7

Within `geom_histogram()` set the argument `position` to `"dodge"`. 

```{r gh-7, exercise = TRUE}

```

```{r gh-7-hint, eval = FALSE}
... +
  geom_histogram(bins = 6, position = "...")
```

### Exercise 8

Within `geom_histogram()` set  `color` to `"black"`. 

```{r gh-8, exercise = TRUE}

```

```{r gh-8-hint, eval = FALSE}
... +
  geom_histogram(bins = 6, position = "dodge", color = "black")
```

### Exercise 9

To finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, legend labels, and caption of your choosing. To change the legend labels use the argument `fill`. 

```{r gh-9, exercise = TRUE}

```

```{r gh-9-hint, eval = FALSE}
... +
  labs(..., 
       fill = "Clarity",
       ...)
```

Reminder: This is what your graph should look like. 

```{r show-hist-p}
hist_p
```

### 

In the previous graph we used `color` to change the legend labels, while here we used `fill`. The argument within labels matches the argument you use within `ggplot()`. `color` is used for objects like lines and points. `fill` is used for larger shapes. 

###

Are you satisfied with the way we have made the bin sizes? Do the axes labels make this easy to understand? We will do better later. 

## `geom_bar()`
###

Let's make the following dodged bar plot using `geom_bar`.

```{r}
bar_p <- ggplot(data = trains, 
                aes(x = race, fill = line)) +
  geom_bar(aes(y = after_stat(count/sum(count)))) +
  facet_wrap(~treatment) + 
  theme_classic() +
  labs(title = "Starting Attitudes Toward Immigration Issue",
       subtitle = "Higher proportion of minorities among treated participants",
       x = "Race",
       y = "Percentage of Participants",
       fill = "Line",
       caption = "Source: Enos (2014)")
bar_p
```

### Exercise 1

`skim` the data set `trains`. 

```{r gb-1, exercise = TRUE}

```

### Exercise 2 

Select the columns `treatment`, `race`, and `line`. 

```{r gb-2, exercise = TRUE}

```
 
Notice that there are 4 unique options for the `race` variable. 

### Exercise 3

Continue your pipe with `ggplot()`. Map the variable `race` to the x-axis. Also add the layer `geom_bar()`.

```{r gb-3, exercise = TRUE}

```

```{r gb-3-hint, eval = FALSE}
ggplot(aes(x = ...)) +
  geom_bar()
```

### Exercise 4

Now, map `line` to `fill`.

```{r gb-4, exercise = TRUE}

```

```{r gb-4-hint, eval = FALSE}
ggplot(data = ... , 
          aes(x = race, fill = ...) +
  geom_bar()
```

### Exercise 5

Within `geom_bar()`, nest the function `aes()` and within that set `y` equal to `after_stat(count / sum(count))`. Keep track of closing parentheses. 

```{r gb-5, exercise = TRUE}

```

```{r gb-5-hint, eval = FALSE}
geom_bar(aes(y = after_stat(count/sum(count))))
```

###

`after_stat` is a function used to manipulate variables like `count` which have been calculated by `ggplot()` to plot the graph. 

### Exercise 6 

Add the layer `facet_wrap` and facet by the variable `treatment`. 

```{r gb-6, exercise = TRUE}

```

```{r gb-6-hint, eval = FALSE}
... + 
  facet_wrap( ~ ...)
```

### Exercise 7

Let's add a theme to our graph. Add the layer `theme_classic()` to your code. 

```{r gb-7, exercise = TRUE}

```

```{r gb-7-hint, eval = FALSE}
... + 
  theme_classic()
```

### Exercise 8

To finish your plot, use `labs()` to give the graph a title, subtitle, axes labels, legend labels,  and caption of your choosing.

```{r gb-8, exercise = TRUE}

```

```{r gb-8-hint, eval = FALSE}
... +
  labs(..., 
       fill = "...",
       ...)
```

Reminder: This is what your plot should look like.

```{r}
bar_p
```

## `geom_col()`
###

Let's make the same plot, using a related function, `geom_col()`. Unlike `geom_bar()`, you have to specify the value for the y-axis when using this function. 

```{r make-col-p}
col_p <- trains  %>% 
  group_by(race, line, treatment) %>% 
  summarize(total = sum(n())) %>% 
 ggplot(aes(x = race, y = total, fill = line)) +
  geom_col() +
  facet_wrap(~ treatment) +
  theme_classic() +
  labs(title = "Starting Attitudes Toward Immigration Issue",
       subtitle = "Higher proportion of minorities among treated participants",
       x = "Race",
       y = "Number of Participants",
       fill = "Line",
       caption = "Source: Enos (2014)")
col_p
```

### Exercise 1

Start a pipe with `trains`. Select the columns `race`, `treatment` and `line`. 

```{r col-1, exercise = TRUE}

```

```{r col-1-hint, eval = FALSE}
trains %>% 
  select(..., ..., ...)
```

### Exercise 2 

Use `group_by()` to group the data by the column `race`, `treatment`, and `line`. 

```{r col-2, exercise = TRUE}

```

```{r col-2-hint, eval = FALSE}
... %>% 
  group_by(..., ..., ...)
```
 
###

After we group the data by these three factors, we can see in the box in the left hand corner of the tibble that we have made fourteen groups. Each groups is a unique combination of the four races, two treatments, and two lines. Note that there are no Blacks or Hispanics from the Franklin Line in the Control Group. 

### Exercise 3

Use `summarize()` to create a new table with the column `total` which is equal to the function `n()`. 

```{r col-3, exercise = TRUE}

```

```{r col-3-hint, eval = FALSE}
... %>% 
  group_by(race, treatment, line) %>% 
  summarize(total = ...)
```

###

`summarize()` runs the function, `n()` for each of the groups defined in `group_by()`. This tibble creates the same data that `ggplot()` plotted automatically for us in `geom_histogram()`. 

### Exercise 4

Continue your pipe with `ggplot()`. Map the variable `race` to the x-axis. Map total to the `y` axis. Add the layer `geom_col()`.

```{r col-4, exercise = TRUE}

```

```{r col-4-hint, eval = FALSE}
ggplot(data = ... , 
          aes(x = ..., y = ...) +
  geom_bar()
```

### 

`geom_col()` will automatically take the three to four values for each `race` in the `total` column and stack them to form one bar. This behavior is from the fact that the `position` argument for `geom_col()` is set by default to "stack". 

### Exercise 5

Now, map `line` to `fill`.

```{r col-5, exercise = TRUE}

```

```{r col-5-hint, eval = FALSE}
ggplot(data = ... , 
          aes(x = race, fill = ...) +
  geom_bar()
```

### Exercise 6 

Add the layer `facet_wrap` and facet by the variable `treatment`. 

```{r col-6, exercise = TRUE}

```

```{r col-6-hint, eval = FALSE}
... + 
  facet_wrap(~ ...)
```

### Exercise 7

Let's add a theme to our graph. Add the layer `theme_classic()` to your code. 

```{r col-7, exercise = TRUE}

```

```{r col-7-hint, eval = FALSE}
... + 
  theme_classic()
```

### Exercise 8

To finish your plot, use `labs()` to give the graph a title, subtitle, axes labels, legend labels,  and caption of your choosing.

```{r col-8, exercise = TRUE}

```

```{r col-8-hint, eval = FALSE}
... +
  labs(..., 
       fill = "...",
       ...)
```

Reminder: This is what your plot should look like.

```{r show-col}
col_p
```

## `geom_smooth()`
###

Let's create this graph using `geom_smooth()`.

```{r}
smooth_p <- ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end, 
                     color = treatment)) +
  geom_smooth(method = "lm", 
              se = FALSE,
              formula = y ~ x) + 
  theme_fivethirtyeight() +
  labs(title = "Starting and Ending Immigration Attitudes",
       subtitle = "The causal effect of treatment is similar regardless of starting attitude",
       x = "Starting Attitudes",
       y = "Ending Attitudes",
       color = "Treatment",
       caption = "Source: Enos (2014)")

smooth_p
```

### Exercise 1

Skim the `trains` data set. 

```{r gs-1, exercise = TRUE}

```

###

Notice that there are no missing values for `att_start` and `att_end`. 

### Exercise 2 

Select the columns `att_end`, `att_start`, and `treatment`. 

```{r gs-2, exercise = TRUE}

```

```{r gs-2-hint, eval = FALSE}
... %>% 
  select(..., ..., ...)
```

### Exercise 3

Add `ggplot()` and map `att_start` to the x axis and `att_end` to the y axis. Add the layer `geom_smooth()`.

```{r gs-3, exercise = TRUE}

```

```{r gs-3-hint, eval = FALSE}
ggplot(data = ..., 
       mapping = aes(x =..., 
                     y = ...))+
  geom_smooth()
```

###

Normally you will see `geom_smooth()` used with `geom_point()` so you can see the points and the trend line going through them. However, here we just have the trendlines shown.

### Exercise 4

Within `geom_smooth()`, set `method` to`"lm"`, `se` to `FALSE`, and `formula` to `y ~ x`. 

```{r gs-4, exercise = TRUE}

```

### Exercise 5

Now set `color` to `treatment`.

```{r gs-5, exercise = TRUE}

```

```{r gs-5-hint, eval = FALSE}
Recall color is an aesthetic, so it goes within aes() argument of ggplot().
```

### Exercise 6

Let's add a theme to our graph. Add the layer `theme_fivethirtyeight()` to your code. 

```{r gs-6, exercise = TRUE}

```

```{r gs-6-hint, eval = FALSE}
  theme_fivethirtyeight()
```

### Exercise 7 

Finally, use `labs()` to give the graph a title, subtitle, axis labels, legend labels, and caption of your choosing.

```{r gs-7, exercise = TRUE}

```

```{r gs-7-hint, eval = FALSE}
... +
  labs(..., 
       color = "...",
       ...)
```

Reminder: This is what your plot should look like.

```{r make-smooth-p}
smooth_p
```

###

Note that this theme does not have axes labels. Do you think it worth it?


## `geom_density()`
###

Let's create the following density plot.

```{r}
dens_p <- trains %>% 
  filter(age >= 40) %>% 
  ggplot(aes(age, fill = party)) +
  geom_density(alpha = 0.5) + 
  xlim(40, 75) +
  labs (title = "Age of Democrats and Republicans in Trains Experiment",
        subtitle = "More seniors are democrats in the experiment",
        x = "Age",
        y = "Density",
        fill = "Party",
        caption = " Source: Enos (2014)")

dens_p
```

### Exercise 1

Type `trains` to view the data set. 

```{r gd-1, exercise = TRUE}

```

### Exercise 2

Use the `$` operator to extract the `age` column as a vector. 

```{r gd-2, exercise = TRUE}

```

### Exercise 3

Start a new pipe with `trains`. Filter for rows in which `age` is greater than or equal to 40 

```{r gd-3, exercise = TRUE}

```

```{r gd-3-hint, eval = FALSE}
filter(age >= ...)
```

### Exercise 4
 
Select the columns `age` and `party`.

```{r gd-4, exercise = TRUE}

```

### Exercise 5

Use `ggplot()` and set `data` to `trains`. Use `ggplot()` to map `age` to the x-axis. Also add the layer `geom_density()`.

```{r gd-5, exercise = TRUE}

```

```{r gd-5-hint, eval = FALSE}
ggplot(data = ..., 
       mapping = aes(x =..., 
                     y = ...))+
  geom_smooth()
```

### Exercise 6

Set `fill` to `party`. 

```{r gd-6, exercise = TRUE}

```

```{r gd-6-hint, eval = FALSE}
Recall fill goes inside the aes() argument of ggplot()
```

### Exercise 7

Within `geom_density()`et the `alpha` argument to .5. 

```{r gd-7, exercise = TRUE}

```

```{r gd-7-hint, eval = FALSE}
... +
  geom_density(alpha = 0.5)
```

### Exercise 8

Let's also add an `xlim()` function, to set the range of x values on our plot from 40 to 75. This way, we can see the full distributions.

```{r gd-8, exercise = TRUE}

```

```{r gd-8-hint, eval = FALSE}
Make sure you put a comma between 40 and 75 within the xlim() function.
```

```{r gd-8-hint-2, eval = FALSE}
... +
  xlim(40, 75)
```

### Exercise 9

To finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, and caption of your choosing.

```{r gd-9, exercise = TRUE}

```

```{r gd-9-hint, eval = FALSE}
... +
  labs(..., 
       fill = "...",
       ...)
```

Reminder: This is what our plot should look like.

```{r}
dens_p
```

## `plotly`
###

`plotly` allows us to make interactive graphs. It's  especially useful with `geom_point()`. Hover over the points to see more information about them.

```{r make-plotly}
nominate_plot <- nominate %>% 
  filter(congress == 116) %>% 
  ggplot(aes(nominate_dim1, nominate_dim2, color = party,
             text = paste("Name:", name, "\n",
                                    "State:", state, "\n",
                                     "Chamber:", chamber))) +
  geom_point(size = 0.8) +
  labs(title = "Economic and Social Ideology of 116th U.S. Congress", 
       x = "Economic Ideology", 
       y = "Social Ideology", 
       color = "Party",
       caption = "Voteview")

nom_p <- ggplotly(nominate_plot, tooltip = "text")

nom_p
```


### Exercise 1

Run `?nominate` to open the help page for the nominate data set. 

```{r nominate-1, exercise = TRUE}

```

### Exercise 2

Start a new pipe with `nominate`. Arrange the tibble by `congress` in descending order to find the number of the most recent congress in the data set. 

```{r nominate-2, exercise = TRUE}

```

```{r nominate-2-hint, eval = FALSE}
... %>% 
  arrange(desc(...))
```

### 

The most recent congress is the 116th. 

### Exercise 3

Start a new pipe with `nominate`. Filter to keep rows in which the value of `congress` is 116. 

```{r nominate-3, exercise = TRUE}

```

```{r nominate-3-hint, eval = FALSE}
... %>% 
  filter(congress == ...)
```

### Exercise 4

Drop any rows with `N/A` values in the `nominate_dim1` and `nominate_dim2` columns. 

```{r nominate-4, exercise = TRUE}

```

```{r nominate-4-hint, eval = FALSE}
... %>% 
  drop_na(..., ...)
```

### Exercise 5

Select the columns `nominate_dim1`, `nominate_dim2`, `party`, `name`, `state`, and `chamber`. 

```{r nominate-5, exercise = TRUE}

```

```{r nominate-5-hint, eval = FALSE}
... %>% 
  select(..., ..., ..., ..., ..., ...)
```

### Exercise 6

Use `ggplot()` and `aes()` to map `nominate_dim1` to `x` and `nominate_dim2` to `y`. Add the layer `geom_point()`. 

```{r nominate-6, exercise = TRUE}

```

```{r nominate-6-hint, eval = FALSE}
... %>% 
  ggplot(mapping = aes(x = ..., y = ...))
```

### Exercise 7

Map `party` to `color`. Within `geom_point()` set the argument `size` to 0.8.

```{r nominate-7, exercise = TRUE}

```

```{r nominate-7-hint, eval = FALSE}
... %>% 
  ggplot(mapping = aes(x = ..., y = ..., color = ...)) +
  geom_point(size = 0.5)
```

### Exercise 8 

Within `aes()` in `ggplot()`, add the argument `text` and set this equal to the function `paste`. This will return an error because we have not assigned anything to `text` yet.  We will do this in the following exercises. 

```{r nominate-8, exercise = TRUE}

```

```{r nominate-8-hint, eval = FALSE}
... %>% 
  ggplot(mapping = aes(x = ..., y = ..., color = ..., 
                       text = paste()))
```

The `paste` function allows quoted strings and variables to be combined into one string. We will use this function to create our `plotly` labels. 

### Exercise 9 

Let's make the first line that will appear on our plotly label. Within `paste()`, first enter the string `"Name:"`. Separate this string by a comma a then write `name` without quotes, this is the column whose info we want to appear in this position on our label. Separate this by a comma, and then write `"\n"`. This is the symbol for a new line and it will not be printed. Keep this all on one line for the easiest formatting. Refer to the hint if needed.

```{r nominate-9, exercise = TRUE}

```

```{r nominate-9-hint, eval = FALSE}
... %>% 
  ggplot(mapping = aes(x = ..., y = ..., color = ..., 
                       text = paste("Name:", name, "\n",
                                    )))
```

### Exercise 10

Let's make an equivalent label for a congressman's state. Place a comma after the `"\n"` from the previous exercise. On a new line within paste, enter the string `"State:"`. Separate this string by a comma and then write `state` without quotes. Separate this by a comma and then include the new line symbol, `"\n"`. 

```{r nominate-10, exercise = TRUE}

```

```{r nominate-10-hint, eval = FALSE}
... %>% 
  ggplot(mapping = aes(x = ..., y = ..., color = ..., 
                       text = paste("Name:", name, "\n",
                                    "State:", state, "\n",
                                    )))
```

### Exercise 11

Let's make an equivalent label for a congressman's chamber. Place a comma after the `"\n"` from the previous exercise. On a new line within paste, enter the string `"Chamber:"`. Separate this string by a comma and then write `chamber` without quotes. Since this is our final line, do not include another new line symbol, simply add the closing the parentheses (if it is not there already). 

```{r nominate-11, exercise = TRUE}

```

```{r nominate-11-hint, eval = FALSE}
... %>% 
  ggplot(mapping = aes(x = ..., y = ..., color = ..., 
                       text = paste("Name:", name, "\n",
                                    "State:", state, "\n",
                                     "Chamber:", chamber)))
```

### Exercise 12

Use `labs()` to add a title, axes labels, legend labels, and a caption to your plot. `ggplotly()` does not support subtitles. 

```{r nominate-12, exercise = TRUE}

```

```{r nominate-12-hint, eval = FALSE}
+ labs(title = "...",
       subtitle = "...",
       x = "...",
       y = "...",
       color = "...",
       caption = "...")
```

### Exercise 13

To make a graph with `plotly`, you need to save your `ggplot()` to an object in R, which you will use in the function `ggplotly`. Copy/paste your full pipe from the previous exercise and assignment. At the beginning of the pipe use the `<-` to assign this to an object named `nominate_plot`.

```{r nominate-13, exercise = TRUE}

```

```{r nominate-13-hint, eval = FALSE}
nominate_plot <- nominate %>% 
  filter(congress == 116) %>% 
  ...
```

### Exercise 14

Copy/paste the code from above. On a new line not connected to the pipe above, type the function `ggplotly()`. The first argument should be the name of the ggplot object, `nominate_p`. Make the second argument `tooltip = "text"`. This tells `ggplotly()` to make the label based on what we have in the `text` argument in `ggplot()`.

```{r nominate-14, exercise = TRUE}

```

```{r nominate-14-hint, eval = FALSE}
nominate_plot <- nominate %>% 
  filter(congress == 116) %>% 
  ... 

ggplotly(nominate_plot, tooltip = "text")

```

Reminder: This is what your graph should look like. Test to make sure you can interact with your graph. 

```{r}
nom_p
```

## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```
