---
title: N Parameters
author: David Kane and Sanaka Dash
tutorial:
  id: n-parameters
output:
  learnr::tutorial:
    progressive: yes
    'allow_skip:': yes
runtime: shiny_prerendered
description: 'Chapter 10 Tutorial: N Parameters'
---

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(tidyverse)
library(brms)
library(tidybayes)
library(gtsummary)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 
```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```


<!-- DK: Key problems with current version: We need (?) to flesh out the Courage and Temperance sections. Key skills to practice each time including writing math formulas in Quarto and creating nice looking tables of regression results. -->

<!-- SD: Note: the [FIX - ] tag in front of some of my comments makes it so I have a tag that I can easily search for when I am fixing issues in the future. It doesn't necessarily mean that the thing has to be fixed, just that it needs to get my attention when I look for things to fix. Is this confusing? -->


## Introduction
### 

This tutorial covers [Chapter 10: N Parameters](https://ppbds.github.io/primer/XX.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 

<!-- You are now ready to make the jump to *N* parameters. -->

<!-- In this chapter, we will consider models with many parameters and the complexities that arise therefrom. As our models grow in complexity, we need to pay extra attention to basic assumptions like validity, stability, representativeness, and unconfoundedness. It is (too!) easy to jump right in and start interpreting. It is harder, but necessary, to ensure that our models are really answering our questions. -->

## Wisdom
### 

*The doorstep to the temple of wisdom is a knowledge of our own ignorance.* - Benjamin Franklin

<!-- Use Case: -->
<!-- Imagine you are a Republican running for Governor in Texas. You need to allocate your campaign spending intelligently. For example, you want to do a better job of getting your voters to vote. 

As you research ways to increase voting, you come across a large-scale experiment showing the effect of sending out a voting reminder that “shames” citizens who do not vote. Perhaps you should pay to send out a shaming voting postcard.-->

Today's Initial Question:
*How can you encourage politically engaged voters to go out to the polls on election day?*

### Exercise 1

In your own words, describe the key components of Wisdom for working on a data science problem.

```{r wisdom-1}
question_text(NULL,
	message = "Wisdom requires the creation of a Preceptor Table, an examination of our data, and a determination, using the concept of validity, as to whether or not we can (reasonably!) assume that the two come from the same population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Recall our initial question: how can we encourage voters to go out to the polls on election day? We now need to translate this into a more precise question, one that we can answer with data:

*What is the causal effect of postcards on voting?*

### Exercise 2

Define a Preceptor Table.

```{r wisdom-2}
question_text(NULL,
	message = "A Preceptor Table is the smallest possible table of data with rows and columns such that, if there is no missing data, it is easy to calculate the quantities of interest.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Our Preceptor Table for today:

```{r}
#| echo: false
tibble(ID = c("1", "2", "...", "10", "11", "...", "N"),
       voting_after_treated = c("1", "1", "...", "1", "0", "...", "1"),
       voting_after_control = c("1", "0", "...", "1", "1", "...", "0"),
       treatment = c("Yes", "No", "...", "Yes", "Yes", "...", "No"),
       engagement = c("1", "3", "...", "6", "2", "...", "2")) |>
  
  gt() |>
  tab_header(title = "Preceptor Table") |> 
  cols_label(ID = md("ID"),
             voting_after_treated = md("Voting After Treatment"),
             voting_after_control = md("Voting After Control"),
             treatment = md("Treatment"),
             engagement = md("Engagement")) |>
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(ID))) |>
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"), 
            locations = cells_column_labels(columns = c(ID))) |>
  cols_align(align = "center", columns = everything()) |>
  cols_align(align = "left", columns = c(ID)) |>
  fmt_markdown(columns = everything()) |>
  tab_spanner(label = "Covariates", columns = c(treatment, engagement)) |>
  tab_spanner(label = "Outcomes", columns = c(voting_after_control, voting_after_treated))
```

### Exercise 3

Describe the key components of Preceptor Tables in general, without worrying about this specific problem.

```{r wisdom-3}
question_text(NULL,
	message = "The rows of the Preceptor Table are the units. The outcome is at least one of the columns. If the problem is causal, there will be at least two (potential) outcome columns. The other columns are covariates. If the problem is causal, at least one of the covariates will be a treatment.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 4

<!-- SD: FIX -  -->

What are the units for this problem?

```{r wisdom-4}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 5

What is/are the outcome/outcomes for this problem?

<!-- SD: FIX -  -->

```{r wisdom-5}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 6

What are the covariates for this problem?

```{r wisdom-6}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 7

What are the treatments, if any, for this problem?

```{r wisdom-7}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 8

What moment in time does the Preceptor Table refer to?

```{r wisdom-8}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 9

Define causal effect.

```{r wisdom-9}
question_text(NULL,
	message = "A causal effect is the difference between two potential outcomes.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 10

What is the fundamental problem of causal inference?

```{r wisdom-10}
question_text(NULL,
	message = "The fundamental problem of causal inference is that we can only observe one potential outcome.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 11

<!-- SD: FIX - Need answer for this question -->

How does the motto "No causal inference without manipulation." apply in this problem?

```{r wisdom-11}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 12

<!-- DK: It is a feature that this question almost forces students to go to the chapter and read about the data. -->

Write one sentence describing the data you have to answer your question.

<!-- SD: FIX - Not sure I like this b/c it answers a question with a question. Might change it later. -->

```{r wisdom-12}
question_text(NULL,
	message = "What is the causal effect of postcards on voting in the 2026 Texas gubernatorial election? Do those effects vary by political engagement?",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 13

Load the **tidyverse** package.

```{r wisdom-13, exercise = TRUE}

```

```{r wisdom-13-hint-1, eval = FALSE}
library(...)
```

```{r wisdom-13-test, include = FALSE}
library(tidyverse)
```

### 

<!-- SD: FIX - Not exactly a comment on the data, so I might change it later on -->
Once we look more closely at the data, we will discover that there are multiple treatments. In fact, we have a total of 5 potential outcomes in this example!

<!-- XX: Insert comments about the data. - DONE -->

<!-- DK: Consider adding more questions about EDA with this data. In particular, add at least one question about the dependent variable in the model along with one or more questions about covariates. If there is a treatment variable, we must include a question about it. -->
<!-- SD: FIX - -->

### Exercise 14

In your own words, define "validity" as we use the term.

```{r wisdom-14}
question_text(NULL,
	message = "Validity is the consistency, or lack thereof, in the columns of the data set and the corresponding columns in the Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 15

What can't we do if the assumption of validity is not true?

```{r wisdom-15}
question_text(NULL,
	message = "We can't combine the Preceptor Table and the data in order to construct the Population Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 16

Provide one reason why the assumption of validity might hold for this problem.

```{r wisdom-16}
question_text(NULL,
	message = "We will assume that validity holds because the outcome variable in our data and in our Preceptor Table are close enough — even though one is for a primary election while the other is for a general election — that we can just stack them.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 17

Summarize the state of your work so far in one or two sentences. Make reference to the data you have and to the question you are trying to answer. 

```{r wisdom-17}
question_text(NULL,
	message = "Using the results of a voting experiment in Michigan in 2006, we seek to forecast the causal effect on voter participation of sending postcards in the Texas gubernatorial general election of 2026.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

## Justice
### 

*It is in justice that the ordering of society is centered.* - Aristotle

### Exercise 1

In your own words, name the four key components of Justice for working on a data science problem.

```{r justice-1}
question_text(NULL,
	message = "Justice concerns four topics: the Population Table, stability, representativeness, and unconfoundedness.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

In your own words, define a Population Table.

```{r justice-2}
question_text(NULL,
	message = "The Population Table includes a row for each unit/time combination in the underlying population from which both the Preceptor Table and the data are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Here is our Population Table for today:
```{r}
#| echo: false
# First, we create a tibble with the values we want for the table

tibble(source = c("...", "...", "...",
                  "Data", "Data", "...", 
                  "...", "...", "...",
                  "Preceptor Table", "Preceptor Table", "...",
                  "...", "..."),
       gender = c("?", "?", "...",
                  "Male", "Female", "...",
                  "?", "?", "...",
                  "Female", "Female", "...",
                  "?", "?"),
       year = c("1990", "1995", "...",
                "2006", "2006", "...",
                "2010", "2012", "...",
                "2026", "2026", "...",
                "2046", "2050"),
       state = c("?", "?", "...",
                 "Michigan", "Michigan", "...",
                 "?", "?", "...",
                 "Texas", "Texas", "...",
                 "?", "?"),
       ytreat = c("?", "?", "...", 
                  "Did not vote", "?", "...",
                  "?", "?", "...",
                  "?", "?", "...",
                  "?", "?"),
       ycontrol = c("?", "?", "...", 
                    "?", "Voted", "...",
                    "?", "?", "...", 
                    "?", "?", "...",
                    "?", "?")) |>
  
  # Then, we use the gt function to make it pretty
  
  gt() |>
  cols_label(source = md("Source"),
             gender = md("Sex"),
             year = md("Year"),
             state = md("State"),
             ytreat = md("Treatment"),
             ycontrol = md("Control")) |>
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(source))) |>
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"), 
            locations = cells_column_labels(columns = c(source))) |>
  cols_align(align = "center", columns = everything()) |>
  cols_align(align = "left", columns = c(source)) |>
  fmt_markdown(columns = everything())  |>
  tab_spanner(label = "Outcomes", c(ytreat, ycontrol)) 
```

### Exercise 3

In your own words, define the assumption of "stability" when employed in the context of data science.

```{r justice-3}
question_text(NULL,
	message = "Stability means that the relationship between the columns in the Population Table is the same for three categories of rows: the data, the Preceptor Table, and the larger population from which both are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Stability is all about *time*. Is the relationship among the columns in the Population Table stable over time? In particular, is the relationship --- which is another way of saying "mathematical formula" --- at the time the data was gathered the same as the relationship at the (generally later) time references by the Preceptor Table.

### Exercise 4

Provide one reason why the assumption of stability might not be true in this case.

<!-- SD: FIX - This could definitely be shortened and made better -->
```{r justice-4}
question_text(NULL,
	message = "Is data collected in 2006 on voting behavior likely to be the same in 2026? Frankly, we don’t know! We aren’t sure what would impact someone’s response to a postcard encouraging them to vote. It is possible, for instance, that a postcard informing neighbors of voting status has a bigger effect in a world with more social media.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

When we are confronted with this uncertainty, we can consider making our timeframe smaller. However, we would still need to assume stability from 2006 (time of data collection) to 2026. Assuming stability allows us to ignore the issue of time.

### Exercise 5

In your own words, define the assumption of "representativeness" when employed in the context of data science.

```{r justice-5}
question_text(NULL,
	message = "Representativeness, or the lack thereof, concerns two relationship, among the rows in the Population Table. The first is between the Preceptor Table and the other rows. The second is between our data and the other rows.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Stability looks *across* time periods. Reprentativeness looks *within* time periods.

### Exercise 6

Provide one reason why the assumption of representativeness might not be true in this case.

```{r justice-6}
question_text(NULL,
	message = "Even if the stability assumption holds, we still have problems with representativeness because Michigan and Texas are (very?) different states.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 7

In your own words, define the assumption of "unconfoundedness" when employed in the context of data science.

```{r justice-7}
question_text(NULL,
	message = "Unconfoundedness means that the treatment assignment is independent of the potential outcomes, when we condition on pre-treatment covariates.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The easiest way to ensure unconfoundedness is to assign treatment randomly.

### Exercise 8

Provide one reason why the assumption of unconfoundedness might be true (or relevant) in this case.

```{r justice-8}
question_text(NULL,
	message = "The great advantage of randomized assignment of treatment is that it guarantees unconfoundedness. There is no way for treatment assignment to be correlated with anything, including potential outcomes, if treatment assignment is random.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 9

Summarize the state of your work so far in two or three sentences. Make reference to the data you have and to the question you are trying to answer. Feel free to copy from your answer at the end of the Wisdom Section. Mention at least one specific problem which casts doubt on your approach. 


```{r justice-9}
question_text(NULL,
	message = "Using the results of a voting experiment in Michigan in 2006 primary election, we seek to forecast the causal effect on voter participation of sending postcards in the Texas gubernatorial general election of 2026. There is concern that data from a primary election might not generalize to a general election and that political culture in the two states differ too much to allow for data from one to enable useful forecasts in the other.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

## Courage
### 

*Courage is found in unlikely places.* - J.R.R. Tolkien

<!-- Questions about models, tests, and the DGM. -->
<!-- SD: FIX -  -->

### Exercise 1

<!-- DK: Not sure I like this answer. -->
<!-- SD: How about this: Justice verifies the Population Table. Courage creates a mathematical model which connects the outcome variable to the covariates, if any. Then, using code, we create a fitted model, including posterior probability distributions for all the unknown parameters. -->

In your own words, name the key goal of Courage and the process we use to get there.

<!-- SD: Note - this section was left blank in the Primer -->

```{r courage-1}
question_text(NULL,
	message = "Courage selects the data generating mechanism. We first specify the mathematical formula which connects the outcome variable we are interested in with the other data that we have. We explore different models. We need to decide which variables to include and to estimate the values of unknown parameters. We check our models for consistency with the data we have. We avoid hypothesis tests. We select one model.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

Load the **brms** package.

```{r courage-2, exercise = TRUE}

```

```{r courage-2-hint-1, eval = FALSE}
library(...)
```

```{r courage-2-test, include = FALSE}
library(brms)
```

### 

Without going too deep into specifics, the `brms` package helps in creating wide range of complex Bayesian models.

### Exercise 3

Load the **tidybayes** package.

```{r courage-3, exercise = TRUE}

```

```{r courage-3-hint-1, eval = FALSE}
library(...)
```

```{r courage-3-test, include = FALSE}
library(tidybayes)
```

### 

This package also helps with the creation of Bayesian Models.

<!-- XX: Some comments about this problem. -->
<!-- SD: FIX -  -->

<!-- XX: Might need an exercise which gets/creates/cleans the data you need for fitting the model. -->

### Exercise 4

Create a model using `brm()` from the **brms** package. Your arguments should XX. 

Assign the result to an object called `fit_XX`.

<!-- Search and replace "fit_XX" as appropriate. -->

<!-- Don't forget to create this model yourself in the setup chunk. Do this once, save the object, comment out that code and then just read_rds to create the object for his tutorial. -->

<!-- Depending on code speed, you can run this function multiple times, without assigning the return value, looking at the printout, and seeing how things change. -->

```{r courage-4, exercise = TRUE}

```

```{r courage-4-hint-1, eval = FALSE}

```

### 

### Exercise 5

Type `fit_XX` and hit "Run Code." This generates the same results as using `print(fit_XX)`.


```{r courage-5, exercise = TRUE}

```

```{r courage-5-hint-1, eval = FALSE}
print(...)
```

```{r courage-5-test, include = FALSE}
# print(fit_XX)
```

### 

<!-- XX Same some general words about the object. Note that we are about to go through the top 4 rows. -->

<!-- Add summary() Exercise if it gives a different answer -->

### Exercise 6

Run `family()` on `fit_XX`. `family()` provides information about the "family" of the error term and the link between it and the dependent variable. 

```{r courage-6, exercise = TRUE}

```

```{r courage-6-hint-1, eval = FALSE}
family(...)
```

```{r courage-6-test, include = FALSE}
# family(fit_XX)
```

### 

<!-- DK: This is a great location for explanations which get much more detailed in later chapters. -->

In this case, XX . . .

### Exercise 7

Run `formula()` on `fit_XX`. `formula()` returns the statistical equation which relates the dependent variable to the independent variable(s). 

```{r courage-7, exercise = TRUE}

```

```{r courage-7-hint-1, eval = FALSE}
formula(...)
```

```{r courage-7-test, include = FALSE}
# formula(fit_XX)
```

### 

In this case, XX . . .

### Exercise 8

Run `nobs()` on `fit_XX`. The `nobs()` function returns the **n**umber of **obs**ervations.

```{r courage-8, exercise = TRUE}

```

```{r courage-8-hint-1, eval = FALSE}
nobs(...)
```

```{r courage-8-test, include = FALSE}
# nobs(fit_XX)
```

### 

In this case, XX

### Exercise 9

Run `posterior_interval()` on `fit_XX`. The `posterior_interval()` function returns 95% intervals for all the parameters in our model.

```{r courage-9, exercise = TRUE}

```

```{r courage-9-hint-1, eval = FALSE}
posterior_interval(...)
```

```{r courage-9-test, include = FALSE}
# posterior_interval(fit_XX)
```

### 

In this case, XX


### Exercise 10

Run `fixef()` on `fit_XX`. The `fixef()` returns information about the **fix**ed **ef**fects in the model.

```{r courage-10, exercise = TRUE}

```

```{r courage-10-hint-1, eval = FALSE}
fixef(...)
```

```{r courage-10-test, include = FALSE}
# fixef(fit_XX)
```

### 

In this case, XX

<!-- DK: Consider adding questions about conditional_effects(), ranef() and other commands, if relevant. -->

### Exercise 11

Run `pp_check()` on `fit_XX`. The `pp_check()` runs a **p**osterior **p**redictive check.

```{r courage-11, exercise = TRUE}

```

```{r courage-11-hint-1, eval = FALSE}
pp_check(...)
```

```{r courage-11-test, include = FALSE}
# pp_check(fit_XX)
```

### 

In this case, XX

<!-- If the fake data had looked very different from the real data, we have had a problem. But, for the most part, we conclude that, although not perfect, pp_check() shows that the fake outcomes generated by our model are like the actual outcome data. -->


### Exercise 12

Use `library()` to load the [**gtsummary**](https://www.danieldsjoberg.com/gtsummary) package.

```{r courage-12, exercise = TRUE}

```

```{r courage-12-hint-1, eval = FALSE}
library(gtsummary)
```

```{r courage-12-test, include = FALSE}
library(gtsummary)
```

### 

<!-- Drop some knowledge about gtsummary. Or say something more about your DGM. -->

### Exercise 13

<!-- DK: This can be just one question or several, especially if you want to teach some more gtsummary or gt tricks. Note that you need to adjust the test to make sure it works. -->

Run `tbl_regression()` on `fit_XX`. 


```{r courage-13, exercise = TRUE}

```

```{r courage-13-hint-1, eval = FALSE}
tbl_regression(...)
```

```{r courage-13-test, include = FALSE}
# tbl_regression(fit_XX)
```

### 

<!-- DK: Give something like the same sentence which you want the students to use at the end of the next question. -->


### Exercise 14

Write a few sentence which summarize your work so far. The first few sentences are the same as what you had at the end of the Justice Section. Add at least one sentence which describes the modelling approach which you are using, specifying at least the functional form and the dependent variable. Add at least one sentence which describes the *direction* (not the magnitude) of the relationship between one of your independent variables and your dependent variable.

```{r courage-14}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

## Temperance
### 

<!-- DK: Choose 1. -->

*Temperance is a tree which as for its root very little contentment, and for its fruit calm and peace.* - Buddha
*Temperance is the greatest of all virtues. It subdues every passion and emotion, and almost creates a Heaven upon Earth.* - Joseph Smith Jr.
*Temperance is a bridle of gold; he, who uses it rightly, is more like a god than a man.* - Robert Burton
*Temperance is the firm and moderate dominion of reason over passion and other unrighteous impulses of the mind.* - Marcus Tullius Cicero
*Temperance to be a virtue must be free, and not forced.* - Philip Massinger
*Temperance is simply a disposition of the mind which binds the passion.* - Thomas Aquinas

<!--  -->

### Exercise 1

In your own words, describe the use of Temperance in finishing your data science project.

```{r temperance-1}
question_text(NULL,
	message = "Temperance guides us in the use of the data generating mechanism --- or the 'model' ---  we have created to answer the questions with which we began. We create posteriors for the quantities of interest.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

Recall the question with which we began:

> ...

Pipe `fit_XX` to . . .

```{r temperance-2, exercise = TRUE}

```

```{r temperance-2-hint-1, eval = FALSE}

```

```{r temperance-2-test, include = FALSE}

```

### 

### Exercise 3

Write a paragraph which summarizes the project in your own words. The first few sentences are the same as what you had at the end of the Courage Section. But, since your question may have evolved, you should feel free to change those sentences. Add at least one sentence which describes at least one quantity of interest (QoI) --- presumably one that answers your question -- and which provides a measure of uncertainty about that QoI. 

```{r temperance-3}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 4

Write a few sentences which explain why the estimates for the quantities of interest, and the uncertainty thereof, might be wrong. Suggest an alternative estimate and confidence interval.

```{r temperance-4}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

## Summary
### 

This tutorial covered [Chapter XX: XX](https://ppbds.github.io/primer/XX.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 



```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
