---
title: Sampling
author: Ryan Southward, Mann Talati and David Kane
tutorial:
  id: sampling
output:
  learnr::tutorial:
    progressive: yes
    'allow_skip:': yes
runtime: shiny_prerendered
description: 'Chapter 3 Tutorial: Sampling'
---

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(tidyverse)
library(gt)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 

# Key Data

set.seed(10)
urn <- tibble(color = c(rep("red", 400), rep("white", 600))) |>
  sample_frac() |> 
  mutate(bead_ID = 1:1000) 

virtual_samples <- tibble(trial_ID = 1:1000) |> 
  mutate(shovel = map(trial_ID, ~ sample_n(urn, size = 50))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) |> 
  mutate(numb_beads = map_int(shovel, ~ length(.$color))) |> 
  mutate(prop_red = numb_red / numb_beads)

shovels_100 <- expand_grid(trial_ID = 1:100, shovel_size = 1:100) |> 
  mutate(shovel = map(shovel_size, ~ slice_sample(urn, n = .))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) |> 
  mutate(prop_red = numb_red / shovel_size) |> 
  group_by(shovel_size) |> 
  summarize(st_dev_p_hat = sd(prop_red)) 
```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

<!-- This tutorial sticks! -->

<!-- Khang: Please fix everything! -->

<!-- Delete everything that you can't defend. -->

<!-- Add test chunks everywhere.  -->

<!-- Section about real sampling? no! -->

<!-- Add courage and temperance sections. -->

<!-- Make the Cardinal Virtues section a simpler version of the ones we use in Chapters 4 through 10. No Github for example. Use the tutorial_tempate.Rmd as much as you think wise. -->

## Introduction
### 

This tutorial covers [Chapter 3: Sampling](https://ppbds.github.io/primer/sampling.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 


## Virtual Sampling
### 

In this section, we mimic physical sampling with virtual sampling, using a computer. In a real sampling activity, we would perform a tactile sampling activity. In this we use a physical urn of beads and a physical shovel which is done by hand so that we could develop our intuition about the ideas behind sampling. 

### 

Let's create the following plot that shows sampling variation for 1000 samples from an urn that contains red and white beads.

```{r}
plot_vs <- virtual_samples |> 
  ggplot(aes(x = prop_red)) +
    geom_histogram(binwidth = 0.01, 
                   boundary = 0.4, 
                   color = "white") +
    labs(x = expression(hat(p)), 
         y = "Count",
         title = "Distribution of 1,000 proportions red") 

plot_vs
```

### Exercise 1

Create a `urn` variable on the second line that is set to a `tibble()`. Within the `tibble()` set `color` to the combination of `rep("red", 400)` and `rep("white", 600)`.

```{r virtual-sampling-1, exercise = TRUE}
set.seed(10)

```

```{r virtual-sampling-1-hint-1, eval = FALSE}
set.seed(10)
urn <- tibble(... = c(rep("...", ...), 
                        rep("...", ...)))
```

```{r virtual-sampling-1-test, include = FALSE}
set.seed(10)
urn <- tibble(color = c(rep("red", 400), 
                        rep("white", 600)))
```

### 

`set.seed()` ensures that the beads in our virtual urn are always in the same order. This ensures that the figures in the book match their written descriptions. We want 40% of the beads to be red. The `rep()` function will repeat the first argument a number of times specified by the second argument. We then combine our 400 red beads and 600 white beads using `c()`.

### Exercise 2

Within the `urn` variable start a pipe and set it to `sample_frac()`.

```{r virtual-sampling-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-2-hint-1, eval = FALSE}
urn <- ... |>
          sample_frac()
```

### 

`sample_frac()` keeps all the rows in the tibble but rearranges their order. We don't need to do this. A virtual urn does not care about the order of the beads. But we find it aesthetically pleasing to mix them up.

### Exercise 3

Finish the pipe with `mutate()` and set `bead_ID` to 1 through 1000.

```{r virtual-sampling-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-3-hint-1, eval = FALSE}
urn <- ... |>
          mutate(... = 1:1000)
```

### 

The first variable `bead_ID` is used as an identification variable. None of the beads in the actual urn are marked with numbers. The second variable `color` indicates whether a particular virtual bead is red or white.

### Exercise 4

To simulate the process of real-world sampling, let’s take a sample of 50 beads from our virtual urn. To do so, create a `tibble()` that has one variable `trial_ID` that takes on the values 1 to 1000.

```{r virtual-sampling-4, exercise = TRUE}

```

```{r virtual-sampling-4-hint-1, eval = FALSE}
tibble(trial_ID = ...)
```

```{r virtual-sampling-4-hint-2, eval = FALSE}
Use the : operator to create a range of integers.
```

```{r virtual-sampling-4-test, include = FALSE}
tibble(trial_ID = 1:1000)
```

### Exercise 5

Now pipe your results to the function `mutate()` to create the variable `shovel`, which is set to the function `map()`. The first argument to `map()` should be `trial_ID`. The second argument should use `slice_sample()`. Within `slice_sample()`, the first argument should be `urn` (the data we want to sample from), and then set `n` equal to our sample size (we want a sample size of 50). 

```{r virtual-sampling-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-5-hint-1, eval = FALSE}
... |> 
  mutate(shovel = map(..., ~ ...))
```

```{r virtual-sampling-5-hint-2, eval = FALSE}
... |> 
  mutate(shovel = map(..., ~slice_sample(urn, n = ...)))
```

### 

The advantage of modern technology is that we can use virtual simulation as many times as we choose, so we have no restrictions on resources. No longer are the days where we have to recruit our friends to tirelessly sample from the physical urn.

### Exercise 6

Continue your pipe with `mutate()` to create the variable `numb_red`. Set `numb_red` to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `sum()` of where `.$color` is equal to red.

```{r virtual-sampling-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-6-hint-1, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~...))
```

```{r virtual-sampling-6-hint-2, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~ sum(.$color == "red")))
```

### 

R evaluates if `color == red`, and treats `TRUE` values like the number `1` and `FALSE` values like the number `0`. So summing the number of `TRUE`s and `FALSE`s is equivalent to summing `1`’s and `0`’s. In the end, this operation counts the number of beads where `color` equals “red”.

### Exercise 7

Use `mutate()` one last time to create the variable `prop_red`. Set `prop_red` to `numb_red` divided by the sample size (in this exercise we are using a set sample size of 50).

```{r virtual-sampling-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-7-hint-1, eval = FALSE}
... |> 
   mutate(prop_red = ... / ...)
```

### 

`prop_red` estimate's our proportion of red beads in the urn.

### Exercise 8

Assign your code from above to an object named `virtual_samples`.

```{r virtual-sampling-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-8-hint-1, eval = FALSE}
Use the assignment operator <-  to do so.
```

### Exercise 9

Now start a pipe with `virtual_samples`. Use `ggplot()` to map `prop_red` to the x-axis.

```{r virtual-sampling-9, exercise = TRUE}

```

```{r virtual-sampling-9-hint-1, eval = FALSE}
virtual_samples |> 
  ggplot(aes(...))
```

### Exercise 10

Add the layer `geom_histogram()` to create a histogram of our data.

```{r virtual-sampling-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-10-hint-1, eval = FALSE}
... +
  geom_histogram()
```

### Exercise 11

Within `geom_histrogram()` set `binwidth` to .01, `boundary` to .4, and `color` to "white".

```{r virtual-sampling-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-11-hint-1, eval = FALSE}
... +
  geom_histrogram(binwidth = ..., boundary = ..., color = ...)
```

### 

Recall that `p` is equal to the proportion of beads which are red in each sample.

### Exercise 12

To finish, use `labs()` to give your graph the appropriate title and axis labels. See **hint** for guidance to create the symbol $\hat{p}$.

```{r virtual-sampling-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like. 

```{r}
plot_vs
```

```{r virtual-sampling-12-hint-1, eval = FALSE}
Within labs(), set x to expression(hat(p))
```

### 

This visualization allows us to see how our results differed between our tactile and virtual urn results. As we can see, there is some variation between our results. This is not a cause for concern, as there is always expected sampling variation between results.


## Standard error of different shovel sizes
### 

<!-- MT: add questions about the definitions/important concepts of standard error -->

Standard errors (SE) quantify the effect of sampling variation on our estimates. In other words, they quantify how much we can expect the calculated proportions of a shovel’s beads that are red to vary from one sample to another sample to another sample, and so on. As a general rule, as sample size increases, the standard error decreases.

### 

Let's create the following plot that displays different standard deviations of red bead proportions for 100 different shovel sizes.

```{r}
shovel_p <- shovels_100 |>
 ggplot(aes(x = shovel_size, y = st_dev_p_hat)) +
 geom_point() +
 labs(title = "Sampling Variation",
      subtitle = "Larger samples have less variation",
      x = "Shovel size",
      y = "Standard deviation of the proportion red")

shovel_p
```

### Exercise 1

First, let's use `expand_grid()` to create the foundation of our tibble. Our first column in `expand_grid()` should be called `trial_ID`, and it should be the range of integers between 1 and 1,000. The second column should be called `shovel_size`, and should be the range of integers between 1 and 100.

```{r standard-error-of-different-sh-1, exercise = TRUE}

```

```{r standard-error-of-different-sh-1-hint-1, eval = FALSE}
expand_grid(trial_ID = ..., shovel_size = ...)
```

```{r standard-error-of-different-sh-1-hint-2, eval = FALSE}
Use the : operator to create a range of integers. 
```

### 

### Exercise 2

Continue the pipe with `mutate()`, creating a new column called `shovel`. Set `shovel` equal to a `map()` function, passing in `shovel_size` as the first argument, and the `slice_sample()` function as the second argument. Within `slice_sample()`, the first argument should be `urn` (the data we want to sample from), and then set `n` equal to `.` (we want to pass in the `shovel_size` using `map()`).

```{r standard-error-of-different-sh-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-2-hint-1, eval = FALSE}
... |>
  mutate(shovel = map(..., ~ ... ))
```

```{r standard-error-of-different-sh-2-hint-2, eval = FALSE}
... |>
  mutate(shovel = map(... , ~ slice_sample(..., n = ...)))
```

### Exercise 3

Continue your pipe with `mutate()` to create the variable `numb_red`, which will tells us the number of red beads present. Set `numb_red` to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `sum()` of where the column `color` of `shovel` is equal to red.

```{r standard-error-of-different-sh-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-3-hint-1, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~ ...))
```

```{r standard-error-of-different-sh-3-hint-2, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~ sum(.$color == "red")))
```

### Exercise 4

Continue your pipe from above, using `mutate()` to create one final column called `prop_red` which represents the proportion of red beads in a sample. Set `prop_red` to `numb_red` divided by the `shovel_size` column. 

```{r standard-error-of-different-sh-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-4-hint-1, eval = FALSE}
... |>
  mutate(prop_red = ... / ...)
```

### Exercise 5

Great. Continue your pipe and use the `group_by()` function to group our tibble by `shovel_size`. 

```{r standard-error-of-different-sh-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-5-hint-1, eval = FALSE}
... |>
  group_by(...)
```

### Exercise 6

Continue your pipe one last time, and use `summarize()` to create a new column named `st_dev_p_hat` which is equal to the standard deviation of `prop_red`. (`sd()` calculates standard deviation).
 

```{r standard-error-of-different-sh-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-6-hint-1, eval = FALSE}
... |> 
  summarize(st_dev_p_hat = sd(...))
```

### Exercise 7

Assign your code from above to an object named `shovels_100`.

```{r standard-error-of-different-sh-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-7-hint-1, eval = FALSE}
Use the assignment operator <-  to do so.
```

### Exercise 8

Start a new pipe from `shovels_100`. Use `ggplot()`to map `shovel_size` to the x-axis and `st_dev_p_hat` to the y axis. Also, add the layer `geom_point()` to create a scatterplot.

```{r standard-error-of-different-sh-8, exercise = TRUE}

```

```{r standard-error-of-different-sh-8-hint-1, eval = FALSE}
shovels_100 |> 
  ggplot(aes(x = ..., y = ...)) + 
  geom_point()
```

### Exercise 9

Now use `labs()` to label the x-axis "Shovel size" and the y-axis 
"Standard deviation of the proportion red". You should also provide a title and subtitle.

```{r standard-error-of-different-sh-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like.

```{r}
shovel_p
```

```{r standard-error-of-different-sh-9-hint-1, eval = FALSE}
... +
   labs(title = "Sampling Variation",
      subtitle = "Larger samples have less variation",
      x = "Shovel size",
      y = "Standard deviation of the proportion red")
```

### 

<!-- DK: Explain what they have just learned. "The standard error of an estimate decreases at the rate of the square root of the population size." -->

## Wisdom
### 

*Wisdom* requires the creation of a Preceptor Table, an examination of our data, and a determination, using the concept of “validity,” as to whether or not we can (reasonably!) assume that the two come from the same population.

### Exercise 1

In your own words, define a Preceptor Table.

```{r wisdom-1}
question_text(NULL,
	message = "Preceptor Table is the smallest possible table of data with rows and columns such that, if there is no missing data, then it is easy to calculate the quantities of interest.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Always start your data science work by determining what data you would like to have in order to answer the question easily.


### Exercise 2

Consider the following question: 

> If we get 17 red beads in a random sample of size 50 taken from a mixed urn, what proportion $\rho$ of the beads in the urn are red?

Our *Preceptor Table* is a table with minimal rows and columns such that we can perfectly answer our question using it. Describe the rows and the columns in a Preceptor Table which would allow us to answer this question. 

```{r wisdom-2}
question_text(NULL,
	message = "There will be one row for each bead in the urn. There will be at least one outcome column: color.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

There might be an ID column, but, strictly speaking we don't need one to answer our question.

### Exercise 3

In one sentence, describe the concept of validity as we use it.

```{r wisdom-3}
question_text(NULL,
	message = "Validity is the consistency, or lack thereof, in the columns of your dataset and the corresponding columns in your Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

We have two tables: the data which we drew from the urn and the Preceptor Table. This case is a little strange since the same rows --- i.e., the same beads --- exist in both the data and in the Preceptor Table.


### Exercise 4

Why might the assumption of "validity" not hold in this example? (You have to be very creative in order to come up with some, admittedly far-fetched, problems with validity in htis case.) 

```{r wisdom-4}
question_text(NULL,
	message = "What if there is a secret hose in the bottom of the urn feeding in new beads, including beads of colors other than red and white? This would violate the assumption of validity since, implicitly, 'color' in our data only allows for red and white while 'color' in the Preceptor Table --- meaning the urn now, after some amount of new bead insertion --- has a different meaning.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Beads from an urn is a toy example, but a useful one because all the assumption necessary for inference are trivially true. So, it is hard to come up with counter-examples. Doing so will be much easier in actual problems.



## Justice
### 

*Justice* creates the Population Table and then examines the assumptions of stability, representativeness, and unconfoundedness.

### Exercise 1

In your own words, describe the rows in the Population table and their sources.

```{r justice-1}
question_text(NULL,
	message = "The rows in the Population Table are defined by unique ID/Time combinations. We have one row for every bead in the urn, at every moment in time under consideration. The three sources are the data we collected, the Preceptor Tbale and the underlying population from which both are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The biggest different between the Preceptor Table and the Population Table is that only the latter has a notion of "time." The Preceptor Table refers to a single moment in time to which you want your answer to apply. The Population Table refers to mutiple moments in time, the two most important of which are the moment when the data is collected and the moment to which the Preceptor Table applies.

### Exercise 2

Describe the columns in the Population Table

```{r justice-2}
question_text(NULL,
	message = "There will certainly be a column for 'color', the only outcome variable. There will generally be an 'ID', 'Source' and 'Time' column.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The Population Table should look something like this:

```{r}
tibble(source = c("Population", "Population", "Population","...",  
                  "Data", "Data", "Data", "...",
                  "Population", "Population", "Population","...", 
                  "Preceptor Table", "Preceptor Table", "Preceptor Table", "...",
                  "Population", "Population", "Population"),
       time = c("Time of sample - 2 years", "Time of sample - 2 years", "Time of sample - 2 years", "...",
                "Time of sample", "Time of sample", "Time of sample", "...",
                "Time of sample + 10 days", "Time of sample + 10 days", "Time of sample + 10 days", "...",
                "Now", "Now", "Now", "...",
                "Now + 3 weeks", "Now + 3 weeks", "Now + 3 weeks"),
       id = c("1", "200", "976", "...",
              "2", "200", "1080", "...",
              "1", "200", "2025", "...",
              "1", "200", "2078", "...",
              "1", "200", "2300"),
       color = c("?", "red", "?", "...",
              "white", "red", "white", "...",
              "?", "red", "?", "...",
              "?", "red", "?", "...",
              "?", "red", "?")) |>

  # Then, we use the gt function to make it pretty

  gt() |>
  cols_label(source = md("Source"),
             time = md("Time"),
             id = md("ID"),
             color = md("Color")) |>
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(source))) |>
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"),
            locations = cells_column_labels(columns = c(source))) |>
  cols_align(align = "center", columns = everything()) |>
  cols_align(align = "left", columns = c(source)) |>
  fmt_markdown(columns = everything())
```

### Exercise 3

In one sentence explain the value for `Time` for the rows sourced from our `Data`.

```{r justice-3}
question_text(NULL,
	message = "The `Time` column for the data is listed as the time of the sample, because only one sample was taken for which we have data.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 4

In one sentence explain the value for `Time` for the rows sourced from the `Preceptor Table`.

```{r justice-4}
question_text(NULL,
	message = "The Preceptor Table has a time column of `Now`, because we want to know the contents of the urn in the present day to answer our question.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 5

In one sentence explain the value for `Time` for the rows sourced from the `Population`.

```{r justice-5}
question_text(NULL,
	message = "The Population has a time range from as far back as 2 years before the sample and up to 3 weeks into the future, because the urn sample could have theoretically been taken from anytime in the past or into the future, so a wider population must be acknowledged.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 6

In two sentences, provide a reason why the assumption of stability might not hold. (You counter-example can be far-fetched.)

```{r justice-6}
question_text(NULL,
	message = "What if someone dumps some red beads into the urn after we take our sample? Then we cannot assume stability, because the proportion of red beads in the urn, `p`, the instant before the dump is different than the proportion red in the urn after.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 7

In two sentences, give an example of why the rows in the data may not be representative of the overall population.

```{r justice-7}
question_text(NULL,
	message = "What if the person drawing the sample cheated by looking in the urn as she inserted the shovel, purposely drawing as many red beads as possible? In that case, the rows in the data would not be representative of the overall population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 8

In two sentences, give an example of why the rows in the Preceptor Table may not be representative of the overall population.

```{r justice-8}
question_text(NULL,
	message = "What if, now, the beads are not well-mixed. All the whites are at the top. If this is the case, then when we use the shovel now, we will get more whites. The new sample will not be representative of the entire urn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 9

In one or two sentences, explain why the assumption of unconfoundedness does not apply.

```{r justice-9}
question_text(NULL,
	message = "Since this is a predictive model, we do not have to worry about unconfoundedness. There is no “treatment” which might be confounded with anything.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

<!-- ## Courage -->
<!-- ###  -->

<!-- *Courage* takes the mathematical formula from *Justice* and, using code, creates a fitted model, included posterior probability distributions for all the unknown parameters. -->




## Summary
### 

This tutorial covered [Chapter 3: Sampling](https://ppbds.github.io/primer/sampling.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 
 

```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
