---
title: Sampling
author: David Kane and Gia Khang
tutorial:
  id: sampling
output:
  learnr::tutorial:
    progressive: yes
    'allow_skip:': yes
runtime: shiny_prerendered
description: 'Chapter 3 Tutorial: Sampling'
---

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(tidyverse)
library(gt)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 

# Key Data

set.seed(10)
urn <- tibble(color = c(rep("red", 400), rep("white", 600))) |>
  sample_frac() |> 
  mutate(bead_ID = 1:1000) 

virtual_samples <- tibble(trial_ID = 1:1000) |> 
  mutate(shovel = map(trial_ID, ~ sample_n(urn, size = 50))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) |> 
  mutate(numb_beads = map_int(shovel, ~ length(.$color))) |> 
  mutate(prop_red = numb_red / numb_beads)

shovels_100 <- expand_grid(trial_ID = 1:100, shovel_size = 1:100) |> 
  mutate(shovel = map(shovel_size, ~ slice_sample(urn, n = .))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) |> 
  mutate(prop_red = numb_red / shovel_size) |> 
  group_by(shovel_size) |> 
  summarize(st_dev_p_hat = sd(prop_red)) 
```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

<!-- This tutorial sticks! -->

<!-- Khang: Please fix everything! -->

<!-- Delete everything that you can't defend. -->

<!-- Add test chunks everywhere.  -->

<!-- Section about real sampling? no! -->

<!-- Add courage and temperance sections. -->

<!-- Make the Cardinal Virtues section a simpler version of the ones we use in Chapters 4 through 10. No Github for example. Use the tutorial_tempate.Rmd as much as you think wise. -->

## Introduction
### 

This tutorial covers [Chapter 3: Sampling](https://ppbds.github.io/primer/sampling.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). In this chapter, we will learn about *sampling*, the beginning of our journey toward inference. When we sample, we take some *units* from a population. With the data collected via sampling, we will create statistical models with just one unknown parameter. With such models, we can make inferences in order to answer questions. Along that journey, we learn to use the **Cardinal Virtues** to guide our actions. 


## Virtual Sampling
### 

<!-- Start by introducing related terminologies, at the end ask students to write a small paragraph to connect those terminologies together to build up an intuitive approach to the problem -->
<!-- GK: Rephrase -->
In this section, we mimic physical sampling with virtual sampling, using a computer. In a real sampling activity, we would perform a tactile sampling activity. In this we use a physical urn of beads and a physical shovel which is done by hand so that we could develop our intuition about the ideas behind sampling. 

### 

We begin this chapter with a specific problem: 
> Given an urn consists of 1,000 identically sized red and white beads in the urn, mixed well together. What proportion, $p$, of this urn's beads are red?

In this section, we will create the following plot to answer this question.

```{r}
plot_vs <- virtual_samples |> 
  ggplot(aes(x = prop_red)) +
    geom_histogram(binwidth = 0.01, 
                   boundary = 0.4, 
                   color = "white") +
    labs(x = expression(hat(p)), 
         y = "Count",
         title = "Distribution of 1,000 proportions red") 

plot_vs
```

### Exercise 1

Define the **Population** in this problem?

```{r virtual-sampling-1}
question_text(NULL,
	message = "In our sampling activities, the population is the collection 1,000 identically sized red and white beads in the urn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- Add knowledge drop about Population parameter -->


### Exercise 2

In your own word, define a **Census** in this problem? 

```{r virtual-sampling-2}
question_text(NULL,
	message = "A **Census** is an exhaustive enumeration or counting of all units in the population in order to compute the population parameter's value exactly.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 3

In your own word, explain how **Census** can help us answer our question?

```{r virtual-sampling-3}
question_text(NULL,
	message = "We can answer our question by counting the number of red beads out of the total 1,000 beads in the urn and then computing the proportion of red beads.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Assuming zero error when counting, this method will return the **exact** portion of red beads in the urn. However, it can be quite expensive in terns of time, energy and money when the population is large or even impossible. 

### Exercise 4

In two sentences, describe the act of **Sampling** and what is the **Sample** in this problem?


```{r virtual-sampling-4}
question_text(NULL,
	message = "Sampling is the act of collecting a sample from the population. In our sampling activity, we use the shovels to collect a certain number of beads from the urn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 5

In your own words, define what is necessary for a sample to be **representative**?

```{r virtual-sampling-5}
question_text(NULL,
	message = "Place correct answer here.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- Add knowledge drop about what can't we do if the sample is not representative  -->

### Exercise 6

In your own words, define what is necessary for a sample to be **generalizable**? 

```{r virtual-sampling-6}
question_text(NULL,
	message = "Place correct answer here.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- Add knowledge drop about what can't we do if the sample is not generalizable  -->


### Exercise 7

In your own words, define **biased sampling**.
```{r virtual-sampling-7}
question_text(NULL,
	message = "Place correct answer here.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 8

Provide one example for this problem where the sampling could be **biased**.

```{r virtual-sampling-8}
question_text(NULL,
	message = "Had the red beads been much smaller than the white beads, and therefore more prone to falling out of the shovel, our sample would have been biased.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

In our sampling activities, since we mixed all 1,000 beads prior to each group’s sampling and since each of the equally sized beads had an equal chance of being sampled, our samples were unbiased.

### Exercise 9

In your own word, define when a sampling procedure is *random* in this specific problem. 


```{r virtual-sampling-9}
question_text(NULL,
	message = "Sampling procedure is random if we sample randomly from the population in an unbiased fashion. In our sampling activities, this would correspond to sufficiently mixing the urn before each use of the shovel.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- The knowledge drop in each exercise can be combined to construct the paragraph.  -->

### Exercise 10

Write a few sentences to summarize our approach to answer the question, use the knowledge drop in each exercise to guide your answer. 

```{r virtual-sampling-10}
question_text(NULL,
	message = "Place correct answer here.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 11

Create a `urn` variable on the second line that is set to a `tibble()`. Within the `tibble()` set `color` to the combination of `rep("red", 400)` and `rep("white", 600)`.

```{r virtual-sampling-11, exercise = TRUE}
set.seed(10)

```

```{r virtual-sampling-11-hint-1, eval = FALSE}
set.seed(10)
urn <- tibble(... = c(rep("...", ...), 
                        rep("...", ...)))
```

```{r virtual-sampling-11-test, include = FALSE}
set.seed(10)
urn <- tibble(color = c(rep("red", 400), 
                        rep("white", 600)))
```

### 

`set.seed()` ensures that the beads in our virtual urn are always in the same order. This ensures that the figures in the book match their written descriptions. We want 40% of the beads to be red. The `rep()` function will repeat the first argument a number of times specified by the second argument. We then combine our 400 red beads and 600 white beads using `c()`.

### Exercise 12

Within the `urn` variable start a pipe and set it to `sample_frac()`.

```{r virtual-sampling-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-12-hint-1, eval = FALSE}
urn <- ... |>
          sample_frac()
```

```{r virtual-sampling-12-test, include = FALSE}
urn <- tibble(color = c(rep("red", 400), 
                        rep("white", 600))) |> 
  sample_frac()
```

### 

`sample_frac()` keeps all the rows in the tibble but rearranges their order. We don't need to do this. A virtual urn does not care about the order of the beads. But we find it aesthetically pleasing to mix them up.

### Exercise 13

Finish the pipe with `mutate()` and set `bead_ID` to 1 through 1000.

```{r virtual-sampling-13, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-13-hint-1, eval = FALSE}
urn <- ... |>
          mutate(... = 1:1000)
```

```{r virtual-sampling-13-test, include = FALSE}
urn <- tibble(color = c(rep("red", 400), 
                        rep("white", 600))) |> 
  sample_frac() |> 
  mutate(bead_ID = 1:1000)
```

### 

The first variable `bead_ID` is used as an identification variable. None of the beads in the actual urn are marked with numbers. The second variable `color` indicates whether a particular virtual bead is red or white.

### Exercise 14

To simulate the process of real-world sampling, let’s take a sample of 50 beads from our virtual urn. To do so, create a `tibble()` that has one variable `trial_ID` that takes on the values 1 to 1000.

```{r virtual-sampling-14, exercise = TRUE}

```

```{r virtual-sampling-14-hint-1, eval = FALSE}
tibble(trial_ID = ...)
```

```{r virtual-sampling-14-hint-2, eval = FALSE}
Use the : operator to create a range of integers.
```

```{r virtual-sampling-14-test, include = FALSE}
tibble(trial_ID = 1:1000)
```

### Exercise 15

<!-- GK: Should be separate into smaller questions -->

Now pipe your results to the function `mutate()` to create the variable `shovel`, which is set to the function `map()`. The first argument to `map()` should be `trial_ID`. The second argument should use `slice_sample()`. Within `slice_sample()`, the first argument should be `urn` (the data we want to sample from), and then set `n` equal to our sample size (we want a sample size of 50). 

```{r virtual-sampling-15, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-15-hint-1, eval = FALSE}
... |> 
  mutate(shovel = map(..., ~ ...))
```

```{r virtual-sampling-15-hint-2, eval = FALSE}
... |> 
  mutate(shovel = map(..., ~slice_sample(urn, n = ...)))
```

```{r virtual-sampling-15-test, include = FALSE}
tibble(trial_ID = 1:1000) |> 
  mutate(shovel = map(trial_ID, ~ slice_sample(urn, n = 50)))
```

### 

The advantage of modern technology is that we can use virtual simulation as many times as we choose, so we have no restrictions on resources. No longer are the days where we have to recruit our friends to tirelessly sample from the physical urn.

### Exercise 16

Continue your pipe with `mutate()` to create the variable `numb_red`. Set `numb_red` to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `sum()` of where `.$color` is equal to red.

```{r virtual-sampling-16, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-16-hint-1, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~...))
```

```{r virtual-sampling-16-hint-2, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~ sum(.$color == "red")))
```

```{r virtual-sampling-16-test, include = FALSE}
tibble(trial_ID = 1:1000) |> 
  mutate(shovel = map(trial_ID, ~ slice_sample(urn, n = 50))) |> 
  mutate(numb_red = map_int(shovel, ~sum(.$color == "red")))
```

### 

R evaluates if `color == red`, and treats `TRUE` values like the number `1` and `FALSE` values like the number `0`. So summing the number of `TRUE`s and `FALSE`s is equivalent to summing `1`’s and `0`’s. In the end, this operation counts the number of beads where `color` equals “red”.

### Exercise 17

Use `mutate()` one last time to create the variable `prop_red`. Set `prop_red` to `numb_red` divided by the sample size (in this exercise we are using a set sample size of 50).

```{r virtual-sampling-17, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-17-hint-1, eval = FALSE}
... |> 
   mutate(prop_red = ... / ...)
```

```{r virtual-sampling-17-test, include = FALSE}
tibble(trial_ID = 1:1000) |> 
  mutate(shovel = map(trial_ID, ~ slice_sample(urn, n = 50))) |> 
  mutate(numb_red = map_int(shovel, ~sum(.$color == "red"))) |> 
  mutate(prop_red = numb_red / 50)
```

### 

`prop_red` estimate's our proportion of red beads in the urn.

### Exercise 18

Assign your code from above to an object named `virtual_samples`.

```{r virtual-sampling-18, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-18-hint-1, eval = FALSE}
Use the assignment operator <-  to do so.
```

```{r virtual-sampling-18-test, include = FALSE}
virtual_samples <- tibble(trial_ID = 1:1000) |> 
  mutate(shovel = map(trial_ID, ~ slice_sample(urn, n = 50))) |> 
  mutate(numb_red = map_int(shovel, ~sum(.$color == "red"))) |> 
  mutate(prop_red = numb_red / 50)
```

### Exercise 19

Now start a pipe with `virtual_samples`. Use `ggplot()` to map `prop_red` to the x-axis.

```{r virtual-sampling-19, exercise = TRUE}

```

```{r virtual-sampling-19-hint-1, eval = FALSE}
virtual_samples |> 
  ggplot(aes(...))
```

```{r virtual-sampling-19-test, include = FALSE}
virtual_samples |> 
  ggplot(aes(x = prop_red))
```

### Exercise 20

Add the layer `geom_histogram()` to create a histogram of our data.

```{r virtual-sampling-20, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-20-hint-1, eval = FALSE}
... +
  geom_histogram()
```

```{r virtual-sampling-20-test, include = FALSE}
virtual_samples |> 
  ggplot(aes(x = prop_red)) + 
  geom_histogram()
```

### Exercise 21

Within `geom_histrogram()` set `binwidth` to .01, `boundary` to .4, and `color` to "white".

```{r virtual-sampling-21, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-21-hint-1, eval = FALSE}
... +
  geom_histrogram(binwidth = ..., boundary = ..., color = ...)
```

```{r virtual-sampling-21-test, include = FALSE}
virtual_samples |> 
ggplot(aes(x = prop_red)) +
  geom_histogram(binwidth = 0.01, 
                 boundary = 0.4, 
                 color = "white")
```

### 

Recall that `p` is equal to the proportion of beads which are red in each sample.

### Exercise 22

To finish, use `labs()` to give your graph the appropriate title and axis labels. See **hint** for guidance to create the symbol $\hat{p}$.

```{r virtual-sampling-22, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like. 

```{r}
plot_vs
```

```{r virtual-sampling-22-hint-1, eval = FALSE}
Within labs(), set x to expression(hat(p))
```

```{r virtual-sampling-22-test, include = FALSE}
virtual_samples |> 
ggplot(aes(x = prop_red)) +
  geom_histogram(binwidth = 0.01, 
                 boundary = 0.4, 
                 color = "white") +
  labs(x = expression(hat(rho)),
       y = "Count",
       title = "Distribution of 1,000 proportions red") 
```

### 

This visualization allows us to see how our results differed between our tactile and virtual urn results. As we can see, there is some variation between our results. This is not a cause for concern, as there is always expected sampling variation between results.


## Standard error of different shovel sizes
### 

<!-- MT: add questions about the definitions/important concepts of standard error -->

Standard errors (SE) quantify the effect of sampling variation on our estimates. In other words, they quantify how much we can expect the calculated proportions of a shovel’s beads that are red to vary from one sample to another sample to another sample, and so on. As a general rule, as sample size increases, the standard error decreases.

### 

In this section, we will create the following plot that displays different standard deviations of red bead proportions for 100 different shovel sizes.

```{r}
shovel_p <- shovels_100 |>
 ggplot(aes(x = shovel_size, y = st_dev_p_hat)) +
 geom_point() +
 labs(title = "Sampling Variation",
      subtitle = "Larger samples have less variation",
      x = "Shovel size",
      y = "Standard deviation of the proportion red")

shovel_p
```

### Exercise 1

In your own word, define *Standard error*.

```{r standard-error-of-different-sh-1}
question_text(NULL,
	message = "The standard error is the standard deviation of a sample statistic (aka point estimate), such as the proportion. For example, the standard error of the mean refers to the standard deviation of the distribution of sample means taken from a population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

<!-- GK: Need paraphrase, does not understand -->
First, let's use `expand_grid()` to create the foundation of our tibble. Our first column in `expand_grid()` should be called `trial_ID`, and it should be the range of integers between 1 and 1,000. The second column should be called `shovel_size`, and should be the range of integers between 1 and 100.

```{r standard-error-of-different-sh-2, exercise = TRUE}

```

```{r standard-error-of-different-sh-2-hint-1, eval = FALSE}
expand_grid(trial_ID = ..., shovel_size = ...)
```

```{r standard-error-of-different-sh-2-hint-2, eval = FALSE}
Use the : operator to create a range of integers. 
```

```{r standard-error-of-different-sh-2-test, include = FALSE}
expand_grid(trial_ID = c(1:1000), shovel_size = c(1:100))
```

### 

### Exercise 3

Continue the pipe with `mutate()`, creating a new column called `shovel`. Set `shovel` equal to a `map()` function, passing in `shovel_size` as the first argument, and the `slice_sample()` function as the second argument. Within `slice_sample()`, the first argument should be `urn` (the data we want to sample from), and then set `n` equal to `.` (we want to pass in the `shovel_size` using `map()`).

```{r standard-error-of-different-sh-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-3-hint-1, eval = FALSE}
... |>
  mutate(shovel = map(..., ~ ... ))
```

```{r standard-error-of-different-sh-3-hint-2, eval = FALSE}
... |>
  mutate(shovel = map(... , ~ slice_sample(..., n = ...)))
```

```{r standard-error-of-different-sh-3-test, include = FALSE}
expand_grid(trial_ID = c(1:1000), shovel_size = c(1:100)) |> 
  mutate(shovel = map(shovel_size, ~ slice_sample(urn, n = .)))
```

### 

### Exercise 4

Continue your pipe with `mutate()` to create the variable `numb_red`, which will tells us the number of red beads present. Set `numb_red` to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `sum()` of where the column `color` of `shovel` is equal to red.

```{r standard-error-of-different-sh-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-4-hint-1, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~ ...))
```

```{r standard-error-of-different-sh-4-hint-2, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~ sum(.$color == "red")))
```

```{r standard-error-of-different-sh-4-test, include = FALSE}
expand_grid(trial_ID = c(1:1000), shovel_size = c(1:100)) |> 
  mutate(shovel = map(shovel_size, ~ slice_sample(urn, n = .))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red")))
```

### Exercise 5

Continue your pipe from above, using `mutate()` to create one final column called `prop_red` which represents the proportion of red beads in a sample. Set `prop_red` to `numb_red` divided by the `shovel_size` column. 

```{r standard-error-of-different-sh-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-5-hint-1, eval = FALSE}
... |>
  mutate(prop_red = ... / ...)
```

```{r standard-error-of-different-sh-5-test, include = FALSE}
expand_grid(trial_ID = c(1:1000), shovel_size = c(1:100)) |> 
  mutate(shovel = map(shovel_size, ~ slice_sample(urn, n = .))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) |> 
  mutate(prop_red = numb_red / shovel_size)
```

### Exercise 6

Great. Continue your pipe and use the `group_by()` function to group our tibble by `shovel_size`. 

```{r standard-error-of-different-sh-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-6-hint-1, eval = FALSE}
... |>
  group_by(...)
```

```{r standard-error-of-different-sh-6-test, include = FALSE}
expand_grid(trial_ID = c(1:1000), shovel_size = c(1:100)) |> 
  mutate(shovel = map(shovel_size, ~ slice_sample(urn, n = .))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) |> 
  mutate(prop_red = numb_red / shovel_size) |> 
  group_by(shovel_size)
```

### Exercise 7

Continue your pipe one last time, and use `summarize()` to create a new column named `st_dev_p_hat` which is equal to the standard deviation of `prop_red`. (`sd()` calculates standard deviation).
 

```{r standard-error-of-different-sh-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-7-hint-1, eval = FALSE}
... |> 
  summarize(st_dev_p_hat = sd(...))
```

```{r standard-error-of-different-sh-7-test, include = FALSE}
expand_grid(trial_ID = c(1:1000), shovel_size = c(1:100)) |> 
  mutate(shovel = map(shovel_size, ~ slice_sample(urn, n = .))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) |> 
  mutate(prop_red = numb_red / shovel_size) |> 
  group_by(shovel_size) |> 
  summarize(st_dev_p_hat = sd(prop_red))
```

### Exercise 8

Assign your code from above to an object named `shovels_100`.

```{r standard-error-of-different-sh-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-8-hint-1, eval = FALSE}
Use the assignment operator <-  to do so.
```

```{r standard-error-of-different-sh-8-test, include = FALSE}
shovels_100 <- expand_grid(trial_ID = c(1:1000), shovel_size = c(1:100)) |> 
  mutate(shovel = map(shovel_size, ~ slice_sample(urn, n = .))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) |> 
  mutate(prop_red = numb_red / shovel_size) |> 
  group_by(shovel_size) |> 
  summarize(st_dev_p_hat = sd(prop_red))
```

### Exercise 9

Start a new pipe from `shovels_100`. Use `ggplot()`to map `shovel_size` to the x-axis and `st_dev_p_hat` to the y axis. Also, add the layer `geom_point()` to create a scatterplot.

```{r standard-error-of-different-sh-9, exercise = TRUE}

```

```{r standard-error-of-different-sh-9-hint-1, eval = FALSE}
shovels_100 |> 
  ggplot(aes(x = ..., y = ...)) + 
  geom_point()
```

```{r standard-error-of-different-sh-9-test, include = FALSE}
shovels_100 |> 
  ggplot(aes(x = shovel_size, y = st_dev_p_hat)) + 
  geom_point()
```

### Exercise 10

Now use `labs()` to label the x-axis "Shovel size" and the y-axis 
"Standard deviation of the proportion red". You should also provide a title and subtitle.

```{r standard-error-of-different-sh-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like.

```{r}
shovel_p
```

```{r standard-error-of-different-sh-10-hint-1, eval = FALSE}
... +
   labs(title = "Sampling Variation",
      subtitle = "Larger samples have less variation",
      x = "Shovel size",
      y = "Standard deviation of the proportion red")
```

```{r standard-error-of-different-sh-10-test, include = FALSE}
shovels_100 |> 
  ggplot(aes(x = shovel_size, y = st_dev_p_hat)) + 
  geom_point() + 
  labs(title = "Sampling Variation",
      subtitle = "Larger samples have less variation",
      x = "Shovel size",
      y = "Standard deviation of the proportion red")
```

### 

### Exercise 11

In one sentence, explain what you learn from the graph.

```{r standard-error-of-different-sh-11}
question_text(NULL,
	answer("The standard error of an estimate decreases at the rate of the square root of the population size.", correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

## Wisdom
### 

*All we can know is that we know nothing. And that’s the height of human wisdom.* - Leo Tolstoy

We have an urn with red and white beads. We do not know the number of beads in total, nor the breakdown between red and white. 

> *We are interested in the number of white and red beads which will come out of the urn in the future.*

### 

We drew a sample of 50 beads from the urn. 17 of them where red. 

> *What proportion of beads in the urn are red?*

### Exercise 1

In your own words, describe the key components of Wisdom when working on a data science problem.

```{r wisdom-1}
question_text(NULL,
	message = "Wisdom requires the creation of a Preceptor Table, an examination of our data, and a determination, using the concept of validity, as to whether or not we can (reasonably!) assume that the two come from the same population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: You have the opportunity, in this and the next few questions, to drop a lot of knowledge about the data and the overall topic. Do so! But, remember, students won't read more than 2 or so sentences in a knowledge drop. -->

<!-- Not only are you discussing the data, but you are also discussing potential problems with the data, problems which will be more fully fleshed out in the Justice section. You want to pick 5 to 10 interesting facts about the data. (You may need to go to the original source, not simply relying on the chapter.) 

You won't be drawing any conclusions or pointing out any problems. That discussion is saved until Justice and the specific questions about stability and representativeness. You are, hwoever, providing the details which you and the students can then use later. -->

### Exercise 2

Define a Preceptor Table.

```{r wisdom-2}
question_text(NULL,
	message = "A Preceptor Table is the smallest possible table of data with rows and columns such that, if there is no missing data, we can easily calculate the quantities of interest.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 3

Describe the key components of Preceptor Tables in general, without worrying about this specific problem. Use words like "units," "outcomes," and "covariates."

```{r wisdom-3}
question_text(NULL,
	message = "The rows of the Preceptor Table are the units. The outcome is at least one of the columns. If the problem is causal, there will be at least two (potential) outcome columns. The other columns are covariates. If the problem is causal, at least one of the covariates will be a treatment.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 4

What are the units for this problem?

```{r wisdom-4}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 5

What is/are the outcome/outcomes for this problem?

```{r wisdom-5}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 6

<!-- XX. You will probably need to make this question much more specific. In other words, you want the student to list some of the covariates that are available for him to consider. We are not just looking for the select few covariates which will end up in the model. Maybe some EDA needs to come first? -->

<!-- This is a lousy question! Which meaning of covariates do you intend? -->

What are some covariates which you think might be useful for this problem?

```{r wisdom-6}
question_text(NULL,
	message = "XX. Answer should be some sensible variables which are plausibly connected to the outcome. Some should be in the data but some shouldn't. You might also add that `You need to have variable X` if the question itself mentions that variable.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 7

What are the treatments, if any, for this problem?

```{r wisdom-7}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 8

What moment in time does the Preceptor Table refer to?

```{r wisdom-8}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Next three questions are only included for a causal model. -->

### Exercise 9

Define causal effect.

```{r wisdom-9}
question_text(NULL,
	message = "A causal effect is the difference between two potential outcomes.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 10

What is the fundamental problem of causal inference?

```{r wisdom-10}
question_text(NULL,
	message = "The fundamental problem of causal inference is that we can only observe one potential outcome.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 11

How does the motto "No causal inference without manipulation." apply in this problem?

```{r wisdom-11}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: End causal model section. If there is not one, you will need to run Format Tutorial Chunk Labels in order to renumber the exercises once you delete these.  -->

### Exercise 12

<!-- XX: It is a feature that this question almost forces students to go to the chapter and read about the data. This entire sentence will not be included in your summary at the end of Wisdom, but bits of it will be mentioned. -->

Write one sentence describing the data you have to answer your question.

```{r wisdom-12}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 13

Load the **tidyverse** package.

```{r wisdom-13, exercise = TRUE}

```

```{r wisdom-13-hint-1, eval = FALSE}
library(...)
```

```{r wisdom-13-test, include = FALSE}
library(tidyverse)
```

### 

<!-- XX: Insert comments about the data. -->

<!-- XX: Load any other packages that are needed, one package per question. (But make sure that they are also included in the setup chunk.) primer.data, for example, is often needed. But save brms and tidybayes for the Courage section. -->

<!-- XX: Add questions about EDA with your data. In particular, add at least one question about the dependent variable in the model along with one or more questions about covariates. If there is a treatment variable, you must include a question about it. -->

<!-- Variable questions come in two types. First there are questions which require the student to run, say, summary() on the variable. Then, knowledge about the variable can be dropped. Second, there are questions which ask for a one sentence summary about the variable, something which could be used in our summary of the project. For example: "Civility is measured on a 1 through 7 scale with higher values corresponding to greater civility." -->

### Exercise 14

In your own words, define "validity" as we use the term.

```{r wisdom-14}
question_text(NULL,
	message = "Validity is the consistency, or lack thereof, in the columns of the data set and the corresponding columns in the Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 15

What can't we do if the assumption of validity is not true?

```{r wisdom-15}
question_text(NULL,
	message = "We can't combine the Preceptor Table and the data in order to construct the Population Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 16

Provide one reason why the assumption of validity might not hold for this problem.

```{r wisdom-16}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 17

<!-- XX: In creating your own answer to questions like this, check with the chapter. One might already be provided! If not, it is often useful to revisit the relevant section of the Key Concepts chapter in the Primer. -->

<!-- Example: *Using data from a 2012 survey of Boston-area commuters, we seek to understand the relationship between income and political ideology in Chicago and similar cities in 2020. In particular, what percentage of individuals who make more than $100,000 per year are liberal?* -->

Summarize the state of your work so far in one sentence. Make reference to the data you have and to the specific question you are trying to answer. 


```{r wisdom-17}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

## Justice
### 

<!-- XX: Choose one. -->

*Justice is truth in action.* - Benjamin Disraeli
*The arc of the moral universe is long, but it bends toward justice.* - Theodore Parker
*Justice delayed is justice denied.* - William E. Gladstone
*It is in justice that the ordering of society is centered.* - Aristotle
*Charity is no substitute for justice withheld.* - Saint Augustine

### Exercise 1

In your own words, name the four key components of Justice for working on a data science problem.

```{r justice-1}
question_text(NULL,
	message = "Justice concerns four topics: the Population Table, stability, representativeness, and unconfoundedness.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

In your own words, define a Population Table.

```{r justice-2}
question_text(NULL,
	message = "The Population Table includes a row for each unit/time combination in the underlying population from which both the Preceptor Table and the data are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 3

In your own words, define the assumption of "stability" when employed in the context of data science.

```{r justice-3}
question_text(NULL,
	message = "Stability means that the relationship between the columns in the Population Table is the same for three categories of rows: the data, the Preceptor Table, and the larger population from which both are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Keep just one of these two. -->

<!-- Stability is all about *time*. Is the relationship among the columns in the Population Table stable over time? In particular, is the relationship --- which is another way of saying "mathematical formula" --- at the time the data was gathered the same as the relationship at the (generally later) time references by the Preceptor Table. -->

<!-- *The longer the time period covered by the Preceptor Table (and the data), the more suspect the assumption of stability becomes.*  -->

### Exercise 4

Provide one reason why the assumption of stability might not be true in this case.

```{r justice-4}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 5

In your own words, define the assumption of "representativeness" when employed in the context of data science.

```{r justice-5}
question_text(NULL,
	message = "Representativeness, or the lack thereof, concerns two relationship, among the rows in the Population Table. The first is between the Preceptor Table and the other rows. The second is between our data and the other rows.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Keep one of these. -->

<!-- Ideally, we would like both the Preceptor Table *and* our data to be random samples from the population. Sadly, this is almost never the case. -->

<!-- Stability looks across time periods. Reprentativeness looks within time periods. -->

<!-- The more expansive your Preceptor Table, the more important the assumption of representativeness becomes. -->

### Exercise 6

Provide one reason why the assumption of representativeness might not be true in this case.

```{r justice-6}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 7

In your own words, define the assumption of "unconfoundedness" when employed in the context of data science.

```{r justice-7}
question_text(NULL,
	message = "Unconfoundedness means that the treatment assignment is independent of the potential outcomes, when we condition on pre-treatment covariates.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Keep one. -->

<!-- This assumption is only relevant for causal models. We describe a model as "confounded" if this is not true.  -->

<!-- The easiest way to ensure unconfoundedness is to assign treatment randomly. -->

### Exercise 8

<!-- XX: Delete this question for non-causal models. -->

Provide one reason why the assumption of unconfoundedness might not be true (or relevant) in this case.

```{r justice-8}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 9

Summarize the state of your work so far in two or three sentences. Make reference to the data you have and to the question you are trying to answer. Feel free to copy from your answer at the end of the Wisdom Section. Mention one specific problem which casts doubt on your approach. 


```{r justice-9}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

## Courage
### 

*Courage is the commitment to begin without any guarantee of success.* - Johann Wolfgang von Goethe


### Exercise 1

In your own words, describe the components of the virtue of Courage for analyzing data.

```{r courage-1}
question_text(NULL,
	message = "Emboldened by Courage, we model the outcome variable as a function of the covariates. We test our model for consistency with the data we have. We create a Data Generating Mechanism.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

Write a few sentence which summarize your work so far. The first few sentences are the same as what you had at the end of the Justice Section. Add one sentence which describes the modelling approach which you are using, specifying the functional form and the dependent variable. Add one sentence which describes the *direction* (not the magnitude) of the relationship between one of your independent variables and your dependent variable.

```{r courage-2}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

## Temperance
### 

<!-- XX: Discuss newdata objects slowly. "A newdata tibble must include columns for all the right-hand side variables --- all the "covariates" --- in the model, and with all the same variable names and, mostly, variable types." 

First ask a question about which columns are needed in the newdata object. This might just be a written question. The answer is all the variables which are on the rightside of the formula. 

Second, ask a question about which values you want those variables to have. That is not easy! Again, a written answer. For each row in the newdata tibble, you get a new posterior. How many posteriors do you want? 

Third, give them the R code which creates the newdata object. All they need to do is run it. Asking them to create it, even after you help them figure out the columns (question 1) and rows (question 2) is too hard, at least until they get more experiences. 

Fourth, inform them that you have, behind the scenes (which really means the setup code chunk), already assigned this tibble to the `ndata` object. In this question, they just type `ndata` to confirm. 

The knowledge drops for all four of these questions allow you to explain/teach more about what goes in the argument for newdata and what does not. Explaining what other newdata objects would produce, if we used them, is a good idea.

-->

<!-- XX: Choose one. -->

*Temperance is a tree which as for its root very little contentment, and for its fruit calm and peace.* - Buddha
*Temperance is the greatest of all virtues. It subdues every passion and emotion, and almost creates a Heaven upon Earth.* - Joseph Smith Jr.
*Temperance is a bridle of gold; he, who uses it rightly, is more like a god than a man.* - Robert Burton
*Temperance is the firm and moderate dominion of reason over passion and other unrighteous impulses of the mind.* - Marcus Tullius Cicero
*Temperance to be a virtue must be free, and not forced.* - Philip Massinger
*Temperance is simply a disposition of the mind which binds the passion.* - Thomas Aquinas

<!--  -->

### Exercise 1

In your own words, describe the use of Temperance in finishing your data science project.

```{r temperance-1}
question_text(NULL,
	message = "Temperance uses the Data Generating Mechanism to answer the question with which we began. Humility reminds us that this answer is always a lie.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

Recall the question with which we began:

> ...

Pipe `fit_XX` to . . .

```{r temperance-2, exercise = TRUE}

```

```{r temperance-2-hint-1, eval = FALSE}

```

```{r temperance-2-test, include = FALSE}

```

### 

### Exercise 3

Write a paragraph which summarizes the project in your own words. The first few sentences are the same as what you had at the end of the Courage Section. But, since your question may have evolved, you should feel free to change those sentences. Add at least one sentence which describes at least one quantity of interest (QoI) --- presumably one that answers your question -- and which provides a measure of uncertainty about that QoI. 

```{r temperance-3}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 4

Write a few sentences which explain why the estimates for the quantities of interest, and the uncertainty thereof, might be wrong. Suggest an alternative estimate and confidence interval.

```{r temperance-4}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

## Summary
### 

This tutorial covered [Chapter 3: Sampling](https://ppbds.github.io/primer/sampling.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 
 

```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
