---
title: Sampling
author: Ryan Southward, Mann Talati and David Kane
tutorial:
  id: sampling
output:
  learnr::tutorial:
    progressive: yes
    'allow_skip:': yes
runtime: shiny_prerendered
description: 'Chapter 3 Tutorial: Sampling'
---

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(tidyverse)
library(gt)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 

# Key Data

set.seed(10)
urn <- tibble(color = c(rep("red", 400), rep("white", 600))) |>
  sample_frac() |> 
  mutate(bead_ID = 1:1000) 

virtual_samples <- tibble(trial_ID = 1:1000) |> 
  mutate(shovel = map(trial_ID, ~ sample_n(urn, size = 50))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) |> 
  mutate(numb_beads = map_int(shovel, ~ length(.$color))) |> 
  mutate(prop_red = numb_red / numb_beads)

shovels_100 <- expand_grid(trial_ID = 1:100, shovel_size = 1:100) |> 
  mutate(shovel = map(shovel_size, ~ slice_sample(urn, n = .))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) |> 
  mutate(prop_red = numb_red / shovel_size) |> 
  group_by(shovel_size) |> 
  summarize(st_dev_p_hat = sd(prop_red)) 
```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

<!-- This tutorial sticks! -->

<!-- Khang: Please fix everything! -->

<!-- Delete everything that you can't defend. -->

<!-- Add test chunks everywhere.  -->

<!-- Section about real sampling? no! -->

<!-- Add courage and temperance sections. -->

<!-- Make the Cardinal Virtues section a simpler version of the ones we use in Chapters 4 through 10. No Github for example. Use the tutorial_tempate.Rmd as much as you think wise. -->

## Introduction
### 

This tutorial covers [Chapter 3: Sampling](https://ppbds.github.io/primer/sampling.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). In this chapter, we will learn about *sampling*, the beginning of our journey toward inference. When we sample, we take some *units* from a population. With the data collected via sampling, we will create statistical models with just one unknown parameter. With such models, we can make inferences in order to answer questions. Along that journey, we learn to use the **Cardinal Virtues** to guide our actions. 


## Virtual Sampling
### 

<!-- Start by introducing related terminologies, at the end ask students to write a small paragraph to connect those terminologies together to build up an intuitive approach to the problem -->
<!-- GK: Rephrase -->
In this section, we mimic physical sampling with virtual sampling, using a computer. In a real sampling activity, we would perform a tactile sampling activity. In this we use a physical urn of beads and a physical shovel which is done by hand so that we could develop our intuition about the ideas behind sampling. 

### 

We begin this chapter with a specific problem: 
> Given an urn consists of 1,000 identically sized red and white beads in the urn, mixed well together. What proportion, $p$, of this urn's beads are red?

In this section, we will create the following plot to answer this question.

```{r}
plot_vs <- virtual_samples |> 
  ggplot(aes(x = prop_red)) +
    geom_histogram(binwidth = 0.01, 
                   boundary = 0.4, 
                   color = "white") +
    labs(x = expression(hat(p)), 
         y = "Count",
         title = "Distribution of 1,000 proportions red") 

plot_vs
```

### Exercise 1

Define the **Population** in this problem?

```{r virtual-sampling-1}
question_text(NULL,
	message = "In our sampling activities, the population is the collection 1,000 identically sized red and white beads in the urn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- Add knowledge drop about Population parameter -->


### Exercise 2

In your own word, define a **Census** in this problem? 

```{r virtual-sampling-2}
question_text(NULL,
	message = "A **Census** is an exhaustive enumeration or counting of all units in the population in order to compute the population parameter's value exactly.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 3

In your own word, explain how **Census** can help us answer our question?

```{r virtual-sampling-3}
question_text(NULL,
	message = "We can answer our question by counting the number of red beads out of the total 1,000 beads in the urn and then computing the proportion of red beads.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Assuming zero error when counting, this method will return the **exact** portion of red beads in the urn. However, it can be quite expensive in terns of time, energy and money when the population is large or even impossible. 

### Exercise 4

In two sentences, describe the act of **Sampling** and what is the **Sample** in this problem?


```{r virtual-sampling-4}
question_text(NULL,
	message = "Sampling is the act of collecting a sample from the population. In our sampling activity, we use the shovels to collect a certain number of beads from the urn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 5

In your own words, define what is necessary for a sample to be **representative**?

```{r virtual-sampling-5}
question_text(NULL,
	message = "Place correct answer here.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- Add knowledge drop about what can't we do if the sample is not representative  -->

### Exercise 6

In your own words, define what is necessary for a sample to be **generalizable**? 

```{r virtual-sampling-6}
question_text(NULL,
	message = "Place correct answer here.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- Add knowledge drop about what can't we do if the sample is not generalizable  -->


### Exercise 7

In your own words, define **biased sampling**.
```{r virtual-sampling-7}
question_text(NULL,
	message = "Place correct answer here.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 8

Provide one example for this problem where the sampling could be **biased**.

```{r virtual-sampling-8}
question_text(NULL,
	message = "Had the red beads been much smaller than the white beads, and therefore more prone to falling out of the shovel, our sample would have been biased.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

In our sampling activities, since we mixed all 1,000 beads prior to each group’s sampling and since each of the equally sized beads had an equal chance of being sampled, our samples were unbiased.

### Exercise 9

In your own word, define when a sampling procedure is *random* in this specific problem. 


```{r virtual-sampling-9}
question_text(NULL,
	message = "Sampling procedure is random if we sample randomly from the population in an unbiased fashion. In our sampling activities, this would correspond to sufficiently mixing the urn before each use of the shovel.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- The knowledge drop in each exercise can be combined to construct the paragraph.  -->

### Exercise 10

Write a few sentences to summarize our approach to answer the question, use the knowledge drop in each exercise to guide your answer. 

```{r virtual-sampling-10}
question_text(NULL,
	message = "Place correct answer here.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 11

Create a `urn` variable on the second line that is set to a `tibble()`. Within the `tibble()` set `color` to the combination of `rep("red", 400)` and `rep("white", 600)`.

```{r virtual-sampling-11, exercise = TRUE}
set.seed(10)

```

```{r virtual-sampling-11-hint-1, eval = FALSE}
set.seed(10)
urn <- tibble(... = c(rep("...", ...), 
                        rep("...", ...)))
```

```{r virtual-sampling-11-test, include = FALSE}
set.seed(10)
urn <- tibble(color = c(rep("red", 400), 
                        rep("white", 600)))
```

### 

`set.seed()` ensures that the beads in our virtual urn are always in the same order. This ensures that the figures in the book match their written descriptions. We want 40% of the beads to be red. The `rep()` function will repeat the first argument a number of times specified by the second argument. We then combine our 400 red beads and 600 white beads using `c()`.

### Exercise 12

Within the `urn` variable start a pipe and set it to `sample_frac()`.

```{r virtual-sampling-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-12-hint-1, eval = FALSE}
urn <- ... |>
          sample_frac()
```

```{r virtual-sampling-12-test, include = FALSE}
urn <- tibble(color = c(rep("red", 400), 
                        rep("white", 600))) |> 
  sample_frac()
```

### 

`sample_frac()` keeps all the rows in the tibble but rearranges their order. We don't need to do this. A virtual urn does not care about the order of the beads. But we find it aesthetically pleasing to mix them up.

### Exercise 13

Finish the pipe with `mutate()` and set `bead_ID` to 1 through 1000.

```{r virtual-sampling-13, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-13-hint-1, eval = FALSE}
urn <- ... |>
          mutate(... = 1:1000)
```

```{r virtual-sampling-13-test, include = FALSE}
urn <- tibble(color = c(rep("red", 400), 
                        rep("white", 600))) |> 
  sample_frac() |> 
  mutate(bead_ID = 1:1000)
```

### 

The first variable `bead_ID` is used as an identification variable. None of the beads in the actual urn are marked with numbers. The second variable `color` indicates whether a particular virtual bead is red or white.

### Exercise 14

To simulate the process of real-world sampling, let’s take a sample of 50 beads from our virtual urn. To do so, create a `tibble()` that has one variable `trial_ID` that takes on the values 1 to 1000.

```{r virtual-sampling-14, exercise = TRUE}

```

```{r virtual-sampling-14-hint-1, eval = FALSE}
tibble(trial_ID = ...)
```

```{r virtual-sampling-14-hint-2, eval = FALSE}
Use the : operator to create a range of integers.
```

```{r virtual-sampling-14-test, include = FALSE}
tibble(trial_ID = 1:1000)
```

### Exercise 15

<!-- GK: Should be separate into smaller questions -->

Now pipe your results to the function `mutate()` to create the variable `shovel`, which is set to the function `map()`. The first argument to `map()` should be `trial_ID`. The second argument should use `slice_sample()`. Within `slice_sample()`, the first argument should be `urn` (the data we want to sample from), and then set `n` equal to our sample size (we want a sample size of 50). 

```{r virtual-sampling-15, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-15-hint-1, eval = FALSE}
... |> 
  mutate(shovel = map(..., ~ ...))
```

```{r virtual-sampling-15-hint-2, eval = FALSE}
... |> 
  mutate(shovel = map(..., ~slice_sample(urn, n = ...)))
```

```{r virtual-sampling-15-test, include = FALSE}
tibble(trial_ID = 1:1000) |> 
  mutate(shovel = map(trial_ID, ~ slice_sample(urn, n = 50)))
```

### 

The advantage of modern technology is that we can use virtual simulation as many times as we choose, so we have no restrictions on resources. No longer are the days where we have to recruit our friends to tirelessly sample from the physical urn.

### Exercise 16

Continue your pipe with `mutate()` to create the variable `numb_red`. Set `numb_red` to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `sum()` of where `.$color` is equal to red.

```{r virtual-sampling-16, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-16-hint-1, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~...))
```

```{r virtual-sampling-16-hint-2, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~ sum(.$color == "red")))
```

```{r virtual-sampling-16-test, include = FALSE}
tibble(trial_ID = 1:1000) |> 
  mutate(shovel = map(trial_ID, ~ slice_sample(urn, n = 50))) |> 
  mutate(numb_red = map_int(shovel, ~sum(.$color == "red")))
```

### 

R evaluates if `color == red`, and treats `TRUE` values like the number `1` and `FALSE` values like the number `0`. So summing the number of `TRUE`s and `FALSE`s is equivalent to summing `1`’s and `0`’s. In the end, this operation counts the number of beads where `color` equals “red”.

### Exercise 17

Use `mutate()` one last time to create the variable `prop_red`. Set `prop_red` to `numb_red` divided by the sample size (in this exercise we are using a set sample size of 50).

```{r virtual-sampling-17, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-17-hint-1, eval = FALSE}
... |> 
   mutate(prop_red = ... / ...)
```

```{r virtual-sampling-17-test, include = FALSE}
tibble(trial_ID = 1:1000) |> 
  mutate(shovel = map(trial_ID, ~ slice_sample(urn, n = 50))) |> 
  mutate(numb_red = map_int(shovel, ~sum(.$color == "red"))) |> 
  mutate(prop_red = numb_red / 50)
```

### 

`prop_red` estimate's our proportion of red beads in the urn.

### Exercise 18

Assign your code from above to an object named `virtual_samples`.

```{r virtual-sampling-18, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-18-hint-1, eval = FALSE}
Use the assignment operator <-  to do so.
```

```{r virtual-sampling-18-test, include = FALSE}
virtual_samples <- tibble(trial_ID = 1:1000) |> 
  mutate(shovel = map(trial_ID, ~ slice_sample(urn, n = 50))) |> 
  mutate(numb_red = map_int(shovel, ~sum(.$color == "red"))) |> 
  mutate(prop_red = numb_red / 50)
```

### Exercise 19

Now start a pipe with `virtual_samples`. Use `ggplot()` to map `prop_red` to the x-axis.

```{r virtual-sampling-19, exercise = TRUE}

```

```{r virtual-sampling-19-hint-1, eval = FALSE}
virtual_samples |> 
  ggplot(aes(...))
```

```{r virtual-sampling-19-test, include = FALSE}
virtual_samples |> 
  ggplot(aes(x = prop_red))
```

### Exercise 20

Add the layer `geom_histogram()` to create a histogram of our data.

```{r virtual-sampling-20, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-20-hint-1, eval = FALSE}
... +
  geom_histogram()
```

```{r virtual-sampling-20-test, include = FALSE}
virtual_samples |> 
  ggplot(aes(x = prop_red)) + 
  geom_histogram()
```

### Exercise 21

Within `geom_histrogram()` set `binwidth` to .01, `boundary` to .4, and `color` to "white".

```{r virtual-sampling-21, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-21-hint-1, eval = FALSE}
... +
  geom_histrogram(binwidth = ..., boundary = ..., color = ...)
```

```{r virtual-sampling-21-test, include = FALSE}
virtual_samples |> 
ggplot(aes(x = prop_red)) +
  geom_histogram(binwidth = 0.01, 
                 boundary = 0.4, 
                 color = "white")
```

### 

Recall that `p` is equal to the proportion of beads which are red in each sample.

### Exercise 22

To finish, use `labs()` to give your graph the appropriate title and axis labels. See **hint** for guidance to create the symbol $\hat{p}$.

```{r virtual-sampling-22, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like. 

```{r}
plot_vs
```

```{r virtual-sampling-22-hint-1, eval = FALSE}
Within labs(), set x to expression(hat(p))
```

```{r virtual-sampling-22-test, include = FALSE}
virtual_samples |> 
ggplot(aes(x = prop_red)) +
  geom_histogram(binwidth = 0.01, 
                 boundary = 0.4, 
                 color = "white") +
  labs(x = expression(hat(rho)),
       y = "Count",
       title = "Distribution of 1,000 proportions red") 
```

### 

This visualization allows us to see how our results differed between our tactile and virtual urn results. As we can see, there is some variation between our results. This is not a cause for concern, as there is always expected sampling variation between results.


## Standard error of different shovel sizes
### 

<!-- MT: add questions about the definitions/important concepts of standard error -->

Standard errors (SE) quantify the effect of sampling variation on our estimates. In other words, they quantify how much we can expect the calculated proportions of a shovel’s beads that are red to vary from one sample to another sample to another sample, and so on. As a general rule, as sample size increases, the standard error decreases.

### 

In this section, we will create the following plot that displays different standard deviations of red bead proportions for 100 different shovel sizes.

```{r}
shovel_p <- shovels_100 |>
 ggplot(aes(x = shovel_size, y = st_dev_p_hat)) +
 geom_point() +
 labs(title = "Sampling Variation",
      subtitle = "Larger samples have less variation",
      x = "Shovel size",
      y = "Standard deviation of the proportion red")

shovel_p
```

### Exercise 1

In your own word, define *Standard error*.

```{r standard-error-of-different-sh-1}
question_text(NULL,
	message = "The standard error is the standard deviation of a sample statistic (aka point estimate), such as the proportion. For example, the standard error of the mean refers to the standard deviation of the distribution of sample means taken from a population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

<!-- GK: Need paraphrase, does not understand -->
First, let's use `expand_grid()` to create the foundation of our tibble. Our first column in `expand_grid()` should be called `trial_ID`, and it should be the range of integers between 1 and 1,000. The second column should be called `shovel_size`, and should be the range of integers between 1 and 100.

```{r standard-error-of-different-sh-2, exercise = TRUE}

```

```{r standard-error-of-different-sh-2-hint-1, eval = FALSE}
expand_grid(trial_ID = ..., shovel_size = ...)
```

```{r standard-error-of-different-sh-2-hint-2, eval = FALSE}
Use the : operator to create a range of integers. 
```

```{r standard-error-of-different-sh-2-test, include = FALSE}
expand_grid(trial_ID = c(1:1000), shovel_size = c(1:100))
```

### 

### Exercise 3

Continue the pipe with `mutate()`, creating a new column called `shovel`. Set `shovel` equal to a `map()` function, passing in `shovel_size` as the first argument, and the `slice_sample()` function as the second argument. Within `slice_sample()`, the first argument should be `urn` (the data we want to sample from), and then set `n` equal to `.` (we want to pass in the `shovel_size` using `map()`).

```{r standard-error-of-different-sh-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-3-hint-1, eval = FALSE}
... |>
  mutate(shovel = map(..., ~ ... ))
```

```{r standard-error-of-different-sh-3-hint-2, eval = FALSE}
... |>
  mutate(shovel = map(... , ~ slice_sample(..., n = ...)))
```

```{r standard-error-of-different-sh-3-test, include = FALSE}
expand_grid(trial_ID = c(1:1000), shovel_size = c(1:100)) |> 
  mutate(shovel = map(shovel_size, ~ slice_sample(urn, n = .)))
```

### 

### Exercise 4

Continue your pipe with `mutate()` to create the variable `numb_red`, which will tells us the number of red beads present. Set `numb_red` to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `sum()` of where the column `color` of `shovel` is equal to red.

```{r standard-error-of-different-sh-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-4-hint-1, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~ ...))
```

```{r standard-error-of-different-sh-4-hint-2, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~ sum(.$color == "red")))
```

```{r standard-error-of-different-sh-4-test, include = FALSE}
expand_grid(trial_ID = c(1:1000), shovel_size = c(1:100)) |> 
  mutate(shovel = map(shovel_size, ~ slice_sample(urn, n = .))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red")))
```

### Exercise 5

Continue your pipe from above, using `mutate()` to create one final column called `prop_red` which represents the proportion of red beads in a sample. Set `prop_red` to `numb_red` divided by the `shovel_size` column. 

```{r standard-error-of-different-sh-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-5-hint-1, eval = FALSE}
... |>
  mutate(prop_red = ... / ...)
```

```{r standard-error-of-different-sh-5-test, include = FALSE}
expand_grid(trial_ID = c(1:1000), shovel_size = c(1:100)) |> 
  mutate(shovel = map(shovel_size, ~ slice_sample(urn, n = .))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) |> 
  mutate(prop_red = numb_red / shovel_size)
```

### Exercise 6

Great. Continue your pipe and use the `group_by()` function to group our tibble by `shovel_size`. 

```{r standard-error-of-different-sh-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-6-hint-1, eval = FALSE}
... |>
  group_by(...)
```

```{r standard-error-of-different-sh-6-test, include = FALSE}
expand_grid(trial_ID = c(1:1000), shovel_size = c(1:100)) |> 
  mutate(shovel = map(shovel_size, ~ slice_sample(urn, n = .))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) |> 
  mutate(prop_red = numb_red / shovel_size) |> 
  group_by(shovel_size)
```

### Exercise 7

Continue your pipe one last time, and use `summarize()` to create a new column named `st_dev_p_hat` which is equal to the standard deviation of `prop_red`. (`sd()` calculates standard deviation).
 

```{r standard-error-of-different-sh-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-7-hint-1, eval = FALSE}
... |> 
  summarize(st_dev_p_hat = sd(...))
```

```{r standard-error-of-different-sh-7-test, include = FALSE}
expand_grid(trial_ID = c(1:1000), shovel_size = c(1:100)) |> 
  mutate(shovel = map(shovel_size, ~ slice_sample(urn, n = .))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) |> 
  mutate(prop_red = numb_red / shovel_size) |> 
  group_by(shovel_size) |> 
  summarize(st_dev_p_hat = sd(prop_red))
```

### Exercise 8

Assign your code from above to an object named `shovels_100`.

```{r standard-error-of-different-sh-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-8-hint-1, eval = FALSE}
Use the assignment operator <-  to do so.
```

```{r standard-error-of-different-sh-8-test, include = FALSE}
shovels_100 <- expand_grid(trial_ID = c(1:1000), shovel_size = c(1:100)) |> 
  mutate(shovel = map(shovel_size, ~ slice_sample(urn, n = .))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) |> 
  mutate(prop_red = numb_red / shovel_size) |> 
  group_by(shovel_size) |> 
  summarize(st_dev_p_hat = sd(prop_red))
```

### Exercise 9

Start a new pipe from `shovels_100`. Use `ggplot()`to map `shovel_size` to the x-axis and `st_dev_p_hat` to the y axis. Also, add the layer `geom_point()` to create a scatterplot.

```{r standard-error-of-different-sh-9, exercise = TRUE}

```

```{r standard-error-of-different-sh-9-hint-1, eval = FALSE}
shovels_100 |> 
  ggplot(aes(x = ..., y = ...)) + 
  geom_point()
```

```{r standard-error-of-different-sh-9-test, include = FALSE}
shovels_100 |> 
  ggplot(aes(x = shovel_size, y = st_dev_p_hat)) + 
  geom_point()
```

### Exercise 10

Now use `labs()` to label the x-axis "Shovel size" and the y-axis 
"Standard deviation of the proportion red". You should also provide a title and subtitle.

```{r standard-error-of-different-sh-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like.

```{r}
shovel_p
```

```{r standard-error-of-different-sh-10-hint-1, eval = FALSE}
... +
   labs(title = "Sampling Variation",
      subtitle = "Larger samples have less variation",
      x = "Shovel size",
      y = "Standard deviation of the proportion red")
```

```{r standard-error-of-different-sh-10-test, include = FALSE}
shovels_100 |> 
  ggplot(aes(x = shovel_size, y = st_dev_p_hat)) + 
  geom_point() + 
  labs(title = "Sampling Variation",
      subtitle = "Larger samples have less variation",
      x = "Shovel size",
      y = "Standard deviation of the proportion red")
```

### 

### Exercise 11

In one sentence, explain what you learn from the graph.

```{r standard-error-of-different-sh-11}
question_text(NULL,
	answer("The standard error of an estimate decreases at the rate of the square root of the population size.", correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

## Wisdom
### 

*Wisdom* requires the creation of a Preceptor Table, an examination of our data, and a determination, using the concept of “validity,” as to whether or not we can (reasonably!) assume that the two come from the same population.

### Exercise 1

In your own words, define a Preceptor Table.

```{r wisdom-1}
question_text(NULL,
	message = "Preceptor Table is the smallest possible table of data with rows and columns such that, if there is no missing data, then it is easy to calculate the quantities of interest.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- Add knowledge drop -->

### Exercise 2

Consider the following question: 

> If we get 17 red beads in a random sample of size 50 taken from a mixed urn, what proportion $\rho$ of the beads in the urn are red?

Our *Preceptor Table* is a table with minimal rows and columns such that we can perfectly answer our question using it. Describe the rows and the columns in a Preceptor Table which would allow us to answer this question. 

```{r wisdom-2}
question_text(NULL,
	message = "There will be one row for each bead in the urn. There will be at least one outcome column: color.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

There might be an ID column, but, strictly speaking we don't need one to answer our question.

### Exercise 3

What are the units for this problem?

```{r wisdom-3}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

### Exercise 4

What is the outcome for this problem?

```{r wisdom-4}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

### Exercise 5

In your own words, define "validity" as we use the term.

```{r wisdom-5}
question_text(NULL,
	message = "Validity is the consistency, or lack thereof, in the columns of your dataset and the corresponding columns in your Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

We have two tables: the data which we drew from the urn and the Preceptor Table. This case is a little strange since the same rows --- i.e., the same beads --- exist in both the data and in the Preceptor Table.

### Exercise 6

What can't we do in this case if the assumption of validity is not true?

```{r wisdom-6}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

### Exercise 7

<!-- Add the hint to make it easier to answer  -->
Provide one reason why the assumption of validity might not hold for this problem. (Hint: ) 

```{r wisdom-7}
question_text(NULL,
	message = "What if there is a secret hose in the bottom of the urn feeding in new beads, including beads of colors other than red and white? This would violate the assumption of validity since, implicitly, 'color' in our data only allows for red and white while 'color' in the Preceptor Table --- meaning the urn now, after some amount of new bead insertion --- has a different meaning.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Beads from an urn is a toy example, but a useful one because all the assumption necessary for inference are trivially true. So, it is hard to come up with counter-examples. Doing so will be much easier in actual problems.

### Exercise 8

In one sentence, summarize the data we have and the question we are trying to answer. 

```{r wisdom-8}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

Using a sample of 50 beads drawn from an urn in which all beads are either red or white, we seek to determine the proportion of beads which are red.

## Justice
### 

*Justice* creates the Population Table and then examines the assumptions of stability, representativeness, and unconfoundedness.

### Exercise 1

In your own words, define a Population Table.

```{r justice-1}
question_text(NULL,
	answer("The Population Table includes a row for each unit/time combination in the underlying population from which both the Preceptor Table and the data are drawn.", correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

### Exercise 2

In your own words, describe the rows in the Population table and their sources.

```{r justice-2}
question_text(NULL,
	message = "The rows in the Population Table are defined by unique ID/Time combinations. We have one row for every bead in the urn, at every moment in time under consideration. The three sources are the data we collected, the Preceptor Tbale and the underlying population from which both are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The biggest different between the Preceptor Table and the Population Table is that only the latter has a notion of "time." The Preceptor Table refers to a single moment in time to which you want your answer to apply. The Population Table refers to mutiple moments in time, the two most important of which are the moment when the data is collected and the moment to which the Preceptor Table applies.

### Exercise 3

Describe the columns in the Population Table

```{r justice-3}
question_text(NULL,
	message = "There will certainly be a column for 'color', the only outcome variable. There will generally be an 'ID', 'Source' and 'Time' column.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The Population Table should look something like this:

```{r}
tibble(source = c("Population", "Population", "Population","...",  
                  "Data", "Data", "Data", "...",
                  "Population", "Population", "Population","...", 
                  "Preceptor Table", "Preceptor Table", "Preceptor Table", "...",
                  "Population", "Population", "Population"),
       time = c("Time of sample - 2 years", "Time of sample - 2 years", "Time of sample - 2 years", "...",
                "Time of sample", "Time of sample", "Time of sample", "...",
                "Time of sample + 10 days", "Time of sample + 10 days", "Time of sample + 10 days", "...",
                "Now", "Now", "Now", "...",
                "Now + 3 weeks", "Now + 3 weeks", "Now + 3 weeks"),
       id = c("1", "200", "976", "...",
              "2", "200", "1080", "...",
              "1", "200", "2025", "...",
              "1", "200", "2078", "...",
              "1", "200", "2300"),
       color = c("?", "red", "?", "...",
              "white", "red", "white", "...",
              "?", "red", "?", "...",
              "?", "red", "?", "...",
              "?", "red", "?")) |>

  # Then, we use the gt function to make it pretty

  gt() |>
  cols_label(source = md("Source"),
             time = md("Time"),
             id = md("ID"),
             color = md("Color")) |>
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(source))) |>
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"),
            locations = cells_column_labels(columns = c(source))) |>
  cols_align(align = "center", columns = everything()) |>
  cols_align(align = "left", columns = c(source)) |>
  fmt_markdown(columns = everything())
```

### Exercise 4

In one sentence explain the value for `Time` for the rows sourced from our `Data`.

```{r justice-4}
question_text(NULL,
	message = "The `Time` column for the data is listed as the time of the sample, because only one sample was taken for which we have data.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 5

In one sentence explain the value for `Time` for the rows sourced from the `Preceptor Table`.

```{r justice-5}
question_text(NULL,
	message = "The Preceptor Table has a time column of `Now`, because we want to know the contents of the urn in the present day to answer our question.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 6

In one sentence explain the value for `Time` for the rows sourced from the `Population`.

```{r justice-6}
question_text(NULL,
	message = "The Population has a time range from as far back as 2 years before the sample and up to 3 weeks into the future, because the urn sample could have theoretically been taken from anytime in the past or into the future, so a wider population must be acknowledged.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 7

In your own words, define the assumption of "stability" when employed in the context of data science.

```{r justice-7}
question_text(NULL,
	message = "Stability means that the relationship between the columns in the Population Table is the same for three categories of rows: the data, the Preceptor Table, and the larger population from which both are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 8

<!-- Add hint -->
In two sentences, provide a reason why the assumption of "stability" might not hold. (Hint: )

```{r justice-8}
question_text(NULL,
	message = "What if someone dumps some red beads into the urn after we take our sample? Then we cannot assume stability, because the proportion of red beads in the urn, `p`, the instant before the dump is different than the proportion red in the urn after.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 9

In your own words, define the assumption of "representativeness" when employed in the context of data science.

```{r justice-9}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

### Exercise 10

In two sentences, give an example of why the rows in the Preceptor Table may not be representative of the overall population.

```{r justice-10}
question_text(NULL,
	message = "What if, now, the beads are not well-mixed. All the whites are at the top. If this is the case, then when we use the shovel now, we will get more whites. The new sample will not be representative of the entire urn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 11

In your own words, define the assumption of "unconfoundedness" when employed in the context of data science.

```{r justice-11}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

### Exercise 12

In one or two sentences, explain why the assumption of unconfoundedness does not apply.

```{r justice-12}
question_text(NULL,
	message = "Since this is a predictive model, we do not have to worry about unconfoundedness. There is no “treatment” which might be confounded with anything.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

However, there is one potential problem that our estimate would be flawed if someone has changed the beads in the urn since we drew our sample.

## Courage 
### 

*Courage* takes the mathematical formula from *Justice* and, using code, creates a fitted model, included posterior probability distributions for all the unknown parameters.

### Exercise 1

In your own word, define a posterior for this problem.

```{r courage-1}
question_text(NULL,
	message = "The probability distribution of our unknown parameter $p$, the probability of red beads in the urn",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

We will create a rough posterior using simple calculations with our data.

### Exercise 2

With 17 red beads within the sample of 50 beads, calculate the percentage of red beads in the sample. 

```{r courage-2}
question_text(NULL,
	message = "17/50 = 0.34",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Common sense suggests that this is a good estimate of the center of the posterior.

### Exercise 3

In the Console, type the command `sd()` with the argument `c(rep(0, 17), rep(1, 33))`. This will return the standard deviation of the sample size.

```{r courage-3}
question_text(NULL,
	message = "0.4785181",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 4

From the standard deviation, calculate the standard error, recall that the difference between this two is that for a given sample size, the standard error equals the standard deviation divided by the square root of the sample size.

```{r courage-4}
question_text(NULL,
	message = "0.67",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 5

With the standard error, calculate the 95% confidence interval for the proportion of red beads in the urn.

```{r courage-5}
question_text(NULL,
	message = "With 95% confidence, the proportion of red beads in the urn is between 21% and 47%.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Recall that the outcome we are interested in, the color of the bead, can only be either red or white. The model that is used for sampling scenarios with only two possible values is called a *Bernoulli* model.

### Exercise 6

Add one sentence about the model we used to draw the outcome we are interested in.

```{r courage-6-ex}
question_text(NULL,
	message = "We model the color of an individual bead as a draw from a Bernoulli distribution with unknown parameter $p$",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

###

## Temperance 
### 

*Temperance* helps us to use that model to answer the question with which we began.

Recall the question we are trying to answer:

> Given an urn consists of 1,000 identically sized red and white beads in the urn, mixed well together. What proportion, $p$, of this urn's beads are red?

We will be creating the following graph to answer the question: 

```{r}
tibble(obs = rnorm(1000000, mean = 0.34, sd = 0.067)) |> 
  ggplot(aes(x = obs)) +
    geom_density(aes(y = after_stat(count/sum(count))))  +
    labs(title = expression(paste("Posterior Distribution for  ", rho)),
         subtitle = "There is a 95% chance for a value between 21% and 47%.",
         x = expression(paste("Proportion, ", rho, ", of Red Beads in Urn")),
         y = "Probability") +
    scale_x_continuous(labels = scales::percent_format()) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()
```

### Exercise 1

Create a `tibble()` command with the argument `obs` equal `rnorm(1000000, mean = 0.34, sd = 0.067`)

```{r temperance-1, exercise = TRUE}

```

```{r temperance-1-hint-1, eval = FALSE}
tibble(... = rnorm(1000000, ... = 0.34, sd = ...))
```

```{r temperance-1-test, include = FALSE}
tibble(obs = rnorm(1000000, mean = 0.34, sd = 0.067))
```

### 

### Exercise 2

Continue the pipe with `ggplot()`, mapping `x` to `obs` in the `aes()` argument. 

```{r temperance-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-2-hint-1, eval = FALSE}
... |> 
  ggplot(...(x = ...))
```

```{r temperance-2-test, include = FALSE}
tibble(obs = rnorm(1000000, mean = 0.34, sd = 0.067)) |> 
  ggplot(aes(x = obs))
```

### 

### Exercise 3

Add `geom_density()`, setting `y` equal to `after_stat(count/sum(count))` in the `aes()` argument.

```{r temperance-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-3-hint-1, eval = FALSE}
... |> 
  ggplot(aes(x = ...)) + 
    geom_density(...(y = after_stat(.../sum(count))))
```

```{r temperance-3-test, include = FALSE}
tibble(obs = rnorm(1000000, mean = 0.34, sd = 0.067)) |> 
  ggplot(aes(x = obs)) +
    geom_density(aes(y = after_stat(count/sum(count))))
```

### 

### Exercise 4

Add `scale_x_continuous()` with the argument `labels` equal `scales::percent_format()`.

```{r temperance-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-4-hint-1, eval = FALSE}
... + 
  scale_x_continuous(... = scales::percent_format())
```

```{r temperance-4-test, include = FALSE}
tibble(obs = rnorm(1000000, mean = 0.34, sd = 0.067)) |> 
  ggplot(aes(x = obs)) +
    geom_density(aes(y = after_stat(count/sum(count)))) + 
    scale_x_continuous(labels = scales::percent_format())
```

### 

### Exercise 5

Add `scale_y_continuous()` with the argument `labels` equal `scales::percent_format()`.

```{r temperance-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-5-hint-1, eval = FALSE}
... + 
  scale_y_continuous(... = scales::percent_format())
```

```{r temperance-5-test, include = FALSE}
tibble(obs = rnorm(1000000, mean = 0.34, sd = 0.067)) |> 
  ggplot(aes(x = obs)) +
    geom_density(aes(y = after_stat(count/sum(count)))) + 
    scale_x_continuous(labels = scales::percent_format()) + 
    scale_y_continuous(labels = scales::percent_format())
```

### 

### Exercise 6

Add `theme_classic()`

```{r temperance-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-6-hint-1, eval = FALSE}
... + 
   theme_classic()
```

```{r temperance-6-test, include = FALSE}
tibble(obs = rnorm(1000000, mean = 0.34, sd = 0.067)) |> 
  ggplot(aes(x = obs)) +
    geom_density(aes(y = after_stat(count/sum(count)))) + 
    scale_x_continuous(labels = scales::percent_format()) + 
    scale_y_continuous(labels = scales::percent_format()) + 
    theme_classic()
```

### 

### Exercise 7

Finally, add `title`, `subtitle`, labels for `x` and `y` axes. Remember this is what your graph should look like. 

```{r}
tibble(obs = rnorm(1000000, mean = 0.34, sd = 0.067)) |> 
  ggplot(aes(x = obs)) +
    geom_density(aes(y = after_stat(count/sum(count))))  +
    labs(title = expression(paste("Posterior Distribution for  ", rho)),
         subtitle = "There is a 95% chance for a value between 21% and 47%.",
         x = expression(paste("Proportion, ", rho, ", of Red Beads in Urn")),
         y = "Probability") +
    scale_x_continuous(labels = scales::percent_format()) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()
```

```{r temperance-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-7-hint-1, eval = FALSE}
... + 
  labs(title = expression(paste("Posterior Distribution for ", rho)), subtitle = "...", 
       x = expression(paste("Proportion, ", rho, ", of Red Beads in Urn")), y = "...")
```

```{r temperance-7-test, include = FALSE}
tibble(obs = rnorm(1000000, mean = 0.34, sd = 0.067)) |> 
  ggplot(aes(x = obs)) +
    geom_density(aes(y = after_stat(count/sum(count))))  +
    labs(title = expression(paste("Posterior Distribution for  ", rho)),
         subtitle = "There is a 95% chance for a value between 21% and 47%.",
         x = expression(paste("Proportion, ", rho, ", of Red Beads in Urn")),
         y = "Probability") +
    scale_x_continuous(labels = scales::percent_format()) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()
```

### 

The percentage of red beads in the urn is about 34%, with a 95% credible interval from 21% to 47%.

### Exercise 8

Write a few sentences summarize your work to answer the question with which we began. 

```{r temperance-8}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

Using a sample of 50 beads drawn from an urn in which all beads are either red or white, we seek to determine the proportion of beads which are red. Our estimate would be flawed if someone has changed the beads in the urn since we drew our sample. We model the color of an individual bead as a draw from a Bernoulli distribution with unknown parameter. The percentage of red beads in the urn is about 34%, with a 95% credible interval from 21% to 47%.

## Summary
### 

This tutorial covered [Chapter 3: Sampling](https://ppbds.github.io/primer/sampling.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 
 

```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
