---
title: "Continuous Response"
tutorial:
  id: "continuous-response"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 11 tutorial"
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(rstanarm)
library(skimr)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

# These models take awhile to build. 



```

<!-- DK: nnet example and code students use does not match up. How is that possible!?! -->

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```


## EDA cces
###

<!-- DK: Better to build these pipes by just spitting them out until the end and then, last step, put the assignment at the front. -->

`cces` is a data set which is part of the collection of **primer.data** packages. Let's start by familiarizing ourselves with this data set.


### Exercise 1

Let's first run `glimpse()` to see all the different variables in the `cces` dataset. 

```{r glimpse, exercise = TRUE}

```


```{r glimpse-hint, eval = FALSE}
glimpse(cces)
```

### Exercise 2

As you can see there are lots of observations! For our purposes, we are going to narrow our data.

Let's create an object named `ch_11`. To do so, start with `cces`. Use `%>%` to add `select()` to select `year`, `gender`, `race`, `approval`, and `age`. 

```{r select-1, exercise = TRUE}

```


```{r select-1-hint, eval = FALSE}
ch_11 <- 
  cces %>%
  select(...)

```

### Exercise 3

Extend the pipe using `filter()`. Set `year` equal to `2016`. Also, use `drop_na()` to get rid of any rows with missing data.

```{r filter, exercise = TRUE }

```

```{r filter-hint, eval = FALSE }
ch_11 <-
  cces %>%
  select(year, gender, race, age, approval) %>%
  filter(year == ...) %>% 
  drop_na()
```


### Exercise 4

`ch_11` is still too big. So, let's add `sample_n(1000)` to the end of the pipe so that we only keep 1,000 observations. Let's also use `set.seed(9)` at the top so that we only get the same sample. Note that `set.seed()` is never part of a pipe. It is a stand-alone line of code. 

```{r filter-last, exercise = TRUE }

```

```{r filter-last-hint, eval = FALSE }
set.seed(9)
ch_11 <-
  cces %>%
  select(year, gender, race, age, approval) %>%
  filter(year == ...) %>% 
  drop_na() %>% 
  sample_n(1000)  
```




## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```

