---
title: "Wrangling B"
tutorial:
  id: "wrangling-b"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 2: Wrangling -- B"
---

<!-- Add Continue at the start of each section, after introductory words and before showing plot. -->

<!-- Replace ntile() because it is no longer in the book. Maybe quintile() can be used? -->

<!-- NL: The effect of grouping with ntile() in Kenya was not obvious to me. Should this be more explicitly introduced as an alternative to fill? -->

<!-- scale_fill_brewer(), coord_cartesian(), and  scale_linetype() all have no explanation in primer. DK: So, don't use them. Or give a clearer hint. [done. However, coord_cartesian() is used in the textbook (1.4.5) and is used exclusively in Wrangling C. scale_x_continuous(limits) does not work with ggdist] -->

<!-- DK: See below for problems with qscores question. Ignore this for now. [I am not sure whether or not this has been resolved. I do not get an error.] -->

<!-- NL: Get rid of arguments in if_else() -->



```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(lubridate)
library(stringr)
library(skimr)
library(primer.data)
library(ggdist)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

# Needed for later sections of the tutorial 

library(ggthemes)
```


## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```


## National Health and Nutrition Survey
###

`nhanes` includes data from the "National Health and Nutrition Examination Survey," which contains the personal and physical information of 10,000 Americans from two surveys in 2009 and 2011.

###

Let's create the following plot.

```{r}
nhanes_p <- nhanes %>%
  mutate(weight = weight * 2.2, height = height / 30.48) %>%
  select(gender, weight, height, bmi) %>%
  drop_na(weight, height) %>% 
  ggplot(mapping = aes(x = weight, y = height, color = bmi)) +
    geom_jitter() +
    geom_smooth(se = FALSE, 
                method = "loess", 
                formula = y ~ x) +
    facet_wrap(~ gender) + 
    theme_clean() + 
    labs(y = "Height (feet)",
         x = "Weight (pounds)",
         title = "Height Versus Weight in the US",
         subtitle = "Relation between weight and height more positive for heavy men",
         color = "BMI",
         caption = "Source: NHANES")

nhanes_p
```

### Exercise 1

`glimpse()` the `nhanes` data set.

```{r nhanes1, exercise = TRUE}

```

```{r nhanes1-hint, eval = FALSE}
glimpse(...)
```

### Exercise 2

In the tibble, `weight` is measured in kg and `height` in cm. Using `mutate()`, multiply `weight` by 2.2 and divide `height` by 30.48 to convert units into pounds and feet. 

```{r nhanes2, exercise = TRUE}

```

```{r nhanes2-hint-1, eval = FALSE}
nhanes %>%
  mutate(weight = ..., 
         height = ...)
```

```{r nhanes2-hint-2, eval = FALSE}
Use * to multiply and / to divide.
```

```{r nhanes2-hint-3, eval = FALSE}
nhanes %>%
  mutate(weight = ... * ..., 
         height = .../ ...)
```

### Exercise 3

Now `select()` the `gender`, `weight`, `height`, and `bmi` columns. 

```{r nhanes3, exercise = TRUE}

```

```{r nhanes3-hint, eval = FALSE}
... %>%
  select(..., ..., ..., ...)
```

### Exercise 4

`nhanes` has NA values in some rows. Start a pipe with `nhanes`. Use `drop_na()` with the arguments `weight`and `height` to remove all rows with a value of NA in the those columns.

```{r nhanes4, exercise = TRUE}

```

```{r nhanes4-hint, eval = FALSE}
... %>%
  drop_na(..., ...)
```

### Exercise 5

Continue you pipe with `ggplot()`. Also add the layer `geom_jitter()` to make a jittered scatterplot. Map `weight` to the x-axis, `height` to the y-axis, and `bmi` to `color`.

```{r nhanes5, exercise = TRUE}

```


```{r nhanes5-hint-1, eval = FALSE}
... %>% 
  ggplot(data = ..., aes(x = ..., 
                        y = ..., 
                        color = ...)) +
  geom_jitter()
```

### Exercise 6

Add a trend line with the layer `geom_smooth()`. Set the argument `se` to FALSE and set `method` to "loess".

```{r nhanes6, exercise = TRUE}

```

```{r nhanes6-hint-2, eval = FALSE}
... + 
  geom_smooth(se = ..., method = ...)
```

### Exercise 7

Notice that we still get a message. Within `geom_smooth()` set the `formula` argument to `y ~ x`.

```{r nhanes7, exercise = TRUE}

```

```{r nhanes7-hint-2, eval = FALSE}
... + 
 geom_smooth(se = FALSE, 
             method = "loess", 
             formula = ...)
```

### Exercise 8

Use `facet_wrap()` to facet the graph by `gender`.

```{r nhanes8, exercise = TRUE}

```

```{r nhanes8-hint, eval = FALSE}
... +
  facet_wrap( ~ ...) 
```

### Exercise 9

Adjust the feel of the graph by adding the theme `theme_clean()`.

```{r nhanes9, exercise = TRUE}

```

```{r nhanes9-hint-1, eval = FALSE}
Recall that when you add a theme, you add a layer! Use the + operator.
```

```{r nhanes9-hint-2, eval = FALSE}
... +
  theme_clean()
```

### Exercise 10

To finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, legend labels, and caption of your choice.

```{r nhanes10, exercise = TRUE}

```

Reminder: This is what your plot should look like.

```{r nhanes10-answer}
nhanes_p
```


## Kenya Voting
###

The `kenya` contains data from a study in which poll stations in Kenya were assigned to either the control group or a group in which one or more methods (an SMS reminder, canvassing, etc.) were used to encourage voter registration. 


###

Let's create the following plot.

```{r kenya-answer}
kenya_p <- kenya %>%
  filter(treatment %in% c("control", "local", 
                          "SMS", "canvass")) %>%
  droplevels() %>%
  select(treatment, mean_age, reg_byrv13) %>%
  drop_na(mean_age) %>%
  group_by(treatment) %>%
  summarize(mean_turnout = mean(reg_byrv13, na.rm = TRUE),
            .groups = "drop") %>% 
  ggplot(mapping = aes(x = fct_reorder(treatment, mean_turnout), 
                       y = mean_turnout)) +
    geom_col() +
    theme_bw() +
    labs(title = "Turnout Changes in a Kenyan Election",
         subtitle = "Local canvassing has the largest effect",
         x = "Treatment",
         y = "Change in Mean Turnout")

kenya_p
```

### Exercise 1

`glimpse()` the `kenya` data set. 

```{r kenya1, exercise = TRUE}

```

```{r kenya1-hint, eval = FALSE}
glimpse(...)
```

### Exercise 2

`filter()` `kenya` to keep only the rows that have a `treatment` of "control," "local," "SMS," or "canvass." Use the `%in% `operator with `c()` to do so.

```{r kenya2, exercise = TRUE}

```

```{r kenya2-hint-1, eval = FALSE}
kenya %>%
  filter(treatment %in% c(..., ..., ..., ...))
```


### Exercise 3

Because `treatment` is a factor, use `%>% ` to  `droplevels()`. This will avoid future complications. 

```{r kenya3, exercise = TRUE}

```

```{r kenya3-hint, eval = FALSE}
... %>% 
  drop_levels()
```

###

If we did not `drop_levels()` then the `treatment` variable, because it is a factor, would "remember" all the levels we began with even though we deleted all the rows with data from those levels. These "phantom" levels can interfere with plotting. 

### Exercise 4

Now `select()` the columns `treatment`, `mean_age`, and `reg_byrv13` columns. 

```{r kenya4, exercise = TRUE}

```

### Exercise 5

Use `drop_na()` to remove all rows with a NA value in the `mean_age` column.

```{r kenya5, exercise = TRUE}

```

```{r kenya5-hint, eval = FALSE}
kenya %>%
  filter(treatment %in% c("control", "local", "SMS", "canvass")) %>%
  droplevels() %>%
  select(treatment, mean_age, reg_byrv13)
  drop_na(...)
```

### Exercise 6

Group the data by `treatment`.

```{r kenya6, exercise = TRUE}

```

```{r kenya6-hint, eval = FALSE}
... %>%
  group_by(..., ...)
```

### Exercise 7

Using `summarize()` and `mean()`, create a tibble with a new column named `mean_turnout`. The first argument to `mean()` should be `reg_byrv13`. The second argument to `mean()` should set `na.rm` to `TRUE`, as there are some NA values in the `reg_byrv13` column. Within `summarize()`, set the argument `.groups` equal to `"drop"`. 


```{r kenya7, exercise = TRUE}

```

```{r kenya7-hint-1, eval = FALSE}
... %>% 
  summarize(... = mean(..., na.rm = ...),
            .groups = "...")
```

```{r kenya7-hint-2, eval = FALSE}
Do not forget the .groups argument to summarize(). Never ignore warning
messages.
```

###

`.groups` is an argument which tells `summarize()` what to do with the grouping of the data after it has used the grouping to produce its summary. `.groups` does not affect the data in the summary tibble. You can either `"keep"` the grouping, `"drop"` the grouping, or `"drop_last"`, i.e. to drop the last of the specified grouping variables (this is because retaining all the same groups after summary creates groups which only contain single rows). `"drop_last"` is the default in most cases. Whenever you exclude `.groups`, you will receive a warning message. 

### Exercise 8

Continue your pipe and add  `ggplot()`.  Use `fct_reorder()` to reorder the `treatment` variable by `mean_turnout` and map this to the x-axis. Also, map `mean_turnout` to the y-axis. Also add the layer `geom_col()`.

```{r kenya8, exercise = TRUE}

```


```{r kenya8-hint-1, eval = FALSE}
... %>% 
  ggplot(mapping = aes(x = fct_reorder(treatment, mean_turnout), 
                       y = ...) +
  geom_col()
```

### 

`geom_col()` is similar to `geom_bar()`, but allows us to specify a y axis other than count. 

### Exercise 9

Add the theme `theme_bw()` to the plot.

```{r kenya9, exercise = TRUE}

```

```{r kenya9-hint-1, eval = FALSE}
... +
  theme_bw()
```

### Exercise 10

To finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, and caption of your choosing. 

Reminder: This is what your plot should look like.

```{r kenya10-answer}
kenya_p
```

```{r kenya10, exercise = TRUE}

```


## Seguro Popular
###

The `sps` data set contains information about a study done on a popular Mexican health insurance program, Seguro Popular. In the study, some Mexican health clusters were randomly "treated." The treatment consisted of encouragement for people in that health cluster to enroll in the health insurance program, as well as funds to improve health facilities in that cluster.

###

Let's create the following plot.

```{r sps_plot}
sps_p <- sps %>%
  filter(education %in% c("preschool", "secondary", 
                          "high school", "college")) %>%
  select(-c(health_exp_1m, t2_health_exp_1m)) %>%
  mutate(change_in_expenses = t2_health_exp_3m - health_exp_3m) %>%
  group_by(treatment, education) %>%
  summarize(mean_change_in_expenses = mean(change_in_expenses),
            .groups = "drop") %>%
  mutate(treatment = as.factor(treatment)) %>% 
  ggplot(mapping = aes(x = fct_reorder(education, mean_change_in_expenses), 
                       y = mean_change_in_expenses, fill = treatment)) +
    geom_col(position = "dodge") + 
    theme_minimal() +
    labs(x = "Education",
         y = "Average Change in Expenses",
         title = "Spending Changes and Seguro Popular",
         subtitle = "Honestly, not sure what is going on here . . .",
         fill = "Treatment",
         caption = "Source: King et al. (2009)")

sps_p
```

### Exercise 1 

`glimpse()` the dataset `sps`.

```{r sps1, exercise = TRUE}

```

```{r sps1-hint, eval = FALSE}
glimpse(...)
```

### Exercise 2

`filter()` `sps` to only the rows with an `education` of "preschool," "secondary," "high school," or "college."  Use the `%in%` and `c()` to do so.

```{r sps2, exercise = TRUE}

```

```{r sps2-hint-1, eval = FALSE}
sps %>%
  filter(education %in% ...)
```

```{r sps2-hint-2, eval = FALSE}
sps %>% 
  filter(education %in% c(..., ..., ..., ...))
```

### Exercise 3

Use `select()` to remove the columns `health_exp_1m` and `t2_health_exp_1m`. 

```{r sps3, exercise = TRUE}

```

```{r sps3-hint-1, eval = FALSE}
Remember that select(-...) returns all columns except for the specified column(s) that come after. When you use a vector, you only need one -
```

```{r sps3-hint-3, eval = FALSE}
... %>% 
  select(-c(..., ...))
```

### Exercise 4 

Use `mutate()` to create a new variable, `change_in_expenses`, which is equal to `health_exp_3m` subtracted from `t2_health_exp_3m` (this measures the change in expenses after the treatment period). 


```{r sps4, exercise = TRUE}

```

```{r sps4-hint, eval = FALSE}
... %>% 
  mutate(... = t2_health_exp_3m - health_exp_3m) 
```

### Exercise 5

Group the data by `treatment` and `education`.

```{r sps5, exercise = TRUE}

```

```{r sps5-hint, eval = FALSE}
Use the group_by() function.
```

### Exercise 6

Using `summarize()`, calculate `mean_change_in_expenses`, the` mean()` of the `change_in_expenses` for each group. Set the argument `.groups` equal to "drop".

```{r sps6, exercise = TRUE}
  
```

```{r sps6-hint, eval = FALSE}
... %>% 
  summarize(... = mean(...),
            .groups = "drop")
```

### Exercise 7

Because the `treatment` column is not a factor, we can't group our data by it. To fix this, use `mutate()` and set the column `treatment` to `as.factor()` with the argument `treatment`. 

```{r sps7, exercise = TRUE}

```

```{r sps7-hint, eval = FALSE}
 ... %>% 
  mutate(treatment = as.factor(...))
```

### Exercise 8

Use `%>%` to add `ggplot()`. Use `fct_reorder()` to reorder the `education` variable by `mean_change_in_expenses` and map this to x-axis. Map `mean_change_in_expenses` to the y-axis, and `treatment` to the `fill`. Also add the layer `geom_col()`.


```{r sps8, exercise = TRUE}

```

```{r sps8-hint-1, eval = FALSE}
.. %>% 
  ggplot(mapping = aes(x = fct_reorder(education, 
                                       mean_change_in_expenses), 
                     y = ..., 
                     fill = ...) +
  geom_col()
```

### Exercise 9

Within `geom_col()`, set the `position` argument equal to `"dodge"`. 

```{r sps9, exercise = TRUE}

```

```{r sps9-hint, eval = FALSE}
... +
  geom_col(position = "dodge")
```

### Exercise 10

Add `theme_minimal()` to change the style of the graph.

```{r sps10, exercise = TRUE}

```

### Exercise 11

To finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, and caption of your choice.

```{r sps11, exercise = TRUE}

```

Reminder: This is what your plot should look like.

```{r sps11-answer}
sps_p
```


## Shaming 
###

The `shaming` data set measures the impact of social pressure on voting. Nearly 350,000 people in Michigan were randomly assigned to 1 of 5 treatment groups before the 2006 Michigan primary. All 5 groups were sent mail before the primary: the "Civic Duty" group had an extra reminder that voting was a civic responsibility, the "Hawthorne" group was told that whether or not they voted would be in the public record, the "Self" group was actually *sent* the public record of whether or not they voted in 2004, and the "Neighbors" group was sent both their voting record and their neighbors' voting record from 2004. 

###

Let's create the following plot.

```{r sh_goal}
shaming_p <- shaming %>%
  select(primary_04, primary_06, treatment) %>%
  mutate(primary_04 = if_else(condition = 
                                str_detect(primary_04, "Yes"),
                                true = 1,
                                false = 0)) %>%
  pivot_longer(cols = c(primary_04, primary_06), 
               names_to = "year", 
               values_to = "voted") %>%
  group_by(treatment, year, voted) %>%
  summarize(num_voters = n(), 
            .groups = "drop") %>%
  mutate(voted = if_else(condition = voted == 1,
                         true = "did_vote",
                         false = "did_not_vote")) %>%
  pivot_wider(names_from = voted, values_from = num_voters)  %>%
  mutate(pct_voted = did_vote / (did_vote + did_not_vote)) %>% 
  ggplot(mapping = aes(x = fct_reorder(treatment, pct_voted), 
                       y = pct_voted, fill = year)) +
    geom_col(position = "dodge") +
    labs(x = "Treatment",
         y = "Voting Percentage",
         title = "Voting Rates Based on Mailings",
         subtitle = "Shaming people makes them more likely to vote",
         fill = "Year",
         caption = "Source: Gerber, Green, and Larimer (2008).") +
    theme_fivethirtyeight()

shaming_p
```

### Exercise 1

`skim()` the `shaming` data set. Pay close attention to the data types of each of the variables.

```{r shaming1, exercise = TRUE}

```

### Exercise 2

`select()` the columns `treatment`, `primary_04`, and `primary_06` of the `shaming` dataset.

```{r shaming2, exercise = TRUE}

```

```{r shaming2-hint, eval = FALSE}
shaming %>% 
  select(..., ..., ..., ...)
```

### Exercise 3

Use `mutate()` to change the `primary_04` column into binary. Set `primary_04` to an `if_else()` statement. Within `if_else()`, set `condition` to `str_detect()`, with arguments to detect the string "Yes" in `primary_04`. If the condition is true, the function should return `1`, and if false, `0`.

```{r shaming3, exercise = TRUE}

```

```{r shaming3-hint-1, eval = FALSE}
mutate(primary_04 = if_else(str_detect(primary_04, "..."), 1, 0))
```

### Exercise 4

Use `pivot_longer()` to map the *names* of the `primary_04` and `primary_06` columns to a new column, "year,". Map the  *values* of the two columns to a new column, "voted."


```{r shaming4, exercise = TRUE}

```

```{r shaming4-hint, eval = FALSE}
...  %>%
  pivot_longer(cols = c(..., ...), 
               names_to = ...,
               values_to = ...)
```

### Exercise 5

Great job! Now group the data by `treatment`, `year`, and `voted`.

```{r shaming5, exercise = TRUE}

```

```{r shaming5-hint, eval = FALSE}
Use the group_by() function.
```

### Exercise 6

Use `summarize()` to create the variable `num_voters`, which is set to the function `n()`. Then, set the `.groups` argument equal to `"drop"`.

**Note:** `n()` simply counts the number of rows in each group. 

```{r shaming6, exercise = TRUE}

```

```{r shaming6-hint, eval = FALSE}
... %>% 
  summarize(num_voters = n(), 
            .groups = "...")
```

### Exercise 7

The `voted` column is a bit difficult to understand because the numerical value (0 or 1) is used to represent an idea (the person did or did not vote). Use `mutate()` to set `voted` to an `if_else()` statement. Within `if_else()`, set the condition to where `voted` is equal to 1. Set the result for true to "did_vote," and the result for false to "did_not_vote."


```{r shaming7, exercise = TRUE}

```

```{r shaming7-hint-2, eval = FALSE}
...%>%
  mutate(voted = if_else(voted == ..., "...", "..."))
```

### Exercise 8

Let's transform `did_vote` and `did_not_vote` into their own columns. Call `pivot_wider()` that gets its column `names_from` `voted` and its `values_from` `num_voters`.


```{r shaming8, exercise = TRUE}

```

```{r shaming8-hint, eval = FALSE}
...  %>%
  pivot_wider(names_from = ..., 
              values_from = ...)
```

### Exercise 9

Use `mutate()` to create a new variable `pct_voted`, which is equal to the number of people who `did_vote` divided by the total number of people.

```{r shaming9, exercise = TRUE}

```

```{r shaming9-hint-1, eval = FALSE}
Note that the total number of people is equal to (did_vote + did_not_vote). Also, use / to divide. 
```

```{r shaming9-hint-2, eval = FALSE}
... %>% 
  mutate(... = ... / (did_vote + did_not_vote))
```

### Exercise 10

Use `%>%` to add `ggplot()`. Use `fct_reorder()` to reorder the `treatment` variable by `pct_voted` and map this to x-axis. Map `pct_voted` to the y-axis, and `year` to the `fill`. Also add the layer `geom_col()`.


```{r shaming10, exercise = TRUE}

```

```{r shaming10-hint-1, eval = FALSE}
... %>% 
  ggplot(mapping = aes(x = fct_reorder(treatment, pct_voted), 
                       y = ..., 
                       fill = ...)) +
  geom_col()
```

### Exercise 11

Within `geom_col()`, set the position argument equal to `position` equal to "dodge"`. 

```{r shaming11, exercise = TRUE}

```

```{r shaming11-hint, eval = FALSE}
... +
  geom_col(position = "dodge")
```

### Exercise 12

Add the theme `theme_fivethirtyeight()` to your plot. 

```{r shaming12, exercise = TRUE}

```

```{r shaming12-hint, eval = FALSE}
Remember when you add a theme, you add a layer. Use +.
```

### Exercise 13

To finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, legend labels, and caption of your choice.

Reminder: This is what your plot should look like. 

```{r shaming13-answer}
shaming_p
```

```{r shaming13, exercise = TRUE}

```

## Q-Guide
###

<!-- DK: Getting some errors here, like "object `q_subset` not found". Not sure what to make of this. Does not seem to happen to everyone. Why haven't we fixed this to make the plot once, save the code, and then reuse it!? -->

<!-- This amount of setup is scary. Can we make an easier example with left_join? -->

The `qscores` data set includes information about 748 courses at Harvard during the 2018-2019 school year, including their department, student enrollment, average time spent on homework, and the average student rating of the course.

Let's create the following plot.

```{r make-qscores-p}
q_subset_2 <- qscores %>%
  filter(department %in% c("ECON", "MATH", "GOV")) %>%
  arrange(department)

q_subset <- qscores %>%
  select(department, hours) %>%
  group_by(department) %>%
  summarize(num_classes = n(), 
            mean_hours = mean(hours), 
            sd_hours = sd(hours), 
            .groups = "drop") %>%
  arrange(desc(num_classes)) %>%
  slice(1:3) %>%
  group_by(department) %>%
  summarize(rnorm_values = rnorm(n = num_classes, 
                                 mean = mean_hours, 
                                 sd = sd_hours),
            .groups = "drop") %>%
  arrange(department)

q_join <- left_join(q_subset, q_subset_2, by = "department") %>%
  pivot_longer(cols = c(rnorm_values, hours), 
               names_to = "type", 
               values_to = "value")

q_p <- ggplot(data = q_join, mapping = aes(x = value)) +
    geom_histogram(binwidth = 2) +
     facet_wrap(~ department) + 
  theme_bw()+
  labs(title = " Homework Patterns of Harvard Classes by Department",
       x = "Value",
       y= "Count",
       caption = "Source: Q-Guide Web App")

q_p

```

### Exercise 1

Use `sample_n()` to view 5 random rows in the data set `qscores`.

```{r qscores1a, exercise = TRUE}

```

```{r qscores1-hint, eval = FALSE}
qscores %>% 
  sample_n(...)
```

### Exercise 2

Let's practice using summary statistics with our data. Take the `mean()` of the `hours` column. Use the `$` operator to extract the `hours` column.

```{r qscores2, exercise = TRUE}

```

```{r qscores2-hint, eval = FALSE}
mean(qscores$hours)
```

### Exercise 3

Start a pipe with `qscores` and `select()` the `department` and `hours` columns.

```{r qscores3, exercise = TRUE}

```

```{r qscores3-hint, eval = FALSE}
qscores %>%
  select(..., ...)
```

### Exercise 4

Now group the data by `department`.

```{r qscores4, exercise = TRUE}

```

```{r qscores4-hint, eval = FALSE}
Use the group_by() function.
```

### Exercise 5

Use `summarize()` to create 3 new variables. `num_classes` should be set to `n()`. `mean_hours` should equal the `mean()` of `hours`. `sd_hours` should equal the `sd()` of `hours`. Then set the `.groups` argument equal to `"drop"`


```{r qscores5, exercise = TRUE}

```

```{r qscores5-hint-1, eval = FALSE}
The n() function returns the number of rows in each group.
```

```{r qscores5-hint-2, eval = FALSE}
qscores %>%
  ... %>%
  ... %>%
  summarize(num_classes = n(), 
            mean_hours = ..., 
            sd_hours = ..., 
            .groups = "drop")
```

### Exercise 6

`arrange()` the data set by `num_classes` in descending order.

```{r qscores6, exercise = TRUE}

```

```{r qscores6-hint, eval = FALSE}
... %>%
  arrange(desc(...))
```

### Exercise 7

Now use `slice()` to return the top 3 rows of the data set, i.e. the 3 largest departments at Harvard by number of classes.

```{r qscores7, exercise = TRUE}

```

```{r qscores7-hint-1, eval = FALSE}
Remember that a:b returns all of the numbers from a to b. For example, 1:10 returns every number between 1 and 10.
```

```{r qscores7-hint-2, eval = FALSE}
... %>% 
  slice (...)
```

### Exercise 8

Group the data by `department` again. We do this because the data is no longer grouped since we set `.groups` to drop.

```{r qscores8, exercise = TRUE}

```

```{r qscores8-hint, eval = FALSE}
... %>%
  group_by(department)
```

### Exercise 9

Using `summarize()`, create a new variable, `rnorm_values`, which should be equal to the result of an `rnorm()` function. Within `rnorm()`, set `n` equal to `num_classes`, `mean` to `mean_hours`, and `sd` to `sd_hours`. Set `.groups` = "drop".


```{r qscores9, exercise = TRUE}

```

```{r qscores9-hint, eval = FALSE}
... %>%
  summarize(rnorm_values = rnorm(... = ..., 
                                 ... = ..., 
                                 ... = ...),
            .groups = "drop")
```

###

The function `rnorm` generates random draws from a normal distribution of specified `mean` and `sd`. 

### Exercise 10

`arrange()` your data by `department`. Assign all your work you have done so far to an object named `q_subset`.

```{r qscores10, exercise = TRUE}

```

### Exercise 11

Our next goal will be to create a new column with the homework values of the *actual* Harvard classes. Start a new pipe with `qscores`.`filter()` `qscores` to the "ECON," "MATH," and "GOV" departments (which we have already discovered are the 3 largest departments in our data set).

```{r qscores11, exercise = TRUE}

```

```{r qscores11-hint-1, eval = FALSE}
Remember to use the %in% operator along with the c() function.
```

```{r qscores11-hint-2, eval = FALSE}
qscores %>%
  filter(department %in% c(..., ..., ...))
```

### Exercise 12

`arrange()` by `department`. Assign your code to an object named `q_subset2`.

```{r qscores12, exercise = TRUE}

```

```{r qscores12-hint, eval = FALSE}
q_subset_2 <- qscores %>%
  filter(department %in% c("ECON", "MATH", "GOV")) %>% 
  arrange(...)
```

### Exercise 13

Finally, use `left_join()`. The first argument to `left_join()` should be `q_subset` and the second argument should be `q_subset_2`. The third argument should set `by` to "department".

```{r qscores13-setup}
q_subset_2 <- qscores %>%
  filter(department %in% c("ECON", "MATH", "GOV")) %>%
  arrange(department)

q_subset <- qscores %>%
  select(department, hours) %>%
  group_by(department) %>%
  summarize(num_classes = n(), 
            mean_hours = mean(hours), 
            sd_hours = sd(hours),
            .groups = "drop") %>%
  arrange(desc(num_classes)) %>%
  slice(1:3) %>%
  group_by(department) %>%
  summarize(rnorm_values = rnorm(n = num_classes, 
                                 mean = mean_hours, 
                                 sd = sd_hours),
            .groups = "drop") %>%
  arrange(department)
```


```{r qscores13, exercise = TRUE}

```

```{r qscores13-hint, eval = FALSE}
left_join(..., ..., by = "...")
```

### Exercise 14

Let's now use `pivot_longer()` to transform the columns `rnorm_values` and `hours`. Pivot the `names_to` "type" and `values_to` "value". Assign your code to an object named `q_join`.


```{r qscores14-setup}
q_subset_2 <- qscores %>%
  filter(department %in% c("ECON", "MATH", "GOV")) %>%
  arrange(department)

q_subset <- qscores %>%
  select(department, hours) %>%
  group_by(department) %>%
  summarize(num_classes = n(), 
            mean_hours = mean(hours), 
            sd_hours = sd(hours), 
            .groups = "drop") %>%
  arrange(desc(num_classes)) %>%
  slice(1:3) %>%
  group_by(department) %>%
  summarize(rnorm_values = rnorm(n = num_classes, 
                                 mean = mean_hours, 
                                 sd = sd_hours),
            .groups = "drop") %>%
  arrange(department)
```

```{r qscores14, exercise = TRUE}

```

```{r qscores14-hint, eval = FALSE}
q_join <- left_join(q_subset, q_subset_2, by = "department") %>%
  pivot_longer(cols = c(rnorm_values, hours), 
               names_to = "...", 
               values_to = "...")
```

### Exercise 15

Use ` %>% ` to add `ggplot()`. Set `data` to `q_join`. Maps `value` to the x-axis. Also add the layer `geom_histogram()`. Within `geom_histogram()` set `binwidth` of 2.

```{r qscores15-setup}
q_join <- left_join(q_subset, q_subset_2, by = "department") %>%
  pivot_longer(cols = c(rnorm_values, hours), 
               names_to = "type", 
               values_to = "value")
```

```{r qscores15, exercise = TRUE}

```

```{r qscores15-hint, eval = FALSE}
ggplot(data = ..., 
       mapping = aes(x = ...)) +
    geom_histogram(binwidth = ...)
```

### Exercise 16

Add the layer `facet_wrap()` to facet our histogram by `department`. Also change the aesthetic of our plot by adding the layer `theme_bw()`.

```{r qscores16-setup}
q_join <- left_join(q_subset, q_subset_2, by = "department") %>%
  pivot_longer(cols = c(rnorm_values, hours), 
               names_to = "type", 
               values_to = "value")
```

```{r qscores16, exercise = TRUE}

```

```{r qscores16-hint-1, eval = FALSE}
Within facet_wrap(), remember to put a ~ before the variable you want to facet by.
```

```{r qscores16-hint-2, eval = FALSE}
... + 
  facet_wrap(...) +
  theme_bw()
```

### Exercise 17

To finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, and caption of your choice.

Reminder: This is what your plot should look like. 

```{r qscores17-setup}
q_subset_2 <- qscores %>%
  filter(department %in% c("ECON", "MATH", "GOV")) %>%
  arrange(department)

q_subset <- qscores %>%
  select(department, hours) %>%
  group_by(department) %>%
  summarize(num_classes = n(), 
            mean_hours = mean(hours), 
            sd_hours = sd(hours),
            .groups = "drop") %>%
  arrange(desc(num_classes)) %>%
  slice(1:3) %>%
  group_by(department) %>%
  summarize(rnorm_values = rnorm(n = num_classes, 
                                 mean = mean_hours, 
                                 sd = sd_hours),
            .groups = "drop") %>%
  arrange(department)

q_join <- left_join(q_subset, q_subset_2, by = "department") %>%
  pivot_longer(cols = c(rnorm_values, hours), 
               names_to = "type", 
               values_to = "value")
```

```{r qscores17, exercise = TRUE}

```


```{r show q-scores-p}
q_p
```

## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```

