---
title: "Two Parameters"
tutorial:
  id: "two-parameters"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 7 tutorial"
---


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(rstanarm)
library(skimr)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

ch7_female <- nhanes %>%
  filter(survey == 2009, gender == "Female", age >= 18) %>%
  select(weight) %>%
  drop_na()

fit_obj <- stan_glm(data = ch7_female,
                    weight ~ 1, 
                    family = gaussian(), 
                    refresh = 0)

newobs <- tibble(constant = 1)

pp <- posterior_predict(fit_obj,
                  newdata = newobs) %>% 
       as_tibble() %>% 
       mutate_all(as.numeric)

ts <- tibble(id = 1:4, 
             test1 = 10:13, 
             test2 = 20:23,
             test3 = 30:33) 

```



```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

## Preliminaries 

In this chapter, there were several functions thrown out there that might need a refresher or a proper introduction. Let's quickly familiarize ourselves with them so we are ready to take on the exercises that follow!

###


### Exercise 1

Consider this tibble, containing the test scores for three students on four tests.

```{r ex_df, echo=TRUE}
ts <- tibble(id = 1:4, 
             test1 = 10:13, 
             test2 = 20:23,
             test3 = 30:33) 
```


We want to create a new column, called `avg` which is the average score, for the four students, on each exam. Run this code which tries to do that:

<!-- DK: This is giving a weird error, like ts has not been defined even though it is in the code chunk above. -->

```{r rowwise1, exercise = TRUE}
ts %>% 
  mutate(avg = mean(c(test1, test2, test3)))
```

Argg! That fails! We have just calculated a single number --- the mean for all exams for all students --- and then assigned it to `avg`. By default, each operation within `mutate` is first performed columns-wise.  R first computed the average of each column, and then averaged over the three columns as indicated in our code. We need something that allows us to only calculate the mean across the rows of the tibble.


### Exercise 2

`rowwise()`, and helper functions like `c_across()`, allow you to compute on a tibble row by row. Run the code chunk below to see `rowwise()` do its job! 


```{r rowwise2, exercise = TRUE}
ts %>% 
  rowwise() %>% 
  mutate(avg = mean(c_across(test1:test3)))
```


### Exercise 3

`c_across()` is designed to work alongside `rowwise()`. It allows you to easily select multiple variables. Calculate the sum and standard deviation of the test scores for each student.

```{r rw2, exercise = TRUE}

```

```{r rw2-hint-1, eval=FALSE}
ts %>%
  rowwise() %>%
  mutate(sum = ...,
         sd = ...)
```

```{r rw2-hint-2, eval=FALSE}
ts %>%
  rowwise() %>%
  mutate(sum = sum(c_across(...)),
         sd = sd(c_across(...)))
```


### Exercise 4

For the remaining questions we will work with the `nhanes` data set. Use `select` to pick the variables `gender`, `age` and `pulse`. Assign the result to an object named `our_data`.

```{r select, exercise = TRUE}


```

```{r select-hint-1, eval = FALSE}
... <- nhanes %>% 
        select(...)
```

```{r select-hint-2, eval = FALSE}
our_data <- nhanes %>% 
              select(gender, age, pulse)
```

`our_data` is available for use in later questions.


### Exercise 5

Before doing any calculations, we should get a rough overview of the data set. Run `skim()` on the tibble `our_data`. 

```{r drop_na-setup}

# This is for the tibble `our_data`. I didn't put it in the
# setup chunk at the beginning since that would make it show
# up in the last exercise when people type it. That may be
# confusing.

our_data <- nhanes %>% 
              select(gender, age, pulse)
```

```{r drop_na, exercise = TRUE}

```

```{r drop_na-hint, eval = FALSE}
skim(our_data)
```


### Exercise 6

Let's get rid of all rows with any missing values. Remove the observations with NA's by creating a pipe and using `drop_na()`. Save the clean tibble again as `our_data` as you did before.

```{r drop_na2-setup}

# Setup from before.

our_data <- nhanes %>% 
              select(gender, age, pulse)
```

```{r drop_na2, exercise = TRUE}

```

```{r drop_na2-hint-1, eval = FALSE}
... <- our_data %>% 
        drop_na()
```

```{r drop_na2-hint-2, eval = FALSE}
our_data <- our_data %>% 
              drop_na()
```


### Exercise 7

The function `ungroup()` removes grouping done by the `group_by()` function. Run the code below to see the tibble `our_data`, which has been grouped by `gender`. 

**Remember**: `group_by()` only affects how the data is grouped for subsequent operations, it does not itself change the appearance of the data!

```{r rowwise3-setup}

# Setup from before.

our_data <- nhanes %>% 
              select(gender, age, pulse) %>% 
              drop_na()
```

```{r rowwise3, exercise = TRUE}
our_data  %>%
  group_by(gender)
```


### Exercise 8

Great! Now we are going to show why using `ungroup()` is important. Let's say we wanted to calculate the average age and pulse of males and females.

Notice that `ungroup()` has been placed at the end of both calculations. Run the following code. 

```{r ungroup1-setup}

# Setup from before.

our_data <- nhanes %>% 
              select(gender, age, pulse) %>% 
              drop_na()
```

```{r ungroup1, exercise = TRUE}
our_data %>%
  group_by(gender) %>%
  mutate(m_age = mean(age)) %>% 
  mutate(m_pulse = mean(pulse)) %>%
  ungroup()
```

The output shows that the mean age (`m`) is approximately 40.3 years for males and 41.7 years for females. It also shows us that the mean pulse (`x`) is 71.67 bpm for males and 75.42 bpm for females. For both calculations, the data is grouped by `Sex` and separate from one another. 


### Exercise 9

Instead of placing `ungroup()` at the end, we are going to place it in between the two `mutate()` functions. Run the following code.

```{r ungroup2-setup}

# This is for the clean tibble `our_data`

our_data <- nhanes %>% 
              select(gender, age, pulse) %>% 
              drop_na()
```

```{r ungroup2, exercise = TRUE}
our_data %>%
  group_by(gender) %>%
  mutate(m_age = mean(age)) %>% 
  ungroup()%>% 
  mutate(x_pulse = mean(pulse)) 
```

Here our mean age (`m`), is still 40.3 years for males and 41.7 years for females. However, our mean pulse (`x`) is 73.55 bpm for every row. Because `group_by(gender)` is removed by `ungroup()` after the first `mutate()` function, the mean score is calculated for _all participants together_, which is what we do not want! Therefore, our first placement of `ungroup()` is correct. 


### Exercise 10

We can `select()` multiple variables using different methods. Suppose we wanted to select the first three variables from `nhanes`, namely `survey`, `gender` and `age`. One way, which we have already seen before, is to type out all names. Run the code below to see this approach in action.

```{r select2, exercise = TRUE}
nhanes %>%
  select(survey, gender, age)
```


### Exercise 11

However, being the tech wizards that we are, we want to make things as simple as possible. Recall the `:` operator, which creates a shortcut! Run the following code. 

```{r select3, exercise = TRUE}
nhanes %>%
  select(survey:age)
```

As you can see, `:` defines a closed interval. `select` returns all columns from (and including) 'survey' to 'age' in the order they appear in the tibble.


### Exercise 12

Awesome! We can also use `[ ]` to extract columns. This is especially useful when we want to extract variables not by their name, but by their position. Extract the third variable from `nhanes` using this method.  

**Note**: When you use `[ ]` , place a comma before the column number you want to extract. 

```{r brackets1, exercise = TRUE }


```

```{r brackets1-hint, eval = FALSE }
nhanes[...]

```


### Exercise 13

As before, we can combine `[ ]` with the `:` operator to extract multiple variables. Use this method to extract the first two variables from `nhanes`.

```{r brackets2, exercise = TRUE }


```

```{r brackets2-hint-1, eval = FALSE }
nhanes[...:...]

```

```{r brackets2-hint-2, eval = FALSE }
nhanes[,1:2]

```

### Exercise 14

We can use the function `rename()` to change the names of the variables in a tibble. For this, simply set the new name equal to the old name within `rename()`.

Copy your code from the last exercise. Add a pipe and `rename()` "survey" to "year" and "gender" to "sex".

```{r set_names, exercise = TRUE }

```

```{r set_names-hint-1, eval = FALSE }
nhanes[,1:2] %>% 
  rename(year = ...,
         sex = ...)

```


### Exercise 15

The function `after_stat()` can be used to pick a different computed metric than the default (here a **fraction** instead of **count**).

Run the following code chunk.

```{r afterstat, exercise = TRUE}
ggplot(nhanes, aes(age)) +
  geom_histogram(bins = 40, aes(y = after_stat(count/sum(count))))
```

As you can see, the y-axis in the plot shows the relative proportion of each age group. Without our transformation, `geom_histogram()` would display only the absolute number of each group.


## Wisdom
###

Consider the graph below.

```{r}
ch7 <- nhanes %>% 
  select(age, gender, weight, survey) %>%
  filter(age >= 18, gender == "Female") %>% 
  drop_na()

ch7 %>%
  ggplot(aes(x = weight, color = gender)) + 
  geom_density() + 
  labs(x = "Weight, in kg",
       y = "Density",
       title = "Adult Female Weight in NHANES") +
  theme(legend.position = "none")
```


### Exercise 1

As you can tell, the graph above displays "Adult Female Weight by Gender in NHANES". Let's say our motive behind generating this graph was to answer the question: _What is the probability that the next adult female we meet in Cambridge today will weigh more than 100kg_? 

###

Using the concept of **Wisdom**, write a paragraph about whether or not this data is relevant for the problem we face. See *The Primer* for guidance. Make sure to use the terms "representative" and "validity."


```{r exercise-2}
question_text(NULL,
	message = "Place the correct answer.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	options = list(nrows = 6))
```




## Justice 

### Exercise 1


$$y_i = \mu + \epsilon_i$$ \n

$$where \ \ \epsilon_i \sim N(0, \sigma^2)$$
&nbsp;

Recall the mathematical relationship above. Write a paragraph describing, in your own words, what each component of this equation describes in the context of our question. You do not need to figure out how to display the symbols in your answer, just write their names, like "phi," mu," "sigma," "epsilon," "delta," and so on.  

```{r Justice1}
question_text(
  "Answer:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```


### Exercise 2

Great! Next, specify which are the two parameters we want to determine. Also mention which one we care most about and why, writing no more than 2 sentences.

```{r Justice2}
question_text(
  "Answer:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```


### Exercise 3

Using your own words, explain in 2 sentences why this is a predictive model. 

```{r Justice3}
question_text(
  "Answer:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```



## Courage 

Let's create a Bayesian model of female weight.


### Exercise 1

We will only need a subset of `nhanes`. Run the following code.

```{r ch7_female, exercise = TRUE}
ch7_female <- nhanes %>%
  filter(survey == 2009, gender == "Female", age >= 18) %>%
  select(weight) %>%
  drop_na()

ch7_female
```

We will use the `ch7_female` tibble in the questions which follow.


### Exercise 2

Use `stan_glm()` to create a simple Bayesian model. Set `data` to `ch7_female`, `family` to `gaussian()`, and `refresh` to 0. The formula argument should be `weight ~ 1`.

```{r stanglm, exercise = TRUE}
library(rstanarm)


```

```{r stanglm-hint, eval = FALSE}
stan_glm(data = ...,
         formula = ..., 
         family = ..., 
         refresh = ...)
```


### Exercise 3

Great! We should save our model to be able to work with it in later questions, so we need to assign it to an object. In this case, we call it `fit_obj`. Run this code.

```{r objfit, exercise = TRUE}
fit_obj <- stan_glm(data = ch7_female,
                    weight ~ 1, 
                    family = gaussian(), 
                    refresh = 0)

fit_obj 
```

While we have saved the model, the model summary is above still somewhat complex. Let's simplify this.


### Exercise 4

Instead of printing out the whole model like before, just use `print` to print out the parameters of the model. Set the `detail` argument to FALSE.

```{r print, exercise = TRUE}

```

```{r print-hint, eval= FALSE}
print(fit_obj, detail = ...)
```


### Exercise 5

Recall that the most important single number related to a distribution is some measure of its location. The two common measures for this are _mean_ and _median_. 

In a single sentence, using your own words, describe why we use the median here.

```{r mean}
question_text(
  "Answer:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```


### Exercise 6

Now, in 2 sentences, use your own words to define `MAD_SD`.

```{r MADS}
question_text(
  "Answer:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```


### Exercise 7

Awesome! Now let's create the following posterior distribution.

```{r courage_plot}
weight_p <- fit_obj %>% 
  as_tibble() %>% 
  rename(mu = `(Intercept)`) %>% 
  ggplot(aes(x = mu)) +
    geom_histogram(aes(y = after_stat(count/sum(count))), 
                   bins = 200, 
                   color = "white") +
    labs(title = "Posterior Probability Distribution",
         subtitle = "Average weight among American adult women in 2009",
         x = "Weight in Kilograms",
         y = "Probability") +
    theme_classic()

weight_p
```

First, create a pipe starting with `fit_obj` and then continuing with `as_tibble()`.

```{r not_print, exercise = TRUE}

```

```{r not_print-hint, eval = FALSE}
fit_obj %>% 
  ...
```


### Exercise 8

Cool. Now copy and paste your work from the previous question and continue the pipe. Use `rename()` and rename `(Intercept)` as `mu`. Recall that column names can be anything you want. But, if you use weird things --- like a parenthesis --- then you need to put backticks around the column names. Since that is a bother, we prefer column names like `mu` to column names like `(Intercept)`.

```{r prev, exercise = TRUE}

```

```{r prev-hint, eval = FALSE}
fit_obj %>% 
  as_tibble() %>%
  rename(mu = `(Intercept)`) 
```


### Exercise 9
  
Continue the pipe and use `ggplot()`. Map x to `mu` in the `aes` argument. Use `geom_histogram()` and map y to the `after_stat()` function. Set its argument to `count` divided by the `sum` of `count`.
    
```{r geom_hist, exercise = TRUE}

```

```{r geom_hist-hint-1, eval=FALSE}
after_stat(count/sum(count)) accomplished the same normalization step 
which we did by hand in previous chapters using dplyr.

```

```{r geom_hist-hint-2, eval=FALSE}
fit_obj %>% 
  as_tibble() %>% 
  rename(mu = `(Intercept)`) %>% 
  ggplot(aes(x = mu)) +
    geom_histogram(aes(y = after_stat(.../sum(...))))

```


### Exercise 10

Also, set `bins` to 200 and `color` to white within `geom_histogram()`.

```{r geom_hist2, exercise = TRUE}

```


### Exercise 11

Title your histogram "Posterior Probability Distribution" with the subtitle, "Average weight among American adult women in 2009". Also name the x-axis "Weight" and the y-axis "Probability". Add a layer and use `theme_classic()`. Reminder: Your plot should look something like this:

```{r courage-answer}
weight_p
```

```{r classic, exercise=TRUE}

```

```{r classic-hint, eval=FALSE}
Use labs() to add labels.
```


## Temperance 

We have a model of female height in 2009. What can we do with it? Let's use it to answer out initial question: _What is the probability that the next adult female we meet in Cambridge today will weigh more than 100 kilos?_

### Exercise 1

Create a tibble with one variable, `constant`, which is set equal to the value 1. Assign this tibble to an object named `newobs`.

```{r newobs, exercise = TRUE}

```

```{r newobs-hint-1, eval = FALSE}
... <- tibble(...)
```

```{r newobs-hint-2, eval = FALSE}
newobs <- tibble(constant = 1)
```

`newobs` is available for use in later questions.


### Exercise 2

Let's now obtain some estimates for the weight of a single woman. 

Use `posterior_predict` with `fit_obj` as the first argument to get some draws from the posterior distribution of our model. Set the `newdata` argument equal to the tibble `newobs` to indicate that we only want estimates for one person.

```{r pp1, exercise = TRUE}

```

```{r pp1-hint, eval = FALSE}
posterior_predict(fit_obj,
                  newdata = ...)
```


### Exercise 3

Good job! We now have 4000 estimates for a random woman's weight in kg.

Copy your code from above and add two pipes with `as_tibble()` and `mutate_all(as.numeric)`. Assign the result to an object named `pp` to save it.

```{r pp2, exercise = TRUE}

```

```{r pp2-hint-1, eval = FALSE}
... <- posterior_predict(fit_obj,
                  newdata = newobs) %>% 
       ... %>% 
       ...
```

```{r pp2-hint-2, eval = FALSE}
pp <- posterior_predict(fit_obj,
                  newdata = newobs) %>% 
       as_tibble() %>% 
       mutate_all(as.numeric)
```

`pp` is available for use in later questions.


### Exercise 4

It is always helpful to plot our data before working with it.

Start by adding a pipe to `pp` and create a histogram with `geom_histogram()`. Use `after_stat()` to display the y-axis in relative proportions of each weight group. Set `bins` to 200 and `color` to "white".

```{r draw_plot1, exercise = TRUE }
pp

```

```{r temperance_plot1-hint-1, eval = FALSE}
pp %>% 
  ggplot(aes(x = ...)) +
    geom_histogram(aes(y = after_stat(...)),
                   binwidth = ...,
                   color = ...)
```

```{r temperance_plot1-hint-2, eval = FALSE}
pp %>% 
  ggplot(aes(x = `1`)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 200,
                   color = "white")
```


### Exercise 5

Your code should now look as shown below.

Add `labs()` to title your histogram "4000 Draws from Posterior Distribution" with the subtitle, "Average weight of a random American adult woman in 2009". Name the x-axis "Weight in Kilograms" and the y-axis "Probability". Finally, add a layer and use `theme_classic()`. 

```{r draw_plot2, exercise = TRUE}
pp %>% 
  ggplot(aes(x = `1`)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 200,
                   color = "white")

```

```{r draw_plot2-hint, eval = FALSE}
pp %>% 
  ggplot(aes(x = `1`)) +
    geom_histogram(aes(y = after_stat(count/sum(count))), 
                   binwidth = 0.02, 
                   color = "white") +
    labs(title = ...,
         subtitle = ...,
         x = ...,
         y = ...) +
    theme_classic()
```

&nbsp;

How does the distribution of our 4000 estimates compare to the actual posterior distribution you plotted earlier? As a reminder, it looked like this:

```{r courage_plot2}
fit_obj %>% 
  as_tibble() %>% 
  rename(mu = `(Intercept)`) %>% 
  ggplot(aes(x = mu)) +
    geom_histogram(aes(y = after_stat(count/sum(count))), 
                   bins = 200, 
                   color = "white") +
    labs(title = "Posterior Probability Distribution",
         subtitle = "Average weight among American adult women in 2009",
         x = "Weight in Kilograms",
         y = "Probability") +
    theme_classic()
```

### Exercise 6

The histogram already shows approximately what the answer to our question might be. Let's calculate it exactly.

Determine the proportion of all women in `pp` who weigh more than 100kg.

```{r frac, exercise = TRUE}

```

```{r frac-hint-1, eval = FALSE}
sum(... > 100) / length(...)
```

```{r frac-hint-2, eval = FALSE}
sum(pp$`1` > 100) / length(pp$`1`)
```

```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
