---
title: "Four Parameters"
tutorial:
  id: "four-parameters"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 9 tutorial"
---


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(rstanarm)
library(broom.mixed)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600,   # Extra time for model building
        tutorial.storage = "local") 

fit_1 <- stan_glm(formula = att_end ~ liberal + att_start,
                  data = trains,
                  refresh = 0,
                  seed = 42)
tidy <- fit_1 %>% 
  tidy() %>% 
  select(term, estimate)
 
intercept <- tidy$estimate[1]
liberal_true <- tidy$estimate[2]
att_start <- tidy$estimate[3]

liberal_false_int <- intercept
liberal_false_slope <- att_start

liberal_true_int <- intercept + liberal_true
liberal_true_slope <- att_start
```

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```

## Wisdom
###

Consider the following plot.

```{r wisdom}
ggplot(trains, aes(x = att_start, y = att_end, color = liberal)) +
  geom_point() +
  labs(title = "Attitude End Compared with Attitude Start and Liberal",
       x = "Attitude at Start of Study",
       y = "Attitude at End of Study",
       color = "Liberal?")
```

<!-- DK: This is a bad question. What question are we trying to answer? Given that tie it to population and representativeness. -->

The following plot shows a comparison of three variables in the `trains` dataset. Using **Wisdom**, write a paragraph about whether or not the variables `att_start` and `liberal` should be used to predict `att_end`. See *The Primer* for guidance.

```{r wisdom-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 6))
```

## Justice and Courage
###

Let's build a model. Our outcome variable will be `att_end` and we will have two explanatory variables: `liberal` and `att_start`. Here is the math we will be using:

$$y_i = \beta_0  + \beta_1 x_1 + \beta_2 x_2$$ 

where 
$y = att\_end$, $x_1 = att\_start$, and $x_2 = liberal$,

If liberal = FALSE:

$$y = \beta_0  + \beta_1 x_1 $$


If liberal = TRUE: 

$$y = (\beta_0  + \beta_2) + \beta_1 x_1 $$


### Exercise 1

Looking at the model above, which are the parameters? You do not need to figure out how to display the symbols in your answer, just write their names (i.e. "epsilon," "delta," etc. ).

```{r justice-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 6))
```

### Exercise 2

Great! Now write a sentence for each parameter that describes what it means.

```{r justice-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 6))
```


### Exercise 3

Let's implement the model using `stan_glm()`. The formula argument should be `att_end ~ liberal + att_start`. Set `data` to`trains`, and `refresh` to 0.  Also set the `seed` argument to 42. Assign your work to an object named `fit_1`.

```{r courage-3, exercise = TRUE}

```


```{r courage-3-hint, eval = FALSE}
fit_1 <- stan_glm(data = ...,
                  formula = ...,
                  refresh = ...,
                  seed = )
```

### Exercise 4

Use `print()` to look at our parameter values. Set the `detail` argument to FALSE.

```{r courage-4, exercise = TRUE}

```
 
```{r courage-4-hint, eval = FALSE}
print(..., detail = ...)
```

### Exercise 5

Look at the results above. Write two sentences, using your own words, that explains the meaning of `(Intercept)`.

```{r courage-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 6

Write two sentences that explains the value of `att_start`.

```{r courage-6}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```


Let's create the following parallel slopes model. The model allows us to observe the differences in liberalTRUE and liberalFALSE in relation to attitude start and attitude end.


```{r}
parallel_p <- ggplot(trains, aes(x = att_start, 
                   y = att_end, 
                   color = liberal)) +
  geom_point() +
  geom_abline(intercept = liberal_false_int,
              slope = liberal_false_slope, 
              color = "#F8766D", 
              size = 1) +
  geom_abline(intercept = liberal_true_int,
              slope = liberal_true_slope,
              color = "#00BFC4", 
              size = 1) +
  labs(title = "Parallel Slopes Model",
       subtitle = "Non-liberals start with higher att_start values",
       x = "Attitude at Start", 
       y = "Attitude at End", 
       color = "Liberal?") 

parallel_p
```


### Exercise 7 

First, we need to tidy our data. Start a pipe with `fit_1` and use the function `tidy()`. Then use`select()` to grab the `term` and `estimate` variables. Save your results to an object named `tidy_1`.

```{r courage-7, exercise = TRUE}

```

### Exercise 8

Great. Let's now extract and name the columns of our tidy object. Start by extracting the first value from the `estimate` column. Save your results to an object named `intercept`.


```{r courage-8, exercise = TRUE}

```

```{r courage-8-hint-1, eval = FALSE}
Use [ ] with the argument 1 to extract the first column 
```

```{r courage-8-hint-2, eval = FALSE}
intercept <- tidy$estimate[1]
```

### Exercise 9

Now extract the second value from the `estimate` column. Save your results to an object named `liberal_true`.


```{r courage-9, exercise = TRUE}

```

```{r courage-9-hint-1, eval = FALSE}
Use [ ] with the argument 2 to extract the first column 
```

```{r courage-9-hint-2, eval = FALSE}
liberal_true <- tidy$estimate[2]
```

### Exercise 10

Lastly, extract the third value from the `estimate` column. Save your results to an object named `att_start`.


```{r courage-10, exercise = TRUE}

```

```{r courage-10-hint-1, eval = FALSE}
Use [ ] with the argument 3 to extract the first column 
```

```{r courage-10-hint-2, eval = FALSE}
att_start <- tidy$estimate[3]
```

### Exercise 11

Great. Now we need intercepts and slopes for our graph for the two lines that are plotted (liberalTRUE and liberalFALSE).  Let's code for liberalFALSE first.

Recall the (Intercept) value of `fit_1` is the intercept for liberalFALSE. Therefore, save `intercept` to an object named `liberal_false_int`. 

```{r courage-11, exercise = TRUE}

```

```{r courage-11-hint-1, eval = FALSE}

```

### Exercise 12

Great. The slopes for both liberalFALSE and liberalTRUE are `att_start`. Save `att_start` to an object named `liberal_false_slope`.

```{r courage-12, exercise = TRUE}

```

```{r courage-12-hint-1, eval = FALSE}

```

### Exercise 13

Great. Now let's do the same thing for liberalTRUE. Recall the intercept value for liberalTRUE requires you to add two values together: `intercept` + `liberal_true`.  Add these two variables together and save their results to an object named `liberal_true_int`.

```{r courage-13, exercise = TRUE}

```

```{r courage-13-hint, eval = FALSE}

```

### Exercise 14

Awesome. Now save `att_start` to an object named `liberal_true_slope`.

```{r courage-14, exercise = TRUE}

```

```{r courage-14-hint, eval = FALSE}

```

### Exercise 15 

Now that we have the variables we need, let's plot our two parallel lines! Use `ggplot()` and `geom_point()` to create a scatterplot. Use the `data``trains`. Also, map `att_start` to the x-axis, `att_end` to the y-axis, and `liberal` to `color`.

```{r courage-15, exercise = TRUE}

```

```{r courage-15-hint, eval = FALSE}
ggplot(..., aes(..., 
                ..., 
                ...)) +
  geom_point()
```

### Exercise 16



```{r courage-16, exercise = TRUE}

```

```{r courage-16-hint, eval = FALSE}
ggplot(..., aes(..., 
                ..., 
                ...)) +
  geom_point()
```

### Exercise 17

Let's create the first line to our graph. Use `geom_abline()` and set `intercept` to `liberal_false_int` and set `slope` to `liberal_false_slope`. Also set `size` to 1 and `color` to "#F8766D".

```{r courage-17, exercise = TRUE}

```

```{r courage-17-hint, eval = FALSE}
 geom_abline(intercept = ...,
              slope = ..., 
              color = ..., 
              size = ...) 
```

### Exercise 18

Let's the second line to our graph. Use `geom_abline()` and set `intercept` to `liberal_true_int` and set `slope` to `liberal_true_slope`. Also set `size` to 1 and `color` to "#00BFC4".

```{r courage-18, exercise = TRUE}

```

```{r courage-18-hint, eval = FALSE}
 geom_abline(intercept = ...,
              slope = ..., 
              color = ..., 
              size = ...) 
```

### Exercise 19

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels to your graph. Also, set the `color` argument to
"Liberal?".

Reminder: This is what your graph should look like. 

```{r}
parallel_p
```


```{r courage-19, exercise = TRUE}

```

```{r courage-19-hint, eval = FALSE}
... + 
  labs(title = ...,
       subtitle = ...,
       x = ..., 
       y = ..., 
       color = ...) 
```


### Exercise 20 

Great! Now write a paragraph that interprets the graph you created above.

```{r courage-20}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 6))
```


## Temperance
###

Consider:

*If there is a group of 10 people at the train station today, all liberal, five of whom have an `att_start` value of 13 and five of whom that have an `att_start` value of 8, how many will have an att_end of greater than 9 at the end of the experiment?*

We will create a plot of the posterior probability distribution of this unknown number that looks something like this:

```{r}
newobs <- tibble(liberal = TRUE, 
       att_start = c(rep(13, 5), rep(8, 5)))

temp_p <- posterior_predict(fit_1, newobs) %>% 
  as_tibble() %>% 
  mutate_all(as.numeric) %>% 
  rowwise() %>% 
  mutate(total = sum(c_across() > 9)) %>% 
  ggplot(aes(x = total)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 100)  +
    labs(title = "Posterior for Number of People with `att_end` > 9",
         subtitle = "Six is the most likely number, but values from 5 to 8 are plausible",
         x = "Number",
         y = "Probability") +
    scale_x_continuous(breaks = 3:10,
      labels = scales::number_format(accuracy = 1)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    theme_classic()

temp_p
```



**Note:** Make sure you copy/paste your code for each step to the next question. If you do not, you will get an error that your object does not exist. 

### Exercise 1

Let's begin by answering the first question. To do so, create a tibble a named `newobs` that has ten rows, one for each of the people in our question.

```{r temp-1, exercise = TRUE}

```

```{r temp-1-hint, eval = FALSE}
newobs <- tibble(liberal = TRUE, 
       att_start = c(rep(13, 5), rep(8, 5)))
```

### Exercise 2

Use `posterior_predict()`. The first argument to `posterior_predict()` should be `fit_1`. Also set `newdata` to `newobs`.

```{r temp-2, exercise = TRUE}

```

```{r temp-2-hint, eval = FALSE}
posterior_predict(fit_1, 
                  newdata = newobs)
```

### Exercise 3

Pipe the results of `posterior_predict()` to `as_tibble()`.

```{r temp-3, exercise = TRUE}

```

```{r temp-3-hint, eval = FALSE}
... %>% 
  as_tibble() 
```

### Exercise 4

Extend the pipe with `mutate_all(as.numeric)`.

```{r temp-4, exercise = TRUE}

```

```{r temp-4-hint, eval = FALSE}
... %>%  
  mutate_all(as.numeric)
```

### Exercise 5

Write a paragraph that interprets the tibble you just created. Make sure to answer the question in your response. Make sure to use the word "draws."

<!-- DK: Could provide more guidance. -->

```{r temp-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```



### Exercise 6

Continue your pipe `rowwise()` and then use `mutate()` with `sum()` and `c_across()` to make a new variable named `total` which is the sum of people with `att_end` greater than 9. 


```{r temp-6, exercise = TRUE}

```

```{r temp-6-hint, eval = FALSE}
... %>% 
  rowwise() %>% 
  mutate(total = sum(c_across() > 9))
```

### Exercise 7

Extend the pipe to create a plot. Recall that this is what it looks like:

```{r}
temp_p
```


```{r temp-7, exercise = TRUE}

```

```{r temp-7-hint, eval = FALSE}
... %>% 
  ggplot(aes(x = total)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 100)  +
    labs(title = ...,
         subtitle = ...,
         x = "Number",
         y = "Probability") +
    scale_x_continuous(breaks = ...,
      labels = scales::number_format(accuracy = ...)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = ...)) +
    theme_classic()
```


## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```
