---
title: DGM Linear
author: Var Kurapati
tutorial:
  id: dgm-linear
  version: 1.2.0
output:
  learnr::tutorial:
    df_print: default
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: 'Learn to fit and interpret linear regression models using tidymodels and marginaleffects, applied to housing prices in Ames, Iowa.'
---

```{r setup, include=FALSE}
library(learnr)
library(tutorial.helpers)
library(knitr)
library(tidyverse)
library(tidymodels)
library(marginaleffects)

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(out.width = '90%')
options(tutorial.exercise.timelimit = 600,
        tutorial.storage = "local")

mod_linear <- linear_reg() |>
  set_engine("lm") |>
  fit(Sale_Price ~ Gr_Liv_Area + Year_Built, data = ames)
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

## Introduction
###

The `ames` dataset records 2,930 houses sold in Ames, Iowa between 2006 and 2010 — the size, age, and condition of each house, along with the price it actually sold for.

This tutorial asks a simple question: **can we predict a house's sale price from its size and age?**

`Sale_Price` is a number — not a category — and that is information a model can use. We use two packages to build and interpret such a model. **[tidymodels](https://www.tidymodels.org/)** fits it. **[marginaleffects](https://marginaleffects.com/)** interprets it — turning raw coefficients into predicted dollar amounts that are immediately understandable.

Interpreting a model with **marginaleffects** almost always comes down to one distinction: **marginal** vs. **conditional**. A marginal prediction runs the model on every *real* house in the dataset and averages the results (the `by` argument). A conditional prediction builds one or more *hypothetical* houses, holding some variables fixed and varying others (the `condition` argument). So every time you see `by`, you are averaging over real houses, and every time you see `condition`, you are looking at a hypothetical.

Every dataset is a shadow cast by some real process — a **data generating mechanism**, or DGM — never the thing itself. Two moves lie ahead: *Courage*, proposing a structure and fitting it to real data (Tidymodels), and *Temperance*, using that fitted machine — with humility — to answer the question we started with (Marginal Effects).

### Exercise 1

You should be connected to a repo named `dgm-linear`. If you are not, create one and connect to it.

Create a new file, `analysis.qmd`, with the title `"Ames Housing"` and your name as the author. Add `execute: echo: false` to the YAML header. In a bash Terminal, render it:

```
quarto render analysis.qmd
```

Open `analysis.html` with Live Server. Create a `.gitignore` with `analysis_files` on the first line. Commit and push.

In the R Terminal, run:

```
show_file(".gitignore")
```

CP/CR.

```{r introduction-1}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 3)
```

###

```
analysis_files
```

###

Every dataset comes from somewhere. `ames` is a record of houses that were actually sold in Ames, Iowa between 2006 and 2010, compiled by the local assessor's office — not a random sample of all houses everywhere.

### Exercise 2

In a new code chunk in `analysis.qmd`, load the libraries you'll need. Add `#| message: false`. Render.

```
#| message: false
library(tidyverse)
library(tidymodels)
library(marginaleffects)
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r introduction-2}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 10)
```

###

<pre><code>#| message: false
library(tidyverse)
library(tidymodels)
library(marginaleffects)
</code></pre>

###

`ames` needs no loading of its own — it comes with **modeldata**, which `library(tidymodels)` attaches. The data is a shadow of the Ames housing market; the DGM we build will be our best account of the process that cast it.

### Exercise 3

In a new code chunk, print the first 10 rows of `ames`, narrowed to the three columns this tutorial uses. Render.

```
ames |>
  select(Sale_Price, Gr_Liv_Area, Year_Built) |>
  head(10)
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r introduction-3}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 4)
```

###

```{r introduction-3-test}
#| echo: true
ames |>
  select(Sale_Price, Gr_Liv_Area, Year_Built) |>
  head(10)
```

###

`Sale_Price` is the outcome we want to predict — the actual price each house sold for in dollars. `Gr_Liv_Area` is above-ground living area in square feet. `Year_Built` is the year the house was constructed.

### Exercise 4

Ask AI to create a scatterplot of `Sale_Price` vs. `Gr_Liv_Area`. Paste its code into a new chunk. Render.

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r introduction-4}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = FALSE,
  incorrect = NULL,
  rows = 10)
```

###

Here's our version, for comparison — yours doesn't need to match exactly, just the same idea:

```{r introduction-4-test}
#| echo: true
ames |>
  ggplot(aes(x = Gr_Liv_Area, y = Sale_Price)) +
  geom_point(alpha = 0.3) +
  labs(
    title = "House sale price vs above-ground living area",
    x = "Above-ground living area (sq ft)",
    y = "Sale price ($)"
  ) +
  scale_y_continuous(labels = scales::dollar)
```

###

There is a clear positive relationship — larger houses sell for more. The relationship is roughly linear, which means a linear regression model is a reasonable choice for this data.

### Exercise 5

Commit and push, with a message like "Add Ames housing data and initial exploration." In the bash Terminal, run:

```
git log -1
```

CP/CR.

```{r introduction-5}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 5)
```

###

```
commit a1b2c3d4e5f6...
Author: Var Kurapati
Date:   Mon Jul 27 2026
    Add Ames housing data and initial exploration
```

###

Before we fit anything, it's worth asking where this data came from. Whatever `mod_linear` learns, it learns about *this* time and place — Ames, Iowa, 2006–2010 — not housing markets in general. Keep asking, as we build the model ahead: *How did this data come to be?*

## Tidymodels
###

Every dataset is produced by some real-world process — a **data generating mechanism**, or DGM. Building one means committing to a structure, choosing a method for estimating it, and fitting it to data: **Structure → Method → Fitting**. `Sale_Price` is a number, so the structure here is `linear_reg()`.

There is no single "correct" DGM for a given question. Which right-hand-side variables to include is a judgment call — one we will make, and remake, several times in this section.

### Exercise 1

In a new code chunk, count how many houses fall into each neighborhood, sorted from most to least common. Render.

```
ames |>
  count(Neighborhood, sort = TRUE) |>
  head(10)
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r tidymodels-1}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 6)
```

###

```{r tidymodels-1-test}
#| echo: true
ames |>
  count(Neighborhood, sort = TRUE) |>
  head(10)
```

###

North Ames is the most common neighborhood with 443 houses. The uneven distribution across neighborhoods is worth remembering — any model we fit will be better calibrated for neighborhoods with many houses than for those with few.

### Exercise 2

In a new code chunk, specify a linear regression with `linear_reg()` and pipe it into `set_engine("lm")`. Print the result. Render.

```
linear_reg() |>
  set_engine("lm")
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r tidymodels-2}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 4)
```

###

```{r tidymodels-2-test}
#| echo: true
linear_reg() |>
  set_engine("lm")
```

###

`linear_reg()` proposes the **structure**: a numeric outcome predicted by a linear combination of predictors. `set_engine("lm")` picks the **method**: R's classical least-squares fitting. These are separate decisions — the DGM and our procedure for estimating it are separate things.

### Exercise 3

Update your chunk to pipe into `fit(Sale_Price ~ Gr_Liv_Area, data = ames)` — just one predictor for now. Then pipe the result into `tidy(conf.int = TRUE)` and `select(term, estimate, conf.low, conf.high)`. Render.

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r tidymodels-3}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 8)
```

###

```{r tidymodels-3-test}
#| echo: true
linear_reg() |>
  set_engine("lm") |>
  fit(Sale_Price ~ Gr_Liv_Area, data = ames) |>
  tidy(conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high)
```

###

`fit()` is where the mechanism meets real data — this is step three of Structure → Method → Fitting. The `Gr_Liv_Area` coefficient is about 111, with an interval well clear of zero: each additional square foot is associated with about $111 more in sale price.

### Exercise 4

Edit the formula to add `Year_Built` as a second predictor. Render.

```
linear_reg() |>
  set_engine("lm") |>
  fit(Sale_Price ~ Gr_Liv_Area + Year_Built, data = ames) |>
  tidy(conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high)
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r tidymodels-4}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 8)
```

###

```{r tidymodels-4-test}
#| echo: true
linear_reg() |>
  set_engine("lm") |>
  fit(Sale_Price ~ Gr_Liv_Area + Year_Built, data = ames) |>
  tidy(conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high)
```

###

Both intervals exclude zero — by this heuristic, `Year_Built` earns its place. Each additional year a house was built later is associated with about $1,087 more in sale price, holding living area fixed.

### Exercise 5

What about overall condition? Edit the formula to add `Overall_Cond`. Render.

```
linear_reg() |>
  set_engine("lm") |>
  fit(Sale_Price ~ Gr_Liv_Area + Year_Built + Overall_Cond, data = ames) |>
  tidy(conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high)
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r tidymodels-5}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 8)
```

###

```{r tidymodels-5-test}
#| echo: true
linear_reg() |>
  set_engine("lm") |>
  fit(Sale_Price ~ Gr_Liv_Area + Year_Built + Overall_Cond, data = ames) |>
  tidy(conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high)
```

###

`Overall_Cond` is categorical, so it produces one row per level — and the intervals are mixed: some levels clearly exclude zero, others don't. This is exactly the "many possible DGMs" problem: there's no automatic rule that resolves it. For this tutorial, we'll make the judgment call to keep things simple and go back to the two-variable model as our final DGM.

### Exercise 6

Edit your working chunk one last time: remove `Overall_Cond`, remove the `tidy()`/`select()` steps, and assign the result to `mod_linear`. Print it. Render.

```
mod_linear <- linear_reg() |>
  set_engine("lm") |>
  fit(Sale_Price ~ Gr_Liv_Area + Year_Built, data = ames)
mod_linear
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r tidymodels-6}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 8)
```

###

```{r tidymodels-6-test}
#| echo: true
mod_linear <- linear_reg() |>
  set_engine("lm") |>
  fit(Sale_Price ~ Gr_Liv_Area + Year_Built, data = ames)
mod_linear
```

###

From here on, you never touch this formula again. `mod_linear` is the fixed, saved model every later exercise addresses — the candidates you discarded never got a permanent name at all, which was deliberate: there are always more DGMs you *could* fit than you actually will, and we never know for certain which one is true.

### Exercise 7

Add `#| cache: true` to the top of your `mod_linear` chunk, and add `*_cache/` to your `.gitignore`. In the R Terminal, run:

```
show_file(".gitignore")
```

CP/CR.

```{r tidymodels-7}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 4)
```

###

```
analysis_files
*_cache/
```

###

Structure → Method → Fitting. You have now completed all three steps. `mod_linear` is your fitted DGM — the machine every later question will be addressed to.

### Exercise 8

This exercise assumes `mod_linear` is exactly the model you assigned in Exercise 6. In a new code chunk, run the following to see `mod_linear`'s coefficients at a readable precision. Render.

```
mod_linear |>
  tidy(conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high) |>
  mutate(across(where(is.numeric), \(x) round(x, 0)))
```

As you can see, the coefficient on `Gr_Liv_Area` is about 96. What does that mean?

```{r tidymodels-8}
question_text(NULL,
  answer("For houses built in the same year, each additional square foot of above-ground living area is associated with an expected increase in sale price of $96, with a 95% confidence interval of $93 to $99.", correct = TRUE),
  allow_retry = FALSE,
  incorrect = NULL,
  rows = 6)
```

###

```{r tidymodels-8-test}
#| echo: true
mod_linear |>
  tidy(conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high) |>
  mutate(across(where(is.numeric), \(x) round(x, 0)))
```

###

Here's the answer:

> For houses built in the same year, each additional square foot of above-ground living area is associated with an expected increase in sale price of $96, with a 95% confidence interval of $93 to $99.

###

This answer describes an expected, average change rather than what happens to any one specific house, and it holds `Year_Built` fixed while describing the change in `Gr_Liv_Area` — we never claim that adding square footage *causes* a $96 increase, only that houses differing by one square foot differ in expected price by about that much.

### Exercise 9

Using the same table from Exercise 8: the coefficient on `Year_Built` is about 1,087. What does that mean?

```{r tidymodels-9}
question_text(NULL,
  answer("Holding above-ground living area constant, each additional year in a house's construction year is associated with an expected increase in sale price of $1,087, with a 95% confidence interval of $1,029 to $1,145.", correct = TRUE),
  allow_retry = FALSE,
  incorrect = NULL,
  rows = 6)
```

###

Here's the answer:

> Holding above-ground living area constant, each additional year in a house's construction year is associated with an expected increase in sale price of $1,087, with a 95% confidence interval of $1,029 to $1,145.

###

Use that same pattern — expected value, other variables held fixed, no causal claim — whenever you're asked to interpret a coefficient in any model. The fitted DGM is not the answer to anything by itself; it is the machine we built so we can answer questions.

### Exercise 10

Add the equation for `mod_linear` as a LaTeX math block above the model chunk:

$$\widehat{\text{Sale\_Price}} = -2{,}106{,}459 + 96 \times \text{Gr\_Liv\_Area} + 1{,}087 \times \text{Year\_Built}$$

Render. In the R Terminal, run `show_file("analysis.qmd")`. CP/CR just the equation line and the `mod_linear` chunk right below it.

```{r tidymodels-10}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 20)
```

###

The relevant part of your output should look like this:

<pre><code>$$\widehat{\text{Sale\_Price}} = -2{,}106{,}459 + 96 \times \text{Gr\_Liv\_Area} + 1{,}087 \times \text{Year\_Built}$$

#| cache: true
mod_linear <- linear_reg() |>
  set_engine("lm") |>
  fit(Sale_Price ~ Gr_Liv_Area + Year_Built, data = ames)
mod_linear
</code></pre>

###

This equation IS the fitted DGM, written out in full — any prediction it produces is just plugging numbers into it. A 1,500 sq ft house built in 1980 gets: $-2{,}106{,}459 + 96 \times 1500 + 1{,}087 \times 1980 \approx \$189{,}801$.

### Exercise 11

Commit and push, with a message like "Fit final linear regression DGM for Ames housing." In the bash Terminal, run:

```
git log -1
```

CP/CR.

```{r tidymodels-11}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 5)
```

###

```
commit b2c3d4e5f6a7...
Author: Var Kurapati
Date:   Mon Jul 27 2026
    Fit final linear regression DGM for Ames housing
```

###

`mod_linear` is not the answer to anything by itself — it's the machine we built so we can answer questions, which is exactly what the next section does with it.

## Marginal Effects
###

We built the DGM with *Courage*. Now we practice *Temperance*: interpreting it, and using it — with humility — to answer the question we started with.

Interpreting a model with **marginaleffects** almost always comes down to one distinction: **marginal** vs. **conditional**. So every time you see `by`, you are averaging over real houses, and every time you see `condition`, you are looking at a hypothetical.

If Tidymodels was Structure → Method → Fitting, this section is **Question → Units → Answer**: pose the question as a quantity, specify which units you're asking about, then run the machine.

In this section we cover five functions from [**marginaleffects**](https://marginaleffects.com/): `predictions()`, `avg_predictions()`, `comparisons()`, `avg_comparisons()`, and `plot_predictions()`. Keep asking yourself, for every function call in this section, which one you're looking at.

### Exercise 1

In a new code chunk, run `predictions()` for one hypothetical house: 1,500 sq ft, built in 1980. Render.

```
predictions(mod_linear,
  newdata = data.frame(Gr_Liv_Area = 1500, Year_Built = 1980))
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-1}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 6)
```

###

```{r predictions-1-test}
#| echo: true
predictions(mod_linear,
  newdata = data.frame(Gr_Liv_Area = 1500, Year_Built = 1980))
```

###

The fitted DGM predicts a price for this house — check the `estimate` column. It should be close to what the equation gives directly: $-2{,}106{,}459 + 96 \times 1500 + 1{,}087 \times 1980 \approx \$189{,}801$. This is a **conditional** prediction — nothing in Ames is actually this exact house.

### Exercise 2

Update your chunk to compare two hypothetical houses that differ *only* in living area — 1,500 vs. 2,500 sq ft — with `Year_Built` held identical. Render.

```
predictions(mod_linear,
  newdata = data.frame(
    Gr_Liv_Area = c(1500, 2500),
    Year_Built  = c(1980, 1980)))
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-2}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 8)
```

###

```{r predictions-2-test}
#| echo: true
predictions(mod_linear,
  newdata = data.frame(
    Gr_Liv_Area = c(1500, 2500),
    Year_Built  = c(1980, 1980)))
```

###

The larger house is predicted to sell for about $96,000 more — one thousand extra square feet at $96 per square foot. That is what a coefficient of 96 *means* in practice. This is the counterfactual question: same age, different size, same machine asked twice.

### Exercise 3

Update your chunk to predict the sale price for the first actual house in the dataset, and separately check its actual sale price. Render.

```
predictions(mod_linear, newdata = ames[1, ])
ames$Sale_Price[1]
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-3}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 8)
```

###

```{r predictions-3-test}
#| echo: true
predictions(mod_linear, newdata = ames[1, ])
ames$Sale_Price[1]
```

###

The model's predicted price and the actual sale price won't match exactly. That gap — actual minus predicted — is the **residual**: the part of this house's price the model couldn't explain from just its size and age. No DGM is perfect; the residual is its honest accounting of what it missed.

### Exercise 4

Update your chunk to call `predictions(mod_linear)` with no `newdata` at all, piped to `as_tibble()`, and print `nrow()` of the result. Render.

```
predictions(mod_linear) |> as_tibble() |> nrow()
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-4}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 6)
```

###

```{r predictions-4-test}
#| echo: true
predictions(mod_linear) |> as_tibble() |> nrow()
```

###

Without `newdata`, `predictions()` defaults to running the model on every row it was fit on — one prediction per real house. That number should match the 2,930 houses mentioned back in the Introduction. `as_tibble()` turns the result into something you can wrangle with ordinary **dplyr** verbs.

### Exercise 5

Update your chunk to use `avg_predictions()` with `by = "Bldg_Type"` to get the average predicted sale price for each building type. Render.

```
avg_predictions(mod_linear, by = "Bldg_Type")
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-5}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 5)
```

###

```{r predictions-5-test}
#| echo: true
avg_predictions(mod_linear, by = "Bldg_Type")
```

###

`by` is always the same operation: run the model on every real house, then average within groups. This is a **marginal** prediction — it uses the actual distribution of houses in each building type, not a hypothetical one.

### Exercise 6

Now build a **conditional** prediction using `datagrid()`: three hypothetical houses at 1,000, 2,000, and 3,000 sq ft, with `Year_Built` held at its typical value automatically. Render.

```
predictions(mod_linear,
  newdata = datagrid(Gr_Liv_Area = c(1000, 2000, 3000)))
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-6}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 8)
```

###

```{r predictions-6-test}
#| echo: true
predictions(mod_linear,
  newdata = datagrid(Gr_Liv_Area = c(1000, 2000, 3000)))
```

###

`datagrid()` fixes every variable you don't mention at a representative value — `Year_Built` lands at its mean — and varies only the ones you specify. This is the **conditional** counterpart to `avg_predictions()` with a `by` argument: no real house needs to exist at any of these three sizes.

### Exercise 7

A prediction says what the model expects; a **comparison** says how much that expectation changes when a predictor changes. In a new code chunk, use `comparisons()` to compute the predicted change in sale price when `Gr_Liv_Area` increases by 100 sq ft, holding each house's other measurements at their own real values. Render.

```
cmp <- comparisons(mod_linear,
  variables = list(Gr_Liv_Area = 100))
nrow(cmp)
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-7}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 6)
```

###

```{r predictions-7-test}
#| echo: true
cmp <- comparisons(mod_linear,
  variables = list(Gr_Liv_Area = 100))
nrow(cmp)
```

###

2,930 rows — one per real house. Each row is the predicted change in sale price for one specific house if its living area were 100 sq ft larger, everything else held fixed. For a linear model this number is the same for every house — but for logistic or ordered models it varies by unit, which is where `comparisons()` becomes essential.

### Exercise 8

Update your chunk to use `avg_comparisons()` instead, to see the average predicted change across all real houses. Render.

```
avg_comparisons(mod_linear,
  variables = list(Gr_Liv_Area = 100))
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-8}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 8)
```

###

```{r predictions-8-test}
#| echo: true
avg_comparisons(mod_linear,
  variables = list(Gr_Liv_Area = 100))
```

###

About $9,600 per 100 sq ft — consistent with the $96 per sq ft coefficient from Tidymodels, translated into units a person can use. This is the coefficient from the model made concrete: not a log-odds or a slope, but a dollar amount for a real-world change.

### Exercise 9

Update your chunk to ask the same question about age: the average predicted change in sale price if every house were built one year later. Render.

```
avg_comparisons(mod_linear,
  variables = list(Year_Built = 1))
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-9}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 8)
```

###

```{r predictions-9-test}
#| echo: true
avg_comparisons(mod_linear,
  variables = list(Year_Built = 1))
```

###

About $1,087 per year — consistent with the coefficient from Tidymodels. `plot_comparisons()` will draw this difference visually: not two groups of different houses, but the same houses imagined in two worlds, one year apart.

### Exercise 10

Ask your AI assistant to write code using `plot_predictions(mod_linear, condition = "Gr_Liv_Area", draw = FALSE)` piped into `ggplot()` to visualize how predicted sale price varies with `Gr_Liv_Area`, with a shaded confidence band, a title, axis labels, and a dollar-formatted y-axis. Paste the code into a new chunk. Render.

```
plot_predictions(mod_linear, condition = "Gr_Liv_Area", draw = FALSE) |>
  ggplot(aes(x = Gr_Liv_Area, y = estimate)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  geom_line() +
  labs(
    title = "Predicted sale price increases with living area",
    x = "Above-ground living area (sq ft)",
    y = "Predicted sale price ($)"
  ) +
  scale_y_continuous(labels = scales::dollar)
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-10}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 10)
```

###

```{r predictions-10-test}
#| echo: true
plot_predictions(mod_linear, condition = "Gr_Liv_Area", draw = FALSE) |>
  ggplot(aes(x = Gr_Liv_Area, y = estimate)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  geom_line() +
  labs(
    title = "Predicted sale price increases with living area",
    x = "Above-ground living area (sq ft)",
    y = "Predicted sale price ($)"
  ) +
  scale_y_continuous(labels = scales::dollar)
```

###

`draw = FALSE` returns the raw numbers behind the plot — `estimate`, `conf.low`, and `conf.high` — so you can build the chart yourself with full control over what it looks like. With `condition = "Gr_Liv_Area"`, the machine runs on hypothetical houses with `Year_Built` held at its mean.

### Exercise 11

Ask your AI assistant to extend that plot to show predicted sale price across both `Gr_Liv_Area` and `Year_Built`, using `condition = c("Gr_Liv_Area", "Year_Built")` with `draw = FALSE`, piped into `ggplot()` — color the lines by `Year_Built`. Paste its code into a new chunk. Render.

```
plot_predictions(mod_linear,
  condition = c("Gr_Liv_Area", "Year_Built"), draw = FALSE) |>
  ggplot(aes(x = Gr_Liv_Area, y = estimate, color = factor(Year_Built))) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = factor(Year_Built)),
    alpha = 0.15, color = NA) +
  geom_line() +
  labs(
    title = "Predicted sale price by size and age",
    x = "Above-ground living area (sq ft)",
    y = "Predicted sale price ($)",
    color = "Year Built",
    fill = "Year Built"
  ) +
  scale_y_continuous(labels = scales::dollar)
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-11}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 10)
```

###

```{r predictions-11-test}
#| echo: true
plot_predictions(mod_linear,
  condition = c("Gr_Liv_Area", "Year_Built"), draw = FALSE) |>
  ggplot(aes(x = Gr_Liv_Area, y = estimate, color = factor(Year_Built))) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = factor(Year_Built)),
    alpha = 0.15, color = NA) +
  geom_line() +
  labs(
    title = "Predicted sale price by size and age",
    x = "Above-ground living area (sq ft)",
    y = "Predicted sale price ($)",
    color = "Year Built",
    fill = "Year Built"
  ) +
  scale_y_continuous(labels = scales::dollar)
```

###

When two variables are passed to `condition`, **marginaleffects** varies the first continuously and shows the second at representative values — that's what `factor(Year_Built)` groups into separate colored lines. Newer houses command higher prices at every size — the lines are parallel because the model has no interaction term.

### Exercise 12

Now plot a **marginal** quantity instead: use `plot_predictions()` with `by = "Bldg_Type"` and `draw = FALSE`, piped into `ggplot()`, to visualize average predicted sale price per building type. Render.

```
plot_predictions(mod_linear, by = "Bldg_Type", draw = FALSE) |>
  ggplot(aes(x = Bldg_Type, y = estimate)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) +
  labs(
    title = "Average predicted sale price by building type",
    x = NULL,
    y = "Average predicted sale price ($)"
  ) +
  scale_y_continuous(labels = scales::dollar)
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-12}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 10)
```

###

```{r predictions-12-test}
#| echo: true
plot_predictions(mod_linear, by = "Bldg_Type", draw = FALSE) |>
  ggplot(aes(x = Bldg_Type, y = estimate)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) +
  labs(
    title = "Average predicted sale price by building type",
    x = NULL,
    y = "Average predicted sale price ($)"
  ) +
  scale_y_continuous(labels = scales::dollar)
```

###

Same function, same package — but passing `by` instead of `condition` switches `plot_predictions()` from showing a hypothetical relationship to showing an average over real houses, grouped by building type. `condition` is a conditional, counterfactual view; `by` is a marginal, descriptive one — the same numbers from the `avg_predictions(by = "Bldg_Type")` table earlier, drawn as a picture.

### Exercise 13

Commit and push, with a message like "Add marginaleffects predictions, comparisons, and plots." In the bash Terminal, run:

```
git log -1
```

CP/CR.

```{r predictions-13}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 5)
```

###

```
commit c3d4e5f6a7b8...
Author: Var Kurapati
Date:   Mon Jul 27 2026
    Add marginaleffects predictions, comparisons, and plots
```

###

You have now used `predictions()`, `avg_predictions()`, `comparisons()`, `avg_comparisons()`, and `plot_predictions()` on a linear regression model, and drawn the marginal/conditional line clearly in both table and plot form. The same five functions work identically on logistic, multinomial, and ordered models — only the number of rows per case changes.

## Summary
###

You have built an analysis page that fits a linear regression model and visualizes its predictions. Now wire it into a navigable Quarto website and publish it.

### Exercise 1

Create a `_quarto.yml` file at the top level of your repo with the following contents:

```
project:
  type: website

website:
  title: "Ames Housing"
  navbar:
    left:
      - href: analysis.qmd
        text: Analysis
      - href: about.qmd
        text: About

format:
  html:
    theme: cosmo
```

In the bash Terminal, run:

```
quarto render
ls
```

In the R Terminal, run `show_file("_quarto.yml")`. CP/CR.

```{r summary-1}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 15)
```

###

<pre><code>project:
  type: website

website:
  title: "Ames Housing"
  navbar:
    left:
      - href: analysis.qmd
        text: Analysis
      - href: about.qmd
        text: About

format:
  html:
    theme: cosmo
</code></pre>

###

`_quarto.yml` turns a folder of `.qmd` files into a navigable website. Without it, each page renders independently.

### Exercise 2

Create `about.qmd` with a YAML title of `"About"`, your name, and today's date. Also clean up `analysis.qmd` so it contains only: a setup chunk, the final `mod_linear` model chunk with its equation, and the final three `plot_predictions()` visualizations from the Marginal Effects section. Remove all intermediate output. Render.

In the R Terminal, run `show_file("about.qmd")`, then `show_file("analysis.qmd")`. CP/CR both.

```{r summary-2}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 12)
```

###

```
---
title: "About"
---

Var Kurapati, July 2026.
```

###

Your `analysis.qmd` should now have exactly five code chunks — setup, the `mod_linear` model, and the three `plot_predictions()` calls — plus one math block (the equation).

###

An About page tells visitors who made the site and when.

### Exercise 3

Before publishing, preview the site locally. In the bash Terminal, run:

```
quarto preview
```

Click through the navbar in the browser preview and confirm both pages load with no errors. In the bash Terminal, stop the preview and CP/CR the first few lines of terminal output from the `quarto preview` command.

```{r summary-3}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 6)
```

###

```
Preparing to preview
Watching files for changes
GET: /
GET: /analysis.html
GET: /about.html
Browse at http://localhost:3417/
```

###

`quarto preview` builds the site and opens a live-reloading local server — catching broken links or missing pages before they go live is much cheaper than catching them after publishing.

### Exercise 4

Publish the website to GitHub Pages. In the bash Terminal, run:

```
quarto publish gh-pages
```

Copy/paste the resulting URL below.

```{r summary-4}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 3)
```

###

`quarto publish gh-pages` without a filename publishes the whole website. Both pages are now live, linked by the navigation bar.

### Exercise 5

Commit and push any remaining changes. Copy/paste the URL to your GitHub repo.

```{r summary-5}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 3)
```

###

The same pattern you used here — `linear_reg() |> set_engine() |> fit()` followed by `predictions()`, `avg_predictions()`, `comparisons()`, `avg_comparisons()`, and `plot_predictions()`, always keeping marginal and conditional straight — applies to logistic, multinomial, and ordered regression too. The interface never changes; only the structure does.

```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
