---
title: Cumulative
author: David Kane and Mihir Kaushal
tutorial:
  id: cumulative
output:
  learnr::tutorial:
    progressive: yes
    'allow_skip:': yes
runtime: shiny_prerendered
description: 'Tutorial: Cumulative'
---

```{r setup, include = FALSE}
# First packages are ones which students don't know about or load up. learnr and
# tutorial.helpers are required for the tutorial to work at all. gt is often
# needed because we often show a Preceptor Table to the students, which is built
# with this package, even though we don't show students how to create it.

library(learnr)
library(tutorial.helpers)
library(gt)

library(primer.data)
library(brms)
library(tidybayes)
library(tidyverse)

# Any package from here is something that we want students to explicitly load up
# in the tutorial. This serves two purposes. First, it provides an occasion for
# knowledge drops. Second, it reminds students that these packages must be
# loaded in the Console if they want any of the code from the tutorial to work
# in the Console. (Of course, different lines of code require different
# packages.) The most common package to be added to this section, and which
# should also be loaded by students, is a data source like primer.data.

library(tidyverse)
library(brms)
library(tidybayes)
library(gtsummary)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 

# XX: Never include setup code that takes more than a few seconds to run. For
# example, using brm() takes too much time. Instead, do the below, and see the
# relevant discussion in instructions.html.

#nhanes_1 <- brm(height ~ age,
#               data = no_na_nhanes,
#               family = gaussian(),
#               silent = 2,
#               refresh = 0,
#               seed = 16)
#write_rds(nhanes_1, "data/nhanes_1.rds")

#nhanes_1 <- read_rds("data/nhanes_1.rds")

```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

<!-- Instructions to Users of this Template -->

<!-- Read https://ppbds.github.io/primer/cardinal-virtues.html for details on the Cardinal Virtues.  -->

<!-- This is the template tutorial for creating any tutorial which uses the Cardinal Virtues to answer a question given a data set. Although its primary use is for the main chapters in the Primer, it could be used for independent tutorials as well. The letters `XX` are used to indicate locations which require editing. Comments with instructions are interspersed. -->

<!-- The tutorial is not done until you deal with, and remove, every XX. In general, XX will either mark a comment, which you should delete entirely once you have read it, or it will mark an object which you need to replace with the name that you have chosen. -->

<!-- We sometimes connect XX to another word or phrase, as in unitXX or `XX: the tibble`. In these cases, the XX indicates that this is something that you need to replace and the other words/symbols are there to guide you as to what the replacement should be. For example, you might replace unitXX with "candidate" or whatever the type of unit we have in this problem. Similarly, `XX: the tibble` would be replaced with `trains` or whatever tibble is used in this tutorial. In both cases, we provide the correct punctuation. The word "candidate" would not have any punctuation since it is just a word in a sentence. But a tibble like `trains` needs to be surrounded by backticks. -->

<!-- Once you have followed an instruction, you should delete it. -->

<!-- How much hand-holding you do depends on tutorial number. For tutorial 4, we would want to provide the same sort of questions and verbiage as we see in Project #2 in the RStudio and Github tutorial. For tutorial 10, we can go much more quickly. -->

<!-- Note that the questions are a mixture of our three types: code, written (with answer) and written (without answer). The last is only (?) used for questions in which we ask the student to run a command like `show_file()`. Otherwise, we always provide an excellent written answer because students will generally look closely at our answer because they are concerned about whether or not their written answer matches ours. -->

<!-- Whenever you tell a student to make a change in the QMD, you should tell them to `Command/Ctrl + Shift + K` in order to render the document. This will also cause it to be saved. This is good practice for catching bugs early. (Professionals do this.) Then, the last step in these exercises is often some version of show_file() and then CP/CR. -->

<!-- Make use of, e.g., `show_file("tutorial-6.qmd", start = -5)` to get just the last 5 lines of the QMD. We don't want students to copy/paste the whole document. We also don't need to ensure that we get whatever it is that was just changed. We never look! Instead, we are just plausibly threatening to look.  -->

<!-- There are many opportunities for knowledge drops, especially after definition questions. Use them! Point out something about the details of the particular problem from the chapter. Recall that students generally won't read the chapter, so we need to pull out the highlights. -->

<!-- Most of the questions in the Temperance section relate to constructing a graphic. This leads lots of opportunities for knowledge drops. This is a good place to mention items from Courage which you might not have had room for in that section. -->

<!-- Make sure to uncomment the test code chunks once you have created the necessary objects. -->

<!-- Future Improvements To Make in This Document -->

<!-- * Turn it into a vignette at some point?  -->

<!-- * In the same way that we give several quotes to choose from at the start of each section, we ought to give several different knowledge drops to choose from, in order of sophistication, for many of the standard questions, especially related to things like families and link functions. No need for authors to reinvent the wheel.  -->

<!-- * We might also consider splitting up some of the Virtues into separate topics. After all, 20+ questions in a single topic is a bit much. -->

<!-- * Would be nice if part of the testing would run all the object creation code so that we can be sure all that code works. But that would have to be during testing only. We don't want that code to execute during Run Tutorial because it often takes too long. -->

## Introduction
### 

This tutorial is best understood when done after reading [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 

## The Question
### 

*The power to question is the basis of all human progress.* - Indira Gandhi

<!-- Both a causal effect and a prediction are much fuzzier notions than you might think because their are so many, depending on AGGREGATION. -->

<!-- If you don't care what Joe would have done in a counter-factual world in which we got a different treatment, if all you care about is predicting what Joe does *given the treatment he received*, then you just need a predictive model. -->

### Exercise 1

Load **tidyverse**.

```{r the-question-1, exercise = TRUE}

```

```{r the-question-1-hint-1, eval = FALSE}
library(tidyverse)
```

```{r the-question-1-test, include = FALSE}
library(tidyverse)
```

### 

The data we will be looking at for this tutorial comes form a study where people rate how much they approve the current president.

The [Cooperative Congressional Election Study](https://cces.gov.harvard.edu/) (CCES) is one of the largest political surveys in the United States.

### Exercise 2

Load the **primer.data** package.

```{r the-question-2, exercise = TRUE}

```

```{r the-question-2-hint-1, eval = FALSE}
library(primer.data)
```

```{r the-question-2-test, include = FALSE}
library(primer.data)
```

### 

A version of the data from the Cooperative Congressional Election Study is available in the `cces` tibble.

### Exercise 3

After loading **primer.data** in your Console, type `?cces` in the Console, and paste in the Description below.

```{r the-question-3}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

The data has `r scales::comma(nrow(cces))` observations and `r scales::comma(ncol(cces))` variables.

### Exercise 4

Approval of the president is the broad topic of this tutorial. Given that topic, which variable in `cces` should we use as our outcome variable? 

```{r the-question-4}
question_text(NULL,
	message = "The `approval_ch` variable shows the approval of the president.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 2)
```

### 

`approval_ch` is an ordered factor variable and takes values of "Strongly Approve", "Approve / Somewhat Approve", "Neither Approve Nor Disapprove", "Disapprove / Somewhat Disapprove", "Never Heard / Not Sure".

### Exercise 5

Pick a variable in the data which might have a connection to the outcome variable and which we might consider to be, at least in theory, a treatment. (If you don't see a reasonable variable in the data, you can just name an imaginary variable which *might have been* included in the data.) How might we manipulate this variable?

```{r the-question-5}
question_text(NULL,
	message = "Consider positive Facebook ads as a treatment. We might expose some people to those ads and not others. Then, we can measure the causal effect of ads on presidential approval.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Such a variable does not exist in our data. There are several variables we can think of that could impact the `approval_ch`, but there is no treatment variable in our data. 

We could look at the predictive relationship between `approval_ch` and one of the many covariates in our data. 

### Exercise 6

Let's consider a *predictive* model. Which variable in `cces` do you think might have an important connection to `approval_ch`? 

```{r the-question-6}
question_text(NULL,
	message = "The ideology of an individual could be connected to their approval of the president. If the president is a Republican, we might expect more conservative individuals to have stronger measured approval.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 2)
```

### 

There is no right answer! The `cces` tibble has 17 variables. For the rest of this tutorial, we will be focusing on `ideology`, `faminc`, and `education`. 

### Exercise 7

Write a few sentences which specify two different groups of people with different values for `ideology`. Explain that the outcome variable might differ between these two groups.

```{r the-question-7}
question_text(NULL,
	message = "Some people might have a value for ideology of Very Liberal. Others might have a value of Very Conservative. Those two groups might, on average, have different values for pesidential approval, our outcome variable.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The survey consists of two waves in election years. In the pre-election wave, respondents answer two-thirds of the questionnaire. In the post-election wave, respondents answer the other third of the questionnaire.

### Exercise 8

Write a predictive question which connects the outcome variable `approval_ch` to covariates of interest. 

```{r the-question-8}
question_text(NULL,
	message = "What is the relationship between the approval of the president and an individual's ideology, family income, and education?",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

There are lots of interesting questions that could be asked. For this tutorial, we will be using the question from above. 

### Exercise 9

What is the Quantity of Interest which might help us to explore the answer to our question?

```{r the-question-9}
question_text(NULL,
	message = "Ideology could take on five forms: Very Liberal, Liberal, Moderate, Conservative, Very Conservative, and Not Sure",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

`approval_ch` is ordered factor variable, this means that it is categorical and the order of the categories matters because it is a rating.

## Wisdom
### 

*The doorstep to the temple of wisdom is a knowledge of our own ignorance.* - Benjamin Franklin

Our question:

> *What is the relationship between the approval of the president and an individual's ideology, family income, and education?*

### Exercise 1

In your own words, describe the key components of Wisdom when working on a data science problem.

```{r wisdom-1}
question_text(NULL,
	message = "Wisdom requires the creation of a Preceptor Table, an examination of our data, and a determination, using the concept of validity, as to whether or not we can (reasonably!) assume that the two come from the same population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The survey consists of two waves in election years. The pre-election wave is in the field from late September to late October. The post-election wave is administered in November.

### Exercise 2

Define a Preceptor Table.

```{r wisdom-2}
question_text(NULL,
	message = "A Preceptor Table is the smallest possible table of data with rows and columns such that, if there is no missing data, we can easily calculate the quantities of interest.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX -->

### Exercise 3

Describe the key components of Preceptor Tables in general, without worrying about this specific problem. Use words like "units," "outcomes," and "covariates."

```{r wisdom-3}
question_text(NULL,
	message = "The rows of the Preceptor Table are the units. The outcome is at least one of the columns. If the problem is causal, there will be at least two (potential) outcome columns. The other columns are covariates. If the problem is causal, at least one of the covariates will be a treatment.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

This problem is not causal so there is no treatment. In order to make causal relationships, the data needs to be manipulated. In `cces`, the data is observed, there was no manipulated data.

### Exercise 4

Create a Github repo called `cumulative`. Make sure to click the "Add a README file" check box.

Connect the `cumulative` Github repo to an R project on your computer. Name the R project `cumulative` also.

Select `File -> New File -> Quarto Document ...`. Provide a title (`"Cumulative"`) and an author (you). Render the document and save it as `analysis.qmd`.

Edit the `.gitignore` by adding `*Rproj`. Save and commit this in the Git tab. Push the commit.

In the Console, run:

```         
show_file(".gitignore")
```

CP/CR.

```{r wisdom-4}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

Remove everything below the YAML header from `causal_effect.qmd` and render the file. `Command/Ctrl + Shift + K` renders the file, this automatically saves the file as well.

### Exercise 5

What are the units for this problem?

```{r wisdom-5}
question_text(NULL,
	message = "Adults in the United States of America.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

If our question was different, we could have different units. For example, if our question was focused only on people who were Conservative, then our units would only be Adults in the United States of America who were also Conservative.

### Exercise 6

What is/are the outcome/outcomes for this problem?

```{r wisdom-6}
question_text(NULL,
	message = "approval_ch has the approval rating of the president.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Again, we could ask another question which might make another variable the outcome variable. If we wanted to know the relationship between ideology and an individual's family income and education, then the outcome variable would have been ideology. 

For this tutorial, we will be focusing on `approval_ch`.

### Exercise 7

What are some covariates which you think might be useful for this problem, regardless of whether or not they might be included in the data?

```{r wisdom-7}
question_text(NULL,
	message = "Sex and race could have a relationship with the approval of the president.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

There are variables outside the data we have that could have a meaningful relationship with `approval_ch`. Whether or not the individual comes from an immigrant family could have a relationship with their approval of the president.

We will be focusing on three variables: `ideology`, `faminc`, and `education`.

### Exercise 8

What are the treatments, if any, for this problem?

```{r wisdom-8}
question_text(NULL,
	message = "There are no treatments.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The data is not manipulated so we cannot assign any variable as the treatment. Therefore, we cannot make any causal models.

### Exercise 9

What moment in time does the Preceptor Table refer to?

```{r wisdom-9}
question_text(NULL,
	message = "2020",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Each president will have different approval rates. We will be focusing on only the year 2020 because that will reduce the amount of data we have and will help us focus on one president.

### Exercise 10

Define causal effect.

```{r wisdom-10}
question_text(NULL,
	message = "A causal effect is the difference between two potential outcomes.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

There is no requirement that there are numbers associated with those outcomes, although we might assign arbitrary numbers. We cannot find the mathematical difference between two values of `approval_ch`; we cannot find "Strongly Approve" - "Disapprove / Somewhat Disapprove" but we can assign numbers to each level of approval to help us find a difference.

### Exercise 11

What is the fundamental problem of causal inference?

```{r wisdom-11}
question_text(NULL,
	message = "The fundamental problem of causal inference is that we can only observe one potential outcome.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

If we observe that a person who is a Liberal ended up approving the president, we can never know for sure that their political identity caused that person to approve of the president because we will never know what the outcome would have been if that person wasn't a Liberal.

### Exercise 12

How does the motto "No causal inference without manipulation." apply in this problem?

```{r wisdom-12}
question_text(NULL,
	message = "Since the data is only a survey, without any manipulation, we cannot make any causal inferences.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The motto does not apply because this is a predictive, not causal, model.

### Exercise 13

Describe in words the Preceptor Table for this problem.

```{r wisdom-13}
question_text(NULL,
	message = "The Preceptor Table has 5 columns. There is a column for the ID, and one for the outcome. There three covariates: ideology, faminc, and education. Each row represents one individual.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The Preceptor Table for this problem looks something like this:

```{r}
#| echo: false
tibble(ID = c("1", "2", "...", "10", "11", "...", "N"),
       approval_ch = c("Neither Approve Nor Disapprove", "Disapprove / Somewhat Disapprove", "...", "Strongly Approve", "Never Heard / Not Sure", "...", "Neither Approve Nor Disapprove"),
       ideology = c("Moderate", "Very Liberal", "...", "Moderate", "Not Sure", "...", "Conservative"),
       faminc = c("120k - 150k", "50k - 60k", "...", "80k - 100k", "50k - 60k", "...", "60k - 70k"),
       education = c("High School Graduate", "4-Year", "...", "4-Year", "4-Year", "...", "Post-Grad")) |>
  
  gt() |>
  tab_header(title = "Preceptor Table") |> 
  cols_label(ID = md("ID"),
             approval_ch = md("Approval of the President"),
             ideology = md("Political Ideology"),
             faminc = md("Family Income"),
             education = md("Education")) |>
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(ID))) |>
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"), 
            locations = cells_column_labels(columns = c(ID))) |>
  cols_align(align = "center", columns = everything()) |>
  cols_align(align = "left", columns = c(ID)) |>
  fmt_markdown(columns = everything()) |>
  tab_spanner(label = "Covariates", columns = c(ideology, faminc, education)) |>
  tab_spanner(label = "Outcomes", columns = c(approval_ch))
```

### Exercise 14

In `analysis.qmd`, delete everything past the YAML heading and load the **tidyverse** and the **primer.data** packages in a new code chunk. Label it the set up by adding `#| label: setup`. Render the file.

Notice that the file does not look good because it is has code that is showing and it also has messages. To take care of this, add `#| message: false` to remove all the messages in the setup chunk. Also add the following to the YAML header to remove all echo from the whole file:

```         
execute: 
  echo: false
```

In the Console, run:

```         
show_file("analysis.qmd", start = -5)
```

CP/CR.

```{r wisdom-14}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

Render again. Everything looks nice because we have added code to make the file look better and more professional.

### Exercise 15

Write one sentence describing the data you have to answer your question.

```{r wisdom-15}
question_text(NULL,
	message = "The CCES is one of the largest political surveys in the United States. The data has how much people approve of the president as well as other useful variables such as ideology.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Insert comments about the data. This continues to be the primary type of knowledge drop. These comments can also be sophisticated, especially in the way that they connect the data to the Preceptor Table and to the population. -->

<!-- XX: Load any other packages that are needed, one package per question. (But make sure that they are also included in the setup chunk.) primer.data, for example, is often needed. But save brms and tidybayes for the Courage section. -->

<!-- XX: It is now time for the third set of QMD edits. Add a new code chunk, the setup chunk, to the QMD. Copy/paste all the library commands to it. Render. Note all the ugliness. Add #| message: false. Add execute: echo: false to the YAML header. Add #| label: setup. Render again. Everything looks nice. Again, these could be several questions in the earlier tutorials or just one long question later. Ends with show_file("analysis.qmd", start = -5). This will be the most common ending question in QMD-editing exercises to come. -->

<!-- XX: Add code questions about EDA with your data. In particular, add at least one question about the dependent variable in the model along with one or more questions about covariates. If there is a treatment variable, you must include a question about it. -->

<!-- Variable questions come in two types. First there are questions which require the student to run, say, summary() on the variable. Then, knowledge about the variable can be dropped. Second, there are questions which ask for a one sentence summary about the variable, something which could be used in our summary of the project. For example: "Civility is measured on a 1 through 7 scale with higher values corresponding to greater civility." -->

<!-- XX: If necessary, provide code exercises which, line-by-line, create the pipeline which creates the cleaned data that will be used in modeling. For many tutorials, this is unnecessary since we can just use the raw tibble that is available in whatever package. But we sometimes need some code like

nes |> 
  filter(year == 1992) |> 
  drop_na()

We have three code exercises, each adding one line to the pipeline, explaining what we are doing and why. It is nice that, for each exercise, something is spat out.
-->

<!-- XX: If such a pipeline was built, there is one QMD question which requires that you add a new code chunk to the QMD, copy/paste the pipeline and assign the result to some object like `model_data` or whatever:

nes_92 <- nes |> 
  filter(year == 1992) |> 
  drop_na()

`Command/ctrl + Shift + K` follows, perhaps with a show_file("analysis.qmd", start = -5)
-->

<!-- XX: For the validity questions, specifics matter. There is always a reason why the outcome column in the data is not the same as the outcome columns in the Preceptor Table, even in the case of simple sampling. For example, consider a historical question connecting sex with presidential vote. Our data is a subset of our Preceptor Table. We have information on a few thousand voters and want to draw inferences about millions of voters. But, even in this case, the outcome columns are different. The data is who people told a survey they voted for. The Preceptor Table is who people actually did vote for. Those are not the same things. If they, in your view, are different enough than validity is violated. -->

### Exercise 16

In your own words, define "validity" as we use the term.

```{r wisdom-16}
question_text(NULL,
	message = "Validity is the consistency, or lack thereof, in the columns of the data set and the corresponding columns in the Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX -->

### Exercise 17

Provide one reason why the assumption of validity might not hold for the outcome variable: `approval_ch`.

```{r wisdom-17}
question_text(NULL,
	message = "The data comes from a survey so there is a chance that people will not answer truthfully. This might lead our data to not be very accurate.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

We can lessen this by reminding the participants that their identity and their response will be kept private. This might make people feel more comfortable and answer more honestly.

### Exercise 18

<!-- XX: Pick the most important covariate or at least one that you know/suspect will be used in the model. This is similar to the previous question, but we want to ensure that students understand that validity is about comparing the columns in the data set with the columns in the Preceptor Table. -->

Provide one reason why the assumption of validity might not hold for the covariate: `ideology`.

```{r wisdom-18}
question_text(NULL,
	message = "It is a survey so people could lie about their ideology, or they might misidentify themselves if they do not know the difference between the ideologies.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The amount of people that lie is insignificant so there is no threat to the assumption of validity.

### Exercise 19

<!-- XX: In creating your own answer to questions like this, check with the chapter. One might already be provided! If not, it is often useful to revisit the relevant section of the Key Concepts chapter in the Primer. -->

<!-- Example: *Using data from a 2012 survey of Boston-area commuters, we seek to understand the relationship between income and political ideology in Chicago and similar cities in 2020. In particular, what percentage of individuals who make more than $100,000 per year are liberal?* -->

<!-- It is very difficult to craft a question which causes students to give a sentence that is good. Do your best. -->

Summarize the state of your work so far in one sentence. Make reference to the data you have and to the specific question you are trying to answer. 


```{r wisdom-19}
question_text(NULL,
	message = "Using the CCES, which is one of the largest political surveys in the United States, we seek to make a predictive model which could help us see a relationship between approval of the president and an individual's political ideology, family income, and education.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Edit you answer as you see fit, but do not copy/paste our answer exactly. Add this summary to `analysis.qmd`, `Command/Ctrl + Shift + K`, and then commit/push.

<!-- XX: As always, we like to do something in the tutorial before we do it in the QMD. But, in this case, we can just include the directions in the knowledge drop for the last question. -->

## Justice
### 

<!-- XX: Choose one. -->

*Justice is truth in action.* - Benjamin Disraeli
*The arc of the moral universe is long, but it bends toward justice.* - Theodore Parker
*Justice delayed is justice denied.* - William E. Gladstone
*It is in justice that the ordering of society is centered.* - Aristotle
*Charity is no substitute for justice withheld.* - Saint Augustine

### Exercise 1

In your own words, name the four key components of Justice for working on a data science problem.

```{r justice-1}
question_text(NULL,
	message = "Justice concerns four topics: the Population Table, stability, representativeness, and unconfoundedness.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: All of Justice is about concerns that you have, reasons why the model you create might not work as well as you hope. Drop knowledge/discussion as you see fit, but the central theme is *worries*. Connect some of the specific data discussion from Wisdom to these assumptions. -->

### Exercise 2

In your own words, define a Population Table.

```{r justice-2}
question_text(NULL,
	message = "The Population Table includes a row for each unit/time combination in the underlying population from which both the Preceptor Table and the data are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 3

In your own words, define the assumption of "stability" when employed in the context of data science.

```{r justice-3}
question_text(NULL,
	message = "Stability means that the relationship between the columns in the Population Table is the same for three categories of rows: the data, the Preceptor Table, and the larger population from which both are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: You can keep just one of these two, if you like. Or delete both and add your own knowledge drop. -->

<!-- Stability is all about *time*. Is the relationship among the columns in the Population Table stable over time? In particular, is the relationship --- which is another way of saying "mathematical formula" --- at the time the data was gathered the same as the relationship at the (generally later) time references by the Preceptor Table. -->

<!-- *The longer the time period covered by the Preceptor Table (and the data), the more suspect the assumption of stability becomes.*  -->

### Exercise 4

Provide one reason why the assumption of stability might not be true in this case.

```{r justice-4}
question_text(NULL,
	message = "XX. Again, students read these 'official' answers as closely as anything else you will write. Make your example precise and excellent.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 5

We use our data to make inferences about the overall population. We use information about the population to make inferences about the Preceptor Table: `Data -> Population -> Preceptor Table`. In your own words, define the assumption of "representativeness" when employed in the context of data science.

```{r justice-5}
question_text(NULL,
	message = "Representativeness, or the lack thereof, concerns two relationships among the rows in the Population Table. The first is between the data and the other rows. The second is between the other rows and the Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Keep one of these. -->

<!-- Ideally, we would like both the Preceptor Table *and* our data to be random samples from the population. Sadly, this is almost never the case. -->

<!-- Stability looks across time periods. Representativeness looks within time periods. -->



### Exercise 6

We do not use the data, directly, to estimate missing values in the Preceptor Table. Instead, we use the data to learn about the overall population. Provide one reason, involving the relationship between the data and the population, for why the assumption of representativeness might not be true in this case.

```{r justice-6}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 7

We use information about the population to make inferences about the Preceptor Table. Provide one reason, involving the relationship between the population and the Preceptor Table, for why the assumption of representativeness might not be true in this case.

```{r justice-7}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 8

In your own words, define the assumption of "unconfoundedness" when employed in the context of data science.

```{r justice-8}
question_text(NULL,
	message = "Unconfoundedness means that the treatment assignment is independent of the potential outcomes, when we condition on pre-treatment covariates.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Keep one. -->

<!-- This assumption is only relevant for causal models. We describe a model as "confounded" if this is not true.  -->

<!-- The easiest way to ensure unconfoundedness is to assign treatment randomly. -->

### Exercise 9

<!-- XX: Delete this question for non-causal models. -->

Provide one reason why the assumption of unconfoundedness might not be true (or relevant) in this case.

```{r justice-9}
question_text(NULL,
	message = "XX. There is nothing harder for students than coming up with examples of possible confounds. So, your example should be a good one, should specify precisely how treatment assignment is correlated with the potential outcomes.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Most of our simple examples use random assignment. So, if fact, confoundedness is not a concern. But this knowledge drop, and perhaps the couple before, should address this topic, by pondering what we would worry about if treatment assignment had not been random.  -->

### Exercise 10

Summarize the state of your work so far in two or three sentences. Make reference to the data you have and to the question you are trying to answer. Feel free to copy from your answer at the end of the Wisdom Section. Mention one specific problem which casts doubt on your approach. 


```{r justice-10}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Edit the summary paragraph in `analysis.qmd` as you see fit, but do not copy/paste our answer exactly. `Command/Ctrl + Shift + K`, and then commit/push.


## Courage
### 

<!-- XX: Choose one. -->

*Courage is found in unlikely places.* - J.R.R. Tolkien
*Courage is being scared to death, but saddling up anyway.* - John Wayne
*Courage is going from failure to failure without losing enthusiasm.* - Winston Churchill
*Courage is the commitment to begin without any guarantee of success.* - Johann Wolfgang von Goethe


<!-- Questions about models, tests, and the DGM. -->


### Exercise 1

In your own words, describe the components of the virtue of Courage for analyzing data.

```{r courage-1}
question_text(NULL,
	message = "Courage begins with the exploration and testing of different models. It concludes with the creation of a Data Generating Mechanism.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

Load the **brms** package.

```{r courage-2, exercise = TRUE}

```

```{r courage-2-hint-1, eval = FALSE}
library(...)
```

```{r courage-2-test, include = FALSE}
library(brms)
```

### 

<!-- XX: The Courage section of each chapter is the most complex because modeling is hard. Use opportunities for knowledge drops, like this one, judiciously. -->

### Exercise 3

Load the **tidybayes** package.

```{r courage-3, exercise = TRUE}

```

```{r courage-3-hint-1, eval = FALSE}
library(...)
```

```{r courage-3-test, include = FALSE}
library(tidybayes)
```

### 

### Exercise 4

Add `library(brms)` and `library(tidybayes)` to `analysis.qmd`. `Command/Ctrl + Shift + K`. At the Console, run:

```
tutorial.helpers::show_file("analysis.qmd", pattern = "brms|tidybayes")
```

CP/CR.

```{r courage-4}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

<!-- XX: For a knowledge drop, there is nothing wrong with discussion regular expressions, which is the magic which allows us to just pull out the two lines in the QMD which we want. But better would just be more Courage knowledge drops. -->


### Exercise 5

Create a model using `brm()` from the **brms** package. Your arguments should be XX. 

<!-- Don't forget to create this model yourself in the setup chunk. Do this once, save the object, comment out that code and then just read_rds to create the object for his tutorial. -->


```{r courage-5, exercise = TRUE}

```

```{r courage-5-hint-1, eval = FALSE}

```

<!-- XX: Note how there is no test case. If there were one, then a student would fit the model each time she hit "Run Tutorial." That takes too much time. -->

### 

### Exercise 6

Behind the scenes, we have assigned the result of the `brm()` call to an object named `fit_president_approval`. Type `fit_president_approval` and hit "Run Code." This generates the same results as using `print(fit_president_approval)`.


```{r courage-6, exercise = TRUE}

```

```{r courage-6-hint-1, eval = FALSE}
fit_president_approval
```

```{r courage-6-test, include = FALSE}
# fit_president_approval
```

### 

<!-- XX Say some general words about the object. Note that we are about to go through the top 4 rows. -->


### Exercise 7

Run `family()` on `fit_president_approval`. `family()` provides information about the "family" of the error term and the link between it and the dependent variable. 

```{r courage-7, exercise = TRUE}

```

```{r courage-7-hint-1, eval = FALSE}
family(...)
```

```{r courage-7-test, include = FALSE}
# family(fit_president_approval)
```

### 

<!-- XX: This is a great location for explanations which get much more detailed in later chapters. That is, we want students to have a more sophisticated understanding of probability distributions, and there use in modeling, as we move through the Primer.

But, at a minimum, you would comment about how the family that is shown --- which is either gaussian, bernoulli or categorical --- is determined by the family argument which you passed in to the brm() call, and that you determined that by looking at the distribution of the output variable. Continuous means gaussian, 2 possible values means bernoullu, and 2+ possible values means categorical.

-->

In this case, XX . . .

### Exercise 8

Run `formula()` on `fit_president_approval`. `formula()` returns the statistical equation which relates the dependent variable to the independent variable(s). 

```{r courage-8, exercise = TRUE}

```

```{r courage-8-hint-1, eval = FALSE}
formula(...)
```

```{r courage-8-test, include = FALSE}
# formula(fit_president_approval)
```

### 

In this case, XX . . .

### Exercise 9

Run `nobs()` on `fit_president_approval`. The `nobs()` function returns the **n**umber of **obs**ervations.

```{r courage-9, exercise = TRUE}

```

```{r courage-9-hint-1, eval = FALSE}
nobs(...)
```

```{r courage-9-test, include = FALSE}
# nobs(fit_president_approval)
```

### 

In this case, XX

### Exercise 10

Write the mathematical formula for your model, using $\LaTeX$ math notation.

```{r courage-10}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Add the formula to `analysis.qmd`. `Command/Ctrl + Shift + K`. Ensure that the formula is looks correct. 

### Exercise 11

Create a new code chunk in `analysis.qmd`. Add two code chunk options: `label: model` and `cache: true`. Copy/paste the code from above for estimating the model using `brm()` into the code chunk, assigning the result to `fit_president_approval`. 

`Command/Ctrl + Shift + K`. It may take some time to render `analysis.qmd`, depending on how complex your model is. But, by including `cache: true` you cause Quarto to cache the results of the chunk. The next time you render `analysis.qmd`, as long as you have not changed the code, Quarto will just load up the saved fitted object.

To confirm, `Command/Ctrl + Shift + K` again. It should be quick.

At the Console, run:

```
tutorial.helpers::show_file("analysis.qmd", start = -8)
```

CP/CR.

```{r courage-11}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

### Exercise 12

Run `posterior_interval()` on `fit_president_approval`. The `posterior_interval()` function returns 95% intervals for all the parameters in our model.

```{r courage-12, exercise = TRUE}

```

```{r courage-12-hint-1, eval = FALSE}
posterior_interval(...)
```

```{r courage-12-test, include = FALSE}
# posterior_interval(fit_president_approval)
```

### 

In this case, XX . . .


### Exercise 13

Run `fixef()` on `fit_president_approval`. The `fixef()` returns information about the **fix**ed **ef**fects in the model.

```{r courage-13, exercise = TRUE}

```

```{r courage-13-hint-1, eval = FALSE}
fixef(...)
```

```{r courage-13-test, include = FALSE}
# fixef(fit_president_approval)
```

### 

In this case, XX . . .

<!-- XX: Add at least three questions which require the student to interpret the meanings of a parameter estimate and/or its associated confidence interval. This is something that students are very bad at! And so we need to give them practice, both by asking them to do it and by providing excellent answers. These questions also feature good opportunities to knowledge drop about the meaning of intervals (confidence verus uncertainty) and about Frequentist versus Bayesian interpretations. See -->

<!-- Let's me give a couple of questions/answers to serve as examples, all based on this display. This is good for linear (meaning the Gaussian family) models. For other models, see the comments below. -->

<!-- fit_obj <- brm(formula = att_end ~ sex + treatment + age, data = trains) -->

<!-- > round(fixef(fit_obj), 2) -->
<!--                  Estimate Est.Error  Q2.5 Q97.5 -->
<!-- Intercept           10.99      0.95  9.17 12.83 -->
<!-- sexMale             -0.83      0.54 -1.88  0.22 -->
<!-- treatmentControl    -1.42      0.54 -2.45 -0.32 -->
<!-- age                 -0.01      0.02 -0.06  0.03 -->

<!-- Q: Write a sentence interpreting the -0.34 estimate for sexMale. -->

<!-- A: When comparing men with women, men have a 0.83 lower value for att_end, meaning that they are more liberal about immigration, relative to women, conditional on the other variables in the model. -->

<!-- Comment_1: Note how, whenever we consider non-treatment variables, we must never use terms like "cause," "impact" and so on. We can't make any statement which implies the existence of more than one potential outcome based on changes in non-treatment variables. We can't make any claims about within row effects. Instead, we can only compare across rows. Always use the phrase "when comparing X and Y" or something very similar. -->

<!-- Comment_2: The phrase "conditional on the other variables in the model" is important. It could be shorted as "conditional on the model." This phrase acknowledges that there are many, many possible models, just considering all the different combintions of indepdendent variables we might include. Each one would produce a different coefficient for sexmale. None of these is the *true* cofficient. Any claim we make about  -0.83, or any specific number, is always conditional on the fact that we assume that this model is true, that these covariates, and no others, belong in the regression. Does that mean that we always use the phrase? No. We leave it out all the time. But it is always understood to be there but knowledge readers. Still, this is probably a point worth making in various knowledge drops. -->


<!-- Q: Write a sentence interpreting the confidence interval for sexMale. -->

<!-- A: We do not know the true value for the coefficient for sexMale, but we can by 95% confident that it lies somewhere between -1.88  and 0.22.  -->

<!-- Comment: Because we are Bayesians, we believe that there is a true value and that the confidence or uncertainty interval includes it at the stated level. These questions provide an occasion in the knowledge drop to compare/contrast the Frequenist interpretation. See: https://ppbds.github.io/primer/cardinal-virtues.html#confidencecredibleuncertainty-intervals -->

<!-- Q: Write a sentence interpreting the -1.42  estimate for treatmentControl. -->

<!-- A: The causal effect of receiving the treatment of hearing Spanish-speakers on the train platform, relative to the control, is to have a 1.42  higher value for att_end, meaning that the treatment, relative to the control, makes one more conservative about immigration. (Note that you need to keep track of signs and of which 0/1 variable is being used.) -->

<!-- Comment: The interpretation of a treatment variable is very different than the interpretation of a standard covariate. Whenever your model includes a treatment variable, you must always have a question about it and about the associated confidence interval. -->

<!-- Q: Write one sentence interpreting the -2.45 to -0.32 interval for the treatmentControl coefficient. -->

<!-- A: Our best estimate for the causal effect is -1.42, meaning that being treated makes someone 1.42 units more conservative about immigration. Yet, the true value could be lower or higher. We are 95% certain that the true effect is somewhere between -2.45 to -0.32.  -->

<!-- Comment: It is OK if our answers are slightly longer than what we might expect from students, as long as those answers are *tight*, meaning that no word is wasted. In this case, the first two sentences are an attempt to ensure that the student understands what is going on. The last sentence is what we might expect students to write.  -->

<!-- Q: Write a sentence interpreting the -0.1 estimate for age.  -->

<!-- A: If we compare one group of people ten years older than another, the older group will, on average, have an attitude toward immigration 1 unit lower, i.e., less conservative. -->

<!-- Comment: Numeric variables are harder than binary variables because there are no longer just two well-defined groups to compare with each other. We must make those two groups ourselves. Fortunately, as long as there are no interaction terms, we can just pick two groups with any values for the variable. The most common two groups differ by one unit of the variable. But it is quite common to use groups which differ by more/less if doing so seems sensible and/or if it makes the math easier. In this case, two groups which differ by 10 years makes sense for both reasons. -->

<!-- Further comment: With a linear model, all these interpretations are fairly straightforward. With any other type of model, the math is too difficult to do in your head. You can't just look at a coefficient of 5 and know what it means in magnitude. But you can tell the direction, that a positive 5 means that -->

### Exercise 14

Run `pp_check()` on `fit_president_approval`. The `pp_check()` runs a **p**osterior **p**redictive check.

```{r courage-14, exercise = TRUE}

```

```{r courage-14-hint-1, eval = FALSE}
pp_check(...)
```

```{r courage-14-test, include = FALSE}
# pp_check(fit_president_approval)
```

### 

In this case, XX

<!-- If the fake data had looked very different from the real data, we have had a problem. But, for the most part, we conclude that, although not perfect, pp_check() shows that the fake outcomes generated by our model are like the actual outcome data. -->


### Exercise 15

Use `library()` to load the [**gtsummary**](https://www.danieldsjoberg.com/gtsummary) package.

```{r courage-15, exercise = TRUE}

```

```{r courage-15-hint-1, eval = FALSE}
library(gtsummary)
```

```{r courage-15-test, include = FALSE}
library(gtsummary)
```

### 

<!-- Drop some knowledge about gtsummary. Or say something more about your DGM. -->

### Exercise 16

<!-- XX: This can be just one question or several, especially if you want to teach some more gtsummary or gt tricks. Make any adjustments to this question, like `intercept = TRUE`, so that this question works. -->

Pipe `fit_president_approval` to `tbl_regression()`.


```{r courage-16, exercise = TRUE}

```

```{r courage-16-hint-1, eval = FALSE}
fit_president_approval |> 
  tbl_...()
```

```{r courage-16-test, include = FALSE}
# fit_president_approval |> 
#   tbl_regression()
```

### 

<!-- XX: Drop some knowledge about what you have learned by looking at the resulting table. Of course, you could have learned the same thing when you first took a look at fit_president_approval. But the table makes it easier to see the relationships between the variables and the outcome. With luck, students will take the hint when they answer the next question. -->

<!-- https://www.danieldsjoberg.com/gtsummary/articles/tbl_regression.html -->


### Exercise 17

Write a few sentence which summarize your work so far. The first few sentences are the same as what you had at the end of the Justice Section. Add one sentence which describes the modelling approach which you are using, specifying the functional form and the dependent variable. Add one sentence which describes the *direction* (not the magnitude) of the relationship between one of your independent variables and your dependent variable.

```{r courage-17}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 18

Update `analysis.qmd`. First, add `library(gtsummary)` to the `setup` code chunk,. Second, add the mathematical formula, in $\LaTeX$ and surrounded by double dollar signs, for your model. Third, add a new code chunk which creates the table of model parameters. `Command/Ctrl + Shift + K` to ensure that everything works.

At the Console, run:

```
tutorial.helpers::show_file("analysis.qmd", start = -8)
```

CP/CR.

```{r courage-18}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

## Temperance
### 

<!-- XX: Choose one. -->

*Temperance is a tree which as for its root very little contentment, and for its fruit calm and peace.* - Buddha
*Temperance is the greatest of all virtues. It subdues every passion and emotion, and almost creates a Heaven upon Earth.* - Joseph Smith Jr.
*Temperance is a bridle of gold; he, who uses it rightly, is more like a god than a man.* - Robert Burton
*Temperance is the firm and moderate dominion of reason over passion and other unrighteous impulses of the mind.* - Marcus Tullius Cicero
*Temperance to be a virtue must be free, and not forced.* - Philip Massinger
*Temperance is simply a disposition of the mind which binds the passion.* - Thomas Aquinas


### Exercise 1

In your own words, describe the use of Temperance in data science.

```{r temperance-1}
question_text(NULL,
	message = "Temperance uses the Data Generating Mechanism to answer the question with which we began. Humility reminds us that this answer is always a lie.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

What is the general topic we are investigating? What is the specific question we are trying to answer? 

```{r temperance-2}
question_text(NULL,
	message = "XX: Should be exactly how you started the Wisdom section.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Data science projects almost always begin with a broad topic of interest. Yet, in order to make progress, we need to drill down to a specific question. This leads to the creation of a data generating mechanism, which can now be used to answer lots of questions, thus allowing us to explore the original topic broadly.

### Exercise 3

To answer our question, we need to create a `newdata` object. Which variables (e.g., which columns) do we need to include in this object?

```{r temperance-3}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Must be all the right hand side variables in fit_president_approval. And note that the type must (maybe not always . . .) match, like if `treatment` is a factor in the original data used to create fit_president_approval then it must (?) be a factor in ndata. -->


### Exercise 4

<!-- XX: Sometimes useful to think about this question and the number of posterior questions together, or event to reverse them. -->

Which values do you want the variables in your `newdata` object to have? This is not easy! At the very least, one of the rows should have values which allow you to answer your original question. But, now that you have a model, there are many questions which you might want to answer, the better to get a fuller understanding.

```{r temperance-4}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Chapter 10 is a great example of this in its full complexity. We want to know how "different" units behave, where the very definition of "different" is that they do not have identical values for all the variables used in fit_president_approval. -->

<!-- For example, one row in ndata will generally represent the answer to the specific question we started with. But that is just the posterior for one sort of unit. There are lots of different units! Which others might we be interested in? We can generate posteriors for each of them, and then, in some cool graphic, display all those posteriors together. -->

<!-- Note that, previously, this document claimed that the number of rows in ndata corresponded to the number of posteriors you wanted to calculate. But that is not true! -->

### Exercise 5

Here is the R code which creates the `newdata` object: `tibble(whatever) code here`. Type it into the code exercise block and hit "Run Code."

<!-- Asking students to create this object --- even after you help them figure out the columns, rows and values --- is too hard, at least until they get more experiences. Your knowledge drop, for this question and the next, should give them advice on the broad topic of how they can create newdata objects themselves. -->

```{r temperance-5, exercise = TRUE}

```

```{r temperance-5-hint-1, eval = FALSE}

```

```{r temperance-5-test, include = FALSE}

```

### 

### Exercise 6

Behind the scenes, we have created the `ndata` object using this code. To confirm, type `ndata` and hit "Run Code."

<!-- Of course, you need to have added the code to create `ndata` in the setup chunk at the top of the file. -->

```{r temperance-6, exercise = TRUE}

```

```{r temperance-6-hint-1, eval = FALSE}

```

```{r temperance-6-test, include = FALSE}

```

### 

Note that, when you add Temperance-related code to your QMD, you will need to also add code which creates the `ndata` object.

### Exercise 7

Now that we have the `newdata` object, we can create a pipe which uses out fitted model to answer our question. Begin by typing `fit_president_approval` and clicking "Run Code."

```{r temperance-7, exercise = TRUE}

```

```{r temperance-7-hint-1, eval = FALSE}

```

```{r temperance-7-test, include = FALSE}

```

### 

<!-- XX: Again, the main point of knowledge drops is this area is to explain to students why the newdata object looks the way it does and what it will produce. A great way to teach is via example. That is, explaining that if we had another way with these values, then we would get this posterior. Or, explaining what would be produced if we used add_epred instead of add_predict, and vice verse. -->


### Exercise 8

Pipe `fit_president_approval` to [XX: either `add_epred_draws()` or `add_predicted_draws()`] with the argument `newdata = ndata`. 



```{r temperance-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-8-hint-1, eval = FALSE}

```

```{r temperance-8-test, include = FALSE}

```

### 

<!-- XX: How do students know whether to use add_epred_draws or add_predicted_draws? This is non-trivial. On some level, we just tell them with the above command. (We don't make them guess.) But we also address this issue explicitly in various knowledg drops, especially this one. -->

<!-- XX: Insert as many questions as necessary to build a nice-looking example of your final plot. In early chapters, this is simple since our questions are simple. They are just one posterior. In later chapters, they become more complex, with the inclusion of several posteriors, as well as manipulation of them to calculate causal effects and whatnot. See the voting postcard example. -->

### Exercise 9

Create a new code chunk in `analysis.qmd`. Label it with `label: plot`. Copy/paste the code which creates your graphic. Don't forget that, at the top of this chunk, you must include code which creates the `ndata` object.

`Command/Ctrl + Shift + K` to ensure that it all works as intended.

At the Console, run:

```
tutorial.helpers::show_file("analysis.qmd", start = -8)
```

CP/CR.

```{r temperance-9}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

### Exercise 10

Write a paragraph which summarizes the project in your own words. The first few sentences are the same as what you had at the end of the Courage section. But, since your question may have evolved, you should feel free to change those sentences. Add at least one sentence which describes at least one quantity of interest (QoI) --- presumably one that answers your question -- and which provides a measure of uncertainty about that QoI.

<!-- XX: Most of the time, there will be some measure of uncertainty associated with your QoI. But not always! The most common counter-example involves a question which asks about the odds or probability of something happening. We would answer such a question by simulating the event with `add_predicted_draws()`. We would then calculate the odds/probability of something happening by seeing how many of the 4,000 draws met the criteria for the event. Assume that was 40%. So, we think that there is a 40% chance that event A will happen. Yet there is no uncertainty associated with that estimate because it, itself, is an expression of uncertainty. (DK: Flesh this out further.) -->

```{r temperance-10}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Edit the summary paragraph in `analysis.qmd` as you see fit, but do not copy/paste our answer exactly. `Command/Ctrl + Shift + K`.


<!-- XX: Again, spend time to make your recommended paragraph perfect. Study the examples in https://ppbds.github.io/primer/cardinal-virtues.html closely. -->

### Exercise 11

Write a few sentences which explain why the estimates for the quantities of interest, and the uncertainty thereof, might be wrong. Suggest an alternative estimate and confidence interval, if you think either might be warranted.

```{r temperance-11}
question_text(NULL,
	message = "XX: This is another example in which the quality of your answer is important. You might or might not suggest an alternate estimate. I always adjust the estimate toward my own subjective sense of a longrun average and/or typical value and/or zero. But that is not necessary. However, you should always increase the confidence interval since the assumptions of your model are always false.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 12

Rearrange the material in `analysis.qmd` so that the order is graphic, paragraph, math and table. Doing so, of course, requires sensible judgment. For example, the code chunk which creates the fitted model must occur before the chunk which creates the graphic. `Command/Ctrl + Shift + K` to ensure that everything works.

At the Console, run:

```
tutorial.helpers::show_file("analysis.qmd")
```

CP/CR.

```{r temperance-12}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

Add `rsconnect` to the `.gitignore` file. You don't want your personal Rpubs details stored in the clear on Github. Commit/push everything.

### Exercise 13

Publish `analysis.qmd` to Rpubs. Choose a sensible slug. Copy/paste the url below.

```{r temperance-13}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

## Summary
### 

This tutorial covered [Chapter XX: XX](https://ppbds.github.io/primer/XX.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 



```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
