---
title: 'Sampling: Overview'
author: Ryan Southward, Mann Talati and David Kane
tutorial:
  id: sampling-overview
output:
  learnr::tutorial:
    progressive: yes
    'allow_skip:': yes
runtime: shiny_prerendered
description: 'Chapter 3 Tutorial: Sampling'
---

<!-- Need one more section which using the posterior to, for example, create the posterior of number red which will be drawn with a shovel of size 20. Use a posterior to create a new posterior. Turtles all the way down. Could also create the plot of the joint distribution. Try to teach again just what a joint distribution. -->

<!-- Maybe make the shovels_100 have 100 shovel sizes again? We cut that down to make it quicker, but maybe having 100 reps instead of a 1,000 was enough to solve our speed problem. Done -->


<!-- RS: Add graph of sampling distributions from shovels of size 25, 50, and 100 but using re factored code!! -->

<!-- RS: Add to 100 shovels graph to overlay theoretical standard deviation using equations. (Call this section standard deviation). -->

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(tidyverse)
library(gt)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 

# Key Data

set.seed(10)
urn <- tibble(color = c(rep("red", 400), rep("white", 600))) |>
  sample_frac() |> 
  mutate(bead_ID = 1:1000) 

virtual_samples <- tibble(trial_ID = 1:1000) |> 
  mutate(shovel = map(trial_ID, ~ sample_n(urn, size = 50))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) |> 
  mutate(numb_beads = map_int(shovel, ~ length(.$color))) |> 
  mutate(prop_red = numb_red / numb_beads)

shovels_100 <- expand_grid(trial_ID = 1:100, shovel_size = 1:100) |> 
  mutate(shovel = map(shovel_size, ~ slice_sample(urn, n = .))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) |> 
  mutate(prop_red = numb_red / shovel_size) |> 
  group_by(shovel_size) |> 
  summarize(st_dev_p_hat = sd(prop_red)) 

shovel_p <- shovels_100 |>
 ggplot(aes(x = shovel_size, y = st_dev_p_hat)) +
 geom_point() +
 labs(title = "Sampling Variation",
      subtitle = "Larger samples have less variation",
      x = "Shovel size",
      y = "Standard deviation of the proportion red")


```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

<!-- DK: Add test chunks everywhere. -->

<!-- Create the plots once and then use the plot object. -->

<!-- Add example Preceptor and Population tables. -->

## Introduction
### 

This tutorial covers [Chapter 3](https://ppbds.github.io/primer/sampling.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/). 


<!-- This tutorial will review topics including One Parameter, shovel method, virtual sampling, standard error, Cardinal Virtues (wisdom, justice, courage, and temperance), and a case study. -->

<!-- DK: Section about real sampling? -->

## Virtual Sampling
### 

In this section, we mimic physical sampling with virtual sampling, using a computer. In a real sampling activity, we would perform a tactile sampling activity. In this we use a physical urn of beads and a physical shovel which is done by hand so that we could develop our intuition about the ideas behind sampling. 

### 

Let's create the following plot that shows sampling variation for 1000 samples from an urn that contains red and white beads.

```{r}
virtual_samples |> 
  ggplot(aes(x = prop_red)) +
    geom_histogram(binwidth = 0.01, 
                   boundary = 0.4, 
                   color = "white") +
    labs(x = expression(hat(p)), 
         y = "Count",
         title = "Distribution of 1,000 proportions red") 
```

### Exercise 1

Create a `urn` variable on the second line that is set to a `tibble()`. Within the `tibble()` set `color` to the combination of `rep("red", 400)` and `rep("white", 600)`.

```{r virtual-sampling-1, exercise = TRUE}
set.seed(10)

```

```{r virtual-sampling-1-hint-1, eval = FALSE}
set.seed(10)
urn <- tibble(... = c(rep("...", ...), 
                        rep("...", ...)))
```

### 

`set.seed()` ensures that the beads in our virtual urn are always in the same order. This ensures that the figures in the book match their written descriptions. We want 40% of the beads to be red. The `rep()` function will repeat the first argument a number of times specified by the second argument. We then combine our 400 red beads and 600 white beads using `c()`.

### Exercise 2

Within the `urn` variable start a pipe and set it to `sample_frac()`.

```{r virtual-sampling-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-2-hint-1, eval = FALSE}
urn <- ... |>
          sample_frac()
```

### 

`sample_frac()` keeps all the rows in the tibble but rearranges their order. We don't need to do this. A virtual urn does not care about the order of the beads. But we find it aesthetically pleasing to mix them up.

### Exercise 3

Finish the pipe with `mutate()` and set `bead_ID` to 1 through 1000.

```{r virtual-sampling-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-3-hint-1, eval = FALSE}
urn <- ... |>
          mutate(... = 1:1000)
```

### 

The first variable `bead_ID` is used as an identification variable. None of the beads in the actual urn are marked with numbers. The second variable `color` indicates whether a particular virtual bead is red or white.

### Exercise 4

To simulate the process of real-world sampling, let’s take a sample of 50 beads from our virtual urn. To do so, create a `tibble()` that has one variable `trial_ID` that takes on the values 1 to 1000.

```{r virtual-sampling-4, exercise = TRUE}

```

```{r virtual-sampling-4-hint-1, eval = FALSE}
tibble(trial_ID = ...)
```

```{r virtual-sampling-4-hint-2, eval = FALSE}
Use the : operator to create a range of integers.
```

### Exercise 5

Now pipe your results to the function `mutate()` to create the variable `shovel`, which is set to the function `map()`. The first argument to `map()` should be `trial_ID`. The second argument should use `slice_sample()`. Within `slice_sample()`, the first argument should be `urn` (the data we want to sample from), and then set `n` equal to our sample size (we want a sample size of 50). 

```{r virtual-sampling-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-5-hint-1, eval = FALSE}
... |> 
  mutate(shovel = map(..., ~ ...))
```

```{r virtual-sampling-5-hint-2, eval = FALSE}
... |> 
  mutate(shovel = map(..., ~slice_sample(urn, n = ...)))
```

### 

The advantage of modern technology is that we can use virtual simulation as many times as we choose, so we have no restrictions on resources. No longer are the days where we have to recruit our friends to tirelessly sample from the physical urn.

### Exercise 6

Continue your pipe with `mutate()` to create the variable `numb_red`. Set `numb_red` to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `sum()` of where `.$color` is equal to red.

```{r virtual-sampling-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-6-hint-1, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~...))
```

```{r virtual-sampling-6-hint-2, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~ sum(.$color == "red")))
```

### 

R evaluates if `color == red`, and treats `TRUE` values like the number `1` and `FALSE` values like the number `0`. So summing the number of `TRUE`s and `FALSE`s is equivalent to summing `1`’s and `0`’s. In the end, this operation counts the number of beads where `color` equals “red”.

### Exercise 7

Use `mutate()` one last time to create the variable `prop_red`. Set `prop_red` to `numb_red` divided by the sample size (in this exercise we are using a set sample size of 50).

```{r virtual-sampling-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-7-hint-1, eval = FALSE}
... |> 
   mutate(prop_red = ... / ...)
```

### 

`prop_red` estimate's our proportion of red beads in the urn.

### Exercise 8

Assign your code from above to an object named `virtual_samples`.

```{r virtual-sampling-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-8-hint-1, eval = FALSE}
Use the assignment operator <-  to do so.
```

### Exercise 9

Now start a pipe with `virtual_samples`. Use `ggplot()` to map `prop_red` to the x-axis.

```{r virtual-sampling-9, exercise = TRUE}

```

```{r virtual-sampling-9-hint-1, eval = FALSE}
virtual_samples |> 
  ggplot(aes(...))
```

### Exercise 10

Add the layer `geom_histogram()` to create a histogram of our data.

```{r virtual-sampling-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-10-hint-1, eval = FALSE}
... +
  geom_histogram()
```

### Exercise 11

Within `geom_histrogram()` set `binwidth` to .01, `boundary` to .4, and `color` to "white".

```{r virtual-sampling-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual-sampling-11-hint-1, eval = FALSE}
... +
  geom_histrogram(binwidth = ..., boundary = ..., color = ...)
```

### 

Recall that `p` is equal to the proportion of beads which are red in each sample.

### Exercise 12

To finish, use `labs()` to give your graph the appropriate title and axis labels. See **hint** for guidance to create the symbol $\hat{p}$.

```{r virtual-sampling-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like. 

```{r}
virtual_samples |> 
  ggplot(aes(x = prop_red)) +
    geom_histogram(binwidth = 0.01, 
                   boundary = 0.4, 
                   color = "white") +
    labs(x = expression(hat(p)), 
         y = "Count",
         title = "Distribution of 1,000 proportions red") 
```

```{r virtual-sampling-12-hint-1, eval = FALSE}
Within labs(), set x to expression(hat(p))
```

### 

This visualization allows us to see how our results differed between our tactile and virtual urn results. As we can see, there is some variation between our results. This is not a cause for concern, as there is always expected sampling variation between results.

<!-- RS: Later on add exercises to build the graph that compares shovel size 25, 50, and 100. In a few days I will edit the primer to remove the bindrows() nonsense and create the graph using expand_grid(). -->

## Standard Error of different shovel sizes
### 

<!-- MT: add questions about the definitions/important concepts of standard error -->

Standard errors (SE) quantify the effect of sampling variation on our estimates. In other words, they quantify how much we can expect the calculated proportions of a shovel’s beads that are red to vary from one sample to another sample to another sample, and so on. As a general rule, as sample size increases, the standard error decreases.

### 

Let's create the following plot that displays different standard deviations of red bead proportions for 100 different shovel sizes.

```{r}
shovel_p
```

### Exercise 1

First, let's use `expand_grid()` to create the foundation of our tibble. Our first column in `expand_grid()` should be called `trial_ID`, and it should be the range of integers between 1 and 1,000. The second column should be called `shovel_size`, and should be the range of integers between 1 and 100.

```{r standard-error-of-different-sh-1, exercise = TRUE}

```

```{r standard-error-of-different-sh-1-hint-1, eval = FALSE}
expand_grid(trial_ID = ..., shovel_size = ...)
```

```{r standard-error-of-different-sh-1-hint-2, eval = FALSE}
Use the : operator to create a range of integers. 
```

### 

### Exercise 2

Continue the pipe with `mutate()`, creating a new column called `shovel`. Set `shovel` equal to a `map()` function, passing in `shovel_size` as the first argument, and the `slice_sample()` function as the second argument. Within `slice_sample()`, the first argument should be `urn` (the data we want to sample from), and then set `n` equal to `.` (we want to pass in the `shovel_size` using `map()`).

```{r standard-error-of-different-sh-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-2-hint-1, eval = FALSE}
... |>
  mutate(shovel = map(..., ~ ... ))
```

```{r standard-error-of-different-sh-2-hint-2, eval = FALSE}
... |>
  mutate(shovel = map(... , ~ slice_sample(..., n = ...)))
```

### Exercise 3

Continue your pipe with `mutate()` to create the variable `numb_red`, which will tells us the number of red beads present. Set `numb_red` to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `sum()` of where the column `color` of `shovel` is equal to red.

```{r standard-error-of-different-sh-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-3-hint-1, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~ ...))
```

```{r standard-error-of-different-sh-3-hint-2, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~ sum(.$color == "red")))
```

### Exercise 4

Continue your pipe from above, using `mutate()` to create one final column called `prop_red` which represents the proportion of red beads in a sample. Set `prop_red` to `numb_red` divided by the `shovel_size` column. 

```{r standard-error-of-different-sh-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-4-hint-1, eval = FALSE}
... |>
  mutate(prop_red = ... / ...)
```

### Exercise 5

Great. Continue your pipe and use the `group_by()` function to group our tibble by `shovel_size`. 

```{r standard-error-of-different-sh-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-5-hint-1, eval = FALSE}
... |>
  group_by(...)
```

### Exercise 6

Continue your pipe one last time, and use `summarize()` to create a new column named `st_dev_p_hat` which is equal to the standard deviation of `prop_red`. (`sd()` calculates standard deviation).
 

```{r standard-error-of-different-sh-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-6-hint-1, eval = FALSE}
... |> 
  summarize(st_dev_p_hat = sd(...))
```

### Exercise 7

Assign your code from above to an object named `shovels_100`.

```{r standard-error-of-different-sh-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r standard-error-of-different-sh-7-hint-1, eval = FALSE}
Use the assignment operator <-  to do so.
```

### Exercise 8

Start a new pipe from `shovels_100`. Use `ggplot()`to map `shovel_size` to the x-axis and `st_dev_p_hat` to the y axis. Also, add the layer `geom_point()` to create a scatterplot.

```{r standard-error-of-different-sh-8, exercise = TRUE}

```

```{r standard-error-of-different-sh-8-hint-1, eval = FALSE}
shovels_100 |> 
  ggplot(aes(x = ..., y = ...)) + 
  geom_point()
```

### Exercise 9

Now use `labs()` to label the x-axis "Shovel size" and the y-axis 
"Standard deviation of the proportion red". You should also provide a title and subtitle.

```{r standard-error-of-different-sh-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like.

```{r}
shovel_p
```

```{r standard-error-of-different-sh-9-hint-1, eval = FALSE}
... +
   labs(title = "Sampling Variation",
      subtitle = "Larger samples have less variation",
      x = "Shovel size",
      y = "Standard deviation of the proportion red")
```

### Exercise 10

In two sentences explain the population of our scenario in terms of standard error.

*Hint*: Check out [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) for more knowledge about the topics discussed.

```{r standard-error-of-different-sh-10}
question_text(NULL,
	message = "The population’s size is upper-case Ν. In our sampling activities, the population is the collection of 1000 identically sized red and white beads in the urn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

A population is the set of relevant units. Other examples are all the adult men in the US, all the classrooms in a school, all the wheelbarrows in Massachusetts, all the values of your blood pressure, read at five minute intervals, for your entire life. Often, the population is extends over time, as with your blood pressure readings and is, therefore, more amorphous. Consider all the people who have run for governor of a US state since 1900, or all the people who will run for governor through 2050. Those are also populations.

### Exercise 11

In one sentence explain the population parameter of our scenario in terms of standard error.

```{r standard-error-of-different-sh-11}
question_text(NULL,
	message = "In our sampling from the urn activity, however, since we were interested in the proportion of the urn’s beads that were red, the population parameter is the population proportion, denoted with ρ",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

A population parameter is a numerical summary quantity about the population that is unknown, but you wish you knew. For example, when this quantity is the mean, the population parameter of interest is the population mean. This is mathematically denoted with the Greek letter μ pronounced “mu.” 

### Exercise 12

In one sentence explain the sampling of our scenario in terms of standard error.

```{r standard-error-of-different-sh-12}
question_text(NULL,
	message = "In our sampling activities, we used shovels with varying slots to extract samples of size η = 1 through η = 100.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Sampling is the act of collecting a sample from the population when we can not, or do not want to, perform a census. The sample size is lower case η, as opposed to upper case Ν for the population’s size. Typically the sample size η is much smaller than the population size N.

### Exercise 13

In two sentences explain a possible example of biased sampling within our scenario in terms of standard error.

```{r standard-error-of-different-sh-13}
question_text(NULL,
	message = "Had the red beads been much smaller than the white beads, and therefore more prone to falling out of the shovel, our sample would have been biased. In our sampling activities, since we mixed all N = 1000 beads prior to each group’s sampling and since each of the equally sized beads had an equal chance of being sampled, our samples were unbiased.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Biased sampling occurs if certain individuals or observations in a population have a higher chance of being included in a sample than others. We say a sampling procedure is unbiased if every observation in a population had an equal chance of being sampled. 



## Wisdom
### 

*Wisdom* requires the creation of a Preceptor Table, an examination of our data, and a determination, using the concept of “validity,” as to whether or not we can (reasonably!) assume that the two come from the same population.

### Exercise 1

In your own words, define a Preceptor Table.

```{r wisdom-1}
question_text(NULL,
	message = "Preceptor Table is the smallest possible table of data with rows and columns such that, if there is no missing data, then it is easy to calculate the quantities of interest.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Always start your data science work by determining what data you would like to have in order to answer the question easily.


### Exercise 2

Consider the following question: 

> If we get 17 red beads in a random sample of size 50 taken from a mixed urn, what proportion $\rho$ of the beads in the urn are red?

Our *Preceptor Table* is a table with minimal rows and columns such that we can perfectly answer our question using it. Describe the rows and the columns in a Preceptor Table which would allow us to answer this question. 

```{r wisdom-2}
question_text(NULL,
	message = "There will be one row for each bead in the urn. There will be at least one outcome column: color.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

There might be an ID column, but, strictly speaking we don't need one to answer our question.

### Exercise 3

In one sentence, describe the concept of validity as we use it.

```{r wisdom-3}
question_text(NULL,
	message = "Validity is the consistency, or lack thereof, in the columns of your dataset and the corresponding columns in your Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

We have two tables: the data which we drew from the urn and the Preceptor Table. This case is a little strange since the same rows --- i.e., the same beads --- exist in both the data and in the Preceptor Table.


### Exercise 4

Why might the assumption of "validity" not hold in this example? (You have to be very creative in order to come up with some, admittedly far-fetched, problems with validity in htis case.) 

```{r wisdom-4}
question_text(NULL,
	message = "What if there is a secret hose in the bottom of the urn feeding in new beads, including beads of colors other than red and white? This would violate the assumption of validity since, implicitly, 'color' in our data only allows for red and white while 'color' in the Preceptor Table --- meaning the urn now, after some amount of new bead insertion --- has a different meaning.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Beads from an urn is a toy example, but a useful one because all the assumption necessary for inference are trivially true. So, it is hard to come up with counter-examples. Doing so will be much easier in actual problems.



## Justice
### 

*Justice* starts with an examination of the stability, representativeness, and unconfoundedness of the Population Table and ends with an assumption about the mathematical form of the data generating mechanism.

### Exercise 1

In your own words, describe the rows in the Population table and their sources.

```{r justice-1}
question_text(NULL,
	message = "The rows in the Population Table are defined by unique ID/Time combinations. We have one row for every bead in the urn, at every moment in time under consideration. The three sources are the data we collected, the Preceptor Tbale and the underlying population from which both are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The biggest different between the Preceptor Table and the Population Table is that only the latter has a notion of "time." The Preceptor Table refers to a single moment in time to which you want your answer to apply. The Population Table refers to mutiple moments in time, the two most important of which are the moment when the data is collected and the moment to which the Preceptor Table applies.

### Exercise 2

Describe the columns in the Population Table

```{r justice-2}
question_text(NULL,
	message = "There will certainly be a column for 'color', the only outcome variable. There will generally be an 'ID', 'Source' and 'Time' column.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The Population Table should look something like this:

```{r}
tibble(source = c("Population", "Population", "Population","...",  
                  "Data", "Data", "Data", "...",
                  "Population", "Population", "Population","...", 
                  "Preceptor Table", "Preceptor Table", "Preceptor Table", "...",
                  "Population", "Population", "Population"),
       time = c("Time of sample - 2 years", "Time of sample - 3 weeks", "Time of sample - 10 days", "...",
                "Time of sample", "Time of sample", "Time of sample", "...",
                "Time of sample + 10 days", "Time of sample + 3 weeks", "Time of sample + 2 years", "...",
                "Now", "Now", "Now", "...",
                "Now + 10 days", "Now + 3 weeks", "Now + 2 years"),
       id = c("1", "200", "976", "...",
              "2", "200", "1080", "...",
              "1", "200", "2025", "...",
              "1", "200", "2078", "...",
              "1", "200", "2300"),
       color = c("?", "red", "?", "...",
              "white", "red", "white", "...",
              "?", "red", "?", "...",
              "?", "red", "?", "...",
              "?", "red", "?")) |>

  # Then, we use the gt function to make it pretty

  gt() |>
  cols_label(source = md("Source"),
             time = md("Time"),
             id = md("ID"),
             color = md("Color")) |>
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(source))) |>
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"),
            locations = cells_column_labels(columns = c(source))) |>
  cols_align(align = "center", columns = everything()) |>
  cols_align(align = "left", columns = c(source)) |>
  fmt_markdown(columns = everything())
```

### Exercise 3

In one sentence explain the time value for our data.

```{r justice-3}
question_text(NULL,
	message = "The time column for the data is listed as the time of the sample, because only one sample was taken for which we have data.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 4

In one sentence explain the time value for our Preceptor Table.

```{r justice-4}
question_text(NULL,
	message = "The Preceptor Table has a time column of now, because we want to know the contents of the urn in the present day to answer our question.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 5

In one sentence explain the time value for our Population.

```{r justice-5}
question_text(NULL,
	message = "The Population has a time range from as far back as 2 years before the sample and upto 2 years into the future, because the urn sample could have theoretically been taken from anytime in the past or into the future, so a wider population must be acknowledged.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 6

In two sentences, provide a reason why the assumption of stability might not hold.

```{r justice-6}
question_text(NULL,
	message = "What if someone dumps some red beads into the urn after we take our sample? Then we cannot assume stability, because the proportion of red beads in the urn, p, the instant before the dump is different than the proportion red in the urn after.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 7

In two sentences, give an example of why the rows in the Preceptor Table may not be representative of the overall population.

```{r justice-7}
question_text(NULL,
	message = "In the context of our problem, the sampling mechanism of using a shovel of size 50 to sample beads from an urn in which the beads are thoroughly mixed should be enough to consider our sample representative of the population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 8

In two sentences, give an example of why the rows in the data may not be representative of the overall population.

```{r justice-8}
question_text(NULL,
	message = "For the sample data to be similar to the actual population proportion, we ideally want the data we have to be a random, unbiased selection from our population. However, our data may not be similar to the actual population as the data is not random and unbiased.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 9

In two sentences, provide a reason why the assumption of unconfoundedness will not apply.

```{r justice-9}
question_text(NULL,
	message = "Since this is a predictive model, we do not have to worry about unconfoundedness. There is no “treatment” which might be confounded with anything.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 10

Now let's turn our attention to the *Data Generating Mechanism (DGM)*. Should our urn problem be modeled by a normal or binomial distribution? Explain your reasoning in 2 sentences.  

```{r justice-10}
question_text(NULL,
	message = "Our urn problem should be modeled by a binomial distribution, because we model the number of times a red bead is selected (successes) over a white bead (failures). There are only 2 possibilities to model, and the urn problem can be modeled by a binomial distribution",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

## Courage
### 

*Courage* takes the mathematical formula from *Justice* and, using code, creates a fitted model, included posterior probability distributions for all the unknown parameters.



## Summary
### 

This tutorial covered [Chapter 3](https://ppbds.github.io/primer/06-one-parameter.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/). This tutorial reviewd the topics including One Parameter, shovel method, virtual sampling, standard error, Cardinal Virtues (wisdom, justice, courage, and temperance), and a case study.

```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
