---
title: "Visualization A"
tutorial:
  id: "visualization-a"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Chapter 1 Tutorial Part A"
---

<!-- DK: Right now, this tutorial takes about 48 minutes. This is shorter than the other Visualization tutorials: 84, 86 and 68 minutes. At the least, we should increas the length of D. 90 minutes is a good target. Should we increase A? Pro is that it should be 90 minutes too. And the whole week should be 8 hours. Con is that we want the first tutorial to be easy, easy. If we want 8 hours, we can just add an E. -->

<!-- DK: Or does it take this long? AS reported much shorter times than this. Revisit this topic over the summer. -->

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```


## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```


## How do I code in R?
###


### Exercise 1

Before you start coding, you must load the packages you are going to use. In the code chunk below, use the function `library()` to load the `tidyverse` package.

```{r howtc-1, exercise = TRUE}

```

```{r howtc-hint, eval = FALSE}
Place tidyverse inside the library() function.
```

### Exercise 2

If you are ever stuck while coding, R has **help pages**. Let's say we want to know what the function `sqrt()` does. Open the help page for `sqrt()` by typing `?sqrt()` below.

```{r howtc-2, exercise = TRUE}

```

### Exercise 3

Recall **code comments** are text placed after a `#` symbol. Nothing will be run after a `#` symbol, which is useful if you want to write human readable comments in your code..

Press Run Code. Afterwards, delete the `#` and re-run the chunk. You should see a result.

```{r howtc-3, exercise = TRUE}
# sqrt(144)
```

### Exercise 4

Let's save the values of `sqrt(144)` to an object named `results`. Remember to use the assignment operator `<-`. 

```{r howtc-4, exercise = TRUE}

```

```{r howtc-4-hint, eval = FALSE}
results <- sqrt(144)
```

### Exercise 5

A **vector** is a series of values that are created using the `c()` function. Create a vector that contains the integers from one to ten.

```{r howtc-5, exercise = TRUE}

```

```{r howtc-5-hint, eval = FALSE}
Type the values 1-10 inside the function c().
```

### Exercise 6

If your vector contains a sequence of contiguous integers, you can create it with the `:` shortcut. Run `1:10` in the chunk below.

```{r howtc-6, exercise = TRUE}

```

### Exercise 7

You can extract any element of a vector by placing a pair of brackets `[ ]` behind the vector. Inside the brackets, place the number of the element that you'd like to extract. For example, `vec[3]` would return the third element of the vector named `vec`.

The code below assigns a vector to an object named `vec`. Use the chunk below to extract the fourth element of `vec`.

```{r howtc-7, exercise = TRUE}
vec <- c(1, 2, 4, 8, 16)
```

```{r howtc-7-hint, eval = FALSE}
vec[...]
```

### Exercise 8

You can also use `[ ]` to extract multiple elements of a vector. Place the vector `c(1,2,5)` between the brackets below. What does R return?

```{r howtc-8, exercise = TRUE}
vec <- c(1, 2, 4, 8, 16)
vec[]
```

### Exercise 9

If the elements inside your vector have names, you can extract them by name. To do so, place a name or vector of names in the brackets behind a vector. Surround each name with quotation marks, e.g. `vec2[c("alpha", "beta")]`.

Below the given code, extract the element named "gamma" from the vector below.

```{r howtc-9, exercise = TRUE}
vec2 <- c(alpha = 1, beta = 2, gamma = 3)

```

```{r howtc-9-hint, eval = FALSE}
Because the names are characters, make sure to use quotation marks inside the brackets, i.e. vec2["..."].
```

## Exploring Data Frames

Data frames, also referred to as "tibbles", are spreadsheet-type data sets. R comes with many toy **data sets** to explore.

### Exercise 1

It's always a good idea to explore the data before you use it. You can simply examine a dataset by typing its name. Let's examine the contents of `iris` data set. Type `iris` in the line below.

```{r df-1, exercise = TRUE}

```

### Exercise 2

Now use `glimpse()` to look at the `iris` data set.

```{r df-2, exercise = TRUE}

```

```{r df-2-hint, eval = FALSE}
Place iris inside the glimpse() function.
```

### Exercise 3

The `$` operator is a great tool for extracting columns from data frames. Extract the `year` column of the `mpg` data frame using the `$` operator.

```{r df-3, exercise = TRUE}

```

```{r df-3-hint-1, eval = FALSE}
data_f$...
```

```{r df-3-hint-2, eval = FALSE}
See the Primer for guidance!
```


## `geom_point` 

Scatterplots allow you to visualize the relationship between two numerical variables. 

Let's create the following scatterplot. 

```{r scat-p}
scat_p <- ggplot(data = iris, 
                 mapping = aes(x = Sepal.Length, 
                               y = Sepal.Width, 
                              color = Species)) +
  geom_point() +
  labs(title = "Measurements for Different Species of Iris",
        x = "Sepal.Length",
        y = "Sepal.Width")

scat_p
```


### Exercise 1

Let's first `view()` the data set used above called `iris`.

```{r gp-1, exercise = TRUE}

```

```{r gp-1-hint, eval = FALSE}
view(...)
```

There is a chance that `view()` may not work for you when you hit **Run Code**, depending on your computer set up, from within this tutorial. Just make sure that it works from a regular RStudio session and press on.

### Exercise 2

Within `ggplot()`, set `data` to `iris`. Also, map `Sepal.Length` to the x-axis and `Sepal.Width` to the y-axis. Add the layer `geom_point()`.

```{r gp-2, exercise = TRUE}

```

```{r gp-2-hint-1, eval = FALSE}
Remember when you add a layer you use +. 
```

```{r gp-2-hint-2, eval = FALSE}
ggplot(data = iris, 
       mapping = aes(x = ..., 
                     y = ...)) + 
    geom_point()
```

### Exercise 3

Awesome! Now we want to add a `color` aesthetic based on the different species of the iris flower. Set the argument `color` to `Species` inside the `aes()` function.

```{r gp-3, exercise = TRUE}

```

```{r gp-3-hint, eval = FALSE}
ggplot(data = iris, 
       mapping = aes(x = Sepal.Length, 
                     y = Sepal.Width, 
                     color = ...)) 
```

### Exercise 4

Now use `labs()` to add a title and axis labels to the graph. Title your graph "Measurements for Different Species of Iris". Label the 
x-axis "Sepal.Length" and y-axis "Sepal.Width".

```{r gp-4, exercise = TRUE }

```

```{r gp-4-hint-1, eval = FALSE}
Remember to add a layer with the function labs()
```
 
```{r gp-4-hint-2, eval = FALSE}
... +
  labs(title = "...",
       x = "...",
       y = "...") 
```

Reminder: This is what our graph should look like.

```{r}
scat_p
```       

### Exercise 5

Sometimes graphs have overplotting. The following code uses the `mpg` tibble to create a scatterplot that displays 126 points. However, it visualizes a data set that contains 234 points. The missing points are hidden behind other points.

Run the code below to see the scatterplot. 

```{r gp-5, exercise = TRUE}
ggplot(data = mpg, 
       mapping = aes(x = displ, 
                     y = hwy)) +
  geom_point()
```

### Exercise 6

One method to fight overplotting is to make each point **semi-transparent**. The code chunk below provides the code used to create the graph above. Change the transparency of the points by setting `alpha = 0.2` within `geom_point()`.

```{r gp-6, exercise = TRUE}
ggplot(data = mpg, 
       mapping = aes(x = displ, 
                     y = hwy)) +
  geom_point()
```

```{r gp-6-hint, eval = FALSE}
ggplot(data = mpg, 
       mapping = aes(x = displ, y = hwy)) +
  geom_point(alpha = ...)
```


##`geom_jitter()` 

We can also use `geom_jitter()` to fight overplotting. It plots a scatterplot and then adds a small amount of random noise to each point in the plot. 


### Exercise 1

Run the code below that creates a scatterplot with overplotting. 

```{r gj-1, exercise = TRUE}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end)) +
  geom_point()
```

### Exercise 2

Let's now replace `geom_point()` with `geom_jitter()`. 

```{r gj-2, exercise = TRUE}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end)) + 
  geom_point()
```

### Exercise 3

Within `geom_jitter()`, set `width` to `.2` to adjust the amount the points are jittered.

```{r gj-3, exercise = TRUE}

```

```{r gj-3-hint, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end)) +
  geom_jitter(width = ...)

```

### Exercise 4

Within `aes()`, set the `color` aesthetic to the `party` variable. 

```{r gj-4, exercise = TRUE}

```


```{r gj-4-hint, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end, 
                     color = ...)) +
  geom_jitter(width = .2)
```

### Exercise 5

As a final exercise, use what you've learned to recreate the plot below. The graph was created using the data set `diamonds`. The `alpha` of the plot is 0.2, and the `width` of the jitter distribution is 5. Use the `labs()` function to add the titles and labels.

```{r}
ggplot(data = diamonds, mapping = aes(x = depth, y = price)) +
  geom_jitter(width = 5, alpha = 0.2) +
  labs(title = "Depth and Price in Diamonds",
       x = "Depth",
       y = "Price")
```

```{r gj-1-5, exercise = TRUE}

```

```{r gj-1-5-hint, eval = FALSE}
ggplot(data = diamonds, 
       mapping = aes(x = ..., 
                     y = ...)) +
  geom_jitter(width = ..., 
              alpha = ...) +
  labs(title = "...",
       x = "...",
       y = "...")
```

## ` geom_histogram()` 

A histogram is a plot that visualizes the distribution of a numerical variable. 

Let's create the following histogram.

```{r}
hist_p <- ggplot(data = qscores, 
                 mapping = aes(x = rating)) +
        geom_histogram(binwidth = 1, 
                       color = "white", 
                       bins = 10)

hist_p
```

### Exercise 1

Within `ggplot()`, set `data` to `qscores`. Map `rating` to the x-axis to see the distribution of Harvard course ratings. Add the layer `geom_histogram()`.

```{r gh-1, exercise = TRUE}

```

```{r gh-1-hint, eval = FALSE}
ggplot(data = ..., 
       mapping = aes(x = ...)) + 
  geom_histogram
```

### Exercise 2

Add white vertical borders demarcating the bins by adding `color = "white"` to `geom_histogram()`.

```{r gh-2, exercise = TRUE}

```

```{r gh-2-hint, eval = FALSE}
ggplot(data = qscores, 
       mapping = aes(x = rating)) +
  geom_histogram(color = ...)
```

### Exercise 3

Specify the number of bins to be 10 using the `bins` argument in `geom_histogram()`.

```{r gh-3, exercise = TRUE}

```

```{r gh-3-hint, eval = FALSE}
ggplot(data = qscores, 
       mapping = aes(x = rating)) +
  geom_histogram(color = "white",
                 bins = 10)
```

### Exercise 4

Set the width of the bins to be 1 using the `binwidth` argument.

```{r gh-4, exercise = TRUE}

```

Reminder: This is what our graph should look like.

```{r}
hist_p
```


```{r gh-4-hint, eval = FALSE}
ggplot(data = qscores, 
       mapping = aes(x = rating)) +
  geom_histogram(color = "white", 
                 bins = 10, 
                 binwidth = ...)
```



## `geom_bar()`

A barplot is a plot that visualizes the distribution of a categorical variable. 

Let's create the following barplot. 

```{r}
bar_p <- ggplot(data = trains, 
       mapping = aes(x = treatment, 
                     fill = party)) +
  geom_bar(position = "dodge")

bar_p
```

### Exercise 1

Use the `trains` data set in the `primer.data` package. Use `ggplot()` and `geom_bar()` to plot `treatment` on the x-axis.

```{r gb-1, exercise = TRUE}

```

```{r gb-1-hint, eval = FALSE}
ggplot(data = ..., 
       mapping = aes(x = ...)) + 
      ...
```

### Exercise 2

Let's now map the additional variable `party` to the `fill` argument inside `aes()`.

```{r gb-2, exercise = TRUE}

```

```{r gb-2-hint, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = treatment, 
                     fill = ...)) + 
  geom_bar()
```

### Exercise 3

Let's make our graph a side-by-side barplot. Set `position` to "dodge" in `geom_bar()`.

```{r gb-3-hint, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = treatment, 
                     fill = party)) +
  geom_bar(position = ...)
```

```{r gb-3, exercise = TRUE}

```

Reminder: This is what our graph should look like.

```{r}
bar_p
```



## `geom_smooth()` 

We can add a regression line to our scatterplots using `geom_smooth()`


### Exercise 1

Run the code below to see the jittered scatterplot we created in the `geom_jitter()` section using the `trains` dataset.

```{r gs-1, exercise = TRUE}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end)) +
  geom_jitter(width = .2)
```

### Exercise 2

Copy/paste the code from above. Add the layer `geom_smooth()` to the graph. Remember you are adding a layer so you need to include `+`. 

```{r gs-2, exercise = TRUE}

```

```{r gs-2-hint, eval = FALSE}
... + 
  geom_smooth()
```

### Exercise 3

Awesome, but see that message R gives us? Let's try setting the method to "lm" inside `geom_smooth()`.

```{r gs-3, exercise = TRUE, warning = FALSE}

```

```{r gs-3-hint-1, eval = FALSE}
Remember to put "lm" in quotes within geom_smooth()
```

```{r gs-3-hint-2, eval = FALSE}
... +
  geom_smooth(method = "...")
```

### Exercise 4

Great, but we still get a message! Set the `formula` argument within geom_smooth() to `y ~ x`. Also set `se` to FALSE to get rid of the grey area surrounds the trendline.

```{r gs-4, exercise = TRUE}


```

```{r gs-4-hint, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end)) +
  geom_jitter(width = .2)  +
    geom_smooth(method = "lm", formula = y ~ x)
```

### Exercise 5

As a final exercise, use what you've learned about `geom_smooth()` to recreate the plot below. The data set used for this scatterplot is `mpg`.

```{r}
ggplot(data = mpg, 
       mapping = aes(x = cty, y = hwy)) + 
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE) +
  labs(title = "City vs. Highway Fuel Economy",
       x = "City Miles Per Gallon",
       y = "Highway Miles Per Gallon")
```

```{r gs-5, exercise = TRUE}

```

```{r gs-5-hint, eval = FALSE}
For geom_smooth(): The method should be set to "lm", the formula should be set to y ~ x, and se should be set to FALSE.
```


## `geom_density()`
###

`geom_density()` is used to make a density plot, a smoothed version of a histogram. It is a useful alternative to the histogram that displays continuous data in a smooth distribution.

Let's create the following density plot. 

```{r}
dens_p <- ggplot(data = cces, 
                 mapping = aes(x = age, 
                               color = ideology, 
                               fill = ideology)) +
  geom_density(alpha = .1,)

dens_p
```

### Exercise 1

Use the dataset `cces` to make a density plot with `age` on the x axis. Add the layer `geom_density()`

```{r gd-1, exercise = TRUE}

```


```{r gd-1-hint, eval = FALSE}
ggplot(data = ..., 
       mapping = aes(x = ..., 
                     color = ...) + 
         geom_density()
```

### Exercise 2

Now set the `ideology` variable to the aesthetics `color` and `fill`.

```{r gd-2, exercise = TRUE}

```

```{r gd-2-hint, eval = FALSE}
ggplot(data = cces, 
       mapping = aes(x = ..., 
                     color = ..., 
                     fill = ...)) + 
  geom_density()
```

### Exercise 3

Great! Now set the `alpha` argument in `geom_density()` to 0.1.

```{r gd-3, exercise = TRUE}

```

Reminder: Your graph should look something like this. 

```{r}
dens_p
```



## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```

