---
title: "Visualization-A"
tutorial:
  id: "01-visualization-a"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Chapter 1 Tutorial Part A"
---



```{r setup, include=FALSE}
library(tidyverse)
library(PPBDS.data)
library(learnr)
library(shiny)
library(ggthemes)
library(viridis)
library(nycflights13)

knitr::opts_chunk$set(echo = FALSE, message = FALSE)
options(tutorial.exercise.timelimit = 60, tutorial.storage="local")  
```



## Name


``` {r name}
question_text(
  "Student Name:",
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Modify your answer",
  incorrect = "Ok"
)
```


## Email

``` {r email}
question_text(
  "Email:",
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Modify your answer",
  incorrect = "Ok"
)
```


## How do I code in R?

### Exercise 1

In the code chunk below, use `library()` to load the `tidyverse` package. Whenever you load a package R will also load all of the packages that the first package depends on. For example, whenever you load `tidyverse`, `tidyverse` also loads `ggplot2`, `dplyr`, `tibble`, `tidyr`, `readr`, and `purrr`.

```{r packages2, exercise = TRUE}

```

<!-- JSE - commented it out for now due to weird error, not sure how to remove "Run Code" button -->

<!-- ### Install packages -->

<!-- But what if the package that you want to load is not installed on your computer? How would you install the dplyr package on your own computer? -->


### Exercise 2 

Now use `library()` to load the `ggplot2` package of tidyverse. 

```{r exercise-1, exercise = TRUE, exercise.lines = 3}

```


**Functions** are the commands that perform tasks in R. They take in inputs called arguments and return outputs. 


### Exercise 3

Use the `sqrt()` function in the chunk below to compute the square root of 962.

```{r functions-1, exercise = TRUE}

```

### Exercise 4

Hit run code to examine the code that `sqrt()` runs.

```{r functions-2, exercise = TRUE}
sqrt
```

### Exercise 5

Compare the code in `sqrt()` to the code in another R function, `lm()`. Press run code to examine`lm()`'s code body in the chunk below.

```{r functions-3, exercise = TRUE}
lm
```

###

**Help pages** gives us access to the documentation pages for R functions, data sets, and other objects. 

### Exercise 6

Say we want to know what `lm()` does. Open the help page for `lm()` by typing `?lm()` below.

```{r functions-4, exercise = TRUE}

```

###

**Code comments** are text placed after a `#` symbol. Nothing will be run after a `#` symbol. This is useful because it lets you write human readable comments in your code..

### Exercise 7

Run the code chunk below. Afterwards, delete the `#` and re-run the chunk. You should see a result.

```{r functions-5, exercise = TRUE}
# sqrt(961)
```

###

**Objects*** are where values are saved in R. We’ll show you how to assign values to objects and how to display the contents of objects. You can choose almost any name you like for an object, as long as the name does not begin with a number or a special character like `+`, `*`, `-`, `/`, `^`, `!`, `@`, or `&`. 

### Exercise 8

```{r objects-1, echo = FALSE}
question("Which of these would be valid object names?",
  answer("today", correct = TRUE),
  answer("1st"),
  answer("+1"),
  answer("vars", correct = TRUE),
  answer("\\^_^"),
  answer("foo", correct = TRUE),
  allow_retry = TRUE,
  correct = "Remember that the most helpful names will remind you what you put in your object."
)
```

### Exercise 9

Use the assignment operator `<-` to save the results of `rnorm(100, mean = 100, sd = 15)` to an object named `data`.

```{r objects-2, exercise=TRUE}

```

### Exercise 10

What do you think would happen if you assigned `data` to a new object named `copy`, like this? Run the code and then inspect both `data` and `copy`.

```{r objects-3, exercise=TRUE}
data <- rnorm(100, mean = 100, sd = 15)
copy <- data
```

### Exercise 11

R comes with many toy **data sets** pre-loaded. Examine the contents of `iris` to see a classic toy data set. Type `iris` in the line below.

```{r objects-4, exercise = TRUE}

```

### Exercise 12

A **vector** is a series of values. These are created using the `c()` function. 

```{r types5, echo = FALSE}
question('How many types of data can you put into a single vector?',
         answer("1", correct = TRUE),
         answer("6"),
         answer("As many as you like"),
         allow_retry = TRUE)
```

### Exercise 13

In the chunk below, create a vector that contains the integers from one to ten.

```{r vectors-1, exercise = TRUE}

```

```{r vectors-1-hint, eval=FALSE}
# use the funciton c(...)
```

### Exercise 14

If your vector contains a sequence of contiguous integers, you can create it with the `:` shortcut. Run `1:10` in the chunk below.

```{r vectors-2, exercise = TRUE}

```

### Exercise 15

You can extract any element of a vector by placing a pair of brackets `[ ]` behind the vector. Inside the brackets, place the number of the element that you'd like to extract. For example, `vec[3]` would return the third element of the vector named `vec`.

Use the chunk below to extract the fourth element of `vec`.

```{r vectors-3, exercise = TRUE}
vec <- c(1, 2, 4, 8, 16)
```

### Exercise 16

You can also use `[ ]` to extract multiple elements of a vector. Place the vector `c(1,2,5)` between the brackets below. What does R return?

```{r vectors-4, exercise = TRUE}
vec <- c(1, 2, 4, 8, 16)
vec[]
```

### Exercise 17

If the elements of your vector have names, you can extract them by name. To do so place a name or vector of names in the brackets behind a vector. Surround each name with quotation marks, e.g. `vec2[c("alpha", "beta")]`.

Extract the element named "gamma" from the vector below.

```{r vectors-5, exercise = TRUE}
vec2 <- c(alpha = 1, beta = 2, gamma = 3)
```

###


Below is the `flights` data frame.
 
```{r flights3, echo = FALSE}
flights
``` 
 
The letter abbreviations that appear under the column names of `flights` describe the _type_ of data that is stored in each column of `flights`:

* `int` : integers.

* `dbl` : doubles, or real numbers.

* `chr` : character vectors, or strings.

* `dttm`: date-times (a date + a time).


### Exercise 18

One of the most common mistakes in R is to call an **object** when you mean to call a **character** string and vice versa.


```{r types6, echo = FALSE}
question('Which of these are object names? What is the difference between object names and character strings?',
         answer("foo", correct = TRUE),
         answer('"num"'),
         answer("mu", correct = TRUE),
         answer('"sigma"'),
         answer('"data"'),
         answer("a", correct = TRUE),
         allow_retry = TRUE,
         correct = "Character strings are surrounded by quotation marks, object names are not.")
```


## Data Frames

Data frames are “spreadsheet”-type datasets.You can make a data frame with the `data.frame()` function, which works similar to `c()`.


### Exercise 1

Assemble the vectors below into a data frame using `data.frame()`with the column names `numbers`, `logicals`, `strings`. Assign the data frame to the object named `df`.

```{r lists4, exercise = TRUE}
nums <- c(1, 2, 3, 4)
logs <- c(TRUE, TRUE, FALSE, TRUE)
strs <- c("apple", "banana", "carrot", "duck")
```

### Exercise 2

Extract the strings column of the `df` data frame using the `$` operator.

```{r lists5, exercise = TRUE}
nums <- c(1, 2, 3, 4)
logs <- c(TRUE, TRUE, FALSE, TRUE)
strs <- c("apple", "banana", "carrot", "duck")
df <- data.frame(numbers = nums, logicals = logs, strings = strs)
```

### Exercise 3

Load the `PPBDS.data` package using `library()`. Then, look run the code below.

```{r exercise-2, exercise = TRUE, exercise.lines = 5}
trains
```

### Exercise 4

Use the `glimpse()` function to look at the `trains` data set. We already loaded the `tidyverse` and `PPBDS.data` packages.

```{r exercise-4, exercise = TRUE, exercise.lines = 5}
library(tidyverse)
library(PPBDS.data)


```

### Exercise 5

Extract the `income` variable in the `trains` data set using the `$` operator.

```{r exercise-5, exercise = TRUE}

```


## Grammar of graphics

Graphics are designed to emphasize the findings and insights you want your audience to understand.

### Exercise 1

```{r quiz-6, echo = FALSE}
quiz(
  question("What are the three essential components of a graphic?",
           answer("the data set containing the variables in question", correct = TRUE),
           answer("the geometric object we can observe in a plot", correct = TRUE),
           answer("axes labels on a plot"),
           answer("the aesthetic attributes", correct = TRUE),
           allow_retry = TRUE
  ),
  question("What are the two important arguments that we need to provide the `ggplot()` function?",
           answer("`data` and `mapping`", correct = TRUE),
           answer("`data` and `aesthetics`"),
           answer("`data` and `layers`"),
           allow_retry = TRUE
  )
)
```


### Exercise 2

```{r trains}
ggplot(data = trains, mapping = aes(x = att_start, y = att_end, color = treatment)) +
  geom_point() + facet_wrap(~party)
```


```{r quiz-7, echo = FALSE}
quiz(
  question("Which `data` variable is mapped to the `x`-position `aes`thetic of the points?",
           answer("`att_start`", correct = TRUE),
           answer("`att_end`"),
           answer("`treatment`"),
           allow_retry = TRUE
  ),
  question("Which `data` variable is mapped to the `y`-position `aes`thetic of the points?",
           answer("`att_start`"),
           answer("`att_end`", correct = TRUE),
           answer("`treatment`"),
           allow_retry = TRUE
  ),
  question("Which `data` variable is mapped to the `color` `aes`thetic of the points?",
           answer("`att_start`"),
           answer("`att_end`"),
           answer("`treatment`", correct = TRUE),
           allow_retry = TRUE
  )
)
```

## ` geom_point` 

Scatterplots allow you to visualize the relationship between two numerical variables. 

Let's create the following scatterplot. 

```{r scat-p}
scat_p <- ggplot(data = qscores, mapping = aes(x = rating, y = hours, size = enrollment)) +
  geom_point()

scat_p
```


### Exercise 1

Load the `PPBDS.data` package and look at the `qscores` data set by simply typing the name of the data set.

```{r exercise-6, exercise = TRUE, exercise.lines = 5}

```

```{r exercise-6-hint, eval=FALSE}
library(...)
...

```


### Exercise 2

Nice! Now load the `ggplot2` package using `library()`. On the line below, use the `ggplot()` function to create a scatterplot using the `qscores` data set. Map `rating` to the x-axis and `hours` to the y-axis.

```{r exercise-7, exercise = TRUE, exercise.lines = 5}

```

```{r exercise-7-hint, eval=FALSE}
library(...)
ggplot(data = qscores, mapping = aes(x = ..., y = ...)) +geom_point()
```

### Exercise 3

Awesome! Now we want to add a `size` aesthetic based on the number of students enrolled in each course. Set the argument `size` to `enrollment` inside the `aes()` function.

```{r exercise-8, exercise = TRUE, exercise.lines = 5}

```

```{r exercise-8-hint, eval=FALSE}
ggplot(data = qscores, mapping = aes(x = rating, y = hours, size = ...)) 
```

Reminder: This is what our graph should look like.

```{r}
scat_p
```


### Exercise 4

The following plot was created using the `mpg` data set. It only displays 126 points, but it visualizes a data set that contains 234 points. In this section, we will fix this issue.

```{r echo = FALSE, out.width = "80%"}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point()
```

The missing points are hidden behind other points, a phenomenon known as _overplotting_. Overplotting provides an incomplete picture of the data set. You cannot determine where the *mass* of the points fall, which makes it difficult to spot relationships in the data. 

**Causes of overplotting**

1. The data points have been rounded to a "grid" of common values, as in the plot above
2. The data set is so large that it cannot be plotted without points overlapping each other


### Exercise 5

One method to fight overplotting is to make each point semi-transparent. The code chunk below provides the code used to create the graph above. Change the transparency of the points by setting `alpha = 0.2` within `geom_point()`.

```{r exercise-9, exercise = TRUE, exercise.lines = 5}
ggplot(data = qscores, mapping = aes(x = rating, y = hours, size = enrollment)) +
  geom_point()
```

```{r exercise-9-hint, eval=FALSE}
ggplot(data = qscores, mapping = aes(x = rating, y = hours, size = enrollment)) +
  geom_point(alpha = ...)
```


##`geom_jitter()` 

`geom_jitter()` is another method to deal with overplotting. It plots a scatterplot and then adds a small amount of random noise to each point in the plot. 

The following scatterplot, which was created using the `mpg` tibble, has overplotting. In this section, we will fix this issue using `geom_jitter()`.

```{r}
ggplot(data = trains, mapping = aes(x = att_start, y = att_end)) +
  geom_point()
```


### Exercise 1

The code for the graph above has been provdied for you below. Replace `geom_point()` with `geom_jitter()`.

```{r jit-I-1, exercise = TRUE}
ggplot(data = trains, mapping = aes(x = att_start, y = att_end)) + geom_point()
```

```{r jit-I-1-hint, eval = FALSE}
ggplot(data = trains, mapping = aes(x = att_start, y = att_end)) +
  geom_jitter()

```

### Exercise 2

As you can see, jittering the points shifted them slightly from under each other. We can adjust the amount that the points are jittered by setting the width. Set the `width` to `.2` within `geom_jitter()`.

```{r jit-I-3, exercise= TRUE, exercise.lines=6}

```

```{r jit-I-3-hint, eval = FALSE}
ggplot(data = trains, mapping = aes(x = att_start, y = att_end)) +
  geom_jitter(width = .2)

```

### Exercise 3

Now set the `color` aesthetic to the `party` variable. 

```{r jit-I-4, exercise=TRUE, exercise.lines=6}

```


```{r jit-I-4-hint, eval=FALSE}
Because color is an aesthetic, set it inside of aes().
```


### Exercise 5

Now use what you've learned to recreate the plot below. The graph was created using the data set `diamonds`. The `alpha` of the plot is 0.2, and the `width` of the jitter distribution is 5. Use the `labs()` function to add titles.

```{r}
ggplot(data = diamonds, mapping = aes(x = depth, y = price)) +
  geom_jitter(width = 5, alpha = 0.2) +
  labs(title = "Depth and Price in Diamonds",
       x = "Depth",
       y = "Price")
```

```{r gj-1-5, exercise=TRUE, exercise.lines = 5}

```

## ` geom_histogram()` 

A histogram is a plot that visualizes the distribution of a numerical variable. Let's create the following plot.

```{r}
hist_p <- ggplot(data = qscores, mapping = aes(x = rating)) +
  geom_histogram(binwidth = 1, color = "white", fill = "red4", bins = 10)

hist_p
```

### Exercise 1

Using the `qscores` data set and `ggplot()`, make a histogram where `rating` is on the x-axis to see the distribution of Harvard course ratings.

```{r exercise-12, exercise = TRUE, exercise.lines = 5}

```

```{r exercise-12-hint, eval=FALSE}
ggplot(data = ..., mapping = aes(x = ...)) + ...
```

### Exercise 2

Add white vertical borders demarcating the bins by adding `color = "white"` and `fill = "red4"` arguments to `geom_histogram()`.

```{r exercise-13, exercise = TRUE, exercise.lines = 5}

```

```{r exercise-13-hint, eval=FALSE}
ggplot(data = qscores, mapping = aes(x = rating)) +
  geom_histogram(color = ..., fill = ...)
```

### Exercise 3

Specify the number of bins to be 10 via the `bins` argument in `geom_histogram()`.

```{r exercise-14, exercise = TRUE, exercise.lines = 5}

```

```{r exercise-14-hint, eval=FALSE}
ggplot(data = qscores, mapping = aes(x = rating)) +
  geom_histogram(color = "white", fill = "red4", bins = 10)
```

### Exercise 4

Specify the width of the bins to be 1 via the `binwidth` argument.

```{r exercise-15, exercise = TRUE, exercise.lines = 5}

```

Reminder: This is what our graph should look like.

```{r}
hist_p
```


```{r exercise-15-hint, eval=FALSE}
ggplot(data = qscores, mapping = aes(x = rating)) +
  geom_histogram(color = "white", fill = "red4", bins = 10, binwidth = 1)
```


## `geom_boxplot()` 
###

A boxplot displays the five-number summary of a set of data(. The five-number summary (minimum, first quartile, median, third quartile, and maximum).

Let's create the following boxplot. 

```{r}
box_p <- ggplot(data = mpg, mapping = aes(x = class, y = hwy )) +
          geom_boxplot() + 
          labs( title = "Highway Fuel Efficiency in Different Types of Cars")

box_p
```

### Exercise 1

Using the `mpg` tibble, which shows the fuel efficiency for different types of cars, set x = `class`, and y = `hwy`.

```{r gb-1-2, exercise=TRUE, exercise.lines = 5}

```

```{r gb-1-2-hint, eval=FALSE}
ggplot(data = mpg, mapping = aes(x = ... , y = ... )) +
  geom_boxplot()
```

### Exercise 2

Nice! Using `labs()` title the plot "Highway Fuel Efficiency in Different Types of Cars".

```{r gb-1-4, exercise=TRUE, exercise.lines = 5}

```


```{r gb-1-4-hint, eval=FALSE}
labs(title = ...)
```


## `geom_bar()`

A barplot is a plot that visualizes the distribution of a categorical variable. 

Let's create the following barplot. 

```{r}
ggplot(data = trains, mapping = aes(x = treatment, fill = party)) +
  geom_bar(position = "dodge")
```

### Exercise 1

Let's go back to the `trains` data set in the `PPBDS.data` package. Use `ggplot()` and `geom_bar()` to plot `treatment` on the x-axis.

```{r exercise-19, exercise = TRUE, exercise.lines = 5}

```

```{r exercise-19-hint, eval=FALSE}
ggplot(data = ..., mapping = aes(x = ...)) + ...
```

### Exercise 2

We can now map the additional variable `party` by adding a `fill = party` inside the `aes()` aesthetic mapping.

```{r exercise-20, exercise = TRUE, exercise.lines = 5}

```

```{r exercise-20-hint, eval=FALSE}
ggplot(data = trains, mapping = aes(x = treatment, fill = ...)) + 
  geom_bar()
```

### Exercise 3

Let's make our graph a side-by-side barplot. Set `position` to "dodge" in `geom_bar()`.

```{r exercise-22, exercise = TRUE, exercise.lines = 5}

```

```{r exercise-22-hint, eval=FALSE}
ggplot(data = trains, mapping = aes(x = treatment, fill = party)) +
  geom_bar(position = ...)
```



## `geom_smooth()` 

` geom_smooth()` adds a regression line on a scatterplot. 

###

### Exercise 1

Let's start by creating a scatterplot using  the `nhanes` dataset. Run the code below.

```{r smooth-I-1, exercise=TRUE, exercise.lines=7}
ggplot(data = nhanes, mapping = aes(x = weight, y = height)) +
  geom_point()

```


### Exercise 2

Now add `geom_smooth()` to the graph. Remember you are adding a layer so you need to include `+`. 

```{r smooth-I-2, exercise=TRUE, exercise.lines=7, eval=FALSE}
ggplot(data = nhanes, mapping = aes(x = weight, y = height)) +
  geom_point()


```

### Exercise 3

Nice! As you can see, the line you just graphed represents the trend that we see in the scatterplot. See the message that R gave us? Because we didn't set the method that R uses to calculate the line, R defaulted to using "gam". Let's try setting the method to "lm" inside `geom_smooth()`.

```{r smooth-I-3, exercise=TRUE, exercise.lines=7}


```

```{r smooth-I-3-hint, eval=FALSE}
Remember to put "lm" in quotes.
```

### Exercise 4

Great! Now get rid of the scatterplot by deleting `geom_point()` and only use `geom_smooth()`. Then, set the `color` aesthetic to the `gender` variable.

```{r smooth-I-4, exercise=TRUE, exercise.lines=7}


```

```{r smooth-I-4-hint, eval=FALSE}
Because color is an aesthetic, set it inside of aes().
```

### Exercise 5

Great! Now, use what you've learned about `geom_smooth()` to recreate the plot below.

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_smooth(color = "red") +
  labs(title = "City vs. Highway Fuel Economy",
       x = "City Miles Per Gallon",
       y = "Highway Miles Per Gallon")
```

```{r gs-1-5, exercise=TRUE, exercise.lines = 5}

```

## `geom_density()`
###

`geom_density()` is used to make a density plot, a smoothed version of a histogram. It is a useful alternative to the histogram that displays continuous data in a smooth distribution.

Let's create the following density plot. 

```{r}
dens_p <- ggplot(data = cces, mapping = aes(x = age, color = ideology, fill = ideology)) +
  geom_density(alpha = .3, position = "fill") + xlim(20, 90)

dens_p
```


### Exercise 1

Use the dataset `cces` to make a density plot with `age` on the x axis and `ideology` set to the aesthetics `color` and `fill`.

```{r den1D-II-1, exercise=TRUE, exercise.lines=6}

```


```{rden1D-II-1-hint, eval = FALSE}
ggplot(data = cces, mapping = aes(x = ..., color = ..., fill = ...))
```


### Exercise 2

Great! As you can see, we have a lot of overlapping going on. Try setting the `alpha` parameter in `geom_density()` to 0.3.

```{r den1D-II-2, exercise=TRUE, exercise.lines=6}


```

### Exercise 3

Nice! Now try setting the `position` parameter in `geom_density()` to "fill". Then try setting it to "stack".

```{r den1D-II-3, exercise=TRUE, exercise.lines=7}


```

### Exercise 4

Great! Now add a limit to the x axis with an upper bound of 90 and a lower bound of 20.

```{r den1D-II-4, exercise=TRUE, exercise.lines=8}


```

Reminder: Your graph should look something like this. 

```{r}
dens_p
```

```{r den1D-II-4-hint, eval=FALSE}
Use xlim() to add a limit on the x axis
```


## The `tidyverse`

Now it's time to learn more about data wrangling using the `tidyverse`. We'll go over the following functions in this tutorial:

* **filter()** a data frame’s existing rows by only picking a subset of them.
* **select()** specific variable columns in a data set. Additional functions like **slice()** can further subset the data.
* **arrange()** its rows. For example, sort the rows of weather in ascending or descending order of temp.
* **group_by()** its rows. In other words, assign different rows to be part of the same group. We can then combine **group_by()** with **summarize()** to report summary statistics for each group separately. 
* **mutate()** its existing columns/variables to create new ones. 

###

### Exercise 1

Before we get started, load the `tidyverse` collection of packages and the package `PPBDS.data`.

```{r data-I-1, exercise=TRUE, exercise.lines=3}

```

```{r data-I-1-hint, eval = FALSE}
Use library()
```


### Exercise 2

Let's take a `glimpse()` at the data set `cces`. Press "Run Code".

```{r data-I-2, exercise=TRUE, exercise.lines=3}
glimpse(cces)
```

### Exercise 3 

Using the pipe operator `%>%`, add `filter()`. Within `filter()` use the argument `state == "Massachusetts"` and `gender == "Female"`.

```{r data-I-4, exercise=TRUE, exercise.lines=10}


```

```{r data-I-4-hint, eval=FALSE}
cces %>% 
  filter(state == "...", gender == "...")
```

### Exercise 3

We now want to organize our code by descending order of age. Copy and paste your code from above. Use `%>% `to add `arrange()`. Within `arrange()`, use the argument `desc(age)`.

```{r data-I-5, exercise=TRUE, exercise.lines=10}

```

```{r data-I-5-hint, eval=FALSE}
cces %>% 
  filter(state == "Massachusetts", gender == "Female") %>% 
  arrange(desc(age))
```

### Exercise 4

Great! Now continue the code using `%>%` again to add `summarize()`. We want to find the mean and median ages from our filtered data.

```{r data-I-6, exercise=TRUE, exercise.lines=10}

```

### Exercise 5

For this section, we will be focusing on a really big data set called `nhanes`. Let's say we wanted to make a graph using data on `height` and `weight` from the 200 youngest black males. We first would `select()` the variables we want to focus on, in this case `height`, `weight`, `age`, `race`, and `gender`. Try doing this below:

```{r data-II-1, exercise=TRUE, exercise.lines=10}


```

### Exercise 6

Now we want to narrow down our data to only black males, so let's use `filter()` to create a tibble made up of rows from `nhanes` where `race == "Black"` and `gender == "Male"`.

```{r data-II-2, exercise=TRUE, exercise.lines=10}


```

### Exercise 7

Great! So what now? Well, we want to look at the youngest black males. To do this, we would have to `arrange()` by age. Do this below:

```{r data-II-3, exercise=TRUE, exercise.lines=10}


```

### Exercise 8

Nice! Now use `slice()` to isolate the 200 rows with the lowest age value.

```{r data-II-4, exercise=TRUE, exercise.lines=10}


```

```{r data-II-4-hint-1, eval=FALSE}

Because of the way we arranged the data, the 200 rows with the lowest age value would be the first 200

```

```{r data-II-4-hint-2, eval=FALSE}

slice(1:200)

```

<!-- Well done. Now, use what you've learned about data wrangling to recreate the data set below. -->

<!-- The data set only takes into account classes with an enrollment of at least 25. To calculate the devation from the median of a variable, use `mad()`, which stands for Median Absolute Deviation -->

<!-- ```{r} -->
<!-- qscores %>% -->
<!--   select(rating, department, enrollment) %>% -->
<!--   filter(enrollment > 25) %>% -->
<!--   group_by(department) %>% -->
<!--   summarise(medianRating = median(rating), -->
<!--             deviation = mad(rating)) -->
<!-- ``` -->

<!-- ```{r da-3-7, exercise=TRUE, exercise.lines = 5} -->

<!-- ``` -->

## Submit

Congrats on finishing your first Gov 50 tutorial! You're on your way to being a master in data visualization and wrangling! :)

```{r context="setup"}
submission_ui
```

```{r context="server"}
submission_server()
```
