---
title: "Three Parameters"
tutorial:
  id: "three-parameters"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 8 tutorial"
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(rstanarm)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

fit_obj <- stan_glm(income ~ liberal - 1, 
                    data = trains, 
                    refresh = 0)

new_obs <- tibble(liberal = TRUE)

pp  <- posterior_predict(fit_obj, 
                         newdata = new_obs)

```


```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```


## EDA trains 

Let's create this graph. 

```{r}
p_trains <- trains %>% 
  select(liberal, att_end, income, treatment) %>% 
  ggplot(aes(x = liberal, y = income)) + 
    geom_jitter(width = 0.1, height = 0) + 
    labs(title = "Income by Liberal Affiliation in Trains Data Set",
         x = "Liberal",
         y = "Income")

p_trains
```

### Exercise 1

Run `glimpse()` to explore the `trains` data set.

```{r glimpse, exercise = TRUE}

```

### Exercise 2

Start a pipe with `trains`. Select the `liberal`, `att_end`, `income`, and `treatment` variables. 


```{r ch_8, exercise = TRUE}

```

```{r ch_8-hint, eval = FALSE}
trains %>% 
  select(...)
```

### Exercise 3

Continue the pipe into `ggplot()`. Map `liberal` to the x-axis and `income` to the y axis. Use `geom_jitter()`. Set `width` to 0.1 and `height` to 0. 

```{r point, exercise = TRUE}

```

```{r point-hint, eval = FALSE}
trains %>% 
  select(liberal, att_end, income, treatment) %>% 
  ggplot(aes(x = ..., y = ...)) + 
    geom_jitter(width = ..., height = ...)
```

### Exercise 4

Title your graph "Income by Liberal Affiliation in Trains Data Set". Label your x-axis "Liberal" and your y-axis "Income". It should look something like our graph, but does not have to be exactly the same.

```{r}
p_trains
```


```{r trains, exercise = TRUE}

```

## income as a function of liberal

Let's take a closer look at the graph you just created in the previous section. Say our motive for creating this graph was to answer the following question: _What is the probability that the next liberal who arrives at the train station today has an income greater than $100,000?_


### Exercise 1


Using **Wisdom**, write a paragraph about whether or not this data is relevant for the problem we face. See *The Primer* for guidance.

```{r wisdom}
question_text(
  "Answer:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

### Exercise 2

In order for us to consider this model as causal, there need to be (at least) two potential outcomes. Let's say we consider this model to be casual. Write a sentence explaining the two potential outcomes. 

```{r potential-outcomes}
question_text(
  "Answer:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

### Exercise 3

Write a paragraph that provides arguments for considering this model as predictive and for considering it as causal. There is no right answer! 

```{r model-type}
question_text(
  "Answer:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

### Exercise 4

Recall the motto from Chapter 4: "No causation without manipulation". Write a paragraph about what manipulation you would propose --- in practice or in theory --- so one might see, for a given individual, one potential outcome or the other.

```{r motto}
question_text(
  "Answer:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

### Exercise 5

In Chapter 4 we learned that one way to estimate the average treatment effect is to use the following formula: average of treated minus the average of control. Write a paragraph explaining the strengths or weaknesses of applying this formula to estimate, using our data set, the causal effect on income of being liberal.

```{r treatment-effect}
question_text(
  "Answer:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

### Exercise 6

$$ \underbrace{y_i}_{outcome} = \underbrace{\beta_1 x_{t,i} + \beta_2 x_{f,i}}_{in\ the\ model} + \underbrace{\epsilon_i}_{not\ in\ the\ model}$$
where \n
$$x_{t,i}, x_{f,i} \in \{0,1\}$$ \n
$$x_{t,i} +  x_{f,i} = 1$$ \n
$$\epsilon_i \sim N(0, \sigma^2)$$  

This set up is very similar to the ones in the *Primer*. Instead of $x_{r,i}$/$x_{d,i}$ indicating whether or not person $i$ is a Republican/Democrat, we now have $x_{t,i}$/$x_{f,i}$ indicating whether or not person $i$ is TRUE/FALSE for liberal. Which are the three parameters here? What do they mean? You do not need to figure out how to display the symbols in your answer, just write their names (i.e. "epsilon," "delta," etc. ).

```{r math-model}
question_text(
  "Answer:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

Great! Now for the rest of the tutorial, we are going to consider this model as **predictive**. 

### Exercise 7

Let's now use `stan_glm()`. Set your outcome variable as `income`and your explanatory variable as `liberal` (Remember you must insert a tilde `~` between the two). Also, include a `-1` after `liberal` so we do not get an intercept.  Set `data` to `trains`, and `refresh` to 0. 

```{r stan-glm, exercise = TRUE}

```

```{r stan-glm-hint, eval = FALSE}
stan_glm(income ~ liberal - 1, 
         data = ..., 
         refresh = ...)
```

### Exercise 8

Copy and paste your work from above, and assign it to an object named `fit_obj`. Then, on the next line, `print()` the object `fit_obj`. 

```{r print-object, exercise = TRUE}

```

```{r print-object-hint, eval = FALSE}
fit_obj <- stan_glm(income ~ liberal - 1, 
                    data = trains, 
                    refresh = 0)

print(...)
```

### Exercise 9

Now look at your printed model. In two sentences, interpret the meaning of the the Median and MAD SD values for `liberalFALSE`. 

```{r interpret-model}
question_text(
  "Answer:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

### Exercise 10

Let's now create the posterior probability distribution for $\beta_1$  and $\beta_2$. Remember: these are the average incomes of liberals and non-liberals in the population. This is the plot we will create.

```{r}
p_post <- fit_obj %>% 
  as_tibble() %>% 
  select(-sigma) %>% 
  pivot_longer(cols = liberalFALSE :liberalTRUE,
              names_to = "parameter",
              values_to = "income") %>% 
  ggplot(aes(x = income, color = parameter)) +
    geom_density() +
    labs(title = "Posterior Probability Distribution",
         subtitle = "Average income for population in 2012",
         x = "Income",
         y = "Probability") +
    theme_classic() + 
    scale_x_continuous(labels=scales::dollar_format()) +  
    scale_y_continuous(labels=scales::percent_format())

p_post 
```


### Exercise 11

Start a pipe with `fit_obj`. Use `as_tibble()`, then continue the pipe with `select()` to remove the `sigma` variable. We want to focus on our other two parameters:  $\beta_1$  and $\beta_2$.

```{r as-tibble, exercise = TRUE}

```

```{r as-tibble-hint-1, eval = FALSE}
fit_obj %>% 
  as_tibble() %>% 
  select(-...) 
```

### Exercise 12

Continue the pipe with `pivot_longer()`. Set `cols` to `liberalFALSE` and `liberalTRUE` (Make sure you insert a colon between them). `names_to` should be set to "parameter" and `values_to` should be set to "income".

```{r colon, exercise = TRUE}

```

```{r colon-hint, eval = FALSE}
... %>% 
pivot_longer(cols = ... : ...,
             names_to = "...",
             values_to = "...")
```

### Exercise 13

Continue your pipe even further. Let's now use `ggplot()` to plot your data. Map `income` to the x-axis, and map `parameter` to the color. Add the layers `geom_density()`and `theme_classic()`. 

```{r gdensity, exercise = TRUE}

```


```{r gdensity-hint, eval = FALSE}
fit_obj %>% 
  as_tibble() %>% 
  select(-sigma) %>% 
  pivot_longer(cols = liberalFALSE :liberalTRUE,
              names_to = "parameter",
              values_to = "income") %>% 
  ggplot(aes(x = income, color = parameter)) +
    geom_density() +
    theme_classic() 
```

### Exercise 14

Let's also change the y-axis values to show percents rather decimals (It is nicer to view probability this way). We do this by using `scale_y_continuous()`. Within `scale_y_continuous()`, set the`labels` to `scales::percent_format()`. Let's change the x-axis values of income to include dollar signs as well. We do this by using `scale_x_continuous()`, Within `scale_x_continuous()`, set the`labels` to `scales::dollar_format()`. 

```{r scale1, exercise = TRUE}

```

```{r scale1-hint, eval = FALSE}
Remember you are adding a layer here! ( you must use "+")
```

```{r scale1-hint-2, eval = FALSE}
... + 
  scale_y_continuous(labels=scales::percent_format()) +
  scale_x_continuous(labels=scales::dollar_format())  
```

### Exercise 15

Your final plot should look something like ours. All that is left to add is some labels.

```{r}
p_post 
```



```{r p-complete, exercise = TRUE}

```

### Exercise 16

How many unique fitted values do we have based on our data below? Provide a sentence of intuition for why.

```{r}
library(gt)
trains %>% 
  select(income, liberal) %>% 
  mutate(fitted = fitted(fit_obj)) %>% 
  mutate(residual = residuals(fit_obj)) %>% 
  slice(1:8) %>% 
  gt() %>%
  cols_label(income = md("**Income**"),
             liberal = md("**Liberal**"),
             fitted = md("**Fitted**"),
             residual = md("**Residual**")) %>%
  fmt_number(columns = c(fitted), decimals = 2) %>% 
  tab_header("8 Observations from Trains Dataset") %>%
  cols_align(align = "center", columns = everything()) 


```

```{r observation}
question_text(
  "Answer:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```


Let's now answer the following question:  _What is the probability that the next liberal who arrives at the train station today has an income greater than $100,000?_ . 


### Exercise 17

Let's create a tibble with a column named `liberal` and a single observation TRUE. Assign your work to an object named `new_obs`.

```{r tibble, exercise = TRUE}

```


```{r tibble-hint, eval = FALSE}
new_obs <- tibble(liberal = ...)
```

### Exercise 18

Let's now use `posterior_predict()`. The first argument should be our fitted model `fit_obj`. The second argument `newdata` should be set to `new_obs`. Assign your work to an object named `pp`.  

```{r pp, exercise = TRUE}

```

```{r pp-hint, eval = FALSE}
pp  <- posterior_predict(fit_obj, 
                         newdata = ...)

```

### Exercise 19

Great! Now start a pipe with a tibble that has one variable `income` and its value is set to equal the first column of `pp`.    

```{r column, exercise = TRUE}

```

```{r column-hint, eval = FALSE}
tibble(income = pp[, 1])
```

### Exercise 20

Pipe the results of the tibble to `mutate()` to create a new variable `gt_1k`. `gt_tk` should use an `ifelse` statement. Within `ifelse()`, check that `income` is a value greater than 100,000. If it is, return TRUE. If it is not, return FALSE.

```{r mutate, exercise = TRUE}

```



```{r mutate-hint, eval = FALSE}
tibble(income = pp[, 1]) %>% 
  mutate(... = ifelse(income > ..., TRUE, FALSE))
```

### Exercise 21

Continue the pipe. Use `summarize()` and create a new variable called `perc`, which is the `sum` of `gt_1k` divided by the function `n()`. 

```{r summarize, exercise = TRUE}

```


```{r summarize-hint, eval = FALSE}
... %>% 
  summarize(perc = sum(...)/n())
```

Awesome! Now we know the probability that the next liberal who arrives at the train station today has an income greater than $100,000.

### Exercise 22

Using **Temperance**, write a paragraph about how you should use this estimate. Are you sure it is correct? How safely can you apply data from 8 years ago to today? How similar is the population from which you drew the data to the population to which you hope to apply your model? See *The Primer* for guidance.

```{r temperance}
question_text(
  "Answer:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```


```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
