---
title: Probability
author: David Kane and Ivy Spratt
tutorial:
  id: probability
output:
  learnr::tutorial:
    progressive: yes
    allow_skip:: yes
runtime: shiny_prerendered
description: 'Chapter 2 Tutorial: Probability'
---

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(gt)

library(tidyverse)
library(primer.data)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 



```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

<!-- We are going to have two examples (Example 1 and Example 2), each of which will cover 20 to 30 questions. The two examples use the same data set. But the first sets up a predictive model and the second a causal model. See below.

Example 1 will be very similar to the template_tutorials in that students will be asked to all the definition questions.

Example 2 will leave out the definition questions (except for unconfoundedness, which I don't mind having students define twice). But it will do all the other template_tutorial questions. (And it is OK if the same knowledge drops are used twice. They are good drops!) But it will have more questions exploring some subtle issues in the data.

We will not have a Wisdom section and so on. We just run the questions together.

The Courage and Temperance sections will be very short, maybe just ask for the definitions and explain that we aren't yet ready to code. -->

<!-- At a later date, we might go and add material about probability distributions, standard errors and so on. But probably not this year. -->


## Introduction
### 

This tutorial covers [Chapter 2: Probability](https://ppbds.github.io/primer/probability.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 

The world confronts us. Make decisions we must.

<!-- Add a summary of what students will learn. Add it at the end also. Includes the four Cardinal Virtues. -->

## Example 1
###

<!-- Follows template_tutorial almost exactly for Wisdom and Justice. Loads no libraries. Courage and Temperance are quick. -->

Imagine you are a high school principal today who wants to forecast how well the juniors in his school will do on the SAT. (Some of the students have taken the PSAT and some have not.) 

The data is from a different high school from the class of 2015. It includes all the members of the graduating class who went on to college. The outcome of interest is each student's SAT score (math + verbal, scores can range from 400 to 1600). The covariates include their sex, high school grades, PSAT scores, the average SAT scores of their parents, their family income, how many hours they studied for the SAT, whether or not they took an SAT tutoring class, and where they were going to college.


## Example 2
###

<!-- same, but don't ask for definitions again. -->

Imagine you are a high school principal at a different high school who is considering providing an SAT tutoring class to all the juniors in her school. What will happen to SAT scores if he does so?

The data is from a high school from the class of 2015. It includes all the members of the graduating class who went on to college. The outcome of interest is each student's SAT score (math + verbal, scores can range from 400 to 1600). The covariates include their sex, high school grades, PSAT scores, the average SAT scores of their parents, their family income, how many hours they studied for the SAT, whether or not they took an SAT tutoring class, and where they were going to college.

## Summary
### 

This tutorial covered [Chapter 2: Probability](https://ppbds.github.io/primer/probability.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/).  

<!-- Add summary from introduction. -->

```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
