---
title: Probability
author: David Kane and Tanay Janmanchi
tutorial:
  id: probability
output:
  learnr::tutorial:
    progressive: yes
    allow_skip:: yes
runtime: shiny_prerendered
description: 'Chapter 2 Tutorial: Probability'
---

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)

library(tidyverse)
library(primer.data)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 



```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

<!-- First, we no longer do line-by-line code. To the extent that we want to code here, the problems would be like: Use the code in the primer and AI to create a histogram of 100 rolls of 9 die, or something like that.

Second, it is not clear how much we should do with the three different types of distributions, or how we might do it. But, still, we should give it a try.

Third, make the Cardinal Virtue stuff much more like the template_tutorial. Maybe the Paris example still works . . .

Fourth, maybe we can create put all this together with by having the question be about die, and then going through all the usual steps . . . or maybe that is too weird and awkward and the Paris example is good . . . or maybe dice are good because it makes things like validity and representativeness easy to check off as OK?

Fifth, don't forget to load up tidyverse and any other packages you need.
-->


## Introduction
### 

This tutorial covers [Chapter 2: Probability](https://ppbds.github.io/primer/probability.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 




## Wisdom
###

*All we can know is that we know nothing. And that’s the height of human wisdom.* - Leo Tolstoy



### Exercise 1

In your own words, describe the key components of Wisdom for working on a data science problem.

```{r wisdom-1}
question_text(NULL,
	message = "Wisdom requires the creation of a Preceptor Table, an examination of our data, and a determination, using the concept of validity, as to whether or not we can (reasonably!) assume that the two come from the same population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 2

Define a Preceptor Table.

```{r wisdom-2}
question_text(NULL,
	message = "A Preceptor Table is the smallest possible table of data with rows and columns such that, if there is no missing data, it is easy to calculate the quantities of interest.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

One key aspect of a Preceptor Table is whether or not we need more than one potential outcome in order to calculate our estimand. For example, if we want to know the causal effect of exposure to Spanish-speakers on attitude toward immigration then we need a causal model, one which estimates that attitude for each person under both treatment and control. 

### Exercise 3

Describe the key components of Preceptor Tables in general. Use words like "units," "outcomes," and "covariates."

```{r wisdom-3}
question_text(NULL,
	message = "The rows of the Preceptor Table are the units. The outcome is at least one of the columns. If the problem is causal, there will be at least two (potential) outcome columns. The other columns are covariates. If the problem is causal, at least one of the covariates will be a treatment.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 4

<!-- need to include units/time -->

Write two sentences explaining a predictive model in your life. Include the one outcome variable of interest. 

```{r wisdom-4}
question_text(NULL,
	message = "A predictive model in my life can be seen as the money that I will potentially spend on groceries per week. I can take all of the data that I have from the previous weeks to estimate how much I will spend on groceries with a predictive model. Outcome: How much will I spend on groceries?",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

	
A predictive models has just one outcome column in its Preceptor Table.

### Exercise 5

Write two sentences explaining a causal model in your life. Include the two potential outcomes and the treatment variable. 

```{r wisdom-5}
question_text(NULL,
	message = "A causal model in my life can be seen as the money that I will spend on groceries based on whether I go to the gym to exercise. Two potential outcomes: dollars spent on groceries if I do go to the gym and dollars spent on groceries if I don't go to the gym. The treatment is going to the gym or not going to the gym. The following situation is an example of a causal model because there are two outcome columns in the Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Causal models aim to determine the effect of manipulating a specific variable on the outcome by comparing two or more potential outcomes for each unit. The difference between predictive models and causal models is that the former has one column for the outcome variable in the Preceptor Table and the latter has more than one column.

### Exercise 6

Scenario: You are an analyst at the mayor's office and want to find out what it will take for people to be more kind towards immigrants. You have previous data regarding individuals who were exposed to one of two possible conditions, and then their attitudes towards immigrants were recorded. One condition was waiting on a train platform near individuals speaking Spanish. The other was being on a train platform without Spanish-speakers. You are going to use this data and conduct your own analysis. You will give speeches on citizens through random assignment that includes a positive message regarding immigrants. Your hope is that the causal effect of those speeches is to make people be kinder. 

### 

Is this scenario a predictive model or a causal model? Explain why in two sentences.

```{r wisdom-6}
question_text(NULL,
	message = "This scenario is a causal model because there are multiple potential outcomes in the Preceptor Table. Causal models have more than one potential outcome while predictive models only have one outcome.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 7

Let's create a Preceptor Table by finding each column needed from the scenario. Write two sentences about what the rows are of the situation and how it relates to the scenario.

```{r wisdom-7}
question_text(NULL,
	message = "We are going to use three rows: Citizens, Treatments, and Potential Outcomes. We are concerned about each citizen and the data that each one of them will contain.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 8

What is the treatment for this problem?

```{r wisdom-8}
question_text(NULL,
	message = "Which citizens have heard the speech?",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```


### Exercise 9

Write two sentences about what the *potential outcomes* are of the situation and how it relates to the scenario. Remember this is a causal model which means that there will be multiple potential outcomes. 

```{r wisdom-9}
question_text(NULL,
	message = "Potential Outcomes: 
	           1. People who heard the speech and changed to be kind
	           2. People who heard the speech and changed to be not kind              3. People who didn't hear the speech and are kind
	           4. People who didn't hear the speech are not kind
	           These are the four potential outcomes at hand because of              the influence from the treatment that will change the                 outcome of the scenario.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 10

In your own words, define "validity" as we use the term.

```{r wisdom-10}
question_text(NULL,
	message = "Validity is the consistency, or lack thereof, in the columns of the data set and the corresponding columns in the Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

In order to consider the two datasets to be drawn from the same population, the columns from one must be have a valid correspondence with the columns in the other. 

### Exercise 11

Provide a reason why the *assumption of validity* might not hold with the data from immigrants with Spanish-speakers on the train to our scenario of giving citizens a speech to be more kind. Explain how that failure might impact the results.

```{r wisdom-11}
question_text(NULL,
	message = "The treatment in the data (Spanish speakers on a train platform) and the treatment in the Preceptor Table (a speech from the mayor about immigrants) are not similar enough that we can reasonably expect them to have the same causal effects. People are often annoyed by stangers but can react very differently to an elected official.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

*Validity*, if true (or at least reasonable), allows us to construct the Population Table.

## Justice
###

*The arc of the moral universe is long, but it bends toward justice.* - Theodore Parker


### Exercise 1

In your own words, name the four key components of Justice for working on a data science problem.

```{r justice-1}
question_text(NULL,
	message = "Justice concerns four topics: the Population Table, stability, representativeness, and unconfoundedness.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 2

In your own words, define a Population Table.

```{r justice-2}
question_text(NULL,
	message = "The Population Table includes a row for each unit/time combination in the underlying population from which both the Preceptor Table and the data are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 3

In your own words, define the assumption of "stability" when employed in the context of data science.

```{r justice-3}
question_text(NULL,
	message = "Stability means that the relationship between the columns in the Population Table is the same for three categories of rows: the data, the Preceptor Table, and the larger population from which both are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Stability is all about *time*. Is the relationship among the columns in the Population Table stable over time? In particular, is the relationship --- which is another way of saying "mathematical formula" --- at the time the data was gathered the same as the relationship at the (generally later) time references by the Preceptor Table.

### Exercise 4

Scenario: You are an analyst at the mayor's office and want to find out what it will take for people to be more kind towards immigrants. You have previous data regarding individuals who were exposed to one of two possible conditions, and then their attitudes towards immigrants were recorded. One condition was waiting on a train platform near individuals speaking Spanish. The other was being on a train platform without Spanish-speakers. You are going to use this data and conduct your own analysis. You will give speeches on citizens through random assignment that includes a positive message regarding immigrants. Your hope is that the causal effect of those speeches is to make people be kinder. 

### 

Provide one reason why the assumption of stability might not be true in this case.

```{r justice-4}
question_text(NULL,
	message = "The assumption of stability might not hold because the relationship with our data (Spanish speakers on a train platform) and Preceptor Table (a speech from the mayor about immigrants) are not similar enough. ",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 5

In your own words, define the assumption of "representativeness" when employed in the context of data science.

```{r justice-5}
question_text(NULL,
	message = "Representativeness, or the lack thereof, concerns two relationship, among the rows in the Population Table. The first is between the Preceptor Table and the other rows. The second is between our data and the other rows.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Ideally, we would like both the Preceptor Table *and* our data to be random samples from the population. Sadly, this is almost never the case.

### Exercise 6

Provide one reason why the assumption of representativeness might not be true in this case.

```{r justice-6}
question_text(NULL,
	message = "The assumption of representatives might not be true because the sample of our data (Spanish speakers on a train platform) and Preceptor Table (a speech from the mayor about immigrants) are not random enough.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 7

In your own words, define the assumption of "unconfoundedness" when employed in the context of data science.

```{r justice-7}
question_text(NULL,
	message = "Unconfoundedness means that the treatment assignment is independent of the potential outcomes, when we condition on pre-treatment covariates.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

This assumption is only relevant for causal models. We describe a model as "confounded" if this is not true.

### Exercise 8

In one sentence, provide a reason why the assumption of unconfoundedness would hold.

```{r justice-8}
question_text(NULL,
	message = "The assumption of unconfoundedness would hold because the sample of our data (Spanish speakers on a train platform) and Preceptor Table (a speech from the mayor about immigrants) are part of a causal model and we are randomly assigning treatment to the citizens.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Unconfoundedness is related to the absence of confounding variables that may bias the relationship between the outcome variable and covariates. It implies that there are no hidden factors influencing both the treatment (if applicable) and the outcome.


## Courage
###

*Courage is the commitment to begin without any guarantee of success.* - Johann Wolfgang von Goethe

### Exercise 1

In your own words, describe the components of the virtue of Courage for analyzing data.

```{r courage-1}
question_text(NULL,
	message = "Courage begins with the exploration and testing of different models. It concludes with the creation of a data generating mechanism.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```


## Temperance
### 

*Temperance to be a virtue must be free, and not forced.* - Philip Massinger

### Exercise 1

In your own words, describe the use of Temperance in finishing your data science project.

```{r temperance-1}
question_text(NULL,
	message = "Temperance uses the data generating mechanism to answer the questions with which we began. Humility reminds us that this answer is always a lie. We can also use the DGM to calculate many similar quantities of interest, displaying the results graphically.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```


## Summary
### 

This tutorial covered [Chapter 2: Probability](https://ppbds.github.io/primer/probability.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/).  


```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
