---
title: 'Visualization: Basic Plots'
author: Kevin Xu
tutorial:
  id: visualization-basic-plots
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: Simply tidyverse introdution and an overview of basic plots.
---

<!-- Tutorial should take about 90 minutes. -->

<!-- Fix tutorial questions to follow current guidance. -->

<!-- Add geom_line(). Use temperate, I think. || DONE-->

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(lubridate)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

temp_modified <- temperature %>% 
  mutate(year = as.character(year)) %>% 
  mutate(month = as.character(month)) %>% 
  mutate(date = ym(paste(year, month,sep = "-")), .before = 1) %>%
  select(-year, -month)
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

## Basic Tidyverse

### 

You will practice the basic syntax and terminology of coding in RStudio. You will learn about the basic ways of storing data in R, vectors and tibbles.

### Exercise 1

Before you start coding, you must load the packages you are going to use. In the code chunk below, use the function `library()` to load the `tidyverse` package.

```{r basic-tidyverse-1, exercise = TRUE}

```

```{r basic-tidyverse-1-hint-1, eval = FALSE}
Place tidyverse inside the library() function.
```

`tidyverse` is a collection of R packages used by data scientists. Learn more about them [here](https://www.tidyverse.org/).

<!-- DK Add https://www.tidyverse.org/-->
<!-- KX: DONE -->

### Exercise 2

If you are ever stuck while coding, R has **help pages**. Let's say we want to know what the function `sqrt()` does. Open the help page for `sqrt()` by typing `?sqrt` below.

```{r basic-tidyverse-2, exercise = TRUE}

```

### 

You can also use the `?` to open descriptions of data sets.

### Exercise 3

Recall **code comments** are text placed after a `#` symbol. Nothing will be run after a `#` symbol, which is useful if you want to write human readable comments in your code..

Press Run Code. Afterwards, delete the `#` and re-run the chunk. You should see a result.

```{r basic-tidyverse-3, exercise = TRUE}
# sqrt(144)
```

### Exercise 4

Let's save the values of `sqrt(144)` to an object named `results`. Remember to use the assignment operator `<-`.

```{r basic-tidyverse-4, exercise = TRUE}

```

```{r basic-tidyverse-4-hint-1, eval = FALSE}
results <- sqrt(144)
```

### Exercise 5

A **vector** is a sequence of elements that are created using the `c()` function. Create a vector that contains the integers from one to ten.

```{r basic-tidyverse-5, exercise = TRUE}

```

```{r basic-tidyverse-5-hint-1, eval = FALSE}
Type the integers 1 through 10, separated by commas, inside the function c().
```

`c()` stands for **c**ombine.

### Exercise 6

If your vector contains a sequence of contiguous integers, you can create it with the `:` shortcut. Run `1:10` in the chunk below.

```{r basic-tidyverse-6, exercise = TRUE}

```

### Exercise 7

You can extract any element of a vector by placing a pair of brackets `[ ]` behind the vector. Inside the brackets, place the 1-based index of the element that you'd like to extract. For example, `vec[3]` would return the third element of the vector named `vec`.

The code below assigns a vector to an object named `vec`. Use the chunk below to extract the fourth element of `vec`.

```{r basic-tidyverse-7, exercise = TRUE}
vec <- c(1, 2, 4, 8, 16)
```

```{r basic-tidyverse-7-hint-1, eval = FALSE}
vec[...]
```

### Exercise 8

You can also use `[ ]` to extract multiple elements of a vector. Place the vector `c(1,2,5)` between the brackets below. What does R return?

```{r basic-tidyverse-8, exercise = TRUE}
vec <- c(1, 2, 4, 8, 16)
vec[]
```

### Exercise 9

If the elements inside your vector have names, you can extract them by name. To do so, place a name or vector of names in the brackets behind a vector. Surround each name with quotation marks, e.g. `vec2[c("alpha", "beta")]`.

Below the given code, extract the element named "gamma" from the vector below.

```{r basic-tidyverse-9, exercise = TRUE}
vec2 <- c(alpha = 1, beta = 2, gamma = 3)

```

```{r basic-tidyverse-9-hint-1, eval = FALSE}
Because the names are characters, make sure to use quotation marks inside the brackets, i.e. vec2["..."].
```

### Exercise 10

Data frames, also referred to as "tibbles", are spreadsheet-type data sets. R comes with many toy **data sets** to explore.

### 

In Data Science, it's always a good idea to explore the data before you use it. You can simply examine a dataset by typing its name. Let's examine the contents of `iris` data set. Type `iris` in the line below.

```{r basic-tidyverse-10, exercise = TRUE}

```

### Exercise 11

Now use `glimpse()` to look at the `iris` data set. Additionally, to learn more about the function, you can run `?glimpse()`.

```{r basic-tidyverse-11, exercise = TRUE}

```

```{r basic-tidyverse-11-hint-1, eval = FALSE}
Place iris inside the glimpse() function.
```

### Exercise 12

The `$` operator is a tool for extracting columns from data frames as vectors. Extract the `year` column of the `mpg` data frame using the `$` operator.

```{r basic-tidyverse-12, exercise = TRUE}

```

```{r basic-tidyverse-12-hint-1, eval = FALSE}
data_f$...
```

```{r basic-tidyverse-12-hint-2, eval = FALSE}
See the Primer for guidance!
```

### 

Columns extracted with the `$` are vectors and can be often used in functions where an "extracted" tibble column would not work. Every column in a tibble can be extracted as a vector.

## `geom_point()`

### 

Scatterplots allow you to visualize the relationship between two numerical variables.

### 

Let's create the following scatterplot from the `mpg` dataset, which provides measurements of attributes from various car models.

```{r scat-p}
scat_p <- ggplot(data = mpg, 
                 mapping = aes(x = displ, 
                               y = hwy)) +
  geom_point(alpha = 0.5, color = "steelblue") +
  labs(title = "Measurements for Engine Displacement and Highway Fuel Efficiency of Select Car Models",
       subtitle = "Cars with greater enginer displacement are less fuel efficient",
        x = "Engine Displacement (L)",
        y = "Highway Efficiency (mpg)", 
       caption = "EPA (2008)")

scat_p
```

<!-- KX: using mpg dataset -->

### Exercise 1

First, let's `view()` the data set used above called `mpg`. What are the names of the two variables we will use?

```{r geompoint-1, exercise = TRUE}

```

```{r geompoint-1-hint-1, eval = FALSE}
view(...)
```

### 

There is a chance that `view()` may not work for you when you hit **Run Code**, depending on your computer set up, from within this tutorial. Just make sure that it works from a regular RStudio session and press on.

We are going to use `displ` and `hwy` to create this plot.

### Exercise 2

Within `ggplot()`, set `data` to `mpg`.

```{r geompoint-2, exercise = TRUE}

```

```{r geompoint-2-hint-1, eval = FALSE}
ggplot(data = ...)
```

### 

ggplot() initializes a ggplot object. Your output should be an empty canvas.

### Exercise 3

Now, map `displ` to the x-axis and `hwy` to the y-axis.

```{r geompoint-3, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geompoint-3-hint-1, eval = FALSE}
ggplot(data = ..., 
       mapping = aes(
         x = ...,
         y = ...))
```

### 

Anything included in `aes()` brings some information from the data in our tibble onto the graph. Elsewhere in ggplot and its layers, we change the appearance of the graph without using information from our data.

### Exercise 4

Let's now add the layer `geom_point()`.

```{r geompoint-4, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geompoint-4-hint-1, eval = FALSE}
Remember when you add a layer you use +. 
```

```{r geompoint-4-hint-2, eval = FALSE}
ggplot(data = ..., 
       mapping = aes(
         x = ...,
         y = ...)) +
  geom_point()
```

### 

`geom_*` functions (such as `geom_point()`) add ggplot objects as an additional layer to the base ggplot. This allows us to visualize the data.

### Exercise 5

The following code uses the `mpg` tibble to create a scatterplot that displays 126 points, however, it visualizes a data set that contains 234 points. Because many points share similar values, this causes individual data points to be hidden behind other points. This is also known as **overplotting.**

One method to fight overplotting is to make each point **semi-transparent**. The code chunk below provides the code used to create the graph above. Change the transparency of the points by setting `alpha` equal to 0.5 within `geom_point()`.

```{r geompoint-5, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geompoint-5-hint-1, eval = FALSE}
ggplot(data = mpg, 
       mapping = aes(x = displ, y = hwy)) +
  geom_point(alpha = ...)
```

### Exercise 6

Now, also within `geom_point()`, set `color` equal to `"steelblue"`.

```{r geompoint-6, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geompoint-6-hint-1, eval = FALSE}
ggplot(data = mpg, 
       mapping = aes(x = displ, y = hwy)) +
  geom_point(alpha = ..., color = "...")
```

### 

Both color and alpha only change the appearance of the graph and do not add new information from the data. Thus, both are arguments within the `geom` and are not nested within an `aes`, unlike when we changed `color` to the variable `Species` above.

### Exercise 7

Now, use `labs()` to add a title and axis labels to the graph. Set the `title` to `"Measurements for Engine Displacement and Highway Fuel Efficiency of Select Car Models"` and the `subtitle` to `"Cars with greater enginer displacement are less fuel efficient"`. To label the the axes, set `x` to `"Engine Displacement (L)"` and `y` to `"Highway Efficiency (mpg)"`. Set the `caption` to `"EPA (2008)"`.

```{r geompoint-7, exercise = TRUE }

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geompoint-7-hint-1, eval = FALSE}
Remember to add a layer with the function labs()
```

```{r geompoint-7-hint-2, eval = FALSE}
... +
  labs(title = "...",
       subtitle = "...",
       x = "...",
       y = "...",
       caption = "...") 
```

Reminder: This is what our graph should look like.

```{r show-scat-p}
scat_p
```

### 

Good work.

## `geom_jitter()`

### 

We can also use `geom_jitter()` to fight overplotting. It plots a scatterplot and then adds a small amount of random noise to each point in the plot.

We will now create a plot with the `trains` dataset to implement this solution to overplotting.

### Exercise 1

To better understand the data, read into the dataset by running `?trains`. Take notice of the variable type for `att_start` and `att_end`.

```{r geomjitter-1, exercise = TRUE}

```

### 

<!-- What do I pay attention to? -->

### Exercise 2

Run `view(trains)` to further explore the data.

```{r geomjitter-2, exercise = TRUE}

```

### 

<!-- Notice something! -->

### Exercise 3

Run the code below that creates a scatterplot of `trains` with overplotting.

```{r geomjitter-3, exercise = TRUE}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end)) +
  geom_point()
```

### Exercise 4

Now, let's replace `geom_point()` with `geom_jitter()`. Try running this chunk multiple times. How does the noise affect the plot?

```{r geomjitter-4, exercise = TRUE}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end)) + 
  geom_point()
```

### Exercise 5

Within `geom_jitter()`, set `width` to `.2` to adjust the amount the points are jittered.

```{r geomjitter-5, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geomjitter-5-hint-1, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end)) +
  geom_jitter(width = ...)

```

### Exercise 6

Within `aes()`, set the `color` aesthetic to the `party` variable.

```{r geomjitter-6, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geomjitter-6-hint-1, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end, 
                     color = ...)) +
  geom_jitter(width = .2)
```

### Exercise 7

Now use `labs()` to set an appropriate title, subtitle, axes labels, and caption for the graph.

```{r geomjitter-7, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geomjitter-7-hint-1, eval = FALSE}
... +
  labs(title = "...",
       subtitle = "..."
       x = "...",
       y = "...",
       caption = "...")
```

Here is an example of what the completed graph should look like:

```{r show-jitter-p}
 jitter_p <- ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end, 
                     color = party)) +
  geom_jitter(width = .2) +
  labs(title = "Starting and Ending Attitudes of Participants", 
       subtitle = "Democrats have a wide range of starting and Ending Attitudes", 
       x = "Starting Attitude", 
       y = "Ending Attitude", 
       caption = "Enos (2014)")

jitter_p
```

### 

Good work.

## `geom_smooth()`

We can add a regression line to our scatterplots using `geom_smooth()`

### Exercise 1

Run the code below to see the jittered scatterplot we started with in the `geom_jitter()` section.

```{r geomsmooth-1, exercise = TRUE}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end)) +
  geom_jitter(width = .2)
```

### Exercise 2

Copy/paste the code from above. Add the layer `geom_smooth()` to the graph. Remember you are adding a layer so you need to include `+`.

```{r geomsmooth-2, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geomsmooth-2-hint-1, eval = FALSE}
... + 
  geom_smooth()
```

### Exercise 3

Awesome, but see that message R gives us? Let's try setting the 'method' to "lm" inside `geom_smooth()`.

```{r geomsmooth-3, exercise = TRUE, warning = FALSE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geomsmooth-3-hint-1, eval = FALSE}
Remember to put "lm" in quotes within geom_smooth()
```

```{r geomsmooth-3-hint-2, eval = FALSE}
... +
  geom_smooth(method = "...")
```

### 

If you do not specify a method, R will give you a warning that you have not done so. By default, the method is set to `"loess", which is short for LOcal regrESSion, produces a non-linear trend curve. `"lm"` stands for Linear Model, thus giving us a linear trend curve. 

### Exercise 4

Great, but we still get a message! Set the `formula` argument within geom_smooth() to `y ~ x`. Also set `se` to FALSE to get rid of the grey area surrounds the trendline.

```{r geomsmooth-4, exercise = TRUE}


```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geomsmooth-4-hint-1, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end)) +
  geom_jitter(width = .2)  +
    geom_smooth(method = "lm", formula = y ~ x, se = FALSE)
```

### 

If you do not specify a formula, R will also give you a warning that you have not done so. By default, the formula to use in smoothing function is set to `y ~ x`. Setting the `se` parameter determines whether or not to display the confidence interval around smooth.

### Exercise 5

Now use `labs()` to set an appropriate title, subtitle, axes labels, and caption for the graph.

```{r geomsmooth-5, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geomsmooth-5-hint-1, eval = FALSE}
... +
  labs(title = "...",
       subtitle = "..."
       x = "...",
       y = "...",
       caption = "...")
```

Reminder: Your graph should look like this.

```{r show-smooth-p}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end)) +
  geom_jitter(width = .2)  +
    geom_smooth(method = "lm", formula = y ~ x, se = FALSE) +
  labs(title = "Starting and Ending Attitudes of Participants", 
       subtitle = "Most participants had similar starting and ending attitudes",
       x = "Starting Attitude", 
       y = "Ending Attitude", 
       caption = "Enos (2014)")
```

### 

Good work.

## `geom_line()`

A line graph is a plot that visualizes the relationship between two numerical variables when there is a sequential nature to the variable on the x-axis, also called the independent variable.

Let's create the following line graph via the `temperature` dataset. We will use a modified version of the dataset, `temp_modified`. 
<!-- KX: since year and month variables need to be put together -->
```{r make-line-p}
temp_modified_plot <- temp_modified %>% 
  ggplot(aes(x = date, y = globe)) +
    geom_line() +
    geom_smooth(method = "loess", formula = y ~ x, se = FALSE) +
    labs(title = "Deviation in Annual Average Global Temperature (°C) since 1978",
         subtitle = "Periodic cycles of temperature changes trend upward",
         x = "Year",
         y = "Global Average Deviation (°C)")

temp_modified_plot
```

### Exercise 1

Let's first explore the `temperature` dataset. Access its help page by running `?temperature`. What value is being measured for each region?

```{r geomline-1, exercise = TRUE}

```

```{r geomline-1-hint-1, eval = FALSE}
?temperature
```

### 

Notice that the monthly temperature deviations relative to the average temperature is being recorded, rather than the average monthly temperature. It's also good to note that values are being measured in °C.

### Exercise 2

Now run the `glimpse()` function on `temp_modified`. Can you find the difference?

```{r geomline-2, exercise = TRUE}

```

```{r geomline-2-hint-1, eval = FALSE}
glimpse(...)
```

### 

`temp_modified` combines the `year` and `month` variables from the original dataset into a single variable named `date`. This will make plotting easier for us later. You will learn the skills to do this yourself in later tutorials.

### Exercise 3

Within `ggplot()` set `data` to `temp_modified`.

```{r geomline-3, exercise = TRUE}

```

```{r geomline-3-hint-1, eval = FALSE}
ggplot(...)
```

### Exercise 4

Within `ggplot()`, now set the argument `mapping` to equal `aes()`. Within `aes()`, map `date` to the x-axis and `globe` to the y-axis.

```{r geomline-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r geomline-4-hint-1, eval = FALSE}
ggplot(data = `temp_modified`, aes(x = ..., y = ...))
```

### 

Because time is an inherently sequential value, it will often be the independent variable in line graphs.

### Exercise 5

Now add a call to the `geom_line()` function.

```{r geomline-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r geomline-5-hint-1, eval = FALSE}
ggplot(data = `temp_modified`, aes(x = date, y = globe)) + 
  ...
```

### 

Congratulations on your first line plot! This graph could stand on its own, but a trend line could be helpful to us here.

### Exercise 6

Now add a call to the `geom_smooth()` function. 

```{r geomline-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r geomline-6-hint-1, eval = FALSE}
ggplot(data = `temp_modified`, aes(x = date, y = globe)) + 
  geom_line() +
  ...
```

### 

Like in the previous section, notice the warning message in the R Console window because we didn't specify certain parameters.

### Exercise 7

Set the `method` parameter to `"loess"`, `formula` to `y ~ x`, and `se` to `FALSE`.

```{r geomline-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r geomline-7-hint-1, eval = FALSE}
ggplot(data = `temp_modified`, aes(x = date, y = globe)) + 
  geom_line() +
  geom_smooth(method = "loess", formula = y ~ x, se = FALSE)
```

### 

### Exercise 8

Now use `labs()` to set an appropriate title, subtitle, axes labels, and caption for the graph.

```{r geomline-8, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r geomline-8-hint-1, eval = FALSE}
... +
  labs(title = "...",
       subtitle = "..."
       x = "...",
       y = "...",
       caption = "...")
```

Reminder: This is what our graph should look like.

```{r show-line-p}
temp_modified_plot
```

### 

Good Work.

## `geom_histogram()`

A histogram is a plot that visualizes the distribution of a numerical variable.

Let's create the following histogram via the `qscores` dataset.

```{r make-hist-p}
hist_p <- ggplot(data = qscores, 
                 mapping = aes(x = rating)) +
  geom_histogram(bins = 5, 
                 color = "white", 
                 fill = "coral") + 
  labs(title = "Histogram of Student Ratings of Harvard Classes", 
       subtitle = "Ratings of 1 and 2 are very rare", 
       x = "Rating", 
       y = "Count", 
       caption = "Source: Harvard Q-Guide (2018-2019)")

hist_p
```

### Exercise 1

As always, let's first explore the data. Run `?qscores`. Which variable(s) would be most useful for making a histogram of student ratings?

```{r geomhistogram-1, exercise = TRUE}

```

### Exercise 2

Within `ggplot()`, set `data` to `qscores`.

```{r geomhistogram-2, exercise = TRUE}

```

```{r geomhistogram-2-hint-1, eval = FALSE}
ggplot(data = ...,)
```

### 

ggplot() initializes a ggplot object. Your output should be an empty canvas.

### Exercise 3

Now, Map `rating` to the x-axis to see the distribution of Harvard course ratings.

```{r geomhistogram-3, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geomhistogram-3-hint-1, eval = FALSE}
ggplot(data = ..., 
       mapping = aes(x = ...))
```

### Exercise 4

Let's now add the layer `geom_histogram()`.

```{r geomhistogram-4, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geomhistogram-4-hint-1, eval = FALSE}
Remember when you add a layer you use +. 
```

```{r geomhistogram-4-hint-2, eval = FALSE}
ggplot(data = ..., 
       mapping = aes(x = ...)) +
  geom_histogram()
```

### 

`geom_histogram()` has a default y-axis which is the count for different values that occur in the x-axis variable.

### Exercise 5

Add white vertical borders demarcating the bins by setting `color` equal to `"white"` within `geom_histogram()`.

```{r geomhistogram-5, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geomhistogram-5-hint-1, eval = FALSE}
ggplot(data = qscores, 
       mapping = aes(x = rating)) +
  geom_histogram(color = ...)
```

### 

For plots that are not points or lines, the argument `color` only changes the outline.

### Exercise 6

Change the color of the bars by setting `fill` equal to `"coral"` within `geom_histogram()`.

```{r geomhistogram-6, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geomhistogram-6-hint-1, eval = FALSE}
ggplot(data = qscores, 
       mapping = aes(x = rating)) +
  geom_histogram(color = "white",
                 fill = "coral")
```

### Exercise 7

Specify the number of bins to be 5 using the `bins` argument in `geom_histogram()`.

```{r geomhistogram-7, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geomhistogram-7-hint-1, eval = FALSE}
ggplot(data = qscores, 
       mapping = aes(x = rating)) +
  geom_histogram(color = "white",
                 fill = "coral",
                 bins = 5)
```

### 

Notice how the values of `count` increased when we decreased the number of `bins`. This is because, more ratings are included in a single bin (e.g. ratings of 4.0-4.9 all included in the fourth bin). By default, geom_histogram has 30 bins.

### Exercise 8

Now use `labs()` to set an appropriate title, subtitle, axes labels, and caption for the graph.

```{r geomhistogram-8, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geomhistogram-8-hint-1, eval = FALSE}
... +
  labs(title = "...",
       subtitle = "..."
       x = "...",
       y = "...",
       caption = "...")
```

Reminder: This is what our graph should look like.

```{r show-hist-p}
hist_p
```

### 

Good work.

## `geom_density()`

`geom_density()` is used to make a density plot, a smoothed version of a histogram. It is a useful alternative to the histogram that data with a smooth distribution.

### 

Let's create the following density plot using the `cces` dataset.

```{r make-dens-p}
dens_p <- ggplot(data = cces, 
                 mapping = aes(x = age, 
                               color = ideology, 
                               fill = ideology)) +
  geom_density(alpha = .1) +
  labs(title = " Distribution of Age by Ideology", 
       subtitle = "Most young people are not sure of their ideology",
       x = "Age", 
       y = "Density",
       caption = "Kuriwaki (2020)")

dens_p
```

### Exercise 1

Let's first explore the data. Run `?cces`. Can you find the two variables that would help us to identifying the age and ideology of a respondent?

```{r geomdensity-1, exercise = TRUE}

```

### Exercise 2

Use the `cces` data set in the `primer.data` package. Within `ggplot()`, set `data` to `cces`.

```{r geomdensity-2, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geomdensity-2-hint-1, eval = FALSE}
ggplot(data = ...)
```

### 

ggplot() initializes a ggplot object. Your output should be an empty canvas.

### Exercise 3

Let's now map the variable `age` to the `x`argument inside `aes()`.

```{r geomdensity-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">

```{r geomdensity-3-hint-1, eval = FALSE}
ggplot(data = cces, 
       mapping = aes(x = ...))
```

### Exercise 4

Let's now add the layer `geom_desnity()`

```{r geomdensity-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">

```{r geomdensity-4-hint-1, eval = FALSE}
ggplot(data = cces, 
       mapping = aes(x = ...)) +
  geom_density()
```

### 

This plot displays a density distribution for all ideologies by age. We will split this distribution by ideology next.

### Exercise 5

Now within `aes`, set `color` and `fill` equal to the variable `ideology`.

```{r geomdensity-5, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geomdensity-5-hint-1, eval = FALSE}
ggplot(data = cces, 
       mapping = aes(x = ..., 
                     color = ..., 
                     fill = ...)) + 
  geom_density()
```

### 

We are getting closer! Right now, the distributions of one ideology are covering others because their `fill` is 100% opaque.

### Exercise 6

Now set the `alpha` argument in `geom_density()` to 0.1.

```{r geomdensity-6, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geomdensity-6-hint-1, eval = FALSE}
... + 
  geom_density(alpha = 0.1)
```

### Exercise 7

Finally set an appropriate title, subtitle, axes labels, and caption for the graph.

```{r geomdensity-7, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geomdensity-7-hint-1, eval = FALSE}
... +
  labs(title = "...",
       subtitle = "..."
       x = "...",
       y = "...",
       caption = "...")
```

Reminder: Your graph should look something like this.

```{r show-dens-p}
dens_p
```

### 

Good work.

## `geom_bar()`

A barplot is a plot that visualizes the distribution of a categorical variable.

Let's create the following barplot using the `trains` dataset.

```{r make-bar-p}
bar_p <- ggplot(data = trains, 
       mapping = aes(x = treatment, 
                     fill = party)) +
  geom_bar(position = "dodge") +
  labs(title = "Democrats and Republicans in Treated and Control Groups",
       subtitle = "Few Republicans in both treated and control groups", 
       x = "Treatment", 
       y = "Count",
       caption = "Enos(2014)")

bar_p
```

### Exercise 1

Let's first explore the data. Run `?trains`.

```{r geombar-1, exercise = TRUE}

```

Consider which variable(s) would be most useful for making a barplot of treatment groups by party.

### Exercise 2

Use the `trains` data set in the `primer.data` package. Within `ggplot()`, set `data` to `trains`.

```{r geombar-2, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geombar-2-hint-1, eval = FALSE}
ggplot(data = ...)
```

### 

ggplot() initializes a ggplot object. Your output should be an empty canvas.

### Exercise 3

Let's now map the variable `treatment` to the `x`argument inside `aes()`.

```{r geombar-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">

```{r geombar-3-hint-1, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = ...))
```

### Exercise 4

Let's now add the layer `geom_bar()`

```{r geombar-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">

```{r geombar-4-hint-1, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = ...)) +
  geom_bar()
```

### 

This plot breaks down the count of the study by treatment group, does not split these groups by party. We will do this next.

### Exercise 5

Let's now also map the variable `party` to the `fill` argument.

```{r geombar-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">

```{r geombar-5-hint-1, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = treatment, 
                     fill = ...)) +
  geom_bar()
```

### 

We use the `fill` argument instead of the `color` argument because we want to color the shape and not its borders.

Now, we can see the composition of each treatment group by party. Notice that the party bars are stacked.

### Exercise 6

Let's make our graph a side-by-side barplot. Set `position` to "dodge" in `geom_bar()`.

```{r geombar-6, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geombar-6-hint-1, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = treatment, 
                     fill = party)) +
  geom_bar(position = ...)
```

### 

By default `position` is set to `"stack"`. `"dodge"` puts different colors side by side.

### Exercise 7

Now use `labs()` to set an appropriate title, subtitle, axes labels, and caption for the graph.

```{r geombar-7, exercise = TRUE}

```

<button onclick="transfer_code(this)">

Copy previous code

</button>

```{r geombar-7-hint-1, eval = FALSE}
... +
  labs(title = "...",
       subtitle = "..."
       x = "...",
       y = "...",
       caption = "...")
```

Reminder: This is what our graph should look like.

```{r show-bar-p}
bar_p
```

### 

Good work.

```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
