---
title: "Visualization A || LOCAL COPY"
tutorial:
  id: "visualization-a"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Chapter 1 Tutorial Part A"
---

<!-- Take ownership. Change anything you like. What are the most important skills to practice? -->

<!-- Put <button onclick = "transfer_code(this)">Copy previous code</button> in the correct places. -->

<!-- Add some data exploration questions to start of each new plotting. view(), glimpse(), summary() and whatever.  -->

<!-- Make each question as small as possible. -->

<!-- Maybe don't use iris.  -->

<!-- Old comments: -->

<!-- DK: Right now, this tutorial takes about 48 minutes. This is shorter than the other Visualization tutorials: 84, 86 and 68 minutes. At the least, we should increase the length of D. 90 minutes is a good target. Should we increase A? Pro is that it should be 90 minutes too.  -->


<!-- NL: Thoughts- A. Combine first two sections to create section that starts with vectors and builds towards understanding a data frame columns as vectors. Students should make their own tibble? B. Combine geom_point(), geom_jitter(), and geom_smooth(), have students understand more about aes by demonstrating fill with data vs with color. C. Combine geom_bar(), geom_histogram(), and geom_density(), introduce aes(y = after_stat(count/sum(count))) as transition from histogram to density and development. Yes! But not this week. [I went ahead and did A] --> 

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```



```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```


## Basic Tidyverse
###

You will practice the basic syntax and terminology of coding in RStudio. You will learn about the basic ways of storing data in R, vectors and tibbles. 

### Exercise 1

Before you start coding, you must load the packages you are going to use. In the code chunk below, use the function `library()` to load the `tidyverse` package.

```{r howtc-1, exercise = TRUE}

```

```{r howtc-hint, eval = FALSE}
Place tidyverse inside the library() function.
```

### Exercise 2

If you are ever stuck while coding, R has **help pages**. Let's say we want to know what the function `sqrt()` does. Open the help page for `sqrt()` by typing `?sqrt()` below.

```{r howtc-2, exercise = TRUE}

```

### 

You can also use the `?` to open descriptions of data sets. 

### Exercise 3

Recall **code comments** are text placed after a `#` symbol. Nothing will be run after a `#` symbol, which is useful if you want to write human readable comments in your code..

Press Run Code. Afterwards, delete the `#` and re-run the chunk. You should see a result.

```{r howtc-3, exercise = TRUE}
# sqrt(144)
```

### Exercise 4

Let's save the values of `sqrt(144)` to an object named `results`. Remember to use the assignment operator `<-`. 

```{r howtc-4, exercise = TRUE}

```

```{r howtc-4-hint, eval = FALSE}
results <- sqrt(144)
```

### Exercise 5

A **vector** is a sequence of elements that are created using the `c()` function. Create a vector that contains the integers from one to ten.

```{r howtc-5, exercise = TRUE}

```

```{r howtc-5-hint, eval = FALSE}
Type the integers 1 through 10, separated by commas, inside the function c().
```

`c()` stands for **c**ombine. 

### Exercise 6

If your vector contains a sequence of contiguous integers, you can create it with the `:` shortcut. Run `1:10` in the chunk below.

```{r howtc-6, exercise = TRUE}

```

### Exercise 7

You can extract any element of a vector by placing a pair of brackets `[ ]` behind the vector. Inside the brackets, place the 1-based index of the element that you'd like to extract. For example, `vec[3]` would return the third element of the vector named `vec`.

The code below assigns a vector to an object named `vec`. Use the chunk below to extract the fourth element of `vec`.

```{r howtc-7, exercise = TRUE}
vec <- c(1, 2, 4, 8, 16)
```

```{r howtc-7-hint, eval = FALSE}
vec[...]
```

### Exercise 8

You can also use `[ ]` to extract multiple elements of a vector. Place the vector `c(1,2,5)` between the brackets below. What does R return?

```{r howtc-8, exercise = TRUE}
vec <- c(1, 2, 4, 8, 16)
vec[]
```

### Exercise 9

If the elements inside your vector have names, you can extract them by name. To do so, place a name or vector of names in the brackets behind a vector. Surround each name with quotation marks, e.g. `vec2[c("alpha", "beta")]`.

Below the given code, extract the element named "gamma" from the vector below.

```{r howtc-9, exercise = TRUE}
vec2 <- c(alpha = 1, beta = 2, gamma = 3)

```

```{r howtc-9-hint, eval = FALSE}
Because the names are characters, make sure to use quotation marks inside the brackets, i.e. vec2["..."].
```

### Exercise 10

Data frames, also referred to as "tibbles", are spreadsheet-type data sets. R comes with many toy **data sets** to explore.

###

In Data Science, it's always a good idea to explore the data before you use it. You can simply examine a dataset by typing its name. Let's examine the contents of `iris` data set. Type `iris` in the line below.

```{r howtc-10, exercise = TRUE}

```

### Exercise 11

Now use `glimpse()` to look at the `iris` data set. Additionally, to learn more about the function, you can run `glimpse()`.

```{r howtc-11, exercise = TRUE}

```

```{r howtc-11-hint, eval = FALSE}
Place iris inside the glimpse() function.
```

### Exercise 12

The `$` operator is a tool for extracting columns from data frames as vectors. Extract the `year` column of the `mpg` data frame using the `$` operator.

```{r howtc-12, exercise = TRUE}

```

```{r howtc-12-hint-1, eval = FALSE}
data_f$...
```

```{r howtc-12-hint-2, eval = FALSE}
See the Primer for guidance!
```

### 

Columns extracted with the `$` are vectors and can be often used in functions where an "extracted" tibble column would not work. Every column in a tibble can be extracted as a vector. 

## `geom_point()` 


Scatterplots allow you to visualize the relationship between two numerical variables. 

###

Let's create the following scatterplot from the `iris` dataset, which compares the sepal (a part of a flower) lengths and widths for three different iris species.

```{r scat-p}
scat_p <- ggplot(data = iris, 
                 mapping = aes(x = Sepal.Width, 
                               y = Sepal.Length, 
                              color = Species)) +
  geom_point() +
  labs(title = "Measurements for Different Species of Iris",
       subtitle = "Virginica has the longest sepals",
        x = "Sepal.Width",
        y = "Sepal.Length", 
       caption = "Fisher (1936)")

scat_p
```

###

### Exercise 1

###

First, let's `view()` the data set used above called `iris`. Can you identify which columns will be relevant in creating our plot?

```{r gp-1, exercise = TRUE}

```

```{r gp-1-hint, eval = FALSE}
view(...)
```

###

There is a chance that `view()` may not work for you when you hit **Run Code**, depending on your computer set up, from within this tutorial. Just make sure that it works from a regular RStudio session and press on.

### Exercise 2

Within `ggplot()`, set `data` to `iris`. 

```{r gp-2, exercise = TRUE}

```

```{r gp-2-hint-1, eval = FALSE}
ggplot(data = ...)
```

###

ggplot() initializes a ggplot object. Your output should be an empty canvas.

### Exercise 3

Now, map `Sepal.Width` to the x-axis and `Sepal.Length` to the y-axis. 
```{r gp-3, exercise = TRUE}

```
<button onclick = "transfer_code(this)">Copy previous code</button>
```{r gp-3-hint, eval = FALSE}
ggplot(data = ..., 
       mapping = aes(
         x = ...,
         y = ...))
```

### Exercise 4
Let's now add the layer `geom_point()`.
```{r gp-4, exercise = TRUE}

```
<button onclick = "transfer_code(this)">Copy previous code</button>
```{r gp-4-hint-1, eval = FALSE}
Remember when you add a layer you use +. 
```

```{r gp-4-hint-2, eval = FALSE}
ggplot(data = ..., 
       mapping = aes(
         x = ...,
         y = ...)) +
  geom_point()
```
<!-- KX: broke up section; how is the flow? -->
### Exercise 5

Congratulations on your first plot! Now we want to add a `color` aesthetic based on the different species of the iris flower. Set the argument `color` to `Species` inside the `aes()` function.

```{r gp-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r gp-5-hint, eval = FALSE}
ggplot(data = iris, 
       mapping = aes(x = Sepal.Width, 
                     y = Sepal.Length, 
                     color = ...)) 
```

###

Anything included in `aes()` brings some information from the data in our tibble onto the graph. Elsewhere in ggplot and its layers, we change the appearance of the graph without using information from our data.

### Exercise 6

Now, use `labs()` to add a title and axis labels to the graph. Set the `title` to `"Measurements for Different Species of Iris"` and the `subtitle` to `"Virginica has the longest sepals"`. To label the the axes, set `x` to  `"Sepal.Width"` and `y` to `"Sepal.Length"`. Set the `caption` to `"Fisher (1936)"`.  

```{r gp-6, exercise = TRUE }

```
<button onclick = "transfer_code(this)">Copy previous code</button>
```{r gp-6-hint-1, eval = FALSE}
Remember to add a layer with the function labs()
```
 
```{r gp-6-hint-2, eval = FALSE}
... +
  labs(title = "...",
       subtitle = "...",
       x = "...",
       y = "...",
       caption = "...") 
```

Reminder: This is what our graph should look like.

```{r show-scat-p}
scat_p
```       

### Exercise 7

The following code uses the `mpg` tibble to create a scatterplot that displays 126 points, however, it visualizes a data set that contains 234 points. Because many points share similar values, this causes individual data points to be hidden behind other points. This is also known as **overplotting.**

Run the code below to see a scatterplot via the `mpg` dataset. 

```{r gp-7, exercise = TRUE}
ggplot(data = mpg, 
       mapping = aes(x = displ, 
                     y = hwy)) +
  geom_point()
```

### Exercise 8

One method to fight overplotting is to make each point **semi-transparent**. The code chunk below provides the code used to create the graph above. Change the transparency of the points by setting `alpha` equal to 0.5 within `geom_point()`.

```{r gp-8, exercise = TRUE}
ggplot(data = mpg, 
       mapping = aes(x = displ, 
                     y = hwy)) +
  geom_point()
```

```{r gp-8-hint, eval = FALSE}
ggplot(data = mpg, 
       mapping = aes(x = displ, y = hwy)) +
  geom_point(alpha = ...)
```

### Exercise 9

Now, also within `geom_point()`, set `color` equal to  `"steelblue"`. 

```{r gp-9, exercise = TRUE}
ggplot(data = mpg, 
       mapping = aes(x = displ, 
                     y = hwy)) +
  geom_point()
```

```{r gp-9-hint, eval = FALSE}
ggplot(data = mpg, 
       mapping = aes(x = displ, y = hwy)) +
  geom_point(alpha = ..., color = "...")
```

###

Both color and alpha only change the appearance of the graph and do not add new information from the data. Thus, both are arguments within the `geom` and are not nested within an `aes`, unlike when we changed `color` to the variable `Species` above. 

###

Good work.

## `geom_jitter()` 

We can also use `geom_jitter()` to fight overplotting. It plots a scatterplot and then adds a small amount of random noise to each point in the plot.



We will now create a plot with the `trains` dataset to implement this solution to overplotting. 

### Exercise 1

To better understand the data, read into the dataset by running `?trains`. Take notice of the variable type for `att_start` and `att_end`.

```{r gj-1, exercise = TRUE}

```

### Exercise 2

Run `view(trains)` to further explore the data. 

```{r gj-2, exercise = TRUE}

```

### Exercise 3

Run the code below that creates a scatterplot of `trains` with overplotting.

```{r gj-3, exercise = TRUE}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end)) +
  geom_point()
```
<!-- KX: more "learning" approach in exercises 1-3. How is flow? -->

### Exercise 4

Now, let's replace `geom_point()` with `geom_jitter()`. Try running this chunk multiple times. How does the noise affect the plot? 
<!-- KX: Thoughts on socrative questions, like above? -->
```{r gj-4, exercise = TRUE}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end)) + 
  geom_point()
```

### Exercise 5

Within `geom_jitter()`, set `width` to `.2` to adjust the amount the points are jittered.

```{r gj-5, exercise = TRUE}

```
<button onclick = "transfer_code(this)">Copy previous code</button>
```{r gj-5-hint, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end)) +
  geom_jitter(width = ...)

```

### Exercise 6

Within `aes()`, set the `color` aesthetic to the `party` variable. 

```{r gj-6, exercise = TRUE}

```
<button onclick = "transfer_code(this)">Copy previous code</button>

```{r gj-6-hint, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end, 
                     color = ...)) +
  geom_jitter(width = .2)
```

### Exercise 7

Now use `labs()` to set an appropriate title, subtitle, axes labels, and caption for the graph. 

```{r gj-7, exercise = TRUE}

```
<button onclick = "transfer_code(this)">Copy previous code</button>
```{r gj-5-hint, eval = FALSE}
... +
  labs(title = "...",
       subtitle = "..."
       x = "...",
       y = "...",
       caption = "...")
```

Here is an example of what the completed graph should look like:

```{r show-jitter-p}
 jitter_p <- ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end, 
                     color = party)) +
  geom_jitter(width = .2) +
  labs(title = "Starting and Ending Attitudes of Participants", 
       subtitle = "Democrats have a wide range of starting and Ending Attitudes", 
       x = "Starting Attitude", 
       y = "Ending Attitude", 
       caption = "Enos (2014)")

jitter_p
```

###

Good work.

## `geom_smooth()` 

We can add a regression line to our scatterplots using `geom_smooth()`

### Exercise 1

Run the code below to see the jittered scatterplot we started with in the `geom_jitter()` section.

```{r gs-1, exercise = TRUE}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end)) +
  geom_jitter(width = .2)
```

### Exercise 2

Copy/paste the code from above. Add the layer `geom_smooth()` to the graph. Remember you are adding a layer so you need to include `+`. 

```{r gs-2, exercise = TRUE}

```

```{r gs-2-hint, eval = FALSE}
... + 
  geom_smooth()
```

### Exercise 3

Awesome, but see that message R gives us? Let's try setting the method to "lm" inside `geom_smooth()`.

```{r gs-3, exercise = TRUE, warning = FALSE}

```

```{r gs-3-hint-1, eval = FALSE}
Remember to put "lm" in quotes within geom_smooth()
```

```{r gs-3-hint-2, eval = FALSE}
... +
  geom_smooth(method = "...")
```

### 

If you do not specify a method, R will give you a warning that you have not done so. By default, the method is set to `"loess"` which produces a non-linear trend curve. 

### Exercise 4

Great, but we still get a message! Set the `formula` argument within geom_smooth() to `y ~ x`. Also set `se` to FALSE to get rid of the grey area surrounds the trendline.

```{r gs-4, exercise = TRUE}


```

```{r gs-4-hint, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end)) +
  geom_jitter(width = .2)  +
    geom_smooth(method = "lm", formula = y ~ x, se = FALSE)
```

###

If you do not specify a formula, R will also give you a warning that you have not done so. By default, the formula is set to `y ~ x`.

### Exercise 5

Now use `labs()` to set an appropriate title, subtitle, axes labels, and caption for the graph. 

```{r gs-5, exercise = TRUE}

```

```{r gs-5-hint, eval = FALSE}
... +
  labs(title = "...",
       subtitle = "..."
       x = "...",
       y = "...",
       caption = "...")
```

Reminder: Your graph should look like this. 

```{r show-smooth-p}
ggplot(data = trains, 
       mapping = aes(x = att_start, 
                     y = att_end)) +
  geom_jitter(width = .2)  +
    geom_smooth(method = "lm", formula = y ~ x, se = FALSE) +
  labs(title = "Starting and Ending Attitudes of Participants", 
       subtitle = "Most participants had similar starting and ending attitudes",
       x = "Starting Attitude", 
       y = "Ending Attitude", 
       caption = "Enos (2014)")
```

### 

Good work.


<!--## 'geom_line()`
KX: A work in progress. Will wait for feedback on other sections.
-->

## `geom_histogram()` 

A histogram is a plot that visualizes the distribution of a numerical variable. 

Let's create the following histogram via the `qscores` dataset.

```{r make-hist-p}
hist_p <- ggplot(data = qscores, 
                 mapping = aes(x = rating)) +
  geom_histogram(bins = 5, 
                 color = "white", 
                 fill = "coral") + 
  labs(title = "Histogram of Student Ratings of Harvard Classes", 
       subtitle = "Ratings of 1 and 2 are very rare", 
       x = "Rating", 
       y = "Count", 
       caption = "Source: Harvard Q-Guide (2018-2019)")

hist_p
```

### Exercise 1

As always, let's first explore the data. Run `?qscores`. Which variable(s) would be most useful for making a histogram of student ratings?
<!-- KX: Socratic question -->
```{r gh-1, exercise = TRUE}

```


### Exercise 2

Within `ggplot()`, set `data` to `qscores`. 

```{r gh-2, exercise = TRUE}

```

```{r gh-2-hint, eval = FALSE}
ggplot(data = ...,)
```

###

ggplot() initializes a ggplot object. Your output should be an empty canvas.

### Exercise 3

Now, Map `rating` to the x-axis to see the distribution of Harvard course ratings. 

```{r gh-3, exercise = TRUE}

```
<button onclick = "transfer_code(this)">Copy previous code</button>
```{r gh-3-hint, eval = FALSE}
ggplot(data = ..., 
       mapping = aes(x = ...))
```

### Exercise 4

Let's now add the layer `geom_histogram()`.

```{r gh-4, exercise = TRUE}

```
<button onclick = "transfer_code(this)">Copy previous code</button>
```{r gh-4-hint-1, eval = FALSE}
Remember when you add a layer you use +. 
```

```{r gh-4-hint-2, eval = FALSE}
ggplot(data = ..., 
       mapping = aes(x = ...)) +
  geom_histogram()
```
<!-- KX: Broke up section, like for scatterplot section -->
###

`geom_histogram()` has a default y-axis which is the count for different values that occur in the x-axis variable. 


### Exercise 5

Add white vertical borders demarcating the bins by setting `color` equal to `"white"` within `geom_histogram()`.

```{r gh-5, exercise = TRUE}

```
<button onclick = "transfer_code(this)">Copy previous code</button>
```{r gh-5-hint, eval = FALSE}
ggplot(data = qscores, 
       mapping = aes(x = rating)) +
  geom_histogram(color = ...)
```

###

For plots that are not points or lines, the argument `color` only changes the outline. 

### Exercise 6

Change the color of the bars by setting `fill` equal to `"coral"` within `geom_histogram()`. 

```{r gh-6, exercise = TRUE}

```
<button onclick = "transfer_code(this)">Copy previous code</button>
```{r gh-6-hint, eval = FALSE}
ggplot(data = qscores, 
       mapping = aes(x = rating)) +
  geom_histogram(color = "white",
                 fill = "coral")
```

### Exercise 7

Specify the number of bins to be 5 using the `bins` argument in `geom_histogram()`.

```{r gh-7, exercise = TRUE}

```
<button onclick = "transfer_code(this)">Copy previous code</button>
```{r gh-7-hint, eval = FALSE}
ggplot(data = qscores, 
       mapping = aes(x = rating)) +
  geom_histogram(color = "white",
                 fill = "coral",
                 bins = 5)
```

### 

Notice how the values of `count` increased when we decreased the number of `bins`. This is because, more ratings are included in a single bin (e.g. ratings of 4.0-4.9 all included in the fourth bin). By default, geom_histogram has 30 bins.

### Exercise 8

Now use `labs()` to set an appropriate title, subtitle, axes labels, and caption for the graph. 

```{r gh-5, exercise = TRUE}

```
<button onclick = "transfer_code(this)">Copy previous code</button>
```{r gh-5-hint, eval = FALSE}
... +
  labs(title = "...",
       subtitle = "..."
       x = "...",
       y = "...",
       caption = "...")
```

Reminder: This is what our graph should look like.

```{r show-hist-p}
hist_p
```

###

Good work. 

## `geom_density()`

`geom_density()` is used to make a density plot, a smoothed version of a histogram. It is a useful alternative to the histogram that displays continuous data in a smooth distribution.

Let's create the following density plot using the `cces` dataset. 

```{r make-dens-p}
dens_p <- ggplot(data = cces, 
                 mapping = aes(x = age, 
                               color = ideology, 
                               fill = ideology)) +
  geom_density(alpha = .1) +
  labs(title = " Distribution of Age by Ideology", 
       subtitle = "Most young people are not sure of their ideology",
       x = "Age", 
       y = "Density",
       caption = "Kuriwaki (2020)")

dens_p
```

### Exercise 1
  
Let's first explore the data. Run `?cces`. Can you find the two variables that would help us to identifying the age and ideology of a respondent?
<!-- KX: How is this question? -->
```{r gd-1, exercise = TRUE}

```

### Exercise 2

Use the `cces` data set in the `primer.data` package. Within `ggplot()`, set `data` to `cces`.

```{r gd-2, exercise = TRUE}

```

```{r gd-2-hint, eval = FALSE}
ggplot(data = ...)
```

###

ggplot() initializes a ggplot object. Your output should be an empty canvas. 

### Exercise 3

Let's now map the variable `age` to the `x`argument inside `aes()`.

```{r gb-3, exercise = TRUE}

```
<button onclick = "transfer_code(this)">
```{r gd-3-hint, eval = FALSE}
ggplot(data = cces, 
       mapping = aes(x = ...))
```

### Exercise 4

Let's now add the layer `geom_desnity()`

```{r gd-4, exercise = TRUE}

```
<button onclick = "transfer_code(this)">
```{r gd-4-hint, eval = FALSE}
ggplot(data = cces, 
       mapping = aes(x = ...)) +
  geom_density()
```

###

This plot displays a density distribution for all ideologies by age. We will  split this distribution by ideology next.
<!-- KX: Unsure about takeaway and use of the word 'split' -->

### Exercise 5

Now within `aes`, set `color` and `fill` equal to the variable `ideology`. 

```{r gd-2, exercise = TRUE}

```

```{r gd-2-hint, eval = FALSE}
ggplot(data = cces, 
       mapping = aes(x = ..., 
                     color = ..., 
                     fill = ...)) + 
  geom_density()
```

###

We are getting closer! Right now, the distributions of one ideology are covering others because their `fill` is 100% opaque.
<!-- KX: Another takeaway. Critique for tone and semantics -->
### Exercise 6

Now set the `alpha` argument in `geom_density()` to 0.1.

```{r gd-3, exercise = TRUE}

```

```{r gd-3-hint, eval = FALSE}
... + 
  geom_density(alpha = 0.1)
```

### Exercise 7 


Finally set an appropriate title, subtitle, axes labels, and caption for the graph. 

```{r gd-4, exercise = TRUE}

```

```{r gd-4-hint, eval = FALSE}
... +
  labs(title = "...",
       subtitle = "..."
       x = "...",
       y = "...",
       caption = "...")
```

Reminder: Your graph should look something like this. 

```{r show-dens-p}
dens_p
```

###

Good work.


```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```

## `geom_bar()`

A barplot is a plot that visualizes the distribution of a categorical variable. 

Let's create the following barplot using the `trains` dataset. 

```{r make-bar-p}
bar_p <- ggplot(data = trains, 
       mapping = aes(x = treatment, 
                     fill = party)) +
  geom_bar(position = "dodge") +
  labs(title = "Democrats and Republicans in Treated and Control Groups",
       subtitle = "Few Republicans in both treated and control groups", 
       x = "Treatment", 
       y = "Count",
       caption = "Enos(2014)")

bar_p
```

### Exercise 1
  
Let's first explore the data. Run `?trains`. 

```{r gb-1, exercise = TRUE}

```

Consider which variable(s) would be most useful for making a barplot of treatment groups by party.

### Exercise 2

Use the `trains` data set in the `primer.data` package. Within `ggplot()`, set `data` to `trains`.

```{r gb-2, exercise = TRUE}

```

```{r gb-2-hint, eval = FALSE}
ggplot(data = ...)
```

###

ggplot() initializes a ggplot object. Your output should be an empty canvas. 

### Exercise 3

Let's now map the variable `treatment` to the `x`argument inside `aes()`.

```{r gb-3, exercise = TRUE}

```
<button onclick = "transfer_code(this)">
```{r gb-3-hint, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = ...))
```

### Exercise 4

Let's now add the layer `geom_bar()`

```{r gb-4, exercise = TRUE}

```
<button onclick = "transfer_code(this)">
```{r gb-4-hint, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = ...)) +
  geom_bar()
```

###

This plot breaks down the count of the study by treatment group, does not split these groups by party. We will do this next.

### Exercise 5

Let's now also map the variable `party` to the `fill` argument.

```{r gb-5, exercise = TRUE}

```
<button onclick = "transfer_code(this)">
```{r gb-5-hint, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = treatment, 
                     fill = ...)) +
  geom_bar()
```

###

We use the `fill` argument instead of the `color` argument because we want to color the shape and not its borders. 

Now, we can see the composition of each treatment group by party. Notice that the party bars are stacked.

### Exercise 6

Let's make our graph a side-by-side barplot. Set `position` to "dodge" in `geom_bar()`.
```{r gb-6, exercise = TRUE}

```

```{r gb-6-hint, eval = FALSE}
ggplot(data = trains, 
       mapping = aes(x = treatment, 
                     fill = party)) +
  geom_bar(position = ...)
```

###

By default `position` is set to `"stack"`. `"dodge"` puts different colors side by side.

### Exercise 7

Now use `labs()` to set an appropriate title, subtitle, axes labels, and caption for the graph. 

```{r gb-7, exercise = TRUE}

```

```{r gb-7-hint, eval = FALSE}
... +
  labs(title = "...",
       subtitle = "..."
       x = "...",
       y = "...",
       caption = "...")
```

Reminder: This is what our graph should look like.

```{r show bar-p}
bar_p
```

###

Good work.

