---
title: "Five Parameters"
tutorial:
  id: "five-parameters"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 10 tutorial"
---


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(rstanarm)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600,   # Extra time for model building
        tutorial.storage = "local") 

# Need to mutate election_age to be centered; zero means the mean value.

ch10 <- governors %>% 
  select(last_name, year, state, sex, lived_after, election_age) %>% 
  mutate(c_election_age = election_age - mean(election_age))

gov_1 <- stan_glm(data = ch10,
                  formula = lived_after ~ sex + c_election_age,
                  refresh = 0,
                  seed = 12)

gov_2 <- stan_glm(data = ch10,
                  formula = lived_after ~ sex*c_election_age,
                  refresh = 0,
                  seed = 13)

```

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```

## EDA of governors 
###

Let's create the following graph.

```{r prep-EDA}
EDA_p <- ch10 %>%
  ggplot(aes(x = sex, y = lived_after)) +
  geom_boxplot() +
  labs(title = "US Gubernatorial Candidate Years Lived Post-Election",
       subtitle = "Male candidates live much longer after the election",
       caption = "Data: Barfort, Klemmensen and Larsen (2019)",
       x = "Gender",
       y = "Years Lived After Election") +
  scale_y_continuous(labels = scales::label_number()) +
  theme_classic() 

EDA_p
```

### Exercise 1

Start a pipe with `governors`. `select()` the `last_name`, `year`, `sex`, `state`, `lived_after`, and `election_age` variables. Save your code to an object named `ch_10`.

```{r eda-1, exercise = TRUE}

```

```{r eda-1-hint, eval = FALSE}
governors %>% 
  select(...)
```

### Exercise 2

Pipe your results to `ggplot()`. Map `sex` to the x-axis and `lived_after` to the y-axis. Use `geom_boxplot`.

```{r eda-2, exercise = TRUE}

```

```{r eda-2-hint, eval = FALSE}
... %>% 
  ggplot(aes(...,...)) +
  geom_boxplot()
```

### Exercise 3

Use `labs()` to add the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.

```{r eda-3, exercise = TRUE}

```

### Exercise 4

Let's also change the y-axis values to look nicer. Use `scale_y_continuous()`. Within `scale_y_continuous()`, set `labels` to `scales::label_number()`. 

Reminder: This is what your plot should look like.

```{r}
EDA_p
```

```{r eda-4, exercise = TRUE}

```

```{r eda-4-hint, eval = FALSE}
... +
  scale_y_continuous(labels = ...)
```

## Wisdom
###


Consider the following question.

*How long will two political candidates — one male and one female, both 10 years older than the average candidate — live after the election? How different will their lifespans be?*

Using **Wisdom**, write a paragraph about whether or not this data --- which covers gubernatorial elections from 1945 to 2012 --- is relevant for the problem we face. See *The Primer* for guidance.

```{r wisdom-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 6))
```


## Justice and Courage I
###


### Exercise 1


Let's build a model. Our outcome variable will be `lived_after`, we will have two explanatory variables: `c_election_age` and `sex`. Recall `c_election_age` is the number of years a candidate has been alive, as of Election Day, relative to the average years alive of all candidates on their respective election days. Below is the math we will be using.

$$lived\_after_i =  \beta_0 + \beta_1 male_i + \beta_2 election\_age\_c_i + \epsilon_i$$

Looking at the model above, which are the parameters? You do not need to figure out how to display the symbols in your answer, just write their names (i.e. "epsilon," "delta," etc. ).

```{r jc-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 6))
```

### Exercise 2

Great! Now write a sentence for each parameter that describes what it means.

```{r jc-ex-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 6))
```

### Exercise 3

Let's implement the model using `stan_glm()`. The `formula` argument should be `lived_after ~ sex + c_election_age`. Set `data` to`ch_10`, and `refresh` to 0.  Also set the `seed` argument to 12. Assign your work to an object named `gov_1`.


```{r jc-ex-3, exercise = TRUE}

```


```{r jc-ex-3-hint, eval = FALSE}
gov_1 <- stan_glm(data = ...,
                  formula = ...,
                  refresh = ...,
                  seed = )
```

### Exercise 4

Use `print()` to look at our parameter values. Set the `detail` argument to FALSE.

```{r jc-ex-4, exercise = TRUE}

```

```{r jc-ex-4-hint, eval = FALSE}
print(gov_1, detail = ...)
```

### Exercise 5

Look at the results above. Write two sentences, using your own words, that explain the meaning of the Median value of `(Intercept)`.

```{r jc-ex-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 6

Write two sentences that explain how you would estimate the `lived_after` value for a male candidate, who has been alive the average number of years of all candidates. In addition to your explanation, provide a numeric value. Note that we do not want you to use `posterior_predict()` or anything fancy. Answer this question by simply looking at the model printout.

```{r jc-ex-6}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 7

Let's create the following posterior probability distribution for $\beta_2$, the coefficient for `c_election_age`.

```{r prep-jc-ex-7}
gov1_p <- gov_1 %>%
  as_tibble() %>%
  ggplot(aes(c_election_age)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 100) +
    labs(title = "Posterior Distribution of the Coefficient of `c_election_age`",
         y = "Probability",
         x = "Coefficient of `c_election_age`") +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()

gov1_p
```

### Exercise 8

Start a pipe with `gov_1` and use `as_tibble()`

```{r jc-ex-8, exercise = TRUE}

```


```{r jc-ex-8-hint, eval = FALSE}
gov_1 %>%
  as_tibble()
```

### Exercise 9

Pipe the results above to `ggplot()`. Map `c_election_age` to the x-axis.

```{r jc-ex-11, exercise = TRUE}

```

```{r jc-ex-11-hint, eval = FALSE}
... %>%
  ggplot(aes(...)) +
    geom_histogram(aes(y = after_stat(.../sum(...))),
                   bins = 100,
                   alpha = 0.5,
                   position = "identity")

```

### Exercise 12

Use `labs()` to add the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.


```{r jc-ex-12, exercise = TRUE}

```

```{r jc-ex-12-hint, eval = FALSE}

```

### Exercise 13

Use `scale_y_continuous()` to put the y-axis in percent format. Within `scale_y_continuous()`, set `labels` to `scales::percent_format()`.


Reminder: This is what your plot should look like.

```{r}
gov1_p
```

```{r jc-ex-13, exercise = TRUE}

```

### Exercise 14

In two sentences, provide an interpretation of the graph you just created.

```{r jc-ex-15}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```


## Justice and Courage II
###

Let's build another model. The outcome variable of `lived_after` will now be a function of the two explanatory variables we used above, `c_election_age` and `sex`, and of their interaction.

Note that this means there are now two different slopes to consider: one for only male candidates and one for only female candidates. In the previous model we built, there was one slope for both men and women. Here is the math:

$$lived\_after_i =  \beta_0 + \beta_1 male_i + \beta_2 election\_age\_c_i + \\ \beta_3 male_i *  election\_age\_c_i + \epsilon_i$$

### Exercise 1

Let's implement the model using `stan_glm()`. The formula argument should be `lived_after ~ state + sex*election_age`. Set `data` to`ch_10`, `refresh` to 0, and set the `seed` argument to 13. Assign your work to an object named `gov_2`.

```{r jc2-ex1, exercise = TRUE}

```



```{r jc2-ex1-hint, eval = FALSE}
gov_2 <- stan_glm(data = ...,
                formula = ...,
                refresh = ...,
                seed = ...)
```

### Exercise 2

Use `print()` to look at our parameter values. Set the `detail` argument to FALSE.

```{r jc2-ex2, exercise = TRUE}

```

```{r jc2-ex2-hint, eval = FALSE}
print(gov_2, detail = ...)
```

### Exercise 3

Look at the results above. Write two sentences, using your own words, explaining the significance of the value for the Median of (Intercept), which should be something around 16.5. (The exact value will vary because of the inherent randomness in fitting Bayesian models.)

```{r jc-2-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 6))
```

### Exercise 4

Write two sentences that explain how you would find the slope value for a male candidate, who has been alive the average amount of days as all male candidates. In addition to your explanation, provide the numerical value.

```{r jc-2-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 6))
```

### Exercise 5

Let's now create the following posterior probability distribution that shows the average slope values for men and women.

```{r prep-state_p}
gov2_p <- gov_2 %>%
  as_tibble() %>%
  mutate(slope_men = c_election_age + `sexMale:c_election_age`) %>%
  rename(slope_women = c_election_age) %>%
  select(slope_women, slope_men) %>%
  pivot_longer(cols = slope_women:slope_men,
               names_to = "parameters",
               values_to = "slope") %>%
  ggplot(aes(slope, fill = parameters)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   alpha = 0.5,
                   bins = 100,
                   position = "identity") +
    labs(title = "Posterior for Slope of Years-Lived on Years-to_Live",
         subtitle = "Men have a steeper slope",
         x = "slope",
         y = "Probability") +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()

gov2_p
```

### Exercise 6

Start a pipe with `gov_2` and use `as_tibble()`. Continue the pipe and use `mutate()` to create the variable `slope_men`. `slope_men` should be equal to the following argument: `c_election_age + sexMale:c_election_age`. Make sure you place backticks around sexMale:c_election_age.

```{r jc-2-ex-6, exercise = TRUE}

```


```{r jc-2-ex-6-hint, eval = FALSE}
gov_2 %>%
  as_tibble() %>%
  mutate(slope_men = ... + `sexMale:c_election_age`)
```

### Exercise 7

Continue the pipe and use `rename()` to rename the variable `slope_women` as `c_election_age`. Also use `select()` to keep just two variables: `slope_women` and `slope_men`.

```{r jc-2-ex-7, exercise = TRUE}

```

```{r jc-2-ex-7-hint, eval = FALSE}
... %>%
  rename(slope_women = ...) %>%
  select(..., ...)
```

### Exercise 8

Pipe your results to `pivot_longer()`. Within `pivot_longer()`, set `cols` to `slope_women` and `slope_men` (Make sure you insert a colon between them). `names_to` should be set to "parameters" and `values_to` should be set to "slope".

```{r jc-2-ex-8, exercise = TRUE}

```

```{r jc2-ex-8-hint, eval = FALSE}
... %>%
  pivot_longer(cols = ...,
               names_to = ...,
               values_to = "...)
```

### Exercise 9

Pipe the results to `ggplot()`. Map `slope` to the x-axis, and map `parameters` to the  `fill` aesthetic. Use `geom_histogram()` with the same tricks we use in the chapter: `after_stat()`, `bins`, `alpha` and `position`.

```{r jc2-ex-9, exercise = TRUE}

```

```{r jc2-ex-9-hint, eval = FALSE}
... %>%
  ggplot(aes(..., fill = ...)) +
    geom_histogram(aes(y = after_stat(.../sum(...))),
                   bins = 100,
                   alpha = 0.5,
                   position = "identity")

```

### Exercise 10

Use `labs()` to add the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.


```{r jc2-ex-10, exercise = TRUE}

```

### Exercise 11

Now use `scale_y_continuous()` to put the y-axis in percent format. Within `scale_y_continuous()`, set `labels` to `scales::percent_format()`.


Reminder: This is what your plot should look like.

```{r}
gov2_p
```

```{r jc2-ex-11, exercise = TRUE}

```

```{r jc2-ex-11-hint, eval = FALSE}
... +
  scale_y_continuous(labels = ...) +
    theme_classic()
```

### Exercise 12

In two sentences, provide an interpretation of the graph you just created.

```{r jc2-ex-12}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```


## Temperance I
###

Consider:

How long will two political candidates — one male and one female, both 10 years older than the average candidate — live after the election? How different will their lifespans be?


First, we create the posterior distributions of the parameters in `gov_2`.

```{r}
newobs = tibble(sex = c("Male", "Female"),
                 c_election_age = 10)

pe <- posterior_epred(object = gov_2,
                      newdata = newobs) %>%
  as_tibble() %>%
  rename("Male" = `1`,
         "Female" = `2`)



temp_p <- pe %>%
 pivot_longer(cols = Male:Female,
               names_to = "Gender",
               values_to = "years") %>%
  ggplot(aes(years, fill = Gender)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   alpha = 0.5,
                   bins = 100,
                   position = "identity") +
    labs(title = "Posterior for Expected Years Lived Post-Election",
         subtitle = "Male candidates live longer",
         x = "Years",
         y = "Probability") +
    scale_x_continuous(labels =
                         scales::number_format(accuracy = 1)) +
    scale_y_continuous(labels =
                         scales::percent_format(accuracy = 1)) +
    theme_classic()

temp_p
```

**Reminder:** Make sure you copy/paste your code for each step to the next question. If you do not, you will get an error that your object does not exist.


### Exercise 1

Create a tibble `newobs` that has two variables. The first variable should be `sex` that has two observations "Male" and "Female". The second variable `c_election_age` should have one observation 10.

```{r temp-1, exercise = TRUE}

```

```{r temp-1-hint-1, eval = FALSE}
You may find the c() function when creating the sex variable.
```

```{r temp-1-hint-2, eval = FALSE}
newobs = tibble(sex = c(...,...),
                c_election_age = ...)
```

### Exercise 2

Use `posterior_epred()`. The first argument to `posterior_epred()` should be `gov_2`. Also set `newdata` to `newobs`.

```{r temp-2, exercise = TRUE}

```

```{r temp-2-hint, eval = FALSE}
posterior_epred(gov_2,
                  newdata = newobs)
```

### Exercise 3

Pipe the results of `posterior_epred()` to `as_tibble()`. Also use `rename()` to rename the column "Male" as `1` and the column "Female" as `2`. Save you results to an object named `pe`.

```{r temp-3, exercise = TRUE}

```

```{r temp-3-hint, eval = FALSE}
pe <- posterior_epred(gov_2,
                  newdata = newobs) %>%
  as_tibble() %>%
  rename(... = `1`,
         ... = `2`)

```

### Exercise 4

Write a paragraph that interprets the tibble you just created. Make sure to answer the question in your response. Make sure to use the word "draws."

```{r temp-3-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 5

Pipe the results of `pe` to `pivot_longer()`. Set `cols` to `Male:Female`, `names_to` to "Gender" and `values_to` to "years".

```{r temp-5, exercise = TRUE}

```

```{r temp-5-hint, eval = FALSE}
pe %>%
 pivot_longer(cols = ...,
               names_to = ...,
               values_to = ...)
```

### Exercise 6

Extend the pipe to create a plot. Recall that this is what it looks like:

```{r}
temp_p
```


```{r temp-6, exercise = TRUE}

```

```{r temp-6-hint, eval = FALSE}
... %>%
  ggplot(aes(years, fill = Gender)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   alpha = 0.5,
                   bins = 100,
                   position = "identity") +
    labs(title = ...,
         subtitle = ...,
         x = ...,
         y = ...) +
    scale_x_continuous(labels = scales::number_format(accuracy = ...)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = ...)) +
    theme_classic()
```

### Exercise 7

Great. Now that we know men live longer...we want to know how much longer? Let's create the following posterior that shows the difference between the two posteriors we just created.

```{r}
pe <- posterior_epred(object = gov_1,
                      newdata = newobs) %>%
  as_tibble() %>%
  mutate(diff = `1` - `2`)


temp2_p <- pe %>%
  ggplot(aes(diff)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   alpha = 0.5,
                   bins = 100,
                   position = "identity") +
    labs(title = "Posterior for Expected Additional Male Years Lived",
         subtitle = "Male candidates live about 4 years longer",
         x = "Expected Additional Years Lived Post Election",
         y = "Probability") +
    scale_x_continuous(labels = scales::number_format(accuracy = 1)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    theme_classic()

temp2_p
```

**Reminder:** Make sure you copy/paste your code for each step to the next question. If you do not, you will get an error that your object does not exist.


### Exercise 8

We start with the same code that began our previous posterior distribution. Pipe the results of `as_tibble()` to `mutate()` to create a new variable `diff` that subtracts "Female" from "Male".

```{r temp-8, exercise = TRUE}
newobs = tibble(sex = c("Male", "Female"),
                 c_election_age = 10)

pe <- posterior_epred(object = gov_1,
                      newdata = newobs) %>%
  as_tibble()
```

```{r temp-8-hint, eval = FALSE}
... %>%
  as_tibble() %>%
    mutate(diff = `1` - `2`)
```

### Exercise 9

Extend the pipe to create a plot. Recall that this is what it looks like:

```{r}
temp2_p
```


```{r temp-9, exercise = TRUE}

```

```{r temp-9-hint, eval = FALSE}
... %>%
 ggplot(aes(diff)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   alpha = 0.5,
                   bins = 100,
                   position = "identity") +
    labs(title = ...,
         subtitle = ...,
         x = ...,
         y = ...) +
    scale_x_continuous(labels = scales::number_format(accuracy = ...)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = ...)) +
    theme_classic()
```

### Exercise 10

Great! Now write a paragraph that interprets the graph you just created.

```{r temp-10}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 6))
```

```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
