---
title: "Wrangling C"
tutorial:
  id: "wrangling-c"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 2 Tutorial -- Part B"
---


<!-- BG: Do we like the dataset descriptions. Will the students read them? If so, should we shorten them to one sentence or is it OK? -->

<!-- BG: need to replace ntile() -->

<!-- Things to discuss about this tutorial: -->

<!-- bind_cols(): we cut it out of the book. Still exists in Q-Guide plot. So, need to get rid of it. replace with mutate(), or some other join. Get rid of it. -->

<!-- ntile(): I added a quick sentence in the primer, a word or two I read in the help page because I saw it in this tutorial. I'm confused about it. DK: Use quantile() instead? -->

<!-- scale_fill_brewer(), coord_cartesian(), and  scale_linetype() all have no explanation in primer. DK: So, don't use them. Or give a clear hint. -->


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(lubridate)
library(stringr)
library(skimr)
library(primer.data)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

# Needed for later sections of the tutorial 

library(ggthemes)
```


## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```


## National Health and Nutrition Survey
###

`nhanes` includes data from the "National Health and Nutrition Examination Survey," which contains the personal and physical information of 10,000 Americans from two surveys in 2009 and 2011.


Let's create the following plot.

```{r}
nhanes_p <- nhanes %>%
  mutate(weight = weight * 2.2, height = height / 30.48) %>%
  select(gender, weight, height, bmi) %>%
  drop_na(weight, height) %>% 
  ggplot(mapping = aes(x = weight, y = height, color = bmi)) +
    geom_jitter() +
    geom_smooth(se = FALSE, 
                method = "gam", 
                formula = y ~ s(x, bs = "cs")) +
    facet_wrap(~ gender) + 
    theme_clean() + 
    labs(y = "Height (feet)",
         x = "Weight (pounds)",
         title = "Height Versus Weight in the US",
         subtitle = "Relation between weight and height more positive for heavy men",
         caption = "Source: NHANES")

nhanes_p
```


### Exercise 1

In the original tibble, `weight` is measured in kg and `height` in cm. Using `mutate()`, multiply `weight` by 2.2 and divide `height` by 30.48 to convert units into pounds and feet. 

```{r nhanes2, exercise = TRUE}

```

```{r nhanes2-hint-1, eval = FALSE}
nhanes %>%
  mutate(weight = ..., height = ...)
```

```{r nhanes2-hint-2, eval = FALSE}
Use * to multiply and / to divide.
```

### Exercise 2

Now `select()` the `gender`, `weight`, `height`, and `bmi` columns. 

```{r nhanes3, exercise = TRUE}

```

```{r nhanes3-hint, eval = FALSE}
... %>%
  select(..., ..., ..., ...)
```

### Exercise 3

`nhanes` has NA values in some rows. Use `drop_na()` to remove all rows with a value of `NA` in the `weight`and `height` columns just to be sure.

```{r nhanes4, exercise = TRUE}

```

```{r nhanes4-hint, eval = FALSE}
... %>%
  drop_na(..., ...)
```

### Exercise 4

Use `ggplot()` to make a jittered scatterplot that maps `weight` to the x-axis, `height` to the y-axis, and `bmi` to `color`.

```{r nhanes5, exercise = TRUE}

```


```{r nhanes5-hint-1, eval = FALSE}
Use geom_jitter()
```

```{r nhanes5-hint-2, eval = FALSE}
... %>% 
  gplot(data = ..., aes(x = ..., 
                        y = ..., 
                        color = ...)) +
  geom_jitter()
```

### Exercise 6

Add a trend line with `geom_smooth()`. Set the `se` to FALSE and  set `method` to "gam".


```{r nhanes6, exercise = TRUE}

```

```{r nhanes6-hint-2, eval = FALSE}
... + 
  geom_smooth(se = ..., method = ...)
```

### Exercise 7

Notice that we still get a message. Let's take their suggestion for formula. Within`geom_smooth()` set the `formula` argument to `y ~ s(x, bs = "cs")`.

```{r nhanes1, exercise = TRUE}

```

```{r nhanes1-hint-2, eval = FALSE}
... + 
 geom_smooth(se = FALSE, 
                method = "gam", 
                formula = ...)
```

### Exercise 8

Use `facet_wrap()` to facet the graph by `gender`.


```{r nhanes7, exercise = TRUE}

```

```{r nhanes7-hint, eval = FALSE}
... +
  facet_wrap( ~ ...) 
```

### Exercise 9

Adjust the feel of the graph with the theme, `theme_clean()`.

```{r nhanes8, exercise = TRUE}

```

```{r nhanes8-hint, eval = FALSE}
... +
  theme_clean()
```

### Exercise 10

To finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, and caption of your choice.

```{r nhanes9, exercise = TRUE}

```

Reminder: This is what your graph should look like.

```{r nhanes9-answer}
nhanes_p
```


## Kenya Voting
###

The `kenya` contains data from a study in which poll stations in Kenya were assigned to either the control group or a group in which one or more methods (an SMS reminder, canvassing, etc.) were used to encourage voter registration. 


Let's create the following plot.

```{r kenya-answer}
kenya_p <- kenya %>%
  filter(treatment %in% c("control", "local", 
                          "SMS", "canvass")) %>%
  droplevels() %>%
  select(treatment, mean_age, reg_byrv13) %>%
  drop_na(mean_age) %>%
  mutate(age_half = ntile(mean_age, 2)) %>%
  group_by(treatment, age_half) %>%
  summarize(mean_turnout = mean(reg_byrv13, na.rm = TRUE)) %>% 
  ggplot(mapping = aes(x = fct_reorder(treatment, mean_turnout), 
                       y = mean_turnout)) +
    geom_col() +
    theme_bw() +
    labs(title = "Turnout Changes in a Kenyan Election",
         subtitle = "Local canvassing has the largest effect",
         x = "Treatment",
         y = "Change in Mean Turnout")

kenya_p
```

### Exercise 1

`glimpse()` the `kenya` data set.

```{r kenya1, exercise = TRUE}

```

```{r kenya1-hint, eval = FALSE}
glimpse(kenya)
```

### Exercise 2

`filter()` `kenya` to only the rows with a `treatment` of "control," "local," "SMS," or "canvass." Use the `%in% `operator to do so.


```{r kenya3, exercise = TRUE}

```

```{r kenya3-hint-1, eval = FALSE}
kenya %>%
  filter(treatment %in% ...)
```

```{r kenya3-hint-2, eval = FALSE}
kenya %>%
  filter(treatment %in% c(...))
```

### Exercise 3

Because `treatment` is a factor, use `%>% ` to  `droplevels()`. This will avoid future complications. 

```{r kenya4, exercise = TRUE}

```

```{r kenya4-hint, eval = FALSE}

```

### Exercise 4

Now `select()` the `treatment`, `mean_age`, and `reg_byrv13` columns. 

```{r kenya5, exercise = TRUE}

```

### Exercise 5

Use `drop_na()` to remove all rows with a value of `NA` in the `mean_age` column.

```{r kenya6, exercise = TRUE}

```

```{r kenya6-hint, eval = FALSE}
kenya %>%
  filter(treatment %in% c("control", "local", "SMS", "canvass")) %>%
  droplevels() %>%
  select(treatment, mean_age, reg_byrv13)
  drop_na(...)
```

### Exercise 6

The `ntile()` function divides a continuous numerical value into categories depending on its size.

Use `mutate()` and `ntile()` to create the variable `age_half`, which categorizes the `mean_age` variable into 2 groups (i.e.the younger half, and the older half).


```{r kenya8, exercise = TRUE}

```

```{r kenya8-hint, eval = FALSE}
... %>% 
  mutate ( ... = ntile(mean_age, 2)
```

### Exercise 7

Group the data by `treatment` and `age_half`.

```{r kenya9, exercise = TRUE}

```

```{r kenya9-hint, eval = FALSE}
... %>%
  group_by(...)
```

### Exercise 8

Using `summarize()`, calculate the variable `mean_turnout` as the `mean()` value of `reg_byrv13` in each group. The second argument to `mean()` should set `na.rm` to `TRUE`, as there are some `NA` values in the `reg_byrv13` column.


```{r kenya10, exercise = TRUE}

```

```{r kenya10-hint, eval = FALSE}
Don't forget the .groups argument to summarize(). Never ignore warning
messages.
```

### Exercise 9

Use `%>% `to add  `ggplot()`.  Use`fct_reorder()` to reorder the `treatment` variable by `mean_turnout` and map this to 'x`. Map `treatment` to the y-axis.

```{r kenya11, exercise = TRUE}

```


```{r kenya11-hint-1, eval = FALSE}
Remember to use geom_col() instead of geom_bar() when 
you map something to the y-axis.
```

```{r kenya11-hint-2, eval = FALSE}
... %>% 
  ggplot(mapping = aes(x = fct_reorder(treatment, mean_turnout), 
                       y = ...) +
  geom_col()
```

### Exercise 10

Add the theme `theme_bw()` to the plot.

```{r kenya14, exercise = TRUE}

```

### Exercise 11

To finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, and caption of your choosing. Your plot should look something like this:

```{r kenya15-answer}
kenya_p
```

```{r kenya15, exercise = TRUE}

```



## Seguro Popular
###

The `sps` data set contains information about a study done on a popular Mexican health insurance program, Seguro Popular. In the study, some Mexican health clusters were randomly "treated." The treatment consisted of encouragement for people in that health cluster to enroll in the health insurance program, as well as funds to improve health facilities in that cluster.

Let's create the following plot.

```{r sps_plot}
sps_p <- sps %>%
  filter(education %in% c("preschool", "secondary", 
                          "high school", "college")) %>%
  select(-c(health_exp_1m, t2_health_exp_1m)) %>%
  mutate(change_in_expenses = t2_health_exp_3m - health_exp_3m) %>%
  group_by(treatment, education) %>%
  summarize(mean_change_in_expenses = mean(change_in_expenses)) %>%
  mutate(treatment = as.factor(treatment)) %>% 
  ggplot(mapping = aes(x = fct_reorder(education, mean_change_in_expenses), 
                       y = mean_change_in_expenses, fill = treatment)) +
    geom_col(position = position_dodge(preserve = "single")) + 
    theme_minimal() +
    labs(x = "Education",
         y = "Average Change in Expenses",
         title = "Spending Changes and Seguro Popular",
         subtitle = "Honestly, not sure what is going on here . . .",
         caption = "Source: King et al. (2009)")

sps_p
```

### Exercise 1 

`glimpse()` the dataset `sps`.

```{r sps1, exercise = TRUE}

```

```{r sps1-hint, eval = FALSE}
glimpse(...)
```

### Exercise 2

`filter()` `sps` to only the rows with an `education` of "preschool," "secondary," "high school," or "college."  Use the `%in% `operator to do so.

```{r sps2, exercise = TRUE}

```

```{r sps2-hint-1, eval = FALSE}
sps %>%
  filter(education %in% ...)
```

```{r sps2-hint-2, eval = FALSE}
sps %>% 
  filter(education %in% c(...))
```

### Exercise 3

Use `select()` to remove the columns `health_exp_1m` and `t2_health_exp_1m`. 


```{r sps3, exercise = TRUE}

```

```{r sps3-hint-1, eval = FALSE}
Remember that select(-...) returns all columns except for the specified column(s).
```

```{r sps3-hint-2, eval = FALSE}
Consider using c()
```

```{r sps3-hint-3, eval = FALSE}
... %>% 
  select(-c(..., ...))
```

### Exercise 4 

Use `mutate()` to create a new variable, `change_in_expenses`, equal to `health_exp_3m` subtracted from `t2_health_exp_3m` (this measures the change in expenses after the treatment period). 


```{r sps4, exercise = TRUE}

```

```{r sps4-hint, eval = FALSE}
... %>% 
  mutate(... = t2_health_exp_3m - health_exp_3m) 
```

### Exercise 5

Group the data by `treatment` and `education`.

```{r sps5, exercise = TRUE}

```

```{r sps5-hint, eval = FALSE}
Use the group_by() function.
```

### Exercise 6

Using `summarize()`, calculate `mean_change_in_expenses`, the` mean()` of the `change_in_expenses` for each group.

```{r sps6, exercise = TRUE}
  
```

```{r sps6-hint, eval = FALSE}
... %>% 
  summarize(... = mean(change_in_expenses))
```

### Exercise 7

Because `treatment` column is an integer and not a factor, we can't group our data by it. To fix this problem, use `mutate()` and `as.factor()` to change `treatment` to a factor. 

```{r sps9, exercise = TRUE}

```

```{r sps9-hint, eval = FALSE}
 ... %>% 
  mutate(treatment = as.factor(...))
```

### Exercise 8

Use ` %>% ` to add `ggplot()` to make a bar graph. Use`fct_reorder()` to reorder the `education` variable by `mean_change_in_expenses` and map this to `x` axis. Map `mean_change_in_expenses` to the y-axis, and `treatment` to the `fill`.


```{r sps7, exercise = TRUE}

```

```{r sps7-hint-1, eval = FALSE}
Remember to use geom_col() instead of geom_bar() 
when mapping a variable to the y-axis.
```

```{r sps7-hint-2, eval = FALSE}
.. %>% 
  ggplot(mapping = aes(x = fct_reorder(education, 
                                       mean_change_in_expenses), 
                     y = ..., 
                     fill = ...) +
  geom_col()
```

### Exercise 9

Within `geom_col()`, set the position argument equal to `position_dodge()`. Inside `position_dodge()`, set `preserve` equal to "single" to create a dodged barplot. It does not work well! Don't worry, we will fix in in the next exercise.

```{r sps8, exercise = TRUE}

```

```{r sps8-hint, eval = FALSE}
... +
  geom_col(... = position_dodge(preserve = "..."))
```

### Exercise 10

Add `theme_minimal()` to change the style of the graph.


```{r sps12, exercise = TRUE}

```

### Exercise 11

To finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, and caption of your choice.


Reminder: This is what your graph should look like.

```{r sps13-answer}
sps_p
```

```{r sps13, exercise = TRUE}

```

## Shaming 
###

The `shaming` data set measures the impact of social pressure on voting. Nearly 350,000 people in Michigan were randomly assigned to 1 of 5 treatment groups before the 2006 Michigan primary. All 5 groups were sent mail before the primary: the "Civic Duty" group had an extra reminder that voting was a civic responsibility, the "Hawthorne" group was told that whether or not they voted would be in the public record, the "Self" group was actually *sent* the public record of whether or not they voted in 2004, and the "Neighbors" group was sent both their voting record and their neighbors' voting record from 2004. 

Let's create the following plot.

```{r sh_goal}
shaming_p <- shaming %>%
  select(primary_04, primary_06, treatment) %>%
  mutate(primary_04 = if_else(condition = 
                                str_detect(primary_04, "Yes"),
                                true = 1,
                                false = 0)) %>%
  pivot_longer(cols = c(primary_04, primary_06), 
               names_to = "year", 
               values_to = "voted") %>%
  group_by(treatment, year, voted) %>%
  summarize(num_voters = n(), .groups = "drop") %>%
  mutate(voted = if_else(condition = voted == 1,
                         true = "did_vote",
                         false = "did_not_vote")) %>%
  pivot_wider(names_from = voted, values_from = num_voters)  %>%
  mutate(pct_voted = did_vote / (did_vote + did_not_vote)) %>% 
  ggplot(mapping = aes(x = fct_reorder(treatment, pct_voted), 
                       y = pct_voted, fill = year)) +
    geom_col(position = position_dodge(preserve = "single")) +
    labs(x = "Treatment",
         y = "Voting Percentage",
         title = "Voting Rates Based on Mailings",
         subtitle = "Shaming people makes them more likely to vote",
         caption = "Source: Gerber, Green, and Larimer (2008).") +
    theme_fivethirtyeight()

shaming_p
```

### Exercise 1

`skim()` the `shaming` data set. Pay close attention to the data types of each of the variables.

```{r shaming1, exercise = TRUE}

```

### Exercise 2

`select()` the columns `treatment`, `primary_04`, and `primary_06`. 

```{r shaming2, exercise = TRUE}

```

### Exercise 3

Use `mutate()` to change the `primary_04` column. Set `primary_04` to an `if_else()` statement. Within `if_else()`, set `condition` to `str_detect()` of the string "Yes" in `primary_04`. If the condition is true, return `1`, and if the condition is false, return `0`.

```{r shaming5, exercise = TRUE}

```

```{r shaming5-hint-1, eval = FALSE}
mutate(primary_04 = if_else(condition = 
                              str_detect(primary_04, "..."),
                                true = ...,
                                false = ...))
```

### Exercise 4

Use `pivot_longer()` to map the *names* of the `primary_04` and `primary_06` columns to a new column, "year," and the *values* of those two columns to a new column, "voted."


```{r shaming3, exercise = TRUE}

```

```{r shaming3-hint, eval = FALSE}
...  %>%
  pivot_longer(cols = ..., 
               names_to = c(...,...),
               values_to = ...)
```

### Exercise 5

Great job! Now group the data by `treatment`, `year`, and `voted`.

```{r shaming6, exercise = TRUE}

```

```{r shaming6-hint, eval = FALSE}
Use the group_by() function.
```

### Exercise 6

Using `summarize()`, create the variable `num_voters` that is set to the function `n()`, which simply counts the number of rows in each group. Then, set the argument `.groups` to "drop".

```{r shaming7, exercise = TRUE}

```

```{r shaming7-hint, eval = FALSE}
... %>% 
  summarize(num_voters = n(), .groups = "..."")
```

### Exercise 7

The `voted` column is a bit difficult to understand, for the numerical value (0 or 1) is used to represent an idea (the person did or did not vote). Use `mutate()` to set `voted` to an `if_else()` statement. Within `if_else()`, set `condition` to where `voted` is equal to 1. Set `true` to "did_vote," and `false` to "did_not_vote."


```{r shaming8, exercise = TRUE}

```

```{r shaming8-hint-2, eval = FALSE}
...%>%
  mutate(voted = if_else(condition = voted == ...,
                         true = "...",
                         false = "..."))
```

### Exercise 8

Now, we want `did_vote` and `did_not_vote` to be their own columns. Call a `pivot_wider()` function that gets its column names from `voted` and its values from `num_voters`.


```{r shaming9, exercise = TRUE}

```

```{r shaming9-hint, eval = FALSE}
...  %>%
  pivot_wider(names_from = ..., values_from = ...)
```

### Exercise 10

Use `mutate()` to create new variable `pct_voted` which is equal to the number of people who `did_vote` divided by the total number of people.

```{r shaming10, exercise = TRUE}

```

```{r shaming10-hint, eval = FALSE}
Note that the total number of people is equal to (did_vote + did_not_vote). Also, use / to divide. 
```

### Exercise 11

Use `%>%` to add`ggplot()` to make a bar chart. Use `fct_reorder()` to reorder the `treatment` variable by `pct_voted` and map this to `x` axis. Map `pct_voted` to the y-axis, and `year` to the `fill`.


```{r shaming11, exercise = TRUE}

```

```{r shaming11-hint-1, eval = FALSE}
Remember to use geom_col() instead of geom_bar() 
when you map something to the y-axis.
```

```{r shaming11-hint-2, eval = FALSE}
... %>% 
  ggplot(mapping = aes(x = fct_reorder(treatment, pct_voted), 
                       y = ..., 
                       fill = ...)) +
  geom_col()
```

### Exercise 12

Within `geom_col()`, set the position argument equal to `position_dodge()`. Inside `position_dodge()`, set `preserve` equal to "single" to create a dodged barplot.

```{r shaming12, exercise = TRUE}

```

```{r shaming12-hint, eval = FALSE}
... +
  geom_col(position = position_dodge(preserve = "single"))
```

### Exercise 13

Add the theme `theme_fivethirtyeight()` to your plot. 

```{r shaming16, exercise = TRUE}

```

```{r shaming16-hint, eval = FALSE}
Remember when you add a theme, you add a layer. Use +.
```

### Exercise 14

To finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, and caption of your choice.

Reminder: This is what your graph should look like. 

```{r shaming15-answer}
shaming_p
```

```{r shaming15, exercise = TRUE}

```

## Q-Guide
###

<!-- BG: need to add in setup chunks for some of exercises  -->

The `qscores` data set includes information about 748 courses at Harvard during the 2018-2019 school year, including their department, student enrollment, average time spent on homework, and the average student rating of the course.


```{r}
q_subset_2 <- qscores %>%
  filter(department %in% c("ECON", "MATH", "GOV")) %>%
  arrange(department)

q_subset <- qscores %>%
  select(department, hours) %>%
  group_by(department) %>%
  summarize(num_classes = n(), 
            mean_hours = mean(hours), 
            sd_hours = sd(hours)) %>%
  arrange(desc(num_classes)) %>%
  slice(1:3) %>%
  group_by(department) %>%
  summarize(rnorm_values = rnorm(n = num_classes, 
                                 mean = mean_hours, 
                                 sd = sd_hours)) %>%
  arrange(department)

q_join <- left_join(q_subset, q_subset_2, by = "department") %>%
  pivot_longer(cols = c(rnorm_values, hours), 
               names_to = "type", 
               values_to = "value")

ggplot(data = q_join, mapping = aes(x = value)) +
    geom_histogram(binwidth = 2) +
     facet_wrap(~ department) + 
  theme_bw()+
  labs(title = " Homework Patterns of Harvard Classes by Department",
       x = "Value",
       y= "Count",
       caption = "Source: Q-Guide Web App")

```

### Exercise 1

Use `sample_n()` to view 5 random rows in the data set `qscores`.

```{r qscores1a, exercise = TRUE}

```

```{r qscores1a-hint, eval = FALSE}
qscores %>% 
  sample_n(...)
```

### Exercise 2

Now let's practice using summary statistics like `mean()` with our data. Take the `mean()` of the `hours` column. Use the `$` operator to extract the `hours` column.

```{r qscores1b, exercise = TRUE}

```

```{r qscores1b-hint, eval = FALSE}
mean(qscores$hours)
```

### Exercise 3

Start a pipe with `qscores` and `select()` the `department` and `hours` columns.

```{r qscores2, exercise = TRUE}

```

```{r qscores2-hint, eval = FALSE}
qscores %>%
  select(..., ...)
```

### Exercise 4

Next, group the data by `department`.

```{r qscores3, exercise = TRUE}

```

```{r qscores3-hint, eval = FALSE}
Use the group_by() function.
```

### Exercise 5

Use `summarize()` to create 3 new variables. `num_classes` should equal the number of rows in each `department` group. `mean_hours` should equal the `mean()` of `hours`. `sd_hours`should equal the `sd()`of `hours`.


```{r qscores4, exercise = TRUE}

```

```{r qscores4-hint-1, eval = FALSE}
The n() function returns the number of rows in each group.
```

```{r qscores4-hint-2, eval = FALSE}
qscores %>%
  ... %>%
  ... %>%
  summarize(num_classes = n(), 
            mean_hours = ..., 
            sd_hours = ...)
```

### Exercise 6

`arrange()` the data set by `num_classes` in `desc()`ending order.

```{r qscores5, exercise = TRUE}

```

```{r qscores5-hint, eval = FALSE}
... %>%
  arrange(desc(...))
```

### Exercise 7

Now use `slice()` to return the top 3 rows of the data set, i.e. the 3 largest departments at Harvard by number of classes.

```{r qscores6, exercise = TRUE}

```

```{r qscores6-hint-1, eval = FALSE}
Remember that a:b returns all of the numbers from a to b. For example, 1:10 returns every number between 1 and 10.
```

```{r qscores6-hint-2, eval = FALSE}
... %>% 
  slice (...)
```

### Exercise 8

Group the data by `department` again. We do so  because the data is no longer grouped since we removed some `department`s with our `slice()` statement.

```{r qscores7, exercise = TRUE}

```

```{r qscores7-hint, eval = FALSE}
... %>%
  group_by(department)
```

### Exercise 9

Using `summarize()`, create a new variable, `rnorm_values`. `rnorm_values` should be equal to the result of an `rnorm()` statement. Within `rnorm()`, set `n` equal to `num_classes`, `mean` to `mean_hours`, and `sd` to `sd_hours`.


```{r qscores8, exercise = TRUE}

```

```{r qscores8-hint, eval = FALSE}
... %>%
  summarize(rnorm_values = rnorm(... = ..., ... = ..., ... = ...))
```

### Exercise 10

Lastly, `arrange()` by `department`. Assign all your work you have done so far to an object named `q_subset`.

```{r qscores0, exercise = TRUE}

```

### Exercise 11

Our next goal will be to create a new column with the homework values of the *actual* Harvard classes. Start a new pipe at the very beginning of your code. Use the pipe to `filter()` `qscores` to the "ECON," "MATH," and "GOV" departments (which we have already discovered are the 3 largest departments in our data set).

```{r qscores9, exercise = TRUE}

```

```{r qscores9-hint-1, eval = FALSE}
Remember to use the %in% operator along with the c() function.
```

```{r qscores9-hint-2, eval = FALSE}
qscores %>%
  filter(department %in% c(..., ..., ...))
```

### Exercise 12

Lastly, `arrange()` by `department`. Assign your code to an object named `q_subset2`.

```{r qscores10, exercise = TRUE}

```

```{r qscores10-hint, eval = FALSE}
q_subset_2 <- qscores %>%
  filter(department %in% c("ECON", "MATH", "GOV")) %>% 
  arrange(...)
```

### Exercise 13

Finally, use `left_join()`. The first argument to `left_join()` should be `q_subset` and the second argument should be `q_subset_2`. The third argument should set `by` to "department".

```{r qscores12-setup}
q_subset_2 <- qscores %>%
  filter(department %in% c("ECON", "MATH", "GOV")) %>%
  arrange(department)

q_subset <- qscores %>%
  select(department, hours) %>%
  group_by(department) %>%
  summarize(num_classes = n(), 
            mean_hours = mean(hours), 
            sd_hours = sd(hours)) %>%
  arrange(desc(num_classes)) %>%
  slice(1:3) %>%
  group_by(department) %>%
  summarize(rnorm_values = rnorm(n = num_classes, 
                                 mean = mean_hours, 
                                 sd = sd_hours)) %>%
  arrange(department)
```


```{r qscores12, exercise = TRUE}

```

```{r qscores12-hint, eval = FALSE}
left_join(..., ..., by = "...")
```

### Exercise 14

Let's now use `pivot_longer()` to transform the columns `rnorm_values` and `hours` into two new columns: "type" and "value". "type" should equal either `rnorm_values` or `hours` values. "value" should equal the value currently contained in one of those two columns. Assign your code so far to an object named `q_join`.


```{r qscores13-setup}
q_subset_2 <- qscores %>%
  filter(department %in% c("ECON", "MATH", "GOV")) %>%
  arrange(department)

q_subset <- qscores %>%
  select(department, hours) %>%
  group_by(department) %>%
  summarize(num_classes = n(), 
            mean_hours = mean(hours), 
            sd_hours = sd(hours)) %>%
  arrange(desc(num_classes)) %>%
  slice(1:3) %>%
  group_by(department) %>%
  summarize(rnorm_values = rnorm(n = num_classes, 
                                 mean = mean_hours, 
                                 sd = sd_hours)) %>%
  arrange(department)
```

```{r qscores13, exercise = TRUE}

```

```{r qscores13-hint, eval = FALSE}
q_join <- left_join(q_subset, q_subset_2, by = "department") %>%
  pivot_longer(cols = c(rnorm_values, hours), 
               names_to = "...", 
               values_to = "...")
```

### Exercise 15

Let's now use `ggplot()`, using `q_join` as our data, to make a histogram that maps `value` to the x-axis. Give the histogram a `binwidth` of 2.

```{r qscores14-setup}
q_join <- left_join(q_subset, q_subset_2, by = "department") %>%
  pivot_longer(cols = c(rnorm_values, hours), 
               names_to = "type", 
               values_to = "value")
```

```{r qscores14, exercise = TRUE}

```

```{r qscores14-hint, eval = FALSE}
ggplot(data = ..., 
       mapping = aes(x = ...)) +
    geom_histogram(binwidth = ...)
```

### Exercise 16

Add the layer `facet_wrap()` to facet our histogram by `department`. Also change the aesthetic of our plot by adding the layer `theme_bw()`.

```{r qscores15-setup}
q_join <- left_join(q_subset, q_subset_2, by = "department") %>%
  pivot_longer(cols = c(rnorm_values, hours), 
               names_to = "type", 
               values_to = "value")
```

```{r qscores15, exercise = TRUE}

```

```{r qscores15-hint-1, eval = FALSE}
Within facet_wrap(), remember to put a ~ before the variable you want to facet by.
```

```{r qscores15-hint-2, eval = FALSE}
ggplot( ...,aes(x = ...)) +
    geom_histogram(binwidth = ...) + 
  facet_wrap(...) +
  theme_bw()
```

### Exercise 17

To finish your plot, use `labs()` to give the graph a title, subtitle, axis labels, and caption of your choice.

Reminder: This is what your graph should look like. 

```{r}
q_subset_2 <- qscores %>%
  filter(department %in% c("ECON", "MATH", "GOV")) %>%
  arrange(department)

q_subset <- qscores %>%
  select(department, hours) %>%
  group_by(department) %>%
  summarize(num_classes = n(), 
            mean_hours = mean(hours), 
            sd_hours = sd(hours)) %>%
  arrange(desc(num_classes)) %>%
  slice(1:3) %>%
  group_by(department) %>%
  summarize(rnorm_values = rnorm(n = num_classes, 
                                 mean = mean_hours, 
                                 sd = sd_hours)) %>%
  arrange(department)

q_join <- left_join(q_subset, q_subset_2, by = "department") %>%
  pivot_longer(cols = c(rnorm_values, hours), 
               names_to = "type", 
               values_to = "value")

ggplot(data = q_join, mapping = aes(x = value)) +
    geom_histogram(binwidth = 2) +
     facet_wrap(~ department) + 
  theme_bw()+
  labs(title = " Homework Patterns of Harvard Classes by Department",
       x = "Value",
       y= "Count",
       caption = "Source: Q-Guide Web App")

```

```{r qscores16-setup}
q_subset_2 <- qscores %>%
  filter(department %in% c("ECON", "MATH", "GOV")) %>%
  arrange(department)

q_subset <- qscores %>%
  select(department, hours) %>%
  group_by(department) %>%
  summarize(num_classes = n(), 
            mean_hours = mean(hours), 
            sd_hours = sd(hours)) %>%
  arrange(desc(num_classes)) %>%
  slice(1:3) %>%
  group_by(department) %>%
  summarize(rnorm_values = rnorm(n = num_classes, 
                                 mean = mean_hours, 
                                 sd = sd_hours)) %>%
  arrange(department)

q_join <- left_join(q_subset, q_subset_2, by = "department") %>%
  pivot_longer(cols = c(rnorm_values, hours), 
               names_to = "type", 
               values_to = "value")
```

```{r qscores16, exercise = TRUE}

```


## National Election Studies
###

<!-- DK: Lots of questions about .fun = first2. This either needs to be explained more slowly or left out. I am not even sure what it does, or what last2 does. -->

`nes`, short for "National Election Studies," contains the personal and political
information of almost 40,000 American voters, as well as whether or not they voted in that year's presidential election. The goal of this exercise is to replicate this plot:

```{r, echo=FALSE}
nes_plot <- nes %>%
  select(year, education, pres_appr, ideology, voted) %>%
  filter(education %in% c("Some Highschool", "Highschool", 
                          "Some College", "Adv. Degree")) %>%
  droplevels() %>%
  mutate(opinion = as.factor(if_else(
    condition = str_detect(pres_appr, "prove"),
    true = "has_opinion",
    false = "no_opinion"))) %>%
  drop_na() %>%
  group_by(year, voted, opinion, education) %>%
  summarize(count = n()) %>%
  pivot_wider(names_from = voted, values_from = count) %>%
  mutate(turnout = Yes / (Yes + No)) %>%
  drop_na() %>%
  ggplot(aes(x = year,
             y = turnout,
             color = fct_reorder2(education, year,
                                  turnout, .fun = first2),
             linetype = fct_reorder2(education, year, 
                                     turnout, .fun = first2))) +
  geom_line() +
  facet_wrap(~ opinion) +
  scale_color_brewer(palette = "Spectral", name = "education") +
  scale_linetype(name = "education") +
  labs(title = "Turnout and Opinions Over Time",
       subtitle = "People with opinions are more likely to vote",
       x = "Turnout Percentage",
       y = "Year")

nes_plot
```

Good luck!



### Exercise 1

Start by running `skim()` on `nes`. See if you can figure out the first and last
years in the data set. You may need to load the **skimr** package first.

```{r nes1, exercise = TRUE}

```


### Exercise 2

Use `levels()` and the `$` operator to explore the levels of the `education` variable.

```{r nes2, exercise = TRUE}

```

```{r nes2-hint}
# The factor that we'd like to investigate is nes$education.
```


### Exercise 3

Select the `year`, `education`, `pres_appr`, `ideology`, and `voted` columns from `nes`.

```{r nes3, exercise = TRUE}

```


### Exercise 4

Continue by filtering the tibble such that `education` is either "Some Highschool," "Highschool," "Some College," or "Adv. Degree."

```{r nes4, exercise = TRUE}

```

```{r nes4-hint}
# Remember to use the %in% operator along with the c() function.
```


### Exercise 5

After filtering a factor, always remember that the *levels* of the factor have not been removed. To fix this, add a call in the pipe that drops (i.e. permanently removes) all deleted levels.

```{r nes5, exercise = TRUE}

```

```{r nes5-hint}
# Use the droplevels() function.
```


### Exercise 6

The dplyr `if_else()` function can be used alongside `mutate()` and `as.factor()` to create a factor with two levels depending on whether a certain `condition` is met. Run the code below to see how we can use `if_else()` to separate the `nes` data set into 2 groups based on whether the value of `ideology` is positive.

```{r nes6, exercise = TRUE}
nes %>%
  select(year, education, pres_appr, ideology, voted) %>%
  filter(education %in% c("Some Highschool", "Highschool", 
                          "Some College", "Adv. Degree")) %>%
  droplevels() %>%
  mutate(pos_ideology = as.factor(if_else(condition = ideology > 0,
                                          true = "ideology_is_positive",
                                          false = "ideology_not_positive")))
```


### Exercise 7

Now, use `if_else()` and `mutate()` tto create a new variable, `opinion`. `opinion` should be a **factor** that equals "has_opinion" if that person either approves *or* disapproves of the president, but "no_opinion" otherwise. To do this, use the `if_else()` function with the condition being detection of the pattern "prove" in the string `pres_appr`. You can remove from your pipe the creation of `pos_ideology` since we won't be using that variable.

```{r nes7, exercise = TRUE, exercise.lines = 10}

```

```{r nes7-hint-1}
# Remember to use as.factor() before if_else().
```

```{r nes7-hint-2}
# The function we want to use for the condition is str_detect().
```

```{r nes7-hint-3, eval = FALSE}
nes %>%
  select(year, education, pres_appr, ideology, voted) %>%
  filter(education %in% c("Some Highschool", "Highschool", 
                          "Some College", "Adv. Degree")) %>%
  droplevels() %>%
  mutate(opinion = as.factor(if_else(condition = str_detect(...),
                                     true = ...,
                                     false = ...)))
```


### Exercise 8

Our goal for the next few exercises will be to calculate voter turnout based on education and whether or not the voter has an opinion of the president at that time.

To start, group the tibble by `year`, `voted`, `opinion`, and `education`. Then, use `summarize()` to make a new variable, `count`, that simply counts the number of people (i.e. rows) in each group. What goes wrong?

```{r nes8, exercise = TRUE, exercise.lines = 10}

```

```{r nes8-hint}
# Remember that the n() function counts the number of rows in each group.
```


### Exercise 9

If we look closely, many of our rows have a value of `NA` for either `voted` or `opinion`. Furthermore, `n()` doesn't have an `na.rm` argument. To remove the `NA`s, use tidyr's `drop_na()` to drop any rows with missing values for any variable before the call to `group_by()` and `summarize()`.

```{r nes9, exercise = TRUE, exercise.lines = 15}

```

```{r nes9-hint, eval = FALSE}
nes %>%
  select(year, education, pres_appr, ideology, voted) %>%
  filter(education %in% c("Some Highschool", "Highschool", 
                          "Some College", "Adv. Degree")) %>%
  droplevels() %>%
  mutate(opinion = as.factor(if_else(condition = str_detect(pres_appr, "prove"),
                                     true = "has_opinion",
                                     false = "no_opinion"))) %>%
  drop_na() %>%
  group_by(year, voted, opinion, education) %>%
  summarize(count = ...)
```


### Exercise 10

Our goal is to calculate voter turnout within each category, the number of people who voted divided by the total number of people. Therefore, we want `Yes` and `No` (currently in the `voted` column) to be their own columns with the values that are currently in the `count` column.

Use one of the `pivot_` functions to tidy our data in this way.

```{r nes10, exercise = TRUE, exercise.lines = 15}

```

```{r nes10-hint-1}
# Because we're making new columns from values, we want the pivot_wider()
# function.
```

```{r nes10-hint-2, eval = FALSE}
... %>%
  pivot_wider(names_from = ..., values_from = ...)
```


### Exercise 11

Great job! Now, to calculate turnout, use `mutate()` to create another variable, `turnout`, equal to the number of people who voted (the number of `Yes`) divided by the total number of people in each category. To make sure you are caught up, we provide the pipe as it should appear by this stage. You need to add a line to create `turnout`. But look at the data when you do! See the rows with are NA for turnout? That will mess up our graphics. So, use `drop_na()` again to remove them.

```{r nes11, exercise = TRUE, exercise.lines = 15}
nes %>%
  select(year, education, pres_appr, ideology, voted) %>%
  filter(education %in% c("Some Highschool", "Highschool", 
                          "Some College", "Adv. Degree")) %>%
  droplevels() %>%
  mutate(opinion = as.factor(if_else(condition = str_detect(pres_appr, "prove"),
                                     true = "has_opinion",
                                    false = "no_opinion"))) %>%
  drop_na() %>%
  group_by(year, voted, opinion, education) %>%
  summarize(count = n()) %>%
  pivot_wider(names_from = voted, values_from = count)
```

```{r nes11-hint}
# Remember that the total number of people in each group is (Yes + No).
```


### Exercise 12

Next, use `ggplot()` to make a line graph that maps `year` to the x-axis, `turnout` to the y-axis, and `education` to both the color and linetype aesthetics.

```{r nes12, exercise = TRUE}

```


### Exercise 13

Use `facet_wrap` to facet the graph by opinion.

```{r nes13, exercise = TRUE, exercise.lines = 15}

```


### Exercise 14

<!-- DK: This question ordering is weird and confusing. It is rarely a good idea to guide students to the "wrong" answer and then fix it in the next question. -->

This graph is starting to look pretty good, but the ordering of the legend is a bit confusing. Try using an `fct_` function to reorder the legend (both the color *and* linetype aesthetics) so that Adv. Degree is first, Some College is second, and so on. Something goes wrong with this first attempt, but we will fix it in the next exercise.

```{r nes14, exercise = TRUE, exercise.lines = 15}

```

```{r nes14-hint-1}
# Because this is a line graph, we want to use fct_reorder2().
```


### Exercise 15

Although 3 of the 4 `education` statuses are reordered successfully, Adv. Degree is left on the bottom because it doesn't appear in the second graph. To fix this problem, change the `.fun` argument of both `fct_reorder2()` calls to `first2` (the default is `last2`).

```{r nes15, exercise = TRUE, exercise.lines = 15}

```

```{r nes15-hint, eval = FALSE}
... %>%
  ggplot(aes(x = year, 
             y = turnout,
             color = fct_reorder2(education, year, 
                                  turnout, .fun = ...),
             linetype = fct_reorder2(education, year,
                                     turnout, .fun = ...))) +
  geom_line() +
  facet_wrap(~ opinion)
```


### Exercise 16

Our graph is looking good, but the very long legend title takes up a lot of space. To fix this problem (and to improve the colors of the graph), add a `scale_color_brewer()` function with the "Spectral" palette as well as a `scale_linetype` function. Use **both** scale functions to set the name of the legend to "education."

```{r nes16, exercise = TRUE, exercise.lines = 18}

```

```{r nes16-hint-1}
# The scale_color_brewer() function should take 2 arguments, but the
# scale_linetype() function should only take 1.
```


### Exercise 17

Amazing work! From this graph, we see that Americans with a higher level of education tend to vote more often. Furthermore, Americans with an opinion of the president generally have higher voter turnout than Americans without an opinion of the president. Finally, pretty much 100% of Americans with an advanced degree are able to form an opinion of the president (this is why there is no Advanced Degree line in the no_opinion graph: there are too few data points in the table).

To finish your plot, use `labs()` to give the graph a title and subtitle of your choosing, along with some axis labels. Here is our answer. It is OK if your answer looks somewhat different from ours. Something sure seems fishy about that perfectly flat red line on the right . . . Indeed, there are a couple of things about our plot which could be improved . . . Why not improve them?

```{r, echo=FALSE}
nes_plot
```

```{r nes17, exercise = TRUE, exercise.lines = 20}

```




## Submit

```{r context="setup"}
submission_ui
```

```{r context="server"}
submission_server()
```

