---
title: DGM Logistic
author: Var Kurapati
tutorial:
  id: dgm-logistic
  version: 1.1.0
output:
  learnr::tutorial:
    df_print: default
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: 'Learn to fit logistic regression models and use them to answer questions, applied to employee attrition.'
---

```{r setup, include=FALSE}
library(learnr)
library(tutorial.helpers)
library(knitr)
library(tidyverse)
library(tidymodels)
library(marginaleffects)

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(out.width = '90%')
options(tutorial.exercise.timelimit = 600,
        tutorial.storage = "local")

mod_logistic <- logistic_reg() |>
  set_engine("glm") |>
  fit(Attrition ~ MonthlyIncome + YearsAtCompany + OverTime, data = attrition)
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

## Introduction
###

The `attrition` dataset records 1,470 employees at a large company — their income, tenure, overtime status, and whether they left. Of the 1,470, 237 left — an attrition rate of about 16%.

This tutorial asks a simple question: **can we predict whether an employee will leave from their income, tenure, and overtime status?**

`Attrition` is not a number — it is a yes/no outcome, and that is information a model can use. We use two packages to build and interpret such a model. **[tidymodels](https://www.tidymodels.org/)** fits it. **[marginaleffects](https://marginaleffects.com/)** interprets it — turning raw log-odds coefficients into predicted probabilities that are immediately understandable.

Interpreting a model with **marginaleffects** almost always comes down to one distinction: **marginal** vs. **conditional**. A marginal prediction runs the model on every *real* employee in the dataset and averages the results (the `by` argument). A conditional prediction builds one or more *hypothetical* employees, holding some variables fixed and varying others (the `condition` argument). So every time you see `by`, you are averaging over real employees, and every time you see `condition`, you are looking at a hypothetical.

Every dataset is a shadow cast by some real process — a **data generating mechanism**, or DGM — never the thing itself. Two moves lie ahead: *Courage*, proposing a structure and fitting it to real data (Tidymodels), and *Temperance*, using that fitted machine — with humility — to answer the question we started with (Marginal Effects).

### Exercise 1

Create a repo named `dgm-logistic` and connect to it. Create `analysis.qmd`, title `"Employee Attrition"`, your name as author, `execute: echo: false` in the YAML. Render, open with Live Server, create `.gitignore` with `analysis_files`, commit and push.

In the R Terminal, run:

```
show_file(".gitignore")
```

CP/CR.

```{r introduction-1}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 3)
```

###

```
analysis_files
```

###

Every dataset comes from somewhere. `attrition` is a synthetic dataset modeled after a real IBM HR survey — the employees are fictional, but the patterns in the data reflect real workforce research.

### Exercise 2

In a new code chunk, load the libraries you'll need. Add `#| message: false`. Render.

```
#| message: false
library(tidyverse)
library(tidymodels)
library(marginaleffects)
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r introduction-2}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 10)
```

###

<pre><code>#| message: false
library(tidyverse)
library(tidymodels)
library(marginaleffects)
</code></pre>

###

`attrition` comes with **modeldata**, which `library(tidymodels)` attaches. The data is a shadow of the IBM workforce; the DGM we build will be our best account of the process that cast it.

### Exercise 3

In a new code chunk, print the first 10 rows of `attrition`, narrowed to the four columns this tutorial uses. Render.

```
attrition |>
  select(Attrition, MonthlyIncome, YearsAtCompany, OverTime) |>
  head(10)
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r introduction-3}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 4)
```

###

```{r introduction-3-test}
#| echo: true
attrition |>
  select(Attrition, MonthlyIncome, YearsAtCompany, OverTime) |>
  head(10)
```

###

`Attrition` is the outcome we want to predict — `Yes` means the employee left, `No` means they stayed. `MonthlyIncome` is in dollars. `YearsAtCompany` is tenure. `OverTime` is a yes/no indicator of whether the employee works overtime.

### Exercise 4

Ask AI to create a bar chart of attrition rate by overtime status. Paste its code into a new chunk. Render.

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r introduction-4}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = FALSE,
  incorrect = NULL,
  rows = 10)
```

###

Here's our version, for comparison:

```{r introduction-4-test}
#| echo: true
attrition |>
  count(OverTime, Attrition) |>
  group_by(OverTime) |>
  mutate(prop = n / sum(n)) |>
  filter(Attrition == "Yes") |>
  ggplot(aes(x = OverTime, y = prop)) +
  geom_col(fill = "steelblue") +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Employees who work overtime are more likely to leave",
    x = "Overtime",
    y = "Attrition rate"
  )
```

###

Employees who work overtime leave at about 30% — nearly three times the rate of those who don't. The pattern is clear in the raw data, but a model lets us ask: how much of this gap remains after controlling for income and tenure?

### Exercise 5

Commit and push, with a message like "Add attrition data and initial exploration." In the bash Terminal, run:

```
git log -1
```

CP/CR.

```{r introduction-5}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 5)
```

###

```
commit a1b2c3d4e5f6...
Author: Var Kurapati
Date:   Mon Aug 03 2026
    Add attrition data and initial exploration
```

###

Before we fit anything, it's worth asking where this data came from. Whatever `mod_logistic` learns, it learns about *this* synthetic dataset — not real employees anywhere. Keep asking, as we build the model ahead: *How did this data come to be?*

## Tidymodels
###

Every dataset is produced by some real-world process — a **data generating mechanism**, or DGM. Building one means committing to a structure, choosing a method for estimating it, and fitting it to data: **Structure → Method → Fitting**. `Attrition` is a yes/no outcome, so the structure here is `logistic_reg()`.

The equation a logistic regression fits looks like this:

$$\log\left(\frac{P(\text{Attrition} = \text{Yes})}{1 - P(\text{Attrition} = \text{Yes})}\right) = \beta_0 + \beta_1 \times \text{MonthlyIncome} + \beta_2 \times \text{YearsAtCompany} + \beta_3 \times \text{OverTimeYes}$$

The left-hand side is a log-odds — a number that runs from negative infinity to positive infinity. `predictions()` will convert it back into a probability between 0 and 1.

There is no single "correct" DGM for a given question. Which right-hand-side variables to include is a judgment call — one we will make, and remake, several times in this section.

### Exercise 1

In a new code chunk, count how many employees are in each attrition category, and the attrition rate by overtime status. Render.

```
attrition |> count(Attrition)
attrition |> count(OverTime, Attrition)
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r tidymodels-1}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 6)
```

###

```{r tidymodels-1-test}
#| echo: true
attrition |> count(Attrition)
attrition |> count(OverTime, Attrition)
```

###

Only 237 of 1,470 employees left — 16%. That imbalance matters: a model that always predicted "No" would be right 84% of the time without learning anything at all.

### Exercise 2

In a new code chunk, specify a logistic regression with `logistic_reg()` and pipe it into `set_engine("glm")`. Print the result. Render.

```
logistic_reg() |>
  set_engine("glm")
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r tidymodels-2}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 4)
```

###

```{r tidymodels-2-test}
#| echo: true
logistic_reg() |>
  set_engine("glm")
```

###

`logistic_reg()` proposes the **structure**: a binary outcome modeled as a probability. `set_engine("glm")` picks the **method**: R's classical maximum-likelihood fitting. These are separate decisions — the DGM and our procedure for estimating it are separate things.

### Exercise 3

Update your chunk to pipe into `fit(Attrition ~ OverTime, data = attrition)` — just one predictor for now. Then pipe the result into `tidy(conf.int = TRUE)` and `select(term, estimate, conf.low, conf.high)`. Render.

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r tidymodels-3}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 8)
```

###

```{r tidymodels-3-test}
#| echo: true
logistic_reg() |>
  set_engine("glm") |>
  fit(Attrition ~ OverTime, data = attrition) |>
  tidy(conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high)
```

###

`fit()` is where the mechanism meets real data — step three of Structure → Method → Fitting. The `OverTimeYes` coefficient is about 1.38 in log-odds, with an interval well clear of zero: working overtime is associated with higher odds of leaving.

### Exercise 4

Edit the formula to add `MonthlyIncome` and `YearsAtCompany`. Render.

```
logistic_reg() |>
  set_engine("glm") |>
  fit(Attrition ~ MonthlyIncome + YearsAtCompany + OverTime,
      data = attrition) |>
  tidy(conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high)
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r tidymodels-4}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 8)
```

###

```{r tidymodels-4-test}
#| echo: true
logistic_reg() |>
  set_engine("glm") |>
  fit(Attrition ~ MonthlyIncome + YearsAtCompany + OverTime,
      data = attrition) |>
  tidy(conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high)
```

###

All three intervals exclude zero — by this heuristic, all three predictors earn their place. `MonthlyIncome` is negative: higher earners are less likely to leave. `YearsAtCompany` is also negative: more tenured employees are less likely to leave.

### Exercise 5

What about job satisfaction? Edit the formula to add `JobSatisfaction`. Render.

```
logistic_reg() |>
  set_engine("glm") |>
  fit(Attrition ~ MonthlyIncome + YearsAtCompany + OverTime + JobSatisfaction,
      data = attrition) |>
  tidy(conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high)
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r tidymodels-5}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 8)
```

###

```{r tidymodels-5-test}
#| echo: true
logistic_reg() |>
  set_engine("glm") |>
  fit(Attrition ~ MonthlyIncome + YearsAtCompany + OverTime + JobSatisfaction,
      data = attrition) |>
  tidy(conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high)
```

###

`JobSatisfaction` is categorical, so it produces one row per level — and the intervals are mixed: some levels clearly exclude zero, others don't. This is exactly the "many possible DGMs" problem: there's no automatic rule that resolves it. For this tutorial, we'll make the judgment call to go back to the three-variable model as our final DGM.

### Exercise 6

Edit your working chunk one last time: remove `JobSatisfaction`, remove the `tidy()`/`select()` steps, and assign the result to `mod_logistic`. Print it. Render.

```
mod_logistic <- logistic_reg() |>
  set_engine("glm") |>
  fit(Attrition ~ MonthlyIncome + YearsAtCompany + OverTime,
      data = attrition)
mod_logistic
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r tidymodels-6}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 8)
```

###

```{r tidymodels-6-test}
#| echo: true
mod_logistic <- logistic_reg() |>
  set_engine("glm") |>
  fit(Attrition ~ MonthlyIncome + YearsAtCompany + OverTime,
      data = attrition)
mod_logistic
```

###

From here on, you never touch this formula again. `mod_logistic` is the fixed, saved model every later exercise addresses — the candidates you discarded never got a permanent name at all, which was deliberate: there are always more DGMs you *could* fit than you actually will, and we never know for certain which one is true.

### Exercise 7

Add `#| cache: true` to the top of your `mod_logistic` chunk, and add `*_cache/` to your `.gitignore`. In the R Terminal, run:

```
show_file(".gitignore")
```

CP/CR.

```{r tidymodels-7}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 4)
```

###

```
analysis_files
*_cache/
```

###

Structure → Method → Fitting. You have now completed all three steps. `mod_logistic` is your fitted DGM — the machine every later question will be addressed to.

### Exercise 8

In a new code chunk, run the following to see `mod_logistic`'s coefficients. Render.

```
mod_logistic |>
  tidy(conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high) |>
  mutate(across(where(is.numeric), \(x) round(x, 4)))
```

The coefficient on `OverTimeYes` is about 1.38. What does that mean?

```{r tidymodels-8}
question_text(NULL,
  answer("Employees who work overtime have higher log-odds of leaving than those who don't, by about 1.38 — holding income and tenure fixed. The confidence interval (0.90 to 1.86) excludes zero, so we can be reasonably confident the direction is positive.", correct = TRUE),
  allow_retry = FALSE,
  incorrect = NULL,
  rows = 6)
```

###

```{r tidymodels-8-test}
#| echo: true
mod_logistic |>
  tidy(conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high) |>
  mutate(across(where(is.numeric), \(x) round(x, 4)))
```

###

Here's the answer:

> Employees who work overtime have higher log-odds of leaving than those who don't, by about 1.38 — holding income and tenure fixed. The confidence interval (0.90 to 1.86) excludes zero, so we can be reasonably confident the direction is positive.

###

For a logistic model, coefficient interpretation stops at the sign and whether the interval excludes zero. We can say overtime is associated with higher odds of leaving — we cannot easily say *how much* higher without converting to probabilities, which is exactly what the next section does.

### Exercise 9

The coefficient on `MonthlyIncome` is about −0.0001. What does that mean?

```{r tidymodels-9}
question_text(NULL,
  answer("Higher monthly income is associated with lower log-odds of leaving — the coefficient is negative, and the confidence interval excludes zero. The exact magnitude is hard to interpret from the raw log-odds.", correct = TRUE),
  allow_retry = FALSE,
  incorrect = NULL,
  rows = 6)
```

###

Here's the answer:

> Higher monthly income is associated with lower log-odds of leaving — the coefficient is negative, and the confidence interval excludes zero. The exact magnitude is hard to interpret from the raw log-odds.

###

Use that same pattern — sign, whether the interval excludes zero, no claim about magnitude — whenever you're asked to interpret a coefficient in a logistic model. The fitted DGM is not the answer to anything by itself; it is the machine we built so we can answer questions.

### Exercise 10

Add the equation for `mod_logistic` as a LaTeX math block above the model chunk:

$$\log\left(\frac{P(\text{Attrition} = \text{Yes})}{1 - P(\text{Attrition} = \text{Yes})}\right) = -1.277 - 0.0001 \times \text{MonthlyIncome} - 0.045 \times \text{YearsAtCompany} + 1.380 \times \text{OverTimeYes}$$

Render. In the R Terminal, run `show_file("analysis.qmd")`. CP/CR just the equation line and the `mod_logistic` chunk right below it.

```{r tidymodels-10}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 20)
```

###

The relevant part of your output should look like this:

<pre><code>$$\log\left(\frac{P(\text{Attrition} = \text{Yes})}{1 - P(\text{Attrition} = \text{Yes})}\right) = -1.277 - 0.0001 \times \text{MonthlyIncome} - 0.045 \times \text{YearsAtCompany} + 1.380 \times \text{OverTimeYes}$$

#| cache: true
mod_logistic <- logistic_reg() |>
  set_engine("glm") |>
  fit(Attrition ~ MonthlyIncome + YearsAtCompany + OverTime, data = attrition)
mod_logistic
</code></pre>

###

This equation IS the fitted DGM. Unlike a linear equation, you can't plug numbers in and read off a probability directly — the left-hand side is a log-odds, which has to be converted back into a probability. That conversion is exactly what the next section does.

### Exercise 11

Commit and push, with a message like "Fit final logistic regression DGM for employee attrition." In the bash Terminal, run:

```
git log -1
```

CP/CR.

```{r tidymodels-11}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 5)
```

###

```
commit b2c3d4e5f6a7...
Author: Var Kurapati
Date:   Mon Aug 03 2026
    Fit final logistic regression DGM for employee attrition
```

###

`mod_logistic` is not the answer to anything by itself — it's the machine we built so we can answer questions, which is exactly what the next section does with it.

## Marginal Effects
###

We built the DGM with *Courage*. Now we practice *Temperance*: using it — with humility — to answer the question we started with.

Interpreting a model with **marginaleffects** almost always comes down to one distinction: **marginal** vs. **conditional**. So every time you see `by`, you are averaging over real employees, and every time you see `condition`, you are looking at a hypothetical.

If Tidymodels was Structure → Method → Fitting, this section is **Question → Units → Answer**: pose the question as a quantity, specify which units you're asking about, then run the machine.

In this section we cover five functions from [**marginaleffects**](https://marginaleffects.com/): `predictions()`, `avg_predictions()`, `comparisons()`, `avg_comparisons()`, and `plot_predictions()`. The one thing that changes for a logistic model: every prediction comes back as one row per outcome category, so you'll filter to `group == "Yes"` to keep just the probability of leaving.

### Exercise 1

In a new code chunk, run `predictions()` for one hypothetical employee: $4,000/month, 3 years at the company, no overtime. Add `type = "class"`. Render.

```
predictions(mod_logistic,
  newdata = data.frame(MonthlyIncome = 4000,
                       YearsAtCompany = 3,
                       OverTime = "No"),
  type = "class")
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-1}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 6)
```

###

```{r predictions-1-test}
#| echo: true
predictions(mod_logistic,
  newdata = data.frame(MonthlyIncome = 4000,
                       YearsAtCompany = 3,
                       OverTime = "No"),
  type = "class")
```

###

The `estimate` column just says "No" — the machine's best guess for this hypothetical employee. This is a **conditional** prediction; no real employee has to match this exact combination.

### Exercise 2

Update your chunk to change `type = "class"` to `type = "prob"`. Render.

```
predictions(mod_logistic,
  newdata = data.frame(MonthlyIncome = 4000,
                       YearsAtCompany = 3,
                       OverTime = "No"),
  type = "prob")
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-2}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 6)
```

###

```{r predictions-2-test}
#| echo: true
predictions(mod_logistic,
  newdata = data.frame(MonthlyIncome = 4000,
                       YearsAtCompany = 3,
                       OverTime = "No"),
  type = "prob")
```

###

Now there are two rows — one for each outcome category — and the `estimate` column shows the predicted probability: about 13.6% chance of leaving. The confident-sounding "No" from Exercise 1 was actually a fairly close call once you see the number behind it.

### Exercise 3

Update your chunk to compare two employees: the same $4,000/month, 3-year employee, once with `OverTime = "No"` and once with `OverTime = "Yes"`. Add `type = "prob"`, then pipe to `filter(group == "Yes")`. Render.

```
predictions(mod_logistic,
  newdata = data.frame(
    MonthlyIncome  = c(4000, 4000),
    YearsAtCompany = c(3, 3),
    OverTime       = c("No", "Yes")),
  type = "prob") |>
  filter(group == "Yes")
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-3}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 8)
```

###

```{r predictions-3-test}
#| echo: true
predictions(mod_logistic,
  newdata = data.frame(
    MonthlyIncome  = c(4000, 4000),
    YearsAtCompany = c(3, 3),
    OverTime       = c("No", "Yes")),
  type = "prob") |>
  filter(group == "Yes")
```

###

Same income and tenure, only `OverTime` differs — the entire gap between the two rows is the `OverTimeYes` coefficient converted from log-odds into probability. This is the counterfactual question: same employee, two worlds, one with overtime and one without.

### Exercise 4

Update your chunk to predict the probability for the first actual employee in the dataset. Pass only the three columns the model uses. Add `type = "prob"` and `filter(group == "Yes")`. Render.

```
predictions(mod_logistic,
  newdata = attrition[1, c("MonthlyIncome", "YearsAtCompany", "OverTime")],
  type = "prob") |>
  filter(group == "Yes")
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-4}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 5)
```

###

```{r predictions-4-test}
#| echo: true
predictions(mod_logistic,
  newdata = attrition[1, c("MonthlyIncome", "YearsAtCompany", "OverTime")],
  type = "prob") |>
  filter(group == "Yes")
```

###

This employee's outcome is already known — so why predict it? Because the fitted DGM earns its keep on someone not in the data, or on a real person with one thing changed. Looking up a known value is never the reason to call `predictions()`.

### Exercise 5

Update your chunk to use `avg_predictions()` with `by = "OverTime"` and `type = "prob"`, filtered to `group == "Yes"`. Render.

```
avg_predictions(mod_logistic, by = "OverTime", type = "prob") |>
  filter(group == "Yes")
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-5}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 5)
```

###

```{r predictions-5-test}
#| echo: true
avg_predictions(mod_logistic, by = "OverTime", type = "prob") |>
  filter(group == "Yes")
```

###

This is a **marginal** prediction — run the model on every real employee, then average within overtime groups. The gap between the two rows is the overtime effect, averaged over the actual income and tenure distribution of real employees in each group.

### Exercise 6

Now build a **conditional** prediction using `datagrid()`: three hypothetical employees at $3,000, $6,000, and $9,000 monthly income, with tenure and overtime held at their typical values. Add `type = "prob"` and filter to `group == "Yes"`. Render.

```
predictions(mod_logistic,
  newdata = datagrid(MonthlyIncome = c(3000, 6000, 9000)),
  type = "prob") |>
  filter(group == "Yes")
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-6}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 8)
```

###

```{r predictions-6-test}
#| echo: true
predictions(mod_logistic,
  newdata = datagrid(MonthlyIncome = c(3000, 6000, 9000)),
  type = "prob") |>
  filter(group == "Yes")
```

###

`datagrid()` fixes every variable you don't mention at a representative value and varies only the ones you specify. This is the **conditional** counterpart to `avg_predictions()` — no real employee needs to exist at any of these three incomes.

### Exercise 7

A prediction says what the model expects; a **comparison** says how much that expectation changes when a predictor changes. In a new code chunk, use `comparisons()` to compute the predicted change in attrition probability when `OverTime` switches from "No" to "Yes", for every real employee. Add `type = "prob"`. Render.

```
cmp <- comparisons(mod_logistic,
  variables = "OverTime",
  type = "prob")
nrow(cmp)
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-7}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 6)
```

###

```{r predictions-7-test}
#| echo: true
cmp <- comparisons(mod_logistic,
  variables = "OverTime",
  type = "prob")
nrow(cmp)
```

###

2,940 rows — two per employee, one per outcome category, just like `predictions()`. Each row is the predicted change in one outcome category's probability for one specific employee if their overtime status were switched from No to Yes. Far too many numbers to read; the next exercise averages them.

### Exercise 8

Update your chunk to use `avg_comparisons()` instead, filtered to `group == "Yes"`. Render.

```
avg_comparisons(mod_logistic,
  variables = "OverTime",
  type = "prob") |>
  filter(group == "Yes")
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-8}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 8)
```

###

```{r predictions-8-test}
#| echo: true
avg_comparisons(mod_logistic,
  variables = "OverTime",
  type = "prob") |>
  filter(group == "Yes")
```

###

About 15 percentage points — switching from no overtime to overtime is associated with an average increase of about 15 points in the predicted probability of leaving. This is the `OverTimeYes` coefficient from Tidymodels translated into units a person can use: not log-odds, but probability points.

### Exercise 9

Update your chunk to ask the same question about income: the average predicted change in attrition probability for a $1,000 increase in monthly income. Add `type = "prob"` and filter to `group == "Yes"`. Render.

```
avg_comparisons(mod_logistic,
  variables = list(MonthlyIncome = 1000),
  type = "prob") |>
  filter(group == "Yes")
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-9}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 8)
```

###

```{r predictions-9-test}
#| echo: true
avg_comparisons(mod_logistic,
  variables = list(MonthlyIncome = 1000),
  type = "prob") |>
  filter(group == "Yes")
```

###

About −1.4 percentage points per $1,000 — a modest effect compared to the 15-point gap from overtime. The income effect is real and statistically solid, but small next to what overtime does in this DGM.

### Exercise 10

Ask your AI assistant to write `plot_predictions()` code that visualizes how predicted attrition probability varies with `MonthlyIncome`, using `mod_logistic`, `type = "prob"`, and `condition = "MonthlyIncome"` with `draw = FALSE`, piped into a `filter(group == "Yes")` step then `ggplot()`. Render.

```
plot_predictions(mod_logistic,
  condition = "MonthlyIncome",
  type = "prob", draw = FALSE) |>
  filter(group == "Yes") |>
  ggplot(aes(x = MonthlyIncome, y = estimate)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  geom_line() +
  labs(
    title = "Predicted attrition probability decreases with income",
    x = "Monthly income ($)",
    y = "Predicted probability of leaving"
  ) +
  scale_x_continuous(labels = scales::dollar) +
  scale_y_continuous(labels = scales::percent)
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-10}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 10)
```

###

```{r predictions-10-test}
#| echo: true
plot_predictions(mod_logistic,
  condition = "MonthlyIncome",
  type = "prob", draw = FALSE) |>
  filter(group == "Yes") |>
  ggplot(aes(x = MonthlyIncome, y = estimate)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  geom_line() +
  labs(
    title = "Predicted attrition probability decreases with income",
    x = "Monthly income ($)",
    y = "Predicted probability of leaving"
  ) +
  scale_x_continuous(labels = scales::dollar) +
  scale_y_continuous(labels = scales::percent)
```

###

`plot_predictions()` draws the machine's answers. With `condition = "MonthlyIncome"`, the machine runs on hypothetical employees with `YearsAtCompany` and `OverTime` held at their typical values. The curve bends rather than running in a straight line — probabilities are squeezed between 0 and 1, so the same change in log-odds produces a smaller change in probability at the extremes.

### Exercise 11

Ask your AI assistant to extend that plot to show predicted attrition probability across both `MonthlyIncome` and `OverTime`, using `condition = c("MonthlyIncome", "OverTime")` — color the lines by `OverTime`. Render.

```
plot_predictions(mod_logistic,
  condition = c("MonthlyIncome", "OverTime"),
  type = "prob", draw = FALSE) |>
  filter(group == "Yes") |>
  ggplot(aes(x = MonthlyIncome, y = estimate, color = OverTime)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = OverTime),
    alpha = 0.15, color = NA) +
  geom_line() +
  labs(
    title = "Predicted attrition probability by income and overtime",
    x = "Monthly income ($)",
    y = "Predicted probability of leaving"
  ) +
  scale_x_continuous(labels = scales::dollar) +
  scale_y_continuous(labels = scales::percent)
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-11}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 10)
```

###

```{r predictions-11-test}
#| echo: true
plot_predictions(mod_logistic,
  condition = c("MonthlyIncome", "OverTime"),
  type = "prob", draw = FALSE) |>
  filter(group == "Yes") |>
  ggplot(aes(x = MonthlyIncome, y = estimate, color = OverTime)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = OverTime),
    alpha = 0.15, color = NA) +
  geom_line() +
  labs(
    title = "Predicted attrition probability by income and overtime",
    x = "Monthly income ($)",
    y = "Predicted probability of leaving"
  ) +
  scale_x_continuous(labels = scales::dollar) +
  scale_y_continuous(labels = scales::percent)
```

###

When two variables are passed to `condition`, **marginaleffects** varies the first continuously and shows the second at its distinct values — that's what `color = OverTime` splits into two separate curves. The gap between the curves is the overtime effect, which the `avg_comparisons()` exercises measured as about 15 percentage points.

### Exercise 12

Now plot a **marginal** quantity instead: use `plot_predictions()` with `by = "OverTime"`, `type = "prob"`, and `draw = FALSE`, filtered to `group == "Yes"`, to visualize average predicted attrition probability by overtime group. Render.

```
plot_predictions(mod_logistic,
  by = "OverTime",
  type = "prob", draw = FALSE) |>
  filter(group == "Yes") |>
  ggplot(aes(x = OverTime, y = estimate)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) +
  labs(
    title = "Average predicted attrition probability by overtime status",
    x = NULL,
    y = "Average predicted probability of leaving"
  ) +
  scale_y_continuous(labels = scales::percent)
```

In the R Terminal, run `show_file("analysis.qmd", chunk = "Last")`. CP/CR.

```{r predictions-12}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 10)
```

###

```{r predictions-12-test}
#| echo: true
plot_predictions(mod_logistic,
  by = "OverTime",
  type = "prob", draw = FALSE) |>
  filter(group == "Yes") |>
  ggplot(aes(x = OverTime, y = estimate)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) +
  labs(
    title = "Average predicted attrition probability by overtime status",
    x = NULL,
    y = "Average predicted probability of leaving"
  ) +
  scale_y_continuous(labels = scales::percent)
```

###

Same function, same package — but passing `by` instead of `condition` switches from a hypothetical relationship to an average over real employees, grouped by overtime status. `condition` is a conditional, counterfactual view; `by` is a marginal, descriptive one — the same two numbers `avg_predictions()` gave you earlier, drawn as a picture.

### Exercise 13

Commit and push, with a message like "Add marginaleffects predictions, comparisons, and plots." In the bash Terminal, run:

```
git log -1
```

CP/CR.

```{r predictions-13}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 5)
```

###

```
commit f6a7b8c9d0e1...
Author: Var Kurapati
Date:   Mon Aug 03 2026
    Add marginaleffects predictions, comparisons, and plots
```

###

You have now used `predictions()`, `avg_predictions()`, `comparisons()`, `avg_comparisons()`, and `plot_predictions()` on a logistic regression model. The same five functions work identically on multinomial and ordered models — except there, filtering by `group` becomes more interesting, since there are more than two categories to choose from.

## Summary
###

You have built an analysis page that fits a logistic regression model and visualizes its predictions. Now wire it into a navigable Quarto website and publish it.

### Exercise 1

Create a `_quarto.yml` file at the top level of your repo:

```
project:
  type: website

website:
  title: "Employee Attrition"
  navbar:
    left:
      - href: analysis.qmd
        text: Analysis
      - href: about.qmd
        text: About

format:
  html:
    theme: cosmo
```

In the bash Terminal, run:

```
quarto render
ls
```

In the R Terminal, run `show_file("_quarto.yml")`. CP/CR.

```{r summary-1}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 15)
```

###

<pre><code>project:
  type: website

website:
  title: "Employee Attrition"
  navbar:
    left:
      - href: analysis.qmd
        text: Analysis
      - href: about.qmd
        text: About

format:
  html:
    theme: cosmo
</code></pre>

###

`_quarto.yml` turns a folder of `.qmd` files into a navigable website. Without it, each page renders independently.

### Exercise 2

Create `about.qmd` with a YAML title of `"About"`, your name, and today's date. Clean up `analysis.qmd` so it contains only: a setup chunk, the final `mod_logistic` model chunk with its equation, and the final three `plot_predictions()` visualizations. Remove all intermediate output. Render.

In the R Terminal, run `show_file("about.qmd")`, then `show_file("analysis.qmd")`. CP/CR both.

```{r summary-2}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 12)
```

###

```
---
title: "About"
---

Var Kurapati, August 2026.
```

###

Your `analysis.qmd` should now have exactly five code chunks — setup, the `mod_logistic` model, and the three `plot_predictions()` calls — plus one math block.

###

An About page tells visitors who made the site and when.

### Exercise 3

Before publishing, preview the site locally. In the bash Terminal, run:

```
quarto preview
```

Confirm both pages load with no errors. Stop the preview and CP/CR the first few lines of terminal output.

```{r summary-3}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 6)
```

###

```
Preparing to preview
Watching files for changes
GET: /
GET: /analysis.html
GET: /about.html
Browse at http://localhost:3417/
```

###

`quarto preview` builds the site and opens a live-reloading local server — catching broken links or missing pages before they go live is much cheaper than catching them after publishing.

### Exercise 4

Publish the website to GitHub Pages. In the bash Terminal, run:

```
quarto publish gh-pages
```

Copy/paste the resulting URL below.

```{r summary-4}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 3)
```

###

`quarto publish gh-pages` without a filename publishes the whole website. Both pages are now live, linked by the navigation bar.

### Exercise 5

Commit and push any remaining changes. Copy/paste the URL to your GitHub repo.

```{r summary-5}
question_text(NULL,
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  rows = 3)
```

###

The same pattern you used here — `logistic_reg() |> set_engine() |> fit()` followed by `predictions()`, `avg_predictions()`, `comparisons()`, `avg_comparisons()`, and `plot_predictions()`, always keeping marginal and conditional straight — applies to multinomial and ordered regression too. Structure → Method → Fitting built the DGM. Question → Units → Answer ran it. Every tutorial in this series is just those six words, pointed at a different kind of outcome.

```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
