---
title: 'Visualization: Case Studies'
author: Heather Li
tutorial:
  id: visualization-case_studies
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: Maps and other case studies.
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(socviz)
library(ggthemes)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

<!-- Maybe use 5 or 6 of these plots: -->

<!-- https://www.cedricscherer.com/slides/RLadiesTunis-2021-favorite-ggplot-extensions.pdf -->

<!-- Although we may need to simplify them so that they don't require 30 Exercises. You will often need to find the code elsewhere, often at the Github repo for the package. Example: https://github.com/davidsjoberg/ggstream. I think the movie type graphic works well. -->

<!-- Create Portland temperature example. Place a screen shot from the NY Times in the images/ directory. Show them the plot we will make, which does not need to be identical, and then make it. Add the portland data to the data/ directory. No need to make it identical to Cedric's. Probably don't have time to do all his magic. See: https://gist.github.com/z3tt/275e6cffa5933c85332bacfad717eb88.  -->

<!-- Als, maybe stuff from: https://www.cedricscherer.com/2019/08/05/a-ggplot2-tutorial-for-beautiful-plotting-in-r/.  -->

## The US Life Expectancy Gap

### 

We will be making this plot here. 

```{r fig.width = 10}
final_plot <- 
  oecd_sum %>% 
  drop_na() %>% 
  ggplot(mapping = aes(x = year, y = diff, fill = hi_lo)) +
      geom_col() + 
      guides(fill = FALSE) +
      theme_minimal() +
      labs(x = NULL, 
           y = "Difference in Years",
           title = "The US Life Expectancy Gap",
           subtitle = "Difference between US and OECD average life expectancies,\n1960-2015",
           caption = "Data: OECD. After a chart by Christopher Ingraham,\nWashington Post, December 27th 2017.") +
      theme(plot.title = element_text(face = "bold",
                                      size = 20,
                                      margin = margin(b = 5)),
            plot.subtitle = element_text(face = "italic",
                                         size = 15,
                                         margin = margin(b = 10)),
            plot.caption = element_text(face = "italic",
                                        margin = margin(t = 5)),
            axis.title.y = element_text(face = "bold"),
            axis.text = element_text(face = "bold"))

final_plot
```

### Exercise 1

We will first explore the data set we will be using for the first graph. Run `oecd_sum` in the code chunk below.

```{r the-us-life-expectan-1, exercise = TRUE}

```

```{r the-us-life-expectan-1-hint-1, eval = FALSE}
oecd_sum
```

### 

The data set is from the Organisation for Economic Co-operation and Development, otherwise known as OECD. 

### Exercise 2

We will explore the `oecd_sum` data set further. Go onto this website [here](https://kjhealy.github.io/socviz/reference/oecd_sum.html). Read what each column in the tibble represents, and copy and paste your answers below.

```{r the-us-life-expectan-2}
  question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### 

This dataset focuses specifically on the USA in relation to OECD stats.

### Exercise 3

We will be building a plot mapping the USA's average life expectancy compared to the OECD's from 1960 to 2015. Start by building a pipe with the data set. Deselect the "other" column.

```{r the-us-life-expectan-3, exercise = TRUE}

```

```{r the-us-life-expectan-3-hint-1, eval = FALSE}
oecd_sum %>% 
  select(-other)
```

### Exercise 4

Built the first ggplot layer. Map `year` to the x-axis and `diff` to the y-axis.

```{r the-us-life-expectan-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r the-us-life-expectan-4-hint-1, eval = FALSE}
oecd_sum %>% 
  select(...) %>% 
  ggplot(mapping = aes(x = ...,
                       y = ...))
```

### 

Remember: simply mapping variables to the x and y axis will create an empty plot. You must add a geom layer to visualize the data.

### Exercise 5

Continue building your plot. Set the `fill` argument to `hi_lo`.
```{r the-us-life-expectan-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r the-us-life-expectan-5-hint-1, eval = FALSE}
oecd_sum %>% 
  select(...) %>% 
  ggplot(mapping = aes(x = ...,
                       y = ...,
                       fill = ...))
```

### 

This will allow the bars to be a different colour if the US' life expectancy is below/above the OECD's.

### Exercise 6

Add the `geom_col()` layer.

```{r the-us-life-expectan-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r the-us-life-expectan-6-hint-1, eval = FALSE}
oecd_sum %>% 
  select(...) %>% 
  ggplot(mapping = aes(x = ...,
                       y = ...,
                       fill = ...)) +
    geom_col()
```

### 

We choose to use `geom_col()` instead of `geom_bar()` since we already have the math done for how big the difference is between the US's life expectancy and OECD's in the `diff` column.

### Exercise 7

Add the layer `guides(fill = FALSE)`

```{r the-us-life-expectan-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r the-us-life-expectan-7-hint-1, eval = FALSE}
oecd_sum %>% 
  select(...) %>% 
  ggplot(mapping = aes(x = ...,
                       y = ...,
                       fill = ...)) +
    geom_col() +
    guides(fill = FALSE)
```

### 

`guides(fill = FALSE)` tells ggplot to drop the legend that would be generated automatically when the `fill` argument is used, when we have no need for it. The other way to accomplish this would be to do `theme(legend.position = "none")`.

### Exercise 8

Add the theme `theme_minimal()`.

```{r the-us-life-expectan-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r the-us-life-expectan-8-hint-1, eval = FALSE}
oecd_sum %>% 
  select(...) %>% 
  ggplot(mapping = aes(x = ...,
                       y = ...,
                       fill = ...)) +
    geom_col() +
    guides(fill = FALSE) +
    theme_minimal()
```

### 

This is part of the ggplot2 package.

### Exercise 9

Use labs() to give your plot the appropriate title, subtitle, captions, etc. Reminder: this is the plot we are trying to create:

```{r}
final_plot
```

```{r the-us-life-expectan-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r the-us-life-expectan-9-hint-1, eval = FALSE}
oecd_sum %>% 
  select(...) %>% 
  ggplot(mapping = aes(x = ...,
                       y = ...,
                       fill = ...)) +
    geom_col() +
    guides(fill = FALSE) +
    theme_minimal() +
    labs(title = ...,
         subtitle = ...,
         caption = ...,
         x = ...,
         y = ...)
```

### Exercise 10

Skim through [this documentation here](https://ggplot2-book.org/polishing.html#modifying-theme-components). We will be using these functions to modify the font of the graph and make it bold. What are the four element functions that can be used in `theme()`? 

```{r the-us-life-expectan-10}
question_text(NULL,
	message = "element_text(), element_line(), element_rect(), element_blank()",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	options = list(nrows = 6))
```

### 

We will primarily be using element_text().

### Exercise 11

Summarize in your own words what the function `element_text()` does.
```{r the-us-life-expectan-11}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Text for button",
	incorrect = NULL)
```

### 

Note: the only family fonts that will reliably work are "serif", "sans", and "mono". The usage of any other is not guaranteed to work.

### Exercise 12

We will now use `theme(plot.title = ...)` to change the plot title. Set the argument `face` to "bold".

```{r the-us-life-expectan-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r the-us-life-expectan-12-hint-1, eval = FALSE}
... +
  theme(plot.title = element_text(face ="bold")
```

### Exercise 13

Add the `size` argument within element_text(). Set the size to 20.

```{r the-us-life-expectan-13, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r the-us-life-expectan-13-hint-1, eval = FALSE}
... +
  theme(plot.title = element_text(face = "bold",
                                  size = 20)
```

### 

This aligns with the typical font sizes you have on your laptop.

### Exercise 14

We will adjust the margins to increase readability. Margins act as a buffer around each individual text block. Add the argument `margin` and then set it to `margin(b = 5)`

```{r the-us-life-expectan-14, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r the-us-life-expectan-14-hint-1, eval = FALSE}
... +
  theme(plot.title = element_text(face = ...,
                                  size = ...,
                                  margin = margin(b = 5))
```

### 

`b` stands for the "bottom" margin. 

### Exercise 15

We will now format the subtitle. Within the big `theme()` function, add a new argument titled `plot.subtitle`. Set it equal to element_text(). Note: there will be an error if you attempt to run this since there is no arguments within element_text().

```{r the-us-life-expectan-15, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r the-us-life-expectan-15-hint-1, eval = FALSE}
... +
  theme(plot.title = element_text(face = ...,
                                  size = ...,
                                  margin = ...),
        plot.subtitle = element_text())
```

### 

### Exercise 16

Add the argument `face` to element_text(). Set it equal to "italic".

```{r the-us-life-expectan-16, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r the-us-life-expectan-16-hint-1, eval = FALSE}
...,
plot.subtitle = element_text(face = "italic")
```

### 

### Exercise 17

Change the font size to 15.

```{r the-us-life-expectan-17, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r the-us-life-expectan-17-hint-1, eval = FALSE}
...,
plot.subtitle = element_text(face = "italic",
                             size = 15)
```

### 

### Exercise 18

From here, set the bottom margin to 10 to create space between the subtitle and the graph.

```{r the-us-life-expectan-18, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r the-us-life-expectan-18-hint-1, eval = FALSE}
...,
plot.subtitle = element_text(face = "italic",
                             size = 15,
                             margin = margin(b = 10))
```

### 

The margin is measured in pixels.

### Exercise 19

We will now modify the caption to make it italic, and also create some space between the caption and the graph. Add the `plot.caption =` argument within `theme()`. Set it to element_text(). 

```{r the-us-life-expectan-19, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r the-us-life-expectan-19-hint-1, eval = FALSE}
...,
plot.subtitle = element_text(face = "italic",
                             size = 15,
                             margin = margin(b = 10)),
plot.caption = element_text()
```

### 

### Exercise 20

Make the font italic.

```{r the-us-life-expectan-20, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r the-us-life-expectan-20-hint-1, eval = FALSE}
...,
plot.caption = element_text(face = "italic")
```

### Exercise 21

Set the top margin to 5. We do this by using `margin = margin(t = 5)`.

```{r the-us-life-expectan-21, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r the-us-life-expectan-21-hint-1, eval = FALSE}
...,
plot.caption = element_text(face = "italic",
                            margin = margin(t = 5))
```

### 

"t" stands for the top margin.

### Exercise 22

We will now simply set the y-axis title to be bold. Add axis.title.y as an argument to theme(). Set it equal to element_text(), and then face = "bold".

```{r the-us-life-expectan-22, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r the-us-life-expectan-22-hint-1, eval = FALSE}
axis.title.y = element_text(face = "bold")
```

### 

Any code that modifies the axes will have the prefix "axis" instead of "plot".

### Exercise 23

Last but not least, we will modify the axes ticks to be bold, so they are more easily readable. Add `axis.text` to within the `theme()` argument. Set it equal to `element_text()`. Make the font bold.

```{r the-us-life-expectan-23, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r the-us-life-expectan-23-hint-1, eval = FALSE}
axis.text = element_text(face = "bold"))
```

### 

Reminder: your final graph should look like this.
```{r}
final_plot
```

## Joe Biden's Approval Rating

In this exercise, we will map Joe Biden's approval rating until June 30th, the first ~6 months of his term.


```{r}
polling_data <- read_csv("data/vis4_polling_data.csv",
              col_types = cols(createddate = col_date(),
                               approval_type = col_character(),
                               rate = col_double()))
```

### 

We will be attempting to recreate this plot below.

```{r}
biden_p <- ggplot(data = polling_data, 
       mapping = aes(x = createddate,
                     y = rate,
                     color = approval_type)) +
  geom_point(alpha = 0.5) + 
  geom_smooth(method = "gam",
              formula = y ~ s(x, bs = "cs"),
              se = TRUE) +
  theme_fivethirtyeight() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  labs(title = "Biden's Approval Rating From Jan 22 to Jun 30",
       subtitle = "While Biden's approval rating has stayed relatively static, his disapproval rating \nhas been rising.",
       color = "",
       caption = "Source: Five Thirty Eight Data")

biden_p
```

### Exercise 1

We will first explore the file that contains this data. Run `polling_data` in the console below.

```{r joe-bidens-approval--1, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r joe-bidens-approval--1-hint-1, eval = FALSE}
polling_data
```

### 

This data was taken from the fivethirtyeight website. You will learn how to modify data into CSVs and use them in R in a later tutorial.

### Exercise 2

Write down the name of the three column headers.

```{r joe-bidens-approval--2}
question_text(NULL,
	message = "createddate, rate, approval_type",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	options = list(nrows = 6))
```

### 

`createddate` stands for the day the poll was finished. `rate` is the % of approval or disapproval, and `approval_type` indicates whether or not the rate is approval or disapproval.

### Exercise 3

We will get started building the plot. Start the function `ggplot()`, and set the argument `data` to `polling_data`.

```{r joe-bidens-approval--3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r joe-bidens-approval--3-hint-1, eval = FALSE}
ggplot(data = polling_data)
```

### 

Remember: you should not see a plot here as you have not mapped anything, nor do you have a geom layer.

### Exercise 4

Now, map `createddate` to the x-axis, and map `rate` to the y-axis.

```{r joe-bidens-approval--4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r joe-bidens-approval--4-hint-1, eval = FALSE}
ggplot(data = polling_data,
       mapping = aes(x = createddate,
                     y = rate))
```

### 

`createddate` is a date column, and `rate` is a double column.

### Exercise 5

We want to be able to see both Joe Biden's approval and disapproval rate. Therefore, we'll change the colour of the dots depending on whether the dot represents an approval/disapproval rating. Set `color` to `approval_type`.
```{r joe-bidens-approval--5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r joe-bidens-approval--5-hint-1, eval = FALSE}
ggplot(data = polling_data,
       mapping = aes(x = createddate,
                     y = rate,
                     color = approval_type))
```

### 

Good! Now we're ready to start building the plot.

### Exercise 6

Next, we will add the points to the graph. Add the layer `geom_point()`.

```{r joe-bidens-approval--6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r joe-bidens-approval--6-hint-1, eval = FALSE}
ggplot(data = polling_data,
       mapping = aes(x = createddate,
                     y = rate,
                     color = approval_type)) +
  geom_point()
```

### 

Currently, we have a bit of overplotting. We will rectify this in the next code chunk.

### Exercise 7

Set the argument `alpha` to 0.5.

```{r joe-bidens-approval--7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r joe-bidens-approval--7-hint-1, eval = FALSE}
ggplot(data = ...,
       mapping = aes(x = ...,
                     y = ...,
                     color = ...)) +
  geom_point(alpha = ...)
```

### 

Good! Now you should be able to see more distinct points.

### Exercise 8

We want to see the trendline for Biden's approval/disapproval ratings throughout his term. Add the layer of `geom_smooth().`

```{r joe-bidens-approval--8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r joe-bidens-approval--8-hint-1, eval = FALSE}
... + 
  geom_smooth()
```

### 

If you just add this layer, you will get a few warning messages. We will fix this in the following exercises.

### Exercise 9

Within geom_smooth(), set the method argument to "gam". We use "gam" since there is a large quantity of data points.

```{r joe-bidens-approval--9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r joe-bidens-approval--9-hint-1, eval = FALSE}
... + 
  geom_smooth(method = "gam")
```

### 

"gam" stands for **generalized additive model**. It is a modified form of a linear model. If you are curious to learn more, [GAMs in R](https://noamross.github.io/gams-in-r-course/chapter1) is a good resource.

### Exercise 10

Next, within geom_smooth still, set the argument formula to `y ~ s(x, bs = "cs")`.

```{r joe-bidens-approval--10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r joe-bidens-approval--10-hint-1, eval = FALSE}
... + 
  geom_smooth(method = "gam",
              formula = y ~ s(x, bs = "cs"))
```

### 

Just like y ~ x indicates a relationship between x and y, `y ~ s(x, bs = "cs")` indicates a "generalized additive model" relationship.

### Exercise 11

Finally, set se = TRUE.
```{r joe-bidens-approval--11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r joe-bidens-approval--11-hint-1, eval = FALSE}
... + 
  geom_smooth(method = "gam",
              formula = y ~ s(x, bs = "cs"),
              se = TRUE)
```

### 

Remember, this creates a margin of error.

### Exercise 12

Since the data comes from the FiveThirtyEight website, we will uses the fivethirtyeight theme! Add `theme_fivethirtyeight()` to your plot.

```{r joe-bidens-approval--12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r joe-bidens-approval--12-hint-1, eval = FALSE}
... + 
  geom_smooth(method = ...,
              formula = ...,
              se = ...) +
  theme_fivethirtyeight()
```

### 

Note: the FiveThirtyEight theme actually comes from the `ggthemes()` package, not the FiveThirtyEight package.

### Exercise 13

Next, we want to change the labels on the graph so they are in percentage format. Use scale_y_continuous to do so. Set the `labels` argument to `scales::percent_format(accuracy = 1)`.

```{r joe-bidens-approval--13, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r joe-bidens-approval--13-hint-1, eval = FALSE}
...+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))
```

### 

We use scale_y_continuous when we want to modify the y-axis for continuous data. [This documentation here](https://ggplot2.tidyverse.org/reference/scale_continuous.html) will tell you more, and all the possible arguments you can use with scale_y_continuous.

### Exercise 14

Finally, use `labs()` to add an appropriate heading, subtitle, caption, etc. 

Reminder - your graph should look like this:

```{r}
biden_p
```

```{r joe-bidens-approval--14, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r joe-bidens-approval--14-hint-1, eval = FALSE}
... +
  labs(title = ...,
       subtitle = ...,
       color = ...,
       caption = ...)
```

### 

Good! Now you have a plot of Biden's approval rating for the first six months of his term.

```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
