---
title: "Gathering-Data"
tutorial:
  id: "02-gathering-data"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Chapter 2 Gathering Data"
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(primer.tutorials)
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
options(tutorial.exercise.timelimit = 60, tutorial.storage="local") 

# Dealing with external files in tutorials is confusing! The biggest problem is
# figuring out when things will be evaluated and where. There is some discussion
# here: https://rstudio.github.io/learnr/. It certainly seems that setup chunks
# are not evaluated until Run Code is pressed on the Exercise chunk.

# We need to get the example file into the working area for each question. I
# initially had this material in its own R code chunk. But then the function was
# not available when the tutorial was run from the Tutorial Pane. Why? 

# I used to believe that any objects which you always want around for the entire
# portfolio should be created here, in the main set-up chunk. That seems to both
# work (an object is available) and fail (you get a weird warning message about
# the object not being available).  For example, code which creates an object
# called `www` does work in that www is around for later questions, but it also
# makes this warning:

# Warning: Error in paste0: object 'www' not found

# Very confusing! Since everything works, this must be a weird evaluation timing
# issue . . .

# For some usage, you want to interact with the file in its main location,
# without copying it over. For that purpose, you need the path to where the
# package is installed.

# Is there a way to force the deletion of any previous work, whenever you
# install a new version of the package? (Maybe just changing the version number
# does this. Maybe using the `id` designation.) There seem to be at least two
# kinds of work that stay on. First, the answers which you have already given,
# which can be removed by hitting the Start Over button. Second, the html file
# itself seems to (often) be a previous version, rather than the latest.


```


## CSV Files
###

We begin by learning how to use `read_csv()` to read in CSV files. "CSV" stands for comma-separate values, meaning that the variable names and data values are separated by commas in the file.

### Exercise 1

```{r ex-1-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_1.csv"), ".")
```

Consider the contents of the `test_1.csv` file. 

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"), 
                     "test_1.csv")), sep = "\n")
```

Write code for reading this file in to R.


```{r ex-1, exercise=TRUE}

```

```{r ex-1-hint, eval=FALSE}
Use `read_csv()` and set the `file` argument to `test_1.csv`.
```

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_1.csv"),
         col_types = cols(a = col_double(),
                          b = col_double(),
                          c = col_double()))
```

The rest of the exercises in this tutorial are like this one. We aren't creating any new R objects. We are just reading in data from different files and looking at the resulting object, which will almost always be a tibble.

### Exercise 2

<!-- Using the skip argument -->

### Exercise 3

<!-- Using col_names = FALSE -->

### Exercise 4

<!-- Using col_names = c("a", "b", "c") with test_3 -->

### Exercise 5

<!-- Use na = c(".") -->

### Exercise 6

<!-- Use comment = "#" -->


<!-- ### More Stuff -->

<!-- Couple questions using col_types argument. Start with examples which show you reading in a number as a character, useful for postal codes, for example.  -->

<!-- Then, show how to use the result from running it initially to make the warning disappear. -->

<!-- Questions using read_delim to read in a csv file. Then, to read in a file with other deliminators, like spaces.  -->

<!-- Couple questions using an Excel file and readxl. -->

<!-- Couple questions on read json? Like we do in the book? -->

<!-- Couple questions on reading in data from the web, like a Wikipedia table? -->

<!-- Couple questions on using an API? -->



