---
title: "Gathering-Data"
tutorial:
  id: "02-gathering-data"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Chapter 2 Gathering Data"
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(readxl)
library(knitr)
library(primer.tutorials)
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
options(tutorial.exercise.timelimit = 60, tutorial.storage="local") 

# Dealing with external files in tutorials is confusing! The biggest problem is
# figuring out when things will be evaluated and where. There is some discussion
# here: https://rstudio.github.io/learnr/. It certainly seems that setup chunks
# are not evaluated until Run Code is pressed on the Exercise chunk.

# We need to get the example file into the working area for each question. I
# initially had this material in its own R code chunk. But then the function was
# not available when the tutorial was run from the Tutorial Pane. Why? 

# I used to believe that any objects which you always want around for the entire
# portfolio should be created here, in the main set-up chunk. That seems to both
# work (an object is available) and fail (you get a weird warning message about
# the object not being available).  For example, code which creates an object
# called `www` does work in that www is around for later questions, but it also
# makes this warning:

# Warning: Error in paste0: object 'www' not found

# Very confusing! Since everything works, this must be a weird evaluation timing
# issue . . .

# For some usage, you want to interact with the file in its main location,
# without copying it over. For that purpose, you need the path to where the
# package is installed.

# Is there a way to force the deletion of any previous work, whenever you
# install a new version of the package? (Maybe just changing the version number
# does this. Maybe using the `id` designation.) There seem to be at least two
# kinds of work that stay on. First, the answers which you have already given,
# which can be removed by hitting the Start Over button. Second, the html file
# itself seems to (often) be a previous version, rather than the latest.
```


## CSV Files
###

We begin by learning how to use `read_csv()` to read in CSV files. "CSV" stands for comma-separate values, meaning that the variable names and data values are separated by commas in the file.

### Exercise 1

```{r ex-1-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_1.csv"), ".")
```

Consider the contents of the `test_1.csv` file.

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"),
                     "test_1.csv")), sep = "\n")
```

Write code for reading this file in to R.


```{r ex-1, exercise=TRUE}

```

```{r ex-1-hint, eval=FALSE}
Use `read_csv()` and set the `file` argument to `test_1.csv`.
```

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_1.csv"),
         col_types = cols(a = col_double(),
                          b = col_double(),
                          c = col_double()))
```

The rest of the exercises in this tutorial are like this one. We aren't creating any new R objects. We are just reading in data from different files and looking at the resulting object, which will almost always be a tibble.

### Exercise 2

```{r ex-2-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_2.csv"), ".")
```

Consider the contents of the `test_2.csv` file. 

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"), 
                     "test_2.csv")), sep = "\n")
```

Write code for reading this file in to R.

```{r ex-2, exercise=TRUE}

```

```{r ex-2-hint, eval=FALSE}
Use the `skip` argument to skip the first two lines.
```

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_2.csv"),
         skip = 2,
         col_types = cols(a = col_double(),
                          b = col_double(),
                          c = col_double()))
```

There are many arguments to `read_csv()` which allow us to deal with data formatted in different ways. Many of these argument also apply to other functions for reading in data, like `read_excel()`.

### Exercise 3

<!-- Using col_names = FALSE -->

```{r ex-3-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_3.csv"), ".")
```

Consider the contents of the `test_3.csv` file. 

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"), 
                     "test_3.csv")), sep = "\n")
```

Write code for reading this file in to R.

```{r ex-3, exercise=TRUE}

```

```{r ex-3-hint, eval=FALSE}
Use the `col_names argument and set it to FALSE
```

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_3.csv"),
         col_names = FALSE)
        
```

### Exercise 4

<!-- Using col_names = c("a", "b", "c") with test_3 -->

```{r ex-4-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_3.csv"), ".")
```

Consider the contents of the `test_3.csv` file. 

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"), 
                     "test_3.csv")), sep = "\n")
```

Write code for reading this file in to R.

```{r ex-4, exercise=TRUE}

```

```{r ex-4-hint, eval=FALSE}
Use the `col_names` argument and set its argument to c("a", "b", "c") 
```

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_3.csv"),
         col_names = (c("a", "b", "c")),
         col_types = cols(a = col_double(),
                          b = col_double(),
                          c = col_double()))
```

### Exercise 5

<!-- Use na = c(".") -->

```{r ex-5-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_5.csv"), ".")
```

Consider the contents of the `test_5.csv` file. 

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"), 
                     "test_5.csv")), sep = "\n")
```

Write code for reading this file in to R.

```{r ex-5, exercise=TRUE}

```

```{r ex-5-hint, eval=FALSE}
Use the `na` to the argument "."
```

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_5.csv"),
         na = ".")
```


### Exercise 6

<!-- Use comment = "#" -->

```{r ex-6-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_6.csv"), ".")
```

Consider the contents of the `test_6.csv` file. 

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"), 
                     "test_6.csv")), sep = "\n")
```

Write code for reading this file in to R.


```{r ex-6, exercise=TRUE}

```

```{r ex-6-hint, eval=FALSE}
Use the `comment` argument and set it to "#".
```

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_6.csv"),
         comment = "#")
```

### Exercise 7

<!-- Use comment = "#" -->

```{r ex-7-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_7.csv"), ".")
```

Consider the contents of the `test_7.csv` file. 

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"), 
                     "test_7.csv")), sep = "\n")
```

Write code for reading this file in to R. Make sure to get the zip codes correct!


```{r ex-7, exercise=TRUE}

```

```{r ex-7-hint, eval=FALSE}

```

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_7.csv"),
         col_types = cols(
  grade = col_character(),
  student = col_character()
))
```




<!-- Meeting Notes -->

<!-- 1. Because there is nothing to fix there only needs to be one image b/c we are just getting used to using the read_excel/arguments?  -->

<!-- 2. code for include_graphics not working... -->


## Excel Files
###

Excel is a spreadsheet program that use tables to analyze, store, or manipulate data. The tables composed of cells which take in text, numbers, or formulas.


### Exercise 1

```{r ex-8-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "Book1.xlsx"), ".")
```

Consider the contents of the excel file `Book1.xlsx`

```{r, echo = FALSE}
#code for graphics needed for Sheet1
#knitr::include_graphics(paste0(system.file("images/", package = "primer.tutorials"),"book1.png"))
```

Write code for reading this file in to R.

```{r ex-8, exercise=TRUE}

```

```{r ex-8-hint, eval = FALSE}
Use `read_excel()` and set the `file` argument to `Book1.xlsx`.
```


The result when your code is run should look like this:

```{r}
read_excel(paste0(system.file("www/", package = "primer.tutorials"), 
                 "Book1.xlsx"))

```

### Exercise 1

```{r}
read_excel(paste0(system.file("www/", package = "primer.tutorials"), 
                "Book1.xlsx"))
```

Let's once again consider the contents of `Book1.xlsx`. However, we want to look at the second sheet of the file. **Note**: Sheet 1 is the default when looking at an excel file, so the last exercise only showed us the contents of Sheet 1.

```{r ex-9, exercise=TRUE}
#code for graphics needed here for Sheet2
```

```{r ex-9-hint, eval = FALSE}
Use the `sheet` argument to look at other sheets. Set `sheet` to "Sheet2".
```


The result when your code is run should look like this:

```{r}
read_excel(paste0(system.file("www/", package = "primer.tutorials"), 
                 "Book1.xlsx"), sheet = "Sheet2")
```




<!-- ### More Stuff -->

<!-- Couple questions using col_types argument. Start with examples which show you reading in a number as a character, useful for postal codes, for example.  -->

<!-- Then, show how to use the result from running it initially to make the warning disappear. -->

<!-- Questions using read_delim to read in a csv file. Then, to read in a file with other deliminators, like spaces.  -->


<!-- Couple questions on read json? Like we do in the book? -->

<!-- Couple questions on reading in data from the web, like a Wikipedia table? -->

<!-- Couple questions on using an API? -->



