---
title: "Tools"
tutorial:
  id: "tools"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Tools Tutorial"
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(png)
library(grid)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

<!-- ```{bash, echo = TRUE} -->
<!-- pwd -->
<!-- ``` -->

<!-- Add some questions which show that they did, in fact, create the productivity repo as instructed in the chapter? Maybe move to that project? -->

<!-- Perhaps the single biggest confusion among students is not understanding how a process can be run from two different places. This causes endless problems when students build their own Shiny App later. Run ls in one location. Move. Run it again. Different answers! What you get depends on where you are. -->

## Introduction
###

This tutorial covers material in the first three parts of the Appendix on [Tools](https://ppbds.github.io/primer/tools.html): "Working with the terminal," "Git, GitHub, and RStudio," and "PDF." You should have already read these sections and followed the instructions therein. One purpose of this section is to confirm that you have done

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```

## The Terminal
###

The Terminal pane is next to the Console pane in the lower left portion of RStudio. We use the Console pane to talk to R. We use the Terminal pane to talk directly with your computer. Sadly, the Console and the Terminal speak different languages.

### Exercise 1

Let's figure out where we are. To see your current location, type `pwd` (present working directory), in the Console. Hit return, and copy/paste both the line on which you typed the command and the line below it.



```{r term-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

This is the standard manner in which you will answer tutorial questions which use the command line. Your pasted answer should look like this:

```{r}
file <- paste0(system.file("images/", 
                           package = "primer.tutorials"),
               "pwd.png")
img <- readPNG(file)
grid.raster(img)
```

Again, you paste in both the line with the command you issued and the result of that command. If the question asked you to issue two commands, then copy/paste them both.

### Exercise 2

Type `ls` (list) in the terminal and hit return to see all the items that are located in the directory in which you are currently located. 

```{r term-ex-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 3

Let's make a folder called `Gov-1005`. Type the command `mkdir Gov-1005` and hit return. Now type `ls` to see your newly created folder! 
 
```{r term-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 4

Type in the command `cd Gov-1005` in order to **c**hange **d**directories into the directory which we just created. There should not be anything in this directory. Type `ls` to be sure. 

```{r term-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 5

Let's now create a file. Type in `touch text.txt`and hit return. Now type `ls`. `touch` creates the file but does nothing else.

```{r term-ex-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

### Exercise 6

Let's change the name of `text.txt` to `my.text`. This is done with the `mv` command. (`mv` stands for "move.") First, type `ls` to confirm the existence of `text.txt`. Second, type `mv text.txt my.text`. Third, type `ls` to demonstrate that the renaming has worked. The (lack of) content in the file has not changed. 

```{r term-ex-6}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

Your pasted code should look something like:

```{r}
file <- paste0(system.file("images/", 
                           package = "primer.tutorials"),
               "mv.png")
img <- readPNG(file)
grid.raster(img)
```



### Exercise 7

Now let's try deleting `my.txt`. First, type `ls` to confirm it is there. Second, type with `rm my.text`. (`rm` stands for "remove.") Third, type `ls` to make sure the file is gone.


```{r term-ex-8}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 4))
```




## Git/Github
### 

Professionals use Git/Guthub to backup and distribute their work. You want to be a professional, right? **Make sure to read (and follow the instructions in) the Tools appendix [section](https://ppbds.github.io/primer/tools.html#git-github-and-rstudio) about Git/Github/RStudio before doing these exercises.**

### Exercise 1

Let's check to see that you have git installed. To check, go to your Terminal and type `git --version`. Copy/paste the command and the results. 

```{r git-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```


### Exercise 2

Type `git config --global user.name` at the Terminal. It should return your name.

```{r git-ex-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```


### Exercise 3

Type `git config --global user.email` at the Terminal. It should return the same email address you use at Github.

```{r git-ex-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 2))
```

### Exercise 4

Type `packageVersion("usethis")` into the Console. (Not into the Terminal! This is an R command. The Terminal does not speak R.) It should return a version number equal to or higher than 2.0.0. Copy/paste the command and results. If this fails, you need to install the latest version of the **usethis** package. (You followed all the steps in the Shopping Week appendix, right?) 

```{r git-ex-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 10))
```


### Exercise 5

Type `git_sitrep()` into the Console. (Not into the Terminal! This is an R command. The Terminal does not speak R.) You will see a bunch of code divided into 4 sections. Copy/paste the first two sections: under **Git config (global)** and **GitHub**.

```{r git-ex-5}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 10))
```

Your version won't be identical to mine, but it should be similar. The most important line is this one:

* Personal access token for 'https://github.com': '<discovered>'

If yours looks different, that probably means you have not set up your personal access token correctly. Please do so.

```{r}
file <- paste0(system.file("images/", 
                           package = "primer.tutorials"),
               "sitrep.png")
img <- readPNG(file)
grid.raster(img)
```

<!-- DK: Discuss and demonstrate that you have done the personal access token thing? -->


## Miscelaneous
###

These questions will help to confirm that your computer is set up correctly. Make sure you have completed the assigned portions of the Tools appendix.

### Exercise 1

You should already have run the command `usethis::use_blank_slate()` from the R Console. This causes RStudio to neither save nor reload old junky data sets. To confirm that you have done this, run `rstudioapi::readRStudioPreference(name = "load_workspace", default = "Code failed.")` from the Console. Copy/paste the command/answer below.

```{r m-ex-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

The response should be FALSE. If it is not, seek help.

<!-- ### Exercise 2 -->

<!-- For RStudio to make PDF files, your computer must be set up with a LaTeX. Open up your Console, and install the package `tinytex` using `install.pacakges()`. Copy/paste both the line on which you typed the command and the lines below it.  -->

<!-- ```{r m-ex-2} -->
<!-- question_text(NULL, -->
<!--     answer(NULL, correct = TRUE), -->
<!--     allow_retry = TRUE, -->
<!--     try_again_button = "Edit Answer", -->
<!--     incorrect = NULL, -->
<!--     options = list(nrows = 10)) -->
<!-- ``` -->

<!-- ### Exercise 3 -->

<!-- Now open the `tinytex` package using `library()`. Then type `search()`and paste below whatever shows up in your search box. -->


<!-- ```{r m-ex-3} -->
<!-- question_text(NULL, -->
<!--     answer(NULL, correct = TRUE), -->
<!--     allow_retry = TRUE, -->
<!--     try_again_button = "Edit Answer", -->
<!--     incorrect = NULL, -->
<!--     options = list(nrows = 10)) -->
<!-- ``` -->

<!-- ### Exercise 4 -->

<!-- Now install the tinytex version of Latex -->


<!-- ```{r m-ex-4} -->
<!-- question_text(NULL, -->
<!--     answer(NULL, correct = TRUE), -->
<!--     allow_retry = TRUE, -->
<!--     try_again_button = "Edit Answer", -->
<!--     incorrect = NULL, -->
<!--     options = list(nrows = 10)) -->
<!-- ``` -->


## Submit

```{r context="setup"}
submission_ui
```

```{r context="server"}
submission_server()
```


