---
title: "Tools"
tutorial:
  id: "tools"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Tools Tutorial"
---

```{r setup, include=FALSE}
library(tidyverse)
library(primer.data)
library(learnr)
library(shiny)
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
options(tutorial.exercise.timelimit = 60, tutorial.storage="local")
```

<!-- Every exercise requires some answer from students. For example, after installing **usethis**, check the installation from the R prompt with: -->

<!-- > packageVersion("usethis") -->

<!-- The answer requires that the student paste in the resulting output. -->

<!-- 4) Should we do more, something with Github? Something with a PDF file? That would certainly get students going to the first set of Study Halls! -->


## Name 


``` {r name}
question_text(
  "Student Name:",
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Modify your answer",
  incorrect = "Ok"
)
```

## Email

``` {r email}
question_text(
  "Email:",
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Modify your answer",
  incorrect = "Ok"
)
```

## The Terminal
###

### Exercise 1

Let's figure out where we are. To see your current folder, type `pwd` (previews working directory). Hit return, and copy/paste both the line on which you typed the command and the line(s) below it.

```{r pwd, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)
```

### Exercise 2

Type `ls` in the terminal and hit return to see all the items that are located in the bottom right window under "Home". Paste both the line on which you typed the command and the line(s) below it.

```{r ls, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)
```

### Exercise 3 (part I)

We will be opening or "changing" into our Desktop directory now. Type in the command `cd Desktop/`. Paste both the line on which you typed the command and the line(s) below it.

```{r cd, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)

```

### Exercise 3 (part II)

Awesome. Now type `ls`. Paste both the line on which you typed the command and the line(s) below it.

```{r cd2, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)

```

### Exercise 4

Let's try making a folder called Gov-50. Use the command `mkdir Gov-50`and hit return. Now type `ls` to see your newly created folder! Paste both the line on which you typed the command and the line(s) below it.
 
```{r mk-1, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)

```

### Exercise 5

Let's now create a file. Type in `touch: text.txt`and hit return. Now type `ls`. Paste both the line on which you typed the command and the line(s) below it

```{r touch, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)

```

### Exercise 6

Now let's move our text.txt file to our Gov-50 folder. Type `mv test.txt Gov-50/`. Now let's check! Use `cd` to open our Gov-50 folder and `ls` to show its contents. Paste both the line on which you typed the command and the line(s) below it

```{r mv, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)
```

### Exercise 7

Try copying the test.txt file into your Gov-50 folder. Use `cp test.txt Gov-50/`. Paste both the line on which you typed the command and the line(s) below it.

```{r cp-1, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)
```

### Exercise 8

Now let's try removing that same text.txt file with `rm`. Use `ls` to make sure it is gone!







## Git/Github
### 

### Exercise 1

Let's check to see that you have git installed. To check, go to your Terminal and type `git --version`. If you do not have git installed, follow the instructions [here](https://happygitwithr.com/install-git.html).


### Exercise 2

Now type `git config --global user.name "Your Name"` into the terminal. Replace "Your Name" with your name. Copy/paste both the line on which you typed the command and the line(s) below it. 

```{r gc-1, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)
```


### Exercise 3

Now Type `git config --global user.mail "your@email.com"`into the terminal. Replace "your@email.com" with the email you used to sign up for GitHub. Copy/paste both the line on which you typed the command and the line(s) below it.

```{r gc-2, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)
```


<!-- BG: here would be where we would do something with repos. is there a way we can check? -->

### Exercise 4

Now, switch out of the Terminal window into the Console window. Install the package `usethis`. Issue the command `install.packages("usethis")`.

**DO NOT** go on until you have done this.

### Exercise 5

Type `git_sitrep()` into the console. You will see a bunch of code divided into 5 sections. Copy/paste the first section under **Git config (global)**.

```{r gc-3, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)
```

### Exercise 6

Awesome. Now copy/paste the third section under **GitHub**.

```{r gc-4, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)
```

<!-- BG: confused about rstudioapi::readRStudioPreference(name = "load_workspace") to front of tools. -->

## PDF
###

### Exercise 1

For RStudio to make PDF files, your computer set up must be set up with a [LaTeX]. Open up your console, and install the package 'tinytex' using `install.pacakges()`. Copy/paste both the line on which you typed the command and the line(s) below it

```{r pdf, echo = FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)
```

### Exercise 2

Now open the `tinytex` package using `library()`. Then type `search()`and paste below whatever shows up in your search box.


```{r pdf-2, echo=FALSE}
question_text("copy/paste here:",
              answer(NULL, correct = TRUE),
              incorrect = "Ok",
              try_again_button = "Modify your answer",
              allow_retry = TRUE)
```




## Submit

Some of these exercises were taken from the collection of [RStudio Primers](https://rstudio.cloud/learn/primers), a great resource for practicing your skills.

```{r context="setup"}
submission_ui
```

```{r context="server"}
submission_server()
```


