---
title: 'Four Parameters: Categorical'
author: David Kane and Tanay Janmanchi
tutorial:
  id: four-parameters-categorical
output:
  learnr::tutorial:
    progressive: yes
    'allow_skip:': yes
runtime: shiny_prerendered
description: 'Chapter 8 Tutorial: Four Parameters: Categorical'
---

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(tidyverse)
library(brms)
library(tidybayes)
library(gtsummary)
library(primer.data)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 

nes_92 <- nes |> 
  filter(year == 1992) |> 
  select(sex, pres_vote) |> 
  drop_na() |> 
  mutate(pres_vote = case_when(
    pres_vote == "Democrat" ~ "Clinton",
    pres_vote == "Republican" ~ "Bush",
    pres_vote == "Third Party" ~ "Perot",
  ))

# fit_nes <- brm(formula = pres_vote ~ sex,
#                data = nes_92,
#                family = categorical(),
#                silent = 2,
#                refresh = 0,
#                seed = 76)
# 
# write_rds(fit_nes, "data/fit_nes.rds")

fit_nes <- read_rds("data/fit_nes.rds")

ndata <- tibble(sex = c("Female", "Male"))

```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

## Introduction
### 

This tutorial covers [Chapter 8: Four Parameters: Categorical](https://ppbds.github.io/primer/four-parameters-categorical.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/).

## Wisdom
### 

*The only true wisdom is in knowing you know nothing.*  - Socrates

We want to know what is the relationship between sex and voting in the 1992 Presidential election.

### 

Specifically, we want to know, which of these three candidates (Bush, Clinton or Perot) did you vote for in 1992?

### Exercise 1

In your own words, describe the key components of Wisdom for working on a data science problem.

```{r wisdom-1}
question_text(NULL,
	message = "Wisdom requires the creation of a Preceptor Table, an examination of our data, and a determination, using the concept of validity, as to whether or not we can (reasonably!) assume that the two come from the same population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

If it is not *valid* to consider the data you have and the (theoretical) data from the Preceptor Table to have arisen out of the same population, your attempt to estimate your quantity of interest ends at the first stage. 

### Exercise 2

Define a Preceptor Table.

```{r wisdom-2}
question_text(NULL,
	message = "A Preceptor Table is the smallest possible table of data with rows and columns such that, if there is no missing data, it is easy to calculate the quantities of interest.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 3

Describe the key components of Preceptor Tables in general, without worrying about this specific problem. Use words like "units," "outcomes," and "covariates."

```{r wisdom-3}
question_text(NULL,
	message = "The rows of the Preceptor Table are the units. The outcome is at least one of the columns. If the problem is causal, there will be at least two (potential) outcome columns. The other columns are covariates. If the problem is causal, at least one of the covariates will be a treatment.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

As we are considering *predicative model*, our Preceptor Table will have three columns for the potential outcomes.

### Exercise 4

What are the units for this problem?

```{r wisdom-4}
question_text(NULL,
	message = "The rows of the Preceptor Table refer to individual US voters.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

We are looking at who voted for these three candidates: Bush, Clinton and Perot. The question suggests that we are not interested in people who did not vote, although one might explore if men were more or less likely to vote in the first place. As always, the initial question rarely specifies the Preceptor Table precisely.

### Exercise 5

What is/are the outcome/outcomes for this problem?

```{r wisdom-5}
question_text(NULL,
	message = "Presidential voting behavior in 1992",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Such explorations are often restricted to just the two “major party” candidates, the nominees of the Democratic and the Republican parties, Bill Clinton and George HW Bush. But, in 1992, Ross Perot was a very successful “third party” candidate, winning almost 19% of the vote. Should he be included in the analysis? Again, the question does not specify. However, the outcome variable is certainly the candidate for whom an individual voted.

### Exercise 6

What are some covariates which you think might be useful for this problem?

```{r wisdom-6}
question_text(NULL,
	message = "We will certainly need sex, with two values: “male” and “female”. Other variables which might be helpful include party, income, race and past voting history.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Covariates are any variable that can influence the outcome. For example, Democrats are almost certainly going to vote for Clinton. For this model we will be measuring the `sex` variable.

### Exercise 7

What are the treatments, if any, for this problem?

```{r wisdom-7}
question_text(NULL,
	message = "There are no treatments.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Since this represents a predicative model, there are no treatments.


### Exercise 8

What moment in time does the Preceptor Table refer to?

```{r wisdom-8}
question_text(NULL,
	message = "Fall of 1992",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 9

Go to the console and type `?nes` to learn more about the data. Write one sentence describing the data you have to answer your question.

<!-- TJ: You give one sentence. Done-->

```{r wisdom-9}
question_text(NULL,
	message = "This dataset contains information starting from 1948, before and after each presidential election, and combines questions about voters' political attitudes with extensive biographical information.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 10

Load the **tidyverse** package.

```{r wisdom-10, exercise = TRUE}

```

```{r wisdom-10-hint-1, eval = FALSE}
library(...)
```

```{r wisdom-10-test, include = FALSE}
library(tidyverse)
```

### Exercise 11

What does the dependent variable represent in this data?

```{r wisdom-11}
question_text(NULL,
	message = "The candidate who an individual that was surveyed voted for.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 12

Create a Github repo called `four-parameters-categorical`. Be sure to add a README file. Connect the repo to a new R project titled `four-parameters-categorical`. Edit the `.gitignore` by adding `*Rproj`. 

In the Console, run:

```
tutorial.helpers::show_file(".gitignore")
```

CP/CR.

```{r wisdom-12}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

Commit and push the changes to GitHub, we will work more with this.

### Exercise 13

Load the **primer.data** package.

```{r wisdom-13, exercise = TRUE}

```

```{r wisdom-13-hint-1, eval = FALSE}
library(...)
```

```{r wisdom-13-test, include = FALSE}
library(primer.data)
```

### Exercise 14

Type `nes` below.

```{r wisdom-14, exercise = TRUE}

```

```{r wisdom-14-hint-1, eval = FALSE}

```

```{r wisdom-14-hint-2, eval = FALSE}
nes
```

```{r wisdom-14-test, include = FALSE}
nes
```

### Exercise 15

Pipe nes to `count()`, set the argument inside to `sex`

```{r wisdom-15, exercise = TRUE}
nes
```

```{r wisdom-15-hint-1, eval = FALSE}
nes |> count(...)
```

```{r wisdom-15-test, include = FALSE}

nes |> count(sex)

```

### 

We can see that there are over 4000 more female voters than male voters

### Exercise 16

Go to `File -> New File -> Quarto Document`. Title it "Four Parameters: Categorical". Make yourself the author. Save the file as `analysis.qmd`. Once you do this, delete everything below the YAML header and render the file.

In the Console, run : `tutorial.helpers::show_file("analysis.qmd")`. CP/CR


```{r wisdom-16}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### Exercise 17

Edit the `.gitignore` file to include `*_files`.
In the Console, run : `tutorial.helpers::show_file(".gitignore")`. CP/CR


```{r wisdom-17}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### Exercise 18

Create a new code chunk. Add `#| label: setup`, `#| echo: FALSE` and `#| message: FALSE` to the top of it. Load the **brms**, **tidybayes**, **tidyverse**, **gtsummary** and **primer.data** packages into this code chunk. Load the packages here as well.

```{r wisdom-18-hint-1, eval = FALSE}

```

```{r wisdom-18-test, include = FALSE}

```

### 

Now we have loaded our libraries, we can start to clean up the data to make our model.



### Exercise 19

Type nes below.

```{r wisdom-19, exercise = TRUE}

```

### Exercise 20

Pipe nes to `filter()` and set the argument `year` to `1992`.  


```{r wisdom-20, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r wisdom-20-hint-1, eval = FALSE}
... |> filter (...)
```

### 

This only looks at data from the year 1992.

### Exercise 21

Continue the pipe with `select()`, be sure to select the `pres_vote` and `sex` columns

```{r wisdom-21, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r wisdom-21-hint-1, eval = FALSE}
... |> select(..., ...)
```

```{r wisdom-21-test, include = FALSE}

```

### 

This only keeps the data that we need, which is the candidate voted and the sex of the voter.


### Exercise 22

Continue the pipe with `drop_na()`

```{r wisdom-22, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r wisdom-22-hint-1, eval = FALSE}
... |> drop_na()
```

```{r wisdom-22-test, include = FALSE}

```

### 

This gets rid of NA values

### Exercise 23

Finish the pipe with `mutate()`. Set the `pres_vote` argument to `case_when()`. Inside of `case_when()`, change `pres_vote` from the name of the political party to the name of the candidate that was voted. (Look in the textbook to find the associated political parties).

```{r wisdom-23, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>


```{r wisdom-23-hint-1, eval = FALSE}
... |> 
  mutate(pres_vote = case_when(
    pres_vote == "Democrat" ~ ...,
    pres_vote == ... ~ "Bush",
    pres_vote == ... ~ ..,
  ))
```

### 

The data uses the name of the political party, but, we want the name of the candidate specifically.

### Exercise 24

Set this equal to a new object called `nes_92`. 

```{r wisdom-24, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r wisdom-24-hint-1, eval = FALSE}
nes_92 <- ...
```

### 

Your code should look like this: 

```
nes_92 <- nes |> 
  filter(year == 1992) |> 
  select(sex, pres_vote) |> 
  drop_na() |> 
  mutate(pres_vote = case_when(
    pres_vote == "Democrat" ~ "Clinton",
    pres_vote == "Republican" ~ "Bush",
    pres_vote == "Third Party" ~ "Perot",
  ))
```

### 

This is the data we will use to create our model. 

### Exercise 25

Create a new code chunk. Add `#| label: cleaning`, `#| echo: FALSE` and `#| message: FALSE` to the top of it once again. Copy and paste the code to above into the code chunk. Render the document.

In the console, run: `tutorial.helpers::show_file("analysis.qmd")`. CP/CR

```{r wisdom-25}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### Exercise 26

In your own words, define "validity" as we use the term.

```{r wisdom-26}
question_text(NULL,
	message = "Validity is the consistency, or lack thereof, in the columns of the data set and the corresponding columns in the Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

In order to consider the two data sets to be drawn from the same population, the columns from one must have a valid correspondence with the columns in the other. Validity, if true (or at least reasonable), allows us to construct the Population Table, which is the first step in Justice.

### Exercise 27

What can't we do if the assumption of validity is not true?

```{r wisdom-27}
question_text(NULL,
	message = "We can't combine the Preceptor Table and the data in order to construct the Population Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 28

Provide one reason why the assumption of validity might not hold for this problem.

```{r wisdom-28}
question_text(NULL,
	message = "People may claim that they voted for one candidate when they really voted for another. This causes the data in the population table to not match up with the columns in the Preceptor Table",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

More people claim to have voted for the winning candidate than the actual number of votes that they receive.

### Exercise 29

Summarize the state of your work so far in one sentence. Make reference to the data you have and to the specific question you are trying to answer. 

```{r wisdom-29}
question_text(NULL,
	message = "Using data from the National Election Studies survey of US citizens, we seek to understand the relationship between voter preference and sex in the 1992 Presidential election.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

## Justice
### 

*Justice delayed is justice denied.* - William E. Gladstone


### Exercise 1

In your own words, name the four key components of Justice for working on a data science problem.

```{r justice-1}
question_text(NULL,
	message = "Justice concerns four topics: the Population Table, stability, representativeness, and unconfoundedness.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 2

In your own words, define a Population Table.

```{r justice-2}
question_text(NULL,
	message = "The Population Table includes a row for each unit/time combination in the underlying population from which both the Preceptor Table and the data are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 3

In your own words, define the assumption of "stability" when employed in the context of data science.

```{r justice-3}
question_text(NULL,
	message = "Stability means that the relationship between the columns in the Population Table is the same for three categories of rows: the data, the Preceptor Table, and the larger population from which both are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Stability is all about *time*. Is the relationship among the columns in the Population Table stable over time? In particular, is the relationship --- which is another way of saying "mathematical formula" --- at the time the data was gathered the same as the relationship at the (generally later) time references by the Preceptor Table.


### Exercise 4

Provide one reason why the assumption of stability might not be true in this case.

```{r justice-4}
question_text(NULL,
	message = "Some voters cast their ballots weeks before election day.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Which would mean that the Preceptor Table and the data do not come from the same moment in time.


### Exercise 5

In your own words, define the assumption of "representativeness" when employed in the context of data science.

```{r justice-5}
question_text(NULL,
	message = "Representativeness, or the lack thereof, concerns two relationship, among the rows in the Population Table. The first is between the Preceptor Table and the other rows. The second is between our data and the other rows.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The more expansive your Preceptor Table, the more important the assumption of representativeness becomes. 



### Exercise 6

Provide one reason why the assumption of representativeness might not be true in this case.

```{r justice-6}
question_text(NULL,
	message = "Representativeness might fail if the data from the Population Table does not match the columns in the Preceptor Table",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The sample that we are using may not accurately represent the rest of the population.



### Exercise 7

In your own words, define the assumption of "unconfoundedness" when employed in the context of data science.

```{r justice-7}
question_text(NULL,
	message = "Unconfoundedness means that the treatment assignment is independent of the potential outcomes, when we condition on pre-treatment covariates.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Because this is a predictive, not causal, model, the assumption of unconfoundedness is irrelevant.


### Exercise 8

Summarize the state of your work so far in two or three sentences. Make reference to the data you have and to the question you are trying to answer. Feel free to copy from your answer at the end of the Wisdom Section. Mention at least one specific problem which casts doubt on your approach. 




```{r justice-8}
question_text(NULL,
	message = "Using data from the National Election Studies (NES) survey of US citizens, we seek to understand the relationship between voter preference and sex in the 1992 Presidential election. Our results might be biased by differential non-response among different categories of voters.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

## Courage
### 

*Courage is the commitment to begin without any guarantee of success.* - Johann Wolfgang von Goethe


### Exercise 1

In your own words, name the key goal of Courage and the process we use to get there.

```{r courage-1}
question_text(NULL,
	message = "Courage selects the data generating mechanism. We first specify the mathematical formula which connects the outcome variable we are interested in with the other data that we have. We explore different models. We need to decide which variables to include and to estimate the values of unknown parameters. We check our models for consistency with the data we have. We avoid hypothesis tests. We select one model.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 2

Make a model using `brm()` from the **brms** package. Your arguments should be: `formula = pres_vote ~ sex`, `data = nes_92`, `family = categorical()`, `silent = 2`, `refresh = 0` and `seed = 76`


Assign the result to an object called `fit_nes`. It may take a while, so be patient.

```{r courage-2, exercise = TRUE}

```

```{r courage-2-hint-1, eval = FALSE}
fit_nes <- brm(... = pres_vote ~ sex,
               ... = nes_92,
               ... = categorical(),
               silent = ...,
               refresh = ...,
               seed = ...)
```

### 

Your code should look like this:

```
fit_nes <- brm(formula = pres_vote ~ sex,
               data = nes_92,
               family = categorical(),
               silent = 2,
               refresh = 0,
               seed = 76)
```

### 

Create a new code chunk with`#| label: model` and `#| echo: FALSE` at the top. Make sure to copy and paste this code into the code chunk. Render the document.

### Exercise 3

Type `fit_nes` and hit "Run Code." This generates the same results as using `print(fit_nes)`.

```{r courage-3, exercise = TRUE}

```

```{r courage-3-hint-1, eval = FALSE}
print(...)
```

```{r courage-3-test, include = FALSE}
print(fit_nes)
```

### Exercise 4

Run `family()` on `fit_nes`. `family()` provides information about the "family" of the error term and the link between it and the dependent variable.


```{r courage-4, exercise = TRUE}

```

```{r courage-4-hint-1, eval = FALSE}
family(...)
```

```{r courage-4-test, include = FALSE}
family(fit_nes)
```

### 

A categorical model is like a logistic model, but, it has more than two options instead of the standard binary dependant variable.

<!-- TJ: Explain what a categorial model is. Hint: It is just like a logistic model, but with more than 2 options. Done-->


### Exercise 5

Run `formula()` on `fit_nes`. `formula()` returns the statistical equation which relates the dependent variable to the independent variable(s).


```{r courage-5, exercise = TRUE}

```

```{r courage-5-hint-1, eval = FALSE}
formula(...)
```

```{r courage-5-test, include = FALSE}
formula(fit_nes)
```

### 

In this case, the formula is `pres_vote ~ sex`. We are finding the correlation between the independant variable (`sex`) and the dependant variable (`pres_vote`)

### Exercise 6

Run `nobs()` on `fit_nes`. The `nobs()` function returns the **n**umber of **obs**ervations.

```{r courage-6, exercise = TRUE}

```

```{r courage-6-hint-1, eval = FALSE}
nobs(...)
```

```{r courage-6-test, include = FALSE}
nobs(fit_nes)
```

### 

In this case, `fit_nes` has 1658 recorded observations

### Exercise 7

Run `posterior_interval()` on `fit_nes`. The `posterior_interval()` function returns 95% intervals for all the parameters in our model.

```{r courage-7, exercise = TRUE}

```

```{r courage-7-hint-1, eval = FALSE}
posterior_interval(...)
```

```{r courage-7-test, include = FALSE}
posterior_interval(fit_nes)
```

### 

The positive value for `muPerot_sexMale` means that men are much more likely to vote for Perot.

<!---TJ: Pick one aspect and describe. The positive value for `muPerot_sexMale` means that men are much more likely to vote for Perot. Same thing for next question, but `muClinton_sexMale`. Done --->




### Exercise 8

Run `fixef()` on `fit_nes`. The `fixef()` returns information about the **fix**ed **ef**fects in the model.

```{r courage-8, exercise = TRUE}

```

```{r courage-8-hint-1, eval = FALSE}
fixef(...)
```

```{r courage-8-test, include = FALSE}
fixef(fit_nes)
```

### 

The negative value for `muClinton_sexMale` means that men are less likely to vote for Perot.

### Exercise 9

Run `pp_check()` on `fit_nes`. The `pp_check()` runs a **p**osterior **p**redictive check.

```{r courage-9, exercise = TRUE}

```

```{r courage-9-hint-1, eval = FALSE}
pp_check(...)
```

```{r courage-9-test, include = FALSE}
pp_check(fit_nes)
```

### 

`pp_check()` is used to examine if the “fake data” created from our DGM matches our actual data. We see that the "fake data" does indeed match our real data.


### Exercise 10

Use `library()` to load the [**gtsummary**](https://www.danieldsjoberg.com/gtsummary) package.

```{r courage-10, exercise = TRUE}

```

```{r courage-10-hint-1, eval = FALSE}
library(gtsummary)
```

```{r courage-10-test, include = FALSE}
library(gtsummary)
```

### Exercise 11

It is also possible to summarize the regression results using the function provided by the **gtsummary** package. 

Pipe `fit_nes` to `tbl_regression()`

<!-- DK: Clean up. -->

```{r courage-11, exercise = TRUE}

```

```{r courage-11-hint-1, eval = FALSE}
tbl_regression(...)
```

```{r courage-11-test, include = FALSE}
tbl_regression(fit_nes)
```

### 

Next we are going to put this table into our document.

### Exercise 12

Make a new code chunk at the bottom of the document, add `#| label: table` and `#| echo: FALSE`. Copy and paste the line `tbl_regression(fit_nes)` into the code chunk. Below that code chunk, add a sentence to describe the results provided by the command. Save the file and in the Console, run:

`tutorial.helpers::show_file("analysis.qmd")`

```{r courage-12}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### Exercise 13

Write a few sentences which summarize your work so far. The first few sentences are the same as what you had at the end of the Justice Section. Add at least one sentence which describes the modelling approach which you are using, specifying at least the functional form and the dependent variable. Add at least one sentence which describes the *direction* (not the magnitude) of the relationship between one of your independent variables and your dependent variable.

```{r courage-13}
question_text(NULL,
	message = "Using data from the National Election Studies (NES) survey of US citizens, we seek to understand the relationship between voter preference and sex in the 1992 Presidential election. Our results might be biased by differential non-response among different categories of voters. We modeled sex, a character variable, as a multinomial logistic regression model. Women are most likely to support Clinton. ",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

## Temperance
### 

*Temperance is a tree which as for its root very little contentment, and for its fruit calm and peace.* - Buddha



### Exercise 1

In your own words, describe the use of Temperance in finishing your data science project.

```{r temperance-1}
question_text(NULL,
	message = "Temperance uses the Data Generating Mechanism to answer the question with which we began. Humility reminds us that this answer is always a lie.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 2

Recall the question with which we began:

> What was the relationship between sex and voting in the 1992 US Presidential election?

### 

<!-- DK: Make plot in tutorial first, then copy/paste. -->

Make a new code chunk above `table` and below `model`. Make sure to add `#| label: temperence` and `#| echo: FALSE`

### Exercise 3

Pipe `fit_nes` to `add_epred_draws()`, set the `newdata` argument equal to `tibble(sex = c("Female", "Male"))`

```{r temperance-3, exercise = TRUE}

```

```{r temperance-3-hint-1, eval = FALSE}
fit_nes |> 
  add_epred_draws(newdata = ...)
```

```{r temperance-3-test, include = FALSE}
fit_nes |> 
  add_epred_draws(newdata = ndata) 
```

### 

<!-- DK: make math look nice. -->

We can use `add_epred_draws()` to explore the posterior distribution of the expected values of $\rho_{clinton}$, Pbush, and Pperot for men and women.



### Exercise 4

Continue the pipe with `select`, select `sex`, `.category` and `.epred`.

```{r temperance-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-4-hint-1, eval = FALSE}
... |> select(...)
```

### Exercise 5

Add `ggplot` to the pipe. Set the argument inside to be `aes(x = .epred, fill = sex)`

```{r temperance-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-5-hint-1, eval = FALSE}
... |> 
  ggplot(aes(...))
```

### Exercise 6

Add `geom_histogram`, set `bins` equal to 100.

```{r temperance-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-6-hint-1, eval = FALSE}
... + 
  geom_histogram(...)
```

### Exercise 7

Next add `facet_grid(~ .category)`

```{r temperance-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-7-hint-1, eval = FALSE}
... + 
  facet_grid(~ .category)
```

### Exercise 8

Add `scale_x_continuous()` to the function. Set `breaks` to `c(0.05, 0.3, 0.6)` and `labels` to `scales::percent_format()`

```{r temperance-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-8-hint-1, eval = FALSE}

```

 
### Exercise 9

Finally, use `labs()` to add your labels. Your plot should look like this:


```{r}
fit_nes |> 
  add_epred_draws(newdata = tibble(sex = c("Female", "Male"))) |>
  select(sex, .category, .epred) |> 
  ggplot(aes(x = .epred, fill = sex)) +
    geom_histogram(bins = 100) +
    facet_grid(~ .category) +
    scale_x_continuous(breaks = c(0.05, 0.3, 0.6),
      labels = scales::percent_format()) +
    labs(title = "Posterior for Expected Probability of Candidate Support Among Women",
          subtitle = "Women are most likely to support Clinton",
          x = "Posterior Probability of Expected Vote Probability",
          y = "Count",
          fill = "Sex") 
```

```{r temperance-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-9-hint-1, eval = FALSE}

```

```{r temperance-9-test, include = FALSE}

```

### 

### Exercise 10

Copy and paste your code into the `temperence` code chunk. Run `tutorial.helpers::show_file("analysis.qmd")`, CP/CR


```{r temperance-10}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### Exercise 11

Write a paragraph which summarizes the project in your own words. The first few sentences are the same as what you had at the end of the Courage Section. But, since your question may have evolved, you should feel free to change those sentences. Add at least one sentence which describes at least one quantity of interest (QoI) --- presumably one that answers your question -- and which provides a measure of uncertainty about that QoI.


```{r temperance-11}
question_text(NULL,
	message = "Using data from the National Election Studies (NES) survey of US citizens, we seek to understand the relationship between voter preference and sex in the 1992 Presidential election. Our results might be biased by differential non-response among different categories of voters. We modeled sex, a character variable, as a multinomial logistic regression model. Women are most likely to support Clinton. ",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- TJ: Need help with the QoI question -->

Copy and Paste your answer to this question underneath the `temperence` code chunk.

### Exercise 12

Write a few sentences which explain why the estimates for the quantities of interest, and the uncertainty thereof, might be wrong. Suggest an alternative estimate and confidence interval.

```{r temperance-12}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- TJ: Need help with this question as well -->

### Exercise 13

Next to The "Run" button, there should be a blue circle-like object. Click that and publish your Quarto document. Copy and paste the RPubs link here:

```{r temperance-13}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

## Summary
### 

This tutorial covered [Chapter 8: Four Parameters: Categorical](https://ppbds.github.io/primer/four-parameters-categorical.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 




```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
