---
title: "Probability B"
tutorial:
  id: "probability-b"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Chapter 5 tutorial Part B"
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(forcats)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

<!-- Start Probability B. Basic structure is the same. Show a plot. And then go through the 15 steps for making the plot, but teach stuff along the way. Note that these examples will not be from the chapter. -->

<!-- First examples show how as sample size increases, you get a distribution which is more and more similar to the mathematical. Do this with rolling two dice. Final plot is 3 x 2 matrix of plots, each an empirical distribution, but with increase N.  Use map functions and list-columns, maybe. -->

<!-- Do tutorial for chapter 6 first! done.-->

<!-- tibble with one column N which is number of samples, one column result,  -->

<!-- N   result -->
<!-- 10    3 -->
<!-- 10    7 -->
<!-- 10    7 -->
<!-- 10    4 -->
<!-- .. -->
<!-- 20 -->
<!-- 20 -->
<!-- 20 -->
<!-- twenty rows -->
<!-- ... -->
<!-- 100 -->
<!-- 100 -->
<!-- one hundred rows -->

<!-- geom_histogram(aes(x = result)) and facet_wrap(~ N) -->

## Rolling two dice
###

The larger the sample size, the more closely your empirical distribution will match the mathematical distribution **if** your mathematical assumptions are correct.

###

This is the plot we will replicate.

```{r}
# Turn your N column into a factor and then give it the levels in the order you
# want it to be. Maybe use forcats. Consider having the plot by 6 x 1. Or maybe
# stacked but with only 4 N values.


set.seed(2)
dice_p <- tibble(N = c(rep("10", 10), 
                       rep("20", 20),
                       rep("50", 50),
                       rep("100", 100),
                       rep("1000", 1000),
                       rep("10000", 10000))) %>%
  mutate(die_1 = map_dbl(N, ~ sample(c(1:6), size = 1))) %>% 
  mutate(die_2 = map_dbl(N, ~ sample(c(1:6), size = 1))) %>% 
  mutate(result = die_1 + die_2) %>%
  mutate(N = as.factor(N)) %>%
  mutate(N = fct_inseq(N)) %>%
  summarise(N, result) %>%
  ggplot(aes(x = result)) +
  geom_histogram(aes(y = stat(density)),
                 binwidth = 1, 
                 color = "white") +
    labs(title = "Empirical Probability Distribution",
         subtitle = "Sum from rolling two dice, Sample size changes",
         x = "Outcome\nSum of Two Die",
         y = "Probability") +
    facet_wrap(~ N, scales = "free") +
    scale_x_continuous(breaks = seq(2, 12, 1), labels = 2:12) +
    scale_y_continuous(labels= scales::percent_format(accuracy = 1))

dice_p

#dice_p use to show the distribution

```

###

The larger the sample size, the more closely your empirical distribution will match the mathematical distribution **if** your mathematical assumptions are correct.


### Exercise 1


Before we begin, write two sentences explaining what is *Empirical Probability Distribution*.

```{r sz-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 3))
```

###

*Empirical Probability Distribution* is a type of distribution that is completely based on data.


### Exercise 2

Use the `rep()` to repeat the value "10" three times.

```{r sz-2, exercise = TRUE}

```


```{r sz-2-hint, eval = FALSE}
rep(10 , = )
```

### Exercise 3

Copy and paste your code from above, now assign the `rep()` to an new column name "C", within the function `tibble()`.
```{r sz-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r sz-3-hint, eval = FALSE}
tibble(C = rep(10, 3))
```

### Exercise 4

Good, now we want to include more values in C, use `c()` to include both `rep(10, 3)` and `rep(500,2)`
```{r sz-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r sz-4-hint, eval = FALSE}
tibble(C = c(rep(10, 3), rep(500, 2)))
```

Your tibble should have 5 rows.

### Exercise 5

Pipe down your result, use `mutate()` to add a new variable "dice" and have "dice" equal to an random values from 1 : 6 using `sample()`, 
```{r sz-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r sz-5-hint, eval = FALSE}
# ...%>% 
#   mutate(dice = sample(1:6))
```

###

This should return an error saying dice` must be size 5 or 1, not 6.


### Exercise 6

We only want one value from 1 to 6, so add in another argument `size` and set it equal to 1.
```{r sz-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r sz-6-hint, eval = FALSE}
# ...%>% 
#   mutate(dice = sample(1:6, size = 1))
```

###

Notice the column dice will always return the same number, this is what we don't want. In order to fix this we need to use the map_* function.


### Exercise 7

Use `map_dbl()` and set the first argument to C and formula to the `sample()` function we create in the last exercise. 
```{r sz-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r sz-7-hint, eval = FALSE}
mutate(dice = map_dbl(C, ~sample(1:6, size = 1)))
```

###

Now let's move in to the real game.


### Exercise 8


<!-- DK: Split this into 3 or 4 separate questions. And then, ask this question. Firts, question has answer of rep(10, 3). Second question has answer of tibble(N = rep(10, 3)). Third question has answer of tibble(N = c(rep(10, 3), rep(500, 2))). Fourth question has answer  tibble(N = c(rep(10, 3), rep(500, 2))) %>%  mutate(result = ...) -->

Create a `tibble()` with variable `N`, and set N to a list of value representing our sample size, then use `rep()` to repeat the function same numbers of times as the sample size. We want 6 different sample size: 10, 20, 50, 100, 1000, 100000.

```{r sz-8, exercise = TRUE}

```


```{r sz-8-hint-1, eval = FALSE}
tibble(N = c(rep("...", ...), 
             rep("...", ...),
             rep("...", ...),
             rep("...", ...),
             rep("...", ...),
             rep("...", ...)))
```

```{r sz-8-hint-2, eval = FALSE}
tibble(N = c(rep("10", 10), 
             rep("20", 20),
             rep("...", ...),
             rep("...", ...),
             rep("...", ...),
             rep("...", ...)))
```

### Exercise 9


Recall exercise 7, let's create another dice,set it equal to one of the 6 value from (1,2,3,4,5,6) for each rows of N using both map_dbl() and `sample()`, lastly assign it to the name "die_1" using `mutate().`
```{r sz-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r sz-9-hint-1, eval = FALSE}
# ...%>%
# mutate(...= map_dbl(..., ~ ...))
```


```{r sz-9-hint-2, eval = FALSE}
# ...%>%
# mutate(...= map_dbl(N, ~sample(c(...: ...), size = 1)))
```

### Exercise 10
Copy and paste the results from above, and do the exact same thing again but instead now named to value to `die_2`, because we need the results for two dices.

```{r sz-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r sz-10-hint, eval = FALSE}
# ...%>%
# mutate(...= map_dbl(N, ~sample(c(...:...), size = 1)))
```

### Exercise 11
Copy and paste the results from above, use the `mutate()` function once again, name the value of the sum of `die_1` and `die_2` to "result"

```{r sz-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r sz-11-hint, eval = FALSE}
# ...%>%
# mutate(result = die_1 + die_2)
```






### Exercise 12

Copy and paste the above, then use `summarise()` to include the column "N" and "result" only

```{r sz-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r sz-12-hint, eval = FALSE}
summarise(N,...)
```


### Exercise 13

Copy and paste the code above, use `ggplot()` to graph the Empirical Distribution, set `x = result` within `aes()`, and then add a layer of `geom_histogram()`
```{r sz-13, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{sz-13-hint, eval = FALSE}
# ...%>%
# ggplot(aes(x = ...)) +
#   geom_histogram()
```

### Exercise 14

Copy and paste your code from above, recalled `facet_wrap()`, use `facet_wrap()` to separate the graph into six small distribution, don't forget the `~` within `facet_wrap()`.

```{r sz-14, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r sz-14-hint-1, eval = FALSE}
# ...+
#   facet_wrap(...)
```


```{r sz-14-hint-2, eval = FALSE}
# ...+
#   facet_wrap(~ N)
```

Your graph should looks similar to this.
```{r}
tibble(N = c(rep("10", 10), 
             rep("20", 20),
             rep("50", 50),
             rep("100", 100),
             rep("1000", 1000),
             rep("10000", 10000))) %>%
  mutate(die_1 = map_dbl(N, ~ sample(c(1:6), size = 1))) %>% 
  mutate(die_2 = map_dbl(N, ~ sample(c(1:6), size = 1))) %>% 
  mutate(result = die_1 + die_2) %>%
  ggplot(aes(x = result)) +
  geom_histogram() +
  facet_wrap(~ N)
```

### Exercise 15

Now we have a graph, but it's not looking very good, it seems like we only have the 10000 strip fills up with bars. This is because the 10000 scales is so big, that the bars in other strip is blocked. In order for them to shows, within `facet_wrap()`, add another argument `scales`, and set it equal to "free". 
```{r sz-15, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r sz-15-hint, eval = FALSE}
# ...+
# facet_wrap(~ ..., scales = "...")
```
This allows the graph to use it's own scale, instead an universal scales that covered all plots.

Your graph should looks like this
```{r}
set.seed(2)
tibble(N = c(rep("10", 10), 
             rep("20", 20),
             rep("50", 50),
             rep("100", 100),
             rep("1000", 1000),
             rep("10000", 10000))) %>%
  mutate(die_1 = map_dbl(N, ~ sample(c(1:6), size = 1))) %>% 
  mutate(die_2 = map_dbl(N, ~ sample(c(1:6), size = 1))) %>% 
  mutate(result = die_1 + die_2) %>%
  ggplot(aes(x = result)) +
  geom_histogram() +
  facet_wrap(~ N,scales = "free")
```

### Exercise 16

Copy and paste your results from above. Note that you see the red `stat_bin()` using `bins = 30`. Pick better value with `binwidth`. Let's get rid of this by adjusting binwidth for our plots, within `geom_histogram()` set "binwidth" equal to 1, and "color" between bins equal to "white".
```{r sz-16, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r sz-16-hint, eval = FALSE}
# ...+
# geom_histogram(binwidth = ..., color = "...") +
#   ...
```


```{r include = FALSE}
# ...%>%
#   ggplot(aes(x = result)) +
#   geom_histogram(binwidth = 1, color = "white") +
#   facet_wrap(~ N,scales = "free")
```

###
Notice the panal(gray bar) above each of the sixth distributions, they are out of order, we want to place them like this (10,20,50,100,1000,10000) so that we can see the evolution of the shape of the graph as the sample size increase.

###


### Exercise 17

Go back to your previous code, right after the `summarize()` and before your `ggplot()`, use `mutate()` and `as.factor()` to reformat N into factor.

```{r sz-17, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r sz-17-hint, eval = FALSE}
mutate(N = as.factor(N))
```

### Exercise 18

Pipe down your results, now do the exact same thing again for N, use `mutate()`, but this time we use th new function `fct_inseq()` to replace `as.factor()`, this allow us to ordered the in sequnce from small to large.
```{r sz-18, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r sz-18-hint, eval = FALSE}
mutate(N = fct_inseq(N))
```

### Exercise 19

Copy and paste your code from above. Now look at the values on the y-axis, for each one of the sixth plot the value is different, this is because we have different sample size, and it makes sense for each to have different *count*. In order to create an *Empirical Probability distribution*. In order to *normalized* the plot, Within `geom_histogram()`, use `aes()` . Inside `aes()`, we use the argument `y = stat(density)` to set it to put percent on y-axis.
```{r sz-19, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r sz-19-hint, eval = FALSE}
# ...+
#     geom_histogram(aes(y = stat(...))) +
#   ...
```

```{r include = FALSE}
set.seed(2)
tibble(N = c(rep("10", 10), 
             rep("20", 20),
             rep("50", 50),
             rep("100", 100),
             rep("1000", 1000),
             rep("10000", 10000))) %>%
  mutate(die_1 = map_dbl(N, ~ sample(c(1:6), size = 1))) %>% 
  mutate(die_2 = map_dbl(N, ~ sample(c(1:6), size = 1))) %>% 
  mutate(result = die_1 + die_2) %>%
  mutate(N = as.factor(N)) %>%
  mutate(N = fct_inseq(N)) %>%
  ggplot(aes(x = result)) +
  geom_histogram(aes(y = stat(density)),binwidth = 1, color = "white") +
  facet_wrap(~ N,scales = "free")
```

### Exercise 20
Now use `scale_x_continuous()` so the x-axis has `breaks` to the sequence between 2 and 12 common difference is 1 using `seq()`. Set the `labels` for the breaks as from 2 to 12.

```{r sz-20, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r sz-20-hint-1, eval = FALSE}
...+
scale_x_continuous(breaks = seq(...,..., ...), labels = ...:...) 
```


```{r sz-20-hint-2, eval = FALSE}
# ...+ 
#   scale_x_continuous(breaks = seq(2, 12, 1), labels = 2:12) 
```


### Exercise 21

Now use `scale_y_continuous()` to put the x-axis in percent format. Within `scale_y_continuous()`, set `labels` to `scales::percent_format()`. Within `percent_format()` set `accuracy` to 1.

```{r sz-21, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r sz-21-hint, eval = FALSE}
# ...+ 
#   scale_y_continuous(labels = scales::percent_format(...))
```

### Exercise 22

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels.

```{r sz-22, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>


```{r sz-22-hint, eval = FALSE}
# ...+ 
#   labs(title = "...",subtitle = "...")
```


Reminder: Your plot should look similar to the the one below. 

```{r}
dice_p
```



```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```



