---
title: "Probability B"
tutorial:
  id: "probability-b"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Chapter 5 tutorial Part B"
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

```

```{js change-code, echo = FALSE}
function transfer_code(elem){
  Shiny.setInputValue("js_to_server", elem.previousElementSibling.dataset.label);
  
}

Shiny.addCustomMessageHandler('set-exercise-code', function(x) {
  var el = $(`.tutorial-exercise[data-label="${x.label}"] .tutorial-exercise-code-editor`)
  var exerciseInput = Shiny.inputBindings.bindingNames["tutorial.exerciseInput"].binding
  exerciseInput.setValue(el, {code: x.code});
  Shiny.setInputValue("js_to_server", null);
})
```

```{r observe-transfers, context = "server"}
observeEvent(input$js_to_server, {
  ex_next = input$js_to_server
  str_num = parse_integer(gsub("[^0-9]", "", ex_next)) - 1
  str_head = gsub("[0-9]", "", ex_next)
  ex_prev = paste0(str_head, str_num)
  code <- learnr:::get_exercise_submission(session, ex_prev)$data$code %>% trimws()
  session$sendCustomMessage("set-exercise-code", list(label = ex_next, code = code))
})
```





## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```

All of the excercise in Probability a is to help you do the example in the primer by yourself, and get yourself familiar rise with different distributions, and how we generally make them step by step. However, this tutorial probability b is dedicate to do something similar to a but different in terms of content, this tutorials will not have any information mentioned in the primer, we are making something new! Let's get started!

## Roulette (outside bet)













```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```



