---
title: Five Parameters
author: David Kane and Sanaka Dash
tutorial:
  id: five-parameters
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: 'Chapter 9 Tutorial: Five Parameters'
---

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(gt)

library(tidyverse)
library(brms)          # Delete soon
library(tidybayes)     # Delete soon
library(primer.data)
library(tidymodels)
library(marginaleffects)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 

df1 <- governors |> 
  filter(year > 1945) |> 
  select(last_name, year, state, sex, lived_after, election_age)

df2 <- df1 |> mutate(sex = recode(sex,
    "Male" = 0, "Female" = 1))

 # fit_all <- lm(lived_after ~ sex * election_age, data = df2)

 # write_rds(fit_all, "data/fit_all.rds")

fit_all <- read_rds("data/fit_all.rds")

governor <- data.frame(sex = 1, election_age = 52)
```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

<!-- DK: Lots of sloppiness everywhere in this tutorial. Too wordy. -->

## Introduction
### 

This tutorial supports [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 

The world confronts us. Make decisions we must.

Imagine that you are ... XX



## The Question
### 

*A Prudent Question is one-half of wisdom.* - Francis Bacon

### Exercise 1

Load **tidyverse**.

```{r the-question-1, exercise = TRUE}

```

```{r the-question-1-hint-1, eval = FALSE}
library(tidyverse)
```

```{r the-question-1-test, include = FALSE}
library(tidyverse)
```

### 

We will be working with information about candidates for governor in the United States. The data was collected for “[Longevity Returns to Political Office](https://doi.org/10.1017/psrm.2019.63)” by Sebastian Barfort, Robert Klemmensen, and Erik Gahner Larsen ([pdf](https://github.com/PPBDS/primer.data/blob/master/inst/papers/governors.pdf)).

### Exercise 2

Load the **primer.data** package.

```{r the-question-2, exercise = TRUE}

```

```{r the-question-2-hint-1, eval = FALSE}
library(primer.data)
```

```{r the-question-2-test, include = FALSE}
library(primer.data)
```

### 

A version of the data from Barfort et al (2020) is available in the `governors` tibble, which is included in the **primer.data** package.


### Exercise 3

After loading **primer.data** in your Console, type `?governors` in the Console, and paste in the Description below.

```{r the-question-3}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

The abstract of the paper that the tibble is based on: 

> Does political office cause worse or better longevity prospects? Two perspectives in the literature offer contradicting answers. First, increased income, social status, and political connections obtained through holding office can increase longevity. Second, increased stress and working hours associated with holding office can have detrimental effects on longevity. To provide causal evidence, we exploit a regression discontinuity design with unique data on the longevity of candidates for US gubernatorial office. The results show that politicians winning a close election live 5–10 years longer than candidates who lose.

### Exercise 4

Longevity i.e., how long people live, is the broad topic of this tutorial. Given this topic, which variable in `governors` should we use as our outcome variable? 

*Hint:* It might be useful to preview the `governors` tibble in the Console (to get an idea of the columns)

```{r the-question-4}
question_text(NULL,
	message = "It would be most logical to use `lived_after`.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 2)
```

### 

`lived_after` is the years a candidate lived after the election took place.

### Exercise 5

Let's imagine a brand new variable which **does not exists** in the data. This variable should be binary, meaning that it only takes on one of two values. It should also, at least in theory, by manipulable. In other words, if the value of the variable is "X," or whatever, then it generates one potential outcome and if it is "Y," or whatever, it generates another potential outcome.

Describe this imaginary variable and how might we manipulate its value.

```{r the-question-5}
question_text(NULL,
	message = "We will use `sex` as a treatment variable. Of course, in reality, you can't really change someone's sex. But, for the sake of this exercise, let's imagine that we have a magic pill that does so.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Besides the names, all other columns would be valid answers to this problem. But going forward, you should use the variable we have selected.


### Exercise 6

Causal models aim to understand how changing one variable (the treatment) causes changes in another variable (the outcome). Each different value of the treatment generates a different potential outcome.

Any data set can be used to construct a causal model as long as there is at least one treatment and covariate that we can manipulate (in theory). It does not matter whether or not anyone did, in fact, manipulate it.

Given our choice of treatment variable `sex`, how many potential outcomes are there for each candidate? Explain why.

```{r the-question-6}
question_text(NULL,
	message = "The value of `sex` would create 2 potential outcomes for each candidate because each sex would drastically change the longevetiy of the candidate.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The point of the Rubin Causal Model is that the definition of a causal effect is the difference between potential outcomes. So, there must be two (or more) potential outcomes for any causal model to make sense. 

<!-- DK: I am not satisfied with the wording of this next question. Our end goal is the calculation, by the student, of a causal effect, as in Exercise 8. The previous step was to just determine the number of potential outcomes, as in Exercise 6. This question wants to get students to see that each different treatment is associated with a potential outcome. Is there a better approach? - DONE -->
<!-- SD: is this a better approach? -->

### Exercise 7

Write a sentence about what the 2 potential outcomes could look like for each candidate when `sex` changes. 

```{r the-question-7}
question_text(NULL,
	message = "When `sex` is male, we expect that the longevity of the candidate after election would be longer. Conversely, when `sex` is female, we expect the longevity of the candidate to drop.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 8

Write a few sentences which specify two different values for the treatment variable, for a single unit, and then guesses at the potential outcomes which would result, and then calculate the causal effect for that unit given those guesses.

```{r the-question-8}
question_text(NULL,
	message = "For a given candidate, the value of `sex` (the treatment variable) might be 'male' or 'female'. If the candidate gets 'male', then the outcome would be 15. If the candidate gets 'female', then the outcome would be 30. The causal effect on the outcome of a treatment of 'male' versus 'female' is 15 - 30, which equals -15.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Again, we are trying to reinforce that the definition of a causal effect is the difference between two potential outcomes. 

Of course, you can't just say that the causal effect is 15. The exact value depends on which potential outcome comes first in the subtraction and which second. In this case, the causal effect is -15, indicating that male candidates live -15 years longer after their election than female candidates. 

Also note that in the real world, you almost never get perfect numbers like this. These were just example figures to help understand the concept of causal effect.

Any causal connection means exploring the *within row* difference between two potential outcomes. We don't need to look at any other rows to have that conversation.

### Exercise 9

Let's now consider a *predictive* model. 

A predictive model handles comparisons across and between rows. Any data set can be used to construct a predictive model. 

Predictive models aim to accurately predict the outcome based on the observed patterns in the data, without necessarily understanding the underlying causal relationships.

Which variable in `governors` do you think might have an important connection to `lived_after`?

```{r the-question-9}
question_text(NULL,
	message = "Again, we can use `sex` to predict the differences in logevity.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 2)
```

### 

Again, there is no "right" answer, but you should follow along with our answer from now onwards.

Notice how we used the same data set across the two types of models. This just proves that with the right set-up, the same data and variables can be used to make two completely different model structures.


### Exercise 10

Write a sentence or two that specifies two different groups of candidates with different values for `sex`. Explain how the outcome variable might differ between these two groups.

```{r the-question-10}
question_text(NULL,
	message = "Some candidates might have a value for `sex` of `male`. Others might have a value of `female`. Those two groups will, on average, have different values for the `lived_after`(outcome variable).",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The key point is that, with a predictive model, there is only one outcome for each individual unit. There are not two potential outcomes because we are not considering any of the covariates to be treatment variables. We assuming that all covariates are "fixed." In that case, we should not use words like "cause," "influence," "impact," or anything else which suggests causation. The best phrasing is in terms of "differences" between groups of units with different values for the covariate of interest.


### Exercise 11

Write a predictive question which connects the outcome variable `lived_after` to a covariate of interest. (It could be the same variable that we used in the previous problems).

```{r the-question-11}
question_text(NULL,
	message = "How does sex impact the number of years that a governor lives after being elected?",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

There are lots of interesting questions that you may write. However, stick with our question as this will be what our tutorial revolves around.


### Exercise 12

What is the quantity of interest which might help us to explore the answer to our question?

```{r the-question-12}
question_text(NULL,
	message = "We want to estimate the difference in the number of years that a male candidate lives after their election and those of a female candidate.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

In general, our question does not include any specific numbers. It just uses words. In all cases, the quantity of interest involves the outcome variable. (How could it not?) It also involves specific values of the covariates.

For predictive models, the specific question is generally of two types. First, what is the *expected* value of the outcome for various values of the independent variables.

For causal models, we are almost always interested in the causal effect of treatment versus control, or, more generally, the difference between various potential outcomes.


## Wisdom
### 

*The only true wisdom is in knowing you know nothing.* - Socrates

### 

Our question:

> *How long do political candidates live after the election?*


### Exercise 1

In your own words, describe the key components of Wisdom for working on a data science problem. 

```{r wisdom-1}
question_text(NULL,
	message = "Wisdom requires the creation of a Preceptor Table, an examination of our data, and a determination, using the concept of validity, as to whether or not we can (reasonably!) assume that the two come from the same population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 2

Define a Preceptor Table.

```{r wisdom-2}
question_text(NULL,
	message = "A Preceptor Table is the smallest possible table of data with rows and columns such that, if there is no missing data, it is easy to calculate the quantities of interest.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 3

Describe the key components of Preceptor Tables in general, without worrying about this specific problem.


```{r wisdom-3}
question_text(NULL,
	message = "The rows of the Preceptor Table are the units. The outcome is at least one of the columns. If the problem is causal, there will be at least two (potential) outcome columns. The other columns are covariates. If the problem is causal, at least one of the covariates will be a treatment.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 4

Create a Github repo called `tutorial-9`. Connect it to an new R Project called `tutorial-9`. Edit the `.gitignore` file to ignore the Rproj file.

In the Console, run `library(tutorial.helpers)` followed by `show_file(".gitignore")`. CP/CR.

```{r wisdom-4}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 6)
```

### Exercise 5

What are the units for this problem?

HINT: Ask yourself "Who's being affected in this scenario?"

```{r wisdom-5}
question_text(NULL,
	message = "Our units for this problem would be individual candidates because the questions are about the life expectancy of those candidates.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

These answers vary based on the question we are answering. 

If we were to have adjusted our question to ask about the number of states that had candidates who lived past a certain age, then our units would have been the individual states rather than the candidates themselves.

For this tutorial, though, we will be sticking to the individual candidates, as they are what goes best with our question.

### Exercise 6

What is the outcome for this problem?

HINT: Ask yourself "What are we trying to get out of this problem?"

NOTE: The outcome is what WE want to get out of the data, based on our QUESTION. It does NOT concern the POSSIBLE values that we CAN extract.

```{r wisdom-6}
question_text(NULL,
	message = "The number of years a candidate lives after the election.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Again, these answers vary based on the question we are answering. 

If we were to have adjusted our question to ask about the number of states that had candidates who lived past a certain age, then our outcome would have been the number of states rather than the age of the candidates.

For this tutorial, though, we will be sticking to the age of the individual candidates, as they are what goes best with our question.


### Exercise 7

What are some covariates which you think might be useful for this problem, regardless of whether or not they might be included in the data?

NOTE: Covariates are any variable that might have some connection with the outcome.

```{r wisdom-7}
question_text(NULL,
	message = "We will certainly need sex, with two values: “male” and “female”. Other variables that might be helpful include age at election, how close the election was, and past voting history (among others).",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The term "covariates" is used in at least three ways in data science. First, it is all the variables which might be useful, regardless of whether or not we have the data. Second, it is all the variables which we have data for. Third, it is the set of covariates which we end up using in the model.


### Exercise 8

What are the treatments, if any, for this problem?

```{r wisdom-8}
question_text(NULL,
	message = "Since this is a predictive model there is no treatment per se. Any variable which one might consider a treatment is just another covariate in this context.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Note how the paper actually uses winning the election as a non-randomly assigned treatment.


### Exercise 9

What moment in time does the Preceptor Table refer to? (You should refer to the *Primer* itself when answering questions like this.)

```{r wisdom-9}
question_text(NULL,
	message = "At this point in time, we don't know what moment in time it should cover because the question itself doesn't state any clear time frame. For all we know, it could include entries from the past, present, and even future!",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Is the question interested in all candidates who are running in the next election? All those who ran in the past? Those who are running right now?

We also wonder how it would be relevant to include a candidate running from the future in our data, as we don't know how long they will live after they get elected. What if they don't get elected at all? What kind of effects would this have on their longevity?


### Exercise 10

Describe in words the Preceptor Table for this problem.

```{r wisdom-10}
question_text(NULL,
	message = "Our Preceptor Table would contain a list of candidates on the right-hand side of the table, and on the left-hand side, would contain variables concerning their sex, the year that they got elected, the age at which they got elected, and the number of years that they lived after getting elected.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The Preceptor Table for this problem looks something like this:

```{r}
#| echo: false

tibble(ID = c("Candidate 1", "Candidate 2", "...", "Candidate 10", "Candidate 11", "...", "Candidate N"),
       lived_after = c("12", "7", "...", "10", "11", "...", "6"),
       year_elected = c("2000", "2012", "...", "2012", "2024", "...", "2050"),
       election_age = c("63", "47", "...", "52", "75", "...", "68"),
       sex = c("Female", "Male", "...", "Female", "Female", "...", "Male")) |>
  gt() |>
  tab_header(title = "Preceptor Table") |>
  cols_label(ID = md("ID"),
             lived_after = md("Years Lived After"),
             year_elected = md("Year of Election"),
             election_age = md("Age at Election"),
             sex = md("Sex")) |>
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(ID))) |>
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"), 
            locations = cells_column_labels(columns = c(ID))) |>
  cols_align(align = "center", columns = everything()) |>
  cols_align(align = "left", columns = c(ID)) |>
  fmt_markdown(columns = everything()) |>
  tab_spanner(label = "Outcome", columns = c(lived_after)) |>
  tab_spanner(label = "Covariates", columns = c(sex, year_elected, election_age))
```

Note that we can calculate anything related to longevity because we know how many years each candidate lived after an election. But, in reality, many of these candidates are still alive, so we don’t know how long they will live.

### 

Note that, like all aspects of a data science problem, the Preceptor Table evolves as we work on the problem. For example, at the start, we aren't sure what right-hand side variables will be included in the model, so we are not yet sure which columns must be in the Preceptor Table.


### Exercise 11

Write one sentence describing the data (from the Preceptor Table) to answer your question.

Hint: Use the phrase *we seek to* to address your intentions for the data.

```{r wisdom-11}
question_text(NULL,
	message = "Using data regarding candidate age, sex and longevity in the United States between 2000 and 2050, we seek to forecast candidate longevity post-election.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Note that in the Preceptor Table, we have an entry for a candidate who is (supposedly) running right now. Doesn't it seem odd that it says he will live for another 11 years after getting elected? How is it real if it's in the future?


### Exercise 12

Let's create a new `.qmd` file. Name it "Five Parameters" and render the document with `Command/Ctrl+Shift+K`. Save the file as `five-parameters.qmd`. 

Run `list.files()` in the Console. CP/CR.

```{r wisdom-12}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### Exercise 13

In `five-parameters.qmd`, remove everything after the YAML Header. Then add the following code to the YAML Header:  

````
execute: 
  echo: false
```` 

In the Console, run `show_file("five-parameters.qmd")`. CP/CR.

```{r wisdom-13}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### Exercise 14

In the same file, add a new code chunk. Add `#| label: setup` and `#| message: false` to the first two lines of the chunk.

Now add the **tidyverse** and **primer.data** packages to the code chunk. Render the document.

In the Console, run `show_file("five-parameters.qmd")`. CP/CR.

```{r wisdom-14}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### Exercise 15

Finally, let's update our `.gitignore`. Open it up, and add `*_files` to the list.

In the Console, run `show_file(".gitignore", start = -5)`. CP/CR.

```{r wisdom-15}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

Commit/Push your changes to GitHub.

### Exercise 16

Now let's get to know our data. Use `glimpse()` on `governors` in the box below.

```{r wisdom-16, exercise = TRUE}

```

```{r wisdom-16-hint-1, eval = FALSE}
glimpse(...)
```

```{r wisdom-16-test, include = FALSE}
glimpse(governors)
```

The reason we used `glimpse()` was to display all of the columns and get a glimpse (get it!) of the kind of data that we have. If we were to have used `head()` or `print()`, then chances are that it wouldn't have showed all of the columns.

If we would have used `summary()`, it would have given us insights on the amount of data that we have, but wouldn't show us the data itself. This is useful when gathering insight on the amount of data in each column.



### Exercise 17

While we're at it, it would still be a good idea to run `summary()` on `governors`.

```{r wisdom-17, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r wisdom-17-hint-1, eval = FALSE}
summary(...)
```

```{r wisdom-17-test, include = FALSE}
summary(governors)
```

### 

Here, we immediately notice how they maximum year is 2011. Note that we were still right though, in that most of the material is still from the previous century (as we can tell by the `Mean` row in the `year` column).


### Exercise 18

In your own words, define "validity" as we use the term.

```{r wisdom-18}
question_text(NULL,
	message = "Validity is the consistency, or lack thereof, in the columns of the data set and the corresponding columns in the Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Is the meaning of the columns consistent, i.e., can we assume validity? That is the heart of validity. To put it simply, does the `lived_after` column in our Preceptor Table equate to same column in our data set?


### Exercise 19

Provide one reason why the assumption of validity might not hold for this problem.

Hint: Refer to the *Primer* for insight on possible concerns for validity.

<!-- SD: Note that this section in the Primer needs some improvement -->

```{r wisdom-19}
question_text(NULL,
	message = "In our data, the information about birth and death dates for *losing* candidates isn't nearly as well-documented a it is for *winning* candidates, so the information was gathered from untrustworthy sources.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 20

Summarize the state of your work so far in one or two sentences. Make reference to the data you have and to the question you are trying to answer. 


```{r wisdom-20}
question_text(NULL,
	message = "Using data from all deceased gubernatorial candidates in the United States between 1945 and 2012, we seek to forecast candidate longevity post-election.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Edit your answer as you see fit, but do not copy/paste our answer exactly. Add this summary to `five-parameters.qmd`, `Command/Ctrl + Shift + K`, and then commit/push.


## Justice
### 

*It is in justice that the ordering of society is centered.* - Aristotle


### Exercise 1

In your own words, name the four key components of Justice for working on a data science problem.

```{r justice-1}
question_text(NULL,
	message = "Justice concerns four topics: the Population Table, stability, representativeness, and unconfoundedness.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 2

In your own words, define a Population Table.

```{r justice-2}
question_text(NULL,
	message = "The Population Table includes a row for each unit/time combination in the underlying population from which both the Preceptor Table and the data are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

We have not specified the rows for either the Preceptor Table or the Population Table concerning what sort of elections we are interested in. How about Senate races? Those are similar to gubernatorial elections in that they are state-wide and attract series candidates. 

But are there rows for other elections? What about mayorial elections? What about the town library committee? We need to make some choices here and, given that we only have data for gubernatorial elections, we need to be careful. Update:

> Using data from all deceased gubernatorial candidates in the United States between 1945 and 2012, we seek to forecast candidate longevity in state-wide US races post-election.

This is a change in our Preceptor Table. We are no longer interested in candiates outside the US, or those running outside of gubernatorial or Senate contests.


### Exercise 3

In your own words, define the assumption of "stability" when employed in the context of data science.

```{r justice-3}
question_text(NULL,
	message = "Stability means that the relationship between the columns in the Population Table is the same for three categories of rows: the data, the Preceptor Table, and the larger population from which both are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Lifespan changes over time. Therefore, our estimates for the future may need some adjustment — that is, to add years to our predicted life expectancy to account for a global change in lifespan over time.


### Exercise 4

Provide one reason why the assumption of stability might not be true in this case.

```{r justice-4}
question_text(NULL,
	message = "The average lifespan in 1950 is different than the average in 2020, so our lifespan in the future must be tweaked in regard to this discrepancy.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

In fact, between 1960 and 2015, life expectancy for the total population in the United States increased by almost 10 years. 

When we are confronted with this uncertainty, we can consider making our timeframe smaller.

*The longer the time period covered by the Preceptor Table (and the data), the more suspect the assumption of stability becomes.*


### Exercise 5

In your own words, define the assumption of "representativeness" when employed in the context of data science.

```{r justice-5}
question_text(NULL,
	message = "Representativeness, or the lack thereof, concerns two relationship, among the rows in the Population Table. The first is between the Preceptor Table and the other rows. The second is between our data and the other rows.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

*The more expansive your Preceptor Table, the more important the assumption of representativeness becomes.*

This data is **highly** representative of gubernatorial candidates (state officials), as it includes every candidate from 1945 to 2012. 

### Exercise 6

Provide one reason why the assumption of representativeness might not be true in this case.

```{r justice-6}
question_text(NULL,
	message = "Only the two candidates with the most votes are included in the data set. This is unfortunate, as we would ideally look at all gubernatorial candidates (regardless of votes).",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Given this data-implementation, we can either:

1) change the question we are answering (restricting it to just major party candidates) or 
2) assume that major party candidates are not systematically different from all candidates.

In this tutorial, we will be assuming Option 2.


### Exercise 7

In your own words, define the assumption of "un   confoundedness" when employed in the context of data science.

```{r justice-7}
question_text(NULL,
	message = "Unconfoundedness means that the treatment assignment is independent of the potential outcomes, when we condition on pre-treatment covariates.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

This assumption is only relevant for causal models. We describe a model as "confounded" if this is not true.


### Exercise 8

Summarize the state of your work so far in two or three sentences. Make reference to the data you have and to the question you are trying to answer. Feel free to copy from your answer at the end of the Wisdom Section. Mention at least one specific problem which casts doubt on your approach. 


```{r justice-8}
question_text(NULL,
	message = "Using data from all deceased gubernatorial candidates in the United States from elections held between 1945 and 2012, we seek to forecast candidate longevity in state-wide US races post-election. There is concern that longevity for gubernatorial candidates will differ significantly from that for candidates in Senate and other state-wide elections.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

Note: Your paragraph doesn't necessarily have to be as long as ours is :)

### 

Edit the summary paragraph in `five-parameters.qmd` as you see fit, but do not copy/paste our answer exactly. `Command/Ctrl + Shift + K`, and then commit/push.

## Courage
### 

*Courage is going from failure to failure without losing enthusiasm.* - Winston Churchill


### Exercise 1

In your own words, name the key goal of Courage and the process we use to get there.

```{r courage-1}
question_text(NULL,
	message = "Courage begins with the exploration and testing of different models. It concludes with the creation of a data generating mechanism.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 2

Load the **brms** package. Load this into the Console as well, as we will be using it later in the Console.

```{r courage-2, exercise = TRUE}

```

```{r courage-2-hint-1, eval = FALSE}
library(...)
```

```{r courage-2-test, include = FALSE}
library(brms)
```

### Exercise 3

Load the **tidybayes** package.

```{r courage-3, exercise = TRUE}

```

```{r courage-3-hint-1, eval = FALSE}
library(...)
```

```{r courage-3-test, include = FALSE}
library(tidybayes)
```

### Exercise 4

Add `library(brms)` and `library(tidybayes)` to `five-parameters.qmd`. `Command/Ctrl + Shift + K`. At the Console, run:

```
show_file("five-parameters.qmd", pattern = "brms|tidybayes")
```

CP/CR.

```{r courage-4}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### Exercise 5

Pipe `governors` to `filter(year > 1945)`.

```{r courage-5, exercise = TRUE}

```

```{r courage-5-hint-1, eval = FALSE}
governors |> 
  ...(year > 1945)
```

```{r courage-5-test, include = FALSE}
governors |> 
  filter(year > 1945)
```

### 

There is some reason to be suspicious of the pre-1945 data. Moreover, the assumption of stability is more difficult to maintain the further back in time our data go.

### Exercise 6

Continue the pipe with `select(last_name, year, state, sex, lived_after, election_age)`.


```{r courage-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r courage-6-hint-1, eval = FALSE}
... |> 
  ...(last_name, year, state, ..., lived_after, election_age)
```

```{r courage-6-test, include = FALSE}
governors |> 
  filter(year > 1945) |> 
  select(last_name, year, state, sex, lived_after, election_age)
```

### 

It is useful to restrict the tibble to just the variables we will be using, the better to notice any problems.


### Exercise 7

We have taken the result of result of the previous pipe and assigned it to an object named `df`. Type `df1` below and hit "Run Code."

```{r courage-7, exercise = TRUE}

```

```{r courage-7-hint-1, eval = FALSE}
df1
```

```{r courage-7-test, include = FALSE}
df1
```

### 

We will use this tibble when we fit the model.


### Exercise 8

We will now begin creating the model. Observe the following model. 

````
fit_all <- brm(data = df1,
                 formula = lived_after ~ sex*election_age,
                 silent = 2,
                 refresh = 0,
                 seed = 13)
````

Type `fit_all` and hit "Run Code". This generates the same results as using `print(fit_all)`.

```{r courage-8, exercise = TRUE}

```

```{r courage-8-hint-1, eval = FALSE}
fit_all
```

```{r courage-8-test, include = FALSE}
print(fit_all)
```

### 

<!-- AC: What has the intercept increased from? IIRC this is the first time seeing one of this model.  -->

The intercept has increased, and is around 19. This is the intercept for females who are the average age. It means the average number of years lived after the election for women who are the average age is 19 or so. 

**Key point:** The interpretation of the intercepts only apply to candidates who are 52 year-old females. Candidates who are not 52 years-old will have a different expected number of years to live. The interpretation of the slope applies to everyone. In other words, the relationship between 
 and 
 is the same, regardless of your gender or how old you are.

<!-- AC: Also, there seem to be symbols missing between lines 998 and 1000.  -->

### Exercise 9

Run `family()` on `fit_all`. `family()` provides information about the "family" of the error term and the link between it and the dependent variable. 

```{r courage-9, exercise = TRUE}

```

```{r courage-9-hint-1, eval = FALSE}
family(...)
```

```{r courage-9-test, include = FALSE}
family(fit_all)
```

### 

In this case, we see that the family of the error term is Gaussian. In a Gaussian data generating mechanism, we have:
$\text{lifespan}_ i \sim \mathcal{N}(\mu, \sigma^2)$
Each governor $i$ who we sample has a certain average lifespan post-election. The value drawn is the number of years each governor lives after their term, with the distribution centered around the mean $\mu$ and spread determined by the variance $\sigma^2$. This is a common way to model continuous data like lifespans.

Also note how in our `brm()` call, we didn't specify the family as being `gaussian`. This worked because the default `family()` call in `brm()` is `gaussian`, so if we didn't specify the parameter, it would use this as the default.


### Exercise 10

Run `nobs()` on `fit_all`. The `nobs()` function returns the **n**umber of **obs**ervations.

```{r courage-10, exercise = TRUE}

```

```{r courage-10-hint-1, eval = FALSE}
nobs(...)
```

```{r courage-10-test, include = FALSE}
nobs(fit_all)
```

### 

`nobs()` is an extremely useful command that tells us the number of useful, non-error observations that we have in the data. In our case, it should have returned "1092" as its answer.


### Exercise 11

Run `formula()` on `fit_all`. `formula()` returns the statistical equation which relates the dependent variable to the independent variable(s). 

```{r courage-11, exercise = TRUE}

```

```{r courage-11-hint-1, eval = FALSE}
formula(...)
```

```{r courage-11-test, include = FALSE}
formula(fit_all)
```

### 

<!-- SD: Shouldn't this be introduced before we make the fitted model? I feel like that would make wayy more logical sense. -->

To look at interactions, we need 5 parameters, which is why we needed to wait until this chapter to introduce the concept. Here is the mathematical formula:

$$ lived\_after_i =  \beta_0 + \beta_1 male_i + \beta_2 c\_election\_age_i + 
\\ \beta_3 male_i *  c\_election\_age_i + \epsilon_i $$

* Our outcome variable is still $lived\_after_i$. We want to know how many years a candidate will live after an election. $male_i$ is one for male candidates and zero for female candidates. $c\_election\_age_i$ the number of years a candidate has lived before the election. In this model, we have a third predictor variable: the interaction between $male_i$ and $c\_election\_age_i$. 

* $\beta_0$ is the average number of years lived after the election for women.

* $\beta_1$ does not have a simple interpretation as a stand-alone parameter. It is a measure of how different women are from men. However, $\beta_0 + \beta_1$ has a straightforward meaning exactly analogous to the meaning of $\beta_0$. The sum is the average number of years lived after the election for *men*, who on the day of election, have been alive the average number of years of all candidates.

* $\beta_2$ is the coefficient of $c\_election\_age_i$. It it just the slope for women. It is the average difference in $lived\_after_i$ between two women, one of whom has an $c\_election\_age_i$ value of 1 greater than the other.

* $\beta_3$ alone is difficult to interpret. However, when it is added to $\beta_2$, the result in the slope for men.


### Exercise 12

Add the mathematical formula for your model to the QMD, using $\LaTeX$ math notation. When it looks good, `Command/Ctrl + Shift + K` to ensure that it works.

```
$$ lived\_after_i =  \beta_0 + \beta_1 male_i + \beta_2 c\_election\_age_i + 
\\ \beta_3 male_i *  c\_election\_age_i + \epsilon_i $$
```

Run `show_file("five-parameters.qmd", start = -5)` in the Console. CP/CR.

```{r courage-12}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

A key distinction when reading formulas is between:

Variables, always scripted with $i$, whose values (potentially) vary across individuals.

Parameters, never scripted with $i$, whose values are constant across individuals.

*Key point*: The interpretation of the intercepts only apply to candidates for whom $c\_election\_age_i = 0$. Candidates who are not `r round(mean(df1$election_age), 0)` years-old will have a different expected number of years to live. The interpretation of the slope applies to everyone. In other words, the relationship between $lived\_after_i$ and $c\_election\_age_i$ is the same, regardless of your gender or how old you are.


### Exercise 13

Create a new code chunk in `five-parameters.qmd`. Add two code chunk options: `#| label: model` and `#| cache: true`. Copy/paste the code from above for estimating the model using `brm()` into the code chunk, assigning the result to `fit_all`. Don't forget the code that makes `df1`. 

`Command/Ctrl + Shift + K`. It may take some time to render `five-parameters.qmd`, depending on how complex your model is. But, by including `cache: true` you cause Quarto to cache the results of the chunk. The next time you render `five-parameters.qmd`, as long as you have not changed the code, Quarto will just load up the saved fitted object.

To confirm, `Command/Ctrl + Shift + K` again. It should be quick.

At the Console, run:

```
show_file("five-parameters.qmd", start = -8)
```

CP/CR.

```{r courage-13}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```





## Temperance
### 

Temperance is a tree which as for its root very little contentment, and for its fruit calm and peace.* - Buddha

### Exercise 1

In your own words, describe the use of Temperance in data science.

```{r temperance-1}
question_text(NULL,
	message = "Temperance uses the data generating mechanism to answer the question with which we began. Humility reminds us that this answer is always a lie. We can also use the DGM to calculate many similar quantities of interest, displaying the results graphically.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Courage gave us the data generating mechanism. Temperance guides us in the use of the DGM — or the “model” — we have created to answer the question with which we began. We create posteriors for the quantities of interest. 

### Exercise 2

Load the [**marginaleffects**](https://marginaleffects.com/) package.

```{r temperance-2, exercise = TRUE}

```

```{r temperance-2-hint-1, eval = FALSE}
library(...)
```

```{r temperance-2-test, include = FALSE}
library(marginaleffects)
```

### 

We should be modest in the claims we make. The posteriors we create are never the “truth.” The assumptions we made to create the model are never perfect. Yet decisions made with flawed posteriors are almost always better than decisions made without them.


### Exercise 3

What is the specific question we are trying to answer? 

```{r temperance-3}
question_text(NULL,
	message = "What is the causal effect of how many years a governor will live after being elected based off of sex?",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Data science projects almost always begin with a broad topic of interest. Yet, in order to make progress, we need to drill down to a specific question. This leads to the creation of a data generating mechanism, which can now be used to answer lots of questions, thus allowing us to explore the original topic more broadly.


### Exercise 4

Enter this code into the exercise code block and hit "Run Code."

```
plot_predictions(fit_all, 
                 condition = "sex")
```               

```{r temperance-4, exercise = TRUE}

```

```{r temperance-4-hint-1, eval = FALSE}
plot_predictions(fit_all, 
                 condition = ...))
```

```{r temperance-4-test, include = FALSE}
plot_predictions(fit_all, 
                 condition = "sex")
```

### 

In the plot above, we examine the predicted life expectancy (lived_after) for males and females (sex), with the corresponding confidence intervals to illustrate uncertainty in these estimates. The solid points represent the model’s predicted life expectancy for each group, while the vertical error bars show the 95% confidence intervals. By comparing these intervals, we can assess the reliability of the estimates. If the confidence intervals between the two groups overlap significantly, it suggests there is no statistically significant difference in life expectancy based on sex. However, if the intervals do not overlap, this would indicate a meaningful difference between the two groups. These estimates, derived from the linear model, provide insight into how sex influences life expectancy post-election.

### Exercise 5

We can compare the differences in ages a female vs male would live after being elected at different ages using `comparisons()`. 

```
comparisons(fit_all, newdata = governor)
```               

```{r temperance-5, exercise = TRUE}

```

```{r temperance-5-hint-1, eval = FALSE}
comparisons(fit_all, newdata = governor)
```

```{r temperance-5-test, include = FALSE}
comparisons(fit_all, newdata = governor)
```

### 

From this we can see that males are expected to live significantly fewer years than females after being elected, with an average difference of 11.7 years. This gap is statistically significant (p < 0.001), meaning the result is unlikely due to chance. The confidence interval suggests that the difference could range from 4.7 to 18.6 fewer years for males compared to females, indicating a consistent and substantial disparity in post-election life expectancy between the sexes.

### Exercise 6

Using `plot_comparisons` we can see the difference between life expectancy, and how it changes as election_age increases for both males and females.

```
plot_comparisons(fit_all,
  variables = "election_age",
condition = "sex")
```               

```{r temperance-6, exercise = TRUE}

```

```{r temperance-6-hint-1, eval = FALSE}
plot_comparisons(fit_all,
  variables = "election_age",
  condition = "sex") +
  scale_x_continuous(breaks = c(0, 1), labels = c("Male (0)", "Female (1)")) +
  labs(x = "Sex", y = "Predicted Life Expectancy")
```

```{r temperance-6-test, include = FALSE}
# plot_comparisons(fit_all,
#   variables = "election_age",
#   condition = "sex") +
#   scale_x_continuous(breaks = c(0, 1), labels = c("Male (0)", "Female (1)")) +
#   labs(x = "Sex", y = "Predicted Life Expectancy")
```

### 

From this we can see that the life expectancy for females has a greater range for the confidence intervals.The plot shows the estimated effect of the variable election_age on an outcome, conditioned by sex. For males, the estimate appears more negative with a narrow confidence interval, indicating a relatively precise estimate. In contrast, for females, the estimate is closer to zero but has a much wider confidence interval, reflecting greater uncertainty in the effect for this group. The overlap in confidence intervals between the two groups suggests that the difference in effect between the two sexes may not be statistically significant.

### Exercise 7

This plot shows the estimated effect of the variable sex on an outcome, conditioned by different values of election_age (40, 50, and 60). 
```
plot_comparisons(fit_all,
  variables = "sex",
condition = list(election_age = c(40, 50, 60)))
```               

```{r temperance-7, exercise = TRUE}

```

```{r temperance-7-hint-1, eval = FALSE}
plot_comparisons(fit_all,
  variables = "sex",
condition = list(election_age = c(40, 50, 60)))
```

```{r temperance-7-test, include = FALSE}
plot_comparisons(fit_all,
  variables = "sex",
condition = list(election_age = c(40, 50, 60)))
```

### 

In other words, the plot is comparing the estimated effect of sex at different ages. It indicates how the impact of sex on the outcome might differ for people of different ages. The "comparison" axis is likely representing the difference between the two groups defined by sex (e.g., male vs. female), with the confidence interval showing the uncertainty around these estimates.

### Exercise 8

Add `library(marginaleffects)` to your QMD setup code chunk. 

Create a new code chunk. Label it with `label: plot`. Copy/paste the code which creates your graphic. 

`Command/Ctrl + Shift + K` to ensure that it all works as intended.

At the Console, run:

```
tutorial.helpers::show_file("XX.qmd", start = -8)
```

CP/CR.

```{r temperance-8}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

### Exercise 9

Write the last sentence of your summary paragraph. It describes at least one quantity of interest (QoI) and provides a measure of uncertainty about that QoI. (It is OK if this QoI is not the one that you began with. The focus of a data science project often changes over time.)


```{r temperance-9}
question_text(NULL,
	message = "The quantity of interest in out problem is the causal effect of sex in terms of how many year the unit will live after being elected. The standard error of our data is 22.10477, indicating that the estimate of -53.3 years could fluctuate by approximately ±22.1 years due to variability in the data.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Add a final sentence to your summary paragraph in your QMD as you see fit, but do not copy/paste our answer exactly. `Command/Ctrl + Shift + K`.

### Exercise 10

Write a few sentences which explain why the estimates for the quantities of interest, and the uncertainty thereof, might be wrong. Suggest an alternative estimate and confidence interval, if you think either might be warranted.

```{r temperance-10}
question_text(NULL,
	message = "The estimates for the effect of sex and the associated uncertainty might be wrong due to potential omitted variables, such as health or socioeconomic factors, which could bias the results. Additionally, measurement error or multicollinearity between sex and election_age may inflate the standard error and widen the confidence interval, making the results less reliable. A more robust approach, such as bootstrapping or a Bayesian method, could yield more accurate estimates with reduced uncertainty, potentially narrowing the confidence interval.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 11

Rearrange the material in your QMD so that the order is graphic, paragraph, math and table. Doing so, of course, requires sensible judgment. For example, the code chunk which creates the fitted model must occur before the chunk which creates the graphic. `Command/Ctrl + Shift + K` to ensure that everything works.

At the Console, run:

```
tutorial.helpers::show_file("XX.qmd")
```

CP/CR.

```{r temperance-11}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

This is the version of your QMD file which your teacher is most likely to take a close look at.

### Exercise 12

Publish your rendered QMD to Rpubs. Choose a sensible slug. Copy/paste the resulting url below.

```{r temperance-12}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

Add `rsconnect` to the `.gitignore` file. You don't want your personal Rpubs details stored in the clear on Github. Commit/push everything.

### Exercise 13

Copy/paste the url to your Github repo.

```{r temperance-13}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

## Summary
### 

This tutorial covered [Chapter 9: Five Parameters](https://ppbds.github.io/primer/five-parameters.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). This tutorial was created by Sanaka Dash and David Kane.



```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
