---
title: Loans
author: Satvika Upperla
tutorial:
  id: loans
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: 'Tutorial: Loans'
---

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(gt)

# DK: Add questions for loading up openintro and ranger.

library(tidyverse)
library(openintro)
library(tidymodels)
library(ranger)
library(gtsummary)
library(equatiomatic)
library(marginaleffects)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 

# XX: Never include setup code that takes more than a few seconds to run. See
# https://ppbds.github.io/tutorial.helpers/articles/instructions.html#data for
# background.

loans <- read_csv("https://raw.githubusercontent.com/vincentarelbundock/Rdatasets/refs/heads/master/csv/openintro/loans_full_schema.csv", show_col_types = FALSE)

fit_loans_model <- rand_forest(mode = "regression", engine = "ranger", mtry = 4, trees = 500, min_n = 4) 

fit_loans <- fit_loans_model |> fit(interest_rate ~ homeownership + annual_income +  debt_to_income + delinq_2y + total_credit_lines + open_credit_lines + total_credit_limit + total_credit_utilized + total_collection_amount_ever + current_installment_accounts + loan_amount + term + grade + sub_grade + initial_listing_status + balance, data = loans)
  


  
```

```{r}
pctiles <- quantile(loans$debt_to_income, probs = seq(0, 1, length.out = 101), na.rm = TRUE)
nd <- datagrid(debt_to_income = pctiles, newdata = loans)
plot_predictions(fit_loans, by = "debt_to_income", newdata = nd)
```

these two both plots are the same, just the one with pctiles converts debt_to_income to percentages to create a range of values, while the other one just uses the existing values.

```{r}
loans <- loans[!is.na(loans$homeownership), ]
nd1 <- datagrid(homeownership = loans$homeownership, newdata = loans)
  
plot_predictions(fit_loans, by = "homeownership", newdata = nd) + geom_point(data = loans, aes(x = homeownership, y = interest_rate), alpha = 0.04) + geom_smooth(data = loans, aes(x = debt_to_income, y = interest_rate), se = FALSE, color = "orange") +
    labs(x = "homeownership", y = "Predicted interest rate",
         title = "Predicted interest rate for different values of homeownership") +
    theme_bw()

```

this one uses condition but is similar to the other two plots
```{r}
loans1 <- loans |> drop_na()
plot_predictions(fit_loans, condition = "homeownership", newdata = loans1)
```

```{r}
loans1 <- loans |> drop_na()
plot_predictions(fit_loans, by = "homeownership", newdata = loans1)
```

```{r}
loans1 <- loans |> drop_na()
plot_predictions(fit_loans, by = "total_credit_limit", newdata = loans1)
```


```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```


<!-- Once you decide the appropriate replacement for `fit_XX` and `XX.qmd`, you can do a global replace to fix them all. -->

<!-- We sometimes connect XX to another word or phrase, as in [XX: unit] or `[XX: the tibble]`. In these cases, the XX indicates that this is something that you need to replace and the other words/symbols are there to guide you as to what the replacement should be. But you delete everything within the brackets. For example, you might replace [XX: unit] with "candidate" (with no quotation marks) or whatever the type of unit we have in this problem. Similarly, `[XX: the tibble]` would be replaced with `trains` or whatever tibble is used in this tutorial. In both cases, we provide the correct punctuation. The word "candidate" would not have any punctuation since it is just a word in a sentence. But a tibble like `trains` needs to be surrounded by backticks, like any other tibble. -->

<!-- Whenever creating an object which will be used in later questions, never have students do the assignment themselves. Instead, have a series of one or more questions which create the object, often by building a pipe line-by-line, with each step creating output which can be examined and discussed. Then, when the creation is done, have a last question which says, more or less, 'Behind the scenes, we have assigned the result of the pipe [or whatever function call was used] to the object `fit_obj`. To confirm, type `fit_obj` and hit "Run Code."' -->

<!-- Note that the questions are a mixture of our three types: code, written (with answer) and written (without answer). The last is only used for questions in which we ask the student to run a command like `show_file()`. Otherwise, we always provide an excellent written answer because students will generally look closely at our answer because they are concerned about whether or not their written answer matches ours. -->

<!-- A plot, especially of the outcome or key covariate, often makes for an excellent knowledge drop. Just have a code chunk with no code chunk label, just ```{r} ```. -->

<!-- Whenever you tell a student to make a change in the QMD, you should tell them to `Command/Ctrl + Shift + K` in order to render the document. (This will also cause it to be saved.) This is good practice for catching bugs early. (Professionals do this.) Then, the last step in these exercises is often some version of show_file() and then CP/CR. -->

<!-- Make use of, e.g., `show_file("tutorial-6.qmd", start = -5)` to get just the last 5 lines of the QMD. We don't want students to copy/paste the whole document. We also don't need to ensure that we get whatever it is that was just changed. We never look! Instead, we are just plausibly threatening to look.  -->

<!-- Make sure to uncomment the test code chunks below, once you have created the necessary objects. -->

<!-- We are still wrestling with what to include in the topic introductions, i.e., the space between the topic header and the first exercise. -->


<!-- Things which DK is considering adding: -->

<!-- The connection between the specific question and the general question is confusing. The specific question will often suggest filtering our universe in ways that are not (?) what we want. -->

<!-- The question just gets you started. It leads to the creation of the model.  -->

<!-- How we are testing now that we don't have pp_check? -->

<!-- Need some discussion in Question about when/how we start to move from the data to the Preceptor Table. That is, our current examples of coming up with a causal question and with a predictive question center around the actual data. That is fine, but our question will be about the Preceptor Table. Need to make that transition clearer. OR SHOULD THE ENTIRE THE QUESTION TOPIC have nothing to do with the actual data . . . -->


<!-- Give better guidance as to the question. I am thinking, more and more, that the specific question is one that can apply to both the data and the Preceptor Table. That is, there are no details about time or location which prevent it from applying in both cases. -->

<!-- Both a causal effect and a prediction are much fuzzier notions than you might think because their are so many, depending on AGGREGATION. That is, you might ask for the average causal effect, or the average causal effect for men and for women, or for the difference in average causal effect between men and women, or . . . The key point is that all these questions are trivial to answer if you have the Preceptor Table *and* they might require very different approaches given that we don't. This is where the power/flexibility of marginaleffects can come in handy. -->


<!-- Think about the connections among all the material in the initial chunk of each section. How does the "Imagine that you are . . . " of the Introduction connect to the material discussion in the Question into, and then Wisdom and so on. There is nothing wrong with the silly quotes. (Or is there? Are we wasting student time?) But we should do more with that space. Maybe the current version of the summary paragraph goes there? -->

<!-- We model units, but only we really care about aggregates. -->


## Introduction
### 

This tutorial supports [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 

The world confronts us. Make decisions we must.

Imagine that you want to take out a loan, and are interested in the factors that banks consider when figuring out the interest rate. You want to maximize your chances of getting the lowest interest rate as possible.


## The Question
### 

*It is not the answer that enlightens, but the question.* - Eugene Ionesco

We don't know what factors banks take into account for the interest_rate of a loan. We can only pick out the variables that seem interesting and explore their relationship with interest rate. For the sake of this tutorial we will only explore the relationship 2-3 variables that seem connected to interest rate.

### Exercise 1

Load [**tidyverse**](https://www.tidyverse.org/) package.

```{r the-question-1, exercise = TRUE}

```

```{r the-question-1-hint-1, eval = FALSE}
library(tidyverse)
```

```{r the-question-1-test, include = FALSE}
library(tidyverse)
```

### 

This dataset was collected from the Lending Club platform, which allows users to lend money to other individuals. This dataset only represents loans actually made, so don't mistake it for loan applications. 

### Exercise 2

Load the [**openintro**] package.

```{r the-question-2, exercise = TRUE}

```

```{r the-question-2-hint-1, eval = FALSE}
library(openintro)
```

```{r the-question-2-test, include = FALSE}
library(openintro)
```

### 

### Exercise 3

After loading **openintro** in your Console, type `?loans_full_schema` in the Console, and paste in the Description below.

```{r the-question-3}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

This data comes from Lending Club (https://www.lendingclub.com/info/statistics.action), which provides a very large, open set of data on the people who received loans through their platform.

### Exercise 4

interest rate is the broad topic of this tutorial. Given that topic, which variable in `loans` should we use as our outcome variable? 

```{r the-question-4}
question_text(NULL,
	message = "The outcome variable is the interest_rate of the loan.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 2)
```

### 

We will use `interest_rate` as our outcome variable.

```{r}
loans |> ggplot(aes(x = interest_rate)) +
  geom_histogram() + 
  scale_x_continuous(breaks = seq(0, 30, by = 2), labels = function(x) paste0(x, "%")) +
  labs(x = "Interest Rate (%)", y = "Count")
```


A data scientist should always look at a plot of the outcome variable.

### Exercise 5

Let's imagine a brand new variable which **does not exists** in the data. This variable should be binary, meaning that it only takes on one of two values. It should also, at least in theory, by manipulable. In other words, if the value of the variable is "X," or whatever, then it generates one potential outcome and if it is "Y," or whatever, it generates another potential outcome.

Describe this imaginary variable and how might we manipulate its value.

<!-- XX: Include these two sentences if this is a causal model: -->

<!-- For now, ignore the actual treatment variable `XX` which we will be using later in the analysis. The point of this exercise is to reinforce our understanding of the [Rubin Causal Model](https://ppbds.github.io/primer/rubin-causal-model.html). -->


```{r the-question-5}
# XX: In your answer, and for the next few questions, always treat this
# imaginary variable as real by putting backticks around the name. For example,
# with nhanes data, we might imagine a variable called `vitamin` for which `1`
# means that the individual ate vitamins growing up and `0` means they did not.
# Using the words "treatment group" and "control group" as part of your answer
# is often helpful since it reinforces the fact that we are using the Rubin
# Causal Model.

question_text(NULL,
	message = "XX: (This is an example answer.) Imagine a variable called `phone_call` which has a value of `1` if the person received a phone call urging them to vote and `0` if they did not receive such a phone call. We, meaning the organization in charge of making such phone calls, can manipulate this variable by deciding, either randomly or otherwise, whether or not we will call a specific individual.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Any data set can be used to construct a causal model as long as there is at least one covariate that we can, at least in theory, manipulate. It does not matter whether or not anyone did, in fact, manipulate it. 

### Exercise 6

Given our (imaginary) treatment variable `XX`, how many potential outcomes are there for each [XX: unit]? Explain why.


```{r the-question-6}
question_text(NULL,
	message = "There are two potential outcomes because the treatment variable `XX` takes on two posible values: list-the-values-here, i.e., exposure to Spanish-speakers on a train paltform versus no such exposure.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The same data set can be used to create, separately, lots and lots of different models, both causal and predictive. We can just use different outcome variables and/or specify different treatment variables. This is a *conceptual* framework we apply to the data. It is never inherent in the data itself.


### Exercise 7

In a few sentences, specify the two different values for the imaginary treatment variable `XX`, for a single unit, guess at the potential outcomes which would result, and then determine the causal effect for that unit given those guesses.

```{r the-question-7}
# XX: Replace [XX: unit] with a better word below given the actual data set we
# are using. Replace all the XX terms as appropriate.

# XX: For a given individual, assume that the value of the treatment variables
# might be 'exposure to Spanish-speakers' or 'no exposure'. If the individual
# gets 'exposure to Spanish-speakers', then her attitude toward immigration
# would be 10. If the individual gets 'no exposure', then her attitude would be
# 8. The causal effect on the outcome of a treatment of exposure to
# Spanish-speakers versus no exposure is 10 - 8 --- i.e., the difference between
# two potential outcomes --- which equals 2, which is the causal effect.

# XX: If the outcome is a character variable, like Strongly Approve, then there
# is no simple metric on which we can pinpoint the causal effect. That is, the
# causal effect is still defined --- as, in this example, the difference between
# Strongly Approve and Neutral --- but can not be expressed as a number, at
# least without further work.

question_text(NULL,
	message = "For a given [XX: unit], assume that the value of the treatment variable might be [XX: treatment] or [XX: control]. If the [XX: unit] gets [XX: treatment], then [XX: the outcome] would be [XX: a number/character]. If the [XX: unit] gets [XX: control], then [XX: the outcome] would be [XX: a different number or character]. The causal effect on the outcome of a treatment of [XX: treatment] versus [XX: control] is [XX: a number] - [XX: a different number] --- i.e., the difference between two potential outcomes --- which equals [XX: the causal effect], which is the causal effect.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The the definition of a causal effect is the difference between two potential outcomes. Of course, you can't just say that the causal effect is 10. The exact value depends on which potential outcome comes first in the subtraction and which second. There is, perhaps, a default sense in which the causal effect is defined as treatment minus control. 

Any causal connection means exploring the *within row* difference between two potential outcomes. We don't need to look at any other rows to have that conversation.

### Exercise 8

<!-- XX: Replace stuff like `[XX: the tibble]` with just the name of the tibble, i.e., `trains`. -->

Let's consider a *predictive* model. Which variable in `loans` do you think might have an important connection to `interest_rate`? 


```{r the-question-8}
question_text(NULL,
	message = "Really any of the covariates would work, but the ones we will be exploring in this tutorial will be homeownership, ...",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 2)
```

### 

With a predictive model, there is only one outcome for each individual unit. There are not two potential outcomes because we are not considering any of the covariates to be a treatment variable. We assuming that the values of all covariates are "fixed." 

### Exercise 9

Specify two different groups of [XX: units] which have specific value for [XX: covariate] and which might have different average values for the [XX: outcome].  

```{r the-question-9}
question_text(NULL,
	message = "XX: Consider two groups, the first with a value for [XX: covariate] of [XX: a value] and the second with value [XX: a different value]. Those two groups might have different average values for the outcome variable.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

In predictive models, do not use words like "cause," "influence," "impact," or anything else which suggests causation. The best phrasing is in terms of "differences" between groups of units with different values for the covariate of interest.

### Exercise 10

Write a [XX: choose causal or predictive] question which connects the outcome variable `XX` to `XXZ`, the covariate of interest. 

```{r the-question-10}
# XX: If it is causal, you should use key causal language in the question, like
# "What is the causal effect of the treatment on the outcome?" Example: "What is
# the causal effect of exposure to Spanish-speakers on attitudes toward
# immigration?" If the model is predictive, the question should clearly compare
# two groups of units. "What is the difference in the outcome variable between
# two groups of units?" Example:  "What is the difference in immigration
# attitudes between Democrats and Republicans?" In both cases, the word
# "average" is implicit in the question.

question_text(NULL,
	message = "XX: Give your question.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

We call the answer to this question is your "Quantity of Interest." 

Our Quantity of Interest might appear too specific, too narrow to capture the full complexity of the topic. There are many, many numbers which we are interested in, many numbers that we want to know. But we don't need to list them all here! We just need to choose one of them since our goal is just to have a specific number which helps to guide us in the creation of the Preceptor Table and, then, the model.


## Wisdom
### 

<!-- XX: Pick one. -->

*The only true wisdom is in knowing you know nothing.* - Socrates
*Patience is the companion of wisdom.* - Saint Augustine
*Wonder is the beginning of wisdom.* - Socrates
*Wisdom begins in wonder.* - Plato
*The doorstep to the temple of wisdom is a knowledge of our own ignorance.* - Benjamin Franklin
*It is the province of knowledge to speak, and it is the privilege of wisdom to listen.* - Oliver Wendell Holmes Sr.
*All we can know is that we know nothing. And that’s the height of human wisdom.* - Leo Tolstoy

Our question:

> *XX: Repeat the question with which you ended The Question topic.*

### Exercise 1

In your own words, describe the key components of Wisdom when working on a data science problem.

```{r wisdom-1}
question_text(NULL,
	message = "Wisdom requires the creation of a Preceptor Table, an examination of our data, and a determination, using the concept of validity, as to whether or not we can (reasonably!) assume that the two come from the same population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The central problem for Wisdom is: Can we use data from [XX: describe your data] to [XX: pick one of predict or understand or control] the variables/relationships in [XX: describe your Preceptor Table]?


### Exercise 2

Define a Preceptor Table.

```{r wisdom-2}
question_text(NULL,
	message = "A Preceptor Table is the smallest possible table of data with rows and columns such that, if there is no missing data, we can easily calculate the quantity of interest.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The Preceptor Table does not include all the covariates which you will eventually include in your model. It only includes covariates which you need to answer your question.

### Exercise 3

Describe the key components of Preceptor Tables in general, without worrying about this specific problem. Use words like "units," "outcomes," and "covariates."

```{r wisdom-3}
question_text(NULL,
	message = "The rows of the Preceptor Table are the units. The outcome is at least one of the columns. If the problem is causal, there will be at least two (potential) outcome columns. The other columns are covariates. If the problem is causal, at least one of the covariates will considered a treatment.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Pick one, and edit, as appropriate: -->

<!-- XX: This problem is causal so one of the covariates is a treatment. In our problem, the treatment is the type of postcard that the resident receives. There is a potential outcome for each possible value of the treatment. -->

<!-- XX: This problem is predictive so [insert something about comparing the outcomes for two different groups] -->

### Exercise 4

Create a Github repo called `XX`. Make sure to click the "Add a README file" check box.

Connect the Github repo to an R project on your computer. Give the R project the same name.

Select `File -> New File -> Quarto Document ...`. Provide a title -- `"[XX: Your Title]"` -- and an author (you). Render the document and save it as `XX.qmd`.

Edit the `.gitignore` by adding `*Rproj`. Save and commit this in the Git tab. Push the commit.

In the Console, run:

```         
show_file(".gitignore")
```

CP/CR.

```{r wisdom-4}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 7)
```

### 

Remove everything below the YAML header from your QMD and render the file. `Command/Ctrl + Shift + K` first saves the file and then renders it.


### Exercise 5

What are the units for this problem?

```{r wisdom-5}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Specifying the Preceptor Table forces us to think clearly about the units and outcomes implied by the question. The resulting discussion sometimes leads us to modify the question with which we started. No data science project follows a single direction. We always backtrack. There is always dialogue.


### Exercise 6

What is the outcome variable for this problem?

```{r wisdom-6}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Regardless, the central lesson is always the same: *You can never look at your data too much.*


### Exercise 7

What are some covariates which you think might be useful for this problem, regardless of whether or not they might be included in the data?

```{r wisdom-7}
question_text(NULL,
	message = "XX. Answer should be some sensible variables which are plausibly connected to the outcome. Some should be in the data but some shouldn't. You might also add that `You need to have variable X` if the question itself mentions that variable.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The term "covariates" is used in at least three ways in data science. First, it is all the variables which might be useful, regardless of whether or not we have the data. Second, it is all the variables for which we have data. Third, it is the set of variables in the data which we end up using in the model.



### Exercise 8

What are the treatments, if any, for this problem?

```{r wisdom-8}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Remember that a treatment is just another covariate which, for the purposes of this specific problem, we are assuming can be manipulated, thereby, creating two or more different potential outcomes for each unit.


### Exercise 9

What moment in time does the Preceptor Table refer to?

```{r wisdom-9}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

```{r}
## XX: Make a nice looking plot which shows the outcome variable on the y-axis
## and the most important/interesting covariate/treatment on the x-axis. This
## doesn't really go here, but we want to show the plot after discussing
## covariates and treatments above. We don't show the code. Plot does not need
## to be fancy, but it should be competent, with a title, a subtitle which
## highlights the main takeaway from the plot, axis labels and so on.
```

### Exercise 10

Define a causal effect. [XX: Include this if the model is predictive: (Note that the model in this tutorial is predictive, not causal. We just want to make sure you understand what a causal model is.)]

```{r wisdom-10}
question_text(NULL,
	message = "A causal effect is the difference between two potential outcomes.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

According to the Rubin Causal Model, there must be two (or more) potential outcomes for any discussion of causation to make sense. This is simplest to discuss when the treatment only has two different values, thereby generating only two potential outcomes. 

### Exercise 11

What is the fundamental problem of causal inference?

```{r wisdom-11}
question_text(NULL,
	message = "The fundamental problem of causal inference is that we can only observe one potential outcome.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

If the treatment variable is continuous (like income), then there are lots and lots of potential outcomes, one for each possible value of the treatment variable. 

### Exercise 12

How does the motto "No causal inference without manipulation." apply in this problem?

```{r wisdom-12}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: With a tutorial which uses a predictive model, it is fair for your answer to this question to be. "The motto does not apply because this is a predictive, not causal, model." -->

<!-- XX: For a causal model, can you really manipulate the treatments? In reality or in theory? How? What details would need to change to make this more or less plausible? -->

### Exercise 13

Describe in words the Preceptor Table for this problem.

```{r wisdom-13}
question_text(NULL,
	message = "XX. Make sure your words given an excellent description of the Preceptor Table which you are about to show the student.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The Preceptor Table for this problem looks something like this:

<!-- XX: Here are two examples which might help you to create your own. In general, your question will only specify the outcome and one covariate, so the Preceptor Table is actually fairly small. -->

<!-- First, for a predictive model: -->

<!-- ```{r} -->
<!-- tibble(ID = c("1", "2", "...", "10", "11", "...", "103,754,865"), -->
<!--        vote = c("Democrat", "Third Party", "...", "Republican", "Democrat", "...", "Republican"), -->
<!--        sex = c("M", "F", "...", "F", "F", "...", "M")) |> -->

<!--   gt() |> -->
<!--   tab_header(title = "Preceptor Table") |>  -->
<!--   cols_label(ID = md("ID"), -->
<!--              vote = md("Vote"), -->
<!--              sex = md("Sex")) |> -->
<!--   tab_style(cell_borders(sides = "right"), -->
<!--             location = cells_body(columns = c(ID))) |> -->
<!--   tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"),  -->
<!--             locations = cells_column_labels(columns = c(ID))) |> -->
<!--   cols_align(align = "center", columns = everything()) |> -->
<!--   cols_align(align = "left", columns = c(ID)) |> -->
<!--   fmt_markdown(columns = everything()) |> -->
<!--   tab_spanner(label = "Outcome", columns = c(vote)) |> -->
<!--   tab_spanner(label = "Covariate", columns = c(sex)) -->
<!-- ``` -->

<!-- Second, for a causal model: -->

<!-- ```{r} -->
<!-- tibble(ID = c("1", "2", "...", "10", "11", "...", "N"), -->
<!--        voting_after_treated = c("1", "1", "...", "1", "0", "...", "1"), -->
<!--        voting_after_control = c("1", "0", "...", "1", "1", "...", "0"), -->
<!--        treatment = c("Yes", "No", "...", "Yes", "Yes", "...", "No"), -->
<!--        engagement = c("1", "3", "...", "6", "2", "...", "2")) |> -->

<!--   gt() |> -->
<!--   tab_header(title = "Preceptor Table") |>  -->
<!--   cols_label(ID = md("ID"), -->
<!--              voting_after_treated = md("Voting After Treatment"), -->
<!--              voting_after_control = md("Voting After Control"), -->
<!--              treatment = md("Treatment"), -->
<!--              engagement = md("Engagement")) |> -->
<!--   tab_style(cell_borders(sides = "right"), -->
<!--             location = cells_body(columns = c(ID))) |> -->
<!--   tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"),  -->
<!--             locations = cells_column_labels(columns = c(ID))) |> -->
<!--   cols_align(align = "center", columns = everything()) |> -->
<!--   cols_align(align = "left", columns = c(ID)) |> -->
<!--   fmt_markdown(columns = everything()) |> -->
<!--   tab_spanner(label = "Covariates", columns = c(treatment, engagement)) |> -->
<!--   tab_spanner(label = "Outcomes", columns = c(voting_after_control, voting_after_treated)) -->
<!-- ``` -->


Like all aspects of a data science problem, the Preceptor Table evolves as we work on the problem. 




### Exercise 14

<!-- XX: Switch primer.data for whichever package you got your data from. -->

In your QMD, load the **tidyverse** and the **primer.data** packages in a new code chunk. Label it as the setup code chunk by adding `#| label: setup`. Render the file.

Notice that the file does not look good because the code is visible and there are annoying messages. To take care of this, add `#| message: false` to remove all the messages in the setup chunk. Also add the following to the YAML header to remove all code echos from the whole file:

```         
execute: 
  echo: false
```

In the Console, run:

```         
show_file("analysis.qmd", start = -5)
```

CP/CR.

```{r wisdom-14}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 6)
```

### 

Render again. Everything looks nice because we have added code to make the file look better and more professional.


<!-- XX: If necessary, provide code exercises which, line-by-line, create the pipeline which creates the cleaned data that will be used in modeling. Name the new object `x`. For many tutorials, this is unnecessary since we can just use the raw tibble that is available in whatever package. But we sometimes need some code like

nes |> 
  filter(year == 1992) |> 
  drop_na()

We have three code exercises, each adding one line to the pipeline, explaining what we are doing and why. It is nice that, for each exercise, something is spat out.
-->

<!-- XX: If such a pipeline was built, there is one QMD question which requires that you add a new code chunk to the QMD, copy/paste the pipeline and assign the result to the new object `x`:

x <- nes |> 
  filter(year == 1992) |> 
  drop_na()

`Command/ctrl + Shift + K` follows, perhaps with a show_file("analysis.qmd", start = -5)
-->



### Exercise 15

In your own words, define "validity" as we use the term.

```{r wisdom-15}
question_text(NULL,
	message = "Validity is the consistency, or lack thereof, in the columns of the data set and the corresponding columns in the Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Validity is always about the *columns* in the Preceptor Table and the data. Just because columns from these two different tables have the same *name* does not mean that they are the same *thing*.



### Exercise 16

<!-- XX: For the validity questions, specifics matter. There is always a reason why the outcome column in the data is not the same as the outcome columns in the Preceptor Table, even in the case of simple sampling. For example, consider a historical question connecting sex with presidential vote. Our data is a subset of our Preceptor Table. We have information on a few thousand voters and want to draw inferences about millions of other voters in the same election. But, even in this case, the outcome columns are different. The data is who people told a survey who they voted for. The Preceptor Table is who people actually did vote for. Those are not the same things. If they, in your view, are different enough than validity is violated. -->

Provide one reason why the assumption of validity might not hold for the outcome variable `XX` or for one of the covariates. Use the words "column" or "columns" in your answer.

```{r wisdom-16}
question_text(NULL,
	message = "XX: Answers to validity question should always use the word 'column(s)'. You should make your answer longer than the one we expect from students, ideally mentioning potential problems with both the outcome and a covariate.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

In order to consider the Preceptor Table and the data to be drawn from the same population, the columns from one must have a *valid correspondence* with the columns in the other. Validity, if true (or at least reasonable), allows us to construct the Population Table, which is the first step in Justice.

Because we control the Preceptor Table and, to a lesser extent, the original question, we can adjust those variables to be “closer” to the data that we actually have. This is another example of the iterative nature of data science. If the data is not close enough to the question, then we check with our boss/colleague/customer to see if we can modify the question in order to make the match between the data and the Preceptor Table close enough for validity to hold.

### Exercise 17

Over the course of this tutorial, we will be creating a summary paragraph. The purpose of this exercise is to write the first two sentences of that paragraph.

The first sentence is a general statement about the overall topic, mentioning both general class of the outcome variable and of at least one of the covariates. It is **not** connected to the initial "Imagine that you are XX" which set the stage for this project. That sentence can be rhetorical. It can be trite, or even a platitude. The purpose of the sentence to let the reader know, gently, about our topic.

The second sentence does two things. First, it introduces the data source. Second, it introduces the specific question. The sentence can't be that long. Important aspects of the data include when/where it was gather, how many observations it includes and the organization (if famous) which collected it.

Type your two sentences below.

<!-- XX: Example:  -->

<!-- XX: Sending postcards and other mailings to registered voters is a traditional part of US political campaigns. Using data from a 2006 experiment in Michigan, we seek to explore the likely causal effects of sending postcards to voters in the current gubernatorial campaign in Texas. -->


```{r wisdom-17}
question_text(NULL,
	message = "XX; Make your own answer excellent!",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Read our answer. It will not be the same as yours. You can, if you want, change your answer to incorporate some of our ideas. Do not copy/paste our answer exactly. Add your two sentences, edited or otherwise, to your QMD, `Command/Ctrl + Shift + K`, and then commit/push.

## Justice
### 

<!-- XX: Choose one. -->

*Justice is truth in action.* - Benjamin Disraeli
*The arc of the moral universe is long, but it bends toward justice.* - Theodore Parker
*Justice delayed is justice denied.* - William E. Gladstone
*It is in justice that the ordering of society is centered.* - Aristotle
*Charity is no substitute for justice withheld.* - Saint Augustine

### Exercise 1

In your own words, name the four key components of Justice for working on a data science problem.

```{r justice-1}
question_text(NULL,
	message = "Justice concerns four topics: the Population Table, stability, representativeness, and unconfoundedness.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Justice is about concerns that you (or your critics) might have, reasons why the model you create might not work as well as you hope. 

### Exercise 2

In your own words, define a Population Table.

```{r justice-2}
question_text(NULL,
	message = "The Population Table includes a row for each unit/time combination in the underlying population from which both the Preceptor Table and the data are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The Population Table is almost always much bigger than the combination of the Preceptor Table and the data because, if we can really assume that both the Preceptor Table and the data are part of the same population, than that population must cover a broad universe of time and units since the Preceptor Table and the data are, themselves, often far apart from each other.

### Exercise 3

In your own words, define the assumption of "stability" when employed in the context of data science.

```{r justice-3}
question_text(NULL,
	message = "Stability means that the relationship between the columns in the Population Table is the same for three categories of rows: the data, the Preceptor Table, and the larger population from which both are drawn.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- XX: Select one of these two knowledge drops. -->

<!-- Stability is all about *time*. Is the relationship among the columns in the Population Table stable over time? In particular, is the relationship --- which is another way of saying "mathematical formula" --- at the time the data was gathered the same as the relationship at the (generally later) time referenced by the Preceptor Table. -->

<!-- *The longer the time period covered by the Preceptor Table (and the data), the more suspect the assumption of stability becomes.*  -->

### Exercise 4

Provide one reason why the assumption of stability might not be true in this case.

```{r justice-4}
question_text(NULL,
	message = "XX. Again, students read these 'official' answers as closely as anything else you will write. Make your example precise and excellent.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

A change in time or the distribution of the data does not, in and of itself, demonstrate a violation of stability. Stability is about the parameters: $\beta_0$, $\beta_1$ and so on. Stability means these parameters are the same in the data as they are in the population as they are in the Preceptor Table.

### Exercise 5

We use our data to make inferences about the overall population. We use information about the population to make inferences about the Preceptor Table: `Data -> Population -> Preceptor Table`. In your own words, define the assumption of "representativeness" when employed in the context of data science.

```{r justice-5}
question_text(NULL,
	message = "Representativeness, or the lack thereof, concerns two relationships among the rows in the Population Table. The first is between the data and the other rows. The second is between the other rows and the Preceptor Table.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Ideally, we would like both the Preceptor Table *and* our data to be random samples from the population. Sadly, this is almost never the case.

### Exercise 6

We do not use the data, directly, to estimate missing values in the Preceptor Table. Instead, we use the data to learn about the overall population. Provide one reason, involving the relationship between the data and the population, for why the assumption of representativeness might not be true in this case. 

```{r justice-6}
# XX: In your answer, try not use of the concept time, even though, in theory,
# it is a perfectly reasonable to do so. Instead, focus on why the data might
# not be representative of the population at that moment in time.

question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The reason that representativeness is important is because, when it is violated, the estimates for the model parameters might be biased. 


### Exercise 7

We use information about the population to make inferences about the Preceptor Table. Provide one reason, involving the relationship between the population and the Preceptor Table, for why the assumption of representativeness might not be true in this case.

```{r justice-7}
# XX: Again, try not use of the concept time. We want to save examples of
# changes caused by time for the discussion about stability. Instead, focus on
# why the Preceptor might not be representative of the population at that moment
# in time. 

question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Stability looks across time periods. Representativeness looks within time periods, for the most part. 

<!-- XX: Use this comment when it is relevant to the problem at hand. Of course, it is sometimes the case that the Preceptor Table includes every row from the Population Table for that moment in time. In that case, the assumption representativeness is met, by definition, if we only consider that moment. So, in that case, the only possible violation of representativeness must involve a claim that this moment in time is not representative of the rest of the Population Table. -->


### Exercise 8

In your own words, define the assumption of "unconfoundedness" when employed in the context of data science.

```{r justice-8}
question_text(NULL,
	message = "Unconfoundedness means that the treatment assignment is independent of the potential outcomes, when we condition on pre-treatment covariates.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

This assumption is only relevant for causal models. We describe a model as "confounded" if this is not true. The easiest way to ensure unconfoundedness is to assign treatment randomly.

### Exercise 9

<!-- XX: Delete this question for non-causal models. -->

Provide one reason why the assumption of unconfoundedness might not be true (or relevant) in this case.

```{r justice-9}
question_text(NULL,
	message = "XX. There is nothing harder for students than coming up with examples of possible confounds. So, your example should be a good one, should specify precisely how treatment assignment is correlated with the potential outcomes.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

The great advantage of randomized assignment of treatment is that it guarantees unconfoundedness. There is no way for treatment assignment to be correlated with anything, including potential outcomes, if treatment assignment is random.

### Exercise 10

Write one sentence which highlights a potential weakness in your model. This will almost always be derived from possible problems with the assumptions discussed above. We will add this sentence to our summary paragraph. So far, our version of the summary paragraph looks like this:

> XX: Paste our first two sentences here.

Of course, your version will be somewhat different.


```{r justice-10}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Add a weakness sentence to the summary paragraph in your QMD. You can modify your paragraph as you see fit, but do not copy/paste our answer exactly. `Command/Ctrl + Shift + K`, and then commit/push.


## Courage
### 

<!-- XX: Choose one. -->

*Courage is found in unlikely places.* - J.R.R. Tolkien
*Courage is being scared to death, but saddling up anyway.* - John Wayne
*Courage is going from failure to failure without losing enthusiasm.* - Winston Churchill
*Courage is the commitment to begin without any guarantee of success.* - Johann Wolfgang von Goethe


### Exercise 1

In your own words, describe the components of the virtue of Courage for analyzing data.

```{r courage-1}
question_text(NULL,
	message = "Courage starts with math, explores models, and then creates the data generating mechanism.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

A statistical model consists of two parts: the *probability family* and the *link function*. The probability family is the probability distribution which generates the randomness in our data. The link function is the mathematical formula which links our data to the unknown parameters in the probability distribution. 

### Exercise 2

Load the [**tidymodels**](https://www.tidymodels.org/) package.

```{r courage-2, exercise = TRUE}

```

```{r courage-2-hint-1, eval = FALSE}
library(...)
```

```{r courage-2-test, include = FALSE}
library(tidymodels)
```

### 

The probability family is determined by the outcome variable $Y$. 

<!-- XX: Choose one: -->

If $Y$ is a continuous variable, the probability family is Normal, also known as Gaussian.

$$Y \sim N(\mu, \sigma^2)$$
If $Y$ is a binary variable (with exactly two possible values), the probability family is Bernoulli.

$$Y \sim \text{Bernoulli}(\rho)$$
where $\rho$ is the probability that one of the two possible values --- conventionally referred to as `1` or `TRUE` --- occurs. By definition, $1 - \rho$ is the probability of the other value.

If $Y$ is a categorical value (with 2+ possible values), the probability family is Multinomial.

$$Y \sim \text{Mutinomial}(\rho_1, \rho_2, \rho_3, \ldots)$$

where $\rho_1 + \rho_2 + \rho_3 + \ldots = 1$.




### Exercise 3

Load the [**gtsummary**](https://www.danieldsjoberg.com/gtsummary/) package.

```{r courage-3, exercise = TRUE}

```

```{r courage-3-hint-1, eval = FALSE}
library(...)
```

```{r courage-3-test, include = FALSE}
library(gtsummary)
```

### 

<!-- XX: Choose the appropriate structure. Delete the others. Still need to add the math for multinomial and cumulative. These are all based on how extract_eq() represents things. -->

The link function, the basic mathematical structure of the model, is (mostly) determined by the type of outcome variable. 

For a continuous outcome variable, we use a linear model for the link function:

$$\mu = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \ldots$$

For a binary outcome variable, we use a log-odds model:

$$
\log\left[ \frac { \rho }{ 1 - \rho } \right] = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \ldots 
$$
The link functions for categorical and cumulative variables are also built out of log-odds link functions.


### Exercise 4

Load the [**equatiomatic**](https://datalorax.github.io/equatiomatic/) package.

```{r courage-4, exercise = TRUE}

```

```{r courage-4-hint-1, eval = FALSE}
library(...)
```

```{r courage-4-test, include = FALSE}
library(equatiomatic)
```

### 

This is the basic mathematical structure of our model:

```{r}
# extract_eq(fit_XX, 
#            intercept = "beta", 
#            wrap = TRUE, 
#            show_distribution = TRUE)
```

Of course, in a normal data science project, we would explore a variety of different combinations of independent variables before selecting a final set. Just pretend that we already did that.


### Exercise 5

Load the [**marginaleffects**](https://marginaleffects.com/) package.

```{r courage-5, exercise = TRUE}

```

```{r courage-5-hint-1, eval = FALSE}
library(...)
```

```{r courage-5-test, include = FALSE}
library(marginaleffects)
```

### 

We should be modest in the claims we make. The posteriors we create are never the “truth.” The assumptions we made to create the model are never perfect. Yet decisions made with flawed posteriors are almost always better than decisions made without them.



### Exercise 6

Add `library(tidymodels)`, `library(gtsummary)`, `library(equatiomatic)`, and `library(marginaleffects)` to the `setup` code chunk in your QMD. `Command/Ctrl + Shift + K`.

At the Console, run:

```
tutorial.helpers::show_file("XX.qmd", pattern = "tidymodels|gtsummary|equatiomatic|marginaleffects")
```

CP/CR.

```{r courage-6}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

<!-- XX: Edit this paragrpah to use an example of a categorical variable from your model, if one is available. -->

Recall that a categorical variable (whether character or factor) like `sex` is turned into a $0/1$ "dummy" variable which is then re-named something like $sex_{Male}$. After all, we can't have words --- like "Male" or "Female" --- in a mathematical formula, hence the need for dummy variables.




<!-- GK: Should add knowledge drop about how we can interpret the value of the intercept (e.g. when the value of race is neither "hispanic" and "white", the value of height is...) -->

<!-- DK: Discuss what one might put here. Like the example from 5 parameter chapter, with three versions of the model, with increasing complexity. -->

### Exercise 7

Because our outcome variable is [XX: binary or continuous or multinomial or cumulative], start to create the model by using `[XX: logistic_reg(engine = "glm") or linear_reg(engine = "lm") or multinom_reg(engine = "glmnet")]`.

```{r courage-7, exercise = TRUE}

```

```{r courage-7-hint-1, eval = FALSE}
XX
```

```{r courage-7-test, include = FALSE}
# XX
```

### 

<!-- XX: If your model has one categorical variable with more than two values, then use the below paragraph, but edit it to use your variable, and its values, instead. If not, then just keep this paragraph but add a sentence which notes that there is no variable like this in your model. -->

The same approach applies to a categorical covariate with $N$ values. Such cases produce $N-1$ dummy $0/1$ variables. The presence of an intercept in most models means that we can't have $N$ categories. The "missing" category is incorporated into the intercept. If `race` has three values --- "black", "hispanic", and "white" --- then the model creates two 0/1 dummy variables, giving them names like $race_{hispanic}$ and $race_{white}$. The results for the *first* category are included in the intercept, which becomes the reference case, relative to which the other coefficients are applied.



### Exercise 8

Continue the pipe to `fit(XX, data = XX)`.

```{r courage-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r courage-8-hint-1, eval = FALSE}
... |> 
  fit(..., data = ...)
```

```{r courage-8-test, include = FALSE}
# XX |> 
#   fit(XX, data = XX)
```

### 

We can translate the fitted model into mathematics, including the best estimates of all the unknown parameters:

```{r}
# XX: You might want to use the `coef_digits` argument to show fewer digits
# after the decimal. wrap = TRUE is necessary for large models.

# extract_eq(fit_XX, 
#            intercept = "beta", 
#            use_coefs = TRUE)
```

There are three main differences between this representation of the model and our previous one. First, we replace the parameters with our best estimate of their values. Second, the error term is gone. Third, the dependent variable now has a "hat," indicating that it is our "fitted" value, our best guess as to the value of the outcome, given the values of the independent variables for any given unit.

### Exercise 9

Behind the scenes of this tutorial, an object called `fit_XX` has been created which is the result of the code above. Type `fit_XX` and hit "Run Code." This generates the same results as using `print(fit_XX)`.


```{r courage-9, exercise = TRUE}

```

```{r courage-9-hint-1, eval = FALSE}
fit_XX
```

```{r courage-9-test, include = FALSE}
# fit_XX
```

### 

In data science, we deal with words, math, and code, but the most important of these is code. We created the mathematical structure of the model and then wrote a model formula in order to estimate the unknown parameters. 

### Exercise 10

Create a new code chunk in your QMD. Add two code chunk options: `label: model` and `cache: true`. Copy/paste the code from above for estimating the model into the code chunk, assigning the result to `fit_XX`. 

`Command/Ctrl + Shift + K`. It may take some time to render your QMD, depending on how complex your model is. But, by including `cache: true` you cause Quarto to cache the results of the chunk. The next time you render your QMD, as long as you have not changed the code, Quarto will just load up the saved fitted object.

To confirm, `Command/Ctrl + Shift + K` again. It should be quick.

At the Console, run:

```
tutorial.helpers::show_file("XX.qmd", start = -8)
```

CP/CR.

```{r courage-10}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 8)
```

### 

Add `*_cache` to `.gitignore` file. Commit and push. Cached objects are often large. They don't belong on Github.

### Exercise 11

Create another code chunk in your QMD. Add the chunk option: `label: math`. In that code chunk, add something like the below. You may find it useful to add the `coef_digits` argument to show fewer significant digits after the decimal.

<!-- XX: Obviously, change the below to include any other arguments, like about digits and wrapping, which are needed to look good in a QMD. -->

```
extract_eq(fit_XX, 
           intercept = "beta", 
           use_coefs = TRUE)
```

`Command/Ctrl + Shift + K`. 

At the Console, run:

```
tutorial.helpers::show_file("XX.qmd", pattern = "extract")
```

CP/CR.

```{r courage-11}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

When you render your document, this formula will appear.

```{r}
# extract_eq(fit_XX, 
#            intercept = "beta", 
#            use_coefs = TRUE)
```

This is our data generating mechanism.

<!-- XX: Explain in words what the mathematical function means. That is, say in English what the formula means. DK: Need some examples. -->


### Exercise 12

Run `tidy()` on `fit_XX` with the argument `conf.int` set equal to `TRUE`. The returns 95% intervals for all the parameters in our model.

```{r courage-12, exercise = TRUE}

```

```{r courage-12-hint-1, eval = FALSE}
tidy(..., conf.int = ...)
```

```{r courage-12-test, include = FALSE}
# tidy(fit_XX, conf.int = TRUE)
```

### 

`tidy()` is part of the [**broom**](https://broom.tidymodels.org/) package, used to summarize information from a wide variety of models.

<!-- XX: Add at least three questions which involve the interpretation of numbers in the table. See the Cardinal Virtues vignette for detailed discussion. You should usually include a call to tidy() at the top of each question, hereby making it easier for students to see what you are talking about. You don't have to do this, if you don't want to. But be aware that scrolling up and can be annoying for students. -->

### Exercise 13

For interactive use, `tidy()` is very handy. But, for presenting our results, we should use a presentation package like **gtsummary**, which includes handy functions like `tbl_regression()`.

Run `tbl_regression(fit_XX)`.


```{r courage-13, exercise = TRUE}

```

```{r courage-13-hint-1, eval = FALSE}
tbl_regression(..)
```

```{r courage-13-test, include = FALSE}
# tbl_regression(fit_XX)
```

### 

See this [tutorial](https://www.danieldsjoberg.com/gtsummary/articles/tbl_regression.html) for a variety of options for customizing your table.

### Exercise 14

Create a new code chunk in your QMD. Add a code chunk option: `label: table`. Add this code to the code chunk.

```
tbl_regression(fit_XX)
```

`Command/Ctrl + Shift + K`. 

At the Console, run:

```
tutorial.helpers::show_file("XX.qmd", pattern = "tbl_regression")
```

CP/CR.


```{r courage-14}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

<!-- XX: Give some advice about making the table look more professional. Maybe show some code and the resulting nice looking table. At the very least, include a title and a caption with the data source. -->


### Exercise 15

Add a sentence to your project summary. 

Explain the structure of the model. Something like: "I/we model Y [the concept of the outcome, not the variable name] as a [linear/logistic/multinomial/ordinal] function of X [and maybe other covariates]."

Recall the beginning of our version of the summary:

> XX: Include what we suggested at the end of Justice

```{r courage-15}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Read our answer. It will not be the same as yours. You can, if you want, change your answer to incorporate some of our ideas. Do not copy/paste our answer exactly. Add your two sentences, edited or otherwise, to summary paragrah portion of your QMD. `Command/Ctrl + Shift + K`, and then commit/push.

## Temperance
### 

<!-- XX: Choose one. -->

*Temperance is a tree which as for its root very little contentment, and for its fruit calm and peace.* - Buddha
*Temperance is the greatest of all virtues. It subdues every passion and emotion, and almost creates a Heaven upon Earth.* - Joseph Smith Jr.
*Temperance is a bridle of gold; he, who uses it rightly, is more like a god than a man.* - Robert Burton
*Temperance is the firm and moderate dominion of reason over passion and other unrighteous impulses of the mind.* - Marcus Tullius Cicero
*Temperance to be a virtue must be free, and not forced.* - Philip Massinger
*Temperance is simply a disposition of the mind which binds the passion.* - Thomas Aquinas


### Exercise 1

In your own words, describe the use of Temperance in data science.

```{r temperance-1}
question_text(NULL,
	message = "Temperance uses the data generating mechanism to answer the question with which we began. Humility reminds us that this answer is always a lie. We can also use the DGM to calculate many similar quantities of interest, displaying the results graphically.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Courage gave us the data generating mechanism. Temperance guides us in the use of the DGM — or the “model” — we have created to answer the question with which we began. We create posteriors for the quantities of interest. 



### Exercise 2

What is the specific question we are trying to answer? 

```{r temperance-2}
question_text(NULL,
	message = "XX: This might be the same question as we started with in Wisdom. But it is also OK if it is different. I think . . .",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Data science projects almost always begin with a broad topic of interest. Yet, in order to make progress, we need to drill down to a specific question. This leads to the creation of a data generating mechanism, which can now be used to answer lots of questions, thus allowing us to explore the original topic more broadly.

<!-- XX: Note that, in some circumstances, functions from the marginaleffects package will not work in exercise code chunks. That is annoying and has something to do with weird interactions involving the shiny prerendered settings on tutorials. So, we always have student perform the calls to functions like plot_predictions() in the Console, and then have them CP/CR. (Note that  there is rarely an response, so they are really just copying/pasting them command itself.) Note that we can't run these function in the tutorial itself for the same reason. Make sure that your knowledge drops explain clearly what the graphic which the students have generated means. -->

<!-- XX: There should be a bunch of questions here, covering examples of plot_predictions(), plot_comparisons(), averages and maybe even slopes. We want to run multiple versions of plot_predictions(), dropping knowledge each time which connects what we see to our coefficients, especially those which we asked interpretation questions about. See the Cardinal Virtues vignette for some examples. The last such question creates the plot which is then included in the QMD. 

Below, we just show one plot_predictions() question, but your tutorial should really have several. -->

### Exercise 3

At the Console, run this code:

```
plot_predictions(fit_XX, 
                 conditions = c("XX", "XX")))
```             

CP/CR, although note that there will be no response.

```{r temperance-3}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

<!-- XX: The knowledge drop MUST discuss the estimate (and its uncertainty) that you go on to include in your summary paragraph. You MUST discuss how you are reading, roughly, the values for the estimate and the confidence interval by looking at this plot. -->

<!-- XX: There are a lot of interesting options in plot_predictions. Check them out. You may want to use some of them in your plot. I think `points` is quite interesting. Feel free to add a couple more questions which add some options.  -->

<!-- XX: You can use the draw = FALSE option to return a tibble which can then be piped directly into ggplot.  -->

<!-- XX: If such a plot would be complex and/or the tutorial is long enough, you can just include all the code for a plot in the exercise code chunk and tell students to just press "Run Code." This will, at least, allow them to see what a good plot looks like. -->

### Exercise 4

Create a new code chunk in your QMD. Label it with `label: plot`. Copy/paste the code which creates your graphic. 

`Command/Ctrl + Shift + K` to ensure that it all works as intended.

At the Console, run:

```
tutorial.helpers::show_file("XX.qmd", start = -8)
```

CP/CR.

```{r temperance-4}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

### Exercise 5

Write the last sentence of your summary paragraph. It describes at least one quantity of interest (QoI) and provides a measure of uncertainty about that QoI. (It is OK if this QoI is not the one that you began with. The focus of a data science project often changes over time.)


```{r temperance-5}
question_text(NULL,
	message = "XX",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Add a final sentence to your summary paragraph in your QMD as you see fit, but do not copy/paste our answer exactly. `Command/Ctrl + Shift + K`.

### Exercise 6

Write a few sentences which explain why the estimates for the quantities of interest, and the uncertainty thereof, might be wrong. Suggest an alternative estimate and confidence interval, if you think either might be warranted.

```{r temperance-6}
question_text(NULL,
	message = "XX: This is another example in which the quality of your answer is important. You might or might not suggest an alternate estimate. I always adjust the estimate toward my own subjective sense of a long-run average and/or typical value and/or zero. But that is not necessary. However, you should always increase the confidence interval since the assumptions of your model are always false.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

### Exercise 7

Rearrange the material in your QMD so that the order is graphic, paragraph, math and table. Doing so, of course, requires sensible judgment. For example, the code chunk which creates the fitted model must occur before the chunk which creates the graphic. `Command/Ctrl + Shift + K` to ensure that everything works.

At the Console, run:

```
tutorial.helpers::show_file("XX.qmd")
```

CP/CR.

```{r temperance-7}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

This is the version of your QMD file which your teacher is most likely to take a close look at.

### Exercise 8

Publish your rendered QMD to Rpubs. Choose a sensible slug. Copy/paste the resulting url below.

```{r temperance-8}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

Add `rsconnect` to the `.gitignore` file. You don't want your personal Rpubs details stored in the clear on Github. Commit/push everything.

### Exercise 9

Copy/paste the url to your Github repo.

```{r temperance-9}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

## Summary
### 

This tutorial supports [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/) by [David Kane](https://davidkane.info/). 

<!-- XX: Give the final plot and our summary paragraph. And a note indicating how this information might be helpful to the Imagine person we created at the start. -->


```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
