---
title: 'Three Parameters: Kenya'
author: Mahima Malhotra
tutorial:
  id: three-parameters-kenya
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: Use data from Kenya voter registration efforts to construct a three parameter
  model.
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(rstanarm)
library(gt)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

kenya_2 <- kenya |> 
  filter(distance < 25)

fit_1 <- stan_glm(distance ~ poverty,
                  data = kenya,
                  refresh = 0)

newobs <- tibble(poverty = 0.2)

pe <- posterior_epred(fit_1, newdata = newobs) |> 
  as_tibble()

exp_poverty <- pe |>
  ggplot(aes(x = `1`)) + 
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = 100) +
  labs(title = "Posterior for Expected Distance",
       subtitle = "Polling locations that are on average 12 km from those assigned to them have\npoverty rates of 0.2",
       x = "Poverty Rate",
       y = "Probability") +
  scale_y_continuous(labels = scales::percent_format()) +
  theme_classic()

fit_2 <- stan_glm(distance ~ poverty,
                  data = kenya_2,
                  refresh = 0)

fit_2

newobs2 <- tibble(poverty = 0.2)

pe2 <- posterior_epred(fit_2, newdata = newobs2) |> 
  as_tibble()

exp_poverty_2 <- pe2 |>
  ggplot(aes(x = `1`)) + 
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = 100) +
  labs(title = "Posterior for Expected Distance",
       subtitle = "Polling locations about 10.5 km away on average from those assigned to them\nhave poverty rates of 0.2",
       x = "Poverty Rate",
       y = "Probability") +
  scale_y_continuous(labels = scales::percent_format()) +
  theme_classic()



pe_combo <- bind_rows(list(rep = pe, unrep = pe2), .id = "type")

combo_plot <- pe_combo |> 
  ggplot(aes(x = `1`, fill = type)) + 
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 100,
                   position = "identity",
                   alpha = 0.5) + 
    labs(title = "Posterior for Expected Distance",
         subtitle = "The expected distance for polling locations with a poverty rate of 0.2 is about\n1.5 km higher in our representative data than in our unrepresentative data.",
         x = "Poverty Rate",
         y = "Probability",
         fill = "Type of Data") +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()

```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

<!-- bind_rows(list(rep = pe, unrep = pe2), .id = "type") |> slice_sample(n = 10) Done. -->

<!-- Four different ways to mess up representative data. First, remove rows on the basis of a variable which is not in your model. Second, remove rows on the basis of an independent variable in the model. Third, remove rows on the basis of the dependent variable. Four, remove rows on the basis of potential outcomes.  -->

## Representative Data

Let's look at how whether or not data is representative can affect our results. To do so, let's consider the following questions.

*The variable "distance" is the number of kilometers, which the person who is assigned to a given polling location, lives from that polling location. In Kenya today, what is the expected value of distance for polling locations with a poverty rate of 0.2?*

We will use the data set `kenya` to answer this question, and will make the following posterior distribution.

```{r}
exp_poverty
```

### 

### Exercise 1

First, run `?kenya` to take a closer look at the data.

```{r representative-data-1, exercise = TRUE}

```

```{r representative-data-1-hint-1, eval = FALSE}
?kenya
```

### 

Pay special attention to the variables we are looking at: distance and poverty. Notice that the definition of distance matches our definition from the questions we seek to answer.

### Exercise 2

Now, call `skim(kenya)`.

```{r representative-data-2, exercise = TRUE}

```

```{r representative-data-2-hint-1, eval = FALSE}
skim(kenya)
```

### 

Notice that there are 1.672 rows in this data set, so we have data for 1,672 polling locations in Kenya.

### Exercise 3

Determine the columns we would like in our Preceptor Table in order to answer our question which is as follows.

*The variable "distance" is the number of kilometers, which the person who is assigned to a given polling location, lives from that polling location. In Kenya today, what is the expected value of distance for polling locations with a poverty rate of 0.2?*

```{r representative-data-3}
question_text(NULL,
	message = "We would like the columns for poverty rates of polling locations and the average distance from polling locations.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Therefore, our Preceptor Table would appear as the following:

```{r}
tibble(ID = c("Polling Location 1", "Polling Location 2", "...", "Polling Location 1000", "Polling Location 1001", "...", "Polling Location 3828"),
       distance = c("23", "5", "...", "47", "32", "...", "19"),
       poverty = c("0.4", "0.85", "...", "0.21", "0.63", "...", "0.32")
       ) |>
  
  # Then, we use the gt function to make it pretty
  
  gt() |>
  cols_label(ID = md("ID"),
             distance = md("Distance"),
             poverty = md("Poverty Rate")) |>
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(ID))) |>
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"), 
            locations = cells_column_labels(columns = c(ID))) |>
  cols_align(align = "center", columns = everything()) |>
  cols_align(align = "left", columns = c(ID)) |>
  fmt_markdown(columns = everything())
```

### Exercise 4

While the population we are considering is from Kenya today, the data from Kenya was collected between November of 2014 and December of 2016. Write two sentences discussing whether you can consider the data from `kenya` and the columns from our Preceptor Table to be drawn from the same population. Give an example of a reason why you may not want to consider this true.

```{r representative-data-4}
question_text(NULL,
	message = "Since this data set dealt with a fairly large number of voting communities in Kenya at the time and our population is that of Kenya now. So, the difference between the data and our Preceptor Table is mostly time, which we will assume had little affect on poverty rates and voting blocks. So, we will assume that they can be drawn from the same population.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Having determined that we can consider the data from `kenya` and our Preceptor Table to be drawn from the same population, our Population Table is shown below. Note that we will consider this larger population to span from 2000 to 2030.

```{r}
tibble(source = c("Other", "Other", "...", "Preceptor Table", "Preceptor Table", "...", "Data", "Data", "...", "Other", "Other", "..."),
       year = c("", "", "", "2021", "2021", "...", "2015", "2016", "...", "?", "?", "..."),
       distance = c("", "", "", "32", "51", "...", "5", "41", "...", "?", "?", "..."),
       poverty = c("", "", "", "0.24", "0.55", "...", "0.81", "0.39", "...", "?", "?", "...")
       ) |>
  
  # Then, we use the gt function to make it pretty
  
  gt() |>
  cols_label(source = md("Source"),
             year = md("Year"),
             distance = md("Distance"),
             poverty = md("Poverty Rate")) |>
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(source))) |>
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"), 
            locations = cells_column_labels(columns = c(source))) |>
  cols_align(align = "center", columns = everything()) |>
  cols_align(align = "left", columns = c(source)) |>
  fmt_markdown(columns = everything())
```

### Exercise 5

Given our Population Table, let's consider the aspects of Justice. First, let's look at validity. Write two sentences giving a possible reason for why you don't think we can consider columns `distance` and `poverty` to have the same meaning in our data and our Preceptor Table?

```{r representative-data-5}
question_text(NULL,
	message = "One point you may consider is if there was large redistricting that changed the size of districts meaning that the average distance a voter would have to travel to reach their polling location per voting block would have vastly changed",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

If we truly believed that any of this occurred, then this would bring us to a halt. However, we will consider our data to be valid and continue.

### Exercise 6

Now, consider stability. Write two sentences considering whether we can consider the relationship between `distance` and `poverty` to be the same between the years the study covered (2014-2016) and 2021. Discuss a possible reason that the relationship may have changed.

```{r representative-data-6}
question_text(NULL,
	message = "One reason that could have caused the model to change would be a large redistricting effort that added more districts and therefore decreased the distance that people have to travel to reach their respective voting location. Another reason you could consider is the possibility that the poverty rate has dramatically increased or decreased between 2016 and now, meaning that the old model wouldn't accurately represent the poverty rate. Since we have no reason to believe anything of the sorts is true, we will consider our model to be stable.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 7

Next, write two sentences considering a reason we may not determine the data from 2014-2016 to be representative of the entirety of Kenya in that time period. 

```{r representative-data-7}
question_text(NULL,
	message = "You may consider reasons such as if several rural areas were left out of the study, or if mostly areas with low poverty rates were studied. Since, to our knowledge, areas of Kenya were not left out of the study and a large number of Kenya's voting block communities were studies, we can consider this data to be representative.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

<!-- MM: possibly edit/add representative questions on only 7 counties, then explain -->

If we were to take a deeper dive into our study, we would actually see that the data is from 7 counties that were deemed to be fairly similar, which could bring issues into our representativeness because that might reduce certain populations of Kenya from being studied. However, we will consider this data to be representative as the polling locations that were selected from those counties were chosen randomly and, as stated in the study, "[followed] a strategy that minimized the chances of spillovers, and blocked on poverty, distance and population density." 

### Exercise 8

Finally, as our last step of Justice, determine whether the data-generating mechanism is linear or logistic and why. Also state the corresponding family argument of `stan_glm()` needed to make that type of model. Use the phrase "outcome variable".

```{r representative-data-8}
question_text(NULL,
	message = "The DGM will be linear because we can consider our outcome variable `distance` to be continuous and therefore we will set the family argument to 'gaussian'",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 9

Having completed Justice, we will now move onto Courage. Let's make our posterior distribution using 'stan_glm()'. Set your outcome variable as `distance`and your explanatory variable as `poverty` (Remember you must insert a tilde `~` between the two). Also, include a `-1` after `poverty` so we do not get an intercept.  Set `data` to `kenya`.

```{r representative-data-9, exercise = TRUE}

```

```{r representative-data-9-hint-1, eval = FALSE}
stan_glm(distance ~ poverty -1,
         data = ...)
```

### Exercise 10

As you can see, the result we get for stan_glm() is fairly messy with a lot of information we don't need. To get rid of that, set the argument `refresh` to 0.

```{r representative-data-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r representative-data-10-hint-1, eval = FALSE}
stan_glm(distance ~ poverty - 1,
         data = ...,
         refresh = ...)
```

### Exercise 11

Lastly, since the model is linear, we will specify the `family` argument to be "gaussian". 
Store this as `fit_1` and then return `fit_1` to take a look at the results.

```{r representative-data-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r representative-data-11-hint-1, eval = FALSE}
stan_glm(distance ~ poverty - 1,
         data = ...,
         refresh = ...,
         family = ...)
```

### 

As you may notice, the output of our model is not significantly different when we specify that the `family` is "gaussian". This is because the default family argument for `stan_glm()` is "gaussian". However, if you notice minor differences, this is because we haven't specified a seed to make draws from both exercises the same.

### Exercise 12

With our fitted model, we can answer our question. Recall:

*In Kenya today, what is the expected value of distance for polling locations with a poverty rate of 0.2?*

To do so, first make a new tibble with the observations we would like. In this case, we are looking at locations where the poverty rate is 0.2. Set this new tibble to `newobs`.

```{r representative-data-12, exercise = TRUE}

```

```{r representative-data-12-hint-1, eval = FALSE}
newobs <- tibble(poverty = ...)
```

### Exercise 13

Recall that `posterior_epred()` is used when looking for expected values such as in this case. Therefore, use `posterior_epred()` with the first argument as our fitted model `fit_1` and the `newdata` argument as `newobs`. Continue this pipe with `as_tibble()`. Store this as `pe`.

```{r representative-data-13, exercise = TRUE}

```

```{r representative-data-13-hint-1, eval = FALSE}
pe <- posterior_epred(..., newdata = ...) |> 
  as_tibble()
```

### Exercise 14

With our posterior distribution, we can now seek to answer our question. To do so, make a new pipe and map `distance` to the x-axis. Then add the layer `geom_histogram()` and map the probability to the y-axis. Set the bins argument to 100.

```{r representative-data-14, exercise = TRUE}

```

```{r representative-data-14-hint-1, eval = FALSE}
Remember that the columns aren't named when `posterior_epred()` is used, but rather numbered. To call the first column, you should use the format `1`.
```

```{r representative-data-14-hint-2, eval = FALSE}
To map the probability to the y-axis, set the first argument of `geom_histogram()` to `aes(y = after_stat(count/sum(count)))`.
```

```{r representative-data-14-hint-3, eval = FALSE}
pe |> 
  ggplot(mapping = aes(x = ...)) + 
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = ...)
```

### Exercise 15

Now add a title, subtitle, and axis labels to your graph.

```{r representative-data-15, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r representative-data-15-hint-1, eval = FALSE}
+
  labs(...)
```

### Exercise 16

Lastly, use `scale_y_continuous()` to format the y-axis to be formatted as a percentage. To do so, Set the first argument of `scale_y_continuous` to `scales::percent_format()`. To finish the plot, add `theme_classic()`.

```{r representative-data-16, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r representative-data-16-hint-1, eval = FALSE}
+ 
  scale_y_continuous(...) +
  theme_classic()
```

### 

Recall that your plot should appear similar to the following plot:

```{r}
exp_poverty
```

### 

Through this, we have determined that we expect polling locations which are about 12 km away on average from those who are assigned to that location to have a poverty rate of 0.2, and achieved this answer with data that we considered to be pretty representative.

## Non-Representative Data

In our last model, we could consider our data to be representative of our population, however, what if that were not the case? Now, let's answer the same question, but with unrepresentative data. To do so, we will make the following graph:

```{r}
exp_poverty_2
```

Recall our question.

*Recall: the variable "distance" is the number of kilometers, which the person who is assigned to a given polling location, lives from that polling location. In Kenya today, what is the expected value of distance for polling locations with a poverty rate of 0.2?*

### 

### Exercise 1

Consider that more rural communities far away from the locations where those conducting the study were staying also tended to have polling locations which spanned larger areas and people had to travel more on average to reach. Given this piece of information, let's also say that our researchers were kind of lazy and wanted to get back home more quickly. So, they decided that places further away from where they were staying were too far to study and would take too much time to reach. This caused them to not travel to any polling locations that were more than 25 km away from those who were assigned to it.

With this scenario, write two sentences discussing representativeness and whether we can consider data from this scenario (2014-2016) to be representative of Kenya during that timespan. Explain a possible reason why not.

```{r nonrepresentative-da-1}
question_text(NULL,
	message = "Given that rural communities are not being reached in this scenario and therefore also communities that are located further away from their polling location, we can't consider this data to be representative of the entirety of Kenya.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Although we might not be able to consider this data very representative of Kenya, if this were the data we had, we would probably want to think about stopping here. However, we will continue and acknowledge that the data is not very representative.

### Exercise 2

Let's mimic this scenario with our data `kenya` and answer our question with non-representative data. To do so, use `kenya` and filter out communities that are on average more than 25 km away from their polling location. Store this as `kenya_2`.

```{r nonrepresentative-da-2, exercise = TRUE}

```

```{r nonrepresentative-da-2-hint-1, eval = FALSE}
kenya_2 |> 
  filter(distance < 25)
```

### 

With this, we have essentially created a data set that could possible come from our lazy researchers scenario.

### Exercise 3

Now, let's make the fitted model. As we did before, use `stan_glm()` and set your outcome variable as `distance`and your explanatory variable as `poverty` (Remember you must insert a tilde `~` between the two). Also, include a `-1` after `poverty` so we do not get an intercept.  Set `data` to `kenya_2`, and `refresh` to 0, as well as `family` to "gaussian" since it's a linear model. Store this as `fit_2`.

```{r nonrepresentative-da-3, exercise = TRUE}

```

```{r nonrepresentative-da-3-hint-1, eval = FALSE}
fit_2 <-
  stan_glm(distance ~ poverty - 1,
           data = ...,
           refresh = ...,
           family = ...)
```

### Exercise 4

Now, make a new tibble with the observations we would like. As before, we are looking at locations where the poverty rate is 0.2. Set this new tibble to `newobs`.

```{r nonrepresentative-da-4, exercise = TRUE}

```

```{r nonrepresentative-da-4-hint-1, eval = FALSE}

```

### Exercise 5

Now, use `posterior_epred()` to make our posterior distribution. Set the first argument to our fitted model `fit_2` and the `newdata` argument to `newobs`. Continue this pipe with `as_tibble()` and store this as `pe2`.

```{r nonrepresentative-da-5, exercise = TRUE}

```

```{r nonrepresentative-da-5-hint-1, eval = FALSE}
pe2 <- posterior_epred(...,
                newdata = ...) |> 
  as_tibble()
```

### Exercise 6

Let's plot our posterior distribution. To do so, make a new pipe and map `distance` to the x-axis. Then add the layer `geom_histogram()` and map the probability to the y-axis. Set the bins argument to 100.

```{r nonrepresentative-da-6, exercise = TRUE}

```

```{r nonrepresentative-da-6-hint-1, eval = FALSE}
Remember that the columns aren't named when `posterior_epred()` is used, but rather numbered. To call the first column, you should use the format `1`.
```

```{r nonrepresentative-da-6-hint-2, eval = FALSE}
To map the probability to the y-axis, set the first argument of `geom_histogram()` to `aes(y = after_stat(count/sum(count)))`.
```

```{r nonrepresentative-da-6-hint-3, eval = FALSE}
pe2 |> 
  ggplot(mapping = aes(x = ...)) + 
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = ...)

```

### Exercise 7

Now, add a title, subtitle, and axis labels to your graph. 

```{r nonrepresentative-da-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r nonrepresentative-da-7-hint-1, eval = FALSE}
... +
  labs(...)
```

### Exercise 8

Lastly, use `scale_y_continuous()` to format the y-axis to be formatted as a percentage. To do so, Set the first argument of `scale_y_continuous` to `scales::percent_format()`. To finish the plot, add `theme_classic()`.

```{r nonrepresentative-da-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r nonrepresentative-da-8-hint-1, eval = FALSE}
... +
  scale_y_continuous(scales::percent_format()) + 
  theme_classic()
```

### 

Recall that your graph should appear similar to the following:

```{r}
exp_poverty_2
```

## Compare

Through the past two sections, we answered the same question with what we would consider very representative data and data that we made to be unrepresentative. Let's compare the resulting models by making the following plot.

```{r}
combo_plot
```

### 

### Exercise 1

First, let's combine our two posterior distributions from the representative data. To do so, use `bind_rows()` with the first argument as `pe` and the second as `pe2`.

```{r compare-1, exercise = TRUE}

```

```{r compare-1-hint-1, eval = FALSE}
bind_rows(..., ...)
```

### 

Notice that the tibble has 8,000 rows, so the distributions have been combined, however, we can't determine which rows are from the representative data and which are from the unrepresentative data.

### Exercise 2

We can fix this issue by adding setting the argument `.id` to "type in `bind_rows()`.

```{r compare-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r compare-2-hint-1, eval = FALSE}
bind_rows(..., ..., .id = ...)
```

### 

As you can see, this adds another column to our tibble that has either entries of 1 or 2. These indicate from which posterior distribution the row is from. 1 indicates `pe` and 2 indicates `pe2`.

### Exercise 3

While we know which distribution is represented by each number, let's change the 1s and 2s to be more clear of which dataset they represent by modifying our arguments in `bind_rows()`. For your first argument in `bind_rows()`, use `list(rep = pe, unrep = pe2)`. Then set the second argument `.id` to "type" as we did in our previous exercise. Save this as `pe_combo`.

```{r compare-3, exercise = TRUE}

```

```{r compare-3-hint-1, eval = FALSE}
bind_rows(list(rep = ..., unrep = ...), .id = ...)
```

### 

Through using this list in the first argument, we essentially specify what we would like the value to be in the "type" column for each tibble when they are combined.

### Exercise 4

View a sample of `pe_combo` by starting a pipe and using `slice_sample()` with the first argument `n` set equal to 10.

```{r compare-4, exercise = TRUE}

```

```{r compare-4-hint-1, eval = FALSE}
pe_combo |> slice_sample(n = ...)
```

### 

As you can see, the type column contains both "unrep" and "rep", indicating the distribution which that row is from.

### Exercise 5

Let's now plot both posteriors onto one plot using our tibble `pe_combo`. Use `ggplot()` and `aes()` to map distance to the x-axis and set `fill` to `type`. Then, add the layer `geom_histogram()` and map probability to the y-axis by setting the first argument to `aes(y = after_stat(count/sum(count)))`. 

```{r compare-5, exercise = TRUE}

```

```{r compare-5-hint-1, eval = FALSE}
Recall that the column with our distances is still unlabeled, but rather numbered. So, to call the column, use `1`.
```

```{r compare-5-hint-2, eval = FALSE}
pe_combo |> 
  ggplot(mapping = aes(x = ..., fill = ...)) +
  geom_histogram(aes(y = after_stat(count/sum(count))))
```

### 

Right now, the bars for representative and unrepresentative data are stacked on top of one another, and we haven't specified the width of `bins`. 

### Exercise 6

In `geom_histogram()`, set the `bins` argument to 100. Additionally, set `position` to "identity" and alpha = 0.5 so we can see both distributions layered on top of one another where they overlap.

```{r compare-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r compare-6-hint-1, eval = FALSE}
... + 
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = ...,
                 position = ...,
                 alpha = ...)
```

### Exercise 7

Now, add a title, subtitle, and labels.

```{r compare-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r compare-7-hint-1, eval = FALSE}
... +
  labs(...)
```

### Exercise 8

Use `scale_y_continuous()` and format the y-axis as a percentage. Add the theme_classic().

```{r compare-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r compare-8-hint-1, eval = FALSE}
To format the y-axis as a percentage, use the argument `scales::percent_format()` in `scale_y_continuous`.
```

```{r compare-8-hint-2, eval = FALSE}
... +
  scale_y_continuous(scales::percent_format()) +
  theme_classic()
```

### 

Reminder, your graph should appear similar to the following:

```{r}
combo_plot
```

### 

As can be seen by the above plot, the two distributions are fairly different, with the expected distance being a bit more than 12 for our representative data and about 10.5 for our unrepresentative data. Additionally, the representative data has a much larger range while the unrepresentative data is narrower. This is why having representative data is so important, because with our unrepresentative data, we would not have considered the a distance of 12 km being very likely at all to have a poverty rate of 0.2, however in our representative data we can see that this our expected distance.

```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
