---
title: 'Three Parameters: Kenya'
author: Mahima Malhotra
tutorial:
  id: three-parameters-kenya
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: Use data from Kenya voter registration efforts to construct a three parameter
  model.
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(rstanarm)
library(gt)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

kenya_2 <- kenya %>% 
  filter(distance < 25)

fit_1 <- stan_glm(distance ~ poverty,
                  data = kenya,
                  refresh = 0)

newobs <- tibble(poverty = 0.2)

pe <- posterior_epred(fit_1, newdata = newobs) %>% 
  as_tibble()

exp_poverty <- pe %>%
  ggplot(aes(x = `1`)) + 
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = 100) +
  labs(title = "Posterior for Expected Distance",
       subtitle = "Polling locations that are on average 12 km from those assigned to them have poverty rates of 0.2",
       x = "Poverty Rate",
       y = "Probability") +
  scale_y_continuous(labels = scales::percent_format()) +
  theme_classic()

fit_2 <- stan_glm(distance ~ poverty,
                  data = kenya_2,
                  refresh = 0)

fit_2

newobs2 <- tibble(poverty = 0.2)

pe2 <- posterior_epred(fit_2, newdata = newobs2) %>% 
  as_tibble()

exp_poverty_2 <- pe2 %>%
  ggplot(aes(x = `1`)) + 
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = 100) +
  labs(title = "Posterior for Expected Distance",
       subtitle = "Polling locations about 11 km away on average from those assigned to them have poverty rates of 0.2",
       x = "Poverty Rate",
       y = "Probability") +
  scale_y_continuous(labels = scales::percent_format()) +
  theme_classic()
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

<!-- Four different ways to mess up representative data. First, remove rows on the basis of a variable which is not in your model. Second, remove rows on the basis of an independent variable in the model. Third, remove rows on the basis of the dependent variable. Four, remove rows on the basis of potential outcomes.  -->


## Representative Data

Let's look at how whether or not data is representative can affect our results. To do so, let's consider the following questions.

*The variable "distance" is the number of kilometers, which the person who is assigned to a given polling location, lives from that polling location. In Kenya today, what is the expected value of distance for polling locations with a poverty rate of 0.2?*

We will use the data set `kenya` to answer this question, and will make the following posterior distribution.

```{r}
exp_poverty
```

### 

### Exercise 1

First, run `?kenya` to take a closer look at the data.

```{r representative-data-1, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r representative-data-1-hint-1, eval = FALSE}
?kenya
```

### 

Pay special attention to the variables we are looking at: distance and poverty. Notice that the definition of distance matches our definition from the questions we seek to answer.

### Exercise 2

Now, call `skim(kenya)`.

```{r representative-data-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r representative-data-2-hint-1, eval = FALSE}
skim(kenya)
```

### 

Notice that there are 1.672 rows in this data set, so we have data for 1,672 polling locations in Kenya. If you were to read the study, you would also find out the total number of polling locations in the Kenyan counties being studies was 3,828.

### Exercise 3

Determine the columns we would like in our Preceptor Table in order to answer our question which is as follows.

*The variable "distance" is the number of kilometers, which the person who is assigned to a given polling location, lives from that polling location. In Kenya today, what is the expected value of distance for polling locations with a poverty rate of 0.2?*

```{r representative-data-3}
question_text(NULL,
	message = "We would like the columns for poverty rates of polling locations and the average distance from polling locations.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Therefore, our Preceptor Table would appear as the following:

```{r}
tibble(ID = c("Polling Location 1", "Polling Location 2", "...", "Polling Location 1000", "Polling Location 1001", "...", "Polling Location 3828"),
       distance = c("23", "5", "...", "47", "32", "...", "19"),
       poverty = c("0.4", "0.85", "...", "0.21", "0.63", "...", "0.32")
       ) %>%
  
  # Then, we use the gt function to make it pretty
  
  gt() %>%
  cols_label(ID = md("ID"),
             distance = md("Distance"),
             poverty = md("Poverty Rate")) %>%
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(ID))) %>%
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"), 
            locations = cells_column_labels(columns = c(ID))) %>%
  cols_align(align = "center", columns = everything()) %>%
  cols_align(align = "left", columns = c(ID)) %>%
  fmt_markdown(columns = everything())
```

### Exercise 4

While the population we are considering is from Kenya today, the data from Kenya was collected between November of 2014 and December of 2016. Write two sentences discussing whether you can consider the data from `kenya` and the columns from our Preceptor Table to be drawn from the same population. Give an example of a reason why you may not want to consider this true.

```{r representative-data-4}
question_text(NULL,
	message = "Since this data set dealt with a fairly large number of voting communities in Kenya at the time and our population is that of Kenya now. So, the difference between the data and our Preceptor Table is mostly time, which we will assume had little affect on poverty rates and voting blocks. So, we will assume that they can be drawn from the same population.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Having determined that we can consider the data from `kenya` and our Preceptor Table to be drawn from the same population, our Population Table is shown below. Note that we will consider this larger population to span from 2000 to 2030.

```{r}
tibble(source = c("Other", "Other", "...", "Preceptor Table", "Preceptor Table", "...", "Data", "Data", "...", "Other", "Other", "..."),
       year = c("", "", "", "2021", "2021", "...", "2015", "2016", "...", "?", "?", "..."),
       distance = c("", "", "", "32", "51", "...", "5", "41", "...", "?", "?", "..."),
       poverty = c("", "", "", "0.24", "0.55", "...", "0.81", "0.39", "...", "?", "?", "...")
       ) %>%
  
  # Then, we use the gt function to make it pretty
  
  gt() %>%
  cols_label(source = md("Source"),
             year = md("Year"),
             distance = md("Distance"),
             poverty = md("Poverty Rate")) %>%
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(source))) %>%
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"), 
            locations = cells_column_labels(columns = c(source))) %>%
  cols_align(align = "center", columns = everything()) %>%
  cols_align(align = "left", columns = c(source)) %>%
  fmt_markdown(columns = everything())
```

### Exercise 5

Given our Population Table, let's consider the aspects of Justice. First, let's look at validity. Write two sentences giving a possible reason for why you don't think we can consider columns `distance` and `poverty` to have the same meaning in our data and our Preceptor Table?

```{r representative-data-5}
question_text(NULL,
	message = "One point you may consider is if there was large redistricting that changed the size of districts meaning that the average distance a voter would have to travel to reach their polling location per voting block would have vastly changed",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

If we truly believed that any of this occurred, then this would bring us to a halt. However, we will consider our data to be valid and continue.

### Exercise 6

Now, consider stability. Write two sentences considering whether we can consider the relationship between `distance` and `poverty` to be the same between the years the study covered (2014-2016) and 2021. Discuss a possible reason that the relationship may have changed.

```{r representative-data-6}
question_text(NULL,
	message = "One reason that could have caused the model to change would be a large redistricting effort that added more districts and therefore decreased the distance that people have to travel to reach their respective voting location. Another reason you could consider is the possibility that the poverty rate has dramatically increased or decreased between 2016 and now, meaning that the old model wouldn't accurately represent the poverty rate. Since we have no reason to believe anything of the sorts is true, we will consider our model to be stable.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 7

Next, write two sentences considering a reason we may not determine the data from 2014-2016 to be representative of the entirety of Kenya in that time period. 

```{r representative-data-7}
question_text(NULL,
	message = "You may consider reasons such as if several rural areas were left out of the study, or if mostly areas with low poverty rates were studied. Since, to our knowledge, areas of Kenya were not left out of the study and a large number of Kenya's voting block communities were studies, we can consider this data to be representative.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

If we were to take a deeper dive into our study, we would actually see that we can consider this data to be very representative of its population as the polling locations that were selected were chosen randomly and, as stated in the study, "[followed] a strategy that minimized the chances of spillovers, and blocked on poverty, distance and population
density."

### Exercise 8

Finally, as our last step of Justice, determine whether the data-generating mechanism is linear or logistic and why. Also state the corresponding family argument of `stan_glm()` needed to make that type of model. Use the phrase "outcome variable".

```{r representative-data-8}
question_text(NULL,
	message = "The DGM will be linear because we can consider our outcome variable `distance` to be continuous and therefore we will set the family argument to 'gaussian'",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 9

Having completed Justice, we will now move onto Courage. Let's make our posterior distribution using 'stan_glm()'. Set your outcome variable as `distance`and your explanatory variable as `poverty` (Remember you must insert a tilde `~` between the two). Also, include a `-1` after `poverty` so we do not get an intercept.  Set `data` to `kenya`, and `refresh` to 0. Store this as `fit_1`.

```{r representative-data-9, exercise = TRUE}

```

```{r representative-data-9-hint-1, eval = FALSE}
fit_1 <- stan_glm(distance ~ poverty -1,
                  data = ...,
                  refresh = ...)
```

### Exercise 10

With our fitted model, we can answer our question. Recall:

*In Kenya today, what is the expected value of distance for polling locations with a poverty rate of 0.2?*

To do so, first make a new tibble with the observations we would like. In this case, we are looking at locations where the poverty rate is 0.2. Set this new tibble to `newobs`.

```{r representative-data-10, exercise = TRUE}

```

```{r representative-data-10-hint-1, eval = FALSE}
newobs <- tibble(poverty = ...)
```

### Exercise 11

Recall that `posterior_epred()` is used when looking for expected values such as in this case. Therefore, use `posterior_epred()` with the first argument as our fitted model `fit_1` and the `newdata` argument as `newobs`. Continue this pipe with `as_tibble()`. Store this as `pe`.

```{r representative-data-11, exercise = TRUE}

```

```{r representative-data-11-hint-1, eval = FALSE}
pe <- posterior_epred(..., newdata = ...) %>% 
  as_tibble()
```

### Exercise 12

With our posterior distribution, we can now seek to answer our question. To do so, make a new pipe and map `distance` to the x-axis. Then add the layer `geom_histogram()` and map the probability to the y-axis. Set the bins argument to 100.

```{r representative-data-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r representative-data-12-hint-1, eval = FALSE}
Remember that the columns aren't named when `posterior_epred()` is used, but rather numbered. To call the first column, you should use the format `1`.
```

```{r representative-data-12-hint-2, eval = FALSE}
To map the probability to the y-axis, set the first argument of `geom_histogram()` to `aes(y = after_stat(count/sum(count)))`.
```

```{r representative-data-12-hint-3, eval = FALSE}
pe %>% 
  ggplot(mapping = aes(x = ...)) + 
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = ...)
```

### Exercise 13

Now add a title, subtitle, and axis labels to your graph.

```{r representative-data-13, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r representative-data-13-hint-1, eval = FALSE}
+
  labs(...)
```

### Exercise 14

Lastly, use `scale_y_continuous()` to format the y-axis to be formatted as a percentage. To do so, Set the first argument of `scale_y_continuous` to `scales::percent_format()`. To finish the plot, add `theme_classic()`.

```{r representative-data-14, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r representative-data-14-hint-1, eval = FALSE}
+ 
  scale_y_continuous(...) +
  theme_classic()
```

### 

Recall that your plot should appear similar to the following:

```{r}
exp_poverty
```

### 

Through this, we have determined that we expect polling locations which are 12 km away on average from those who are assigned to that location to have a poverty rate of 0.2, and achieved this answer with data that we considered to be pretty representative.

## Non-Representative Data

In our last model, we could consider our data to be representative of our population, however, what if that were not the case? Now, let's answer the same question, but with unrepresentative data. To do so, we will make the following graph:

```{r}
exp_poverty_2
```

Recall our question.

*Recall: the variable "distance" is the number of kilometers, which the person who is assigned to a given polling location, lives from that polling location. In Kenya today, what is the expected value of distance for polling locations with a poverty rate of 0.2?*

### 

### Exercise 1

Consider that more rural communities far away from the locations where those conducting the study were staying also tended to have polling locations which spanned larger areas and people had to travel more on average to reach. Given this piece of information, let's also say that our researchers were kind of lazy and wanted to get back home more quickly. So, they decided that places further away from where they were staying were too far to study and would take too much time to reach. This caused them to not travel to any polling locations that were more than 25 km away from those who were assigned to it.

With this scenario, write two sentences discussing representativeness and whether we can consider data from this scenario in that same year to be representative of Kenya that year.

```{r nonrepresentative-da-1}
question_text(NULL,
	message = "Given that rural communities are not being reached in this scenario and therefore also communities that are located further away from their polling location, we can't consider this data to be representative of the entirety of Kenya.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### 

Although we might not be able to consider this data very representative of Kenya, if this were the data we had, we could acknowledge the problems with it and consider it representative enough to continue.

### Exercise 2

Let's mimic this scenario with our data `kenya` and answer our question with non-representative data. To do so, use `kenya` and filter out communities that are on average more than 25 km away from their polling location. Store this as `kenya_2`.

```{r nonrepresentative-da-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r nonrepresentative-da-2-hint-1, eval = FALSE}
kenya_2 %>% 
  filter(distance < 25)
```

### 

With this, we have essentially created a data set that could possible come from our lazy researchers scenario.

### Exercise 3

Now, let's make the fitted model. As we did before, use `stan_glm()` and set your outcome variable as `distance`and your explanatory variable as `poverty` (Remember you must insert a tilde `~` between the two). Also, include a `-1` after `poverty` so we do not get an intercept.  Set `data` to `kenya_2`, and `refresh` to 0. Store this as `fit_2`.

```{r nonrepresentative-da-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r nonrepresentative-da-3-hint-1, eval = FALSE}
fit_2 <-
  stan_glm(distance ~ poverty - 1,
           data = ...,
           refresh = ...)
```

### Exercise 4

Now, make a new tibble with the observations we would like. As before, we are looking at locations where the poverty rate is 0.2. Set this new tibble to `newobs`.

```{r nonrepresentative-da-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r nonrepresentative-da-4-hint-1, eval = FALSE}

```

### Exercise 5

Now, use `posterior_epred()` to make our posterior distribution. Set the first argument to our fitted model `fit_2` and the `newdata` argument to `newobs`. Continue this pipe with `as_tibble()` and store this as `pe2`.

```{r nonrepresentative-da-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r nonrepresentative-da-5-hint-1, eval = FALSE}
pe2 <- posterior_epred(...,
                newdata = ...) %>% 
  as_tibble()
```

### Exercise 6

Let's plot our posterior distribution. To do so, make a new pipe and map `distance` to the x-axis. Then add the layer `geom_histogram()` and map the probability to the y-axis. Set the bins argument to 100.

```{r nonrepresentative-da-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r nonrepresentative-da-6-hint-1, eval = FALSE}
Remember that the columns aren't named when `posterior_epred()` is used, but rather numbered. To call the first column, you should use the format `1`.
```

```{r nonrepresentative-da-6-hint-2, eval = FALSE}
To map the probability to the y-axis, set the first argument of `geom_histogram()` to `aes(y = after_stat(count/sum(count)))`.
```

```{r nonrepresentative-da-6-hint-3, eval = FALSE}
pe2 %>% 
  ggplot(mapping = aes(x = ...)) + 
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = ...)

```

### Exercise 7

Now, add a title, subtitle, and axis labels to your graph. 

```{r nonrepresentative-da-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r nonrepresentative-da-7-hint-1, eval = FALSE}
... +
  labs(...)
```

### Exercise 8

Lastly, use `scale_y_continuous()` to format the y-axis to be formatted as a percentage. To do so, Set the first argument of `scale_y_continuous` to `scales::percent_format()`. To finish the plot, add `theme_classic()`.

```{r nonrepresentative-da-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r nonrepresentative-da-8-hint-1, eval = FALSE}
... +
  scale_y_continuous(scales::percent_format()) + 
  theme_classic()
```

### 

Recall that your graph should appear similar to the following:

```{r}
exp_poverty_2
```

## Compare

Through the past two sections, we answered the same question with what we would consider very representative data and data that we made to be unrepresentative. Let's compare the resulting models.

### Exercise 1

```{r}
pe <- pe %>% mutate(ID = "rep")

pe2 <- pe2 %>% mutate(ID = "unrep")

combo <- merge(pe, pe2, all = T)

combo %>% 
  ggplot(aes(x = `1`, fill = ID)) + 
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 100,
                   position = "identity",
                   alpha = 0.5)
```


```{r compare-1, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r compare-1-hint, eval = FALSE}

```

###



```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
