---
title: Downloading Census Data
author: Anmay Gupta
tutorial:
  id: downloading-census-data
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: Downloading US Census Bureau data into R
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(tidycensus)
library(ipumsr)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

# This is all of the data that the Census Key is needed for.

# rural <- get_decennial(geography = "state",
#                        variables = c("P001001", "P002005"),
#                        year = 2010,
#                        output = "wide")
# write_rds(rural, "data/05-census-rural.rds")

rural <- read_rds("data/rural.rds")

# il_pums <- get_pums(variables = c("PUMA", "FINCP"),
#                     state     = "Illinois",
#                     recode    = TRUE,
#                     survey    = "acs1",
#                     year      = 2019)
# write_rds(il_pums, "data/05-census-il-pums.rds")

il_pums <- read_rds("data/il-pums.rds")
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```


## Accessing the Census API
###

In this tutorial, we will cover how to download US Census Bureau data into R and then use it to create graphs.

### Exercise 1

First, we need to access the US Census API. We will do this by using the **tidycensus** package. This will allow us to use an API key to then access Census data.

###

Load the **tidycensus** package into your R session using `library(tidycensus)`. You may have to install the package before loading it in.

###

Run `search()` in the Console to see the libraries that you've currently loaded, then copy and paste the command and the result into the space below. 

```{r api-access-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    rows = 3)
```

###

The output should include the string "package:tidycensus" in the output. This will be the main package that we are going to use to access the US Census, as it allows us to use simple R functions without having to use the complicated `GET()` requests described in Chapter 3.

### Exercise 2

Now that we have the package needed to access the Census database, we need to get an API key. 

An API key is basically a password for an API, but it often comes with certain restrictions. For example, the Census only allows you to collect 50 variables (or columns) from a database at a time. 

###

First, visit [https://api.census.gov/data/key_signup.html](https://api.census.gov/data/key_signup.html) and request an API key. Use your school or other organization name for the `Organization Name` field. Then, follow the steps and verify your API key through the email that it sends.

###

Copy and paste your API key into the box below. If you don't want to share your API key, change a few letters to make it invalid.

```{r api-access-2}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    rows = 3)
```

###

While an API key isn't mandatory for accessing the Census, it allows you to do more requests and use multiple computers to collect data. It's also a necessity for using the `tidycensus` package.

### Exercise 3

You may remember putting your GitHub Personal Access Token into your `.Renviron` file for safekeeping. We'll be doing the same for our Census API key, but the process looks a little bit different.

###

The **tidycensus** package makes the process much simpler. Run `census_api_key("YOUR API KEY HERE", install = TRUE)` in the Console, substituting your API key in the field.

This should save your key into your `.Renviron` file.

###

Run `Sys.getenv("CENSUS_API_KEY")` in the Console. Copy-paste the command and the output in the space below. If you are nervous about sharing your Census API key, feel free to change it after your copy/paste it into the answer.

```{r api-access-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    rows = 2)
```

###

This should contain your Census API key. If you want to see where the key is stored, run `usethis::edit_r_environ()` in the Console. It should open up your `.Renviron` file and show you all of the keys that you have stored there so far.

###

## Getting data from the Census API
###

The Census API works by accessing Census databases and tables. We can find these tables by visiting [data.census.gov](data.census.gov). For this tutorial, we'll be using the **American Community Survey** and the **Decennial Census**.

###

If you want to see all supported Census tables, please visit [here](https://api.census.gov/data.html). 

If you want to learn more about how the Census API is structured, please look at the official documentation [here](https://www.census.gov/content/dam/Census/data/developers/api-user-guide/api-guide.pdf).

### Exercise 1

Let's try accessing the American Community Survey database. In order to do this, we'll use the `get_acs()` function with the `geography`, `variables`, and `year` arguments.

### 

The geography argument determines the scope of the data (such as `us` for the entire country and `county` for counties), the `year` argument defines the year the data was accessed and the `variables` argument defines which variables you want to use.

###

<!-- AG: 
I think that the Primer is incorrect here. It shows a method for finding table
IDs rather than variable names by going through data.census.gov. However, this
seems to provide a table ID instead of a variable ID, and you can see their
differences here:
https://www.census.gov/content/dam/Census/library/publications/2019/acs/acs_summary-file_handbook_2019_ch03.pdf.
As of right now, it seems like the only method to access variable names is
through an API request.
-->

<!-- DK: Please fix the Primer. -->

Let's try to find the total American population. First of all, we need to access the variable containing that population. We can do this by using the `load_variables()` function.

###

Run the `load_variables()` function below, setting the `year` argument to 2010 and the `dataset` argument to `"acs5"`.

```{r download-1, exercise = TRUE}

```

```{r download-1-hint-1, eval = FALSE}
load_variables(year    = ...,
               dataset = ...)
```

###

This should show all of the variables that the **A**merican **C**ommunity **S**urvey (ACS) has as well as a brief explanation as to what they actually mean.

As you can see, the first row of the table is the "UNWEIGHTED SAMPLE COUNT OF THE POPULATION", as shown by the `concept` column. That means that the population count is stored within the `B00001_001` variable. Let's try accessing the data under that variable.

### Exercise 2

Now that we have our variable name, we need to use it in our code.

###

Run the `get_acs()` function below and set the `geography` argument to `"us"`, the `year` argument to `2010`, and the `variables` argument to a string containing the variable that we just found.

```{r download-2, exercise = TRUE}

```

```{r download-2-hint-1, eval = FALSE}
get_acs(geography = ...,
        year      = ...,
        variables = ...)
```

###

This returns a tibble with the geography, the name of the area described, the variable, and the estimate of the total population.

### Exercise 3

But variables contain a lot more information than just that. They also contain information about the different geographies located within that region. Think about each variable as a classification for different information. A variable about population includes information about the population at every level and at every scope.

###

Run the `get_acs()` function again, setting the `geography` argument to `"state"`, the `year` argument to `2010`, and the `variables` argument to a string containing the variable that we used earlier.

```{r download-3, exercise = TRUE}

```

```{r download-3-hint-1, eval = FALSE}
get_acs(geography = ...,
        year      = ...,
        variables = ...)
```

### 

As you can see, variables contain a lot of different information at a lot of different levels. 

The GEOID column contains the FIPS code of the area the data covers. This code is a standardized way to identify the different areas and gets larger as the scope narrows down. You can learn more about FIPS codes [here](https://transition.fcc.gov/oet/info/maps/census/fips/fips.txt#:~:text=FIPS%20codes%20are%20numbers%20which,to%20which%20the%20county%20belongs.).

## Graphing Census data
###

Now that we've successfully accessed a variable name and the information contained within it, let's try graphing the ratio of rural population to the actual population for every state.

### Exercise 1

First, let's try to access the Decennial Census. The Decennial Census is conducted every 10 years and is the survey that the Census Bureau was established for in the first place.

###

Run the `load_variables()` function, setting the `year` argument to `2010` and the `dataset` argument to `"sf1"`.

```{r graphing-1, exercise = TRUE}

```

```{r graphing-1-hint-1, eval = FALSE}
load_variables(year    = ...,
               dataset = ...)
```

###

This returns all of the variables that the Decennial Census uses. The `"sf1"` dataset contains the summary files for the Decennial Census, so we can look at it in order to see all of the variables used by the Census Bureau.

### Exercise 2

This returned a lot of information, but it's a little harder to find what we actually need. In this case, we need to find the actual population variable and the rural population so that we can determine the final ratio.

###

We can do this by using a standard `filter()` command like we did with tidyverse. 

###

Pipe the `load_variables()` function into a `filter()` command that filters the `concept` so that it is only `"URBAN AND RURAL"` and filters the `name` so that it contains the letter `"P"`.

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r graphing-2, exercise = TRUE}

```

```{r graphing-2-hint-1, eval = FALSE}
load_variables(year    = ...,
               dataset = ...) %>%
  filter(context == ... & grepl(..., ...))
```


###

This filters the variables so that it only has data about the urban and rural populations. Since we want the amount of the population that's rural, we're variable `P002005` since it's named `Total!!Rural` and as such describes the rural populations.

### Exercise 3

Now that we have our variable names, let's actually load in our data. We can do this using the `get_decennial()` function, which is very similar to the `get_acs()` function that we used earlier.

###

This time, we need to get data from 2 variables: The total population ("P001001") and the rural population ("P002005"). 

###

Run the `get_decennial()` function, setting the `geography` argument to `"state"`, the `year` argument to `2010`, the `variables` argument to a vector containing these two variable IDs, and the `output` argument to `"wide"`. 

```{r graphing-3, exercise = TRUE}

```

```{r graphing-3-hint-1, eval = FALSE}
get_decennial(geography = ...,
              variables = c(..., ...),
              year      = ...,
              output    = "wide")
```

###

By setting the `output` argument to wide, we make the variables their own columns, much like the `pivot_wider()` function. If you don't set the `output` argument to wide, a `variable` column containing the variable name will be created instead.

### Exercise 4

Let's create the following plot using this data.

```{r}
# Including this in the tutorial instead of in the setup chunk because the
# students aren't supposed to be able to access it.

rural_graph <- rural %>%
                 mutate(prop_rural = P002005/P001001) %>% 
                 ggplot(aes(x = prop_rural, y = fct_reorder(NAME, prop_rural))) +
                   geom_point() +
                   labs(title    = "Rural Population in US States in 2010",
                        subtitle = "Maine and Vermont are the most rural states",
                        caption  = "Source: US Census",
                        x        = "Rural Population Proportion",
                        y        = NULL) +
                   theme(axis.text.y = element_text(size = 5))

rural_graph
```

###

Save the previous output to a variable named `rural` so that we can start out graph.

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r graphing-4, exercise = TRUE}

```

```{r graphing-4-hint-1, eval = FALSE}
rural <- ...
```

###

We'll be using this value to create a graph and save our data.

### Exercise 5

Start a new pipe using `rural` and add a column containing the ratio between P002005 and P001001.

```{r graphing-5, exercise = TRUE}

```

```{r graphing-5-hint-1, eval = FALSE}
rural %>%
  mutate(prop_rural = ...)
```

### Exercise 6

Continue the pipe and use the `ggplot()` function to create a graph. Map the `x` argument to the ratio and the `y` argument to `NAME`, then add a `geom_point()` layer.

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r graphing-6, exercise = TRUE}

```

```{r graphing-6-hint-1, eval = FALSE}
... %>%
  ggplot(aes(x = ..., y = ...)) +
    geom_point()
```

###

This should show all of the states and their rural population proportion in alphabetical order.

### Exercise 7

Let's sort the states by their rural population. Change the `y` argument to reorder the names based on the rural population ratio.

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r graphing-7, exercise = TRUE}

```

```{r graphing-7-hint-1, eval = FALSE}
... %>%
  ggplot(aes(x = ..., y = fct_reorder(..., ...))) +
    geom_point()
```

### Exercise 8

Now let's add the labels to the graph.

As a reminder, here's what the graph should look like:

```{r}
rural_graph
```
###

Additionally, continue the pipe and add the function `theme(axis.text.y = element_text(size = 5))` in order to shrink the size of the labels and let them all fit onto the graph.

###

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r graphing-8, exercise = TRUE}

```

```{r graphing-8-hint-1, eval = FALSE}
... +
  labs(title    = ...,
       subtitle = ...,
       caption  = ...,
       x        = ...,
       y        = ...)
```

###

Now that we've looked at American Community Survey and Decennial Census data, let's look at PUMS data.

## PUMS data
###

**P**ublic **U**se **M**icrodata **S**amples, or **PUMS** data, contains advanced census data on individual people. While it only contains data for about 1% of the US, it's extremely deep and lets you do a lot of cool things.

### Exercise 1

While this may seem intimidating, PUMS is largely the same as the previous functions with a few small differences. 

###

Run the `glimpse()` function on the dataset `pums_variables` to see what each of the variables represents.

```{r pums-1, exercise = TRUE}

```

```{r pums-1-hint-1, eval = FALSE}
pums_variables
```

###

The `pums_variables` dataset is automatically constructed by the **tidycensus** package and contains a large amount of information, with 31,759 different variables.

### Exercise 2

Let's try to collect the age, sex, and income data for every single person in PUMS. The `AGEP` variable is for age, the `FINCP` variable is for income, and the `SEX` variable is the sex.

###

We can do this by using the `get_pums()` function. Run the `get_pums()` function, setting the `variables` argument to the ones described above, `state` to your state's name, `recode` to `TRUE`, and `survey` to `"acs1"`.

```{r pums-2, exercise = TRUE}

```

```{r pums-2-hint-1, eval = FALSE}
get_pums(variables = c(..., ..., ...),
         state     = ...,
         recode    = TRUE,
         survey    = "acs1")
```

###

If you wanted to import data from the entire United States, you can set the `state` argument to `state.name`. Keep in mind that this is all 3 million participants in the PUMS program, so it takes up a large amount of space (over 100 megabytes).

The `recode` argument transforms numerical ID codes into human-readable strings, with columns like `ST` holding the FIPS code while `ST_label` has the actual name of the state.

### Exercise 3


Let's try graphing the percent of PUMS participants below the poverty line in Illinois.

Here's what your graph should look like.

<!-- All of these hide stuff so I'm using them all. It's lazy but it works. -->

```{r, results='hide', warning=FALSE}
il_graph <- il_pums %>%
              group_by(PUMA) %>%
              summarize(total_pop  = sum(PWGTP),
                        pct_income = sum(PWGTP[FINCP < 12880]) / total_pop,
                        .groups    = "drop") %>%
              ggplot(aes(x = pct_income, y = fct_reorder(PUMA, pct_income))) +
              geom_point() +
              labs(title    = "Poverty in Illinois PUMA Zones in 2019",
                   subtitle = "PUMA zones in Will County and Kane County have the lowest poverty rates.",
                   x        = "Poverty Population Percentage",
                   y        = "PUMA Zone Code") +
              theme(axis.text.y = element_text(size = 3))

il_graph
```

###

First we need to load our data. Run `get_pums()`, setting the `variables` argument to `"PUMA"` and `"FINCP"`, the `state` to Illinois, `recode` to `TRUE`, the `survey` to `"acs1"`, and the year to 2019. Save this to the `il_pums` variable.

```{r pums-3, exercise = TRUE}

```

```{r pums-3-hint-1, eval = FALSE}
il_pums <- get_pums(variables = c(..., ...),
                    state     = ...,
                    recode    = TRUE,
                    survey    = "acs1",
                    year      = ...)
```

### Exercise 4

Second, we need to filter and group the different people by their PUMA zones so that we can talk about the things done over the entire population.

###

Start a new pipe with `il_pums` and group it by the `PUMA` column.

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r pums-4, exercise = TRUE}

```

```{r pums-4-hint-1, eval = FALSE}
il_pums %>%
  group_by(PUMA)
```

### Exercise 5

Now let's use those groups and summarize the entire population by their income. 

###

Continue the pipe with the `summarize()` function, creating a column named `total_pop` that contains the sum of `PWGTP`.

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r pums-5, exercise = TRUE}

```

```{r pums-5-hint-1, eval = FALSE}
... %>%
  summarize(total_pop = sum(...))
```

###

The `PWGTP` column is the number of people contained within that sample, so if you total all of the `PWGTP` column then you can get the total population within the study.

### Exercise 6

We just totaled the population, but now we need to add the income information. 

###

Within the `summarize()` function, add a new column called `pct_income`. This column should include the sum of all the elements of `PWGTP` that have a `FINCP` less than `12880`, then divide it by the total population.

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r pums-6, exercise = TRUE}

```

```{r pums-6-hint-1, eval = FALSE}
... %>%
  summarize(total_pop  = sum(...),
            pct_income = sum(PWGTP[... < ...]) / ...)
```

###

This gets the percentage of people below the poverty line. It's also advisable to drop the groups after the `summarize()` in order to avoid conflicts later down the road.

### Exercise 7

Continue the pipe with a `ggplot()`, mapping the `x` to `pct_income` and the `y` to `PUMA`. Then add a `geom_point()` layer in order to display the point graph.

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r pums-7, exercise = TRUE}

```

```{r pums-7-hint-1, eval = FALSE}
... %>%
  ggplot(aes(x = ..., y = ...)) +
  geom_point()
```

### Exercise 8

Let's sort the zones by their poverty rates. Change the `y` argument to reorder the names based on the rural population ratio.

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r pums-8, exercise = TRUE}

```

```{r pums-8-hint-1, eval = FALSE}
... %>%
  ggplot(aes(x = ..., y = fct_reorder(..., ...))) +
    geom_point()
```

### Exercise 9

Now let's add the labels to the graph.

As a reminder, here's what the graph should look like:

```{r}
rural_graph
```
###

Additionally, continue the pipe and add the function `theme(axis.text.y = element_text(size = 3))` in order to shrink the size of the labels and let them all fit onto the graph.

###

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r pums-9, exercise = TRUE}

```

```{r pums-9-hint-1, eval = FALSE}
... +
  labs(title    = ...,
       subtitle = ...,
       caption  = ...,
       x        = ...,
       y        = ...)
```

###

If you want to see what PUMA zones correlate to what counties, you can visit the [interactive map](https://iecam.illinois.edu/maps/public-use-microdata-areas-pumas/) or the [Census Bureau documentation](https://www.census.gov/geographies/reference-maps/2010/geo/2010-pumas/illinois.html).

## IPUMS data

<!-- AG: 
I'm just copying from the Primer because my account hasn't been approved yet.

Also, I thought that images and data should be hosted in primer.tutorials if
they're used both in the Primer and the tutorials. 
Should I change the Primer to pull from the tutorials rather than from its own
files?
-->

IPUMS, or the **I**ntegrated **P**ublic **U**se **M**icrodata **S**eries, is a great source for big data. 

It includes the Current Population Survey (CPS) from the U.S. Census as well as other health and housing data. 

This allows you to create a subset of these massive repositories of collected data that fits your needs and interests.

###

An initial word of caution to those new to the system is that your requests are not filled immediately, so **start early!**

You **will** have to close out the tutorial while you wait for your account to be approved.

### Exercise 1

First, 

```{r ipums-data-1}
question_text(NULL,
	message = "answer here",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

###



Congratulations on completing this tutorial.

###

```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
