---
title: "Data A"
tutorial:
  id: "data-a"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Chapter 3: Data -- A"
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(readxl)
library(jsonlite)
library(png)
library(grid)


knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 

tbl_1 <- tibble( a = 1 , b = 2, c = 3)

iris_p <- iris %>% 
  ggplot(aes(x = Sepal.Length, y = Sepal.Width)) +
  geom_jitter() +
  labs(title = "Sepal Dimensions of Various Species of Iris",
       x = "Sepal Length",
       y = "Sepal Width")


# Dealing with external files in tutorials is confusing! The biggest problem is
# figuring out when things will be evaluated and where. There is some discussion
# here: https://rstudio.github.io/learnr/. It certainly seems that setup chunks
# are not evaluated until Run Code is pressed on the Exercise chunk.

# We need to get the example file into the working area for each question. I
# initially had this material in its own R code chunk. But then the function was
# not available when the tutorial was run from the Tutorial Pane. Why? 

# I used to believe that any objects which you always want around for the entire
# portfolio should be created here, in the main set-up chunk. That seems to both
# work (an object is available) and fail (you get a weird warning message about
# the object not being available).  For example, code which creates an object
# called `www` does work in that www is around for later questions, but it also
# makes this warning:

# Warning: Error in paste0: object 'www' not found

# Very confusing! Since everything works, this must be a weird evaluation timing
# issue . . .

# For some usage, you want to interact with the file in its main location,
# without copying it over. For that purpose, you need the path to where the
# package is installed.

# Is there a way to force the deletion of any previous work, whenever you
# install a new version of the package? (Maybe just changing the version number
# does this. Maybe using the `id` designation.) There seem to be at least two
# kinds of work that stay on. First, the answers which you have already given,
# which can be removed by hitting the Start Over button. Second, the html file
# itself seems to (often) be a previous version, rather than the latest.
```

<!-- Would be nice if running the code did not produce TRUE and the col types message. But I can't think of a way to get rid of that, and still get the object printed out. -->

<!-- Couple more questions using col_types argument.  -->

<!-- Show how to use the result from running it initially to make the warning disappear. -->

<!-- For data-B -->

<!-- Couple questions on read json? Like we do in the book? -->

<!-- Couple questions on reading in data from the web, like a Wikipedia table? -->




## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```


## CSV Files
###

"CSV" stands for **c**omma-**s**eparated **v**alues, meaning that the variable names and data values are separated by commas in the file.


### Exercise 1

```{r ex-1-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_1.csv"), ".")
```

Consider the contents of the `test_1.csv` file.

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"),
                     "test_1.csv")), sep = "\n")
```

###

Write code to read this file into R.

```{r ex-1, exercise = TRUE}

```

```{r ex-1-hint, eval = FALSE}
Use read_csv() to read in a csv file. 
Set the `file` argument to "test_1.csv".
```

```{r ex-2-hint, eval = FALSE}
read_csv(file = "...")
```

###

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_1.csv"))
```

###

The column specification message is a suggestion to specify the data types for each column of data. R "guesses" a data type until you do. For now, ignore the message. You will resolve this issue in a later exercise.

### Exercise 2

```{r ex-2-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_2.csv"), ".")
```

Consider the contents of the `test_2.csv` file. 

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"), 
                     "test_2.csv")), sep = "\n")
```

###

Write code for skipping the text at the top of this file.

```{r ex-2, exercise = TRUE}

```

```{r ex-2-hint-1, eval = FALSE}
In addition to the `file` argument, you will 
need to use the`skip` argument here. Set `skip` 
to 2.
```

```{r ex-2-hint-2, eval = FALSE}
read_csv(file = "test_2.csv",
          skip = ...)
```

###

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_2.csv"),
         skip = 2)
```

###

There are many arguments to `read_csv()` which allow us to deal with data formatted in different ways.

### Exercise 3


```{r ex-3-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_3.csv"), ".")
```

Consider the contents of the `test_3.csv` file. 

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"), 
                     "test_3.csv")), sep = "\n")
```

###

Write code that will create default names for the file.

```{r ex-3, exercise = TRUE}

```

```{r ex-3-hint-1, eval = FALSE}
Use the `col_names argument and set it to FALSE
```

```{r ex-3-hint-2, eval = FALSE}
read_csv(file = "...",
          col_names = ...)
```

###

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_3.csv"),
         col_names = FALSE)
        
```

###

The argument `col_names()` can also be used to create custom column names. You will learn to do so in the next exercise.

### Exercise 4

```{r ex-4-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_3.csv"), ".")
```

Consider, again, the contents of the `test_3.csv` file. 

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"), 
                     "test_3.csv")), sep = "\n")
```

###

Write code that will name the columns `a`, `b` and `c`, respectively. 

```{r ex-4, exercise = TRUE}

```

```{r ex-4-hint, eval = FALSE}
Use the `col_names` argument and set it to c("a", "b", "c"). 
```

###

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_3.csv"),
         col_names = (c("a", "b", "c")))
```

###

Recall the column specification message. To get rid of this message, we need to use the `col_types()` argument and specify the data types.

### Exercise 5 

```{r ex-5-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_3.csv"), ".")
```

Set the `col_types()` argument to `cols(a = col_double(), b = col_double(), c = col_double())`.


```{r ex-5, exercise = TRUE}

```

###

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"), 
                "test_3.csv"),
         col_names = (c("a", "b", "c")),
         col_types = cols(a = col_double(), 
                        b = col_double(), 
                        c = col_double()))
```

###

There are many other arguments to `col_types()`. You can type `?col_types()` into your console to see all the different arguments!

### Exercise 6

```{r ex-6-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"),
                 "test_5.csv"), ".")
```

Consider the contents of the `test_5.csv` file. Note the "." for the first value for `b`. In this file, a period indicates a missing value. **This is not always true.** Missing values can be indicated in many different ways. And, sometimes, a period is just a period.

```{r, comment =''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"),
                     "test_5.csv")), sep = "\n")
```

###

Write code to recognize the `.` value for `b` as an NA value.

```{r ex-6, exercise = TRUE}

```

```{r ex-6-hint-1, eval = FALSE}
Use the `na` argument and set it to "."
```

```{r ex-6-hint-2, eval = FALSE}
read_csv(file = "test_5.csv",
         comment = "...")
```

###

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"),
                "test_5.csv"),
         na = ".")
```

### Exercise 7

```{r ex-7-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"),
                 "test_6.csv"), ".")
```

Consider the contents of the `test_6.csv` file.

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"),
                     "test_6.csv")), sep = "\n")
```

###

Write code for skipping the text lines within the file.

```{r ex-7, exercise = TRUE}

```

```{r ex-7-hint-1, eval = FALSE}
Use the `comment` argument and set it to "#".
```

```{r ex-7-hint-2, eval = FALSE}
read_csv(file = "...",
         comment = "...")
```

###

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"),
                "test_6.csv"),
         comment = "#")
```

### Exercise 8

```{r ex-8-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"),
                 "test_7.csv"), ".")
```

Consider the contents of the `test_7.csv` file.

```{r, comment=''}
cat(readLines(paste0(system.file("www/", package = "primer.tutorials"),
                     "test_7.csv")), sep = "\n")
```

###

Write code to make sure the column `grade` appear as an integer variable (`<int>`), and `student` as a character variable (`<chr>`).

```{r ex-8, exercise = TRUE}

```

```{r ex-8-hint, eval = FALSE}
Use the col_types argument and set it 
to cols(grade = col_integer(), 
        student = col_character())
```

###

The result when your code is run should look like this:

```{r}
read_csv(paste0(system.file("www/", package = "primer.tutorials"),
                "test_7.csv"),
         col_types = cols(grade = col_integer(),
                          student = col_character()))
```

###

Recall R "guesses" the data types when you do not explicitly specify them with `col_types()`. Besides getting rid of the message, it's smart to specify the data types because R could guess wrong!

### Exercise 9

Consider the following tibble `tbl_1`.

```{r}
tbl_1 <- tibble(John = 1 , Aliya = 2, Maxilla = 3)
tbl_1
```

###

Use `write_csv()` to save this tibble to a file named "tbl_1.csv". *Note*: Nothing will be displayed for you to see. 

```{r ex-9, exercise = TRUE}

```

```{r ex-9-hint-1, eval = FALSE}
The first argument should be the object you want 
to save. The second argument should be the name you 
want the file saved as.
```

```{r ex-9-hint-2, eval = FALSE}
See the Primer for guidance!
```

<!-- BG: add takeaway here -->

### Exercise  10

```{r ex-10-csv-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "tbl_1.csv"), ".")
```

Run `list.files()`. You should see your newly created file listed.

```{r ex-10-csv, exercise = TRUE}

```

Your result should look like include two files: `exercise.Rmd`, which is a file used by the **learnr** package and `tbl_1.csv`, which is the file you created.


## Text Files
###

CSV files are just one type of **text** file. A text file is any file which includes plain text. The contents of such files are easy to look at in any text editor, or in RStudio.

### Exercise 1

```{r delim-1-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "delim_1.txt"), ".")
```

Consider the contents of the text file `delim_1.txt`:

```{r}
cat(readLines(paste0(system.file("www/", 
                                 package = "primer.tutorials"), 
                     "delim_1.txt")), 
    sep = "\n")
```

###

Write code for reading this file in to R. The values in the file are separated by pipes rather than commas. So, instead of `read_csv()`, you should use `read_delim()`. 

```{r delim-1, exercise=TRUE}

```

```{r delim-1-hint, eval = FALSE}
Set the file argument to "delim_1.txt". 
Also use the `delim` argument and set it to "|".
```

###

The result when your code is run should look like this:

```{r}
read_delim(paste0(system.file("www/", package = "primer.tutorials"), 
                "delim_1.txt"), delim = "|")
```

###

Note how the spaces and commas are included in the values for `town`. You can't use `read_csv()` here because not all the columns are denoted by commas.


### Exercise 2

```{r delim-2-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "delim_2.txt"), ".")
```

Consider the contents of the text file `delim_2.txt`:

```{r}
cat(readLines(paste0(system.file("www/", 
                                 package = "primer.tutorials"), 
                     "delim_2.txt")), 
    sep = "\n")
```

###

Write code for reading this file in to R, using the argument tricks you used in the previous question. Also, use the `col_types` argument to both prevent the col_types message from printing out and to set `population` as an integer.

```{r delim-2, exercise=TRUE}

```

```{r delim-2-hint, eval = FALSE}
Set the `col_types` argument to 
cols(date = col_date(format = ""),
     population = col_integer(),
     town = col_character())
```

###

The result when your code is run should look like this:

```{r}
read_delim(paste0(system.file("www/", package = "primer.tutorials"), 
                "delim_2.txt"), 
           delim = "|",
           col_types = cols(date = col_date(format = ""),
                            population = col_integer(),
                            town = col_character()))
```

###

Sadly, many text files you encounter will be much more of a mess than these examples. 


## Excel Files
###

Excel is a spreadsheet program that use tables to analyze, store, or manipulate data. The tables are composed of cells which include text, numbers, or formulas.


### Exercise 1

```{r excel-1-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "excel_1.xlsx"), ".")
```

Consider the contents of the excel file `excel_1.xlsx`:

```{r}
file <- paste0(system.file("images/", 
                           package = "primer.tutorials"),
               "/excel_1.png")
img <- readPNG(file)
grid.raster(img)
```

###

Write code for reading this file in to R. Use the `read_excel()` function from the **readxl** package. (You may assume that the package has already been loaded for you.)

```{r excel-1, exercise = TRUE}

```

```{r excel-1-hint, eval = FALSE}
Use `read_excel()` and set the `path` argument to `excel_1.xlsx`.
```

###

The result when your code is run should look like this:

```{r}
read_excel(paste0(system.file("www/", package = "primer.tutorials"), 
                 "excel_1.xlsx"))

```

###

You use the function `read_excel()` more than `write_excel()`. Writing excel files is a tricky process. 

### Exercise 2

```{r excel-2-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "excel_1.xlsx"), ".")
```

Let's once again consider the contents of `excel_1.xlsx`. However, we want to look at the second sheet of the file. **Note**: Sheet 1 is the default when looking at an Excel file, so the last exercise only showed us the contents of Sheet 1.


```{r}
file <- paste0(system.file("images/", 
                           package = "primer.tutorials"),
               "/excel_2.png")
img <- readPNG(file)
grid.raster(img)
```

###

Write code for reading the second sheet of the file into R.

```{r excel-2, exercise = TRUE}

```

```{r excel-2-hint, eval = FALSE}
Use the `sheet` argument to look at other sheets.
Set `sheet` to "Sheet2".
```

###

The result when your code is run should look like this:

```{r}
read_excel(paste0(system.file("www/", package = "primer.tutorials"), 
                 "excel_1.xlsx"), sheet = "Sheet2")
```

###

To write Excel files out, you need to use a different package.


## RDS Files


RDS files store R objects in a file which can be saved on your computer. Then, if you come back to a project, even after restarting R, you can quickly load back the object, without redoing all the code which created it.

###

### Exercise 1


Consider the following plot.

```{r}
iris %>% 
  ggplot(aes(x = Sepal.Length, y = Sepal.Width)) +
  geom_jitter() +
  labs(title = "Sepal Dimensions of Various Species of Iris",
       x = "Sepal Length",
       y = "Sepal Width")
```

###

We have saved the plot for you to an object named `iris_p`. On the line 8, use `write_rds()` to save this plot to a file named "test_1.rds". *Note*: Nothing will be displayed for you to see.


```{r rds-1, exercise = TRUE}
iris_p <- iris %>% 
  ggplot(aes(x = Sepal.Length, y = Sepal.Width)) +
  geom_jitter() +
  labs(title = "Sepal Dimensions of Various Species of Iris",
       x = "Sepal Length",
       y = "Sepal Width")

```

```{r rds-1-hint-1, eval = FALSE}
The first argument should be the object you want to save. 
The second argument should be the name you want the 
file saved as.
```

```{r rds-1-hint-2, eval = FALSE}
write_rds(iris_p, 
          "test_1.rds")
```

###

The big advantage of creating an rds file is that we can reload the object it contains later, without re-running the code which created it.

### Exercse 2

```{r ex-2-rds-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_1.rds"), ".")
```

Run `list.files()`. You should see your newly created file listed.

```{r ex-2-rds, exercise = TRUE}

```

###

Your result should look like include two files: `exercise.Rmd`, which is a file used by the **learnr** package and `test_1.rds`, which is the file you created.



### Exercise 3

```{r rds-3-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_1.rds"), ".")
```

Let's now use `read_rds()` to read in the newly created file! Set the `file` argument to "test_1.rds".

```{r rds-3, exercise = TRUE}

```

```{r rds-3-hint, eval = FALSE}
read_rds(file = "test_1.rds")
```

###

Plots are just one example of what we can store in and .rds file. Let's now try to store the dataset `mtcars`.

### Exercise 4

Consider the following dataset.

```{r}
glimpse(mtcars)
```

###

Use `write_rds()` to save `mtcars` to a file named `test_2.rds`.

```{r rds-4, exercise = TRUE}

```

```{r rds-4-hint-1, eval = FALSE}
The first argument should be the object you want to save. 
The second argument should be the name you want the 
file saved as.
```

```{r rds-4-hint-2, eval = FALSE}
write_csv(mtcars, "test_2.rds")
```

###

You are not limited to just one object in an .rds file. You can save multiple!


### Exercise 5

```{r ex-5-rds-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_2.rds"), ".")
```

Run `list.files()`. You should see your newly created file listed.

```{r ex-5-rds, exercise = TRUE}

```

###

Your result should look like include two files: `exercise.Rmd`, which is a file used by the **learnr** package and `test_2.rds`, which is the file you created.



### Exercise 6

```{r rds-6-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_2.rds"), ".")
```

Great. Let's now use `read_rds()` to read in the newly created file! Set the `file` argument to "test_2.rds".

```{r rds-6, exercise = TRUE}

```

## JSON files 
###

```{r json-1-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_1.json"), ".")
```

Consider the file `test_1.json`, which is in JSON format. 


```{r}
# cat(readLines(paste0(system.file("www/", 
#                                  package = "primer.tutorials"), 
#                      "test_1.json")), 
#     sep = "\n")
```

###


### Exercise 1

Write code for reading this JSON file into R as a tibble. Use the `fromJSON()` function from the **jsonlite** package.

```{r json-1, exercise = TRUE}

```

```{r json-1-hint, eval = FALSE}
fromJSON("test_1.json")
```


### Exercise 2

```{r json-2-setup}
file.copy(paste0(system.file("www/", package = "primer.tutorials"), 
                 "test_2.json"), ".")
```

Consider the file `test_1.json`, which contains a tibble.


```{r}
# cat(readLines(paste0(system.file("www/", 
#                                  package = "primer.tutorials"), 
#                      "test_2.json")), 
#     sep = "\n")
```

###


Write code for reading the file so it converts the tibble into JSON format. Use the `toJSON()` function from the **jsonlite** package.

```{r json-2, exercise = TRUE}

```

```{r json-2-hint, eval = FALSE}
fromJSON("test_2.json")
```



## Parsing Functions 
###

`parse_*()` functions take a character vector and return a more specialized vector such as a logical, integer, or date.

<!-- 10 questions here -->


## Messy Test Files 
###

<!-- add a three CSV files, each with four annoying columns, meaning columns that by default parse incorrectly. The usual trick is to force R to read in these columns as character and then parse. -->





## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```
