---
title: "Rubin Causal Model: Shaming"
author: Sophia Zhu
tutorial:
  id: rubin-causal-model-shaming
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: "Exploring a data set involving attempts to get-out-the-vote in Michigan."
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(skimr)
library(gt)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

<!-- THE STUDENT DID NOT READ THE CHAPTER! -->

<!-- You can't drop knowledge about the line of code. The code is easy! So, drop knowledge about the Chapter. -->

<!-- Write and answer written question.  -->

<!-- fix wonky "" marks -->

<!-- check `` marks -->

<!-- RELOCATION -->

<!-- leftjoin  -->



## Table of outcomes and covariates
###

The tibble `shaming` from the **primer.data** package includes data from "Social Pressure and Voter Turnout: Evidence from a Large-Scale Field Experiment" ([pdf](https://github.com/PPBDS/primer.data/blob/master/inst/papers/shaming.pdf)) by Gerber, Green, and Larimer (2008). The aim of the study was to explore to what extent people are motivated to vote by social pressure. 

###

Using the data, we'll be making this table to find how the treatment 'Neighbour' impacts the amount of people who vote (primary_06).

```{r}
tibbleone <- tibble(ID = c("1", "3", "10", "48", "51", "68", "198", "323", "875", "338640"),
       ycivic = c("0","?", "?", "?","1", "?", "?","?", "?","?"),
       yhawth = c("?", "1","?", "0", "?","?","?","?", "?","?"),
       yself = c("?","?", "?", "?","?","0","1", "?", "?","?"),
       yneigh = c("?","?", "?", "?","?","?", "?","?", "1","0"),
       ycontrol = c("?", "?","0", "?","?", "?","?", "1", "?", "?"),
       Age = c("65", "55","39", "53", "38 ", "56","46", "56", "47", "72"),
       Sex = c("Male", "Male", "Male", " Male", "Female", 
               "Female", "Female", "Male", "Female", "Male")) %>% 

  
  gt() %>%   
  
    # Adding curly braces { } allows the entire word (i.e. civic, hawth, etc) to
    # be subscript. If we did not use the curly braces, only the first letter
    # would be subscript, which we do not want.
  
    cols_label(ycivic = md("Y<sub>civic</sub>"),
               yhawth = md("Y<sub>hawth</sub>"),
               yself = md("Y<sub>self</sub>"),
               yneigh = md("Y<sub>neigh</sub>"),
               ycontrol = md("Y<sub>control</sub>")) %>% 
    tab_spanner(label = "Outcomes", c(ycivic, yhawth, yself, 
                                         yneigh, ycontrol)) %>% 
    tab_spanner(label = "Covariates", c(Age, Sex))
```


### Exercise 1

Load in libraries **tidyverse**, **gt**, and **skimr**.

```{r shaming-ex-1, exercise = TRUE}

```

```{r shaming-ex-1-hint, eval = FALSE}

```

###

The experimenters sent 5 different postcards to all the voters in Michigan before the 2006 primary election. They wanted to understand if certain types of messages increase voter turnout.

### Exercise 2

Run `glimpse()` into the data set `shaming`.

```{r shaming-ex-2, exercise = TRUE}

```

```{r shaming-ex-2-hint, eval = FALSE}
glimpse(shaming)
```

###

The first postcard was named "Civic Duty", contained a letter "to do their civic duty and vote". The second postcard was named "Hawthorne" which contained the same letter, as well as a notice  that they were being studied by researchers. The third postcard "Self" contained everything in the Hawthorn postcard, and added a message which said that every household member would be notified of each others' voting behaviors. The last postcard "Neighbors" would list not only the voting behavior of household members, but also voting records of people nearby. 

### Exercise 3

Try out `?shaming` to compare it to `glimpse(shaming)`

```{r shaming-ex-3, exercise = TRUE}

```

```{r shaming-ex-3-hint, eval = FALSE}
?shaming
```

###

Notice how `?shaming` gives you an explanation of the experiment, and each column! It can also tell you the column type and number of empty rows. 

###

For your reference, this is row 1 of the `shaming` data set

``` {r}
shaming %>% 
  slice(1)  
```

### Exercise 4

Type `tibble(ID = "1")` in order to create the start of the pipe which we will build into the Preceptor Table which we showed you above. The number 1 is the way that we will refer to the first person in the table, since we do not know their name.


```{r shaming-ex-4, exercise = TRUE}
 
```

```{r shaming-ex-4-hint, eval = FALSE}
tibble(ID = "1")
```

###

For review, you can find the basics of `gt()` [here](https://gt.rstudio.com/articles/intro-creating-gt-tables.html).

### Exercise 5

Create another column in your tibble by adding `, ytreat = "0"` after `ID = "1"`.


```{r shaming-ex-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-ex-5-hint, eval = FALSE}
tibble(ID = "1",
       ytreat = "0")

```

###

ytreat is the column where we input whether or not they voted (primary_06), *if they were apart of one of the treatment groups*. If person 1 was part of the control group, we would list a "?" in the ytreat column, since we do not know whether they would have voted. 

Also notice how primary_06 only has two answers, 0 and 1. 0 means that they did not vote, while 1 means that they did. 

### Exercise 6

Add a new column named `ycontrol`. Set the value of `ycontrol` to '?'.

```{r shaming-ex-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-ex-6-hint, eval = FALSE}
tibble(ID = ("1"),
       ytreat = "0",
       ycontrol = "?")
```

###

The ? in the ycontrol column is because of the Fundamental Problem of Causal Inference. Since we are already observing one potential outcome (Person 1 is given a treatment postcard), we can not also see the other potential outcome (Person 1 is given a control postcard). 

### Exercise 7

Let's add Person 10 into the tibble. Use `c()` to add more than one number into the column. Notice how this is a control group. How will this change the entry? 

```{r shaming-ex-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-ex-7-hint-1, eval = FALSE}
Remember to use c("..", "...") if you want to add more than 
1 number in each column.
```

```{r shaming-ex-7-hint-2, eval = FALSE}
tibble(ID = c("1","10"),
       ytreat = ("0", "?"),
       ycontrol = ("?", "0"))
```

###

Your table should look like this. 
```{r}
tibble(ID = c("1","10"),
       ytreat = c("0", "?"),
       ycontrol = c("?", "0"))
```

### Exercise 8

Expand your tibble by adding Person 313, 875, and 344084. Pipe `gt()` at the end to make it a gt table. 

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-ex-8, exercise = TRUE}

```

For your reference, here are the rows 

``` {r}
shaming %>% 
  mutate(row_number = row_number()) %>% 
  filter(row_number == "323" | row_number == "875" | row_number == "344084") %>% 
  relocate(row_number)
```


```{r shaming-ex-8-hint-1, eval = FALSE}
`View(shaming)` will let you see all the data.
```

```{r shaming-ex-8-hint-2, eval = FALSE}
tibble(ID = c("1", "10", "323", "875", "344084"),
       ytreat = c("0", "?", "?", "1", "?"),
       ycontrol= c("?", "0", "1", "?", "1")) %>% 
  gt()
```

###
`View(shaming)` would have also allowed you to see all the `shaming` data.

Your table should look like this.

```{r}
tibble(ID = c("1", "10", "323", "875", "344084"),
       ytreat = c("0", "?", "?", "1", "?"),
       ycontrol= c("?", "0", "1", "?", "1")) %>% 
  gt()
```

### Exercise 9

Add columns "age" and "sex" to the tibble. Use the data from the table to fill in the rows accordingly.

```{r shaming-ex-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-ex-9-hint, eval = FALSE}
tibble(.... 
       age = c("65","39"), 
       sex = c("Male","Male"))
```

###

Age and sex are covariants, variables which could *possibly* influence whether a person votes or not. Other examples of covariants include income, and whether they voted in the previous election. 

<!-- Edit primer, add definition of covariants -->

### Exercise 10

We want to separate the covariants from the outcome data. Use `tab_spanner()` to create an overarching title. Set label = "Outcomes", and have it contain the columns ytreat and ycontrol.
```{r shaming-ex-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-ex-10-hint-1, eval = FALSE}
It should be placed after the gt(). Continue the pipe with %>% before adding in your commands. 
```

```{r shaming-ex-10-hint-2, eval = FALSE}
tibble(....) %>% 
  gt() %>% 
  tab_spanner(label = "Outcomes", c(..., ...))
```

###

Your table should look like this
```{r}
tibble(ID = c("1", "10", "323", "875", "344084"),
       ytreat = c("0", "?", "?", "1", "?"),
       ycontrol= c("?", "0", "1", "?", "1"),
       Age = c("65", "39", "56", "47", "57"),
       Sex = c("Male", "Male", "Male", "Female", "Female")) %>% 
 
   gt() %>% 
     
   tab_spanner(label = "Outcomes", c(ytreat, ycontrol))
```


### Exercise 11

Use `tab_spanner()` to create another overarching title. Set the label = "Covariants", and include columns age and sex
```{r table-of-outcomes-an-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r table-of-outcomes-an-11-hint, eval = FALSE}
tibble(....) %>% 
  gt() %>% 
  tab_spanner(label = "Outcomes", c(..., ...)) %>% 
  tab_spanner(label = "Covariants", c(age, sex))
```

###

If you want more info on gt functions that help with formatting/style, click [here](https://gt.rstudio.com/reference/index.html). 

### Exercise 12

To be more specific about which treatment each person got, replace the column "ytreat" with the four different treated categories: "Civic Duty", "Hawthorne", "Self", and "Neighbors". Call the column "ycivic", "yhawth", "yself", and "yneigh". Change entries as necessary. 

<!-- Make these into several questions; one for each treatment. directly give them the code for ycivic -->

```{r shaming-ex-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-ex-12-hint-1, eval = FALSE}
Assume Person 20 was part of treatment "Civic" Keep them under the same tab spanner

```

```{r shaming-ex-11-hint-2, eval = FALSE}
tibble(ID = c("1", "10", "323", "875", "344084"),
       ycivic = c("...","...","...","...","..."),
       yhawth = c("...", "...","...","...","..."),
       ycontrol= c("?", "0", "1", "?", "1"), ...
....
```
###

Your table should look something like this
```{r}
tibble(ID = c("1","10", "323", "875", "338640"),
       ycivic = c("0", "?","?", "?","?"),
       yhawth = c("?","?","?", "?","?"),
       yself = c("?", "?", "?", "?","?"),
       yneigh = c("?", "?", "?", "1","0"),
       ycontrol = c("?","0", "1", "?", "?"),
       Age = c("65","39", "56", "47", "72"),
       Sex = c("Male", "Male", "Male", "Female", "Male")) %>% 

  
  gt() %>%   


    tab_spanner(label = "Outcomes", c(ycivic, yhawth, yself, 
                                         yneigh, ycontrol)) %>% 
    tab_spanner(label = "Covariates", c(Age, Sex))
```

### Exercise 13

Format these variables to look more professional by changing ycivic into $\sf{Y_{civic}}$ using `cols_label()`, and using `<sub>`. Window users may have issues with this function, if it isn't working, feel free to skip this part. 

<!-- Separate this into two questions. One for ycivic, code is given, one for the rest. -->

```{r shaming-ex-13, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-ex-13-hint-1, eval = FALSE}
... %>%
cols_label(columnname = md("inserttext<sub>insertsubscripttext</sub>")
```

```{r shaming-ex-13-hint-2, eval = FALSE}
... %>%
cols_label(ycivic = md("Y<sub>civic</sub>"),
               yhawth = md("Y<sub>hawth</sub>")....
```

###

Use `?gt::md` if you want more info about the `md()` function. Helps with converting text into t R Markdown-formatted text. Super useful for things like footnotes, fonts, currency, and more. 

### Exercise 14

Add Person 3, 48, 51, 68 and 198 into the table! Fill in each column as necessary.  

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-ex-14, exercise = TRUE}

```

For your reference, the rows look like this: 

```{r}
shaming %>% 
  mutate(row_number = row_number()) %>% 
  filter(row_number == "3" | row_number == "48" | row_number == "51" | row_number == "68" | row_number == "198") %>% 
  relocate(row_number)
```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-ex-14-hint, eval = FALSE}

```

###

Your table should look like this 
```{r}
tibbleone 
```

### 

You can also add a title using `tab_header()`. I propose the title "WOO! Peer pressure works wonders." Good job with this section!


## Explaining shaming

### Exercise 1
Write a paragraph that explain the shaming experiment in the context of the Rubin Causal Model. The first paragraph should use these terms: “unit,” “treatment,” “outcome,” “potential outcomes,” “casual effect,” “assignment mechanism,” and “heterogeneous treatment effects.” Do not discuss “Preceptor Tables.”  
<!-- ** this can be broken down even further -->

```{r written-ex-1}
question_text(NULL,
	message = "The shaming experiment consists of dividing the population of Michigan residents who voted in the 2004 general election into five parts. The *units* were Michigan individual voters. Half the residents were assigned to one of 5 possible *treatments*: being mailed one of four post card types or, the *control group*, being mailed nothing. The *assignment mechanism* by which the authors choose who received which post cards was random assignment. Each card contained different messages about voting. The *outcome* variable was voting (1) or not voting (0) in the 2006 primary election. Relative to the control, the largest *causal effect* --- the largest difference between the probability of voting --- was for the 'Neighbors' treatment. The causal effect of sending someone a Neighbors postcard was an increase in 8% in their likelihood of voting relative to what it would have been with no postcard. However, the treatment effect was not the same for all groups in our study population, in other words there were *heterogeneous treatment effects*. For example, the treatment effect was smaller in younger people.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 2

Discuss 'population.' For context, imagine you are running for governor in Indiana 2022, and you are trying to decide if this experiment is relevant to your campaign. Use the terms “representative” and “validity.”
```{r explaining-shaming-ex-2}
question_text(NULL,
	message = "If I was running for governor in Indiana 2022, I would hesitate to use the experimental data. The outcome of the experiment is not relevant to my campaign. That is, it is not *valid* for my purposes. The goal is to win the election, yet the experimental data is about getting people to vote. I do not care if a postcard causes someone to vote who otherwise would not have voted. I want to cause people to vote for me! In addition, the *representativness* of the sample is a concern. The sample includes only Michigan voters, which may not be useful for making inferences about Indiana voters. In other words, the population for the study we have here does not look like the population we would have in 2022.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 3

<!-- Insert q about ate, and potentially something about necessity of assumptions -->
<!-- Meaning of ATE for which group, how many do you think we need, something along those lines  -->
<!-- or don't even need q, just drop it along the way -->
<!-- ** smoething abotu 2 sentences about ATE, go further in depth later in descript -->
```{r explaining-shaming-ex-3}
question_text(NULL,
	message = "answer here",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

###

## One ATE

###

We will create a tibble with one ATE (average treatment effect), which looks like this:

``` {r}
object_1 <- shaming %>% 
  filter(treatment %in% c("Neighbors", "Control")) %>% 
  
  # Group by treatment so summarize() does not take the average of all 
  # treatments together, but instead for each individual treatment individually.
  
  group_by(treatment) %>% 
  summarize(avg.percent = mean(primary_06), .groups = "drop")  %>%

  # Use pivot_wider() to have the columns take the name of each treatment. Better
  # to visualize the avg.percent values this way.
  
  pivot_wider(names_from = treatment,
              values_from = avg.percent) %>%
  
  
  # Lastly, creating a column for the ATE values. Note that the tibble is already
  # grouped by treatment so we do not need to do it here.
  
  mutate(ATE = Neighbors - Control) %>% 
  relocate(Neighbors) 
  

object_1
```

###

The purpose of this tibble is to estimate the ATE to see how the treatment "Neighbor" compares to the control. 
 
### Exercise 1

Start a new pipe with shaming, and `filter()` it to find the value of control and neighbors within treatment 

```{r object-ex-1, exercise = TRUE}

```

```{r object-ex-1-hint-1, eval = FALSE}
Use %in% and c()
```

```{r object-ex-1-hint-2, eval = FALSE}
shaming %>% 
  filter(treatment %in% c("...","..."))
```

###

Data science is mostly filtering out all the important parts of a data set, helping you analyze it. The main purpose is to remove values which contain errors, or anything unnecessary.  


### Exercise 2

Now let's `group_by` treatment 

```{r object-ex-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r object-ex-2-hint, eval = FALSE}
... %>% 
group_by(treatment) %>% 

```

###  
Group by treatment so summarize() does not take the average of all treatments together, but instead for each individual treatment individually.

### Exercise 3

Create a new column called avg.percent using `summarize()`. Set the first input to the mean of `primary_06`, and set .groups equal to "drop". 

<!-- SZ: How do i phrase this? -->

```{r object-ex-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r object-ex-3-hint, eval = FALSE}
... %>%  
summarize(avg.percent = mean(primary_06), .groups = "drop")
```

###

Recall that we don't want every single person in the data set, we just want to see the general trends. 

### Exercise 4

Use `pivot_wider()` to make the table look better. Set `names_from` to treatment, and `values_from` to avg.percent
```{r object-ex-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r object-ex-4-hint, eval = FALSE}
... %>% 
pivot_wider(names_from = ...., 
            values_from = ....)
```

###

Details matter! `pivot_wider()` ensures that the table is easier to look at, by displaying all the data in one row, rather than multiple. This is the opposite of `pivot_longer()`, but is clearly superior. 

### Exercise 5

Create a new column using `mutate` called ATE. 
```{r object-ex-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r object-ex-5-hint-1, eval = FALSE}
ATE = Difference between treated group and control group
```

```{r object-ex-5-hint-2, eval = FALSE}
... %>% 
mutate(ATE = Neighbour - Control) 
```

###

Remember that ATE is the average treatment effect, and in this tibble, it shows that using the neighbor treatment increases voting by 0.0813! WOW!

### Exercise 6

Use `relocate()` to put the neighbor column in front of control. This syntax is `relocate(column1, .after = column you want to put in front of column1)`. Once you're finished, save the tibble to 'object_1'.
```{r object-ex-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r object-ex-6-hint-1, eval = FALSE}
... %>% 
relocate(Control, .after = Neighbors)
```

###
 
This makes the table clearer, since the way you calculate ATE is Neighbors - Control, rather than Control - Neighbors. 

## Multiple ATE

In this table, our goal is to see how each treatment compares to the other, by showing the ATE! This is the table we want to recreate. 

``` {r}
results <- shaming %>% 
  group_by(treatment) %>% 
  summarize(avg.vote = mean(primary_06), 
            .groups = "drop")
 
# crossing() and unique() are functions that might be useful. unique() returns a
# the unique values in a vector.

object_2 <- crossing(treatment = unique(shaming$treatment), 
         control = unique(shaming$treatment)) %>%
  filter(! treatment==control) %>% 
  left_join(results, by = "treatment") %>% 
  left_join(results, 
            by = c("control" = "treatment"), 
            suffix = c(".treatment", ".control")) %>% 
  mutate(ATE = avg.vote.treatment - avg.vote.control)

object_2
```


### Exercise 1

Start a new pipe with the data set `shaming`, and `group_by()` treatment

```{r objecttwo-ex-1, exercise = TRUE}


```


```{r objecttwo-ex-1-hint, eval = FALSE}
shaming %>% 
group_by(treatment)

```

###

`group_by()` can be undone by using `ungroup()`. 

<!-- SZ: is this necessary? Didn't know what else to put-->

### Exercise 2

Use `summarize` with the mean of primary_06, and save it to 'avg_vote'. Set `.groups` to "drop". When finished, save this as `results`

```{r objecttwo-ex-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objecttwo-ex-2-hint, eval = FALSE}
... %>% 
summarize(avg_vote = mean(...), 
          .groups = "drop")

```

###

### Exercise 3

Start a new pipe. Using `crossing()`, we want to find all the different possible pairs between treatment types. Within `crossing()`, put shaming$treatment to grab all treatments. 

<!-- SZ: too direct? -->
```{r objecttwo-ex-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objecttwo-ex-3-hint-1, eval = FALSE}
... %>% 
crossing(treatment = (...$...), 
         control = (...$...)) 
```

```{r objecttwo-ex-3-hint-2, eval = FALSE}
... %>% 
crossing(treatment = (shaming$treatment), 
         control = (shaming$treatment)) 
```

###

Notice how row 1 has Control in both treatment and control. Same thing happens with Civic Duty. Let's change that.


### Exercise 4

Put shaming$treatment inside of `unique()`. This ensures that both columns will not have the same thing. 

<!-- Change wording --> 

```{r multiple-ate-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r multiple-ate-4-hint, eval = FALSE}
... %>% 
crossing(treatment = unique(shaming$treatment), 
         control = unique(shaming$treatment))
```

###

Your table should look like this
```{r}
crossing(treatment = unique(shaming$treatment), 
         control = unique(shaming$treatment))
```

<!-- Does not show a unique table, will need to fix  -->

### Exercise 5

`filter()` results so that anything in the treatment column is not equal to anything in the control column. 
```{r objecttwo-ex-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objecttwo-ex-5-hint-1, eval = FALSE}
... %>%   
filter(! ...==...)
```

```{r objecttwo-ex-5-hint-2, eval = FALSE}
... %>%   
filter(! treatment==control)
```

###

`!=` is typically the way to symbolize "is not equal to". This also applies to various other languages, such as Python, Java, and C. Comes from the symbol $≠/$ in math. 
 
### Exercise 6

Use `left_join()' to join `results` by "treatment".

```{r objecttwo-ex-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objecttwo-ex-6-hint-1, eval = FALSE}
 ... %>%  l
left_join(..., by = "...")

```

```{r objecttwo-ex-6-hint-2, eval = FALSE}
... %>% 
left_join(results, by = "treatment")
```
###

Typically, `left_join()` is done using two tibbles from the same data source. If left empty, it will automatically join if they end up having two columns with the same name. Introduce suffixes. 

### Exercise 7

Use `left_join()` again to join 'results' by  

join results again, now further niching down to avg.vote.treatment and avg.vote.control

<!-- phrase this better + add other hint -->

```{r objecttwo-ex-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objecttwo-ex-7-hint, eval = FALSE}
... %>% 
left_join(results, 
            by = c("control" = "treatment"), 
            suffix = c(".treatment", ".control"))
```

###

### Exercise 8

Using `mutate` to create the column ATE. Save your code to 'object_2'
```{r objecttwo-ex-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objecttwo-ex-8-hint-1, eval = FALSE}
ATE = Difference between treated group and control group
```

```{r objecttwo-ex-8-hint-2, eval = FALSE}
mutate(ATE = avg.vote.treatment - avg.vote.control)
```
###

Notice how there are can be mutiple ATEs. Before, we were finding the ATE of Control and Neighbor, but now we're finding the ATE of each treatment pair. This can be further niched down, such as the ATE of each gender, each age group, etc. 

## Percentage ATE

For our last table, We will investigate whether the causal effect of Neighbors relative to Control is the same for older and younger people.'Old people' is anyone older than 64.

``` {r}
object_3 <- shaming %>% 
  filter(treatment %in% c("Neighbors", "Control")) %>% 

  # Here, we use an ifelse() statement here to return "old" in the rows where
  # age is 64 # or older, and "young" elsewhere.
  
  mutate(age = ifelse(age > 64, "old", "young")) %>% 

  # Group by treatment AND age here so the avg.percent values are calculated for
  # "old" and "young" separately.
  
  group_by(treatment, age) %>% 
  summarize(avg.perc = mean(primary_06),
            .groups = "drop") %>% 
  pivot_wider(names_from = treatment,
            values_from = avg.perc) %>% 
  mutate(ATE = Neighbors - Control) %>% 
  
  # Using rename() to make the column names less confusing. We want to be specific
  # as possible. Having "Control" or "Neighbors" is too confusing.

  rename(c("control.perc" = Control,
           "neighbors.perc" = Neighbors))

object_3
```


### Exercise 1

Start a pipe with `shaming`. Since we want to compare neighbor and control, let's `filter` those variables, which are located `%in%` treatment 
```{r objectthree-ex-1, exercise = TRUE}

```

```{r objectthree-ex-1-hint-1, eval = FALSE}
Filter uses %in% and if you want to filter multiple variables, we use c("...","...")
```

```{r objectthree-ex-1-hint-2, eval = FALSE}
shaming %>% 
  filter(treatment %in% c("...", "...") )
```

###

### Exercise 2

Continue the pipe. Use `mutate` to create a column called age that tells us whether a person is "young" or "old" by checking if they are over 64 (old) or younger or equal to 64 (young).
```{r objectthree-ex-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objectthree-ex-2-hint-1, eval = FALSE}
For if statements, we want to use ifelse. It contains 3 parts within the function: the criteia, what happens if it returns true, and what happens if it returns false.

```

```{r objectthree-ex-2-hint-2, eval = FALSE}
... %>% 
mutate(age =ifelse(age > 64, "...", "..."))
```

###

This syntax is different from other programming languages, which usually split up "if" and "else". 

<!-- SZ: Necessary?  -->

### Exercise 3

`group_by` the data using both treatment and age
```{r objectthree-ex-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objectthree-ex-3-hint, eval = FALSE}
... %>% 
  group_by(treatment, age)
```

###

This allows for values in avg.percent to calculate "old" and "young" separately, which allows for efficiency. 

### Exercise 4

Use `summarize()` to create a new column which contains the mean of primary_06. Set .groups = "drop". 

```{r objectthree-ex-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objectthree-ex-4-hint-1, eval = FALSE}
... %>% 
summarize (avg.perc = mean(...),
            .groups = "drop")
```

```{r objectthree-ex-4-hint-2, eval = FALSE}
... %>% 
summarize (avg.perc = mean(primary_06),
            .groups = "drop")
```

###

<!-- SZ: consider putting something about average percentile -->

### Exercise 5

Using `pivot_wider`, clean up your table. Set the `names_from` to treatment, and `values_from` to avg.perc. 
```{r objectthree-ex-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objectthree-ex-5-hint, eval = FALSE}
... %>%   
pivot_wider(names_from = treatment,
            values_from = avg.perc)
```

###

### Exercise 6

Create a new column with `mutate`, which displays the ATE value between the two different treatment types. 
```{r objectthree-ex-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objectthree-ex-6-hint-1, eval = FALSE}
You calculate the ATE by finding the difference between neighbor and control, the two different treatment types.  
```

```{r objectthree-ex-6-hint-2, eval = FALSE}
... %>% 
mutate(ATE = Neighbors - Control)
```
###

Here, you can see that the ATE has been reduced 

### Exercise 7

Lastly, let's rename column 'Control' to 'control.perc' and column 'neighbor' into 'neighbor.perc'. Save the tibble as object_3. 
```{r objectthree-ex-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objectthree-ex-7-hint-1, eval = FALSE}
... %>% 
rename(c(...))
```

```{r objectthree-ex-7-hint-2, eval = FALSE}
... %>% 
rename(c("control.perc" = Control,
           "neighbors.perc" = Neighbors))
```

###

Using rename() to make the column names less confusing. We want to be as specific as possible. Having "Control" or "Neighbors" is too confusing.

<!-- SWTICH COLUMNS CONTROL AND NEIGHBOR -->


## Age and ATE 

We will be creating this plot, to see the effect of age on the ATE of treatment 'Neighbor'. 

``` {r}
age_p <- shaming %>% 
  filter(treatment %in% c("Neighbors", "Control")) %>% 
  filter(age < 90) %>% 
  
  # We filter here because there are NA values in ages such as 102 that give us a
  # "missing rows" message when we plot our values. The plot also looks nicer this way.

  group_by(treatment, age) %>% 
  summarize(avg.perc = mean(primary_06),
            .groups = "drop") %>% 

  # Using arrange allows us to see show the rows that have the youngest ages 
  # first.
  
  arrange(age) %>% 
  pivot_wider(names_from = treatment,
              values_from = avg.perc) %>% 
  mutate(ATE = Neighbors - Control) %>% 
  rename(c("control.perc" = Control,
           "neighbors.perc" = Neighbors)) %>% 
  ggplot(aes(x = age, y = ATE)) +
    geom_point() +
    geom_smooth(method = "loess",
                formula = y ~ x) +
  
    # Possibly revisit removing the gray area here because confidence intervals have
    # not been discussed yet.
  
    labs(title = "Effect on Voting of Neighbors Postcard",
        subtitle = "Average treatment effect is lower for the young and the very old",
         y = "Average Treatment Effect",
         x = "Age",
         caption = "Source: Gerber, Green, and Larimer (2008)") +
    theme_bw()

age_p
```

### Exercise 1

Start your pipe with `shaming`. `filter()` the data to only see Control and Neighbor in treatment, using `%in%` as part of the code. 

```{r plot-ex-1, exercise = TRUE}

```


```{r plot-ex-1-hint-1, eval = FALSE}
shaming %>% 
  filter(treatment %in% c("...", "..."))
```

```{r plot-ex-1-hint-2, eval = FALSE}
shaming %>% 
  filter(treatment %in% c("Neighbors", "Control"))
```

###

If instead of including just these two types of `treatment`, we could exclude them both with the "not" (!) symbol:  `filter(! treatment %in% c("...", "..."))`.


### Exercise 2

`group_by` the data by treatment and age

```{r plot-ex-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r plot-ex-2-hint, eval = FALSE}
... %>% 
group_by(treatment, age)
```

###

### Exercise 3

Calculate the avg.perc of of each age group by finding the mean of primary_06. Create a new column called "avg.perc" using `summarize` to display the mean. 

```{r plot-ex-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r plot-ex-3-hint, eval = FALSE}
... %>%  
summarize(avg.perc = mean(...),
            .groups = "drop")
```

###

<!-- Importance for avg.perc? -->

### Exercise 4

`arrange()` the data by age. 

```{r shaming-plot-ex-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-plot-ex-4-hint, eval = FALSE}
... %>% 
arrange(age)
```

###

Arrange automatically sorts by ascending. Recall how using `desc()` will sort things in a descending order.

### Exercise 5

Use `pivot_wider` to make the tibble look better. Set `names_from` as treatment and `values_from` to average perc. 
```{r shaming-plot-ex-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-plot-ex-5-hint, eval = FALSE}
... %>% 
pivot_wider(names_from = ...,
              values_from = ...)
```

###

### Exercise 6

Using `mutate`, create a new column called ATE, which has the ATE of treatment neighbor and control. 

```{r shaming-plot-ex-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-plot-ex-6-hint-1, eval = FALSE}
ATE is calculated from subtracting the treatment group from the control group
```

```{r shaming-plot-ex-6-hint-2, eval = FALSE}
... %>% 
  mutate(ATE = Neighbors - Control)
```

###

<!-- knowledge: Since we arranged + group_by... -->

### Exercise 7

Lets `rename` control to `control.perc`, and neighbors to `neighbor.perc`

```{r shaming-plot-ex-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-plot-ex-7-hint, eval = FALSE}
... %>% 
rename(c("control.perc" = Control,
         "neighbors.perc" = Neighbors))
```

###

Your table should look like this 

```{r}
shaming %>% 
  filter(treatment %in% c("Neighbors", "Control")) %>% 

  # We filter here because there are NA values in ages such as 102 that give us a
  # "missing rows" message when we plot our values. The plot also looks nicer this way.

  group_by(treatment, age) %>% 
  summarize(avg.perc = mean(primary_06),
            .groups = "drop") %>% 

  # Using arrange allows us to see show the rows that have the youngest ages 
  # first.
  
  arrange(age) %>% 
  pivot_wider(names_from = treatment,
              values_from = avg.perc) %>% 
  mutate(ATE = Neighbors - Control) %>% 
  rename(c("control.perc" = Control,
           "neighbors.perc" = Neighbors))
```

### Exercise 8

Using ggplot, create a scatterplot with age on the x axis, and ATE on the y axis. 

```{r shaming-plot-ex-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-plot-ex-8-hint, eval = FALSE}
... %>% 
ggplot(aes(x = ..., y = ...)) +
    geom_point() 
```

### Exercise 9

Let's add a regression line using `geom_smooth`. Set method to "loess", and formula  to y ~ x 
```{r shaming-plot-ex-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-plot-ex-9-hint, eval = FALSE}
geom_smooth(method = "loess", formula = y ~ x)
```

###
R does automatically set the parameters of method and formula to 'loess' and 'y ~ x' respectively, however it is always nice to add them in. Additionally, this will show our confidence interval, which shows the range of possible ATE values

<!-- SZ: Advice for describing confidence interval? -->

### Exercise 10

Adjust the feel of the graph by adding the `theme_bw()`. To finish your plot, use labs() to give the graph a title, subtitle, axes labels, legend heading, and caption.

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-plot-ex-10, exercise = TRUE}

```

```{r shaming-plot-ex-10-hint, eval = FALSE}
labs(title = "..."
     ....) +
  theme_bw()
```


Your graph should look like this 

```{r}
shaming %>% 
  filter(treatment %in% c("Neighbors", "Control")) %>% 

  # We filter here because there are NA values in ages such as 102 that give us a
  # "missing rows" message when we plot our values. The plot also looks nicer this way.

  group_by(treatment, age) %>% 
  summarize(avg.perc = mean(primary_06),
            .groups = "drop") %>% 

  # Using arrange allows us to see show the rows that have the youngest ages 
  # first.
  
  arrange(age) %>% 
  pivot_wider(names_from = treatment,
              values_from = avg.perc) %>% 
  mutate(ATE = Neighbors - Control) %>% 
  rename(c("control.perc" = Control,
           "neighbors.perc" = Neighbors)) %>% 
  ggplot(aes(x = age, y = ATE)) +
    geom_point() +
    geom_smooth(method = "loess",
                formula = y ~ x) +
  
    # Possibly revisit removing the gray area here because confidence intervals have
    # not been discussed yet.
  
    labs(title = "Effect on Voting of Neighbors Postcard",
        subtitle = "Average treatment effect is lower for the young and the very old",
         y = "Average Treatment Effect",
         x = "Age",
         caption = "Source: Gerber, Green, and Larimer (2008)") +
    theme_bw()
```

###

However, notice the right hand side of the graph, starts behaving strangely past ~90, and how there are error messages which show up.


### Exercise 11

`filter()` the data so that only people younger than 90 are included in the data. 
```{r age-and-ate-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r age-and-ate-11-hint, eval = FALSE}
... %>% 
filter(age < 90) %>% 
... 
```

###

We need to do this because there is a lot of missing data when for older ages, and the sample size for each age group (Ex. there is only one person who is 103 years old), skewing the results. 

###

Your graph should look like this
```{r}
age_p
```


Good job, you made it through. I'm proud of you buddy :)


```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
