---
title: "Rubin Causal Model: Shaming (draft)"
tutorial:
  id: rubin-causal-model-shaming
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: "Exploring a data set involving attempts to get-out-the-vote in Michigan."
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(skimr)
library(gt)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

<!-- CHECKLIST BEFORE STARTING: -->
<!-- * Load necessary libraries for tutorial in the first code chunk -->
<!-- * Edit yaml at the START OF THIS FILE -->
<!-- * Review: https://ppbds.github.io/primer.tutorials/articles/instructions.html -->


<!-- ## First section (use sentence case) -->
<!-- ### Exploratiry data analysis, check three parameters for future reference -->
<!-- Let's look at the help page! (?shaming)   -->
<!-- then drop frmo more knowedlge  -->
<!-- wrangling more plots AS REFERENCE  -->

## Shaming


<!-- what's giong on?? tell me more on why I should care -->

The tibble `shaming` from **primer.data** includes data from "Social Pressure and Voter Turnout: Evidence from a Large-Scale Field Experiment" by Gerber, Green, and Larimer (2008). The aim of the study was to find out whether and to what extent people are motivated to vote by social pressure. We'll be building 1 table, several written answers, 3 tibbles,  and one plot. Should take ~ 3 hours. 

###

Using the data, we'll be making this table. 

```{r}
tibble(ID = c("1", "3", "10", "48", "51", "68", "198", "323", "875", "338640"),
       ycivic = c("0","?", "?", "?","1", "?", "?","?", "?","?"),
       yhawth = c("?", "1","?", "0", "?","?","?","?", "?","?"),
       yself = c("?","?", "?", "?","?","0","1", "?", "?","?"),
       yneigh = c("?","?", "?", "?","?","?", "?","?", "1","0"),
       ycontrol = c("?", "?","0", "?","?", "?","?", "1", "?", "?"),
       Age = c("65", "55","39", "53", "38 ", "56","46", "56", "47", "72"),
       Sex = c("Male", "Male", "Male", " Male", "Female", 
               "Female", "Female", "Male", "Female", "Male")) %>% 

  
  gt() %>%   
  
    # Adding curly braces { } allows the entire word (i.e. civic, hawth, etc) to
    # be subscript. If we did not use the curly braces, only the first letter
    # would be subscript, which we do not want.
  
    cols_label(ycivic = md("Y<sub>civic</sub>"),
               yhawth = md("Y<sub>hawth</sub>"),
               yself = md("Y<sub>self</sub>"),
               yneigh = md("Y<sub>neigh</sub>"),
               ycontrol = md("Y<sub>control</sub>")) %>% 
    tab_spanner(label = "Outcomes", c(ycivic, yhawth, yself, 
                                         yneigh, ycontrol)) %>% 
    tab_spanner(label = "Covariates", c(Age, Sex))
```


### Exercise 1

Load in libraries **tidyverse**, **gt**, and **skimr**.

```{r shaming-ex-1, exercise = TRUE}

```

```{r shaming-ex-1-hint, eval = FALSE}

```


### Exercise 2

Run `glimpse()` into the data set `shaming`.

```{r shaming-ex-2, exercise = TRUE}

```

```{r shaming-ex-2-hint, eval = FALSE}
glimpse(shaming)
```

###

You can see info within the dataset presented through various means, such as `glimpse(shaming)`, `shaming`, `summary(shaming)`, `skim(shaming)`, `View(shaming)`, and `?shaming`. The commands have been ordered from least info to most info.


### Exercise 3

Try out `?shaming` to compare it to `glimpse(shaming)`
```{r shaming-ex-3, exercise = TRUE}

```

```{r shaming-ex-3-hint, eval = FALSE}
?shaming
```

###

There's much more info when using ?shaming instead of glimpse(shaming). Try out the different commands when you get new data sets in later exercises.
  
  
### Exercise 4

Start a gt table by creating a `tibble()` with 1 variable called ID. This will contain our row number. Let's add a 1 to symbolize row 1. 
```{r shaming-ex-4, exercise = TRUE}

```

```{r shaming-ex-4-hint, eval = FALSE}
tibble(ID = ("1"))
```

###
### Exercise 5

Let's continue the table and add column ytreat. We can see that in row one, it contains treatment "Civic Duty", and has a primary_06 of 0. Since it isn't a control treatment, and has a value of 0, we will add 0 as the ytreat.  add something that says that primary_06 is whether they voted or not
```{r shaming-ex-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-ex-5-hint, eval = FALSE}
tibble(ID = ("1"),
       ytreat = ("..."))

```

###

### Exercise 6

Now add column ycontrol. With row 1, notice how we are apart of one of the treatments, and are not a control group. Thus, we set control as ?
```{r shaming-ex-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-ex-6-hint, eval = FALSE}
tibble(ID = ("1"),
       ytreat = ("..."),
       ycontrol = ("..."))
```

###
<!-- TALK ABOUT THE FOUR DIFFERENT OPTIONS  -->
This goes back to the Fundamental Problem of Causal Inference, where we can not see the result of control on this group, since we are already doing a treatment. We can only o bserve one potential outcome, which is the effect of Civic Duty on voting. 

### Exercise 7

Let's add a new entry, using row 10. Notice how this is a control group. How will this change the entry? 
```{r shaming-ex-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-ex-7-hint-1, eval = FALSE}
Remember to use c("..", "...") if you want to add more than 1 number in each column
```
```{r shaming-ex-7-hint-2, eval = FALSE}
tibble(ID = c("1","10"),
       ytreat = ("...", "?"),
       ycontrol = ("...", "0"))
```
###

Your table should look like this. 
```{r}
tibble(ID = c("1","10"),
       ytreat = c("0", "?"),
       ycontrol = c("?", "0"))
```

### Exercise 8

Add in entries for row 323, 875, and 344084. We should also make it look pretty by piping `gt()` at the end 
```{r shaming-ex-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-ex-8-hint-1, eval = FALSE}
View(shaming) will let you see the whole table
```
```{r shaming-ex-8-hint-2, eval = FALSE}
add code
```
###
Your table should look like this 

```{r}
tibble(ID = c("1", "10", "323", "875", "344084"),
       ytreat = c("0", "?", "?", "1", "?"),
       ycontrol= c("?", "0", "1", "?", "1")) %>% 
  gt()
```

### Exercise 9

Next, let's add age and sex as columns. Fill in the rows accordingly.

```{r shaming-ex-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-ex-9-hint, eval = FALSE}
tibble(.... 
       age = c("...","..."), 
       sex = c("...","..."))
```

###

Age and sex are called covariants.. drop more knowledge 

### Exercise 10

To really emphasize this, let's split these into two sections using `tab_ spanner()`. One should be called Outcomes, and contain the columns ytreat and ycontrol, while the other tabspanner will be called Covariates, and contain the columns age and sex.
```{r shaming-ex-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-ex-10-hint-1, eval = FALSE}
It should be placed after the gt(). Continue the pipe with %>% before adding in your commands. 
```
```{r shaming-ex-10-hint-2, eval = FALSE}
tibble(....) %>% 
  gt() %>% 
  tab_spanner(label = "...", c(..., ...)) %>% 
  tab_spanner(label = "...", c(..., ...))
```

###
Your table should look like this
```{r}
tibble(ID = c("1", "10", "323", "875", "344084"),
       ytreat = c("0", "?", "?", "1", "?"),
       ycontrol= c("?", "0", "1", "?", "1"),
       Age = c("65", "39", "56", "47", "57"),
       Sex = c("Male", "Male", "Male", "Female", "Female")) %>% 
 
   gt() %>% 
     
   tab_spanner(label = "Outcomes", c(ytreat, ycontrol)) %>% 
   tab_spanner(label = "Covariates", c(Age, Sex))   
```

### Exercise 11

Let's get a bit more specific, let's breakdown ytreated in the four different treated categories: Civic Duty, Hawthorne, Self and Neighbors. Change entries as necessary. 

```{r shaming-ex-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-ex-11-hint-1, eval = FALSE}
Replace the column ytreat with columns ycivic, yhawth, yself, yneigh. Keep them under the same tab spanner

```
```{r shaming-ex-11-hint-2, eval = FALSE}
tibble(ID = c("1", "10", "323", "875", "344084"),
       ycivic = c("...","...","...","...","..."),
       yhawth = c("...", "...","...","...","..."),
       ycontrol= c("?", "0", "1", "?", "1"), ...
....
```
###

Your table should look something like this
```{r}
tibble(ID = c("1","10", "323", "875", "338640"),
       ycivic = c("0", "?","?", "?","?"),
       yhawth = c("?","?","?", "?","?"),
       yself = c("?", "?", "?", "?","?"),
       yneigh = c("?", "?", "?", "1","0"),
       ycontrol = c("?","0", "1", "?", "?"),
       Age = c("65","39", "56", "47", "72"),
       Sex = c("Male", "Male", "Male", "Female", "Male")) %>% 

  
  gt() %>%   


    tab_spanner(label = "Outcomes", c(ycivic, yhawth, yself, 
                                         yneigh, ycontrol)) %>% 
    tab_spanner(label = "Covariates", c(Age, Sex))
```

### Exercise 12

Looking nice, but let's change things to look more mathematical by formatting the ytreat columns with mathematical symbols instead. Let's change ycivic into $\sf{Y_{civic}}$ using `cols_label()`. 

```{r shaming-ex-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-ex-12-hint-1, eval = FALSE}
cols_label(columnname = md("text<sub>subscript</sub>")
```
```{r shaming-ex-12-hint-2, eval = FALSE}
cols_label(ycivic = md("Y<sub>civic</sub>"),
               yhawth = md("Y<sub>hawth</sub>")....
```
###

Drop knowledge abotu cols_label and style idk 

### Exercise 13

Nice! Finally, let's add rows 3, 48, 51, 68 and 198 into the table! Fill in each row as neccessary.  
```{r shaming-ex-13, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-ex-13-hint, eval = FALSE}

```

###

Your table should look like this 
```{r}
tibble(ID = c("1", "3", "10", "48", "51", "68", "198", "323", "875", "338640"),
       ycivic = c("0","?", "?", "?","1", "?", "?","?", "?","?"),
       yhawth = c("?", "1","?", "0", "?","?","?","?", "?","?"),
       yself = c("?","?", "?", "?","?","0","1", "?", "?","?"),
       yneigh = c("?","?", "?", "?","?","?", "?","?", "1","0"),
       ycontrol = c("?", "?","0", "?","?", "?","?", "1", "?", "?"),
       Age = c("65", "55","39", "53", "38 ", "56","46", "56", "47", "72"),
       Sex = c("Male", "Male", "Male", " Male", "Female", 
               "Female", "Female", "Male", "Female", "Male")) %>% 
  
  gt() %>%   
  
  
    cols_label(ycivic = md("Y<sub>civic</sub>"),
               yhawth = md("Y<sub>hawth</sub>"),
               yself = md("Y<sub>self</sub>"),
               yneigh = md("Y<sub>neigh</sub>"),
               ycontrol = md("Y<sub>control</sub>")) %>% 
    tab_spanner(label = "Outcomes", c(ycivic, yhawth, yself, 
                                         yneigh, ycontrol)) %>% 
    tab_spanner(label = "Covariates", c(Age, Sex))
```

### 
only feels right to aprt some knowledge about more stuff, talk maybe more about shaming? or about style. 

## Explaining Shaming



### Exercise 1
Write a paragraph that explain the shaming experiment in the context of the Rubin Causal Model. The first paragraph should use these terms: “unit,” “treatment,” “outcome,” “potential outcomes,” “casual effect,” “assignment mechanism,” and “heterogeneous treatment effects.” Do not discuss “Preceptor Tables.”  ** this can be broken down even further

```{r written-ex-1}
question_text(NULL,
	message = "The shaming experiment consists of dividing the population of Michigan residents who voted in the 2004 general election into five parts. The *units* were Michigan individual voters. Half the residents were assigned to one of 5 possible *treatments*: being mailed one of four post card types or, the *control group*, being mailed nothing. The *assignment mechanism* by which the authors choose who received which post cards was random assignment. Each card contained different messages about voting. The *outcome* variable was voting (1) or not voting (0) in the 2006 primary election. Relative to the control, the largest *causal effect* --- the largest difference between the probability of voting --- was for the 'Neighbors' treatment. The causal effect of sending someone a Neighbors postcard was an increase in 8% in their likelihood of voting relative to what it would have been with no postcard. However, the treatment effect was not the same for all groups in our study population, in other words there were *heterogeneous treatment effects*. For example, the treatment effect was smaller in younger people.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	options = list(nrows = 6))
```

### Exercise 2

Discuss 'population.' For context, imagine you are running for governor in Indiana 2022, and you are trying to decide if this experiment is relevant to your campaign. Use the terms “representative” and “validity.”
```{r explaining-shaming-ex-2}
question_text(NULL,
	message = "If I was running for governor in Indiana 2022, I would hesitate to use the experimental data. The outcome of the experiment is not relevant to my campaign. That is, it is not *valid* for my purposes. The goal is to win the election, yet the experimental data is about getting people to vote. I do not care if a postcard causes someone to vote who otherwise would not have voted. I want to cause people to vote for me! In addition, the *representativness* of the sample is a concern. The sample includes only Michigan voters, which may not be useful for making inferences about Indiana voters. In other words, the population for the study we have here does not look like the population we would have in 2022.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	options = list(nrows = 6))
```

###

### Exercise 3

Insert q about ate, and potentially something about necessity of assumptions
Meaning of ATE --> for which group, how many do you think we need, something along those lines 
or don't even need q, just drop it along the way
** smoething abotu 2 sentences about ATE, go further in depth later in descript
```{r explaining-shaming-ex-3}
question_text(NULL,
	message = "answer here",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	options = list(nrows = 6))
```

###



## Object 1
###

###

We will create a tibble which looks like this:

``` {r}
object_1 <- shaming %>% 
  filter(treatment %in% c("Control", "Neighbors")) %>% 
  
  # Group by treatment so summarize() does not take the average of all 
  # treatments together, but instead for each individual treatment individually.
  
  group_by(treatment) %>% 
  summarize(avg.percent = mean(primary_06), .groups = "drop")  %>%

  # Use pivot_wider() to have the columns take the name of each treatment. Better
  # to visualize the avg.percent values this way.
  
  pivot_wider(names_from = treatment,
              values_from = avg.percent) %>%
  
  # Lastly, creating a column for the ATE values. Note that the tibble is already
  # grouped by treatment so we do not need to do it here.
  
  mutate(ATE = Neighbors - Control)

object_1
```

###


 
### Exercise 1

Start a new pipe with shaming, and `filter` it to find the value of control and neighbors within treatment 

```{r object-ex-1, exercise = TRUE}

```

```{r object-ex-1-hint-1, eval = FALSE}
Use %in% and c()
```

```{r object-ex-1-hint-2, eval = FALSE}
shaming %>% 
  filter(treatment %in% c("...","..."))
```

###

### Exercise 2

Now let's `group_by` treatment 

```{r object-ex-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r object-ex-2-hint, eval = FALSE}
  group_by(treatment) %>% 

```

###  
Group by treatment so summarize() does not take the average of all 
treatments together, but instead for each individual treatment individually.

### Exercise 3

Hmm... well we don't care about EVERYBODY, we just care about the general public. Let's reduce the data so we find the mean for people in primary 06
```{r object-ex-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r object-ex-3-hint, eval = FALSE}
 summarize(avg.percent = mean(primary_06), .groups = "drop")
```

###

### Exercise 4

Let's make this a bit cleaner using pivot wider. Set `names_from` to treatment, and `values_from` to avg.percent
```{r object-ex-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r object-ex-4-hint, eval = FALSE}
pivot_wider(names_from = ...., 
            values_from = ....)
```

###


### Exercise 5

Create a new colmun using `mutate` called ATE. 
```{r object-ex-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r object-ex-5-hint-1, eval = FALSE}
ATE = Difference between treated group and control group
```

```{r object-ex-5-hint-2, eval = FALSE}
ATE = Neighbour - Control 
```

###


 
 
## Objecttwo

``` {r}
results <- shaming %>% 
  group_by(treatment) %>% 
  summarize(avg.vote = mean(primary_06), 
            .groups = "drop")
 
# crossing() and unique() are functions that might be useful. unique() returns a
# the unique values in a vector.

object_2 <- crossing(treatment = unique(shaming$treatment), 
         control = unique(shaming$treatment)) %>%
  filter(! treatment==control) %>% 
  left_join(results, by = "treatment") %>% 
  left_join(results, 
            by = c("control" = "treatment"), 
            suffix = c(".treatment", ".control")) %>% 
  mutate(ATE = avg.vote.treatment - avg.vote.control)

object_2
```


### Exercise 1

Start a new pipe with shaming, and group it by treatment

```{r objecttwo-ex-1, exercise = TRUE}

```


```{r objecttwo-ex-1-hint, eval = FALSE}


```

###

### Exercise 2

Once again, we want to focus on primary_06. `Summarize` the avg vote by finding the mean of primary_06. Save this to an object named results

```{r objecttwo-ex-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objecttwo-ex-2-hint, eval = FALSE}
summarize(avg_vote = mean(...), 
          .groups = "drop")

```

###

### Exercise 3

With col treatment and control, find all possible combinations 

```{r objecttwo-ex-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objecttwo-ex-3-hint, eval = FALSE}
... %>% 
crossing(treatment = unique(shaming$treatment), 
         control = unique(shaming$treatment)) 
```

###
### Exercise 4

`Filter` results so that the group in treatment is not the same as the one in control
```{r objecttwo-ex-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objecttwo-ex-4-hint, eval = FALSE}
  filter(! treatment==control)
```

###

### Exercise 5

Join the object results with the current tibble by using `left_join.` Recall that it _____. Join with treatment
```{r objecttwo-ex-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objecttwo-ex-5-hint, eval = FALSE}
  left_join(..., by = "...")

```

###

### Exercise 6

join results again, no further niching down to avg.vote.treatment and avg.vote.control
```{r objecttwo-ex-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objecttwo-ex-6-hint, eval = FALSE}

```

###

### Exercise 7

Using `mutate` column ATE. Save your code  to object_2
```{r objecttwo-ex-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objecttwo-ex-7-hint-1, eval = FALSE}
ATE = Difference between treated group and control group
```
```{r objecttwo-ex-7-hint-2, eval = FALSE}
ATE = avg.vote.treatment - avg.vote.control
```
###




## Objectthree

``` {r}
object_3 <- shaming %>% 
  filter(treatment %in% c("Neighbors", "Control")) %>% 

  # Here, we use an ifelse() statement here to return "old" in the rows where
  # age is 64 # or older, and "young" elsewhere.
  
  mutate(age = ifelse(age > 64, "old", "young")) %>% 

  # Group by treatment AND age here so the avg.percent values are calculated for
  # "old" and "young" separately.
  
  group_by(treatment, age) %>% 
  summarize(avg.perc = mean(primary_06),
            .groups = "drop") %>% 
  pivot_wider(names_from = treatment,
            values_from = avg.perc) %>% 
  mutate(ATE = Neighbors - Control) %>% 
  
  # Using rename() to make the column names less confusing. We want to be specific
  # as possible. Having "Control" or "Neighbors" is too confusing.

  rename(c("control.perc" = Control,
           "neighbors.perc" = Neighbors))

object_3
```
### 
Say something about the purpose of the table - we will investigate whether the causal effect of Neighbors relative to Control is the same for older and younger people. Define old people as anyone older than 64.**will need to be fixed**

### Exercise 1

Start a pipe with shaming. Since we want to compare neighbor and control, let's filter those variables, which are located in treatment 
```{r objectthree-ex-1, exercise = TRUE}

```

```{r objectthree-ex-1-hint-1, eval = FALSE}
Filter uses %in% and if you want to filter multiple variables, we use c("...","...")
```

```{r objectthree-ex-1-hint-2, eval = FALSE}
shaming %>% 
  filter(treatment %in% c("...", "...") )
```

###

### Exercise 2

Now, we want to seperate the young from the old, natural selection. Continue the pipe and mutate a new column called age that tells us whether a person is "young" or "old" by checking if they are over 64 (old) or younger or equal to 64 (young).
```{r objectthree-ex-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objectthree-ex-2-hint-1, eval = FALSE}
For if statements, we want to use ifelse. It contains 3 parts: the if statement, what happens if it returns true, and what happens if it returns false.

```
```{r objectthree-ex-2-hint-2, eval = FALSE}
mutate(age =ifelse(age > 64, "...", "..."))
```
###


### Exercise 3

Group the data by treatment and age
```{r objectthree-ex-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objectthree-ex-3-hint, eval = FALSE}
... %>% 
  group_by(treatment, age)
```

###

avg.percent values are calculated for "old" and "young" separately.efficency.. etc. 

### Exercise 4

We want to find the avg percentile for primary_06. Use summarize 
<!--replace primary 06 with what it actually means -->
```{r objectthree-ex-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objectthree-ex-4-hint, eval = FALSE}
summarize (avg.perc = mean(primary_06),
            .groups = "drop")
```

###

### Exercise 5

Clean it up using pivot wider. Set the names from to treatment, and values from avg perc to see the average percentage for young and old in each treatment type
```{r objectthree-ex-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objectthree-ex-5-hint, eval = FALSE}
  pivot_wider(names_from = treatment,
            values_from = avg.perc)
```

###

### Exercise 6

Create a new column with mutate, which displays the ATE value. 
```{r objectthree-ex-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objectthree-ex-6-hint-1, eval = FALSE}
You calculate the ATE by finding the difference between the two treatment types. 
```
```{r objectthree-ex-6-hint-2, eval = FALSE}
mutate(ATE = Neighbors - Control)
```
###
### Exercise 7

Lastly, let's rename column Control to control.perc and column neighbor into neighbor.perc. Save the tibble as object_3. 
```{r objectthree-ex-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r objectthree-ex-7-hint, eval = FALSE}

```

###

Using rename() to make the column names less confusing. We want to be specific. as possible. Having "Control" or "Neighbors" is too confusing.


## Shaming Plot

We will be creating this plot. 
``` {r}
shaming %>% 
  filter(treatment %in% c("Neighbors", "Control")) %>% 
  filter(age < 90) %>% 
  
  # We filter here because there are NA values in ages such as 102 that give us a
  # "missing rows" message when we plot our values. The plot also looks nicer this way.

  group_by(treatment, age) %>% 
  summarize(avg.perc = mean(primary_06),
            .groups = "drop") %>% 

  # Using arrange allows us to see show the rows that have the youngest ages 
  # first.
  
  arrange(age) %>% 
  pivot_wider(names_from = treatment,
              values_from = avg.perc) %>% 
  mutate(ATE = Neighbors - Control) %>% 
  rename(c("control.perc" = Control,
           "neighbors.perc" = Neighbors)) %>% 
  ggplot(aes(x = age, y = ATE)) +
    geom_point() +
    geom_smooth(method = "loess",
                formula = y ~ x) +
  
    # Possibly revisit removing the gray area here because confidence intervals have
    # not been discussed yet.
  
    labs(title = "Effect on Voting of Neighbors Postcard",
        subtitle = "Average treatment effect is lower for the young and the very old",
         y = "Average Treatment Effect",
         x = "Age",
         caption = "Source: Gerber, Green, and Larimer (2008)") +
    theme_bw()
```

### Exercise 1

Start your pipe with shaming. Once again, we just want to see the effect of the neighbor postcards against control. Filter the data accordingly. 
```{r plot-ex-1, exercise = TRUE}

```


```{r plot-ex-1-hint, eval = FALSE}
filter(treatment %in% c("...", "..."))
```

###

### Exercise 2

You know what, anybody above 90 is too old for this dataset. Filter the data so that everyones age is below 90. 
```{r plot-ex-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r plot-ex-2-hint, eval = FALSE}
filter(age < ..)
```

###

If you've looked at the data, anybody above 102 actually gives us a missing rows message when plotting values. 
Consider having them plot all the data then letting them discover the age seperately?

### Exercise 3

Group the data by treatment and age

```{r plot-ex-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r plot-ex-3-hint, eval = FALSE}
group_by(treatment, age)
```

###

### Exercise 4

Calculate the avg.perc of of each age group by finding the mean of primary_06. Create a new column called "avg.perc" using summarize to display the avg. 
```{r plot-ex-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r plot-ex-4-hint, eval = FALSE}
 summarize(avg.perc = mean(...),
            .groups = "drop")
```
### Exercise 5

Arrange the data by age, showing the youngest participants first
```{r shaming-plot-ex-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-plot-ex-5-hint, eval = FALSE}
arrange(age)
```

###

### Exercise 6

Use pivot wider to make the plot look better. Set names from as treatment and values from average perc. 
```{r shaming-plot-ex-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-plot-ex-6-hint, eval = FALSE}
pivot_wider(names_from = ...,
              values_from = ...)
```

###

### Exercise 7

Using mutate, create a new column called ATE. Add in the ATE for each age group. 
```{r shaming-plot-ex-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-plot-ex-7-hint-1, eval = FALSE}
ATE is calculated from subtracting the treatment group from the control group
```
```{r shaming-plot-ex-7-hint-2, eval = FALSE}
mutate(ATE = Neighbors - Control)
```
###

### Exercise 8

Lets rename control to control.perc, and neighbors to neighbor.perc to be more specific. 
```{r shaming-plot-ex-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-plot-ex-8-hint, eval = FALSE}

```

###
### Exercise 9

Let's start creating our scatterplot graph using ggplot. We want age to be on the x axis, and the ATE to be on the y axis. 
```{r shaming-plot-ex-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-plot-ex-9-hint, eval = FALSE}
ggplot(aes(x = ..., y = ...)) +
    geom_point() 
```

###

### Exercise 10

Let's add a regression line using geom_smooth. Set method to loess, and formula  to y ~ x 
```{r shaming-plot-ex-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-plot-ex-10-hint, eval = FALSE}

```

###
It does automatically set the parameters to the same thing, however it is always nice to add them in 
add more for this. Maybe add something abotu confidence level as a small intro? or add it in somwhere else. 

### Exercise 11

Adjust the feel of the graph by adding the `theme_bw()`. To finish your plot, use labs() to give the graph a title, subtitle, axes labels, legend heading, and caption.
```{r shaming-plot-ex-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r shaming-plot-ex-11-hint, eval = FALSE}

```


Remember that your graph should look like this 

```{r}
shaming %>% 
  filter(treatment %in% c("Neighbors", "Control")) %>% 
  filter(age < 90) %>% 
  
  # We filter here because there are NA values in ages such as 102 that give us a
  # "missing rows" message when we plot our values. The plot also looks nicer this way.

  group_by(treatment, age) %>% 
  summarize(avg.perc = mean(primary_06),
            .groups = "drop") %>% 

  # Using arrange allows us to see show the rows that have the youngest ages 
  # first.
  
  arrange(age) %>% 
  pivot_wider(names_from = treatment,
              values_from = avg.perc) %>% 
  mutate(ATE = Neighbors - Control) %>% 
  rename(c("control.perc" = Control,
           "neighbors.perc" = Neighbors)) %>% 
  ggplot(aes(x = age, y = ATE)) +
    geom_point() +
    geom_smooth(method = "loess",
                formula = y ~ x) +
  
    # Possibly revisit removing the gray area here because confidence intervals have
    # not been discussed yet.
  
    labs(title = "Effect on Voting of Neighbors Postcard",
        subtitle = "Average treatment effect is lower for the young and the very old",
         y = "Average Treatment Effect",
         x = "Age",
         caption = "Source: Gerber, Green, and Larimer (2008)") +
    theme_bw()
```




```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
