---
title: Final Projec
tutorial:
  id: final-project
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: Terminal Tutorial
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```


### Exercise 1


###



## Introduction
### 

Your final project is the first entry in your professional portfolio. Few employers will ever ask to see your high school or college transcripts. They will want to see what you can **do**, what you can **make** with your own two 


## Pimp Your Github Account
### 

Your Github account should look professional. Read [this essay](https://www.davidkane.info/post/2020-01-18-pimp-my-github/) for details about what that means. This section will guide you. 

### Exercise 1

Write a bio for your Github account. Once you have added it to your account, copy and paste the bio below.

### 

```{r pimp-your-github-acc-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    rows = 6)
```

### 


### Exercise 2

Add a photo to your Github account. You do not have to use a photo of yourself — some people are shy — but you should use something other than the GitHub default.


###

Once the photo is uploaded, you can click on it and a URL will appear. It will looking something like this:

https://avatars.githubusercontent.com/u/some-number-and-stuff

Copy/paste the url for your photo here:


```{r pimp-your-github-acc-2}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 1)
```

###




## Summary
### 

```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
