---
title: "Visualization-B"
tutorial:
  id: "01-visualization-b"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Chapter 1 Tutorial Part B"
---




```{r setup, include=FALSE}
library(tidyverse)
library(PPBDS.data)
library(learnr)
library(shiny)
library(ggthemes)
library(viridis)
library(nycflights13)

knitr::opts_chunk$set(echo = FALSE, message = FALSE)
options(tutorial.exercise.timelimit = 60, tutorial.storage="local")  
```



## Name
###

``` {r name, echo=FALSE}
question_text(
  "Student Name:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

## Email
###

``` {r email, echo=FALSE}
question_text(
  "Email:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

## Advanced Plotting - `geom_point()`
###

Let's begin by making this scatterplot using `geom_point()`.

```{r qcores}
scat_1 <- ggplot(data=qscores, mapping= aes(x=hours, y=enrollment, color=term)) + 
  scale_y_sqrt() +
  geom_point(alpha=.5)


scat_1
```

### Exercise 1

The data set used is `qscores`. Put `hours` on the x axis and `enrollment` on the y axis. Then map the `term` variable to the `color` aesthetic.

```{r point-II-2, exercise=TRUE, exercise.lines=8}


```

### Exercise 2

Change the scale to square root using `scale_y_sqrt()`.(Remember you need to add a layer here using `+`). Also, use `geom_point()` set `alpha` to 0.5 


```{r point-II-3, exercise=TRUE, exercise.lines=8}


```


## Advanced Plotting - `geom_jitter()`
###

Let's make this scatterplot using `geom_jitter()`.

```{r diamonds-11, eval= TRUE}
ggplot(data=diamonds, mapping= aes(x=price, y=carat)) +
  scale_x_log10()+
  geom_jitter(alpha=.5, height= .25, size=1)+
  geom_smooth(method="lm")
```


### Exercise 1

Use the data set `diamonds`. Put `carat` on the y-axis, and `price` on the x-axis.

```{r gj-2-1, exercise=TRUE, exercise.lines = 5}

```

### Exercise 2

Nice...but our plot looks a little sloppy. Try to minimize our overplotting. Within `geom_jitter()` set `size` to 1, `height` to 0.25, and `alpha` to 0.2.

```{r gj-2-2, exercise=TRUE, exercise.lines = 5}

```

### Exercise 3

That looks a bit better! Now, try adding a trendline using `geom_smooth()`, with the argument `method` set to the `lm`. Let's also use the `scale_x_log10` function to make the scale of the plot logarithmic.

```{r gj-2-3, exercise=TRUE, exercise.lines = 5}

```


### Exercise 4

As a final exercise, use what you've learned to recreate the plot below. Make sure you set`width` = 1, and `alpha` = 0.2. `Length` is recorded as the variable `x`. 

```{r}
ggplot(data = diamonds) +
  geom_jitter(aes(x = x, y = price, color = carat), width = 1, alpha = 0.2) +
  labs(title = "Length and Price in Cut Diamonds",
       x = "Length (Millimeters)",
       y = "Price (US Dollars)")
```

```{r gj-2-5, exercise=TRUE, exercise.lines = 7}

```

```{r gj-2-5-hint, eval=FALSE}
 Note that this is a bit tricky. There are two --- completely separate! ---
 meanings of `x` in this problem. First, `x` is the name of a variable in the
 `diamonds` dataset which measures the length of each diamond. (There is
 nothing wrong with use `x` as a variable name after all.) Second, `x` is the
name of the first argument to the `aes()` function. But you can still use
 both of them because R is smart enough to keep the meanings separate because
 of how it uses the position of each in the code you write.
```


## Advanced Plotting - `geom_histogram()` 
###


### Exercise 1

Let's keep working with our `qscores` histogram plot, which you can see below. See the message R gave us about bin widths? Change the bin width by setting the number of bins to 20.

```{r, warning=TRUE, message=TRUE}
ggplot(data = qscores, aes(x = rating)) +
  geom_histogram(fill = "red4", color = "white") +
  labs(title = "Course Rating Distribution", y = "Count", x = "Rating")
```

```{r hist-II-1, exercise=TRUE, exercise.lines=7}
ggplot(data = qscores, aes(x = rating)) +
  geom_histogram(fill = "red4", color = "white") +
  labs(title = "Course Rating Distribution", y = "Count", x = "Rating")

```

```{r hist-II-1-hint, eval=FALSE}
Set the argument bins in geom_histogram() to 20.

```

### Exercise 2

Change the plot so that the bins are .25 wide. (To do this you must delete the bins argument you set in the previous question)

```{r hist-II-2, exercise=TRUE, exercise.lines=7}


```

```{r hist-II-2-hint, eval=FALSE}
Set the argument binwidth in geom_histogram() to .25

```

### Exercise 3

Now use `facet_wrap()` to facet the plot by `term` and set the number of columns to 2.

```{r hist-II-3, exercise=TRUE, exercise.lines=7}


```

```{r hist-II-3-hint, eval=FALSE}
Within facet_wrap(), set ncol to 2.
```

### Exercsie 4

Recreate the histogram below. It was made with data set `nhanes` with `height` on the x axis and faceted by `gender`.

```{r}
ggplot(data = nhanes, aes(x = height)) +
    geom_histogram(color = "white", fill = "black", bins = 30) +
    facet_wrap(~ gender, ncol = 1)

```

```{r hist-II-5, exercise=TRUE, exercise.lines=7}


```

```{r hist-II-5-hint, eval=FALSE}
Use facet_wrap() and set ncol to 1.
```

### Exercise 5

As a final exercise, use what you've learned about `geom_histogram()` to replicate the plot below.

```{r}
mpg %>% ggplot(aes(x = hwy, color = class)) +
  geom_histogram(fill = "white", bins = 5, position = "dodge") +
  labs(title = "Highway Fuel Economy by Car Type",
       x = "Miles Per Gallon (Highway)",
       y = "Number of Car Models")
```

```{r gh-2-5, exercise=TRUE, exercise.lines = 5}

```

```{r gh-2-5-hint, eval=FALSE}
Within geom_histogram, use the arguments: fill= "white", bins = 5, position = "dodge"
```


## Advanced Plotting - `geom_boxplot()`
###


### Exercise 1

Use the data set `diamonds` to create a boxplot with `clarity` on the x-axis and `price` on the y-axis.

```{r box-II-1, exercise=TRUE, exercise.lines=10}

```


### Exercise 2

Changing the scale of the y axis to log base 10

```{r box-II-2, exercise=TRUE, exercise.lines=10}

```

```{r box-II-2-hint, eval=FALSE}
Use the scale_y_log10() function; remember you are adding a layer!
```

### Exercise 3

Great! Now, use `coord_flip()` to convert the plot into a horizontal boxplot.

```{r gb-2-2, exercise=TRUE, exercise.lines = 5}

```


```{r gb-2-2-hint, eval=FALSE}
Remember that you are adding a layer here
```


### Exercise 4

Great! Now, let's zoom in on our plot by setting  `ylim()` to the vector `c(500, 7000)`. Remember that `ylim()` should be placed inside of the `coord_` function, in this case, `coord_flip`.

```{r gb-2-4, exercise=TRUE, exercise.lines = 5}

```




## Advanced Plotting - `geom_bar()`
###

Let's make the following dodged bar plot using `geom_bar`.

```{r}
ggplot(data = trains, aes(x = att_start, fill = party)) +
  geom_bar() +
  facet_wrap(~liberal)
```

### Exercise 1

Let's make a barplot using `trains`, a tibble that records attitudes towards immigration on a Boston train platform before and after an experiment. Map our x variable to `att_start`.

```{r gbr-2-1, exercise=TRUE, exercise.lines = 5}

```

### Exercise 2

Great. Now, map `fill` to `party`. Notice any patterns?

```{r gbr-2-2, exercise=TRUE, exercise.lines = 5}

```

### Exercise 3

Good work. Now, let's use `facet_wrap()` to divide our graph by the `liberal` variable.

```{r gbr-2-4-hint, eval=FALSE}
facet_wrap( ~ ...)
```

```{r gbr-2-4, exercise=TRUE, exercise.lines = 5}

```

### Exercise 4

As a final exercise, use what you've learned to recreate the plot below.

```{r}
ggplot(data = trains, mapping = aes(x = att_end, fill = gender)) +
  geom_bar() +
  facet_wrap( ~ treatment) +
  labs(title = "Attitudes Towards Immigration After Experimentation",
       x = "Attitude Towards Immigration (Higher Means More Conservative)",
       y = "Number of People")
```

```{r gbr-2-5, exercise=TRUE, exercise.lines = 5}

```



## Advanced Plotting - `geom_smooth()`
###

Let's create this graph using `geom_smooth()`.

```{r}
ggplot(data = trains, mapping = aes(x =att_start, y = att_end, color= treatment)) +
  geom_smooth(method = "gam", alpha= .75)
```

### Exercise 1

Use the data set `trains`, which includes data on an experiment about attitudes towards immigration. Use `geom_smooth()`, and set its argument `method` to`"gam"`. Put `att_start` on the x axis and `att_end` on the y axis.

```{r smooth-II-1, exercise=TRUE, exercise.lines=7}

```

```{r smooth-II-1-hint, eval=FALSE}
ggplot(data = ..., mapping = aes(x = ..., y = ...)) +
  geom_smooth(method = "...")
```

### Exercise 2

Great. Now set `alpha` to `.75`.

```{r smooth-II-2, exercise=TRUE, exercise.lines=7}


```

```{r smooth-II-2-hint, eval=FALSE}
Because color is an aesthetic, set it inside of aes(). Set alpha inside of geom_smooth().
```

### Exercise 3

As a final exercise, use what you've learned to recreate the graph below. (Note: You are going to need to use the argument 'se= FALSE' in the `geom_smooth()` function)

```{r}
ggplot(data = iris, mapping = aes(x = Sepal.Width, y = Sepal.Length, linetype = Species)) +
    geom_smooth(se = FALSE, color = "purple") +
    labs(title = "Sepal Width and Length in Iris Species",
         x = "Sepal Width",
         y = "Sepal Height")
```

```{r gs-2-5, exercise=TRUE, exercise.lines = 5}

```


## Advanced Plotting - `geom_density()`
###

### Exercise 1

Let's make a plot using `geom_density()` and the `qscores` tibble. Put `rating` on the x-axis and `number` on the y-axis.

```{r gd-2-1, exercise=TRUE, exercise.lines = 5}

```

### Exercise 2

Nice. Now, let's use `labs()` to label our x-axis "Rating", and our y-axis "Density of Classes".

```{r labs, exercise = TRUE}


```

### Exercise 3

Let's also add an `xlim()` function, to set the range of x values on our plot to (2.5, 5).

```{r gd-2-3, exercise=TRUE, exercise.lines = 5}

```

### Exercise 4

As a final exercise, use what you've learned about `geom_density()` to recreate the plot below.

```{r}
ggplot(data = qscores, aes(x = enrollment, color = term)) +
  geom_density() +
  xlim(0, 200) +
  labs(title = "Distribution of Students Enrolled in Harvard Classes",
       x = "Number of Students Enrolled",
       y = "Density of Classes")
```

```{r gd-2-5, exercise=TRUE, exercise.lines = 5}

```


## Submit

Congrats on finishing your first Gov 50 tutorial! You're on your way to being a master in data visualization and wrangling! :)

```{r context="setup"}
submission_ui
```

```{r context="server"}
submission_server()
```
