---
title: "Getting Help"
author: Anmay Gupta
tutorial:
  id: "getting-help"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Getting help on GitHub using reprex"
---


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

<!-- * A "help" tutorial which covers all aspects of finding help. Start with the reprex package. Make the reprex in a .R file and show that file as you make progress. Perhaps make a bad reprex first, one which leaves out the library(tidyverse) calls. Also the R package which searches all packages on CRAN. https://www.zuckarelli.de/packagefinder/tutorial.html (Maybe add something about searching Github to help, which I don't know how to do well.) -->

<!-- This is nice: https://themockup.blog/posts/2021-07-28-reminder-to-test-with-a-reprex/ -->

<!-- More knowledge to drop: -->

<!-- https://reprex.tidyverse.org/index.html -->
<!-- https://www.youtube.com/watch?v=5gqksthQ0cM -->
<!-- https://reprex.tidyverse.org/articles/articles/learn-reprex.html -->

<!-- https://www.r-project.org/help.html -->

<!-- AG: I'm kind of taking this a weird way. I first walk them through helping somebody with buggy code. I'll make a few GitHub issues that each have their own version of issue display. For example, one is an r-console copy, one is an image, and one is a reprex. Then I have them debug the thing (hey you forgot to add a geom_point(), you forgot to add aes(), you didn't call tidyverse) and have them fix it. That lets you feel the frustration of the person looking at the code. -->

## Searching

<!-- AG: This section is about a few important forums and searching for them. I'd like more suggestions for valuable forums because there's only RStudio Community, Stack Overflow, and GitHub right now -->

In this tutorial, we're going to be going over how you can get help with your projects and formatting your questions so that people don't ignore them.

This is useful especially for when you start working on your own independent projects and need to reach out to somebody helpful.

R is the most painful game of spot-the-difference ever, and you're going to run into some errors along the way.

### Exercise 1

Let's preface with the fact that a simple Google search can solve a lot of your problems. 

There's no shame in looking stuff up and it comes with the job.

However, there are certain forums that are especially suited to the problems you may encounter.

###

The first forum you should look at is [RStudio Community](https://community.rstudio.com/).

This is a community of over 38,000 R developers with hundreds of users active at any given time.

It's basically like Stack Overflow but specifically focused on R and for R packages.

###

Let's try making an advanced search on RStudio. 

Go to [https://community.rstudio.com/](https://community.rstudio.com/) and navigate to the "Search" button, then click "Options". These are the advanced search options.

Search for posts containing the word "students" that are posted by David Kane (@dkane). Then copy-paste the URL of the first result into the space below.

```{r searching-1}
question_text(NULL,
	message = "answer here",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

###

As you can see, RStudio Community is a great place to find other people who have had the same question as you with the same packages, letting you quickly find a solution.

### Exercise 2

The next forum to look at is Stack Overflow.

This is **the** most widespread coding forum and it's helped millions of developers.

It's not an understatement to say that modern development runs on Stack Overflow simply because of how many people ask questions on it and how many people it helps.

###

It's pretty easy to find issues on Stack Overflow similar to yours.

They'll show up on most Google searches and are pretty reliable.

However, it's a little rough to do advanced searches on Stack Overflow because it's based on the text in your search rather than toggleable options.

###

Go to [https://stackoverflow.com/](https://stackoverflow.com/) and search `"geom_point" [ggplot2]`. Then copy-paste the URL of the first result into the space below.

```{r searching-2}
question_text(NULL,
	message = "answer here",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

###

This searches for a question containing the text "geom_point" with the tag "ggplot2". The full documentation for advanced searching can be found at [Stack Overflow's help page](https://stackoverflow.com/help/searching).

However, most of the time Stack Overflow pages will show up with a Google search, so advanced searches are rarely used.

### Exercise 3

And finally we have GitHub Issues. 

This is for cases where you think that you have a bug and want to see if anybody's had the same issue.

It's less about getting help with your problem and more about figuring out whether this is a genuine bug and if you can avoid it or not.

###

GitHub advanced searches are a little bit tougher to do because you need to go to [their special website](https://github.com/search/advanced) for advanced searches.

###

Go to [https://github.com/search/advanced](https://github.com/search/advanced) and search for closed issues (you have to scroll down for this) containing the word `ggplot()` from the owner `AnmayG` in the repository `demo-issue-repo`.

Then copy-paste the URL 

```{r searching-3}
question_text(NULL,
	message = "answer here",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

###

Your search request should look like `ggplot() user:AnmayG repo:demo-issue-repo state:closed`.

As you can see, the only thing that the advanced search did was change your search request so that it contained a few special keywords. That means that you can do the same searches in the default GitHub search bar if you just add those keywords in naturally.

## Reprex

<!-- AG: 

I kind of want to show off this long chain: https://community.rstudio.com/t/ggplot-not-working-in-r-markdown-html-document/112037 

This is a really long RStudio Community thread that is basically the perfect example of a bad reprex causing a bunch of issues. 

The guy used a pretty intelligible reprex, put in R code and everything, but it's still taking 14 comments of back-and-forth communication to not even get close to the answer. 

Thing is, the person technically didn't use a reprex. -->

But what if you already scoured the forums piece by piece and post by post for your error (or just got too lazy) and feel the need to ask a new question?

The point of these forums is that they're there to answer questions, so you can obviously post your own.

However, as the totally-real-world issue that you pulled up in the last exercise shows you, nobody will answer your question if you don't give them any context about it.

Just to show you how painful it is, let's walk you through how a bad question can cause problems for the people trying to solve it.

### Exercise 1

The first issue we'll be going through is posting an image instead of the actual code.

###

Let's try to fix the issue that [this lovely person](https://github.com/AnmayG/demo-issue-repo/issues/1) found. You can also find this issue by going to the "Issues" page at [https://github.com/AnmayG/demo-issue-repo](https://github.com/AnmayG/demo-issue-repo) and opening the first issue.

###

Copy the code in the issue into the box below, then add the `aes()` function into `ggplot()` so that the code works and displays a working graph. Feel free to tinker a little.

```{r reprex-1, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r reprex-1-hint, eval = FALSE}
library(tidyverse)
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) +
  geom_point()
```

###

This likely was a **pain** to do. Manually typing every single command into the box would have sucked, and you can't even copy-paste the code since it's contained in an image of all things. 

This is the perfect example of what you should **not** do if you have a project because people who want to help you need to put in way too much effort. 

And the worst part is that the people trying to help you can't see your error message either, so they have to bring it all the way into their code, type out every single command, run it, find the problem, fix the problem and *then* answer your question. That's too much work, and it means that nobody will answer the question from the getgo.

### Exercise 2

The next problem 

```{r reprex-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r reprex-2-hint, eval = FALSE}

```

###



```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
