---
title: "Functions A"
tutorial:
  id: "functions-a"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 3 Tutorial Part A"
---


<!-- Once we rewrite the chapter, there should be lots of good questions. The more that questions can match the chapter, the better. Recall that soon (?), I want to embed the tutorial inside of the chapter itself. This should be relatively easy to do for good questions. -->


<!-- We should have at least two, if not three, tutorials for chapter 3, each 1 to 2 hours long. First does all the list-columns, map_ functions, write your own function preliminaries. The second explores measures of center and variability. The third does some version of the prediction game. -->


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(gapminder)
library(skimr)
library(primer.data)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

```

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))


```

## Functions 
###

A function is a piece of code that is packaged in a way that makes it easy to reuse. 

### Exercise 1

Use `sample()` and set `x` to values 5 to 10. Then, set `size` to 1. 


```{r functions-1, exercise = TRUE}

```


```{r functions-1-hint-1, eval = FALSE}
Use the  : operator as a shortcut!
```

```{r functions-1-hint-2, eval = FALSE}
sample(x = ...,
       size = ...)
```


### Exercise 2

Let's use `replicate()` to repeat the code you just created. The first argument to `replicate()` should be 5. For the second argument, copy and paste your code from the previous exercise. 


```{r functions-2, exercise = TRUE}

```

```{r functions-2-hint, eval = FALSE}
replicate(..., sample(...))
```

### Exercise 3

Great. Now create a `tibble()` with one variable called `x` . Have `x` take on the values 3, 5, and 9.

```{r functions-3, exercise = TRUE}

```

```{r functions-3-hint-1, eval = FALSE}
tibble(x = c(...))
```

### Exercise 4

Copy/ paste your code from above. Use ` %>% ` operator to use `mutate()` to create a column named `sqrt_x`. `sqrt_x` should be set to `sqrt()` of `x`.

```{r functions-4, exercise = TRUE}

```

```{r functions-4-hint, eval = FALSE}
tibble(x = c(3,5,9)) %>% 
  mutate(... = ...)
```

### Exercise 5

Let's create the same output, but now using a `map*` function. We have already provided the tibble. 

Use `mutate()` to create a column named `sqrt_x` set to `map_dbl()`. The first argument to `map_dbl()` should be `x`. The second argument should be  `sqrt()` with the argument `.` inside it.

```{r functions-5, exercise = TRUE}
tibble(x = c(3, 7, 2))
```

```{r functions-5-hint-1, eval = FALSE}
... %>% 
  mutate(sqrt_x = map_dbl(..., ~...))
```

```{r functions-5-hint-2, eval = FALSE}
... %>% 
  mutate(sqrt_x = map_dbl(..., ~sqrt(.))
```

## List-columns and map functions
###

Let's create a list column.


### Exercise 1

Let's begin by creating a tibble with a column `x`.  Have `x` take on the values 3,7,2,8, and 4. 

```{r lm-1, exercise = TRUE}

```

```{r lm-1-hint, eval = FALSE}
tibble(x = c(...))
```

### Exercise 2

Great. Now assign your work to an object named `tbl`. 

```{r lm-2, exercise = TRUE}

```

```{r lm-2-hint, eval = FALSE}
tbl <- tibble(x = c(3,7,2,8,4))
```

### Exercise 3

Now take the `range()` of the `x` column. To do so, use `$` operator.

```{r lm-3-setup}
tbl <- tibble(x = c(3,7,2,8,4))
```

```{r lm-3, exercise = TRUE}

```

```{r lm-3-hint, eval = FALSE}
range(tbl$x)
```

### Exercise 4

Great! Now use let's start a pipe with `tbl`. Use `summarize()` to create the column `range_x`, which is set to `range(x)` wrapped in `list()`. 

```{r lm-4-setup}
tbl <- tibble(x = c(3,7,2,8,4))
```

```{r lm-4, exercise = TRUE}

```

```{r lm-4-hint-1, eval = FALSE}
Recall that when you create a pipe, you need to use %>% to add in functions like summarize.
```

```{r lm-4-hint-2, eval = FALSE}
tbl %>% 
  summarize(... = list(range(x)) 
```

### Exercise 5

Copy/paste your code. Now add the function `str()` to the pipe.

```{r lm-5-setup}
tbl <- tibble(x = c(3,7,2,8,4))
```


```{r lm-5, exercise = TRUE}
tbl %>% 
  summarize(range_x = list(range(x)))

```

```{r lm-5-hint, eval = FALSE}

```

### Exercise 6

Copy/ paste your code from above. Within `str()`, use `[[ ]]` to extract the first value of `tbl`.

```{r lm-6-setup}
tbl <- tibble(x = c(3,7,2,8,4))
```


```{r lm-6, exercise = TRUE}

```

```{r lm-6-hint-1, eval = FALSE}
tbl %>% 
  summarize(range_x = list(range(x))) %>% 
  str(...)
```

```{r lm-6-hint-2, eval = FALSE}
tbl %>% 
  summarize(range_x = list(range(x))) %>% 
  str(tbl[[...]])

```

### Exercise 7

Let’s now practice with the `nhanes` dataset. Start a pipe with `nhanes`. `Select()` the variables `gender` and `height`. Also add the function `drop_na()`. 

```{r lm-7, exercise = TRUE}

```

```{r lm-7-hint, eval = FALSE}
nhanes %>%
  select(...,...)
  drop_na() %>% 
```

### Exercise 8

Copy/paste your code from above. Continue your pipe with `group_by()` with the argument  `gender`. 

```{r lm-8, exercise = TRUE}

```

```{r lm-8-hint, eval = FALSE}
...
  group_by(...) %>% 
```

### Exercise 9

Copy/ paste your code from above. Continue your pipe with `mutate()` to create a new variable `height_quant`. `height_quant` should be set to `map()`. The first argument to `map()` should be `height`. The second argument should be  `quantile()` with the argument `.` inside it.

```{r lm-9, exercise = TRUE}

```

```{r lm-9-hint-1, eval = FALSE}
... %>% 
  mutate(... = map(..., ~ ...)))
````

### Exercise 10

Good work. Copy/ paste your code from above. Save your work to an object named `tmp`. 

```{r lm-10, exercise = TRUE}

```

```{r lm-10-hint-1, eval = FALSE}
tmp <- nhanes %>%
  select(gender, height) %>%
  drop_na() %>% 
  group_by(gender) %>% 
  mutate(height_quantiles = map(height, ~ quantile(.)))
````

### Exercise 11

Start a new pipe with `tmp`. `select()` the variables `gender` and `height_quantiles`. 

```{r lm-11-setup}
tmp <- nhanes %>%
  select(gender, height) %>%
  drop_na() %>% 
  group_by(gender) %>% 
  mutate(height_quantiles = map(height, ~ quantile(.)))
```

```{r lm-11, exercise = TRUE}

```

```{r lm-11-hint, eval = FALSE}
... %>% 
  select(..., ...)
```

### Exercise 12

Copy/paste your code from above. Continue your pipe with `slice()` to grab the rows 1-5. 

```{r lm-12, exercise = TRUE}

```

```{r lm-12-hint-1, eval = FALSE}
... %>% 
  slice(...,...)
```

```{r lm-12-hint-2, eval = FALSE}
... %>% 
  slice(1,5)
```

### Exercise 13

Continue your pipe one last time to add the function `str()`.

```{r lm-13, exercise = TRUE}

```

```{r lm-13 -hint, eval = FALSE}
... %>% 
  str()
```


## Anonymous functions
###

We can create functions that do operations “on the fly” without bothering to give them a name. 

### Exercise 1

Let's conduct a mathematical operation. Use `tibble()` to create a column `before`. Have `before` take on the values 4, 6, and 8. 

```{r af-1, exercise = TRUE}

```

```{r af-1-hint, eval = FALSE}
tibble(... = c(...))
```

### Exercise 2

Copy/ paste your code from above. Use ` %>% ` to add `mutate()` to create a new column `after`, which is set to `map_dbl()`. The first argument to `map_dbl()` should be `before`. The second argument should be  `~ (. - 1)`, which subtracts the value 1 from each value in `before`.

```{r af-2, exercise = TRUE}

```

```{r af-2-hint, eval = FALSE}
... %>% 
  mutate(... = map_dbl(..., ~ (. - 1)))
```

## Creating your own functions
###


### Exercise 1

Use `function()` and `{ }` to create a function that multiplies 2 by 3. Name this function `mult_two_three`. On the line below, call your function.

```{r cf-1, exercise = TRUE}

```

```{r cf-1-hint-1, eval = FALSE}
mult_two_three <- function(){
  ...
}

mult_two_three()
```

```{r cf-1-hint-2, eval = FALSE}
mult_two_three <- function(){
  2 * 3
}

mult_two_three()
```

### Exercise 2

Adjust your function by adding the argument `x` inside `function()`. Then, replace the value 3 within `{ }` with `x`. This way, any value we put inside our function will be multiplied by 3. 


```{r cf-2, exercise = TRUE}

```

```{r cf-2-hint-1, eval = FALSE}
mult_two_three <- function(...){
  ...
}

```

```{r cf-2-hint-2, eval = FALSE}
mult_two_three <- function(x){
  x * 3
}

```

### Exercise 3

Put your function `mult_two_three()` to the test! Use `mult_two_three()` and set `x` to 4.  

```{r cf-3-setup}
mult_two_three <- function(x){
  x * 3
}

```


```{r cf-3, exercise = TRUE}

```


```{r cf-3-hint-1, eval = FALSE}
mult_two_three(...)
```

```{r cf-3-hint-2, eval = FALSE}
mult_two_three(x = ...)
```

### Exercise 4

Now write a function that subtracts 2 from 5. Name this function `five_minus_two()`. On the line below, call your function.

```{r cf-4, exercise = TRUE}

```


```{r cf-4-hint-1, eval = FALSE}
five_minus_two <- function(){
  ... 
}

five_minus_two()
```

```{r cf-4-hint-2, eval = FALSE}
five_minus_two <- function(){
  ... - ...
}

five_minus_two()
```

### Exercise 5

Now adjust your function `five_minus_two()` so that it now subtracts 2 from `x`.

```{r cf-5, exercise = TRUE}

```


```{r cf-5-hint-1, eval = FALSE}
five_minus_two <- function(...){
  ...
}

```

### Exercise 6

Put your function into action! Use `five_minus_two()` and set `x` set to 18.

```{r cf-6-setup}
five_minus_two <- function(x){
  x - 2
}
```


```{r cf-6, exercise = TRUE}

```

### Exercise 7

Now write a function that takes two variables `x` and `y` and will add them together. Name your function `add_2_var`.

```{r cf-7, exercise = TRUE}

```

```{r cf-7-hint-1, eval = FALSE}
add_2_var <- function(..., ...){
 ...
}

```

```{r cf-7-hint-2, eval = FALSE}
add_2_var <- function(..., ...){
 ... + ...
}

```

### Exercise 8

Put your function into action! Use `add_2_var()` with the values 4 and 2 as arguments. 

```{r cf-8-setup}
add_2_var <- function(x){
  x - 2
}
```

```{r cf-8, exercise = TRUE}

```

```{r cf-8-hint-1, eval = FALSE}
add_2_var(...,...)
```


### Acknowledgements

Some of these exercises were taken from the collection of [RStudio Primers](https://rstudio.cloud/learn/primers), a great resource for practicing your skills.


## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```

