---
title: "Functions A"
tutorial:
  id: "functions-a"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 3 Tutorial Part A"
---


<!-- Once we rewrite the chapter, there should be lots of good questions. The more that questions can match the chapter, the better. Recall that soon (?), I want to embed the tutorial inside of the chapter itself. This should be relatively easy to do for good questions. -->


<!-- We should have at least two, if not three, tutorials for chapter 3, each 1 to 2 hours long. First does all the list-columns, map_ functions, write your own function preliminaries. The second explores measures of center and variability. The third does some version of the prediction game. -->


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(gapminder)
library(skimr)
library(primer.data)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

```

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))


```

## Functions 
###

A function is a piece of code that is packaged in a way that makes it easy to reuse. 
### Exercise 1

Use `sample()` and set `x` to values 5 to 10. Then, set `size` to 1. 


```{r functions-1, exercise = TRUE}

```

```{r functions-1-hint, eval = FALSE}
Use the  : operator as a shortcut!
```

### Exercise 2

Let's use `replicate()` to repeat the code you just created. The first argument to `replicate()` should be 5. For the second argument, copy and paste your code from the previous exercise. 


```{r functions-2, exercise = TRUE}

```

```{r functions-2-hint, eval = FALSE}
replicate(..., sample(...))
```

### Exercise 3

Great. Now create a `tibble()` where `x` takes on the values 3, 5, and 9.

```{r functions-3, exercise = TRUE}

```

```{r functions-3-hint, eval = FALSE}
Place the numbers inside c() 
```

### Exercise 4

Now use `mutate()` to create a column named `sqrt_x`. `sqrt_x` should be set to `sqrt()` of `x`.

```{r functions-4, exercise = TRUE}

```

```{r functions-4-hint, eval = FALSE}

```

### Exercise 5

Let's create the same output, but now using a `map*` function. We have already provided the tibble. 

Use `mutate()` to create a column named `sqrt_x` set to `map_dbl()`. The first argument to `map_dbl()` should be `x`. The second argument should be  `sqrt()` with the argument `.` inside it.

```{r functions-5, exercise = TRUE}
tibble(x = c(3, 7, 2))
```

```{r functions-5-hint, eval = FALSE}
Don't forget to place ~ before sqrt()
```


## List-columns and map functions
###


### Exercise 1

Let's create a list column. First, let's begin by using `rnorm()` with the argument `12`. Assign your work to an object named `x`. One the line below, take the `range()` of `x`.

```{r lm-1, exercise = TRUE}

```

```{r lm-1-hint, eval = FALSE}

```

### Exercise 2

Great! Now use `tibble()` to create a column named `col_1`, which is set to `list()`. Within `list()`, take the `range()` of `x`.

```{r lm-2, exercise = TRUE}

```

```{r lm-2-hint, eval = FALSE}

```

### Exercise 3

Let's view our column in an easier way. Copy and paste your code from above. Use ` %>%` to pipe in the function `str()`.

```{r lm-3, exercise = TRUE}

```

```{r lm-3-hint, eval = FALSE}

```

### Exercise 4

Let's now try using `map()` to make a list column. First, let's `select()` `gender` and `height`.

```{r lm-4, exercise = TRUE}

```

```{r lm-4-hint, eval = FALSE}
nhanes %>%
  select(..., ...)
```

### Exercise 5

Continue your code with ` %>% ` to `drop_na()` and `group_by()` `gender`.

```{r lm-5, exercise = TRUE}

```

```{r lm-5-hint, eval = FALSE}
... %>%
  drop_na() %>% 
  group_by(...)
```

### Exercise 6

Lastly, use `mutate()` to create `height_quant` set to `map()`. The first argument to `map()` should be `height`. The second argument should be  `quantile()` with the argument `.` inside it.

```{r lm-6, exercise = TRUE}

```

```{r lm-6-hint-1, eval = FALSE}
... %>% 
  mutate(... = map(..., ~ ...)))
````

### Exercise 7

Good work. Let's now work with list columns. Begin by using `tibble()` with a column `score` set to values 5 to 10.

```{r lm-7, exercise = TRUE}

```

```{r lm-7-hint-1, eval = FALSE}
Use the : operator as a shortcut instead of typing values out 
````

```{r lm-7-hint-2, eval = FALSE}
tibble(... = ...:...)
```

### Exercise 8

Now use `mutate()` to create a new column named `draws`, which is set to `map()`. The first argument to `map()` should be `scores`. The second argument should be  `rnorm()` with the argument 10.

```{r lm-8, exercise = TRUE}

```

```{r lm-8-hint-1, eval = FALSE}
Put a tilde before rnorm(10), i.e. map(scores, ~rnorm(10)
```

```{r lm-8-hint-2, eval = FALSE}
... %>% 
  mutate(... = map(..., ~ rnorm(...)))
```

### Exercise 9

Create another variable named `max` using `mutate()`. `max`should be set to `map_dbl()`. The first argument to `map_dbl()` should be `scores`. The second argument should be  `max()` with the argument `.` inside it.

```{r lm-9, exercise = TRUE}

```

```{r lm-9-hint-1, eval = FALSE}
Put a tilde before max(.), i.e. map(scores, ~ max(.))
```

```{r lm-9-hint-2, eval = FALSE}
... %>% 
  ... %>% 
  mutate(... = map_dbl(..., ~ max(...)))
```

### Exercise 10

Use `mutate()` a final time to create the variable `range` set to `map()`. The first argument to `map_dbl()` should be `scores`. The second argument should be  `range()` with the argument `.` inside it.

```{r lm-10, exercise = TRUE}

```

```{r lm-10-hint, eval = FALSE}
Put a tilde before range(.), i.e. map(scores, ~ range(.))
```


## Anonymous functions
###

We can create functions that do operations “on the fly” without bothering to give them a name. 

### Exercise 1

Let's conduct a mathematical operation. Use `tibble()` to create a column named `before`, which is set to `c()` that contains values 4, 6, and 8. 

```{r af-1, exercise = TRUE}

```

```{r af-1-hint, eval = FALSE}
tibble(... = c(...))
```

### Exercise 2

Use `mutate()` to create a new column `after`, which is set to `map_dbl()`. The first argument to `map_dbl()` should be `before`. The second argument should be  `~ (. - 1)`, which subtracts the value 1 from each value in `before`.

```{r af-2, exercise = TRUE}

```

```{r af-2-hint, eval = FALSE}
... %>% 
  mutate(... = map_dbl(..., ~ (. + 1)))
```

## Creating your own functions
###


### Exercise 1

Use `function()` and `{ }` to create a function that multiply 2 by 3. Name this function `mult_two_three`. On the line below, call your function.

```{r cf-1, exercise = TRUE}

```

```{r cf-1-hint-1, eval = FALSE}
mult_two_three <- function(){
  ...
}

mult_two_three()
```

```{r cf-1-hint-2, eval = FALSE}
mult_two_three <- function(){
  2 * 3
}
mult_two_three()
```

### Exercise 2

Adjust your function by adding an `x` inside `function()`. Then, replace the 3 within `{ }` with `x`. This way, any value we put inside our function will be multiplied by 3. 


```{r cf-2, exercise = TRUE}

```

```{r cf-2-hint-1, eval = FALSE}
mult_two_three <- function(...){
  ...
}

mult_two_three()
```

```{r cf-2-hint-2, eval = FALSE}
mult_two_three <- function(x){
  x * 3
}
mult_two_three()
```

### Exercise 3

Put your function `mult_two_three()` to the test! Use `mult_two_three()` and set `x` to 4.  

```{r cf-3-setup}
mult_two_three <- function(x){
  x * 3
}
mult_two_three()
```


```{r cf-3, exercise = TRUE}

```


```{r cf-3-hint-1, eval = FALSE}
mult_two_three(...)
```

```{r cf-3-hint-2, eval = FALSE}
mult_two_three(x = ...)
```

### Exercise 4

Now write a function that subtracts 2 from 5. Name this function `five_minus_two()`. On the line below, call your function.

```{r cf-4, exercise = TRUE}

```


```{r cf-4-hint-1, eval = FALSE}
five_minus_two <- function(){
  ...
}
five_minus_two()
```

### Exercise 5

Now adjust your function `five_minus_two()` so that it now subtracts 2 from `x`.

```{r cf-5, exercise = TRUE}

```


```{r cf-5-hint-1, eval = FALSE}
five_minus_two <- function(...){
  ...
}
five_minus_two()
```

### Exercise 6

Put your function into action! Use `five_minus_two()` and set `x` set to 18.

```{r cf-6-setup}
five_minus_two <- function(x){
  x - 2
}
```



```{r cf-6, exercise = TRUE}

```

### Exercise 7

Now write a function that takes two variables `x` and `y` and will add them together. Name your function `add_2_var`. On the line below, call your function.

```{r cf-7, exercise = TRUE}

```

```{r cf-7-hint-1, eval = FALSE}
five_minus_two <- function(..., ...){
 ...
}
```

### Exercise 8

Put your function into action! Use `add_2_var()` with the values 4 and 2 as arguments. 

```{r cf-8, exercise = TRUE}

```

```{r cf-8-hint-1, eval = FALSE}

```

## no_NA_sampler()
###


### Exercise 1

Recall the `nhanes` dataset. Use `$` to extract the `weight` column. 

```{r no-1, exercise = TRUE}

```


```{r no-1-hint-1, eval = FALSE}

```

### Exercise 2

Let's write a function that allows us to sample `weight` from individuals who have no NA's for any variables.

Start your code with`nhanes`. Use `drop_na()` to get rid of any NA values.

```{r no-2, exercise = TRUE}

```


```{r no-2-hint-1, eval = FALSE}

```

### Exercise 3

Now use `sample_n()` with the argument 10. Then, `pull()` `height`. 

```{r no-3, exercise = TRUE}

```


```{r no-3-hint-1, eval = FALSE}

```

### Exercise 4

Great, we have code that does what we want. To turn this into a function, we just need to copy/paste our code above within the body `{ }` of our `function()`. Assign your work to an object named `no_NA_sampler`, then call your function.

```{r no-4, exercise = TRUE}

```


```{r no-4-hint-1, eval = FALSE}
no_NA_sampler <- function(){
  ...
}

no_NA_sampler()
```

### Exercise 5

Let's adjust our code so we pull any sample, not just 10! To do so, place an `n` inside `function()`. Also replace 10 with `n` inside `sample_n()`. 

```{r no-5, exercise = TRUE}

```


```{r no-5-hint-1, eval = FALSE}
no_NA_sampler <- function(...){
  nhanes %>% 
    drop_na() %>%
    sample_n(...) %>% 
    pull(weight)
}
no_NA_sampler()
```

### Exercise 6

Put your function in action! Use the function `no_NA_sampler()` and set `n` to 20. 

```{r no-6-setup}
no_NA_sampler <- function(n){
  nhanes %>% 
    drop_na() %>%
    sample_n(n) %>% 
    pull(weight)
}
```

```{r no-6, exercise = TRUE}

```

### Exercise 7

Let's adjust our function one more time to allow sampling from a different variable than `weight` or from a different tibble than `nhanes`.

Copy and paste your code from above. First, add the argument `tbl` within `function()`. Also replace `nhanes` with `tbl`. 

```{r no-7, exercise = TRUE}

```


```{r no-7-hint-1, eval = FALSE}
no_NA_sampler <- function(..., n){
  ... %>% 
    drop_na() %>%
    sample_n(n) %>% 
    pull(weight)
}
no_NA_sampler()
```

### Exercise 8

Great. Now add the argument `var` inside `function()`. Also replace `weight` with the argument `{{var}}`

```{r no-8, exercise = TRUE}

```


```{r no-8-hint-1, eval = FALSE}
no_NA_sampler <- function(..., tbl, n){
  tbl %>% 
    drop_na() %>%
    sample_n(n) %>% 
    pull(...)
}
no_NA_sampler()
```

### Exercise 9

Put your function in action! Use the function `no_NA_sampler()`. The first argument to `no_NA_sampler()` should be `cces`. The second argument should be `age`. Then, set `n` to 10. 

```{r no-9-setup}
no_NA_sampler <- function(var, tbl, n){
  tbl %>% 
    drop_na() %>%
    sample_n(n) %>% 
    pull({{var}})
}

```

```{r no-9, exercise = TRUE}

```



## Submit

Some of these exercises were taken from the collection of [RStudio Primers](https://rstudio.cloud/learn/primers), a great resource for practicing your skills.

```{r context="setup"}
submission_ui
```

```{r context="server"}
submission_server()
```
