---
title: "Functions B"
tutorial:
  id: "functions-b"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 3 Tutorial Part B"
---


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(skimr)
library(primer.data)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

# Functions used later.

no_NA_sampler <- function(tbl, var, n){
  tbl %>% 
    drop_na() %>%
    sample_n(size = n) %>% 
    pull({{var}})
}

prediction_game <- function(guesses, tbl, var){
  stopifnot(all(is_double(guesses)))
  stopifnot(length(guesses) == 2)
  
  your_guess <- guesses[1]
  my_guess <- guesses[2]
  
  sampled_value <- no_NA_sampler(tbl, {{var}}, n = 1) 
  
  your_error <- abs(your_guess - sampled_value)
  my_error <- abs(my_guess - sampled_value)

  if(your_error < my_error){ 
    return(paste("Guess", your_guess, "wins!"))
  }
  
  if(your_error > my_error){ 
    return(paste("Guess", my_guess, "wins!"))
  }
  
}
```

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```


## no_NA_sampler()
###

In this section, we will make a custom function called `no_NA_sampler()`.

### Exercise 1

Recall the `nhanes` dataset. Use `$` to extract the `weight` column. 

```{r no-1, exercise = TRUE}

```


```{r no-1-hint-1, eval = FALSE}
nhanes$...
```

```{r no-1-hint-2, eval = FALSE}
nhanes$weight
```

### Exercise 2

We will create a function that allows us to sample `weight` from a tibble that contains no NA values for any of its variables. To warm up, use `sample()` to sample 5 values from `nhanes$weight`.

```{r no-2, exercise = TRUE}

```


```{r no-2-hint-1, eval = FALSE}
sample(..., ...)
```

```{r no-2-hint-2, eval = FALSE}
sample(nhanes$..., size = ...)
```

### Exercise 3

Start a pipe with `nhanes`. Use `drop_na()` to get rid of any NA values.

```{r no-3, exercise = TRUE}

```

```{r no-3-hint, eval = FALSE}
... %>% 
  drop_na()
```

### Exercise 4

Copy/paste your code from above. Pipe the result to `sample_n()`, setting the `size` argument to 3. **Note**: that we are using `sample_n()` --- because we want all the rows from the tibble --- and not `sample()` --- which just gets values from a vector --- as we did in Exercise 2

```{r no-4, exercise = TRUE}

```

```{r no-4-hint, eval = FALSE}
... %>% 
  sample_n(size = ...)
```

### Exercise 5 

Copy/paste your code from above. Pipe the result to `pull()` with the argument `weight`. 

```{r no-5, exercise = TRUE}

```


```{r no-5-hint, eval = FALSE}
... %>% 
  pull(...)
```

### Exercise 6

The above code does what we want. Now we need to place it into a function. But, first, let's make a function `no_NA_sampler()` that doesn't do anything.

```{r no-6, exercise = TRUE}

```


```{r no-6-hint, eval = FALSE}
no_NA_sampler <- function(){
  
}
```

### Exercise 7

Copy/paste your code from above. Then, on the line below, call `no_NA_sampler()` to confirm that no output, beyond NULL, is returned. This is a common structure for tutorial questions going forward: define the function and then call the function you have, in this answer, just defined.

```{r no-7, exercise = TRUE}

```


```{r no-7-hint-1, eval = FALSE}
no_NA_sampler <- function(){
  
}

no_NA_sampler()
```

### Exercise 8

Copy/paste your code from Exercise 5 and place it inside the body `{ }` of `no_NA_sampler()`. Then, call `no_NA_sampler()`. 

```{r no-8, exercise = TRUE}

```


```{r no-8-hint-1, eval = FALSE}
no_NA_sampler <- function(){
  ...
}

no_NA_sampler()
```

### Exercise 9

Let's now adjust the code so we can pull any sample, not just 3! To do so, add the `n` argument inside `function()`. Also replace the 3 within `sample_n()` with `n`. 

```{r no-9, exercise = TRUE}

```


```{r no-9-hint-1, eval = FALSE}
no_NA_sampler <- function(...){
  nhanes %>% 
    drop_na() %>%
    sample_n(size = ...) %>% 
    pull(weight)
}
```

### Exercise 10

Copy/ paste your code from above. Then call `no_NA_sampler()`. Notice that you receive an error message. We will explain in the next exercise.

```{r no-10, exercise = TRUE}

```

```{r no-10-hint, eval = FALSE}
no_NA_sampler <- function(n){
  nhanes %>% 
    drop_na() %>%
    sample_n(size = n) %>% 
    pull(weight)
}

no_NA_sampler()
```

### Exercise 11

The error message suggested that we need to pass an argument for `n` when we call `no_NA_sampler()`. Call `no_NA_sampler()` setting the `n` argument to 5.

```{r no-11, exercise = TRUE}

```

```{r no-11-hint, eval = FALSE}
no_NA_sampler <- function(n){
  nhanes %>% 
    drop_na() %>%
    sample_n(size = n) %>% 
    pull(weight)
}

no_NA_sampler(n = ...)
```

Great. Now we can use `no_NA_sampler()` to get however many values of weight that we want!


### Exercise 12

Copy/paste your code from above. Let's adjust our function to allow sampling from any variable. To do so, add the `var` argument inside `function()`. Also replace `weight` within `pull()` with `{{var}}`. (See *The Primer* for a discussion of the magic associated with "{{}}")

```{r no-12, exercise = TRUE}

```


```{r no-12-hint-1, eval = FALSE}
no_NA_sampler <- function(n, ...){
  nhanes %>% 
    drop_na() %>%
    sample_n(size = n) %>% 
    pull(...)
}
```

```{r no-12-hint-2, eval = FALSE}
no_NA_sampler <- function(n, var){
  nhanes %>% 
    drop_na() %>%
    sample_n(size = n) %>% 
    pull({{var}})
}
```

### Exercise 13

Now call `no_NA_sampler()`. (Recall that you need to copy/paste the definition of the function into any answer which is using that function.) Recall that we will receive an error message if we don't specify the `n` and `var` arguments. Call `no_NA_sampler()` setting the `n` argument to 5 and `var` to `height`.


```{r no-13, exercise = TRUE}

```


```{r no-13-hint-1, eval = FALSE}
no_NA_sampler <- function(n, var){
  nhanes %>% 
    drop_na() %>%
    sample_n(size = n) %>% 
    pull({{var}})
}

no_NA_sampler(n = ..., var = ...)
```

### Exercise 14

Let's adjust our function one last time to now allow sampling from any tibble. (The code so far has been provided for you because we are nice.)  Add the `tbl` argument inside `function()`. Also replace `nhanes` with `tbl`.

```{r no-14, exercise = TRUE}
no_NA_sampler <- function(n, var){
  nhanes %>% 
    drop_na() %>%
    sample_n(size = n) %>% 
    pull({{var}})
}
```


```{r no-14-hint-1, eval = FALSE}
no_NA_sampler <- function(n, var, ...){
... %>% 
    drop_na() %>%
    sample_n(size = n) %>% 
    pull({{var}})
}
```

### Exercise 15

Great. Now call the `no_NA_sampler()` with the argument `n` set to 5. Also set `var` to `age` and set `tbl` to `cces`.

```{r no-15, exercise = TRUE}

```

```{r no-15-hint, eval = FALSE}
no_NA_sampler <- function(n, var, tbl){
  tbl %>% 
    drop_na() %>%
    sample_n(size = n) %>% 
    pull({{var}})
}

no_NA_sampler(n = ..., var = ..., tbl = ...)
```

Great work. `no_NA_sampler()` allows us to sample values from any variable in any tibble, after removing any rows with NA values. 

## Prediction Game
###

In this section, we will create a function called `prediction_game()`. It will return the name of the winner whose guess is closest to the sampled value.

### Exercise 1

Let's start by using `glimpse()` to look at `kenya`.

```{r pg-1, exercise = TRUE}

```

### Exercise 2

Assign the value 500 to the object `your_guess`. Then assign the value 600 to the object `my_guess`.

```{r pg-2, exercise = TRUE}

```

```{r pg-2-hint-1, eval = FALSE}
your_guess <- ...
my_guess <- ...
```

### Exercise 3

Copy/paste your code from above. Now call `no_NA_sampler()`, setting `tbl` to `kenya` and `var` to `rv13`. Also set the argument `n` to 1. Assign your code to an object named `sampled_value`.

```{r pg-3, exercise = TRUE}

```

```{r pg-3-hint-1, eval = FALSE}
your_guess <- 500
my_guess <- 600
sampled_value <- no_NA_sampler(..., ..., ...) 
```

### Exercise 4

Copy/paste your code from above. Let's now use `abs()` to calculate error for `your_guess`. Within `abs()`, subtract `sampled_value` from `your_guess`. Assign your code to an object named `your_error`.

```{r pg-4, exercise = TRUE}

```

```{r pg-4-hint, eval = FALSE}
...
your_error <- abs(... - ...)
```

### Exercise 5

Copy/paste your code from above. Now do the same for `my_guess`. Within `abs()`, subtract `sampled_value` from `my_guess`. Assign your code to an object named `my_error`.

```{r pg-5, exercise = TRUE}

```

```{r pg-5-hint-1, eval = FALSE}
...
your_error <- abs(... - ...)
```

```{r pg-5-hint-2, eval = FALSE}
Your code so far should look like this:

your_guess <- 500
my_guess <- 600
sampled_value <- no_NA_sampler(tbl = kenya, var = rv13, n = 1) 
your_error <- abs(your_guess - sampled_value)
my_error <- abs(my_guess - sampled_value)
```

### Exercise 6

Copy/paste your code from above. Use `if()` with the argument `my_error` set greater than `your_error`. Then call `cat()` with the argument "You win!".


```{r pg-6, exercise = TRUE}

```

```{r pg-6-hint-1, eval = FALSE}
...
if(... < ...) cat(...)
```

### Exercise 7

Copy/paste your code from above. Use `if()` with the argument `your_error` set greater than `my_error`. Then call `cat()` with the argument "I win!".

```{r pg-7, exercise = TRUE}

```

```{r pg-7-hint, eval = FALSE}
if(... > ...) cat(...)
```

Press "Run Code" a few times. You will see that the winner varies because there will be a new sampled guess each time.

### Exercise 8

Good work. The above code does what we want. Now we need to place it into a function. But, first, let's make a function called `prediction_game` that doesn't do anything.

```{r pg-8, exercise = TRUE}

```

```{r pg-8-hint, eval = FALSE}
prediction_game <- function(){
  
}
```

### Exercise 9

Copy/paste your code from Exercise 7 and place it inside the body `{ }` of `prediction_game()`. Then, call `prediction_game()`. 

```{r pg-9, exercise = TRUE}

```

```{r pg-9-hint, eval = FALSE}
prediction_game<- function() { 
your_guess <- 500
my_guess <- 600
  
sampled_value <- no_NA_sampler(tbl = kenya, var = rv13, n = 1) 
  
your_error <- abs(your_guess - sampled_value)
my_error <- abs(my_guess - sampled_value)
  
if(your_error < my_error) cat("You win!")
if(your_error > my_error) cat("I win!")

}

prediction_game()
```

### Exercise 10

Awesome. Copy/paste your code from above. On the line below, use `replicate()` to run our function multiple times. The first argument to `replicate()` should be 4. The second argument should be the function `prediction_game()`.


```{r pg-10, exercise = TRUE}

```

```{r pg-10-hint-1, eval = FALSE}
prediction_game <- function(){
...
}

replicate(..., ...)
```

```{r pg-10-hint-2, eval = FALSE}
prediction_game <- function(){
...
}

replicate(4, prediction_game())
```

Our function tells us *who* wins. What if we want our function print out the numerical guess that wins? For example, "Guess 500 wins!"


### Exercise 11

The code you have created so far has been provided below. Replace both `cat()` functions with the `return()` function. Then call `prediction_game()`.

```{r pg-11, exercise = TRUE}
prediction_game <- function(){
  your_guess <- 500
  my_guess <- 600
  
  sampled_value <- no_NA_sampler(tbl = kenya, var = rv13, n = 1) 
  
  your_error <- abs(your_guess - sampled_value)
  my_error <- abs(my_guess - sampled_value)
  
  if(your_error < my_error) cat("You win!")
  if(your_error > my_error) cat("I win!")
  
}

```

### Exercise 12

Great. Copy/paste your code from above. Now place the `return()` functions inside their own `{ }`. Then call `prediction_game()`.

```{r pg-12, exercise = TRUE}

```

```{r pg-12-hint-1, eval = FALSE}
...

 if(your_error < my_error) { 
   return("You win!")
 }
  if(your_error > my_error) { 
    return("I win!")
}
```

### Exercise 13

Let's change the input to each `return()` function. Within each `return()` statement, use the argument `paste()`. The first argument to `paste()` should be "Guess". The second argument should be `your_guess`(or `my_guess` based on the `if()` statement). The third argument should be "wins!". Then call `prediction_game()`.

```{r pg-14, exercise = TRUE}

```

```{r pg-14-hint-1, eval = FALSE}
...
  if(your_error < my_error){ 
    return(paste(..., your_guess, ...))
  }

   if(your_error > my_error){ 
    return(paste(..., my_guess, ...))
  }

prediction_game()
```

```{r pg-14-hint-2, eval = FALSE}
...
  if(your_error < my_error){ 
    return(paste("Guess", your_guess, "wins!"))
  }

   if(your_error > my_error){ 
    return(paste("Guess", my_guess, "wins!"))
  }
prediction_game()
```

So far, we have a function that tells us which guess (500 or 600) is closer to the sampled value guess for the variable `rv13` of the `kenya` tibble. Let’s now adjust our function to allow for any guesses to be passed in as an argument (not just 500 and 600). Also, let's allow any tibble and variable to be used! 


### Exercise 15

Copy/paste your code from above. Add the argument `guesses` inside `function()`. Then call `prediction_game()`. Notice that this will not change anything.

```{r pg-15, exercise = TRUE}

```

```{r pg-15-hint-1, eval = FALSE}
prediction_game <- function(...){
...
}
prediction_game()
```

### Exercise 16

Copy/paste your code from above. Replace the code assigned to `your_guess` with `guesses[1]`. Also replace the code assigned to `my_guess` with `guesses[2]`. Then call `prediction_game()`.

```{r pg-16, exercise = TRUE}

```

```{r pg-16-hint-1, eval = FALSE}
prediction_game <- function(guesses) {
your_guess <- guesses[1]
my_guess <- ...

...

}

prediction_game()
```

Oh no! We get the error. Recall from the previous section that we need to pass in arguments for whatever we place inside `function()`. So here, we must pass in `guesses` as an argument now whenever we call the function. 


### Exercise 17

Copy/paste your code from above. Call `prediction_game()`, setting the `guesses` argument to `c(430, 870)`.

```{r pg-17, exercise = TRUE}

```

### Exercise 18

Copy/paste your code from above. Let's now allow any tibble or variable to be passed as an argument. First, add the arguments `tbl` and `var`. 

Make sure you call `prediction_game()` with the same `guesses` argument specified as before.

```{r pg-18, exercise = TRUE}

```

```{r pg-18-hint-1, eval = FALSE}
prediction_game <- function(guesses,..., ... ){

 ...
}

prediction_game(guesses = c(430, 870))
```

### Exercise 19

Copy/paste your code from above. Change the input to `no_NA_sampler()`. The first argument to `no_NA_sampler()` should be `tbl`. The second argument should be `{{var}}`. Then set `n` to 1. 

```{r pg-19, exercise = TRUE}

```

```{r pg-19-hint-1, eval = FALSE}
prediction_game <- function(guesses, tbl, var){
 your_guess <- guesses[1]
 my_guess <- guesses[2]
 
 sampled_value <- no_NA_sampler(..., ..., ...) 
 
 ...
}

```

```{r pg-19-hint-2, eval = FALSE}
prediction_game <- function(guesses,tbl, var){
 your_guess <- guesses[1]
 my_guess <- guesses[2]
 
 sampled_value <- (tbl, {{var}}, n = 1)
 
 ...
}

```

Oh no! We get another error for not passing in arguments when we call `prediction_game()`.


### Exercise 20

Copy/paste your code from above. Recall that we must pass an argument also for `tbl` and `var` now whenever we call the function. Call `prediction_game()` , setting the `guesses` argument to `c(30, 18)`. Also set `tbl` to `cces` and `var` to `age`.


```{r pg-20, exercise = TRUE}

```


### Exercise 21

Let's now tell our function to stop if we do not select two guesses. Use `stopifnot()` with the argument `all()`. Within `all()` use the argument `is_double(guesses)`. Add the function above the code for `your_guess`.

We have provided the code you have completed so far.

```{r pg-22, exercise = TRUE}
prediction_game <- function(guesses, tbl, var){
  
  your_guess <- guesses[1]
  my_guess <- guesses[2]

  sampled_value <- no_NA_sampler(tbl, {{var}}, n = 1)

  your_error <- abs(your_guess - sampled_value)
  my_error <- abs(my_guess - sampled_value)

    if(your_error < my_error){
    return(paste("Guess", your_guess, "wins!"))
  }

   if(your_error > my_error){
    return(paste("Guess", my_guess, "wins!"))
  }
}
```

```{r pg-22-hint-1, eval = FALSE}
prediction_game <- function(guesses){
  
  stopifnot(...)
  
  ...
  
}

```

```{r pg-22-hint-2, eval = FALSE}
prediction_game <- function(guesses){
  
  stopifnot(all(is_double(guesses)))

 ...
}

```

### Exercise 21

Great. Now let's make sure we select guesses in the format of  c(guess 1, guess 2).  Copy/paste your code from above. Add another `stopifnot()` below the one you just created.  Within `stopifnot()` use`length()` with the argument `guesses`. Set the `length()` statement equal to 2.



```{r pg-21, exercise = TRUE}

```

```{r pg-21-hint-1, eval = FALSE}
prediction_game <- function(guesses){
  
  stopifnot(all(is_double(guesses)))
  stopifnot(... == ...)

 ...
 
}
```

```{r pg-21-hint-2, eval = FALSE}
prediction_game <- function(guesses){
  
  stopifnot(all(is_double(guesses)))
  stopifnot(length(guesses) == ...)
  
...

}

```


## Plotting Prediction Game
###

<!-- DK: Where is the plot? This needs a full plot and then enough questions to make the plot look nice. -->

Let's create the following plot using our previously created function `prediction_game()`.

```{r}


```

### Exercise 1

Let's start a pipe. Use `tibble()` with with one variable called `ID` . Have `ID` take on the values 1 though 1000.

```{r plot-1, exercise = TRUE}

```

```{r plot-1-hint, eval = FALSE}
tibble(ID = ...)
```

```{r plot-1-hint-2, eval = FALSE}
tibble(ID = 1:1000)
```

### Exercise 2 

Pipe the results above to `mutate()`. Use `mutate()` to create the variable `result` which is set to `map_chr()`. The first argument to `map_chr()` should be `ID`. The second argument should be `prediction_game()`, setting `guesses` to c(442, 539). Also set `tbl` to `kenya` and `var` to `rv13`.

```{r plot-2, exercise = TRUE}

```

```{r plot-2-hint-1, eval = FALSE}
Make sure you use a ~ before prediction_game()
```

```{r plot-2-hint-2, eval = FALSE}
... %>% 
  mutate(result = map_chr(..., 
                          ~ prediction_game(... , 
                                            ..., 
                                            ...)
```

### Exercise 3 

Continue your pipe with `ggplot()`. Map `result` to the x-axis. Add the layer `geom_bar()`. 

```{r plot-3, exercise = TRUE}

```

```{r plot-3-hint, eval = FALSE}
... %>% 
  ... %>% 
  ggplot(aes(...)) + 
  geom_bar()
```




```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
