---
title: "Probability A"
tutorial:
  id: "probability-a"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 5 tutorial Part A"
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)

joint_dist <- tibble(in_bag = rep(c(0, 1, 2), 1000)) %>%
  mutate(in_sample = map_int(in_bag, ~ rbinom(n = 1, 
                                              size = 3, 
                                              p = ./2))) 

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```


## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```



## Flipping a coin 
###


Let's create the following *empirical distribution* of flipping a fair coin. 

```{r}
emp_p <- tibble(results = rbinom(n = 100, size = 1, prob = 0.5)) %>%
  ggplot(aes(x = results)) +
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 binwidth = 0.5,
                 color = "white") +
  scale_x_continuous(breaks = c(0, 1),
                     labels = c("Heads", "Tails")) +
  scale_y_continuous(labels =
                      scales::percent_format(accuracy = 1)) +
  labs(title = "Mathematical Probability Distribution",
       subtitle = "Expectations for flipping a fair coin",
       x = "Outcome\nResult of Coin Flip",
       y = "Probability") +
  theme_classic()

emp_p
```

### Exercise 1

Let's simulate a fair coin, i.e. $p_h = p_t = 0.5$. To do so, use the function `rbinom()`. Recall `rbinom()` is used to draw from a binomial distribution (when there are only two possible outcomes). Within `rbinom()`, set `n` to 100, `size` to 1, and `prob` to .05.  

```{r fac-1, exercise = TRUE}

```

```{r fac-1-hint-1, eval = FALSE}
rbinom(... , ..., ....)
```

```{r fac-1-hint-2, eval = FALSE}
rbinom(n = ..., size = ..., prob = ....)
```

### Exercise 2

Create a `tibble()` with one variable `results` . Have `results` take on the values of the `rbinom()` code in the previous exercise.  

```{r fac-2, exercise = TRUE}

```

```{r fac-2-hint-1, eval = FALSE}
tibble(... = rbinom(..., ..., ...))
```

### Exercise 3

Pipe your results to `ggplot()`. Map `results` to the x-axis. Also add the layer `geom_histogram()`. 

```{r fac-3, exercise = TRUE}

```

```{r fac-3-hint-1, eval = FALSE}
... %>% 
  ggplot(mapping = aes(...) + 
  geom_histogram()
```

### Exercise 4

Within `geom_histogram()`, use `after_stat()` . Inside `after_stat()`, use `aes()` with the argument `y = count/sum(count)` to put percents on the y-axis.

```{r fac-4, exercise = TRUE}

```


```{r fac-4-hint, eval = FALSE}
... +
    geom_histogram(aes(y = after_stat(...) 
```

### Exercise 5

Also set `binwidth` to .5 and `color` to "white" within `geom_histrogram()`.

```{r fac-5, exercise = TRUE}

```

### Exercies 6

Now use `scale_x_continuous()` so the x-axis has `breaks` at 0 and 1. Set the `labels` for the breaks as "Heads" and "Tails", respectively. 


```{r fac-6, exercise = TRUE}

```

```{r fac-6-hint-1, eval = FALSE}
Use the c() function for specifying the breaks and labels.
```

```{r fac-6-hint-2, eval = FALSE}
... + 
  scale_x_continuous(breaks = c(..., ...),
                     labels = c(..., ...))
```

### Exercise 7

Now use `scale_y_continuous()` to put the x-axis in percent format. Within `scale_y_continuous()`, set `labels` to `scales::percent_format()`. Within `percent_format()` set `accuracy` to 1.

```{r fac-7, exercise = TRUE}

```

```{r fac-7-hint-1, eval = FALSE}
... + 
  scale_y_continuous(labels = scales::percent_format(...))
```

### Exercise 8

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.

```{r face-8, exercise = TRUE}

```

Reminder: Your plot should look similar to the the one below. **Note**: the height of the bars will vary because our `rbinom()` statements generate different proportions every time! 

```{r}
emp_p
```

###

Awesome! Remember, if were to increase the number of trials in our simulation, the empirical distribution would look more level like the mathematical distribution.

###

Let's now create the following *posterior distribution* of flipping a coin.

```{r}
post_p <- tibble(results = c(rep(0, 95),
                   rep(1, 5))) %>% 
ggplot(aes(x = results)) +
  geom_histogram(aes(y = after_stat(count/sum(count))), 
                 binwidth = 0.5, 
                 color = "white") +
  labs(title = "Posterior Probability Distribution",
       subtitle = "Your beliefs about flipping one coin to bet your friend",
       x = "Outcome\nResult of Coin Flip",
       y = "Probability") +
  scale_x_continuous(breaks = c(0, 1), 
                     labels = c("Heads", "Tails")) +
  scale_y_continuous(labels = 
                       scales::percent_format(accuracy = 1)) +
  theme_classic()

post_p

```


### Exercise 10

Suppose you believe that $\rho_h$ is 0.95 and $\rho_t$ is 0.05. Create a `tibble()` with one variable `results` . Have `results` set to the `c()` function with the arguments `rep(0, 95)` and `rep(1, 5)`.

```{r fac-10, exercise = TRUE}

```

```{r fac-10-hint-1, eval = FALSE}
tibble(results = c(rep(...),
                   rep(...)))
```

### Exercise 11

Pipe your results to `ggplot()`. Map `results` to the x-axis. Also add the layer `geom_histogram()`. 

```{r fac-11, exercise = TRUE}

```

```{r fac-11-hint-1, eval = FALSE}
... %>% 
  ggplot(mapping = aes(...) + 
  geom_histogram()
```

### Exercise 12

Within `geom_histogram()`, use `after_stat()` . Inside `after_stat()`, use `aes()` with the argument `y = count/sum(count)` to put percents on the y-axis.

```{r fac-12, exercise = TRUE}

```


```{r fac-12-hint, eval = FALSE}
... +
    geom_histogram(aes(y = after_stat(...) 
```

### Exercise 13

Also set `binwidth` to .5 and `color` to "white" within `geom_histrogram()`.

```{r fac-13, exercise = TRUE}

```

### Exercies 14

Now use `scale_x_continuous()` so the x-axis has `breaks` at 0 and 1. Set the `labels` for the breaks as "Heads" and "Tails", respectively. 


```{r fac-14, exercise = TRUE}

```

```{r fac-14-hint-1, eval = FALSE}
Use the c() function for specifying the breaks and labels.
```

```{r fac-14-hint-2, eval = FALSE}
... + 
  scale_x_continuous(breaks = c(..., ...),
                     labels = c(..., ...))
```

### Exercise 15

Now use `scale_y_continuous()` to put the y-axis in percent format. Within `scale_y_continuous()`, set `labels` to `scales::percent_format()`. Within `percent_format()` set `accuracy` to 1.

```{r fac-15, exercise = TRUE}

```

```{r fac-15-hint-1, eval = FALSE}
... + 
  scale_y_continuous(labels = scales::percent_format(...))
```

### Exercise 16

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.

```{r face-16, exercise = TRUE}

```

Reminder: This is what your plot should look like.

```{r}
post_p
```


### Three Models 
###

Let's create the following *joint distribution* of the number of white marbles in a bag and the number of white marbles pulled out in the sample.

```{r}
joint_p <- joint_dist %>%
  ggplot(aes(x = in_sample, y = in_bag)) +
    geom_jitter(alpha = 0.5) +
    labs(title = "Black and White Marbles",
         subtitle = "More white marbles in bag mean more white marbles selected",
         x = "White Marbles Selected",
         y = "White Marbles in the Bag") +
    scale_y_continuous(breaks = c(0, 1, 2)) +
  theme_classic()

joint_p
```

### Exercise 1

Create a `tibble()` with one variable `in_bag`. Have `in_bag` take on the values of `rep()`. Within `rep()` use the arguments 0, 1, and 2. 

```{r tm-1, exercise = TRUE}

```

```{r tm-1-hint-1, eval = FALSE}
tibble(in_bag = rep(c(..., ..., ...)))
```

Great. We now have generated the number of white marbles that exist in our bag. 

### Exercise 2

Great. Let's have our code run 1000 times. Add the argument 1000 to `rep()`

```{r tm-2, exercise = TRUE}

```

```{r tm-2-hint-1, eval = FALSE}
 tibble(in_bag = rep(c(0, 1, 2), ...))
```

### Exercise 3

Pipe your results to `mutate()` to create the variable `in_sample`. Set `in_sample` to the function `map_int()`. The first argument to `map_int()` should be `in_bag`. The second argument should be an `rbinom()` where `n` is set to 1, `size` is set to 3, and `p` is set to `./2`.

```{r tm-3, exercise = TRUE}

```

```{r tm-3-hint-1, eval = FALSE}
 ... %>% 
  mutate(in_sample = map_int(..., ~ rbinom(..., 
                                           ..., 
                                           ...)))
```

### Exercise 4

Copy/paste your code from above. Assign in to the object `joint_dist`.

```{r tm-4, exercise = TRUE}

```

```{r tm-4-hint-1, eval = FALSE}
 joint_dist <- ...
```

### Exercise 5

Pipe your `joint_dist` to `ggplot()`. Map `in_sample` to the x-axis and `in_bag` to the y-axis. Also add the layer `geom_jitter()`. 

```{r tm-5, exercise = TRUE}

```

```{r tm-5-hint-1, eval = FALSE}
joint_dist %>% 
  ggplot(aes(x = ..., y = ...)) +
    geom_jitter()
```

### Exercise 6

Set `alpha` to .5 within `geom_jitter()`. 

```{r tm-6, exercise = TRUE}

```

```{r tm-6-hint-1, eval = FALSE}
... +
    geom_jitter(...)
```

### Exercise 7

Now use `scale_y_continuous()` to break the y-axis into three values. Within `scale_y_continuous()`, set `breaks` to 0, 1, and 2.

```{r tm-7, exercise = TRUE}

```

```{r tm-7-hint-1, eval = FALSE}
... + 
  scale_y_continuous(breaks = c(..., ..., ...)
```

Why do we do this? Each value on the y-axis represents a different version or belief about the world.

### Exercise 8

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.

```{r tm-8, exercise = TRUE}

```

Reminder: This is what your plot should look like.

```{r}
joint_p
```


```{r tm-8-hint-1, eval = FALSE}

```

### 

Awesome. We can now see the number of simulations in each "bucket." Take note that this distribution is unnormalized.

###

Let's create the following *unnormalized conditional distribution*. This is essentially a slice of the joint distribution we previously created. 

```{r}
unnorm_p <- joint_dist %>% 
  filter(in_sample == 3) %>% 
  ggplot(aes(in_bag)) +
    geom_histogram(binwidth = 0.25, color = "white") +
    labs(title = "Unnormalized Conditional Distribution",
         subtitle = "Number of white marbles in bag given that three were selected in the sample",
         x = "Number of White Marbles in the Bag",
         y = "Count") +
    scale_x_continuous(breaks = seq(1, 2)) +
    theme_classic()

unnorm_p
```

### Exercise 9

`filter()` `joint_dist` for where `in_sample` is equal to 3.

```{r tm-9, exercise = TRUE}

```

```{r tm-9-hint-1, eval = FALSE}
joint_dist %>% 
  filter(in_sample == ...)
```

### Exercise 10

Pipe your code above to `ggplot()`. Map `in_bag` to the x-axis. Also add the layer `geom_histogram()`.

```{r tm-10, exercise = TRUE}

```

```{r tm-10-hint-1, eval = FALSE}
... %>% 
  ggplot(aes(...)) +
  geom_histogram()
```

### Exercise 11 

Set `binwidth` to .25 and `color` to "white" within `geom_histogram()`.

```{r tm-11, exercise = TRUE}

```

```{r tm-11-hint-1, eval = FALSE}
... +
  geom_histogram(..., ...)
```

### Exercise 12

Now use `scale_x_continuous()`. Set `breaks` to `seq()` that contains the values 1 and 2.

```{r tm-13, exercise = TRUE}

```

```{r tm-13-hint-1, eval = FALSE}
... +
  scale_x_continuous(... = seq(..., ...))
```

### Exercise 13

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.

```{r tm-14, exercise = TRUE}

```

Reminder: This is what your plot should look like.

```{r}
unnorm_p
```

### 

Let's create the following *normalized conditional distribution*. In other words, we are normalizing the graph we just created.

```{r}
norm_p <- joint_dist %>% 
  filter(in_sample == 3) %>% 
  ggplot(aes(in_bag)) +
    geom_histogram(aes(y = after_stat(count/sum(count))), 
                   binwidth = 0.25, 
                   color = "white") +
    labs(title = "Posterior Probability Distribution",
         subtitle = "Number of white marbles in bag given that three were selected in the sample",
         x = "Number of White Marbles in the Bag",
         y = "Probability") +
    scale_x_continuous(breaks = c(1, 2)) +
    scale_y_continuous(labels = 
                         scales::percent_format(accuracy = 1)) +
    theme_classic()

norm_p
```

### Exercise 14

We begin our code the same way we began our code for the *unnormalized conditional distribution*. We have provided the code for you below. To begin, add the `after_stat()` argument to `geom_histogram()`. Within `after_stat()`, use `aes()` with the argument `y = count/sum(count)` to put percents on the y-axis.


```{r tm-15, exercise = TRUE}
 joint_dist %>% 
  filter(in_sample == 3) %>% 
  ggplot(aes(in_bag)) +
    geom_histogram(binwidth = 0.25, color = "white")
```

```{r tm-15-hint-1, eval = FALSE}
... +
  geom_histogram(binwidth = 0.25, color = "white", ...)
```

### Exercies 15

Now use `scale_x_continuous()` so the x-axis has `breaks` at 1 and 2.

```{r tm-16, exercise = TRUE}

```

```{r tm-16-hint-1, eval = FALSE}
Use the c() function for specifying the breaks and labels.
```

```{r tm-16-hint-2, eval = FALSE}
... + 
  scale_x_continuous(breaks = c(..., ...))
```

### Exercise 16

Now use `scale_y_continuous()` to put the y-axis in percent format. Within `scale_y_continuous()`, set `labels` to `scales::percent_format()`. Within `percent_format()` set `accuracy` to 1.

```{r tm-17, exercise = TRUE}

```

```{r tm-17-hint-1, eval = FALSE}
... + 
  scale_y_continuous(labels = scales::percent_format(...))
```

### Exercise 17

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.

```{r tm-18, exercise = TRUE}

```

Reminder: This is what your plot should look like.

```{r}
norm_p
```


## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```

