---
title: "Probability"
tutorial:
  id: "probability"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 5 tutorial"
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

<!-- DK: Add some discussion, here and maybe in the chapter, about pdfs and random draws. A pdf can describe random draws and random draws can describe a pdf.   -->


## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```



## Flipping a coin 
###


Let's create the following *empirical distribution* of flipping a fair coin. 

```{r}
emp_p <- tibble(results = rbinom(n = 100, size = 1, prob = 0.5)) %>%
  ggplot(aes(x = results)) +
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 binwidth = 0.5,
                 color = "white") +
  scale_x_continuous(breaks = c(0, 1),
                     labels = c("Heads", "Tails")) +
  scale_y_continuous(labels =
                      scales::percent_format(accuracy = 1)) +
  labs(title = "Mathematical Probability Distribution",
       subtitle = "Expectations for flipping a fair coin",
       x = "Outcome\nResult of Coin Flip",
       y = "Probability") +
  theme_classic()

emp_p
```

### Exercise 1

Let's simulate a fair coin, i.e. $p_h = p_t = 0.5$. To do so, use the function `rbinom()`. Recall `rbinom()` is used to draw from a binomial distribution (when there are only two possible outcomes). Within `rbinom()`, set `n` to 100, `size` to 1, and `prob` to .05.  

```{r fac-1, exercise = TRUE}

```

```{r fac-1-hint-1, eval = FALSE}
rbinom(... , ..., ....)
```

```{r fac-1-hint-2, eval = FALSE}
rbinom(n = ..., size = ..., prob = ....)
```

### Exercise 2

Create a `tibble()` with one variable `results` . Have `results` take on the values of the `rbinom()` code in the previous exercise.  

```{r fac-2, exercise = TRUE}

```

```{r fac-2-hint-1, eval = FALSE}
tibble(... = rbinom(..., ..., ...))
```

### Exercise 3

Pipe your results to `ggplot()`. Map `results` to the x-axis. Also add the layer `geom_histogram()`. 

```{r fac-3, exercise = TRUE}

```

```{r fac-3-hint-1, eval = FALSE}
... %>% 
  ggplot(mapping = aes(...) + 
  geom_histogram()
```

### Exercise 4

Within `geom_histogram()`, use `after_stat()` . Inside `after_stat()`, use `aes()` with the argument `y = count/sum(count)` to put percents on the y-axis.

```{r fac-4, exercise = TRUE}

```


```{r fac-4-hint, eval = FALSE}
... +
    geom_histogram(aes(y = after_stat(...) 
```

### Exercise 5

Also set `binwidth` to .5 and `color` to "white" within `geom_histrogram()`.

```{r fac-5, exercise = TRUE}

```

### Exercies 6

Now use `scale_x_continuous()` so the x-axis has `breaks` at 0 and 1. Set the `labels` for the breaks as "Heads" and "Tails", respectively. 


```{r fac-6, exercise = TRUE}

```

```{r fac-6-hint-1, eval = FALSE}
Use the c() function for specifying the breaks and labels.
```

```{r fac-6-hint-2, eval = FALSE}
... + 
  scale_x_continuous(breaks = c(..., ...),
                     labels = c(..., ...))
```

### Exercise 7

Now use `scale_y_continuous()` to put the x-axis in percent format. Within `scale_y_continuous()`, set `labels` to `scales::percent_format()`. Within `percent_format()` set `accuracy` to 1.

```{r fac-7, exercise = TRUE}

```

```{r fac-7-hint-1, eval = FALSE}
... + 
  scale_y_continuous(labels = scales::percent_format(...))
```

### Exercise 8

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels. 

```{r face-8, exercise = TRUE}

```

Reminder: Your plot should look similar to the the one below. **Note**: the height of the bars will vary because our `rbinom()` statements generate different proportions every time! 

```{r}
emp_p
```

###

Awesome! Remember, if were to increase the number of trials in our simulation, the empirical distribution would look more level like the mathematical distribution.

###

Let's now create the following *posterior distribution* of flipping a coin.

```{r}
post_p <- tibble(results = c(rep(0, 95),
                   rep(1, 5))) %>% 
ggplot(aes(x = results)) +
  geom_histogram(aes(y = after_stat(count/sum(count))), 
                 binwidth = 0.5, 
                 color = "white") +
  labs(title = "Posterior Probability Distribution",
       subtitle = "Your beliefs about flipping one coin to bet your friend",
       x = "Outcome\nResult of Coin Flip",
       y = "Probability") +
  scale_x_continuous(breaks = c(0, 1), 
                     labels = c("Heads", "Tails")) +
  scale_y_continuous(labels = 
                       scales::percent_format(accuracy = 1)) +
  theme_classic()

post_p

```


### Exercise 10

Suppose you believe that $\rho_h$ is 0.95 and $\rho_t$ is 0.05. Create a `tibble()` with one variable `results` . Have `results` set to the `c()` function with the arguments `rep(0, 95)` and `rep(1, 5)`.

```{r fac-10, exercise = TRUE}

```

```{r fac-10-hint-1, eval = FALSE}
tibble(results = c(rep(...),
                   rep(...)))
```

### Exercise 11

Pipe your results to `ggplot()`. Map `results` to the x-axis. Also add the layer `geom_histogram()`. 

```{r fac-11, exercise = TRUE}

```

```{r fac-11-hint-1, eval = FALSE}
... %>% 
  ggplot(mapping = aes(...) + 
  geom_histogram()
```

### Exercise 12

Within `geom_histogram()`, use `after_stat()` . Inside `after_stat()`, use `aes()` with the argument `y = count/sum(count)` to put percents on the y-axis.

```{r fac-12, exercise = TRUE}

```


```{r fac-12-hint, eval = FALSE}
... +
    geom_histogram(aes(y = after_stat(...) 
```

### Exercise 13

Also set `binwidth` to .5 and `color` to "white" within `geom_histrogram()`.

```{r fac-13, exercise = TRUE}

```

### Exercies 14

Now use `scale_x_continuous()` so the x-axis has `breaks` at 0 and 1. Set the `labels` for the breaks as "Heads" and "Tails", respectively. 


```{r fac-14, exercise = TRUE}

```

```{r fac-14-hint-1, eval = FALSE}
Use the c() function for specifying the breaks and labels.
```

```{r fac-14-hint-2, eval = FALSE}
... + 
  scale_x_continuous(breaks = c(..., ...),
                     labels = c(..., ...))
```

### Exercise 15

Now use `scale_y_continuous()` to put the x-axis in percent format. Within `scale_y_continuous()`, set `labels` to `scales::percent_format()`. Within `percent_format()` set `accuracy` to 1.

```{r fac-15, exercise = TRUE}

```

```{r fac-15-hint-1, eval = FALSE}
... + 
  scale_y_continuous(labels = scales::percent_format(...))
```

### Exercise 16

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels. 

```{r face-16, exercise = TRUE}

```

Reminder: This is what your plot should look like.

```{r}
post_p
```


### Three Models 
###

Let's create the following *joint distribution* of the number of white marbles in a bag and the number of white marbles pulled out in the sample.

```{r}
joint_dist <- tibble(in_bag = rep(c(0, 1, 2), 1000)) %>%
  mutate(in_sample = map_int(in_bag, ~ rbinom(n = 1, 
                                              size = 3, 
                                              p = ./2))) 
joint_dist %>%
  ggplot(aes(x = in_sample, y = in_bag)) +
    geom_jitter(alpha = 0.5) +
    labs(title = "Black and White Marbles",
         subtitle = "More white marbles in bag mean more white marbles selected",
         x = "White Marbles Selected",
         y = "White Marbles in the Bag") +
    scale_y_continuous(breaks = c(0, 1, 2)) +
  theme_classic()

```


### Exercise 1

```{r tm-1, exercise = TRUE}

```

```{r tm-1-hint-1, eval = FALSE}

```


## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```

