---
title: N Parameters
tutorial:
  id: n-parameters
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: Chapter 11 tutorial
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
library(rstanarm)
library(skimr)
library(ggdist)


knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

# These models take awhile to build. 


ch_11 <- shaming %>% 
  filter(treatment %in% c("No Postcard", "Neighbors")) %>% 
  droplevels() %>% 
  mutate(solo = ifelse(hh_size == 1, TRUE, FALSE)) %>% 
  select(primary_06, treatment, solo, sex, age) %>% 
  slice_sample(n = 10000, replace = FALSE)

sham_1 <- stan_glm(data = ch_11, 
                 formula = primary_06 ~ treatment + age, 
                 refresh = 0)

sham_2 <- stan_glm(data = ch_11, 
                 formula = primary_06 ~ age + solo + treatment + solo * treatment,
                 refresh = 0)


treatment = c("Neighbors", "No Postcard")
solo = c(TRUE,FALSE)
age = c(30, 45, 60)

newobs <- expand_grid(treatment, solo, age) %>% 
  mutate(names = paste(treatment, solo, age, sep = "_"))

```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

<!-- WARNING! I think this tutorial is broken. Check out the warning message when you knit it: -->

<!-- Warning messages: -->
<!-- 1: Problem with `mutate()` column `Neighbors`. -->
<!-- ℹ `Neighbors = soloTRUE + soloTRUE:treatmentNeighbors`. -->
<!-- ℹ numerical expression has 4000 elements: only the first used  -->
<!-- 2: Problem with `mutate()` column `Neighbors`. -->
<!-- ℹ `Neighbors = soloTRUE + soloTRUE:treatmentNeighbors`. -->
<!-- ℹ numerical expression has 4000 elements: only the first used  -->


## EDA of shaming

### 

### Exercise 1

First `glimpse()` the `shaming` data to familiarize yourself with the variables.

```{r eda-of-shaming-1, exercise = TRUE}

```

### Exercise 2

Let’s focus on a subset of the data to work with. Start a pipe with `shaming`. `filter()` to where treatment is either "No Postcard" or "Neighbors".

```{r eda-of-shaming-2, exercise = TRUE}

```

```{r eda-of-shaming-2-hint-1, eval = FALSE}
When you filter(), consider using the %in% operator along with the function c()
```

### Exercise 3

Continue your pipe to `droplevels()`. Then use `mutate()` to create the variable `solo` which returns TRUE if `hh_size` is equal to 1. 


```{r eda-of-shaming-3, exercise = TRUE }

```

```{r eda-3-hint, eval = FALSE }
... %>% 
  mutate(solo = ifelse(hh_size == 1, TRUE, FALSE)) 
```

### Exercise 4

Continue the pipe and `select()` the variables `primary_06`, `treatment`, `solo`, `sex` and `age`. 

```{r eda-of-shaming-4, exercise = TRUE }

```

```{r eda-4-hint, eval = FALSE }
shaming %>% 
  filter(treatment %in% c("No Postcard", "Neighbors")) %>% 
  droplevels() %>% 
  mutate(solo = ifelse(hh_size == 1, TRUE, FALSE)) %>% 
  select(..., ..., ...., ..., ...)
```

### Exercise 5

Finally, let's limit our observations to 10,000 rows. To do so, use `sample_n()` and set the `n` argument to 10,000. Also set `replace` to FALSE. Save the results of your code to an object named `ch_11`.

```{r eda-of-shaming-5, exercise = TRUE }

```

```{r eda-5-hint, eval = FALSE }
ch_11 <- shaming %>% 
  filter(treatment %in% c("No Postcard", "Neighbors")) %>% 
  droplevels() %>% 
  mutate(solo = ifelse(hh_size == 1, TRUE, FALSE)) %>% 
  select(primary_06, treatment, solo, sex, age) %>% 
  slice_sample(...,...)
```

## Wisdom

### 

Consider the following question: 

*What is the influence on different types of postcards on the likelihood of voting for various types of people who live alone?*

Using **Wisdom**, write a paragraph about whether or not this data --- which covers voter turnout for the primary election in 2006 --- is relevant for the problem we face. See *The Primer* for guidance.

```{r wisdom-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    rows = 6)
```

## I. Justice and Courage

### 

Let’s build a model.The outcome variable will be `primary_06`, which represents whether a citizen voted or not. We will model `primary_06` against the `age` and `treatment` variables to see if there is a connection.

### Exercise 1

Let's implement the model using `stan_glm()`. The `formula` argument should be `primary_06 ~ treatment + age`. Set `data` to`ch_11`, and `refresh` to 0. Save your results to an object named `sham_1`.


```{r i-justice-and-courag-1, exercise = TRUE}

```

```{r i-justice-and-courag-1-hint-1, eval = FALSE}
sham_1 <- stan_glm(data = ...,
                  formula = ...,
                  refresh = ...)
```

### Exercise 2

Use `print()` to look at our parameter values. Set the `detail` argument to FALSE.

```{r i-justice-and-courag-2, exercise = TRUE}

```

```{r i-justice-and-courag-2-hint-1, eval = FALSE}
print(sham_1, detail = ...)
```

### Exercise 3

Look at the results above. Write two sentences, using your own words, that explain the meaning of the Median value of `(Intercept)`.

```{r i-justice-and-courag-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    rows = 3)
```

### Exercise 4

Now write two sentences that explains how you calculate the percent voting in the Neighbors group.

```{r i-justice-and-courag-4}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    rows = 3)
```

### Exercise 5

Let’s model the following posterior probability distribution for the rates of voting.

```{r}
sham_p <- sham_1 %>% 
  as_tibble() %>% 
  mutate(Neighbors = `(Intercept)` + treatmentNeighbors) %>% 
  mutate(`No Postcard` = `(Intercept)`) %>% 
  select(Neighbors, `No Postcard`) %>% 
  pivot_longer(cols = Neighbors:`No Postcard`,
               names_to = "parameters",
               values_to = "percent_voting") %>% 
  ggplot(aes(percent_voting, fill = parameters)) +
  geom_histogram(aes(y = after_stat(count/sum(count))),
                   alpha = 0.5, 
                   bins = 100, 
                   position = "identity") +
    labs(title = "Posterior Probability Distribution",
         subtitle = "for No Postcard versus Neighbors voting rates",
         x = "% of group voting",
         y = "Probability") + 
    scale_x_continuous(labels = scales::number_format()) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()

sham_p
```

### Exercise 6

Start a pipe with `sham_1` and use `as_tibble()`

```{r i-justice-and-courag-6, exercise = TRUE}

```

```{r i-justice-and-courag-6-hint-1, eval = FALSE}
sham_1 %>%
  as_tibble()
```

### Exercise 7

Continue the pipe and use `mutate()` to create the variable `Neighbors`, which is equal to the following argument: `(Intercept)` + `treatmentNeighbors`. Make sure you place backticks around (Intercept).

```{r i-justice-and-courag-7, exercise = TRUE}

```

```{r i-justice-and-courag-7-hint-1, eval = FALSE}
sham_1 %>%
  as_tibble() %>%
  mutate(Neighbors = ... + treatmentNeighbors)
```

### Exercise 8

Continue your pipe with `mutate()` to create the variable `No Postcard` which is equal to `(Intercept)`. Make sure you place backticks around (Intercept).

```{r i-justice-and-courag-8, exercise = TRUE}

```

```{r i-justice-and-courag-8-hint-1, eval = FALSE}
... %>% 
  mutate(`No Postcard` = ...)
```

### Exercise 9

Now `select()` the variables `No Postcard` and `Neighbors`.

```{r i-justice-and-courag-9, exercise = TRUE}

```

```{r i-justice-and-courag-9-hint-1, eval = FALSE}
... %>%
 select(...,...)
```

### Exercise 10

Pipe your results to `pivot_longer()`. Within `pivot_longer()`, set `names_to` to "parameters" and set `cols` to`Neighbors:No Postcard`.Also `values_to` should be set to "percent_voting".

```{r i-justice-and-courag-10, exercise = TRUE}

```

```{r i-justice-and-courag-10-hint-1, eval = FALSE}
... %>%
  pivot_longer(cols = ...,
               names_to = ...,
               values_to = ...)
```

### Exercise 11

Pipe the results to `ggplot()`. Map `percent_voting` to the x-axis, and map `parameters` to the  `fill` aesthetic. Use `geom_histogram()` with the same tricks we use in the chapter: `after_stat()`, `bins`, `alpha` and `position`.

```{r i-justice-and-courag-11, exercise = TRUE}

```

```{r i-justice-and-courag-11-hint-1, eval = FALSE}
... %>%
  ggplot(aes(..., fill = ...)) +
    geom_histogram(aes(y = after_stat(.../sum(...))),
                   bins = 100,
                   alpha = 0.5,
                   position = "identity")
```

### Exercise 12

Use `labs()` to add the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.

```{r i-justice-and-courag-12, exercise = TRUE}

```

### Exercise 13

Now use `scale_x_continuous()` to put the y-axis in percent format. Within `scale_x_continuous()`, set `labels` to `scales::number_format()`.


```{r i-justice-and-courag-13, exercise = TRUE}

```

```{r i-justice-and-courag-13-hint-1, eval = FALSE}
... +
  scale_x_continuous(labels = ...)
```

### Exercise 14

Now use `scale_y_continuous()` to put the y-axis in percent format. Within `scale_y_continuous()`, set `labels` to `scales::percent_format()`.

Reminder: This is what your plot should look like.

```{r}
sham_p
```

```{r i-justice-and-courag-14, exercise = TRUE}

```

```{r i-justice-and-courag-14-hint-1, eval = FALSE}
... +
  scale_y_continuous(labels = ...)
```

### Exercise 15

In two sentences, provide an interpretation of the graph you just created.

```{r i-justice-and-courag-15}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    rows = 3)
```

## II. Justice and Courage

### 

Let's build a model with N parameters! We will look at the `primary_06` variable as a function of `age`, `solo`, `treatment`, and the interaction between `solo` and `treatment` (i.e. solo*treatment). 

### Exercise 1

Let's implement the model using `stan_glm()`. The `formula` argument should be `primary_06 ~ age + solo + treatment + solo * treatment`. Set `data` to`ch_11`, and `refresh` to 0. Save your results to an object named `sham_2`.


```{r ii-justice-and-coura-1, exercise = TRUE}

```

```{r ii-justice-and-coura-1-hint-1, eval = FALSE}
There should be three arguments to stan_glm()
```

### Exercise 2

Use `print()` to look at our parameter values. Set the `digits` argument to 3.

```{r ii-justice-and-coura-2, exercise = TRUE}

```

```{r ii-justice-and-coura-2-hint-1, eval = FALSE}
print(sham_2, digits = ...)
```

### Exercise 3

Look at the results above. Write two sentences, using your own words, that explain the meaning of the value for `soloTRUE:treatmentNeighbors`.

```{r ii-justice-and-coura-3}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    rows = 3)
```

### Exercise 4

Let's create the following posterior distribution for the likeliness of voting for people who live alone.

```{r}
sham2_p <- sham_2 %>% 
  as_tibble() %>% 
  mutate(`No Postcard` = soloTRUE) %>% 
  mutate(Neighbors = soloTRUE + soloTRUE:treatmentNeighbors) %>% 
  select(Neighbors, `No Postcard`) %>% 
  pivot_longer(cols = Neighbors:`No Postcard`,
               names_to = "parameters",
               values_to = "percent_voting") %>% 
  ggplot(aes(percent_voting, fill = parameters)) +
  geom_histogram(aes(y = after_stat(count/sum(count))),
                   alpha = 0.5, 
                   bins = 100, 
                   position = "identity") +
    labs(title = "Posterior Probability Distribution for Solo Households",
         subtitle = "Solo households with Neighbors treatment are more likely to vote",
         x = "% of group voting",
         y = "Probability") + 
    scale_x_continuous(labels = scales::number_format()) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()

sham2_p
```

### Exercise 5

Start a pipe with `sham_2` and use `as_tibble()`

```{r ii-justice-and-coura-5, exercise = TRUE}

```

```{r ii-justice-and-coura-5-hint-1, eval = FALSE}
sham_2 %>%
  as_tibble()
```

### Exercise 6

Continue the pipe and use `mutate()` to create the variable `No Postcard`, which should be equal to soloTRUE.

```{r ii-justice-and-coura-6, exercise = TRUE}

```

```{r ii-justice-and-coura-6-hint-1, eval = FALSE}
sham_2 %>%
  as_tibble() %>%
  mutate(...)
```

### Exercise 7

Continue the pipe and use `mutate()` to create the variable `Neighbors`, which should be equal to the following argument: soloTRUE + soloTRUE:treatmentNeighbors.

```{r ii-justice-and-coura-7, exercise = TRUE}

```

```{r ii-justice-and-coura-7-hint-1, eval = FALSE}
sham_2 %>%
  as_tibble() %>%
  mutate(Neighbors = ... + `treatmentNeighbors`)
```

### Exercise 8

Now `select()` the variables `No Postcard` and `Neighbors`.

```{r ii-justice-and-coura-8, exercise = TRUE}

```

```{r ii-justice-and-coura-8-hint-1, eval = FALSE}
... %>%
 select(...,...)
```

### Exercise 9

Pipe your results to `pivot_longer()`. Within `pivot_longer()`, set `cols` to `Neighbors:No Postcard`. Also set `names_to` to "parameters" and `values_to` should be set to "percent_voting".

```{r ii-justice-and-coura-9, exercise = TRUE}

```

```{r ii-justice-and-coura-9-hint-1, eval = FALSE}
... %>%
  pivot_longer(cols = ...,
               names_to = ...,
               values_to = ...)
```

### Exercise 10

Pipe the results to `ggplot()`. Map `percent_voting` to the x-axis, and map `parameters` to the  `fill` aesthetic. Use `geom_histogram()` with the same tricks we use in the chapter: `after_stat()`, `bins`, `alpha` and `position`.

```{r ii-justice-and-coura-10, exercise = TRUE}

```

```{r ii-justice-and-coura-10-hint-1, eval = FALSE}
... %>%
  ggplot(aes(..., fill = ...)) +
    geom_histogram(aes(y = after_stat(.../sum(...))),
                   bins = 100,
                   alpha = 0.5,
                   position = "identity")
```

### Exercise 11

Use `labs()` to add the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.


```{r ii-justice-and-coura-11, exercise = TRUE}

```

### Exercise 12

Now use `scale_x_continuous()` to put the y-axis in percent format. Within `scale_x_continuous()`, set `labels` to `scales::number_format()`.


```{r ii-justice-and-coura-12, exercise = TRUE}

```

```{r ii-justice-and-coura-12-hint-1, eval = FALSE}
... +
  scale_x_continuous(labels = ...)
```

### Exercise 13

Now use `scale_y_continuous()` to put the y-axis in percent format. Within `scale_y_continuous()`, set `labels` to `scales::percent_format()`.

Reminder: This is what your plot should look like.

```{r}
sham2_p
```

```{r ii-justice-and-coura-13, exercise = TRUE}

```

```{r ii-justice-and-coura-13-hint-1, eval = FALSE}
... +
  scale_y_continuous(labels = ...)
```

## Temperance 

### 

Consider: 

*What is the influence on different types of postcards on the likelihood of voting for various types of people who live alone?*


Let's create the following posterior probability distribution. 

**Note:** The types of people included in this distribution are people who are 30, 45, 60 years old. For every age, each treatment (Neighbors and No Postcard) and living situation (lives alone or not) is accounted for. 

```{r}
treatment <- c("Neighbors", "No Postcard")
solo <- c(TRUE,FALSE)
age <- c(30, 45, 60)

newobs <- expand_grid(treatment, solo, age) %>% 
  mutate(names = paste(treatment, solo, age, sep = "_"))
  
temp_p <- posterior_epred(sham_2,
                      newdata = newobs) %>%
  as_tibble() %>%
  set_names(newobs$names) %>% 
  mutate(solo_30       = Neighbors_TRUE_30 - `No Postcard_TRUE_30`,
         `not-solo_30` = Neighbors_FALSE_30 - `No Postcard_FALSE_30`,
         solo_45       = Neighbors_TRUE_45 - `No Postcard_TRUE_45`,
         `not-solo_45` = Neighbors_FALSE_45 - `No Postcard_FALSE_45`,
         solo_60       = Neighbors_TRUE_60 - `No Postcard_TRUE_60`,
         `not-solo_60` = Neighbors_FALSE_60 - `No Postcard_FALSE_60`) %>% 
  select(solo_30:`not-solo_60`) %>% 
  pivot_longer(names_to = "Group",
               values_to = "Treatment_Effect",
               cols = everything()) %>% 
 separate(Group, c("Solo", "Age"), "_") %>% 
  ggplot(aes(x = Treatment_Effect, y = Age, alpha = .5, fill = Solo)) +
           stat_slab() +
           guides(alpha = FALSE) +
  labs(title = "Treatment Effects of Different Post Cards on Various Types of People",
       subtitle = "Postcards are more effective on people who live alone",
       x = "Treatment Effect",
       y = "Age")
  
temp_p
```

### Exercise 1

We want to make sure our data includes every possible combination. To do so, let's start by creating three separate objects that includes the information what we want to combine. The first object should be `treatment`, which is equal to "Neighbors" and "No Postcard". The second object should be `solo` , which is set to TRUE and FALSE. THe third object should be `age` which is set to 30,45,60.

```{r temperance-1, exercise = TRUE}

```

```{r temperance-1-hint-1, eval = FALSE}
treatment <- c("Neighbors", "No Postcard")
solo <- c(..., ...)
age <- c(..., ..., ...)
```

### Exercise 2

Great. The function `expand_grid()` allows us to create a tibble from all combinations of inputs, which is our goal as stated above. Use `expand_grid()` with the arguments `treatment`, `solo`, and `age`. 

```{r temperance-2, exercise = TRUE}

```

```{r temperance-2-hint-1, eval = FALSE}
expand_grid(..., ..., ...)
```

### Exercise 3

Pipe the results to `mutate()`. Within `mutate()` set `names` to the function `paste()`. Within `paste()` use the arguments `treatment`, `solo`, and `age`. Also, set `sep` to "_". Save your code to an object named `newobs`.


```{r temperance-3, exercise = TRUE}

```

```{r temperance-3-hint-1, eval = FALSE}
newobs <- expand_grid(treatment, solo, age) %>% 
  mutate(names = paste(..., ... , ..., sep = "_"))
```

### Exercise 4

Great. Now use `posterior_epred()`. The first argument to `posterior_epred()` should be `sham_2`. Also set `newdata` to `newobs`.

```{r temperance-4, exercise = TRUE}

```

```{r temperance-4-hint-1, eval = FALSE}
posterior_epred(sham_2,
                newdata = newobs)
```

### Exercise 5

Pipe the results of `posterior_epred()` to `as_tibble()`. Also, use the function `set_names()` with the argument `newobs$names`. 


```{r temperance-5, exercise = TRUE}

```

```{r temperance-5-hint-1, eval = FALSE}
... %>%
  as_tibble() %>%
  set_names(newobs$names)
```

### Exercise 6

Continue the pipe with `mutate()` and create a variable for each treatment effect. There should be six treatment effects in total (solo and not solo for every age). See *hint* for an example of what the first two treatment effects could look like.


```{r temperance-6, exercise = TRUE}

```

```{r temperance-6-hint-1, eval = FALSE}
... %>% 
    mutate(solo_30 = Neighbors_TRUE_30 - `No Postcard_TRUE_30`,
         `not-solo_30` = Neighbors_FALSE_30 - `No Postcard_FALSE_30`)
```

```{r temperance-6-hint-2, eval = FALSE}
Note: We use back ticks with `not-solo_60` because the hyphen - is an irregular character so we need to tell R to ignore it. We cannot use two underscores in the names because it will conflict with code we use later.
```

### Exercise 7

Great. Now continue your pipe and use `select()` to grab all the treatment effect variables you just created. You can use the `:` shortcut rather than writing out all the names. For example, if the first treatment effect variables you created was `solo_30` and the last one you created was ``not-solo_60``, your code would look like: select(solo_30: `not-solo_60`).

```{r temperance-7, exercise = TRUE}

```

```{r temperance-7-hint-1, eval = FALSE}

```

### Exercise 8

Pipe your results to `pivot_longer()`. Set `names_to` to "Group", `values_to` to "Treatment_Effect", and `cols` to `everything().

```{r temperance-8, exercise = TRUE}

```

```{r temperance-8-hint-1, eval = FALSE}
... %>% 
  pivot_longer(names_to = ...,
               values_to = ...,
               cols = ...)
```

### Exercise 9

The function `separate()` turns one column into multiple columns. Continue your pipe and use `separate()`. The first argurment to `separate()` should be `Group`. The second argument should be c("Solo", "Age"). The third argument should be ` "_", which tells R what each column should be separated by. 

```{r temperance-9, exercise = TRUE}

```

```{r temperance-9-hint-1, eval = FALSE}
 ... %>% 
 separate(Group, c("Solo", "Age"), "_") 
```

### Exercise 10

Now pipe your results to `ggplot()`. Map `Treatment_Effect` to the x-axis and `Age` to the y-axis. Map `Solo` to `fill` and set alpha to .5. Also add the layer `stat_slab()`. Note: `stat_slab()` acts like geom which does all the work to create the graphic. 


```{r temperance-10, exercise = TRUE}

```

```{r temperance-10-hint-1, eval = FALSE}
%>% 
  ggplot(aes(..., ..., ..., ...) +
           stat_slab()
```

### Exercise 11

Now add the layer `guides()` and set the `alpha` argument to FALSE.

<!-- BG: should we explain what guides means here? -->

```{r temperance-11, exercise = TRUE}

```

```{r temperance-11-hint-1, eval = FALSE}
... +
  guides(alpha = FALSE)
```

### Exercise 12

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels to your graph.

Reminder: This is what your graph should look like. 

```{r}
temp_p
```

```{r temperance-12, exercise = TRUE}

```

### Exercise 13

Great! Now write a paragraph that interprets the graph you just created.

```{r temperance-13}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    rows = 6)
```

```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
