---
title: "One Parameter: Overview"
author: Ryan Southward and Mann Talati
tutorial:
  id: one-parameter-overview
output:
  learnr::tutorial:
    progressive:  true
    allow_skip::  true
runtime: shiny_prerendered
description: Chapter 6 tutorial
---

<!-- Make it more like the chapter, and the chapter more like it. -->

<!-- Need one more section which using the posterior to, for example, create the posterior of number red which will be drawn with a shovel of size 20. Use a posterior to create a new posterior. Turtles all the way down. Could also create the plot of the joint distribution. Try to teach again just what a joint distribution. -->

<!-- Maybe make the shovels_100 have 100 shovel sizes again? We cut that down to make it quicker, but maybe having 100 reps instead of a 1,000 was enough to solve our speed problem. Done -->

<!-- Should we do something with stan_glm? Probably. -->

<!-- RS: Add graph of sampling distributions from shovels of size 25, 50, and 100 but using re factored code!! -->

<!-- RS: Add to 100 shovels graph to overlay theoretical standard deviation using equations. (Call this section standard deviation). -->

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(tidyverse)
library(rstanarm)
library(gt)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 

# Key Data

set.seed(10)
urn <- tibble(color = c(rep("red", 400), rep("white", 600))) |>
  sample_frac() |> 
  mutate(bead_ID = 1:1000) 

virtual_samples <- tibble(trial_ID = 1:1000) |> 
  mutate(shovel = map(trial_ID, ~ sample_n(urn, size = 50))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) |> 
  mutate(numb_beads = map_int(shovel, ~ length(.$color))) |> 
  mutate(prop_red = numb_red / numb_beads)

shovels_100 <- expand_grid(trial_ID = 1:100, shovel_size = 1:100) |> 
  mutate(shovel = map(shovel_size, ~ slice_sample(urn, n = .))) |> 
  mutate(numb_red = map_int(shovel, ~ sum(.$color == "red"))) |> 
  mutate(prop_red = numb_red / shovel_size) |> 
  group_by(shovel_size) |> 
  summarize(st_dev_p_hat = sd(prop_red)) 

shovel_p <- shovels_100 |>
 ggplot(aes(x = shovel_size, y = st_dev_p_hat)) +
 geom_point() +
 labs(title = "Sampling Variation",
      subtitle = "Larger samples have less variation",
      x = "Shovel size",
      y = "Standard deviation of the proportion red")

fit_1 <- read_rds("data/fit_1.rds")

ppd_for_p <- posterior_epred(fit_1, 
            newdata = tibble(constant = 1)) |> 
  as_tibble() |>
  rename(p = `1`)

ppd_plot <- ppd_for_p |>
  ggplot(aes(x = p)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 50) + 
    labs(title = "Posterior Probability Distribution",
         subtitle = "Distribution is centered at .34",
         x = "Proportion p of Red Beads in Urn",
         y = "Probability") + 
  
    scale_x_continuous(labels = scales::number_format()) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()

#rstanarm stuff:

urn_data <- tibble(red = c(rep(1, 17), rep(0, 33)))

#fit_1 <- stan_glm(formula = red ~ 1, 
#                   data = tibble(red = c(rep(1, 17), 
#                                        rep(0, 33))),
#                  family = binomial,
#                   refresh = 0,
#                   seed = 10) 
# 
#write_rds(iop_fit, "data/fit_1.rds")

ppd_reds_in_20 <- posterior_predict(fit_1, 
                    newdata = tibble(constant = rep(1, 20))) |> 
  as_tibble() |> 
  mutate(total = rowSums(across(`1`:`20`))) |>
  select(total) |>
  mutate(above_eight = ifelse(total > 8, TRUE, FALSE))
```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

## Introduction
###

This tutorial covers [Chapter 3](https://ppbds.github.io/primer/06-one-parameter.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/). This tutorial will review topics including One Parameter, shovel method, virtual sampling, standard error, cardinal virtues (wisdom, justice, courage, and temperance), and a case study.

## Virtual Sampling Through a Similar Real Sampling Activity
###

In this section, we mimic this physical sampling with virtual sampling, using a computer. In a real sampling activity, we would perform a tactile sampling activity. In this we use a physical urn of beads and a physical shovel which is done by hand so that we could develop our intuition about the ideas behind sampling. 

### 

Let's create the following plot that shows sampling variation for 1000 samples from an urn that contains red and white beads.

```{r}
virtual_samples |> 
  ggplot(aes(x = prop_red)) +
    geom_histogram(binwidth = 0.01, 
                   boundary = 0.4, 
                   color = "white") +
    labs(x = expression(hat(p)), 
         y = "Count",
         title = "Distribution of 1,000 proportions red") 
```

### Exercise 1

Create a `urn` variable on the second line that is set to a `tibble()`. Within the `tibble()` set `color` to the combination of `rep("red", 400)` and `rep("white", 600)`.

```{r 32-virtual-sampling-1, exercise = TRUE}
set.seed(10)

```

```{r 32-virtual-sampling-1-hint, eval = FALSE}
set.seed(10)
urn <- tibble(... = c(rep("...", ...), 
                        rep("...", ...)))
```

###

`set.seed()` ensures that the beads in our virtual urn are always in the same order. This ensures that the figures in the book match their written descriptions. We want 40% of the beads to be red. The `rep()` function will repeat the first argument a number of times specified by the second argument. We then combine our 400 red beads and 600 white beads using `c()`.

### Exercise 2

Within the `urn` variable start a pipe and set it to `sample_frac()`.

```{r 32-virtual-sampling-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r 32-virtual-sampling-2-hint, eval = FALSE}
urn <- ... |>
          sample_frac()
```

###

`sample_frac()` keeps all the rows in the tibble but rearranges their order. We don't need to do this. A virtual urn does not care about the order of the beads. But we find it aesthetically pleasing to mix them up.

### Exercise 3

Finish the pipe with `mutate()` and set `bead_ID` to 1 through 1000.

```{r 32-virtual-sampling-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r 32-virtual-sampling-3-hint, eval = FALSE}
urn <- ... |>
          mutate(... = 1:1000)
```

###

The first variable `bead_ID` is used as an identification variable. None of the beads in the actual urn are marked with numbers. The second variable `color` indicates whether a particular virtual bead is red or white.

### Exercise 4

To simulate the process of real-world sampling, let’s take a sample of 50 beads from our virtual urn. To do so, create a `tibble()` that has one variable `trial_ID` that takes on the values 1 to 1000.

```{r virtual_sampling-4, exercise = TRUE}

```

```{r virtual_sampling-4-hint-1, eval = FALSE}
tibble(trial_ID = ...)
```

```{r virtual_sampling-4-hint-2, eval = FALSE}
Use the : operator to create a range of integers.
```

### Exercise 5

Now pipe your results to the function `mutate()` to create the variable `shovel`, which is set to the function `map()`. The first argument to `map()` should be `trial_ID`. The second argument should use `slice_sample()`. Within `slice_sample()`, the first argument should be `urn` (the data we want to sample from), and then set `n` equal to our sample size (we want a sample size of 50). 

```{r virtual_sampling-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual_sampling-5-hint-1, eval = FALSE}
... |> 
  mutate(shovel = map(..., ~ ...))
```

```{r virtual_sampling-5-hint-2, eval = FALSE}
... |> 
  mutate(shovel = map(..., ~slice_sample(urn, n = ...)))
```

###

The advantage of modern technology is that we can use virtual simulation as many times as we choose, so we have no restrictions on resources. No longer are the days where we have to recruit our friends to tirelessly sample from the physical urn.

### Exercise 6

Continue your pipe with `mutate()` to create the variable `numb_red`. Set `numb_red` to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `sum()` of where `.$color` is equal to red.

```{r virtual_sampling-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual_sampling-6-hint-1, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~...))
```

```{r virtual_sampling-6-hint-2, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~ sum(.$color == "red")))
```

###

R evaluates if `color == red`, and treats `TRUE` values like the number `1` and `FALSE` values like the number `0`. So summing the number of `TRUE`s and `FALSE`s is equivalent to summing `1`’s and `0`’s. In the end, this operation counts the number of beads where `color` equals “red”.

### Exercise 7

Use `mutate()` one last time to create the variable `prop_red`. Set `prop_red` to `numb_red` divided by the sample size (in this exercise we are using a set sample size of 50).

```{r virtual_sampling-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual_sampling-7-hint-1, eval = FALSE}
... |> 
   mutate(prop_red = ... / ...)
```

###

`prop_red` estimate's our proportion of red beads in the urn.

### Exercise 8

Assign your code from above to an object named `virtual_samples`.

```{r virtual_sampling-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual_sampling-8-hint-1, eval = FALSE}
Use the assignment operator <-  to do so.
```

### Exercise 9

Now start a pipe with `virtual_samples`. Use `ggplot()` to map `prop_red` to the x-axis.

```{r virtual_sampling-9, exercise = TRUE}

```

```{r virtual_sampling-9-hint-1, eval = FALSE}
virtual_samples |> 
  ggplot(aes(...))
```

### Exercise 10

Add the layer `geom_histogram()` to create a histogram of our data.

```{r 32-virtual-sampling-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r 32-virtual-sampling-10-hint, eval = FALSE}
... +
  geom_histogram()
```

### Exercise 11

Within `geom_histrogram()` set `binwidth` to .01, `boundary` to .4, and `color` to "white".

```{r virtual_sampling-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r virtual_sampling-11-hint-1, eval = FALSE}
... +
  geom_histrogram(binwidth = ..., boundary = ..., color = ...)
```

###

Recall that `p` is equal to the proportion of beads which are red in each sample.

### Exercise 12

To finish, use `labs()` to give your graph the appropriate title and axis labels. See **hint** for guidance to create the symbol $\hat{p}$.

```{r virtual_sampling-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like. 

```{r}
virtual_samples |> 
  ggplot(aes(x = prop_red)) +
    geom_histogram(binwidth = 0.01, 
                   boundary = 0.4, 
                   color = "white") +
    labs(x = expression(hat(p)), 
         y = "Count",
         title = "Distribution of 1,000 proportions red") 
```

```{r virtual_sampling-12-hint-1, eval = FALSE}
Within labs(), set x to expression(hat(p))
```

###

This visualization allows us to see how our results differed between our tactile and virtual urn results. As we can see, there is some variation between our results. This is not a cause for concern, as there is always expected sampling variation between results.

<!-- RS: Later on add exercises to build the graph that compares shovel size 25, 50, and 100. In a few days I will edit the primer to remove the bindrows() nonsense and create the graph using expand_grid(). -->

## Standard Error of different shovel sizes

### 

<!-- MT: add questions about the definitions/important concepts of standard error -->

Standard errors (SE) quantify the effect of sampling variation on our estimates. In other words, they quantify how much we can expect the calculated proportions of a shovel’s beads that are red to vary from one sample to another sample to another sample, and so on. As a general rule, as sample size increases, the standard error decreases.

###

Let's create the following plot that displays different standard deviations of red bead proportions for 100 different shovel sizes.

```{r}
shovel_p <- shovels_100 |>
 ggplot(aes(x = shovel_size, y = st_dev_p_hat)) +
 geom_point() +
 labs(title = "Sampling Variation",
      subtitle = "Larger samples have less variation",
      x = "Shovel size",
      y = "Standard deviation of the proportion red")

shovel_p
```

### Exercise 1

First, let's use `expand_grid()` to create the foundation of our tibble. Our first column in `expand_grid()` should be called `trial_ID`, and it should be the range of integers between 1 and 1,000. The second column should be called `shovel_size`, and should be the range of integers between 1 and 100.

```{r different_shovel_siz-1, exercise = TRUE}

```

```{r different_shovel_siz-1-hint-1, eval = FALSE}
expand_grid(trial_ID = ..., shovel_size = ...)
```

```{r different_shovel_siz-1-hint-2, eval = FALSE}
Use the : operator to create a range of integers. 
```

###

### Exercise 2

Continue the pipe with `mutate()`, creating a new column called `shovel`. Set `shovel` equal to a `map()` function, passing in `shovel_size` as the first argument, and the `slice_sample()` function as the second argument. Within `slice_sample()`, the first argument should be `urn` (the data we want to sample from), and then set `n` equal to `.` (we want to pass in the `shovel_size` using `map()`).

```{r different_shovel_siz-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r different_shovel_siz-2-hint-1, eval = FALSE}
... |>
  mutate(shovel = map(..., ~ ... ))
```

```{r different_shovel_siz-2-hint-2, eval = FALSE}
... |>
  mutate(shovel = map(... , ~ slice_sample(..., n = ...)))
```

### Exercise 3

Continue your pipe with `mutate()` to create the variable `numb_red`, which will tells us the number of red beads present. Set `numb_red` to the function `map_int()`. The first argument to `map_int()` should be `shovel`. The second argument should take the `sum()` of where the column `color` of `shovel` is equal to red.

```{r different_shovel_siz-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r different_shovel_siz-3-hint-1, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~ ...))
```

```{r different_shovel_siz-3-hint-2, eval = FALSE}
... |> 
  mutate(... = map_int(..., ~ sum(.$color == "red")))
```

### Exercise 4

Continue your pipe from above, using `mutate()` to create one final column called `prop_red` which represents the proportion of red beads in a sample. Set `prop_red` to `numb_red` divided by the `shovel_size` column. 

```{r different_shovel_siz-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r different_shovel_siz-4-hint-1, eval = FALSE}
... |>
  mutate(prop_red = ... / ...)
```

### Exercise 5

Great. Continue your pipe and use the `group_by()` function to group our tibble by `shovel_size`. 

```{r different_shovel_siz-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r different_shovel_siz-5-hint-1, eval = FALSE}
... |>
  group_by(...)
```

### Exercise 6

Continue your pipe one last time, and use `summarize()` to create a new column named `st_dev_p_hat` which is equal to the standard deviation of `prop_red`. (`sd()` calculates standard deviation).
 

```{r different_shovel_siz-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r different_shovel_siz-6-hint-1, eval = FALSE}
... |> 
  summarize(st_dev_p_hat = sd(...))
```

### Exercise 7

Assign your code from above to an object named `shovels_100`.

```{r different_shovel_siz-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r different_shovel_siz-7-hint-1, eval = FALSE}
Use the assignment operator <-  to do so.
```

### Exercise 8

Start a new pipe from `shovels_100`. Use `ggplot()`to map `shovel_size` to the x-axis and `st_dev_p_hat` to the y axis. Also, add the layer `geom_point()` to create a scatterplot.

```{r different_shovel_siz-8, exercise = TRUE}

```

```{r different_shovel_siz-8-hint-1, eval = FALSE}
shovels_100 |> 
  ggplot(aes(x = ..., y = ...)) + 
  geom_point()
```

### Exercise 9

Now use `labs()` to label the x-axis "Shovel size" and the y-axis 
"Standard deviation of the proportion red". You should also provide a title and subtitle.

```{r different_shovel_siz-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: This is what your plot should look like.

```{r}
shovel_p
```

```{r different-shovel-siz-9-hint-1, eval = FALSE}
... +
   labs(title = "Sampling Variation",
      subtitle = "Larger samples have less variation",
      x = "Shovel size",
      y = "Standard deviation of the proportion red")
```

## Cardinal Virtues with Wisdom
###

*Wisdom* requires the creation of a Preceptor Table, an examination of our data, and a determination, using the concept of “validity,” as to whether or not we can (reasonably!) assume that the two come from the same population.

### Exercise 1

Consider the following question: 

> If we get 17 red beads in a random sample of size 50 taken from a mixed urn, what proportion $\rho$ of the beads in the urn are red?

Our *Preceptor Table* is a table with minimal rows and columns such that we can perfectly answer our question using it. In one sentence explain the columns for our Preceptor Table for the question. 

```{r wisdom-1}
question_text(NULL,
	message = "There would be 2 columns: One for the bead ID and one for bead color because the Preceptor Table would have as many rows as there are beads in the urn.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 2

How can the *assumption of validity* apply to this question? Write one sentence applying this key concept to our situation. 

```{r wisdom-2}
question_text(NULL,
	message = "Our sample comes directly from the urn that we are infering about which means that the data and Preceptor refer to the same population, allowing the assumption of validity to hold true because of the similarity.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

## Cardinal Virtues with Justice
###

*Justice* starts with an examination of the stability, representativeness, and unconfoundedness of the Population Table and ends with an assumption about the mathematical form of the data generating mechanism.

###

For the next three exercises, use the following Population Table for our urn problem:

```{r}
tibble(source = c("Population", "Population", "Population","...",  
                  "Data", "Data", "Data", "...",
                  "Population", "Population", "Population","...", 
                  "Preceptor Table", "Preceptor Table", "Preceptor Table", "...",
                  "Population", "Population", "Population"),
       location = c("Known, specific urn", "Known, specific urn", "Known, specific urn", "...",
                    "Known, specific urn", "Known, specific urn", "Known, specific urn", "...",
                    "Known, specific urn", "Known, specific urn", "Known, specific urn", "...",
                    "Known, specific urn", "Known, specific urn", "Known, specific urn", "...",
                  "Known, specific urn", "Known, specific urn", "Known, specific urn"),
       time = c("Time of sample - 2 years", "Time of sample - 3 weeks", "Time of sample - 10 days", "...",
                "Time of sample", "Time of sample", "Time of sample", "...",
                "Time of sample + 10 days", "Time of sample + 3 weeks", "Time of sample + 2 years", "...",
                "Now", "Now", "Now", "...",
                "Now + 10 days", "Now + 3 weeks", "Now + 2 years"),
       id = c("1", "200", "976", "...",
              "2", "200", "1080", "...",
              "1", "200", "2025", "...",
              "1", "200", "2078", "...",
              "1", "200", "2300"),
       color = c("?", "red", "?", "...",
              "white", "red", "white", "...",
              "?", "red", "?", "...",
              "?", "red", "?", "...",
              "?", "red", "?")) |>

  # Then, we use the gt function to make it pretty

  gt() |>
  cols_label(source = md("Source"),
             location = md("Location"),
             time = md("Time"),
             id = md("ID"),
             color = md("Color")) |>
  tab_style(cell_borders(sides = "right"),
            location = cells_body(columns = c(source))) |>
  tab_style(style = cell_text(align = "left", v_align = "middle", size = "large"),
            locations = cells_column_labels(columns = c(source))) |>
  cols_align(align = "center", columns = everything()) |>
  cols_align(align = "left", columns = c(source)) |>
  fmt_markdown(columns = everything())
```

### Exercise 1

In one sentence explain the time value for our data.

```{r justice-1}
question_text(NULL,
	message = "The time column for the data is listed as the time of the sample, because only one sample was taken for which we have data.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 2

In one sentence explain the time value for our Preceptor Table.

```{r justice-2}
question_text(NULL,
	message = "The Preceptor Table has a time column of now, because we want to know the contents of the urn in the present day to answer our question.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 3

In one sentence explain the time value for our Population.

```{r justice-3}
question_text(NULL,
	message = "The Population has a time range from as far back as 2 years before the sample and upto 2 years into the future, because the urn sample could have theoretically been taken from anytime in the past or into the future, so a wider population must be acknowledged.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 4

In two sentences, provide a reason why the assumption of stability might not hold.

```{r 34-justice-4}
question_text(NULL,
	message = "What if someone dumps some red beads into the urn after we take our sample? Then we cannot assume stability, because the proportion of red beads in the urn, p, the instant before the dump is different than the proportion red in the urn after.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 5

In two sentences, provide a reason why the assumption of representativeness will hold.

```{r 34-justice-5}
question_text(NULL,
	message = "For the sample proportion to be similar to the actual population proportion, we ideally want the data we have to be a random, unbiased selection from our population. In the context of our problem, the sampling mechanism of using a shovel of size 50 to sample beads from an urn in which the beads are thoroughly mixed should be enough to consider our sample representative of the population.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 6

In two sentences, provide a reason why the assumption of unconfoundedness will not apply.

```{r 34-justice-6}
question_text(NULL,
	message = "Since this is a predictive model, we do not have to worry about unconfoundedness. There is no “treatment” which might be confounded with anything.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 7

Now let's turn our attention to the *Data Generating Mechanism (DGM)*. Should our urn problem be modeled by a normal or binomial distribution? Explain your reasoning in 2 sentences.  

```{r justice-7}
question_text(NULL,
	message = "Our urn problem should be modeled by a binomial distribution, because we model the number of times a red bead is selected (successes) over a white bead (failures). There are only 2 possibilities to model, and the urn problem can be modeled by a binomial distribution",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

## Cardinal Virtues with Courage
###

*Courage* takes the mathematical formula from *Justice* and, using code, creates a fitted model, included posterior probability distributions for all the unknown parameters.

###

Consider our question:  

> If we get 17 red beads in a random sample of size 50 taken from a mixed urn, what proportion $\rho$ of the beads in the urn are red?

Let's create the *Posterior Probability Distribution* of $\rho$ using **rstanarm** 

```{r}
ppd_plot <- ppd_for_p |>
  ggplot(aes(x = p)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 50) + 
    labs(title = "Posterior Probability Distribution",
         subtitle = "Distribution is centered at 0.34",
         x = "Proportion p of Red Beads in Urn",
         y = "Probability") + 
  
    scale_x_continuous(labels = scales::number_format()) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()

ppd_plot
```

### Exercise 1

Our urn problem can be represented by a binomial model, so we structure our data in a binomial format:  1's represent the number of successes (red beads drawn), and the 0's represent the number of failures (white beads drawn). 

###

Load the **rstanarm** package first. 

```{r courage-1, exercise = TRUE}

```

```{r courage-1-hint-1, eval = FALSE}
library(...)
```

### Exercise 2

Create a `urn_data` variable set to it to a `tibble()`. Within the `tibble()` set `red` to a combination of `rep(1, 17)` and `rep(0, 33)`.

```{r 34-courage-2, exercise = TRUE}

```

```{r 34-courage-2-hint, eval = FALSE}
urn_data <- tibble(... = c(rep(1, 17), ...))
```

### Exercise 3

Next we'll use `stan_glm()` to create a simple Bayesian model. When using `stan_glm()`, we have to use five arguments. Set `data` to `urn_data`. Set `family` to `binomial`. Set `formula` to `red ~ 1`. Set `refresh` to 0. Finally, set `seed` to 10.

```{r courage-3, exercise = TRUE}


```

```{r courage-3-hint-1, eval = FALSE}
stan_glm(data = ...,
         family = ...,
         formula = ..., 
         refresh = ...,
         seed = ...)
```

###

The `data` argument tells `stan_glm()` what data frame to work with. Set `data` to `urn_data`. The `family` argument tells `stan_glm()` what mathematical formula should be used to create our model. Set `family` to `binomial`. The `formula` argument tells `stan_glm()` what model is to be fitted. Because we have no predictors, we use the argument `formula = red ~ 1`, which means that we only model the outcome based on the unknown proportion of red beads in the urn. We use `refresh` at 0 in order to suppress the behavior of printing to the console, and `seed` to 10 so that we get the same output every time we run the code.

### Exercise 4

We need to save our model to be able to work with it in later questions. Copy your code from the previous exercise, and assign it to an object called `fit_1`.  

```{r courage-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r courage-4-hint-1, eval = FALSE}
Use the assignment operator <-  to do so.
```

### Exercise 5

Let's recreate our posterior distribution using `posterior_epred()`, assigning our code to a variable called `ppd_for_p`. Pass in `fit_1` as the first argument, and then set the argument `newdata` equal to a `tibble()`. Within the `tibble()`, include `constant = 1`. 

```{r courage-5, exercise = TRUE}

```

```{r courage-5-hint-1, eval = FALSE}
ppd_for_p <- posterior_epred(..., 
                 newdata = ...)
```

###

We use `constant = 1` as junk data to make sure our tibble has just 1 row. 

### Exercise 6

Copy your code from above. First pipe `as_tibble()` to your code. Then continue your pipe by renaming the column of the resulting tibble from `1` to `p` by using `p = 1` within `rename()`. **Remember to include backticks around 1**. 

```{r courage-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r courage-6-hint-1, eval = FALSE}
... |>
  ... |>
  rename(...)
```

```{r courage-6-hint-2, eval = FALSE}
Within rename, set p equal to `1`. Make sure to include backticks around 1!
```

### Exercise 7

Type `ppd_for_p` below to view 4,000 draws from our posterior. 

```{r courage-7, exercise = TRUE}

```

### Exercise 8

Now let's graph the draws from the posterior. First, start a pipe with `ppd_for_p`, and using `ggplot()` map `p` to the x axis. Add the layer `geom_histogram()`.

```{r courage-8, exercise = TRUE}

```


```{r courage-8-hint-1, eval = FALSE}
ppd_for_p |>
  ggplot(aes(x = ...)) + 
  geom_histogram
```

### Exercise 9

Within `geom_histogram()`, use `aes()` to set `y` equal to `after_stat(count/sum(count))` in order to convert the y-axis to percent values and set `bins` to 50. 

```{r courage-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r courage-9-hint-1, eval = FALSE}
... +
  geom_histogram(aes(... = ...),
                 bins = ...)
```

### Exercise 10

Add the layer `scale_x_continuous()` with the argument `labels` set to `scales::number_format()`.
    
```{r courage-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r courage-10-hint-1, eval = FALSE}
... +
  scale_x_continuous(... = ...)
```

### Exercise 11

Great. Now add the layer `scale_y_continuous()` with the argument `labels` set to `scales::percent_format()`.

```{r courage-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r courage-11-hint-1, eval = FALSE}
... +
   scale_y_continuous(... = ...)
```

### Exercise 12

To finish, use `labs()` to give your graph the appropriate title, subtitle, and axis labels. Finally, add the layer `theme_classic()`. 

```{r courage-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: Your plot should look something like this:

```{r}
ppd_plot
```

### Exercise 13

Using the posterior, answer the initial question in 2 sentences: 

> If we get 17 red beads in a random sample of size 50 taken from a mixed urn, what proportion $\rho$ of the beads in the urn are red?

Because the exact value of the parameter (the proportion of red beads in the urn) is unknown, your answer should not be a single number, but instead a range of values that the true value of the parameter is likely to fall between.  

```{r courage-13}
question_text(NULL,
	message = "We know that there is the greatest chance that the proportion of red beads in the whole urn is between .28 and about .42, and some chance that it falls between .15 and .24 or between .42 and .56. However, there is almost no chance that the proprtion is below .15 or above .56.",
	answer(NULL,
	correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

## Cardinal Virtues with Temperance
###

*Temperance* guides us in the use of the model we have created to answer the questions we began with. We create posteriors of quantities of interest. We should be modest in the claims we make. The posteriors we create are never the “truth.”

### 

Recall our second question: 

>What is the probability, using the same urn, that we will draw more than 8 red beads if we use a shovel of size 20?

In order to answer our question we need the probability of drawing one red bead from the urn. Because we do not know this probability exactly, we will use our `fit_1` posterior from *Courage*. 

The easiest way to calculate the probability of drawing more than 8 red beads out of 20 is to predict future samples using our new shovel size, and calculate the number of samples that yield more than 8 red beads. 

### Exercise 1

The two functions to predict future outcomes in **rstanarm** are `posterior_epred()` and `posterior_predict()` Let's compare the two to determine which one we should use. 

### 

First let's use `posterior_predict()`. 

```{r}
ppd_reds_in_20 |> 
  ggplot(aes(x = total)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 50) +
    labs(title = "Posterior Probability Distribution",
         subtitle = "Created with posterior_predict()",
         x = "Number of Red Beads",
         y = "Probability") +  
    scale_x_continuous(labels = scales::number_format(accuracy = 1)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    theme_classic()
```

###

Next `posterior_epred()`.

```{r}
# Create posterior_epred() model
posterior_epred(fit_1, 
  newdata = tibble(constant = rep(1, 20))) |> 
  as_tibble() |> 
  mutate(total = rowSums(across(`1`:`20`))) |> 
  select(total) |> 
#Graph it
  ggplot(aes(x = total)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 50) +
    labs(title = "Posterior Probability Distribution",
         subtitle = "Created with posterior_epred()",
         x = "Number of red beads",
         y = "Probability") + 
    scale_x_continuous(labels = scales::number_format(accuracy = 1)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    theme_classic()
```

###

In a paragraph, compare the results of using `posterior_predict()` and `posterior_epred()`. Which one do you think we should use to answer our question and why? Refer to *Temperance* in the *Primer* for reference. Make sure to use the terms "individuals" and "population". 

```{r temperance-1}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    rows = 6)
```

###

If you answered that we should use `posterior_predict()`, you are correct!

### Exercise 2

Let's assign `posterior_predict()` to a variable called `ppd_reds_in_20`. Pass in `fit_1` as the first argument, and then set the argument `newdata` equal to a `tibble()`. Within the `tibble()`, set `constant` to a vector that repeats the number 1, 20 times. Hint: use the function `rep()` to repeat, passing what you want to repeat as the first argument, and the number of times you want to repeat it as the second argument. 

```{r temperance-2, exercise = TRUE}

```

```{r temperance-2-hint-1, eval = FALSE}
ppd_reds_in_20 <- posterior_predict(...,
                  newdata = tibble(constant = ...))
```

```{r temperance-2-hint-2, eval = FALSE}
ppd_reds_in_20 <- posterior_predict(...,
                  newdata = tibble(constant = rep(..., ...)))
```

###

We use pass a tibble with 20 rows into `newdata` because we want to estimate the number of red draws with a shovel size of 20. 

### Exercise 3

Copy your code from above and pipe on `as_tibble()`. Then type `ppd_reds_in_20` to view the results. 

```{r temperance-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-3-hint-1, eval = FALSE}
... |>
  ...
```

###

Each of our 4,000 rows represent one instance of us predicting a future sample from the urn, and each column represents the color bead in a shovel slot. 

### Exercise 4

Let's find the total number of red beads drawn. Copy your code from above and create a column named `total` using `mutate()`. Set `total` to `rowSums(across(1:20))`, making sure to surround both the 1 and 20 in back ticks! Then continue your pipe and select the `total` column. 

```{r temperance-4, exercise = TRUE }

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-4-hint-1, eval = FALSE}
... |>
  mutate(total = ...) |>
  select(...)
```

### Exercise 5

Great work! We have created the posterior probability distribution for sampling  red beads out of urn with a shovel size of 20, which is where the name `ppd_reds_in_20` comes from. 

###

Now let's answer our question: 

*What is the probability, using the same urn, that we will draw more than 8 red beads if we use a shovel of size 20?*

To calculate the probability, we want to know the number of draws **above** 8, and divide by the total number of draws. 

*The number of draws above 8 can be calculated by using the `sum()` function, passing in a Boolean expression to evaluate the number of times `ppd_reds_in_20$total` is greater than 8. 

*The total number of draws can be calculated by using the `length()` function to find the length of the `total` column in `ppd_reds_in_20`

```{r temperance-5, exercise = TRUE}

```

```{r temperance-5-hint-1, eval = FALSE}
... / ...
```

```{r temperance-5-hint-2, eval = FALSE}
sum(ppd_reds_in_20$total > ...) / length(...)
```
### 

If your code doesn't output `r sum(ppd_reds_in_20$total > 8)/length(ppd_reds_in_20$total)`, go back and try again. 

### Exercise 6

The answer to our question is: there is approximately a `r round(100 *sum(ppd_reds_in_20$total > 8)/length(ppd_reds_in_20$total))`% chance that we will draw more than 8 red beads out of a sample size of 20. 

Let's visualize this graphically. To do so, first and add a new column called `above_eight`, and use `ifelse()` to set `above_eight` to `TRUE` if `total > 8`, and `FALSE` if not. 

<!-- RS: Are we concerned about students skipping to this exercise and copying the code? -->

```{r temperance-6, exercise = TRUE}
ppd_reds_in_20 <- posterior_predict(fit_1, 
                  newdata = tibble(constant = rep(1, 20))) |> 
  as_tibble() |> 
  mutate(total = rowSums(across(`1`:`20`))) |> 
  select(total)
```

```{r temperance-6-hint-1, eval = FALSE}
... |>
  mutate(above_eight = ...)
```

```{r temperance-6-hint-2, eval = FALSE}
... |>
  mutate(above_eight = ifelse(..., ..., ...))
```

### Exercise 7

Awesome! Now let's graph our distribution. Start a new pipe with `ppd_reds_in_20`, and use `ggplot()` to map `total` to the x axis, and fill to `above_eight`. Also add the layer `geom_histogram()`. 


```{r temperance-7, exercise = TRUE}

```

```{r temperance-7-hint-1, eval = FALSE}
prob_dist |>
  ggplot(aes(x = ..., fill = ...)) + 
  ...()
```

### Exercise 8

Within `geom_histogram()`, use `aes()` to set `y` equal to `after_stat(count/sum(count))` in order to convert the y-axis to percent values and set `bins` to 50. 

```{r temperance-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-8-hint-1, eval = FALSE}
... +
  geom_histogram(aes(y = ...),
                 bins = ...)
```

### Exercise 9

Now add a layer with `scale_fill_manual()` to change the color of our bars. Inside `scale_fill_manual()`, set `values` to a vector that combines 'grey50' and 'red'.

```{r temperance-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-9-hint-1, eval = FALSE}
... +
  scale_fill_manual(values = c(..., ...))
```

### Exercise 10

Add the layer `scale_x_continuous()` with the argument `labels` set to `scales::number_format()`.

```{r temperance-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-10-hint-1, eval = FALSE}
... +
  scale_x_continuous(labels = ...)
```

### Exercise 11

Now add the layer `scale_y_continuous()` with the argument `labels` set to `scales::percent_format()`.

```{r temperance-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r temperance-11-hint-1, eval = FALSE}
... +
   scale_y_continuous(labels = ...)
```

### Exercise 12

To finish, use `labs()` to give your graph the appropriate title, subtitle, and axis labels. Also add the layer `theme_classic()`.

```{r probability_dist-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

Reminder: Your plot should look something like this:

```{r}
ppd_reds_in_20   |> 
  
  # Set fill as above_eight. 
  
  ggplot(aes(x = total, fill = above_eight)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 50) +
  
  # Scale_fill_manual()  is calling grey for the first color and red for the
  # second color. This is going to highlight the portion of the curve that we
  # want to highlight in red.

  scale_fill_manual(values = c('grey50', 'red')) +
    labs(title = "Posterior Probability Distribution",
         subtitle = "Number of red beads in 20-slot shovel",
         x = "Number of Red Beads",
         y = "Probability",
         fill = "More than 8 Red Beads Drawn?") +  
    scale_x_continuous(labels = scales::number_format(accuracy = 1)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    theme_classic()
```

###

The red bars illustrate the area under a specific section of the curve, as compared to the entire area under the curve. When someones asks you a question, they are doing two things. First, they are providing instructions as to the posterior your should create. Here, the results with a shovel of 20 slots. Second, they are asking a question about the area under the curve in a specific region. Here, the region where the number of red beads is greater than 8 is highlighted in red. Therefore, the area below the curve that is red is how we get our estimate.

## Case Study
###

Let’s now switch gears to a more realistic sampling scenario: a poll. In practice, pollsters do not take 1,000 repeated samples as we did in our previous sampling activities, but rather take only a single sample that’s as large as possible.

###

On December 4, 2013, National Public Radio in the US reported on a poll of President Obama’s approval rating among young Americans aged 18-29 in an article, [*“Poll: Support For Obama Among Young Americans Eroding.”*](https://www.npr.org/sections/itsallpolitics/2013/12/04/248793753/poll-support-for-obama-among-young-americans-eroding).

###

We are going to use our knowledge from our previous topics and apply them within our case study to answer questions.

### Exercise 1

Who is the (Study) Population of, `N`, individuals or observations of interest? In our Urn scenario it was 50 identically sized red and white beads. Write one sentence explaining what the study population is of the case study from above.

```{r case-study-1}
question_text(NULL,
	message = "In the Obama poll we are concerned with young Americans aged from 18-29",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

###

If the sampling of a sample of size, `n`, is done at random, then
the sample is unbiased and representative of the population of size, `N`, thus any result based on the sample can generalize to the population.

### Exercise 2

What is the population parameter? In our Urn scenario the population proportion, `p`, of all the beads in the urn that are red. Write one sentence explaining what the population parameter is of the case study from above.

```{r case-study-2}
question_text(NULL,
	message = "In the case study our population parameter is the the population proportion of all young Americans who approve of Obama’s job performance.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 3

What is the sampling procedure representative? In our Urn scenario were the contents of the shovel representative of the contents of the urn? Because we mixed the urn before sampling, we can feel confident that they are. Write one sentence explaining what the sampling procedure representative is of the case study from above.

```{r case-study-3}
question_text(NULL,
	message = "In our case study the sampling procedure representative was the the sample of young Americans representative of all young Americans aged 18-29? This depends on whether the sampling was random (which samples rarely are).",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

### Exercise 4

Is the sampling procedure unbiased? In our Urn scenario each bead was equally sized and we mixed the urn before using the shovel, each bead had an equal chance of being included in a sample and hence the sampling was unbiased. Write one sentence explaining if the sampling procedure unbiased based on the case study from above.

```{r case-study-4}
question_text(NULL,
	message = "In our case study: Did all young Americans have an equal chance at being represented in this poll? Again, this depends on whether the sampling was random.",
	answer(NULL, correct = TRUE),
	allow_retry = FALSE,
	incorrect = NULL,
	rows = 6)
```

###

To learn more key concepts and ideas, check out [**Case Study**](https://ppbds.github.io/primer/06-one-parameter.html#sec-sampling-case-study) that goes over the entire case study in detail.

## Summary
###

This tutorial covered [Chapter 3](https://ppbds.github.io/primer/06-one-parameter.html) of [*Preceptor’s Primer for Bayesian Data Science: Using the Cardinal Virtues for Inference*](https://ppbds.github.io/primer/). This tutorial reviewd the topics including One Parameter, shovel method, virtual sampling, standard error, cardinal virtues (wisdom, justice, courage, and temperance), and a case study.

```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
