---
title: "Functions"
tutorial:
  id: "04-functions"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 4 Tutorial"
---
<!-- TO DO -->

<!-- BG: r chunk for bar plot needs to be inserted at the top of the Crooked Casino section -->

```{r setup, include=FALSE}
library(tidyverse)
library(PPBDS.data)
library(learnr)
library(shiny)
library(gapminder)
library(skimr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
options(tutorial.exercise.timelimit = 60, tutorial.storage="local")
```

## Confirm Correct Package Version
###

Confirm that you have the correct version of PPBDS.data installed by pressing "Run Code."

```{r confirm, exercise=TRUE}
packageVersion('PPBDS.data')
```

The answer should be ‘0.3.2.9006’, or a higher number. If it is not, you should upgrade your installation by issuing these commands:


```{r confirm-advice, echo=TRUE, eval=FALSE}
remove.packages('PPBDS.data')  
library(remotes)  
remotes::install_github('davidkane9/PPBDS.data')  
```

Strictly speaking, it should not be necessary to remove a package. Just installing it again should overwrite the current version. But weird things sometimes happen, so removing first is the safest approach. 

## Name 
###

``` {r name}
question_text(
  "Student Name:",
  answer(NULL, correct = TRUE),
  allow_retry = TRUE,
  try_again_button = "Modify your answer",
  incorrect = "Ok"
)
```

## Email
###

``` {r email, echo=FALSE}
question_text(
  "Email:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```


## Introduction
###

Let's do a quick refresher about functions.


### Exercise 1

```{r if-1}
quiz(
  question("Select all that apply: Which of the following operations can be achieved by running a function in R?",
           answer("Taking a log value", correct = TRUE),
           answer("Fitting a linear model", correct = TRUE),
           answer("Averaging two numbers", correct = TRUE),
           allow_retry = TRUE)
)
```

### Exercise 2

```{r if-2}
quiz(
question("Which of the following is not a part of a function?",
         allow_retry = TRUE,
         random_answer_order = TRUE,
         answer("A name", correct = TRUE, message = "That's right, functions contain a code body, a set of formal arguments, and an environment, but not a name. They just happen to inherit a name from the object they are stored in."),
         answer("A code body", message = "Functions do require a code body! You can inspect this part of the function by using the helper function body()."),
         answer("A (potentially empty) set of formal arguments", message = "Functions do require formal arguments, even if they are empty! You can inspect this part of the function by using the helper function formals()."),
         answer("An environment", message = "Functions do require an environment, which is a self-contained space to look up the values of any objects within it. You can inspect this part of the function by using the helper function environment()."))  
)
```

### Exercise 3

```{r if-4}
quiz(
question("Which of these will run the `Sys.time` function?",
         answer("Sys.time"),
         answer("Sys.time()", correct = TRUE, 
         message = "The open and closed parentheses tell R to execute the code in the code body of the function stored in the object names Sys.time."))
)
```


## Lists and list-columns
###


### Exercise 1


We use map_* functions to create list
```{r ll-2}
quiz(
question("What does map_dbl() mean?",
           answer("The input to the map_dbl() function must be numeric"),
           answer("The output of the map_dbl() function will be numeric", 
                  correct = TRUE),
           allow_retry = TRUE)
)
```

### Exercise 2


```{r ll-3}
quiz(
question("How are map_* functions different than mutate()?",
           allow_retry = TRUE,
           answer("They can take list inputs and iterate over each element of a list", correct = TRUE),
           answer("They are the same, except you can specify what output data type you'd like to have"),
           answer("They can apply functions to their inputs, whereas mutate() cannot"),
           answer("They can apply custom and anonymous functions to their inputs, whereas mutate() can only apply built-in functions to their inputs"))  
)
```

### Exercise 3 

```{r ll-4}
quiz(
  question("Which of the following is correct about map_* functions?",
            allow_retry = TRUE,
           answer("You do not need the parentheses when specifying a function for the map_* function to apply. Ex: map(data, mean)", correct = TRUE),
           answer("You do need the parentheses when specifying a function for the map_* function to apply. Ex: map(data, mean())"),
           answer("You cannot have a list with NAs, or else using the map_* function will return an error", message = "This is not necessarily true. Hint: What does the \"...\" mean in map_*? Refer to the next question!")),
  question("What does the \"...\" argument mean in a map_* function?",
           allow_retry = TRUE,
           answer("Nothing. R functions commonly have an auxiliary \"...\" argument"),
           answer("It means that the map_* function will take in its default arguments"),
           answer("It means that you can specify additional arguments to be passed into the given function", correct = TRUE))
)
```


### Exercise 4
A simple tibble was created with one variable. Add to the pipe some code which creates a new list-column called `col_2`. Use `mutate` function and the argument `str_split()` to split the phrases into "Government", "Data Science", "Preceptor", and "Primer".

```{r exercise-0, exercise=TRUE}
tibble(col_1 = c("Government and Data Science", "Preceptor and Primer"))
```

```{r exercise-0-hint, eval=FALSE}
tibble(col_1 = c("Government and Data Science", "Preceptor and Primer")) %>%
  mutate(col_2 = str_split(..., " and "))
```

### Exercise 5


Now append `str()` to the end of the pipe in order to read the tibble contents. 


```{r exercise-1b, exercise=TRUE}
tibble(col_1 = c("Government and Data Science", "Preceptor and Primer")) %>%
  mutate(col_2 = str_split(col_1, " and "))
```

```{r exercise-1b-hint, eval=FALSE}
tibble(col_1 = c("Government and Data Science", "Preceptor and Primer")) %>%
  mutate(col_2 = str_split(..., " and ")) %>%
  str()
```

## Creating columns using map_*

###

### Exercise 1

Explore the `ChickWeight` dataset using `skim()`.

```{r exercise-1, exercise=TRUE}

```

```{r exercise-1-hint, eval=FALSE}
skim(...)
```

### Exercise 2


Great! Now create a list-column of `weight`s using `mutate()`called `weight_groups`, grouping by `Diet` and `Time`.

```{r exercise-2, exercise=TRUE, eval=FALSE}
ChickWeight %>%
  group_by(Diet, Time) %>%
  mutate(...)
```

```{r exercise-2-hint, eval=FALSE}
ChickWeight %>%
  group_by(Diet, Time) %>%
  mutate(weight_groups = list(...))
```

### Exercise 3

Use the `map_dbl` function  and `mutate()` to add a new column, `mean_weight`, which is the mean weight per row. Recall that each row corresponds to a unique combination of `Diet` and `Time`. As always, you should start by copy-pasting from the last answer.


```{r exercise-3, exercise=TRUE}

```

```{r exercise-3-hint, eval=FALSE}
ChickWeight %>%
  group_by(Diet, Time) %>%
  mutate(weight_groups = list(weight)) %>%
  mutate(mean_weight = map_dbl(weight_groups, ...))
```

### Exercise 4

Now let's use `map_dbl()` to round each `mean_weight` to the nearest integer. Name this new column `rounded_mean`. 

```{r exercise-4, exercise=TRUE}

```

```{r exercise-4-hint, eval=FALSE}
ChickWeight %>%
  group_by(Diet, Time) %>%
  mutate(weight_groups = list(weight)) %>%
  mutate(mean_weight = map_dbl(weight_groups, mean)) %>%
  mutate(rounded_mean = map_dbl(mean_weight, ...))
```



###


### Exercise 5
Now let's use the `gapminder` dataset. Create a list-column named `gdpPercap_yearly` that lists the `gdpPercap` per year grouping by continent.

```{r exercise-7a, exercise=TRUE, eval=FALSE}

```

```{r exercise-7a-hint, eval=FALSE}
gapminder %>%
  group_by(year, continent) %>%
  mutate(gdpPercap_yearly = list(...))
```

### Exercise 6
Now, let's build upon the previous question's code. Instead of taking the `gdpPercap`, calculate the *annual GDP of the country* in a new variable called `annual_gdp`.

```{r exercise-8a, exercise=TRUE, eval=FALSE}
gapminder %>%
  group_by(year, continent) %>%
  mutate(annual_gdp = list(...))
```

```{r exercise-8a-hint, eval=FALSE}
gapminder %>%
  group_by(year, continent) %>%
  mutate(annual_gdp = list(gdpPercap * ...))
```

### Exercise 7

What was the lowest GDP in each `year` x `continent` category? Create a new column named `lowest` of data type "double" that contains the lowest GDP per year/continent. Pay attention to the `map_*` function you use.

```{r exercise-9a, exercise=TRUE, eval=FALSE}
gapminder %>%
  group_by(year, continent) %>%
  mutate(annual_gdp = list(gdpPercap * pop)) %>%
  mutate(lowest = ...)
```

```{r exercise-9a-hint, eval=FALSE}
gapminder %>%
  group_by(year, continent) %>%
  mutate(annual_gdp = list(gdpPercap * pop)) %>%
  mutate(lowest = map_dbl(annual_gdp, ...))
```

###



## Custom Functions 
###


### Exercise 1


Here is a custom function we will call `foo`:

```{r foo-1, echo = FALSE}
foo <- function(){
  a <- 10
  a
}
```

```{r foo-2, echo=TRUE}
body(foo)
```

What will be the final value of `a` if I run the following three lines of code in order?

```{r foo-3, eval=FALSE, echo=TRUE}
a <- 1
foo()
a
```

```{r quiz-1b, echo = FALSE}
quiz(
  question("",
         answer("1", correct = TRUE, message = "What happens in a function, stays in the function. foo() will not change the value of a outside of foo()."),
         answer("10"),
         answer("Running a will return an error."),
         allow_retry = TRUE)
  )
```




### Exercise 2


Put yourself in the shoes of a teacher: You've given your students 10 homework assignments and announced that you will drop their lowest homework score. Their final grade will be the average score of the remaining homeworks.

To make your life easier, you want to write an R function that will take a vector of 10 homework scores and return a final grade. 

Create an object named `x` that contains the vector `c(100, 100, 100, 100, 100, 100, 100, 100, 100, 90)`.
*`x` will be the grades of your test student. 

```{r obj, exercise=TRUE}

```



### Exercise 3


Use `sum()`, `min()`, `/`, `9` and parentheses to calculate the final grade for student `x`.

```{r norm, exercise=TRUE}
x <- c(100, 100, 100, 100, 100, 100, 100, 100, 100, 90)
```

```{r norm-hint, eval=FALSE}
(sum(x) - min(x)) / ...
```


### Exercise 4


Save the code below as a function named `grade`.
```{r grade-setup}
x <- c(100, 100, 100, 100, 100, 100, 100, 100, 100, 90)
```

```{r grade, exercise=TRUE}
(sum(x) - min(x)) / 9
```

```{r grade-hint, eval=FALSE}
grade <- function(){ 
  ...
}
```


### Exercise 6


Each time you call `grade()` it computes the final grade of the vector `x` that contains `c(100, 100, 100, 100, 100, 100, 100, 100, 100, 90)`. We'd like to use `grade()` with new vectors that have new values.

Make `x` a formal argument.

```{r exercise-random-name, exercise=TRUE, eval=FALSE}
grade <- function(){ 
  ...
}
```

```{r exercise-random-name-hint, eval=FALSE}
grade <- function(...){ 
  (sum(x) - min(x)) / 9
}
```


### Exercise 7


Calculate the final grade of the vector `c(100, 90, 90, 90, 90, 90, 90, 90, 90, 80)`. 

```{r make-grade-setup}
grade <- function(x){ 
  (sum(x) - min(x)) / 9
}
```

```{r make-grade, exercise=TRUE}

```

```{r make-grade-hint, eval=FALSE}
Use the provided vector!
```






## Using `runif()` and `rnorm()`
###

`runif()` and `rnorm() generate a random uniform and normal distribution, respectively. 


### Exercise 1

Write a custom function named `add_rvs()` that adds together 1 random variable generated by `runif()` and 1 random variable generated by `rnorm()`. Use `n=1` and the default values for the other arguments.

```{r rvs_q, exercise=TRUE}

```


```{r rvs_q-hint-2, eval=FALSE}
add_rvs <- function(){
  runif(1) + rnorm(...)
}
```

### Exercise 2

What if you wanted to customize `n`? Add a formal argument `n` to your `add_rvs()` function with a default value of 1.

```{r rvs_q2, exercise=TRUE}

```

```{r rvs_q2-hint, eval=FALSE}
add_rvs <- function(n = 1){
  runif(n) + rnorm(...)
}
```



### Exercise 3


Lets say we want to call `add_rvs()` twenty times. Call `add_rvs()` twenty times using `replicate()`. Use the default value of the `n` argument in `add_rvs()`.



```{r replicate-setup}
add_rvs <- function(n = 1){
  runif(n) + rnorm(n)
}
```

```{r replicate, exercise= TRUE}

```



```{r replicate-hint, eval=FALSE}
replicate(20, ...)
Remember to use the parentheses when calling a function from inside replicate()!
  
 
```
<!-- better hint here -->



## Testing
###

Testing is very useful when you are going to run a certain function a lot.


### Exercise 1
We use the `return()` function whenever we want to return a value that is not the last line of the code body.

```{r is-1, echo=TRUE, eval=FALSE}
impatient_square <- function(x){
  return(x)
  x^2
}
```

###


### Exercise 2

This function is called `angry()`. Add a line of code that throws the message "Wrong! I am angry!" using `stop()`.

```{r angry, exercise=TRUE}
angry <- function(x){
  x
}
```

```{r angry-hint, eval=FALSE}
angry <- function(x){
  ...("Wrong! I am angry!")
  x
}
```

### Exercise 3

Now make it so that `angry()` only yells at us `if` the x input is not a character. Also change the error message to something more useful: "x must be a character." This method is also known as the "if then stop".

```{r ifthenstop, exercise=TRUE}
angry <- function(x){
  x
}
```

```{r ifthenstop-hint, eval=FALSE}
angry <- function(x){
  if(!is.character(x)){
    ...("x must be a character.")
  }
  x
}
```

### Exercise 4

What if we wanted to incorporate `testthat`? Use the `showfailure()` function to see what happens when we plug in `x = 1` to `angry()`.

```{r showfailure-setup}
library(testthat)
angry <- function(x){
  if(!is.character(x)){
    stop("x must be a character.")
  }
  x
}
```

```{r showfailure, exercise=TRUE, eval=FALSE}
show_failure(...)
```

```{r showfailure-hint, eval=FALSE}
show_failure(angry(x=...))
```

## Handling NAs
###

### Exercise 1

```{r if-quiz, echo = FALSE}
question("Which describes `if`'s behavior? (Check all that apply).",
         answer("`if` takes a logical test and a piece of code. It runs the code _if_ the test returns TRUE.", correct = TRUE, message = "`if` is a way to run code only in certain cases. When you use `if`, you first pass it a logical test surrounded by parentheses and then a piece of code."),
         answer("`if` takes a logical test and a piece of code. It does not run the code _if_ the logical test returns FALSE.", correct = TRUE, message = "`if` will run the piece of code if the logical test returns TRUE and not run the code if the logical test returns FALSE."),
         answer("`if` returns the results of the code that appears in _parentheses_ behind `if`."),
         answer("`if` always executes all of the code that follows it.", message = "`if` will always execute the logical test that appears in parentheses behind `if`. However, `if` will only execute the code that appears after the logical test if the logical test returns TRUE."),
         allow_retry = TRUE)
```

### Exercise 2

Many data sets use their own symbols to represent missing values. For example, NOAA will often use -99 to represent missing values in weather data sets. Let's write a function that checks whether a value is -99, and if so replaces the value with NA, like this:

```{r clean-1, echo = FALSE}
clean <- function(x){
  if(x == -99) x <- NA
  x
}
```

```{r clean-2, echo=TRUE}
clean(1)
clean(-99)
```

### Exercise 3

Add an `if` statement to the beginning of `clean()`. Your statement should assign NA to x if x equals -99.

```{r clean-setup}
x <- -99
```

```{r clean, exercise=TRUE}
clean <- function(x){
  # add if statement here
  x
}
```

```{r clean-solution}
clean <- function(x){
  if(x == -99) x <- NA
  x
}
```

<!-- DK: Given that we never use `stopifnot()`, we are they here? Why are they in the chapter? -->

## Using `stopifnot()`
###

### Exercise 1


```{r stopifnot-quiz, echo = FALSE}
quiz(
  question("How is stopifnot() different from if` + stop()?",
           allow_retry = TRUE,
           random_answer_order = TRUE,
           answer("Instead of checking whether a condition is met, `stopifnot()` checks whether a condition is not met", correct = TRUE),
           answer("stopifnot() always passes along a custom error message"),
           answer("stopifnot() cannot take logical arguments")))
```


### Exercise 2

Rewrite the below function using `case_when()`.

```{r foo-6, echo=TRUE}
foo <- function(x){
  if(x > 2) "a"
  else if(x < 2) "b"
  else if(x == 1) "c"
  else "d"
}
```

```{r foo_rewrite, exercise=TRUE}
foo2 <- function(x){
  case_when(
    
    # Insert code here!
    
  )
}
```

```{r foo_rewrite-hint-1, eval=FALSE}
foo2 <- function(x){
  case_when(
    x > 2  ~ "a",
    x < 2  ~ "b",
    ...
  )
}
```

```{r foo_rewrite-hint-2, eval=FALSE}
foo2 <- function(x){
  case_when(
    x > 2  ~ "a",
    x < 2  ~ "b",
    x == 1 ~ "c",
    TRUE ~ ...
  )
}
```




### Exercise 3

```{r foo-10, eval=FALSE, echo=TRUE}
foo <- function(x){
  if(x > 2) "a"
  else if(x < 2) "b"
  else if(x == 1) "c"
  else "d"
}
foo(1)
```

```{r else-if-quiz, echo = FALSE}
quiz(
  question("What will this code return?",
         answer('"a"', message = "R will not return a because the condition 1 > 2 is false."),
         answer('"b"', correct = TRUE, message = 'The condition 1 < 2 is true, so R will evaluate the code that follows it (i.e. "b") and then skip the remainder of the multi-part if statement.'),
         answer('"a" "b"', message = "The conditions 1 < 2 and 1 == 1 are both TRUE, but R will stop after the _first_ true condition."),
         allow_retry = TRUE))
```

### Exercise 4

```{r missing_code_chunk_name, eval=FALSE, echo=TRUE}
clean <- function(x){
  if(x == -99) NA 
  if(x == ".") NA
  if(x == "NaN") NA
  x
}
clean(-99)
```

```{r clean3-quiz, echo = FALSE}
quiz(
  question("What will this code return?",
         answer("NA", message = "Did you notice that the `if` statements are not linked by `else`? What difference does this make?"),
         answer("-99", correct = TRUE, message = "Since the `if` clauses are not linked by `else`, R treats them as separate statements. R checks each if statement. After the first statement it runs NA, but does not return this as the result of the function (because this is not the final statement in the function). R does not run NA for the next two if statements because their conditions are false. Then R reaches `x`, which is the last line and last statement in the function. R evaluates `x`, which equals -99, and returns -99 as the result of the function."),
         allow_retry = TRUE))
```





## Practice: Monthly Temperatures 
###



#### Exercise 1


Using the data set `airquality`, create a list-column of monthly temperatures called `monthly_temp`, grouping by `Month`.

```{r exercise-2a, exercise=TRUE}

```

```{r exercise-2a-hint, eval=FALSE}
airquality %>%
   group_by(Month) %>%
   mutate(monthly_temp = list(...))
```



#### Exercise 2


```{r quiz-4}
quiz(question("Which of the following possibilities for filling in the blank is syntactically correct and converts from Fahrenheit to Celsius?",
           answer("(. - 32) * 5/9)"),
           answer("(- 32 * 5/9)"),
           answer("~ (. - 32) * 5/9)", correct = TRUE),
           answer("~ (fahrenheit - 32) * 5/9)"))
)
```


#### Exercise 3


Use a `map_*` function to convert all of the temperatures in `monthly_temp` from Fahrenheit to Celsius, creating a new variable `temp_celsius`. Hint: Use the formula from the quiz above!

```{r exercise-3a, exercise=TRUE, eval=FALSE}
airquality %>%
  group_by(Month) %>%
  mutate(monthly_temp = list(Temp)) %>%
  mutate(...)
```

```{r exercise-3a-hint, eval=FALSE}
airquality %>%
  group_by(Month) %>%
  mutate(monthly_temp = list(Temp)) %>%
  mutate(temp_celsius = map(monthly_temp, ...))
```


#### Exercise 4


Oops! The scientists made a mistake in which all of the temperatures were mis-recorded. For temperatures recorded at or below 20 degrees Celsius, the true temperature is actually 1 degree Celsius lower. For temperatures recorded as higher than 20 degrees Celsius, the true temperature is actually 3 degrees Celsius higher.

Write an anonymous function that rectifies the scientists' mistake by using `case_when()`.

```{r exercise-4a, exercise=TRUE, eval=FALSE}
function(x) 
  case_when(...)
```

```{r exercise-4a-solution}
function(x) 
  case_when(x <= 20 ~ x - 1,
            x > 20 ~ x + 3)
```


#### Exercise 5

Now use this function along with `map()`, swapping out the function code after the `~` in the `map()` argument.

```{r exercise-5a, exercise=TRUE, eval=FALSE}
airquality %>%
  group_by(Month) %>%
  mutate(monthly_temp = list(Temp)) %>%
  mutate(temp_celsius = map(monthly_temp, ~ (. - 32)* 5/9)) %>%
  mutate(temp_celsius = map(temp_celsius, ~ ...))
```

```{r exercise-5a-hint, eval=FALSE}
airquality %>%
  group_by(Month) %>%
  mutate(monthly_temp = list(Temp)) %>%
  mutate(temp_celsius = map(monthly_temp, ~ (. - 32)* 5/9)) %>%
  mutate(temp_celsius = map(temp_celsius, ~ case_when(...)))
```




## Coin Flipping exercise

###

Let's create a function, `coin_flip()`, that takes an input `n` of the number of times to flip a coin and adds up the number of Tails.

### Exercise 1

Let's start by creating a minimally viable function called `starter_coin()` that flips one coin once and prints out `H` or `T`. Remember: You can paste vectors as an argument into `sample()`!

```{r coin1, exercise=TRUE, eval=FALSE}

```

```{r coin1-hint, eval=FALSE}
starter_coin <- function() sample(c("H", "T"), ...)
```

### Exercise 2

Now let's take it up a notch and add in a formal argument `n` that specifies the number of times to flip the coin.

```{r coin2, exercise=TRUE, eval=FALSE}

```

```{r coin2-hint, eval=FALSE}
starter_coin <- function(n) sample(c("H", "T"), n, replace = ...)
```

### Exercise 3

Add in a sensible `stopifnot()` to your function that checks whether the input `n` is numeric.

```{r coin3, exercise=TRUE}

```

```{r coin3-hint, eval=FALSE}
starter_coin <- function(n){
  stopifnot(is.numeric(...))
  sample(c("H", "T"), n, replace = TRUE)
}
```

### Exercise 4

Great! Now we should be able to create `coin_flip()`, which counts the number of Tails for `n` flips. Set the default value of `n` to 1.

```{r coin4, exercise=TRUE, eval=FALSE}
coin_flip <- function(n = 1){
  ...
}
```

```{r coin4-hint-1, eval=FALSE}
Use the code from starter_coin() and sum().
```

```{r coin4-hint-2, eval=FALSE}
coin_flip <- function(n = 1){
  stopifnot(is.numeric(n))
  sum(sample(c("H", "T"), n, replace = TRUE) == ...)
}
```

### Exercise 5

Now let's create a function called `five_flips` that counts how many Tails occur in five coin flips, or the equivalent of `coin_flip(5)`, but calls it `n` times.
* Set the default value of `n` separate flips to 1.
* Use a `map_*` function to apply the `rep()` function to `coin_flip()` `n` times.

```{r coin5, exercise=TRUE}
five_flips <- function(n = 1){
}
```

```{r coin5-hint-1, eval=FALSE}
The map function you are looking for is map_int().
```

```{r coin5-hint-2, eval=FALSE}
rep(x,n) means that you are flipping x coins n times.
```

```{r coin5-hint-3, eval=FALSE}
five_flips <- function(n = 1){
  stopifnot(is.numeric(n))
  map_int(rep(5, n), ...)
}
```


### Exercise 6

Create a tibble named `x` with one variable: `flips`. `flips` is a list column of 10 observations, each element of which is result of flipping 5 coins 10 times.  Make sure to use the correct `map_*` function.

```{r coin7, exercise=TRUE, eval=FALSE}
x <- tibble(flips = ...)
```

```{r coin7-hint, eval=FALSE}
x <- tibble(flips = map(rep(10, 10), ...))
```




## Random variables
###

### Exercise 1


Let's create a function `biggest()`, which takes the larger of two random variables. Use `n = 1` for both random variables.

```{r biggest1, exercise=TRUE, eval=FALSE}
biggest <- function(){
  ...
}

```

```{r biggest1-hint, eval=FALSE}
biggest <- function(){
  max(runif(...), rnorm(...))
}

```

### Exercise 2

Modify `biggest()` so that it prints out "Uniform" if the larger variable is the uniformally distributed random variable, and "Normal" if otherwise.
* Use `case_when()` with `TRUE ~ "Tie"`.
* Remember that `runif()` and `rnorm()` generate *random* values every time they are called...

```{r biggest2, exercise=TRUE, eval=FALSE}
biggest <- function(){
  ...
}

```

```{r biggest2-hint-1, eval=FALSE}
biggest <- function(){
  x <- runif(1)
  y <- rnorm(1)
  case_when(...)
}
```

```{r biggest2-hint-2, eval=FALSE}
biggest <- function(){
  x <- runif(1)
  y <- rnorm(1)
  case_when(x > y ~ "Uniform",
           y > x ~ "Normal",
           ...)
}
```

### Exercise 3

We'd like for `biggest()` to return a vector of two elements: The name of the distribution of the larger random variable and its value. If the two values are identical, we'd like for the function to return "Tie" and the value of one of the variables (since they are identical).

```{r biggest3, exercise=TRUE, eval=FALSE}
biggest <- function(){
  x <- runif(1)
  y <- rnorm(1)
  case_when(x > y ~ ...,
            y > x ~ ...,
            TRUE ~ ...)
}
```

```{r biggest3-hint, eval=FALSE}
biggest <- function(){
  x <- runif(1)
  y <- rnorm(1)
  case_when(x > y ~ c("Uniform", x),
           y > x ~ c("Normal", y),
           TRUE ~ c("Tie", ...))
}
```

### Exercise 4

Let's create a new function named `repeat_biggest()` that does so by calling `biggest()` `n` number of times.
* Use `replicate()` to call the function multiple times.

```{r newfunc, exercise=TRUE, eval=FALSE}
repeat_biggest <- function(n){
  replicate(...)
}
```

```{r newfunc-solution}
repeat_biggest <- function(n = 1){
  replicate(n, biggest())
}
```


## The Crooked Casino
###


<!-- Show the plot at the start. Discuss its meaning. Hint at what we will discuss in chapter 5. Then, walk through the step-by-step creation of it. -->

Recall the function we wrote in the chapter to model a crooked game of craps. `crooked_craps()` is expected to return a winning 7 or 11 only *half* of the time the sum is actually 7 or 11. It returns a 2 much more often than it should. Code:

```{r crooks, echo=TRUE}
crooked_dice <- function(n = 1){
  stopifnot(is.numeric(n))
  stopifnot(n >= 0)
  roll <- sum(sample(1:6, n, replace = TRUE))
  ifelse((roll == 7 | roll == 11) && runif(1) >= 0.5, 2, roll)
}

crooked_craps <- function(n = 1){
  stopifnot(is.numeric(n))
  map_dbl(rep(2, n), crooked_dice)
}
```

Let's put our visualization skills to the test.

### Exercise 1

Create a tibble with column "games" and run `crooked_craps()` 100 times.


```{r crooked-1, exercise=TRUE}

```

```{r crooked-1-hint, eval=FALSE}
tibble(games = crooked_craps(...))
```

### Exercise 2

Create a barplot with `games` on the `x` axis.


```{r crooked-2, exercise=TRUE, eval=FALSE}
tibble(games = crooked_craps(100))
```

### Exercise 3

Now, change the `x` axis scale to increment by integers from 2 to 12.

```{r crooked-3, exercise=TRUE, eval=FALSE}
tibble(games = crooked_craps(100)) %>%
  ggplot(aes(x = games)) +
  geom_bar()
```

```{r crooked-3-hint, eval=FALSE}
tibble(games = crooked_craps(100)) %>%
  ggplot(aes(x = games)) +
  geom_bar() %>%
  scale_x_continuous(breaks = seq(...))
```

### Exercise 4

Use an appropriate `map_*` function and `rep()` to call `crooked_craps(100)` 10 times. Create a tibble named `x` with a column named `games`.

```{r crooked-4, exercise=TRUE, eval=FALSE}

```

```{r crooked-4-hint, eval=FALSE}
x <- tibble(games = map(rep(100, 10), ...))
```

### Exercise 5

Inside each of these iterations of 100 rolls, we want to count the number of 3's and 11's. Technically, with a fair die one would expect as many 11's to appear as 3's. 11's can be obtained in two different ways: by adding 5 + 6 and 6 + 5. The same goes for 3's: by adding 1 + 2 and 2 + 1.

First, count the number of 3's. You can do so by using a the appropriate `map_*` function and an anonymous function defined as `sum(. == 3)`.


```{r crooked-5, exercise=TRUE, eval=FALSE}
x <- tibble(games = map(rep(100, 10), crooked_craps)) %>%
  mutate(counts = ...)
```

```{r crooked-5-hint, eval=FALSE}
x <- tibble(games = map(rep(100, 10), crooked_craps)) %>%
  mutate(counts = map_int(games, ~(...)))
```

### Exercise 6

Now, modify `counts` so that it is a list-column of 2 elements per list: The number of 3's, then the number of 11's.


```{r crooked-6, exercise = TRUE}
x <- tibble(games = map(rep(100, 10), crooked_craps)) %>%
  mutate(counts = map_int(games, ~sum(. == 3)))
```

```{r crooked-6-hint}
x <- tibble(games = map(rep(100, 10), crooked_craps)) %>%
  mutate(counts = map(games, ~list(sum(. == 3), ...)))
```


## Submit

Some of these exercises were taken from the collection of [RStudio Primers](https://rstudio.cloud/learn/primers), a great resource for practicing your skills.

```{r context="setup"}
submission_ui
```

```{r context="server"}
submission_server()
```
