---
title: "Functions B"
tutorial:
  id: "functions-b"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 3 Tutorial Part B"
---


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(gapminder)
library(skimr)
library(primer.data)

# Key Data

no_NA_sampler <- function(var, tbl, n){
  tbl %>% 
    drop_na() %>%
    sample_n(n) %>% 
    pull({{var}})
}

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

```

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```


## no_NA_sampler()
###


### Exercise 1

Recall the `nhanes` dataset. Use `$` to extract the `weight` column. 

```{r no-1, exercise = TRUE}

```


```{r no-1-hint-1, eval = FALSE}
nhanes$...
```

```{r no-1-hint-2, eval = FALSE}
nhanes$weight
```

### Exercise 2

Let's write a function that allows us to sample `weight` from individuals who have no NA's for any variables.

Start a pipe with`nhanes`. Use `drop_na()` to get rid of any NA values.

```{r no-2, exercise = TRUE}

```


```{r no-2-hint-1, eval = FALSE}
... %>% 
  drop_na()
```

### Exercise 3

Copy/paste your code from above. Pipe in `sample_n()` with the argument 10. Then, `pull()` `height`. 

```{r no-3, exercise = TRUE}

```


```{r no-3-hint-1, eval = FALSE}
... %>% 
  sample_n(...) %>% 
  pull(...)
```

### Exercise 4

Great, we have code that does what we want. To turn this into a function, we just need to copy/paste our code from above and place it within the body `{ }` of our `function()`. Assign your work to an object named `no_NA_sampler`, then call your function.

```{r no-4, exercise = TRUE}

```


```{r no-4-hint-1, eval = FALSE}
no_NA_sampler <- function(){
  ...
}

no_NA_sampler()
```

```{r no-4-hint-2, eval = FALSE}
Put your code from the previous exercise in place of the ... 
```

### Exercise 5

Let's adjust our code so we can pull any sample, not just 10! To do so, place an `n` inside `function()`. Also replace 10 with `n` inside `sample_n()`. 

```{r no-5, exercise = TRUE}

```


```{r no-5-hint-1, eval = FALSE}
no_NA_sampler <- function(...){
  nhanes %>% 
    drop_na() %>%
    sample_n(...) %>% 
    pull(weight)
}
no_NA_sampler()
```

### Exercise 6

Put your function in action! Use the function `no_NA_sampler()` and set `n` to 20. 

```{r no-6-setup}
no_NA_sampler <- function(n){
  nhanes %>% 
    drop_na() %>%
    sample_n(n) %>% 
    pull(weight)
}
```

```{r no-6, exercise = TRUE}

```

### Exercise 7

Let's adjust our function one last time to allow sampling from any variable or tibble.

Copy/paste your code from above. First, add the argument `tbl` within `function()`. Also replace `nhanes` with `tbl`. 

```{r no-7, exercise = TRUE}

```


```{r no-7-hint-1, eval = FALSE}
no_NA_sampler <- function(..., n){
  ... %>% 
    drop_na() %>%
    sample_n(n) %>% 
    pull(weight)
}
```

### Exercise 8

Great. Now add the argument `var` inside `function()`. Also replace `weight` with the argument `{{var}}`

```{r no-8, exercise = TRUE}

```


```{r no-8-hint-1, eval = FALSE}
no_NA_sampler <- function(..., tbl, n){
  tbl %>% 
    drop_na() %>%
    sample_n(n) %>% 
    pull(...)
}
```

### Exercise 9

Put your function in action! Use the function `no_NA_sampler()`. The first argument to `no_NA_sampler()` should be `cces`. The second argument should be `age`. Then, set `n` to 10. 

```{r no-9-setup}
no_NA_sampler <- function(var, tbl, n){
  tbl %>% 
    drop_na() %>%
    sample_n(n) %>% 
    pull({{var}})
}
```

```{r no-9, exercise = TRUE}

```


## Prediction Game
###

Before you complete this section, make sure to read the [Prediction Game](https://ppbds.github.io/primer/functions.html#prediction-game) section of the primer!

In this section, we will build a function called `prediction_game()` that allows for any guesses, tibble, and variable as an argument.


### Exercise 1

Let's start by using `glimpse()` to look at `kenya`.

```{r pg-1, exercise = TRUE}

```

### Exercise 2

Now create a function named `prediction_game()` `that does nothing. 

```{r pg-2, exercise = TRUE}

```

```{r pg-2-hint-1, eval = FALSE}
Use function() and { }
```

```{r pg-2-hint-2, eval = FALSE}
prediction_game<- function() { 
  }
```

### Exercise 3

Copy/paste your code from above. Have your function always `return()` "I win!". Then, call your function.

```{r pg-3, exercise = TRUE}

```

```{r pg-3-hint-1, eval = FALSE}
prediction_game<- function() { 
  ...
}

prediction_game()
```

```{r pg-3-hint-2, eval = FALSE}
prediction_game<- function() { 
  return(...)
}

prediction_game()
```

### Exercise 4

Now add the argument `guesses` inside `function()`. Then, call your function. Notice that doesn't change anything yet. 

```{r pg-4, exercise = TRUE}

```

```{r pg-4-hint, eval = FALSE}
prediction_game<- function(...) { 
  return("I win!")
}

prediction_game()
```

### Exercise 5

Now use `stopifnot()` to make our function stop if we do not select two guesses. Inside `stopifnot()`, use the argument `all(is_double())`. Within `is_double()` use the argument `guesses`. Then, call your function.

```{r pg-5, exercise = TRUE}

```

```{r pg-5-hint, eval = FALSE}
prediction_game<- function(guesses) { 
  return("I win")
  stopifnot(all(is_double(...)))
  
}

prediction_game()
```

### Exercise 6

Let's also use `stopifnot()` to make our function stop if the guesses are not in the format of c(guess 1, guess 2). Inside `stopifnot()`, use the argument `length()` with the argument `guesses`. Set the `length()` statement equal to 2. Then, call your function.

```{r pg-6, exercise = TRUE}

```

```{r pg-6-hint-1, eval = FALSE}
Use the equal operator outside of length(guesses). Recall to use == rather than = . 
   
```

```{r pg-6-hint-2, eval = FALSE}
prediction_game<- function(guesses) { 
  return("I win")
  stopifnot(all(is_double(guesses)))
  stopifnot(length(...) == ...)
   

}

prediction_game()
```

### Exercise 7

Great. Now tell the function that the "guess" inputted first is `guess_1` and the second input is `guess_2`. 

Assign `guesses[1]` to `guess_1`. Also, assign `guesses[2]` to `guess_2`. Then, call your function.

```{r pg-7, exercise = TRUE}

```

```{r pg-7-hint, eval = FALSE}
prediction_game<- function(guesses) { 
  return("I win")
  stopifnot(all(is_double(guesses)))
  stopifnot(length(...) == ...)
  
  guess_1 <- guesses[...]
  guess_2 <- guesses[...]

}

prediction_game()

```

### Exercise 8

Now add the `tbl` and `var` arguments within `function()`. Also, use `no_NA_sampler()`. The first argument to `no_NA_sampler()` should be `tbl`. The second argument should be `{{var}}`. Then, set `n` to 1.  Assign your work to an object named `sampled_value`. Then, call your function.

```{r pg-8, exercise = TRUE}

```

```{r pg-8-hint, eval = FALSE}
prediction_game<- function(guesses, ..., ...) { 
  return("I win")
  stopifnot(all(is_double(guesses)))
  stopifnot(length(guesses) == 2)

  guess_1 <- guesses[1]
  guess_2 <- guesses[2]
  
  sampled_value <- no_NA_sampler(..., ..., ...)
  
}

prediction_game()
```

### Exercise 9

Let's calculate the error for each guess. Use `abs()` and subtract `sampled_value` from `guess_1`. Save your work to an object named `guess1_error`. Then, call your function.

```{r pg-9, exercise = TRUE}

```

```{r pg-9-hint, eval = FALSE}
prediction_game<- function(guesses, tbl, var) { 
  return("I win")
  stopifnot(all(is_double(guesses)))
  stopifnot(length(guesses) == 2)

  guess_1 <- guesses[1]
  guess_2 <- guesses[2]

  sampled_value <- no_NA_sampler(tbl, {{var}}, n = 1)
  guess1_error <- abs(...- ...)
  
}

prediction_game()
```

### Exercise 10

Let's calculate the error for the second guess. Use `abs()` and subtract `sampled_value` from `guess_2`.Save your work to an object named `guess2_error`. Then, call your function.

```{r pg-10, exercise = TRUE}

```

```{r pg-10-hint, eval = FALSE}
prediction_game<- function(guesses, tbl, var) { 
  return("I win")
  stopifnot(all(is_double(guesses)))
  stopifnot(length(guesses) == 2)
  
  guess_1 <- guesses[1]
  guess_2 <- guesses[2]
  
  sampled_value <- no_NA_sampler(tbl, {{var}}, n = 1)

  guess1_error <- abs(guess_1- sampled_value)
  guess2_error <- abs(...- ...)

}

prediction_game()
```

### Exercise 11

Let's now have our code tell which is closer to the sampled value. First, remove `return("I win")` from your code. On the line below, call your function. Then, call your function.

```{r pg-11, exercise = TRUE, error = TRUE}

```

```{r pg-11-hint, eval = FALSE}
prediction_game<- function(guesses, tbl, var) { 
  stopifnot(all(is_double(guesses)))
  stopifnot(length(guesses) == 2)
  
  guess_1 <- guesses[1]
  guess_2 <- guesses[2]
  
  sampled_value <- no_NA_sampler(tbl, {{var}}, n = 1)

  guess1_error <- abs(guess_1- sampled_value)
  guess2_error <- abs(guess_2- sampled_value)

  
}

prediction_game()
```

Oh no! We get the error message *argument "guesses" is missing, with no default*. That is because we need to set the argument `guesses` to a value within `prediction_game()`. Note that we also need to specify the `tbl` and `var` arguments too. 


### Exercise 12

Let's add in the required arguments for `guesses`, `tbl`, and `var`. Copy and paste your code from above. When you call your function, set the argument `guesses` to `c(150, 700)`. Also set `tbl` to `kenya` and `var` to `rv13`.

```{r pg-13, exercise = TRUE, error = TRUE}

```

```{r pg-13-hint, eval = FALSE}
prediction_game<- function(guesses, tbl, var) { 
  stopifnot(all(is_double(guesses)))
  stopifnot(length(guesses) == 2)
  
  guess_1 <- guesses[1]
  guess_2 <- guesses[2]
  
  sampled_value <- no_NA_sampler(tbl, {{var}}, n = 1)

  guess1_error <- abs(guess_1- sampled_value)
  guess2_error <- abs(guess_2- sampled_value)

  if(guess1_error < guess2_error) { 
    return(paste("Guess", guess_1, "wins!"))
  }

}
prediction_game(guesses = ..., tbl = ..., var = ...)
```

<!-- BG: I get "object not found" whenever I try to use kenya and the rv13 variable -->

### Exercise 13

How do we know which guess was better? Let's have our function print out a message.

Use `if()` with the argument `guess1_error` less than `guess2_error`. Then use `{ }`. Within `{ }`, use `return()` with the argument `paste()`. The first argument to `paste()` should be "Guess". The second argument should be `guess_1`. The third argument should be "wins!".

```{r pg-12, exercise = TRUE}

```

```{r pg-12-hint, eval = FALSE}
prediction_game<- function(guesses, tbl, var) { 
  stopifnot(all(is_double(guesses)))
  stopifnot(length(guesses) == 2)
  
  guess_1 <- guesses[1]
  guess_2 <- guesses[2]
  
  sampled_value <- no_NA_sampler(tbl, {{var}}, n = 1)

  guess1_error <- abs(guess_1- sampled_value)
  guess2_error <- abs(guess_2- sampled_value)

  if( ... < ...) { 
    return(paste(..., ..., ...))
    
  }

}
prediction_game(guesses = c(150, 700), tbl = kenya, var = rv13)
```

### Exercise 14

Let's repeat the same code, but now for `guess_2`. When you call your function, you should get a message that reveals which guess wins.

```{r pg-14, exercise = TRUE}

```

```{r pg-14-hint, eval = FALSE}
prediction_game<- function(guesses, tbl, var) { 
  stopifnot(all(is_double(guesses)))
  stopifnot(length(guesses) == 2)
  
  guess_1 <- guesses[1]
  guess_2 <- guesses[2]
  
  sampled_value <- no_NA_sampler(tbl, {{var}}, n = 1)

  guess1_error <- abs(guess_1- sampled_value)
  guess2_error <- abs(guess_2- sampled_value)

  if(guess1_error < guess2_error) { 
    return(paste("Guess", guess_1, "wins!"))
  }
  
 if( ... < ...) { 
    return(paste(..., ..., ...))
 }
  
}

prediction_game(guesses = c(150, 700), tbl = kenya, var = rv13)
```

### Exercise 15

Copy/paste your code from above. Use `replicate()` to run our game five times. The first argument to `replicate()` should be 5. The second argument should be `prediction_game(guesses = c(150, 700), tbl = kenya, var = rv13)`.

```{r pg-15, exercise = TRUE}

```

```{r pg-15-hint, eval = FALSE}
prediction_game<- function(guesses, tbl, var) { 
  stopifnot(all(is_double(guesses)))
  stopifnot(length(guesses) == 2)
  
  guess_1 <- guesses[1]
  guess_2 <- guesses[2]
  
  sampled_value <- no_NA_sampler(tbl, {{var}}, n = 1)

  guess1_error <- abs(guess_1- sampled_value)
  guess2_error <- abs(guess_2- sampled_value)

  if( guess1_error < guess2_error) { 
    return(paste("Guess", guess_1, "wins!"))
  }
    
  if(guess2_error < guess1_error) { 
    return(paste("Guess", guess_2, "wins!"))
  }

}

replicate(..., prediction_game(guesses = c(150, 700), tbl = kenya, var = rv13))
```

