---
title: "Functions B"
tutorial:
  id: "functions-b"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Chapter 3 Tutorial Part B"
---


```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(skimr)
library(primer.data)

# Key Data

no_NA_sampler <- function(var, tbl, n){
  tbl %>% 
    drop_na() %>%
    sample_n(n) %>% 
    pull({{var}})
}

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

```

## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```


## no_NA_sampler()
###

In this section, we will make a custom function called `no_NA_sampler()`.

### Exercise 1

Recall the `nhanes` dataset. Use `$` to extract the `weight` column. 

```{r no-1, exercise = TRUE}

```


```{r no-1-hint-1, eval = FALSE}
nhanes$...
```

```{r no-1-hint-2, eval = FALSE}
nhanes$weight
```

### Exercise 2

We will create a function that allows us to sample `weight` from a tibble that contains no NA values for any of its variables. To warm up, use `sample()` to sample 5 values from `nhanes$weight`.

```{r no-2, exercise = TRUE}

```


```{r no-2-hint-1, eval = FALSE}
sample(..., ...)
```

```{r no-2-hint-2, eval = FALSE}
sample(nhanes$..., size = ...)
```

### Exercise 3

Start a pipe with `nhanes`. Use `drop_na()` to get rid of any NA values.

```{r no-3, exercise = TRUE}

```

```{r no-3-hint, eval = FALSE}
... %>% 
  drop_na()
```

### Exercise 4

Copy/paste your code from above. Pipe the result to `sample_n()`, setting the `size` argument to 3. Note that we are using `sample_n()` --- because we want all the rows from the tibble --- and not `sample()` --- which just gets values from a vector --- as we did in Exercise 2

```{r no-4, exercise = TRUE}

```

```{r no-4-hint, eval = FALSE}
... %>% 
  sample_n(size = ...)
```

### Exercise 5 

Copy/paste your code from above. Pipe the result to `pull()` with the argument `weight`. 

```{r no-5, exercise = TRUE}

```


```{r no-5-hint, eval = FALSE}
... %>% 
  pull(...)
```

### Exercise 6

The above code does what we want. Now we need to place it into a function. But, first, let's make a function `no_NA_sampler()` that doesn't do anything.

```{r no-6, exercise = TRUE}

```


```{r no-6-hint, eval = FALSE}
no_NA_sampler <- function(){
  
}
```

### Exercise 7

Copy/paste your code from above. Then, on the line below, call `no_NA_sampler()` to confirm that no output, beyond NULL, is returned. This is a common structure for tutorial questions going forward: define the function and then call the function you have, in this answer, just defined.

```{r no-7, exercise = TRUE}

```


```{r no-7-hint-1, eval = FALSE}
no_NA_sampler <- function(){
  
}

no_NA_sampler()
```

### Exercise 8

Copy/paste your code from Exercise 5 and place it inside the body `{ }` of `no_NA_sampler()`. Then, call `no_NA_sampler()`. 

```{r no-8, exercise = TRUE}

```


```{r no-8-hint-1, eval = FALSE}
no_NA_sampler <- function(){
  ...
}

no_NA_sampler()
```

### Exercise 9

Now adjust the code so we can pull any sample, not just 3! To do so, add the `n` argument inside `function()`. Also replace the 3 within `sample_n()` with `n`. 

```{r no-9, exercise = TRUE}

```


```{r no-9-hint-1, eval = FALSE}
no_NA_sampler <- function(...){
  nhanes %>% 
    drop_na() %>%
    sample_n(size = ...) %>% 
    pull(weight)
}
```

### Exercise 10

Add a call `no_NA_sampler()`. Notice that you receive an error message.


```{r no-10, exercise = TRUE}

```

```{r no-10-hint, eval = FALSE}
no_NA_sampler <- function(n){
  nhanes %>% 
    drop_na() %>%
    sample_n(size = n) %>% 
    pull(weight)
}

no_NA_sampler()
```

### Exercise 11

The error message suggested that we need to pass an argument for `n` when we call `no_NA_sampler()`. Call `no_NA_sampler()` setting the `n` argument to 5.


```{r no-11, exercise = TRUE}

```

```{r no-11-hint, eval = FALSE}
no_NA_sampler <- function(n){
  nhanes %>% 
    drop_na() %>%
    sample_n(size = n) %>% 
    pull(weight)
}

no_NA_sampler(...)
```

Great. Now we can use `no_NA_sampler()` to get however many values of weight that we want!


### Exercise 12

Copy/paste your code from above. Let's adjust our function to allow sampling from any variable. To do so, add the `var` argument inside `function()`. Also replace `weight` within `pull()` with `{{var}}`. (See *The Primer* for a discussion of the magic associated with "{{}}")

```{r no-12, exercise = TRUE}

```


```{r no-12-hint-1, eval = FALSE}
no_NA_sampler <- function(n, ...){
  nhanes %>% 
    drop_na() %>%
    sample_n(size = n) %>% 
    pull(...)
}
```

```{r no-12-hint-2, eval = FALSE}
no_NA_sampler <- function(n, var){
  nhanes %>% 
    drop_na() %>%
    sample_n(size = n) %>% 
    pull({{var}})
}
```

### Exercise 13

Now call `no_NA_sampler()`. (Recall that you need to copy/paste the definition of the function into any answer which is using that function.) Recall that we will receive an error message if we don't specify the `n` and `var` arguments. Call `no_NA_sampler()` setting the `n` argument to 5 and `var` to `height`.



```{r no-13, exercise = TRUE}

```


```{r no-13-hint-1, eval = FALSE}
no_NA_sampler <- function(n, var){
  nhanes %>% 
    drop_na() %>%
    sample_n(size = n) %>% 
    pull({{var}})
}

no_NA_sampler(n = ..., var = ...)
```

### Exercise 14

Let's adjust our function one last time to now allow sampling from any tibble. (The code so far has been provided for you because we are nice.)  Add the `tbl` argument inside `function()`. Also replace `nhanes` with `tbl`. We do not need to use the magic of "{{}}" for passing a tibble into a function.

```{r no-14, exercise = TRUE}
no_NA_sampler <- function(n, var){
  nhanes %>% 
    drop_na() %>%
    sample_n(size = n) %>% 
    pull({{var}})
}
```


```{r no-14-hint-1, eval = FALSE}
no_NA_sampler <- function(n, var, ...){
... %>% 
    drop_na() %>%
    sample_n(size = n) %>% 
    pull({{var}})
}
```

### Exercise 15

Great. Now call the `no_NA_sampler()` with the argument `n` set to 5. Also set `var` to `age` and set `tbl` to `cces`.



```{r no-15, exercise = TRUE}

```

```{r no-15-hint, eval = FALSE}
no_NA_sampler <- function(n, var, tbl){
  tbl %>% 
    drop_na() %>%
    sample_n(size = n) %>% 
    pull({{var}})
}

no_NA_sampler(n = ..., var = ..., tbl = ...)
```

Great work. `no_NA_sampler()` allows us to sample values from any variable in any tibble, after removing any rows with NA values. 

## Prediction Game
###

Before you complete this section, make sure to read the [Prediction Game](https://ppbds.github.io/primer/functions.html#prediction-game) section of *The Primer*!

In this section, we will build a function called `prediction_game()`. In the game, you submit two guesses, along with a tibble and a variable. The winner is the guess which is closest to a value of a random sample of that variable from that tibble.  

### Exercise 1

Let's start by using `glimpse()` to look at `kenya`.

```{r pg-1, exercise = TRUE}

```

### Exercise 2

Now create a function named `prediction_game()` `that does nothing. 

```{r pg-2, exercise = TRUE}

```

```{r pg-2-hint-1, eval = FALSE}
Use function() and { }
```

```{r pg-2-hint-2, eval = FALSE}
prediction_game <- function() { 
  
}
```

### Exercise 3

Copy/paste your code from above. Have your function always `return()` "I win!". On the line below, call your function.

```{r pg-3, exercise = TRUE}

```

```{r pg-3-hint-1, eval = FALSE}
prediction_game<- function() { 
  ...
}

prediction_game()
```

```{r pg-3-hint-2, eval = FALSE}
prediction_game<- function() { 
  return("I win!")
}

prediction_game()
```

### Exercise 4

Now add the argument `guesses` inside `function()`. Then, call your function. Note that this change doesn't affect anything yet sinece you have not used `guesses` for anything. Note, also, that the function still works, even if you don't pass in a value for `guesses` because the argument is not used in the function.

```{r pg-4, exercise = TRUE}

```

```{r pg-4-hint, eval = FALSE}
prediction_game<- function(...) { 
  return("I win!")
}

prediction_game()
```

### Exercise 5

<!-- DK: This goes too fast. First check that length of guesses is two. Then check if both are doubles. Explain in the question what all() is doing. Maybe only two one check, that guesses is length 2. -->

Now use `stopifnot()` to make our function stop if we do not provide two guesses. Inside `stopifnot()`, use the argument `all(is_double())`. Within `is_double()` use the argument `guesses`. Then, call your function.

```{r pg-5, exercise = TRUE}

```

```{r pg-5-hint, eval = FALSE}
prediction_game<- function(guesses){ 
  stopifnot(all(is_double(...)))
  return("I win")
}

prediction_game()
```

### Exercise 6

Let's also use `stopifnot()` to make our function stop if the guesses are not in the format of c(guess 1, guess 2). Inside `stopifnot()`, use the argument `length()` with the argument `guesses`. Set the `length()` statement equal to 2. Then, call your function.

```{r pg-6, exercise = TRUE}

```

```{r pg-6-hint-1, eval = FALSE}
Use the equal operator outside of length(guesses). Recall to use == rather than = . 
   
```

```{r pg-6-hint-2, eval = FALSE}
prediction_game<- function(guesses) { 
  stopifnot(all(is_double(guesses)))
  stopifnot(length(...) == ...)
  return("I win")
}

prediction_game()
```

### Exercise 7

Great. Now tell the function that the "guess" inputted first is `guess_1` and the second input is `guess_2`. 

Assign `guesses[1]` to `guess_1`. Also, assign `guesses[2]` to `guess_2`. Then, call your function.

```{r pg-7, exercise = TRUE}

```

```{r pg-7-hint, eval = FALSE}
prediction_game<- function(guesses) { 
  return("I win")
  stopifnot(all(is_double(guesses)))
  stopifnot(length(...) == ...)
  
  guess_1 <- guesses[...]
  guess_2 <- guesses[...]

}

prediction_game()

```

### Exercise 8

Now add the `tbl` and `var` arguments within `function()`. Also, use `no_NA_sampler()`. The first argument to `no_NA_sampler()` should be `tbl`. The second argument should be `{{var}}`. Then, set `n` to 1.  Assign your work to an object named `sampled_value`. Then, call your function.

```{r pg-8, exercise = TRUE}

```

```{r pg-8-hint, eval = FALSE}
prediction_game<- function(guesses, ..., ...) { 
  return("I win")
  stopifnot(all(is_double(guesses)))
  stopifnot(length(guesses) == 2)

  guess_1 <- guesses[1]
  guess_2 <- guesses[2]
  
  sampled_value <- no_NA_sampler(..., ..., ...)
  
}

prediction_game()
```

### Exercise 9

Let's calculate the error for each guess. Use `abs()` and subtract `sampled_value` from `guess_1`. Save your work to an object named `guess1_error`. Then, call your function.

```{r pg-9, exercise = TRUE}

```

```{r pg-9-hint, eval = FALSE}
prediction_game<- function(guesses, tbl, var) { 
  return("I win")
  stopifnot(all(is_double(guesses)))
  stopifnot(length(guesses) == 2)

  guess_1 <- guesses[1]
  guess_2 <- guesses[2]

  sampled_value <- no_NA_sampler(tbl, {{var}}, n = 1)
  guess1_error <- abs(...- ...)
  
}

prediction_game()
```

### Exercise 10

Let's calculate the error for the second guess. Use `abs()` and subtract `sampled_value` from `guess_2`.Save your work to an object named `guess2_error`. Then, call your function.

```{r pg-10, exercise = TRUE}

```

```{r pg-10-hint, eval = FALSE}
prediction_game<- function(guesses, tbl, var) { 
  return("I win")
  stopifnot(all(is_double(guesses)))
  stopifnot(length(guesses) == 2)
  
  guess_1 <- guesses[1]
  guess_2 <- guesses[2]
  
  sampled_value <- no_NA_sampler(tbl, {{var}}, n = 1)

  guess1_error <- abs(guess_1- sampled_value)
  guess2_error <- abs(...- ...)

}

prediction_game()
```

### Exercise 11

Let's now have our code tell us which guess is closer to the sampled value. First, remove `return("I win")` from your code. On the line below, call your function. Then, call your function.

```{r pg-11, exercise = TRUE, error = TRUE}

```

```{r pg-11-hint, eval = FALSE}
prediction_game <- function(guesses, tbl, var) { 
  stopifnot(all(is_double(guesses)))
  stopifnot(length(guesses) == 2)
  
  guess_1 <- guesses[1]
  guess_2 <- guesses[2]
  
  sampled_value <- no_NA_sampler(tbl, {{var}}, n = 1)

  guess1_error <- abs(guess_1- sampled_value)
  guess2_error <- abs(guess_2- sampled_value)

  
}

prediction_game()
```

Oh no! We get the error message *argument "guesses" is missing, with no default*. That is because we need to set the argument `guesses` to a value within `prediction_game()`. Note that we also need to specify the `tbl` and `var` arguments too. 


### Exercise 12

Let's add in the required arguments for `guesses`, `tbl`, and `var`. Copy and paste your code from above. When you call your function, set the argument `guesses` to `c(150, 700)`. Also set `tbl` to `kenya` and `var` to `rv13`.

```{r pg-13, exercise = TRUE, error = TRUE}

```

```{r pg-13-hint, eval = FALSE}
prediction_game<- function(guesses, tbl, var) { 
  stopifnot(all(is_double(guesses)))
  stopifnot(length(guesses) == 2)
  
  guess_1 <- guesses[1]
  guess_2 <- guesses[2]
  
  sampled_value <- no_NA_sampler(tbl, {{var}}, n = 1)

  guess1_error <- abs(guess_1- sampled_value)
  guess2_error <- abs(guess_2- sampled_value)

  if(guess1_error < guess2_error) { 
    return(paste("Guess", guess_1, "wins!"))
  }

}
prediction_game(guesses = ..., tbl = ..., var = ...)
```

<!-- BG: I get "object not found" whenever I try to use kenya and the rv13 variable -->

### Exercise 13

How do we know which guess was better? Let's have our function print out a message.

Use `if()` with the argument `guess1_error` less than `guess2_error`. Then use `{ }`. Within `{ }`, use `return()` with the argument `paste()`. The first argument to `paste()` should be "Guess". The second argument should be `guess_1`. The third argument should be "wins!".

```{r pg-12, exercise = TRUE}

```

```{r pg-12-hint, eval = FALSE}
prediction_game<- function(guesses, tbl, var) { 
  stopifnot(all(is_double(guesses)))
  stopifnot(length(guesses) == 2)
  
  guess_1 <- guesses[1]
  guess_2 <- guesses[2]
  
  sampled_value <- no_NA_sampler(tbl, {{var}}, n = 1)

  guess1_error <- abs(guess_1- sampled_value)
  guess2_error <- abs(guess_2- sampled_value)

  if( ... < ...) { 
    return(paste(..., ..., ...))
    
  }

}
prediction_game(guesses = c(150, 700), tbl = kenya, var = rv13)
```

### Exercise 14

Let's repeat the same code, but now for `guess_2`. When you call your function, you should get a message that reveals which guess wins.

```{r pg-14, exercise = TRUE}

```

```{r pg-14-hint, eval = FALSE}
prediction_game<- function(guesses, tbl, var) { 
  stopifnot(all(is_double(guesses)))
  stopifnot(length(guesses) == 2)
  
  guess_1 <- guesses[1]
  guess_2 <- guesses[2]
  
  sampled_value <- no_NA_sampler(tbl, {{var}}, n = 1)

  guess1_error <- abs(guess_1- sampled_value)
  guess2_error <- abs(guess_2- sampled_value)

  if(guess1_error < guess2_error) { 
    return(paste("Guess", guess_1, "wins!"))
  }
  
 if( ... < ...) { 
    return(paste(..., ..., ...))
 }
  
}

prediction_game(guesses = c(150, 700), tbl = kenya, var = rv13)
```

### Exercise 15

Copy/paste your code from above. Use `replicate()` to run our game five times. The first argument to `replicate()` should be 5. The second argument should be `prediction_game(guesses = c(150, 700), tbl = kenya, var = rv13)`.

```{r pg-15, exercise = TRUE}

```

```{r pg-15-hint, eval = FALSE}
prediction_game<- function(guesses, tbl, var) { 
  stopifnot(all(is_double(guesses)))
  stopifnot(length(guesses) == 2)
  
  guess_1 <- guesses[1]
  guess_2 <- guesses[2]
  
  sampled_value <- no_NA_sampler(tbl, {{var}}, n = 1)

  guess1_error <- abs(guess_1- sampled_value)
  guess2_error <- abs(guess_2- sampled_value)

  if( guess1_error < guess2_error) { 
    return(paste("Guess", guess_1, "wins!"))
  }
    
  if(guess2_error < guess1_error) { 
    return(paste("Guess", guess_2, "wins!"))
  }

}

replicate(..., prediction_game(guesses = c(150, 700), tbl = kenya, var = rv13))
```

## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```


