---
title: 'Probability: Distributions'
tutorial:
  id: probability-distributions
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: Practice working with and understanding distributions.
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(primer.data)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

```{r copy-code-chunk, child = "../../child_documents/copy_button.Rmd"}
```

```{r info-section, child = "../../child_documents/info_section.Rmd"}
```

<!-- Change Monte Hall plot to use geom_bar(aes(y = after_stat(count/sum(count))) -->


<!-- Two other possible exercises to add to this tutorial. First is the game of craps. The shooter rolls. If she gets 7 or 11, she wins. If she gets 2, 3, or 12, she loses. Either way, the round is over. If, however, she gets 4, 5, 6, 8, 9 or 10, then this new value because her "point." She then rolls, over and over again, until she either "hits" or "makes" her point (by rolling it) or until she gets a 7, in which case you loses. Turns out that the odds of the shooter winning is about 49.3%. So, the house wins if you play long enough.  -->

<!-- Second simulation is like the 538 NCAA basketball model. Simplified version of the basketball. Assume 64 teams, single elimination. Use historical performance to give a rough sense of how well different seeds do against each other. Come up with a "strength" measure for each seed.  -->


<!-- Define a distribution. A mathematical object with two components: a list of possible outcomes and a corresponding frequency for each outcome. In a normalized distribution, the sum of the frequencies is 1.  -->

<!-- Note that this is a sloppy definition because it does not apply to continuous distributions. Need to mention this and then wave our hands. -->

<!-- Define a random variable is "a variable whose values depend on outcomes of a random phenomenon." Example: Result of one coin flip. -->

<!-- Add to chapter 5 a tutorial whose sole focus is distributions. First part of this is going slowly through the process by which counts can be turned into percentages. Do this in, at least, five ways. First, with geom_bar() which (I think) does the counting for us. Second, with geom_col(), in which we need to create the counts ourselves. Third with geom_histogram(). Fourth then maybe create a histogram by hand, using cut() and then counting up the elements in each range. -->

<!-- Maybe have a section explaining how the distribution of the error term is what motivates the selection of the appropriate family argument in stan_glm(). -->


## Introduction
### 

A distribution is a mathematical object with two components: a list of possible outcomes and a corresponding frequency for each outcome or simply *the collection of data on a single variable*. Normalized distribution is essentially turning the frequency into percent, and which sum up equal to 1.


This tutorial has three missions:
1. Digging deep in distribution
2. Using simulation to solve problem
3. Practice the manipulation of distribution


## Random variables
### 

### Exercise 1

Type `rolls` to inspect the vector below.

```{r random-variables-1, exercise = TRUE}
rolls <- c(5, 5, 1, 5, 4, 2, 6, 2, 1, 5)
```

### Exercise 2

Great. Now use `table()` with the argument `rolls` to record the number of times each value appears.

```{r random-variables-2, exercise = TRUE}

```

```{r random-variables-2-hint-1, eval = FALSE}
table(...)
```

### Exercise 3

Now use `rep()` to repeat `rolls` 1,000 times. The first argument to `rep()` should be `rolls`. The second argument should be 1000.


```{r random-variables-3, exercise = TRUE}

```

```{r random-variables-3-hint-1, eval = FALSE}
rep(..., ...)
```

What does this show us? Well, rather than keeping around a vector of length 10,000, we can just keep 10 values, without losing any information!


### Exercise 4

Let's create a distribution of the possible values from rolling a fair die. To do so, use the `c()` that contain values 1-6. Save your code to an object named `die`.

```{r random-variables-4, exercise = TRUE}

```

```{r random-variables-4-hint-1, eval = FALSE}
die <- c(...)
```

```{r random-variables-4-hint-2, eval = FALSE}
You can use the `:` operator as a shortcut!
```

### Exercise 5

Let's now complete a single draw from our distribution using `sample()`. Within `sample()`, set the argument `x` to `die` and `size` to 1.

```{r random-variables-5, exercise = TRUE}

```

```{r random-variables-5-hint-1, eval = FALSE}
sample(x = ..., size = ...)
```

### Exercise 6

Copy/paste your code from above. Adjust the `size` argument to 12. Also add the argument `replace` set to TRUE.

```{r random-variables-6, exercise = TRUE}

```

```{r random-variables-6-hint-1, eval = FALSE}
Within `sample()`, you should have 3 arguments: x, size, and replace.
```

### Exercise 7

Let's say that before we draw, the probability of rolling a 5 is 0.5, and the probability of rolling any other value is 0.1. Copy/paste your code from above. Set the `prob` argument to a vector that contains each number's probability.

```{r random-variables-7, exercise = TRUE}

```

```{r random-variables-7-hint-1, eval = FALSE}
Within c(), there should be six decimals (probability values) that correspond to each number of the die respectively.
```

```{r random-variables-7-hint-2, eval = FALSE}
sample(x = die,
       size = 10,
       replace = TRUE,
       prob = c(..., ..., ..., ... , 0.5, ...))
```

### Exercise 8

Let's now use `runif()` to draw from a uniform distribution. Within `runif()`, set `n` to 5 (the number of draws), `min` to 5, and `max` to 8.


```{r random-variables-8, exercise = TRUE}

```

```{r random-variables-8-hint-1, eval = FALSE}
runif(n = ..., min = ..., max =...)
```

### Exercise 9

Let's now use `rbinom` to draw from a binomial distribution like flipping a coin. Within `rbinom()`, set `n` to 1, `size` to 1, and `prob` to .05.

```{r random-variables-9, exercise = TRUE}

```

```{r random-variables-9-hint-1, eval = FALSE}
rbinom(... , ..., ....)
```

```{r random-variables-9-hint-2, eval = FALSE}
rbinom(n = ..., size = ..., prob = ....)
```

### Exercise 10

Let's put our code in tibble format using `tibble()`. Within `tibble()`, create a column `heads` which is set to the results of `rbinom()`. Within `rbinom()`, set `n` to 50, `size` to 1, and `prob` to .5.

```{r random-variables-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r random-variables-10-hint-1, eval = FALSE}
tibble(... = rbinom(..., ..., ...))
```

Notice that we now are drawing from a binomial distribution 50 times! We put the code in tibble format so we can plot it.

### Exercise 11

Let's now plot our results. Copy/paste your code from above. Use `|>` to add `ggplot()`. Map `heads` to the x-axis. Also add the layer `geom_bar()`.

```{r random-variables-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r random-variables-11-hint-1, eval = FALSE}
... |>
  ggplot(aes(...)) +
    geom_bar()
```

### Exercise 12

Use `labs()` to title your graph "Flipping a Coin 50 Times". Also label your x-axis "Result" and y-axis "Count".

```{r random-variables-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r random-variables-12-hint-1, eval = FALSE}
... +
  labs(title = ...,
       x= ...,
       y = ...)
```

### Exercise 13

Now use `scale_x_continuous()` so the x-axis has `breaks` at 0 and 1. Set the `labels` for the breaks as "Tails" and "Heads", respectively.


```{r random-variables-13, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

This is what your plot should look like.

```{r}
tibble(heads = rbinom(n = 50, size = 1, prob = 0.5)) |>
  ggplot(aes(x = heads)) +
    geom_bar() +
    labs(title = "Flipping a Fair Coin 50 Times",
         x = "Result",
         y = "Count") +
    scale_x_continuous(breaks = c(0, 1),
                       labels = c("Tails", "Heads"))
```

```{r random-variables-13-hint-1, eval = FALSE}
Use the c() function for specifying the breaks and labels.
```

```{r random-variables-13-hint-2, eval = FALSE}
... +
  scale_x_continuous(breaks = ...,
                     labels = ...)
```

```{r random-variables-13-hint-3, eval = FALSE}
... +
  scale_x_continuous(breaks = c(..., ...),
                     labels = c(..., ...))
```

### Exercise 14

Let's use `rnorm()` to draw from a normal distribution. Within `rnorm()`, set `n` to 40.

```{r random-variables-14, exercise = TRUE}

```

### Exercise 15

Let's now add the arguments `mean` and `sd` to our code above. Set `mean` to  0 and `sd` to 3.

```{r random-variables-15, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r random-variables-15-hint-1, eval = FALSE}
rnorm() should now have three arguments: n, mean, and sd.
```

### Exercise 16

Save your code above to an object named `draws`.

```{r random-variables-16, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r random-variables-16-hint-1, eval = FALSE}
draws <- rnorm(..., ..., ... )
```

### Exercise 17

Use `c()` to find the `mean()`, `sd()`,`median()`, and `mad()` of `draws`.

```{r random-variables-17, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r random-variables-17-hint-1, eval = FALSE}
Place mean(), sd(), median(), and mad() all inside c(), each with the argument draws.
```

### Exercise 18

Let's now use `quantile()` to find the values that occupies the 2.5th and 97.5th percentiles. The first argument to `quantile()` should be `draws`. The second argument should set `probs` to a `c()` function that contains values .025 and .975.

```{r random-variables-18, exercise = TRUE}


```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r random-variables-18-hint-1, eval = FALSE}
quantile(..., probs = ...)
```

```{r random-variables-18-hint-2, eval = FALSE}
quantile(..., probs = c(..., ..))
```

## Monty Hall
### 

Suppose you're on a game show, and you're given the choice of three doors: Behind one door is a car; behind the others, goats. You pick a door, say No. 1, and the host, who knows what's behind the doors, opens another door, say No. 3, which has a goat. He then says to you, "Do you want to pick door No. 2?" Is it to your advantage to switch your choice? This is the (in)famous [Monty Hall problem](https://en.wikipedia.org/wiki/Monty_Hall_problem).

### 

<!-- Maybe start with just 5 rows so that you can see what is happening each time. Only at the end, do you make the tibble be 10,000 rows and then use summarize to calculate your answer or, maybe better, show a graph.  -->


```{r echo = FALSE}
monte_p <- expand_grid(sim = 1:10000, door = 1:3) |>
  
    # my_vec <- c(TRUE, rep(FALSE, n_doors - 1))
  
    # Very handy to do stuff for each simulation separately. Don't forget to
    # ungroup() when you want to act on on the whole tibble at once.
  
    group_by(sim) |>
  
    # sample() returns the whole vector, which is what we want since, in any
    # individual sim, the car is behind one of the three doors and exactly one
    # door is guessed initially.
  
    mutate(car = sample(c(FALSE, FALSE, TRUE))) |>  
    mutate(guess = sample(c(FALSE, FALSE, TRUE))) |> 

    
    # Convenient to always put the guessed door in the first row of each sim
    # group. Then have the actual location of the car as low in the sim group as
    # you can. This sort only matters in cases where the you did not guess the
    # car location. In those cases, you are always placing the car location as
    # the lowest row within the sim group.
  
    # sample_frac() to rearrnage the rows randomly, maybe.
  
    arrange(sim, -guess, car) |> 
    mutate(row_n = row_number(sim)) |>
    mutate(switch_to = row_n == 3) |> 
    mutate(stay_win = if_else(guess & car, TRUE, FALSE)) |> 
    mutate(switch_win = if_else(switch_to & car, TRUE, FALSE))  |>  
  
    # Now, within each sim, we need to see if switch or stay won. They won if
    # there is at least one TRUE value for the stay_win (or switch_win) variable
    # calculated in the previous steps. So, we just need a max.

    summarise(stayWin = max(stay_win),
              switchWin = max(switch_win)) |> 
    
    # For each sim, we now now if staying was a winning strategy and/or if
    # switching was a winning strategy. (With more than three doors, it will
    # often be the case that neither staying nor switching wins, like when you
    # switch from one empty door to the other.)
  
    ungroup() |> 
  
    summarise(stayWin, switchWin) |>
      
    pivot_longer(cols = everything(), 
                 names_to = "decision", 
                 values_to = "result") |>
    filter(result == 1) |>
    ggplot(aes(x = decision)) +
      geom_bar(aes(y = after_stat(count/sum(count))))+
      scale_x_discrete(labels = c("Stay", "Switch"))+
      scale_y_continuous(labels = 
                         scales::percent_format(accuracy = 1)) +
      labs(title = "Monty Hall Problem",
           subtitle = "Probability of winning is higher when you switch doors",
           x = "Results",
           y = "Probability",
           fill = "Decision")
  
monte_p    
```

                          

### Exercise 1

Use `expand_grid()`,create the first variable `sim` and set it equal to the consecutive integer from 1 to 10, create the second variable `door`, and set it equal to 1, 2 and 3.

```{r monty-hall-1, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-1-hint-1, eval = FALSE}
expand_grid(sim = 1:10000, door = 1:3)
```

### 

The reason we create this `sim` value is because later we can switch around the size value, making observation when we increase the simulation size. 

### Exercise 2

Use `group_by()` include the variable `sim`.

```{r monty-hall-2, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-2-hint-1, eval = FALSE}
... |> 
 group_by(sim)
```

### 

We will be doing the simulation within each `sim` separately. We can do this because there is no connection between the separate simulations. Each stands on its own. Running `group_by(sim)` at the stage guarantees that all later code --- at least until we `ungroup()` --- will be run for each value of `sim` separately.

### Exercise 3

Use `mutate()` to create a new variable `car` and set it equal to a call to `sample()` in which which the `x` argument is set to `c(FALSE, FALSE, TRUE)`.

```{r monty-hall-3, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-3-hint-1, eval = FALSE}
... |> 
  mutate(car = sample(c(FALSE, FALSE, TRUE)))
```

### 

`car` is a variable which indicates, for a given `sim`, which door the car is behind. So, within a sim, it must be TRUE once and FALSE the other two times. `sample()`, when called without the `size` argument returns a vector of the same length as the input vector `x`.


### Exercise 4

Use `mutate()` create a new variable `guess` and set it equal to `sample()` which includes 3 values `FALSE`,`FALSE`,`TRUE` wrap around by `c()`.


```{r monty-hall-4, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-4-hint-1, eval = FALSE}
mutate(guess = sample(c(FALSE, FALSE, TRUE))) |> 
```

### 

The reason we don't have an single `sim` correspond to an list in `car` is because we include the `group_by()` statement before.

### Exercise 5

Use `arrange()` which have only one argument `sim`.

```{r monty-hall-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-5-hint-1, eval = FALSE}
... |> 
  arrange(sim)
```

### 

This should have no difference than the outcome of previous exercises, because what we do here is simply making sure that the same number in `sim` s stays together and order from small to greatest.


### Exercise 6

Add another argument within `arrange()`, after `sim` add `-guess`

```{r monty-hall-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-6-hint-1, eval = FALSE}
... |> 
  arrange(sim, -guess)
```

### 

This statement `-guess` means ordering the `guess` column by descending order, normally we would have the `FALSE` (0) in front of the `TRUE` (1), or in random order. This line of code essentially reorder so that `TRUE` always come first in every single `sim`. So now if you observe the `guess` column, you would find that the order is basically the repeat of `TRUE`, `FALSE`, `FALSE` for each `sim`.

### Exercise 7

Add another argument within `arrange()` , after ``-guess` add `car`

```{r monty-hall-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-7-hint-1, eval = FALSE}
arrange(sim, -guess,car)
```

### 

We add `car` in `arrange()`means arrange car in ascending order, which means putting `FALSE` at the beginning, and `TRUE` at the bottom. Therefore now if you look the your tibble, we arrange the `guess` door to be the first row for each `sim`, and `car` door for the last row for each `sim` if possible.


### Exercise 8

Use `mutate()` create a variable `row_n` and set it equal to `row_number(sim)`.

```{r monty-hall-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-8-hint-1, eval = FALSE}
mutate(row_n = row_number(sim)) |>
```

### 

`row_number(sim)` creates the order within each `sim`, for the three rows of each `sim`, generate the rank from top to bottom. This step is setting the stage for the next excercise which we set the door that the contestent is going to switch to is always the third door in order, since we can't choose the first door in order because we arrange it so that we `choose` the first door, then Monty have to open the second door giving that he can't open the door with car and the chosen door, therefore the only option left we chose to open is to open the third door.

<!-- Sentence above which takes from below and explains the plan. -->

### Exercise 9

Use `mutate()` create a new variable `switch_to` and set it equal to the logical if `row_n` is equal to `3`.

```{r monty-hall-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-9-hint-1, eval = FALSE}
mutate(switch_to = row_n == 3)
```

### 

What this step does is if the contestant decided to switch doors,contestant is going to switch the third door in order for each `sim`. This is true because for the first scenario when the contestant guess is not the same as the car door,  For this case Monty can only choose the second door in order for each `sim`, when contestant is going to switch they only can switch to the third door. For second scenario when contestant choose the door with the car, then the other two doors is completely identical, it doesn't really matter which door the contestant choose.

### Exercise 10

Use `mutate()` create a variable `stay_win`, and set it equal to `if_else()` which has three arguments, the first being `guess & car`, the second being `TRUE`, and the third is `FALSE`.

```{r monty-hall-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-10-hint-1, eval = FALSE}
mutate(stay_win = if_else(guess & car, TRUE, FALSE))
```

### 

The `if_else()` statement here means if `guess` and `car` are both `TRUE`, then return `TRUE`, if at least one of `guess` or `car` then returns `FALSE`.

### Exercise 11

Use `mutate()` create a variable `switch_win`, and set it equal to `if_else()` which has three arguments, the first being `switch_to & car`, the second being `TRUE`, and the third is `FALSE`.

```{r monty-hall-11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-11-hint-1, eval = FALSE}
mutate(switch_win = if_else(switch_to & car, TRUE, FALSE))
```

### 

The `if_else()` statement here means if `switch_to` and `car` are both `TRUE`, then return `TRUE`, if at least one of `switch_to` or `car` then returns `FALSE`.

### Exercise 12

Use `summarise()`include two arguments, the first argument create a new variable `stayWin` and set it equal to `max()` of `stay_win`, 

```{r monty-hall-12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-12-hint-1, eval = FALSE}
summarise(stayWin = max(stay_win))
```

### 

Now, within each `sim`, we need to see if switch or stay won. They won if there is at least one TRUE value for the` stay_win` (or `switch_win`) variable calculated in the previous steps. So, we just need a max. Also by looking at the data the first thing you should notice is that we no longer have 30,000 rows, instead we only have 10,000 rows, this is because we `summarise()` with the `group_by()` function at the start of the data, `summarise()` deal with the group with the operation we define, and keeping it to the same length as the result of the operation

### Exercise 13

Then add the second argument create a new variable `switchWin` and set it equal to `max()` of `switch_win`.

```{r monty-hall-13, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-13-hint-1, eval = FALSE}
... |>
  summarise(stayWin = max(stay_win),
          switchWin = max(switch_win))
```

### 

Now this time even without looking at the graph you can clearly see that the 1s which means win occur alot more in `switchWin` than in `stayWin`



### Exercise 14

Now let's `ungroup()`
```{r monty-hall-14, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-14-hint-1, eval = FALSE}
... |>
  ungroup() 
```

### Exercise 15

Use `summarise()` one last time, include arguments, `stayWin` and `switchWin`.
```{r monty-hall-15, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-15-hint-1, eval = FALSE}
... |>
  summarise(stayWin, switchWin)
```

### 

Get rid of `sim`, only keeping the two columns we need to graph.

### Exercise 16

Add the function `pivot_longer()`. Set `cols` to `everything()`, `names_to` to "decision", and `values_to` to  "result".
```{r monty-hall-16, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-16-hint-1, eval = FALSE}
... |>
  pivot_longer(cols = everything(), 
               names_to = "decision", 
               values_to = "result")
```

### 

This step combine the two columns while giving names for it to fill later.

### Exercise 17

Use `filter()` to filter out `result` equal to 1.

```{r monty-hall-17, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-17-hint-1, eval = FALSE}
...|>
  filter(result == 1)
```

### 

This is is essentially pulling the conditional probability of Winning, from the joint distribution which includes both wins and loses.


### Exercise 18

Continue your pipe with `ggplot()` to map `x` to `decison` . Add the layer `geom_bar()`. 

```{r monty-hall-18, exercise = TRUE}
... |>
  ggplot(aes(x = decision)) +
    geom_bar()
```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-18-hint-1, eval = FALSE}

```

### Exercise 19

Within `geom_bar()`,use `aes()`, set `y` equal to  `after_stat()` with the argument `count/sum(count)` to put percents on the y-axis, then outside of `aes()`.

```{r monty-hall-19, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-19-hint-1, eval = FALSE}
... |>
  ggplot(aes(x = result, fill = decision)) +
    geom_bar(aes(y = after_stat(count/sum(count))))
```

### Exercise 20

Now use `scale_x_discrete()` Set the `labels` for the breaks as "Stay" and "Switch", respectively. 

```{r monty-hall-20, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-20-hint-1, eval = FALSE}
... +
  scale_x_continuous(labels = c("Stay", "Switch"))
```

### Exercise 21

Now use `scale_y_continuous()` to put the y-axis in percent format. Within `scale_y_continuous()`, set `labels` to `scales::percent_format()`. Within `percent_format()` set `accuracy` to 1.

```{r monty-hall-21, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-21-hint-1, eval = FALSE}
... + 
  scale_y_continuous(labels = scales::percent_format(...))
```

### Exercise 22

Finally, use `labs()` to add the appropriate title, subtitle, and axis labels.

```{r monty-hall-22, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r monty-hall-22-hint-1, eval = FALSE}
... +
  labs(title = "...")

```

Reminder: Your plot should look like the the one below.

```{r}
monte_p
```

<!-- ## Two daughter puzzle -->
<!-- ### -->

<!-- Consider all the families in town with two children. All children are either boys or girls, each of which occur randomly with 50/50 odds. Pick a family with at least one girl at random. What are the chances that the other child is a girl? -->


<!-- ## Four children problem -->

<!-- All children are either boys or girls, each of which occur randomly with 50/50 odds. Consider families with 4 children. What combination of of genders (2 of each, 3 of 1 and 1 of the other, or all four the same) is most likely. -->




## Summary
### 

```{r download-answers, child = "../../child_documents/download_answers.Rmd"}
```
