---
title: "Data Webscraping"
tutorial:
  id: "data-webscraping"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Chapter 3: Data -- Webscraping"
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(rvest)
library(png)
library(grid)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 
```


## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```

## HTML

HTML, or "HyperText Markup Language" is a markup language that is used to display webpages on browsers. You might have seen html files as a result of knitting Rmd files.

###

### Exercise 1

In this tutorial, you will use the `rvest` package to read the HTML of websites and extract data. First, import the `rvest` package.

You may need to install the `rvest` package in RStudio's console if the code box below outputs an error. If so, use `install.packages("rvest")` in console.

```{r html1, exercise=TRUE}

```

``` {r html1-hint-1, eval=FALSE}
library(...)
```

###

`rvest` is part of the `tidyverse` package. https://rvest.tidyverse.org/ is its official website.

### Exercise 2

HTML uses many nested layers of different tags to organize structure.

For example:

An html file like this:
```{.html}
<html>
<p>
Hello World
  <a>
    link to somewhere
  </a>
</p>

</html>
```

creates the following:
<br><br><br>

<p>
Hello World
<a>
  link to somewhere
</a>
</p>

<br><br><br>

Tags are represented like `<...>` and you will see different kinds of tags and what they can do. This example uses the anchor tag (`<a>`) which creates links and the paragraph tag (`<p>`).

###

A piece of html code is provided in the variable `raw_html`.

First, let's load in a piece of html code into R to understand the html structure using `minimal_html()`. This function takes the raw html text and creates an object to easily access information.

Later, you will read html directly from websites.


```{r html2, exercise=TRUE}
raw_html <- '<html><head><title>Hello World!</title></head><body><p id="p1">This is a paragraph.</p><br><a id="someKindOfLink">This is an anchor, or hyperlink.</a><br>Below is a table:<table><tr><td class="coolData">row1data1</td><td class="coolData">row1data2</td><td class="uncoolData">row1data3</td><td>row1data4</td></tr><tr><td>row2data1</td><td class="uncoolData">row2data2</td><td>row2data3</td><td>row2data4</td></tr></table></body></html>'

```

```{r html2-hint-1, eval=FALSE}
minimal_html(...)
```

```{r html2-hint-2, eval=FALSE}
minimal_html(raw_html)
```


###

`rvest` reads html data and constructs a nested list-like object to represent the usual nested structure of html.

### Exercise 3

Copy/paste your code above and extend the pipe with `%>%`. You can view the pure text of an html object with `html_text()`.

```{r html3, exercise=TRUE}

```

```{r html3-hint-1, eval=FALSE}
... %>% html_text()
```

###

You can see that the output is a mess. This is because html_text() simply took the inner text of all tags and strung them together. That results in a messy string, which is why you want to select specific parts of data.

### Exercise 4

Copy/paste your code above and remove `html_text()`. Instead, select the paragraph tag `<p>` using `html_element()`. Then use `html_text()` to view the text inside the tag.

```{r html4, exercise=TRUE}

```

```{r html4-hint-1, eval=FALSE}
minimal_html(...) %>% html_element("p") %>% ...
```

```{r html4-hint-2, eval=FALSE}
minimal_html(...) %>% html_element("p") %>% html_text()
```

###

You should see just "This is a paragraph." printed out. By selecting specific elements, you can find and extract what you need from html pages.

### Exercise 5

Usually, however, there are more than one of the same tag.

###

Copy/paste your code from above and replace the `"p"` in `html_element()` with `"td"`.

```{r html5, exercise=TRUE}

```

```{r html5-hint-1, eval=FALSE}
... %>% html_element("td") %>% ...
```

###

There are 8 total table data tags `<td>`. However, `html_element()` only selected the first `<td>`.

### Exercise 6

There are a few ways to navigate the structure to find the specific element you want.

###

`raw_html` is provided below.

Start a new pipe with the same `minimal_html(raw_html)`. Use the function `html_element()` to find the table tag `<table>`.

```{r html6, exercise=TRUE}
raw_html <- '<html><head><title>Hello World!</title></head><body><p id="p1">This is a paragraph.</p><br><a id="someKindOfLink">This is an anchor, or hyperlink.</a><br>Below is a table:<table><tr><td class="coolData">row1data1</td><td class="coolData">row1data2</td><td class="uncoolData">row1data3</td><td>row1data4</td></tr><tr><td>row2data1</td><td class="uncoolData">row2data2</td><td>row2data3</td><td>row2data4</td></tr></table></body></html>'

```

```{r html6-hint-1, eval=FALSE}
minimal_html(raw_html) %>% html_element(...)
```

```{r html6-hint-2, eval=FALSE}
minimal_html(raw_html) %>% html_element("table")
```

###

Note to self: next part uses parent and children to navigate table structure and explore tree structure of html.





<!-- This should be a 60 to 90 minutes worth of exercises devoted to webscraping, with a big focus on the rvest package. Also need to teach some CSS and Selector Gadget. Resources: -->

<!-- If students would just read this paper closely and try out the associated commands -->

<!-- https://github.com/mdogucu/web-scrape -->

<!-- then a tutorial would not be necessary. But they won't! And, even if most of them would, teachers still need a way of knowing that they did. Hence, tutorials. Can we write something that, in essence, forces students to type out everything in that article and understand what it is doing? That is the goal! -->

<!-- https://github.com/rstudio-education/dsbox/tree/master/inst/tutorials/05-moneyinpolitics -->
<!-- https://minecr.shinyapps.io/dsbox-05-moneyinpolitics/ -->


<!-- There is no need to reinvest the wheel. All this code is CC0, so we can just copy/paste it, including the links to images which appear on the web. But how do we ensure that students do things? What questions do we ask? -->

<!-- https://rvest.tidyverse.org/ -->
<!-- https://github.com/tidyverse/rvest/blob/master/vignettes/rvest.Rmd -->
<!-- https://github.com/tidyverse/rvest/blob/master/vignettes/articles/selectorgadget.Rmd -->

<!-- Maybe the tutorial starts the same way as this chapter, with a concrete example of what we are trying to do. Note that we just used this prose in our chapter. Again, it is all CC0. -->

<!-- https://rafalab.github.io/dsbook/web-scraping.html -->

<!-- Reminders: -->

<!-- 1) You can put a raw html (or any other kind of file) in inst/www and then be certain is available on Github. You may want to submit a PR which does that, and then, when I accept it, you can write code which accesses it directly. Example url: -->

<!-- https://raw.githubusercontent.com/PPBDS/primer.tutorials/master/inst/www/delim_1.txt -->

<!-- 2) This tutorial is just about raw webscraping, not about working with APIs or JSON. Other tutorials handle that. -->

<!-- 3) Key structure is to, first, begin with sections which highlights the key issues and key commands. Then, have 5 or so concrete examples, each of which works with an html file which we have a permanent copy of. (But how do we show how that file looks in a browser? I am confused about that.) Nothing wrong with all the examples being from Wikipedia and referencing specific versions, even if they are old. -->

<!-- 4) Plan is to write this tutorial and then, afterwards, update the Chapter to be consistent with it. -->

<!-- 5) Use html_text2(). Background: https://www.tidyverse.org/blog/2021/03/rvest-1-0-0/ -->


 

## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```
