---
title: "Data Webscraping"
tutorial:
  id: "data-webscraping"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Chapter 3: Data -- Webscraping"
---

```{r setup, include = FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
library(rvest)
library(png)
library(grid)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 
```


## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```

## Basic HTML
###

HTML, or "HyperText Markup Language" is a markup language that is used to display webpages on browsers. You might have seen html files as a result of knitting Rmd files.

###

### Exercise 1

In this tutorial, you will use the `rvest` package to read the HTML of websites and extract data. First, import the `rvest` package.

You may need to install the `rvest` package in RStudio's console if the code box below outputs an error. If so, use `install.packages("rvest")` in console.

```{r html1, exercise=TRUE}

```

``` {r html1-hint-1, eval=FALSE}
library(...)
```

###

`rvest` is part of the `tidyverse` package. https://rvest.tidyverse.org/ is the documentation.

### Exercise 2
###


<!-- This should be a 60 to 90 minutes worth of exercises devoted to webscraping, with a big focus on the rvest package. Also need to teach some CSS and Selector Gadget. Resources: -->

<!-- If students would just read this paper closely and try out the associated commands -->

<!-- https://github.com/mdogucu/web-scrape -->

<!-- then a tutorial would not be necessary. But they won't! And, even if most of them would, teachers still need a way of knowing that they did. Hence, tutorials. Can we write something that, in essence, forces students to type out everything in that article and understand what it is doing? That is the goal! -->

<!-- https://github.com/rstudio-education/dsbox/tree/master/inst/tutorials/05-moneyinpolitics -->
<!-- https://minecr.shinyapps.io/dsbox-05-moneyinpolitics/ -->


<!-- There is no need to reinvest the wheel. All this code is CC0, so we can just copy/paste it, including the links to images which appear on the web. But how do we ensure that students do things? What questions do we ask? -->

<!-- https://rvest.tidyverse.org/ -->
<!-- https://github.com/tidyverse/rvest/blob/master/vignettes/rvest.Rmd -->
<!-- https://github.com/tidyverse/rvest/blob/master/vignettes/articles/selectorgadget.Rmd -->

<!-- Maybe the tutorial starts the same way as this chapter, with a concrete example of what we are trying to do. Note that we just used this prose in our chapter. Again, it is all CC0. -->

<!-- https://rafalab.github.io/dsbook/web-scraping.html -->

<!-- Reminders: -->

<!-- 1) You can put a raw html (or any other kind of file) in inst/www and then be certain is available on Github. You may want to submit a PR which does that, and then, when I accept it, you can write code which accesses it directly. Example url: -->

<!-- https://raw.githubusercontent.com/PPBDS/primer.tutorials/master/inst/www/delim_1.txt -->

<!-- 2) This tutorial is just about raw webscraping, not about working with APIs or JSON. Other tutorials handle that. -->

<!-- 3) Key structure is to, first, begin with sections which highlights the key issues and key commands. Then, have 5 or so concrete examples, each of which works with an html file which we have a permanent copy of. (But how do we show how that file looks in a browser? I am confused about that.) Nothing wrong with all the examples being from Wikipedia and referencing specific versions, even if they are old. -->

<!-- 4) Plan is to write this tutorial and then, afterwards, update the Chapter to be consistent with it. -->

<!-- 5) Use html_text2(). Background: https://www.tidyverse.org/blog/2021/03/rvest-1-0-0/ -->


 

## Submit

```{r context = "setup"}
submission_ui
```

```{r context = "server"}
submission_server()
```
