---
title: "Shopping Week"
tutorial:
  id: "00-shopping-week"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Complete a simple tutorial during the first class to ensure your computer is set up correctly."
---

```{r setup, include=FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

## Chapter 00 tutorial

Welcome to your first tutorial! The goal of this exercise is to learn how to complete and submit a tutorial. For every chapter, there will be a tutorial for you to complete that puts what you read to practice. Let's now answer some questions about the "Shopping Week" chapter.

## Name 
###

You always begin a tutorial by filling out your name and then clicking the submit button. If you made a mistake, you can click **"Try Again"** and edit your name. 

``` {r name, echo=FALSE}
question_text(
  "Student Name:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```

## Tutorial Exercises 
###

Throughout each tutorial, there will be a set of exercises for you to complete. You will be instructed to interact with code chunks where you write code, then run it. 

### Exercise 1

Let's practice interacting a code chunk with some simple math. We've already assigned variables `x` to 5 and `y` to 4. On the line below, add the two variables by typing `x + y`. Hit **"Run Code"** to see your output results. Clicking "**Hint"** gives you a hint about what to type into the console. Clicking **"Start Over"** clears the console and allows you to begin again.

```{r question-1-1, exercise = TRUE}
x <- 5
y <- 4
```

```{r question-1-1-hint, silent = TRUE}
x + y
```

### Exercise 2

One type of exercise you will encounter is looking at data sets. Let's practice loading our first dataset. We provide the code to load the `primer.data` library -- this is the package our dataset will come from. Type `trains` in the console and hit **"Run Code"**. This will display some observations from the trains dataset. 

```{r question-1-4, exercise = TRUE}
library(primer.data)

```

```{r question-1-4-hint, silent = TRUE}
trains
```

### Exercise 3

Let's check the version of R running on your computer. You can do this by copy-pasting `version[['version.string']]` into your console and then by hitting **"Run Code"**. You will use the output of this line of code to answer the following question. 

```{r question-1-2, exercise = TRUE}

```

```{r question-1-2-hint, silent = TRUE}
version[['version.string']]
```

### Exercise 4

A different type of question you will encounter in tutorials is **multiple choice**. If you get the wrong answer for this question, you haven't installed the most recent version of R and should redo the steps from chapter 00. If you click the wrong answer in general on multiple choice questions, you can hit **"Try Again"** for another attempt. 

```{r question-1-3}
question("What is the R version running on your computer?",
    answer("4.0.3", correct = TRUE),
    answer("4.0.1"),
    answer("4.0.0"),
    answer("3.9.9"),
    allow_retry = TRUE)
```

### Exercise 5

Let's see if you can save your progress on tutorials. Close your tutorial and restart your R session, then open up this tutorial again. Was your progress on the first four questions saved? If not, ask for help. 

## Submit Your Work
###

At the end of every tutorial, you will submit your work. Let's now submit this tutorial. Follow the instructions.


## Submit

```{r context="setup"}
submission_ui
```

```{r context="server"}
submission_server()
```
