---
title: "Shopping Week"
tutorial:
  id: "shopping-week"
output:
  learnr::tutorial:
      progressive: true
      allow_skip: true
runtime: shiny_prerendered
description: "Complete a simple tutorial during the first class to ensure your computer is set up correctly."
---

```{r setup, include=FALSE}
library(learnr)
library(primer.tutorials)
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

## Welcome
###

Welcome to your first tutorial! The goal of this exercise is to learn how to complete and submit a tutorial. For every chapter, there will be one or more tutorials for you to complete and submit via Canvas. 

You always begin a tutorial by filling out your name/email and then clicking the "Submit Answer" button. If you make a mistake, you can click **"Edit Answer"** and try again. 


## Information
###

```{r information}
quiz(caption = "",
  question_text(
    "Name:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL),
  question_text(
    "Email:",
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL))
```


## Tutorial Exercises 
###

Throughout each tutorial, there will be a set of exercises for you to complete. You write your answer within the exercise coding area and hit the "Submit Code" button when you are done.

Clicking **"Start Over"** --- look for small letters at the bottom of the lefthand side menu --- deletes all your work for this tutorial and allows you to begin the entire tutorial again.

### Exercise 1

Let's practice interacting a code chunk with some simple math. We've already assigned variables `x` to 5 and `y` to 4. On the line below those assignments, add the two variables by typing `x + y`. Hit **"Run Code"** to see your output results. Clicking "**Hint"** gives you a hint about what to type. 

```{r ex-1, exercise = TRUE}
x <- 5
y <- 4
```

```{r ex-1-hint, eval = FALSE}
x <- 5
y <- 4
x + y
```

Once you click **"Run Code"** the answer --- [1] 9 --- should appear below the code you entered. This is the same behavior you would see if you ran this same code in the Console.

### Exercise 2

Let's examine our first dataset. We provide the code to load the `primer.data` library -- this is the package our dataset will come from. Type `trains` in the console and hit **"Run Code"**. This will display some observations from the `trains` dataset. 

```{r ex-2, exercise = TRUE}
library(primer.data)
```

```{r ex-2-hint, eval = FALSE}
trains
```

### Exercise 3

Let's check the version of R running on your computer. You can do this by copy-pasting `version[['version.string']]` into your console and then by hitting **"Run Code"**. You will use the output of this line of code to answer a later question. 

```{r ex-3, exercise = TRUE}

```

```{r ex-3-hint, eval = FALSE}
version[['version.string']]
```

### Exercise 4

Let's confirm that your progress on tutorials is automatically saved between sessions. **Close your tutorial and quit RStudio.** Restart RStudio and then run this tutorial again. Was your progress on the first three questions saved? If so, good! If not, ask for help. 

### Exercise 5

Tutorials can include **multiple choice** questions. If you get the wrong answer for this question, you haven't installed the most recent version of R and should redo the steps from the Shopping Week chapter. 

```{r ex-5}
question("What is the R version running on your computer?",
    answer("4.0.3", correct = TRUE),
    answer("4.0.1"),
    answer("4.0.0"),
    answer("3.9.9"),
    allow_retry = TRUE)
```

### Exercise 6

Tutorials can include written responses. You have already seen one example of that when you provided your name and e-mail address at the start.

Copy 

```{r ex-6}
question_text(NULL,
    answer(NULL, correct = TRUE),
    allow_retry = TRUE,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    options = list(nrows = 6))
```



## Submit Your Work
###

At the end of every tutorial, you will submit your work. Let's now submit this tutorial. Follow the instructions. After hitting the "Download" button, you will be prompted to save a file named `shopping-week_answer.rds`. Future tutorials will prompt with different file names, to match the tutorial. The suffix will always be `.rds`, indicating that the file was created by R.


## Submit

```{r context="setup"}
submission_ui
```

```{r context="server"}
submission_server()
```
